### 2014-09-17 ms.tex
Brian revisions

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
% \usepackage{natbib}

% \renewcommand{\l}{\left}
% \renewcommand{\r}{\right}

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}
\newcommand{\rs}{r_s}
\newcommand{\rb}{r_b}
\newcommand{\rcirc}{r_{\rm circ}}
\newcommand{\rss}{r_{\rm ss}}
\newcommand{\lrs}{\l_{\rs}}
\newcommand{\lambdars}{\lambda_{\rs}}
\newcommand{\vw}{v_w}

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}

\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}

\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}

\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\pc}{\rm pc}

\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\Mbheight}{M_{\bullet,8}}
\newcommand{\MbheightExp}{\frac{\Mbh}{10^8 \Msun}}

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\ff}{\rm ff}
\newcommand{\tff}{t_{\ff}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\EIa}{E_{\rm Ia}}
\newcommand{\RateIa}{R_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\vwOFH}{v_{w,0,500}}
\newcommand{\vwOFHexp}{\frac{\vwO}{500 \, {\rm km/s}}}

\newcommand{\pyear}{{\rm yr}^{-1}}
\newcommand{\tage}{t_{\star}}
\renewcommand{\th}{t_h}

\topmargin -1 cm
\defcitealias{WangMerritt:2004a}{WM04}

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

\begin{document}
\title{Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

\begin{abstract}
We calculate the steady-state hydrodynamic profiles of hot gas in the nuclei of a sample of early-type quiescent galaxies from the Nuker database.  We assume that mass is supplied to the circumnuclear medium (CNM) entirely by stellar winds according to the radial stellar profiles for each galaxy, while the gas is heated by a combination of shocked stellar winds and supernovae.    
Our analytic and numerical results are used to estimate the accretion rates onto the central supermassive black holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the heating efficiency, the latter of which is related schematically to the age of the stellar population, the frequency of supernovae, and the efficacy of accretion feedback processes.  For a fixed heating efficiency, we find that the SMBH accretion Eddington factor increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for core and cusp nuclei, respectively.  However, considering the potentially lower heating efficiency of low mass SMBHs (due to a younger stellar population and the rareity of supernovae within the stagnation radius) and their resulting higher susceptibility to cooling instability, we find a flatter relationship $\alpha \approx 0$.  Our results are used to check previous estimates of the SMBH accretion rate assuming Bondi accretion and extrapolating the X-ray measured density and temperature to the unresolved Bondi radius.  We also discuss the implications of our results for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies.  
\end{abstract}

\begin{keywords}
  black hole physics --  galaxies: active
\end{keywords}

\section{Introduction}
\label{sec:introduction}

%% Maybe active galaxies constitute 10% need reference here?
Supermassive black holes (SMBHs) lurk in the centers of most, if not all nearby galaxies (see reviews by,
e.g. \citealt{KormendyRichstone:1995a}; \citealt{FerrareseFord:2005a}). However, only a few percent of these manifest
themselves as luminous Active Galactic Nuclei (AGN).  Nearly quiescent SMBHs, such as those hosting low luminosity AGN, constitute a silent majority (e.g.~\citealt{Ho:2009a}).

In order to understand why most SMBHs appear to be inactive, it is necessary to understand their gaseous environments.  Hot gas near the SMBH sphere of influence (the `circumnuclear medium' or CNM) controls the central mass accretion rate $\dot{M}$.  Better knowledge of how $\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the galactic nucleus is necessary to understand the co-evolution of SMBHs and their host galaxies with cosmic time.  SMBH growth in the low redshift universe, for instance, appears to be dominated by low mass black holes (e.g.~\citealt{Heckman+04}).  Although this is often attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}), the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.

The accretion rates of low mass SMBHs and their resulting nuclear X-ray luminosities $L_X$ also have implications for observational constraints on their occupation fraction in low mass galaxies and the possible existence of intermediate mass black holes.  \citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and $L_X$ from a sample of relatively high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass galaxies, to infer tentative evidence for an occupation fraction less than unity.  However, this method relies on extrapolating a power-law fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the instrumental detection threshold.  The conclusions of \citet{MillerGallo+:2014a} are thus sensitive to possible changes in the $L_X$-$\Mbh$ relationship at small $\Mbh$.
% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold

The density profile of the CNM also influences the emission from stellar tidal disruption events (TDEs), such as the high energy transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).  This event was powered by an transient relativistic jet, which produced synchrotron radio emission as the jet material was decelerated by shock interaction with the CNM of the previously quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed modeling of {\it Swift} J1644+57 showed that the CNM density was significantly lower than that measured surrounding Sgr A$^{\star}$ (\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet injected into a denser CNM would be decelerated more rapidly, producing substantially different radio emission than in {\it Swift} J1644+57.  Variations in the properties of the CNM could thus in principle help explain why most TDEs appear to be radio quiet (e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).

Gas that forms the CNM of a SMBH may originate from several sources (\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved) stars; (2) star-star collisions; (3) the unbound debris from TDEs.  Stellar wind mass loss is probably the dominant source in most cases insofar as collisions are relevant only in very dense stellar environments for young stellar populations (\citealt{Rubin&Loeb11}), while TDEs are estimated to provide a subdominant contribution to the time-averaged accretion rate of quiescent SMBHs (\citealt{MacLeod+13}).

\citet{Ho:2009a} calculates the accretion rates onto a sample of early-type galaxies both by using X-ray observations to determine the Bondi accretion rate, and by estimating the contributions from the mass loss of evolved stars.  Both methods lead him to conclude that the available reservoir of gas is more than sufficient to power low-luminosity AGN, assuming the standard radiative efficiency $\eta \sim 0.1$ for thin disk accretion.  Indeed, there is now strong observational evidence that the low levels of AGN activity in quiescent galaxies results from accretion proceeding in a radiatively inefficient mode (\citealt{Yuan&Narayan14}), either due to the gravitationally-released energy being advected across the SMBH horizon (e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas inflowing on large scales ultimately reaching the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).

The accretion rates of SMBHs can in principle be estimated directly by assuming Bondi accretion and using {\it Chandra} X-ray observations to estimate the gas temperature and density near the Bondi radius.  This technique has led to the intriguing result that the Bondi accretion power correlates with the AGN jet power (e.g., \citealt{AllenDunn+:2006a}; \citealt{Russell+13}; \citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy required to inflate the observed cavities within the X-ray emitting gas.  It is, however, almost never possible to resolve the Bondi radius, thus requiring all such studies to extrapolate the observed gas temperature and density profiles to much smaller radial scales.  
%In fact, the temperature profile is assumed to be flat inside of the
%Bondi radius.  In reality, the cusp in the velocity dispersion near
%the SMBH, should cause a cusp in the gas temperature profile (assuming
%the kinetic energy of stellar winds is efficiently thermalized in
%shocks).
%% AG-give sense of scale.

Another approach to determine the SMBH accretion rate, which we adopt in this paper, is to directly calculate the density, velocity and temperature profiles of the CNM using a physically motivated hydrodynamic model.  Mass is injected to the nuclear environment via stellar winds, while energy input results from a number of sources, such as wind shock heating and supernovae (e.g., \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).  Unlike previous works, however, which focus on modeling the nuclei of individual galaxies, here we systematically analyze the properties of the CNM across a large sample of quiescent galaxies with a range of SMBH masses and other properties (\citealt{WangMerritt:2004a}; hereafter WM04).  For each galaxy, stellar winds deposit mass and energy across a range of radii calculated directly from the observed {\it stellar} density profile.

The one-dimensional steady state flow of gas is usually characterized by an inflow-outflow structure, with a critical radius known as the ``stagnation radius" $\rs$ where the radial velocity goes to zero.  Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.  The stagnation radius, rather than the Bondi radius, is thus ultimately responsible for setting the SMBH accretion rate.  Although we find that $\rs$ typically lies within a factor of few of the nominal Bondi radius, the difference in the accretion rate can be significant.  Furthermore, in some cases we find that no stagnation radius exists at all; this formally implies that the entire of ISM of the galaxy is feeding the SMBH, potentially resulting in much higher accretion rate than would be predicted by simple Bondi accretion.  The main goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the relatively well understood physics of stellar winds and supernova heating.

This paper is organized as followed.  In $\S\ref{sec:model}$ we describe our model, including the sample of galaxies used in our analysis ($\S\ref{sec:sample}$) and our numerical procedure for calculating the steady-state hydrodynamic profile of the CNM ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our results.  In $\S\ref{sec:applications}$ we describe applicaiton of our results, including a comparison of our gas profiles to those inferred from {\it Chandra} observations and to the measured $L_X-\Mbh$ relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In $\S\ref{sec:summary}$ we summarize our results.

\section{Model}
\label{sec:model}

\subsection{Galaxy Sample}

\label{sec:sample}

Our sample includes 61 early-type galaxies from \citetalias{WangMerritt:2004a}, as represent a subset of a larger sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We focus on elliptical galaxies because we are interested in isolating SMBHs fed by the steady mass loss from the relatively old stellar population, instead of fresh gas flowing into the sphere of influence from larger scales.

The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
\begin{equation}
  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
\end{equation}
The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

Given $I(\xi)$ we follow the procedure outlined by \citetalias{WangMerritt:2004a} to compute the spherically-symmetric stellar density profile $\rhostar(r)$ and stellar mass profile $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in our model.  For reference, note that stellar density $\rhostar\sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r \gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the SMBH mass $\Mbh$ is determined from.... ({\bf BDM: more info!}).

% AG:Is there a systematic dependence of beta on galaxy type$.

%% AG--some discussion of alternate parameterizations.  My intuition
%% is that for our purposes the parameterization should not
%% matter. But some discussion of alternate possibilities could
%% prevent Alistar Graham from yelling at us.

\subsection{Hydrodynamic Equations}
\label{sec:hydro}

Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the gas density profile $\rho$ of the CNM for each galaxy within our sample by solving the equations of one-dimensional (spherically symmetric) time-dependent hydrodynamics,
\begin{align}
  &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr-\rho \dphidr-q v \label{eq:dvdt}\\
  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] + \nabla\cdot(\kappa \nabla T), \label{eq:dsdt}
\end{align}
where $v$, $T$, $p$ and $s$ are the radial velocity, temperature, pressure and entropy of the gas, respectively.  Here $\partial \Phi/\partial r = GM_{\rm enc}/r^{2}$ is the gravitational acceleration, where $M_{\rm enc} = M_{\star}(r) + M_{\bullet}$ is the enclosed mass.  We assume an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$ {\bf BDM: correct?} and $\gamma = 4/3$.

The source term in the continuity equation (eq.~[\ref{eq:drhodt}]),
\begin{align}
  q=\frac{\eta \rhostar}{\th},
\label{eq:q}
\end{align}
represents mass input from stellar winds, which we parameterize in terms of the fraction $\eta$ of the stellar density $\rhostar$ being recycled into gas on the Hubble time $\th = 10^{10}$ years (see, e.g., \citealt{Ciotti+91}).  In Appendix \ref{app:eta} we estimate that $\eta \approx 0.11(t_{\star}/t_{\rm h})^{-1.26}$ for a Salpeter IMF, assuming that all stars are formed in a burst of star formation at a common age of $t_{\star}$ (eq.~[\ref{eq:eta}]).  We adopt $\eta=1$ as fiducial, but note that changing $\eta$ is equivalent to rescaling $\rho$ by the same factor.\footnote{This is {\it not} true once cooling is included, since the cooling rate is proportional to density {\it squared}.}

Source terms $\propto q$ also appear in the momentum and entropy equations (eq.~[\ref{eq:dvdt}], [\ref{eq:dsdt}]) due to the fact that the isotropic mass injection in the rest frame of the SMBH represents a source of momentum and energy upon being incorporated into the mean flow (see also below).  The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).

Following \citet{ShcherbakovWong+:2014a}, the term in the entropy equation $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ accounts for external heating sources.  Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the velocity dispersion of the stars, thus accounting for the fact that at a minimum the gas experiences shock heating between the stellar winds of velocities moving with respect to each other a characteristic velocity $\sim \sigma$, i.e. even if the wind velocities themselves are low, $\ll \sigma$, as characterize the majority of AGB mass loss.  The term $v_{w,0}^{2}$ parameterizes additional sources of heating, such as main sequence winds, millisecond pulsars, supernovae, etc.  As discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in general depend on the SMBH mass and the age of the stellar population.

Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) are solved for each galaxy using a standard Runge-Kutta integration for different assumed values of $v_{\rm w,0}$ spanning the physically expected range.  Although we are most interested in the steady-state CNM structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.

We do not include radiative cooling in the entropy equation because across much of the parameter space radiative cooling is negligible compared to other sources of cooling (e.g., advection).  Radiative cooling cannot be neglected in some cases (especially if $\eta$ is high), but the onset of a thermal instability when radiative cooling dominates precludes obtaining a steady-state solution anyways.  Our steady state solutions neglecting radiation can nevertheless be used to ascertain over what parameter space cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).

The accuracy of our numerical solutions is assessed by checking the level of conservation of mass across the grid, as well as the integral constraint on the Bernoulli parameter.  Mass and Bernoulli are conserved to $\lesssim 10$ per cent for all solutions presented in this paper.  {\bf BDM: more details...}

\section{Results}

We begin by describing a number of useful analytic results before describing our numerical solutions.

\label{sec:results}
\subsection{Analytics: Flow properties at $\rs$}

This section provides analytic estimates for several quantities of interest, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.  All of our results are derived under the assumption that thermal conductivity can be neglected.

When possible our results are expressed in terms of the wind heating parameter $v_{\rm w,0}$; the power-law slope of the density profile $n$ (also evaluated at $r = \rs$); and the dimensionless parameter
\be
\chi \equiv \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx \left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right),
\ee
where $v_{500} \equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the $M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09})
\be
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{5.1}M_{\odot}.
\label{eq:Msigma}
\ee
Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.

First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by (eq.~[\ref{eq:Tanalytic}])
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 4 \times 10^6\,v_{500}^2 \, \chi   \,\,{\rm K} 
\end{align}
{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived (eq.~[\ref{eq:rstag}]),
\begin{align}
  \x=\frac{1}{\zeta^2 n}\left[ (1+\Mstar(\rs)/\Mbh)\left(A-\frac{n}{2}\right)-B\right],
  \label{eq:stag_analytic}
\end{align}
where $\zeta \equiv v_{w,0}/\sigma$ {\bf BDM: note new definition}, $r_{\rm soi} = GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of influence (soi), and A/B are constants that depend on the Nuker parameter $\Gamma$ and the adiabatic index of the gas.

If the SMBH dominates the potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg 200 M_{\bullet,8}^{0.2}$ km s$^{-1}$) then the relationship between $\rs$ and $v_{w}$ is simplified greatly:
\begin{align}
  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \simeq 6 \, \pc \,\, \Mbheight v_{500}^{-2},
  \label{eq:stag_simple}
\end{align}
where we have assumed $n = 1$ {\bf BDM: true?  should there be a $\chi$ in this?}.  Note that this expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their eq.~[6]).

The SMBH accretion rate is simply given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.6 \times 10^{-3}  M_{\bullet,8}^{1.9}
    v_{500}^{-4} \chi^{-2} \eta \Msun \, \pyear& \text{core} \\
    3.4 \times 10^{-3} \Mbheight^{1.4}
    v_{500}^{-2} \chi^{-1} \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where the numerical estimates again assume that $M_{\bullet} \gg M_{\star}$ at the stagnation radius.  Note that equation (\ref{eq:mdot_analytic}) predicts that $\dot{M}$ should increase with BH mass at fixed $v_{500}$ but that $\dot{M}$ is extremely sensitive to the assumed heating rate $\propto v_{500}$.

Finally, the density at the stagnation radius $\rho(r_{\rm s})$ can be estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}(\rs)},
  \label{eq:mdot_gas}
\end{align}
from which one derives 
\begin{align}
  \rho(\rs)\simeq
  \begin{cases}
    3 \times 10^{-24} \Mbheight^{-0.14} v_{500}^{-1} \chi^{-1/2} \eta \,
    \, {\rm g \, cm^{-3}}& \text{core}\\
    6 \times 10^{-24}  \Mbheight^{-0.56} v_{500}  \chi^{1/2}  \eta \,\, {\rm g \,cm^{-3}} & \text{cusp}
  \end{cases}
  \label{eq:rhors}
\end{align}

\subsection{Comparison with Bondi Accretion}
The spherical accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and density is given by (\citealt{Bondi52}) 
\begin{align}
  \dot{M}_{\rm B} =4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b),
\label{eq:bondi}
\end{align}
where $r_b \equiv GM/c_{s}^{2}$ is the ``Bondi radius", $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.

Rewriting equation (\ref{eq:mdot_gas}) as
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
\end{align}
we note the qualitative similarity between this expression and the Bondi formula (eq.~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
\begin{align}
  \rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}}\frac{v_{w}^{2}}{v_{w,0}^{2}},
  \label{eq:rs_simple}
\end{align}
where in the second line we have used the fact that $v_{w}^{2}/2 = c_s^2/(\gamma-1)$ at $\rs$ ({\bf BDM: Check - as this depends on whether eq 10 is correct}).  Thus, provided that a stagnation radius exists which is interior to the sphere of influence radius, the accretion rate predicted by our model is quite close to $\dot{M}_{\rm B}$.

%% AG-Apparently even in the low heating case, it is still possible to
%% an outflow (from the analytic results above the gas density must be
%% quite steep in this case). However, at low heating we will probably
%% become subject to a cooling instablity.  AG-I believe that in the
%% case of core galaxy, the negative root of the quadratic should be
%% taken...

\subsection{Numerical Solutions}

Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 200, 500, 1000 km s$^{-1}$.

Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $v(r)$, as well as the cumulative X-ray luminosity.  As expected, the gas density increases towards the SMBH, with a characteristic radial slope $\rho \propto r^{n}$ with $n \approx 1$ near the stagnation radius (marked as a square in Fig.~\ref{fig:profiles}; {\bf BDM:check!?}).  On very small scales the gas density profile appropaches the behavior $\rho \propto r^{-3/2}$ predicted for Bondi accretion.  The temperature profile is relatively flat at large radii, but increases as $\propto 1/r$ interior to the sphere of influence, both behaviors expected for virialized gas in near hydrostatic equilibrium.  The inwardly directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii. {\bf BDM: I made this up - in general we need more explanation of what the plots are actually showing, with some physical explanation.}

Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.  Cusp and core galaxies are marked with square and triangles, respectively.  The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}

Our results for $r_{\rm s}/r_{\rm soi}$ can be compared directly to our analytic estimate in equation \ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag} shows the fractional difference between our numerical and analytic results for $r_{\rm s}/r_{\rm soi}$.  The generally good agreement (especially for $v_{w,0}$ = 500, 1000 km s$^{-1}$) provides a useful check of the numerical results.

%% AG: Describe conservation checks to additionally validate the results.

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density ({\it top}), temperature ({\it top}), velocity ({\it ADD}), and interior X-ray luminosity ({\it bottom}), calculated for three characteristic galaxies from our samples: NGC1172 ({\it blue}), NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line styles denote different values of the effective wind heating rate, $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it dot-dashed}).   {\bf BDM: add velocity profiles...xray luminosity can probably go elsewhere}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a function of the ratio of the effective wind heating rate $v_{w,0}$ to the stellar velocity dispersion $\sigma$.  Green, orange, and blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$, respectively.  Squares correspond to cusp galaxies, while triangles correspond to cores. \emph{Bottom panel}: Fractional difference between our numerical calculation of $r_{\rm s}/r_{\rm soi}$ and the analytic result in equation~(\ref{eq:stag_analytic}). }
\end{figure}

\section{Applications}
\label{sec:applications}
\subsection{Sources of Heating}
\label{sec:heating}

Our results show that the location of the stagnation rate and resulting accretion rate, is very sensitive to the assumed heating rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating rate will vary from galaxy to galaxy.. For example, SNe Ia represent a potentialy important source of heating, but since they are rare they will only be relevant in a time-averaged sense if the supernova rate exceeds the inflow time of the gas near the stagnation point.

In this section we discuss potential sources of heating and provide estimates of the value of $\vwO$ corresponding to each.  Before proceeding, note that $\vwO$ is related to the heating rate per volume $e$ according to 
\begin{align}
  &\frac{q \vwO^2}{2}=e \,\,\,\Rightarrow\,\,\,\vwO = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
  \label{eq:vw_eff}
\end{align}

subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.

Though representing a much smaller quantity of mass, main sequence winds have much higher velocities and hence contribute a disproportionally large share of the kinetic energy of winds.  \citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.  On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.  In Appendix C we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age.

\subsubsection{Millisecond Pulsars} The spin down power of millisecond pulsars (MSPs) could in principle be an important heating source.  If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $L_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm msp}\epsilon$ corresponds to an effective heating rate (eq.~ [\ref{eq:vw_eff}])
  \begin{align}
    \vwO=\sqrt{\frac{2 t_h n_{\rm msp} L_{\rm sd}}{\eta}},
  \end{align}
where $\eta < 1$ is the thermalization efficiency of the wind.  The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$.  If we assume an average spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of Fermi pulsars, then we find that $\vwO\simeq 120\epsilon (\eta/0.1)^{-1/2}$ km s$^{-1}$.  Thus, assuming a high thermalization efficiency $\epsilon \sim 1$, MSP heating can be comparable to main sequence heating.  However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}, while the binaries giving rise to through accretion MSPs may be disocciated by stellar interactions in the dense nuclear cluster.  
\subsubsection{Type Ia Supernovae}

Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.  Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the instellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}])
\begin{align}
    \vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
\end{align}
The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq \epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$ with which the blast wave energy is converted into bulk or turbulent motion instead of being lost to radiation.  \cite{Thornton+98} estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$, depending weakly on surrounding density, but \citet{Sharma+14} argues that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if the SNe occur in a hot dilute medium, as may characterize the CNM.

The Ia SN rate $\RateIa$ depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.  In the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally inferred DTD (see Fig. 1 of \citet{MaozMannucci+:2012a} has the approximate functional form
\begin{align}
    \Psi(\tau)=\frac{0.03
      \left(\tau/10^8\,{\rm yr}\right)^{-1.12}}{10^{10} \Msun},
  \end{align}
where $\tau$ is the time of the Ia SN since star formation.

In the limit of an old stellar population of age $t_{\star} \sim t_{\rm h}$ the Ia rate just becomes $R_{\rm Ia} \sim 2\times 10^{-55} $ g$^{-1}$ s$^{-1}$ (e.g.~\citealt{Scannapieco&Bildsten05}).  Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$ also depends on the stellar age (eq.~[\ref{eq:eta}]).  Thus, from equation (\ref{eq:vw_eff}) we estimate $v_{w,0} \approx 350\epsilon_{\rm Ia}^{0.5}(\eta/0.1)^{-0.5}$ for an old stellar population.  For a younger stellar population the increasing rate of Ia SN is compensated by the larger stellar mass loss rate, resulting in a value of $v_{w,0}$ that is roughly independent of stellar age.  The high value of $v_{w,0}$ implies that Ia SNe represent a potentially dominant source of heating as compared to ms pulsars or main sequence winds.

However, SNe can only be approximated as constant source of heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).  To estimate when this approximation is valid, we estimate the ``Ia radius" 
\begin{eqnarray}
r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx 40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc} \sim 43 M_{\bullet,8}^{0.1}\,{\rm pc}
\label{eq:rIa}
\end{eqnarray}
as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship (eq.~[\ref{eq:Msigma}]).

Note that the stagnation radius scales approximately linearly with $M_{\bullet}$ (eq.~[\ref{eq:stag_simple}]), while $\rIa$ is roughly indpendent of SMBH mass.  For small $\Mbh$, the stagnation radius thus lies well inside $\rIa$ and hence Ia SNe will not contribute appreciably to the heating rate.  On the other hand, for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia  represent an important, and possibly dominant, contribution to the overall heating.
  % Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with
  % heating mostly coming from main sequence winds. On the other hand,
  % for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with
  % the main contribution coming from type Ia SNe. These two regimes are
  % illustrated in Figure~\ref{fig:vw_eff}.
  % \end{enumerate}

\subsubsection{AGN Heating}

AGN feedback also represents an additional source of heating.  In this case, since the rate of feedback is likely proportional to the mass accretion rate $\dot{M}$, which itself is inversely proportional to the heating rate (eq.~[\ref{eq:mdot_analytic}]), then, if dominant, the effective heating rate from AGN $v_{\rm w,0}$ may be regulated to a fixed value.

\subsubsection{Combined Heating Rate} The overall heating rate $\vwO$ has contributions from Type Ia SNes and main sequence winds.  The relative contributions will depend on both the age of the stellar population, $\tage$, and $\Mbh$.  This is illustrated in Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe
  Ia will not contribute to $\vwO$ as the flow time scale is short
  compared to $t_{\rm Ia}$, and the heating is dominated by main
  sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for
  $\Mbh \gsim 10^8 \Msun$, heating from Ias becomes important, as
  $\rs>\rIa$. In this regime, we add the $\vwO$ values from SNe Ias
  and from main sequence winds in quadrature. $\vwO$ from SNe Ia's
  depends on the rate of mass loss ($\eta$), which is in turn a
  function of $t_{\star}$. This dependence is why the effective
  $\vwO$ increases with $\tage$ for large $\Mbh$.

  For very young stellar populations ($\tage \lsim 10^7$ years),
  $\vwO\simeq 1000$ km/s due to contributions from line driven winds
  from high mass main sequence stars.

  \begin{figure}
    \includegraphics[width=\columnwidth]{vw-contour.eps}
    \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM in the parameter space of SMBH mass $\Mbh$ and age of the stellar population $t_{\star}$.  We assume that stellar winds contribute a constant heating rate $100$ km/s. The contribution from SNe Ia is calculated using equation (\ref{eq:vw_sne}). The contribution from SNe Ia is only added if the $r_s$ corresponding to the resulting $\vwO$ is outside $\rIa$.}%describe other cases here.
  \end{figure}

  % AG-I am not comfortable saying type Ia SNe's don't contribute to
  % heating for smaller mass BHs. If the cooling time for the SNe is
  % long then it would be wrong to ignore the SNe contribution. The
  % difference would be that the SNe heating would just be less steady.
  % AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...

\subsection{Mass accretion rate}

For each solution we calculate the accretion rate $\dot{M}$ onto the SMBH  in units of the Eddington accretion rate $\dot{M}_{\rm edd} \equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times 10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different values of $\vwO =$ 200, 500 and 1000 km s$^{-1}$.

Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy (eq.~[\ref{eq:mdot_analytic}]), the mass accretion rate is expected to be a sensitive function of the assumed heating rate.  However,  the accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.  This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For $\vwO=1000$ km s$^{-1}$, core galaxies have a smaller accretion rate for a given SMBH mass.
%% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
%% AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.

We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase increase with SMBH mass $M_{\bullet}$.  This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the fact that for quiescent galaxies the nuclear X-ray luminosity obeys $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot \sim
\Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x \sim \Mbh^{1.5-2}$, steeper than the observed relationship. (If $L_x \sim \Mdot^2$ the discrepance becomes worse).  One possible solution that the wind mass loss rate $\eta$ decreases with $\Mbh$, as would be expected if low mass SMBH preferentially hosted younger stellar populations.  Another possible explanation, which we favor, is that the effective heating rate of the CNM $v_{\rm w,0}$ decreases with decreasing SMBH mass.  This could again be due to a young stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating sources such as SN Ia and millisecond pulsars, or it could be due to the fact that Ia occur too infrequently inside the stagnation radius for low mass black holes.

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass}  Accretion rate $\dot{M}$ in units of the Eddington rate $\dot{M}_{\rm edd}$ as a function of SMBH mass for each galaxy in our sample, calculated for different values of the wind heating parameter $\vwO =$ 200 km s$^{-1}$ ({\it green}), 500 km s$^{-1}$ ({\it orange}), and 1000 km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies, while triangles correspond to cores.}
\end{figure}

%% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).

\subsection{Comparison to Observations}
\subsubsection{Comparison to measured temperature and density profiles}
\citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.  \citet{RussellMcNamara+:2013a} performed a similar analysis with a somewhat enlarged galaxy sample.  Interestingly, these works find a correlation between the accretion rate inferred assuming Bondi accretion and the AGN jet power, which is estimated by the PdV work required to inflate observed cavities in the X-ray emitting gas.  
% At some point it would be useful to describe the differences between
% these two sets of observations \citealt{RussellMcNamara+:2013a}
% tries several different extrapolation schemes for the gas density,
% and finds that that the uncertainty in extrapolating the density
% profile is the dominant source of uncertainty in measuring the
% accretion rate. Find total number which overlaps once the Russell
% galaxies are included...

Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.  We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.  The results of this exercise are presented in Figure~\ref{fig:allen_compare}.

Note that we have two free parameters ($\eta$ and $\vwO$) in our model, which implies that we can always match the observed temperature and densities at at least one point.  As a general rule, we find that a wind heating parameter $\vwO=500$
km s$^{-1}$ (close to, but somewhat higher than that expected from SNe Ia) gives rough agreement with the observed temperatures.  We now highlight results for specific galaxies.
% Thus, we choose $\vwO=500$ km/s.  We choose an
% $\eta$ so that our solution would be consistent with the observed
% density profiles. The comparison is shown in
%% AG-The chosen properties, in particular eta may be summarized in a table.
%% AG-Mention rising temperature profiles on large scales.

\begin{itemize}
% \item \emph{NGC4486} %eta=0.2
%   On scales of $\sim1$ kpc the density profile in
%   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
%   has a break in the gas density at $\sim 300$ pc--near the location
%   of the Nuker break radius for this galaxy at 560 pc. There is an
%   observed break in the density, but on a scale of a few kpc.

%   The temperature is assumed to be flat from the resolution limit
%   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
%   increases monotonically towards the galactic center. This increase
%   is due to the increased velocity dispersion (and thus increased
%   heating) towards the galactic center.

\item \emph{NGC5813} %eta=0.1
  The observed density profile (\citealt{RussellMcNamara+:2013a}) is
  shallower than our calculated density profile, which has a sharp
  break at $\sim$0.1 kpc, the location of the break radius in the
  Nuker profile (this is the radius where the stellar light profile
  transitions from a shallower inner power law slope to a steeper
  outer power law slope).

  For this galaxy we found that we could reproduce the observed
  temperature on large scales with $\vwO=500$ km/s. The increased
  velocity disperision towards the galactic center results in a sharp
  increase in $T$ at small radii, which is not captured in the
  observations due to resolution issues.
\end{itemize}

%It would be nice to have error bars for the observational points in this plot...
\begin{figure*}
  \includegraphics[width=\columnwidth]{NGC5813_T.eps}
  \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
  \caption{\label{fig:allen_compare} Comparison of the radial profiles of electron number density $n_e$ and temperature $T$ to
    the measured radial profiles provided in \citet{AllenDunn+:2006a} and \citet{ RussellMcNamara+:2013a}}.
  %% AG in the future we will have to be carfeful of the mean molecular weight.
\end{figure*}

\section{Discussion}
\label{sec:discussion}

\subsection{Cooling}
\label{sec:cooling}
Our models neglect radiative cooling, an assumption we now check.  At high temperatures  $T\gsim
2\times 10^7$ K gas cools through free-free emission, while at lower temperatures it cools predominantly through metal lines.  
To assess the importance of radiative cooling in our solutions we compare the heating rate $H=q
\vw^2/2$ to the nominal cooling rate
\begin{align}
  c =\Lambda(T) n^2,
\label{eq:cooling}
\end{align}
where $n = \rho/\mu m_p$ and we approximate the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (Fig. 34.1 in \cite{Draine:2011a}).   Note that because heating is proportional to density, while cooling is proportional to density squared, this implies that the ratio $H/C$ depends on the rate of stellar wind mass loss $\eta$, which we assume to be $\eta = 1$ below.

Figure~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.  For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.  With a few exceptions this is also true for $\vwO$=500 km s$^{-1}$.  However, for our lowest heating rate $\vwO$=200 km s$^{-1}$ cooling may be quite important, especially for high $\eta$ (young stellar population;  Appendix~\ref{app:eta}).

For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.  Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.  If cooling is important, the CNM is likely to be thermally unstable, resulting in the formation of a cold medium that could substantially enhance the rate of accretion onto the SMBH.

%\begin{align}
 % \Lambda(T)\simeq
  %\begin{cases}
   % 2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
   % 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
  %\end{cases}
  %\label{eq:cooling}
%\end{align}

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate ($C$) for each of our solutions. The cooling rate is calculated using the approximate (solar metallicity) cooling function in Equation~(\ref{eq:cooling}). The heating rate is estimated as $q \vw^2/2$. The ratio is computed from equation (\ref{eq:cooling}) assuming a stellar mass loss rate parameter $\eta=1$.}
\end{figure}

\input{figures/eta_tab.tex}

\subsection{Conduction}
\label{sec:conduction}{

  \subsection{Angular Momentum}
  \label{sec:ang}
  Our models are spherically symmetric and do not include the effects of
  the gas' angular momentum. However, galaxies will in general have some
  net rotation, and the gas will generally have some non-zero angular
  momentum. At some radius, $\rcirc$, the specific angular momentum of
  the gas will equal the specific angular momentum of a circular
  orbit. Inside of this radius our assumptions of no rotation and
  spherical symmetry will break down. But if $\rcirc$ is inside of the
  inner sonic point of the flow, the region where angular momentum
  becomes important will be causally disconnected from the rest of the
  flow, and we would be justified in neglecting angular momentum (at
  least on large scales).

  $\rcirc$ depends on the gas injection radius. The largest
  injection radius is $\rs$. Let $\lrs$ be the gas specific angular
  momentum at $\rs$, then

  \begin{align}
    \rcirc=\frac{\lrs}{G \Mbh}
  \end{align}

  \citet{EmsellemCappellari+:2007a} used two-dimensional kinematic
  data to measure the ratio of ordered to random motion in a sample of
  early type galaxies. More precisely, they measure

  \begin{align}
    \lambda_R=\frac{\left<R|V|\right>}{\left<R\sqrt{V^2+\sigma^2}\right>}
  \end{align}

  Where $R$ is the distance is the distance from the galactic center, $V$ is
  the mean stellar velocity, and $\sigma$ is the velocity
  dispersion. The brackets represent a luminosity weighted average.

  We may rewrite the specific angular momentum at $\rs$ in terms of $\lambda_R$.

  \begin{align}
    \lrs\simeq\lambdars \sigma(\rs)^2 \rs^2
  \end{align}

  Then

  \begin{align}
    \rcirc&\simeq\lambdars^2 \frac{\sigma(\rs)^2}{G \Mbh} \rs^2\\
    &\simeq\lambdars^2 \frac{\rs^2}{\rsoi} \lsim \lambdars^2 \rsoi
  \end{align}

  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
  $\rsoi$. %%AG-Need to explain this somehow.
  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Figure 2 of
  \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
  of radius for a sample of early type galaxies. On scales of $\sim 0.1
  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
  of their sample %%need to be clearer on rapidly declining also compare
  %% this scale to the sphere of influence scale.
  This suggests that angular momentum should generally be unimportant.

  \section{Summary}
\label{sec:summary}

  \clearpage
  \appendix
  \section{Analytic Expression for the stagnation radius}
  \label{app:rs}
  \input{rs}

  \section{Dependence of q on stellar age}
  \label{app:eta}
  \input{eta}

  \footnotesize{
    \bibliographystyle{mn2e}
    \bibliography{master}
  }
\end{document}

### 2014-09-17 ms.tex
Some edits

@@
 \begin{abstract}
-We calculate the steady-state hydrodynamic profiles of hot gas in the nuclei of a sample of early-type quiescent galaxies from the Nuker database.
-We assume that mass is supplied to the circumnuclear medium (CNM) entirely by stellar winds according to the radial stellar profiles for each galaxy, while the gas is heated by a combination of shocked stellar winds and supernovae.
-Our analytic and numerical results are used to estimate the accretion rates onto the central supermassive black holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the heating efficiency, the latter of which is related schematically to the age of the stellar population, the frequency of supernovae, and the efficacy of accretion feedback processes.
-For a fixed heating efficiency, we find that the SMBH accretion Eddington factor increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for core and cusp nuclei, respectively.
-However, considering the potentially lower heating efficiency of low mass SMBHs (due to a younger stellar population and the rareity of supernovae within the stagnation radius) and their resulting higher susceptibility to cooling instability, we find a flatter relationship $\alpha \approx 0$.
-Our results are used to check previous estimates of the SMBH accretion rate assuming Bondi accretion and extrapolating the X-ray measured density and temperature to the unresolved Bondi radius.
-We also discuss the implications of our results for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies.
+  We calculate the steady-state hydrodynamic profiles of hot gas in
+  the nuclei of a sample of early-type quiescent galaxies from the
+  Nuker database.  We assume that mass is supplied to the
+  circumnuclear medium (CNM) entirely by stellar winds according to
+  the radial stellar profiles for each galaxy, while the gas is heated
+  by a combination of shocked stellar winds and supernovae.  Our
+  analytic and numerical results are used to estimate the accretion
+  rates onto the central supermassive black holes (SMBH) as a function
+  of the SMBH mass $M_{\bullet}$ and the heating efficiency, the
+  latter of which is related schematically to the age of the stellar
+  population, the frequency of supernovae, and the efficacy of
+  accretion feedback processes.  For a fixed heating efficiency, we
+  find that the SMBH accretion Eddington factor increases with the
+  SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{\alpha}$
+  with $\alpha \approx 0.5, 1$ for core and cusp nuclei, respectively.
+  % However, considering the potentially lower heating efficiency of low
+  % mass SMBHs (due to a younger stellar population and the rareity of
+  % supernovae within the stagnation radius) and their resulting higher
+  % susceptibility to cooling instability, we find a flatter
+  % relationship $\alpha \approx 0$. 
+  Our results are used to check previous estimates of the SMBH
+  accretion rate assuming Bondi accretion and extrapolating the X-ray
+  measured density and temperature to the unresolved Bondi radius.  We
+  also discuss the implications of our results for the diversity of
+  CNM environments encountered by the jetted outflows from tidal
+  disruption events, and for the use of an assumed
+  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
+  fraction of SMBHs in low mass galaxies.
 \end{abstract}
@@
 %% Maybe active galaxies constitute 10% need reference here?
-Supermassive black holes (SMBHs) lurk in the centers of most, if not all nearby galaxies (see reviews by,
-e.g. \citealt{KormendyRichstone:1995a}; \citealt{FerrareseFord:2005a}). However, only a few percent of these manifest
-themselves as luminous Active Galactic Nuclei (AGN).  Nearly quiescent SMBHs, such as those hosting low luminosity AGN, constitute a silent majority (e.g.~\citealt{Ho:2009a}).
+Supermassive black holes (SMBHs) lurk in the centers of most, if not
+all nearby galaxies (see reviews by,
+e.g. \citealt{KormendyRichstone:1995a};
+\citealt{FerrareseFord:2005a}). However, only a few percent of these
+manifest themselves as luminous Active Galactic Nuclei (AGN).  Nearly
+quiescent SMBHs, such as those hosting low luminosity AGN, constitute
+a silent majority (e.g.~\citealt{Ho:2009a}).
 
-In order to understand why most SMBHs appear to be inactive, it is necessary to understand their gaseous environments.
-Hot gas near the SMBH sphere of influence (the `circumnuclear medium' or CNM) controls the central mass accretion rate $\dot{M}$.
-Better knowledge of how $\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the galactic nucleus is necessary to understand the co-evolution of SMBHs and their host galaxies with cosmic time.
-SMBH growth in the low redshift universe, for instance, appears to be dominated by low mass black holes (e.g.~\citealt{Heckman+04}).
-Although this is often attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}), the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
+In order to understand why most SMBHs appear to be inactive, it is
+necessary to understand their gaseous environments.  Hot gas near the
+SMBH sphere of influence (the `circumnuclear medium' or CNM) controls
+the central mass accretion rate $\dot{M}$.  Better knowledge of how
+$\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
+galactic nucleus is necessary to understand the co-evolution of SMBHs
+and their host galaxies with cosmic time.  SMBH growth in the low
+redshift universe, for instance, appears to be dominated by low mass
+black holes (e.g.~\citealt{Heckman+04}).  Although this is often
+attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}),
+the physical processes involved may be distinct from those operating
+at higher SMBH masses and accretion rates in quasars.
 
-The accretion rates of low mass SMBHs and their resulting nuclear X-ray luminosities $L_X$ also have implications for observational constraints on their occupation fraction in low mass galaxies and the possible existence of intermediate mass black holes.
-\citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and $L_X$ from a sample of relatively high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass galaxies, to infer tentative evidence for an occupation fraction less than unity.
-However, this method relies on extrapolating a power-law fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the instrumental detection threshold.
-The conclusions of \citet{MillerGallo+:2014a} are thus sensitive to possible changes in the $L_X$-$\Mbh$ relationship at small $\Mbh$.
+The accretion rates of low mass SMBHs and their resulting nuclear
+X-ray luminosities $L_X$ also have implications for observational
+constraints on their occupation fraction in low mass galaxies and the
+possible existence of intermediate mass black holes.
+\citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and
+$L_X$ from a sample of relatively high mass galaxies
+(\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass
+galaxies, to infer tentative evidence for an occupation fraction less
+than unity.  However, this method relies on extrapolating a power-law
+fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the
+instrumental detection threshold.  The conclusions of
+\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
+the $L_X$-$\Mbh$ relationship at small $\Mbh$.
 % AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
-The density profile of the CNM also influences the emission from stellar tidal disruption events (TDEs), such as the high energy transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
-This event was powered by an transient relativistic jet, which produced synchrotron radio emission as the jet material was decelerated by shock interaction with the CNM of the previously quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).
-Detailed modeling of {\it Swift} J1644+57 showed that the CNM density was significantly lower than that measured surrounding Sgr A$^{\star}$ (\citealt{Metzger+12}; \citealt{Berger+12}).
-However, a TDE jet injected into a denser CNM would be decelerated more rapidly, producing substantially different radio emission than in {\it Swift} J1644+57.
-Variations in the properties of the CNM could thus in principle help explain why most TDEs appear to be radio quiet (e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).
+The density profile of the CNM also influences the emission from
+stellar tidal disruption events (TDEs), such as the high energy
+transient {\it Swift} J1644+57 (\citealt{Levan+11};
+\citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
+This event was powered by a transient relativistic jet, which produced
+synchrotron radio emission as the jet material was decelerated by
+shock interaction with the CNM of the previously quiescent SMBH
+(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
+modeling of {\it Swift} J1644+57 showed that the CNM density was
+significantly lower than that measured surrounding Sgr A$^{\star}$
+(\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
+injected into a denser CNM would be decelerated more rapidly,
+producing substantially different radio emission than in {\it Swift}
+J1644+57.  Variations in the properties of the CNM could thus in
+principle help explain why most TDEs appear to be radio quiet
+(e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).
 
-Gas that forms the CNM of a SMBH may originate from several sources (\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved) stars; (2) star-star collisions; (3) the unbound debris from TDEs.
-Stellar wind mass loss is probably the dominant source in most cases insofar as collisions are relevant only in very dense stellar environments for young stellar populations (\citealt{Rubin&Loeb11}), while TDEs are estimated to provide a subdominant contribution to the time-averaged accretion rate of quiescent SMBHs (\citealt{MacLeod+13}).
+Gas that forms the CNM of a SMBH may originate from several sources
+(\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved)
+stars; (2) star-star collisions; (3) the unbound debris from TDEs.
+Stellar wind mass loss is probably the dominant source in most cases
+insofar as collisions are relevant only in very dense stellar
+environments for young stellar populations (\citealt{Rubin&Loeb11}),
+while TDEs are estimated to provide a subdominant contribution to the
+time-averaged accretion rate of quiescent SMBHs
+(\citealt{MacLeod+13}).
 
@@
   &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr-\rho \dphidr-q v \label{eq:dvdt}\\
-  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] + \nabla\cdot(\kappa \nabla T), \label{eq:dsdt}
+  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
+      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
+  %+\nabla\cdot(\kappa \nabla T)
+, 
+\label{eq:dsdt}
 \end{align}
-where $v$, $T$, $p$ and $s$ are the radial velocity, temperature, pressure and entropy of the gas, respectively.
-Here $\partial \Phi/\partial r = GM_{\rm enc}/r^{2}$ is the gravitational acceleration, where $M_{\rm enc} = M_{\star}(r) + M_{\bullet}$ is the enclosed mass.
-We assume an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$ {\bf BDM: correct?} and $\gamma = 4/3$.
+where $v$, $T$, $p$ and $s$ are the radial velocity, temperature,
+pressure and specific entropy of the gas, respectively.  Here $\partial
+\Phi/\partial r = GM_{\rm enc}/r^{2}$ is the gravitational
+acceleration, where $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
+enclosed mass.  We assume an ideal gas equation of state with $p =
+\rho kT/\mu m_p$ with $\mu = 1$  and $\gamma = 5/3$.
 
-The source term in the continuity equation (eq.~[\ref{eq:drhodt}]),
+The source term in the continuity equation (equation~\ref{eq:drhodt}),
+%Should equations be referenced as equation of equation
 \begin{align}
@@
 \end{align}
-represents mass input from stellar winds, which we parameterize in terms of the fraction $\eta$ of the stellar density $\rhostar$ being recycled into gas on the Hubble time $\th = 10^{10}$ years (see, e.g., \citealt{Ciotti+91}).
-In Appendix \ref{app:eta} we estimate that $\eta \approx 0.11(t_{\star}/t_{\rm h})^{-1.26}$ for a Salpeter IMF, assuming that all stars are formed in a burst of star formation at a common age of $t_{\star}$ (eq.~[\ref{eq:eta}]).
-We adopt $\eta=1$ as fiducial, but note that changing $\eta$ is equivalent to rescaling $\rho$ by the same factor.\footnote{This is {\it not} true once cooling is included, since the cooling rate is proportional to density {\it squared}.}
+represents mass input from stellar winds, which we parameterize in
+terms of the fraction $\eta$ of the stellar density $\rhostar$ being
+recycled into gas on the Hubble time $\th = 10^{10}$ years (see, e.g.,
+\citealt{Ciotti+91}).  In Appendix \ref{app:eta} we estimate that
+$\eta \approx 0.11(t_{\star}/t_{\rm h})^{-1.26}$ for a Salpeter IMF,
+assuming that all stars are formed in a burst of star formation at a
+common age of $t_{\star}$ (equation~\ref{eq:eta}).  We adopt
+$\eta=1$ as fiducial, but note that changing $\eta$ is equivalent to
+rescaling $\rho$ by the same factor.\footnote{This is {\it not} true
+  if cooling is included, since the cooling rate is proportional to
+  density {\it squared}.}
 
-Source terms $\propto q$ also appear in the momentum and entropy equations (eq.~[\ref{eq:dvdt}], [\ref{eq:dsdt}]) due to the fact that the isotropic mass injection in the rest frame of the SMBH represents a source of momentum and energy upon being incorporated into the mean flow (see also below).
-The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
+Source terms $\propto q$ also appear in the momentum and entropy
+equations (equation~\ref{eq:dvdt} and \ref{eq:dsdt}) due to the fact
+that the isotropic mass injection in the rest frame of the SMBH
+represents a source of momentum and energy upon being incorporated
+into the mean flow (see also below).  
+%No net momentum is in the winds, but mass is being added which adds a
+%term in the velocity equation...
 
-Following \citet{ShcherbakovWong+:2014a}, the term in the entropy equation $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ accounts for external heating sources.
-Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the velocity dispersion of the stars, thus accounting for the fact that at a minimum the gas experiences shock heating between the stellar winds of velocities moving with respect to each other a characteristic velocity $\sim \sigma$, i.e.
-even if the wind velocities themselves are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
-The term $v_{w,0}^{2}$ parameterizes additional sources of heating, such as main sequence winds, millisecond pulsars, supernovae, etc.
-As discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in general depend on the SMBH mass and the age of the stellar population.
+% The second source term in
+% equation (\ref{eq:dsdt}) accounts for heating transportation by
+% electron conductivity, where the conductivity $\kappa = \kappa_0
+% T^{5/2}$ is assumed to equal the classical ``Spitzer" value
+% (\citealt{Spitzer62}); although even a weak magnetic field could in
+% principle strongly suppress the conductivity perpendicular to the
+% field, the radially-decreasing temperature profiles of interest are
+% susceptible to the magneto-thermal instability (\citealt{Balbus01}),
+% the non-linear evolution of which is believed to result in a
+% radially-directed field structure (\citealt{Parrish&Stone07}).
 
-Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) are solved for each galaxy using a standard Runge-Kutta integration for different assumed values of $v_{\rm w,0}$ spanning the physically expected range.
-Although we are most interested in the steady-state CNM structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.
+Following \citet{ShcherbakovWong+:2014a}, the term in the entropy
+equation $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ accounts for external
+heating sources.  Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the
+velocity dispersion of the stars, thus accounting for the fact that at
+a minimum the gas experiences shock heating between the stellar winds
+of velocities moving with respect to each other a characteristic
+velocity $\sim \sigma$, i.e. even if the wind velocities themselves
+are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
+The term $v_{w,0}^{2}$ parameterizes additional sources of heating,
+such as main sequence winds, millisecond pulsars, supernovae, etc.  As
+discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is
+uncertain and will in general depend on the SMBH mass and the age of
+the stellar population.
 
-We do not include radiative cooling in the entropy equation because across much of the parameter space radiative cooling is negligible compared to other sources of cooling (e.g., advection).
-Radiative cooling cannot be neglected in some cases (especially if $\eta$ is high), but the onset of a thermal instability when radiative cooling dominates precludes obtaining a steady-state solution anyways.
-Our steady state solutions neglecting radiation can nevertheless be used to ascertain over what parameter space cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).
+Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) are solved using a sixth
+order finite difference scheme with a third order Runge-Kutta scheme
+for time integration and artificial viscosity terms in the velocity
+and entropy equations for numerical stability. This scheme is
+described in \citealt{Brandenburg:2003a}.  We solve the equations for
+different choices of $v_{\rm w,0}$ spanning the physically expected
+range.  Although we are most interested in the steady-state CNM
+structure, the time-dependent equations are solved to avoid numerical
+issues that arise near the critical sonic points, of which there are
+up to two because of the supersonic inflow on small radial scales and
+a possible supersonic outflow on large scales.
 
-The accuracy of our numerical solutions is assessed by checking the level of conservation of mass across the grid, as well as the integral constraint on the Bernoulli parameter.
-Mass and Bernoulli are conserved to $\lesssim 10$ per cent for all solutions presented in this paper.
-{\bf BDM: more details...}
+We do not include radiative cooling in the entropy equation because
+across much of the parameter space radiative cooling is negligible
+compared to other sources of cooling (e.g., advection).  Radiative
+cooling cannot be neglected in some cases (especially if $\vwO$ is low
+or $\eta$ is high), but the onset of a thermal instability when
+radiative cooling dominates precludes obtaining a steady-state
+solution anyways.  Our steady state solutions neglecting radiation can
+nevertheless be used to ascertain over what parameter space cooling
+instabilities are likely to develop ($\S\ref{sec:cooling}$).
+%Dependence of the heating to cooling ratio has a far steeper
+%dependence on vwO than on eta...
+
+The accuracy of our numerical solutions is assessed by checking the
+level of conservation of mass across the grid, as well as the integral
+constraint on the energy.  Mass and energy are conserved to $\lesssim
+40$ per cent for all solutions presented in this
+paper. % {\bf BDM: more details...}
 
@@
 
-When possible our results are expressed in terms of the wind heating parameter $v_{\rm w,0}$; the power-law slope of the density profile $n$ (also evaluated at $r = \rs$); and the dimensionless parameter
-\be
-\chi \equiv \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx \left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right),
-\ee
-where $v_{500} \equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the $M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09})
-\be
-M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{5.1}M_{\odot}.
+When possible our results are expressed in terms of the wind heating
+parameter $v_{\rm w,0}$; the power-law slope of the density profile
+$n$ (also evaluated at $r = \rs$); and the dimensionless parameter \be
+\chi \equiv \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
+\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right), \ee where $v_{500}
+\equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv
+M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the
+$M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09}) \be
+M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
+      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
 \label{eq:Msigma}
@@
 
-First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by (eq.~[\ref{eq:Tanalytic}])
+First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by (equation~[\ref{eq:Tanalytic}])
 \begin{align}
@@
 
-Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived (eq.~[\ref{eq:rstag}]),
+Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived (equation~[\ref{eq:rstag}]),
 \begin{align}
@@
 
-If the SMBH dominates the potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg 200 M_{\bullet,8}^{0.2}$ km s$^{-1}$) then the relationship between $\rs$ and $v_{w}$ is simplified greatly:
+If the SMBH dominates the potential at the stagnation radius
+($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg 200 M_{\bullet,8}^{0.2}$ km
+s$^{-1}$) then the relationship between $\rs$ and $v_{w}$ is
+simplified greatly:
 \begin{align}
@@
 \end{align}
-where we have assumed $n = 1$ {\bf BDM: true?  should there be a $\chi$ in this?}.  Note that this expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their eq.~[6]).
+where we have assumed $n = 1$ {\bf BDM: true?  should there be a
+  $\chi$ in this?}.  Note that this expression is similar to that
+obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
 
-The SMBH accretion rate is simply given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
+The SMBH accretion rate is simply given by the integrated mass loss rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
 \begin{eqnarray}
@@
 \end{align}
-we note the qualitative similarity between this expression and the Bondi formula (eq.~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
+we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
 \begin{align}
@@
 \end{align}
-where in the second line we have used the fact that $v_{w}^{2}/2 = c_s^2/(\gamma-1)$ at $\rs$ ({\bf BDM: Check - as this depends on whether eq 10 is correct}).
-Thus, provided that a stagnation radius exists which is interior to the sphere of influence radius, the accretion rate predicted by our model is quite close to $\dot{M}_{\rm B}$.
+where in the second line we have used the fact that $v_{w}^{2}/2 =
+c_s^2/(\gamma-1)$ at $\rs$ ({\bf BDM: Check - as this depends on
+  whether eq 10 is correct}).  Thus, provided that a stagnation radius
+exists which is interior to the sphere of influence radius, the
+accretion rate predicted by our model is quite close to $\dot{M}_{\rm
+  B}$.
 
@@
 
-Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $v(r)$, as well as the cumulative X-ray luminosity.
-As expected, the gas density increases towards the SMBH, with a characteristic radial slope $\rho \propto r^{n}$ with $n \approx 1$ near the stagnation radius (marked as a square in Fig.~\ref{fig:profiles}; {\bf BDM:check!?}).
-On very small scales the gas density profile appropaches the behavior $\rho \propto r^{-3/2}$ predicted for Bondi accretion.
-The temperature profile is relatively flat at large radii, but increases as $\propto 1/r$ interior to the sphere of influence, both behaviors expected for virialized gas in near hydrostatic equilibrium.
-The inwardly directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
-{\bf BDM: I made this up - in general we need more explanation of what the plots are actually showing, with some physical explanation.}
+Figure~\ref{fig:profiles} shows three representative profiles of the
+density $\rho(r)$, temperature $T(r)$, and radial velocity $v(r)$, as
+well as the cumulative X-ray luminosity.  As expected, the gas density
+increases towards the SMBH, with a characteristic radial slope $\rho
+\propto r^{n}$ with $n \approx 1$ near the stagnation radius (marked
+as a square in Fig.~\ref{fig:profiles}. The gas density The
+temperature profile is relatively flat at large radii, but increases
+as $\propto 1/r$ interior to the sphere of influence, both behaviors
+expected for virialized gas in near hydrostatic equilibrium.  The
+inwardly directed velocity increases towards the hole approaching the
+expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
+interior to the sonic point, and then increases outwards towards large
+radii. {\bf BDM: I made this up - in general we need more explanation
+  of what the plots are actually showing, with some physical
+  explanation.}
 
-Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.
-Cusp and core galaxies are marked with square and triangles, respectively.
-The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.
-{\bf BDM: I see no lines!}
+Figure~\ref{fig:stag} (top panel) shows numerical results for the
+stagnation radius $r_{\rm s}$ where the radial velocity goes to zero
+(expressed in ratio to the radius of the SMBH sphere of influence
+$r_{\rm soi}$), with different colors representing different values of
+$v_{w,0}$.  Cusp and core galaxies are marked with square and
+triangles, respectively.  
+%The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}
 
@@
   \includegraphics[width=\columnwidth]{profiles.eps}
-  \caption{\label{fig:profiles}Radial profiles of the CNM density ({\it top}), temperature ({\it top}), velocity ({\it ADD}), and interior X-ray luminosity ({\it bottom}), calculated for three characteristic galaxies from our samples: NGC1172 ({\it blue}), NGC4478 ({\it green}), and NGC3115 ({\it black}).
-Different line styles denote different values of the effective wind heating rate, $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it dot-dashed}).
-{\bf BDM: add velocity profiles...xray luminosity can probably go elsewhere}}
+  \caption{\label{fig:profiles}Radial profiles of the CNM density
+    ({\it top}), temperature ({\it top}), velocity ({\it ADD}), and
+    interior X-ray luminosity ({\it bottom}), calculated for three
+    characteristic galaxies from our samples: NGC1172 ({\it blue}),
+    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
+    styles denote different values of the effective wind heating rate,
+    $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
+      dot-dashed}).  {\bf BDM: add velocity profiles...xray luminosity
+      can probably go elsewhere}}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{rs.eps}
-  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a function of the ratio of the effective wind heating rate $v_{w,0}$ to the stellar velocity dispersion $\sigma$.
-Green, orange, and blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$, respectively.
-Squares correspond to cusp galaxies, while triangles correspond to cores.
-\emph{Bottom panel}: Fractional difference between our numerical calculation of $r_{\rm s}/r_{\rm soi}$ and the analytic result in equation~(\ref{eq:stag_analytic}).
-}
+  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
+    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
+      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
+    function of the ratio of the effective wind heating rate $v_{w,0}$
+    to the stellar velocity dispersion $\sigma$.  Green, orange, and
+    blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$,
+    respectively.  Squares correspond to cusp galaxies, while
+    triangles correspond to cores. \emph{Bottom panel}: Fractional
+    difference between our numerical calculation of $r_{\rm s}/r_{\rm
+      soi}$ and the analytic result in
+    equation~(\ref{eq:stag_analytic}). }
 \end{figure}
@@
 
-Our results show that the location of the stagnation rate and resulting accretion rate, is very sensitive to the assumed heating rate $\propto v_{w,0}^{2}$.
-Physically, we expect that the heating rate will vary from galaxy to galaxy..
-For example, SNe Ia represent a potentialy important source of heating, but since they are rare they will only be relevant in a time-averaged sense if the supernova rate exceeds the inflow time of the gas near the stagnation point.
+Our results show that the location of the stagnation rate and
+resulting accretion rate, is very sensitive to the assumed heating
+rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating
+rate will vary from galaxy to galaxy.. For example, SNe Ia represent a
+potentialy important source of heating, but since they are rare they
+will only be relevant in a time-averaged sense if the supernova rate
+exceeds the inflow time of the gas near the stagnation point.
 
@@
 \subsubsection{Millisecond Pulsars} The spin down power of millisecond pulsars (MSPs) could in principle be an important heating source.
-If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $L_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm msp}\epsilon$ corresponds to an effective heating rate (eq.~ [\ref{eq:vw_eff}])
+If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $L_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm msp}\epsilon$ corresponds to an effective heating rate (equation~ [\ref{eq:vw_eff}])
   \begin{align}
@@
 Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the instellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}])
+Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the instellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}])
 \begin{align}
@@
 In the limit of an old stellar population of age $t_{\star} \sim t_{\rm h}$ the Ia rate just becomes $R_{\rm Ia} \sim 2\times 10^{-55} $ g$^{-1}$ s$^{-1}$ (e.g.~\citealt{Scannapieco&Bildsten05}).
-Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$ also depends on the stellar age (eq.~[\ref{eq:eta}]).
+Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$ also depends on the stellar age (equation~[\ref{eq:eta}]).
 Thus, from equation (\ref{eq:vw_eff}) we estimate $v_{w,0} \approx 350\epsilon_{\rm Ia}^{0.5}(\eta/0.1)^{-0.5}$ for an old stellar population.
@@
 \end{eqnarray}
-as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship (eq.~[\ref{eq:Msigma}]).
+as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship (equation~[\ref{eq:Msigma}]).
 
-Note that the stagnation radius scales approximately linearly with $M_{\bullet}$ (eq.~[\ref{eq:stag_simple}]), while $\rIa$ is roughly indpendent of SMBH mass.
+Note that the stagnation radius scales approximately linearly with $M_{\bullet}$ (equation~[\ref{eq:stag_simple}]), while $\rIa$ is roughly indpendent of SMBH mass.
 For small $\Mbh$, the stagnation radius thus lies well inside $\rIa$ and hence Ia SNe will not contribute appreciably to the heating rate.
@@
 AGN feedback also represents an additional source of heating.
-In this case, since the rate of feedback is likely proportional to the mass accretion rate $\dot{M}$, which itself is inversely proportional to the heating rate (eq.~[\ref{eq:mdot_analytic}]), then, if dominant, the effective heating rate from AGN $v_{\rm w,0}$ may be regulated to a fixed value.
+In this case, since the rate of feedback is likely proportional to the mass accretion rate $\dot{M}$, which itself is inversely proportional to the heating rate (equation~[\ref{eq:mdot_analytic}]), then, if dominant, the effective heating rate from AGN $v_{\rm w,0}$ may be regulated to a fixed value.
 
@@
 
-Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy (eq.~[\ref{eq:mdot_analytic}]), the mass accretion rate is expected to be a sensitive function of the assumed heating rate.
+Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy (equation~[\ref{eq:mdot_analytic}]), the mass accretion rate is expected to be a sensitive function of the assumed heating rate.
 However,  the accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.

### 2014-09-18 ms.tex
Updating the figures

@@
   We calculate the steady-state hydrodynamic profiles of hot gas in
-  the nuclei of a sample of early-type quiescent galaxies from the
-  Nuker database.  We assume that mass is supplied to the
-  circumnuclear medium (CNM) entirely by stellar winds according to
-  the radial stellar profiles for each galaxy, while the gas is heated
-  by a combination of shocked stellar winds and supernovae.  Our
-  analytic and numerical results are used to estimate the accretion
-  rates onto the central supermassive black holes (SMBH) as a function
-  of the SMBH mass $M_{\bullet}$ and the heating efficiency, the
-  latter of which is related schematically to the age of the stellar
-  population, the frequency of supernovae, and the efficacy of
-  accretion feedback processes.  For a fixed heating efficiency, we
-  find that the SMBH accretion Eddington factor increases with the
-  SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{\alpha}$
-  with $\alpha \approx 0.5, 1$ for core and cusp nuclei, respectively.
+  the nuclei of a sample of early-type quiescent galaxies.  We assume
+  that mass is supplied to the circumnuclear medium (CNM) entirely by
+  stellar winds according to the radial stellar profiles for each
+  galaxy, while the gas is heated by a combination of shocked stellar
+  winds and supernovae.  Our analytic and numerical results are used
+  to estimate the accretion rates onto the central supermassive black
+  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
+  heating efficiency, the latter of which is related schematically to
+  the age of the stellar population, the frequency of supernovae, and
+  the efficacy of accretion feedback processes.  For a fixed heating
+  efficiency, we find that the SMBH accretion Eddington factor
+  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
+  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cups and core
+  nuclei, respectively.
   % However, considering the potentially lower heating efficiency of low
@@
 \begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 4 \times 10^6\,v_{500}^2 \, \chi   \,\,{\rm K} 
+T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 6
+\times 10^6\,v_{500}^2 \, \mu  \,\,{\rm K} 
 \end{align}
-{\bf BDM: i picked $\mu = 0.62$ and stick to it.}
+%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}
 
@@
 \begin{align}
-  \x=\frac{1}{\zeta^2 n}\left[ (1+\Mstar(\rs)/\Mbh)\left(A-\frac{n}{2}\right)-B\right],
+  \x=\frac{1}{\zeta^2 n}\left[
+    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
   \label{eq:stag_analytic}
 \end{align}
-where $\zeta \equiv v_{w,0}/\sigma$ {\bf BDM: note new definition}, $r_{\rm soi} = GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of influence (soi), and A/B are constants that depend on the Nuker parameter $\Gamma$ and the adiabatic index of the gas.
+where $\zeta \equiv v_{w,0}/\sigma$, $r_{\rm soi}
+=GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of
+influence (soi), and A and B are constants that depend on the Nuker
+parameter $\Gamma$ and the adiabatic index of the gas.
 
@@
 \end{align}
-where we have assumed $n = 1$ {\bf BDM: true?  should there be a
-  $\chi$ in this?}.  Note that this expression is similar to that
+where we have assumed $n = 1$.  Note that this expression is similar to that
 obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
@@
     1.6 \times 10^{-3}  M_{\bullet,8}^{1.9}
-    v_{500}^{-4} \chi^{-2} \eta \Msun \, \pyear& \text{core} \\
+    v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
     3.4 \times 10^{-3} \Mbheight^{1.4}
-    v_{500}^{-2} \chi^{-1} \eta \Msun \, \pyear  & \text{cusp}, 
+    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
   \begin{cases}
-    3 \times 10^{-24} \Mbheight^{-0.14} v_{500}^{-1} \chi^{-1/2} \eta \,
+    3 \times 10^{-24} \Mbheight^{-0.14} v_{500}^{-1}  \eta \,
     \, {\rm g \, cm^{-3}}& \text{core}\\
-    6 \times 10^{-24}  \Mbheight^{-0.56} v_{500}  \chi^{1/2}  \eta \,\, {\rm g \,cm^{-3}} & \text{cusp}
+    6 \times 10^{-24}  \Mbheight^{-0.56} v_{500}    \eta \,\, {\rm g \,cm^{-3}} & \text{cusp}
   \end{cases}
@@
   \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it top}), velocity ({\it ADD}), and
+    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
     interior X-ray luminosity ({\it bottom}), calculated for three
@@
     $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
-      dot-dashed}).  {\bf BDM: add velocity profiles...xray luminosity
-      can probably go elsewhere}}
+     dot-dashed}).}
 \end{figure}
@@
   \begin{align}
-    \vwO=\sqrt{\frac{2 t_h n_{\rm msp} L_{\rm sd}}{\eta}},
+    \vwO=\sqrt{\frac{\epsilon 2 t_h n_{\rm msp} L_{\rm sd}}{\eta}},
   \end{align}
-where $\eta < 1$ is the thermalization efficiency of the wind.
+where $\epsilon< 1$ is the thermalization efficiency of the wind.
 The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$.
-If we assume an average spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of Fermi pulsars, then we find that $\vwO\simeq 120\epsilon (\eta/0.1)^{-1/2}$ km s$^{-1}$.
+If we assume an average spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of Fermi pulsars, then we find that $\vwO\simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$ km s$^{-1}$.
 Thus, assuming a high thermalization efficiency $\epsilon \sim 1$, MSP heating can be comparable to main sequence heating.
@@
 
+\subsubsection{Comparison with observed X-ray Luminosity-Mass
+  Relation}
+%Note currently I reverse-engineer the stellar mass from the black
+%hole mass inferred from M-sigma; however, it would be better to use
+%the tabulated black hole mass from the Mbh-Mbulge relation.
+Figure 1 of \citealt{MillerGallo+:2014a} plots the observed
+relationship of unresolved x-ray luminosity versus galactic stellar
+mass for a sample of quiescent galaxies. We may construct a similar
+relationship with our own sample using the inferred accretion rates
+from our solutions.  To infer an x-ray luminosity for each solution,
+we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
+10^{-7}$, which gives comparable an x-ray luminosities comparable to
+those in \citealt{MillerGallo+:2014a}.
+%describe the quadratic procedure.
+
+Our results are plotted in Figure~\ref{fig:bh_xray}. For each galaxy
+in our sample we select the $\vwO$=200 km/s if $\rs<\rIa$
+for this solution,  $\vwO$=500 km/s is $\rs>\rIa$ for this solution,
+or exclude it.  $\vwO$ encapsulates heating SNe Ia heating, and it
+would only make sense to include this heating if $\rs$>$\rIa$ as
+discussed in Section~\ref{sec:heating}. At low $\Mbh$ we have
+$\vwO$=200 km/s and at high $\Mbh$ we have $\vwO$=500 km/s.
+Note that much of our sample is excluded in this Figure, since for
+$\vwO$=200 km/s we would have $\rs>\rIa$ and four $\vwO$=500 km/s we
+would have $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$
+would be inconsistent with the assumed level of heating).
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{bh_xray.eps}
+\caption{\label{fig:bh_xray} Accretion power plotted as a function of 
+  stellar mass for our solutions (points) with the trend of nuclear
+  x-ray luminosity with stellar mass and the detection upper limit
+  from Figure 1 of \citealt{MillerGallo+:2014a}. In the top panel we
+  take the accretion power to be $\epsilon \Mdot c^2$, with
+  $\epsilon=5\time 10^{-7}$ chosen to make our accretion powers
+  comparable to the observed x-ray luminosities..}
+\end{figure}
+
 \section{Discussion}
@@
 \label{sec:cooling}
-Our models neglect radiative cooling, an assumption we now check.  At high temperatures  $T\gsim
-2\times 10^7$ K gas cools through free-free emission, while at lower temperatures it cools predominantly through metal lines.  
-To assess the importance of radiative cooling in our solutions we compare the heating rate $H=q
-\vw^2/2$ to the nominal cooling rate
+Our models neglect radiative cooling, an assumption we now check.  At
+high temperatures $T\gsim 2\times 10^7$ K gas cools through free-free
+emission, while at lower temperatures it cools predominantly through
+metal lines.  To assess the importance of radiative cooling in our
+solutions we compare the heating rate $H=q \vw^2/2$ to the nominal
+cooling rate
 \begin{align}
@@
 
-  \section{Summary}
-\label{sec:summary}
+  \section{Summary and conclusions}
+  We have calculated steady-state models for circumnuclear medium of a
+  sample of early type galaxies, assuming that gas is supplied
+  entirely by stellar wind mass loss and heated by shocked stellar
+  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
+  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
+  with $\Mbh$. We may then compare our results with observed trends of
+  nuclear x-ray luminosity. Our main conclusions may be summarized as
+  follows.
+
+  \begin{enumerate}
+    \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value
+      of $\alpha$ depends on the slope of the stellar density profile
+      ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively).
+
+  \end{enumerate}
 

### 2014-09-19 ms.tex
More edits.

@@
 
-The one-dimensional steady state flow of gas is usually characterized by an inflow-outflow structure, with a critical radius known as the ``stagnation radius" $\rs$ where the radial velocity goes to zero.
-Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.
-The stagnation radius, rather than the Bondi radius, is thus ultimately responsible for setting the SMBH accretion rate.
-Although we find that $\rs$ typically lies within a factor of few of the nominal Bondi radius, the difference in the accretion rate can be significant.
-Furthermore, in some cases we find that no stagnation radius exists at all; this formally implies that the entire of ISM of the galaxy is feeding the SMBH, potentially resulting in much higher accretion rate than would be predicted by simple Bondi accretion.
-The main goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the relatively well understood physics of stellar winds and supernova heating.
+The one-dimensional steady state flow of gas is usually characterized
+by an inflow-outflow structure, with a critical radius known as the
+``stagnation radius" $\rs$ where the radial velocity goes to zero.
+Mass loss from stars interior to the stagnation radius is accreted,
+while that outside $\rs$ is unbound in an outflow from the nucleus.
+The stagnation radius, rather than the Bondi radius, is thus
+ultimately responsible for setting the SMBH accretion rate.  Although
+we find that $\rs$ typically lies within a factor of few of the
+nominal Bondi radius, the difference in the accretion rate can be
+significant.  Furthermore, in some cases we find that no stagnation
+radius exists at all; this formally implies that the entire of ISM of
+the galaxy is feeding the SMBH, potentially resulting in much higher
+accretion rate than would be predicted by simple Bondi accretion.  The
+main goal of our analysis is to provide a framework for interpreting
+the properties of quiescent galactic nuclei given the relatively well
+understood physics of stellar winds and supernova heating.
 
-This paper is organized as followed.
-In $\S\ref{sec:model}$ we describe our model, including the sample of galaxies used in our analysis ($\S\ref{sec:sample}$) and our numerical procedure for calculating the steady-state hydrodynamic profile of the CNM ($\S\ref{sec:hydro}$).
-In $\S\ref{sec:results}$ we describe our results.
-In $\S\ref{sec:applications}$ we describe applicaiton of our results, including a comparison of our gas profiles to those inferred from {\it Chandra} observations and to the measured $L_X-\Mbh$ relationship.
-In $\S\ref{sec:discussion}$ we discuss our results.
-In $\S\ref{sec:summary}$ we summarize our results.
-
+This paper is organized as followed.  In $\S\ref{sec:model}$ we
+describe our model, including the sample of galaxies used in our
+analysis ($\S\ref{sec:sample}$) and our numerical procedure for
+calculating the steady-state hydrodynamic profile of the CNM
+($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
+results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
+results, including a comparison of our gas profiles to those inferred
+from {\it Chandra} observations and to the measured $L_X-\Mbh$
+relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
+$\S\ref{sec:summary}$ we summarize our results.
 \section{Model}
@@
 
-Given $I(\xi)$ we follow the procedure outlined by \citetalias{WangMerritt:2004a} to compute the spherically-symmetric stellar density profile $\rhostar(r)$ and stellar mass profile $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in our model.
-For reference, note that stellar density $\rhostar\sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r \gg \rb$.
-Since $\Gamma\approx 1$ for ``cusp" galaxies, while $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.
-For each galaxy the SMBH mass $\Mbh$ is determined from....
-({\bf BDM: more info!}).
+Given $I(\xi)$ we follow the procedure outlined by
+\citetalias{WangMerritt:2004a} to compute the spherically-symmetric
+stellar density profile $\rhostar(r)$ and stellar mass profile
+$M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
+our model.  For reference, note that stellar density $\rhostar\sim
+r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
+\gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
+$\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
+thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
+r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
+SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
+%%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
+%%calculated from an outdated M-sigma. It would be bizarre to use 2
+%%different relations.
 
@@
 where in the second line we have used the fact that $v_{w}^{2}/2 =
-c_s^2/(\gamma-1)$ at $\rs$ ({\bf BDM: Check - as this depends on
-  whether eq 10 is correct}).  Thus, provided that a stagnation radius
+c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
 exists which is interior to the sphere of influence radius, the
@@
   B}$.
+ %({\bf BDM: Check - as this depends on
+ % whether eq 10 is correct})
 
@@
 Figure~\ref{fig:profiles} shows three representative profiles of the
-density $\rho(r)$, temperature $T(r)$, and radial velocity $v(r)$, as
-well as the cumulative X-ray luminosity.  As expected, the gas density
-increases towards the SMBH, with a characteristic radial slope $\rho
-\propto r^{n}$ with $n \approx 1$ near the stagnation radius (marked
-as a square in Fig.~\ref{fig:profiles}. The gas density The
-temperature profile is relatively flat at large radii, but increases
-as $\propto 1/r$ interior to the sphere of influence, both behaviors
-expected for virialized gas in near hydrostatic equilibrium.  The
-inwardly directed velocity increases towards the hole approaching the
-expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
-interior to the sonic point, and then increases outwards towards large
-radii. {\bf BDM: I made this up - in general we need more explanation
-  of what the plots are actually showing, with some physical
-  explanation.}
+density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
+As expected, the gas density increases towards the SMBH.  For some
+profiles (e.g. NGC1172 and NGC4478) the density $\rho$ follows a power
+law from the stagnation radius (squares in Fig.~\ref{fig:profiles})
+inwards $\rho \propto r^{n}$ with $n \approx 1$. Note that this is
+shallower than the $-3/2$ for Bondi accretion. However, the power law
+behavior does not extend through all radii. NGC4365 which has a
+prominent break in the gas density profile, near the stagnation
+radius. This is also roughly the location of the break in the stellar
+light profile ($\rb$). The temperature profile is relatively flat at
+large radii, but increases as $\propto 1/r^{k}$ interior to the sphere
+of influence, where $k$ is smaller than 1 (which would be expected for
+virialized gas).  The inwardly directed velocity increases towards the
+hole approaching the expected free-fall rate $v \propto v_{\rm
+  ff}\propto r^{-1/2}$ interior to the sonic point, and then increases
+outwards towards large radii.
+% {\bf BDM: I made this up - in general we need
+%   more explanation of what the plots are actually showing, with some
+%   physical explanation.}
+% AG -- things are not quite approaching Bondi on the inner grid. I
+% don't have a good physical explanation yet...
+% AG -- I am somewhat concerned about boundary effects in
+% NGC3115. Perhaps the break in the gas density profile is due to
+% boundary effects--I know that in this case the break is not
+% associated with a break in the stellar density profile
 
@@
     styles denote different values of the effective wind heating rate,
-    $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
+    $v_{w,0}$=500 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
      dot-dashed}).}
@@
 
-subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.
+\subsubsection{Stellar winds} Although most of the mass supplied to
+the CNM by stellar winds occurs during the giant AGB phase, these
+winds represent a negligible heating source compared to the random
+wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is
+much less than the stellar potential $\sigma$.
 
-Though representing a much smaller quantity of mass, main sequence winds have much higher velocities and hence contribute a disproportionally large share of the kinetic energy of winds.
-\citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.
-On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.
-In Appendix C we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age.
+Though representing a much smaller quantity of mass, main sequence
+winds have much higher velocities and hence contribute a
+disproportionally large share of the kinetic energy of winds.
+\citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim
+100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
+stellar population.  On the other hand, for a very young stellar
+population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
+heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
+s$^{-1}$.  
+%In Appendix C we present a toy model for how $v_{\rm w,0}$
+%varies as a function of stellar age.
+%AG-Appendix C is not written! As this draft will be circulated I
+%don't want references to things which do not exist!
 
-\subsubsection{Millisecond Pulsars} The spin down power of millisecond pulsars (MSPs) could in principle be an important heating source.
-If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $L_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm msp}\epsilon$ corresponds to an effective heating rate (equation~ [\ref{eq:vw_eff}])
+\subsubsection{Millisecond Pulsars} The spin down power of millisecond
+pulsars (MSPs) could in principle be an important heating source.  If
+the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each
+contributes an average spin-down luminosity $L_{\rm sd}$, then the
+resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
+  msp}\epsilon$ corresponds to an effective heating rate (equation~
+[\ref{eq:vw_eff}])
   \begin{align}
@@
 
-However, SNe can only be approximated as constant source of heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
-To estimate when this approximation is valid, we estimate the ``Ia radius"
-\begin{eqnarray}
-r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx 40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc} \sim 43 M_{\bullet,8}^{0.1}\,{\rm pc}
+However, SNe can only be approximated as constant source of heating
+throughout space and time if the rate of SNe is rapid compared to the
+inflow time at the radius of interest
+(\citealt{ShcherbakovWong+:2014a}).  To estimate when this
+approximation is valid, we estimate the ``Ia radius"
+\begin{align}
+r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx
+&40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc}\sim 43 M_{\bullet,8}^{0.1}\,{\rm pc} 
 \label{eq:rIa}
-\end{eqnarray}
-as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship (equation~[\ref{eq:Msigma}]).
+\end{align}
+as the location exterior of which the time interval between subsequent
+supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim
+G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
+  dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old
+stellar population and in the final equality we estimate the velocity
+dispersion using the $M_{\bullet}-\sigma$ relationship
+(equation~[\ref{eq:Msigma}]).
 
@@
 
-\subsubsection{Combined Heating Rate} The overall heating rate $\vwO$ has contributions from Type Ia SNes and main sequence winds.
-The relative contributions will depend on both the age of the stellar population, $\tage$, and $\Mbh$.
-This is illustrated in Figure~\ref{fig:vweff}.
-For black hole masses below $10^7 \Msun$ SNe
+\subsubsection{Combined Heating Rate} The overall heating rate $\vwO$
+has contributions from Type Ia SNes and main sequence winds.  The
+relative contributions will depend on both the age of the stellar
+population, $\tage$, and $\Mbh$.  This is illustrated in
+Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe
 Ia will not contribute to $\vwO$ as the flow time scale is short
@@
 $\Mbh \gsim 10^8 \Msun$, heating from Ias becomes important, as
-  $\rs>\rIa$. In this regime, we add the $\vwO$ values from SNe Ias
-  and from main sequence winds in quadrature. $\vwO$ from SNe Ia's
-  depends on the rate of mass loss ($\eta$), which is in turn a
-  function of $t_{\star}$. This dependence is why the effective
-  $\vwO$ increases with $\tage$ for large $\Mbh$.
+$\rs>\rIa$. In this regime, we add the $\vwO$ values from SNe Ias and
+from main sequence winds in quadrature. $\vwO$ from SNe Ia's depends
+on the rate of mass loss ($\eta$), which is in turn a function of
+$t_{\star}$. This dependence is why the effective $\vwO$ increases
+with $\tage$ for large $\Mbh$.
 
@@
     \includegraphics[width=\columnwidth]{vw-contour.eps}
-    \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM in the parameter space of SMBH mass $\Mbh$ and age of the stellar population $t_{\star}$.
-We assume that stellar winds contribute a constant heating rate $100$ km/s.
-The contribution from SNe Ia is calculated using equation (\ref{eq:vw_sne}).
-The contribution from SNe Ia is only added if the $r_s$ corresponding to the resulting $\vwO$ is outside $\rIa$.}%describe other cases here.
+    \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM
+      in the parameter space of SMBH mass $\Mbh$ and age of the
+      stellar population $t_{\star}$.  We assume that stellar winds
+      contribute a constant heating rate $100$ km/s. The contribution
+      from SNe Ia is calculated using equation (\ref{eq:vw_sne}). The
+      contribution from SNe Ia is only added if the $r_s$
+      corresponding to the resulting $\vwO$ is outside
+      $\rIa$.}%describe other cases here.
   \end{figure}
@@
 
-For each solution we calculate the accretion rate $\dot{M}$ onto the SMBH  in units of the Eddington accretion rate $\dot{M}_{\rm edd} \equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times 10^{46}M_{\bullet,8}$ erg s$^{-1}$.
-Figure~\ref{fig:mdot_mass} shows $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different values of $\vwO =$ 200, 500 and 1000 km s$^{-1}$.
+For each solution we calculate the accretion rate $\dot{M}$ onto the
+SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
+\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
+10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
+$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
+values of $\vwO =$ 200, 500 and 1000 km s$^{-1}$.
 
-Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy (equation~[\ref{eq:mdot_analytic}]), the mass accretion rate is expected to be a sensitive function of the assumed heating rate.
-However,  the accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.
-This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag}).
-Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.
-For $\vwO=1000$ km s$^{-1}$, core galaxies have a smaller accretion rate for a given SMBH mass.
+Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and
+$\dot{M}\sim\vwO^{-4}$ for a core galaxy
+(equation~[\ref{eq:mdot_analytic}]), the mass accretion rate is
+expected to be a sensitive function of the assumed heating rate.
+However, the accretion rate is proportional to the stellar mass
+enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh
+(\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh
+(\rs/\rsoi)$.  This steeper dependence is enough to offset the
+tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed
+$\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core
+galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
+$\vwO=1000$ km s$^{-1}$, core galaxies have a smaller accretion rate
+for a given SMBH mass.
 %% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
@@
 
-We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase increase with SMBH mass $M_{\bullet}$.
-This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the fact that for quiescent galaxies the nuclear X-ray luminosity obeys $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.
-Our model instead predicts that $\Mdot \sim
-\Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x \sim \Mbh^{1.5-2}$, steeper than the observed relationship.
-(If $L_x \sim \Mdot^2$ the discrepance becomes worse).
-One possible solution that the wind mass loss rate $\eta$ decreases with $\Mbh$, as would be expected if low mass SMBH preferentially hosted younger stellar populations.
-Another possible explanation, which we favor, is that the effective heating rate of the CNM $v_{\rm w,0}$ decreases with decreasing SMBH mass.
-This could again be due to a young stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating sources such as SN Ia and millisecond pulsars, or it could be due to the fact that Ia occur too infrequently inside the stagnation radius for low mass black holes.
+We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH
+mass $M_{\bullet}$.  This appears to be in contradiction with the
+general down sizing trend observed for SMBH accretion in the local
+universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
+fact that for quiescent galaxies the nuclear X-ray luminosity obeys
+$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
+\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
+\sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
+\sim \Mbh^{1.5-2}$, steeper than the observed relationship.
+
+This is shown in the top panel Figure~\ref{fig:bh_xray}. The
+relationship from \citealt{MillerGallo+:2014a} and their detection
+upper limits are shown as the blue and black solid lines
+respectively. The points correspond to the $\dot{M} c^2$ for our
+solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
+each galaxy.  We select $\vwO$=200 km/s if $\rs<\rIa$ for this $\vwO$,
+$\vwO$=500 km/s if $\rs>\rIa$ for this $\vwO$, or exclude it. If
+$L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
+bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
+10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
+\citealt{MillerGallo+:2014a}.
+
+One possible solution that the wind mass loss rate $\eta$ decreases
+with $\Mbh$, as would be expected if low mass SMBH preferentially
+hosted older stellar populations.  Another possible explanation is
+that the effective heating rate of the CNM $v_{\rm w,0}$ decreases
+with decreasing SMBH mass.  This could again be due to an older
+stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating
+sources such as SN Ia and millisecond pulsars.
+%, or it could be due to the fact that Ia occur too infrequently inside
+%the stagnation radius for low mass black holes.
+%AG-We now think that SNe Ia would become important only at the
+%highest values of Mbh.
+%AG-Note sure where the best place for this discussion would
+%be--here or after presenting the comparisons with Miller et al.
 
@@
 We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
-The results of this exercise are presented in Figure~\ref{fig:allen_compare}.
+The results of this exercise are presented in Fig.~\ref{fig:allen_compare}.
 
-Note that we have two free parameters ($\eta$ and $\vwO$) in our model, which implies that we can always match the observed temperature and densities at at least one point.
-As a general rule, we find that a wind heating parameter $\vwO=500$
-km s$^{-1}$ (close to, but somewhat higher than that expected from SNe Ia) gives rough agreement with the observed temperatures.  We now highlight results for specific galaxies.
+Note that we have two free parameters ($\eta$ and $\vwO$) in our
+model, which implies that we can always match the observed temperature
+and densities at at least one point.  As a general rule, we find that
+a wind heating parameter $\vwO=500$ km s$^{-1}$ (close to, but
+somewhat higher than that expected from SNe Ia) gives rough agreement
+with the observed temperatures.  We now highlight results for specific
+galaxies.
 % Thus, we choose $\vwO=500$ km/s.  We choose an
@@
 
-\subsubsection{Comparison with observed X-ray Luminosity-Mass
-  Relation}
-%Note currently I reverse-engineer the stellar mass from the black
-%hole mass inferred from M-sigma; however, it would be better to use
-%the tabulated black hole mass from the Mbh-Mbulge relation.
-Figure 1 of \citealt{MillerGallo+:2014a} plots the observed
-relationship of unresolved x-ray luminosity versus galactic stellar
-mass for a sample of quiescent galaxies. We may construct a similar
-relationship with our own sample using the inferred accretion rates
-from our solutions.  To infer an x-ray luminosity for each solution,
-we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
-10^{-7}$, which gives comparable an x-ray luminosities comparable to
-those in \citealt{MillerGallo+:2014a}.
-%describe the quadratic procedure.
+% \subsubsection{Comparison with observed X-ray Luminosity-Mass
+%   Relation}
+% %Note currently I reverse-engineer the stellar mass from the black
+% %hole mass inferred from M-sigma; however, it would be better to use
+% %the tabulated black hole mass from the Mbh-Mbulge relation.
+% Fig. 1 of \citealt{MillerGallo+:2014a} plots the observed
+% relationship of unresolved x-ray luminosity versus galactic stellar
+% mass for a sample of quiescent galaxies. We may construct a similar
+% relationship with our own sample using the inferred accretion rates
+% from our solutions.  To infer an x-ray luminosity for each solution,
+% we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
+% 10^{-7}$, which gives x-ray luminosities comparable to
+% those in \citealt{MillerGallo+:2014a}. We also try an alternate
+% prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
+% take $L_x=2 \times 10^{-4} (\eddr) \Mdot c^2$.
 
-Our results are plotted in Figure~\ref{fig:bh_xray}. For each galaxy
-in our sample we select the $\vwO$=200 km/s if $\rs<\rIa$
-for this solution,  $\vwO$=500 km/s is $\rs>\rIa$ for this solution,
-or exclude it.  $\vwO$ encapsulates heating SNe Ia heating, and it
-would only make sense to include this heating if $\rs$>$\rIa$ as
-discussed in Section~\ref{sec:heating}. At low $\Mbh$ we have
-$\vwO$=200 km/s and at high $\Mbh$ we have $\vwO$=500 km/s.
-Note that much of our sample is excluded in this Figure, since for
-$\vwO$=200 km/s we would have $\rs>\rIa$ and four $\vwO$=500 km/s we
-would have $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$
-would be inconsistent with the assumed level of heating).
+% We must make choose a $\vwO$ for each galaxy.  We select $\vwO$=200
+% km/s if $\rs<\rIa$ for this solution, $\vwO$=500 km/s if $\rs>\rIa$
+% for this solution, or exclude it.  At low $\Mbh$ we have $\vwO$=200
+% km/s and at high $\Mbh$ we have $\vwO$=500 km/s.  Note that much of
+% our sample is excluded in this Fig., since for $\vwO$=200 km/s we
+% would have $\rs>\rIa$ and four $\vwO$=500 km/s we would have
+% $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$ would be
+% inconsistent with the assumed level of heating).
+
+% %AG-power law may be closer to 1.4 & 1.8 than to 1.5 & 2.
+% Our results are plotted in Fig.~\ref{fig:bh_xray}. In our model
+% there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
+% \citealt{MillerGallo+:2014a}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
+% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{MillerGallo+:2014a} finds
+% that $L_x \propto M_{\rm gal}^{0.7-0.8}$.
 
@@
 \caption{\label{fig:bh_xray} Accretion power plotted as a function of
-  stellar mass for our solutions (points) with the trend of nuclear
-  x-ray luminosity with stellar mass and the detection upper limit
-  from Figure 1 of \citealt{MillerGallo+:2014a}. In the top panel we
-  take the accretion power to be $\epsilon \Mdot c^2$, with
-  $\epsilon=5\time 10^{-7}$ chosen to make our accretion powers
-  comparable to the observed x-ray luminosities..}
+  stellar mass for our solutions (points) and the trend of nuclear
+  x-ray luminosity with stellar mass (black line) and the detection
+  upper limit (blue line) from Fig. 1 of
+  \citealt{MillerGallo+:2014a}. In the top panel we take the accretion
+  power to be $\epsilon_1 \Mdot c^2$, with $\epsilon_1=5\times
+  10^{-7}$ chosen to make our accretion powers comparable to the
+  observed x-ray luminosities. In the bottom panel, we take the
+  accretion power to be quadratic in $\Mdot$--$\epsilon_2 \eddr \Mdot
+  c^2$ with $\epsilon2$=$2\times10^{-4}$. For a given galaxy, we take
+  either $\vwO=200$ km/s (green points) or $\vwO=500$ km/s (orange
+  points). We choose the solution for which the relative positions of
+  $\rs$ and $\rIa$ are consistent with the assumed level of heating}
+  %(see text for details).}
 \end{figure}
@@
 
-Figure~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.
+Fig.~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.
 For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.
@@
   $\rsoi$. %%AG-Need to explain this somehow.
-  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Figure 2 of
+  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Fig. 2 of
   \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
@@
   \section{Summary and conclusions}
+  \label{sec:summary}
   We have calculated steady-state models for circumnuclear medium of a
@@
   \begin{enumerate}
-    \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value
-      of $\alpha$ depends on the slope of the stellar density profile
-      ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively).
-
+  \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
+    $\alpha$ depends on the slope of the stellar density profile
+    ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively). One
+    possible solution that the wind mass loss rate (i.e. $\eta$)
+    decreases with $\Mbh$, as would be expected if low mass SMBH
+    preferentially hosted older stellar populations. Another possible
+    explanation is that the effective heating rate of the CNM $v_{\rm w,0}$
+    decreases with decreasing SMBH mass. This could again be due to an
+    older stellar population, since $v_{\rm w,0} \propto \eta^{−1/2}$
+    for heating sources such as SN Ia and millisecond pulsars.
+  \item We compare the $\Mdot$ for each of our solution to the one
+    calculated from the Bondi formula. We find that they generally to
+    a factor of a few. In our model the accretion rate is determined
+    from the gas properties at the stagnation radius, $\rs$, which
+    agrees with the Bondi radius, $\rb$, within a factor of a
+    few. Thus, use of the Bondi formula is a good approximation.
+  \item We compare our solutions for density and temperature to those
+    inferred from Chandra x-ray observations by \citealt{Allen+:2006a}
+    and \citealt{RussellMcNamara+:2013a} for a handful of galaxies in
+    which our sample overlap with theirs. In general, we cannot match
+    the observed gas density slope on large scales. 
   \end{enumerate}

### 2014-09-19 ms.tex
More edits

@@
   increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
-  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cups and core
+  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
   nuclei, respectively.
@@
 assuming that all stars are formed in a burst of star formation at a
-common age of $t_{\star}$ (equation~\ref{eq:eta}).  We adopt
+common age of $t_{\star}$ (equation~[\ref{eq:eta}]).  We adopt
 $\eta=1$ as fiducial, but note that changing $\eta$ is equivalent to
@@
 Source terms $\propto q$ also appear in the momentum and entropy
-equations (equation~\ref{eq:dvdt} and \ref{eq:dsdt}) due to the fact
+equations (equation~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) due to the fact
 that the isotropic mass injection in the rest frame of the SMBH
@@
 and entropy equations for numerical stability. This scheme is
-described in \citealt{Brandenburg:2003a}.  We solve the equations for
+described in \cite{Brandenburg:2003a}.  We solve the equations for
 different choices of $v_{\rm w,0}$ spanning the physically expected
@@
 inwards $\rho \propto r^{n}$ with $n \approx 1$. Note that this is
-shallower than the $-3/2$ for Bondi accretion. However, the power law
-behavior does not extend through all radii. NGC4365 which has a
-prominent break in the gas density profile, near the stagnation
-radius. This is also roughly the location of the break in the stellar
-light profile ($\rb$). The temperature profile is relatively flat at
-large radii, but increases as $\propto 1/r^{k}$ interior to the sphere
-of influence, where $k$ is smaller than 1 (which would be expected for
-virialized gas).  The inwardly directed velocity increases towards the
-hole approaching the expected free-fall rate $v \propto v_{\rm
-  ff}\propto r^{-1/2}$ interior to the sonic point, and then increases
-outwards towards large radii.
+shallower than the $-3/2$ power law for Bondi accretion. However, the
+power law behavior does not extend through all radii, and the gas
+density profile may have breaks mirroring those in the stellar density
+profile. For example, NGC4365 has a prominent break in the gas density
+profile, near the stagnation radius. This coincides with the location
+of the break in the stellar light profile ($\rb$). The temperature
+profile is relatively flat at large radii, but increases as $\propto
+1/r^{k}$ interior to the sphere of influence, where $k$ is smaller
+than 1--the power expected for virialized gas.  The inwardly
+directed velocity increases towards the hole approaching the expected
+free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the
+sonic point, and then increases outwards towards large radii.
 % {\bf BDM: I made this up - in general we need
@@
 relationship from \citealt{MillerGallo+:2014a} and their detection
-upper limits are shown as the blue and black solid lines
+upper limits are the black and blue solid lines
 respectively. The points correspond to the $\dot{M} c^2$ for our
@@
 \includegraphics[width=\columnwidth]{bh_xray.eps}
-\caption{\label{fig:bh_xray} Accretion power plotted as a function of
-  stellar mass for our solutions (points) and the trend of nuclear
+\caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
+  stellar mass for our solutions (points), the trend of nuclear
   x-ray luminosity with stellar mass (black line) and the detection
   upper limit (blue line) from Fig. 1 of
-  \citealt{MillerGallo+:2014a}. In the top panel we take the accretion
-  power to be $\epsilon_1 \Mdot c^2$, with $\epsilon_1=5\times
-  10^{-7}$ chosen to make our accretion powers comparable to the
-  observed x-ray luminosities. In the bottom panel, we take the
-  accretion power to be quadratic in $\Mdot$--$\epsilon_2 \eddr \Mdot
+  \citealt{MillerGallo+:2014a}. In the top panel we take the X-ray
+  luminosity to be $\epsilon_1 \Mdot c^2$, with $\epsilon_1=5\times
+  10^{-7}$ chosen to make our luminosities comparable to those
+  observed. In the bottom panel, we take the
+  accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2 \eddr \Mdot
   c^2$ with $\epsilon2$=$2\times10^{-4}$. For a given galaxy, we take
@@
   $\rs$ and $\rIa$ are consistent with the assumed level of heating}
-  %(see text for details).}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate ($C$) for each of our solutions.
-The cooling rate is calculated using the approximate (solar metallicity) cooling function in Equation~(\ref{eq:cooling}).
-The heating rate is estimated as $q \vw^2/2$.
-The ratio is computed from equation (\ref{eq:cooling}) assuming a stellar mass loss rate parameter $\eta=1$.}
+  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
+    ($C$) for each of our solutions. The cooling rate is calculated
+    using the approximate (solar metallicity) cooling function in
+    Equation~(\ref{eq:cooling}). The heating rate is estimated as $q
+    \vw^2/2$. The ratio is computed from equation (\ref{eq:cooling})
+    assuming a stellar mass loss rate parameter $\eta=1$.}
 \end{figure}
@@
 \input{figures/eta_tab.tex}
-
-\subsection{Conduction}
-\label{sec:conduction}{
 
@@
 
-  \section{Summary and conclusions}
+  \section{Summary}
   \label{sec:summary}
@@
   \item We compare our solutions for density and temperature to those
-    inferred from Chandra x-ray observations by \citealt{Allen+:2006a}
+    inferred from Chandra x-ray observations by \citealt{AllenDunn+:2006a}
     and \citealt{RussellMcNamara+:2013a} for a handful of galaxies in

### 2014-09-19 ms.tex
more edits

@@
 
-\citet{Ho:2009a} calculates the accretion rates onto a sample of early-type galaxies both by using X-ray observations to determine the Bondi accretion rate, and by estimating the contributions from the mass loss of evolved stars.
-Both methods lead him to conclude that the available reservoir of gas is more than sufficient to power low-luminosity AGN, assuming the standard radiative efficiency $\eta \sim 0.1$ for thin disk accretion.
-Indeed, there is now strong observational evidence that the low levels of AGN activity in quiescent galaxies results from accretion proceeding in a radiatively inefficient mode (\citealt{Yuan&Narayan14}), either due to the gravitationally-released energy being advected across the SMBH horizon (e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas inflowing on large scales ultimately reaching the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
-The accretion rates of SMBHs can in principle be estimated directly by assuming Bondi accretion and using {\it Chandra} X-ray observations to estimate the gas temperature and density near the Bondi radius.
-This technique has led to the intriguing result that the Bondi accretion power correlates with the AGN jet power (e.g., \citealt{AllenDunn+:2006a}; \citealt{Russell+13}; \citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy required to inflate the observed cavities within the X-ray emitting gas.
-It is, however, almost never possible to resolve the Bondi radius, thus requiring all such studies to extrapolate the observed gas temperature and density profiles to much smaller radial scales.
+\citet{Ho:2009a} calculates the accretion rates onto a sample of
+early-type galaxies both by using X-ray observations to determine the
+Bondi accretion rate, and by estimating the contributions from the
+mass loss of evolved stars.  Both methods lead him to conclude that
+the available reservoir of gas is more than sufficient to power
+low-luminosity AGN, assuming the standard radiative efficiency $\eta
+\sim 0.1$ for thin disk accretion.  Indeed, there is now strong
+observational evidence that the low levels of AGN activity in
+quiescent galaxies results from accretion proceeding in a radiatively
+inefficient mode (\citealt{Yuan&Narayan14}), either due to the
+gravitationally-released energy being advected across the SMBH horizon
+(e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas
+inflowing on large scales ultimately reaching the SMBH
+(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+
+The accretion rates of SMBHs can in principle be estimated directly by
+assuming Bondi accretion and using {\it Chandra} X-ray observations to
+estimate the gas temperature and density near the Bondi radius.  This
+technique has led to the intriguing result that the Bondi accretion
+power correlates with the AGN jet power (e.g.,
+\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
+\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
+required to inflate the observed cavities within the X-ray emitting
+gas.  It is, however, almost never possible to resolve the Bondi
+radius, thus requiring all such studies to extrapolate the observed
+gas temperature and density profiles to much smaller radial scales.
 %In fact, the temperature profile is assumed to be flat inside of the
@@
 
-Another approach to determine the SMBH accretion rate, which we adopt in this paper, is to directly calculate the density, velocity and temperature profiles of the CNM using a physically motivated hydrodynamic model.
-Mass is injected to the nuclear environment via stellar winds, while energy input results from a number of sources, such as wind shock heating and supernovae (e.g., \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works, however, which focus on modeling the nuclei of individual galaxies, here we systematically analyze the properties of the CNM across a large sample of quiescent galaxies with a range of SMBH masses and other properties (\citealt{WangMerritt:2004a}; hereafter WM04).
-For each galaxy, stellar winds deposit mass and energy across a range of radii calculated directly from the observed {\it stellar} density profile.
+Another approach to determine the SMBH accretion rate, which we adopt
+in this paper, is to directly calculate the density, velocity and
+temperature profiles of the CNM using a physically motivated
+hydrodynamic model.  Mass is injected to the nuclear environment via
+stellar winds, while energy input results from a number of sources,
+such as wind shock heating and supernovae (e.g.,
+\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+Unlike previous works, however, which focus on modeling the nuclei of
+individual galaxies, here we systematically analyze the properties of
+the CNM across a large sample of quiescent galaxies with a range of
+SMBH masses and other properties (\citealt{WangMerritt:2004a};
+hereafter WM04).  For each galaxy, stellar winds deposit mass and
+energy across a range of radii calculated directly from the observed
+{\it stellar} density profile.
 
@@
 The stagnation radius, rather than the Bondi radius, is thus
-ultimately responsible for setting the SMBH accretion rate.  Although
+ultimately responsible for setting the SMBH accretion rate, although
 we find that $\rs$ typically lies within a factor of few of the
-nominal Bondi radius, the difference in the accretion rate can be
-significant.  Furthermore, in some cases we find that no stagnation
-radius exists at all; this formally implies that the entire of ISM of
-the galaxy is feeding the SMBH, potentially resulting in much higher
-accretion rate than would be predicted by simple Bondi accretion.  The
-main goal of our analysis is to provide a framework for interpreting
-the properties of quiescent galactic nuclei given the relatively well
-understood physics of stellar winds and supernova heating.
+nominal Bondi radius.
+% Furthermore, in some cases we find that no stagnation
+% radius exists at all; this formally implies that the entire of ISM of
+% the galaxy is feeding the SMBH, potentially resulting in much higher
+% accretion rate than would be predicted by simple Bondi accretion. 
+The main goal of our analysis is to provide a framework for
+interpreting the properties of quiescent galactic nuclei given the
+relatively well understood physics of stellar winds and supernova
+heating.
 
@@
 \begin{align}
-  \rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}}\frac{v_{w}^{2}}{v_{w,0}^{2}},
+  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}},
   \label{eq:rs_simple}
@@
 
-In the limit of an old stellar population of age $t_{\star} \sim t_{\rm h}$ the Ia rate just becomes $R_{\rm Ia} \sim 2\times 10^{-55} $ g$^{-1}$ s$^{-1}$ (e.g.~\citealt{Scannapieco&Bildsten05}).
-Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$ also depends on the stellar age (equation~[\ref{eq:eta}]).
-Thus, from equation (\ref{eq:vw_eff}) we estimate $v_{w,0} \approx 350\epsilon_{\rm Ia}^{0.5}(\eta/0.1)^{-0.5}$ for an old stellar population.
-For a younger stellar population the increasing rate of Ia SN is compensated by the larger stellar mass loss rate, resulting in a value of $v_{w,0}$ that is roughly independent of stellar age.
-The high value of $v_{w,0}$ implies that Ia SNe represent a potentially dominant source of heating as compared to ms pulsars or main sequence winds.
+In the limit of an old stellar population of age $t_{\star} \sim
+t_{\rm h}$ the Ia rate just becomes $R_{\rm Ia} \sim 2\times 10^{-55}
+$ g$^{-1}$ s$^{-1}$ (e.g.~\citealt{Scannapieco&Bildsten05}).
+Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$
+also depends on the stellar age (equation~[\ref{eq:eta}]).  Thus, from
+equation (\ref{eq:vw_eff}) we estimate $v_{w,0} \approx
+350\epsilon_{\rm Ia}^{0.5}(\eta/0.1)^{-0.5}$ for an old stellar
+population.  For a younger stellar population the increasing rate of
+Ia SN is compensated by the larger stellar mass loss rate, resulting
+in a value of $v_{w,0}$ that is roughly independent of stellar age.
+The high value of $v_{w,0}$ implies that Ia SNe represent a
+potentially dominant source of heating as compared to ms pulsars or
+main sequence winds.
 
@@
 compared to $t_{\rm Ia}$, and the heating is dominated by main
-sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for
-$\Mbh \gsim 10^8 \Msun$, heating from Ias becomes important, as
-$\rs>\rIa$. In this regime, we add the $\vwO$ values from SNe Ias and
-from main sequence winds in quadrature. $\vwO$ from SNe Ia's depends
-on the rate of mass loss ($\eta$), which is in turn a function of
-$t_{\star}$. This dependence is why the effective $\vwO$ increases
-with $\tage$ for large $\Mbh$.
+sequence winds (with $\vwO\simeq 100-150$ km/s), and possibly
+millisecond pulsars ($\vwO\simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$
+km s$^{-1}$).  Optimistically, we would obtain $\vwO\simeq 200$ km/s
+from the combined effects of MSPs and main sequence winds. On the
+other hand, for $\Mbh \gsim 10^8 \Msun$, heating from Ias becomes
+important, as $\rs>\rIa$. In this regime, we add the $\vwO$ values
+from SNe Ias and from main sequence winds in quadrature. $\vwO$ from
+SNe Ia's depends on the rate of mass loss ($\eta$), which is in turn a
+function of $t_{\star}$. This dependence is why the effective $\vwO$
+increases with $\tage$ for large $\Mbh$.
 
@@
       contribute a constant heating rate $100$ km/s. The contribution
-      from SNe Ia is calculated using equation (\ref{eq:vw_sne}). The
+      from SNe Ia is calculated using equation (\ref{eq:vw_sne}), with
+      thermalization efficiency $\epsilon_{\rm Ia}=0.4$. The
       contribution from SNe Ia is only added if the $r_s$
@@
 solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
-each galaxy.  We select $\vwO$=200 km/s if $\rs<\rIa$ for this $\vwO$,
-$\vwO$=500 km/s if $\rs>\rIa$ for this $\vwO$, or exclude it. If
+each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
+heating expected from main sequence the stellar winds and MSPs. If
 $L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
@@
 and densities at at least one point.  As a general rule, we find that
-a wind heating parameter $\vwO=500$ km s$^{-1}$ (close to, but
-somewhat higher than that expected from SNe Ia) gives rough agreement
+a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
 with the observed temperatures.  We now highlight results for specific
@@
   \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
-  \caption{\label{fig:allen_compare} Comparison of the radial profiles of electron number density $n_e$ and temperature $T$ to
-    the measured radial profiles provided in \citet{AllenDunn+:2006a} and \citet{ RussellMcNamara+:2013a}}.
+  \caption{\label{fig:allen_compare} Comparison of the radial profiles
+    (blue lines) of electron number density $n_e$ and temperature $T$
+    to the measured values (black square) in \citet{AllenDunn+:2006a}
+    and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
+    power law extrapolations of our profiles. Note that in going from
+    $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
   %% AG in the future we will have to be carfeful of the mean molecular weight.
@@
 \caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
-  stellar mass for our solutions (points), the trend of nuclear
-  x-ray luminosity with stellar mass (black line) and the detection
-  upper limit (blue line) from Fig. 1 of
-  \citealt{MillerGallo+:2014a}. In the top panel we take the X-ray
-  luminosity to be $\epsilon_1 \Mdot c^2$, with $\epsilon_1=5\times
-  10^{-7}$ chosen to make our luminosities comparable to those
-  observed. In the bottom panel, we take the
-  accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2 \eddr \Mdot
-  c^2$ with $\epsilon2$=$2\times10^{-4}$. For a given galaxy, we take
-  either $\vwO=200$ km/s (green points) or $\vwO=500$ km/s (orange
-  points). We choose the solution for which the relative positions of
-  $\rs$ and $\rIa$ are consistent with the assumed level of heating}
+  stellar mass for our solutions (points), the trend of nuclear x-ray
+  luminosity with stellar mass (black line) and the detection upper
+  limit (blue line) from Fig. 1 of \citealt{MillerGallo+:2014a}. In
+  the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
+  c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
+  luminosities comparable to those observed. In the bottom panel, we
+  take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
+  \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
+  we choose the $\vwO=200$ km/s solution.}
 \end{figure}
@@
   \item We compare our solutions for density and temperature to those
-    inferred from Chandra x-ray observations by \citealt{AllenDunn+:2006a}
-    and \citealt{RussellMcNamara+:2013a} for a handful of galaxies in
+    inferred from Chandra x-ray observations by \citet{AllenDunn+:2006a}
+    and \citet{RussellMcNamara+:2013a} for a handful of galaxies in
     which our sample overlap with theirs. In general, we cannot match

### 2014-09-20 ms.tex
Fixing some equation numbers

@@
 
-This section provides analytic estimates for several quantities of interest, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
-All of our results are derived under the assumption that thermal conductivity can be neglected.
+This section provides analytic estimates for several quantities of
+interest, such as the stagnation radius $\rs$ and the mass accretion
+rate, the detailed derivation of which are given in Appendix
+\ref{app:rs}.  All of our results are derived under the assumption
+that thermal conductivity can be neglected.
 
@@
 
-First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by (equation~[\ref{eq:Tanalytic}])
+First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
 \begin{align}
@@
 \times 10^6\,v_{500}^2 \, \mu  \,\,{\rm K} 
+\label{eq:Tanalytic}
 \end{align}
@@
 
-Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived (equation~[\ref{eq:rstag}]),
+Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived,
 \begin{align}

### 2014-10-13 ms.tex
Brian revision to manuscripts, changes to vw-contour plot

@@
 ultimately responsible for setting the SMBH accretion rate, although
-we find that $\rs$ typically lies within a factor of few of the
+$\rs$ can in many cases lie within a factor of few of the
 nominal Bondi radius.
@@
 interpreting the properties of quiescent galactic nuclei given the
-relatively well understood physics of stellar winds and supernova
+comparatively well understood physics of stellar winds and supernova
 heating.
@@
   &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
-  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr-\rho \dphidr-q v \label{eq:dvdt}\\
+  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr- \rho\frac{GM_{\bf enc}}{r^{2}} -q v \label{eq:dvdt}\\
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
-      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
-  %+\nabla\cdot(\kappa \nabla T)
+      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] +\nabla\cdot(\kappa \nabla T)
 , 
@@
 where $v$, $T$, $p$ and $s$ are the radial velocity, temperature,
-pressure and specific entropy of the gas, respectively.  Here $\partial
-\Phi/\partial r = GM_{\rm enc}/r^{2}$ is the gravitational
-acceleration, where $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
+pressure and specific entropy of the gas, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
 enclosed mass.  We assume an ideal gas equation of state with $p =
-\rho kT/\mu m_p$ with $\mu = 1$  and $\gamma = 5/3$.
+\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$. {\bf BDM: take $\mu = 0.62$ here for fully ionized gas}
 
@@
 common age of $t_{\star}$ (equation~[\ref{eq:eta}]).  We adopt
-$\eta=1$ as fiducial, but note that changing $\eta$ is equivalent to
+$\eta=0.1$ as fiducial {\bf BDM: take $\eta = 0.1$ instead of 1}, but note that changing $\eta$ is equivalent to
 rescaling $\rho$ by the same factor.\footnote{This is {\it not} true
@@
 that the isotropic mass injection in the rest frame of the SMBH
-represents a source of momentum and energy upon being incorporated
-into the mean flow (see also below).  
+represents a source of momentum and energy relative to the mean flow (see also below).  
 %No net momentum is in the winds, but mass is being added which adds a
@@
 
-% The second source term in
-% equation (\ref{eq:dsdt}) accounts for heating transportation by
-% electron conductivity, where the conductivity $\kappa = \kappa_0
-% T^{5/2}$ is assumed to equal the classical ``Spitzer" value
-% (\citealt{Spitzer62}); although even a weak magnetic field could in
-% principle strongly suppress the conductivity perpendicular to the
-% field, the radially-decreasing temperature profiles of interest are
-% susceptible to the magneto-thermal instability (\citealt{Balbus01}),
-% the non-linear evolution of which is believed to result in a
-% radially-directed field structure (\citealt{Parrish&Stone07}).
+The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
 
@@
 of velocities moving with respect to each other a characteristic
-velocity $\sim \sigma$, i.e. even if the wind velocities themselves
+velocity $\sim \sigma$.  This heating is present if the wind velocities themselves
 are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
@@
 for time integration and artificial viscosity terms in the velocity
-and entropy equations for numerical stability. This scheme is
-described in \cite{Brandenburg:2003a}.  We solve the equations for
+and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for
 different choices of $v_{\rm w,0}$ spanning the physically expected
@@
 across much of the parameter space radiative cooling is negligible
-compared to other sources of cooling (e.g., advection).  Radiative
+compared to other sources of cooling (e.g., advection).  Although radiative
 cooling cannot be neglected in some cases (especially if $\vwO$ is low
-or $\eta$ is high), but the onset of a thermal instability when
-radiative cooling dominates precludes obtaining a steady-state
-solution anyways.  Our steady state solutions neglecting radiation can
+or $\eta$ is high), our 1D scheme cannot account for the true multi-phase behavior of local thermal instabilities anyways (e.g.~\citealt{textit}).  Our steady state solutions neglecting radiation can
 nevertheless be used to ascertain over what parameter space cooling
@@
 40$ per cent for all solutions presented in this
-paper. % {\bf BDM: more details...}
+paper. 
+{\bf BDM: more details...}
 
@@
 
-This section provides analytic estimates for several quantities of
-interest, such as the stagnation radius $\rs$ and the mass accretion
-rate, the detailed derivation of which are given in Appendix
-\ref{app:rs}.  All of our results are derived under the assumption
-that thermal conductivity can be neglected.
+This section summarizes analytic estimates of several physical quantities of interest, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
+All of our results are derived under the assumption that thermal conductivity can be neglected.
 
@@
 $n$ (also evaluated at $r = \rs$); and the dimensionless parameter \be
-\chi \equiv \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
+\chi \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
 \left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right), \ee where $v_{500}
@@
 \begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 6
-\times 10^6\,v_{500}^2 \, \mu  \,\,{\rm K} 
+T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
+\times 10^6\,\chi v_{500}^2 \,\,{\rm K} 
 \label{eq:Tanalytic}
@@
 
-Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived,
+Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
 \begin{align}
@@
 \end{align}
-where $\zeta \equiv v_{w,0}/\sigma$, $r_{\rm soi}
-=GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of
+where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
+density profile at $r = r_{\rm s}$,
+
+\begin{align}
+r_{\rm soi} = \frac{GM_{\bullet}}{\sigma^{2}} \approx 14M_{\bullet,8}^{0.6}\,\,{\rm pc}
+\end{align}
+
+is the radius of the SMBH sphere of
 influence (soi), and A and B are constants that depend on the Nuker
@@
 \end{align}
-where we have assumed $n = 1$.  Note that this expression is similar to that
-obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
+where in the numerical estimate we have assume $n = 1$.
+This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
+On the other hand, if wind heating is much weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
+
+Though important across some radii, the importance of conductive heating can be estimated by comparing its magnitude to that of wind heating, viz.~
+\begin{eqnarray}
+\left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0 T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}} \nonumber \\
+&\sim& 0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
+\end{eqnarray}
+where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.
+We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.
 
@@
 where the numerical estimates again assume that $M_{\bullet} \gg M_{\star}$ at the stagnation radius.
-Note that equation (\ref{eq:mdot_analytic}) predicts that $\dot{M}$ should increase with BH mass at fixed $v_{500}$ but that $\dot{M}$ is extremely sensitive to the assumed heating rate $\propto v_{500}$.
-
-Finally, the density at the stagnation radius $\rho(r_{\rm s})$ can be estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
+Equation (\ref{eq:mdot_analytic}) predicts that $\dot{M}$ should increase with SMBH mass at fixed heating $v_{500}$, but decreases rapidly with increased heating.
+
+The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
 \begin{align}
@@
 
-Figure~\ref{fig:profiles} shows three representative profiles of the
-density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
-As expected, the gas density increases towards the SMBH.  For some
-profiles (e.g. NGC1172 and NGC4478) the density $\rho$ follows a power
-law from the stagnation radius (squares in Fig.~\ref{fig:profiles})
-inwards $\rho \propto r^{n}$ with $n \approx 1$. Note that this is
-shallower than the $-3/2$ power law for Bondi accretion. However, the
-power law behavior does not extend through all radii, and the gas
-density profile may have breaks mirroring those in the stellar density
-profile. For example, NGC4365 has a prominent break in the gas density
-profile, near the stagnation radius. This coincides with the location
-of the break in the stellar light profile ($\rb$). The temperature
-profile is relatively flat at large radii, but increases as $\propto
-1/r^{k}$ interior to the sphere of influence, where $k$ is smaller
-than 1--the power expected for virialized gas.  The inwardly
-directed velocity increases towards the hole approaching the expected
-free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the
-sonic point, and then increases outwards towards large radii.
+Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
+As expected, the gas density increases towards the SMBH.
+For some profiles (e.g.
+NGC1172 and NGC4478) the density $\rho$ follows a power law from the stagnation radius (squares in Fig.~\ref{fig:profiles}) inwards $\rho \propto r^{-n}$ with $n \approx 1$.
+Note that this is shallower than the $-3/2$ power law for Bondi accretion.
+However, the power law behavior does not extend through all radii, and the gas density profile may have breaks mirroring those in the stellar density profile.
+For example, NGC4365 has a prominent break in the gas density profile, near the stagnation radius.
+This coincides with the location
+of the break in the stellar light profile ($\rb$). The temperature profile is relatively flat at large radii, but increases as $\propto
+1/r^{k}$ interior to the sphere of influence, where $k$ is smaller than 1--the power expected for virialized gas.  The inwardly
+directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
 % {\bf BDM: I made this up - in general we need
@@
 
-Figure~\ref{fig:stag} (top panel) shows numerical results for the
-stagnation radius $r_{\rm s}$ where the radial velocity goes to zero
-(expressed in ratio to the radius of the SMBH sphere of influence
-$r_{\rm soi}$), with different colors representing different values of
-$v_{w,0}$.  Cusp and core galaxies are marked with square and
-triangles, respectively.  
+Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.
+Cusp and core galaxies are marked with square and triangles, respectively.
 %The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}
@@
 
-Our results show that the location of the stagnation rate and
-resulting accretion rate, is very sensitive to the assumed heating
-rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating
-rate will vary from galaxy to galaxy.. For example, SNe Ia represent a
+Our results show that the location of the stagnation rate and resulting accretion rate, is very sensitive to the assumed heating
+rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating rate will vary from galaxy to galaxy.. For example, SNe Ia represent a
 potentialy important source of heating, but since they are rare they
@@
 
-\subsubsection{Stellar winds} Although most of the mass supplied to
-the CNM by stellar winds occurs during the giant AGB phase, these
-winds represent a negligible heating source compared to the random
-wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is
-much less than the stellar potential $\sigma$.
-
-Though representing a much smaller quantity of mass, main sequence
-winds have much higher velocities and hence contribute a
+\subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.
+
+Main sequence winds, though contributing a much smaller quantity of mass, have much higher velocities and hence contribute a
 disproportionally large share of the kinetic energy of winds.
-\citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim
-100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
-stellar population.  On the other hand, for a very young stellar
-population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
-heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
-s$^{-1}$.  
-%In Appendix C we present a toy model for how $v_{\rm w,0}$
-%varies as a function of stellar age.
-%AG-Appendix C is not written! As this draft will be circulated I
-%don't want references to things which do not exist!
+\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.
+On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.
+In what follows below, we take an effective stellar wind heating rate
+\be
+v_{\rm w,0}^{\star} =  150\,{\rm km\,s^{-1}}
+\ee
+In Appendix \ref{app:windheat} we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age ({\bf BDM: Nick can create}).
 
@@
 the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each
-contributes an average spin-down luminosity $L_{\rm sd}$, then the
+contributes an average spin-down luminosity $\bar{L}_{\rm sd}$, then the
 resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
-  msp}\epsilon$ corresponds to an effective heating rate (equation~
+  msp}\epsilon$ corresponds to an effective heating rate (eq.~
 [\ref{eq:vw_eff}])
-  \begin{align}
-    \vwO=\sqrt{\frac{\epsilon 2 t_h n_{\rm msp} L_{\rm sd}}{\eta}},
-  \end{align}
+
+  \begin{align}
+    v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
+&\approx&  40\epsilon^{1/2}\left(\frac{\bar{L}_{\rm sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \left(\frac{\eta}{0.1}\right)^{-1/2}\,{\rm km\,s^{-1}},
+  \end{align}
+
 where $\epsilon< 1$ is the thermalization efficiency of the wind.
-The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$.
-If we assume an average spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of Fermi pulsars, then we find that $\vwO\simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$ km s$^{-1}$.
-Thus, assuming a high thermalization efficiency $\epsilon \sim 1$, MSP heating can be comparable to main sequence heating.
-However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}, while the binaries giving rise to through accretion MSPs may be disocciated by stellar interactions in the dense nuclear cluster.
+The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we assume in the numerical estimate.
+Using the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate the average spin-down luminosity of millisecond pulsars in the field (excluding those in globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, in which case $v_{\rm w,0}$ is negligibly small even for $\eta = 0.1$ and $\epsilon = 1$.
+
+If we assume a higher spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi pulsars, then we find that $v_{\rm w,0}^{\rm p} \simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$ km s$^{-1}$, in which case MSP heating can be comparable to main sequence wind heating for $\eta = 0.1$, $\epsilon = 1$.
+However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
+Also, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population.
 \subsubsection{Type Ia Supernovae}
@@
 \begin{align}
-    \vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
+    v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
 \end{align}
@@
 In the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.
-The observationally inferred DTD (see Fig.
-1 of \citet{MaozMannucci+:2012a} has the approximate functional form
-\begin{align}
-    \Psi(\tau)=\frac{0.03
-      \left(\tau/10^8\,{\rm yr}\right)^{-1.12}}{10^{10} \Msun},
-  \end{align}
-where $\tau$ is the time of the Ia SN since star formation.
-
-In the limit of an old stellar population of age $t_{\star} \sim
-t_{\rm h}$ the Ia rate just becomes $R_{\rm Ia} \sim 2\times 10^{-55}
-$ g$^{-1}$ s$^{-1}$ (e.g.~\citealt{Scannapieco&Bildsten05}).
-Likewise, as already discussed, the mass loss rate $\eta \sim 0.1-1$
-also depends on the stellar age (equation~[\ref{eq:eta}]).  Thus, from
-equation (\ref{eq:vw_eff}) we estimate $v_{w,0} \approx
-350\epsilon_{\rm Ia}^{0.5}(\eta/0.1)^{-0.5}$ for an old stellar
-population.  For a younger stellar population the increasing rate of
-Ia SN is compensated by the larger stellar mass loss rate, resulting
-in a value of $v_{w,0}$ that is roughly independent of stellar age.
-The high value of $v_{w,0}$ implies that Ia SNe represent a
-potentially dominant source of heating as compared to ms pulsars or
-main sequence winds.
-
-However, SNe can only be approximated as constant source of heating
-throughout space and time if the rate of SNe is rapid compared to the
-inflow time at the radius of interest
+The observationally inferred DTD (Fig.
+1 of \citealt{MaozMannucci+:2012a}) has the approximate functional form
+\begin{align}
+    R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
+\label{eq:DTD}
+  \end{align}
+where $\tau_{\star}$ is the time since star formation (c.f.~\citealt{Scannapieco&Bildsten05}).
+
+Using equations (\ref{eq:vw_sne}), (\ref{eq:DTD}), and (\ref{eq:eta}) we thus estimate that
+\be
+v_{w,0}^{\rm Ia} \approx 250(\epsilon_{\rm Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.07}\,{\rm km \,s^{-1}},
+\ee
+showing that the effective velocity due to SN heating is (coincidentally) a weak function of the stellar age.
+
+The relatively high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent a potentially dominant source of non-AGN heating in the CNM.
+However, SNe can only be approximated as "constant" heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest
 (\citealt{ShcherbakovWong+:2014a}).  To estimate when this
@@
 \begin{align}
-r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx
-&40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc}\sim 43 M_{\bullet,8}^{0.1}\,{\rm pc} 
+r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \sim 38 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc} 
 \label{eq:rIa}
@@
 (equation~[\ref{eq:Msigma}]).
+Between subsequent supernova, stars release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm gas}\sigma^{2}$.
+Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
 
@@
 On the other hand, for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia  represent an important, and possibly dominant, contribution to the overall heating.
-  % Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with
-  % heating mostly coming from main sequence winds. On the other hand,
-  % for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with
-  % the main contribution coming from type Ia SNe. These two regimes are
-  % illustrated in Figure~\ref{fig:vw_eff}.
-  % \end{enumerate}
-
-\subsubsection{AGN Heating}
-
-AGN feedback also represents an additional source of heating.
-In this case, since the rate of feedback is likely proportional to the mass accretion rate $\dot{M}$, which itself is inversely proportional to the heating rate (equation~[\ref{eq:mdot_analytic}]), then, if dominant, the effective heating rate from AGN $v_{\rm w,0}$ may be regulated to a fixed value.
-
-\subsubsection{Combined Heating Rate} The overall heating rate $\vwO$
-has contributions from Type Ia SNes and main sequence winds.  The
-relative contributions will depend on both the age of the stellar
-population, $\tage$, and $\Mbh$.  This is illustrated in
-Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe
-Ia will not contribute to $\vwO$ as the flow time scale is short
-compared to $t_{\rm Ia}$, and the heating is dominated by main
-sequence winds (with $\vwO\simeq 100-150$ km/s), and possibly
-millisecond pulsars ($\vwO\simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$
-km s$^{-1}$).  Optimistically, we would obtain $\vwO\simeq 200$ km/s
-from the combined effects of MSPs and main sequence winds. On the
-other hand, for $\Mbh \gsim 10^8 \Msun$, heating from Ias becomes
-important, as $\rs>\rIa$. In this regime, we add the $\vwO$ values
-from SNe Ias and from main sequence winds in quadrature. $\vwO$ from
-SNe Ia's depends on the rate of mass loss ($\eta$), which is in turn a
-function of $t_{\star}$. This dependence is why the effective $\vwO$
-increases with $\tage$ for large $\Mbh$.
-
-  For very young stellar populations ($\tage \lsim 10^7$ years),
-  $\vwO\simeq 1000$ km/s due to contributions from line driven winds
-  from high mass main sequence stars.
+
+\subsubsection{SMBH Feedback}
+
+Feedback from accretion onto the SMBH also represents a potentially important source of heating which is the most difficult to quantify.
+A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$.
+We assume that the total heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
+If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm out}$ results in an effective wind heating rate of
+\be
+v_w^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm out}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{\beta/2},
+\ee
+where we have used the fact that $\dot{M} \approx \eta M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto M_{\bullet}(r/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$ for radii interior to the outer break radius.
+Thus for $r_{\rm heat} \sim r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim 10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other sources of non-accretion powered heating.
+
+For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm w,0}^{-\beta}$, where in the last proportionality we have used equation (\ref{eq:stag_simple}).
+Hence, when SMBH heating dominates, it may ``self-regulate" itself.
+
+What is a physically motivated value of $r_{\rm heat}$?
+\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half opening angle $\theta_{\rm j} = 0.1$ (similar to those of AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a timescale
+\begin{eqnarray}
+t_{\rm jet} &\sim& 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
+\end{eqnarray}
+Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is given by
+
+\begin{equation}
+\frac{t_{\rm jet}}{r/\sigma} \sim 8\times 10^{-5}\sigma_{200}^{2/3}\epsilon_{\rm j}^{-1/3},
+\end{equation}
+which is notably independent of radius $r$.  Thus we require $\epsilon_{\rm j} \gtrsim 10^{-12}$ for the jet to escape, and if it escapes it is free to travel a long distance.
+
+\subsubsection{Combined Heating Rate}
+
+The total heating rate $\vwO = \sqrt{v_{\rm w,0}^{\star} + v_{\rm w,0}^{\rm Ia} + v_{\rm w,0}^{\rm p} + v_{\rm w,0}^{\bullet}}$ has contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
+Since pulsar heating appears unlikely to contribute appreciably, and since SMBH heating is uncertain, we first focus on heating from stellar winds and supernovae.
+
+Figure~\ref{fig:vweff} shows an estimate of how the combined heating depends on the age of the stellar population $\tage$ and the SMB mass $\Mbh$.
+For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}]) to contribute their full heating rate.
+$v_{\rm w,0}^{\rm Ia} \sim 250$ km s$^{-1}$.
+On the other hand, for lower mass BHs Ia SNe are infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star} \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of interest.\footnote{Although SN Ia will still occur surrounding low mass SMBHs, if they are infrequent interior to the radius where the accretion rate is being set, then they will not affect the flow at most near the SMBH at most epochs.}  For very young stellar populations ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to contributions from line driven winds from high mass main sequence stars.
 
@@
       corresponding to the resulting $\vwO$ is outside
-      $\rIa$.}%describe other cases here.
+      $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on time! among other things}}%describe other cases here.
   \end{figure}
@@
   \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
-  we choose the $\vwO=200$ km/s solution.}
+  we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
 \end{figure}
@@
 
+\subsection{Demographics of SMBHs}
+
+Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
+\begin{eqnarray}
+  t_{\rm growth}/t_{\rm h} \approx 
+  \begin{cases}
+    6.3 M_{\bullet,8}^{-0.9}
+    v_{500}^{4}  \eta \Msun \, \pyear& \text{core} \\
+    2.9 \Mbheight^{-0.4}
+    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
+  \end{cases}
+  \label{eq:tgrow_analytic}
+\end{eqnarray}
+which we have normalized in terms of the Hubble time.
+
+{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{\rm w,0}^{\bullet}$ and $\sigma = v_{\rm w,0}^{\star}$.
+}
+
 \subsection{Cooling}
 \label{sec:cooling}
-Our models neglect radiative cooling, an assumption we now check.  At
-high temperatures $T\gsim 2\times 10^7$ K gas cools through free-free
-emission, while at lower temperatures it cools predominantly through
-metal lines.  To assess the importance of radiative cooling in our
-solutions we compare the heating rate $H=q \vw^2/2$ to the nominal
-cooling rate
-\begin{align}
-  c =\Lambda(T) n^2,
+Our models neglect radiative cooling, an assumption we now check.
+At high temperatures $T\gsim 2\times 10^7$ K gas cools through free-free emission, while at lower temperatures it cools predominantly through metal lines.
+To assess the importance of radiative cooling in our solutions we compare the heating rate $H=q \vw^2/2$ to the nominal cooling rate
+\begin{align}
+  \dot{q}_{\rm cool} =\Lambda(T) n^2,
 \label{eq:cooling}
 \end{align}
-where $n = \rho/\mu m_p$ and we approximate the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (Fig.
-34.1 in \cite{Draine:2011a}).
-Note that because heating is proportional to density, while cooling is proportional to density squared, this implies that the ratio $H/C$ depends on the rate of stellar wind mass loss $\eta$, which we assume to be $\eta = 1$ below.
-
-Fig.~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.
+where $n = \rho/\mu m_p$ and we approximate the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (Fig. 34.1 in \cite{Draine:2011a}):
+\begin{align}
+\Lambda(T)\simeq
+  \begin{cases}
+    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}&, T \gsim 2 \times 10^7 \text{K} \\
+    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}&, T \lsim 2 \times 10^7 \text{K}     
+  \end{cases}
+  \label{eq:cooling2}
+\end{align}
+
+If cooling becomes important in the flow, it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes (e.g.~\citealt{Fabian&Peterson06}).
+In practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citealt{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\be
+t_{\rm cool} \equiv \frac{3n kT/2}{\dot{q}_{\rm cool}}
+\ee 
+is locally shorter than the approximately 10 times the free-fall timescale $t_{\rm ff}$.
+
+Using equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), (\ref{eq:rhors}), (\ref{eq:cooling}), (\ref{eq:cooling2}), we can estimate the ratio of the cooling timescale to the free-fall time $\sim r/\sigma$ at the stagnation radius
+\begin{align}
+  \left.\frac{t_{\rm cool}}{t_{\rm ff}}\right|_{r_{\rm s}}\simeq
+  \begin{cases}
+    12 \Mbheight^{-0.66} \eta^{-1}(\chi v_{500})^{6.4}, & \text{core}\\
+    6  \Mbheight^{-0.24} \eta^{-1}(\chi v_{500})^{4.4} ,   & \text{cusp}
+  \end{cases}
+  \label{eq:coolingratio}
+\end{align}
+We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if $\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
+
+Fig.~\ref{fig:cooling} shows $t_{\rm cool}/t_{\rm ff}$ as a function of radius for all of our solutions {\bf BDM: change plots}, with different colors denoting different values of $v_{w,0}$.
 For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.
@@
 
-  \section{Dependence of q on stellar age}
+  \section{Analytic model for dependence of wind mass loss rate on stellar age}
   \label{app:eta}
@@
 
+\section{Analytic model for dependence of wind heating $v_{\rm w,0}^{\star}$ on stellar age}
+\label{app:windheat}
+{\bf BDM: Nick add}
   \footnotesize{

### 2014-10-27 ms.tex
Fixing some issues w/ the citations, and re-adding Nick's appendix.

@@
 
-Our sample includes 61 early-type galaxies from \citetalias{WangMerritt:2004a}, as represent a subset of a larger sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.
-We focus on elliptical galaxies because we are interested in isolating SMBHs fed by the steady mass loss from the relatively old stellar population, instead of fresh gas flowing into the sphere of influence from larger scales.
+Our sample includes 61 early-type galaxies from
+\citetalias{WangMerritt:2004a}, as represent a subset of a larger
+sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
+focus on elliptical galaxies because we are interested in isolating
+SMBHs fed by the steady mass loss from the relatively old stellar
+population, instead of fresh gas flowing into the sphere of influence
+from larger scales.
 
@@
 across much of the parameter space radiative cooling is negligible
-compared to other sources of cooling (e.g., advection).  Although radiative
-cooling cannot be neglected in some cases (especially if $\vwO$ is low
-or $\eta$ is high), our 1D scheme cannot account for the true multi-phase behavior of local thermal instabilities anyways (e.g.~\citealt{textit}).  Our steady state solutions neglecting radiation can
-nevertheless be used to ascertain over what parameter space cooling
-instabilities are likely to develop ($\S\ref{sec:cooling}$).
+compared to other sources of cooling (e.g., advection).  Although
+radiative cooling cannot be neglected in some cases (especially if
+$\vwO$ is low or $\eta$ is high), our 1D scheme cannot account for the
+true multi-phase behavior of local thermal instabilities anyways
+(e.g.~\citealt{McCourt+12}).  Our steady state solutions neglecting
+radiation can nevertheless be used to ascertain over what parameter
+space cooling instabilities are likely to develop
+($\S\ref{sec:cooling}$).
 %Dependence of the heating to cooling ratio has a far steeper
@@
 
-Though important across some radii, the importance of conductive heating can be estimated by comparing its magnitude to that of wind heating, viz.~
-\begin{eqnarray}
-\left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0 T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}} \nonumber \\
-&\sim& 0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
+The importance of conductive heating can be estimated by comparing its
+magnitude to that of wind heating, viz.~
+\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
+w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
+T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
+\nonumber \\ &\sim&
+0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
+soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
 \end{eqnarray}
+
 where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.
@@
 $v_{\rm w,0}^{\rm Ia} \sim 250$ km s$^{-1}$.
-On the other hand, for lower mass BHs Ia SNe are infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star} \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of interest.\footnote{Although SN Ia will still occur surrounding low mass SMBHs, if they are infrequent interior to the radius where the accretion rate is being set, then they will not affect the flow at most near the SMBH at most epochs.}  For very young stellar populations ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to contributions from line driven winds from high mass main sequence stars.
+On the other hand, for lower mass BHs Ia SNe are infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star} \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of interest.\footnote{Although SN Ia will still occur surrounding low mass SMBHs, if they are infrequent interior to the radius where the accretion rate is being set, then they will not affect the flow near the SMBH at most epochs.}  For very young stellar populations ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to contributions from line driven winds from high mass main sequence stars.
 
@@
 
-If cooling becomes important in the flow, it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes (e.g.~\citealt{Fabian&Peterson06}).
-In practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+If cooling becomes important in the flow, it may lead to thermal
+instabilities.  There are two kinds of ``instabilities", global and
+local.  The global instability is simply that, if cooling becomes very
+rapid, the gas loses thermal pressure and starts to inflow faster,
+i.e. the entire CNM accretes (e.g. ).  In
+practice this should could manifest as a large increase in the
+stagnation radius, due an effective {\it decrease} in the effective
+heating rate.  This global ``instability" is not a true instability
+insofar as the gas does not necessarily clump locally into low-T
+clouds.
 
@@
 \label{app:windheat}
-{\bf BDM: Nick add}
+If we assume that a stellar population forms impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any future time $t$ is given by
+\begin{equation}
+f(t) =\frac{ \int_{m_0}^{m_{\rm max}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
+\end{equation}
+where 
+\begin{equation}
+m_{\rm max}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
+\end{equation}
+For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
+\begin{equation}
+f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
+\end{equation}
+{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
+If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
+\begin{equation}
+q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm max}(t)) m_{\rm max}(t) \frac{df}{dt},
+\end{equation}
+where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm max}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
+\begin{equation}
+q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
+\end{equation}
+This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
+Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
+Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
+Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{NickPlot.eps}
+\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
+The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
+Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
+\end{figure}
+
+In Fig.
+\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
+We parametrize the wind velocity as
+\begin{equation}
+\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
+\end{equation}
+The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
+We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
+Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
   \footnotesize{

### 2014-11-03 ms.tex
some comments

@@
 \label{sec:sample}
-
+%AG:It is unclear whether if/how the Nuker profile will show up in
+%this parametrized study.
 Our sample includes 61 early-type galaxies from
@@
 
-The SMBH accretion rate is simply given by the integrated mass loss rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
+The SMBH accretion rate is simply given by the integrated mass loss
+rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
+%AG: Should we have separate cores and cusps? Or just write a general
+%relationship in terms of gamma?
 \begin{eqnarray}
@@
     1.6 \times 10^{-3} M_{\bullet,8}^{1.9}
-    v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
-    3.4 \times 10^{-3} \Mbheight^{1.4}
-    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
+    \chi^{-4} v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
+    3.4 \times 10^{-3} \Mbheight^{1.4} \chi^{-2}
+    \chi^{-2} v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
 \end{eqnarray}
-where the numerical estimates again assume that $M_{\bullet} \gg M_{\star}$ at the stagnation radius.
-Equation (\ref{eq:mdot_analytic}) predicts that $\dot{M}$ should increase with SMBH mass at fixed heating $v_{500}$, but decreases rapidly with increased heating.
 
@@
 $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 200, 500 and 1000 km s$^{-1}$.
+values of $\vwO =$ 150, 300 and 600 km s$^{-1}$.
 

### 2014-11-11 ms.tex
Changing appendix around.

@@
 
-\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
+\newcommand{\dxdy}[2]{\frac{d #1}{d #2} }
 \newcommand{\ddr}[1]{\dxdy{#1}{r}}
@@
   &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
-  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr- \rho\frac{GM_{\bf enc}}{r^{2}} -q v \label{eq:dvdt}\\
+  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial
+      v}{\partial r}\right) =-\frac{\partial p}{\partial r}- \rho\frac{GM_{\bf enc}}{r^{2}} -q v \label{eq:dvdt}\\
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
@@
 %AG: Should we have separate cores and cusps? Or just write a general
-%relationship in terms of gamma?
+
 \begin{eqnarray}
@@
   \begin{cases}
-    1.6 \times 10^{-3} M_{\bullet,8}^{1.9}
-    \chi^{-4} v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
-    3.4 \times 10^{-3} \Mbheight^{1.4} \chi^{-2}
-    \chi^{-2} v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
+    1.5 \times 10^{-3} M_{\bullet,8}^{1.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
+    2.6 \times 10^{-3} \Mbheight^{1.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
   \label{eq:mdot_analytic}
+\end{eqnarray}
+
+The Eddington ratio $\eddr$ is given by
+
+\begin{eqnarray}
+\eddr&\approx&
+  \begin{cases}
+    6.6 \times 10^{-4} M_{\bullet,8}^{0.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
+    1.2 \times 10^{-3} \Mbheight^{0.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
+  \end{cases}
+  \label{eq:eddr_analytic}
 \end{eqnarray}
@@
 $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 150, 300 and 600 km s$^{-1}$.
+values of $\vwO =$ 150, 300 and 600 km s$^{-1}$, and for both core
+($\gamma$=0.1) and cusp galaxies ($\gamma$=0.8).
 
@@
 galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
-$\vwO=1000$ km s$^{-1}$, core galaxies have a smaller accretion rate
-for a given SMBH mass.
+$\vwO=600$ km s$^{-1}$, core galaxies have a smaller accretion rate
+for a given SMBH mass. On the other hand, if  $\rs/\rsoi>1$ (as would
+be expected for small $\vwO$), core galaxies would have a larger
+accretion rate. Thus, for $\vwO=150$ km/s, core galaxies have a large
+accretion rate for a given $\Mbh$.  
 %% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
@@
   \includegraphics[width=\columnwidth]{mdot_mass.eps}
-  \caption{\label{fig:mdot_mass}  Accretion rate $\dot{M}$ in units of the Eddington rate $\dot{M}_{\rm edd}$ as a function of SMBH mass for each galaxy in our sample, calculated for different values of the wind heating parameter $\vwO =$ 200 km s$^{-1}$ ({\it green}), 500 km s$^{-1}$ ({\it orange}), and 1000 km s$^{-1}$ ({\it blue}).
-Squares correspond to cusp galaxies, while triangles correspond to cores.}
+  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}$ in units of
+    the Eddington rate $\dot{M}_{\rm edd}$ as a function of SMBH mass
+    for each galaxy in our sample, calculated for different values of
+    the wind heating parameter $\vwO =$ 150 km s$^{-1}$ ({\it green}),
+    600 km s$^{-1}$ ({\it orange}), and 1000 km s$^{-1}$ ({\it blue}).
+    Squares correspond to cusp galaxies ($\gamma=0.8$), while
+    triangles correspond to cores ($\gamma$=0.1). The curves correspond
+    to the analytic results for $\eddr$ from equation
+    (\ref{eq:eddr_analytic}) for cusps (solid lines) and cores (dashed
+    lines).  }
 \end{figure}
@@
   \begin{enumerate}
+  %Younger population=>higher accretion rate; generally higher eta and
+  %lower vw except for very young stellar populations.
   \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
@@
     decreases with $\Mbh$, as would be expected if low mass SMBH
-    preferentially hosted older stellar populations. Another possible
+    preferentially hosted younger stellar populations. Another possible
     explanation is that the effective heating rate of the CNM $v_{\rm w,0}$
@@
 
-In Fig.
-\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
-We parametrize the wind velocity as
+In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
+function of time, for three different stellar density profiles $\Gamma
+= \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
+influence radius $r
+_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).  We parametrize the wind velocity as 
 \begin{equation}

### 2014-11-11 eta.tex
Indicate master file in appendices for easier compilation

--- 2014-11-03 ms.tex
@@
-\documentclass[usenatbib,fleqn]{mn2e}
-\usepackage{amsmath,amssymb}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\epstopdfsetup{outdir=./figures/}
-\graphicspath{{./figures/}}
-\usepackage{url}
-\usepackage{aas_macros}
-\usepackage{astro}
-% \usepackage{natbib}
+We now describe the rate of start formation $q$ varies with the age of the stellar population.
 
-% \renewcommand{\l}{\left}
-% \renewcommand{\r}{\right}
-
-\newcommand{\Mdot}{\dot{M}}
-\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
-\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
-\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}
-
-\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$<$}}}
-\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$>$}}}
-\newcommand{\rs}{r_s}
-\newcommand{\rb}{r_b}
-\newcommand{\rcirc}{r_{\rm circ}}
-\newcommand{\rss}{r_{\rm ss}}
-\newcommand{\lrs}{\l_{\rs}}
-\newcommand{\lambdars}{\lambda_{\rs}}
-\newcommand{\vw}{v_w}
-
-\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
-\newcommand{\ddr}[1]{\dxdy{#1}{r}}
-\newcommand{\drhodt}{\dxdy{\rho}{t}}
-\newcommand{\dpdr}{\dxdy{p}{r}}
-\newcommand{\dvdr}{\dxdy{v}{r}}
-\newcommand{\dsdr}{\dxdy{s}{r}}
-\newcommand{\dphidr}{\dxdy{\Phi}{r}}
-
-\newcommand{\ke}{\frac{v^2}{2}}
-\newcommand{\kew}{\frac{v_w^2}{2}}
-
-\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
-\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
-\newcommand{\cs}{\frac{p}{\rho}}
-\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
-
-\newcommand{\kb}{k_{\rm b}}
-\renewcommand{\mp}{m_{\rm p}}
-\newcommand{\pc}{\rm pc}
-
-\newcommand{\Menc}{M_{\rm enc}}
-\newcommand{\rhostar}{\rho_*}
-\newcommand{\Mstar}{M_{\star}}
-\newcommand{\Mseight}{M_{\star,8}}
-\newcommand{\Mbh}[1][]{M_{\bullet#1}}
-\newcommand{\Mbheight}{M_{\bullet,8}}
-\newcommand{\MbheightExp}{\frac{\Mbh}{10^8 \Msun}}
-
-\newcommand{\phirs}{\frac{G \Menc}{\rs}}
-\newcommand{\soi}{\rm soi}
-\newcommand{\rsoi}{r_{\soi}}
-\newcommand{\ff}{\rm ff}
-\newcommand{\tff}{t_{\ff}}
-\newcommand{\rIa}{r_{\rm Ia}}
-\newcommand{\EIa}{E_{\rm Ia}}
-\newcommand{\RateIa}{R_{\rm Ia}}
-\newcommand{\sigsoi}{\sigma_{\soi}}
-
-\newcommand{\vwO}{v_{w,0}}
-\newcommand{\kewO}{\frac{\vwO^2}{2}}
-\newcommand{\x}{\frac{r_s}{\rsoi}}
-\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
-\newcommand{\vwOFH}{v_{w,0,500}}
-\newcommand{\vwOFHexp}{\frac{\vwO}{500 \, {\rm km/s}}}
-
-\newcommand{\pyear}{{\rm yr}^{-1}}
-\newcommand{\tage}{t_{\star}}
-\renewcommand{\th}{t_h}
-
-\topmargin -1 cm
-\defcitealias{WangMerritt:2004a}{WM04}
-
-\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
-  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
-
-\begin{document}
-\title{Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes}
-\maketitle
-
-\begin{abstract}
-  We calculate the steady-state hydrodynamic profiles of hot gas in
-  the nuclei of a sample of early-type quiescent galaxies.  We assume
-  that mass is supplied to the circumnuclear medium (CNM) entirely by
-  stellar winds according to the radial stellar profiles for each
-  galaxy, while the gas is heated by a combination of shocked stellar
-  winds and supernovae.  Our analytic and numerical results are used
-  to estimate the accretion rates onto the central supermassive black
-  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
-  heating efficiency, the latter of which is related schematically to
-  the age of the stellar population, the frequency of supernovae, and
-  the efficacy of accretion feedback processes.  For a fixed heating
-  efficiency, we find that the SMBH accretion Eddington factor
-  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
-  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
-  nuclei, respectively.
-  % However, considering the potentially lower heating efficiency of low
-  % mass SMBHs (due to a younger stellar population and the rareity of
-  % supernovae within the stagnation radius) and their resulting higher
-  % susceptibility to cooling instability, we find a flatter
-  % relationship $\alpha \approx 0$. 
-  Our results are used to check previous estimates of the SMBH
-  accretion rate assuming Bondi accretion and extrapolating the X-ray
-  measured density and temperature to the unresolved Bondi radius.  We
-  also discuss the implications of our results for the diversity of
-  CNM environments encountered by the jetted outflows from tidal
-  disruption events, and for the use of an assumed
-  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
-  fraction of SMBHs in low mass galaxies.
-\end{abstract}
-
-\begin{keywords}
-  black hole physics --  galaxies: active
-\end{keywords}
-
-\section{Introduction}
-\label{sec:introduction}
-
-%% Maybe active galaxies constitute 10% need reference here?
-Supermassive black holes (SMBHs) lurk in the centers of most, if not
-all nearby galaxies (see reviews by,
-e.g. \citealt{KormendyRichstone:1995a};
-\citealt{FerrareseFord:2005a}). However, only a few percent of these
-manifest themselves as luminous Active Galactic Nuclei (AGN).  Nearly
-quiescent SMBHs, such as those hosting low luminosity AGN, constitute
-a silent majority (e.g.~\citealt{Ho:2009a}).
-
-In order to understand why most SMBHs appear to be inactive, it is
-necessary to understand their gaseous environments.  Hot gas near the
-SMBH sphere of influence (the `circumnuclear medium' or CNM) controls
-the central mass accretion rate $\dot{M}$.  Better knowledge of how
-$\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
-galactic nucleus is necessary to understand the co-evolution of SMBHs
-and their host galaxies with cosmic time.  SMBH growth in the low
-redshift universe, for instance, appears to be dominated by low mass
-black holes (e.g.~\citealt{Heckman+04}).  Although this is often
-attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}),
-the physical processes involved may be distinct from those operating
-at higher SMBH masses and accretion rates in quasars.
-
-The accretion rates of low mass SMBHs and their resulting nuclear
-X-ray luminosities $L_X$ also have implications for observational
-constraints on their occupation fraction in low mass galaxies and the
-possible existence of intermediate mass black holes.
-\citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and
-$L_X$ from a sample of relatively high mass galaxies
-(\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass
-galaxies, to infer tentative evidence for an occupation fraction less
-than unity.  However, this method relies on extrapolating a power-law
-fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the
-instrumental detection threshold.  The conclusions of
-\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
-the $L_X$-$\Mbh$ relationship at small $\Mbh$.
-% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
-
-The density profile of the CNM also influences the emission from
-stellar tidal disruption events (TDEs), such as the high energy
-transient {\it Swift} J1644+57 (\citealt{Levan+11};
-\citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
-This event was powered by a transient relativistic jet, which produced
-synchrotron radio emission as the jet material was decelerated by
-shock interaction with the CNM of the previously quiescent SMBH
-(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of {\it Swift} J1644+57 showed that the CNM density was
-significantly lower than that measured surrounding Sgr A$^{\star}$
-(\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
-injected into a denser CNM would be decelerated more rapidly,
-producing substantially different radio emission than in {\it Swift}
-J1644+57.  Variations in the properties of the CNM could thus in
-principle help explain why most TDEs appear to be radio quiet
-(e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).
-
-Gas that forms the CNM of a SMBH may originate from several sources
-(\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved)
-stars; (2) star-star collisions; (3) the unbound debris from TDEs.
-Stellar wind mass loss is probably the dominant source in most cases
-insofar as collisions are relevant only in very dense stellar
-environments for young stellar populations (\citealt{Rubin&Loeb11}),
-while TDEs are estimated to provide a subdominant contribution to the
-time-averaged accretion rate of quiescent SMBHs
-(\citealt{MacLeod+13}).
-
-\citet{Ho:2009a} calculates the accretion rates onto a sample of
-early-type galaxies both by using X-ray observations to determine the
-Bondi accretion rate, and by estimating the contributions from the
-mass loss of evolved stars.  Both methods lead him to conclude that
-the available reservoir of gas is more than sufficient to power
-low-luminosity AGN, assuming the standard radiative efficiency $\eta
-\sim 0.1$ for thin disk accretion.  Indeed, there is now strong
-observational evidence that the low levels of AGN activity in
-quiescent galaxies results from accretion proceeding in a radiatively
-inefficient mode (\citealt{Yuan&Narayan14}), either due to the
-gravitationally-released energy being advected across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas
-inflowing on large scales ultimately reaching the SMBH
-(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
-The accretion rates of SMBHs can in principle be estimated directly by
-assuming Bondi accretion and using {\it Chandra} X-ray observations to
-estimate the gas temperature and density near the Bondi radius.  This
-technique has led to the intriguing result that the Bondi accretion
-power correlates with the AGN jet power (e.g.,
-\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-required to inflate the observed cavities within the X-ray emitting
-gas.  It is, however, almost never possible to resolve the Bondi
-radius, thus requiring all such studies to extrapolate the observed
-gas temperature and density profiles to much smaller radial scales.
-%In fact, the temperature profile is assumed to be flat inside of the
-%Bondi radius.  In reality, the cusp in the velocity dispersion near
-%the SMBH, should cause a cusp in the gas temperature profile (assuming
-%the kinetic energy of stellar winds is efficiently thermalized in
-%shocks).
-%% AG-give sense of scale.
-
-Another approach to determine the SMBH accretion rate, which we adopt
-in this paper, is to directly calculate the density, velocity and
-temperature profiles of the CNM using a physically motivated
-hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from a number of sources,
-such as wind shock heating and supernovae (e.g.,
-\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works, however, which focus on modeling the nuclei of
-individual galaxies, here we systematically analyze the properties of
-the CNM across a large sample of quiescent galaxies with a range of
-SMBH masses and other properties (\citealt{WangMerritt:2004a};
-hereafter WM04).  For each galaxy, stellar winds deposit mass and
-energy across a range of radii calculated directly from the observed
-{\it stellar} density profile.
-
-The one-dimensional steady state flow of gas is usually characterized
-by an inflow-outflow structure, with a critical radius known as the
-``stagnation radius" $\rs$ where the radial velocity goes to zero.
-Mass loss from stars interior to the stagnation radius is accreted,
-while that outside $\rs$ is unbound in an outflow from the nucleus.
-The stagnation radius, rather than the Bondi radius, is thus
-ultimately responsible for setting the SMBH accretion rate, although
-$\rs$ can in many cases lie within a factor of few of the
-nominal Bondi radius.
-% Furthermore, in some cases we find that no stagnation
-% radius exists at all; this formally implies that the entire of ISM of
-% the galaxy is feeding the SMBH, potentially resulting in much higher
-% accretion rate than would be predicted by simple Bondi accretion. 
-The main goal of our analysis is to provide a framework for
-interpreting the properties of quiescent galactic nuclei given the
-comparatively well understood physics of stellar winds and supernova
-heating.
-
-This paper is organized as followed.  In $\S\ref{sec:model}$ we
-describe our model, including the sample of galaxies used in our
-analysis ($\S\ref{sec:sample}$) and our numerical procedure for
-calculating the steady-state hydrodynamic profile of the CNM
-($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
-results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
-results, including a comparison of our gas profiles to those inferred
-from {\it Chandra} observations and to the measured $L_X-\Mbh$
-relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
-$\S\ref{sec:summary}$ we summarize our results.
-\section{Model}
-\label{sec:model}
-
-\subsection{Galaxy Sample}
-
-\label{sec:sample}
-%AG:It is unclear whether if/how the Nuker profile will show up in
-%this parametrized study.
-Our sample includes 61 early-type galaxies from
-\citetalias{WangMerritt:2004a}, as represent a subset of a larger
-sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
-focus on elliptical galaxies because we are interested in isolating
-SMBHs fed by the steady mass loss from the relatively old stellar
-population, instead of fresh gas flowing into the sphere of influence
-from larger scales.
-
-The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
-\begin{equation}
-  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
-\end{equation}
-The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
-
-Given $I(\xi)$ we follow the procedure outlined by
-\citetalias{WangMerritt:2004a} to compute the spherically-symmetric
-stellar density profile $\rhostar(r)$ and stellar mass profile
-$M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
-our model.  For reference, note that stellar density $\rhostar\sim
-r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
-\gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
-$\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
-thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
-r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
-SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
-%%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
-%%calculated from an outdated M-sigma. It would be bizarre to use 2
-%%different relations.
-
-% AG:Is there a systematic dependence of beta on galaxy type$.
-
-%% AG--some discussion of alternate parameterizations.  My intuition
-%% is that for our purposes the parameterization should not
-%% matter. But some discussion of alternate possibilities could
-%% prevent Alistar Graham from yelling at us.
-
-\subsection{Hydrodynamic Equations}
-\label{sec:hydro}
-
-Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the gas density profile $\rho$ of the CNM for each galaxy within our sample by solving the equations of one-dimensional (spherically symmetric) time-dependent hydrodynamics,
-\begin{align}
-  &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
-  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial v}{\partial r}\right) =-\dpdr- \rho\frac{GM_{\bf enc}}{r^{2}} -q v \label{eq:dvdt}\\
-  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
-      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] +\nabla\cdot(\kappa \nabla T)
-, 
-\label{eq:dsdt}
-\end{align}
-where $v$, $T$, $p$ and $s$ are the radial velocity, temperature,
-pressure and specific entropy of the gas, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
-enclosed mass.  We assume an ideal gas equation of state with $p =
-\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$. {\bf BDM: take $\mu = 0.62$ here for fully ionized gas}
-
-The source term in the continuity equation (equation~\ref{eq:drhodt}),
-%Should equations be referenced as equation of equation
-\begin{align}
-  q=\frac{\eta \rhostar}{\th},
-\label{eq:q}
-\end{align}
-represents mass input from stellar winds, which we parameterize in
-terms of the fraction $\eta$ of the stellar density $\rhostar$ being
-recycled into gas on the Hubble time $\th = 10^{10}$ years (see, e.g.,
-\citealt{Ciotti+91}).  In Appendix \ref{app:eta} we estimate that
-$\eta \approx 0.11(t_{\star}/t_{\rm h})^{-1.26}$ for a Salpeter IMF,
-assuming that all stars are formed in a burst of star formation at a
-common age of $t_{\star}$ (equation~[\ref{eq:eta}]).  We adopt
-$\eta=0.1$ as fiducial {\bf BDM: take $\eta = 0.1$ instead of 1}, but note that changing $\eta$ is equivalent to
-rescaling $\rho$ by the same factor.\footnote{This is {\it not} true
-  if cooling is included, since the cooling rate is proportional to
-  density {\it squared}.}
-
-Source terms $\propto q$ also appear in the momentum and entropy
-equations (equation~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) due to the fact
-that the isotropic mass injection in the rest frame of the SMBH
-represents a source of momentum and energy relative to the mean flow (see also below).  
-%No net momentum is in the winds, but mass is being added which adds a
-%term in the velocity equation...
-
-The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
-
-Following \citet{ShcherbakovWong+:2014a}, the term in the entropy
-equation $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ accounts for external
-heating sources.  Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the
-velocity dispersion of the stars, thus accounting for the fact that at
-a minimum the gas experiences shock heating between the stellar winds
-of velocities moving with respect to each other a characteristic
-velocity $\sim \sigma$.  This heating is present if the wind velocities themselves
-are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
-The term $v_{w,0}^{2}$ parameterizes additional sources of heating,
-such as main sequence winds, millisecond pulsars, supernovae, etc.  As
-discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is
-uncertain and will in general depend on the SMBH mass and the age of
-the stellar population.
-
-Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) are solved using a sixth
-order finite difference scheme with a third order Runge-Kutta scheme
-for time integration and artificial viscosity terms in the velocity
-and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for
-different choices of $v_{\rm w,0}$ spanning the physically expected
-range.  Although we are most interested in the steady-state CNM
-structure, the time-dependent equations are solved to avoid numerical
-issues that arise near the critical sonic points, of which there are
-up to two because of the supersonic inflow on small radial scales and
-a possible supersonic outflow on large scales.
-
-We do not include radiative cooling in the entropy equation because
-across much of the parameter space radiative cooling is negligible
-compared to other sources of cooling (e.g., advection).  Although
-radiative cooling cannot be neglected in some cases (especially if
-$\vwO$ is low or $\eta$ is high), our 1D scheme cannot account for the
-true multi-phase behavior of local thermal instabilities anyways
-(e.g.~\citealt{McCourt+12}).  Our steady state solutions neglecting
-radiation can nevertheless be used to ascertain over what parameter
-space cooling instabilities are likely to develop
-($\S\ref{sec:cooling}$).
-%Dependence of the heating to cooling ratio has a far steeper
-%dependence on vwO than on eta...
-
-The accuracy of our numerical solutions is assessed by checking the
-level of conservation of mass across the grid, as well as the integral
-constraint on the energy.  Mass and energy are conserved to $\lesssim
-40$ per cent for all solutions presented in this
-paper. 
-{\bf BDM: more details...}
-
-\section{Results}
-
-We begin by describing a number of useful analytic results before describing our numerical solutions.
-
-\label{sec:results}
-\subsection{Analytics: Flow properties at $\rs$}
-
-This section summarizes analytic estimates of several physical quantities of interest, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
-All of our results are derived under the assumption that thermal conductivity can be neglected.
-
-When possible our results are expressed in terms of the wind heating
-parameter $v_{\rm w,0}$; the power-law slope of the density profile
-$n$ (also evaluated at $r = \rs$); and the dimensionless parameter \be
-\chi \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
-\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right), \ee where $v_{500}
-\equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv
-M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the
-$M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09}) \be
-M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
-      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
-\label{eq:Msigma}
-\ee
-Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.
-
-First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
-\begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
-\times 10^6\,\chi v_{500}^2 \,\,{\rm K} 
-\label{eq:Tanalytic}
-\end{align}
-%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}
-
-Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
-\begin{align}
-  \x=\frac{1}{\zeta^2 n}\left[
-    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
-  \label{eq:stag_analytic}
-\end{align}
-where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
-density profile at $r = r_{\rm s}$,
-
-\begin{align}
-r_{\rm soi} = \frac{GM_{\bullet}}{\sigma^{2}} \approx 14M_{\bullet,8}^{0.6}\,\,{\rm pc}
-\end{align}
-
-is the radius of the SMBH sphere of
-influence (soi), and A and B are constants that depend on the Nuker
-parameter $\Gamma$ and the adiabatic index of the gas.
-
-If the SMBH dominates the potential at the stagnation radius
-($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg 200 M_{\bullet,8}^{0.2}$ km
-s$^{-1}$) then the relationship between $\rs$ and $v_{w}$ is
-simplified greatly:
-\begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \simeq 6 \, \pc \,\, \Mbheight v_{500}^{-2},
-  \label{eq:stag_simple}
-\end{align}
-where in the numerical estimate we have assume $n = 1$.
-This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
-On the other hand, if wind heating is much weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
-
-The importance of conductive heating can be estimated by comparing its
-magnitude to that of wind heating, viz.~
-\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
-w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
-\nonumber \\ &\sim&
-0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
-soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
-\end{eqnarray}
-
-where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.
-We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.
-
-The SMBH accretion rate is simply given by the integrated mass loss
-rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
-%AG: Should we have separate cores and cusps? Or just write a general
-%relationship in terms of gamma?
-\begin{eqnarray}
-  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
-&\approx&
-  \begin{cases}
-    1.6 \times 10^{-3} M_{\bullet,8}^{1.9}
-    \chi^{-4} v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
-    3.4 \times 10^{-3} \Mbheight^{1.4} \chi^{-2}
-    \chi^{-2} v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
-  \end{cases}
-  \label{eq:mdot_analytic}
-\end{eqnarray}
-
-The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
-\begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}(\rs)},
-  \label{eq:mdot_gas}
-\end{align}
-from which one derives 
-\begin{align}
-  \rho(\rs)\simeq
-  \begin{cases}
-    3 \times 10^{-24} \Mbheight^{-0.14} v_{500}^{-1}  \eta \,
-    \, {\rm g \, cm^{-3}}& \text{core}\\
-    6 \times 10^{-24}  \Mbheight^{-0.56} v_{500}    \eta \,\, {\rm g \,cm^{-3}} & \text{cusp}
-  \end{cases}
-  \label{eq:rhors}
-\end{align}
-
-\subsection{Comparison with Bondi Accretion}
-The spherical accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and density is given by (\citealt{Bondi52}) 
-\begin{align}
-  \dot{M}_{\rm B} =4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b),
-\label{eq:bondi}
-\end{align}
-where $r_b \equiv GM/c_{s}^{2}$ is the ``Bondi radius", $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
-
-Rewriting equation (\ref{eq:mdot_gas}) as
-\begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
-\end{align}
-we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
-\begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}},
-  \label{eq:rs_simple}
-\end{align}
-where in the second line we have used the fact that $v_{w}^{2}/2 =
-c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
-exists which is interior to the sphere of influence radius, the
-accretion rate predicted by our model is quite close to $\dot{M}_{\rm
-  B}$.
- %({\bf BDM: Check - as this depends on
- % whether eq 10 is correct})
-
-%% AG-Apparently even in the low heating case, it is still possible to
-%% an outflow (from the analytic results above the gas density must be
-%% quite steep in this case). However, at low heating we will probably
-%% become subject to a cooling instablity.  AG-I believe that in the
-%% case of core galaxy, the negative root of the quadratic should be
-%% taken...
-
-\subsection{Numerical Solutions}
-
-Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 200, 500, 1000 km s$^{-1}$.
-
-Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
-As expected, the gas density increases towards the SMBH.
-For some profiles (e.g.
-NGC1172 and NGC4478) the density $\rho$ follows a power law from the stagnation radius (squares in Fig.~\ref{fig:profiles}) inwards $\rho \propto r^{-n}$ with $n \approx 1$.
-Note that this is shallower than the $-3/2$ power law for Bondi accretion.
-However, the power law behavior does not extend through all radii, and the gas density profile may have breaks mirroring those in the stellar density profile.
-For example, NGC4365 has a prominent break in the gas density profile, near the stagnation radius.
-This coincides with the location
-of the break in the stellar light profile ($\rb$). The temperature profile is relatively flat at large radii, but increases as $\propto
-1/r^{k}$ interior to the sphere of influence, where $k$ is smaller than 1--the power expected for virialized gas.  The inwardly
-directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
-% {\bf BDM: I made this up - in general we need
-%   more explanation of what the plots are actually showing, with some
-%   physical explanation.}
-% AG -- things are not quite approaching Bondi on the inner grid. I
-% don't have a good physical explanation yet...
-% AG -- I am somewhat concerned about boundary effects in
-% NGC3115. Perhaps the break in the gas density profile is due to
-% boundary effects--I know that in this case the break is not
-% associated with a break in the stellar density profile
-
-Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.
-Cusp and core galaxies are marked with square and triangles, respectively.
-%The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}
-
-Our results for $r_{\rm s}/r_{\rm soi}$ can be compared directly to our analytic estimate in equation \ref{eq:stag_analytic}.
-The bottom panel of Figure \ref{fig:stag} shows the fractional difference between our numerical and analytic results for $r_{\rm s}/r_{\rm soi}$.
-The generally good agreement (especially for $v_{w,0}$ = 500, 1000 km s$^{-1}$) provides a useful check of the numerical results.
-
-%% AG: Describe conservation checks to additionally validate the results.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{profiles.eps}
-  \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
-    interior X-ray luminosity ({\it bottom}), calculated for three
-    characteristic galaxies from our samples: NGC1172 ({\it blue}),
-    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
-    styles denote different values of the effective wind heating rate,
-    $v_{w,0}$=500 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
-     dot-dashed}).}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{rs.eps}
-  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
-    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
-      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
-    function of the ratio of the effective wind heating rate $v_{w,0}$
-    to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$,
-    respectively.  Squares correspond to cusp galaxies, while
-    triangles correspond to cores. \emph{Bottom panel}: Fractional
-    difference between our numerical calculation of $r_{\rm s}/r_{\rm
-      soi}$ and the analytic result in
-    equation~(\ref{eq:stag_analytic}). }
-\end{figure}
-
-\section{Applications}
-\label{sec:applications}
-\subsection{Sources of Heating}
-\label{sec:heating}
-
-Our results show that the location of the stagnation rate and resulting accretion rate, is very sensitive to the assumed heating
-rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating rate will vary from galaxy to galaxy.. For example, SNe Ia represent a
-potentialy important source of heating, but since they are rare they
-will only be relevant in a time-averaged sense if the supernova rate
-exceeds the inflow time of the gas near the stagnation point.
-
-In this section we discuss potential sources of heating and provide estimates of the value of $\vwO$ corresponding to each.
-Before proceeding, note that $\vwO$ is related to the heating rate per volume $e$ according to
-\begin{align}
-  &\frac{q \vwO^2}{2}=e \,\,\,\Rightarrow\,\,\,\vwO = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
-  \label{eq:vw_eff}
-\end{align}
-
-\subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.
-
-Main sequence winds, though contributing a much smaller quantity of mass, have much higher velocities and hence contribute a
-disproportionally large share of the kinetic energy of winds.
-\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.
-On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.
-In what follows below, we take an effective stellar wind heating rate
-\be
-v_{\rm w,0}^{\star} =  150\,{\rm km\,s^{-1}}
-\ee
-In Appendix \ref{app:windheat} we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age ({\bf BDM: Nick can create}).
-
-\subsubsection{Millisecond Pulsars} The spin down power of millisecond
-pulsars (MSPs) could in principle be an important heating source.  If
-the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each
-contributes an average spin-down luminosity $\bar{L}_{\rm sd}$, then the
-resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
-  msp}\epsilon$ corresponds to an effective heating rate (eq.~
-[\ref{eq:vw_eff}])
-
-  \begin{align}
-    v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
-&\approx&  40\epsilon^{1/2}\left(\frac{\bar{L}_{\rm sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \left(\frac{\eta}{0.1}\right)^{-1/2}\,{\rm km\,s^{-1}},
-  \end{align}
-
-where $\epsilon< 1$ is the thermalization efficiency of the wind.
-The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we assume in the numerical estimate.
-Using the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate the average spin-down luminosity of millisecond pulsars in the field (excluding those in globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, in which case $v_{\rm w,0}$ is negligibly small even for $\eta = 0.1$ and $\epsilon = 1$.
-
-If we assume a higher spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi pulsars, then we find that $v_{\rm w,0}^{\rm p} \simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$ km s$^{-1}$, in which case MSP heating can be comparable to main sequence wind heating for $\eta = 0.1$, $\epsilon = 1$.
-However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
-Also, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population.
-\subsubsection{Type Ia Supernovae}
-
-Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the instellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}])
-\begin{align}
-    v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
-\end{align}
-The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq \epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$ with which the blast wave energy is converted into bulk or turbulent motion instead of being lost to radiation.
-\cite{Thornton+98} estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$, depending weakly on surrounding density, but \citet{Sharma+14} argues that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if the SNe occur in a hot dilute medium, as may characterize the CNM.
-
-The Ia SN rate $\RateIa$ depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
-In the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.
-The observationally inferred DTD (Fig.
-1 of \citealt{MaozMannucci+:2012a}) has the approximate functional form
-\begin{align}
-    R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
-\label{eq:DTD}
-  \end{align}
-where $\tau_{\star}$ is the time since star formation (c.f.~\citealt{Scannapieco&Bildsten05}).
-
-Using equations (\ref{eq:vw_sne}), (\ref{eq:DTD}), and (\ref{eq:eta}) we thus estimate that
-\be
-v_{w,0}^{\rm Ia} \approx 250(\epsilon_{\rm Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.07}\,{\rm km \,s^{-1}},
-\ee
-showing that the effective velocity due to SN heating is (coincidentally) a weak function of the stellar age.
-
-The relatively high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent a potentially dominant source of non-AGN heating in the CNM.
-However, SNe can only be approximated as "constant" heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest
-(\citealt{ShcherbakovWong+:2014a}).  To estimate when this
-approximation is valid, we estimate the ``Ia radius"
-\begin{align}
-r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \sim 38 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc} 
-\label{eq:rIa}
-\end{align}
-as the location exterior of which the time interval between subsequent
-supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim
-G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
-  dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old
-stellar population and in the final equality we estimate the velocity
-dispersion using the $M_{\bullet}-\sigma$ relationship
-(equation~[\ref{eq:Msigma}]).
-Between subsequent supernova, stars release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm gas}\sigma^{2}$.
-Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
-
-Note that the stagnation radius scales approximately linearly with $M_{\bullet}$ (equation~[\ref{eq:stag_simple}]), while $\rIa$ is roughly indpendent of SMBH mass.
-For small $\Mbh$, the stagnation radius thus lies well inside $\rIa$ and hence Ia SNe will not contribute appreciably to the heating rate.
-On the other hand, for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia  represent an important, and possibly dominant, contribution to the overall heating.
-
-\subsubsection{SMBH Feedback}
-
-Feedback from accretion onto the SMBH also represents a potentially important source of heating which is the most difficult to quantify.
-A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$.
-We assume that the total heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
-If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm out}$ results in an effective wind heating rate of
-\be
-v_w^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm out}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{\beta/2},
-\ee
-where we have used the fact that $\dot{M} \approx \eta M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto M_{\bullet}(r/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$ for radii interior to the outer break radius.
-Thus for $r_{\rm heat} \sim r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim 10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other sources of non-accretion powered heating.
-
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm w,0}^{-\beta}$, where in the last proportionality we have used equation (\ref{eq:stag_simple}).
-Hence, when SMBH heating dominates, it may ``self-regulate" itself.
-
-What is a physically motivated value of $r_{\rm heat}$?
-\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half opening angle $\theta_{\rm j} = 0.1$ (similar to those of AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a timescale
-\begin{eqnarray}
-t_{\rm jet} &\sim& 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
-\end{eqnarray}
-Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is given by
-
-\begin{equation}
-\frac{t_{\rm jet}}{r/\sigma} \sim 8\times 10^{-5}\sigma_{200}^{2/3}\epsilon_{\rm j}^{-1/3},
-\end{equation}
-which is notably independent of radius $r$.  Thus we require $\epsilon_{\rm j} \gtrsim 10^{-12}$ for the jet to escape, and if it escapes it is free to travel a long distance.
-
-\subsubsection{Combined Heating Rate}
-
-The total heating rate $\vwO = \sqrt{v_{\rm w,0}^{\star} + v_{\rm w,0}^{\rm Ia} + v_{\rm w,0}^{\rm p} + v_{\rm w,0}^{\bullet}}$ has contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
-Since pulsar heating appears unlikely to contribute appreciably, and since SMBH heating is uncertain, we first focus on heating from stellar winds and supernovae.
-
-Figure~\ref{fig:vweff} shows an estimate of how the combined heating depends on the age of the stellar population $\tage$ and the SMB mass $\Mbh$.
-For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}]) to contribute their full heating rate.
-$v_{\rm w,0}^{\rm Ia} \sim 250$ km s$^{-1}$.
-On the other hand, for lower mass BHs Ia SNe are infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star} \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of interest.\footnote{Although SN Ia will still occur surrounding low mass SMBHs, if they are infrequent interior to the radius where the accretion rate is being set, then they will not affect the flow near the SMBH at most epochs.}  For very young stellar populations ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to contributions from line driven winds from high mass main sequence stars.
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{vw-contour.eps}
-    \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM
-      in the parameter space of SMBH mass $\Mbh$ and age of the
-      stellar population $t_{\star}$.  We assume that stellar winds
-      contribute a constant heating rate $100$ km/s. The contribution
-      from SNe Ia is calculated using equation (\ref{eq:vw_sne}), with
-      thermalization efficiency $\epsilon_{\rm Ia}=0.4$. The
-      contribution from SNe Ia is only added if the $r_s$
-      corresponding to the resulting $\vwO$ is outside
-      $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on time! among other things}}%describe other cases here.
-  \end{figure}
-
-  % AG-I am not comfortable saying type Ia SNe's don't contribute to
-  % heating for smaller mass BHs. If the cooling time for the SNe is
-  % long then it would be wrong to ignore the SNe contribution. The
-  % difference would be that the SNe heating would just be less steady.
-  % AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
-
-\subsection{Mass accretion rate}
-
-For each solution we calculate the accretion rate $\dot{M}$ onto the
-SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
-\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
-10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
-$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 150, 300 and 600 km s$^{-1}$.
-
-Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and
-$\dot{M}\sim\vwO^{-4}$ for a core galaxy
-(equation~[\ref{eq:mdot_analytic}]), the mass accretion rate is
-expected to be a sensitive function of the assumed heating rate.
-However, the accretion rate is proportional to the stellar mass
-enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh
-(\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh
-(\rs/\rsoi)$.  This steeper dependence is enough to offset the
-tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed
-$\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core
-galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
-$\vwO=1000$ km s$^{-1}$, core galaxies have a smaller accretion rate
-for a given SMBH mass.
-%% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
-%% AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.
-
-We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH
-mass $M_{\bullet}$.  This appears to be in contradiction with the
-general down sizing trend observed for SMBH accretion in the local
-universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
-fact that for quiescent galaxies the nuclear X-ray luminosity obeys
-$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
-\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
-\sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
-\sim \Mbh^{1.5-2}$, steeper than the observed relationship.
-
-This is shown in the top panel Figure~\ref{fig:bh_xray}. The
-relationship from \citealt{MillerGallo+:2014a} and their detection
-upper limits are the black and blue solid lines
-respectively. The points correspond to the $\dot{M} c^2$ for our
-solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
-each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
-heating expected from main sequence the stellar winds and MSPs. If
-$L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
-bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
-10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
-\citealt{MillerGallo+:2014a}.
-
-One possible solution that the wind mass loss rate $\eta$ decreases
-with $\Mbh$, as would be expected if low mass SMBH preferentially
-hosted older stellar populations.  Another possible explanation is
-that the effective heating rate of the CNM $v_{\rm w,0}$ decreases
-with decreasing SMBH mass.  This could again be due to an older
-stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating
-sources such as SN Ia and millisecond pulsars.
-%, or it could be due to the fact that Ia occur too infrequently inside
-%the stagnation radius for low mass black holes.
-%AG-We now think that SNe Ia would become important only at the
-%highest values of Mbh.
-%AG-Note sure where the best place for this discussion would
-%be--here or after presenting the comparisons with Miller et al.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{mdot_mass.eps}
-  \caption{\label{fig:mdot_mass}  Accretion rate $\dot{M}$ in units of the Eddington rate $\dot{M}_{\rm edd}$ as a function of SMBH mass for each galaxy in our sample, calculated for different values of the wind heating parameter $\vwO =$ 200 km s$^{-1}$ ({\it green}), 500 km s$^{-1}$ ({\it orange}), and 1000 km s$^{-1}$ ({\it blue}).
-Squares correspond to cusp galaxies, while triangles correspond to cores.}
-\end{figure}
-
-%% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
-
-\subsection{Comparison to Observations}
-\subsubsection{Comparison to measured temperature and density profiles}
-\citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.
-\citet{RussellMcNamara+:2013a} performed a similar analysis with a somewhat enlarged galaxy sample.
-Interestingly, these works find a correlation between the accretion rate inferred assuming Bondi accretion and the AGN jet power, which is estimated by the PdV work required to inflate observed cavities in the X-ray emitting gas.
-% At some point it would be useful to describe the differences between
-% these two sets of observations \citealt{RussellMcNamara+:2013a}
-% tries several different extrapolation schemes for the gas density,
-% and finds that that the uncertainty in extrapolating the density
-% profile is the dominant source of uncertainty in measuring the
-% accretion rate. Find total number which overlaps once the Russell
-% galaxies are included...
-
-Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.
-We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
-The results of this exercise are presented in Fig.~\ref{fig:allen_compare}.
-
-Note that we have two free parameters ($\eta$ and $\vwO$) in our
-model, which implies that we can always match the observed temperature
-and densities at at least one point.  As a general rule, we find that
-a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
-with the observed temperatures.  We now highlight results for specific
-galaxies.
-% Thus, we choose $\vwO=500$ km/s.  We choose an
-% $\eta$ so that our solution would be consistent with the observed
-% density profiles. The comparison is shown in
-%% AG-The chosen properties, in particular eta may be summarized in a table.
-%% AG-Mention rising temperature profiles on large scales.
-
-\begin{itemize}
-% \item \emph{NGC4486} %eta=0.2
-%   On scales of $\sim1$ kpc the density profile in
-%   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
-%   has a break in the gas density at $\sim 300$ pc--near the location
-%   of the Nuker break radius for this galaxy at 560 pc. There is an
-%   observed break in the density, but on a scale of a few kpc.
-
-%   The temperature is assumed to be flat from the resolution limit
-%   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
-%   increases monotonically towards the galactic center. This increase
-%   is due to the increased velocity dispersion (and thus increased
-%   heating) towards the galactic center.
-
-\item \emph{NGC5813} %eta=0.1
-  The observed density profile (\citealt{RussellMcNamara+:2013a}) is
-  shallower than our calculated density profile, which has a sharp
-  break at $\sim$0.1 kpc, the location of the break radius in the
-  Nuker profile (this is the radius where the stellar light profile
-  transitions from a shallower inner power law slope to a steeper
-  outer power law slope).
-
-  For this galaxy we found that we could reproduce the observed
-  temperature on large scales with $\vwO=500$ km/s. The increased
-  velocity disperision towards the galactic center results in a sharp
-  increase in $T$ at small radii, which is not captured in the
-  observations due to resolution issues.
-\end{itemize}
-
-%It would be nice to have error bars for the observational points in this plot...
-\begin{figure*}
-  \includegraphics[width=\columnwidth]{NGC5813_T.eps}
-  \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
-  \caption{\label{fig:allen_compare} Comparison of the radial profiles
-    (blue lines) of electron number density $n_e$ and temperature $T$
-    to the measured values (black square) in \citet{AllenDunn+:2006a}
-    and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
-    power law extrapolations of our profiles. Note that in going from
-    $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
-  %% AG in the future we will have to be carfeful of the mean molecular weight.
-\end{figure*}
-
-% \subsubsection{Comparison with observed X-ray Luminosity-Mass
-%   Relation}
-% %Note currently I reverse-engineer the stellar mass from the black
-% %hole mass inferred from M-sigma; however, it would be better to use
-% %the tabulated black hole mass from the Mbh-Mbulge relation.
-% Fig. 1 of \citealt{MillerGallo+:2014a} plots the observed
-% relationship of unresolved x-ray luminosity versus galactic stellar
-% mass for a sample of quiescent galaxies. We may construct a similar
-% relationship with our own sample using the inferred accretion rates
-% from our solutions.  To infer an x-ray luminosity for each solution,
-% we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
-% 10^{-7}$, which gives x-ray luminosities comparable to
-% those in \citealt{MillerGallo+:2014a}. We also try an alternate
-% prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
-% take $L_x=2 \times 10^{-4} (\eddr) \Mdot c^2$.
-
-% We must make choose a $\vwO$ for each galaxy.  We select $\vwO$=200
-% km/s if $\rs<\rIa$ for this solution, $\vwO$=500 km/s if $\rs>\rIa$
-% for this solution, or exclude it.  At low $\Mbh$ we have $\vwO$=200
-% km/s and at high $\Mbh$ we have $\vwO$=500 km/s.  Note that much of
-% our sample is excluded in this Fig., since for $\vwO$=200 km/s we
-% would have $\rs>\rIa$ and four $\vwO$=500 km/s we would have
-% $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$ would be
-% inconsistent with the assumed level of heating).
-
-% %AG-power law may be closer to 1.4 & 1.8 than to 1.5 & 2.
-% Our results are plotted in Fig.~\ref{fig:bh_xray}. In our model
-% there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
-% \citealt{MillerGallo+:2014a}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
-% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{MillerGallo+:2014a} finds
-% that $L_x \propto M_{\rm gal}^{0.7-0.8}$.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{bh_xray.eps}
-\caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
-  stellar mass for our solutions (points), the trend of nuclear x-ray
-  luminosity with stellar mass (black line) and the detection upper
-  limit (blue line) from Fig. 1 of \citealt{MillerGallo+:2014a}. In
-  the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
-  c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
-  luminosities comparable to those observed. In the bottom panel, we
-  take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
-  \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
-  we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Demographics of SMBHs}
-
-Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
-\begin{eqnarray}
-  t_{\rm growth}/t_{\rm h} \approx 
-  \begin{cases}
-    6.3 M_{\bullet,8}^{-0.9}
-    v_{500}^{4}  \eta \Msun \, \pyear& \text{core} \\
-    2.9 \Mbheight^{-0.4}
-    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
-  \end{cases}
-  \label{eq:tgrow_analytic}
-\end{eqnarray}
-which we have normalized in terms of the Hubble time.
-
-{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{\rm w,0}^{\bullet}$ and $\sigma = v_{\rm w,0}^{\star}$.
-}
-
-\subsection{Cooling}
-\label{sec:cooling}
-Our models neglect radiative cooling, an assumption we now check.
-At high temperatures $T\gsim 2\times 10^7$ K gas cools through free-free emission, while at lower temperatures it cools predominantly through metal lines.
-To assess the importance of radiative cooling in our solutions we compare the heating rate $H=q \vw^2/2$ to the nominal cooling rate
-\begin{align}
-  \dot{q}_{\rm cool} =\Lambda(T) n^2,
-\label{eq:cooling}
-\end{align}
-where $n = \rho/\mu m_p$ and we approximate the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (Fig. 34.1 in \cite{Draine:2011a}):
-\begin{align}
-\Lambda(T)\simeq
-  \begin{cases}
-    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}&, T \gsim 2 \times 10^7 \text{K} \\
-    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}&, T \lsim 2 \times 10^7 \text{K}     
-  \end{cases}
-  \label{eq:cooling2}
-\end{align}
-
-If cooling becomes important in the flow, it may lead to thermal
-instabilities.  There are two kinds of ``instabilities", global and
-local.  The global instability is simply that, if cooling becomes very
-rapid, the gas loses thermal pressure and starts to inflow faster,
-i.e. the entire CNM accretes (e.g. ).  In
-practice this should could manifest as a large increase in the
-stagnation radius, due an effective {\it decrease} in the effective
-heating rate.  This global ``instability" is not a true instability
-insofar as the gas does not necessarily clump locally into low-T
-clouds.
-
-However, \citealt{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\be
-t_{\rm cool} \equiv \frac{3n kT/2}{\dot{q}_{\rm cool}}
-\ee 
-is locally shorter than the approximately 10 times the free-fall timescale $t_{\rm ff}$.
-
-Using equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), (\ref{eq:rhors}), (\ref{eq:cooling}), (\ref{eq:cooling2}), we can estimate the ratio of the cooling timescale to the free-fall time $\sim r/\sigma$ at the stagnation radius
-\begin{align}
-  \left.\frac{t_{\rm cool}}{t_{\rm ff}}\right|_{r_{\rm s}}\simeq
-  \begin{cases}
-    12 \Mbheight^{-0.66} \eta^{-1}(\chi v_{500})^{6.4}, & \text{core}\\
-    6  \Mbheight^{-0.24} \eta^{-1}(\chi v_{500})^{4.4} ,   & \text{cusp}
-  \end{cases}
-  \label{eq:coolingratio}
-\end{align}
-We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if $\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
-
-Fig.~\ref{fig:cooling} shows $t_{\rm cool}/t_{\rm ff}$ as a function of radius for all of our solutions {\bf BDM: change plots}, with different colors denoting different values of $v_{w,0}$.
-For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.
-With a few exceptions this is also true for $\vwO$=500 km s$^{-1}$.
-However, for our lowest heating rate $\vwO$=200 km s$^{-1}$ cooling may be quite important, especially for high $\eta$ (young stellar population;  Appendix~\ref{app:eta}).
-
-For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
-Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
-If cooling is important, the CNM is likely to be thermally unstable, resulting in the formation of a cold medium that could substantially enhance the rate of accretion onto the SMBH.
-
-%\begin{align}
- % \Lambda(T)\simeq
-  %\begin{cases}
-   % 2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
-   % 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
-  %\end{cases}
-  %\label{eq:cooling}
-%\end{align}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
-    ($C$) for each of our solutions. The cooling rate is calculated
-    using the approximate (solar metallicity) cooling function in
-    Equation~(\ref{eq:cooling}). The heating rate is estimated as $q
-    \vw^2/2$. The ratio is computed from equation (\ref{eq:cooling})
-    assuming a stellar mass loss rate parameter $\eta=1$.}
-\end{figure}
-
-\input{figures/eta_tab.tex}
-
-  \subsection{Angular Momentum}
-  \label{sec:ang}
-  Our models are spherically symmetric and do not include the effects of
-  the gas' angular momentum. However, galaxies will in general have some
-  net rotation, and the gas will generally have some non-zero angular
-  momentum. At some radius, $\rcirc$, the specific angular momentum of
-  the gas will equal the specific angular momentum of a circular
-  orbit. Inside of this radius our assumptions of no rotation and
-  spherical symmetry will break down. But if $\rcirc$ is inside of the
-  inner sonic point of the flow, the region where angular momentum
-  becomes important will be causally disconnected from the rest of the
-  flow, and we would be justified in neglecting angular momentum (at
-  least on large scales).
-
-  $\rcirc$ depends on the gas injection radius. The largest
-  injection radius is $\rs$. Let $\lrs$ be the gas specific angular
-  momentum at $\rs$, then
-
-  \begin{align}
-    \rcirc=\frac{\lrs}{G \Mbh}
-  \end{align}
-
-  \citet{EmsellemCappellari+:2007a} used two-dimensional kinematic
-  data to measure the ratio of ordered to random motion in a sample of
-  early type galaxies. More precisely, they measure
-
-  \begin{align}
-    \lambda_R=\frac{\left<R|V|\right>}{\left<R\sqrt{V^2+\sigma^2}\right>}
-  \end{align}
-
-  Where $R$ is the distance is the distance from the galactic center, $V$ is
-  the mean stellar velocity, and $\sigma$ is the velocity
-  dispersion. The brackets represent a luminosity weighted average.
-
-  We may rewrite the specific angular momentum at $\rs$ in terms of $\lambda_R$.
-
-  \begin{align}
-    \lrs\simeq\lambdars \sigma(\rs)^2 \rs^2
-  \end{align}
-
-  Then
-
-  \begin{align}
-    \rcirc&\simeq\lambdars^2 \frac{\sigma(\rs)^2}{G \Mbh} \rs^2\\
-    &\simeq\lambdars^2 \frac{\rs^2}{\rsoi} \lsim \lambdars^2 \rsoi
-  \end{align}
-
-  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
-  $\rsoi$. %%AG-Need to explain this somehow.
-  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Fig. 2 of
-  \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
-  of radius for a sample of early type galaxies. On scales of $\sim 0.1
-  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
-  of their sample %%need to be clearer on rapidly declining also compare
-  %% this scale to the sphere of influence scale.
-  This suggests that angular momentum should generally be unimportant.
-
-  \section{Summary}
-  \label{sec:summary}
-  We have calculated steady-state models for circumnuclear medium of a
-  sample of early type galaxies, assuming that gas is supplied
-  entirely by stellar wind mass loss and heated by shocked stellar
-  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
-  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
-  with $\Mbh$. We may then compare our results with observed trends of
-  nuclear x-ray luminosity. Our main conclusions may be summarized as
-  follows.
-
-  \begin{enumerate}
-  \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
-    $\alpha$ depends on the slope of the stellar density profile
-    ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively). One
-    possible solution that the wind mass loss rate (i.e. $\eta$)
-    decreases with $\Mbh$, as would be expected if low mass SMBH
-    preferentially hosted older stellar populations. Another possible
-    explanation is that the effective heating rate of the CNM $v_{\rm w,0}$
-    decreases with decreasing SMBH mass. This could again be due to an
-    older stellar population, since $v_{\rm w,0} \propto \eta^{−1/2}$
-    for heating sources such as SN Ia and millisecond pulsars.
-  \item We compare the $\Mdot$ for each of our solution to the one
-    calculated from the Bondi formula. We find that they generally to
-    a factor of a few. In our model the accretion rate is determined
-    from the gas properties at the stagnation radius, $\rs$, which
-    agrees with the Bondi radius, $\rb$, within a factor of a
-    few. Thus, use of the Bondi formula is a good approximation.
-  \item We compare our solutions for density and temperature to those
-    inferred from Chandra x-ray observations by \citet{AllenDunn+:2006a}
-    and \citet{RussellMcNamara+:2013a} for a handful of galaxies in
-    which our sample overlap with theirs. In general, we cannot match
-    the observed gas density slope on large scales. 
-  \end{enumerate}
-
-  \clearpage
-  \appendix
-  \section{Analytic Expression for the stagnation radius}
-  \label{app:rs}
-  \input{rs}
-
-  \section{Analytic model for dependence of wind mass loss rate on stellar age}
-  \label{app:eta}
-  \input{eta}
-
-\section{Analytic model for dependence of wind heating $v_{\rm w,0}^{\star}$ on stellar age}
-\label{app:windheat}
 If we assume that a stellar population forms impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any future time $t$ is given by
@@
 \end{equation}
-{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
+%{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
 If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
@@
 \begin{equation}
-q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
+q(t) = \frac{\rho_*}{\th} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
 \end{equation}
-This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
-Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
-Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
-Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
+This is a specific, time-dependent definition of $\eta$:
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{NickPlot.eps}
-\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
-The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
-Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
-\end{figure}
+\begin{equation}
+\eta(t) (=0.11(t/t_{\rm h})^{-1.26})
+\label{eq:eta}
+\end{equation}
 
-In Fig.
-\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
-We parametrize the wind velocity as
-\begin{equation}
-\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
-\end{equation}
-The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
-We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
-Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
-  \footnotesize{
-    \bibliographystyle{mn2e}
-    \bibliography{master}
-  }
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "ms"
+%%% End:

### 2014-11-15 ms.tex
Some changes in the conductive heating section, as well as in the bib file.

@@
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
-      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] +\nabla\cdot(\kappa \nabla T)
+      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right]
+  +\nabla\cdot(\kappa \nabla T)
 , 
@@
 
-The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
+The second source term in equation (\ref{eq:dsdt}) accounts for
+heating transportation by electron conductivity. We take the
+conductivity to be $\kappa_{\rm eff}=\kappa_{\rm spitzer}/(1+\psi)$,
+as described in \citealt{DaltonBalbus:1993a}. $\kappa_{\rm spitzer}$
+is the classical \citealt{Spitzer62} value, $\kappa_{\rm spitzer} =
+\kappa_0 T^{5/2}$ ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units). The
+term in the denominator is a flux limiter. The conductive flux should
+saturate when the mean free path for electron coulomb scattering
+becomes comparable to the temperature length scale.  More precisely
+$\psi=\frac{\kappa_{\rm spitzer} \nabla T}{5\phi \rho c_s^3}$ (the
+Spitzer conductive flux over the saturated conductive flux; $\phi$ is
+a dimensionless constant of order unity or less). Although even a weak
+magnetic field could in principle strongly suppress the conductivity
+perpendicular to the field, the radially-decreasing temperature
+profiles of interest are susceptible to the magneto-thermal
+instability (\citealt{Balbus01}), the non-linear evolution of which is
+believed to result in a radially-directed field structure
+(\citealt{Parrish&Stone07}).
 
@@
 of velocities moving with respect to each other a characteristic
-velocity $\sim \sigma$.  This heating is present if the wind velocities themselves
-are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
-The term $v_{w,0}^{2}$ parameterizes additional sources of heating,
-such as main sequence winds, millisecond pulsars, supernovae, etc.  As
-discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is
-uncertain and will in general depend on the SMBH mass and the age of
-the stellar population.
+velocity $\sim \sigma$.  This heating is present if the wind
+velocities themselves are low, $\ll \sigma$, as characterize the
+majority of AGB mass loss.  The term $v_{w,0}^{2}$ parameterizes
+additional sources of heating, such as main sequence winds,
+millisecond pulsars, supernovae, etc.  As discussed in
+$\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in
+general depend on the SMBH mass and the age of the stellar population.
 
@@
 
-The importance of conductive heating can be estimated by comparing its
-magnitude to that of wind heating, viz.~
-\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
-w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
-\nonumber \\ &\sim&
-0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
-soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
-\end{eqnarray}
-
-where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.
-We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.
-
 The SMBH accretion rate is simply given by the integrated mass loss
@@
 
-\subsection{Comparison with Bondi Accretion}
-The spherical accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and density is given by (\citealt{Bondi52}) 
+The importance of conductive heating can be estimated by comparing its
+magnitude to that of wind heating, viz.~
+\begin{eqnarray} \left.\frac{\nabla\cdot(f_{\rm cond})}{q v_{\rm
+w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h} \phi \rho(\rs) c_s(\rs)^3}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
+\nonumber \\ &\sim&
+\frac{10 \phi}{2-\Gamma}, \label{eq:condRatio}
+\end{eqnarray}
+
+%Is the stagnation radius the best choice for evaluating the
+%importance of conduction? I think it would be greater on the inner
+%grid. 
+where we have used the saturated heat conduction flux and approximated
+$\nabla \sim 1/r_{\rm st}$ and in the second equality have made use of
+equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and
+(\ref{eq:rhors}). The stellar density is assumed to be a power law
+$\rho_{\star}=\frac{\Mbh \left(2-\Gamma\right)}{4 \pi \rsoi^3}
+\left(\frac{\rs}{\rsoi}\right)^{-1-\Gamma}$.
+% We thus see that
+% conductive heating is important near the stagnation radius for high
+% values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
+% but that it is safely neglected to first order for lower heating
+% rates.
+
+By using the saturated value of the conductive heat flux we have found
+an upper bound on the ratio of the rate of heating to the rate of heat
+conduction is equation~\eqref{eq:condRatio}.  For $\phi\simeq 1$, the
+conductive flux could be quite important. However, the value of $\phi$
+has some uncertainty as it will depend on various details from plasma
+physics, and could plausibly be an order of magnitude smaller. In
+light of these uncertainties we neglect the effect of the conductive flux
+
 \begin{align}
@@
 
-Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
-As expected, the gas density increases towards the SMBH.
-For some profiles (e.g.
-NGC1172 and NGC4478) the density $\rho$ follows a power law from the stagnation radius (squares in Fig.~\ref{fig:profiles}) inwards $\rho \propto r^{-n}$ with $n \approx 1$.
-Note that this is shallower than the $-3/2$ power law for Bondi accretion.
-However, the power law behavior does not extend through all radii, and the gas density profile may have breaks mirroring those in the stellar density profile.
-For example, NGC4365 has a prominent break in the gas density profile, near the stagnation radius.
-This coincides with the location
-of the break in the stellar light profile ($\rb$). The temperature profile is relatively flat at large radii, but increases as $\propto
-1/r^{k}$ interior to the sphere of influence, where $k$ is smaller than 1--the power expected for virialized gas.  The inwardly
-directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
+Figure~\ref{fig:profiles} shows three representative profiles of the
+density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
+As expected, the gas density increases towards the SMBH.  For some
+profiles (e.g. NGC1172 and NGC4478) the density $\rho$ follows a power
+law from the stagnation radius (squares in Fig.~\ref{fig:profiles})
+inwards $\rho \propto r^{-n}$ with $n \approx 1$. Note that this is
+shallower than the $-3/2$ power law for Bondi accretion. However, the
+power law behavior does not extend through all radii, and the gas
+density profile may have breaks mirroring those in the stellar density
+profile. For example, NGC4365 has a prominent break in the gas density
+profile, near the stagnation radius. This coincides with the location
+of the break in the stellar light profile ($\rb$). The temperature
+profile is relatively flat at large radii, but increases as $\propto
+1/r^{k}$ interior to the sphere of influence, where $k$ is smaller
+than 1--the power expected for virialized gas.  The inwardly directed
+velocity increases towards the hole approaching the expected free-fall
+rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic
+point, and then increases outwards towards large radii.
 % {\bf BDM: I made this up - in general we need

### 2014-11-15 ms.tex
brian revisions

--- 2014-11-11 ms.tex
@@
 %this parametrized study.
+{\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}
+
 Our sample includes 61 early-type galaxies from
@@
 
-The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
+The stellar density at the stagnation radius (eq.~[\ref{eq:stag_simple}]) is usefully approximated as
+\begin{eqnarray}
+  && \rho_{\star}(r_{\rm s}) \approx \nonumber \\
+&& \begin{cases}
+    1.0\times 10^{-18}M_{\bullet,8}^{-1.2}v_{500}^{2}\chi^{2}\,{\rm g\,cm^{-3}}
+& \text{core} \\
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.6}v_{500}^{4}\chi^{4}
+      \,{\rm g\,cm^{-3}}  & \text{cusp}, 
+  \end{cases}
+  \label{eq:rhostarrs}
+\end{eqnarray}
+
+The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be roughly estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
 \begin{align}
@@
 
+Radiative cooling can have an important on even the qualitative features of the flow, because initially hydrostatic gas that cools at constant pressure $P \propto nT$ according to $\dot{q}_{\rm cool} \propto T^{-2.7}$ (eq.~[\ref{eq:cooling}]) is thermally unstable.
+Radiative cooling can be stabilized, however, by the other source of (stable) wind cooling, given by the last term $\propto T$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$.
+
+An important ratio controlling the importance of thermal stability is thus
+\begin{align}
+\left.\frac{\dot{q}_{\rm cool}}{q v_{\rm w}^{2}/2}\right|_{\rm r{s}} \simeq
+  \begin{cases}
+   0.02\eta M_{\bullet,8}^{0.92}v_{500}^{-7.8}\chi^{-7.8}  &, \text{core}\\
+   0.08\eta M_{\bullet,8}^{0.5}v_{500}^{-5.4}\chi^{-5.4}  &, \text{cusp},     
+  \end{cases}
+  \label{eq:cooling2}
+\end{align}
+where we have used equations (\ref{eq:rhostarrs}) and (\ref{eq:rhors}).
+We thus see that we require $v_{\rm w} \gtrsim $ 300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and $M_{\bullet}$.
+
 If cooling becomes important in the flow, it may lead to thermal
@@
 
-However, \citealt{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
 However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
@@
 We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if $\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
+
+{\bf BDM: in fact, I think the above criteria for tcool/tff and qdotcool/qdotwind are identical to constants of order unit, since we are using gas density estimated from free-fall time...
+since the BH mass dependencies are different we need to recheck algebra}
 

### 2014-11-15 ms.tex
Reincorporating my changes for the conductivity.

@@
 magnitude to that of wind heating, viz.~
-\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
-w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
+\begin{align} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
+w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
 T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
+\nonumber \\ &\sim
+10.5 \left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
+soi}}\right)^{-\beta} v_{500}^{9}\chi^{9} \nonumber \\ &\sim
+4.53 \, 0.43^{\beta-1} \left(\frac{\eta}{0.1}\right)^{-1}
+M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}\chi^{9-2\beta}
+\label{eq:condRatio1}
+\end{align}
+
+where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in
+the second equality have made use of equations (\ref{eq:Tanalytic}),
+(\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm
+  s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm
+  soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that
+conductive heating is important near the stagnation radius for high
+values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
+but that it is safely neglected to first order for lower heating
+rates. {\bf AG:Should probably include mass. Although this is tricky
+  as cusp and core galaxies have opposite dependencies on mass.}
+
+In fact, for high heating rates conductive heating is less important
+than equation~\eqref{eq:condRatio1} would suggest due to the effects
+of saturation. In this regime the importance of conductive heating can
+be estimated the conductive flux in equation~\eqref{eq:condRatio1}
+with its saturated value.
+\begin{eqnarray} \left.\frac{\nabla\cdot(f_{\rm cond})}{q v_{\rm
+w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h} \phi \rho(\rs) c_s(\rs)^3}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
 \nonumber \\ &\sim&
-0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
-soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
+\frac{10 \phi}{2-\Gamma}, \label{eq:condRatio}
 \end{eqnarray}
 
-where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.
-We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.
+where we have approximated $\nabla \sim 1/r_{\rm st}$ and in the
+second equality have made use of equations (\ref{eq:Tanalytic}),
+(\ref{eq:stag_simple}), and (\ref{eq:rhors}). The stellar density is
+assumed to be a power law $\rho_{\star}=\frac{\Mbh
+  \left(2-\Gamma\right)}{4 \pi \rsoi^3}
+\left(\frac{\rs}{\rsoi}\right)^{-1-\Gamma}$.
+
+From the saturated value of the conductive heat flux we have found an
+upper bound on the ratio of the rate of heating to the rate of heat
+conduction in equation~\eqref{eq:condRatio}.  For $\phi\simeq 1$, the
+conductive flux could be quite important. However, the value of $\phi$
+depends various details from plasma physics, and could plausibly be an
+order of magnitude smaller. In light of these uncertainties we neglect
+the effect of the conductive flux.
 
@@
     \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
-    2.6 \times 10^{-3} \Mbheight^{1.48} 
+    2.6 \times 10^{-3} M_{\bullet,8}^{1.48} 
     \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 

### 2014-12-01 ms.tex
Some modifications to the appendix equations.
Rescaling to new defaults.

@@
 \begin{align}
-  \x=\frac{1}{\zeta^2 n}\left[
-    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
+  \x=\frac{1}{2 \zeta^2 n}\left[ \frac{\Mstar}{\Mbh}\left(A-n\right)+\left(B-n\right)\right],
   \label{eq:stag_analytic}
 \end{align}
+
 where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
@@
 \begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \simeq 6 \, \pc \,\, \Mbheight v_{500}^{-2},
+  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \simeq 6
+ \, \pc \,\, \Mbheight v_{500}^{-2},
   \label{eq:stag_simple}
@@
   \begin{cases}
-    1.5 \times 10^{-3} M_{\bullet,8}^{1.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
-    2.6 \times 10^{-3} M_{\bullet,8}^{1.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
+    1.5 \times 10^{-4} M_{\bullet,8}^{1.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
+    2.6 \times 10^{-4} M_{\bullet,8}^{1.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
   \begin{cases}
-    6.6 \times 10^{-4} M_{\bullet,8}^{0.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
-    1.2 \times 10^{-3} \Mbheight^{0.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
+    6.6 \times 10^{-5} M_{\bullet,8}^{0.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
+    1.2 \times 10^{-4} \Mbheight^{0.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
 \begin{align}
-\left.\frac{\dot{q}_{\rm cool}}{q v_{\rm w}^{2}/2}\right|_{\rm r{s}} \simeq
+\left.\frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rm r{s}} \simeq
   \begin{cases}
-   0.02\eta M_{\bullet,8}^{0.92}v_{500}^{-7.8}\chi^{-7.8}  &, \text{core}\\
-   0.08\eta M_{\bullet,8}^{0.5}v_{500}^{-5.4}\chi^{-5.4}  &, \text{cusp},     
+   12\eta^{-1} M_{\bullet,8}^{-0.9}v_{500}^{7.2}\chi^{7.2}  &, \text{core}\\
+   4\eta^{-1} M_{\bullet,8}^{-0.5}v_{500}^{5.8}\chi^{5.8}  &, \text{cusp},     
   \end{cases}
@@
 \end{align}
-where we have used equations (\ref{eq:rhostarrs}) and (\ref{eq:rhors}).
-We thus see that we require $v_{\rm w} \gtrsim $ 300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and $M_{\bullet}$.
+where we have used equations (\ref{eq:rhostarrs}) and
+(\ref{eq:rhors}).  We thus see that we require $v_{\rm w} \gtrsim $
+300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and
+$M_{\bullet}$.  {\bf AG:I flipped the ratio to be consistent with the
+  ratio of timescales given below (NB here we are comparing heating
+  and cooling rates as opposed to timescales). Modulo factors of order
+  unity I find no inconsistency. We should probably only keep one of
+  these ratios. Note I have adopted the new convention of Gamma=0.8 is
+  a cusp galaxy and Gamma=0.1 is a core galaxy.}
 
@@
   \begin{cases}
-    12 \Mbheight^{-0.66} \eta^{-1}(\chi v_{500})^{6.4}, & \text{core}\\
-    6  \Mbheight^{-0.24} \eta^{-1}(\chi v_{500})^{4.4} ,   & \text{cusp}
+    11 \Mbheight^{-0.8} \eta^{-1}(\chi v_{500})^{7.2}, & \text{core}\\
+    6  \Mbheight^{-0.5} \eta^{-1}(\chi v_{500})^{5.8} ,   & \text{cusp}
   \end{cases}
@@
 \end{align}
-We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if $\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
-
-{\bf BDM: in fact, I think the above criteria for tcool/tff and qdotcool/qdotwind are identical to constants of order unit, since we are using gas density estimated from free-fall time...
-since the BH mass dependencies are different we need to recheck algebra}
+We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the
+stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if
+$\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
 

### 2014-12-07 ms.tex
Rescaling analytic expression, and adding some references.

@@
 The source term in the continuity equation (equation~\ref{eq:drhodt}),
-%Should equations be referenced as equation of equation
 \begin{align}
@@
 terms of the fraction $\eta$ of the stellar density $\rhostar$ being
-recycled into gas on the Hubble time $\th = 10^{10}$ years (see, e.g.,
-\citealt{Ciotti+91}).  In Appendix \ref{app:eta} we estimate that
-$\eta \approx 0.11(t_{\star}/t_{\rm h})^{-1.26}$ for a Salpeter IMF,
-assuming that all stars are formed in a burst of star formation at a
-common age of $t_{\star}$ (equation~[\ref{eq:eta}]).  We adopt
-$\eta=0.1$ as fiducial {\bf BDM: take $\eta = 0.1$ instead of 1}, but note that changing $\eta$ is equivalent to
-rescaling $\rho$ by the same factor.\footnote{This is {\it not} true
-  if cooling is included, since the cooling rate is proportional to
-  density {\it squared}.}
+recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
+years. $\eta\simeq 0.02 \left(\frac{t}{th}\right)^{-1.3}$ 
+(see, e.g., \citealt{Ciotti+91})\footnote{Note that 
+\citealt{Ciotti+91} gives the overall mass return rate from evolved
+stars as a function of B-band luminosity. We give the mass return rate
+per unit volume. However, our expressions are equivalent.}
 
@@
   \begin{cases}
-    1.5 \times 10^{-4} M_{\bullet,8}^{1.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
-    2.6 \times 10^{-4} M_{\bullet,8}^{1.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
+    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
+    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
   \begin{cases}
-    6.6 \times 10^{-5} M_{\bullet,8}^{0.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
-    1.2 \times 10^{-4} \Mbheight^{0.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
+    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
+    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
+    2.4 \times 10^{-5} \Mbheight^{0.48} 
+    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
   \end{cases}
@@
   && \begin{cases}
-    1.0\times 10^{-18}M_{\bullet,8}^{-1.2}v_{500}^{2}\chi^{2}\,{\rm g\,cm^{-3}}
+    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\chi^{2.2}\,{\rm g\,cm^{-3}}
     & \text{core} \\
-    1.1 \times 10^{-18} M_{\bullet,8}^{-1.6}v_{500}^{4}\chi^{4}
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}\chi^{3.6}
     \,{\rm g\,cm^{-3}}  & \text{cusp}, 
@@
   \begin{cases}
-    3 \times 10^{-24} \Mbheight^{-0.14} v_{500}^{-1}  \eta \,
+    5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
     \, {\rm g \, cm^{-3}}& \text{core}\\
-    6 \times 10^{-24}  \Mbheight^{-0.56} v_{500}    \eta \,\, {\rm g \,cm^{-3}} & \text{cusp}
+    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}
   \end{cases}
@@
   \begin{cases}
-    6.3 M_{\bullet,8}^{-0.9}
-    v_{500}^{4}  \eta \Msun \, \pyear& \text{core} \\
-    2.9 \Mbheight^{-0.4}
-    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
+    250 M_{\bullet,8}^{-0.76}
+    v_{500}^{3.8} \chi^{3.8}  \eta_{0.02}  & \text{core} \\
+    140 \Mbheight^{-0.48}
+    v_{500}^{2.4} \chi^{2.4}  \eta_{0.02}  & \text{cusp}, 
   \end{cases}
@@
   \begin{cases}
-   12\eta^{-1} M_{\bullet,8}^{-0.9}v_{500}^{7.2}\chi^{7.2}  &, \text{core}\\
-   4\eta^{-1} M_{\bullet,8}^{-0.5}v_{500}^{5.8}\chi^{5.8}  &, \text{cusp},     
+   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}\chi^{7.2}  &, \text{core}\\
+   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}\chi^{5.8}  &, \text{cusp},     
   \end{cases}
@@
   \begin{cases}
-    11 \Mbheight^{-0.8} \eta^{-1}(\chi v_{500})^{7.2}, & \text{core}\\
-    6  \Mbheight^{-0.5} \eta^{-1}(\chi v_{500})^{5.8} ,   & \text{cusp}
+    560 \Mbheight^{-0.76} \eta_{0.02}^{-1}(\chi v_{500})^{7.2}, & \text{core}\\
+    310  \Mbheight^{-0.48} \eta_{0.02}^{-1}(\chi v_{500})^{5.8} ,   & \text{cusp}
   \end{cases}
@@
 
-  \section{Analytic model for dependence of wind mass loss rate on stellar age}
-  \label{app:eta}
-  \input{eta}
+  % \section{Analytic model for dependence of wind mass loss rate on stellar age}
+  % \label{app:eta}
+%  \input{eta}
 

### 2014-12-08 ms.tex
Getting rid chi parameter

@@
 
-This section summarizes analytic estimates of several physical quantities of interest, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
-All of our results are derived under the assumption that thermal conductivity can be neglected.
+This section summarizes analytic estimates of several physical
+quantities of interest, such as the stagnation radius $\rs$ and the
+mass accretion rate, the detailed derivation of which are given in
+Appendix \ref{app:rs}.  All of our results are derived under the
+assumption that thermal conductivity can be neglected.
 
 When possible our results are expressed in terms of the wind heating
-parameter $v_{\rm w,0}$; the power-law slope of the density profile
-$n$ (also evaluated at $r = \rs$); and the dimensionless parameter \be
-\chi \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
-\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right), \ee where $v_{500}
-\equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv
-M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the
-$M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09}) \be
+parameter $\vw$; the power-law slope of the density profile
+$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vw0^2+\sigma^2$,
+where the $\sigma$ accounts for shock heating between stellar winds moving
+with respect to each other with relative velocity $\sigma$, and $\vwO$
+is a free parameter accounting for additional sources of
+heating.  $\vw$ may be calculated analytically (for a given $\Mbh$ and
+$\vwO$) using $\vw=\chi \vwO$, where
+
+ \begin{align}
+&\chi^2 \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 +
+  \sigma^{2}/v_{\rm w,0}^{2}\right) \approx \\
+&\left(1+0.14 \Mbheight^{0.43}\frac{\vwO}{500 {\rm km/s}}^{-1}\right), 
+\end{align}
+
+% where $v_{500} $M_{\bullet,8} \equiv
+where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$, and the
+second equality makes use of the $M_{\bullet}-\sigma$ correlation
+(\citealt{Gultekin+09})
+
+ \begin{align}
 M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
@@
 \label{eq:Msigma}
-\ee
+\end{align}
+
 Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.

### 2014-12-14 ms.tex
Updating figures to reflect the new parameterized approach.

@@
 \newcommand{\rsoi}{r_{\soi}}
-\newcommand{\ff}{\rm ff}
-\newcommand{\tff}{t_{\ff}}
 \newcommand{\rIa}{r_{\rm Ia}}
@@
 \renewcommand{\th}{t_h}
+\newcommand{\tcool}{t_{\rm cool}}
+\newcommand{\tff}{t_{\rm ff}}
 
@@
 \label{sec:model}
-
-\subsection{Galaxy Sample}
-
-\label{sec:sample}
-%AG:It is unclear whether if/how the Nuker profile will show up in
-%this parametrized study.
-{\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}
-
-Our sample includes 61 early-type galaxies from
-\citetalias{WangMerritt:2004a}, as represent a subset of a larger
-sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
-focus on elliptical galaxies because we are interested in isolating
-SMBHs fed by the steady mass loss from the relatively old stellar
-population, instead of fresh gas flowing into the sphere of influence
-from larger scales.
-
-The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
+\subsection{Galaxy models}
+\citealt{LauerFaber+:2007a} used Hubble WFPC2 imaging to measure the
+surface brightness profiles for hundred of nearby early type
+galaxies. The measured surface brightness profile can generally be
+well fit using a Nuker law
+
 \begin{equation}
@@
 \end{equation}
-The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
-
-Given $I(\xi)$ we follow the procedure outlined by
-\citetalias{WangMerritt:2004a} to compute the spherically-symmetric
-stellar density profile $\rhostar(r)$ and stellar mass profile
-$M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
-our model.  For reference, note that stellar density $\rhostar\sim
-r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
-\gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
-$\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
-thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
-r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
-SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
-%%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
-%%calculated from an outdated M-sigma. It would be bizarre to use 2
-%%different relations.
+The Nuker profile is a broken power law which transitions from an
+inner power law slope, $\Gamma$, to an outer power law slope, $\beta$,
+at a break radius, $\rb$.
+
+Assuming spherical symmetry this corresponds to a stellar density
+$\rhostar \sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim
+r^{-1-\beta}$ for $r \gg \rb$. Thus, we adopt a broken power law for 
+$\rhostar$
+
+\begin{align}
+\rho_\star = 
+\begin{cases}
+\rho_\star(\rsoi) \left(r/\rsoi\right)^{-1-\Gamma} & r \leq r_b\\
+\rho_\star(r_b) \left(r/r_b\right)^{-1-\beta} & r > r_b,
+\end{cases}
+\end{align}
+
+where $\rho_\star(\rsoi)$ is the stellar density at the black hole
+sphere of influence, $\rsoi$. $\rho_\star(\rsoi)$ is chosen so that
+the stellar mass inside $\rsoi$, $\Mstar(\rsoi)$, is equal to the
+black hole mass.  $\rsoi=G \Mbh/\sigma^2$. Using the $\Mbh-\sigma$ relation
+from \citealt{Gultekin+09}
+
+ \begin{align}
+M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
+      km\,s^{-1}}}\right)^{5.1}M_{\odot}, 
+\label{eq:Msigma}
+\end{align}
+
+we obtain $\rsoi \approx 14 M_{\bullet,8}^{0.6}$. In order to
+completely specify the galaxy model we must choose $\Mbh$, $\Gamma$, $r_b$,
+and $\beta$. We compute models for three different models of
+$\Mbh$: $10^6$, $10^7$, $10^8 \Msun$. In the
+\citealt{LauerFaber+:2007a} sample the distribution of the $\Gamma$s
+is bimodal, with a concentration of core galaxies with $\Gamma \lsim
+0.3$ and a concentration of cusp galaxies with $\Gamma \gsim
+0.7$. We calculate models for $\Gamma=0.8$ and $\Gamma=0.1$.
+
+We are interested in the gas flow on scales smaller than
+the break radius $\rb$, which typically occurs at a radius of 100s of
+parsecs. Thus, we fix $\beta$ to be 2 {\bf AG:I have not yet checked this
+  directly via numerical experiments}.  The presence of $\rb$ is 
+necessary for to obtain a converged steady state for some regions of
+our parameter space. For cusp galaxies, $r_b$ is a few hundred parsecs
+independently of $\Mbh$. We adopt $\rb=100$ pc for our cusp
+galaxies ($\Gamma=0.8$), while for our core galaxy models we use the
+scaling relation...{\bf AG: Need to figure out normalization for
+  scaling relation from Lauer. Fixed rb at a given Mbh only has a
+  factor of a few effect on rs--this will be discussed in the section
+  on numerical solutions.}
+
+% \subsection{Galaxy Sample}
+
+% \label{sec:sample}
+% %AG:It is unclear whether if/how the Nuker profile will show up in
+% %this parametrized study.
+% {\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}
+
+% Our sample includes 61 early-type galaxies from
+% \citetalias{WangMerritt:2004a}, as represent a subset of a larger
+% sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
+% focus on elliptical galaxies because we are interested in isolating
+% SMBHs fed by the steady mass loss from the relatively old stellar
+% population, instead of fresh gas flowing into the sphere of influence
+% from larger scales.
+
+% The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
+% \begin{equation}
+%   I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
+% \end{equation}
+% The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+
+% Given $I(\xi)$ we follow the procedure outlined by
+% \citetalias{WangMerritt:2004a} to compute the spherically-symmetric
+% stellar density profile $\rhostar(r)$ and stellar mass profile
+% $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
+% our model.  For reference, note that stellar density $\rhostar\sim
+% r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
+% \gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
+% $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
+% thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
+% r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
+% SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
+% %%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
+% %%calculated from an outdated M-sigma. It would be bizarre to use 2
+% %%different relations.
 
@@
 parameter $\vw$; the power-law slope of the density profile
-$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vw0^2+\sigma^2$,
+$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vwO^2+\sigma^2$,
 where the $\sigma$ accounts for shock heating between stellar winds moving
@@
 T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
-\times 10^6\,\chi v_{500}^2 \,\,{\rm K} 
+\times 10^6\ \, v_{500}^2 \,\,{\rm K} 
 \label{eq:Tanalytic}
@@
 
-Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
-\begin{align}
-  \x=\frac{1}{2 \zeta^2 n}\left[ \frac{\Mstar}{\Mbh}\left(A-n\right)+\left(B-n\right)\right],
+Demanding hydrostatic equilibrium at the stagnation point provides an
+expression for the stagnation radius
+
+\begin{align}
+  \frac{\rs}{\rsoi}=\frac{1}{2 \zeta^2 n}\left[
+   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right]
  \label{eq:stag_analytic}
@@
 \nonumber \\ &\sim
-10.5 \left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
-soi}}\right)^{-\beta} v_{500}^{9}\chi^{9} \nonumber \\ &\sim
-4.53 \, 0.43^{\beta-1} \left(\frac{\eta}{0.1}\right)^{-1}
-M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}\chi^{9-2\beta}
+53 \eta_{0.02}^{-1}\left(\frac{r_{\rm s}}{r_{\rm
+soi}}\right)^{-\beta} v_{500}^{9} \nonumber \\ &\sim
+23 \,\, 0.43^{\beta-1} \eta_{0.02}^{-1}
+M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}
 \label{eq:condRatio1}
@@
 conductive heating is important near the stagnation radius for high
-values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
-but that it is safely neglected to first order for lower heating
-rates. {\bf AG:Should probably include mass. Although this is tricky
-  as cusp and core galaxies have opposite dependencies on mass.}
+values of $v_{\rm w} \gtrsim 300$ km s$^{-1}$ and $\eta=0.02$, but
+that it is safely neglected to first order for lower heating
+rates. {\bf AG:Note that threshold vw is rather--the 300 km/s is
+  estimated for cusp galaxies. The change in normalization is due to
+  the change in the fiducial eta from 0.1 to 0.02. This seems like bad
+  news. Should probably include mass. Although this is tricky as cusp
+  and core galaxies have opposite dependencies on mass. Perhaps we
+  will have to lean on the saturated argument more if we really would
+  like to avoid conductivity. Or perhaps including conductivity is
+  truly unavoidable. ):}
 
@@
     2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
+    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
     5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
+    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
   \end{cases}
@@
     1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
-    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
+    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
     2.4 \times 10^{-5} \Mbheight^{0.48} 
-    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
+    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
   \end{cases}
@@
   && \begin{cases}
-    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\chi^{2.2}\,{\rm g\,cm^{-3}}
+    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
     & \text{core} \\
-    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}\chi^{3.6}
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
     \,{\rm g\,cm^{-3}}  & \text{cusp}, 
@@
 \begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}(\rs)},
+  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff(\rs)},
   \label{eq:mdot_gas}
@@
 
+Note that combining equations~\eqref{eq:mdot_analytic}
+and~\eqref{eq:mdot_gas} we can rewrite the $\rho(\rs)$
+
+\begin{align}
+\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
+\label{eq:rhors2}
+\end{align}
+
 \subsection{Comparison with Bondi Accretion}
-The spherical accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and density is given by (\citealt{Bondi52}) 
+The spherical accretion rate onto a point source from a surrounding
+medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and
+density is given by (\citealt{Bondi52})
 \begin{align}
@@
 \begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
+  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff} =\frac{4
+    \pi}{3} \rs^2 \rho(\rs) v_{\rm ff}(\rs)
 \end{align}
@@
 
-Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 200, 500, 1000 km s$^{-1}$.
-
-Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
-As expected, the gas density increases towards the SMBH.
-For some profiles (e.g.
-NGC1172 and NGC4478) the density $\rho$ follows a power law from the stagnation radius (squares in Fig.~\ref{fig:profiles}) inwards $\rho \propto r^{-n}$ with $n \approx 1$.
-Note that this is shallower than the $-3/2$ power law for Bondi accretion.
-However, the power law behavior does not extend through all radii, and the gas density profile may have breaks mirroring those in the stellar density profile.
-For example, NGC4365 has a prominent break in the gas density profile, near the stagnation radius.
-This coincides with the location
-of the break in the stellar light profile ($\rb$). The temperature profile is relatively flat at large radii, but increases as $\propto
-1/r^{k}$ interior to the sphere of influence, where $k$ is smaller than 1--the power expected for virialized gas.  The inwardly
-directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
+Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
+
+Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
+temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
+($\Gamma=0.8$) solutions within our grid.  As expected, the gas
+density increases towards the SMBH $\rho\propto r^{-n}$ with
+$n\simeq1$.  Note that this is shallower than the $-3/2$ power law for
+Bondi accretion. However, the power law behavior does not extend
+through all radii, and the gas density profile has a break coincident
+with the location of the break in the stellar light profile ($\rb=100$
+pc). The temperature profile is relatively flat at large radii, but
+increases as $\propto 1/r^{k}$ interior to the sphere of influence,
+where $k$ is smaller than 1--the power expected for virialized gas.
+The inwardly directed velocity increases towards the hole approaching
+the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
+interior to the sonic point, and then increases outwards towards large
+radii.
 % {\bf BDM: I made this up - in general we need
@@
 % don't have a good physical explanation yet...
-% AG -- I am somewhat concerned about boundary effects in
-% NGC3115. Perhaps the break in the gas density profile is due to
-% boundary effects--I know that in this case the break is not
-% associated with a break in the stellar density profile
-
-Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.
-Cusp and core galaxies are marked with square and triangles, respectively.
-%The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}
-
-Our results for $r_{\rm s}/r_{\rm soi}$ can be compared directly to our analytic estimate in equation \ref{eq:stag_analytic}.
-The bottom panel of Figure \ref{fig:stag} shows the fractional difference between our numerical and analytic results for $r_{\rm s}/r_{\rm soi}$.
-The generally good agreement (especially for $v_{w,0}$ = 500, 1000 km s$^{-1}$) provides a useful check of the numerical results.
+
+Figure~\ref{fig:stag} (top panel) shows numerical results for the
+stagnation radius $r_{\rm s}$ where the radial velocity goes to zero
+(expressed in ratio to the radius of the SMBH sphere of influence
+$r_{\rm soi}$), with different colors representing different values of
+$v_{w,0}$.  Cusp and core galaxies are marked with square and
+triangles, respectively.
+
+We also show the simplified analytic result corresponding to $\rs$
+approximated from \eqref{eq:stag_simple} as a solid black line. For
+$\vwO$, we find good agreement with the analytic prediction. However,
+\eqref{eq:stag_simple} is only valid that $\Mstar(\rs) \ll \Mbh$, and
+this approximation breaks down for small $\vwO$. In fact, $\rs$
+diverges for smaller $\vwO$.
+
+{\bf AG perhaps it would be better to solve the implicit equation for
+  rs/rsoi, and plot this in the top panel--assuming a fixed n of say
+  1}. We may also compare our numerical results $r_{\rm s}/r_{\rm
+  soi}$ an be compared directly to our analytic estimate in equation
+\ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag}
+shows the fractional difference between our numerical and analytic
+results for $r_{\rm s}/r_{\rm soi}$.  The good agreement provides a
+useful check of the numerical results.
 
@@
   \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
-    interior X-ray luminosity ({\it bottom}), calculated for three
-    characteristic galaxies from our samples: NGC1172 ({\it blue}),
-    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
-    styles denote different values of the effective wind heating rate,
-    $v_{w,0}$=500 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
-     dot-dashed}).}
+    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
+    and interior X-ray luminosity ({\it bottom}) calculated for the
+    cusp galaxies ($\Gamma=0.8$) within our grid.  Different colors
+    denote different values of the effective wind heating rate,
+    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
+      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
+    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
+    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
+    $\Mbh=10^8 \Msun$ ({\it dashed}). Squares mark out the location of
+    the stagnation radius for each solution.
+ }
 \end{figure}
@@
     to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$,
+    blue symbols represent $v_{w,0} =$ 300, 600, and 1200 km s$^{-1}$,
     respectively.  Squares correspond to cusp galaxies, while
@@
 
-\subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.
-
-Main sequence winds, though contributing a much smaller quantity of mass, have much higher velocities and hence contribute a
+\subsubsection{Stellar winds} 
+{\bf AG: This section may have to be substantially modified in light
+  of our more careful analysis of stellar winds.}
+
+Although most of the mass supplied to the CNM by stellar winds occurs
+during the giant AGB phase, these winds represent a negligible heating
+source compared to the random wind velocity because the wind velocity
+$\lesssim 40$ km s$^{-1}$ is much less than the stellar potential
+$\sigma$.
+
+Main sequence winds, though contributing a much smaller quantity of
+mass, have much higher velocities and hence contribute a
 disproportionally large share of the kinetic energy of winds.
-\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.
-On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.
-In what follows below, we take an effective stellar wind heating rate
-\be
-v_{\rm w,0}^{\star} =  150\,{\rm km\,s^{-1}}
-\ee
-In Appendix \ref{app:windheat} we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age ({\bf BDM: Nick can create}).
+\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim
+100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
+stellar population.  On the other hand, for a very young stellar
+population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
+heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
+s$^{-1}$.  In what follows below, we take an effective stellar wind
+heating rate \be v_{\rm w,0}^{\star} = 150\,{\rm km\,s^{-1}} \ee In
+Appendix \ref{app:windheat} we present a toy model for how $v_{\rm
+  w,0}$ varies as a function of stellar age ({\bf BDM: Nick can
+  create}).
 
@@
   v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
-&\approx&  40\epsilon^{1/2}\left(\frac{\bar{L}_{\rm sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \left(\frac{\eta}{0.1}\right)^{-1/2}\,{\rm km\,s^{-1}},
+  &\approx& 90\epsilon^{1/2}\left(\frac{\bar{L}_{\rm
+        sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2}
+  \eta_{0.02}^{-1/2}\,{\rm km\,s^{-1}},
   \end{align}
@@
   where $\epsilon< 1$ is the thermalization efficiency of the wind.
-The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we assume in the numerical estimate.
-Using the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate the average spin-down luminosity of millisecond pulsars in the field (excluding those in globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, in which case $v_{\rm w,0}$ is negligibly small even for $\eta = 0.1$ and $\epsilon = 1$.
-
-If we assume a higher spin-down luminosity $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi pulsars, then we find that $v_{\rm w,0}^{\rm p} \simeq 120\epsilon^{1/2} (\eta/0.1)^{-1/2}$ km s$^{-1}$, in which case MSP heating can be comparable to main sequence wind heating for $\eta = 0.1$, $\epsilon = 1$.
-However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
-Also, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population.
+  The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass
+  $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to
+  $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we
+  assume in the numerical estimate.  Using the ATNF radio pulsar
+  catalog (\citealt{Manchester+05}), we estimate the average spin-down
+  luminosity of millisecond pulsars in the field (excluding those in
+  globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg
+  s$^{-1}$ {\bf For eta=0.02 we cannot really
+    say that vw from msps is negligible}
+
+  If we assume a higher spin-down luminosity $L_{\rm sd}\simeq
+  10^{35}$ ergs s$^{-1}$ characteristic of some Fermi pulsars, then we
+  find that $v_{\rm w,0}^{\rm p} \simeq 270\epsilon^{1/2}
+  (\eta/0.1)^{-1/2}$ km s$^{-1}$, in which case MSP heating can be
+  comparable to main sequence wind heating for $\eta = 0.1$, $\epsilon
+  = 1$.  However, much lower thermalization efficiencies of $\epsilon
+  \lesssim 0.1$ are inferred based on modeling the insterstellar
+  mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
+  Also, the binaries giving rise to MSPs may be disocciated by stellar
+  interactions in the dense nuclear cluster, reducing their numbers as
+  compared to the field population.
 \subsubsection{Type Ia Supernovae}
 
-Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the instellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}])
-\begin{align}
-    v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
-\end{align}
-The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq \epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$ with which the blast wave energy is converted into bulk or turbulent motion instead of being lost to radiation.
-\cite{Thornton+98} estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$, depending weakly on surrounding density, but \citet{Sharma+14} argues that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if the SNe occur in a hot dilute medium, as may characterize the CNM.
-
-The Ia SN rate $\RateIa$ depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
-In the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.
-The observationally inferred DTD (Fig.
-1 of \citealt{MaozMannucci+:2012a}) has the approximate functional form
-\begin{align}
-    R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
+Energy injected by Type Ia supernovae (SNe Ia) represents a
+potentially important source of heating, which unlike core collapse
+SNe is present even in an evolved stellar population.  Assuming that
+each Ia injects a thermal energy $E_{\rm Ia}$ into the interstellar
+medium, and that the SNe rate (per stellar mass) is given by $R_{\rm
+  Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm
+  Ia}$ produces an effective wind heating parameter
+(equation~[\ref{eq:vw_eff}])
+\begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
+\end{align} The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq
+\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$
+with which the blast wave energy is converted into bulk or turbulent
+motion instead of being lost to radiation.  \cite{Thornton+98}
+estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$,
+depending weakly on surrounding density, but \citet{Sharma+14} argues
+that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
+the SNe occur in a hot dilute medium, as may characterize the CNM.
+
+The Ia SN rate $\RateIa$ depends on the age of the stellar population,
+as it represent the convolution of the star formation rate and the Ia
+delay time distribution (DTD) divided by the present stellar mass.  In
+the limit of impulsive star formation, $\RateIa$ is the DTD evaluated
+at the time since the star formation episode.  The observationally
+inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
+approximate functional form
+\begin{align}
+  R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm
+      h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
 \label{eq:DTD}
   \end{align}
-where $\tau_{\star}$ is the time since star formation (c.f.~\citealt{Scannapieco&Bildsten05}).
-
-Using equations (\ref{eq:vw_sne}), (\ref{eq:DTD}), and (\ref{eq:eta}) we thus estimate that
-\be
-v_{w,0}^{\rm Ia} \approx 250(\epsilon_{\rm Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.07}\,{\rm km \,s^{-1}},
-\ee
-showing that the effective velocity due to SN heating is (coincidentally) a weak function of the stellar age.
-
-The relatively high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent a potentially dominant source of non-AGN heating in the CNM.
-However, SNe can only be approximated as "constant" heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest
+  where $\tau_{\star}$ is the time since star formation
+  (c.f.~\citealt{Scannapieco&Bildsten05}). {\bf AG:I deleted the extra
+    factor of $\chi$ that was hanging out here.}
+
+  Using equations (\ref{eq:vw_sne}), (\ref{eq:DTD}), and
+  (\ref{eq:eta}) we thus estimate that
+
+  \begin{align} 
+    v_{w,0}^{\rm Ia} \approx 700(\epsilon_{\rm
+      Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.09} \eta_{0.02}^{-1/2}\,{\rm km
+      \,s^{-1}},
+  \end{align}
+
+ showing that the effective
+  velocity due to SN heating is (coincidentally) a weak function of
+  the stellar age.
+
+  The relatively high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe
+  represent a potentially dominant source of non-AGN heating in the
+  CNM.  However, SNe can only be approximated as "constant" heating
+  source throughout space and time if the rate of SNe is rapid
+  compared to the inflow time at the radius of interest
   (\citealt{ShcherbakovWong+:2014a}).  To estimate when this
@@
   \begin{align}
-r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \sim 38 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc} 
+    r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \sim
+    38 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc}
     \label{eq:rIa}
@@
 dispersion using the $M_{\bullet}-\sigma$ relationship
-(equation~[\ref{eq:Msigma}]).
-Between subsequent supernova, stars release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm gas}\sigma^{2}$.
-Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
-
-Note that the stagnation radius scales approximately linearly with $M_{\bullet}$ (equation~[\ref{eq:stag_simple}]), while $\rIa$ is roughly indpendent of SMBH mass.
-For small $\Mbh$, the stagnation radius thus lies well inside $\rIa$ and hence Ia SNe will not contribute appreciably to the heating rate.
-On the other hand, for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia  represent an important, and possibly dominant, contribution to the overall heating.
+(equation~[\ref{eq:Msigma}]).  Between subsequent supernova, stars
+release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm
+Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally
+bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm
+gas}\sigma^{2}$.  Thus, according to the above definitions, $E_{\rm
+Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
+
+Note that the stagnation radius scales approximately linearly with
+$M_{\bullet}$ (equation~[\ref{eq:stag_simple}]), while $\rIa$ is
+roughly indpendent of SMBH mass.  For small $\Mbh$, the stagnation
+radius thus lies well inside $\rIa$ and hence Ia SNe will not
+contribute appreciably to the heating rate.  On the other hand, for
+massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia represent an
+important, and possibly dominant, contribution to the overall heating.
 
@@
 
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm w,0}^{-\beta}$, where in the last proportionality we have used equation (\ref{eq:stag_simple}).
-Hence, when SMBH heating dominates, it may ``self-regulate" itself.
+For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm
+  w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm
+  w,0}^{-\beta}$, where in the last proportionality we have used
+equation (\ref{eq:stag_simple}).  Hence, when SMBH heating dominates,
+it may ``self-regulate" itself.
 
 What is a physically motivated value of $r_{\rm heat}$?
-\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half opening angle $\theta_{\rm j} = 0.1$ (similar to those of AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a timescale
+\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half
+opening angle $\theta_{\rm j} = 0.1$ (similar to those of AGN jets)
+propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a
+timescale
 \begin{eqnarray}
@@
 
-Figure~\ref{fig:vweff} shows an estimate of how the combined heating depends on the age of the stellar population $\tage$ and the SMB mass $\Mbh$.
-For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}]) to contribute their full heating rate.
-$v_{\rm w,0}^{\rm Ia} \sim 250$ km s$^{-1}$.
-On the other hand, for lower mass BHs Ia SNe are infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star} \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of interest.\footnote{Although SN Ia will still occur surrounding low mass SMBHs, if they are infrequent interior to the radius where the accretion rate is being set, then they will not affect the flow near the SMBH at most epochs.}  For very young stellar populations ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to contributions from line driven winds from high mass main sequence stars.
+Figure~\ref{fig:vweff} shows an estimate of how the combined heating
+depends on the age of the stellar population $\tage$ and the SMB mass
+$\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
+  h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
+stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
+to contribute their full heating rate.  $v_{\rm w,0}^{\rm Ia} \sim
+250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
+infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star}
+\simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
+interest.\footnote{Although SN Ia will still occur surrounding low
+  mass SMBHs, if they are infrequent interior to the radius where the
+  accretion rate is being set, then they will not affect the flow near
+  the SMBH at most epochs.}  For very young stellar populations
+($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
+contributions from line driven winds from high mass main sequence
+stars.
+{\bf AG: We should mention that regime with stellar wind heating only
+  is likely to be thermally unstable.}
 
@@
       corresponding to the resulting $\vwO$ is outside
-      $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on time! among other things}}%describe other cases here.
+      $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on time!
+      among  other things}}%describe other cases here.
   \end{figure}
@@
 $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 150, 300 and 600 km s$^{-1}$, and for both core
-($\gamma$=0.1) and cusp galaxies ($\gamma$=0.8).
+values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for
+both core ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
 
@@
 expected to be a sensitive function of the assumed heating rate.
-However, the accretion rate is proportional to the stellar mass
-enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh
-(\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh
-(\rs/\rsoi)$.  This steeper dependence is enough to offset the
-tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed
-$\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core
-galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
-$\vwO=600$ km s$^{-1}$, core galaxies have a smaller accretion rate
-for a given SMBH mass. On the other hand, if  $\rs/\rsoi>1$ (as would
-be expected for small $\vwO$), core galaxies would have a larger
-accretion rate. Thus, for $\vwO=150$ km/s, core galaxies have a large
-accretion rate for a given $\Mbh$.  
+% However, the accretion rate is proportional to the stellar mass
+% enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh
+% (\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh
+% (\rs/\rsoi)$.  This steeper dependence is enough to offset the
+% tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed
+% $\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core
+% galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
+% $\vwO=600$ km s$^{-1}$, core galaxies have a smaller accretion rate
+% for a given SMBH mass. On the other hand, if  $\rs/\rsoi>1$ (as would
+% be expected for small $\vwO$), core galaxies would have a larger
+% accretion rate. Thus, for $\vwO=150$ km/s, core galaxies have a large
+% accretion rate for a given $\Mbh$.
+
 %% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
@@
 
-This is shown in the top panel Figure~\ref{fig:bh_xray}. The
-relationship from \citealt{MillerGallo+:2014a} and their detection
-upper limits are the black and blue solid lines
-respectively. The points correspond to the $\dot{M} c^2$ for our
-solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
-each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
-heating expected from main sequence the stellar winds and MSPs. If
-$L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
-bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
-10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
-\citealt{MillerGallo+:2014a}.
-
-One possible solution that the wind mass loss rate $\eta$ decreases
+% This is shown in the top panel Figure~\ref{fig:bh_xray}. The
+% relationship from \citealt{MillerGallo+:2014a} and their detection
+% upper limits are the black and blue solid lines
+% respectively. The points correspond to the $\dot{M} c^2$ for our
+% solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
+% each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
+% heating expected from main sequence the stellar winds and MSPs. If
+% $L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
+% bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
+% 10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
+% \citealt{MillerGallo+:2014a}.
+
+One possible solution that the wind mass loss rate $\eta$ increases
 with $\Mbh$, as would be expected if low mass SMBH preferentially
-hosted older stellar populations.  Another possible explanation is
+hosted younger stellar populations.  Another possible explanation is
 that the effective heating rate of the CNM $v_{\rm w,0}$ decreases
@@
 sources such as SN Ia and millisecond pulsars.
+{\bf AG given our new results on stellar wind heating as a function of
+Mbh. It seems like the first statement is indeed true but I suspect
+vwO actually increases for low Mbh and that this effect actually dominates.}
 %, or it could be due to the fact that Ia occur too infrequently inside
@@
     for each galaxy in our sample, calculated for different values of
-    the wind heating parameter $\vwO =$ 150 km s$^{-1}$ ({\it green}),
-    600 km s$^{-1}$ ({\it orange}), and 1000 km s$^{-1}$ ({\it blue}).
-    Squares correspond to cusp galaxies ($\gamma=0.8$), while
-    triangles correspond to cores ($\gamma$=0.1). The curves correspond
+    the wind heating parameter $\vwO =$ 300 km s$^{-1}$ ({\it green}),
+    600 km s$^{-1}$ ({\it orange}), and 1200 km s$^{-1}$ ({\it blue}).
+    Squares correspond to cusp galaxies ($\Gamma=0.8$), while
+    triangles correspond to cores ($\Gamma$=0.1). The curves correspond
     to the analytic results for $\eddr$ from equation
@@
 \subsection{Comparison to Observations}
-\subsubsection{Comparison to measured temperature and density profiles}
-\citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.
+{\bf AG: I do want some discussion of reproducing the density profiles
+for individual observations, but I am not sure how to do it with our
+new gridded approach.}
+% \subsubsection{Comparison to measured temperature and density profiles}
+% \citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.
 \citet{RussellMcNamara+:2013a} performed a similar analysis with a somewhat enlarged galaxy sample.
 Interestingly, these works find a correlation between the accretion rate inferred assuming Bondi accretion and the AGN jet power, which is estimated by the PdV work required to inflate observed cavities in the X-ray emitting gas.
-% At some point it would be useful to describe the differences between
-% these two sets of observations \citealt{RussellMcNamara+:2013a}
-% tries several different extrapolation schemes for the gas density,
-% and finds that that the uncertainty in extrapolating the density
-% profile is the dominant source of uncertainty in measuring the
-% accretion rate. Find total number which overlaps once the Russell
-% galaxies are included...
-
-Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.
+% % At some point it would be useful to describe the differences between
+% % these two sets of observations \citealt{RussellMcNamara+:2013a}
+% % tries several different extrapolation schemes for the gas density,
+% % and finds that that the uncertainty in extrapolating the density
+% % profile is the dominant source of uncertainty in measuring the
+% % accretion rate. Find total number which overlaps once the Russell
+% % galaxies are included...
+
+% Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.
 We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
@@
 
-Note that we have two free parameters ($\eta$ and $\vwO$) in our
-model, which implies that we can always match the observed temperature
-and densities at at least one point.  As a general rule, we find that
-a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
-with the observed temperatures.  We now highlight results for specific
-galaxies.
-% Thus, we choose $\vwO=500$ km/s.  We choose an
-% $\eta$ so that our solution would be consistent with the observed
-% density profiles. The comparison is shown in
-%% AG-The chosen properties, in particular eta may be summarized in a table.
-%% AG-Mention rising temperature profiles on large scales.
-
-\begin{itemize}
-% \item \emph{NGC4486} %eta=0.2
-%   On scales of $\sim1$ kpc the density profile in
-%   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
-%   has a break in the gas density at $\sim 300$ pc--near the location
-%   of the Nuker break radius for this galaxy at 560 pc. There is an
-%   observed break in the density, but on a scale of a few kpc.
-
-%   The temperature is assumed to be flat from the resolution limit
-%   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
-%   increases monotonically towards the galactic center. This increase
-%   is due to the increased velocity dispersion (and thus increased
-%   heating) towards the galactic center.
-
-\item \emph{NGC5813} %eta=0.1 
-  The observed density profile (\citealt{RussellMcNamara+:2013a}) is
-  shallower than our calculated density profile, which has a sharp
-  break at $\sim$0.1 kpc, the location of the break radius in the
-  Nuker profile (this is the radius where the stellar light profile
-  transitions from a shallower inner power law slope to a steeper
-  outer power law slope).
-
-  For this galaxy we found that we could reproduce the observed
-  temperature on large scales with $\vwO=500$ km/s. The increased
-  velocity disperision towards the galactic center results in a sharp
-  increase in $T$ at small radii, which is not captured in the
-  observations due to resolution issues.
-\end{itemize}
-
-%It would be nice to have error bars for the observational points in this plot...
-\begin{figure*}
-  \includegraphics[width=\columnwidth]{NGC5813_T.eps}
-  \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
-  \caption{\label{fig:allen_compare} Comparison of the radial profiles
-    (blue lines) of electron number density $n_e$ and temperature $T$
-    to the measured values (black square) in \citet{AllenDunn+:2006a}
-    and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
-    power law extrapolations of our profiles. Note that in going from
-    $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
-  %% AG in the future we will have to be carfeful of the mean molecular weight.
-\end{figure*}
+% Note that we have two free parameters ($\eta$ and $\vwO$) in our
+% model, which implies that we can always match the observed temperature
+% and densities at at least one point.  As a general rule, we find that
+% a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
+% with the observed temperatures.  We now highlight results for specific
+% galaxies.
+% % Thus, we choose $\vwO=500$ km/s.  We choose an
+% % $\eta$ so that our solution would be consistent with the observed
+% % density profiles. The comparison is shown in
+% %% AG-The chosen properties, in particular eta may be summarized in a table.
+% %% AG-Mention rising temperature profiles on large scales.
+
+% \begin{itemize}
+% % \item \emph{NGC4486} %eta=0.2
+% %   On scales of $\sim1$ kpc the density profile in
+% %   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
+% %   has a break in the gas density at $\sim 300$ pc--near the location
+% %   of the Nuker break radius for this galaxy at 560 pc. There is an
+% %   observed break in the density, but on a scale of a few kpc.
+
+% %   The temperature is assumed to be flat from the resolution limit
+% %   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
+% %   increases monotonically towards the galactic center. This increase
+% %   is due to the increased velocity dispersion (and thus increased
+% %   heating) towards the galactic center.
+
+% \item \emph{NGC5813} %eta=0.1 
+%   The observed density profile (\citealt{RussellMcNamara+:2013a}) is
+%   shallower than our calculated density profile, which has a sharp
+%   break at $\sim$0.1 kpc, the location of the break radius in the
+%   Nuker profile (this is the radius where the stellar light profile
+%   transitions from a shallower inner power law slope to a steeper
+%   outer power law slope).
+
+%   For this galaxy we found that we could reproduce the observed
+%   temperature on large scales with $\vwO=500$ km/s. The increased
+%   velocity disperision towards the galactic center results in a sharp
+%   increase in $T$ at small radii, which is not captured in the
+%   observations due to resolution issues.
+% \end{itemize}
+
+% %It would be nice to have error bars for the observational points in this plot...
+% \begin{figure*}
+%   \includegraphics[width=\columnwidth]{NGC5813_T.eps}
+%   \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
+%   \caption{\label{fig:allen_compare} Comparison of the radial profiles
+%     (blue lines) of electron number density $n_e$ and temperature $T$
+%     to the measured values (black square) in \citet{AllenDunn+:2006a}
+%     and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
+%     power law extrapolations of our profiles. Note that in going from
+%     $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
+%   %% AG in the future we will have to be carfeful of the mean molecular weight.
+% \end{figure*}
 
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{bh_xray.eps}
-\caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
-  stellar mass for our solutions (points), the trend of nuclear x-ray
-  luminosity with stellar mass (black line) and the detection upper
-  limit (blue line) from Fig. 1 of \citealt{MillerGallo+:2014a}. In
-  the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
-  c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
-  luminosities comparable to those observed. In the bottom panel, we
-  take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
-  \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
-  we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{bh_xray.eps}
+% \caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
+%   stellar mass for our solutions (points), the trend of nuclear x-ray
+%   luminosity with stellar mass (black line) and the detection upper
+%   limit (blue line) from Fig. 1 of \citealt{MillerGallo+:2014a}. In
+%   the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
+%   c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
+%   luminosities comparable to those observed. In the bottom panel, we
+%   take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
+%   \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
+%   we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
+% \end{figure}
 
@@
     250 M_{\bullet,8}^{-0.76}
-    v_{500}^{3.8} \chi^{3.8}  \eta_{0.02}  & \text{core} \\
+    v_{500}^{3.8}   \eta_{0.02}  & \text{core} \\
     140 \Mbheight^{-0.48}
-    v_{500}^{2.4} \chi^{2.4}  \eta_{0.02}  & \text{cusp}, 
+    v_{500}^{2.4}   \eta_{0.02}  & \text{cusp}, 
   \end{cases}
@@
   \begin{cases}
-   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}\chi^{7.2}  &, \text{core}\\
-   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}\chi^{5.8}  &, \text{cusp},     
+   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
+   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
   \end{cases}
@@
 rapid, the gas loses thermal pressure and starts to inflow faster,
-i.e. the entire CNM accretes (e.g. ).  In
+i.e. the entire CNM accretes (e.g. {\bf AG citation missing here.}).  In
 practice this should could manifest as a large increase in the
@@
 
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\be
-t_{\rm cool} \equiv \frac{3n kT/2}{\dot{q}_{\rm cool}}
-\ee 
-is locally shorter than the approximately 10 times the free-fall timescale $t_{\rm ff}$.
-
-Using equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), (\ref{eq:rhors}), (\ref{eq:cooling}), (\ref{eq:cooling2}), we can estimate the ratio of the cooling timescale to the free-fall time $\sim r/\sigma$ at the stagnation radius
-\begin{align}
-  \left.\frac{t_{\rm cool}}{t_{\rm ff}}\right|_{r_{\rm s}}\simeq
-  \begin{cases}
-    560 \Mbheight^{-0.76} \eta_{0.02}^{-1}(\chi v_{500})^{7.2}, & \text{core}\\
-    310  \Mbheight^{-0.48} \eta_{0.02}^{-1}(\chi v_{500})^{5.8} ,   & \text{cusp}
-  \end{cases}
-  \label{eq:coolingratio}
-\end{align}
-We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the
-stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if
-$\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
-
-Fig.~\ref{fig:cooling} shows $t_{\rm cool}/t_{\rm ff}$ as a function of radius for all of our solutions {\bf BDM: change plots}, with different colors denoting different values of $v_{w,0}$.
-For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.
-With a few exceptions this is also true for $\vwO$=500 km s$^{-1}$.
-However, for our lowest heating rate $\vwO$=200 km s$^{-1}$ cooling may be quite important, especially for high $\eta$ (young stellar population;  Appendix~\ref{app:eta}).
-
-For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
+However, \citet{McCourt+12} argue that even if cooling is exactly
+balanced by heating everywhere, there is still a local thermal
+instability that operates to turn hot gas into cold clouds.  However,
+this local instability only causes a significant local drop-out of
+mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$.
+
+At the stagnation $\tcool/\tff$ is equal to the ratio of the heating to
+the cooling rate to factors of order unity as shown below
+
+\begin{align}
+\left. \frac{\tcool}{\tff}\right|_{\rs}&=\left. \frac{3}{5} \frac{\rho 
+  \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}\\
+&=\frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}.
+\end{align}
+
+In the first line we have used equation~\eqref{eq:Tanalytic} and in
+the second line we have used equation~\eqref{eq:rhors2}.
+
+Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
+as a function of radius for all of our solutions. {\bf BDM: change
+  plots}, with different colors denoting different values of $\vwO$.
+For our highest heating rates we observe that cooling is unimportant
+for all solutions across all radii--neither the local nor the global
+thermal instability would be present. However,  for our smallest value
+of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
+thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
+precise region of the parameter space which would be thermally
+unstable would depend on the value of $\eta$--in
+Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
+appropriate for a stellar population with $\tage\simeq \th$. This
+value is on the low end of what we would physically expect for
+$\eta$.
+
+For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
+$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
+diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
+approximation away from $\rs$. Similarly, it is poorer approximation
+for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
+closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
+  clarify the physics here a little more.}
+
+% For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
 Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
@@
   \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
-    ($C$) for each of our solutions. The cooling rate is calculated
-    using the approximate (solar metallicity) cooling function in
-    Equation~(\ref{eq:cooling}). The heating rate is estimated as $q
-    \vw^2/2$. The ratio is computed from equation (\ref{eq:cooling})
-    assuming a stellar mass loss rate parameter $\eta=1$.}
+    ($C$) for each of our solutions (solid lines). The cooling rate is
+    calculated using the approximate (solar metallicity) cooling
+    function in Equation~(\ref{eq:cooling}). The heating rate is
+    estimated as $q \vw^2/2+q v^2/2$. The ratio is computed from
+    equation (\ref{eq:cooling}) assuming a stellar mass loss rate
+    parameter $\eta=0.02$. We also plot the ratio $\tcool/\tff$
+    vs. radius. $H/C$ is a diagnostic for global thermal stability,
+    and a solution should be stable as long as
+    $H/C\gsim1$. $\tcool/\tff$ is a diagnostic for local thermal
+    instability, solutions should be stable as long as $\tcool/t_{\rm
+      ff}\gsim$10 \citealt{McCourt+12}. Notice that for high $\vwO$
+    the two ratios coincide at $\rs$ (marked with a square for each
+    solution).}
 \end{figure}
 
-\input{figures/eta_tab.tex}
+%\input{figures/eta_tab.tex}
 
@@
 
-  We may rewrite the specific angular momentum at $\rs$ in terms of $\lambda_R$.
+  We may rewrite the specific angular momentum at $\rs$ in terms of
+  $\lambda_R$.
 
@@
   The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
-  $\rsoi$. %%AG-Need to explain this somehow.
+  $\rsoi$. {\bf AG need to explain this somehow. Also, note in our
+    simulations the inner sonic point is not properly resolved.}
   So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Fig. 2 of
@@
     possible solution that the wind mass loss rate (i.e. $\eta$)
-    decreases with $\Mbh$, as would be expected if low mass SMBH
+    increases with $\Mbh$, as would be expected if low mass SMBH
     preferentially hosted younger stellar populations. Another possible
@@
 
-  % \section{Analytic model for dependence of wind mass loss rate on stellar age}
-  % \label{app:eta}
-%  \input{eta}
-
-\section{Analytic model for dependence of wind heating $v_{\rm w,0}^{\star}$ on stellar age}
+\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
 \label{app:windheat}
-If we assume that a stellar population forms impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any future time $t$ is given by
-\begin{equation}
-f(t) =\frac{ \int_{m_0}^{m_{\rm max}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
-\end{equation}
-where 
-\begin{equation}
-m_{\rm max}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
-\end{equation}
-For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
-\begin{equation}
-f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
-\end{equation}
-{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
-If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
-\begin{equation}
-q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm max}(t)) m_{\rm max}(t) \frac{df}{dt},
-\end{equation}
-where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm max}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
-\begin{equation}
-q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
-\end{equation}
-This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
-Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
-Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
-Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{NickPlot.eps}
-\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
-The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
-Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
-\end{figure}
-
-In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
-function of time, for three different stellar density profiles $\Gamma
-= \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
-influence radius $r
-_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).  We parametrize the wind velocity as 
-\begin{equation}
-\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
-\end{equation}
-The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
-We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
-Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
+\input{windheat}
+
   \footnotesize{

### 2014-12-14 ms.tex
Fixing description of velocity profile

@@
 The inwardly directed velocity increases towards the hole approaching
-the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
-interior to the sonic point, and then increases outwards towards large
-radii.
+The inwardly directed velocity is steeper than what would be expected
+for the free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
 % {\bf BDM: I made this up - in general we need

### 2014-12-15 ms.tex
mispelled alskeys middlename

@@
 
-\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
+\author[Generozov, Stone, \& Metzger]{Aleksey S. Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
   Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

### 2014-12-16 ms.tex
mispelled alskeys middlename
updated 2.1

@@
 \subsection{Galaxy models}
-\citealt{LauerFaber+:2007a} used Hubble WFPC2 imaging to measure the
-surface brightness profiles for hundred of nearby early type
-galaxies. The measured surface brightness profile can generally be
-well fit using a Nuker law
-
+\citet{LauerFaber+:2007a} use Hubble WFPC2 imaging to measure the
+radial surface brightness profiles for hundreds of nearby early type galaxies. The measured surface brightness profile is generally well-fit by a ``Nuker" law parameterization:
 \begin{equation}
@@
 \end{equation}
-The Nuker profile is a broken power law which transitions from an
-inner power law slope, $\Gamma$, to an outer power law slope, $\beta$,
-at a break radius, $\rb$.
-
-Assuming spherical symmetry this corresponds to a stellar density
-$\rhostar \sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim
-r^{-1-\beta}$ for $r \gg \rb$. Thus, we adopt a broken power law for 
-$\rhostar$
-
+
+The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+Assuming spherical symmetry, this corresponds to a stellar density $\rhostar \sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r \gg \rb$, thus motivating us to adopt a broken power-law profile
 \begin{align}
@@
 \end{align}
-
-where $\rho_\star(\rsoi)$ is the stellar density at the black hole
-sphere of influence, $\rsoi$. $\rho_\star(\rsoi)$ is chosen so that
-the stellar mass inside $\rsoi$, $\Mstar(\rsoi)$, is equal to the
-black hole mass.  $\rsoi=G \Mbh/\sigma^2$. Using the $\Mbh-\sigma$ relation
-from \citealt{Gultekin+09}
-
+where $\rho_\star(\rsoi)$ is the stellar density at the radius of the black hole sphere of influence, 
+\be
+\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6},
+\label{eq:rsoi}
+\ee
+and the final equality in (\ref{eq:rsoi}) employs a recent version of the $\Mbh-\sigma$ relationship (\citealt{Gultekin+09}),
  \begin{align}
 M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
-      km\,s^{-1}}}\right)^{5.1}M_{\odot}, 
+      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
 \label{eq:Msigma}
@@
 
-we obtain $\rsoi \approx 14 M_{\bullet,8}^{0.6}$. In order to
-completely specify the galaxy model we must choose $\Mbh$, $\Gamma$, $r_b$,
-and $\beta$. We compute models for three different models of
-$\Mbh$: $10^6$, $10^7$, $10^8 \Msun$. In the
-\citealt{LauerFaber+:2007a} sample the distribution of the $\Gamma$s
-is bimodal, with a concentration of core galaxies with $\Gamma \lsim
-0.3$ and a concentration of cusp galaxies with $\Gamma \gsim
-0.7$. We calculate models for $\Gamma=0.8$ and $\Gamma=0.1$.
-
-We are interested in the gas flow on scales smaller than
-the break radius $\rb$, which typically occurs at a radius of 100s of
-parsecs. Thus, we fix $\beta$ to be 2 {\bf AG:I have not yet checked this
-  directly via numerical experiments}.  The presence of $\rb$ is 
-necessary for to obtain a converged steady state for some regions of
-our parameter space. For cusp galaxies, $r_b$ is a few hundred parsecs
-independently of $\Mbh$. We adopt $\rb=100$ pc for our cusp
-galaxies ($\Gamma=0.8$), while for our core galaxy models we use the
-scaling relation...{\bf AG: Need to figure out normalization for
-  scaling relation from Lauer. Fixed rb at a given Mbh only has a
-  factor of a few effect on rs--this will be discussed in the section
-  on numerical solutions.}
-
-% \subsection{Galaxy Sample}
-
-% \label{sec:sample}
-% %AG:It is unclear whether if/how the Nuker profile will show up in
-% %this parametrized study.
-% {\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}
-
-% Our sample includes 61 early-type galaxies from
-% \citetalias{WangMerritt:2004a}, as represent a subset of a larger
-% sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
-% focus on elliptical galaxies because we are interested in isolating
-% SMBHs fed by the steady mass loss from the relatively old stellar
-% population, instead of fresh gas flowing into the sphere of influence
-% from larger scales.
-
-% The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
-% \begin{equation}
-%   I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
-% \end{equation}
-% The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
-
-% Given $I(\xi)$ we follow the procedure outlined by
-% \citetalias{WangMerritt:2004a} to compute the spherically-symmetric
-% stellar density profile $\rhostar(r)$ and stellar mass profile
-% $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
-% our model.  For reference, note that stellar density $\rhostar\sim
-% r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
-% \gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
-% $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
-% thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
-% r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
-% SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
-% %%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
-% %%calculated from an outdated M-sigma. It would be bizarre to use 2
-% %%different relations.
-
-% AG:Is there a systematic dependence of beta on galaxy type$.
-
-%% AG--some discussion of alternate parameterizations.  My intuition
-%% is that for our purposes the parameterization should not
-%% matter. But some discussion of alternate possibilities could
-%% prevent Alistar Graham from yelling at us.
+A galaxy model is fully specified by four parameters: $\Mbh$, $\Gamma$, $r_b$,
+and $\beta$.
+We compute models for three different black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.
+The distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim 0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
+We bracket these possibilities by considering models with $\Gamma=0.8$ and $\Gamma=0.1$.
+Since we are generally interested in properties of the gas flow on radial scales $\ll r_b$, we fix $\beta = 2$ (a typical value), an assumption to which most of our results is not sensitive.
+However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.
+We adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core galaxy models we employ the scaling relation $\rb = $, motivated again by the \citet{LauerFaber+:2007a} sample.
+({\bf BDM: fill in!}).
+Though simplistic, our results are not sensitive to our assumption about the value of $\rb$.
 
@@
 
-The source term in the continuity equation (equation~\ref{eq:drhodt}),
+The source term in the continuity equation (eq.~[\ref{eq:drhodt}]),
 \begin{align}
@@
 
-\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
-\label{app:windheat}
-\input{windheat}
+%\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
+%\label{app:windheat}
+%\input{windheat}
 

### 2014-12-16 ms.tex
updated 2.2

@@
 
-Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the gas density profile $\rho$ of the CNM for each galaxy within our sample by solving the equations of one-dimensional (spherically symmetric) time-dependent hydrodynamics,
+Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the gas density profile $\rho$ of the CNM for each galaxy model by solving the equations of one-dimensional (spherically symmetric) time-dependent hydrodynamics,
 \begin{align}
@@
   &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial
-      v}{\partial r}\right) =-\frac{\partial p}{\partial r}- \rho\frac{GM_{\bf enc}}{r^{2}} -q v \label{eq:dvdt}\\
+      v}{\partial r}\right) =-\frac{\partial p}{\partial r}- \rho\frac{GM_{\rm enc}}{r^{2}} -q v \label{eq:dvdt}\\
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
@@
 enclosed mass.  We assume an ideal gas equation of state with $p =
-\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$. {\bf BDM: take $\mu = 0.62$ here for fully ionized gas}
+\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$. {\bf BDM: take $\mu = 0.62$ here for fully ionized gas - what did you do?}
 
@@
 recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
-years. $\eta\simeq 0.02 \left(\frac{t}{th}\right)^{-1.3}$ 
-(see, e.g., \citealt{Ciotti+91})\footnote{Note that 
-\citealt{Ciotti+91} gives the overall mass return rate from evolved
+years.  To good approximation $\eta\simeq 0.02 (t/t_h)^{-1.3}$ at time $t$ following a burst of star formation (e.g., \citet{Ciotti+91}),\footnote{Note that 
+\citet{Ciotti+91} gives the overall mass return rate from evolved
 stars as a function of B-band luminosity. We give the mass return rate
-per unit volume. However, our expressions are equivalent.}
-
-Source terms $\propto q$ also appear in the momentum and entropy
-equations (equation~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) due to the fact
-that the isotropic mass injection in the rest frame of the SMBH
+per unit volume. However, our expressions are equivalent.} although $\eta$ will generally be higher in cases of ongoing star formation.
+
+Source terms $\propto q$ also appear in the momentum and entropy equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) due to the fact that the isotropic mass injection in the rest frame of the SMBH
 represents a source of momentum and energy relative to the mean flow (see also below).
-%No net momentum is in the winds, but mass is being added which adds a
-%term in the velocity equation...
-
-The second source term in equation (\ref{eq:dsdt}) accounts for
-heating transportation by electron conductivity. We take the
-conductivity to be $\kappa_{\rm eff}=\kappa_{\rm spitzer}/(1+\psi)$,
-as described in \citealt{DaltonBalbus:1993a}. $\kappa_{\rm spitzer}$
-is the classical \citealt{Spitzer62} value, $\kappa_{\rm spitzer} =
-\kappa_0 T^{5/2}$ ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units). The
-term in the denominator is a flux limiter. The conductive flux should
-saturate when the mean free path for electron coulomb scattering
-becomes comparable to the temperature length scale.  More precisely
-$\psi=\frac{\kappa_{\rm spitzer} \nabla T}{5\phi \rho c_s^3}$ (the
-Spitzer conductive flux over the saturated conductive flux; $\phi$ is
-a dimensionless constant of order unity or less). Although even a weak
-magnetic field could in principle strongly suppress the conductivity
-perpendicular to the field, the radially-decreasing temperature
-profiles of interest are susceptible to the magneto-thermal
-instability (\citealt{Balbus01}), the non-linear evolution of which is
-believed to result in a radially-directed field structure
-(\citealt{Parrish&Stone07}).
-
-Following \citet{ShcherbakovWong+:2014a}, the term in the entropy
-equation $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ accounts for external
-heating sources.  Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the
-velocity dispersion of the stars, thus accounting for the fact that at
-a minimum the gas experiences shock heating between the stellar winds
-of velocities moving with respect to each other a characteristic
-velocity $\sim \sigma$.  This heating is present if the wind velocities themselves
-are low, $\ll \sigma$, as characterize the majority of AGB mass loss.
-The term $v_{w,0}^{2}$ parameterizes additional sources of heating,
-such as main sequence winds, millisecond pulsars, supernovae, etc.  As
-discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is
-uncertain and will in general depend on the SMBH mass and the age of
-the stellar population.
+Physically these terms result from the mismatch between the properties of virialized gas injected locally by stellar winds and the mean properties of the background flow.
+As we shall discuss in $\S$, the cooling term $\propto q p/\rho$ represents an important stabilizing term in comparison to radiative cooling.
+
+The last term in equation (\ref{eq:dsdt}) accounts for heat transportation by electron conductivity, where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units).
+The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale.
+Here $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi$ is an uncertain dimensionless constant, typically taken to be of order unity of less (we adopt $\phi = XXX$).
+Even a weak magnetic field could in principle also suppress the conductivity perpendicular to the field.
+However, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
+
+Following \citet{ShcherbakovWong+:2014a}, the term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy equation accounts heating sources.
+Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the velocity dispersion of the stars, accounting for the minimum amount of shock heating from the stellar winds due to the random movement of stars with respect to each other at the characteristic velocity $\sim \sigma$.
+This heating is present even for low wind velocities $\ll \sigma$, as characterize the majority of AGB mass loss.
+The term $v_{w,0}^{2}$ parameterizes the contribution of additional sources of heating, including main sequence winds, millisecond pulsars, supernovae, AGN feedback, etc.
+As discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in general depend on the SMBH mass and the age of the stellar population.
 
@@
 and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for
-different choices of $v_{\rm w,0}$ spanning the physically expected
-range.  Although we are most interested in the steady-state CNM
-structure, the time-dependent equations are solved to avoid numerical
-issues that arise near the critical sonic points, of which there are
-up to two because of the supersonic inflow on small radial scales and
-a possible supersonic outflow on large scales.
-
-We do not include radiative cooling in the entropy equation because
-across much of the parameter space radiative cooling is negligible
-compared to other sources of cooling (e.g., advection).  Although
-radiative cooling cannot be neglected in some cases (especially if
-$\vwO$ is low or $\eta$ is high), our 1D scheme cannot account for the
-true multi-phase behavior of local thermal instabilities anyways
-(e.g.~\citealt{McCourt+12}).  Our steady state solutions neglecting
-radiation can nevertheless be used to ascertain over what parameter
-space cooling instabilities are likely to develop
-($\S\ref{sec:cooling}$).
-%Dependence of the heating to cooling ratio has a far steeper
-%dependence on vwO than on eta...
-
-The accuracy of our numerical solutions is assessed by checking the
-level of conservation of mass across the grid, as well as the integral
-constraint on the energy.  Mass and energy are conserved to $\lesssim
-40$ per cent for all solutions presented in this
-paper. 
+different choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning the physically expected
+range.
+Although we are most interested in the steady-state CNM structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.
+
+Radiative cooling is not included in the entropy equation, although its effect is assessed critically in $\S\ref{sec:cooling}$.
+Across much of the parameter space radiative cooling is negligible compared to other sources of cooling (e.g., advection).
+Radiative cooling cannot be neglected in some cases (if
+$\vwO$ is low and/or $\eta$ is high), once it becomes important it leads to thermal instabilities, which our one-dimensional time-dependent modeal cannot account for anyways (e.g.~\citealt{McCourt+12}).
+A chief goal of this work is instead to use our steady state solutions neglecting radiation to ascertain over what physical conditions cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).
+
+The accuracy of our numerical solutions is assessed by checking the level of conservation of mass across the grid, as well as the integral constraint on the energy.
+Mass and energy are conserved to $\lesssim
+40$ per cent for all solutions presented in this paper. 
 {\bf BDM: more details...}

### 2014-12-16 ms.tex
updated 3.1

@@
 \rho_\star(r_b) \left(r/r_b\right)^{-1-\beta} & r > r_b,
+\label{eq:rhostar}
 \end{cases}
@@
 \be
-\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6},
+\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
 \label{eq:rsoi}
@@
 \end{align}
+Although the use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), our results are not overly sensitive to this assumption.
 
@@
 Radiative cooling is not included in the entropy equation, although its effect is assessed critically in $\S\ref{sec:cooling}$.
-Across much of the parameter space radiative cooling is negligible compared to other sources of cooling (e.g., advection).
+Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling (e.g., advection).
 Radiative cooling cannot be neglected in some cases (if
@@
 
-We begin by describing a number of useful analytic results before describing our numerical solutions.
+We begin by describing useful analytic results before presenting our numerical solutions.
 
 \label{sec:results}
-\subsection{Analytics: Flow properties at $\rs$}
-
-This section summarizes analytic estimates of several physical
-quantities of interest, such as the stagnation radius $\rs$ and the
-mass accretion rate, the detailed derivation of which are given in
-Appendix \ref{app:rs}.  All of our results are derived under the
-assumption that thermal conductivity can be neglected.
-
-When possible our results are expressed in terms of the wind heating
-parameter $\vw$; the power-law slope of the density profile
-$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vwO^2+\sigma^2$,
-where the $\sigma$ accounts for shock heating between stellar winds moving
-with respect to each other with relative velocity $\sigma$, and $\vwO$
-is a free parameter accounting for additional sources of
-heating.  $\vw$ may be calculated analytically (for a given $\Mbh$ and
-$\vwO$) using $\vw=\chi \vwO$, where
-
- \begin{align}
-&\chi^2 \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 +
-  \sigma^{2}/v_{\rm w,0}^{2}\right) \approx \\
-&\left(1+0.14 \Mbheight^{0.43}\frac{\vwO}{500 {\rm km/s}}^{-1}\right), 
-\end{align}
-
-% where $v_{500} $M_{\bullet,8} \equiv
-where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$, and the
-second equality makes use of the $M_{\bullet}-\sigma$ correlation
-(\citealt{Gultekin+09})
-
- \begin{align}
-M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
-      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
-\label{eq:Msigma}
-\end{align}
-
-Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.
-
-First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
+\subsection{Properties near the stagnation radius}
+
+Here we summarize analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
+Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter (eq.~[\ref{eq:dsdt}])
+\begin{eqnarray}
+v_{\rm w} &=& v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2} \nonumber \\
+ &\approx& v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}\left[\frac{\vwO}{500\,{\rm km/s}}\right]^{-1}\right)^{1/2},
+\end{eqnarray}
+where $\vwO$ is a free parameter accounting for sources of heating beyond the baseline level produced by the stellar winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+
+First, continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by
 \begin{align}
@@
 
-Demanding hydrostatic equilibrium at the stagnation point provides an
-expression for the stagnation radius
-
-\begin{align}
-  \frac{\rs}{\rsoi}=\frac{1}{2 \zeta^2 n}\left[
-   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right]
+Hydrostatic equilibrium at the stagnation radius ($v = 0$) can be used to determine the stagnation radius
+\begin{align}
+  \frac{\rs}{\rsoi}=\frac{\sigma^{2}}{2 v_{w,0}^{2} n}\left[
+   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right],
  \label{eq:stag_analytic}
 \end{align}
-
-where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
-density profile at $r = r_{\rm s}$,
-
-\begin{align}
-r_{\rm soi} = \frac{GM_{\bullet}}{\sigma^{2}} \approx 14M_{\bullet,8}^{0.6}\,\,{\rm pc}
-\end{align}
-
-is the radius of the SMBH sphere of
-influence (soi), and A and B are constants that depend on the Nuker
+in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the
+density profile at $r = r_{\rm s}$, and A and B are constants that depend on the Nuker
 parameter $\Gamma$ and the adiabatic index of the gas.
 
-If the SMBH dominates the potential at the stagnation radius
-($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg 200 M_{\bullet,8}^{0.2}$ km
-s$^{-1}$) then the relationship between $\rs$ and $v_{w}$ is
-simplified greatly:
-\begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \simeq 6
+If the SMBH dominates the gravitational potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg \sigma$) then equation (\ref{eq:stag_analytic}) simplifies greatly
+\begin{align}
+  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx 6
  \, \pc \,\, \Mbheight v_{500}^{-2},
@@
 \end{align}
-where in the numerical estimate we have assume $n = 1$.
+where the numerical estimate assumes $n = 1$.
 This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
-On the other hand, if wind heating is much weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
-
+On the other hand, if wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
+
+Our above analysis neglects heat conduction near the stagnation radius, an assumption we can now check.
 The importance of conductive heating can be estimated by comparing its
 magnitude to that of wind heating, viz.~
-\begin{align} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
+\begin{align}
+  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
 w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
-\nonumber \\ &\sim
-53 \eta_{0.02}^{-1}\left(\frac{r_{\rm s}}{r_{\rm
-soi}}\right)^{-\beta} v_{500}^{9} \nonumber \\ &\sim
-23 \,\, 0.43^{\beta-1} \eta_{0.02}^{-1}
-M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}
-\label{eq:condRatio1}
-\end{align}
-
-where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in
-the second equality have made use of equations (\ref{eq:Tanalytic}),
-(\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm
-  s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm
-  soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that
-conductive heating is important near the stagnation radius for high
-values of $v_{\rm w} \gtrsim 300$ km s$^{-1}$ and $\eta=0.02$, but
-that it is safely neglected to first order for lower heating
-rates. {\bf AG:Note that threshold vw is rather--the 300 km/s is
-  estimated for cusp galaxies. The change in normalization is due to
-  the change in the fiducial eta from 0.1 to 0.02. This seems like bad
-  news. Should probably include mass. Although this is tricky as cusp
-  and core galaxies have opposite dependencies on mass. Perhaps we
-  will have to lean on the saturated argument more if we really would
-  like to avoid conductivity. Or perhaps including conductivity is
-  truly unavoidable. ):}
-
-In fact, for high heating rates conductive heating is less important
-than equation~\eqref{eq:condRatio1} would suggest due to the effects
-of saturation. In this regime the importance of conductive heating can
-be estimated the conductive flux in equation~\eqref{eq:condRatio1}
-with its saturated value.
-\begin{eqnarray} \left.\frac{\nabla\cdot(f_{\rm cond})}{q v_{\rm
-w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h} \phi \rho(\rs) c_s(\rs)^3}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
-\nonumber \\ &\sim&
-\frac{10 \phi}{2-\Gamma}, \label{eq:condRatio}
+T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}(1+\phi)}
+\nonumber \\ &\sim {\rm min}
+  \begin{cases}
+  10 \eta_{0.02}^{-1}
+M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
+ 10 \eta_{0.02}^{-1}
+M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
+  10 \phi/(2-\Gamma) & \text{saturated},
+  \end{cases}
+ \label{eq:rhors}
+\end{align}
+where in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$, $\nabla \sim 1/r_{\rm st}$.
+Since the stagnation radius is usually well inside the break radius, the stellar density is approximated as (eq.~[\ref{eq:rhostar}])
+\begin{eqnarray}
+  \rho_{\star}(r_{\rm s}) &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
+ &\approx& \begin{cases}
+    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
+    & \text{core} \\
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
+    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
+  \end{cases}
+  \label{eq:rhostarrs}
 \end{eqnarray}
-
-where we have approximated $\nabla \sim 1/r_{\rm st}$ and in the
-second equality have made use of equations (\ref{eq:Tanalytic}),
-(\ref{eq:stag_simple}), and (\ref{eq:rhors}). The stellar density is
-assumed to be a power law $\rho_{\star}=\frac{\Mbh
-  \left(2-\Gamma\right)}{4 \pi \rsoi^3}
-\left(\frac{\rs}{\rsoi}\right)^{-1-\Gamma}$.
-
-From the saturated value of the conductive heat flux we have found an
-upper bound on the ratio of the rate of heating to the rate of heat
-conduction in equation~\eqref{eq:condRatio}.  For $\phi\simeq 1$, the
-conductive flux could be quite important. However, the value of $\phi$
-depends various details from plasma physics, and could plausibly be an
-order of magnitude smaller. In light of these uncertainties we neglect
-the effect of the conductive flux.
+Even in the case of saturated heat flux, we see that for expected values $\phi < 1$, heat condution is at most moderately important at the stagnation radius, justifying its neglect in our analysis.
 
@@
 rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
-%AG: Should we have separate cores and cusps? Or just write a general
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-
 The Eddington ratio $\eddr$ is given by 
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-The stellar density at the stagnation radius (eq.~[\ref{eq:stag_simple}]) is usefully approximated as
-\begin{eqnarray}
-  && \rho_{\star}(r_{\rm s}) \approx \nonumber \\
-  && \begin{cases}
-    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
-    & \text{core} \\
-    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
-    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
-  \end{cases}
-  \label{eq:rhostarrs}
-\end{eqnarray}
-
-The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be roughly estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
+The density of gas at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate.
+We roughly estimate its value using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
 \begin{align}

### 2014-12-16 ms.tex
updated 3.1B
arg chaos

@@
 \label{sec:results}
-\subsection{Properties near the stagnation radius}
+\subsection{Analytic Results}
 
@@
 
+\subsubsection{Properties at the Stagnation Radius}
+
 First, continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by
@@
 
-Our above analysis neglects heat conduction near the stagnation radius, an assumption we can now check.
-The importance of conductive heating can be estimated by comparing its
-magnitude to that of wind heating, viz.~
-\begin{align}
-  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
-w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}(1+\phi)}
-\nonumber \\ &\sim {\rm min}
-  \begin{cases}
-  10 \eta_{0.02}^{-1}
-M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
- 10 \eta_{0.02}^{-1}
-M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
-  10 \phi/(2-\Gamma) & \text{saturated},
-  \end{cases}
- \label{eq:rhors}
-\end{align}
-where in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$, $\nabla \sim 1/r_{\rm st}$.
-Since the stagnation radius is usually well inside the break radius, the stellar density is approximated as (eq.~[\ref{eq:rhostar}])
-\begin{eqnarray}
-  \rho_{\star}(r_{\rm s}) &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
- &\approx& \begin{cases}
-    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
-    & \text{core} \\
-    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
-    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
-  \end{cases}
-  \label{eq:rhostarrs}
-\end{eqnarray}
-Even in the case of saturated heat flux, we see that for expected values $\phi < 1$, heat condution is at most moderately important at the stagnation radius, justifying its neglect in our analysis.
+\subsubsection{SMBH Accretion Rate}
 
@@
 \begin{eqnarray}
-\eddr&\approx&
+\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
   \begin{cases}
@@
 \end{eqnarray}
+
 The density of gas at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate.
@@
 \end{align}
-
-Note that combining equations~\eqref{eq:mdot_analytic}
-and~\eqref{eq:mdot_gas} we can rewrite the $\rho(\rs)$
-
+Note that by combining equations~\eqref{eq:mdot_analytic}
+and~\eqref{eq:mdot_gas}, one can also write
 \begin{align}
@@
 
-\subsection{Comparison with Bondi Accretion}
-The spherical accretion rate onto a point source from a surrounding
-medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and
-density is given by (\citealt{Bondi52})
+Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) is usefully compared to the traditional ``Bondi" accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and
+density (\citealt{Bondi52}):
 \begin{align}
@@
 \end{align}
-where $r_b \equiv GM/c_{s}^{2}$ is the ``Bondi radius", $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
-
-Rewriting equation (\ref{eq:mdot_gas}) as
-\begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff} =\frac{4
-    \pi}{3} \rs^2 \rho(\rs) v_{\rm ff}(\rs)
-\end{align}
-we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
-\begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}},
+where $r_b \equiv GM/c_{s}^{2}$ is the Bondi radius, $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
+Rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho(\rs) v_{\rm ff}(\rs)/3$,
+we note a similarity Bondi formula (eq.~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.
+In fact, when the stagnation radius resides interior to the sphere of influence we have (eq.~[\ref{eq:stag_simple}])
+\begin{align}
+  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}} = \frac{14}{3}r_{\rm B},
   \label{eq:rs_simple}
 \end{align}
-where in the second line we have used the fact that $v_{w}^{2}/2 =
-c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
-exists which is interior to the sphere of influence radius, the
-accretion rate predicted by our model is quite close to $\dot{M}_{\rm
-  B}$.
- %({\bf BDM: Check - as this depends on
- % whether eq 10 is correct})
-
-%% AG-Apparently even in the low heating case, it is still possible to
-%% an outflow (from the analytic results above the gas density must be
-%% quite steep in this case). However, at low heating we will probably
-%% become subject to a cooling instablity.  AG-I believe that in the
-%% case of core galaxy, the negative root of the quadratic should be
-%% taken...
-
-\subsection{Numerical Solutions}
-
+where in the second line we have used equation (\ref{eq:Tanalytic}).
+
+\subsubsection{Importance of Heat Conduction}
+
+Our analytic results neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
+The importance of conductive heating can be estimated by comparing its magnitude to that of ``wind" heating, viz.~
+\begin{align}
+  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
+w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
+T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}(1+\phi)}
+\nonumber \\ &\sim {\rm min}
+  \begin{cases}
+  10 \eta_{0.02}^{-1}
+M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
+ 10 \eta_{0.02}^{-1}
+M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
+  10 \phi/(2-\Gamma) & \text{saturated},
+  \end{cases}
+ \label{eq:rhors}
+\end{align}
+where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$, $\nabla \sim 1/r_{\rm st}$.
+Because the stagnation radius is usually well inside the break radius, the stellar density is approximated as (eq.~[\ref{eq:rhostar}])
+\begin{eqnarray}
+  \rho_{\star}(r_{\rm s}) &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
+ &\approx& \begin{cases}
+    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
+    & \text{core} \\
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
+    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
+  \end{cases}
+  \label{eq:rhostarrs}
+\end{eqnarray}
+Even in the saturated heat flux case, heat conduction is at most moderately important for expected values of the saturation parameter $\phi < 1$, justifying its neglect in our analysis.
+
+\subsubsection{Thermal Instability}
+
+Radiative cooling, if important, can qualitative alter key features of the flow.
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ according to $\dot{q}_{\rm cool} \propto T^{-2.7}$ (eq.~[\ref{eq:cooling}] below) is thermally unstable.
+Thermal instability leads to higher black hole accretion rates and enhanced star formation which, when coupled by feed-back processes, can lead to limit cycle behavior, inconsistent with our assumption of a a steady-state flow (e.g.
+Ciotti refs).
+
+Radiative cooling can, however, be stabilized by the other source of (stable) wind cooling, such as the last term $\propto c_{s}^{2} \propto T$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$.
+To assess the conditions for thermal stability we compare the nominal rate of wind heating to the rate of radiative cooling $\dot{q}_{\rm cool} =\Lambda(T) n^2$ at the stagnation radius,
+\begin{align}
+\left.\frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rm r{s}} \simeq
+  \begin{cases}
+   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
+   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
+  \end{cases}
+  \label{eq:cooling2}
+\end{align}
+where we have used equations (\ref{eq:rhostarrs}) and
+(\ref{eq:rhors}).  Here $n = \rho/\mu m_p$ and we have approximated the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (\citealt{Draine:2011a}, Fig. 34.1):
+\begin{align}
+\Lambda(T)\simeq
+  \begin{cases}
+    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}&, T > 2 \times 10^7 \text{K} \\
+    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}&, T < 2 \times 10^7 \text{K}     
+  \end{cases}
+  \label{eq:cooling2}
+\end{align}
+Note that at the stagnation radius equation (\ref{eq:cooling2}) is equivalent to the ratio of the cooling to free-fall timescale, i.e.
+\begin{align}
+\left. \frac{\tcool}{\tff}\right|_{\rs}&= \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs},
+\end{align}
+where we have used equations~(\eqref{eq:Tanalytic}) and (\eqref{eq:rhors2}).
+
+There thus exists a critical minimum wind velocity required for thermal stability at the stagnation radius
+\begin{align}
+v_{\rm crit} \simeq
+  \begin{cases}
+   200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+  \end{cases}
+  \label{eq:cooling2}
+\end{align}
+In $\S\ref{sec:numerical}$ we will show that $v_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
+
+If cooling becomes important in the flow, it may lead to thermal
+instabilities.  There are two kinds of ``instabilities", global and
+local.  The global instability is simply that, if cooling becomes very
+rapid, the gas loses thermal pressure and starts to inflow faster,
+i.e. the entire CNM accretes (e.g. {\bf AG citation missing here.}).  In
+practice this should could manifest as a large increase in the
+stagnation radius, due an effective {\it decrease} in the effective
+heating rate.  This global ``instability" is not a true instability
+insofar as the gas does not necessarily clump locally into low-T
+clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly
+balanced by heating everywhere, there is still a local thermal
+instability that operates to turn hot gas into cold clouds.  However,
+this local instability only causes a significant local drop-out of
+mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$.
+
+Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
+as a function of radius for all of our solutions. {\bf BDM: change
+  plots}, with different colors denoting different values of $\vwO$.
+For our highest heating rates we observe that cooling is unimportant
+for all solutions across all radii--neither the local nor the global
+thermal instability would be present. However,  for our smallest value
+of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
+thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
+precise region of the parameter space which would be thermally
+unstable would depend on the value of $\eta$--in
+Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
+appropriate for a stellar population with $\tage\simeq \th$. This
+value is on the low end of what we would physically expect for
+$\eta$.
+
+For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
+$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
+diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
+approximation away from $\rs$. Similarly, it is poorer approximation
+for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
+closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
+  clarify the physics here a little more.}
+
+% For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
+Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
+If cooling is important, the CNM is likely to be thermally unstable, resulting in the formation of a cold medium that could substantially enhance the rate of accretion onto the SMBH.
+
+%\begin{align}
+ % \Lambda(T)\simeq
+  %\begin{cases}
+   % 2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
+   % 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
+  %\end{cases}
+  %\label{eq:cooling}
+%\end{align}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{cooling.eps}
+  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
+    ($C$) for each of our solutions (solid lines). The cooling rate is
+    calculated using the approximate (solar metallicity) cooling
+    function in Equation~(\ref{eq:cooling}). The heating rate is
+    estimated as $q \vw^2/2+q v^2/2$. The ratio is computed from
+    equation (\ref{eq:cooling}) assuming a stellar mass loss rate
+    parameter $\eta=0.02$. We also plot the ratio $\tcool/\tff$
+    vs. radius. $H/C$ is a diagnostic for global thermal stability,
+    and a solution should be stable as long as
+    $H/C\gsim1$. $\tcool/\tff$ is a diagnostic for local thermal
+    instability, solutions should be stable as long as $\tcool/t_{\rm
+      ff}\gsim$10 \citealt{McCourt+12}. Notice that for high $\vwO$
+    the two ratios coincide at $\rs$ (marked with a square for each
+    solution).}
+\end{figure}
+
+%\input{figures/eta_tab.tex}
+
+\subsection{Numerical Results}
+\label{sec:numerical}
+
+This section describes the results of our numerical calculations and tests the accuracy of the analytic expressions provided in the previous section.
 Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
@@
 \label{sec:cooling}
-Our models neglect radiative cooling, an assumption we now check.
-At high temperatures $T\gsim 2\times 10^7$ K gas cools through free-free emission, while at lower temperatures it cools predominantly through metal lines.
-To assess the importance of radiative cooling in our solutions we compare the heating rate $H=q \vw^2/2$ to the nominal cooling rate
-\begin{align}
-  \dot{q}_{\rm cool} =\Lambda(T) n^2,
-\label{eq:cooling}
-\end{align}
-where $n = \rho/\mu m_p$ and we approximate the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (Fig. 34.1 in \cite{Draine:2011a}):
-\begin{align}
-\Lambda(T)\simeq
-  \begin{cases}
-    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}&, T \gsim 2 \times 10^7 \text{K} \\
-    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}&, T \lsim 2 \times 10^7 \text{K}     
-  \end{cases}
-  \label{eq:cooling2}
-\end{align}
-
-Radiative cooling can have an important on even the qualitative features of the flow, because initially hydrostatic gas that cools at constant pressure $P \propto nT$ according to $\dot{q}_{\rm cool} \propto T^{-2.7}$ (eq.~[\ref{eq:cooling}]) is thermally unstable.
-Radiative cooling can be stabilized, however, by the other source of (stable) wind cooling, given by the last term $\propto T$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$.
-
-An important ratio controlling the importance of thermal stability is thus
-\begin{align}
-\left.\frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rm r{s}} \simeq
-  \begin{cases}
-   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
-   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
-  \end{cases}
-  \label{eq:cooling2}
-\end{align}
-where we have used equations (\ref{eq:rhostarrs}) and
-(\ref{eq:rhors}).  We thus see that we require $v_{\rm w} \gtrsim $
-300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and
-$M_{\bullet}$.  {\bf AG:I flipped the ratio to be consistent with the
-  ratio of timescales given below (NB here we are comparing heating
-  and cooling rates as opposed to timescales). Modulo factors of order
-  unity I find no inconsistency. We should probably only keep one of
-  these ratios. Note I have adopted the new convention of Gamma=0.8 is
-  a cusp galaxy and Gamma=0.1 is a core galaxy.}
-
-If cooling becomes important in the flow, it may lead to thermal
-instabilities.  There are two kinds of ``instabilities", global and
-local.  The global instability is simply that, if cooling becomes very
-rapid, the gas loses thermal pressure and starts to inflow faster,
-i.e. the entire CNM accretes (e.g. {\bf AG citation missing here.}).  In
-practice this should could manifest as a large increase in the
-stagnation radius, due an effective {\it decrease} in the effective
-heating rate.  This global ``instability" is not a true instability
-insofar as the gas does not necessarily clump locally into low-T
-clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly
-balanced by heating everywhere, there is still a local thermal
-instability that operates to turn hot gas into cold clouds.  However,
-this local instability only causes a significant local drop-out of
-mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$.
-
-At the stagnation $\tcool/\tff$ is equal to the ratio of the heating to
-the cooling rate to factors of order unity as shown below
-
-\begin{align}
-\left. \frac{\tcool}{\tff}\right|_{\rs}&=\left. \frac{3}{5} \frac{\rho 
-  \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}\\
-&=\frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}.
-\end{align}
-
-In the first line we have used equation~\eqref{eq:Tanalytic} and in
-the second line we have used equation~\eqref{eq:rhors2}.
-
-Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
-as a function of radius for all of our solutions. {\bf BDM: change
-  plots}, with different colors denoting different values of $\vwO$.
-For our highest heating rates we observe that cooling is unimportant
-for all solutions across all radii--neither the local nor the global
-thermal instability would be present. However,  for our smallest value
-of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
-thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
-precise region of the parameter space which would be thermally
-unstable would depend on the value of $\eta$--in
-Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
-appropriate for a stellar population with $\tage\simeq \th$. This
-value is on the low end of what we would physically expect for
-$\eta$.
-
-For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
-$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
-diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
-approximation away from $\rs$. Similarly, it is poorer approximation
-for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
-closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
-  clarify the physics here a little more.}
-
-% For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
-Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
-If cooling is important, the CNM is likely to be thermally unstable, resulting in the formation of a cold medium that could substantially enhance the rate of accretion onto the SMBH.
-
-%\begin{align}
- % \Lambda(T)\simeq
-  %\begin{cases}
-   % 2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
-   % 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
-  %\end{cases}
-  %\label{eq:cooling}
-%\end{align}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
-    ($C$) for each of our solutions (solid lines). The cooling rate is
-    calculated using the approximate (solar metallicity) cooling
-    function in Equation~(\ref{eq:cooling}). The heating rate is
-    estimated as $q \vw^2/2+q v^2/2$. The ratio is computed from
-    equation (\ref{eq:cooling}) assuming a stellar mass loss rate
-    parameter $\eta=0.02$. We also plot the ratio $\tcool/\tff$
-    vs. radius. $H/C$ is a diagnostic for global thermal stability,
-    and a solution should be stable as long as
-    $H/C\gsim1$. $\tcool/\tff$ is a diagnostic for local thermal
-    instability, solutions should be stable as long as $\tcool/t_{\rm
-      ff}\gsim$10 \citealt{McCourt+12}. Notice that for high $\vwO$
-    the two ratios coincide at $\rs$ (marked with a square for each
-    solution).}
-\end{figure}
-
-%\input{figures/eta_tab.tex}
 

### 2014-12-16 ms.tex
i hate shortcut notation

@@
 \end{align}
-Note that at the stagnation radius equation (\ref{eq:cooling2}) is equivalent to the ratio of the cooling to free-fall timescale, i.e.
-\begin{align}
-\left. \frac{\tcool}{\tff}\right|_{\rs}&= \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs},
-\end{align}
-where we have used equations~(\eqref{eq:Tanalytic}) and (\eqref{eq:rhors2}).
-
 There thus exists a critical minimum wind velocity required for thermal stability at the stagnation radius
@@
 In $\S\ref{sec:numerical}$ we will show that $v_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
-
-If cooling becomes important in the flow, it may lead to thermal
-instabilities.  There are two kinds of ``instabilities", global and
-local.  The global instability is simply that, if cooling becomes very
-rapid, the gas loses thermal pressure and starts to inflow faster,
-i.e. the entire CNM accretes (e.g. {\bf AG citation missing here.}).  In
-practice this should could manifest as a large increase in the
-stagnation radius, due an effective {\it decrease} in the effective
-heating rate.  This global ``instability" is not a true instability
-insofar as the gas does not necessarily clump locally into low-T
-clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly
-balanced by heating everywhere, there is still a local thermal
-instability that operates to turn hot gas into cold clouds.  However,
-this local instability only causes a significant local drop-out of
-mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}}
+Our estimate in equation (\ref{eq:cooling2}) assumes the existence of a stagnation radius according to equation (\ref{eq:rs}), the validity of which requires $v_{\rm w} \gtrsim \sigma \sim v_{\rm crit}$.
+
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
 \end{align} 
 is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$.
-
-Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
-as a function of radius for all of our solutions. {\bf BDM: change
-  plots}, with different colors denoting different values of $\vwO$.
-For our highest heating rates we observe that cooling is unimportant
-for all solutions across all radii--neither the local nor the global
-thermal instability would be present. However,  for our smallest value
-of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
-thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
-precise region of the parameter space which would be thermally
-unstable would depend on the value of $\eta$--in
-Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
-appropriate for a stellar population with $\tage\simeq \th$. This
-value is on the low end of what we would physically expect for
-$\eta$.
-
-For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
-$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
-diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
-approximation away from $\rs$. Similarly, it is poorer approximation
-for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
-closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
-  clarify the physics here a little more.}
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
 
@@
 
+Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
+as a function of radius for all of our solutions. {\bf BDM: change
+  plots}, with different colors denoting different values of $\vwO$.
+For our highest heating rates we observe that cooling is unimportant
+for all solutions across all radii--neither the local nor the global
+thermal instability would be present. However,  for our smallest value
+of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
+thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
+precise region of the parameter space which would be thermally
+unstable would depend on the value of $\eta$--in
+Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
+appropriate for a stellar population with $\tage\simeq \th$. This
+value is on the low end of what we would physically expect for
+$\eta$.
+
+For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
+$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
+diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
+approximation away from $\rs$. Similarly, it is poorer approximation
+for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
+closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
+  clarify the physics here a little more.}
+
 \section{Applications}
@@
 
-Our results show that the location of the stagnation rate and resulting accretion rate, is very sensitive to the assumed heating
-rate $\propto v_{w,0}^{2}$.  Physically, we expect that the heating rate will vary from galaxy to galaxy.. For example, SNe Ia represent a
-potentialy important source of heating, but since they are rare they
-will only be relevant in a time-averaged sense if the supernova rate
-exceeds the inflow time of the gas near the stagnation point.
-
-In this section we discuss potential sources of heating and provide estimates of the value of $\vwO$ corresponding to each.
-Before proceeding, note that $\vwO$ is related to the heating rate per volume $e$ according to
+Important properties such as the location of the stagnation radius, the SMBH accretion rate, and the possibility of thermal instability depend sensitively on the assumed heating rate $\propto v_{w,0}^{2}$  This section discusses individual heating sources, providing estimates of the value of $\vwO$ corresponding to each.
+Before proceeding, note that $\vwO$ is related to the volumetric heating rate $e$ according to
 \begin{align}
@@
 
-\subsubsection{Millisecond Pulsars} The spin down power of millisecond
-pulsars (MSPs) could in principle be an important heating source.  If
-the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each
-contributes an average spin-down luminosity $\bar{L}_{\rm sd}$, then the
-resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
-  msp}\epsilon$ corresponds to an effective heating rate (eq.~
-[\ref{eq:vw_eff}])
-
-\begin{align}
-  v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
+\subsubsection{Millisecond Pulsars} Energy injection due to the spin-down of millisecond pulsars (MSPs) is a potentially important heating source.
+If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
+  msp}\epsilon$ corresponds to an effective heating rate (eq.~ [\ref{eq:vw_eff}])
+\begin{eqnarray}
+  v_{\rm w,0}^{\rm MSP} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
   &\approx& 90\epsilon^{1/2}\left(\frac{\bar{L}_{\rm
@@
   \eta_{0.02}^{-1/2}\,{\rm km\,s^{-1}},
-  \end{align}
-
+  \end{eqnarray}
 where $\epsilon< 1$ is the thermalization efficiency of the wind.
-  The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass
-  $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to
-  $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we
-  assume in the numerical estimate.  Using the ATNF radio pulsar
-  catalog (\citealt{Manchester+05}), we estimate the average spin-down
-  luminosity of millisecond pulsars in the field (excluding those in
-  globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg
-  s$^{-1}$ {\bf For eta=0.02 we cannot really
-    say that vw from msps is negligible}
-
-  If we assume a higher spin-down luminosity $L_{\rm sd}\simeq
-  10^{35}$ ergs s$^{-1}$ characteristic of some Fermi pulsars, then we
-  find that $v_{\rm w,0}^{\rm p} \simeq 270\epsilon^{1/2}
-  (\eta/0.1)^{-1/2}$ km s$^{-1}$, in which case MSP heating can be
-  comparable to main sequence wind heating for $\eta = 0.1$, $\epsilon
-  = 1$.  However, much lower thermalization efficiencies of $\epsilon
-  \lesssim 0.1$ are inferred based on modeling the insterstellar
-  mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
-  Also, the binaries giving rise to MSPs may be disocciated by stellar
-  interactions in the dense nuclear cluster, reducing their numbers as
-  compared to the field population.
+The above estimate adopts a pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$ motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
+
+From the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate that the average spin-down luminosity of millisecond pulsars in the field (excluding those in globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, in which case $v_{\rm w,0} \lesssim 100$ km s$^{-1}$ is unimportant even for $\epsilon = 1$.
+For higher spin-down luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0} \lesssim 300$ km s$^{-1}$ makes MSP heating in principle be important for $\epsilon = 1$.
+However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
+Also, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population.
+We thus conclude that MSPs are unlikely to be an important source of heating.
+
 \subsubsection{Type Ia Supernovae}
@@
 that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
-the SNe occur in a hot dilute medium, as may characterize the CNM.
+the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.
 

### 2014-12-16 ms.tex
Ia

@@
 recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
-years.  To good approximation $\eta\simeq 0.02 (t/t_h)^{-1.3}$ at time $t$ following a burst of star formation (e.g., \citet{Ciotti+91}),\footnote{Note that 
+years.  To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a burst of star formation (e.g., \citet{Ciotti+91}),\footnote{Note that 
 \citet{Ciotti+91} gives the overall mass return rate from evolved
@@
 
-Energy injected by Type Ia supernovae (SNe Ia) represents a
-potentially important source of heating, which unlike core collapse
-SNe is present even in an evolved stellar population.  Assuming that
-each Ia injects a thermal energy $E_{\rm Ia}$ into the interstellar
-medium, and that the SNe rate (per stellar mass) is given by $R_{\rm
-  Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm
-  Ia}$ produces an effective wind heating parameter
-(equation~[\ref{eq:vw_eff}])
-\begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
+Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the interstellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
@@
 \epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$
-with which the blast wave energy is converted into bulk or turbulent
+with which the initial blast wave energy is converted into bulk or turbulent
 motion instead of being lost to radiation.  \cite{Thornton+98}
@@
 
-The Ia SN rate $\RateIa$ depends on the age of the stellar population,
-as it represent the convolution of the star formation rate and the Ia
-delay time distribution (DTD) divided by the present stellar mass.  In
-the limit of impulsive star formation, $\RateIa$ is the DTD evaluated
-at the time since the star formation episode.  The observationally
-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
-approximate functional form
-\begin{align}
+The Ia SN rate $\RateIa$ depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
+In
+the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
+approximate functional form \begin{align}
   R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm
@@
 
-  Using equations (\ref{eq:vw_sne}), (\ref{eq:DTD}), and
-  (\ref{eq:eta}) we thus estimate that
-
-  \begin{align} 
-    v_{w,0}^{\rm Ia} \approx 700(\epsilon_{\rm
-      Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.09} \eta_{0.02}^{-1/2}\,{\rm km
+From equations (\ref{eq:vw_sne}), (\ref{eq:DTD}) we thus estimate that 
+  \begin{eqnarray} 
+    v_{w,0}^{\rm Ia} &\approx& 700(\epsilon_{\rm
+      Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{-0.56}\eta_{0.02}^{-1/2}\,{\rm km
+      \,s^{-1}} \nonumber \\
+&\approx& 700(\epsilon_{\rm
+      Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{0.09}\,{\rm km
       \,s^{-1}},
-  \end{align}
-
- showing that the effective
-  velocity due to SN heating is (coincidentally) a weak function of
-  the stellar age.
-
-  The relatively high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe
-  represent a potentially dominant source of non-AGN heating in the
-  CNM.  However, SNe can only be approximated as "constant" heating
-  source throughout space and time if the rate of SNe is rapid
-  compared to the inflow time at the radius of interest
-  (\citealt{ShcherbakovWong+:2014a}).  To estimate when this
-  approximation is valid, we estimate the ``Ia radius"
+\label{eq:vIa}
+  \end{eqnarray}
+where in the second line we have taken $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (\citealt{Ciotti+91}).
+
+The high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent a potentially dominant source of non-AGN heating in the CNM.
+However, SNe can only be approximated as being a constant heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
+To estimate when this approximation is valid, we estimate the ``Ia radius"
   \begin{align}
@@
   \end{align}
-as the location exterior of which the time interval between subsequent
-supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim
-G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
-dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old
-stellar population and in the final equality we estimate the velocity
-dispersion using the $M_{\bullet}-\sigma$ relationship
-(equation~[\ref{eq:Msigma}]).  Between subsequent supernova, stars
-release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm
-Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally
-bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm
-gas}\sigma^{2}$.  Thus, according to the above definitions, $E_{\rm
-Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
-
-Note that the stagnation radius scales approximately linearly with
-$M_{\bullet}$ (equation~[\ref{eq:stag_simple}]), while $\rIa$ is
-roughly indpendent of SMBH mass.  For small $\Mbh$, the stagnation
-radius thus lies well inside $\rIa$ and hence Ia SNe will not
-contribute appreciably to the heating rate.  On the other hand, for
-massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$, SNe Ia represent an
-important, and possibly dominant, contribution to the overall heating.
+as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
+dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship
+(equation~[\ref{eq:Msigma}]).
+Between subsequent supernovae, stars release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm gas}\sigma^{2}$.
+Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
+
+Assuming that $v_{\rm w,0}^{\rm Ia} \gg \sigma$ then by substituting equation (\ref{eq:vIa}) into (\ref{eq:rs_simple}) we can write
+\begin{eqnarray}
+\frac{r_{\rm Ia}}{r_{\rm s}} &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68}\eta_{0.02}  \nonumber \\
+&\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
+\end{eqnarray}
+Thus only for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$ and/or very young populations will SNe Ia represent a steady source of heating at the nominal stagnation radius.
 

### 2014-12-16 ms.tex
compton

@@
 
-\section{Applications}
-\label{sec:applications}
-\subsection{Sources of Heating}
+\section{Sources of Heating}
 \label{sec:heating}
@@
 A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$.
+There are two types of SMBH feedback: kinetic and radiative.
+
+Radiative feedback can be effective even in low luminosity AGN via Compton heating (e.g.,~\citealt{Gan+14}).  Compton heating provides a volumetric heating rate (\citealt{Gan+14})
+\be
+\dot{e}_{\rm C} = 4.1\times 10^{-35}n^{2}\xi T_{\rm C}\,{\rm erg\,cm^{-3}\,s^{-1}},
+\ee
+where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K, which is assumed to be much higher than the gas temperature.
+We can estimate the importance of Compton heating by assuming that $L = \epsilon \dot{M}c^{2}$, where $\epsilon$ is the radiative efficiency and where $\dot{M}$ is estimated from equation (\ref{eq:mdot_analytic}).
+
+Using equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}), (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we thus calculate that (eq.~[\ref{eq:vw_eff}])
+\begin{align}
+v_{\rm w,0}^{\rm C}  \simeq
+  \begin{cases}
+   125 T_{\rm C,9}^{0.5}\epsilon^{0.5}\eta_{0.02}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   200 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+  \end{cases}
+  \label{eq:vC}
+\end{align}
+Assuming that heating were dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) we find that
+\begin{align}
+v_{\rm w,0}^{\rm C}  \simeq
+  \begin{cases}
+   106 \eta_{0.02}^{0.21}T_{\rm C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   76 \eta_{0.02}^{0.29}T_{\rm C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+  \end{cases}
+  \label{eq:vC2}
+\end{align}
+where $\epsilon_{-2} = \epsilon/0.01$.  So, unless we have high $\eta$ then Compton heating will not be sufficient to stabilize the flow.
+
+Kinetic feedback occurs in the form of an mass outflow or jet from the viscinity of the black hole, which deposits its energy at much larger radii.
 We assume that the total heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
-If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm out}$ results in an effective wind heating rate of
+If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind heating rate of
 \be
-v_w^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm out}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{\beta/2},
+v_w^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{\beta/2},
 \ee
@@
   % AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
+
+\section{Applications}
+\label{sec:applications}
 

### 2014-12-16 ms.tex
2.2 second pass

@@
 recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
-years.  To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a burst of star formation (e.g., \citet{Ciotti+91}),\footnote{Note that 
-\citet{Ciotti+91} gives the overall mass return rate from evolved
-stars as a function of B-band luminosity. We give the mass return rate
-per unit volume. However, our expressions are equivalent.} although $\eta$ will generally be higher in cases of ongoing star formation.
-
-Source terms $\propto q$ also appear in the momentum and entropy equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) due to the fact that the isotropic mass injection in the rest frame of the SMBH
-represents a source of momentum and energy relative to the mean flow (see also below).
-Physically these terms result from the mismatch between the properties of virialized gas injected locally by stellar winds and the mean properties of the background flow.
-As we shall discuss in $\S$, the cooling term $\propto q p/\rho$ represents an important stabilizing term in comparison to radiative cooling.
+years.
+To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a burst of star formation (e.g., \citealt{Ciotti+91}),\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
+Although we give the mass return rate per unit volume, our expressions are equivalent.} although $\eta$ is higher in cases of ongoing star formation.
+
+Source terms $\propto q$ also appear in the momentum and entropy equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because isotropic mass injection in the SMBH rest frame represents a source of momentum and energy relative to the mean flow.
+Physically, these result from the mismatch between the properties of virialized gas injected locally by stellar winds and the mean properties of the background flow.
+The term $\propto -q c_{s}^{2}$ turns out to be an important in stabilizing the flow to runaway cooling ($\S$).
 
 The last term in equation (\ref{eq:dsdt}) accounts for heat transportation by electron conductivity, where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units).
-The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale.
-Here $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi$ is an uncertain dimensionless constant, typically taken to be of order unity of less (we adopt $\phi = XXX$).
-Even a weak magnetic field could in principle also suppress the conductivity perpendicular to the field.
+The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi \lesssim 1$ is an uncertain dimensionless constant (we adopt $\phi = XXX$).
+Even a weak magnetic field perpendicular to the flow could in principle suppress the conductivity.
 However, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
 
-Following \citet{ShcherbakovWong+:2014a}, the term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy equation accounts heating sources.
-Here $\sigma(r) = \sqrt{GM_{\rm enc}/r}$ is the velocity dispersion of the stars, accounting for the minimum amount of shock heating from the stellar winds due to the random movement of stars with respect to each other at the characteristic velocity $\sim \sigma$.
-This heating is present even for low wind velocities $\ll \sigma$, as characterize the majority of AGB mass loss.
-The term $v_{w,0}^{2}$ parameterizes the contribution of additional sources of heating, including main sequence winds, millisecond pulsars, supernovae, AGN feedback, etc.
+The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy equation accounts for external heating sources (e.g., \citealt{ShcherbakovWong+:2014a}).
+The first term accounts for the minimum shock heating of the stellar winds due to the random movement of stars with respect to each other at the characteristic velocity $\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low wind velocities $\ll \sigma$ that characterize AGB mass loss in old stellar populations.
+The second term, $v_{w,0}^{2}$, parameterizes the contribution of additional sources of heating, such as faster main sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN feedback, etc.
 As discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in general depend on the SMBH mass and the age of the stellar population.
@@
 for time integration and artificial viscosity terms in the velocity
-and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for
-different choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning the physically expected
+and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for different choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning a physically plausible
 range.
-Although we are most interested in the steady-state CNM structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.
-
-Radiative cooling is not included in the entropy equation, although its effect is assessed critically in $\S\ref{sec:cooling}$.
-Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling (e.g., advection).
-Radiative cooling cannot be neglected in some cases (if
-$\vwO$ is low and/or $\eta$ is high), once it becomes important it leads to thermal instabilities, which our one-dimensional time-dependent modeal cannot account for anyways (e.g.~\citealt{McCourt+12}).
-A chief goal of this work is instead to use our steady state solutions neglecting radiation to ascertain over what physical conditions cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).
+Although we are interested in the steady-state intflow/outflow structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.
+
+Radiative cooling is not included in our calculation.
+Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling.
+Radiative cooling cannot be neglected when $\vwO$ is low (and/or $\eta$ is high), but once important it leads to thermal instabilities (e.g.~\citealt{McCourt+12}) which our 1D time-independent model cannot account for self-consistently anyways.
+Indeed, one of the main goals of this work is to use our analytic and numerical solutions neglecting radiation to ascertain over what physical conditions cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).
 

### 2014-12-16 ms.tex
3.1 ongoing

@@
 \begin{eqnarray}
-v_{\rm w} &=& v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2} \nonumber \\
- &\approx& v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}\left[\frac{\vwO}{500\,{\rm km/s}}\right]^{-1}\right)^{1/2},
+v_{\rm w} = v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2} 
+ \approx v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right)^{1/2},
 \end{eqnarray}
-where $\vwO$ is a free parameter accounting for sources of heating beyond the baseline level produced by the stellar winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
-
-\subsubsection{Properties at the Stagnation Radius}
-
-First, continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by
+where the parameter $\vwO = 500 v_{500}$ km s$^{-1}$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+
+\subsubsection{Flow Properties Near the Stagnation Radius}
+
+Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs})
 \begin{align}
@@
 
-Hydrostatic equilibrium at the stagnation radius ($v = 0$) can be used to determine the stagnation radius
+Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs})
 \begin{align}
@@
 This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
-On the other hand, if wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
+In the opposite limit when the wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
 
@@
 
-The SMBH accretion rate is simply given by the integrated mass loss
-rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
+The SMBH accretion rate is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
 \begin{eqnarray}
@@
 \end{eqnarray}
-The Eddington ratio $\eddr$ is given by 
+where we have made use of equation (\ref{eq:stag_simple}), i.e. assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
 \begin{eqnarray}
@@
 
-The density of gas at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate.
-We roughly estimate its value using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
-\begin{align}
-  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff(\rs)},
+The gas density at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate.
+Its value can be crudely estimated using equation (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
+\begin{align}
+  &\dot{M}\sim\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff(\rs)},
   \label{eq:mdot_gas}
@@
 \begin{align}
-  \rho(\rs)\simeq
+  \rho(\rs)\approx
   \begin{cases}
     5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
-    \, {\rm g \, cm^{-3}}& \text{core}\\
-    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}
+    \, {\rm g \, cm^{-3}}& \text{core},\\
+    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp},
   \end{cases}
@@
 \end{align}
-Note that by combining equations~\eqref{eq:mdot_analytic}
-and~\eqref{eq:mdot_gas}, one can also write
-\begin{align}
-\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
-\label{eq:rhors2}
-\end{align}
-
-Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) is usefully compared to the traditional ``Bondi" accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and
-density (\citealt{Bondi52}):
+again using equation (\ref{eq:rs_simple}) for the stagnation radius.
+
+%Note that by combining equations~\eqref{eq:mdot_analytic}
+%and~\eqref{eq:mdot_gas}, one can also write
+%\begin{align}
+%\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
+%\label{eq:rhors2}
+%\end{align}
+
+It is useful to compare our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) to the traditional ``Bondi" rate for accretion onto a point source from an external medium of fixed density and temperature density (\citealt{Bondi52}):
 \begin{align}
@@
 Rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho(\rs) v_{\rm ff}(\rs)/3$,
-we note a similarity Bondi formula (eq.~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.
-In fact, when the stagnation radius resides interior to the sphere of influence we have (eq.~[\ref{eq:stag_simple}])
+we note a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $\rb$ is replaced by $\rs$.
+When the stagnation radius resides interior to the sphere of influence we indeed have (eq.~[\ref{eq:stag_simple}])
 \begin{align}
@@
 \end{align}
-where in the second line we have used equation (\ref{eq:Tanalytic}).
+where the second equality makes use of equation (\ref{eq:Tanalytic}).
 
@@
 
-Our analytic results neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
-The importance of conductive heating can be estimated by comparing its magnitude to that of ``wind" heating, viz.~
+The above analytic results neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
+The importance of conductive heating can be estimated by comparing its magnitude to the nominal level of ``wind" heating:
 \begin{align}
@@
 where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$, $\nabla \sim 1/r_{\rm st}$.
-Because the stagnation radius is usually well inside the break radius, the stellar density is approximated as (eq.~[\ref{eq:rhostar}])
+Because the stagnation radius is usually well inside the break radius, we have approximated the stellar density as (eq.~[\ref{eq:rhostar}])
 \begin{eqnarray}
@@
 \end{eqnarray}
-Even in the saturated heat flux case, heat conduction is at most moderately important for expected values of the saturation parameter $\phi < 1$, justifying its neglect in our analysis.
+Even in the saturated case, heat conduction is at most an order unity correction for expected values of the saturation parameter $\phi < 0.3$, justifying its neglect in our analysis.
 

### 2014-12-16 ms.tex
3.1 ongoing2

@@
 the available reservoir of gas is more than sufficient to power
-low-luminosity AGN, assuming the standard radiative efficiency $\eta
+low-luminosity AGN, assuming the s
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
+
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
+
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
+tandard radiative efficiency $\eta
 \sim 0.1$ for thin disk accretion.  Indeed, there is now strong
@@
 \end{equation}
+
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
 
@@
 
-Radiative cooling, if important, can qualitative alter key features of the flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ according to $\dot{q}_{\rm cool} \propto T^{-2.7}$ (eq.~[\ref{eq:cooling}] below) is thermally unstable.
-Thermal instability leads to higher black hole accretion rates and enhanced star formation which, when coupled by feed-back processes, can lead to limit cycle behavior, inconsistent with our assumption of a a steady-state flow (e.g.
-Ciotti refs).
-
-Radiative cooling can, however, be stabilized by the other source of (stable) wind cooling, such as the last term $\propto c_{s}^{2} \propto T$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$.
-To assess the conditions for thermal stability we compare the nominal rate of wind heating to the rate of radiative cooling $\dot{q}_{\rm cool} =\Lambda(T) n^2$ at the stagnation radius,
-\begin{align}
-\left.\frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rm r{s}} \simeq
+Radiative cooling, if important, qualitative alters key features of the accretion flow.
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} \propto T^{-2.7}$ (see below) is thermally unstable.
+If manifest, thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Wang+14}).
+
+Radiative cooling can, however, be stabilized by the other sources of cooling, such as the stellar wind source term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$ (neglecting conduction and radiative cooling).
+Thermal stability at the stagnation radius can thus be assessed by comparing the nominal wind heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$,
+\begin{align}
+\left.\frac{q \vw^2/2}{|\dot{q}_{\rm cool}|}\right|_{\rm r{s}} \simeq
   \begin{cases}
@@
 \end{align}
-where we have used equations (\ref{eq:rhostarrs}) and
-(\ref{eq:rhors}).  Here $n = \rho/\mu m_p$ and we have approximated the cooling function $\Lambda(T)$ assuming solar metallicity gas using piece-wise power law (\citealt{Draine:2011a}, Fig. 34.1):
-\begin{align}
-\Lambda(T)\simeq
-  \begin{cases}
-    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}&, T > 2 \times 10^7 \text{K} \\
-    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}&, T < 2 \times 10^7 \text{K}     
+where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gaseous and stellar densities at the stagnation radius, respectively.
+Here $n = \rho/\mu m_p$ and we have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}, Fig.
+34.1).
+To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3\rho kT/2\mu m_p)/\dot{q}_{\rm cool}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
+\begin{align}
+\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
+\label{eq:rhors2}
+\end{align}
+that results by combining equations~\eqref{eq:mdot_analytic} and~\eqref{eq:mdot_gas}.
+
+Thermal stability ($0.5 q \vw^2/|\dot{q}_{\rm cool}| > 1$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
+\begin{align}
+v_{w,0} > v_{\rm crit} \simeq
+  {\rm max}\begin{cases}
+   200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}\\
+\sigma,     
   \end{cases}
@@
 \end{align}
-There thus exists a critical minimum wind velocity required for thermal stability at the stagnation radius
-\begin{align}
-v_{\rm crit} \simeq
-  \begin{cases}
-   200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp},     
-  \end{cases}
-  \label{eq:cooling2}
-\end{align}
-In $\S\ref{sec:numerical}$ we will show that $v_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
-Our estimate in equation (\ref{eq:cooling2}) assumes the existence of a stagnation radius according to equation (\ref{eq:rs}), the validity of which requires $v_{\rm w} \gtrsim \sigma \sim v_{\rm crit}$.
-
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
+Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $v_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
+The inclusion of $\sigma$ in equation (\ref{eq:cooling2}) results because the top two lines apply only for $v_{w} > \sigma$ since their derivation assumed the existence of a stagnation radius given by equation (\ref{eq:rs_simple}).
 
@@
 
-This section describes the results of our numerical calculations and tests the accuracy of the analytic expressions provided in the previous section.
+This section describes the results of our numerical calculations, which we use to assess the validity of the analytic expressions provided in the previous section.
 Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
@@
 \end{eqnarray}
-Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is given by
+Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
 
@@
   This suggests that angular momentum should generally be unimportant.
+
+\section{Discussion}
+
+If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
+However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
+We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
 

### 2014-12-17 ms.tex
keeping going

@@
 
-Important properties such as the location of the stagnation radius, the SMBH accretion rate, and the possibility of thermal instability depend sensitively on the assumed heating rate $\propto v_{w,0}^{2}$  This section discusses individual heating sources, providing estimates of the value of $\vwO$ corresponding to each.
-Before proceeding, note that $\vwO$ is related to the volumetric heating rate $e$ according to
-\begin{align}
-  &\frac{q \vwO^2}{2}=e \,\,\,\Rightarrow\,\,\,\vwO = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
+Key properties of the flow, such as the stagnation radius, the SMBH accretion rate, and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w,0}^{2}$.
+This section summarizes individual heating sources, providing estimates of the value of
+\begin{align}
+  v_{\rm w,0} = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
   \label{eq:vw_eff}
 \end{align}
-
-\subsubsection{Stellar winds} 
+for each, where $e$ is volumetric heating rate.
+
+\subsection{Stellar winds} 
 {\bf AG: This section may have to be substantially modified in light
@@
 
-\subsubsection{Millisecond Pulsars} Energy injection due to the spin-down of millisecond pulsars (MSPs) is a potentially important heating source.
-If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes an average spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit volume $e \approx L_{\rm sd}n_{\rm
-  msp}\epsilon$ corresponds to an effective heating rate (eq.~ [\ref{eq:vw_eff}])
+\subsection{Millisecond Pulsars} Energy injection from the spin-down of millisecond pulsars (MSPs) is a potentially important heating source.
+If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes on average a spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit volume $e \approx \bar{L}_{\rm sd}n_{\rm
+  msp}\epsilon$ results in an effective heating rate (eq.~ [\ref{eq:vw_eff}])
 \begin{eqnarray}
-  v_{\rm w,0}^{\rm MSP} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
-  &\approx& 90\epsilon^{1/2}\left(\frac{\bar{L}_{\rm
+  v_{\rm w,0}^{\rm MSP} \approx 30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
         sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2}
@@
   \end{eqnarray}
-where $\epsilon< 1$ is the thermalization efficiency of the wind.
+where $\epsilon$ is the thermalization efficiency of the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
 The above estimate adopts a pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$ motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
 
-From the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate that the average spin-down luminosity of millisecond pulsars in the field (excluding those in globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, in which case $v_{\rm w,0} \lesssim 100$ km s$^{-1}$ is unimportant even for $\epsilon = 1$.
-For higher spin-down luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0} \lesssim 300$ km s$^{-1}$ makes MSP heating in principle be important for $\epsilon = 1$.
-However, much lower thermalization efficiencies of $\epsilon \lesssim 0.1$ are inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
-Also, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population.
-We thus conclude that MSPs are unlikely to be an important source of heating.
-
-\subsubsection{Type Ia Supernovae}
+The average spin-down luminosity of millisecond pulsars in the field is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.
+For higher spin-down luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0} \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important under the optimistc assumption $\epsilon = 1$.
+On the other hand, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population estimate above.
+We conclude that MSPs are unlikely to be an important source of heating.
+
+\subsection{Type Ia Supernovae}
 

### 2014-12-17 ms.tex
AGN section

@@
 The last term in equation (\ref{eq:dsdt}) accounts for heat transportation by electron conductivity, where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units).
-The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi \lesssim 1$ is an uncertain dimensionless constant (we adopt $\phi = XXX$).
+The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi \lesssim 1$ is an uncertain dimensionless constant (we adopt $\phi = 0.1$).
 Even a weak magnetic field perpendicular to the flow could in principle suppress the conductivity.
@@
 On the other hand, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population estimate above.
-We conclude that MSPs are unlikely to be an important source of heating.
+We conclude that MSPs are unlikely to be an important source of heating, probably insufficient to stabilize the steady flow against cooling instability (e.g.
+$v_{\rm w,0}^{\rm MSP} < v_{\rm critt}$; eq.~[\ref{eq:cooling2}])
 
@@
 
-Energy injected by Type Ia supernovae (SNe Ia) represents a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-Assuming that each Ia injects a thermal energy $E_{\rm Ia}$ into the interstellar medium, and that the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
+If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
@@
   where $\tau_{\star}$ is the time since star formation
-  (c.f.~\citealt{Scannapieco&Bildsten05}). {\bf AG:I deleted the extra
-    factor of $\chi$ that was hanging out here.}
+  (c.f.~\citealt{Scannapieco&Bildsten05}).
 
@@
   \end{eqnarray}
-where in the second line we have taken $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (\citealt{Ciotti+91}).
+where the second line assumes $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (\citealt{Ciotti+91}).
 
@@
 However, SNe can only be approximated as being a constant heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
-To estimate when this approximation is valid, we estimate the ``Ia radius"
+We define the ``Ia radius"
   \begin{align}
@@
 (equation~[\ref{eq:Msigma}]).
-Between subsequent supernovae, stars release a gaseous mass $M_{\rm gas} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm gas}\sigma^{2}$.
-Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2}$.
 
@@
 \begin{eqnarray}
-\frac{r_{\rm Ia}}{r_{\rm s}} &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68}\eta_{0.02}  \nonumber \\
+\frac{r_{\rm Ia}}{r_{\rm s}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
 &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
 \end{eqnarray}
-Thus only for massive SMBHs $M_{\bullet} \gtrsim 10^8 \Msun$ and/or very young populations will SNe Ia represent a steady source of heating at the nominal stagnation radius.
-
-\subsubsection{SMBH Feedback}
-
-Feedback from accretion onto the SMBH also represents a potentially important source of heating which is the most difficult to quantify.
-A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$.
+The fact that $r_{\rm Ia} \gg r_{\rm s}$ implies that Ia heating only represents a sources of steady heating near the stagnation radius for very massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ and/or very young populations ($\tau_{\star} \ll t_{\rm h}$).
+
+What is the effect of the Ia radius?
+Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm g}\sigma^{2}$.
+Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
+Hence Ia SN can in principle periodically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+
+\subsection{SMBH Feedback}
+
+Feedback from accretion onto the SMBH represents an important source of heating which is, however, the most difficult to quantify.
+A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$, which is itself a function of the heating rate (eq.~[\ref{eq:mdot_analytic}]).
+
 There are two types of SMBH feedback: kinetic and radiative.
-
-Radiative feedback can be effective even in low luminosity AGN via Compton heating (e.g.,~\citealt{Gan+14}).  Compton heating provides a volumetric heating rate (\citealt{Gan+14})
+Radiative feedback is potentially effective even in low luminosity AGN via Compton heating (e.g.,~\citealt{Gan+14}), which provides a volumetric heating rate (\citealt{Gan+14})
 \be
@@
 \ee
-where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K, which is assumed to be much higher than the gas temperature.
-We can estimate the importance of Compton heating by assuming that $L = \epsilon \dot{M}c^{2}$, where $\epsilon$ is the radiative efficiency and where $\dot{M}$ is estimated from equation (\ref{eq:mdot_analytic}).
-
-Using equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}), (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we thus calculate that (eq.~[\ref{eq:vw_eff}])
+where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$.
+
+We estimate the importance of Compton heating by assuming the SMBH radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where $\epsilon$ is the radiative efficiency and where $\dot{M}$ is estimated from equation (\ref{eq:mdot_analytic}).
+Then using equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}), (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation (\ref{eq:vw_eff}) that
 \begin{align}
@@
   \begin{cases}
-   125 T_{\rm C,9}^{0.5}\epsilon^{0.5}\eta_{0.02}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   200 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+   13 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   20 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm km\,s^{-1}}   &, \text{cusp},     
   \end{cases}
@@
 \end{align}
-Assuming that heating were dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) we find that
+where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} = \epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick accretion flow (e.g.~\citealt{Narayan&Yi95}).
+Assuming that heating is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds that
 \begin{align}
@@
 \end{align}
-where $\epsilon_{-2} = \epsilon/0.01$.  So, unless we have high $\eta$ then Compton heating will not be sufficient to stabilize the flow.
-
-Kinetic feedback occurs in the form of an mass outflow or jet from the viscinity of the black hole, which deposits its energy at much larger radii.
+Unless $\eta$ is very high, we conclude that Compton heating is insufficient to stabilize the steady flow against cooling instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$; eq.~[\ref{eq:cooling2}]).
+
+In contrast to radiative feedback, kinetic feedback occurs in the form of an mass outflow or jet from the viscinity of the black hole, which deposits its energy at much larger radii.
 We assume that the total heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
 If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind heating rate of
-\be
-v_w^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{\beta/2},
-\ee
-where we have used the fact that $\dot{M} \approx \eta M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto M_{\bullet}(r/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$ for radii interior to the outer break radius.
+\begin{eqnarray}
+v_{w,0}^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2}  \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{1-\Gamma/2},
+\end{eqnarray}
+where we have used the fact that $\dot{M} \approx \eta M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ for radii interior to the outer break radius (eq.~[\ref{eq:rhostar}]).
 Thus for $r_{\rm heat} \sim r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim 10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other sources of non-accretion powered heating.
 
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm
-  w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm
-  w,0}^{-\beta}$, where in the last proportionality we have used
-equation (\ref{eq:stag_simple}).  Hence, when SMBH heating dominates,
-it may ``self-regulate" itself.
-
-What is a physically motivated value of $r_{\rm heat}$?
-\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half
-opening angle $\theta_{\rm j} = 0.1$ (similar to those of AGN jets)
-propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a
+For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm w,0}^{\Gamma-2}$ is proportional to $v_{w,0}$ to a negative power, where the last proportionality makes use of equation (\ref{eq:stag_simple}).
+As in the case of Compton heating, SMBH kinetic heating, when dominant, may thus ``self-regulate".
+However, unlike in the case of local stellar wind heating, SMBH heating may not be thermally stable, since the central accretion rate does not respond instantaneously to a change in the thermodynamic properties of the gas on larger scales.
+
+What is a physically motivated value of the heating radius $r_{\rm heat}$?
+\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a
 timescale
@@
 Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
-
 \begin{equation}

### 2014-12-17 ms.tex
AGN section

@@
 
-\subsection{Millisecond Pulsars} Energy injection from the spin-down of millisecond pulsars (MSPs) is a potentially important heating source.
+\subsection{Millisecond Pulsars} Energy injection from millisecond pulsars (MSPs) is a potentially important heating source.
 If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes on average a spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit volume $e \approx \bar{L}_{\rm sd}n_{\rm
@@
 
-Assuming that $v_{\rm w,0}^{\rm Ia} \gg \sigma$ then by substituting equation (\ref{eq:vIa}) into (\ref{eq:rs_simple}) we can write
+Assuming that $v_{\rm w,0}^{\rm Ia} \gg \sigma$ then by substituting $v_{\rm w,0}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into our expression for the stagnation radius (\ref{eq:rs_simple}), we can write
 \begin{eqnarray}
-\frac{r_{\rm Ia}}{r_{\rm s}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
+\left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w,0}^{\rm Ia}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
 &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
 \end{eqnarray}
-The fact that $r_{\rm Ia} \gg r_{\rm s}$ implies that Ia heating only represents a sources of steady heating near the stagnation radius for very massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ and/or very young populations ($\tau_{\star} \ll t_{\rm h}$).
+The fact that $r_{\rm Ia} \gg r_{\rm s}$ would appear to imply that Ia heating only represents a sources of steady heating near the stagnation radius for very massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ and/or very young populations ($\tau_{\star} \ll t_{\rm h}$).
+However, this expression underestimates the importance of Ia heating, since the actual stagnation radius will be substantially larger than its value for $v_{\rm w,0}^{\rm Ia}$ if the nominal heating rate is much less than this.
+In general it is reasonable to expect that the impact of Ia SN will increase for larger SMBH masses.
 
@@
 \begin{eqnarray}
-v_{w,0}^{\bullet} \approx  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2}  \approx c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{1-\Gamma/2},
+v_{w,0}^{\bullet} &\approx&  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2}   \nonumber \\
+&\approx& c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{1-\Gamma/2},
 \end{eqnarray}
@@
 Thus for $r_{\rm heat} \sim r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim 10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other sources of non-accretion powered heating.
-
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto v_{\rm w,0}^{\Gamma-2}$ is proportional to $v_{w,0}$ to a negative power, where the last proportionality makes use of equation (\ref{eq:stag_simple}).
+However, if the jet distributes its energy on much larger scales comparable to the galaxy $r_{\rm heat} \sim $ kpc $\sim 10^{3}r_{\rm s}$ then the heating rate would be much smaller.
+
+For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto M_{\bullet}^{1-\Gamma/2}v_{\rm w,0}^{\Gamma-2}$ is proportional to $v_{w,0}$ to a negative power, where the last proportionality makes use of equation (\ref{eq:stag_simple}).
 As in the case of Compton heating, SMBH kinetic heating, when dominant, may thus ``self-regulate".
 However, unlike in the case of local stellar wind heating, SMBH heating may not be thermally stable, since the central accretion rate does not respond instantaneously to a change in the thermodynamic properties of the gas on larger scales.
+Also note that $v_{\rm w,0}^{\bullet}$ is proportional to a positive power of SMBH mass $\propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies, respectively.
+This is dependence may have important implications for the predicted dependence of X-ray luminosity on SMBH mass ($\S\ref{sec:mdot}$).
 
@@
 
-\subsubsection{Combined Heating Rate}
+\subsection{Combined Heating Rate}
 
@@
 \subsection{Mass accretion rate}
-
-For each solution we calculate the accretion rate $\dot{M}$ onto the
-SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
-\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
-10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
-$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
+\label{sec:mdot}
+
+For each solution we calculate the accretion rate $\dot{M}$ onto the SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd} \equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times 10^{46}M_{\bullet,8}$ erg s$^{-1}$.
+Figure~\ref{fig:mdot_mass} shows $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
 values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for
@@
 
-Note that since we expect $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and
-$\dot{M}\sim\vwO^{-4}$ for a core galaxy
-(equation~[\ref{eq:mdot_analytic}]), the mass accretion rate is
-expected to be a sensitive function of the assumed heating rate.
-% However, the accretion rate is proportional to the stellar mass
-% enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh
-% (\rs/\rsoi)^{2}$,while for cusp galaxies $\dot{M}\sim \Mbh
-% (\rs/\rsoi)$.  This steeper dependence is enough to offset the
-% tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed
-% $\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core
-% galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For
-% $\vwO=600$ km s$^{-1}$, core galaxies have a smaller accretion rate
-% for a given SMBH mass. On the other hand, if  $\rs/\rsoi>1$ (as would
-% be expected for small $\vwO$), core galaxies would have a larger
-% accretion rate. Thus, for $\vwO=150$ km/s, core galaxies have a large
-% accretion rate for a given $\Mbh$.
-
-%% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
-%% AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.
-
-We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH
-mass $M_{\bullet}$.  This appears to be in contradiction with the
-general down sizing trend observed for SMBH accretion in the local
-universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
-fact that for quiescent galaxies the nuclear X-ray luminosity obeys
-$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
-\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
+For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH mass  $\propto  M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively.
+This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local
+universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the fact that for quiescent galaxies the nuclear X-ray luminosity obeys $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.
+Our model instead predicts that $\Mdot
 \sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
 \sim \Mbh^{1.5-2}$, steeper than the observed relationship.
+
+Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
+Thus, only a weak positive dependence of $v_{\rm w,0} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{\rm w,0} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.
+What could cause this dependence?
+Maybe Ia SNa...
 

### 2014-12-17 ms.tex
fixed mccourt mania

@@
 the available reservoir of gas is more than sufficient to power
-low-luminosity AGN, assuming the s
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
-
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
-
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
-tandard radiative efficiency $\eta
+low-luminosity AGN, assuming the standard radiative efficiency $\eta
 \sim 0.1$ for thin disk accretion.  Indeed, there is now strong
@@
 \end{equation}
-
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
-
 The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

### 2014-12-17 ms.tex
fixed stag radius

@@
 \usepackage{epstopdf}
+\usepackage{hyperref}
 \epstopdfsetup{outdir=./figures/}
@@
 \usepackage{astro}
+\usepackage{deluxetable}
 % \usepackage{natbib}
@@
 \begin{eqnarray}
-v_{\rm w} = v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2} 
- \approx v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right)^{1/2},
+v_{\rm w} &=& v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2}  \nonumber \\
+ &\approx& v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}\left[\frac{v_{w,0}}{500\,\rm km\,s^{-1}}\right]^{-1}\right)^{1/2},
 \end{eqnarray}
-where the parameter $\vwO = 500 v_{500}$ km s$^{-1}$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+where we remind that the parameter $\vwO$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
 
@@
 
-Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs})
+Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs}, eq.~[\ref{eq:first_law}])
 \begin{align}
@@
 \end{align}
-%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}
-
-Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs})
-\begin{align}
-  \frac{\rs}{\rsoi}=\frac{\sigma^{2}}{2 v_{w,0}^{2} n}\left[
-   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right],
- \label{eq:stag_analytic}
-\end{align}
-in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the
-density profile at $r = r_{\rm s}$, and A and B are constants that depend on the Nuker
-parameter $\Gamma$ and the adiabatic index of the gas.
+
+Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
+\begin{align}
+\rs=\frac{G \Mbh}{n \vw(\rs)^2}\left(\frac{9-\Gamma}{2} \frac{\Mstar(\rs)}{\Mbh} +\frac{7}{2}\right),
+\label{eq:stag_analytic})
+\end{align}
+in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
 
@@
 \begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx 6
+  &\rs=\frac{7}{2}\frac{G \Mbh}{n v_{\rm w}^{2}} \approx 6
  \, \pc \,\, \Mbheight v_{500}^{-2},
@@
 \end{eqnarray}
+To reproduce the estimated values $\sim 10^{-XX}$ in low luminosity AGN, we thus require $v_{w,0} \sim $.  {\bf BDM: put some realistic numbers, e.g. from Ho 2009 or better references}
 
@@
 \label{sec:numerical}
+
+\begin{deluxetable}{lccccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{6}
+\tabcolsep0.05in\footnotesize
+\tablewidth{0pc}
+\tablecaption{Results
+\label{tab:surveys}}
+\tablehead {
+\colhead{Name}           &
+\colhead{Ang.~Res.}  &
+\colhead{$\nu$}          &
+\colhead{F$_{\rm lim}^{(a)}$}               & 
+\colhead{Area}          &
+\colhead{$\Delta T$$^{(c)}$}            &
+%\colhead{$T$$^{(d)}$}        &
+\colhead{N$_{\rm obs}$$^{(e)}$}        &
+\colhead{ref.}           
+}
+\startdata
+\colhead{}           &
+\colhead{(arcsec)}  &
+\colhead{(GHz)}          &
+\colhead{(mJy)}               & 
+\colhead{(deg$^{2}$)}          &
+\colhead{(d)}            &
+%\colhead{(yr)}      &       
+\colhead{}      \\
+\hline
+LOFAR & 80 & 0.15 & 11 & 1500 & 30 & 36 & 1\\
+LOFAR-Expanded  & - & - & 1.1 & $10^{4}$  & 30  & 36 & -\\
+VAST-Wide  & 10 & 1.3 & 0.5 & 10$^{4}$ & 1   & 1096 & 2\\
+VAST-Deep & - & - & 0.05 & -  & 365  & 4 & - \\
+VAST-Deep Single Field & - & - & - & -  & 1  & 365 & - \\
+VLASS-Wide  & 2 & 3 & 0.1 & $10^{4}$ & 365  & 4 & - \\
+VLASS-Deep  & 0.6 & - & 0.003 & 10  & 365  & 4 & - \\
+%VLASS-Deep-Short  & - & - & 0.01 & 40  & 10  & 10 & - \\
+%CMB50cm  & 840 & 150 & 3.2 & 10$^{4}$  & 1  & 1096 & - \\
+%CMB2m  & - & - & 1.0 & -  & -  & - & - \\
+CMB-fast  & 840 & 150 & 1.0 & 10$^{4}$  & 1  & 1096 & - \\
+CMB-deep  & - & - & 0.1 & -  & 100  & 11 & - \\
+\enddata
+\tablecomments{Put Results Here}
+\end{deluxetable}
 

### 2014-12-17 ms.tex
Uncommenting windheat appendix and then. Few more citations.

--- 2014-12-17 ms.tex
@@
 
-\author[Generozov, Stone, \& Metzger]{Aleksey S. Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
+\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
   Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
@@
 
-However, \citet{McCourt+12} argue that even if cooling is exactly balanced by heating everywhere, there is still a local thermal instability that operates to turn hot gas into cold clouds.
-However, this local instability only causes a significant local drop-out of mass from the hot medium (to low-T clouds), if the cooling timescale,
+However, \citet{McCourt+12} argue that even if cooling is exactly
+balanced by heating everywhere, there is still a local thermal
+instability that operates to turn hot gas into cold clouds.  However,
+this local instability only causes a significant local drop-out of
+mass from the hot medium (to low-T clouds), if the cooling timescale,
 \begin{align}
@@
 is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and (\ref{eq:rhors2}).
-We thus see that the condition $v_w \gtrsim v_{\rm crit}$ is also the condition for local instability, although the prefactor may be slightly different.
+timescale $t_{\rm ff}$, where the last equality is evaluated at the
+stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
+(\ref{eq:rhors2}).  We thus see that the condition $v_w \gtrsim v_{\rm
+  crit}$ is also the condition for local instability, although the
+prefactor may be slightly different.
 
@@
 
-%\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
-%\label{app:windheat}
-%\input{windheat}
+\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
+\label{app:windheat}
+\input{windheat}
 

### 2014-12-17 windheat.tex
Adding windheat appendix

If we assume that a stellar population forms
impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
$m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
future time $t$ is given by
\begin{equation}
f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
\end{equation}
where the main sequence turnoff mass is approximately
\begin{equation}
m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
\end{equation}
For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
\begin{equation}
f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
\end{equation}
{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
\begin{equation}
q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
\end{equation}
where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
\begin{equation}
q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
\end{equation}
This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.  Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.  Crudely approximating $v_{\rm w}=75~{\rm km~s}^{-1}$ for $m_{\rm T} < 10M_{\odot}$ and $v_{\rm w}=3000~{\rm km~s}^{-1}$ for $m_{\rm T} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss from Wolf-Rayet stars), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
{\bf AG:As I previously mentioned this discussion of the eta is not
  quite correct...}
\begin{figure}
\includegraphics[width=\columnwidth]{NickPlot.eps}
\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.  The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.  Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation. {\bf NCS: I think these old continuous curves are wrong, need to revise}}
\end{figure}

In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
function of time, for three different stellar density profiles $\Gamma
= \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
SMBH).  We parametrize the wind velocity as
\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
yr}}\right). \label{NickV1}
\end{equation} This counts Type II SNe heating as ``winds;'' if
instead we are in the portion of parameter space where $r_{\rm II}$ is
very large, then we use the alternate parametrization
\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
yr}}\right), \label{NickV2}
\end{equation} which only allows short lived Wolf-Rayet stars to
contribute to the high-heating mode.  The ``impulsive burst'' mode of
star formation produces large ($\sim 10$) differences between the
three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
large.  We also plot, as dotted curves, a simple model for the
``continuous'' mode of star formation, where mass loss is calculated
as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
energy injection in the wind is calculated as $\bar{v_{\rm
w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
produces small differences from late-time $\dot{M}$ seen in cusp
galaxies with impulsive star formation; however, continuous mode star
formation decreases late-time $\dot{M}$ by an order of magnitude
relative to impulsive star formation in core galaxies.  {\bf NCS: I
think this old discussion of MDot in the continuous limit is wrong,
need to revise}

The continuous mode of star formation can be studied more accurately
by including arbitrary star formation histories $S(t)$, measured in
units of mass per time.  In particular, if an impulsively formed
stellar population that is $t$ years of age, we can write its current
mass loss rate, $\dot{\bar{m}}(t)$, and its current effective wind
speed, $\bar{v}_{\rm w}(t)$.  Specifically,
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu(M_{\rm TO}(t))
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm ms} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(m_*, t) \mu(m_*) {\rm d}m_* }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(t) \dot{m}(m_*, t) \mu(m_*) {\rm d}m_*}{\bar{m}_*}.
\end{align}

The first term corresponds to a more impulsive contribution from
post-main sequence (PMS) stars, while the second term corresponds to
the contribution from main-sequence winds.

{\bf Note that I have not written the turnoff contribution in terms of
  a wind velocity. One can simply read off the specific energy
  injection rate from Voss '09...}

The effective wind velocity in the impulsive limit may then be written
as

\begin{align}
\bar{v}_w=2 \dot{\bar{e}}/\dot{\bar{m}}
\end{align}

We can then use these integrated quantities to determine the effective
$V_w$ for arbitrary star formation histories.

\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1\\
  V_w^2(t) &=2 \dot{E}(t)/\dot{M}(t)
\end{align}

\begin{figure}
\includegraphics[width=\columnwidth]{vw.pdf}
\caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
different $S(t)$.  The yellow and orange curves are the Moster SF
histories, with and without Type II SNe, respectively.  The red,
purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
respectively.  These solid curves lack SN, but the dashed purple curve
possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
variability timescale is greater than $\sim$ twice the duration of
high-velocity winds.}
\end{figure}

We show $V_{\rm W}$ for different star formation histories in
Fig. \ref{NickPlot2}.  In particular, we use Eqs. 17-20 from Moster et
al and the $M_{\rm BH}-M_{\rm halo}$ relation from Bandara et al {\bf
(NCS: add real refs)} to define $S(t)$ for particular galaxies.  It
seems that ``bumpy'' SF histories severely diminish $V_{\rm w}$ if the
timescale for SF variability is a factor of a few or more greater than
the duration of high-velocity winds (either 10 or 40 Myr).

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ms"
%%% End:

### 2015-01-07 ms.tex
Modifying the windheating appendix

@@
 \usepackage{amsmath,amssymb}
+\usepackage{mathrsfs}
 \usepackage{graphicx}
@@
 
-\begin{deluxetable}{lccccccccc}
+\begin{deluxetable}{lllllll}
 \tabletypesize{\scriptsize}
-\tablecolumns{6}
 \tabcolsep0.05in\footnotesize
 \tablewidth{0pc}
-\tablecaption{Results
-\label{tab:surveys}}
-\tablehead {
-\colhead{Name}           &
-\colhead{Ang.~Res.}  &
-\colhead{$\nu$}          &
-\colhead{F$_{\rm lim}^{(a)}$}               & 
-\colhead{Area}          &
-\colhead{$\Delta T$$^{(c)}$}            &
-%\colhead{$T$$^{(d)}$}        &
-\colhead{N$_{\rm obs}$$^{(e)}$}        &
-\colhead{ref.}           
-}
+\tablecaption{Cusp Results
+\label{tab:sols}}
+\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
+  \colhead{$\gamma$} & \colhead{$r_b$} &
+  \colhead{$\dot{M}/\dot{M}_{\rm Edd}$} & \colhead{$t_{\rm
+      cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
 \startdata
-\colhead{}           &
-\colhead{(arcsec)}  &
-\colhead{(GHz)}          &
-\colhead{(mJy)}               & 
-\colhead{(deg$^{2}$)}          &
-\colhead{(d)}            &
-%\colhead{(yr)}      &       
-\colhead{}      \\
-\hline
-LOFAR & 80 & 0.15 & 11 & 1500 & 30 & 36 & 1\\
-LOFAR-Expanded  & - & - & 1.1 & $10^{4}$  & 30  & 36 & -\\
-VAST-Wide  & 10 & 1.3 & 0.5 & 10$^{4}$ & 1   & 1096 & 2\\
-VAST-Deep & - & - & 0.05 & -  & 365  & 4 & - \\
-VAST-Deep Single Field & - & - & - & -  & 1  & 365 & - \\
-VLASS-Wide  & 2 & 3 & 0.1 & $10^{4}$ & 365  & 4 & - \\
-VLASS-Deep  & 0.6 & - & 0.003 & 10  & 365  & 4 & - \\
-%VLASS-Deep-Short  & - & - & 0.01 & 40  & 10  & 10 & - \\
-%CMB50cm  & 840 & 150 & 3.2 & 10$^{4}$  & 1  & 1096 & - \\
-%CMB2m  & - & - & 1.0 & -  & -  & - & - \\
-CMB-fast  & 840 & 150 & 1.0 & 10$^{4}$  & 1  & 1096 & - \\
-CMB-deep  & - & - & 0.1 & -  & 100  & 11 & - \\
+0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+unresolved \\
+0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+10^{ 2 }$ &  rb in fact unresolved\\
+0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+10^{ 4 }$ &  rb in fact unresolved\\
+0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
+cons on outer grid \\
+0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
+0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+10^{ 3 }$ &  energy cons on inner grid\\
+1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
+1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
+1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
+0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
+0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
+0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
+0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
+1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+  -3 }$ &  rb=400 pc was unsuccessful\\
 \enddata
-\tablecomments{Put Results Here}
 \end{deluxetable}
 
-This section describes the results of our numerical calculations, which we use to assess the validity of the analytic expressions provided in the previous section.
-Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
+\begin{deluxetable}{lllllll}
+\tabletypesize{\scriptsize}
+%\tablecolumns{6}
+\tabcolsep0.05in\footnotesize
+\tablewidth{0pc}
+\tablecaption{Core Results \label{tab:sols}}
+\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
+\colhead{$\gamma$} & \colhead{$r_b$} & \colhead{$\dot{M}/\dot{M}_{\rm
+Edd}$}  & \colhead{$t_{\rm cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
+\startdata
+0.01 & 600.0 & 0.1 & 100.0 & $ 3.4 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ &  \\
+0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
+0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
+1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
+1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  \\
+\enddata
+\end{deluxetable}
+
+This section describes the results of our numerical calculations,
+which we use to assess the validity of the analytic expressions
+provided in the previous section.  Numerical solutions are calculated
+for each galaxy for three different values of the stellar wind heating
+parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
 
@@
 
-We estimate the importance of Compton heating by assuming the SMBH radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where $\epsilon$ is the radiative efficiency and where $\dot{M}$ is estimated from equation (\ref{eq:mdot_analytic}).
-Then using equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}), (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation (\ref{eq:vw_eff}) that
-\begin{align}
-v_{\rm w,0}^{\rm C}  \simeq
-  \begin{cases}
-   13 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   20 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+{\bf AG: Note that I obtain Compton heating which is a factor of 2
+  higher--although power law dependences look right to me. Note that
+  the Compton heating will depend on radius--I use rs in my own
+  estimate. }
+We estimate the importance of Compton heating by assuming the SMBH
+radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
+$\epsilon$ is the radiative efficiency and where $\dot{M}$ is
+estimated from equation (\ref{eq:mdot_analytic}).  Then using
+equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}),
+(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
+(\ref{eq:vw_eff}) that
+\begin{align} v_{\rm w,0}^{\rm C} \simeq
+  \begin{cases} 13 \eta_{0.02}^{0.5}T_{\rm
+C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
+km\,s^{-1}} &, \text{core}\\ 20 \eta_{0.02}^{0.5}T_{\rm
+C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
+km\,s^{-1}} &, \text{cusp},
   \end{cases}
   \label{eq:vC}
-\end{align}
-where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} = \epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick accretion flow (e.g.~\citealt{Narayan&Yi95}).
-Assuming that heating is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds that
-\begin{align}
-v_{\rm w,0}^{\rm C}  \simeq
-  \begin{cases}
-   106 \eta_{0.02}^{0.21}T_{\rm C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   76 \eta_{0.02}^{0.29}T_{\rm C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}   &, \text{cusp},     
+\end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
+\epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick
+accretion flow (e.g.~\citealt{Narayan&Yi95}).  Assuming that heating
+is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds
+that
+\begin{align} v_{\rm w,0}^{\rm C} \simeq
+  \begin{cases} 106 \eta_{0.02}^{0.21}T_{\rm
+C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
+&, \text{core}\\ 76 \eta_{0.02}^{0.29}T_{\rm
+C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
+&, \text{cusp},
   \end{cases}
   \label{eq:vC2}
-\end{align}
-Unless $\eta$ is very high, we conclude that Compton heating is insufficient to stabilize the steady flow against cooling instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$; eq.~[\ref{eq:cooling2}]).
-
-In contrast to radiative feedback, kinetic feedback occurs in the form of an mass outflow or jet from the viscinity of the black hole, which deposits its energy at much larger radii.
-We assume that the total heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
-If this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat}$, then the local heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind heating rate of
-\begin{eqnarray}
-v_{w,0}^{\bullet} &\approx&  \left(\frac{2t_{\rm h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta \rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2}   \nonumber \\
-&\approx& c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm heat}}\right)^{1-\Gamma/2},
-\end{eqnarray}
-where we have used the fact that $\dot{M} \approx \eta M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ for radii interior to the outer break radius (eq.~[\ref{eq:rhostar}]).
-Thus for $r_{\rm heat} \sim r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim 10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other sources of non-accretion powered heating.
-However, if the jet distributes its energy on much larger scales comparable to the galaxy $r_{\rm heat} \sim $ kpc $\sim 10^{3}r_{\rm s}$ then the heating rate would be much smaller.
-
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto M_{\bullet}^{1-\Gamma/2}v_{\rm w,0}^{\Gamma-2}$ is proportional to $v_{w,0}$ to a negative power, where the last proportionality makes use of equation (\ref{eq:stag_simple}).
-As in the case of Compton heating, SMBH kinetic heating, when dominant, may thus ``self-regulate".
-However, unlike in the case of local stellar wind heating, SMBH heating may not be thermally stable, since the central accretion rate does not respond instantaneously to a change in the thermodynamic properties of the gas on larger scales.
-Also note that $v_{\rm w,0}^{\bullet}$ is proportional to a positive power of SMBH mass $\propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies, respectively.
-This is dependence may have important implications for the predicted dependence of X-ray luminosity on SMBH mass ($\S\ref{sec:mdot}$).
-
-What is a physically motivated value of the heating radius $r_{\rm heat}$?
-\citet{Bromberg+11} show that a jet of luminosity $L_{\rm j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius $r$ in a
-timescale
+\end{align} Unless $\eta$ is very high, we conclude that Compton
+heating is insufficient to stabilize the steady flow against cooling
+instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$;
+eq.~[\ref{eq:cooling2}]).
+
+In contrast to radiative feedback, kinetic feedback occurs in the form
+of an mass outflow or jet from the viscinity of the black hole, which
+deposits its energy at much larger radii.  We assume that the total
+heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where
+$\epsilon_{\rm j} < 1$ is an efficiency factor.  If this energy is
+deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm
+heat}$, then the local heating rate $e = \epsilon_{\rm
+j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind heating rate
+of
+\begin{eqnarray} v_{w,0}^{\bullet} &\approx& \left(\frac{2t_{\rm
+h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
+\rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
+j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
+&\approx& c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
+heat}}\right)^{1-\Gamma/2},
+\end{eqnarray} where we have used the fact that $\dot{M} \approx \eta
+M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto
+M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ for radii interior to the outer
+break radius (eq.~[\ref{eq:rhostar}]).  Thus for $r_{\rm heat} \sim
+r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim
+10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other
+sources of non-accretion powered heating.  However, if the jet
+distributes its energy on much larger scales comparable to the galaxy
+$r_{\rm heat} \sim $ kpc $\sim 10^{3}r_{\rm s}$ then the heating rate
+would be much smaller.
+
+For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm
+  w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto
+M_{\bullet}^{1-\Gamma/2}v_{\rm w,0}^{\Gamma-2}$ is proportional to
+$v_{w,0}$ to a negative power, where the last proportionality makes
+use of equation (\ref{eq:stag_simple}).  As in the case of Compton
+heating, SMBH kinetic heating, when dominant, may thus
+``self-regulate".  However, unlike in the case of local stellar wind
+heating, SMBH heating may not be thermally stable, since the central
+accretion rate does not respond instantaneously to a change in the
+thermodynamic properties of the gas on larger scales.  Also note that
+$v_{\rm w,0}^{\bullet}$ is proportional to a positive power of SMBH
+mass $\propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies,
+respectively.  This is dependence may have important implications for
+the predicted dependence of X-ray luminosity on SMBH mass
+($\S\ref{sec:mdot}$).
+
+What is a physically motivated value of the heating radius $r_{\rm
+  heat}$?  \citet{Bromberg+11} show that a jet of luminosity $L_{\rm
+  j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
+AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius
+$r$ in a timescale
 \begin{eqnarray}
@@
 % % density profiles. The comparison is shown in
-% %% AG-The chosen properties, in particular eta may be summarized in a table.
+% %% AG-The chosen properties, in particular eta may be summarized in a tabe.
 % %% AG-Mention rising temperature profiles on large scales.

### 2015-01-07 windheat.tex
Modifying the windheating appendix

@@
-If we assume that a stellar population forms
-impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
-$m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
-future time $t$ is given by
-\begin{equation}
-f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
-\end{equation}
-where the main sequence turnoff mass is approximately
-\begin{equation}
-m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
-\end{equation}
-For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
-\begin{equation}
-f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
-\end{equation}
-{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
-If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
-\begin{equation}
-q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
-\end{equation}
-where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
-\begin{equation}
-q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
-\end{equation}
-This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
+% If we assume that a stellar population forms
+% impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
+% $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
+% future time $t$ is given by
+% \begin{equation}
+% f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
+% \end{equation}
+% where the main sequence turnoff mass is approximately
+% \begin{equation}
+% m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
+% \end{equation}
+% For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
+% \begin{equation}
+% f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
+% \end{equation}
+% {\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
+% If we approximate post-main sequence evolution as instantaneous and define $\lambda(\Mstar)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
+% \begin{equation}
+% q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
+% \end{equation}
+% where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} \Mstar\mu(\Mstar)d\Mstar \approx 0.3 M_\odot$.
+Further approximating $\lambda(\Mstar)=0.5$, and using the Salpeter IMF once more, gives
+% \begin{equation}
+% q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
+% \end{equation}
+% This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
 Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
@@
 Crudely approximating $v_{\rm w}=75~{\rm km~s}^{-1}$ for $m_{\rm T} < 10M_{\odot}$ and $v_{\rm w}=3000~{\rm km~s}^{-1}$ for $m_{\rm T} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss from Wolf-Rayet stars), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
-{\bf AG:As I previously mentioned this discussion of the eta is not
-  quite correct...}
-\begin{figure}
-\includegraphics[width=\columnwidth]{NickPlot.eps}
-\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
+% {\bf AG:As I previously mentioned this discussion of the eta is not
+%   quite correct...}
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{NickPlot.eps}
+% \caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times \Mstar(r_{\rm s})$, in arbitrary units.
 The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
@@
 {\bf NCS: I think these old continuous curves are wrong, need to revise}}
-\end{figure}
+% \end{figure}
 
-In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
-function of time, for three different stellar density profiles $\Gamma
-= \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
-influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
-SMBH).  We parametrize the wind velocity as
-\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
-km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
-yr}}\right). \label{NickV1}
-\end{equation} This counts Type II SNe heating as ``winds;'' if
-instead we are in the portion of parameter space where $r_{\rm II}$ is
-very large, then we use the alternate parametrization
-\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
-km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
-yr}}\right), \label{NickV2}
-\end{equation} which only allows short lived Wolf-Rayet stars to
-contribute to the high-heating mode.  The ``impulsive burst'' mode of
-star formation produces large ($\sim 10$) differences between the
-three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
-smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
-large.  We also plot, as dotted curves, a simple model for the
-``continuous'' mode of star formation, where mass loss is calculated
-as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
-energy injection in the wind is calculated as $\bar{v_{\rm
-w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
-km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
-produces small differences from late-time $\dot{M}$ seen in cusp
-galaxies with impulsive star formation; however, continuous mode star
-formation decreases late-time $\dot{M}$ by an order of magnitude
-relative to impulsive star formation in core galaxies.  {\bf NCS: I
-think this old discussion of MDot in the continuous limit is wrong,
-need to revise}
+% In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
+% function of time, for three different stellar density profiles $\Gamma
+% = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
+% influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
+% SMBH).  We parametrize the wind velocity as
+% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
+% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
+% yr}}\right). \label{NickV1}
+% \end{equation} This counts Type II SNe heating as ``winds;'' if
+% instead we are in the portion of parameter space where $r_{\rm II}$ is
+% very large, then we use the alternate parametrization
+% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
+% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
+% yr}}\right), \label{NickV2}
+% \end{equation} which only allows short lived Wolf-Rayet stars to
+% contribute to the high-heating mode.  The ``impulsive burst'' mode of
+% star formation produces large ($\sim 10$) differences between the
+% three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
+% smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
+% large.  We also plot, as dotted curves, a simple model for the
+% ``continuous'' mode of star formation, where mass loss is calculated
+% as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
+% energy injection in the wind is calculated as $\bar{v_{\rm
+% w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
+% km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
+% produces small differences from late-time $\dot{M}$ seen in cusp
+% galaxies with impulsive star formation; however, continuous mode star
+% formation decreases late-time $\dot{M}$ by an order of magnitude
+% relative to impulsive star formation in core galaxies.  {\bf NCS: I
+% think this old discussion of MDot in the continuous limit is wrong,
+% need to revise}
 
-The continuous mode of star formation can be studied more accurately
-by including arbitrary star formation histories $S(t)$, measured in
-units of mass per time.  In particular, if an impulsively formed
-stellar population that is $t$ years of age, we can write its current
-mass loss rate, $\dot{\bar{m}}(t)$, and its current effective wind
-speed, $\bar{v}_{\rm w}(t)$.  Specifically,
+The energy and mass injection from stellar winds will be the sum ofthe
+contributions from main sequence and post-main sequence (PMS) stars.
+For an impulsively formed stellar population of age $t$, the mass
+injection rate per unit stellar mass ($\dot{\bar{m}}(t)$) and energy
+injection rate per unit stellar mass will be given by
+($\dot{\bar{e}}(t)$).
+
 \begin{align} 
   \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu(M_{\rm TO}(t))
-    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm ms} \int_{m_0}^{m_{\rm
+    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
         T}(t)}
-    \dot{m}(m_*, t) \mu(m_*) {\rm d}m_* }{\bar{m}_*}\\
-  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
-  \frac{\vw^2(t) \dot{m}(m_*, t) \mu(m_*) {\rm d}m_*}{\bar{m}_*}.
+    \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar }{\bar{m}_*}\\
+  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
+  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar}{\bar{m}_*}.
+  \label{eq:edotImp}
 \end{align}
 
-The first term corresponds to a more impulsive contribution from
-post-main sequence (PMS) stars, while the second term corresponds to
-the contribution from main-sequence winds.
+The first terms in each expression above correspond to the
+contributions from PMS stars, while the second terms correspond to the
+contributions from main sequence stars. The main sequence winds are
+subdominant in mass, and may be not be thermalized and
+mixed with the rest of the injected gas. Thus, we include a
+thermalization efficiency, $ 0\le f_{\rm MS}\le 1$, in
+equation~\eqref{eq:edotImp}. Throughout this paper we set $f_{\rm
+  MS}=1$.
 
-{\bf Note that I have not written the turnoff contribution in terms of
-  a wind velocity. One can simply read off the specific energy
-  injection rate from Voss '09...}
+We assume a Salpeter IMF $\mu(\Mstar)\sim M^{-2.35}$, truncated at $0.1
+\Msun$ on the low mass end and at $100 \Msun$ on the high mass
+end. The corresponding $\bar{m}_*$ is 0.35 $\Msun$.
+
+For the turnoff mass, $M_{\rm TO}$, we take the following fitting
+formula
+
+\begin{align}
+\log(M_{\rm TO})=0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
+\end{align}
+
+where $x=\log(t/10^9 {\rm years})$ and $M_{\rm TO}$ is in units
+$\Msun$. This fit is designed to reproduce the results in 
+Table 9 of \citet{MaederMeynet:1987a} and then asymptotes to the fit
+for $M_{\rm TO}$ given in equation (9) of \citet{CiottiOstriker:2007a}
+for intermediate and late times ($t \gsim 10^8$ years).
+
+For $\Delta M(t)$ we use equation (10) from \citet{CiottiOstriker:2007a}
+
+\begin{align}
+\Delta M=
+\begin{cases}
+0.945 M_{\rm TO}-0.503 & M_{\rm TO} < 9 \Msun\\
+ M_{\rm TO}-1.4 \Msun &  M_{\rm TO} \ge 9 \Msun
+\end{cases}
+\end{align}
+
+To estimate the mass loss from main sequence stars $\dot{\Mstar,t}$,
+we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This
+  prescription is a generalization of the Reimers' mass loss law. This
+expression is derived assuming the stellar wind results from the
+turbulent overflow of moaterial in the chromosphere or underneath it.} {\bf AG:
+  unfortunately this is not really meant for MS stars...}
+
+\begin{align}
+  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
+  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
+  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
+\end{align}
+
+where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
+luminosity, effective and surface gravity respectively. $g_{\odot}$ is
+the stellar surface gravity. To calculate $R_*$ and $L_*$ we use the
+following scaling relations (taken from Kippenhann and Weygert Figures
+22.2 and 22.3).
+
+\begin{align}
+L_*=
+\begin{cases}
+L_{\odot} (\Mstar/\Msun)^{3.2} & \Mstar > \Msun \\
+L_{\odot} (\Mstar/\Msun)^{2.5} & \Mstar \le \Msun
+\end{cases}
+\end{align}
+
+\begin{align}
+r_*=
+\begin{cases}
+R_{\odot} (\Mstar/\Msun)^{0.57} & \Mstar > \Msun \\
+R_{\odot} (\Mstar/\Msun)^{0.8} & \Mstar \le \Msun
+\end{cases}
+\end{align}
+
+To get a handle on $\dot{e}_{\rm TO}(t)$, we use the results from
+\citet{VossDiehl+:2009a} who use a population synthesis code to
+simulate the mass and energy injection into the ISM from an OB
+association. For the first $\sim 10$ Myr the energy injection will
+come from energetic Wolf-Rayet star winds. The energy injection rate
+per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
+stellar winds is plotted in the top panel of their Figure 7 and is
+well fit {\bf AG: A little more detail here...} by
+
+\begin{align}
+\dot{\mathcal{E}} (t)=
+\begin{cases}
+  1.3 \times 10^{36} {\rm ergs/s} & t<4 \times 10^6 {\rm years}\\
+  1.3  \times 10^{36} {\rm ergs/s} \left(\frac{t}{4 \times  10^6}\right)^{-3.73} & t \ge 4 \times 10^6 {\rm years}.
+\end{cases}
+\label{eq:voss}
+\end{align}
+
+ $\dot{e}_{\rm TO}(t)$ is related to $\dot{\mathcal{E}}$  via
+
+\begin{align}
+\dot{e}_{\rm TO}(t)=f_{8} \dot{\mathcal{E}} / \bar{m}_*,
+\label{eq:eto}
+\end{align}
+
+where $f_{8}$ is the fraction of the stellar population with
+$\Mstar>8 \Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter
+IMF.  Equation~\eqref{eq:voss} and~\eqref{eq:eto} will be valid onlyfor $t
+\lsim 10$ Myr. However, the turnoff contribution will become extremely
+energetically subdominant at later times as far slower dust-driven
+winds come to dominate the energy budget {\bf AG: Nick check--is the
+  preceding sentence accurate}
+
+We calculate the wind velocity for main sequence winds $v_w (\Mstar,
+t)$ using...{\bf AG:Current just use the value for the sun~430 km/s
+  replace with the real prescription we end up using.}
 
@@
 \begin{align}
-\bar{v}_w=2 \dot{\bar{e}}/\dot{\bar{m}}
+\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
+\label{eq:vwImp}
 \end{align}
 
+We plot $\bar{v}_w$ in Figure~\ref{fig:vwImp}.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{vwImp.pdf}
+\caption{\label{fig:vwImp} The effective $\vw$ from stellar winds from
+  a stellar population formed in a starburst $t$ years ago.}
+\end{figure}
+
 We can then use these integrated quantities to determine the effective
-$V_w$ for arbitrary star formation histories.
+$V_w$ for arbitrary star formation histories. For a stellar population
+with star formation rate $S(t)$
 

### 2015-01-07 windheat.tex
More changes to windheat appendix.

@@
 For an impulsively formed stellar population of age $t$, the mass
-injection rate per unit stellar mass ($\dot{\bar{m}}(t)$) and energy
-injection rate per unit stellar mass will be given by
-($\dot{\bar{e}}(t)$).
+injection rate per unit stellar mass,$\dot{\bar{m}}(t)$, and  the energy
+injection rate per unit stellar mass, $\dot{\bar{e}}(t)$,  will be given by
 
@@
 contributions from PMS stars, while the second terms correspond to the
-contributions from main sequence stars. The main sequence winds are
-subdominant in mass, and may be not be thermalized and
+contributions from main sequence stars. The main sequence winds are a
+small fraction of the mass, and they may be not be thermalized and
 mixed with the rest of the injected gas. Thus, we include a
@@
 \Msun$ on the low mass end and at $100 \Msun$ on the high mass
-end. The corresponding $\bar{m}_*$ is 0.35 $\Msun$.
+end. The corresponding mean stellar mass, $\bar{m}_*$ is 0.35 $\Msun$.
 
@@
 
-To estimate the mass loss from main sequence stars $\dot{\Mstar,t}$,
+To estimate the mass loss from main sequence stars
+$\dot{m}(\Mstar, t)$,
 we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This

### 2015-01-07 windheat.tex
More modifications to the appendix.

@@
 \begin{align}
-  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
+  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* r_*}{\Mstar}
   \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
@@
 association. For the first $\sim 10$ Myr the energy injection will
-come from energetic Wolf-Rayet star winds. The energy injection rate
+be dominated by fast Wolf-Rayet star winds. The energy injection rate
 per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
@@
 
+Equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr. For $t\gsim
+10$ Myr, $\dot{e}_{\rm TO}$ will be negligible as lower mass stars
+shed their gas is slow dust-driven winds during their post-main
+sequence evolution {\bf AG-Nick is the preceding statement accurate},
+and for our purposes the exact functional form of $\dot{e}_{\rm
+  TO}(t)$ is unimportant. So we adopt Equation~\eqref{eq:voss} for all times.
+
  $\dot{e}_{\rm TO}(t)$ is related to $\dot{\mathcal{E}}$  via
@@
 
-where $f_{8}$ is the fraction of the stellar population with
-$\Mstar>8 \Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter
-IMF.  Equation~\eqref{eq:voss} and~\eqref{eq:eto} will be valid onlyfor $t
-\lsim 10$ Myr. However, the turnoff contribution will become extremely
-energetically subdominant at later times as far slower dust-driven
-winds come to dominate the energy budget {\bf AG: Nick check--is the
-  preceding sentence accurate}
+where $f_{8}$ is the fraction of the stellar population with $\Mstar>8
+\Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter IMF.
 
@@
 
-We plot $\bar{v}_w$ in Figure~\ref{fig:vwImp}.
+We plot $\bar{v}_w$ versus time in Figure~\ref{fig:vwImp}.
 

### 2015-01-07 windheat.tex
Fixing citations at the end of appendix.

@@
 We show $V_{\rm W}$ for different star formation histories in
-Fig. \ref{NickPlot2}.  In particular, we use Eqs. 17-20 from Moster et
-al and the $M_{\rm BH}-M_{\rm halo}$ relation from Bandara et al {\bf
-(NCS: add real refs)} to define $S(t)$ for particular galaxies.  It
-seems that ``bumpy'' SF histories severely diminish $V_{\rm w}$ if the
-timescale for SF variability is a factor of a few or more greater than
-the duration of high-velocity winds (either 10 or 40 Myr).
+Fig. \ref{NickPlot2} {\bf AG: this plot still uses the old ad hoc vw
+  prescription? If so it would need to be fixed. In any case, we still
+  differ in detail on the vw from stars}.  In particular, we use
+Eqs. 17-20 from \citet{MosterNaab+:2013a} and the $M_{\rm BH}-M_{\rm
+  halo}$ relation from \citet{BandaraCrampton+:2009a} to define $S(t)$
+for particular galaxies.  It seems that ``bumpy'' SF histories
+severely diminish $V_{\rm w}$ if the timescale for SF variability is a
+factor of a few or more greater than the duration of high-velocity
+winds (either 10 or 40 Myr).
 

### 2015-01-09 ms.tex
More modifications to the appendix.
Adding new versions of figures corresponding to cusp galaxies.

@@
 \newcommand{\rhostar}{\rho_*}
-\newcommand{\Mstar}{M_{\star}}
+\newcommand{\Mstar}{m_{\star}}
 \newcommand{\Mseight}{M_{\star,8}}
@@
 1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
-1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+  -2 }$ &  possible issue w/ conv \\
 1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
-  -3 }$ &  rb=400 pc was unsuccessful\\
+  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
 \enddata
 \end{deluxetable}
+
+\begin{table*}
+\centering
+\begin{minipage}{18cm}
+\caption{Models Evolved and Outflow
+Properties\label{t:models}\label{t:results}. The first
+six columns show model name, HMNS lifetime, stellar period, fractional
+radial resolution
+at inner boundary, and irradiation by the neutron star, respectively.
+The last eight columns show integrated properties of the outflow,
+restricted to equatorial
+ ($\theta \in [30^\circ,150^\circ]$) and polar ($\theta<30^\circ$ and
+$\theta > 150^\circ$)
+latitudes. Each group of four columns includes the mass-flux weighted
+electron fraction, entropy,
+and expansion time at a radius where the mass-flux weighted temperature is
+$5\times10^9$~K, as
+well as the net mass in unbound material crossing a surface at $10^9$~cm,
+normalized
+by the initial torus mass.}
+\begin{tabular}{lccccccccccccc}
+\hline
+{Model}&
+{$t_{\rm ns}$} &
+{$P_\star$} &
+{$\alpha$} &
+{$\Delta r_{\rm min}/R_\star$} &
+{$\star$-Irr.} &
+\multicolumn{4}{c}{Equatorial Outflow} &
+\multicolumn{4}{c}{Polar Outflow$^b$}\\
+{ } & \multicolumn{2}{c}{(ms)} &  {}  &  {}  & {} &
+{$\bar{Y}_e$} &
+{$\bar{s}$ } &
+{$t_{\rm exp}$} &
+{$M_{\rm ej,unb}/M_{\rm t0}$} &
+{$\bar{Y}_e$} &
+{$\bar{s}$ } &
+{$t_{\rm exp}$} &
+{$M_{\rm ej,unb}/M_{\rm t0}$}\\
+\multicolumn{6}{c}{} & {} & {($k$/b)} & {(ms)} & {(\%)} & {} & {($k$/b)} &
+{(ms)} & {(\%)}\\
+%}
+\hline
+t000A3      & 0        & ... & 0.03 & 5E-3 & No   & 0.18 & 18 & 27  & 2.1
+& ...  & ... & ... & 0.9 \\
+t010A3p15   & 10       & 1.5 &      &      & Yes  & 0.19 & 20 & 30  & 2.5
+& ...  & ... & ... & 1.0 \\
+t030A3p15   & 30       &     &      &      &      & 0.23 & 21 & 27  & 3.9
+& 0.50 & 45  & 7.6 & 1.3 \\
+t100A3p15   & 100      &     &      &      &      & 0.28 & 20 & 33  & 9.2
+& 0.47 & 42  & 11  & 4.0 \\
+t300A3p15   & 300      &     &      &      &      & 0.30 & 20 & 32  & 28
+& 0.44 & 38  & 17  & 8.8 \\
+tInfA3p15   & $\infty$ &     &      &      &      & 0.32 & 21 & 42  & 67
+& 0.43 & 52  & 17  & 22  \\
+\noalign{\smallskip}
+pA1p15      & $\infty$ & 1.5 & 0.01 & 5E-3 & Yes  & 0.36 & 21 & 61  & 47
+& 0.45 & 52  & 19  & 22 \\
+pA3p20      &          & 2   & 0.03 &      &      & 0.30 & 29 & 37  & 62
+& 0.37 & 62  & 15  & 17 \\
+pA3p15xs    &          & 1.5 &      &      & No   & 0.27 & 21 & 45  & 56
+& 0.35 & 61  & 15  & 23 \\
+\noalign{\smallskip}
+rA3p15r1    & $\infty$ & 1.5 & 0.03 & 1E-2 & Yes  & 0.32 & 21 & 45  & 69
+& 0.43 & 53  & 17  & 22 \\
+rA3p15r2$^a$   &       &     &      & 2E-3 &      & ... & ... & ... & ...
+& ...  & ... & ... & ... \\
+\hline
+\hline
+\multicolumn{14}{l}{$^a$ Model rA3p15r2 was evolved for a shorter time.
+See Appendix~\ref{s:neutrino_details}
+                    for details.}\\
+\multicolumn{14}{l}{$^b$ Average thermodynamic quantities are not computed
+if there is no region
+                         where the average temperature is $\sim 5\times 10^9$~K.}
+\label{table:models}
+\end{tabular}
+\end{minipage}
+\end{table*}
 
@@
     \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
-    $\Mbh=10^8 \Msun$ ({\it dashed}). Squares mark out the location of
+    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
+    galaxies ($\gamma$=0.8) and thick lines correspond to core
+    galaxies ($gamma$=0.1). Squares mark out the location of
     the stagnation radius for each solution.

### 2015-01-09 ms.tex
test

@@
 
-\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
+\author[Generozov, Stone, \& Metzger]{Aleksey S.~Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
   Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
@@
 \begin{abstract}
-  We calculate the steady-state hydrodynamic profiles of hot gas in
-  the nuclei of a sample of early-type quiescent galaxies.  We assume
+  Steady-state hydrodynamic profiles of hot gas in  the nuclei of a sample of early-type quiescent galaxies are calculated.  We assume
   that mass is supplied to the circumnuclear medium (CNM) entirely by

### 2015-01-09 ms.tex
test2
updated abstract

--- 2015-01-09 ms.tex
@@
 \begin{abstract}
-  We calculate the steady-state hydrodynamic profiles of hot gas in
-  the nuclei of a sample of early-type quiescent galaxies.  We assume
-  that mass is supplied to the circumnuclear medium (CNM) entirely by
-  stellar winds according to the radial stellar profiles for each
-  galaxy, while the gas is heated by a combination of shocked stellar
-  winds and supernovae.  Our analytic and numerical results are used
-  to estimate the accretion rates onto the central supermassive black
-  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
-  heating efficiency, the latter of which is related schematically to
-  the age of the stellar population, the frequency of supernovae, and
-  the efficacy of accretion feedback processes.  For a fixed heating
-  efficiency, we find that the SMBH accretion Eddington factor
-  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
-  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
-  nuclei, respectively.
-  % However, considering the potentially lower heating efficiency of low
-  % mass SMBHs (due to a younger stellar population and the rareity of
-  % supernovae within the stagnation radius) and their resulting higher
-  % susceptibility to cooling instability, we find a flatter
-  % relationship $\alpha \approx 0$. 
-  Our results are used to check previous estimates of the SMBH
-  accretion rate assuming Bondi accretion and extrapolating the X-ray
-  measured density and temperature to the unresolved Bondi radius.  We
-  also discuss the implications of our results for the diversity of
-  CNM environments encountered by the jetted outflows from tidal
-  disruption events, and for the use of an assumed
-  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
-  fraction of SMBHs in low mass galaxies.
+Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.
+Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
+Neglecting radiative cooling, analytic estimates are derived for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+We assess over what range of conditions radiative instability will develop, assuming a star formation history corresponding to the average of that for galaxies of a given black hole mass.
+Our main conclusion is that.....
+Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
 \end{abstract}

### 2015-01-09 ms.tex
updated abstract2

@@
 Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-Neglecting radiative cooling, analytic estimates are derived for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-We assess over what range of conditions radiative instability will develop, assuming a star formation history corresponding to the average of that for galaxies of a given black hole mass.
+Analytic estimates are derived, neglecting radiative cooling, for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+These results are used to assess over what range of conditions radiative instability will develop, assuming a feedback due to the average star formation history for galaxies of the given black hole mass.
 Our main conclusion is that.....

### 2015-01-09 ms.tex
editing intro

@@
 
-In order to understand why most SMBHs appear to be inactive, it is
-necessary to understand their gaseous environments.  Hot gas near the
-SMBH sphere of influence (the `circumnuclear medium' or CNM) controls
-the central mass accretion rate $\dot{M}$.  Better knowledge of how
-$\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
-galactic nucleus is necessary to understand the co-evolution of SMBHs
-and their host galaxies with cosmic time.  SMBH growth in the low
-redshift universe, for instance, appears to be dominated by low mass
-black holes (e.g.~\citealt{Heckman+04}).  Although this is often
-attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}),
-the physical processes involved may be distinct from those operating
-at higher SMBH masses and accretion rates in quasars.
-
-The accretion rates of low mass SMBHs and their resulting nuclear
-X-ray luminosities $L_X$ also have implications for observational
+To understand why most SMBHs appear to be inactive requires understanding their gaseous environments.  Hot gas near the
+SMBH sphere of influence (hereafter the `circumnuclear medium', or CNM) controls the central mass accretion rate $\dot{M}$.
+The latter in turn affects the luminosity of the accretion flow and the possible impact of its energy and momentum input (`feedback') on larger scales.
+The presence of dense gas in the nucleus can also lead to runaway cooling instabilities, resulting in bursty star-formation or episodic AGN activity (reference Ciotti and others).
+
+Knowledge of how $\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
+galactic nucleus informs key questions related to co-evolution of SMBHs and their host galaxies with cosmic time.
+SMBH growth in the low redshift universe appears to be dominated by lower mass black holes (e.g.~\citealt{Heckman+04}).
+This is often
+attributed to cosmological `down sizing' (e.g, \citealt{Gallo+08}), even though the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
+
+The accretion rates of low mass SMBHs, and their resulting nuclear X-ray luminosities $L_X$, also have implications for observational
 constraints on their occupation fraction in low mass galaxies and the
-possible existence of intermediate mass black holes.
-\citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and
-$L_X$ from a sample of relatively high mass galaxies
-(\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass
-galaxies, to infer tentative evidence for an occupation fraction less
-than unity.  However, this method relies on extrapolating a power-law
-fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the
-instrumental detection threshold.  The conclusions of
-\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
-the $L_X$-$\Mbh$ relationship at small $\Mbh$.
+possible existence of intermediate mass black holes.  By combining the average relationship between $\Mbh$ and
+$L_X$ measured from a sample of high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in lower mass
+galaxies, \citet{MillerGallo+:2014a}  infer tentative evidence for an occupation fraction less than unity in the latter.
+This method, however, relies on extrapolating a power-law fit to the $L_X-\Mbh$ distribution to low $\Mbh$ below the detection threshold.
+
+%The conclusions of
+%\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
+%the $L_X$-$\Mbh$ relationship at small $\Mbh$.
 % AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
-The density profile of the CNM also influences the emission from
-stellar tidal disruption events (TDEs), such as the high energy
-transient {\it Swift} J1644+57 (\citealt{Levan+11};
-\citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
+The gas density of the CNM also influences the emission from stellar tidal disruption events (TDEs), such as the high energy
+transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
 This event was powered by a transient relativistic jet, which produced
@@
 (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of {\it Swift} J1644+57 showed that the CNM density was
+modeling of J1644+57 showed that the CNM density was
 significantly lower than that measured surrounding Sgr A$^{\star}$
@@
 injected into a denser CNM would be decelerated more rapidly,
-producing substantially different radio emission than in {\it Swift}
-J1644+57.  Variations in the properties of the CNM could thus in
+producing substantially different radio emission than in J1644+57.  Variations in the properties of the CNM could thus in
 principle help explain why most TDEs appear to be radio quiet
@@
 
-Gas that forms the CNM of a SMBH may originate from several sources
-(\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved)
-stars; (2) star-star collisions; (3) the unbound debris from TDEs.
-Stellar wind mass loss is probably the dominant source in most cases
-insofar as collisions are relevant only in very dense stellar
-environments for young stellar populations (\citealt{Rubin&Loeb11}),
-while TDEs are estimated to provide a subdominant contribution to the
-time-averaged accretion rate of quiescent SMBHs
-(\citealt{MacLeod+13}).
-
-\citet{Ho:2009a} calculates the accretion rates onto a sample of
-early-type galaxies both by using X-ray observations to determine the
-Bondi accretion rate, and by estimating the contributions from the
-mass loss of evolved stars.  Both methods lead him to conclude that
-the available reservoir of gas is more than sufficient to power
-low-luminosity AGN, assuming the standard radiative efficiency $\eta
-\sim 0.1$ for thin disk accretion.  Indeed, there is now strong
-observational evidence that the low levels of AGN activity in
-quiescent galaxies results from accretion proceeding in a radiatively
-inefficient mode (\citealt{Yuan&Narayan14}), either due to the
-gravitationally-released energy being advected across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas
-inflowing on large scales ultimately reaching the SMBH
-(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
-The accretion rates of SMBHs can in principle be estimated directly by
-assuming Bondi accretion and using {\it Chandra} X-ray observations to
-estimate the gas temperature and density near the Bondi radius.  This
-technique has led to the intriguing result that the Bondi accretion
-power correlates with the AGN jet power (e.g.,
-\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-required to inflate the observed cavities within the X-ray emitting
-gas.  It is, however, almost never possible to resolve the Bondi
-radius, thus requiring all such studies to extrapolate the observed
-gas temperature and density profiles to much smaller radial scales.
+Gas comprising the CNM can in principle originate from a variety of sources: (1) wind mass loss from (predominantly evolved) stars; (2) star-star collisions; and (3) unbound debris from TDEs.
+Stellar wind mass loss is probably the dominant source insofar as collisions are relevant only in very dense stellar environments for young stellar populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find that TDEs contribute subdominantly to the time-averaged accretion rate of quiescent SMBHs.
+
+\citet{Ho:2009a} estimates the accretion rates onto a sample of early-type galaxies both by using X-ray observations to determine the Bondi accretion rate and using estimates for the mass loss rate of evolved stars.
+Both methods lead to the conclusion that the available gas reservoir is more than sufficient to power the observed low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative efficiency for thin disk accretion.
+Several independent strains of evidence now suggest that low-luminosity AGN result from accretion proceeding in a radiatively inefficient mode (\citealt{Yuan&Narayan14}), due either to the advection of gravitationally-released energy across the SMBH horizon (e.g.~\citealt{Narayan&Yi95}) or due to a low efficiency for the gas inflowing on large scales ultimately reaching the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+
 %In fact, the temperature profile is assumed to be flat inside of the
@@
 
-Another approach to determine the SMBH accretion rate, which we adopt
-in this paper, is to directly calculate the density, velocity and
-temperature profiles of the CNM using a physically motivated
+Another approach to determine the SMBH accretion rate, which we adopt in this paper, is to directly calculate the density, velocity and temperature profiles of the CNM using a physically motivated
 hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from a number of sources,
-such as wind shock heating and supernovae (e.g.,
-\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works, however, which focus on modeling the nuclei of
-individual galaxies, here we systematically analyze the properties of
-the CNM across a large sample of quiescent galaxies with a range of
-SMBH masses and other properties (\citealt{WangMerritt:2004a};
-hereafter WM04).  For each galaxy, stellar winds deposit mass and
-energy across a range of radii calculated directly from the observed
-{\it stellar} density profile.
+stellar winds, while energy input results from several sources including stellar winds, supernovae, and AGN feedback (e.g., \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+Unlike previous works focusing on modeling individual galaxies, here we systematically analyze the properties of the CNM across a sample of galaxies with a range of SMBH masses, stellar density profiles, and star formation histories (\citealt{WangMerritt:2004a};
+hereafter WM04).
+
+Many past studies have focused on relatively massive galaxies.
+A key result of this work is the onset of , and the need for AGN feedback.
+Here we instead neglect radiative cooling, focusing on time-dependent models.
+This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring their sensitivity on.
 
@@
 The stagnation radius, rather than the Bondi radius, is thus
-ultimately responsible for setting the SMBH accretion rate, although
+ultimately responsible for setting the SMBH accretion rate, although (when it exists)
 $\rs$ can in many cases lie within a factor of few of the
@@
 
+\subsection{TDE Jets}
+
+Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
+
+\subsection{Jet Power Correlation}
+
+Accretion rates onto SMBHs can in principle be estimated directly by assuming Bondi accretion and using high resolution X-ray observations to estimate the gas temperature and density near the Bondi radius.
+This technique has led to the intriguing conclusion that the Bondi accretion power correlates with the AGN jet power (e.g.,
+\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
+\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
+required to inflate the observed cavities within the X-ray emitting
+gas.
+In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
+
   \section{Summary}

### 2015-01-09 ms.tex
editing intro2

@@
 
-Many past studies have focused on relatively massive galaxies.
-A key result of this work is the onset of , and the need for AGN feedback.
-Here we instead neglect radiative cooling, focusing on time-dependent models.
-This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring their sensitivity on.
-
-The one-dimensional steady state flow of gas is usually characterized
-by an inflow-outflow structure, with a critical radius known as the
-``stagnation radius" $\rs$ where the radial velocity goes to zero.
-Mass loss from stars interior to the stagnation radius is accreted,
-while that outside $\rs$ is unbound in an outflow from the nucleus.
-The stagnation radius, rather than the Bondi radius, is thus
-ultimately responsible for setting the SMBH accretion rate, although (when it exists)
-$\rs$ can in many cases lie within a factor of few of the
-nominal Bondi radius.
+Past studies, including multi-dimensional hydrodynamics and a variety of (parameterized) physical effects, have focused on relatively massive elliptical galaxies (Ciotti refs).
+A key result of this work is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate before black hole feedback grows sufficiently important to halt this growth.
+Here we instead focus on time-independent models, neglecting radiative cooling.
+This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties are always manifest, or whether other forms of non-AGN feedback can result in steady accretion.
+Even if cooling instabilties develop on galactic scales, phases of stable accretion may persist on small scales.
+We are thus motivated to explore whether it steady-flow is possible under any circumstances, or whether accretion is always building towards instability.
+
+In the presence of strong heating, one-dimensional steady-state flow is characterized by an inflow-outflow structure, with a critical radius known as the``stagnation radius" $\rs$ where the radial velocity passes through zero.
+Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.
+The stagnation radius, rather than the Bondi radius, thus controls the SMBH accretion rate, although $\rs$ can in many cases lie within a factor of few of the nominal Bondi radius.
+In the case of weak heating, however, no stagnation radius may exist at all, i.e.
+the entire ISM of the galaxy is feeding the SMBH.
+Another goal of this work is to assess under what conditions a stagnation radius exists, as this question is intimately tied to the one of cooling instability.
 % Furthermore, in some cases we find that no stagnation

### 2015-01-09 ms.tex
editing intro3

@@
 \subsection{Galaxy models}
-\citet{LauerFaber+:2007a} use Hubble WFPC2 imaging to measure the
-radial surface brightness profiles for hundreds of nearby early type galaxies. The measured surface brightness profile is generally well-fit by a ``Nuker" law parameterization:
+\citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to measure the radial surface brightness profiles for hundreds of nearby early type galaxies.
+The measured brightness profile is generally well-fit by a ``Nuker" law parameterization:
 \begin{equation}
-  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
+  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b},
 \end{equation}
-The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
-Assuming spherical symmetry, this corresponds to a stellar density $\rhostar \sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r \gg \rb$, thus motivating us to adopt a broken power-law profile
+i.e., a broken power law that transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+Assuming the stellar population is spherically symmetric, this corresponds to a stellar density $\rhostar \propto r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for $r \gg \rb$.
+To good approximation
 \begin{align}
@@
 \end{align}
-where $\rho_\star(\rsoi)$ is the stellar density at the radius of the black hole sphere of influence, 
+where $\rho_\star(\rsoi)$ is the stellar density at the radius of the black hole sphere of influence (soi), 
 \be
-\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
+\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc}.
 \label{eq:rsoi}
 \ee
-and the final equality in (\ref{eq:rsoi}) employs a recent version of the $\Mbh-\sigma$ relationship (\citealt{Gultekin+09}),
+The second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$ relationship of \citet{Gultekin+09},
  \begin{align}

### 2015-01-09 ms.tex
Fleshing out heating section

--- 2015-01-09 ms.tex
@@
 \begin{abstract}
-Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.
-Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-Analytic estimates are derived, neglecting radiative cooling, for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-These results are used to assess over what range of conditions radiative instability will develop, assuming a feedback due to the average star formation history for galaxies of the given black hole mass.
-Our main conclusion is that.....
-Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
+  Steady-state hydrodynamic profiles of hot gas in  the nuclei of a sample of early-type quiescent galaxies are calculated.  We assume
+  that mass is supplied to the circumnuclear medium (CNM) entirely by
+  stellar winds according to the radial stellar profiles for each
+  galaxy, while the gas is heated by a combination of shocked stellar
+  winds and supernovae.  Our analytic and numerical results are used
+  to estimate the accretion rates onto the central supermassive black
+  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
+  heating efficiency, the latter of which is related schematically to
+  the age of the stellar population, the frequency of supernovae, and
+  the efficacy of accretion feedback processes.  For a fixed heating
+  efficiency, we find that the SMBH accretion Eddington factor
+  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
+  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
+  nuclei, respectively.
+  % However, considering the potentially lower heating efficiency of low
+  % mass SMBHs (due to a younger stellar population and the rareity of
+  % supernovae within the stagnation radius) and their resulting higher
+  % susceptibility to cooling instability, we find a flatter
+  % relationship $\alpha \approx 0$. 
+  Our results are used to check previous estimates of the SMBH
+  accretion rate assuming Bondi accretion and extrapolating the X-ray
+  measured density and temperature to the unresolved Bondi radius.  We
+  also discuss the implications of our results for the diversity of
+  CNM environments encountered by the jetted outflows from tidal
+  disruption events, and for the use of an assumed
+  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
+  fraction of SMBHs in low mass galaxies.
 \end{abstract}
@@
 
-To understand why most SMBHs appear to be inactive requires understanding their gaseous environments.  Hot gas near the
-SMBH sphere of influence (hereafter the `circumnuclear medium', or CNM) controls the central mass accretion rate $\dot{M}$.
-The latter in turn affects the luminosity of the accretion flow and the possible impact of its energy and momentum input (`feedback') on larger scales.
-The presence of dense gas in the nucleus can also lead to runaway cooling instabilities, resulting in bursty star-formation or episodic AGN activity (reference Ciotti and others).
-
-Knowledge of how $\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
-galactic nucleus informs key questions related to co-evolution of SMBHs and their host galaxies with cosmic time.
-SMBH growth in the low redshift universe appears to be dominated by lower mass black holes (e.g.~\citealt{Heckman+04}).
-This is often
-attributed to cosmological `down sizing' (e.g, \citealt{Gallo+08}), even though the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
-
-The accretion rates of low mass SMBHs, and their resulting nuclear X-ray luminosities $L_X$, also have implications for observational
+In order to understand why most SMBHs appear to be inactive, it is
+necessary to understand their gaseous environments.  Hot gas near the
+SMBH sphere of influence (the `circumnuclear medium' or CNM) controls
+the central mass accretion rate $\dot{M}$.  Better knowledge of how
+$\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
+galactic nucleus is necessary to understand the co-evolution of SMBHs
+and their host galaxies with cosmic time.  SMBH growth in the low
+redshift universe, for instance, appears to be dominated by low mass
+black holes (e.g.~\citealt{Heckman+04}).  Although this is often
+attributed to cosmological ``down sizing" (e.g, \citealt{Gallo+08}),
+the physical processes involved may be distinct from those operating
+at higher SMBH masses and accretion rates in quasars.
+
+The accretion rates of low mass SMBHs and their resulting nuclear
+X-ray luminosities $L_X$ also have implications for observational
 constraints on their occupation fraction in low mass galaxies and the
-possible existence of intermediate mass black holes.  By combining the average relationship between $\Mbh$ and
-$L_X$ measured from a sample of high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in lower mass
-galaxies, \citet{MillerGallo+:2014a}  infer tentative evidence for an occupation fraction less than unity in the latter.
-This method, however, relies on extrapolating a power-law fit to the $L_X-\Mbh$ distribution to low $\Mbh$ below the detection threshold.
-
-%The conclusions of
-%\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
-%the $L_X$-$\Mbh$ relationship at small $\Mbh$.
+possible existence of intermediate mass black holes.
+\citet{MillerGallo+:2014a} combine the relationship between $\Mbh$ and
+$L_X$ from a sample of relatively high mass galaxies
+(\citealt{Gallo+08}) with upper limits on $L_X$ in several lower mass
+galaxies, to infer tentative evidence for an occupation fraction less
+than unity.  However, this method relies on extrapolating a power-law
+fit to the $L_X-\Mbh$ distribution to low $\Mbh$, below the
+instrumental detection threshold.  The conclusions of
+\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
+the $L_X$-$\Mbh$ relationship at small $\Mbh$.
 % AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
-The gas density of the CNM also influences the emission from stellar tidal disruption events (TDEs), such as the high energy
-transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
+The density profile of the CNM also influences the emission from
+stellar tidal disruption events (TDEs), such as the high energy
+transient {\it Swift} J1644+57 (\citealt{Levan+11};
+\citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
 This event was powered by a transient relativistic jet, which produced
@@
 (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of J1644+57 showed that the CNM density was
+modeling of {\it Swift} J1644+57 showed that the CNM density was
 significantly lower than that measured surrounding Sgr A$^{\star}$
@@
 injected into a denser CNM would be decelerated more rapidly,
-producing substantially different radio emission than in J1644+57.  Variations in the properties of the CNM could thus in
+producing substantially different radio emission than in {\it Swift}
+J1644+57.  Variations in the properties of the CNM could thus in
 principle help explain why most TDEs appear to be radio quiet
@@
 
-Gas comprising the CNM can in principle originate from a variety of sources: (1) wind mass loss from (predominantly evolved) stars; (2) star-star collisions; and (3) unbound debris from TDEs.
-Stellar wind mass loss is probably the dominant source insofar as collisions are relevant only in very dense stellar environments for young stellar populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find that TDEs contribute subdominantly to the time-averaged accretion rate of quiescent SMBHs.
-
-\citet{Ho:2009a} estimates the accretion rates onto a sample of early-type galaxies both by using X-ray observations to determine the Bondi accretion rate and using estimates for the mass loss rate of evolved stars.
-Both methods lead to the conclusion that the available gas reservoir is more than sufficient to power the observed low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative efficiency for thin disk accretion.
-Several independent strains of evidence now suggest that low-luminosity AGN result from accretion proceeding in a radiatively inefficient mode (\citealt{Yuan&Narayan14}), due either to the advection of gravitationally-released energy across the SMBH horizon (e.g.~\citealt{Narayan&Yi95}) or due to a low efficiency for the gas inflowing on large scales ultimately reaching the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
+Gas that forms the CNM of a SMBH may originate from several sources
+(\citealt{Ho:2009a}): (1) wind mass loss from (predominantly evolved)
+stars; (2) star-star collisions; (3) the unbound debris from TDEs.
+Stellar wind mass loss is probably the dominant source in most cases
+insofar as collisions are relevant only in very dense stellar
+environments for young stellar populations (\citealt{Rubin&Loeb11}),
+while TDEs are estimated to provide a subdominant contribution to the
+time-averaged accretion rate of quiescent SMBHs
+(\citealt{MacLeod+13}).
+
+\citet{Ho:2009a} calculates the accretion rates onto a sample of
+early-type galaxies both by using X-ray observations to determine the
+Bondi accretion rate, and by estimating the contributions from the
+mass loss of evolved stars.  Both methods lead him to conclude that
+the available reservoir of gas is more than sufficient to power
+low-luminosity AGN, assuming the standard radiative efficiency $\eta
+\sim 0.1$ for thin disk accretion.  Indeed, there is now strong
+observational evidence that the low levels of AGN activity in
+quiescent galaxies results from accretion proceeding in a radiatively
+inefficient mode (\citealt{Yuan&Narayan14}), either due to the
+gravitationally-released energy being advected across the SMBH horizon
+(e.g.~\citealt{Narayan&Yi95}) or due to only a fraction of the gas
+inflowing on large scales ultimately reaching the SMBH
+(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+
+The accretion rates of SMBHs can in principle be estimated directly by
+assuming Bondi accretion and using {\it Chandra} X-ray observations to
+estimate the gas temperature and density near the Bondi radius.  This
+technique has led to the intriguing result that the Bondi accretion
+power correlates with the AGN jet power (e.g.,
+\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
+\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
+required to inflate the observed cavities within the X-ray emitting
+gas.  It is, however, almost never possible to resolve the Bondi
+radius, thus requiring all such studies to extrapolate the observed
+gas temperature and density profiles to much smaller radial scales.
 %In fact, the temperature profile is assumed to be flat inside of the
@@
 
-Another approach to determine the SMBH accretion rate, which we adopt in this paper, is to directly calculate the density, velocity and temperature profiles of the CNM using a physically motivated
+Another approach to determine the SMBH accretion rate, which we adopt
+in this paper, is to directly calculate the density, velocity and
+temperature profiles of the CNM using a physically motivated
 hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from several sources including stellar winds, supernovae, and AGN feedback (e.g., \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works focusing on modeling individual galaxies, here we systematically analyze the properties of the CNM across a sample of galaxies with a range of SMBH masses, stellar density profiles, and star formation histories (\citealt{WangMerritt:2004a};
-hereafter WM04).
-
-Many past studies have focused on relatively massive galaxies.
-A key result of this work is the onset of , and the need for AGN feedback.
-Here we instead neglect radiative cooling, focusing on time-dependent models.
-This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring their sensitivity on.
+stellar winds, while energy input results from a number of sources,
+such as wind shock heating and supernovae (e.g.,
+\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+Unlike previous works, however, which focus on modeling the nuclei of
+individual galaxies, here we systematically analyze the properties of
+the CNM across a large sample of quiescent galaxies with a range of
+SMBH masses and other properties (\citealt{WangMerritt:2004a};
+hereafter WM04).  For each galaxy, stellar winds deposit mass and
+energy across a range of radii calculated directly from the observed
+{\it stellar} density profile.
 
@@
 The stagnation radius, rather than the Bondi radius, is thus
-ultimately responsible for setting the SMBH accretion rate, although (when it exists)
+ultimately responsible for setting the SMBH accretion rate, although
 $\rs$ can in many cases lie within a factor of few of the
@@
 enclosed mass.  We assume an ideal gas equation of state with $p =
-\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$. {\bf BDM: take $\mu = 0.62$ here for fully ionized gas - what did you do?}
+\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
 
@@
 
-Source terms $\propto q$ also appear in the momentum and entropy equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because isotropic mass injection in the SMBH rest frame represents a source of momentum and energy relative to the mean flow.
-Physically, these result from the mismatch between the properties of virialized gas injected locally by stellar winds and the mean properties of the background flow.
-The term $\propto -q c_{s}^{2}$ turns out to be an important in stabilizing the flow to runaway cooling ($\S$).
-
-The last term in equation (\ref{eq:dsdt}) accounts for heat transportation by electron conductivity, where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units).
-The flux limitor $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free path for electron coulomb scattering becomes comparable to the temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the isothermal sound speed and $\phi \lesssim 1$ is an uncertain dimensionless constant (we adopt $\phi = 0.1$).
-Even a weak magnetic field perpendicular to the flow could in principle suppress the conductivity.
-However, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).
-
-The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy equation accounts for external heating sources (e.g., \citealt{ShcherbakovWong+:2014a}).
-The first term accounts for the minimum shock heating of the stellar winds due to the random movement of stars with respect to each other at the characteristic velocity $\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low wind velocities $\ll \sigma$ that characterize AGB mass loss in old stellar populations.
-The second term, $v_{w,0}^{2}$, parameterizes the contribution of additional sources of heating, such as faster main sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN feedback, etc.
-As discussed in $\S\ref{sec:heating}$, the value of $v_{w,0}$ is uncertain and will in general depend on the SMBH mass and the age of the stellar population.
+Source terms $\propto q$ also appear in the momentum and entropy
+equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because isotropic
+mass injection in the SMBH rest frame represents a source of momentum
+and energy relative to the mean flow.  Physically, these result from
+the mismatch between the properties of virialized gas injected locally
+by stellar winds and the mean properties of the background flow.  The
+term $\propto -q c_{s}^{2}$ turns out to be an important in
+stabilizing the flow to runaway cooling ($\S$).
+
+The last term in equation (\ref{eq:dsdt}) accounts for heat
+transportation by electron conductivity, where $\kappa_{\rm
+  eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
+the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
+classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
+cgs units).  The flux limitor $\psi = \kappa_{\rm spitz} \nabla
+T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free
+path for electron coulomb scattering becomes comparable to the
+temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the
+isothermal sound speed and $\phi \lesssim 1$ is an uncertain
+dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
+field perpendicular to the flow could in principle suppress the
+conductivity.  However, the radially-decreasing temperature profiles
+of interest are susceptible to the magneto-thermal instability
+(\citealt{Balbus01}), the non-linear evolution of which is believed to
+result in a radially-directed field structure
+(\citealt{Parrish&Stone07}).
+
+The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy
+equation accounts for external heating sources (e.g.,
+\citealt{ShcherbakovWong+:2014a}).  The first term accounts for the
+minimum shock heating of the stellar winds due to the random movement
+of stars with respect to each other at the characteristic velocity
+$\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low
+wind velocities $\ll \sigma$ that characterize AGB mass loss in old
+stellar populations.  The second term, $v_{w,0}^{2}$, parameterizes
+the contribution of additional sources of heating, such as faster main
+sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN
+feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
+$v_{w,0}$ is uncertain and will in general depend on the SMBH mass and
+the age of the stellar population.
 
@@
 for time integration and artificial viscosity terms in the velocity
-and entropy equations for numerical stability (\citealt{Brandenburg:2003a}).  We solve the equations for different choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning a physically plausible
-range.
-Although we are interested in the steady-state intflow/outflow structure, the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic inflow on small radial scales and a possible supersonic outflow on large scales.
-
-Radiative cooling is not included in our calculation.
-Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling.
-Radiative cooling cannot be neglected when $\vwO$ is low (and/or $\eta$ is high), but once important it leads to thermal instabilities (e.g.~\citealt{McCourt+12}) which our 1D time-independent model cannot account for self-consistently anyways.
-Indeed, one of the main goals of this work is to use our analytic and numerical solutions neglecting radiation to ascertain over what physical conditions cooling instabilities are likely to develop ($\S\ref{sec:cooling}$).
-
-The accuracy of our numerical solutions is assessed by checking the level of conservation of mass across the grid, as well as the integral constraint on the energy.
-Mass and energy are conserved to $\lesssim
-40$ per cent for all solutions presented in this paper. 
-{\bf BDM: more details...}
+and entropy equations for numerical stability
+(\citealt{Brandenburg:2003a}).  We solve the equations for different
+choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning a
+physically plausible range.  Although we are interested in the
+steady-state intflow/outflow structure, the time-dependent equations
+are solved to avoid numerical issues that arise near the critical
+sonic points, of which there are up to two because of the supersonic
+inflow on small radial scales and a possible supersonic outflow on
+large scales.
+
+Radiative cooling is not included in our calculation.  Across much of
+the parameter space radiative cooling is subdominant compared to other
+sources of cooling.  Radiative cooling cannot be neglected when $\vwO$
+is low (and/or $\eta$ is high), but once important it leads to thermal
+instabilities (e.g.~\citealt{McCourt+12}) which our 1D
+time-independent model cannot account for self-consistently anyways.
+Indeed, one of the main goals of this work is to use our analytic and
+numerical solutions neglecting radiation to ascertain over what
+physical conditions cooling instabilities are likely to develop
+($\S\ref{sec:cooling}$).
+
+The accuracy of our numerical solutions is assessed by checking the
+level of conservation of mass across the grid, as well as the integral
+constraint on the energy.  Mass and energy are conserved to $\lesssim
+40$ per cent for all solutions presented in this paper.  {\bf BDM:
+  more details...}
 
@@
 
-Here we summarize analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
-Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter (eq.~[\ref{eq:dsdt}])
+Here we summarize analytic estimates of physical quantities, such as
+the stagnation radius $\rs$ and the mass accretion rate, the detailed
+derivation of which are given in Appendix \ref{app:rs}.  Our results
+are expressed in terms of the SMBH mass $M_{\bullet} =
+10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter
+(eq.~[\ref{eq:dsdt}])
 \begin{eqnarray}
@@
     ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
-    and interior X-ray luminosity ({\it bottom}) calculated for the
-    cusp galaxies ($\Gamma=0.8$) within our grid.  Different colors
+    and interior X-ray luminosity ({\it bottom}) calculated for a
+    sample of galaxies within our grid.  Different colors
     denote different values of the effective wind heating rate,
@@
     $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
-    galaxies ($\gamma$=0.8) and thick lines correspond to core
-    galaxies ($gamma$=0.1). Squares mark out the location of
+    galaxies ($\Gamma$=0.8) and thick lines correspond to core
+    galaxies ($Gamma$=0.1). Squares mark out the location of
     the stagnation radius for each solution.
@@
 
-Fig.~\ref{fig:cooling} shows $H/C=(q \vw^2+q v^2)/2$ and $\tcool/\tff$
+Fig.~\ref{fig:cooling} shows $H/C=\frac{1}{2} (q \vw^2+q
+v^2)/\left|\Lambda(T) n^2\right|$ and $\tcool/\tff$
 as a function of radius for all of our solutions. {\bf BDM: change
@@
 heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
-s$^{-1}$.  In what follows below, we take an effective stellar wind
-heating rate \be v_{\rm w,0}^{\star} = 150\,{\rm km\,s^{-1}} \ee In
-Appendix \ref{app:windheat} we present a toy model for how $v_{\rm
-  w,0}$ varies as a function of stellar age ({\bf BDM: Nick can
-  create}).
-
-\subsection{Millisecond Pulsars} Energy injection from millisecond pulsars (MSPs) is a potentially important heating source.
-If the number of MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes on average a spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit volume $e \approx \bar{L}_{\rm sd}n_{\rm
-  msp}\epsilon$ results in an effective heating rate (eq.~ [\ref{eq:vw_eff}])
-\begin{eqnarray}
-  v_{\rm w,0}^{\rm MSP} \approx 30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
-        sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2}
-  \eta_{0.02}^{-1/2}\,{\rm km\,s^{-1}},
+s$^{-1}$.  In Appendix \ref{app:windheat} we present a model for
+how $v_{\rm w,0}$ varies as a function of stellar age.
+
+\subsection{Millisecond Pulsars}
+ Energy injection from millisecond pulsars (MSPs) is a potentially
+important heating source.  If the number of MSPs per unit stellar mass
+is $n_{\rm msp}$ and each contributes on average a spin-down
+luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
+volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon$ results in an
+effective heating rate (eq.~ [\ref{eq:vw_eff}])
+
+\begin{eqnarray} v_{\rm w,0}^{\rm MSP} \approx
+30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
+sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \eta_{0.02}^{-1/2}\,{\rm
+km\,s^{-1}},
+ \label{eq:vmsp}
   \end{eqnarray}
-where $\epsilon$ is the thermalization efficiency of the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based on modeling the insterstellar mediums of globular clusters \citep{NaimanSoares-Furtado+:2013a}.
-The above estimate adopts a pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$ motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
-
-The average spin-down luminosity of millisecond pulsars in the field is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.
-For higher spin-down luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0} \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important under the optimistc assumption $\epsilon = 1$.
-On the other hand, the binaries giving rise to MSPs may be disocciated by stellar interactions in the dense nuclear cluster, reducing their numbers as compared to the field population estimate above.
-We conclude that MSPs are unlikely to be an important source of heating, probably insufficient to stabilize the steady flow against cooling instability (e.g.
-$v_{\rm w,0}^{\rm MSP} < v_{\rm critt}$; eq.~[\ref{eq:cooling2}])
+
+where $\epsilon$ is the thermalization efficiency of
+the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based
+on modeling the insterstellar mediums of globular clusters
+\citep{NaimanSoares-Furtado+:2013a}.  The above estimate adopts a
+pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$
+motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of
+stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
+
+The average spin-down luminosity of millisecond pulsars in the field
+is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based
+on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
+case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.  For higher spin-down
+luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
+of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0}
+\lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
+under the optimistc assumption $\epsilon = 1$.  On the other hand, the
+binaries giving rise to MSPs may be disocciated by stellar
+interactions in the dense nuclear cluster, reducing their numbers as
+compared to the field population estimate above.  We conclude that
+MSPs are unlikely to be an important source of heating, probably
+insufficient to stabilize the steady flow against cooling instability
+(e.g. $v_{\rm w,0}^{\rm MSP} < v_{\rm critt}$;
+eq.~[\ref{eq:cooling2}])
 
@@
 
-The total heating rate $\vwO = \sqrt{v_{\rm w,0}^{\star} + v_{\rm w,0}^{\rm Ia} + v_{\rm w,0}^{\rm p} + v_{\rm w,0}^{\bullet}}$ has contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
-Since pulsar heating appears unlikely to contribute appreciably, and since SMBH heating is uncertain, we first focus on heating from stellar winds and supernovae.
-
-Figure~\ref{fig:vweff} shows an estimate of how the combined heating
-depends on the age of the stellar population $\tage$ and the SMB mass
-$\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
-  h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
-stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
-to contribute their full heating rate.  $v_{\rm w,0}^{\rm Ia} \sim
-250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
-infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star}
-\simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
-interest.\footnote{Although SN Ia will still occur surrounding low
-  mass SMBHs, if they are infrequent interior to the radius where the
-  accretion rate is being set, then they will not affect the flow near
-  the SMBH at most epochs.}  For very young stellar populations
-($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
-contributions from line driven winds from high mass main sequence
-stars.
+The total heating rate $\vwO = \sqrt{v_{\rm w,0}^{\star \, 2} + v_{\rm
+    w,0}^{\rm Ia \, 2} + v_{\rm w,0}^{\rm p \, 2} + v_{\rm
+    w,0}^{\bullet \, 2}}$ has
+contributions from stellar winds, supernovae, pulsars, and SMBH
+feedback. %  Since pulsar heating appears unlikely to contribute
+% appreciably, and since SMBH heating is uncertain, we first focus on
+% heating from stellar winds and supernovae.
+
+Each of these heating sources will depend on the integrated star
+formation history. This in term will will vary systematically with
+galaxy mass and thus with $\Mbh$.  
+%Qualitatively smaller galaxies willhave recent star formation and
+% energetic winds from Wolf-Rayet stars will dominate the mass
+% budget--$\vwO\gsim 1000 $ km/s.  On the other hand for larger galaxies
+% will have older populations, and heating will be dominated by Ia
+% supernovae on large scales and SMBH feedback on small scales.
+We calculate the star formation history as a function of $\Mbh$ and
+the $\vwO$ for each heating source using the cosmic star formation
+histories in \citet{MosterNaab+:2013a}.  For $v_{\rm w,0}^{\rm p}$ we
+use equation~\eqref{eq:vmsp}. The star formation history simply enters
+in through $\eta$. The effective $\eta$ for a given star formation
+history will be the convolution of the star formation history with
+$\eta_{\rm imp}\simeq $ {\bf AG: should have expression for $\eta_{\rm
+    Imp}$ in appendix. Have to be careful as we also have the
+  simplified expression for $\eta_{\rm Imp}$} ($\eta$ in the impulsive
+limit). For $v_{\rm w,0}^{\rm Ia}$ we use
+equation~\eqref{eq:vIa}. Besides $\eta$ there is additional dependence
+on the star formation history from the Ia rate--which is a convolution
+of the star formation history with the delay-time distribution from
+\citet{MaozMannucci+:2012a}. The calculation of $v_{\rm w,0}^{\star}$
+is somewhat involved: we leave the detailed description for
+Appendix~\ref{app:windheat}. {\bf AG: still need a description of the
+  Compton heating. In general, I struggled with the level of detail
+  here. I couldn't think of a natural place to put the details for the
+  other heating sources}
+
+$\vwO$ from each heating source (stars, MSPs, SNe Ia, and black hole
+feedback) is plotted in as a function of $\Mbh$ in
+Figure~\ref{fig:vwSources}. $v_{\rm w,0}^{\rm p}$ is negligible across
+all $\Mbh$. For $\Mbh\lsim 10^{7.5} \Msun$, have substantial recent
+star formation and $v_{\rm w,0}^{\star}$ is dominant. For $\Mbh\gsim
+10^{7.5} \Msun$ , the younger stellar population with their energetic
+stellar winds is dead, and Compton heating plays an important role.
+
+For reference we also plot the inferred $\eta$ for each $\Mbh$ in
+Figure~\ref{fig:eta}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{vwSources.pdf}
+\caption{\label{fig:vwSources} $\vwO$ for stellar winds ({\it solid
+    blue}), SNe Ia ({\it dashed red}), MSPs ({\it solid orange}), as a
+  function of $\Mbh$. Each heating source varies with the star
+  formation history, which is a function of $\Mbh$--see
+  appendix~\ref{app:windheat} for the detailed description of how we
+  calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
+  resulting from stellar winds and MSPs ({\it dashed black}) and stellar
+  winds, MSPs, and black hole feedback ({\it solid black}). The heating
+  will have a weak dependence on the stellar density power law slope,
+  $\Gamma$, since $v_{\rm w,0}^{\bullet \, 2}$ depends on
+  $\Gamma$. The solid black curve corresponds to $\Gamma=0.8$
+  and the dash-dotted black curve corresponds to $\Gamma=0.1$.}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{eta.pdf}
+\caption{\label{fig:eta} $\eta$ vs. $\Mbh$.}
+\end{figure}
+
+For each $\Mbh$ we may check whether the solution for corresponding
+$\vwO$ and $\eta$ would be thermally stable, using
+equation~\eqref{eq:cooling2} {\bf: AG--double check that this is
+  equivalent to what I did.}
+
+The combined heating rate from stellar winds and Compton heating is
+insufficient to prevent thermal instability for the high $\Mbh$.  This
+is shown in Figure~\ref{fig:cooling2}, which shows the heating over
+cooling rate at $\rs$ as a function of $\Mbh$. For $\Mbh\gsim 10^8
+\Msun$, the cooling rate will exceed the cooling rate at $\rs$ and
+and the gas would be thermally unstable.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{cooling2.pdf}
+\caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
+  $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
+  and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
+  using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
+  $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
+\end{figure}
+
+Although, in principle the Ia contribution to the heating is
+substantial, in practice Ia's occur too infrequently to be a steady
+contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
+r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
+by itself would not be able to prevent cooling instability.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{rs_rIa.pdf}
+\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
+  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
+    referring to the first part of the equation here--I use the
+    appropriate convolution the Ia rate here}. $\rs$ is calculated
+  using the equation~\eqref{eq:stag_simple} and the $\vwO$
+  corresponding to each $\Mbh$--see Figure~\ref{fig:vwSources}. For
+  the blue curve we use the total $\vwO$ from stars, MSP, and
+  black hole feedback (e.g. the solid black curve in
+  Figure~\ref{fig:vwSources}). For the purple curve we also include
+  the $\vwO$ from Ia's (the dashed red curve
+  Figure~\ref{fig:vwSources}).}
+\end{figure}
+
+% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
+% depends on the age of the stellar population $\tage$ and the SMB mass
+% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
+%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
+% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
+% to contribute their full heating rate.  $v_{\rm w,0}^{\rm Ia} \sim
+% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
+% infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star}
+% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
+% interest.\footnote{Although SN Ia will still occur surrounding low
+%   mass SMBHs, if they are infrequent interior to the radius where the
+%   accretion rate is being set, then they will not affect the flow near
+%   the SMBH at most epochs.}  For very young stellar populations
+% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
+% contributions from line driven winds from high mass main sequence
+% stars.
 {\bf AG: We should mention that regime with stellar wind heating only
@@
 
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{vw-contour.eps}
-    \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM
-      in the parameter space of SMBH mass $\Mbh$ and age of the
-      stellar population $t_{\star}$.  We assume that stellar winds
-      contribute a constant heating rate $100$ km/s. The contribution
-      from SNe Ia is calculated using equation (\ref{eq:vw_sne}), with
-      thermalization efficiency $\epsilon_{\rm Ia}=0.4$. The
-      contribution from SNe Ia is only added if the $r_s$
-      corresponding to the resulting $\vwO$ is outside
-      $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on time!
-      among  other things}}%describe other cases here.
-  \end{figure}
-
-  % AG-I am not comfortable saying type Ia SNe's don't contribute to
-  % heating for smaller mass BHs. If the cooling time for the SNe is
-  % long then it would be wrong to ignore the SNe contribution. The
-  % difference would be that the SNe heating would just be less steady.
-  % AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
+ %  \begin{figure}
+%     \includegraphics[width=\columnwidth]{vw-contour.eps}
+%     \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM
+% in the parameter space of SMBH mass $\Mbh$ and age of the stellar
+% population $t_{\star}$.  We assume that stellar winds contribute a
+% constant heating rate $100$ km/s. The contribution from SNe Ia is
+% calculated using equation (\ref{eq:vw_sne}), with thermalization
+% efficiency $\epsilon_{\rm Ia}=0.4$. The contribution from SNe Ia is
+% only added if the $r_s$ corresponding to the resulting $\vwO$ is
+% outside $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on
+% time!  among other things}}%describe other cases here.
+%   \end{figure}
 
@@
 
-For each solution we calculate the accretion rate $\dot{M}$ onto the SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd} \equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times 10^{46}M_{\bullet,8}$ erg s$^{-1}$.
-Figure~\ref{fig:mdot_mass} shows $\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for
-both core ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
-
-For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH mass  $\propto  M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively.
-This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local
-universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the fact that for quiescent galaxies the nuclear X-ray luminosity obeys $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.
-Our model instead predicts that $\Mdot
+For each solution we calculate the accretion rate $\dot{M}$ onto the
+SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
+\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
+10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
+$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
+values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core
+($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
+
+For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ tends to increase
+with SMBH mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp)
+galaxies, respectively.  This appears to be in contradiction with the
+general down sizing trend observed for SMBH accretion in the local
+universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
+fact that for quiescent galaxies the nuclear X-ray luminosity obeys
+$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
+\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
 \sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
@@
 prefactor may be slightly different.
-
-\subsection{TDE Jets}
-
-Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
-
-\subsection{Jet Power Correlation}
-
-Accretion rates onto SMBHs can in principle be estimated directly by assuming Bondi accretion and using high resolution X-ray observations to estimate the gas temperature and density near the Bondi radius.
-This technique has led to the intriguing conclusion that the Bondi accretion power correlates with the AGN jet power (e.g.,
-\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-required to inflate the observed cavities within the X-ray emitting
-gas.
-In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
 

### 2015-01-12 ms.tex
editing

@@
 \begin{abstract}
-Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.
+We calculate steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.
 Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-Analytic estimates are derived, neglecting radiative cooling, for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-These results are used to assess over what range of conditions radiative instability will develop, assuming a feedback due to the average star formation history for galaxies of the given black hole mass.
+We derive analytic estimates for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+These results (neglecting radiative cooling) are used to assess over what range of conditions radiative instability will develop, assuming an average star formation history for galaxies of the given black hole mass.
 Our main conclusion is that.....
-Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
+We briefly discuss implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies.
 \end{abstract}
@@
 
-To understand why most SMBHs appear to be inactive requires understanding their gaseous environments.  Hot gas near the
-SMBH sphere of influence (hereafter the `circumnuclear medium', or CNM) controls the central mass accretion rate $\dot{M}$.
-The latter in turn affects the luminosity of the accretion flow and the possible impact of its energy and momentum input (`feedback') on larger scales.
-The presence of dense gas in the nucleus can also lead to runaway cooling instabilities, resulting in bursty star-formation or episodic AGN activity (reference Ciotti and others).
-
-Knowledge of how $\dot{M}$ varies with the SMBH mass $\Mbh$ and other properties of the
-galactic nucleus informs key questions related to co-evolution of SMBHs and their host galaxies with cosmic time.
+To determine why most SMBHs appear to be inactive requires an understanding of their gaseous environments.
+Hot gas near the sphere of influence of the SMBH (hereafter the `circumnuclear medium', or CNM) controls the mass accretion rate, $\dot{M}$.
+The latter in turn sets the luminosity of the accretion flow and the impact of its energy and momentum input (`feedback') on larger physical scales.
+The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty star-formation and AGN activity (reference Ciotti and others).
+
+Knowledge of how $\dot{M}$ varies with the SMBH mass, $\Mbh$, and other properties of the
+galactic nucleus informs key questions, such as the co-evolution of SMBHs and their host galaxies with cosmic time.
 SMBH growth in the low redshift universe appears to be dominated by lower mass black holes (e.g.~\citealt{Heckman+04}).
@@
 
-The accretion rates of low mass SMBHs, and their resulting nuclear X-ray luminosities $L_X$, also have implications for observational
-constraints on their occupation fraction in low mass galaxies and the
-possible existence of intermediate mass black holes.  By combining the average relationship between $\Mbh$ and
+The accretion rates of low mass SMBHs, and their resulting X-ray luminosities $L_X$, also have implications for what observational constraints can be placed on their occupation fraction in low mass galaxies and the possible existence of intermediate mass black holes.
+By combining the average relationship between $\Mbh$ and
 $L_X$ measured from a sample of high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in lower mass
@@
 
-Past studies, including multi-dimensional hydrodynamics and a variety of (parameterized) physical effects, have focused on relatively massive elliptical galaxies (Ciotti refs).
-A key result of this work is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate before black hole feedback grows sufficiently important to halt this growth.
+Past studies, employing multi-dimensional numerical hydrodynamics and including variety of (parameterized) physical effects, have focused on massive elliptical galaxies (Ciotti refs).
+A key finding of these works is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate until black hole feedback becomes sufficiently important to shut off the flow and halt SMBH growth.
 Here we instead focus on time-independent models, neglecting radiative cooling.
-This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties are always manifest, or whether other forms of non-AGN feedback can result in steady accretion.
-Even if cooling instabilties develop on galactic scales, phases of stable accretion may persist on small scales.
-We are thus motivated to explore whether it steady-flow is possible under any circumstances, or whether accretion is always building towards instability.
+This approach allows us to systematically explore the relevant parameter space and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties manifest across the expected range of galaxy properties, or whether other (non-AGN) forms of feedback can result in steady accretion.
+Even if cooling instabilties develop on galactic scales over long timescales, quasi-steady accretion may persist for briefer periods on small scales.
+We are thus motivated to explore whether steady flow is achieved under any circumstances, or whether accretion is always building towards instability.
+%A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
 
@@
 Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.
-The stagnation radius, rather than the Bondi radius, thus controls the SMBH accretion rate, although $\rs$ can in many cases lie within a factor of few of the nominal Bondi radius.
-In the case of weak heating, however, no stagnation radius may exist at all, i.e.
+The stagnation radius, rather than the Bondi radius, thus controls the SMBH accretion rate (although we will show that $\rs$ can in many cases lie within a factor of few of the nominal Bondi radius).
+In the case of sufficiently weak heating, however, no stagnation radius may exist at all, i.e.
 the entire ISM of the galaxy is feeding the SMBH.
-Another goal of this work is to assess under what conditions a stagnation radius exists, as this question is intimately tied to the one of cooling instability.
+Another goal of this work is to assess under what conditions a stagnation radius exists, as this question is intimately tied to that of cooling instability.
 % Furthermore, in some cases we find that no stagnation
@@
 % accretion rate than would be predicted by simple Bondi accretion.
-The main goal of our analysis is to provide a framework for
-interpreting the properties of quiescent galactic nuclei given the
-comparatively well understood physics of stellar winds and supernova
-heating.
 
@@
 \be
-\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc}.
+\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
 \label{eq:rsoi}
 \ee
-The second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$ relationship of \citet{Gultekin+09},
+where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$ relationship of \citet{Gultekin+09},
  \begin{align}
@@
 \end{align}
-Although the use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), our results are not overly sensitive to this assumption.
+The use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), but our results are not sensitive to this assumption.
 
@@
 We bracket these possibilities by considering models with $\Gamma=0.8$ and $\Gamma=0.1$.
-Since we are generally interested in properties of the gas flow on radial scales $\ll r_b$, we fix $\beta = 2$ (a typical value), an assumption to which most of our results is not sensitive.
+Since our results are most sensitive to the properties of the gas flow on radial scales $\ll r_b$, we fix $\beta = 2$ (a typical value).
 However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.
@@
 
-Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the gas density profile $\rho$ of the CNM for each galaxy model by solving the equations of one-dimensional (spherically symmetric) time-dependent hydrodynamics,
+Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the density $\rho$, temperature $T$, and radial velocity $v$ of the CNM for each galaxy model by solving the equations of one-dimensional, time-dependent hydrodynamics,
 \begin{align}
@@
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
-      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] +\nabla\cdot(\kappa \nabla T)
+      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
 , 
@@
 \end{align}
-where $v$, $T$, $p$ and $s$ are the radial velocity, temperature,
-pressure and specific entropy of the gas, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
-enclosed mass.  We assume an ideal gas equation of state with $p =
-\rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
+where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
+enclosed mass.  We assume an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
 
@@
 years.
-To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a burst of star formation (e.g., \citealt{Ciotti+91}),\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
-Although we give the mass return rate per unit volume, our expressions are equivalent.} although $\eta$ is higher in cases of ongoing star formation.
+To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a star burst (e.g., \citealt{Ciotti+91}),\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
+Although we give the mass return rate per unit volume, our expressions are equivalent.} although $\eta$ can be higher if star formation is ongoing (Fig X).
 
@@
 by stellar winds and the mean properties of the background flow.  The
-term $\propto -q c_{s}^{2}$ turns out to be an important in
-stabilizing the flow to runaway cooling ($\S$).
-
-The last term in equation (\ref{eq:dsdt}) accounts for heat
-transportation by electron conductivity, where $\kappa_{\rm
+term $\propto -q c_{s}^{2}$ acts as an important agent in stabilizing the flow to runaway cooling ($\S\ref{sec:instability}$).
+
+The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy
+equation accounts for external heating sources (e.g.,
+\citealt{ShcherbakovWong+:2014a}).  The first term accounts for the
+minimum shock heating of the stellar winds due to the random movement
+of stars with respect to each other at the characteristic velocity
+$\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low
+wind velocities $\ll \sigma$ that characterize AGB mass loss in old
+stellar populations.  The second term, $v_{w,0}^{2}$, parameterizes
+the contribution of additional sources of heating, such as faster main
+sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN
+feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
+$v_{w,0}$ is uncertain and will in general depend on the SMBH mass and
+the age of the stellar population.
+
+To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.
+Heat transport by electron conductivity is included with an additional term to the right hand side of the entropy equation of the form
+\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
+where $\kappa_{\rm
   eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
@@
 
-The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy
-equation accounts for external heating sources (e.g.,
-\citealt{ShcherbakovWong+:2014a}).  The first term accounts for the
-minimum shock heating of the stellar winds due to the random movement
-of stars with respect to each other at the characteristic velocity
-$\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low
-wind velocities $\ll \sigma$ that characterize AGB mass loss in old
-stellar populations.  The second term, $v_{w,0}^{2}$, parameterizes
-the contribution of additional sources of heating, such as faster main
-sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN
-feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
-$v_{w,0}$ is uncertain and will in general depend on the SMBH mass and
-the age of the stellar population.
+Radiative cooling is also not included in our baseline calculations.  Across much of
+the parameter space radiative cooling is subdominant compared to other
+sources of cooling.  Radiative cooling cannot be neglected when $\vwO$
+is low (and/or $\eta$ is high), but once important it leads to thermal
+instabilities (e.g.~\citealt{McCourt+12}) which our 1D
+time-independent model cannot account for self-consistently anyways.
+Indeed, one of the main goals of this work is to use our analytic and
+numerical solutions neglecting radiation to ascertain over what
+physical conditions cooling instabilities are likely to develop
+($\S\ref{sec:cooling}$).
 
@@
 
-Radiative cooling is not included in our calculation.  Across much of
-the parameter space radiative cooling is subdominant compared to other
-sources of cooling.  Radiative cooling cannot be neglected when $\vwO$
-is low (and/or $\eta$ is high), but once important it leads to thermal
-instabilities (e.g.~\citealt{McCourt+12}) which our 1D
-time-independent model cannot account for self-consistently anyways.
-Indeed, one of the main goals of this work is to use our analytic and
-numerical solutions neglecting radiation to ascertain over what
-physical conditions cooling instabilities are likely to develop
-($\S\ref{sec:cooling}$).
-
 The accuracy of our numerical solutions is assessed by checking the
@@
 
-\section{Results}
-
-We begin by describing useful analytic results before presenting our numerical solutions.
-
+\section{Analytic Results}
 \label{sec:results}
-\subsection{Analytic Results}
-
-Here we summarize analytic estimates of physical quantities, such as
-the stagnation radius $\rs$ and the mass accretion rate, the detailed
-derivation of which are given in Appendix \ref{app:rs}.  Our results
-are expressed in terms of the SMBH mass $M_{\bullet} =
-10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter
+
+We begin by describing analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the derivation of which are given in Appendix \ref{app:rs}.
+Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter
 (eq.~[\ref{eq:dsdt}])
@@
 \end{eqnarray}
-where we remind that the parameter $\vwO$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
-
-\subsubsection{Flow Properties Near the Stagnation Radius}
-
-Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs}, eq.~[\ref{eq:first_law}])
+where the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+
+\subsection{Flow Properties Near the Stagnation Radius}
+
+Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (eq.~[\ref{eq:first_law}])
 \begin{align}
 T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
-\times 10^6\ \, v_{500}^2 \,\,{\rm K} 
+\times 10^6\ \, v_{500}^2 \,\,{\rm K},
 \label{eq:Tanalytic}
 \end{align}
+where $v_{500} \equiv v_{\rm w}/500$ km s$^{-1}$.
 
@@
 \rs=\frac{G \Mbh}{n \vw(\rs)^2}\left(\frac{9-\Gamma}{2} \frac{\Mstar(\rs)}{\Mbh} +\frac{7}{2}\right),
-\label{eq:stag_analytic})
-\end{align}
-in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
-
-If the SMBH dominates the gravitational potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg \sigma$) then equation (\ref{eq:stag_analytic}) simplifies greatly
+\label{eq:stag_analytic}
+\end{align}
+where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
+If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w,0} \gg \sigma$ and $r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
+In this case equation (\ref{eq:stag_analytic}) simplifies to
 \begin{align}
@@
 where the numerical estimate assumes $n = 1$.
-This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).
-In the opposite limit when the wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.
-
-\subsubsection{SMBH Accretion Rate}
+This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their eq.~6).
+In the opposite limit of weak heating ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all.
+This makes intuitive sense: gas is injected by stars which are gravitationally bound to the black hole, so outflows only occur if the heating rate per gram $\sim v_{\rm w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+
+\subsection{SMBH Accretion Rate}
 
@@
 \end{eqnarray}
-where we have made use of equation (\ref{eq:stag_simple}), i.e. assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
+where we have made use of equation (\ref{eq:stag_simple}), assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
 \begin{eqnarray}
@@
 \end{eqnarray}
-To reproduce the estimated values $\sim 10^{-XX}$ in low luminosity AGN, we thus require $v_{w,0} \sim $.  {\bf BDM: put some realistic numbers, e.g. from Ho 2009 or better references}
-
-The gas density at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate.
-Its value can be crudely estimated using equation (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
+%To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w,0} \gtrsim 150M_{\bullet,8}^{0.5}$
+
+The gas density at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate accurately.
+Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$ in conjuction with equation (\ref{eq:mdot_analytic}), one finds
 \begin{align}
@@
 
-It is useful to compare our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) to the traditional ``Bondi" rate for accretion onto a point source from an external medium of fixed density and temperature density (\citealt{Bondi52}):
+Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) may be compared to the traditional Bondi rate for accretion onto a point source from an external medium of fixed density and temperature density (\citealt{Bondi52}):
 \begin{align}
@@
 
-\subsubsection{Importance of Heat Conduction}
+\subsection{Importance of Heat Conduction}
 
@@
 \end{align}
-where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$, $\nabla \sim 1/r_{\rm st}$.
+where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.
 Because the stagnation radius is usually well inside the break radius, we have approximated the stellar density as (eq.~[\ref{eq:rhostar}])
@@
 \end{eqnarray}
-Even in the saturated case, heat conduction is at most an order unity correction for expected values of the saturation parameter $\phi < 0.3$, justifying its neglect in our analysis.
-
-\subsubsection{Thermal Instability}
+Even in the saturated case, heat conduction is at most an order unity correction for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
+
+\subsection{Thermal Instability}
+\label{sec:instability}
 
 Radiative cooling, if important, qualitative alters key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} \propto T^{-2.7}$ (see below) is thermally unstable.
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{-2.7}$ (see below) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \in [-0.7,0.5]$.
 If manifest, thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Wang+14}).
@@
 
-\subsection{Numerical Results}
+\section{Numerical Results}
 \label{sec:numerical}

### 2015-01-12 ms.tex
editing

@@
 Radiative cooling, if important, qualitative alters key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{-2.7}$ (see below) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \in [-0.7,0.5]$.
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{\beta-2}$ (see below) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \in [-0.7,0.5]$.
 If manifest, thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Wang+14}).
@@
 
-\subsection{Millisecond Pulsars}
- Energy injection from millisecond pulsars (MSPs) is a potentially
-important heating source.  If the number of MSPs per unit stellar mass
-is $n_{\rm msp}$ and each contributes on average a spin-down
-luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
-volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon$ results in an
-effective heating rate (eq.~ [\ref{eq:vw_eff}])
-
-\begin{eqnarray} v_{\rm w,0}^{\rm MSP} \approx
-30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
-sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \eta_{0.02}^{-1/2}\,{\rm
-km\,s^{-1}},
- \label{eq:vmsp}
-  \end{eqnarray}
-
-where $\epsilon$ is the thermalization efficiency of
-the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based
-on modeling the insterstellar mediums of globular clusters
-\citep{NaimanSoares-Furtado+:2013a}.  The above estimate adopts a
-pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$
-motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of
-stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
-
-The average spin-down luminosity of millisecond pulsars in the field
-is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based
-on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
-case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.  For higher spin-down
-luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
-of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0}
-\lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the optimistc assumption $\epsilon = 1$.  On the other hand, the
-binaries giving rise to MSPs may be disocciated by stellar
-interactions in the dense nuclear cluster, reducing their numbers as
-compared to the field population estimate above.  We conclude that
-MSPs are unlikely to be an important source of heating, probably
-insufficient to stabilize the steady flow against cooling instability
-(e.g. $v_{\rm w,0}^{\rm MSP} < v_{\rm critt}$;
-eq.~[\ref{eq:cooling2}])
-
 \subsection{Type Ia Supernovae}
@@
 that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
-the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.
+the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  We hereafter adopt $\epsilon_{\rm Ia} = 0.4$.
 
@@
 
-The high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent a potentially dominant source of non-AGN heating in the CNM.
-However, SNe can only be approximated as being a constant heating source throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
+The high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
+However, SNe can only be approximated as supplying constant heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
 We define the ``Ia radius"
@@
 Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
-Hence Ia SN can in principle periodically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Hence, even if $r_{\rm s} > r_{\rm Ia}$, the accretion rate will be limited to a value set by substituting $r_{\rm Ia}$ for $r_{\rm s}$ in derivigin equation $\ref{eq:eddr_analytic}$, i.e.
+{\bf calculate:}
+\begin{eqnarray}
+\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx&
+  \begin{cases}
+    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
+    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
+    2.4 \times 10^{-5} \Mbheight^{0.48} 
+    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
+  \end{cases}
+  \label{eq:eddr_Ia}
+\end{eqnarray}
+
+\subsection{Millisecond Pulsars}
+ Energy injection from millisecond pulsars (MSPs) is a potentially
+important heating source.  If the number of MSPs per unit stellar mass
+is $n_{\rm msp}$ and each contributes on average a spin-down
+luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
+volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon$ results in an
+effective heating rate (eq.~ [\ref{eq:vw_eff}])
+
+\begin{eqnarray} v_{\rm w,0}^{\rm MSP} \approx
+30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
+sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \eta_{0.02}^{-1/2}\,{\rm
+km\,s^{-1}},
+ \label{eq:vmsp}
+  \end{eqnarray}
+
+where $\epsilon$ is the thermalization efficiency of
+the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based
+on modeling the insterstellar mediums of globular clusters
+\citep{NaimanSoares-Furtado+:2013a}.  The above estimate adopts a
+pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$
+motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of
+stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
+
+The average spin-down luminosity of millisecond pulsars in the field
+is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based
+on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
+case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.  For higher spin-down
+luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
+of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0}
+\lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
+under the optimistc assumption $\epsilon = 1$.  On the other hand, the
+binaries giving rise to MSPs may be disocciated by stellar
+interactions in the dense nuclear cluster, reducing their numbers as
+compared to the field population estimate above.  MSPs are thus unlikely to be an important source of heating in comparison to stellar heating.
 

### 2015-01-12 ms.tex
editing2

@@
 \newcommand{\lambdars}{\lambda_{\rs}}
-\newcommand{\vw}{v_w}
+\newcommand{\vw}{\tilde{v}_{w}}
 
@@
 \newcommand{\ke}{\frac{v^2}{2}}
-\newcommand{\kew}{\frac{v_w^2}{2}}
+\newcommand{\kew}{\frac{\tilde{v}_{w}^2}{2}}
 
@@
 
-\newcommand{\vwO}{v_{w,0}}
+\newcommand{\vwO}{v_{w}}
 \newcommand{\kewO}{\frac{\vwO^2}{2}}
@@
 \newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
-\newcommand{\vwOFH}{v_{w,0,500}}
+\newcommand{\vwOFH}{v_{500}}
 \newcommand{\vwOFHexp}{\frac{\vwO}{500 \, {\rm km/s}}}
@@
 This is often
-attributed to cosmological `down sizing' (e.g, \citealt{Gallo+08}), even though the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
+attributed to general trend  of cosmological `down-sizing' (e.g, \citealt{Gallo+08}).
+However, the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
 
@@
 
-The term $\propto \vw^2 = \sigma(r)^2+v_{w,0}^2$ in the entropy
+The term $\propto \vw^2 = \sigma(r)^2+v_{w}^2$ in the entropy
 equation accounts for external heating sources (e.g.,
@@
 wind velocities $\ll \sigma$ that characterize AGB mass loss in old
-stellar populations.  The second term, $v_{w,0}^{2}$, parameterizes
+stellar populations.  The second term, $v_{w}^{2}$, parameterizes
 the contribution of additional sources of heating, such as faster main
@@
 feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
-$v_{w,0}$ is uncertain and will in general depend on the SMBH mass and
+$v_{w}$ is uncertain and will in general depend on the SMBH mass and
 the age of the stellar population.
@@
 (\citealt{Brandenburg:2003a}).  We solve the equations for different
-choices of $v_{\rm w,0} = 300, 600, 1200$ km s$^{-1}$ spanning a
+choices of $v_{w} = 300, 600, 1200$ km s$^{-1}$ spanning a
 physically plausible range.  Although we are interested in the
@@
 We begin by describing analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the derivation of which are given in Appendix \ref{app:rs}.
-Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter
-(eq.~[\ref{eq:dsdt}])
-\begin{eqnarray}
-  v_{\rm w} &=& v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2}  \nonumber \\
-  &\approx& v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}\left[\frac{v_{w,0}}{500\,\rm km\,s^{-1}}\right]^{-1}\right)^{1/2},
-\end{eqnarray}
-where the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+Our results are expressed in terms of the SMBH mass $M_{\bullet}$, heating parameter $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
 
@@
 \begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
+T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2} \approx 3.7
 \times 10^6\ \, v_{500}^2 \,\,{\rm K},
@@
 \end{align}
-where $v_{500} \equiv v_{\rm w}/500$ km s$^{-1}$.
+where $v_{500} \equiv \tilde{v}_{w}/500$ km s$^{-1}$.
 
@@
 where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
-If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w,0} \gg \sigma$ and $r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
+If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w} \gg \sigma$ and $r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
 In this case equation (\ref{eq:stag_analytic}) simplifies to
 \begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n v_{\rm w}^{2}} \approx 6
+  &\rs=\frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx 6
  \, \pc \,\, \Mbheight v_{500}^{-2},
@@
 This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their eq.~6).
-In the opposite limit of weak heating ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all.
-This makes intuitive sense: gas is injected by stars which are gravitationally bound to the black hole, so outflows only occur if the heating rate per gram $\sim v_{\rm w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all.
+This makes intuitive sense: gas is injected by stars which are gravitationally bound to the black hole, so outflows only occur if the heating rate per gram $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
 
@@
 \end{eqnarray}
-where we have made use of equation (\ref{eq:stag_simple}), assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
+where we have made use of equation (\ref{eq:stag_simple}), assuming that $v_{w} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
 \begin{eqnarray}
@@
 \end{eqnarray}
-%To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w,0} \gtrsim 150M_{\bullet,8}^{0.5}$
+%To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$
 
@@
 w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}(1+\phi)}
+T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) \tilde{v}_{w}^{2}(1+\phi)}
 \nonumber \\ &\sim {\rm min}
@@
 
-Radiative cooling can, however, be stabilized by the other sources of cooling, such as the stellar wind source term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q v_{\rm w}^{2}/2$ (neglecting conduction and radiative cooling).
+Radiative cooling can, however, be stabilized by the other sources of cooling, such as the stellar wind source term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q \tilde{v}_{w}^{2}/2$ (neglecting conduction and radiative cooling).
 Thermal stability at the stagnation radius can thus be assessed by comparing the nominal wind heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$,
@@
 \begin{align}
-v_{w,0} > v_{\rm crit} \simeq
+v_{w} > v_{\rm crit} \simeq
   {\rm max}\begin{cases}
@@
 \end{align}
-Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $v_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
-The inclusion of $\sigma$ in equation (\ref{eq:cooling2}) results because the top two lines apply only for $v_{w} > \sigma$ since their derivation assumed the existence of a stagnation radius given by equation (\ref{eq:rs_simple}).
+Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
+The inclusion of $\sigma$ in equation (\ref{eq:cooling2}) results because the top two lines apply only for $\tilde{v}_{w} > \sigma$ since their derivation assumed the existence of a stagnation radius given by equation (\ref{eq:rs_simple}).
 
@@
 \label{tab:sols}}
-\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
+\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w}$} &
   \colhead{$\gamma$} & \colhead{$r_b$} &
@@
 \tablecaption{Core Results \label{tab:sols}}
-\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
+\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w}$} &
 \colhead{$\gamma$} & \colhead{$r_b$} & \colhead{$\dot{M}/\dot{M}_{\rm
@@
 for each galaxy for three different values of the stellar wind heating
-parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.
+parameter $v_{w}$ = 300, 600, 1200 km s$^{-1}$.
+In cases when the stagnation radius become very large and was difficult to resolve on the grid, we conclude that such solutions will be thermally unstable and terminated their calculations (these are marked as `thermally unstable' in the tables.
 
@@
 $r_{\rm soi}$), with different colors representing different values of
-$v_{w,0}$.  Cusp and core galaxies are marked with square and
+$v_{w}$.  Cusp and core galaxies are marked with square and
 triangles, respectively.
@@
       soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
-    function of the ratio of the effective wind heating rate $v_{w,0}$
+    function of the ratio of the effective wind heating rate $v_{w}$
     to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols represent $v_{w,0} =$ 300, 600, and 1200 km s$^{-1}$,
+    blue symbols represent $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
     respectively.  Squares correspond to cusp galaxies, while
@@
 
-Key properties of the flow, such as the stagnation radius, the SMBH accretion rate, and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w,0}^{2}$.
+Key properties of the flow, such as the stagnation radius, the SMBH accretion rate, and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w}^{2}$.
 This section summarizes individual heating sources, providing estimates of the value of
 \begin{align}
-  v_{\rm w,0} = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
+  v_{w} = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
   \label{eq:vw_eff}
@@
 disproportionally large share of the kinetic energy of winds.
-\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim
+\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{w} \sim
 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
@@
 s$^{-1}$.  In Appendix \ref{app:windheat} we present a model for
-how $v_{\rm w,0}$ varies as a function of stellar age.
+how $v_{w}$ varies as a function of stellar age.
 
@@
 Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{\rm w,0}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
@@
   \begin{eqnarray} 
-    v_{w,0}^{\rm Ia} &\approx& 700(\epsilon_{\rm
+    v_{w}^{\rm Ia} &\approx& 700(\epsilon_{\rm
       Ia}/0.4)^{0.5}(\tau_{\star}/t_{\rm h})^{-0.56}\eta_{0.02}^{-1/2}\,{\rm km
@@
 
-The high value of $v_{w,0}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
+The high value of $v_{w}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
 However, SNe can only be approximated as supplying constant heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
@@
 
-Assuming that $v_{\rm w,0}^{\rm Ia} \gg \sigma$ then by substituting $v_{\rm w,0}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into our expression for the stagnation radius (\ref{eq:rs_simple}), we can write
+Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting $v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into our expression for the stagnation radius (\ref{eq:rs_simple}), we can write
 \begin{eqnarray}
-\left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w,0}^{\rm Ia}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
+\left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
 &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
@@
 The fact that $r_{\rm Ia} \gg r_{\rm s}$ would appear to imply that Ia heating only represents a sources of steady heating near the stagnation radius for very massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ and/or very young populations ($\tau_{\star} \ll t_{\rm h}$).
-However, this expression underestimates the importance of Ia heating, since the actual stagnation radius will be substantially larger than its value for $v_{\rm w,0}^{\rm Ia}$ if the nominal heating rate is much less than this.
+However, this expression underestimates the importance of Ia heating, since the actual stagnation radius will be substantially larger than its value for $v_{w}^{\rm Ia}$ if the nominal heating rate is much less than this.
 In general it is reasonable to expect that the impact of Ia SN will increase for larger SMBH masses.
@@
 Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm g}\sigma^{2}$.
-Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{\rm w,0}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
+Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
 Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Hence, even if $r_{\rm s} > r_{\rm Ia}$, the accretion rate will be limited to a value set by substituting $r_{\rm Ia}$ for $r_{\rm s}$ in derivigin equation $\ref{eq:eddr_analytic}$, i.e.
-{\bf calculate:}
+Hence, even if $r_{\rm s} > r_{\rm Ia}$, the accretion rate will be limited to a value set by substituting $r_{\rm Ia}$ for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.
 \begin{eqnarray}
-\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx&
-  \begin{cases}
-    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
-    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
-    2.4 \times 10^{-5} \Mbheight^{0.48} 
-    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
+\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+ && \begin{cases}
+    3 \times 10^{-4} M_{\bullet,8}^{-1.26}(\tau_{\star}/t_{\rm h})^{-0.3}
+   & \text{core} \\
+    1.5 \times 10^{-4} \Mbheight^{-0.77}(\tau_{\star}/t_{\rm h})^{-0.7}   & \text{cusp}, 
   \end{cases}
@@
 
-\begin{eqnarray} v_{\rm w,0}^{\rm MSP} \approx
+\begin{eqnarray} v_{w}^{\rm MSP} \approx
 30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
@@
 on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
-case $v_{\rm w,0} \lesssim 30$ km s$^{-1}$.  For higher spin-down
+case $v_{w} \lesssim 30$ km s$^{-1}$.  For higher spin-down
 luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
-of some Fermi-detected pulsars, then the higher value of $v_{\rm w,0}
+of some Fermi-detected pulsars, then the higher value of $v_{w}
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
@@
 (\ref{eq:vw_eff}) that
-\begin{align} v_{\rm w,0}^{\rm C} \simeq
+\begin{align} v_{w}^{\rm C} \simeq
   \begin{cases} 13 \eta_{0.02}^{0.5}T_{\rm
@@
 accretion flow (e.g.~\citealt{Narayan&Yi95}).  Assuming that heating
-is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds
+is dominated by Compton heating ($\tilde{v}_{w} = v_{w}^{C}$) one finds
 that
-\begin{align} v_{\rm w,0}^{\rm C} \simeq
+\begin{align} v_{w}^{\rm C} \simeq
   \begin{cases} 106 \eta_{0.02}^{0.21}T_{\rm
@@
 heating is insufficient to stabilize the steady flow against cooling
-instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$;
+instability (e.g. $v_{w}^{C} < v_{\rm critt}$;
 eq.~[\ref{eq:cooling2}]).
@@
 of
-\begin{eqnarray} v_{w,0}^{\bullet} &\approx& \left(\frac{2t_{\rm
+\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
 h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
@@
 r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim
-10^{-6}$ is sufficient for $v_{\rm w,0}^{\bullet}$ to exceed other
+10^{-6}$ is sufficient for $v_{w}^{\bullet}$ to exceed other
 sources of non-accretion powered heating.  However, if the jet
@@
   w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto
-M_{\bullet}^{1-\Gamma/2}v_{\rm w,0}^{\Gamma-2}$ is proportional to
-$v_{w,0}$ to a negative power, where the last proportionality makes
+M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to
+$v_{w}$ to a negative power, where the last proportionality makes
 use of equation (\ref{eq:stag_simple}).  As in the case of Compton
@@
 thermodynamic properties of the gas on larger scales.  Also note that
-$v_{\rm w,0}^{\bullet}$ is proportional to a positive power of SMBH
+$v_{w}^{\bullet}$ is proportional to a positive power of SMBH
 mass $\propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies,
@@
 
-The total heating rate $\vwO = \sqrt{v_{\rm w,0}^{\star \, 2} + v_{\rm
-    w,0}^{\rm Ia \, 2} + v_{\rm w,0}^{\rm p \, 2} + v_{\rm
+The total heating rate $\vwO = \sqrt{v_{w}^{\star \, 2} + v_{\rm
+    w,0}^{\rm Ia \, 2} + v_{w}^{\rm p \, 2} + v_{\rm
     w,0}^{\bullet \, 2}}$ has
@@
 the $\vwO$ for each heating source using the cosmic star formation
-histories in \citet{MosterNaab+:2013a}.  For $v_{\rm w,0}^{\rm p}$ we
+histories in \citet{MosterNaab+:2013a}.  For $v_{w}^{\rm p}$ we
 use equation~\eqref{eq:vmsp}. The star formation history simply enters
@@
   simplified expression for $\eta_{\rm Imp}$} ($\eta$ in the impulsive
-limit). For $v_{\rm w,0}^{\rm Ia}$ we use
+limit). For $v_{w}^{\rm Ia}$ we use
 equation~\eqref{eq:vIa}. Besides $\eta$ there is additional dependence
@@
 of the star formation history with the delay-time distribution from
-\citet{MaozMannucci+:2012a}. The calculation of $v_{\rm w,0}^{\star}$
+\citet{MaozMannucci+:2012a}. The calculation of $v_{w}^{\star}$
 is somewhat involved: we leave the detailed description for
@@
 feedback) is plotted in as a function of $\Mbh$ in
-Figure~\ref{fig:vwSources}. $v_{\rm w,0}^{\rm p}$ is negligible across
+Figure~\ref{fig:vwSources}. $v_{w}^{\rm p}$ is negligible across
 all $\Mbh$. For $\Mbh\lsim 10^{7.5} \Msun$, have substantial recent
-star formation and $v_{\rm w,0}^{\star}$ is dominant. For $\Mbh\gsim
+star formation and $v_{w}^{\star}$ is dominant. For $\Mbh\gsim
 10^{7.5} \Msun$ , the younger stellar population with their energetic
@@
   will have a weak dependence on the stellar density power law slope,
-  $\Gamma$, since $v_{\rm w,0}^{\bullet \, 2}$ depends on
+  $\Gamma$, since $v_{w}^{\bullet \, 2}$ depends on
   $\Gamma$. The solid black curve corresponds to $\Gamma=0.8$
@@
 % stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
-% to contribute their full heating rate.  $v_{\rm w,0}^{\rm Ia} \sim
+% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
 % 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
-% infrequent, in which case main sequence stars ($v_{\rm w,0}^{\star}
+% infrequent, in which case main sequence stars ($v_{w}^{\star}
 % \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
@@
 Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
-Thus, only a weak positive dependence of $v_{\rm w,0} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{\rm w,0} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.
+Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.
 What could cause this dependence?
@@
 hosted younger stellar populations.  Another possible explanation is
-that the effective heating rate of the CNM $v_{\rm w,0}$ decreases
+that the effective heating rate of the CNM $v_{w}$ decreases
 with decreasing SMBH mass.  This could again be due to an older
-stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating
+stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
 sources such as SN Ia and millisecond pulsars.
@@
 
-{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{\rm w,0}^{\bullet}$ and $\sigma = v_{\rm w,0}^{\star}$.
+{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{w}^{\bullet}$ and $\sigma = v_{w}^{\star}$.
 }
@@
 
-If cooling becomes important in the flow ($v_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+\begin{itemize}
+\item{Fact that some low mass BHs appear to have nearly Eddington accretion rates, suggest an external origin - since the maximum Ia rate appears to be below this}
+\end{itemize}
+
+If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
 There are two kinds of ``instabilities", global and local.
@@
 stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
-(\ref{eq:rhors2}).  We thus see that the condition $v_w \gtrsim v_{\rm
+(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
   crit}$ is also the condition for local instability, although the
@@
     preferentially hosted younger stellar populations. Another possible
-    explanation is that the effective heating rate of the CNM $v_{\rm w,0}$
+    explanation is that the effective heating rate of the CNM $v_{w}$
     decreases with decreasing SMBH mass. This could again be due to an
-    older stellar population, since $v_{\rm w,0} \propto \eta^{−1/2}$
+    older stellar population, since $v_{w} \propto \eta^{−1/2}$
     for heating sources such as SN Ia and millisecond pulsars.

### 2015-01-13 ms.tex
Putting description of what I did with the break radius.

@@
 
-A galaxy model is fully specified by four parameters: $\Mbh$, $\Gamma$, $r_b$,
-and $\beta$.
-We compute models for three different black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.
-The distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim 0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
-We bracket these possibilities by considering models with $\Gamma=0.8$ and $\Gamma=0.1$.
-Since our results are most sensitive to the properties of the gas flow on radial scales $\ll r_b$, we fix $\beta = 2$ (a typical value).
-However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.
-We adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core galaxy models we employ the scaling relation $\rb = $, motivated again by the \citet{LauerFaber+:2007a} sample.
-({\bf BDM: fill in!}).
-Though simplistic, our results are not sensitive to our assumption about the value of $\rb$.
+A galaxy model is fully specified by four parameters: $\Mbh$,
+$\Gamma$, $r_b$, and $\beta$.  We compute models for three different
+black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.  The
+distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is
+bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim
+0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
+We bracket these possibilities by considering models with $\Gamma=0.8$
+and $\Gamma=0.1$.  Since our results are most sensitive to the
+properties of the gas flow on radial scales $\ll r_b$, we fix $\beta =
+2$ (a typical value). In any case, the flow inside $\rb$ is
+insensitive the outer power law slope of the stellar density
+profile. However, the presence of $\rb$ is necessary for to obtain a
+converged steady state for some regions of our parameter space.  We
+consider four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
+and 400 pc. These choices are motivated by the observed break radii in
+the \citet{LauerFaber+:2007a} sample. For the core galaxies
+($\Gamma$<0.3) in this sample the break radius follows the scaling
+relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
+approximately one dex. Most the cusp ($\Gamma>0.5$) galaxies have
+$\rb$ between 100 and 1000 pc, and there is not trend with
+$\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
+  significant effect on rs it may not be necessary to do runs. For
+  instance for Mbh=$10^8$ Msun, gamma=0.8, and vw0=600 km/s the
+  stagnation radius changes by only 8\%. So for cusp galaxies with
+  vw0$\gsim$600 km/s and Mbh$\lsim 10^8$ Msun it seems like it is a
+  safe bet to neglect the effect of the break radius on the
+  solution. For low heating rates it my be difficult to converged
+  solution for large values of rb=200 and 400 pc.}
+% However, the presence of $\rb$ is necessary for to obtain a
+% converged steady state for some regions of our parameter space. We
+% adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core
+% galaxy models we employ the scaling relation $\rb = $, motivated again
+% by the \citet{LauerFaber+:2007a} sample. ({\bf BDM: fill in!}).
+% Though simplistic, our results are not sensitive to our assumption
+% about the value of $\rb$.
 

### 2015-01-13 ms.tex
Fixing a couple of typos in the description of rb.

@@
 the \citet{LauerFaber+:2007a} sample. For the core galaxies
-($\Gamma$<0.3) in this sample the break radius follows the scaling
+($\Gamma \le$0.3) in this sample the break radius follows the scaling
 relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
-approximately one dex. Most the cusp ($\Gamma>0.5$) galaxies have
+approximately one dex. Most the cusp ($\Gamma \ge0.5$) galaxies have
 $\rb$ between 100 and 1000 pc, and there is not trend with

### 2015-01-13 ms.tex
Starting to clean up the table of models.

@@
 \begin{minipage}{18cm}
-\caption{Models Evolved and Outflow
-Properties\label{t:models}\label{t:results}. The first
-six columns show model name, HMNS lifetime, stellar period, fractional
-radial resolution
-at inner boundary, and irradiation by the neutron star, respectively.
-The last eight columns show integrated properties of the outflow,
-restricted to equatorial
- ($\theta \in [30^\circ,150^\circ]$) and polar ($\theta<30^\circ$ and
-$\theta > 150^\circ$)
-latitudes. Each group of four columns includes the mass-flux weighted
-electron fraction, entropy,
-and expansion time at a radius where the mass-flux weighted temperature is
-$5\times10^9$~K, as
-well as the net mass in unbound material crossing a surface at $10^9$~cm,
-normalized
-by the initial torus mass.}
+\caption{}
 \begin{tabular}{lccccccccccccc}
 \hline
-{Model}&
-{$t_{\rm ns}$} &
-{$P_\star$} &
-{$\alpha$} &
-{$\Delta r_{\rm min}/R_\star$} &
-{$\star$-Irr.} &
-\multicolumn{4}{c}{Equatorial Outflow} &
-\multicolumn{4}{c}{Polar Outflow$^b$}\\
-{ } & \multicolumn{2}{c}{(ms)} &  {}  &  {}  & {} &
-{$\bar{Y}_e$} &
-{$\bar{s}$ } &
-{$t_{\rm exp}$} &
-{$M_{\rm ej,unb}/M_{\rm t0}$} &
-{$\bar{Y}_e$} &
-{$\bar{s}$ } &
-{$t_{\rm exp}$} &
-{$M_{\rm ej,unb}/M_{\rm t0}$}\\
-\multicolumn{6}{c}{} & {} & {($k$/b)} & {(ms)} & {(\%)} & {} & {($k$/b)} &
-{(ms)} & {(\%)}\\
-%}
+{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
 \hline
-t000A3      & 0        & ... & 0.03 & 5E-3 & No   & 0.18 & 18 & 27  & 2.1
-& ...  & ... & ... & 0.9 \\
-t010A3p15   & 10       & 1.5 &      &      & Yes  & 0.19 & 20 & 30  & 2.5
-& ...  & ... & ... & 1.0 \\
-t030A3p15   & 30       &     &      &      &      & 0.23 & 21 & 27  & 3.9
-& 0.50 & 45  & 7.6 & 1.3 \\
-t100A3p15   & 100      &     &      &      &      & 0.28 & 20 & 33  & 9.2
-& 0.47 & 42  & 11  & 4.0 \\
-t300A3p15   & 300      &     &      &      &      & 0.30 & 20 & 32  & 28
-& 0.44 & 38  & 17  & 8.8 \\
-tInfA3p15   & $\infty$ &     &      &      &      & 0.32 & 21 & 42  & 67
-& 0.43 & 52  & 17  & 22  \\
-\noalign{\smallskip}
-pA1p15      & $\infty$ & 1.5 & 0.01 & 5E-3 & Yes  & 0.36 & 21 & 61  & 47
-& 0.45 & 52  & 19  & 22 \\
-pA3p20      &          & 2   & 0.03 &      &      & 0.30 & 29 & 37  & 62
-& 0.37 & 62  & 15  & 17 \\
-pA3p15xs    &          & 1.5 &      &      & No   & 0.27 & 21 & 45  & 56
-& 0.35 & 61  & 15  & 23 \\
-\noalign{\smallskip}
-rA3p15r1    & $\infty$ & 1.5 & 0.03 & 1E-2 & Yes  & 0.32 & 21 & 45  & 69
-& 0.43 & 53  & 17  & 22 \\
-rA3p15r2$^a$   &       &     &      & 2E-3 &      & ... & ... & ... & ...
-& ...  & ... & ... & ... \\
+0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+unresolved \\
+0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+10^{ 2 }$ &  rb in fact unresolved\\
+0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+10^{ 4 }$ &  rb in fact unresolved\\
+0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
+cons on outer grid \\
+0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
+0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+10^{ 3 }$ &  energy cons on inner grid\\
+1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
+1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
+1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
+0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
+0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
+0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
+0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
+1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+  -2 }$ &  possible issue w/ conv \\
+1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
 \hline
-\hline
-\multicolumn{14}{l}{$^a$ Model rA3p15r2 was evolved for a shorter time.
-See Appendix~\ref{s:neutrino_details}
-                    for details.}\\
-\multicolumn{14}{l}{$^b$ Average thermodynamic quantities are not computed
-if there is no region
-                         where the average temperature is $\sim 5\times 10^9$~K.}
 \label{table:models}

### 2015-01-13 ms.tex
Changing some of the comments in the solution table.

@@
 10^{ 3 }$ &  energy cons on inner grid\\
-1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+  -2 }$ &  TI\\
 1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
-1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
+1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+  3 }$ &  \\
+1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
+1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+  -2 }$ &  TI/convergence \\
+1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+  -3 }$ &  TI/convergence\\
+1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+  -3 }$ &  TI/run unsuccessful\\
 0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
@@
 0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
-1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
-1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
-  -2 }$ &  possible issue w/ conv \\
-1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
-  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
+
 \hline

### 2015-01-13 ms.tex
Cusp part of the table is pretty much finished.

--- 2015-01-13 ms.tex
@@
 
-\begin{deluxetable}{lllllll}
-\tabletypesize{\scriptsize}
-\tabcolsep0.05in\footnotesize
-\tablewidth{0pc}
-\tablecaption{Cusp Results
-\label{tab:sols}}
-\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w}$} &
-  \colhead{$\gamma$} & \colhead{$r_b$} &
-  \colhead{$\dot{M}/\dot{M}_{\rm Edd}$} & \colhead{$t_{\rm
-      cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
-\startdata
-0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
-unresolved \\
-0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
-10^{ 2 }$ &  rb in fact unresolved\\
-0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
-10^{ 4 }$ &  rb in fact unresolved\\
-0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
-cons on outer grid \\
-0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
-0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
-10^{ 3 }$ &  energy cons on inner grid\\
-1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
-1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
-1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
-0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
-0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
-0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
-0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
-1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
-1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
-  -2 }$ &  possible issue w/ conv \\
-1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
-  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
-\enddata
-\end{deluxetable}
-
 \begin{table*}
@@
 10^{ 3 }$ &  energy cons on inner grid\\
-1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
+1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+  -2 }$ &  TI\\
 1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
-1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
-0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
-0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
-0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
-0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
+1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+  3 }$ &  \\
 1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
 1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
-  -2 }$ &  possible issue w/ conv \\
-1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
-  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
+  -2 }$ &  TI/convergence \\
+%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+%  -3 }$ &  TI/convergence\\
+1 & 300.0 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
+0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
+0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
+%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
+%10^{ -2 }$   & TI/convergence  \\
+0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ & TI/convergence \\
+
 \hline

### 2015-01-13 ms.tex
Putting in core galaxies into table. Break radii still need cleanup

@@
 \hline
-0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+0.01 & 300.0 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
 unresolved \\
-0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+0.01 & 600.0 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
 10^{ 2 }$ &  rb in fact unresolved\\
-0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+0.01 & 1200.0 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
 10^{ 4 }$ &  rb in fact unresolved\\
@@
 %10^{ -2 }$   & TI/convergence  \\
-0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ & TI/convergence \\
+0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
+10^{ -2 }$ & TI/convergence \\
+0.01 & 1200.0 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
+10^{ 4 }$ &  rb is unsresolved\\
+0.1 & 1200.0 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
+  3 }$ &  tried run in which rb=100 pc was resolvedwhat would happen if rb=400 pc?\\
+
+1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
+1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{
+  2 }$ &  \\
+0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
+0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
+1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
+1 & 1200.0 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
+1 & 1200.0 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  convergence\\
+1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
+1 & 1200.0 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
 
@@
 \end{table*}
-
-\begin{deluxetable}{lllllll}
-\tabletypesize{\scriptsize}
-%\tablecolumns{6}
-\tabcolsep0.05in\footnotesize
-\tablewidth{0pc}
-\tablecaption{Core Results \label{tab:sols}}
-\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w}$} &
-\colhead{$\gamma$} & \colhead{$r_b$} & \colhead{$\dot{M}/\dot{M}_{\rm
-Edd}$}  & \colhead{$t_{\rm cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
-\startdata
-0.01 & 600.0 & 0.1 & 100.0 & $ 3.4 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ &  \\
-0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
-0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
-1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
-1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  \\
-\enddata
-\end{deluxetable}
 

### 2015-01-15 ms.tex
Replacing the heating source figure

@@
 0.1 & 1200.0 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
-  3 }$ &  tried run in which rb=100 pc was resolvedwhat would happen if rb=400 pc?\\
-
+  3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
 1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
@@
 1 & 1200.0 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
-1 & 1200.0 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  convergence\\
-1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
+1 & 1200.0 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
+%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
 1 & 1200.0 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\

### 2015-01-23 ms.tex
updating figures

@@
   calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
-  resulting from stellar winds and MSPs ({\it dashed black}) and stellar
-  winds, MSPs, and black hole feedback ({\it solid black}). The heating
-  will have a weak dependence on the stellar density power law slope,
-  $\Gamma$, since $v_{w}^{\bullet \, 2}$ depends on
-  $\Gamma$. The solid black curve corresponds to $\Gamma=0.8$
-  and the dash-dotted black curve corresponds to $\Gamma=0.1$.}
+  resulting from stellar winds, MSPs, and black hole feedback ({\it
+    solid black}). The heating will have a weak dependence on the
+  stellar density power law slope, $\Gamma$, since $v_{w}^{\bullet \,
+    2}$ depends on $\Gamma$. The solid black curve corresponds to
+  $\Gamma=0.8$ and the dash-dotted black curve corresponds to
+  $\Gamma=0.1$. Finally the vertical dashed black line marks the value
+  critical value of $\Mbh$, $M_{\rm bh, crit}$, such that... }
 \end{figure}

### 2015-01-25 ms.tex
random

@@
 \end{align}
-The use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), but our results are not sensitive to this assumption.
+The use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), but our results are not overly sensitive to this assumption.
 
@@
 We bracket these possibilities by considering models with $\Gamma=0.8$
-and $\Gamma=0.1$.  Since our results are most sensitive to the
-properties of the gas flow on radial scales $\ll r_b$, we fix $\beta =
-2$ (a typical value). In any case, the flow inside $\rb$ is
-insensitive the outer power law slope of the stellar density
-profile. However, the presence of $\rb$ is necessary for to obtain a
-converged steady state for some regions of our parameter space.  We
+and $\Gamma=0.1$.  We fix $\beta = 2$ (a typical value) because our results are most sensitive to the
+properties of the gas flow on radial scales $\ll r_b$ and do not depend sensitively on the outer power law slope of the stellar density profile.
+However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.
+Depending on the model, we
 consider four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
-and 400 pc. These choices are motivated by the observed break radii in
-the \citet{LauerFaber+:2007a} sample. For the core galaxies
-($\Gamma \le$0.3) in this sample the break radius follows the scaling
-relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
+and 400 pc, a range motivated by the observed break radii in
+the \citet{LauerFaber+:2007a} sample. For the core galaxies ($\Gamma \le$0.3) in this sample the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
 approximately one dex. Most the cusp ($\Gamma \ge0.5$) galaxies have
-$\rb$ between 100 and 1000 pc, and there is not trend with
-$\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
+$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
   significant effect on rs it may not be necessary to do runs. For
@@
 years.
-To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a star burst (e.g., \citealt{Ciotti+91}),\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
-Although we give the mass return rate per unit volume, our expressions are equivalent.} although $\eta$ can be higher if star formation is ongoing (Fig X).
+To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
+Although we give the mass return rate per unit volume, our expressions are equivalent.}, although we will show later that $\eta$ can be higher if star formation is ongoing (Fig.~\ref{fig:eta}).
 
@@
 by stellar winds and the mean properties of the background flow.  The
-term $\propto -q c_{s}^{2}$ acts as an important agent in stabilizing the flow to runaway cooling ($\S\ref{sec:instability}$).
+term $\propto -q c_{s}^{2}$ is important because it acts to potentially stabilize the flow to runaway cooling ($\S\ref{sec:instability}$).
 
@@
 equation accounts for external heating sources (e.g.,
-\citealt{ShcherbakovWong+:2014a}).  The first term accounts for the
-minimum shock heating of the stellar winds due to the random movement
-of stars with respect to each other at the characteristic velocity
-$\sim \sigma = \sqrt{GM_{\rm enc}/r}$, as is present even for the low
+\citealt{ShcherbakovWong+:2014a}).  The first term approximates the
+minimum amount of shock heating from stellar winds due to the random movement
+of stars with respect to one another at the characteristic velocity
+$\sim \sigma = \sqrt{GM_{\rm enc}/r}$.  This heating is present even for the low
 wind velocities $\ll \sigma$ that characterize AGB mass loss in old
@@
 the contribution of additional sources of heating, such as faster main
-sequence or Wolf-Rayet winds, millisecond pulsars, supernovae, AGN
+sequence or Wolf-Rayet stellar winds, spin-down energy from millisecond pulsars, supernovae, AGN
 feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
@@
 To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.
-Heat transport by electron conductivity is included with an additional term to the right hand side of the entropy equation of the form
+Heat transport by electron conductivity results in an an additional term on the right hand side of the entropy equation of the form
 \be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
@@
 field perpendicular to the flow could in principle suppress the
-conductivity.  However, the radially-decreasing temperature profiles
-of interest are susceptible to the magneto-thermal instability
-(\citealt{Balbus01}), the non-linear evolution of which is believed to
-result in a radially-directed field structure
-(\citealt{Parrish&Stone07}).
-
-Radiative cooling is also not included in our baseline calculations.  Across much of
-the parameter space radiative cooling is subdominant compared to other
-sources of cooling.  Radiative cooling cannot be neglected when $\vwO$
-is low (and/or $\eta$ is high), but once important it leads to thermal
-instabilities (e.g.~\citealt{McCourt+12}) which our 1D
+conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
+of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).
+
+Radiative cooling is also not included in our baseline calculations.
+Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling.
+Radiative cooling becomes important when $\vwO$ is low and/or $\eta$ is high, but once important it leads to thermal instabilities (e.g.~\citealt{McCourt+12}) which our 1D
 time-independent model cannot account for self-consistently anyways.
-Indeed, one of the main goals of this work is to use our analytic and
-numerical solutions neglecting radiation to ascertain over what
-physical conditions cooling instabilities are likely to develop
-($\S\ref{sec:cooling}$).
+Indeed, one of the main goals of this work is to use our analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities will develop ($\S\ref{sec:cooling}$).
 
@@
 and entropy equations for numerical stability
-(\citealt{Brandenburg:2003a}).  We solve the equations for different
+(\citealt{Brandenburg:2003a}).  We assume different
 choices of $v_{w} = 300, 600, 1200$ km s$^{-1}$ spanning a
-physically plausible range.  Although we are interested in the
-steady-state intflow/outflow structure, the time-dependent equations
-are solved to avoid numerical issues that arise near the critical
-sonic points, of which there are up to two because of the supersonic
-inflow on small radial scales and a possible supersonic outflow on
-large scales.
-
-The accuracy of our numerical solutions is assessed by checking the
-level of conservation of mass across the grid, as well as the integral
-constraint on the energy.  Mass and energy are conserved to $\lesssim
+physically plausible range of heating rates.  Although we are interested in the
+steady-state inflow/outflow structure (assuming it exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
+inflow on small radial scales and a possible supersonic outflow on large scales.
+
+We assess the accuracy of our numerical solutions by checking that mass is conserved across the grid, in addition to the integral constraint on the energy (Bernoulli integral).
+Mass and energy are conserved to $\lesssim
 40$ per cent for all solutions presented in this paper.  {\bf BDM:

### 2015-01-25 ms.tex
random2

@@
 \newcommand{\rhostar}{\rho_*}
-\newcommand{\Mstar}{m_{\star}}
+\newcommand{\Mstar}{M_{\star}}
 \newcommand{\Mseight}{M_{\star,8}}
@@
 
-Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (eq.~[\ref{eq:first_law}])
+Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at the stagnation radius is given by (eq.~[\ref{eq:first_law}])
 \begin{align}
@@
 \end{align}
-where $v_{500} \equiv \tilde{v}_{w}/500$ km s$^{-1}$.
-
-Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
-\begin{align}
-\rs=\frac{G \Mbh}{n \vw(\rs)^2}\left(\frac{9-\Gamma}{2} \frac{\Mstar(\rs)}{\Mbh} +\frac{7}{2}\right),
+where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$).  Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
+\begin{align}
+\rs=\frac{G \Mbh}{n \vw^{2}|_{\rs}}\left(\frac{9-\Gamma}{2} \frac{M_{\star}|_{\rs}}{\Mbh} +\frac{7}{2}\right),
 \label{eq:stag_analytic}
@@
 where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
-If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w} \gg \sigma$ and $r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
+
+If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w} \gg \sigma$ and hence the stagnation radius resides well inside the sphere of influence, i.e.~$r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
 In this case equation (\ref{eq:stag_analytic}) simplifies to
@@
 In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all.
-This makes intuitive sense: gas is injected by stars which are gravitationally bound to the black hole, so outflows only occur if the heating rate per gram $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+This result makes intuitive sense: gas is supplied by stars which are gravitationally bound to the black hole, so outflows occur only if the specific heating rate $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
 
@@
 
-The SMBH accretion rate is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
+The accretion rate onto the SMBH is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
 \begin{eqnarray}
@@
 \end{eqnarray}
-where we have made use of equation (\ref{eq:stag_simple}), assuming that $v_{w} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
+where we have made use of equation (\ref{eq:stag_simple}; assuming that $v_{w} \gg \sigma$) and have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
+The resulting Eddington ratio $\eddr$ is given by
 \begin{eqnarray}
@@
 \end{eqnarray}
+where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$  is the Eddington accretion rate, assuming a radiative efficiency of ten per cent.
+Note the sensitive inverse dependence of the accretion rate on the wind heating rate.
 %To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$
@@
 
-Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) may be compared to the traditional Bondi rate for accretion onto a point source from an external medium of fixed density and temperature density (\citealt{Bondi52}):
+Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) may be compared to the traditional Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
 \begin{align}
@@
 where $r_b \equiv GM/c_{s}^{2}$ is the Bondi radius, $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
-Rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho(\rs) v_{\rm ff}(\rs)/3$,
-we note a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $\rb$ is replaced by $\rs$.
+By rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho(\rs) v_{\rm ff}(\rs)/3$,
+one notices a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $\rb$ is replaced by $\rs$.
 When the stagnation radius resides interior to the sphere of influence we indeed have (eq.~[\ref{eq:stag_simple}])
@@
 
-The above analytic results neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
-The importance of conductive heating can be estimated by comparing its magnitude to the nominal level of ``wind" heating:
+Our analytic results above neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
+The ratio of the magnitude of conductive heating to the nominal level of ``wind" heating is given by
 \begin{align}
@@
 w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
-T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) \tilde{v}_{w}^{2}(1+\phi)}
+T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}} \tilde{v}_{w}^{2}(1+\phi)}
 \nonumber \\ &\sim {\rm min}
@@
 M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
-  10 \phi/(2-\Gamma) & \text{saturated},
+  1.0(\phi/0.1)/(2-\Gamma) & \text{saturated},
   \end{cases}
@@
 Radiative cooling, if important, qualitative alters key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{\beta-2}$ (see below) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \in [-0.7,0.5]$.
-If manifest, thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Wang+14}).
-
-Radiative cooling can, however, be stabilized by the other sources of cooling, such as the stellar wind source term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius equals $q \tilde{v}_{w}^{2}/2$ (neglecting conduction and radiative cooling).
-Thermal stability at the stagnation radius can thus be assessed by comparing the nominal wind heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$,
-\begin{align}
-\left.\frac{q \vw^2/2}{|\dot{q}_{\rm cool}|}\right|_{\rm r{s}} \simeq
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{-2.7}$ is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \sim -0.7$ is the cooling function (see below).
+Thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Gan+14}).
+
+Radiative cooling can, however, be stabilized by the other sources of cooling, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius is balanced by wind heating $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$ (neglecting radiative cooling).
+Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$,
+\begin{align}
+\left.\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm cool}|}\right|_{\rm r_{\rm s}} \simeq
   \begin{cases}
@@
 \end{align}
-where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gaseous and stellar densities at the stagnation radius, respectively.
-Here $n = \rho/\mu m_p$ and we have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}, Fig.
+where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gas and stellar densities at the stagnation radius, respectively.
+Here $n = \rho/\mu m_p$ is the particle number density and we have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}; Fig.
 34.1).
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3\rho kT/2\mu m_p)/\dot{q}_{\rm cool}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
+To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm cool}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
 \begin{align}
@@
 
-Thermal stability ($0.5 q \vw^2/|\dot{q}_{\rm cool}| > 1$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
+Thermal stability ($\dot{q}_{\rm heat} > \dot{q}_{\rm cool}$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
 \begin{align}
@@
 \end{align}
-Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
-The inclusion of $\sigma$ in equation (\ref{eq:cooling2}) results because the top two lines apply only for $\tilde{v}_{w} > \sigma$ since their derivation assumed the existence of a stagnation radius given by equation (\ref{eq:rs_simple}).
+Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
+The requirement that $v_{\rm w} \gtrsim \sigma$ in equation (\ref{eq:cooling2}) results because the top two lines are derived under the assumption that the stagnation radius is given by equation (\ref{eq:rs_simple}).
+When $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to larger radii than predicted by by equation (\ref{eq:rs_simple}) or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
 

### 2015-01-26 ms.tex
random3

@@
 \begin{eqnarray}
-  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
+  \dot{M} &=& \frac{\eta \Menc|_{r_{\rm s}}}{\th} \nonumber \\
 &\approx&
@@
 The gas density at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate accurately.
-Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$ in conjuction with equation (\ref{eq:mdot_analytic}), one finds
-\begin{align}
-  &\dot{M}\sim\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff(\rs)},
+Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}|_{r_{\rm s}} = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$ in conjuction with equation (\ref{eq:mdot_analytic}), one finds
+\begin{align}
+  &\dot{M}\sim\frac{(4 \pi/3) \rs^3 \rho|_{r_{\rm s}}}{\tff|_{r_{\rm s}}},
   \label{eq:mdot_gas}
@@
 \begin{align}
-  \rho(\rs)\approx
+  \rho|_{r_{\rm s}}\approx
   \begin{cases}
@@
 %\begin{align}
-%\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
+%\rho|_{r_{\rm s}}=\frac{3 q|_{r_{\rm s}} \tff|_{r_{\rm s}}}{2-\Gamma}.
 %\label{eq:rhors2}
@@
 where $r_b \equiv GM/c_{s}^{2}$ is the Bondi radius, $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
-By rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho(\rs) v_{\rm ff}(\rs)/3$,
+By rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho|_{r_{\rm s}} v_{\rm ff}|_{r_{\rm s}}/3$,
 one notices a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $\rb$ is replaced by $\rs$.
@@
 \begin{align}
-\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
+\rho|_{r_{\rm s}}=\frac{3 q|_{r_{\rm s}} \tff|_{r_{\rm s}}}{2-\Gamma}.
 \label{eq:rhors2}
@@
 \end{align}
-Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius.
+Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
 The requirement that $v_{\rm w} \gtrsim \sigma$ in equation (\ref{eq:cooling2}) results because the top two lines are derived under the assumption that the stagnation radius is given by equation (\ref{eq:rs_simple}).
@@
   \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate
-    ($C$) for each of our solutions (solid lines). The cooling rate is
-    calculated using the approximate (solar metallicity) cooling
-    function in Equation~(\ref{eq:cooling}). The heating rate is
-    estimated as $q \vw^2/2+q v^2/2$. The ratio is computed from
-    equation (\ref{eq:cooling}) assuming a stellar mass loss rate
-    parameter $\eta=0.02$. We also plot the ratio $\tcool/\tff$
-    vs. radius. $H/C$ is a diagnostic for global thermal stability,
-    and a solution should be stable as long as
-    $H/C\gsim1$. $\tcool/\tff$ is a diagnostic for local thermal
-    instability, solutions should be stable as long as $\tcool/t_{\rm
-      ff}\gsim$10 \citealt{McCourt+12}. Notice that for high $\vwO$
-    the two ratios coincide at $\rs$ (marked with a square for each
-    solution).}
+  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/\dot{q}_{\rm cool}$, as a function of radius for each of our solutions (solid lines).
+Shown for comparison with dashed lines is the ratio of the cooling to the local free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
+For high heating rates both ratios are approximately equal at the stagnation radius (marked with a square for each solution).
+When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and $t_{\rm cool}/t_{\rm ff} \lesssim 10$ the flow will be susceptible to global and local thermal instability, respectively (e.g.,  \citealt{McCourt+12}).
+{\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
 \end{figure}
@@
 \begin{minipage}{18cm}
-\caption{}
+\caption{Summary of Numerical Solutions}
 \begin{tabular}{lccccccccccccc}
 \hline
-{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
+{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
 \hline
-0.01 & 300.0 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+0.01 & 300 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
 unresolved \\
-0.01 & 600.0 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+0.01 & 600 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
 10^{ 2 }$ &  rb in fact unresolved\\
-0.01 & 1200.0 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+0.01 & 1200 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
 10^{ 4 }$ &  rb in fact unresolved\\
-0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
+0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
 cons on outer grid \\
-0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
-0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
+0.1 & 1200 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
 10^{ 3 }$ &  energy cons on inner grid\\
-1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+1 & 300 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
   -2 }$ &  TI\\
-1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
-1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+1 & 600 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
+1 & 1200 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
   3 }$ &  \\
-1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
-1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+1 & 300 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
+1 & 300 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
   -2 }$ &  TI/convergence \\
@@
 %  -3 }$ &  TI/convergence\\
-1 & 300.0 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
-0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
-0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
+1 & 300 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
+0.1 & 300 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
+0.1 & 300 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
 %0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
 %10^{ -2 }$   & TI/convergence  \\
-0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
+0.1 & 300 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
 10^{ -2 }$ & TI/convergence \\
-0.01 & 1200.0 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
+0.01 & 1200 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
 10^{ 4 }$ &  rb is unsresolved\\
-0.1 & 1200.0 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
+0.1 & 1200 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
   3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
-1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
-1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{
+1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
+1 & 1200 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{
   2 }$ &  \\
-0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
-0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
-1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
-1 & 1200.0 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
-1 & 1200.0 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
+0.01 & 1200 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
+0.1 & 1200& 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
+1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
+1 & 1200 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
+1 & 1200 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
 %1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
-1 & 1200.0 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
-
+1 & 1200 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
 \hline
@@
 \end{tabular}
+$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.
 \end{minipage}
@@
 density increases towards the SMBH $\rho\propto r^{-n}$ with
-$n\simeq1$.  Note that this is shallower than the $-3/2$ power law for
-Bondi accretion. However, the power law behavior does not extend
-through all radii, and the gas density profile has a break coincident
+$n\simeq1$, i.e. shallower than the $-3/2$ power law for
+Bondi accretion. This power law behavior does not extend
+through all radii, however, as the gas density profile has a break coincident
 with the location of the break in the stellar light profile ($\rb=100$
@@
 increases as $\propto 1/r^{k}$ interior to the sphere of influence,
-where $k$ is smaller than 1--the power expected for virialized gas.
-The inwardly directed velocity increases towards the hole approaching
-The inwardly directed velocity is steeper than what would be expected
-for the free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
+where $k$ is smaller than 1--the power expected for virialized gas within the black hole sphere of influence.
+The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
 % {\bf BDM: I made this up - in general we need
@@
 
-Figure~\ref{fig:stag} (top panel) shows numerical results for the
-stagnation radius $r_{\rm s}$ where the radial velocity goes to zero
-(expressed in ratio to the radius of the SMBH sphere of influence
-$r_{\rm soi}$), with different colors representing different values of
-$v_{w}$.  Cusp and core galaxies are marked with square and
-triangles, respectively.
-
-We also show the simplified analytic result corresponding to $\rs$
-approximated from \eqref{eq:stag_simple} as a solid black line. For
-$\vwO$, we find good agreement with the analytic prediction. However,
-\eqref{eq:stag_simple} is only valid that $\Mstar(\rs) \ll \Mbh$, and
+The top panel of Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$, with different colors showing different values of $v_{w}$.
+Cusp and core galaxies are marked with square and triangles, respectively.
+Shown for comparison as a solid black line is the simplified analytic approximation for $r_{\rm s}$ from \eqref{eq:stag_simple}.
+For high $\vwO$ the analytic prediction agrees well with our numerical results.
+However, \eqref{eq:stag_simple} is only valid that $\Mstar|_{r_{\rm s}} \ll \Mbh$, and
 this approximation breaks down for small $\vwO$. In fact, $\rs$
@@
   \begin{align}
-    \lrs\simeq\lambdars \sigma(\rs)^2 \rs^2
+    \lrs\simeq\lambdars \sigma|_{r_{\rm s}}^2 \rs^2
   \end{align}
@@
   \begin{align}
-    \rcirc&\simeq\lambdars^2 \frac{\sigma(\rs)^2}{G \Mbh} \rs^2\\
+    \rcirc&\simeq\lambdars^2 \frac{\sigma|_{r_{\rm s}}^2}{G \Mbh} \rs^2\\
     &\simeq\lambdars^2 \frac{\rs^2}{\rsoi} \lsim \lambdars^2 \rsoi

### 2015-01-26 ms.tex
random3

@@
 \end{align} The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq
-\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$
+\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon_{\rm Ia}$
 with which the initial blast wave energy is converted into bulk or turbulent

### 2015-01-27 ms.tex
append

@@
 \begin{align}
-v_{w} > v_{\rm crit} \simeq
+v_{w} > v_{\rm CI} \simeq
   {\rm max}\begin{cases}
@@
 \end{align}
-Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm crit} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
+Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
 The requirement that $v_{\rm w} \gtrsim \sigma$ in equation (\ref{eq:cooling2}) results because the top two lines are derived under the assumption that the stagnation radius is given by equation (\ref{eq:rs_simple}).
@@
 that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
-the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  We hereafter adopt $\epsilon_{\rm Ia} = 0.4$.
+the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  Hereafter we adopt $\epsilon_{\rm Ia} = 0.4$ as fiducial.
 
@@
   \end{align}
-as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
+as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm Ia})^{-1} \sim G/(r\sigma^{2}R_{\rm Ia})$ exceeds the local dynamical timescale $t_{\rm
 dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship
@@
 
-Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting $v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into our expression for the stagnation radius (\ref{eq:rs_simple}), we can write
+Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting $v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:rs_simple}) for the stagnation radius, we find that
 \begin{eqnarray}
@@
 &\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
+\label{eq:rIars}
 \end{eqnarray}
-The fact that $r_{\rm Ia} \gg r_{\rm s}$ would appear to imply that Ia heating only represents a sources of steady heating near the stagnation radius for very massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ and/or very young populations ($\tau_{\star} \ll t_{\rm h}$).
-However, this expression underestimates the importance of Ia heating, since the actual stagnation radius will be substantially larger than its value for $v_{w}^{\rm Ia}$ if the nominal heating rate is much less than this.
-In general it is reasonable to expect that the impact of Ia SN will increase for larger SMBH masses.
+The fact that $r_{\rm Ia} \gg r_{\rm s}$ appears to imply that Ia heating can only be approximated as a steady heating source near the stagnation radius for extremely massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ or very young populations ($\tau_{\star} \ll t_{\rm h}$).
+However, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the nominal heating rate (without Ia contribution) is much less than this.
+Nevertheless, the impact of Ia SN is clearly greater for larger SMBH masses for which $r_{\rm Ia} \lesssim r_{\rm s}$.
 
 What is the effect of the Ia radius?
-Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \approx M_{\rm g}\sigma^{2}$.
+Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.
 Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
 Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Hence, even if $r_{\rm s} > r_{\rm Ia}$, the accretion rate will be limited to a value set by substituting $r_{\rm Ia}$ for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.
+Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the SMBH accretion rate is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.
 \begin{eqnarray}
@@
    & \text{core} \\
-    1.5 \times 10^{-4} \Mbheight^{-0.77}(\tau_{\star}/t_{\rm h})^{-0.7}   & \text{cusp}, 
+    1.5 \times 10^{-4} \Mbheight^{-0.77}(\tau_{\star}/t_{\rm h})^{-0.7}   & \text{cusp}.
   \end{cases}
@@
 \end{eqnarray}
+{\bf BDM: check!}
 
@@
 luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
-volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon$ results in an
+volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
 effective heating rate (eq.~ [\ref{eq:vw_eff}])
-
 \begin{eqnarray} v_{w}^{\rm MSP} \approx
-30\left(\frac{\epsilon}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
+30\left(\frac{\epsilon_{\rm msp}}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
 sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \eta_{0.02}^{-1/2}\,{\rm
@@
   \end{eqnarray} 
-
-where $\epsilon$ is the thermalization efficiency of
+where $\epsilon_{\rm msp}$ is the thermalization efficiency of
 the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based
@@
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the optimistc assumption $\epsilon = 1$.  On the other hand, the
+under the optimistc assumption $\epsilon_{\rm msp} = 1$.  On the other hand, the
 binaries giving rise to MSPs may be disocciated by stellar
@@
 
-Feedback from accretion onto the SMBH represents an important source of heating which is, however, the most difficult to quantify.
-A key difference between AGN heating and other sources discussed thus far is its likely dependence on the mass accretion rate $\dot{M}$, which is itself a function of the heating rate (eq.~[\ref{eq:mdot_analytic}]).
+Feedback from accretion onto the SMBH represents an important source of heating which, however, is also the most difficult to quantify.
+A key difference between AGN heating and the other sources discussed thus far is its dependence on the SMBH accretion rate $\dot{M}$, which is itself a function of the heating rate (eq.~[\ref{eq:mdot_analytic}]).
 
 There are two types of SMBH feedback: kinetic and radiative.
-Radiative feedback is potentially effective even in low luminosity AGN via Compton heating (e.g.,~\citealt{Gan+14}), which provides a volumetric heating rate (\citealt{Gan+14})
+Radiative feedback is potentially effective even in low luminosity AGN via Compton heating, which provides a volumetric heating rate (\citealt{Gan+14})
 \be
@@
 \ee
-where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$.
+where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$ (\citealt{Gan+14}).
 
@@
   the Compton heating will depend on radius--I use rs in my own
-  estimate. }
-We estimate the importance of Compton heating by assuming the SMBH
-radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
-$\epsilon$ is the radiative efficiency and where $\dot{M}$ is
+  estimate.  BDM: if so, the please update the numbers!  }
+The importance of Compton heating can be estimated by assuming the SMBH
+radiates with a luminosity $L = \epsilon_{\rm rad} \dot{M}c^{2}$, where
+$\epsilon_{\rm rad}$ is the radiative efficiency and where $\dot{M}$ is
 estimated from equation (\ref{eq:mdot_analytic}).  Then using
@@
 (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
-(\ref{eq:vw_eff}) that
+(\ref{eq:vw_eff}) that the effective Compton heating rate at the stagnation radius is given by
 \begin{align} v_{w}^{\rm C} \simeq
@@
 \end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
-\epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick
-accretion flow (e.g.~\citealt{Narayan&Yi95}).  Assuming that heating
-is dominated by Compton heating ($\tilde{v}_{w} = v_{w}^{C}$) one finds
-that
+\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency for a thick
+accretion flow (e.g.~\citealt{Narayan&Yi95}).  If heating
+were dominated by Compton heating, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
 \begin{align} v_{w}^{\rm C} \simeq
@@
   \label{eq:vC2}
-\end{align} Unless $\eta$ is very high, we conclude that Compton
-heating is insufficient to stabilize the steady flow against cooling
-instability (e.g. $v_{w}^{C} < v_{\rm critt}$;
-eq.~[\ref{eq:cooling2}]).
+\end{align} 
+The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for $\eta \lesssim 1$ shows that Compton heating alone is insufficient to stabilize the flow against cooling
+instability, i.e. $v_{w}^{C} < v_{\rm CI}$ (eq.~[\ref{eq:cooling2}]).
 
@@
 
-If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm crit}$), it may lead to thermal instabilities.
+If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
 There are two kinds of ``instabilities", global and local.

### 2015-01-27 windheat.tex
editing2
append

@@
 
-The energy and mass injection from stellar winds will be the sum ofthe
-contributions from main sequence and post-main sequence (PMS) stars.
-For an impulsively formed stellar population of age $t$, the mass
-injection rate per unit stellar mass,$\dot{\bar{m}}(t)$, and  the energy
-injection rate per unit stellar mass, $\dot{\bar{e}}(t)$,  will be given by
+\subsection{Single Burst}
 
+For a stellar population that forms impulsively of age $t$, the rate of mass and energy injection per unit stellar mass are given, respectively, by 
 \begin{align} 
-  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu(M_{\rm TO}(t))
+  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
     \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
         T}(t)}
-    \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar }{\bar{m}_*}\\
+    \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar }{\bar{m}_*}\\
   \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
-  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar}{\bar{m}_*}.
+  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
   \label{eq:edotImp}
 \end{align} 
+where the first and second terms in each expression corresponds to contributions from main sequence stars and post-main sequence (PMS) stars, respectively.
+Here $ f_{\rm MS} < 1$ is an efficiency, which accounts for the efficiency with which main sequence winds thermalize their energy with the rest of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$ is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean stellar mass.
+The turn-off mass $M_{\rm TO}$ at time $t$ is calculated according to the following functional fit
+\begin{align}
+\log(M_{\rm TO})/M_{\odot} =0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
+\end{align}
+where $x=\log(t/10^9 {\rm years})$, so designed to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9) for massive stars while asymptoting to the fitting formula provided by \citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late times ($t \gsim 10^8$ years).
 
-The first terms in each expression above correspond to the
-contributions from PMS stars, while the second terms correspond to the
-contributions from main sequence stars. The main sequence winds are a
-small fraction of the mass, and they may be not be thermalized and
-mixed with the rest of the injected gas. Thus, we include a
-thermalization efficiency, $ 0\le f_{\rm MS}\le 1$, in
-equation~\eqref{eq:edotImp}. Throughout this paper we set $f_{\rm
-  MS}=1$.
-
-We assume a Salpeter IMF $\mu(\Mstar)\sim M^{-2.35}$, truncated at $0.1
-\Msun$ on the low mass end and at $100 \Msun$ on the high mass
-end. The corresponding mean stellar mass, $\bar{m}_*$ is 0.35 $\Msun$.
-
-For the turnoff mass, $M_{\rm TO}$, we take the following fitting
-formula
-
-\begin{align}
-\log(M_{\rm TO})=0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
-\end{align}
-
-where $x=\log(t/10^9 {\rm years})$ and $M_{\rm TO}$ is in units
-$\Msun$. This fit is designed to reproduce the results in 
-Table 9 of \citet{MaederMeynet:1987a} and then asymptotes to the fit
-for $M_{\rm TO}$ given in equation (9) of \citet{CiottiOstriker:2007a}
-for intermediate and late times ($t \gsim 10^8$ years).
-
-For $\Delta M(t)$ we use equation (10) from \citet{CiottiOstriker:2007a}
-
+The mass lost in PMS winds $\Delta M(t)$ is calculating from \citet{CiottiOstriker:2007a} (their eq.~[10]) according to
 \begin{align}
@@
 \end{align}
-
-To estimate the mass loss from main sequence stars
-$\dot{m}(\Mstar, t)$,
-we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This
-  prescription is a generalization of the Reimers' mass loss law. This
-expression is derived assuming the stellar wind results from the
-turbulent overflow of moaterial in the chromosphere or underneath it.} {\bf AG:
-  unfortunately this is not really meant for MS stars...}
-
+The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]):
 \begin{align}
@@
 \end{align}
-
 where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
-luminosity, effective and surface gravity respectively. $g_{\odot}$ is
-the stellar surface gravity. To calculate $R_*$ and $L_*$ we use the
-following scaling relations (taken from Kippenhann and Weygert Figures
-22.2 and 22.3).
-
+luminosity, effective temperature, and surface gravity, respectively, the latter normalized to its stellar value $g_{\odot}$.  The stellar radius and luminosity are estimated as 
 \begin{align}
@@
 \end{align}
-
 \begin{align}
-r_*=
+R_*=
 \begin{cases}
@@
 \end{align}
+based on \citealt{Kippenhahn&Weigert} (their Figs.~22.2, 22.3)
 
@@
 \end{align}
+while {\bf BDM: insert correct expression}
+\begin{align}
+\eta = \dot{\bar{m}}(t)
+\label{eq:vwImp}
+\end{align}
 
@@
 \end{figure}
+
+\subsection{Over Star Formation History}
 

### 2015-01-27 windheat.tex
appendix

@@
 
-For a stellar population that forms impulsively of age $t$, the rate of mass and energy injection per unit stellar mass are given, respectively, by 
+For a stellar population that forms impulsively, the rate of mass and energy injection per unit stellar mass at age $t$ are given, respectively, by 
 \begin{align} 
@@
 \end{align} 
-where the first and second terms in each expression corresponds to contributions from main sequence stars and post-main sequence (PMS) stars, respectively.
-Here $ f_{\rm MS} < 1$ is an efficiency, which accounts for the efficiency with which main sequence winds thermalize their energy with the rest of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$ is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean stellar mass.
-The turn-off mass $M_{\rm TO}$ at time $t$ is calculated according to the following functional fit
-\begin{align}
-\log(M_{\rm TO})/M_{\odot} =0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
-\end{align}
-where $x=\log(t/10^9 {\rm years})$, so designed to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9) for massive stars while asymptoting to the fitting formula provided by \citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late times ($t \gsim 10^8$ years).
+where the first and second terms in each expression corresponds to contributions from main sequence (MS) stars and post-main sequence (PMS) stars, respectively.
+Here $ f_{\rm MS} < 1$ is the efficiency with which main sequence winds thermalize their energy with the rest of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$ is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean stellar mass.
 
-The mass lost in PMS winds $\Delta M(t)$ is calculating from \citet{CiottiOstriker:2007a} (their eq.~[10]) according to
+The quantity of mass lost in PMS winds $\Delta M(t)$ is estimated from the expression given by \citet{CiottiOstriker:2007a} (their eq.~[10]),
 \begin{align}
@@
 0.945 M_{\rm TO}-0.503 & M_{\rm TO} < 9 \Msun\\
- M_{\rm TO}-1.4 \Msun &  M_{\rm TO} \ge 9 \Msun
+ M_{\rm TO}-1.4 \Msun &  M_{\rm TO} \ge 9 \Msun,
 \end{cases}
 \end{align}
-The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]):
+where $M_{\rm TO}$ is the turn-off mass, which at time $t$ is calculated as
 \begin{align}
-  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* r_*}{\Mstar}
+\log(M_{\rm TO})/M_{\odot} =0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
+\end{align}
+where $x=\log(t/10^9 {\rm years})$.
+This functional fit is designed to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9) for massive stars while asymptoting to the formula provided by \citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late times ($t \gsim 10^8$ years).
+
+The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]) as
+\begin{align}
+  \dot{m}=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
   \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
@@
 where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
-luminosity, effective temperature, and surface gravity, respectively, the latter normalized to its stellar value $g_{\odot}$.  The stellar radius and luminosity are estimated as 
+luminosity, effective temperature, and surface gravity, respectively, the latter normalized to its solar value $g_{\odot}$.
+The stellar radius and luminosity are estimated as (\citet{Kippenhahn&Weigert90}; Figs.~22.2) 22.3)
 \begin{align}
@@
 \end{align}
-based on \citealt{Kippenhahn&Weigert} (their Figs.~22.2, 22.3)
+The wind velocity of main sequence winds $v_w (\Mstar, t)$ is assumed to equal 430 km s$^{-1}$, corresponding to the escape speed of the Sun; this produces an effective wind heating velocity for main sequence winds alone of $XXX$, in agreement with the value of 150 km s$^{-1}$ found by \citet{NaimanSoares-Furtado+:2013a} based on a more sophisticated population synthesis treatment.
+{\bf BDM: true?
+correct}...{\bf AG:Current just use the value for the sun~430 km/s
+  replace with the real prescription we end up using.}
 
-To get a handle on $\dot{e}_{\rm TO}(t)$, we use the results from
-\citet{VossDiehl+:2009a} who use a population synthesis code to
-simulate the mass and energy injection into the ISM from an OB
-association. For the first $\sim 10$ Myr the energy injection will
-be dominated by fast Wolf-Rayet star winds. The energy injection rate
-per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
-stellar winds is plotted in the top panel of their Figure 7 and is
-well fit {\bf AG: A little more detail here...} by
-
+The rate of energy input from PMS winds, $\dot{e}_{\rm TO}(t) = f_{8}\dot{\mathcal{E}}/\bar{m}_*$, is dominated by fast Wolf-Rayet winds and core-collapse supernovae from massive stars ($M_{\star} > 8M_{\odot}$), where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the stellar mass with $M_{\star} > 8M_{\odot}$ for our assumed Salpeter IMF.
+Here $\dot{\mathcal{E}} (t)$ is the energy injection rate per massive star, which we estimate as
 \begin{align}
-\dot{\mathcal{E}} (t)=
+\dot{\mathcal{E}} (t)=  1.3 \times 10^{36} {\rm erg\,s^{-1}}
 \begin{cases}
-  1.3 \times 10^{36} {\rm ergs/s} & t<4 \times 10^6 {\rm years}\\
-  1.3  \times 10^{36} {\rm ergs/s} \left(\frac{t}{4 \times  10^6}\right)^{-3.73} & t \ge 4 \times 10^6 {\rm years}.
+  1 & t<4 \times 10^6 {\rm yr}\\
+  \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} & t \ge 4 \times 10^6 {\rm yr},
 \end{cases}
@@
 \end{align}
+based on the results of \citet{VossDiehl+:2009a} (their Fig.~7, top panel), who use a population synthesis code to simulate the mass and energy injection into the ISM from an OB association.
+Although equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr, in practice the precise functional form of $\dot{e}_{\rm TO}(t)$ is generally unimportant for our purposes, so we adopt equation~\eqref{eq:voss} as being valid for all times.
 
-Equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr. For $t\gsim
-10$ Myr, $\dot{e}_{\rm TO}$ will be negligible as lower mass stars
-shed their gas is slow dust-driven winds during their post-main
-sequence evolution {\bf AG-Nick is the preceding statement accurate},
-and for our purposes the exact functional form of $\dot{e}_{\rm
-  TO}(t)$ is unimportant. So we adopt Equation~\eqref{eq:voss} for all times.
-
- $\dot{e}_{\rm TO}(t)$ is related to $\dot{\mathcal{E}}$  via
-
-\begin{align}
-\dot{e}_{\rm TO}(t)=f_{8} \dot{\mathcal{E}} / \bar{m}_*,
-\label{eq:eto}
-\end{align}
-
-where $f_{8}$ is the fraction of the stellar population with $\Mstar>8
-\Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter IMF.
-
-We calculate the wind velocity for main sequence winds $v_w (\Mstar,
-t)$ using...{\bf AG:Current just use the value for the sun~430 km/s
-  replace with the real prescription we end up using.}
-
-The effective wind velocity in the impulsive limit may then be written
+The effective wind velocity in the limit of an impulsive star formation may then be written
 as 
-
 \begin{align}
@@
 \end{align}
-
-We plot $\bar{v}_w$ versus time in Figure~\ref{fig:vwImp}.
+We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and XXX.
 
@@
 \caption{\label{fig:vwImp} The effective $\vw$ from stellar winds from
-  a stellar population formed in a starburst $t$ years ago.}
+  a stellar population of age $t$.}
 \end{figure}
@@
 \subsection{Over Star Formation History}
-
-We can then use these integrated quantities to determine the effective
-$V_w$ for arbitrary star formation histories. For a stellar population
-with star formation rate $S(t)$
-
+Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
 \begin{align} 
@@
   \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
-      d}t_1\\
-  V_w^2(t) &=2 \dot{E}(t)/\dot{M}(t)
+      d}t_1,\\
+\end{align}
+resulting in an effective wind heating rate of
+\begin{align}
+  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t)
 \end{align}
@@
 
-We show $V_{\rm W}$ for different star formation histories in
-Fig. \ref{NickPlot2} {\bf AG: this plot still uses the old ad hoc vw
+We estimate the stellar wind heating provided by the {\it average} star formation history of galaxies of a given mass using the results of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]) and the $M_{\bullet}-M_{\rm
+  halo}$ relation from \citet{BandaraCrampton+:2009a}.
+Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.
+For comparison we also show cases in which the star formation rate is modulated sinuisoidally from its average value.
+It seems that ``bumpy'' SF histories severely diminish $v_{\rm w}$ if the timescale for SF variability is a factor of a few or more greater than the duration of high-velocity winds (either 10 or 40 Myr).
+{\bf AG: this plot still uses the old ad hoc vw
   prescription? If so it would need to be fixed. In any case, we still
-  differ in detail on the vw from stars}.  In particular, we use
-Eqs. 17-20 from \citet{MosterNaab+:2013a} and the $M_{\rm BH}-M_{\rm
-  halo}$ relation from \citet{BandaraCrampton+:2009a} to define $S(t)$
-for particular galaxies.  It seems that ``bumpy'' SF histories
-severely diminish $V_{\rm w}$ if the timescale for SF variability is a
-factor of a few or more greater than the duration of high-velocity
-winds (either 10 or 40 Myr).
+  differ in detail on the vw from stars}.
 

### 2015-01-27 ms.tex
smbh heating

@@
 \end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
-\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency for a thick
-accretion flow (e.g.~\citealt{Narayan&Yi95}).  If heating
-were dominated by Compton heating, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
+\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency for an advective
+accretion flow expected to produce high $T_{\rm C}$ emission (e.g.~\citealt{Narayan&Yi95}).
+If heating is provided by Compton heating alone, i.e.
+$\tilde{v}_{w} = v_{w}^{C}$, then equation (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
 \begin{align} v_{w}^{\rm C} \simeq
@@
 \end{align} 
-The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for $\eta \lesssim 1$ shows that Compton heating alone is insufficient to stabilize the flow against cooling
+The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for physically realized values of $\eta \lesssim 1$ shows that Compton heating alone is insufficient to stabilize the flow against cooling
 instability, i.e. $v_{w}^{C} < v_{\rm CI}$ (eq.~[\ref{eq:cooling2}]).
 
-In contrast to radiative feedback, kinetic feedback occurs in the form
-of an mass outflow or jet from the viscinity of the black hole, which
-deposits its energy at much larger radii.  We assume that the total
-heating rate from the SMBH is $\epsilon_{\rm j} \dot{M}c^{2}$, where
-$\epsilon_{\rm j} < 1$ is an efficiency factor.  If this energy is
-deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm
-heat}$, then the local heating rate $e = \epsilon_{\rm
-j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind heating rate
-of
+Kinetic feedback occurs from an outflow of mass or energy  from the viscinity of the black hole in the form of a disk wind or jet, which deposits its energy across a much wider range of radii.
+If the total outflow power is proportional to the SMBH accretion rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
+Assuming that this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$, then the volumetric heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind velocity at the stagnation radius given by
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
@@
 j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
-&\approx& c\epsilon_{\rm j}^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
+&\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
 heat}}\right)^{1-\Gamma/2},
@@
 break radius (eq.~[\ref{eq:rhostar}]).  Thus for $r_{\rm heat} \sim
-r_{\rm s}$, even a small heating efficiency $\epsilon_{\rm j} \sim
-10^{-6}$ is sufficient for $v_{w}^{\bullet}$ to exceed other
-sources of non-accretion powered heating.  However, if the jet
-distributes its energy on much larger scales comparable to the galaxy
-$r_{\rm heat} \sim $ kpc $\sim 10^{3}r_{\rm s}$ then the heating rate
-would be much smaller.
-
-For a fixed heating radius $r_{\rm heat}$ we just see that $v_{\rm
-  w,0}^{\bullet} \propto r_{\rm s}^{\beta/2} \propto
-M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to
-$v_{w}$ to a negative power, where the last proportionality makes
-use of equation (\ref{eq:stag_simple}).  As in the case of Compton
-heating, SMBH kinetic heating, when dominant, may thus
-``self-regulate".  However, unlike in the case of local stellar wind
-heating, SMBH heating may not be thermally stable, since the central
-accretion rate does not respond instantaneously to a change in the
-thermodynamic properties of the gas on larger scales.  Also note that
-$v_{w}^{\bullet}$ is proportional to a positive power of SMBH
-mass $\propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies,
-respectively.  This is dependence may have important implications for
-the predicted dependence of X-ray luminosity on SMBH mass
-($\S\ref{sec:mdot}$).
+r_{\rm s}$, even a modest heating efficiency $\epsilon_{\rm j} \gtrsim
+10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other
+sources of non-accretion powered heating.
+However, if the jet distributes its energy on much larger scales comparable to the size of the galaxy, i.e.
+$r_{\rm heat} \gtrsim $ kpc $\gtrsim 10^{3}r_{\rm s}$ then the heating rate would be much less significant, even for an efficient jet ($\epsilon_{\rm j} \sim 1$).
+
+Also note that for a fixed $r_{\rm heat}$, the effective heating rate $v_{\rm  w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$ to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
+This shows that SMBH kinetic heating, if dominant, could thus `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
+Importantly, however, unlike in the case of local heating sources such as stellar winds, even a dominant SMBH heating may not allow for a thermally-stable steady flow because the central accretion rate does not respond instantaneously to changes in the
+thermodynamic properties of the gas on larger scale.
+We also note here that the kinetic heating rate is proportional to the SMBH mass to a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies, respectively.
+This dependence could have important implications for the dependence of the average nuclear X-ray luminosity of quiescent galaxies on the SMBH mass ($\S\ref{sec:mdot}$).
 

### 2015-01-27 ms.tex
more

@@
 heat}}\right)^{1-\Gamma/2},
+\label{eq:vjet}
 \end{eqnarray} where we have used the fact that $\dot{M} \approx \eta
@@
 
-The total heating rate $\vwO = \sqrt{v_{w}^{\star \, 2} + v_{\rm
-    w,0}^{\rm Ia \, 2} + v_{w}^{\rm p \, 2} + v_{\rm
-    w,0}^{\bullet \, 2}}$ has
-contributions from stellar winds, supernovae, pulsars, and SMBH
-feedback. %  Since pulsar heating appears unlikely to contribute
-% appreciably, and since SMBH heating is uncertain, we first focus on
-% heating from stellar winds and supernovae.
-
-Each of these heating sources will depend on the integrated star
-formation history. This in term will will vary systematically with
-galaxy mass and thus with $\Mbh$.  
-%Qualitatively smaller galaxies willhave recent star formation and
-% energetic winds from Wolf-Rayet stars will dominate the mass
-% budget--$\vwO\gsim 1000 $ km/s.  On the other hand for larger galaxies
-% will have older populations, and heating will be dominated by Ia
-% supernovae on large scales and SMBH feedback on small scales.
-We calculate the star formation history as a function of $\Mbh$ and
-the $\vwO$ for each heating source using the cosmic star formation
-histories in \citet{MosterNaab+:2013a}.  For $v_{w}^{\rm p}$ we
-use equation~\eqref{eq:vmsp}. The star formation history simply enters
-in through $\eta$. The effective $\eta$ for a given star formation
-history will be the convolution of the star formation history with
-$\eta_{\rm imp}\simeq $ {\bf AG: should have expression for $\eta_{\rm
-    Imp}$ in appendix. Have to be careful as we also have the
-  simplified expression for $\eta_{\rm Imp}$} ($\eta$ in the impulsive
-limit). For $v_{w}^{\rm Ia}$ we use
-equation~\eqref{eq:vIa}. Besides $\eta$ there is additional dependence
-on the star formation history from the Ia rate--which is a convolution
-of the star formation history with the delay-time distribution from
-\citet{MaozMannucci+:2012a}. The calculation of $v_{w}^{\star}$
-is somewhat involved: we leave the detailed description for
-Appendix~\ref{app:windheat}. {\bf AG: still need a description of the
-  Compton heating. In general, I struggled with the level of detail
-  here. I couldn't think of a natural place to put the details for the
-  other heating sources}
-
-$\vwO$ from each heating source (stars, MSPs, SNe Ia, and black hole
-feedback) is plotted in as a function of $\Mbh$ in
-Figure~\ref{fig:vwSources}. $v_{w}^{\rm p}$ is negligible across
-all $\Mbh$. For $\Mbh\lsim 10^{7.5} \Msun$, have substantial recent
-star formation and $v_{w}^{\star}$ is dominant. For $\Mbh\gsim
-10^{7.5} \Msun$ , the younger stellar population with their energetic
+The total gas heating rate $\vwO$ includes contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
+The strength of each heating source will depend on the SMBH mass and the star formation history in the galactic nuclear region, the latter of which will vary systematically with the galaxy mass and hence with $\Mbh$.
+Qualitatively, smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.
+Larger galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
+
+The average star formation history as a function of $\Mbh$ and the $\vwO$ for each heating source is estimated by using the average cosmic star formation histories determined by \citet{MosterNaab+:2013a}.
+As described in detail in Appendix \ref{app:windheat}, the average star formation history is used to estimate the stellar wind heating $v_{\rm w}^{\star}$ and the mass input parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]), the latter of which also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}])
+
+Figure~\ref{fig:vwSources} shows $\vwO$ from each heating source (stars, MSPs, SNe Ia, and black hole
+feedback) as a function of black hole mass.
+MSP heating is found to be negligible at all black hole masses.
+The young stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$ results in $v_{w}^{\star}$ being dominant.
+For $\Mbh\gsim 10^{7.5} \Msun$ , the younger stellar population with their energetic
 stellar winds is dead, and Compton heating plays an important role.
-
-For reference we also plot the inferred $\eta$ for each $\Mbh$ in
-Figure~\ref{fig:eta}
 
@@
 \includegraphics[width=\columnwidth]{eta.pdf}
-\caption{\label{fig:eta} $\eta$ vs. $\Mbh$.}
+\caption{\label{fig:eta} Parameter characterizing stellar mass loss $\eta$ (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories corresponding to galaxies with halo masses corresponding to $\Mbh$ according to the results of \citet{MosterNaab+:2013a}.
+}
 \end{figure}

### 2015-01-27 ms.tex
more

@@
 \includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} $\vwO$ for stellar winds ({\it solid
-    blue}), SNe Ia ({\it dashed red}), MSPs ({\it solid orange}), as a
-  function of $\Mbh$. Each heating source varies with the star
-  formation history, which is a function of $\Mbh$--see
-  appendix~\ref{app:windheat} for the detailed description of how we
-  calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
-  resulting from stellar winds, MSPs, and black hole feedback ({\it
-    solid black}). The heating will have a weak dependence on the
-  stellar density power law slope, $\Gamma$, since $v_{w}^{\bullet \,
-    2}$ depends on $\Gamma$. The solid black curve corresponds to
-  $\Gamma=0.8$ and the dash-dotted black curve corresponds to
-  $\Gamma=0.1$. Finally the vertical dashed black line marks the value
-  critical value of $\Mbh$, $M_{\rm bh, crit}$, such that... }
+\caption{\label{fig:vwSources} Sources contributing to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it solid blue}), Ia supernovae ({\it dashed red}), millisecond pulsars ({\it solid orange}).
+Each heating source varies with black hole mass $\Mbh$ due to the different average star formation history of galaxies of a given halo mass (see Appendix~\ref{app:windheat} for the detailed description).
+We assume a stellar density power law slope of $\Gamma = 0.8$ in calculating $v_{w}^{\bullet \, 2}$ although the dependence on $\Gamma$ is weak {\bf BDM: just pick a value of Gamma!}.
+The Ia heating rate is shown as a solid above the critical black hole mass for which $r_{\rm Ia} < r_{\rm s}$ (Fig.~\ref{fig:rs_rIa}), since this represents the condition for SN Ia to be well-approximated a continuously heating source.
+}
 \end{figure}
@@
 \includegraphics[width=\columnwidth]{eta.pdf}
-\caption{\label{fig:eta} Parameter characterizing stellar mass loss $\eta$ (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories corresponding to galaxies with halo masses corresponding to $\Mbh$ according to the results of \citet{MosterNaab+:2013a}.
+\caption{\label{fig:eta} Parameter  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories from \citet{MosterNaab+:2013a} for galaxies with halo masses corresponding to $\Mbh$.
 }

### 2015-01-27 ms.tex
more

@@
 Depending on the model, we
-consider four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
+consider up to four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
 and 400 pc, a range motivated by the observed break radii in
@@
 To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
-Although we give the mass return rate per unit volume, our expressions are equivalent.}, although we will show later that $\eta$ can be higher if star formation is ongoing (Fig.~\ref{fig:eta}).
+Although we give the mass return rate per unit volume, our expressions are equivalent.}, although we will show later that $\eta$ can be significantly higher if star formation is ongoing (Fig.~\ref{fig:eta}).
 
@@
 of stars with respect to one another at the characteristic velocity
-$\sim \sigma = \sqrt{GM_{\rm enc}/r}$.  This heating is present even for the low
-wind velocities $\ll \sigma$ that characterize AGB mass loss in old
-stellar populations.  The second term, $v_{w}^{2}$, parameterizes
+$\sim \sigma \approx \sqrt{GM_{\rm enc}/r}$.
+This heating is present even in old stellar populations for which mass and energy injection are dominated by AGB winds with low velocities $\ll \sigma$.
+The second term, $v_{w}^{2}$, parameterizes
 the contribution of additional sources of heating, such as faster main
@@
 dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
-field perpendicular to the flow could in principle suppress the
+field oriented perpendicular to the flow could in principle suppress the
 conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
@@
 
-Our analytic results above neglect the effects of heat conduction near the stagnation radius, an assumption we now check.
-The ratio of the magnitude of conductive heating to the nominal level of ``wind" heating is given by
+Our analytic results neglect the effects of heat conduction, an assumption we now check.
+The ratio of the magnitude of the conductive heating rate to the nominal level of wind heating at the stagnation radius is given by
 \begin{align}

### 2015-01-27 ms.tex
more

@@
 \subsection{Stellar winds}
-{\bf AG: This section may have to be substantially modified in light
-  of our more careful analysis of stellar winds.}
-
-Although most of the mass supplied to the CNM by stellar winds occurs
-during the giant AGB phase, these winds represent a negligible heating
-source compared to the random wind velocity because the wind velocity
-$\lesssim 40$ km s$^{-1}$ is much less than the stellar potential
-$\sigma$.
-
-Main sequence winds, though contributing a much smaller quantity of
-mass, have much higher velocities and hence contribute a
-disproportionally large share of the kinetic energy of winds.
-\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{w} \sim
-100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
-stellar population.  On the other hand, for a very young stellar
-population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
-heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
-s$^{-1}$.  In Appendix \ref{app:windheat} we present a model for
-how $v_{w}$ varies as a function of stellar age.
+
+Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence stars.
+At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars, while at later times energy input is dominated by main sequence winds.
+Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages mass input is dominated by the slow AGB winds of low mass stars.
+
+Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
+At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating is much lower, $v_{\rm w} \sim 50 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).
+As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
+Thus stellar winds contribute a potentialy important source of energy as well as mass for the CNM.
 

### 2015-01-27 windheat.tex
Incorporating impulsive eta figure into appendix
more

@@
 \end{align}
-We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and XXX.
+We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and~\ref{fig:etaImp}.
 
@@
 \includegraphics[width=\columnwidth]{vwImp.pdf}
-\caption{\label{fig:vwImp} The effective $\vw$ from stellar winds from
-  a stellar population of age $t$.}
+\caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
+  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{etaImp.pdf}
+\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
+  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
 \end{figure}

### 2015-01-28 ms.tex
more

@@
 Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
-At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating is much lower, $v_{\rm w} \sim 50 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).
+At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v_{\rm w} \sim 50-100 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).
 As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
@@
 
-\subsection{Combined Heating Rate}
+\subsection{Combined Heating Rate for Representative Star Formation History}
 
@@
 
-For each $\Mbh$ we may check whether the solution for corresponding
-$\vwO$ and $\eta$ would be thermally stable, using
-equation~\eqref{eq:cooling2} {\bf: AG--double check that this is
-  equivalent to what I did.}
-
-The combined heating rate from stellar winds and Compton heating is
-insufficient to prevent thermal instability for the high $\Mbh$.  This
-is shown in Figure~\ref{fig:cooling2}, which shows the heating over
-cooling rate at $\rs$ as a function of $\Mbh$. For $\Mbh\gsim 10^8
-\Msun$, the cooling rate will exceed the cooling rate at $\rs$ and
-and the gas would be thermally unstable.
+Figure~\ref{fig:cooling2} shows the ratio of heating to radiative cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total heating rate from Figure \ref{fig:vWsources}.
+The combined heating rate from stellar winds and Compton heating is insufficient to prevent thermal instability for the high $\Mbh$.
+However, if Ia supernovae are included in the schematic way described above, the flow again becomes thermally stable for $\Mbh \gtrsim XXXX$.
+
+%Although, in principle the Ia contribution to the heating is
+%substantial, in practice Ia's occur too infrequently to be a steady
+%contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
+%r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
+%by itself would not be able to prevent cooling instability.
 
@@
 \end{figure}
-
-Although, in principle the Ia contribution to the heating is
-substantial, in practice Ia's occur too infrequently to be a steady
-contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
-r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
-by itself would not be able to prevent cooling instability.
 
@@
 % stars.
-{\bf AG: We should mention that regime with stellar wind heating only
-  is likely to be thermally unstable.}
 

### 2015-01-29 ms.tex
Minor adjustmments to equations and table.

--- 2015-01-27 ms.tex
@@
 0.1 & 1200 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
-10^{ 3 }$ &  energy cons on inner grid\\
+10^{ 3 }$ &  \\
 1 & 300 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
@@
   3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
-1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
-1 & 1200 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{
-  2 }$ &  \\
 0.01 & 1200 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
@@
  && \begin{cases}
-    3 \times 10^{-4} M_{\bullet,8}^{-1.26}(\tau_{\star}/t_{\rm h})^{-0.3}
+    4.5 \times 10^{-4} M_{\bullet,8}^{-1.33}(\tau_{\star}/t_{\rm h})^{1.1}
    & \text{core} \\
-    1.5 \times 10^{-4} \Mbheight^{-0.77}(\tau_{\star}/t_{\rm h})^{-0.7}   & \text{cusp}.
+    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{0.7}   & \text{cusp}.
   \end{cases}
@@
 \end{eqnarray}
-{\bf BDM: check!}
+{\bf AG: Fixed this expression. I will check again! Ia accretion rate should
+  increase with time, as in the burst limit the Ia rate would decline
+  with time, so the Ia radius would move outwards (need more volume to
+  get a supernova per dynamical time.}
 
@@
 
-{\bf AG: Note that I obtain Compton heating which is a factor of 2
-  higher--although power law dependences look right to me. Note that
-  the Compton heating will depend on radius--I use rs in my own
-  estimate.  BDM: if so, the please update the numbers!  }
+{\bf AG: Note that the Compton heating will depend on the distance of
+  the hole as $1/r^2$ so Compton heating will be stronger closer to the
+  black hole! }
 The importance of Compton heating can be estimated by assuming the SMBH
@@
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 13 \eta_{0.02}^{0.5}T_{\rm
+  \begin{cases} 29 \eta_{0.02}^{0.5}T_{\rm
 C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
-km\,s^{-1}} &, \text{core}\\ 20 \eta_{0.02}^{0.5}T_{\rm
+km\,s^{-1}} &, \text{core}\\ 50 \eta_{0.02}^{0.5}T_{\rm
 C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
@@
 \end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
-\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency for an advective
-accretion flow expected to produce high $T_{\rm C}$ emission (e.g.~\citealt{Narayan&Yi95}).
-If heating is provided by Compton heating alone, i.e.
-$\tilde{v}_{w} = v_{w}^{C}$, then equation (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
+\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency
+for an advective accretion flow expected to produce high $T_{\rm C}$
+emission (e.g.~\citealt{Narayan&Yi95}).  If heating is provided by
+Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
+(\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
 \begin{align} v_{w}^{\rm C} \simeq

### 2015-01-29 windheat.tex
Minor adjustmments to equations and table.

@@
 \end{align}
-where $x=\log(t/10^9 {\rm years})$.
-This functional fit is designed to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9) for massive stars while asymptoting to the formula provided by \citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late times ($t \gsim 10^8$ years).
+where $x=\log(t/10^9 {\rm years})$.  This functional fit is designed
+to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9)
+for massive stars while asymptoting to the formula provided by
+\citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late
+times ($t \gsim 10^8$ years). {\bf AG: Mathematical aside--this
+  expression divereges for t>>$t_{hubble}$}
 
@@
 \end{align}
-while {\bf BDM: insert correct expression}
+while {\bf AG: eta expression is now fixed--note that
+  $\dot{\bar{m}}(t)$ is the mass injection rate per stellar mass, so
+  that eta is dimensionless as it should be }
 \begin{align}
-\eta = \dot{\bar{m}}(t)
+\eta = \dot{\bar{m}}(t) \th
 \label{eq:vwImp}

### 2015-01-29 ms.tex
Some more modifications to the mdot_Ia expression.

@@
  && \begin{cases}
-    4.5 \times 10^{-4} M_{\bullet,8}^{-1.33}(\tau_{\star}/t_{\rm h})^{1.1}
+    4.5 \times 10^{-4} M_{\bullet,8}^{-1.33}(\tau_{\star}/t_{\rm h})^{-0.2}
    & \text{core} \\
-    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{0.7}   & \text{cusp}.
+    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{-0.6}   & \text{cusp}.
   \end{cases}
@@
 \end{eqnarray}
-{\bf AG: Fixed this expression. I will check again! Ia accretion rate should
-  increase with time, as in the burst limit the Ia rate would decline
-  with time, so the Ia radius would move outwards (need more volume to
-  get a supernova per dynamical time.}
+{\bf AG: Changed this expression somewhat from that of BDM (slightly
+  different scaling relations were used?). I will
+  check again! Note that the time dependence of eta~t$^{-1.3}$ is
+  folded in above.}
 

### 2015-01-30 ms.tex
figures. yay!

@@
 
-The top panel of Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$, with different colors showing different values of $v_{w}$.
-Cusp and core galaxies are marked with square and triangles, respectively.
-Shown for comparison as a solid black line is the simplified analytic approximation for $r_{\rm s}$ from \eqref{eq:stag_simple}.
-For high $\vwO$ the analytic prediction agrees well with our numerical results.
-However, \eqref{eq:stag_simple} is only valid that $\Mstar|_{r_{\rm s}} \ll \Mbh$, and
-this approximation breaks down for small $\vwO$. In fact, $\rs$
-diverges for smaller $\vwO$.
-
-{\bf AG perhaps it would be better to solve the implicit equation for
-  rs/rsoi, and plot this in the top panel--assuming a fixed n of say
-  1}. We may also compare our numerical results $r_{\rm s}/r_{\rm
+Figure~\ref{fig:stag} shows our results for the
+stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the
+SMBH sphere of influence $r_{\rm soi}$, with different colors showing
+different values of $v_{w}$.  Cusp and core galaxies are marked with
+square and triangles, respectively.
+
+ We may also compare our numerical results $r_{\rm s}/r_{\rm
   soi}$ an be compared directly to our analytic estimate in equation
-\ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag}
-shows the fractional difference between our numerical and analytic
-results for $r_{\rm s}/r_{\rm soi}$.  The good agreement provides a
-useful check of the numerical results.
-
+\ref{eq:stag_analytic}.  The solid and dashed black curves in  Figure
+\ref{fig:stag} show the analytic results for $r_{\rm s}/r_{\rm soi}$.
+The good agreement provides a useful check of the numerical
+results. Note that the analytic curves implicitly assume a density
+slope, $n$ at $\rs$, which we have fixed to be 1 (0.5) for the solid
+(dashed) curve. For small $\vw/\sigma$ this assumption breaks down.
+
+For $\vw/\sigma \gg 1$ the value $\rs/\rinf$ does not depend on break
+radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
+have an effect. Notice that near where the solid analytic curve
+diverges there are three green square, one over the other. These
+points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
+(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
+break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
 %% AG: Describe conservation checks to additionally validate the results.
@@
     respectively.  Squares correspond to cusp galaxies, while
-    triangles correspond to cores. \emph{Bottom panel}: Fractional
-    difference between our numerical calculation of $r_{\rm s}/r_{\rm
-      soi}$ and the analytic result in
-    equation~(\ref{eq:stag_analytic}). }
+    triangles correspond to cores. The black curves correspond to the
+    analytic prediction from Equation~\eqref{stag_analytic}. The solid
+    (dashed) curve is the correponds to $\Gamma=0.8$ and $n=1$
+    ($\Gamma=0.1$ and $n=0.5$.}
 \end{figure}
@@
 \includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} Sources contributing to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it solid blue}), Ia supernovae ({\it dashed red}), millisecond pulsars ({\it solid orange}).
-Each heating source varies with black hole mass $\Mbh$ due to the different average star formation history of galaxies of a given halo mass (see Appendix~\ref{app:windheat} for the detailed description).
-We assume a stellar density power law slope of $\Gamma = 0.8$ in calculating $v_{w}^{\bullet \, 2}$ although the dependence on $\Gamma$ is weak {\bf BDM: just pick a value of Gamma!}.
-The Ia heating rate is shown as a solid above the critical black hole mass for which $r_{\rm Ia} < r_{\rm s}$ (Fig.~\ref{fig:rs_rIa}), since this represents the condition for SN Ia to be well-approximated a continuously heating source.
-}
+\caption{\label{fig:vwSources} {\emph Top Panel:}Sources contributing
+  to the heating rate of the CNM, $\vwO$, including stellar wind
+  heating ({\it orange}), Ia supernovae ({\it green}), millisecond
+  pulsars ({\it blue}), and compton heating (\it pink).  Each heating
+  source varies with black hole mass $\Mbh$ due to the different
+  average star formation history of galaxies of a given halo mass (see
+  Appendix~\ref{app:windheat} for the detailed description). The total
+  heating rate is shown in black. To account for the non-steady nature
+  of the Ia heating we multiply the Ia heating by $e^{-\rs/\rIa}$, so
+  the contribution that the heating contribiution from Ia supernovae
+  will be suppressed if the time between successive supernovae is much
+  greater than the dynamical time at $\rs$. {\emph Bottom panel} The
+  ratio of the heating ($\dot{q}_{\rm heat}$) to the cooling rate
+  ($\dot{q}_{\rm cool}$) at $\rs$ from the total heating rate in the
+  top panel. Above $\Mbh\simeq 5\times 10^7 \Msun$ $\dot{q}_{\rm
+    heat}(\rs)<\dot{q}_{\rm cool}(\rs)$ and a thermal instability
+  would arise. The thermally unstable region is marked in red in the
+  bottom panel. All curves become dashed in the thermally unstable
+  region of parameter space: we expect our model to break down in this
+  regime as the steady-state assumption would be violated.}
 \end{figure}

### 2015-01-30 ms.tex
Fixing typo plus a particular table entry

@@
 10^{ 4 }$ &  rb in fact unresolved\\
-0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
-cons on outer grid \\
+0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & \\
 0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
@@
 
-For $\vw/\sigma \gg 1$ the value $\rs/\rinf$ does not depend on break
+For $\vw/\sigma \gg 1$ the value $\rs/\rsoi$ does not depend on break
 radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does

### 2015-02-02 ms.tex
Sketching some in the discussion section.

@@
 % 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
-% infrequent, in which case main sequence stars ($v_{w}^{\star}
+ infrequent, in which case main sequence stars ($v_{w}^{\star}
 % \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
@@
 
-Accretion rates onto SMBHs can in principle be estimated directly by assuming Bondi accretion and using high resolution X-ray observations to estimate the gas temperature and density near the Bondi radius.
-This technique has led to the intriguing conclusion that the Bondi accretion power correlates with the AGN jet power (e.g.,
+Accretion rates onto SMBHs can in principle be estimated directly by
+assuming Bondi accretion and using high resolution X-ray observations
+to estimate the gas temperature and density near the Bondi radius.
+This technique has led to the intriguing conclusion that the Bondi
+accretion power correlates with the AGN jet power (e.g.,
 \citealt{AllenDunn+:2006a}; \citealt{Russell+13};
@@
 required to inflate the observed cavities within the X-ray emitting
-gas.
-In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
+gas.  In practice is it almost never possible to resolve the Bondi
+radius, therefore requiring all such studies to extrapolate the
+observed gas temperature and density profiles to smaller radial
+scales.
+
+\subsection{Nuclear Star Clusters}
+Do nuclear star clusters in other galaxies look like scaled up/down
+versions of the one in our own galaxy? If so this would imply a radial
+gradient in the average of the stellar population which would imply a
+heating which would be dependent on radius.
+
+\subsection{SFR-AGN connection}
+In fact it seems like the star formation rate may trace AGN
+episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
 

### 2015-02-03 ms.tex
More points for the discussion.
Fixed syntax error causing compile issues. Minor changes in table.

@@
 \hline
-0.01 & 300 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+0.01 & 300 & 0.8 & U & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
 unresolved \\
-0.01 & 600 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
-10^{ 2 }$ &  rb in fact unresolved\\
-0.01 & 1200 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
-10^{ 4 }$ &  rb in fact unresolved\\
+0.01 & 600 & 0.8 & U & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+10^{ 2 }$ &  \\
+0.01 & 1200 & 0.8 & U & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+10^{ 4 }$ &  \\
 0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & \\
 0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
-0.1 & 1200 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+0.1 & 1200 & 0.8 & U & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
 10^{ 3 }$ &  \\
@@
 \end{tabular}
-$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.
+$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
+Break radius of stellar Nuker profile.  For profiles marked U, the
+break radius is not resolved on the grid.
 \end{minipage}
@@
 % 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
- infrequent, in which case main sequence stars ($v_{w}^{\star}
+% infrequent, in which case main sequence stars ($v_{w}^{\star}
 % \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
@@
 episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
+
+\subsection{Type II Supernovae}
+Type II supernovae should provide some heating as well for younger
+stellar populations...In fact at least on large scales they may be the
+dominant source of heating on timescales of 10-40 Myr.
 

### 2015-02-03 ms.tex
Added Xray luminosity discussion, SMBH sensitivity

--- 2015-01-30 ms.tex
@@
 
+\subsection{X-ray Diagnostics of SMBH Occupation}
+\label{sec:occ}
+The free-free emission from steady state gas flows in low mass galactic nuclei may serve as useful diagnostics of the presence or absence of a SMBH.
+We focus primarily on low-mass galaxies in this subsection, both because this is the portion of parameter space in which gas inflow will generally proceed in a steady-state fashion, and because of recent observations suggesting that a nontrivial fraction of these galaxies may lack nuclear SMBHs.
+If this absence is confirmed, it could have implications for galaxy evolution, SMBH recoil distributions, and SMBH seed formation models.
+
+Assuming that the stagnation radius is interior to the sphere of influence ($r_{\rm s} < r_{\rm soi}$), we can approximate the gas temperature as 
+\begin{equation}
+T \approx \frac{\mu m_{\rm p}}{2\gamma k_{\rm B}} \left(\tilde{v}_{\rm w}^2 + 2GM_\bullet/r \right).
+\end{equation}
+In the absence of a central SMBH, we can expect to see an exponential cutoff in the free-free X-ray spectrum at energies above
+\begin{equation}
+E_{\rm cut} = 0.78~{\rm keV}~\mu^{-1} v_{500}^2,
+\end{equation}
+assuming $\gamma = 5/3$.  This cutoff will therefore be located in the portion of the soft X-ray covered by {\it Chandra}'s ACIS spectrometer.  By writing the free-free emissivity as 
+\begin{equation}
+\varepsilon_{\nu}^{\rm ff} = 6.8\times10^{-39} \frac{\rm erg}{\rm s~cm^3~Hz} Z^2n_{\rm e}n_{\rm i}T^{-1/2}\bar{g}_{\rm ff}\exp\left(\frac{-h\nu}{k_{\rm B}T}\right),
+\end{equation}
+where $Z$ is the atomic number of the ions, $n_{\rm e}$ and $n_{\rm i}$ are respectively the electron and ion number density, and $\bar{g}_{\rm ff}$ is the Gaunt factor.
+In the following we set $n_{\rm e}=Y_{\rm e}n_{\rm i}$, and approximate
+\begin{equation}
+n_{\rm i} \approx \frac{\dot{M}}{4\pi r_{\rm s}^2 \mu m_{\rm p}}\sqrt{ \frac{r_{\rm s}}{GM_\bullet} } \left( \frac{r}{r_{\rm s}} \right)^{-n}.
+\end{equation}
+We now write the total spectral luminosity density seen in unresolved X-ray observations above the cutoff energy as 
+\begin{align}
+L_{\nu}^{\rm ff} =& \int_0^{r_{\rm s}} 4\pi r^2 \varepsilon_{\nu}^{\rm ff}{\rm d}r \\
+\approx & 3.42\times 10^{8} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm s}} \right)^2 \left(\frac{r_{\rm s}}{10^{-2}~{\rm pc}} \right)^{1/2} \left( \frac{M_\bullet}{10^6M_\odot} \right)^{-3/2}   \notag \\
+& \times \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \Gamma(7/2-2n) {\rm W/Hz} \notag \\
+\approx & 1.41 \times 10^9 \frac{\rm W}{\rm Hz} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm s}} \right)^2 \left(\frac{r_{\rm s}}{10^{-2}~{\rm pc}} \right)^{-1}  \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
+\end{align}
+The second line of this equation makes the approximation that $GM_\bullet/r$ dominates $\tilde{v}_{\rm w}^2$ throughout the integrand, which will be true for energies modestly higher than $E_{\rm cut}$.
+The lower (upper) endpoint for this integral are arbitrary so long as it is somewhat less (greater) than the radius at which the observed frequency $\nu$ sees its exponential free-free cutoff.
+The final line of this equation sets $n=1$.
+
+In general, these ``cut-off'' X-ray luminosities are quite small, and even {\it Chandra} would have little hope of detecting them in any but the nearest dwarf galaxies (e.g.
+the Magellanic clouds).
+However, if source confusion is not present, this technique could test for the presence of IMBHs in very nearby dwarf galaxies, or more speculatively Galactic star clusters.
+
 \section{Discussion}

### 2015-02-03 ms.tex

@@
 required to inflate the observed cavities within the X-ray emitting
-gas.
-In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
+gas.  In practice is it almost never possible to resolve the Bondi
+radius, therefore requiring all such studies to extrapolate the
+observed gas temperature and density profiles to smaller radial
+scales.
+
+\subsection{Nuclear Star Clusters}
+Do nuclear star clusters in other galaxies look like scaled up/down
+versions of the one in our own galaxy? If so this would imply a radial
+gradient in the average of the stellar population which would imply a
+heating which would be dependent on radius.
+
+\subsection{SFR-AGN connection}
+In fact it seems like the star formation rate may trace AGN
+episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
+
+\subsection{Type II Supernovae}
+Type II supernovae should provide some heating as well for younger
+stellar populations...In fact at least on large scales they may be the
+dominant source of heating on timescales of 10-40 Myr.
 

### 2015-02-03 windheat.tex

@@
 times ($t \gsim 10^8$ years). {\bf AG: Mathematical aside--this
-  expression divereges for t>>$t_{hubble}$}
+  expression divereges for $t \gg t_{\rm hubble}$}
 
@@
 \end{align}
-The wind velocity of main sequence winds $v_w (\Mstar, t)$ is assumed to equal 430 km s$^{-1}$, corresponding to the escape speed of the Sun; this produces an effective wind heating velocity for main sequence winds alone of $XXX$, in agreement with the value of 150 km s$^{-1}$ found by \citet{NaimanSoares-Furtado+:2013a} based on a more sophisticated population synthesis treatment.
-{\bf BDM: true?
-correct}...{\bf AG:Current just use the value for the sun~430 km/s
-  replace with the real prescription we end up using.}
+The wind velocity of main sequence winds $v_w (\Mstar, t)$ is assumed
+to equal 430 km s$^{-1}$, corresponding to the escape speed of the
+Sun; this produces an effective wind heating velocity for main
+sequence winds alone of $XXX$, in agreement with the value of 150 km
+s$^{-1}$ found by \citet{NaimanSoares-Furtado+:2013a} based on a more
+sophisticated population synthesis treatment. {\bf BDM: true?
+  correct}...{\bf AG: Wind velocity should depend on stellar
+  properties like escape speed. But choose normalization so that we
+  get the correct vw for the sun.}
 

### 2015-02-03 ms.tex
More small changes to the table.

--- 2015-02-03 ms.tex
@@
 10^{ -2 }$ & TI/convergence \\
-0.01 & 1200 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
-10^{ 4 }$ &  rb is unsresolved\\
-0.1 & 1200 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
+0.01 & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
+10^{ 4 }$ &  \\
+0.1 & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
   3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\

### 2015-02-04 ms.tex
More changes to the detection of black holes appendix...

--- 2015-02-03 ms.tex
@@
 
+\subsection{X-ray Diagnostics of SMBH Occupation}
+\label{sec:occ}
+The free-free emission from steady state gas flows in low mass
+galactic nuclei may serve as useful diagnostics of the presence or
+absence of a SMBH.  We focus primarily on low-mass galaxies in this
+subsection, both because this is the portion of parameter space in
+which gas inflow will generally proceed in a steady-state fashion, and
+because of recent observations suggesting that a nontrivial fraction
+of these galaxies may lack nuclear SMBHs.  If this absence is
+confirmed, it could have implications for galaxy evolution, SMBH
+recoil distributions, and SMBH seed formation models.
+
+We can approximate the gas temperature as
+
+\begin{equation}
+% T \approx \frac{\mu m_{\rm p} (\gamma-1)}{2\gamma k_{\rm B}}
+% \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r \right).
+ \kb T \approx 2.1\times 10^{-25} \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r
+ \right) {\rm [cgs]}.
+\end{equation}
+
+In the absence of a central SMBH, we can expect to see an exponential
+cutoff in the free-free X-ray spectrum at energies above
+
+\begin{equation}
+E_{\rm cut} = 0.32~{\rm keV} v_{500}^2,
+\end{equation}
+
+assuming $\gamma = 5/3$.  This cutoff will therefore be located in the
+portion of the soft X-ray covered by {\it Chandra}'s ACIS
+spectrometer.  By writing the free-free emissivity as
+
+\begin{equation} 
+\varepsilon_{\nu}^{\rm ff} = 6.8\times10^{-38}
+\frac{\rm erg}{\rm s~cm^3~Hz} Z^2n_{\rm e}n_{\rm
+i}T^{-1/2}\bar{g}_{\rm ff}\exp\left(\frac{-h\nu}{k_{\rm B}T}\right),
+\end{equation}
+
+where $Z$ is the atomic number of the ions, $n_{\rm e}$ and $n_{\rm
+  i}$ are respectively the electron and ion number density, and
+$\bar{g}_{\rm ff}$ is the Gaunt factor.  In the following we set
+$n_{\rm e}=Y_{\rm e}n_{\rm i}$, and approximate
+\begin{equation}
+n_{\rm i} \approx \frac{\dot{M}}{(4\pi/3) \rs^2 \mu \mp}\sqrt{ \frac{r_{\rm s}}{ 2 G \Mbh} } \left( \frac{r}{\rs} \right)^{-n}.
+\end{equation}
+
+We now write the total spectral luminosity density seen in unresolved
+X-ray observations above the cutoff energy as
+
+\begin{align}
+ L_{\nu}^{\rm ff} =& \int_0^{r_{\rm s}} 4\pi r^2 \varepsilon_{\nu}^{\rm ff}{\rm d}r \\
+\approx & 2.8\times 10^{16} \, {\rm ergs \, s^{-1}
+  \, Hz^{-1}} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm
+      year}} \right)^2 \left(\frac{\rs}{10^{-2}~{\rm pc}} \right)^{-1}
+   \notag \\
+& \times \left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \notag \\
+\approx & 4.6\times 10^{15} {\rm ergs~s^{-1}~Hz^{-1}}
+\left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm year}} \right)^2
+\left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{-1} \notag\\&\times
+\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^2 \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
+\end{align}
+
+The second line of this equation makes the approximation that
+$GM_\bullet/r$ dominates $\tilde{v}_{\rm w}^2$ throughout the
+integrand, which will be true for energies modestly higher than
+$E_{\rm cut}$.  The lower (upper) endpoint for this integral are
+arbitrary so long as it is somewhat less (greater) than the radius at
+which the observed frequency $\nu$ sees its exponential free-free
+cutoff. We have also set $n=1$.
+
+In general, these ``cut-off'' X-ray luminosities are quite small, and
+even {\it Chandra} would have little hope of detecting them in any but
+the nearest dwarf galaxies (e.g. the Magellanic clouds).  However, if
+source confusion is not present, this technique could test for the
+presence of IMBHs in very nearby dwarf galaxies, or more speculatively
+Galactic star clusters.
+
 \section{Discussion}

### 2015-02-04 ms.tex
Scaling relationship for free-free luminosity in terms of our parameters.

@@
 & \times \left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \notag \\
-\approx & 4.6\times 10^{15} {\rm ergs~s^{-1}~Hz^{-1}}
-\left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm year}} \right)^2
-\left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{-1} \notag\\&\times
-\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^2 \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
+\approx & 3.9\times 10^{14} {\rm ergs~s^{-1}~Hz^{-1}}
+\eta^2 \left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{1.96} \notag\\&\times
+\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^{-2.8} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
 \end{align}

### 2015-02-05 ms.tex
more

@@
 When $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to larger radii than predicted by by equation (\ref{eq:rs_simple}) or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
+
+The condition (\ref{eq:cooling2}) in conjunction with equation (\ref{eq:mdot_analytic}) also implies a maximum accretion rate for a thermally stable flow, which is given by
+\begin{align}
+\frac{\dot{M}_{\rm max}}{\dot{M}_{\rm edd}} \simeq
+  {\rm min}\begin{cases}
+   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34}\,{\rm M_{\odot}\,yr^{-1}}  &, \text{core}\\
+   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}\,{\rm M_{\odot}\,yr^{-1}}    &, \text{cusp}\\
+\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}\,{\rm M_{\odot}\,yr^{-1}} &, v_{\rm CL} < \sigma
+  \end{cases}
+  \label{eq:Mdotmax}
+\end{align}
 

### 2015-02-05 ms.tex
more

--- 2015-02-04 ms.tex
@@
 When $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to larger radii than predicted by by equation (\ref{eq:rs_simple}) or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
+
+The condition (\ref{eq:cooling2}) in conjunction with equation (\ref{eq:mdot_analytic}) also implies a maximum accretion rate for a thermally stable flow, which is given by
+\begin{align}
+\frac{\dot{M}_{\rm max}}{\dot{M}_{\rm edd}} \simeq
+  {\rm min}\begin{cases}
+   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
+   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
+\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm CL} < \sigma
+  \end{cases}
+  \label{eq:Mdotmax}
+\end{align}
 

### 2015-02-05 ms.tex
Adding table which shows cooling solution.

--- 2015-02-04 ms.tex
@@
 \begin{minipage}{18cm}
-\caption{Summary of Numerical Solutions}
+\caption{Summary of Numerical Solutions (without cooling or conductivity)}
 \begin{tabular}{lccccccccccccc}
 \hline
-{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
+{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} &
+{$\dot{M}/\dot{M}_{\rm edd} \eta$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s} \eta^{-1}$} & {comments}\\
 \hline
@@
 
+\begin{table*}
+\centering
+\begin{minipage}{18cm}
+\caption{Comparison of numerical solutions with and without
+  cooling. We have chosen $\eta=0.04$, which one would expect for 
+  the average star formation history for $\Mbh=10^8\Msun$ 
+  (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
+    figure once it is made.}). Note that we have deliberately chosen a solution
+  near our thermal stability threshold where cooling is beginning
+  to become important.
+}
+\begin{tabular}{lccccccccccccc}
+\hline
+{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
+{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
+\hline
+1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
+1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
+\hline
+\label{table:models}  
+\end{tabular}
+\end{minipage}
+\end{table*}
+
 This section describes the results of our numerical calculations,
@@
 (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
+
 \begin{align} v_{w}^{\rm C} \simeq
@@
 \end{align}
-The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for physically realized values of $\eta \lesssim 1$ shows that Compton heating alone is insufficient to stabilize the flow against cooling
-instability, i.e. $v_{w}^{C} < v_{\rm CI}$ (eq.~[\ref{eq:cooling2}]).
-
-Kinetic feedback occurs from an outflow of mass or energy  from the viscinity of the black hole in the form of a disk wind or jet, which deposits its energy across a much wider range of radii.
-If the total outflow power is proportional to the SMBH accretion rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
-Assuming that this energy is deposited uniformly out to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$, then the volumetric heating rate $e = \epsilon_{\rm j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind velocity at the stagnation radius given by
+
+The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for physically
+realized values of $\eta \lesssim 1$ shows that Compton heating alone
+is insufficient to stabilize the flow against cooling instability,
+i.e. $v_{w}^{C} < v_{\rm CI}$ (eq.~[\ref{eq:cooling2}]).
+
+Kinetic feedback occurs from an outflow of mass or energy from the
+viscinity of the black hole in the form of a disk wind or jet, which
+deposits its energy across a much wider range of radii.  If the total
+outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
+\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an
+efficiency factor.  Assuming that this energy is deposited uniformly
+out to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
+heat}^{3}$, then the volumetric heating rate $e = \epsilon_{\rm
+j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind velocity at
+the stagnation radius given by
+
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
@@
 \label{eq:vjet}
-\end{eqnarray} where we have used the fact that $\dot{M} \approx \eta
-M_{\rm enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto
+\end{eqnarray}
+
+where we have used the fact that $\dot{M} \approx \eta M_{\rm
+enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto
 M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ for radii interior to the outer
@@
 r_{\rm s}$, even a modest heating efficiency $\epsilon_{\rm j} \gtrsim
-10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other
-sources of non-accretion powered heating.
-However, if the jet distributes its energy on much larger scales comparable to the size of the galaxy, i.e.
-$r_{\rm heat} \gtrsim $ kpc $\gtrsim 10^{3}r_{\rm s}$ then the heating rate would be much less significant, even for an efficient jet ($\epsilon_{\rm j} \sim 1$).
-
-Also note that for a fixed $r_{\rm heat}$, the effective heating rate $v_{\rm  w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$ to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
-This shows that SMBH kinetic heating, if dominant, could thus `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
-Importantly, however, unlike in the case of local heating sources such as stellar winds, even a dominant SMBH heating may not allow for a thermally-stable steady flow because the central accretion rate does not respond instantaneously to changes in the
-thermodynamic properties of the gas on larger scale.
-We also note here that the kinetic heating rate is proportional to the SMBH mass to a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for core(cusp) galaxies, respectively.
-This dependence could have important implications for the dependence of the average nuclear X-ray luminosity of quiescent galaxies on the SMBH mass ($\S\ref{sec:mdot}$).
+10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources
+of non-accretion powered heating.  However, if the jet distributes its
+energy on much larger scales comparable to the size of the galaxy,
+i.e. $r_{\rm heat} \gtrsim $ kpc $\gtrsim 10^{3}r_{\rm s}$ then the
+heating rate would be much less significant, even for an efficient jet
+($\epsilon_{\rm j} \sim 1$).
+
+Also note that for a fixed $r_{\rm heat}$, the effective heating rate
+$v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto
+M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
+to a negative power (where we have used of
+eq.~[\ref{eq:stag_simple}]).  This shows that SMBH kinetic heating, if
+dominant, could thus `self-regulate' insofar as a lower heating rate
+results in a higher accretion rate, which in turn results in stronger
+jet feedback.  Importantly, however, unlike in the case of local
+heating sources such as stellar winds, even a dominant SMBH heating
+may not allow for a thermally-stable steady flow because the central
+accretion rate does not respond instantaneously to changes in the
+thermodynamic properties of the gas on larger scale.  We also note
+here that the kinetic heating rate is proportional to the SMBH mass to
+a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
+core(cusp) galaxies, respectively. This dependence could have
+important implications for the dependence of the average nuclear X-ray
+luminosity of quiescent galaxies on the SMBH mass
+($\S\ref{sec:mdot}$).
 
@@
 $r$ in a timescale
+
 \begin{eqnarray}
@@
 \end{eqnarray}
-Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is
+
+Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating
+$M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet
+crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is
+
 \begin{equation}
@@
 \end{equation}
-which is notably independent of radius $r$.  Thus we require $\epsilon_{\rm j} \gtrsim 10^{-12}$ for the jet to escape, and if it escapes it is free to travel a long distance.
+
+which is notably independent of radius $r$.  Thus we require
+$\epsilon_{\rm j} \gtrsim 10^{-12}$ for the jet to escape, and if it
+escapes it is free to travel a long distance.
 

### 2015-02-08 ms.tex
abstract

@@
 \topmargin -1 cm
-\defcitealias{WangMerritt:2004a}{WM04}
 
@@
 \begin{document}
-\title{Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes}
+\title{The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
 \maketitle
@@
 \begin{abstract}
-We calculate steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.
+We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses $M_{\bullet}$, parameterized gas heating rates, and physically-motivated stellar density profiles.
 Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-We derive analytic estimates for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-These results (neglecting radiative cooling) are used to assess over what range of conditions radiative instability will develop, assuming an average star formation history for galaxies of the given black hole mass.
-Our main conclusion is that.....
-We briefly discuss implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies.
+Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies with a given black hole mass.
+Our results for the average accretion rates, as well as the maximum thermally-stable and -unstable accreion rates, are compared to the measured nuclear X-ray luminosities of a sample of quiescent black holes, from which we conclude that...
+We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
 \end{abstract}

### 2015-02-08 ms.tex
moreabstract

@@
 Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies with a given black hole mass.
-Our results for the average accretion rates, as well as the maximum thermally-stable and -unstable accreion rates, are compared to the measured nuclear X-ray luminosities of a sample of quiescent black holes, from which we conclude that...
+Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies corresponding to a given black hole mass.
+Results for the average accretion rate, as well as the maximum thermally-stable and -unstable accretion rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.
+We find that the high accretion rates and short growth times of low mass black holes in the low redshift universe must be the result of an external gas supply, rather than secular processes from stellar mass loss within the galactic nucleus.
 We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.

### 2015-02-08 ms.tex
blah

@@
 
-%% Maybe active galaxies constitute 10% need reference here?
 Supermassive black holes (SMBHs) lurk in the centers of most, if not
@@
 The latter in turn sets the luminosity of the accretion flow and the impact of its energy and momentum input (`feedback') on larger physical scales.
-The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty star-formation and AGN activity (reference Ciotti and others).
-
-Knowledge of how $\dot{M}$ varies with the SMBH mass, $\Mbh$, and other properties of the
-galactic nucleus informs key questions, such as the co-evolution of SMBHs and their host galaxies with cosmic time.
-SMBH growth in the low redshift universe appears to be dominated by lower mass black holes (e.g.~\citealt{Heckman+04}).
-This is often
-attributed to general trend  of cosmological `down-sizing' (e.g, \citealt{Gallo+08}).
-However, the physical processes involved may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
-
-The accretion rates of low mass SMBHs, and their resulting X-ray luminosities $L_X$, also have implications for what observational constraints can be placed on their occupation fraction in low mass galaxies and the possible existence of intermediate mass black holes.
-By combining the average relationship between $\Mbh$ and
-$L_X$ measured from a sample of high mass galaxies (\citealt{Gallo+08}) with upper limits on $L_X$ in lower mass
-galaxies, \citet{MillerGallo+:2014a}  infer tentative evidence for an occupation fraction less than unity in the latter.
-This method, however, relies on extrapolating a power-law fit to the $L_X-\Mbh$ distribution to low $\Mbh$ below the detection threshold.
+The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty star-formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
+
+Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other properties of the
+galactic nucleus informs key questions related to the co-evolution of SMBHs and their host galaxies with cosmic time (e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).
+SMBH growth in the low redshift universe is dominated by low mass black holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a fact which is often attributed to the general trend of `cosmic down-sizing' resulting from hierarchical structure growth (e.g, \citealt{Gallo+08}).
+However, the physical processes involved in the growth of loss mass blacks may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
+One important question is whether SMBHs grow primarily by accreting gas which is fed directly from large scales, or whether some of the growth growth results from internal or secular processes such as stellar mass loss.
+
+The accretion rates of low mass SMBHs have implications for observational constraints on the occupation fraction of SMBHs in low mass galaxies, and the potential existence of intermediate mass black holes.
+\citet{Miller+15} combine the average correlation between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample of elliptical galaxies to infer tentative evidence for a SMBH occupation fraction less than unity in galaxies with stellar masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim 10^{7}M_{\odot}$).
+This method relies on extrapolating a power-law fit of the $L_X-\Mbh$ distribution to low values of $\Mbh$ (and hence $L_{\rm X}$) below the detection threshold, despite the potential for very different physics to control the accretion rates onto the lowest mass SMBHs.
 
 %The conclusions of
-%\citet{MillerGallo+:2014a} are thus sensitive to possible changes in
+%\citet{Miller+15} are thus sensitive to possible changes in
 %the $L_X$-$\Mbh$ relationship at small $\Mbh$.
@@
 
-The gas density of the CNM also influences the emission from stellar tidal disruption events (TDEs), such as the high energy
+The CNM density also influences the emission from stellar tidal disruption events (TDEs), such as the high energy
 transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
@@
 
-Gas comprising the CNM can in principle originate from a variety of sources: (1) wind mass loss from (predominantly evolved) stars; (2) star-star collisions; and (3) unbound debris from TDEs.
-Stellar wind mass loss is probably the dominant source insofar as collisions are relevant only in very dense stellar environments for young stellar populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find that TDEs contribute subdominantly to the time-averaged accretion rate of quiescent SMBHs.
+Gas comprising the CNM can in principle originate from several sources: (1) wind mass loss from predominantly evolved stars; (2) stellar binary collisions; and (3) unbound debris from a recent TDE.
+Stellar wind mass loss is probably the dominant source insofar as collisions are relevant only in extremely dense stellar environments for very young stellar populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find that TDEs contribute subdominantly to the time-averaged accretion rate of quiescent SMBHs.
 
@@
 hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from several sources including stellar winds, supernovae, and AGN feedback (e.g., \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works focusing on modeling individual galaxies, here we systematically analyze the properties of the CNM across a sample of galaxies with a range of SMBH masses, stellar density profiles, and star formation histories (\citealt{WangMerritt:2004a};
-hereafter WM04).
+stellar winds, while energy input results from several sources including stellar winds, supernovae, and AGN feedback (\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+Unlike previous works focusing on modeling individual galaxies, here we systematically analyze the properties of the CNM across a sample of galaxies with a range of SMBH masses, stellar density profiles, and star formation histories (\citealt{WangMerritt:2004a}).
 
@@
 $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
-\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
+\citep{Miller+15}.  Our model instead predicts that $\Mdot
 \sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
@@
 % This is shown in the top panel Figure~\ref{fig:bh_xray}. The
-% relationship from \citealt{MillerGallo+:2014a} and their detection
+% relationship from \citealt{Miller+15} and their detection
 % upper limits are the black and blue solid lines
@@
 % 10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
-% \citealt{MillerGallo+:2014a}.
+% \citealt{Miller+15}.
 
@@
 % %the tabulated black hole mass from the Mbh-Mbulge relation.
-% Fig. 1 of \citealt{MillerGallo+:2014a} plots the observed
+% Fig. 1 of \citealt{Miller+15} plots the observed
 % relationship of unresolved x-ray luminosity versus galactic stellar
@@
 % 10^{-7}$, which gives x-ray luminosities comparable to
-% those in \citealt{MillerGallo+:2014a}. We also try an alternate
+% those in \citealt{Miller+15}. We also try an alternate
 % prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
@@
 % there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
-% \citealt{MillerGallo+:2014a}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
-% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{MillerGallo+:2014a} finds
+% \citealt{Miller+15}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
+% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{Miller+15} finds
 % that $L_x \propto M_{\rm gal}^{0.7-0.8}$.
@@
 %   luminosity with stellar mass (black line) and the detection upper
-%   limit (blue line) from Fig. 1 of \citealt{MillerGallo+:2014a}. In
+%   limit (blue line) from Fig. 1 of \citealt{Miller+15}. In
 %   the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot

### 2015-02-08 ms.tex
2.1 update

@@
 We bracket these possibilities by considering models with $\Gamma=0.8$
-and $\Gamma=0.1$.  We fix $\beta = 2$ (a typical value) because our results are most sensitive to the
-properties of the gas flow on radial scales $\ll r_b$ and do not depend sensitively on the outer power law slope of the stellar density profile.
-However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.
-Depending on the model, we
-consider up to four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
-and 400 pc, a range motivated by the observed break radii in
-the \citet{LauerFaber+:2007a} sample. For the core galaxies ($\Gamma \le$0.3) in this sample the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
-approximately one dex. Most the cusp ($\Gamma \ge0.5$) galaxies have
-$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
-  significant effect on rs it may not be necessary to do runs. For
-  instance for Mbh=$10^8$ Msun, gamma=0.8, and vw0=600 km/s the
-  stagnation radius changes by only 8\%. So for cusp galaxies with
-  vw0$\gsim$600 km/s and Mbh$\lsim 10^8$ Msun it seems like it is a
-  safe bet to neglect the effect of the break radius on the
-  solution. For low heating rates it my be difficult to converged
-  solution for large values of rb=200 and 400 pc.}
-% However, the presence of $\rb$ is necessary for to obtain a
-% converged steady state for some regions of our parameter space. We
-% adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core
-% galaxy models we employ the scaling relation $\rb = $, motivated again
-% by the \citet{LauerFaber+:2007a} sample. ({\bf BDM: fill in!}).
-% Though simplistic, our results are not sensitive to our assumption
-% about the value of $\rb$.
+and $\Gamma=0.1$.
+
+We fix $\beta = 2$ (a typical value) because our results are generally not sensitive to the
+properties of the gas flow on radial scales $\gtrsim r_b$.
+The presence of the break radius $r_{b}$ is, however, necessary to obtain a converged steady state for some regions of our parameter space.
+We consider solutions calculated for up to four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the range of break radii from the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.
+Most the cusp galaxies have
+$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In practice we calculate solutions for a range of $\rb$ only in cases when its precise value is expected to have a significant affect on the solution, in particular for high SMBH masses and low heating rates, for which the stagnation radius approaches large radii.
 

### 2015-02-08 ms.tex
2.2 update

@@
 where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
-enclosed mass.  We assume an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
-
-The source term in the continuity equation (eq.~[\ref{eq:drhodt}]),
+enclosed mass.  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
+
+The source term in equation (\ref{eq:drhodt}),
 \begin{align}
@@
 recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
-years.
-To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following a star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the overall mass return rate from evolved stars as a function of B-band luminosity.
-Although we give the mass return rate per unit volume, our expressions are equivalent.}, although we will show later that $\eta$ can be significantly higher if star formation is ongoing (Fig.~\ref{fig:eta}).
+yr.
+To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following an impulsive star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return rate from evolved stars as a function of B-band luminosity instead of volumetrically, but our expressions are equivalent.}, although $\eta$ is significantly higher for continuous star formation histories (Fig.~\ref{fig:eta}).
 
 Source terms $\propto q$ also appear in the momentum and entropy
-equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because isotropic
-mass injection in the SMBH rest frame represents a source of momentum
+equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because the isotropic injection of mass represents, in the SMBH rest frame, a source of momentum
 and energy relative to the mean flow.  Physically, these result from
@@
 minimum amount of shock heating from stellar winds due to the random movement
-of stars with respect to one another at the characteristic velocity
-$\sim \sigma \approx \sqrt{GM_{\rm enc}/r}$.
+of stars with respect to one another at the characteristic velocity of $\sigma \approx \sqrt{GM_{\rm enc}/r}$.
 This heating is present even in old stellar populations for which mass and energy injection are dominated by AGB winds with low velocities $\ll \sigma$.
-The second term, $v_{w}^{2}$, parameterizes
-the contribution of additional sources of heating, such as faster main
+The second term, $v_{w}^{2}$, parameterizes all additional sources of heating, including faster main
 sequence or Wolf-Rayet stellar winds, spin-down energy from millisecond pulsars, supernovae, AGN
-feedback, etc.  As discussed in $\S\ref{sec:heating}$, the value of
-$v_{w}$ is uncertain and will in general depend on the SMBH mass and
+feedback, etc.  As will be discussed in $\S\ref{sec:heating}$, the value of
+$v_{w}$ will in general depend on the SMBH mass and
 the age of the stellar population.
@@
 To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.
-Heat transport by electron conductivity results in an an additional term on the right hand side of the entropy equation of the form
+Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
 \be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
@@
 T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free
-path for electron coulomb scattering becomes comparable to the
+path for electron coulomb scattering exceeds the
 temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the
@@
 dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
-field oriented perpendicular to the flow could in principle suppress the
+field that is oriented perpendicular to the flow could suppress the
 conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
 of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).
-
-Radiative cooling is also not included in our baseline calculations.
-Across much of the parameter space radiative cooling is subdominant compared to other sources of cooling.
-Radiative cooling becomes important when $\vwO$ is low and/or $\eta$ is high, but once important it leads to thermal instabilities (e.g.~\citealt{McCourt+12}) which our 1D
+We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity corrections to the key properties of solutions calculated assuming its presence.
+
+We also neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instabilities (e.g.~\citealt{McCourt+12}) that our 1D
 time-independent model cannot account for self-consistently anyways.
-Indeed, one of the main goals of this work is to use our analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities will develop ($\S\ref{sec:cooling}$).
+A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
 
@@
 physically plausible range of heating rates.  Although we are interested in the
-steady-state inflow/outflow structure (assuming it exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
+steady-state inflow/outflow solution (assuming one exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
 inflow on small radial scales and a possible supersonic outflow on large scales.
@@
 \subsection{Importance of Heat Conduction}
+\label{sec:conductivity}
 

### 2015-02-08 ms.tex
2.3 update

@@
 
-We also neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
+Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
+\be
+\dot{q}_{\rm rad} = -\Lambda(T)n^{2},
+\label{eq:qdot_rad}
+\ee
+where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
+We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
 However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instabilities (e.g.~\citealt{McCourt+12}) that our 1D

### 2015-02-08 ms.tex
3.1 update

@@
 \begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2} \approx 3.7
+T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
 \times 10^6\ \, v_{500}^2 \,\,{\rm K},
@@
 \end{align}
-where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.
-
-If the SMBH dominates the gravitational potential at the stagnation radius then $v_{w} \gg \sigma$ and hence the stagnation radius resides well inside the sphere of influence, i.e.~$r_{\rm s} < r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]).
-In this case equation (\ref{eq:stag_analytic}) simplifies to
+where $n \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the density power-law slope at $r = r_{\rm s}$.
+
+If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gg \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
+In this limit equation (\ref{eq:stag_analytic}) simplifies to
 \begin{align}
@@
 \end{align}
-where the numerical estimate assumes $n = 1$.
-This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their eq.~6).
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all.
-This result makes intuitive sense: gas is supplied by stars which are gravitationally bound to the black hole, so outflows occur only if the specific heating rate $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+where for the numerical estimate we adopt $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
+
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all (formally implying that the entire ISM of the galaxy is accreting).
+This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
 
@@
 \end{eqnarray}
-where we have made use of equation (\ref{eq:stag_simple}; assuming that $v_{w} \gg \sigma$) and have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
-The resulting Eddington ratio $\eddr$ is given by
+where we have made use of equation (\ref{eq:stag_simple}), i.e.
+assuming that $v_{w} \gg \sigma$, and we have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
+The resulting Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ is given by
 \begin{eqnarray}
@@
     1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
-    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
+    v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
     2.4 \times 10^{-5} \Mbheight^{0.48} 
@@
 
-The gas density at the stagnation radius $\rho(r_{\rm s})$ is more challenging to estimate accurately.
-Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}|_{r_{\rm s}} = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$ in conjuction with equation (\ref{eq:mdot_analytic}), one finds
+The gas density at the stagnation radius $\rho|_{r_{\rm s}}$ is more challenging to estimate accurately.
+Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}|_{r_{\rm s}} = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$,
 \begin{align}
@@
 \end{align}
-from which one derives 
+ in conjuction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:rs_simple}), one derives
 \begin{align}
@@
     \, {\rm g \, cm^{-3}}& \text{core},\\
-    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp},
+    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
   \end{cases}
@@
 \end{align}
-again using equation (\ref{eq:rs_simple}) for the stagnation radius.
 
@@
 
-Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) may be compared to the traditional Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
-\begin{align}
-  \dot{M}_{\rm B} =4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b),
+Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be compared to the traditional Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
+\begin{align}
+  \dot{M}_{\rm B} =4\pi \lambda r_{\rm B}^2 \rho|_{r_{\rm B}}v_{\rm ff}|_{r_{\rm B}},
 \label{eq:bondi}
 \end{align}
-where $r_b \equiv GM/c_{s}^{2}$ is the Bondi radius, $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
-By rewriting equation (\ref{eq:mdot_gas}) as $\dot{M}\simeq 4\pi \rs^2 \rho|_{r_{\rm s}} v_{\rm ff}|_{r_{\rm s}}/3$,
-one notices a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $\rb$ is replaced by $\rs$.
+where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
+One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $R_{\rm B}$ is replaced by $\rs$.
 When the stagnation radius resides interior to the sphere of influence we indeed have (eq.~[\ref{eq:stag_simple}])
 \begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}} = \frac{14}{3}r_{\rm B},
+  \rs\approx\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx \frac{7}{6n}r_{\rm B},
   \label{eq:rs_simple}
 \end{align}
-where the second equality makes use of equation (\ref{eq:Tanalytic}).
+where the second equality makes use of equation (\ref{eq:Tanalytic}).  {\bf BDM: please check, as I found something different than what was here before}.
 

### 2015-02-08 ms.tex
3.2 update

@@
 Our analytic results neglect the effects of heat conduction, an assumption we now check.
-The ratio of the magnitude of the conductive heating rate to the nominal level of wind heating at the stagnation radius is given by
+The ratio of the magnitude of the conductive heating rate to the nominal external (``wind") heating rate at the stagnation radius is given by
 \begin{align}
@@
 
-Radiative cooling, if important, qualitative alters key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm cool} = n^{2}\Lambda \propto T^{-2.7}$ is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \sim -0.7$ is the cooling function (see below).
+If important, radiative cooling qualitative alters key features of the accretion flow.
+Radiative cooling is usually of greatest important near the stagnation radius, where the gas is in nearly hydrostatic balance.
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdotrad}]) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \sim -0.7$ is the cooling function (see below).
 Thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Gan+14}).
@@
 Radiative cooling can, however, be stabilized by the other sources of cooling, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius is balanced by wind heating $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$ (neglecting radiative cooling).
-Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$,
-\begin{align}
-\left.\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm cool}|}\right|_{\rm r_{\rm s}} \simeq
+Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$ (eq.~[\ref{eq:qdot_rad}]),
+\begin{align}
+\left.\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\right|_{\rm r_{\rm s}} \simeq
   \begin{cases}
@@
 where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gas and stellar densities at the stagnation radius, respectively.
-Here $n = \rho/\mu m_p$ is the particle number density and we have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}; Fig.
+We have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}; his Fig.
 34.1).
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm cool}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
+To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
 \begin{align}
@@
 
-Thermal stability ($\dot{q}_{\rm heat} > \dot{q}_{\rm cool}$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
-\begin{align}
-v_{w} > v_{\rm CI} \simeq
+Thermal stability ($\dot{q}_{\rm heat} > |\dot{q}_{\rm rad}|$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
+\begin{align}
+v_{w} > v_{\rm TI} \simeq
   {\rm max}\begin{cases}
@@
 \end{align}
-Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally a condition for stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
-The requirement that $v_{\rm w} \gtrsim \sigma$ in equation (\ref{eq:cooling2}) results because the top two lines are derived under the assumption that the stagnation radius is given by equation (\ref{eq:rs_simple}).
-When $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to larger radii than predicted by by equation (\ref{eq:rs_simple}) or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
+Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally produces stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
+The stability requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines of equation (\ref{eq:cooling2}) are derived using equation (\ref{eq:rs_simple}) for the stagnation radius.
+However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to much larger radii or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
 

### 2015-02-09 ms.tex
3.3 update

@@
 We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instabilities (e.g.~\citealt{McCourt+12}) that our 1D
-time-independent model cannot account for self-consistently anyways.
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that our 1D
+time-independent model cannot account for anyways.
 A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
@@
 
-If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gg \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
+If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
 In this limit equation (\ref{eq:stag_analytic}) simplifies to
@@
   &\rs=\frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx 6
- \, \pc \,\, \Mbheight v_{500}^{-2},
+ \, \pc \,\, \Mbheight v_{500}^{-2}\,\,\,\,(v_{\rm w} \gtrsim \sigma),
   \label{eq:stag_simple}
@@
 \end{align}
-where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
+where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r_{\rm B})^{1/2}$ and $\lambda$ is a parameter of order unity.
 One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $R_{\rm B}$ is replaced by $\rs$.
@@
 \begin{eqnarray}
-  \rho_{\star}(r_{\rm s}) &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
+  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
  &\approx& \begin{cases}
@@
 Radiative cooling can, however, be stabilized by the other sources of cooling, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius is balanced by wind heating $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$ (neglecting radiative cooling).
-Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}| =|\Lambda(T) n^2|$ (eq.~[\ref{eq:qdot_rad}]),
+Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
 \begin{align}
@@
 \end{align}
-that results by combining equations~\eqref{eq:mdot_analytic} and~\eqref{eq:mdot_gas}.
+that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.
 
@@
   \end{cases}
-  \label{eq:cooling2}
-\end{align}
-Our numerical results in $\S\ref{sec:numerical}$ will demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally produces stability at all radii, not just at the stagnation radius (Fig.~\ref{fig:cooling}).
-The stability requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines of equation (\ref{eq:cooling2}) are derived using equation (\ref{eq:rs_simple}) for the stagnation radius.
+  \label{eq:cooling3}
+\end{align}
+The stability requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines of equation (\ref{eq:cooling3}) are derived using equation (\ref{eq:rs_simple}) for the stagnation radius.
 However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to much larger radii or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
-
-The condition (\ref{eq:cooling2}) in conjunction with equation (\ref{eq:mdot_analytic}) also implies a maximum accretion rate for a thermally stable flow, which is given by
-\begin{align}
-\frac{\dot{M}_{\rm max}}{\dot{M}_{\rm edd}} \simeq
+%Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
+
+Substituting condition (\ref{eq:cooling2}) into our analytic expression (\ref{eq:eddr_analytic}) for $\dot{M}(v_{\rm w})$ shows a thermally stable flow possesses a maximum accretion rate, which is given by
+\begin{align}
+\frac{\dot{M}_{\rm max,TI}}{\dot{M}_{\rm edd}} \simeq
   {\rm min}\begin{cases}
@@
    2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
-\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm CL} < \sigma
+\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma.
   \end{cases}
@@
 \begin{minipage}{18cm}
-\caption{Summary of Numerical Solutions (without cooling or conductivity)}
+\caption{Summary of Numerical Solutions}
 \begin{tabular}{lccccccccccccc}
 \hline
-{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} &
-{$\dot{M}/\dot{M}_{\rm edd} \eta$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s} \eta^{-1}$} & {comments}\\
+{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
+{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}$$^{(c)}$} & TI?$^{(d)}$ & {comments}\\
 \hline
-0.01 & 300 & 0.8 & U & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
+0.01 & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
 unresolved \\
-0.01 & 600 & 0.8 & U & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
-10^{ 2 }$ &  \\
-0.01 & 1200 & 0.8 & U & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
-10^{ 4 }$ &  \\
-0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & \\
-0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
-0.1 & 1200 & 0.8 & U & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
-10^{ 3 }$ &  \\
-1 & 300 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
-  -2 }$ &  TI\\
-1 & 600 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
-1 & 1200 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
-  3 }$ &  \\
-1 & 300 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
-1 & 300 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
-  -2 }$ &  TI/convergence \\
+0.01 & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+10^{ 2 }$ & N & \\
+0.01 & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+10^{ 4 }$ &  N &\\
+0.1 & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
+0.1 & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
+0.1 & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+10^{ 3 }$ & N & \\
+\hline
+1 & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+  -2 }$ & Y  & \\
+1 & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
+1 & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+  3 }$ & N &  \\
+1 & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
+1$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
+1 & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+  -2 }$ &Y & TI/convergence \\
 %1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
 %  -3 }$ &  TI/convergence\\
-1 & 300 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
-0.1 & 300 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
-0.1 & 300 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
+1 & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
+0.1 & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
+0.1 & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
 %0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
 %10^{ -2 }$   & TI/convergence  \\
-0.1 & 300 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
-10^{ -2 }$ & TI/convergence \\
+0.1 & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
+10^{ -2 }$ & Y &TI/convergence \\
 0.01 & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
-10^{ 4 }$ &  \\
+10^{ 4 }$ & N & \\
 0.1 & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
-  3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
-0.01 & 1200 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
-0.1 & 1200& 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
-1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
-1 & 1200 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
-1 & 1200 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
+  3 }$ & N & tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
+0.01 & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
+0.1 & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
+1 & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
+1 & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
+1 & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
 %1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
-1 & 1200 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
+1 & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
 \hline
@@
 \end{tabular}
-$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
-Break radius of stellar Nuker profile.  For profiles marked U, the
-break radius is not resolved on the grid.
+$^{(a)}$ Inner power-law index of stellar Nuker profile.
+$^{(b)}$ Break radius of stellar Nuker profile.
+$^{(c)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.
+$^{(d)}$ Is solution thermally unstable?
+$\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.
+{\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
 \end{minipage}
@@
 
-\begin{table*}
-\centering
-\begin{minipage}{18cm}
-\caption{Comparison of numerical solutions with and without
-  cooling. We have chosen $\eta=0.04$, which one would expect for 
-  the average star formation history for $\Mbh=10^8\Msun$ 
-  (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
-    figure once it is made.}). Note that we have deliberately chosen a solution
-  near our thermal stability threshold where cooling is beginning
-  to become important.
-}
-\begin{tabular}{lccccccccccccc}
-\hline
-{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
-{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
-\hline
-1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
-1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
-\hline
-\label{table:models}  
-\end{tabular}
-\end{minipage}
-\end{table*}
-
-This section describes the results of our numerical calculations,
-which we use to assess the validity of the analytic expressions
-provided in the previous section.  Numerical solutions are calculated
-for each galaxy for three different values of the stellar wind heating
-parameter $v_{w}$ = 300, 600, 1200 km s$^{-1}$.
-In cases when the stagnation radius become very large and was difficult to resolve on the grid, we conclude that such solutions will be thermally unstable and terminated their calculations (these are marked as `thermally unstable' in the tables.
+%\begin{table*}
+%\centering
+%\begin{minipage}{18cm}
+%\caption{Comparison of numerical solutions with and without
+ % cooling. We have chosen $\eta=0.04$, which one would expect for 
+  %the average star formation history for $\Mbh=10^8\Msun$ 
+ % (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
+  %  figure once it is made.}). Note that we have deliberately chosen a solution
+  %near our thermal stability threshold where cooling is beginning
+  %to become important.
+%}
+%\begin{tabular}{lccccccccccccc}
+%\hline
+%{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
+%{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
+%\hline
+%1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
+%1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
+%\hline
+%\label{table:models}  
+%\end{tabular}
+%\end{minipage}
+%\end{table*}
+
+This section describes the results of our numerical calculations, which we use to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.
+Our results are summarized in Table \ref{table:models} and Figure XXX.
+Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.
 

### 2015-02-09 ms.tex
3.3 update2

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/\dot{q}_{\rm cool}$, as a function of radius for each of our solutions (solid lines).
-Shown for comparison with dashed lines is the ratio of the cooling to the local free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
-For high heating rates both ratios are approximately equal at the stagnation radius (marked with a square for each solution).
-When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and $t_{\rm cool}/t_{\rm ff} \lesssim 10$ the flow will be susceptible to global and local thermal instability, respectively (e.g.,  \citealt{McCourt+12}).
-{\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
+  \includegraphics[width=\columnwidth]{profiles.eps}
+  \caption{\label{fig:profiles}Radial profiles of the CNM density
+    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
+    and interior X-ray luminosity ({\it bottom}) calculated for a
+    sample of galaxies within our grid.  Different colors
+    denote different values of the effective wind heating rate,
+    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
+      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
+    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
+    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
+    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
+    galaxies ($\Gamma$=0.8) and thick lines correspond to core
+    galaxies ($Gamma$=0.1). Squares mark out the location of
+    the stagnation radius for each solution.
+ }
 \end{figure}
@@
 
-This section describes the results of our numerical calculations, which we use to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.
+The results of our numerical calculations are uses to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.
 Our results are summarized in Table \ref{table:models} and Figure XXX.
-Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.
+Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.
 
@@
 increases as $\propto 1/r^{k}$ interior to the sphere of influence,
-where $k$ is smaller than 1--the power expected for virialized gas within the black hole sphere of influence.
+where $k\lesssim 1$, somewhat shallower than expected for virialized gas within the black hole sphere of influence.
 The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
@@
 
-Figure~\ref{fig:stag} shows our results for the
-stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the
-SMBH sphere of influence $r_{\rm soi}$, with different colors showing
-different values of $v_{w}$.  Cusp and core galaxies are marked with
-square and triangles, respectively.
-
- We may also compare our numerical results $r_{\rm s}/r_{\rm
-  soi}$ an be compared directly to our analytic estimate in equation
-\ref{eq:stag_analytic}.  The solid and dashed black curves in  Figure
-\ref{fig:stag} show the analytic results for $r_{\rm s}/r_{\rm soi}$.
-The good agreement provides a useful check of the numerical
-results. Note that the analytic curves implicitly assume a density
-slope, $n$ at $\rs$, which we have fixed to be 1 (0.5) for the solid
-(dashed) curve. For small $\vw/\sigma$ this assumption breaks down.
-
-For $\vw/\sigma \gg 1$ the value $\rs/\rsoi$ does not depend on break
-radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
-have an effect. Notice that near where the solid analytic curve
-diverges there are three green square, one over the other. These
-points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
-(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
-break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
+Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm soi}$, with different colors showing different values of $v_{w}$.
+Cusp and core galaxies are marked with square and triangles, respectively.
+Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively.
+Our analytic estimates provide reasonably accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but for low $v_{\rm w}$ they break down as the stagnation radius diverges to large radii.
+For $v_{w} \gg \sigma$ the value $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
+The three green squares located at the same value of $\vw =300 {\rm km/s}$, close to where the solid analytic line diverges, correspond to models with the same black hole masses $\Mbh = 10^7 \Msun=$ but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
 %% AG: Describe conservation checks to additionally validate the results.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{profiles.eps}
-  \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
-    and interior X-ray luminosity ({\it bottom}) calculated for a
-    sample of galaxies within our grid.  Different colors
-    denote different values of the effective wind heating rate,
-    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
-      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
-    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
-    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
-    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
-    galaxies ($\Gamma$=0.8) and thick lines correspond to core
-    galaxies ($Gamma$=0.1). Squares mark out the location of
-    the stagnation radius for each solution.
- }
-\end{figure}
 
@@
   \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
-    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
-      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
+    $r_{s}$ in units of the sphere of influence radius $r_{\rm
+      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
     function of the ratio of the effective wind heating rate $v_{w}$
     to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols represent $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
-    respectively.  Squares correspond to cusp galaxies, while
-    triangles correspond to cores. The black curves correspond to the
-    analytic prediction from Equation~\eqref{stag_analytic}. The solid
-    (dashed) curve is the correponds to $\Gamma=0.8$ and $n=1$
-    ($\Gamma=0.1$ and $n=0.5$.}
+    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
+    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
+    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
+    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.
+{\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?}}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{cooling.eps}
+  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a function of radius (solid lines) for each of our solutions shown in Figure \ref{fig:profiles}.
+Dashed lines show for comparison the ratio of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
+For high heating rates both ratios are approximately equal at the stagnation radius (marked as squares).
+When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff} \lesssim 10$, the flow is susceptible thermal instabilities.
+{\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
 \end{figure}

### 2015-02-09 ms.tex
sect 4

@@
 Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively.
-Our analytic estimates provide reasonably accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but for low $v_{\rm w}$ they break down as the stagnation radius diverges to large radii.
-For $v_{w} \gg \sigma$ the value $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
-The three green squares located at the same value of $\vw =300 {\rm km/s}$, close to where the solid analytic line diverges, correspond to models with the same black hole masses $\Mbh = 10^7 \Msun=$ but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
+Our analytic estimates provide accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but they break down for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
+For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
+The three vertically-aligned green squares located at the same value of $v_{w}/\sigma$ close to where the solid analytic line diverges correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
 %% AG: Describe conservation checks to additionally validate the results.
@@
     analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.
-{\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?}}
+{\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?
+fold $\eta$ into the y axis.
+}}
 \end{figure}
@@
 
-Fig.~\ref{fig:cooling} shows $H/C=\frac{1}{2} (q \vw^2+q
-v^2)/\left|\Lambda(T) n^2\right|$ and $\tcool/\tff$
-as a function of radius for all of our solutions. {\bf BDM: change
-  plots}, with different colors denoting different values of $\vwO$.
-For our highest heating rates we observe that cooling is unimportant
-for all solutions across all radii--neither the local nor the global
-thermal instability would be present. However,  for our smallest value
-of $\vwO$=300 km s$^{-1}$ with $\Mbh=10^8 \Msun$, the solution would be
-thermally unstable as $H/C<1$ and $\tcool/\tff<10$. Note that the
-precise region of the parameter space which would be thermally
-unstable would depend on the value of $\eta$--in
-Fig.~\pageref{fig:cooling} we have chosen $\eta=0.02$, which would be
-appropriate for a stellar population with $\tage\simeq \th$. This
-value is on the low end of what we would physically expect for
-$\eta$.
-
-For $\vwO=1200$ km s$^{-1}$ and $\vwO=600$ km s$^{-1}$, we have
-$H/C\simeq\tcool/\tff$ at $\rs$ as expected. However, the two ratios
-diverge away from $\rs$, as equation~\eqref{eq:rhors2} is not a good
-approximation away from $\rs$. Similarly, it is poorer approximation
-for $\vwO=300$ km s$^{-1}$. Hence, $H/C$ and $\tcool/\tff$ do not
-closely match at $\rs$ for this $\vwO$. {\bf AG would be good to
-  clarify the physics here a little more.}
+Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
+For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$ and $\tcool/\tff \lesssim 1,$ depending on the wind mass loss parameter $\eta$.
+Note that the ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ at the stagnation radius deviates from its minimum value across the entire grid by less than a factor of two; thus the ratio of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ indeed represents a useful proxy for the presence of thermal instabilty across the entire grid.
+Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$ near the stagnation radius.
+However, the two ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the gas density, which is greater in a subsonic inflow (weak heating) instead of a supersonic outflow (strong heating).
 

### 2015-02-09 ms.tex
salvaging the unsalvagable table

@@
 \hline
-{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
-{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}$$^{(c)}$} & TI?$^{(d)}$ & {comments}\\
+{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
+{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
 \hline
-0.01 & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
+$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
+\hline
+10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
 unresolved \\
-0.01 & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
 10^{ 2 }$ & N & \\
-0.01 & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
 10^{ 4 }$ &  N &\\
-0.1 & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
-0.1 & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
-0.1 & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
+10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
+10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
 10^{ 3 }$ & N & \\
 \hline
-1 & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
   -2 }$ & Y  & \\
-1 & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
-1 & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
+10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
   3 }$ & N &  \\
-1 & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
-1$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
-1 & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
+10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
+10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
   -2 }$ &Y & TI/convergence \\
@@
 %  -3 }$ &  TI/convergence\\
-1 & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
-0.1 & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
-0.1 & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
+10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
+10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
+10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
 %0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
 %10^{ -2 }$   & TI/convergence  \\
-0.1 & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
+10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
 10^{ -2 }$ & Y &TI/convergence \\
-0.01 & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
+10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
 10^{ 4 }$ & N & \\
-0.1 & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
-  3 }$ & N & tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
-0.01 & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
-0.1 & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
-1 & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
-1 & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
-1 & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
+10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
+  3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
+10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
+10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
+10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
+10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
+10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
 %1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
-1 & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
+10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
 \hline
@@
 $^{(b)}$ Break radius of stellar Nuker profile.
-$^{(c)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.
-$^{(d)}$ Is solution thermally unstable?
+$^{(c)}$Accretion rate in Eddington units, normalized to a stellar mass input parameter $\eta = 0.04$.
+$^{(d)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.
+$^{(e)}$ Is solution thermally unstable?
 $\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.

### 2015-02-09 ms.tex
salvaging the unsalvagable table2

@@
 Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$ near the stagnation radius.
-However, the two ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the gas density, which is greater in a subsonic inflow (weak heating) instead of a supersonic outflow (strong heating).
+However, the two ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true gas density, which is greater in a subsonic inflow (weak heating) than in a supersonic outflow (strong heating).
 
@@
 
-Key properties of the flow, such as the stagnation radius, the SMBH accretion rate, and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w}^{2}$.
+Key properties of the flow, such as the SMBH accretion rate and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w}^{2}$.
 This section summarizes individual heating sources, providing estimates of the value of
@@
 Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence stars.
-At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars, while at later times energy input is dominated by main sequence winds.
-Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages mass input is dominated by the slow AGB winds of low mass stars.
+At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars (e.g., \citealt{VossDiehl+:2009a}), while at later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
+Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages mass input is dominated by the slow AGB winds of evolved low mass stars.
 
 Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
-At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v_{\rm w} \sim 50-100 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).
+At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v_{\rm w} \sim 50-100 $ km s$^{-1}$.
 As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
@@
 
-What is the effect of the Ia radius?
+Another effect of SN Ia is that they cap the accretion rate onto the SMBH by periodically blowing gas out of the nucleus of low mass galaxies.
 Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.
 Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
-Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the SMBH accretion rate is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.
+Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, especially for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
+Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the accretion rate onto low mass SMBHs is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]), i.e.
 \begin{eqnarray}
-\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm max,Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 \end{eqnarray}
+Note that in general $\dot{M}_{\rm max,Ia}$ exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm max,TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow out' from SNe Ia cannot alone prevent cooling instabilities in low mass galaxies.
+
 {\bf AG: Changed this expression somewhat from that of BDM (slightly

### 2015-02-09 ms.tex
Fixing italics in one of the captions.

@@
   heating ({\it orange}), Ia supernovae ({\it green}), millisecond
-  pulsars ({\it blue}), and compton heating (\it pink).  Each heating
+  pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating
   source varies with black hole mass $\Mbh$ due to the different

### 2015-02-09 ms.tex
Changing figure somewhat

@@
 
-Figure~\ref{fig:cooling2} shows the ratio of heating to radiative cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total heating rate from Figure \ref{fig:vWsources}.
-The combined heating rate from stellar winds and Compton heating is insufficient to prevent thermal instability for the high $\Mbh$.
-However, if Ia supernovae are included in the schematic way described above, the flow again becomes thermally stable for $\Mbh \gtrsim XXXX$.
+Figure~\ref{fig:cooling2} shows the ratio of heating to radiative
+cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a
+function of SMBH mass, using our total heating rate from Figure
+\ref{fig:vWsources}.  The combined heating rate from stellar winds and
+Compton heating is insufficient to prevent thermal instability for the
+high $\Mbh$.  However, if Ia supernovae are included in the schematic
+way described above, the flow again becomes thermally stable for $\Mbh
+\gtrsim XXXX$.
 
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{cooling2.pdf}
-\caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
-  $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
-  and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
-  using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
-  $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{cooling2.pdf}
+% \caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
+%   $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
+%   and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
+%   using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
+%   $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
+% \end{figure}
 
@@
   black hole feedback (e.g. the solid black curve in
-  Figure~\ref{fig:vwSources}). For the purple curve we also include
-  the $\vwO$ from Ia's (the dashed red curve
   Figure~\ref{fig:vwSources}).}

### 2015-02-09 windheat.tex
Changing figure somewhat

@@
 \caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
-  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
+  a stellar population of age $\tau_{\star}$.}
 \end{figure}
@@
 \caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
-  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
+  a stellar population of age $\tau_{\star}$.}
 \end{figure}

### 2015-02-10 ms.tex
blah

--- 2015-02-09 ms.tex
@@
 \begin{document}
-\title{The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
+\title{Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
 \maketitle
@@
 of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).
-We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity corrections to the key properties of solutions calculated assuming its presence.
+We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity errors in the key properties of the solutions.
 
@@
 where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
-We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that our 1D
-time-independent model cannot account for anyways.
+We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
+time-independent model.
 A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).

### 2015-02-10 ms.tex
more edits 3.3

@@
 time-independent model.
-A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
+A main goal of this work is to use solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
 
@@
 
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all (formally implying that the entire ISM of the galaxy is accreting).
-This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim \tilde{v}_{w}^{2}$ exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all, formally implying that the entire ISM of the galaxy is accreting.
+This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
 
@@
 \end{eqnarray}
-where we have made use of equation (\ref{eq:stag_simple}), i.e.
-assuming that $v_{w} \gg \sigma$, and we have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
-The resulting Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ is given by
+where we have assumed $v_{w} \gg \sigma$ by adopting equation (\ref{eq:stag_simple}) for $r_s$, and we have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
+The resulting Eddington ratio is given by
 \begin{eqnarray}
@@
 where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r_{\rm B})^{1/2}$ and $\lambda$ is a parameter of order unity.
-One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $R_{\rm B}$ is replaced by $\rs$.
-When the stagnation radius resides interior to the sphere of influence we indeed have (eq.~[\ref{eq:stag_simple}])
+One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $r_{\rm B}$ is replaced by $\rs$.
+Indeed, when the stagnation radius resides interior to the sphere of influence we find that (eq.~[\ref{eq:stag_simple}])
 \begin{align}
@@
 
-Our analytic results neglect the effects of heat conduction, an assumption we now check.
-The ratio of the magnitude of the conductive heating rate to the nominal external (``wind") heating rate at the stagnation radius is given by
+Our analytic derviations neglect the effects of heat conduction, an assumption we now check.
+The ratio of the magnitude of the conductive heating rate to the external heating rate at the stagnation radius is given by
 \begin{align}
@@
   \end{cases}
- \label{eq:rhors}
+ \label{eq:conduction}
 \end{align}
 where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.
-Because the stagnation radius is usually well inside the break radius, we have approximated the stellar density as (eq.~[\ref{eq:rhostar}])
+We have approximated the stellar density profile as (eq.~[\ref{eq:rhostar}])
 \begin{eqnarray}
@@
 \end{eqnarray}
-Even in the saturated case, heat conduction is at most an order unity correction for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
+where we have assumed that the stagnation radius is well inside the Nuker break radius.
+Equation (\ref{eq:conduction}) shows that even in the saturated case, neglecting heat conduction results in at most an order unity error in the entropy source term for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
+Numerical experiments including conductivity are seen confirm this ($\S\ref{sec:numerical}$).
 
@@
 
-If important, radiative cooling qualitative alters key features of the accretion flow.
-Radiative cooling is usually of greatest important near the stagnation radius, where the gas is in nearly hydrostatic balance.
+If radiative cooling becomes important, it can qualitatively alter key features of the accretion flow.
+Radiative cooling usually has its greatest impact near or external to the stagnation radius, where the gas resides in near hydrostatic balance.
 Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdotrad}]) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \sim -0.7$ is the cooling function (see below).

### 2015-02-10 ms.tex
Rescaling table entries (a few entries have additional changes...).

--- 2015-02-10 ms.tex
@@
 \documentclass[usenatbib,fleqn]{mn2e}
+
+\makeatletter
+\newlength{\abovecaptionskip}%
+\setlength{\abovecaptionskip}{10\p@}
+\makeatother
+\usepackage{threeparttable}
+
 \usepackage{amsmath,amssymb}
@@
 \begin{document}
-\title{Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
+\title{The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
 \maketitle
@@
 of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).
-We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity errors in the key properties of the solutions.
+We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity corrections to the key properties of solutions calculated assuming its presence.
 
@@
 where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
-We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
-time-independent model.
+We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that our 1D
+time-independent model cannot account for anyways.
 A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
@@
 \begin{table*}
-\centering
+\begin{threeparttable}
+%\centering
 \begin{minipage}{18cm}
@@
 {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
-{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
+{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
 \hline
@@
 \hline
-10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
-unresolved \\
-10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
-10^{ 2 }$ & N & \\
-10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
-10^{ 4 }$ &  N &\\
-10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
-10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
-10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
-10^{ 3 }$ & N & \\
-\hline
-10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
-  -2 }$ & Y  & \\
-10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
-10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
-  3 }$ & N &  \\
-10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
-10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
-10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
-  -2 }$ &Y & TI/convergence \\
-%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
-%  -3 }$ &  TI/convergence\\
-10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
-10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
-10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
-%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
-%10^{ -2 }$   & TI/convergence  \\
-10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
-10^{ -2 }$ & Y &TI/convergence \\
-10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
-10^{ 4 }$ & N & \\
-10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
-  3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
-10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
-10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
-10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
-10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
-10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
-%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
-10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
+$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
+$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
+$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
+$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
+$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
+$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
+$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
+$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
+$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
+$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
+$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
+$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
+$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
+$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
+$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
+$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
+$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
+$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
+$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
+$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
+$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
 \hline
@@
 \end{tabular}
-$^{(a)}$ Inner power-law index of stellar Nuker profile.
+\begin{tablenotes}
+\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
+Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
+Eddington units, normalized to a stellar mass input parameter $\eta =
+0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
+stagnation radius.  $^{(e)}$ Is solution thermally unstable?
+$\dagger$Calculated including radiative cooling, assuming $\eta =
+0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
+  are included. AG: Realized that the solution I ran earlier, with
+  cooling was actually a solution that would be thermally unstable
+  according to our thermal instability. I am worried that this
+  solution may not be representative due to the small break radius.}
+\end{tablenotes}
+\end{minipage}
+\end{threeparttable}
+
+\end{table*}
+
+% \begin{table*}
+% \centering
+% \begin{minipage}{18cm}
+% \caption{Summary of Numerical Solutions}
+% \begin{tabular}{lccccccccccccc}
+% \hline
+% {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
+% {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
+% \hline
+% $(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
+% \hline
+% 10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
+% unresolved \\
+% 10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
+% 10^{ 2 }$ & N & \\
+% 10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
+% 10^{ 4 }$ &  N &\\
+% 10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
+% 10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
+% 10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
+% 10^{ 3 }$ & N & \\
+% \hline
+% 10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
+%   -2 }$ & Y  & \\
+% 10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
+% 10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
+%   3 }$ & N &  \\
+% 10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
+% 10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
+% 10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
+%   -2 }$ &Y & TI/convergence \\
+% %1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
+% %  -3 }$ &  TI/convergence\\
+% 10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
+% 10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
+% 10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
+% %0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
+% %10^{ -2 }$   & TI/convergence  \\
+% 10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
+% 10^{ -2 }$ & Y &TI/convergence \\
+% 10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
+% 10^{ 4 }$ & N & \\
+% 10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
+%   3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
+% 10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
+% 10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
+% 10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
+% 10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
+% 10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
+% %1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
+% 10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
+% \hline
+% \label{table:models}  
+% \end{tabular}
+% $^{(a)}$ Inner power-law index of stellar Nuker profile.
 $^{(b)}$ Break radius of stellar Nuker profile.
@@
 {\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
-\end{minipage}
-\end{table*}
-
-%\begin{table*}
-%\centering
-%\begin{minipage}{18cm}
-%\caption{Comparison of numerical solutions with and without
- % cooling. We have chosen $\eta=0.04$, which one would expect for 
-  %the average star formation history for $\Mbh=10^8\Msun$ 
- % (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
-  %  figure once it is made.}). Note that we have deliberately chosen a solution
-  %near our thermal stability threshold where cooling is beginning
-  %to become important.
-%}
-%\begin{tabular}{lccccccccccccc}
-%\hline
-%{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
-%{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
-%\hline
-%1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
-%1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
-%\hline
-%\label{table:models}  
-%\end{tabular}
-%\end{minipage}
-%\end{table*}
+% \end{minipage}
+% \end{table*}
 
@@
     triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
-    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.
-{\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?
-fold $\eta$ into the y axis.
-}}
+    analytic prediction from equation (\ref{eq:rs2main}), with solid
+    and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$
+    and $\{\Gamma=0.1,n=0.5\}$, respectively.  {\bf BDM: is the x axis
+      here $v_{w}$ or $\vw$ !!?  fold $\eta$ into the y axis. AG: The
+      axis here is $v_{w}$--it does not include the contribution from
+      sigma. Should it be changed}}
 \end{figure}

### 2015-02-10 ms.tex

@@
 where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
-We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that our 1D
-time-independent model cannot account for anyways.
-A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
+We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
+time-independent model.
+A main goal of this work is to use solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
 

### 2015-02-10 ms.tex
more edits 3.3

--- 2015-02-10 ms.tex
@@
 
+Radiative cooling usually has its greatest impact near or external to the stagnation radius, where the gas resides in near hydrostatic balance.
 If radiative cooling becomes important, it can qualitatively alter key features of the accretion flow.
-Radiative cooling usually has its greatest impact near or external to the stagnation radius, where the gas resides in near hydrostatic balance.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdotrad}]) is thermally unstable, where $\Lambda(T) \propto T^{-\beta}$ with $\beta \sim -0.7$ is the cooling function (see below).
-Thermal instability leads to initially higher black hole accretion rates and enhanced star formation which, when coupled to the flow by feed-back processes, can lead to limit cycle behavior inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Gan+14}).
-
-Radiative cooling can, however, be stabilized by the other sources of cooling, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]), which at the stagnation radius is balanced by wind heating $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$ (neglecting radiative cooling).
-Thermal stability at the stagnation radius can thus be assessed by comparing the external (``wind") heating rate to the rate of radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdot_rad}]) is thermally unstable, where $\Lambda(T) \propto T^{-0.7}$ (see below).
+Thermal instability can lead to enhanced star formation and temporarily increases the black hole accretion rate; when coupled to feed-back processes, the latter can lead to time-dependent (e.g.
+limit cycle) behavior which is inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Gan+14}).
+
+Radiative cooling can, however, be stabilized if other sources of cooling dominate over it, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
+Neglecting radiative cooling, this term is balanced at the stagnation radius by the wind heating term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.
+Thermal stability near the stagnation radius can thus be assessed by the ratio of wind heating to radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
 \begin{align}
@@
 \begin{align}
-\rho|_{r_{\rm s}}=\frac{3 q|_{r_{\rm s}} \tff|_{r_{\rm s}}}{2-\Gamma}.
+\rho|_{r_{\rm s}}=\frac{3 q\tff|_{r_{\rm s}}}{2-\Gamma}.
 \label{eq:rhors2}

### 2015-02-10 ms.tex
more edits 4.3

--- 2015-02-10 ms.tex
@@
 34.1).
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ if one uses the equality
+To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
 \begin{align}
@@
 \end{align}
-The stability requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines of equation (\ref{eq:cooling3}) are derived using equation (\ref{eq:rs_simple}) for the stagnation radius.
-However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to much larger radii or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
+The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
+However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to very large radii, or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
 %Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
 
-Substituting condition (\ref{eq:cooling2}) into our analytic expression (\ref{eq:eddr_analytic}) for $\dot{M}(v_{\rm w})$ shows a thermally stable flow possesses a maximum accretion rate, which is given by
+The existence of a minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) implies a corresponding maximum accretion rate,
 \begin{align}
@@
    2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
-\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma.
+\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
   \end{cases}
@@
 \end{align}
+which is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$.
 
@@
 For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$ and $\tcool/\tff \lesssim 1,$ depending on the wind mass loss parameter $\eta$.
-Note that the ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ at the stagnation radius deviates from its minimum value across the entire grid by less than a factor of two; thus the ratio of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ indeed represents a useful proxy for the presence of thermal instabilty across the entire grid.
+At the stagnation radius, the ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor of two of its minimum across the entire grid;  thus, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a diagnostic of thermal instabilty for the entire solution.
+
 Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$ near the stagnation radius.

### 2015-02-10 ms.tex
more edits 5.3

@@
   \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
-    and interior X-ray luminosity ({\it bottom}) calculated for a
-    sample of galaxies within our grid.  Different colors
+    ({\it top}), temperature ({\it middle}), and velocity ({\it bottom}),
+    calculated for a representative sample of galaxies.  Different colors
     denote different values of the effective wind heating rate,
@@
     galaxies ($\Gamma$=0.8) and thick lines correspond to core
-    galaxies ($Gamma$=0.1). Squares mark out the location of
-    the stagnation radius for each solution.
+    galaxies ($\Gamma$=0.1). Squares mark the location of
+    the stagnation radius for each solution {\bf BDM: added colored labels for the $v_w$ value, e.g. a blue 1200 km/s directly to the top figure} .
  }
@@
     triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
-    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.
-{\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?
-fold $\eta$ into the y axis.
-}}
+    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively. }
 \end{figure}
@@
 When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff} \lesssim 10$, the flow is susceptible thermal instabilities.
-{\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
+{\bf BDM: change y axis labels to qdotheat/qdotrad, tcool/tff}.}
 \end{figure}
@@
 Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
-At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v_{\rm w} \sim 50-100 $ km s$^{-1}$.
+At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.
 As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
@@
 Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
-\end{align} The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq
-\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon_{\rm Ia}$
+\end{align} The thermal energy injected by a Ia SN, $E_{\rm Ia} \simeq
+\epsilon_{\rm Ia} 10^{51}$ erg, depends on the efficiency $\epsilon_{\rm Ia}$
 with which the initial blast wave energy is converted into bulk or turbulent
@@
 
-The Ia SN rate $\RateIa$ depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
+The Ia SN rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
 In
@@
 The high value of $v_{w}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
-However, SNe can only be approximated as supplying constant heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
+However, SNe can only be approximated as supplying heating which is spatially and temporally homogeneous if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
 We define the ``Ia radius"
@@
 dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship
-(equation~[\ref{eq:Msigma}]).
+(eq.~[\ref{eq:Msigma}]).
 
@@
 \end{eqnarray}
-The fact that $r_{\rm Ia} \gg r_{\rm s}$ appears to imply that Ia heating can only be approximated as a steady heating source near the stagnation radius for extremely massive SMBHs $M_{\bullet} \gtrsim 10^9 \Msun$ or very young populations ($\tau_{\star} \ll t_{\rm h}$).
-However, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the nominal heating rate (without Ia contribution) is much less than this.
-Nevertheless, the impact of Ia SN is clearly greater for larger SMBH masses for which $r_{\rm Ia} \lesssim r_{\rm s}$.
-
-Another effect of SN Ia is that they cap the accretion rate onto the SMBH by periodically blowing gas out of the nucleus of low mass galaxies.
+If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be approximated as a steady heating source near the stagnation radius for extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in the case of a very young stellar population ($\tau_{\star} \ll t_{\rm h}$).
+On the other hand, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the heating rate without SN Ia is less than this.
+
+Even if SN Ia are rare near the stagnation radius, they may cap the SMBH accretion rate by periodically blowing gas out of the nucleus of low mass galaxies.
 Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.
 Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
-Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, especially for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
-Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the accretion rate onto low mass SMBHs is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]), i.e.
+Hence, SN Ia are in principle capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, especially for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
+Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the accretion rate is limited to the value,
 \begin{eqnarray}
@@
    & \text{core} \\
-    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{-0.6}   & \text{cusp}.
+    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{-0.6}   & \text{cusp},
   \end{cases}
@@
 \end{eqnarray}
-Note that in general $\dot{M}_{\rm max,Ia}$ exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm max,TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow out' from SNe Ia cannot alone prevent cooling instabilities in low mass galaxies.
-
-{\bf AG: Changed this expression somewhat from that of BDM (slightly
-  different scaling relations were used?). I will
-  check again! Note that the time dependence of eta~t$^{-1.3}$ is
-  folded in above.}
+obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]).
+Note that $\dot{M}_{\rm max,Ia}$ usually exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm max,TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in low mass galaxies.
+Also note that this maximum Ia accretion rate only applies if the gas within the CNM is supplied by local stellar mass loss, since the quantity of gaseous mass can be much greater if is fed externally, e.g.
+due to a galactic merger.
 
@@
 on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
-case $v_{w} \lesssim 30$ km s$^{-1}$.  For higher spin-down
+case $v_{w}^{\rm MSP} \lesssim 30$ km s$^{-1}$.  For higher spin-down
 luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
-of some Fermi-detected pulsars, then the higher value of $v_{w}
+of some Fermi-detected pulsars, then the higher value of $v_{w}^{\rm MSP}
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important

### 2015-02-10 ms.tex
more edits 6.3

@@
 Thermal instability can lead to enhanced star formation and temporarily increases the black hole accretion rate; when coupled to feed-back processes, the latter can lead to time-dependent (e.g.
-limit cycle) behavior which is inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Gan+14}).
+limit cycle) behavior which is inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}).
 
@@
 
-Feedback from accretion onto the SMBH represents an important source of heating which, however, is also the most difficult to quantify.
+Feedback from accretion onto the SMBH represents an important source of heating which, however, is also the most difficult to quantify (e.g., \citealt{Brighenti&Mathews03}, \citealt{DiMatteo+05}; \citealt{Kurosawa&Proga09}; \citealt{Fabian12} for a recent review).
 A key difference between AGN heating and the other sources discussed thus far is its dependence on the SMBH accretion rate $\dot{M}$, which is itself a function of the heating rate (eq.~[\ref{eq:mdot_analytic}]).
@@
 There are two types of SMBH feedback: kinetic and radiative.
-Radiative feedback is potentially effective even in low luminosity AGN via Compton heating, which provides a volumetric heating rate (\citealt{Gan+14})
+Radiative feedback is potentially effective even in low luminosity AGN via Compton heating (e.g., \citealt{Sazonov+04}, \citealt{Ciotti+10}), which provides a volumetric heating rate (\citealt{Gan+14})
 \be
@@
 \ee
-where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$ (\citealt{Gan+14}).
-
-{\bf AG: Note that the Compton heating will depend on the distance of
-  the hole as $1/r^2$ so Compton heating will be stronger closer to the
-  black hole! }
+where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$ (e.g., \citealt{Ho99}, \citealt{Eracleous+10}).
+
 The importance of Compton heating can be estimated by assuming the SMBH
@@
 viscinity of the black hole in the form of a disk wind or jet, which
-deposits its energy across a much wider range of radii.  If the total
+deposits its energy across a much wider range of radii (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).  If the total
 outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
@@
 \item{Fact that some low mass BHs appear to have nearly Eddington accretion rates, suggest an external origin - since the maximum Ia rate appears to be below this}
+\item{Growth of low mass BHS, e.g. \citealt{Kauffmann&Heckman09}}
 \end{itemize}

### 2015-02-11 ms.tex
Putting back modified table

@@
 \end{tabular}
-$^{(a)}$ Inner power-law index of stellar Nuker profile.
-$^{(b)}$ Break radius of stellar Nuker profile.
-$^{(c)}$Accretion rate in Eddington units, normalized to a stellar mass input parameter $\eta = 0.04$.
-$^{(d)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.
-$^{(e)}$ Is solution thermally unstable?
-$\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.
-{\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
+\begin{tablenotes}
+\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
+Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
+Eddington units, normalized to a stellar mass input parameter $\eta =
+0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
+stagnation radius.  $^{(e)}$ Is solution thermally unstable?
+$\dagger$Calculated including radiative cooling, assuming $\eta =
+0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
+  are included. AG: Realized that the solution I ran earlier, with
+  cooling was actually a solution that would be thermally unstable
+  according to our thermal instability. I am worried that this
+  solution may not be representative due to the small break radius.}
+\end{tablenotes}
 \end{minipage}
+\end{threeparttable}
+
 \end{table*}

### 2015-02-12 ms.tex
3
githole

@@
 \begin{abstract}
-We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses $M_{\bullet}$, parameterized gas heating rates, and physically-motivated stellar density profiles.
-Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.
-Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies corresponding to a given black hole mass.
+We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
+Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
+Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
+We assess the conditions under which radiative instabilities will develop absent black hole feedback, based on the heating supplied by the average star formation history for galaxies corresponding to a given black hole mass.
 Results for the average accretion rate, as well as the maximum thermally-stable and -unstable accretion rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.
-We find that the high accretion rates and short growth times of low mass black holes in the low redshift universe must be the result of an external gas supply, rather than secular processes from stellar mass loss within the galactic nucleus.
+We determine that the measured high accretion rates and short growth times of low mass black holes in the local universe must be the result of an external gas supply, rather than secular processes resulting from stellar mass loss within the galactic nucleus.
 We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
@@
 $v_{w}$ will in general depend on the SMBH mass and
-the age of the stellar population.
+the age of the stellar population.  We further assume that $v_w$ is constant with radius, i.e. that the volumetric heating rate is proportional to the local stellar density.
 
@@
 We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}; $\S\ref{sec:instability}$) that cannot be accounted for by our 1D
 time-independent model.
@@
 
-We begin by describing analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the derivation of which are given in Appendix \ref{app:rs}.
-Our results are expressed in terms of the SMBH mass $M_{\bullet}$, heating parameter $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
+We first describe analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
+Our results are expressed in terms of the SMBH mass $M_{\bullet}$, total heating rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
 
@@
 
-Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at the stagnation radius is given by (eq.~[\ref{eq:first_law}])
-\begin{align}
-T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
+Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
+\begin{align}
+T|_{r_{s}} \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
 \times 10^6\ \, v_{500}^2 \,\,{\rm K},
@@
 If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
-In this limit equation (\ref{eq:stag_analytic}) simplifies to
+In this limit, equation (\ref{eq:stag_analytic}) simplifies to
 \begin{align}
@@
 \end{align}
-where for the numerical estimate we adopt $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
+where for the numerical estimate we adopt a typical value of $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
 
@@
 \end{eqnarray}
-where we have assumed that the stagnation radius is well inside the Nuker break radius.
-Equation (\ref{eq:conduction}) shows that even in the saturated case, neglecting heat conduction results in at most an order unity error in the entropy source term for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
-Numerical experiments including conductivity are seen confirm this ($\S\ref{sec:numerical}$).
+where the stagnation radius is assume to reside well inside the Nuker break radius.
+Equation (\ref{eq:conduction}) shows that even in the case of saturated conduction, the neglect of heat conduction results in at most an order unity correction for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
+Numerical experiments including conductivity confirm this ($\S\ref{sec:numerical}$).
 
@@
 If radiative cooling becomes important, it can qualitatively alter key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdot_rad}]) is thermally unstable, where $\Lambda(T) \propto T^{-0.7}$ (see below).
-Thermal instability can lead to enhanced star formation and temporarily increases the black hole accretion rate; when coupled to feed-back processes, the latter can lead to time-dependent (e.g.
-limit cycle) behavior which is inconsistent with our assumption of steady flow (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}).
-
-Radiative cooling can, however, be stabilized if other sources of cooling dominate over it, in particular the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
+Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable (\citealt{McCourt+12} and references therein), potentially resulting in the formation of a multi-phase medium and enhanced star formation.
+Even if the hot plasma of the CNM does not condense into cold clouds, the loss of pressure can temporarily increase the black hole accretion rate; when coupled to feed-back processes, the latter can lead to time-dependent (e.g.
+limit cycle) behavior (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}), which is also inconsistent with our assumption of a steady, single-phase flow.
+
+Radiative cooling can, however, be stabilized if it is overwhelmed by other sources of cooling, namely the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
 Neglecting radiative cooling, this term is balanced at the stagnation radius by the wind heating term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.
-Thermal stability near the stagnation radius can thus be assessed by the ratio of wind heating to radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
+Thermal stability near the stagnation radius can thus be assessed by comparing the ratio of wind heating to radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
 \begin{align}
@@
 34.1).
+
 To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
@@
 that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.
+\citet{McCourt+12} have argued that cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$.
 
@@
 \begin{align}
-\frac{\dot{M}_{\rm max,TI}}{\dot{M}_{\rm edd}} \simeq
+\frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq
   {\rm min}\begin{cases}
@@
 Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence stars.
-At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars (e.g., \citealt{VossDiehl+:2009a}), while at later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
-Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages mass input is dominated by the slow AGB winds of evolved low mass stars.
-
-Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
-At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.
-As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
-Thus stellar winds contribute a potentialy important source of energy as well as mass for the CNM.
+At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars (e.g., \citealt{VossDiehl+:2009a}).
+At later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
+Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low mass stars dominates the mass budget.
+
+In Appendix \ref{app:windheat} we calculate the wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
+At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.
+We show in $\S\ref{sec:combined}$ that for the case of quasi-continueous star formation representative of the average star formation history of loss mass galaxies, the stellar wind heating rate produced by stellar winds can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
+Stellar wind heating thus contributes a potentially important source of both energy and mass for the CNM.
 
@@
 Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
-\end{align} The thermal energy injected by a Ia SN, $E_{\rm Ia} \simeq
+\end{align} The thermal energy injected by each SN Ia, $E_{\rm Ia} \simeq
 \epsilon_{\rm Ia} 10^{51}$ erg, depends on the efficiency $\epsilon_{\rm Ia}$
@@
 
-The Ia SN rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
+The SN Ia rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
 In
-the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
+the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
 approximate functional form \begin{align}
@@
   \end{eqnarray}
-where the second line assumes $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (\citealt{Ciotti+91}).
+where the second line assumes $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (e.g. , \citealt{Ciotti+91}).
 
 The high value of $v_{w}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
-However, SNe can only be approximated as supplying heating which is spatially and temporally homogeneous if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
+However, SNe can only be approximated as supplying heating which is spatially and temporally homogeneous if the rate of SNe is rapid compared to the characteristic evolution time of the flow at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
 We define the ``Ia radius"
@@
 \begin{eqnarray}
-\frac{\dot{M}_{\rm max,Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
-effective heating rate (eq.~ [\ref{eq:vw_eff}])
+effective heating rate (eq.~ [\ref{eq:vw_eff}]) of 
 \begin{eqnarray} v_{w}^{\rm MSP} \approx
@@
 \subsection{Combined Heating Rate for Representative Star Formation History} 
+\label{sec:combined}
 

### 2015-02-12 ms.tex
githole2

@@
 If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be approximated as a steady heating source near the stagnation radius for extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in the case of a very young stellar population ($\tau_{\star} \ll t_{\rm h}$).
-On the other hand, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the heating rate without SN Ia is less than this.
+On the other hand, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the heating rate excluding SN Ia is less than this.
 
@@
 Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
-Hence, SN Ia are in principle capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, especially for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
-Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the accretion rate is limited to the value,
+Hence, SN Ia are in principle capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, at least for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
+Thus, even in cases when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the accretion rate is limited to a maximum value,
 \begin{eqnarray}
@@
 obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]).
-Note that $\dot{M}_{\rm max,Ia}$ usually exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm max,TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in low mass galaxies.
-Also note that this maximum Ia accretion rate only applies if the gas within the CNM is supplied by local stellar mass loss, since the quantity of gaseous mass can be much greater if is fed externally, e.g.
-due to a galactic merger.
+Note that $\dot{M}_{\rm Ia}$ usually exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
+Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.
+due to a galaxy merger or to cooling flows developing within the galaxy over much longer timescales (e.g.~\citealt{Ciotti&Ostriker07}).
 
 \subsection{Millisecond Pulsars}
- Energy injection from millisecond pulsars (MSPs) is a potentially
+ Energy injection from the spin-down of millisecond pulsars (MSPs) is a potentially
 important heating source.  If the number of MSPs per unit stellar mass
@@
 effective heating rate (eq.~ [\ref{eq:vw_eff}]) of 
-\begin{eqnarray} v_{w}^{\rm MSP} \approx
+\begin{eqnarray} v_{w}^{\rm MSP} \sim
 30\left(\frac{\epsilon_{\rm msp}}{0.1}\right)^{1/2}\left(\frac{\bar{L}_{\rm
@@
 where $\epsilon_{\rm msp}$ is the thermalization efficiency of
-the wind, normalized to a value $\epsilon \lesssim 0.1$ inferred based
-on modeling the insterstellar mediums of globular clusters
-\citep{NaimanSoares-Furtado+:2013a}.  The above estimate adopts a
-pulsar density $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$
-motivated by the $\sim 30,000$ estimated MSPs in the Milky Way of
-stellar mass $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}).
+the wind, normalized to a value $\lesssim 0.1$ based on that inferred by modeling the interstellar media of globular clusters
+\citep{NaimanSoares-Furtado+:2013a}.  Our numerical estimate assumes a
+pulsar density $n_{\rm msp} \sim 3 \times 10^{-40} $ MSPs g$^{-1}$, calculated from the estimated $\sim 30,000$ MSPs in the Milky Way (\citealt{Lorimer13}) of stellar mass $\approx 6\times 10^{10}M_{\odot}$.
 
@@
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the optimistc assumption $\epsilon_{\rm msp} = 1$.  On the other hand, the
-binaries giving rise to MSPs may be disocciated by stellar
-interactions in the dense nuclear cluster, reducing their numbers as
-compared to the field population estimate above.  MSPs are thus unlikely to be an important source of heating in comparison to stellar heating.
+under the optimistc assumption $\epsilon_{\rm msp} = 1$.  However, the
+stellar binaries giving rise to MSPs may be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
+MSPs are thus unlikely to be an important source of heating.
 

### 2015-02-12 ms.tex
githole3

@@
 \begin{align}
-  v_{w} = \sqrt{\frac{2 t_h e}{\eta \rhostar}}
+  v_{w} = \sqrt{\frac{2 t_h \dot{e}}{\eta \rhostar}}
   \label{eq:vw_eff}
 \end{align}
-for each, where $e$ is volumetric heating rate.
+for each, where $\dot{e}$ is volumetric heating rate.
 
@@
 luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
-volume $e \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
+volume $\dot{e} \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
 effective heating rate (eq.~ [\ref{eq:vw_eff}]) of 
@@
 \be
-\dot{e}_{\rm C} = 4.1\times 10^{-35}n^{2}\xi T_{\rm C}\,{\rm erg\,cm^{-3}\,s^{-1}},
+\dot{e} = 4.1\times 10^{-35}n^{2}\xi T_{\rm C}\,{\rm erg\,cm^{-3}\,s^{-1}},
 \ee
@@
 for an advective accretion flow expected to produce high $T_{\rm C}$
-emission (e.g.~\citealt{Narayan&Yi95}).  If heating is provided by
-Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
+emission (e.g.~\citealt{Narayan&Yi95}).
+Note that, unlike stellar wind heating, Compton heating depends on radius as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
+$\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
+
+If heating is provided by Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
 (\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
-
 \begin{align} v_{w}^{\rm C} \simeq

### 2015-02-12 ms.tex
githole5

@@
 
+\subsubsection{Compton Heating}
+
 There are two types of SMBH feedback: kinetic and radiative.
@@
 
-Kinetic feedback occurs from an outflow of mass or energy from the
-viscinity of the black hole in the form of a disk wind or jet, which
-deposits its energy across a much wider range of radii (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).  If the total
-outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
-\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an
-efficiency factor.  Assuming that this energy is deposited uniformly
-out to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
+\subsubsection{Kinetic Feedback}
+
+Kinetic feedback results from outflows of energy or momentum from near the black hole in the form of a disk wind or jet, which deposits its energy across a potentially much larger range of radii (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
+
+Assume that the jet or disk outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
+\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
+If this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
 heat}^{3}$, then the volumetric heating rate $e = \epsilon_{\rm
@@
 the stagnation radius given by
-
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
@@
 \end{eqnarray} 
-
-where we have used the fact that $\dot{M} \approx \eta M_{\rm
-enc}(r_{\rm s})/t_{\rm h}$ and that $M_{\rm enc}(r) \propto
-M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ for radii interior to the outer
-break radius (eq.~[\ref{eq:rhostar}]).  Thus for $r_{\rm heat} \sim
-r_{\rm s}$, even a modest heating efficiency $\epsilon_{\rm j} \gtrsim
+where we have used the facts that $\dot{M} = \eta M_{\rm
+enc}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\rm enc}(r) \propto
+M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).  If the outflow deposits much of its energy close to the sphere of influence, $r_{\rm heat} \sim
+r_{\rm s}$, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
 10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources
-of non-accretion powered heating.  However, if the jet distributes its
-energy on much larger scales comparable to the size of the galaxy,
-i.e. $r_{\rm heat} \gtrsim $ kpc $\gtrsim 10^{3}r_{\rm s}$ then the
-heating rate would be much less significant, even for an efficient jet
-($\epsilon_{\rm j} \sim 1$).
+of non-accretion powered heating.
+However, if the disk outflow instead distributes energy over much larger scales comparable to the size of the galaxy, i.e.
+$r_{\rm heat} \gtrsim $ kpc $\sim 10^{3}r_{\rm s}$, then even for an efficient jet ($\epsilon_{\rm j} \sim 1$) the heating from kinetic feedback is unimportant compared to other local sources.
 

### 2015-02-12 ms.tex
githole6

@@
 
-Kinetic feedback results from outflows of energy or momentum from near the black hole in the form of a disk wind or jet, which deposits its energy across a potentially much larger range of radii (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
-
-Assume that the jet or disk outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
-\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor.
-If this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
-heat}^{3}$, then the volumetric heating rate $e = \epsilon_{\rm
-j}\dot{M}c^{2}/V_{\rm heat}$ results in an effective wind velocity at
-the stagnation radius given by
+Kinetic feedback results from outflows of energy or momentum in the form of a disk wind or jet from close to the black hole, which deposits its energy over much larger radial scales (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
+
+Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
+\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor, and that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
+heat}^{3}$.  The resulting volumetric heating rate $\dot{e} = \epsilon_{\rm
+j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius produces an effective wind velocity given by
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
@@
 \end{eqnarray} 
-where we have used the facts that $\dot{M} = \eta M_{\rm
-enc}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\rm enc}(r) \propto
-M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).  If the outflow deposits much of its energy close to the sphere of influence, $r_{\rm heat} \sim
-r_{\rm s}$, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
+where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
+M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
+If most of the outflow energy is released close to the stagnation ardius, $r_{\rm heat} \sim r_{\rm s}$, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
 10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources
@@
 However, if the disk outflow instead distributes energy over much larger scales comparable to the size of the galaxy, i.e.
-$r_{\rm heat} \gtrsim $ kpc $\sim 10^{3}r_{\rm s}$, then even for an efficient jet ($\epsilon_{\rm j} \sim 1$) the heating from kinetic feedback is unimportant compared to other local sources.
+$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then even for an efficient jet, kinetic feedback is unimportant.
 
@@
 
-The total gas heating rate $\vwO$ includes contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
-The strength of each heating source will depend on the SMBH mass and the star formation history in the galactic nuclear region, the latter of which will vary systematically with the galaxy mass and hence with $\Mbh$.
+The total gas heating rate, $\vwO$, includes contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
+The strength of each heating source will depend explicitely on the SMBH mass and the star formation history in the galactic nuclear region, the latter of which will also vary systematically with the galaxy mass and hence with $\Mbh$.
+
+Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.
+These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Figure ) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).
+The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).
+At early times ($\tau_{\star} \lesssim XXX$), stellar wind heating dominates, but at later times Compton heating dominates.
+MSP heating is again found to be negligible at all black hole masses.
+Epochs of thermally-unstable accretion are shown as a dashed line, indicating that Compton heating becomes important only during the phase of unstable accretion.
+
+From Figure X we conclude that thermally unstable accretion is the norm.
+However, a single burst of star formation does not describe the average star formation histories of most galaxies.
 Qualitatively, smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.
-Larger galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
-
-The average star formation history as a function of $\Mbh$ and the $\vwO$ for each heating source is estimated by using the average cosmic star formation histories determined by \citet{MosterNaab+:2013a}.
-As described in detail in Appendix \ref{app:windheat}, the average star formation history is used to estimate the stellar wind heating $v_{\rm w}^{\star}$ and the mass input parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]), the latter of which also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}])
-
-Figure~\ref{fig:vwSources} shows $\vwO$ from each heating source (stars, MSPs, SNe Ia, and black hole
-feedback) as a function of black hole mass.
-MSP heating is found to be negligible at all black hole masses.
+Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
+The average value of $\vwO$ is estimated as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
+Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
+
+Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole
+feedback).
+MSP heating is again found to be negligible at all black hole masses.
 The young stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$ results in $v_{w}^{\star}$ being dominant.
-For $\Mbh\gsim 10^{7.5} \Msun$ , the younger stellar population with their energetic
-stellar winds is dead, and Compton heating plays an important role.
+For $\Mbh\gsim 10^{7.5} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, but Compton heating plays an important role.
 

### 2015-02-12 ms.tex
githole7

@@
 Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.
-These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Figure ) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).
+These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).
 The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).

### 2015-02-12 windheat.tex
githole7

@@
 \end{align} 
-where the first and second terms in each expression corresponds to contributions from main sequence (MS) stars and post-main sequence (PMS) stars, respectively.
-Here $ f_{\rm MS} < 1$ is the efficiency with which main sequence winds thermalize their energy with the rest of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$ is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean stellar mass.
+where the first and second terms in each expression corresponds to
+contributions from main sequence (MS) stars and post-main sequence
+(PMS) stars, respectively.  Here $ f_{\rm MS} < 1$ is the efficiency
+with which main sequence winds thermalize their energy with the rest
+of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
+is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim
+M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at
+$100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is
+the corresponding mean stellar mass.
 
@@
 \end{align}
-The wind velocity of main sequence winds $v_w (\Mstar, t)$ is assumed
-to equal 430 km s$^{-1}$, corresponding to the escape speed of the
-Sun; this produces an effective wind heating velocity for main
-sequence winds alone of $XXX$, in agreement with the value of 150 km
-s$^{-1}$ found by \citet{NaimanSoares-Furtado+:2013a} based on a more
-sophisticated population synthesis treatment. {\bf BDM: true?
-  correct}...{\bf AG: Wind velocity should depend on stellar
-  properties like escape speed. But choose normalization so that we
-  get the correct vw for the sun.}
+The wind velocity of main sequence winds is assumed
+to equal $v_w (\Mstar, t) = v_{w,\odot}(M_{\star}/M_{\odot})^{1/2}(R_{\star}/R_{\odot})^{-1/2}$, i.e.~scaling as the stellar escape velocity and normalized to the velocity of the solar wind $v_{w,\odot} = 430$ km s$^{-1}$; this produces an effective wind heating velocity for main
+sequence winds alone of $\sim 100$ km s$^{-1}$ for $\tau_{\star} \sim t_{\rm h}$, close to the value found by \citet{NaimanSoares-Furtado+:2013a} for globular clusters based on a more
+sophisticated population synthesis treatment.
 
@@
 \caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
-  a stellar population of age $\tau_{\star}$.}
+  a stellar population of age $\tau_{\star}$  {\bf BDM: combine with above figure into one}.}
 \end{figure}

### 2015-02-20 ms.tex
adding sty
Incoporating new figures into text.

@@
 \newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
-\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
+\newcommand{\MdotEdd}{\dot{M}_{\rm Edd}}
 \newcommand{\Mdotb}{\dot{M}_{\rm bondi}}
@@
   \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a function of radius (solid lines) for each of our solutions shown in Figure \ref{fig:profiles}.
-Dashed lines show for comparison the ratio of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
-For high heating rates both ratios are approximately equal at the stagnation radius (marked as squares).
-When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff} \lesssim 10$, the flow is susceptible thermal instabilities.
-{\bf BDM: change y axis labels to qdotheat/qdotrad, tcool/tff}.}
+  \caption{\label{fig:cooling} Ratio of the rate of heating to
+radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
+function of radius (solid lines) for each of our solutions shown in
+Figure \ref{fig:profiles}.  Dashed lines show for comparison the ratio
+of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
+For high heating rates both ratios are approximately equal at the
+stagnation radius (marked as squares).  When $\dot{q}_{\rm
+heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
+\lesssim 10$, the flow is susceptible thermal instabilities.  {\bf
+BDM: change y axis labels to qdotheat/qdotrad, tcool/tff}.}
 \end{figure}
@@
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 106 \eta_{0.02}^{0.21}T_{\rm
+  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
 C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
-&, \text{core}\\ 76 \eta_{0.02}^{0.29}T_{\rm
+&, \text{core}\\ 130 \eta_{0.02}^{0.29}T_{\rm
 C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
@@
 
-The total gas heating rate, $\vwO$, includes contributions from stellar winds, supernovae, pulsars, and SMBH feedback.
-The strength of each heating source will depend explicitely on the SMBH mass and the star formation history in the galactic nuclear region, the latter of which will also vary systematically with the galaxy mass and hence with $\Mbh$.
-
-Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.
-These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).
-The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).
-At early times ($\tau_{\star} \lesssim XXX$), stellar wind heating dominates, but at later times Compton heating dominates.
-MSP heating is again found to be negligible at all black hole masses.
-Epochs of thermally-unstable accretion are shown as a dashed line, indicating that Compton heating becomes important only during the phase of unstable accretion.
-
-From Figure X we conclude that thermally unstable accretion is the norm.
-However, a single burst of star formation does not describe the average star formation histories of most galaxies.
-Qualitatively, smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.
-Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
-The average value of $\vwO$ is estimated as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
-
-Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole
-feedback).
-MSP heating is again found to be negligible at all black hole masses.
-The young stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$ results in $v_{w}^{\star}$ being dominant.
-For $\Mbh\gsim 10^{7.5} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, but Compton heating plays an important role.
+The total gas heating rate, $\vwO$, includes contributions from
+stellar winds, supernovae, pulsars, and SMBH feedback.  The strength
+of each heating source will depend explicitely on the SMBH mass and
+the star formation hstory in the galactic nuclear region, the latter
+of which will also vary systematically with the galaxy mass and hence
+with $\Mbh$.
+
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a
+function of time $\tau_{\star}$ after a burst of star formation for a
+black hole masses of $\Mbh = 10^{6} \Msun$.  These heating
+rates are calculated using the stellar wind heating $v_{\rm
+  w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$
+(Fig.~\ref{fig:eta}), the latter of which affects the other sources of
+feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}],
+[\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$;
+eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$;
+eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a
+convolution of the star formation history and the Ia delay-time
+distribution (eq.~[\ref{eq:DTD}]).  At very early times ($\tau_{\star}
+\lesssim XXX$), stellar wind heating dominates, but at later times
+Compton heating dominates.  MSP heating is again found to be
+negligible at all black hole masses.  Epochs of thermally-unstable
+accretion are shown as a dashed line, indicating that Compton heating
+becomes important only during the phase of unstable accretion.
+
+From Figure~\ref{fig:vwSourcesImp} we conclude that thermally unstable accretion is the
+norm.  However, a single burst of star formation does not describe the
+average star formation histories of most galaxies.  Qualitatively,
+smaller galaxies will on average have more recent star formation,
+resulting in energetic young stellar winds and supernovae which
+dominate the energy budget, resulting in a high heating rate of $\vwO
+\sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on
+average have older stellar populations, with their heating rates
+dominated by Ia supernovae (on large radial scales) and SMBH feedback.
+The average value of $\vwO$ is estimated as a function of SMBH mass
+for each heating source by calculating its value using the average
+cosmic star formation histories of \citet{MosterNaab+:2013a}.
+Appendix \ref{app:windheat} describes how the average star formation
+history is used to determine the stellar wind heating $v_{\rm
+  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
+
+Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
+source (stars, MSPs, SNe Ia, and black hole feedback).  MSP heating is
+again found to be negligible at all black hole masses.  The young
+stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$
+results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 10^{7.5}
+\Msun$, the lack of younger stellar populations reduces the role of
+stellar wind heating, but Compton heating plays an important role.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
+\caption{\label{fig:vwSourcesImp} Blah Blah}
+\end{figure}
 
@@
 \includegraphics[width=\columnwidth]{eta.pdf}
-\caption{\label{fig:eta} Parameter  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories from \citet{MosterNaab+:2013a} for galaxies with halo masses corresponding to $\Mbh$.
-}
+\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
+  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
+  $\Mbh$, calculated for average star formation histories from
+  \citet{MosterNaab+:2013a}  Note that the star
+  formation histories in \citet{MosterNaab+:2013a} are in terms of
+  halo mass and for each $\Mbh$ we assign the halo mass,
+  whose star formation history would produce a bulge consistent with
+  the $\Mbh-M_{\rm bulge}$ relationship from
+  \citet{McConnellMa:2013a}.}
 \end{figure}
@@
 
-Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
+Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
+core (blue) and cusp (green) galaxies superimposed with x-ray
+measurements (red stars), upper limits (red triangles) from
+\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
+\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
+calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
+the wind heating parameter, $\vw$, and the mass return parameter,
+$\eta$ set by the average star formation history for each $\Mbh$ (see
+the black lines in Figures~\ref{fig:vwSource} and~\ref{fig:eta}). We
+try two different prescriptions for $\epsilon$: 
+$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
+\Mdot/0.01 \MdotEdd$ right-hand panel.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{miller.pdf}
+\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
+  from our models compared to $L_X/L_{Edd}$ values (red stars) and
+  upper limits (red triangles) from \citet{Miller+15}.
+  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
+  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
+  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
+  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
+  from equation~\eqref{eq:mdot_analytic}. The wind heating
+  parameter, $v_w$ and mass return parameter, $\eta$, calculated for
+  the average star formation histories in \citet{MosterNaab+:2013a}
+  (the black lines in Figures~\ref{fig:vwSources}
+  and~\ref{fig:eta}). Note that the star formation histories in
+  \citet{MosterNaab+:2013a} are in terms of halo mass and for each
+  $\Mbh$ we assign the halo mass, whose star formation history would
+  produce a bulge consistent with the $\Mbh-M_{\rm bulge}$
+  relationship from \citet{McConnellMa:2013a}.  We also show upper
+  limits $\epsilon_X \Mdot c^2/L_{edd}$ from thermal stability
+  (purple) and Ia supernovae (orange).}
+\end{figure*}
+
+% Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
 Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.
@@
 
-One possible solution that the wind mass loss rate $\eta$ increases
-with $\Mbh$, as would be expected if low mass SMBH preferentially
-hosted younger stellar populations.  Another possible explanation is
-that the effective heating rate of the CNM $v_{w}$ decreases
-with decreasing SMBH mass.  This could again be due to an older
-stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
-sources such as SN Ia and millisecond pulsars.
-{\bf AG given our new results on stellar wind heating as a function of
-Mbh. It seems like the first statement is indeed true but I suspect
-vwO actually increases for low Mbh and that this effect actually dominates.}
+% One possible solution that the wind mass loss rate $\eta$ increases
+% with $\Mbh$, as would be expected if low mass SMBH preferentially
+% hosted younger stellar populations.  Another possible explanation is
+% that the effective heating rate of the CNM $v_{w}$ decreases
+% with decreasing SMBH mass.  This could again be due to an older
+% stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
+% sources such as SN Ia and millisecond pulsars.
+% {\bf AG given our new results on stellar wind heating as a function of
+% Mbh. It seems like the first statement is indeed true but I suspect
+% vwO actually increases for low Mbh and that this effect actually dominates.}
 %, or it could be due to the fact that Ia occur too infrequently inside

### 2015-02-20 ms.tex
Reworking description of the instantaneous heating rate.

@@
 
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a
-function of time $\tau_{\star}$ after a burst of star formation for a
-black hole masses of $\Mbh = 10^{6} \Msun$.  These heating
-rates are calculated using the stellar wind heating $v_{\rm
-  w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$
-(Fig.~\ref{fig:eta}), the latter of which affects the other sources of
-feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}],
-[\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$;
-eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$;
-eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a
-convolution of the star formation history and the Ia delay-time
-distribution (eq.~[\ref{eq:DTD}]).  At very early times ($\tau_{\star}
-\lesssim XXX$), stellar wind heating dominates, but at later times
-Compton heating dominates.  MSP heating is again found to be
-negligible at all black hole masses.  Epochs of thermally-unstable
-accretion are shown as a dashed line, indicating that Compton heating
-becomes important only during the phase of unstable accretion.
-
-From Figure~\ref{fig:vwSourcesImp} we conclude that thermally unstable accretion is the
-norm.  However, a single burst of star formation does not describe the
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various
+heating sources as a function of time $\tau_{\star}$ after a burst of
+star formation for a black hole masses of $\Mbh = 10^{6} \Msun$ (top
+panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The stellar wind
+heating is calculated as described in appendix~\ref{app:windheat}. The
+and Ia heating ($v_{w}^{\rm Ia}$) and compton heating ($v_{\rm
+  w}^{\bullet}$) are calculated using equations~\eqref{eq:vIa}
+and~\eqref{eq:vC} respectively. Both heating sources depend on the
+value of the mass return parameter, $\eta$. We have plotted this for a
+burst of star formation Figure~\ref{fig:etaImp}.  The Ia heating rate
+also depends be a convolution of the delay time distribution
+(eq. [\ref{eq:DTD}]) and the star formation history. This convolution
+reduces to the delay time distribution itself for a burst of star
+formation. To account for the non-steady nature of the Ia heating we
+multiply the Ia heating by $e^{-\rs/\rIa}$, where $\rIa$ is the radius
+where the time between subsequent supernovae is equal to the local
+dynamical time. The heating contribiution from
+Ia supernovae will be suppressed if the time between successive
+supernovae is much greater than the dynamical time at $\rs$. Note that
+both $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ depend on the
+total heating rate (all of the heating sources added in quadrature),
+and so we have to solve a system of impllicit eqautions for these.
+The MSP contribution is negligible for both cases and is not plotted.
+
+The overall heating rate declines with time and after some time the
+flow would become thermally unstable. The epoch when this occurs is
+shown by dashed lines in Figure~\ref{fig:vwSourcesImp}. In calculating
+this transition we have not included the compton heating. However,
+this would not be able stabilize flow as it would not respond
+immediately to cooling instabilities. Thus, if Compton
+heating is the dominant source of heating we do not expect a steady,
+thermally stable flow. Thermal instability is the norm in the burst
+limit except for very early times ($\lsim 10^7$ years) and small
+$\Mbh$ ($\Mbh\simeq 10^6 \Msun$).
+
+However, a single burst of star formation does not describe the
 average star formation histories of most galaxies.  Qualitatively,

### 2015-02-20 ms.tex
More

@@
   and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
-  from equation~\eqref{eq:mdot_analytic}. The wind heating
-  parameter, $v_w$ and mass return parameter, $\eta$, calculated for
-  the average star formation histories in \citet{MosterNaab+:2013a}
-  (the black lines in Figures~\ref{fig:vwSources}
-  and~\ref{fig:eta}). Note that the star formation histories in
-  \citet{MosterNaab+:2013a} are in terms of halo mass and for each
-  $\Mbh$ we assign the halo mass, whose star formation history would
-  produce a bulge consistent with the $\Mbh-M_{\rm bulge}$
-  relationship from \citet{McConnellMa:2013a}.  We also show upper
-  limits $\epsilon_X \Mdot c^2/L_{edd}$ from thermal stability
-  (purple) and Ia supernovae (orange).}
+  from equation~\eqref{eq:mdot_analytic}, with the wind heating
+  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
+  the the average star formation histories in
+  \citet{MosterNaab+:2013a} (the black lines in
+  Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Note that the star
+  formation histories in \citet{MosterNaab+:2013a} are in terms of
+  halo mass and for each $\Mbh$ we assign the halo mass, whose star
+  formation history would produce a bulge consistent with the
+  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
+  We also show upper limits $\epsilon_X \Mdot c^2/L_{edd}$ from
+  thermal stability (purple) and Ia supernovae (orange).}
 \end{figure*}

### 2015-02-20 ms.tex
Bandara begone.

@@
 $\eta$ set by the average star formation history for each $\Mbh$ (see
-the black lines in Figures~\ref{fig:vwSource} and~\ref{fig:eta}). We
+the black lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). We
 try two different prescriptions for $\epsilon$: 
@@
   \citet{MosterNaab+:2013a} (the black lines in
-  Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Note that the star
-  formation histories in \citet{MosterNaab+:2013a} are in terms of
-  halo mass and for each $\Mbh$ we assign the halo mass, whose star
-  formation history would produce a bulge consistent with the
-  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
-  We also show upper limits $\epsilon_X \Mdot c^2/L_{edd}$ from
+  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
+  Appendix~\ref{windheat} for a detailed description)).
+  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
   thermal stability (purple) and Ia supernovae (orange).}

### 2015-02-20 windheat.tex
Bandara begone.

@@
 
-We estimate the stellar wind heating provided by the {\it average} star formation history of galaxies of a given mass using the results of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]) and the $M_{\bullet}-M_{\rm
-  halo}$ relation from \citet{BandaraCrampton+:2009a}.
-Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.
+We estimate the stellar wind heating provided by the {\it average}
+star formation history of galaxies of a given $\Mbh$ using the results
+of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]).  Note that the
+star formation histories in \citet{MosterNaab+:2013a} are in terms of
+halo mass. For a given $\Mbh$ we assign the halo mass whose star
+formation history would produce a bulge consistent with the
+$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
+
+ % Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.
 For comparison we also show cases in which the star formation rate is modulated sinuisoidally from its average value.
@@
 {\bf AG: this plot still uses the old ad hoc vw
-  prescription? If so it would need to be fixed. In any case, we still
-  differ in detail on the vw from stars}.
+  % prescription? If so it would need to be fixed. In any case, we still
+  % differ in detail on the vw from stars}.
 

### 2015-02-20 ms.tex
Start on impulsive caption

@@
 \includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
-\caption{\label{fig:vwSourcesImp} Blah Blah}
+\caption{\label{fig:vwSourcesImp} Most important sources of heating
+  after a burst of star formation for $\Mbh=10^6 \Msun$ (top panel)
+  and $\Mbh= 10^8 \Msun$ (bottom panel). We also show the velocity
+  dispersion from the $\Mbh-\sigma$ relationship as a horizontal gray line
+  \citep{Gultekin+09}.}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{miller.pdf}
-\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
-  from our models compared to $L_X/L_{Edd}$ values (red stars) and
+\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
+  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
   upper limits (red triangles) from \citet{Miller+15}.
@@
   Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
-  Appendix~\ref{windheat} for a detailed description)).
+  Appendix~\ref{app:windheat} for a detailed description).
   We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from

### 2015-02-20 ms.tex
Minor changes

@@
 again found to be negligible at all black hole masses.  The young
-stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$
-results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 10^{7.5}
+stellar populations in galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$
+results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 5\times 10^{8}
 \Msun$, the lack of younger stellar populations reduces the role of
@@
 
-Figure~\ref{fig:cooling2} shows the ratio of heating to radiative
-cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a
-function of SMBH mass, using our total heating rate from Figure
-\ref{fig:vWsources}.  The combined heating rate from stellar winds and
-Compton heating is insufficient to prevent thermal instability for the
-high $\Mbh$.  However, if Ia supernovae are included in the schematic
-way described above, the flow again becomes thermally stable for $\Mbh
-\gtrsim XXXX$.
+The bottom panel of Figure~\ref{fig:vwSources} shows the ratio of
+heating to radiative cooling at the stagnation radius
+(eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total
+heating rate from the top panel Figure \ref{fig:vwSources}.  The
+combined heating rate from stellar winds and Compton heating is
+insufficient to prevent thermal instability for the high $\Mbh$.
+{\bf AG: Should we really be talking about Compton heating stabilizing
+the flow}?
+% However, if Ia supernovae are included in the schematic way described
+% above, the flow again becomes thermally stable for $\Mbh \gtrsim
+% XXXX$.
 
@@
   \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
-  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
+  blue curves represent our predictions for core ($\Gamma=0.1$)
   and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated

### 2015-02-20 ms.tex
hi

@@
 \begin{document}
-\title{Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
+\title{Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes}
 \maketitle
@@
 \begin{abstract}
-We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
-Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
-Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.
-We assess the conditions under which radiative instabilities will develop absent black hole feedback, based on the heating supplied by the average star formation history for galaxies corresponding to a given black hole mass.
-Results for the average accretion rate, as well as the maximum thermally-stable and -unstable accretion rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.
-We determine that the measured high accretion rates and short growth times of low mass black holes in the local universe must be the result of an external gas supply, rather than secular processes resulting from stellar mass loss within the galactic nucleus.
+We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of nominally quiescent galaxies for a range of central black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
+Mass is supplied to the circumnuclear medium by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
+Analytic estimates are provided for the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of black hole mass and the gas heating efficiency, the latter of which is related to the star-formation history.
+We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
+The nuclear X-ray luminosities of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
+The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.
+The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
+The accretion rate estimated in the latter case, as well as the maximum thermally-stable and thermal-unstable rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.
 We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.

### 2015-02-20 ms.tex
working

@@
 The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
-The accretion rate estimated in the latter case, as well as the maximum thermally-stable and thermal-unstable rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.
-We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
+We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of circumnuclear environments encountered by the jetted outflows from tidal disruption events.
 \end{abstract}
@@
 
-To determine why most SMBHs appear to be inactive requires an understanding of their gaseous environments.
-Hot gas near the sphere of influence of the SMBH (hereafter the `circumnuclear medium', or CNM) controls the mass accretion rate, $\dot{M}$.
-The latter in turn sets the luminosity of the accretion flow and the impact of its energy and momentum input (`feedback') on larger physical scales.
-The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty star-formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
+Understanding why most SMBHs appear to be inactive requires characterizing their gaseous environments.
+Gas near the sphere of influence of the SMBH, hereafter the `circumnuclear medium' (CNM), controls the mass accretion rate, $\dot{M}$.
+The accretion rate in turn sets the luminosity of the black hole and the impact of this energy and momentum output on larger physical scales (`feedback').
+The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty episodes of star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
 
@@
 However, the physical processes involved in the growth of loss mass blacks may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
-One important question is whether SMBHs grow primarily by accreting gas which is fed directly from large scales, or whether some of the growth growth results from internal or secular processes such as stellar mass loss.
-
-The accretion rates of low mass SMBHs have implications for observational constraints on the occupation fraction of SMBHs in low mass galaxies, and the potential existence of intermediate mass black holes.
+A key question here is whether SMBHs grow primarily by accreting gas fed in directly from large scales, or whether significant growth results also from internal, secular processes such as local stellar mass loss.
+
+Obtaining a better undersatnding of the physical mechanisms responsible for accretion onto quiescent SMBHs would have implications for observational constraints on the occupation fraction of SMBHs in low mass galaxies, and the potential existence of intermediate mass black holes.
 \citet{Miller+15} combine the average correlation between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample of elliptical galaxies to infer tentative evidence for a SMBH occupation fraction less than unity in galaxies with stellar masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim 10^{7}M_{\odot}$).
-This method relies on extrapolating a power-law fit of the $L_X-\Mbh$ distribution to low values of $\Mbh$ (and hence $L_{\rm X}$) below the detection threshold, despite the potential for very different physics to control the accretion rates onto the lowest mass SMBHs.
+This method relies on extrapolating a power-law fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below the detection threshold, despite the potential that rather different physical processes control the accretion rates onto the lowest mass SMBHs.
 
@@
 
-Past studies, employing multi-dimensional numerical hydrodynamics and including variety of (parameterized) physical effects, have focused on massive elliptical galaxies (Ciotti refs).
+Past studies, employing multi-dimensional numerical hydrodynamics and including variety of (parameterized) physical effects, have focused on massive elliptical galaxies (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
 A key finding of these works is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate until black hole feedback becomes sufficiently important to shut off the flow and halt SMBH growth.
@@
 This approach allows us to systematically explore the relevant parameter space and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties manifest across the expected range of galaxy properties, or whether other (non-AGN) forms of feedback can result in steady accretion.
-Even if cooling instabilties develop on galactic scales over long timescales, quasi-steady accretion may persist for briefer periods on small scales.
-We are thus motivated to explore whether steady flow is achieved under any circumstances, or whether accretion is always building towards instability.
+Even if cooling instabilties develop on galactic scales over longer timescales, e.g.
+$\sim$ Gyr, a state of quasi-steady accretion may exist between these inflow events on smaller radial scales comparable to the sphere of influence.
+We are thus motivated to explore whether steady flow is achieved within the nucleus under any circumstances, or whether the gas content is always building towards instability.
 %A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
@@
 relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
-$\S\ref{sec:summary}$ we summarize our results.
+$\S\ref{sec:summary}$ we summarize our results.  Table \ref{table:definitions} provides the definitions of commonly used variables.
+
+\begin{table*}
+\begin{threeparttable}
+%\centering
+\begin{minipage}{18cm}
+\caption{Definitions of commonly used variables}
+\begin{tabular}{lc}
+\hline
+{Variable} & {Definition} \\
+\hline
+$M_{\bullet}$ & Black hole mass \\
+$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
+$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
+$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
+$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
+$r_{\rm b}$ & outer break radius of stellar density profile \\  
+\hline
+\label{table:definitions}  
+\end{tabular}
+\begin{tablenotes}
+\item{$^{(a)}FILL IN$}
+\end{tablenotes}
+\end{minipage}
+\end{threeparttable}
+
+\end{table*}
+
 \section{Model}
@@
 yr.
-To good approximation $\eta\simeq 0.02 (t_{\star}/t_h)^{-1.3}$ at time $t_{\star}$ following an impulsive star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return rate from evolved stars as a function of B-band luminosity instead of volumetrically, but our expressions are equivalent.}, although $\eta$ is significantly higher for continuous star formation histories (Fig.~\ref{fig:eta}).
+To good approximation $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ at time $\tau_{\star}$ following an impulsive star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return rate from evolved stars as a function of B-band luminosity instead of volumetrically, but our expressions are equivalent.}, although $\eta$ is significantly higher for continuous star formation histories (Fig.~\ref{fig:eta}).
 
@@
 where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r_{\rm B})^{1/2}$ and $\lambda$ is a parameter of order unity.
+
 One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $r_{\rm B}$ is replaced by $\rs$.
@@
 Neglecting radiative cooling, this term is balanced at the stagnation radius by the wind heating term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.
-Thermal stability near the stagnation radius can thus be assessed by comparing the ratio of wind heating to radiative cooling $|\dot{q}_{\rm cool}|$ (eq.~[\ref{eq:qdot_rad}]),
+Thermal stability near the stagnation radius can thus be assessed by comparing the ratio of wind heating to radiative cooling $|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:qdot_rad}]),
 \begin{align}

### 2015-02-20 ms.tex
working2

@@
 In this limit, equation (\ref{eq:stag_analytic}) simplifies to
-\begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx 6
- \, \pc \,\, \Mbheight v_{500}^{-2}\,\,\,\,(v_{\rm w} \gtrsim \sigma),
+\begin{eqnarray}
+  &\rs \underset{v_w \gtrsim \sigma}\approx \frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx \begin{cases}
+    12
+ \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
+    6
+ \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
+  \end{cases}
   \label{eq:stag_simple}
-\end{align}
-where for the numerical estimate we adopt a typical value of $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
+\end{eqnarray}
+where for the numerical estimate we adopt values of $n \approx 1$ and $n \approx 0.5$ for core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies, respectively, so chosen to match the results of our numerical calculations (Fig.~\ref{fig:stag}).
+This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
+{\bf BDM: all analytic expressions have to be updated in core case to reflect this larger rs}
 
@@
 \end{eqnarray}
-where we have assumed $v_{w} \gg \sigma$ by adopting equation (\ref{eq:stag_simple}) for $r_s$, and we have divided our results into core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.
-The resulting Eddington ratio is given by
+where we have assumed $v_{w} \gg \sigma$ by adopting equation (\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is given by 
 \begin{eqnarray}
@@
 Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
-For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$ and $\tcool/\tff \lesssim 1,$ depending on the wind mass loss parameter $\eta$.
+For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$ can be less than unity, depending on the wind mass loss parameter $\eta$.
 At the stagnation radius, the ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor of two of its minimum across the entire grid;  thus, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a diagnostic of thermal instabilty for the entire solution.

### 2015-02-20 ms.tex
working2

@@
 0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
-stagnation radius.  $^{(e)}$ Is solution thermally unstable?
+stagnation radius.  Thermally unstable solutions are shown in bold text.  $^{(e)}$ Is solution thermally unstable?
 $\dagger$Calculated including radiative cooling, assuming $\eta =
@@
   according to our thermal instability. I am worried that this
-  solution may not be representative due to the small break radius.}
+  solution may not be representative due to the small break radius. BDM: change TI column to simply bolding tcool ratio in those cases which are thermally unstable.}
 \end{tablenotes}

### 2015-02-21 ms.tex
working3

@@
 that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.
-\citet{McCourt+12} have argued that cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$.
+\citet{McCourt+12} argue cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$, so equation (\ref{eq:cooling2}) represents a good proxy for instability in this case as well.
 
@@
 
-The results of our numerical calculations are uses to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.
-Our results are summarized in Table \ref{table:models} and Figure XXX.
-Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.
+Our numerical results, summarized in Table \ref{table:models} and Figure XXX, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
+Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
 

### 2015-02-21 ms.tex
mopping up appendix B

@@
 Cusp and core galaxies are marked with square and triangles, respectively.
-Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively.
-Our analytic estimates provide accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but they break down for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
+Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively, calculated assuming $n = 1$ and $n= 0.5$, respectively.
+Our analytic estimates are found to provide accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but the assumptions leading to these estimates become invalid for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
 For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
-The three vertically-aligned green squares located at the same value of $v_{w}/\sigma$ close to where the solid analytic line diverges correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
+The three green squares which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
+As $r_{\rm b} \rightarrow r_{s}$, the effects of the break radius is to the push the stagnation radius inwards, decreasing the SMBH accretion rate.
 %% AG: Describe conservation checks to additionally validate the results.
@@
 
-Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence stars.
+Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence populations.
 At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars (e.g., \citealt{VossDiehl+:2009a}).
 At later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
-Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low mass stars dominates the mass budget.
-
-In Appendix \ref{app:windheat} we calculate the wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).
+Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low-mass stars dominates the mass budget.
+
+In Appendix \ref{app:windheat} we calculate the wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a stellar population which is formed impulsively (Fig.~\ref{fig:vwimp}).
 At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.
@@
 value of the mass return parameter, $\eta$. We have plotted this for a
-burst of star formation Figure~\ref{fig:etaImp}.  The Ia heating rate
+burst of star formation in Figure~\ref{fig:vwImp}.  The Ia heating rate
 also depends be a convolution of the delay time distribution

### 2015-02-21 windheat.tex
mopping up appendix B

@@
 of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
-is the IMF, which we take to be of the Salpeter form $\mu(\Mstar)\sim
-M^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at
+is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar} \propto
+M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at
 $100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is
@@
 \end{align}
-where $M_{\rm TO}$ is the turn-off mass, which at time $t$ is calculated as
+where $M_{\rm TO}$ is the turn-off mass, which at time $t < t_{\rm h}$ is calculated as
 \begin{align}
@@
 \citet{CiottiOstriker:2007a} (their eq.~[9]) for intermediate and late
-times ($t \gsim 10^8$ years). {\bf AG: Mathematical aside--this
-  expression divereges for $t \gg t_{\rm hubble}$}
+times ($t \gsim 10^8$ years).
 
@@
 \end{align}
-while {\bf AG: eta expression is now fixed--note that
-  $\dot{\bar{m}}(t)$ is the mass injection rate per stellar mass, so
-  that eta is dimensionless as it should be }
+while 
 \begin{align}
@@
 \end{align}
-We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and~\ref{fig:etaImp}.
+ Figur~\ref{fig:vwImp} shows the values of $\bar{v}_w(t)$ and $\eta(t)$ as a function of stellar age, $\tau_{\star}$.
 
@@
 \includegraphics[width=\columnwidth]{vwImp.pdf}
-\caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
-  a stellar population of age $\tau_{\star}$.}
-\end{figure}
-
-\begin{figure}
 \includegraphics[width=\columnwidth]{etaImp.pdf}
-\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
-  a stellar population of age $\tau_{\star}$  {\bf BDM: combine with above figure into one}.}
+\caption{\label{fig:vwImp} Effective heating rate, $v_w^{\star}$, and mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from a stellar population of age $\tau_{\star}$.}
 \end{figure}

### 2015-02-21 ms.tex
blop

@@
 \end{equation}
-i.e., a broken power law that transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+i.e., a broken power law that transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta > \Gamma$, at a break radius, $\rb$.
 Assuming the stellar population is spherically symmetric, this corresponds to a stellar density $\rhostar \propto r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for $r \gg \rb$.
@@
 choices of $v_{w} = 300, 600, 1200$ km s$^{-1}$ spanning a
-physically plausible range of heating rates.  Although we are interested in the
-steady-state inflow/outflow solution (assuming one exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
+physically plausible range of heating rates.
+Although we are interested in the steady-state inflow/outflow solution (assuming one exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
 inflow on small radial scales and a possible supersonic outflow on large scales.
+Also note that our solutions can be scaled to any value of the mass input parameter, $\eta$, since the mass and energy source terms scale linearly with $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be specified when cooling or thermal conduction are included, since these scale as gas density {\it squared}.
 
@@
 \begin{eqnarray}
-  \dot{M} &=& \frac{\eta \Menc|_{r_{\rm s}}}{\th} \nonumber \\
+  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta \Menc|_{r_{\rm s}}}{\th} \nonumber \\
 &\approx&

### 2015-02-21 ms.tex
fixed kinetic feedback section

@@
 At later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
-Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low-mass stars dominates the mass budget.
+Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low-mass stars dominate the mass budget.
 
@@
 
-The average spin-down luminosity of millisecond pulsars in the field
-is estimated to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$ based
-on the ATNF radio pulsar catalog (\citealt{Manchester+05}), in which
-case $v_{w}^{\rm MSP} \lesssim 30$ km s$^{-1}$.  For higher spin-down
+Based on the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate the average spin-down luminosity of millisecond pulsars in the field to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, resulting in $v_{w}^{\rm MSP} \lesssim 30$ km s$^{-1}$ for $\eta \gtrsim 0.02$.
+For higher spin-down
 luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
@@
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the optimistc assumption $\epsilon_{\rm msp} = 1$.  However, the
-stellar binaries giving rise to MSPs may be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
-MSPs are thus unlikely to be an important source of heating.
+under the most optimistc assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
+On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
 
@@
 emission (e.g.~\citealt{Narayan&Yi95}).
-Note that, unlike stellar wind heating, Compton heating depends on radius as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
+We caveat that, unlike stellar wind heating, Compton heating depends on radius as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
 $\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
+Thus, although the assumption of our numerical calculations that heating is radially constant is not satisfied, this radial dependence is sufficiently weak that we do not expect its presence to significantly alter our results.
 
@@
 \end{align} 
-
-The fact that $v_{w}^{\rm C} \lesssim 200$ km s$^{-1}$ for physically
-realized values of $\eta \lesssim 1$ shows that Compton heating alone
-is insufficient to stabilize the flow against cooling instability,
-i.e. $v_{w}^{C} < v_{\rm CI}$ (eq.~[\ref{eq:cooling2}]).
+The fact that $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for physically realized values of $\eta \gtrsim 1$ shows that Compton heating can be significant in relatively young stellar populations with relatively high mass loss rates.
 
@@
 Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
-\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is an efficiency factor, and that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
+\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor, and that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
 heat}^{3}$.  The resulting volumetric heating rate $\dot{e} = \epsilon_{\rm
@@
 
-Also note that for a fixed $r_{\rm heat}$, the effective heating rate
-$v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto
-M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
-to a negative power (where we have used of
-eq.~[\ref{eq:stag_simple}]).  This shows that SMBH kinetic heating, if
-dominant, could thus `self-regulate' insofar as a lower heating rate
-results in a higher accretion rate, which in turn results in stronger
-jet feedback.  Importantly, however, unlike in the case of local
-heating sources such as stellar winds, even a dominant SMBH heating
-may not allow for a thermally-stable steady flow because the central
-accretion rate does not respond instantaneously to changes in the
-thermodynamic properties of the gas on larger scale.  We also note
-here that the kinetic heating rate is proportional to the SMBH mass to
-a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
-core(cusp) galaxies, respectively. This dependence could have
-important implications for the dependence of the average nuclear X-ray
-luminosity of quiescent galaxies on the SMBH mass
-($\S\ref{sec:mdot}$).
-
-What is a physically motivated value of the heating radius $r_{\rm
-  heat}$?  \citet{Bromberg+11} show that a jet of luminosity $L_{\rm
+Indeed, using the results of \citet{Bromberg+11}, we estimate that a jet of luminosity $L_{\rm
   j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
-AGN jets) propagates through a gaseous mass $M_{\rm g}$ to a radius
-$r$ in a timescale
-
+AGN jets) will propagate through a gaseous mass $M_{\rm g}$ to a radius $r$ in a timescale
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-Writing $L_{\rm j} = \epsilon_{\rm j}\dot{M}c^{2}$ and approximating
-$M_{\rm g} \sim \dot{M}t_{\rm ff}$ we find that the ratio of the jet
-crossing time to the free-fall time $t_{\rm ff} \sim r/\sigma$ is
-
+If we write $M_{\rm g} \sim \dot{M}t_{\rm ff}$ then the ratio of the jet crossing time to the dynamical in the bulge $t_{\rm dyn} \sim r/\sigma$ is given by
 \begin{equation}
-\frac{t_{\rm jet}}{r/\sigma} \sim 8\times 10^{-5}\sigma_{200}^{2/3}\epsilon_{\rm j}^{-1/3},
+\frac{t_{\rm jet}}{t_{\rm dyn}} \sim 7\times 10^{-3}M_{\bullet,8}^{0.13}\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{-1/3},
 \end{equation}
-
-which is notably independent of radius $r$.  Thus we require
-$\epsilon_{\rm j} \gtrsim 10^{-12}$ for the jet to escape, and if it
-escapes it is free to travel a long distance.
+independent of radius $r$.
+Thus a jet with sufficient power, $\epsilon_{j} \gtrsim 10^{-6}$, to appreciably heat the CNM on radial scales $\sim r_{\rm s}$, also has sufficient power to escape the gas within the nucleus and propogate to much larger radii.
+Slower outflows from the accretion disk, instead of a collimated relativistic jet, may provide a more promising source of feedback in these systems (e.g.~\citealt{Li+13}).
+
+For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
+to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
+Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
+However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat deceptive because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
+Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
 
@@
 Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
+
+\subsection{Jet Feedback}
+
+We also note
+here that the kinetic heating rate is proportional to the SMBH mass to
+a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
+core(cusp) galaxies, respectively. This dependence could have
+important implications for the dependence of the average nuclear X-ray
+luminosity of quiescent galaxies on the SMBH mass
+($\S\ref{sec:mdot}$).
 

### 2015-02-21 ms.tex
rotation salvaged

@@
 
-To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.
+To isolate the physics of interest, our baseline calculations neglects three potentially important effects: heat conduction, radiative cooling, and rotation.
+Our justification for neglecting rotation will be discussed further in $\S\ref{sec:rotation}$.
 Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
@@
 
-\subsection{Importance of Heat Conduction}
+\subsection{Heat Conduction}
 \label{sec:conductivity}
@@
 
-%\input{figures/eta_tab.tex}
+  \subsection{Angular Momentum}
+  \label{sec:ang}
+
+Our spherically symmetric model neglects the effects of angular momentum on the gas evolution.
+However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$, where $l_{r_{s}} = r_{s}\langle V_{\phi}\rangle |_{r_s}$ is the specific angular momentum of stars near the stagnation radius, from which most of the accreted mass originates, and $\langle v_{\phi}\rangle$ is their average azimuthal velocity.
+
+Using two-dimensional kinematic data, \citet{EmsellemCappellari+:2007a} measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
+  \begin{align}
+    \lambda_R=\frac{\langle R|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
+  \end{align}
+where $\sigma$ is the velocity dispersion and the brackets indicate a luminosity-weighted average.  The circularization radius of the accretion flow can be written in terms of $\lambda_R$ as
+\be
+\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
+\label{eq:rcirc}
+\ee
+where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$ for the thermally-stable solutions of interest.
+
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R < 0.1$ on scales less that 10 per cent of the galaxy radius, in which case equation (\ref{eq:rcirc}) shows that $r_{\rm circ} \lesssim 0.01r_{s}$.
+Since this location lies well inside the inner sonic point of the flow, we conclude that angular momentum will only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow, justifying its neglect in calculating quantities such as the mass accretion rate.
 
@@
 
-  \subsection{Angular Momentum}
-  \label{sec:ang}
-  Our models are spherically symmetric and do not include the effects of
-  the gas' angular momentum. However, galaxies will in general have some
-  net rotation, and the gas will generally have some non-zero angular
-  momentum. At some radius, $\rcirc$, the specific angular momentum of
-  the gas will equal the specific angular momentum of a circular
-  orbit. Inside of this radius our assumptions of no rotation and
-  spherical symmetry will break down. But if $\rcirc$ is inside of the
-  inner sonic point of the flow, the region where angular momentum
-  becomes important will be causally disconnected from the rest of the
-  flow, and we would be justified in neglecting angular momentum (at
-  least on large scales).
-
-  $\rcirc$ depends on the gas injection radius. The largest
-  injection radius is $\rs$. Let $\lrs$ be the gas specific angular
-  momentum at $\rs$, then
-
-  \begin{align}
-    \rcirc=\frac{\lrs}{G \Mbh}
-  \end{align}
-
-  \citet{EmsellemCappellari+:2007a} used two-dimensional kinematic
-  data to measure the ratio of ordered to random motion in a sample of
-  early type galaxies. More precisely, they measure
-
-  \begin{align}
-    \lambda_R=\frac{\left<R|V|\right>}{\left<R\sqrt{V^2+\sigma^2}\right>}
-  \end{align}
-
-  Where $R$ is the distance is the distance from the galactic center, $V$ is
-  the mean stellar velocity, and $\sigma$ is the velocity
-  dispersion. The brackets represent a luminosity weighted average.
-
-  We may rewrite the specific angular momentum at $\rs$ in terms of
-  $\lambda_R$.
-
-  \begin{align}
-    \lrs\simeq\lambdars \sigma|_{r_{\rm s}}^2 \rs^2
-  \end{align}
-
-  Then
-
-  \begin{align}
-    \rcirc&\simeq\lambdars^2 \frac{\sigma|_{r_{\rm s}}^2}{G \Mbh} \rs^2\\
-    &\simeq\lambdars^2 \frac{\rs^2}{\rsoi} \lsim \lambdars^2 \rsoi
-  \end{align}
-
-  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
-  $\rsoi$. {\bf AG need to explain this somehow. Also, note in our
-    simulations the inner sonic point is not properly resolved.}
-  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Fig. 2 of
-  \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
-  of radius for a sample of early type galaxies. On scales of $\sim 0.1
-  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
-  of their sample %%need to be clearer on rapidly declining also compare
-  %% this scale to the sphere of influence scale.
-  This suggests that angular momentum should generally be unimportant.
-
 \section{Discussion}

### 2015-02-21 ms.tex
fixed kinetic feedback section2

@@
     galaxies ($\Gamma$=0.1). Squares mark the location of
-    the stagnation radius for each solution {\bf BDM: added colored labels for the $v_w$ value, e.g. a blue 1200 km/s directly to the top figure} .
+    the stagnation radius for each solution {\bf BDM: added colored labels for the $v_w$ value, e.g. a blue 1200 km/s directly to the top figure.  what does v/cs look like?} .
  }
@@
 We show in $\S\ref{sec:combined}$ that for the case of quasi-continueous star formation representative of the average star formation history of loss mass galaxies, the stellar wind heating rate produced by stellar winds can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
-Stellar wind heating thus contributes a potentially important source of both energy and mass for the CNM.
+Stellar winds thus contributes a potentially important source of both energy and mass for the CNM.
 
@@
 (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
-(\ref{eq:vw_eff}) that the effective Compton heating rate at the stagnation radius is given by
+(\ref{eq:vw_eff}) that the effective heating rate at the stagnation radius is given by
 \begin{align} v_{w}^{\rm C} \simeq
@@
 emission (e.g.~\citealt{Narayan&Yi95}).
-We caveat that, unlike stellar wind heating, Compton heating depends on radius as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
+We caveat that, unlike stellar wind heating, Compton heating depends on radius, scaling as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
 $\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
-Thus, although the assumption of our numerical calculations that heating is radially constant is not satisfied, this radial dependence is sufficiently weak that we do not expect its presence to significantly alter our results.
-
-If heating is provided by Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
-(\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
+The assumption of our model that the heating parameter be constant with radius is not satisfied, but this radial variation is sufficiently weak that it should not significantly alter our conclusions.
+
+If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
+(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
 \begin{align} v_{w}^{\rm C} \simeq
@@
 \end{align} 
-The fact that $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for physically realized values of $\eta \gtrsim 1$ shows that Compton heating can be significant in relatively young stellar populations with relatively high mass loss rates.
+Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.
 
@@
 
-Kinetic feedback results from outflows of energy or momentum in the form of a disk wind or jet from close to the black hole, which deposits its energy over much larger radial scales (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
+Kinetic feedback results from outflows of energy or momentum from close to the black hole in the form of a disk wind or jet, which deposits its energy as heat, e.g.
+via shocks or wave dissipation, over much larger radial scales (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
 
 Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
-\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor, and that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
+\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor.
+Further assume that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
 heat}^{3}$.  The resulting volumetric heating rate $\dot{e} = \epsilon_{\rm
-j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius produces an effective wind velocity given by
+j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a heating parameter given by
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
@@
 M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
-If most of the outflow energy is released close to the stagnation ardius, $r_{\rm heat} \sim r_{\rm s}$, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
-10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources
-of non-accretion powered heating.
-However, if the disk outflow instead distributes energy over much larger scales comparable to the size of the galaxy, i.e.
-$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then even for an efficient jet, kinetic feedback is unimportant.
-
-Indeed, using the results of \citet{Bromberg+11}, we estimate that a jet of luminosity $L_{\rm
+If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
+10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.
+However, if this energy is deposited over much larger physical scales comparable to the size of the galaxy, i.e.
+$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 1$.
+
+Using the results of \citet{Bromberg+11}, the time required for a jet of luminosity $L_{\rm
   j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
-AGN jets) will propagate through a gaseous mass $M_{\rm g}$ to a radius $r$ in a timescale
+AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated to be
 \begin{eqnarray}
@@
 \end{eqnarray}
-If we write $M_{\rm g} \sim \dot{M}t_{\rm ff}$ then the ratio of the jet crossing time to the dynamical in the bulge $t_{\rm dyn} \sim r/\sigma$ is given by
-\begin{equation}
+Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet escape timescale to the dynamical timescale $t_{\rm dyn} \sim r/\sigma$ is given by
+\be
 \frac{t_{\rm jet}}{t_{\rm dyn}} \sim 7\times 10^{-3}M_{\bullet,8}^{0.13}\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{-1/3},
-\end{equation}
-independent of radius $r$.
-Thus a jet with sufficient power, $\epsilon_{j} \gtrsim 10^{-6}$, to appreciably heat the CNM on radial scales $\sim r_{\rm s}$, also has sufficient power to escape the gas within the nucleus and propogate to much larger radii.
+\ee
+independent of $r$.
+A jet with power sufficient to appreciably heat the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim 10^{-6}$) also necessarily has sufficient power to escape the nucler region and propagate to much larger radii.
 Slower outflows from the accretion disk, instead of a collimated relativistic jet, may provide a more promising source of feedback in these systems (e.g.~\citealt{Li+13}).

### 2015-02-21 ms.tex
Filling in BH demo section

@@
    2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
-\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
+\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 6. 6\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
   \end{cases}
@@
 
-{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{w}^{\bullet}$ and $\sigma = v_{w}^{\star}$.
-}
+There is a maximum accretion rate for a thermally stable flow
+(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
+time from thermally stable accretion
+
+\begin{align}
+  t_{\rm growth}/t_{\rm h} \gsim
+  \rm{max}\begin{cases}
+    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
+    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
+    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
+  \end{cases}
+  \label{eq:tgrow_min}
+\end{align}
+
+In Figure~\ref{fig:bh_growth} we plot the growth times for core and
+cusp galaxies, with parameters chosen for the average star formation
+history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
+and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
+respectively.  We also plot the maximum growth time for thermal
+instability from equation~\eqref{eq:tgrow_min} in purple.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{bh_growth.eps}
+\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
+  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
+  ($\Gamma=0.8$, green). These are calculated from
+  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
+  average star formation history at each $\Mbh$. We also plot a lower
+  bound on growth time for a themally stable flow (purple) from
+  equation~\eqref{eq:tgrow_min}.}
+\end{figure}
 

### 2015-02-22 ms.tex
double-checked Bondi
Fixing Ia scaling

@@
 
-Understanding why most SMBHs appear to be inactive requires characterizing their gaseous environments.
-Gas near the sphere of influence of the SMBH, hereafter the `circumnuclear medium' (CNM), controls the mass accretion rate, $\dot{M}$.
-The accretion rate in turn sets the luminosity of the black hole and the impact of this energy and momentum output on larger physical scales (`feedback').
-The presence of dense gas in the nucleus may also lead to runaway cooling, resulting in bursty episodes of star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
-
-Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other properties of the
-galactic nucleus informs key questions related to the co-evolution of SMBHs and their host galaxies with cosmic time (e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).
-SMBH growth in the low redshift universe is dominated by low mass black holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a fact which is often attributed to the general trend of `cosmic down-sizing' resulting from hierarchical structure growth (e.g, \citealt{Gallo+08}).
-However, the physical processes involved in the growth of loss mass blacks may be distinct from those operating at higher SMBH masses and accretion rates in quasars.
-A key question here is whether SMBHs grow primarily by accreting gas fed in directly from large scales, or whether significant growth results also from internal, secular processes such as local stellar mass loss.
-
-Obtaining a better undersatnding of the physical mechanisms responsible for accretion onto quiescent SMBHs would have implications for observational constraints on the occupation fraction of SMBHs in low mass galaxies, and the potential existence of intermediate mass black holes.
-\citet{Miller+15} combine the average correlation between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample of elliptical galaxies to infer tentative evidence for a SMBH occupation fraction less than unity in galaxies with stellar masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim 10^{7}M_{\odot}$).
-This method relies on extrapolating a power-law fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below the detection threshold, despite the potential that rather different physical processes control the accretion rates onto the lowest mass SMBHs.
+Understanding why most SMBHs appear to be inactive requires
+characterizing their gaseous environments.  Gas near the sphere of
+influence of the SMBH, hereafter the `circumnuclear medium' (CNM),
+controls the mass accretion rate, $\dot{M}$.  The accretion rate in
+turn sets the luminosity of the black hole and the impact of this
+energy and momentum output on larger physical scales (`feedback').
+The presence of dense gas in the nucleus may also lead to runaway
+cooling, resulting in bursty episodes of star formation and AGN
+activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
+
+Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
+properties of the galactic nucleus informs key questions related to
+the co-evolution of SMBHs and their host galaxies with cosmic time
+(e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).  SMBH growth
+in the low redshift universe is dominated by low mass black holes,
+$M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a
+fact which is often attributed to the general trend of `cosmic
+down-sizing' resulting from hierarchical structure growth (e.g,
+\citealt{Gallo+08}).  However, the physical processes involved in the
+growth of low mass blacks may be distinct from those operating at
+higher SMBH masses and accretion rates in quasars.  A key question
+here is whether SMBHs grow primarily by accreting gas fed in directly
+from large scales, or whether significant growth results also from
+internal, secular processes such as local stellar mass loss.
+
+Obtaining a better undersatnding of the physical mechanisms
+responsible for accretion onto quiescent SMBHs would have implications
+for observational constraints on the occupation fraction of SMBHs in
+low mass galaxies, and the potential existence of intermediate mass
+black holes.  \citet{Miller+15} combine the average correlation
+between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample
+of elliptical galaxies to infer tentative evidence for a SMBH
+occupation fraction less than unity in galaxies with stellar masses
+$M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
+10^{7}M_{\odot}$).  This method relies on extrapolating a power-law
+fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
+the detection threshold, despite the potential that rather different
+physical processes control the accretion rates onto the lowest mass
+SMBHs.
 
@@
 \end{align}
-where the second equality makes use of equation (\ref{eq:Tanalytic}).  {\bf BDM: please check, as I found something different than what was here before}.
+where the second equality makes use of equation (\ref{eq:Tanalytic}).
 
@@
 \end{align}
-that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.
-\citet{McCourt+12} argue cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$, so equation (\ref{eq:cooling2}) represents a good proxy for instability in this case as well.
-
-Thermal stability ($\dot{q}_{\rm heat} > |\dot{q}_{\rm rad}|$; $t_{\rm cool} > t_{\rm ff}$) at the stagnation radius thus requires a critical minimum heating rate
+that results by combining equations
+\eqref{eq:mdot_analytic},\eqref{eq:mdot_gas}, and
+\eqref{eq:rhostarrs}.  \citet{McCourt+12} argue cooling instability
+develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$,
+so equation (\ref{eq:cooling2}) represents a good proxy for
+instability in this case as well.
+
+Thermal stability ($\dot{q}_{\rm heat} > |\dot{q}_{\rm rad}|$; $t_{\rm
+  cool} > t_{\rm ff}$) at the stagnation radius thus requires a
+critical minimum heating rate
 \begin{align}
@@
 
-In Appendix \ref{app:windheat} we calculate the wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a stellar population which is formed impulsively (Fig.~\ref{fig:vwimp}).
-At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.
-We show in $\S\ref{sec:combined}$ that for the case of quasi-continueous star formation representative of the average star formation history of loss mass galaxies, the stellar wind heating rate produced by stellar winds can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
-Stellar winds thus contributes a potentially important source of both energy and mass for the CNM.
+In Appendix \ref{app:windheat} we calculate the wind heating rate from
+stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter,
+$\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
+stellar population which is formed impulsively (Fig.~\ref{fig:vwimp}).
+At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
+heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star}
+\sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  We show
+in $\S\ref{sec:combined}$ that for the case of quasi-continueous star
+formation representative of the average star formation history of loss
+mass galaxies, the stellar wind heating rate produced by stellar winds
+can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
+Stellar winds thus contribute a potentially important source of both
+energy and mass for the CNM.
 
@@
 
-The high value of $v_{w}^{\rm Ia}$ implies that Ia SNe represent an important source of CNM heating.
-However, SNe can only be approximated as supplying heating which is spatially and temporally homogeneous if the rate of SNe is rapid compared to the characteristic evolution time of the flow at the radius of interest (\citealt{ShcherbakovWong+:2014a}).
-We define the ``Ia radius"
+The high value of $v_{w}^{\rm Ia}$ implies that Ia SNe represent an
+important source of CNM heating.  However, SNe can only be
+approximated as supplying heating which is spatially and temporally
+homogeneous if the rate of SNe is rapid compared to the characteristic
+evolution time of the flow at the radius of interest
+(\citealt{ShcherbakovWong+:2014a}).  We define the ``Ia radius"
   \begin{align}
@@
   \end{align}
-as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm Ia})^{-1} \sim G/(r\sigma^{2}R_{\rm Ia})$ exceeds the local dynamical timescale $t_{\rm
-dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship
-(eq.~[\ref{eq:Msigma}]).
-
-Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting $v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:rs_simple}) for the stagnation radius, we find that
+  as the location exterior of which the time interval between
+  subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm
+    Ia})^{-1} \sim G/(r\sigma^{2}R_{\rm Ia})$ exceeds the local
+  dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again
+  adopt the Ia rate for an old stellar population and in the final
+  equality we estimate the velocity dispersion using the
+  $M_{\bullet}-\sigma$ relationship (eq.~[\ref{eq:Msigma}]).
+
+Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting
+$v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:rs_simple})
+for the stagnation radius, we find that
+
 \begin{eqnarray}
-\left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}} &\approx& 12.4\eta_{0.02} M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{1.68} \nonumber \\
-&\approx& 12.4M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4)^{-1}(\tau_{\star}/t_{\rm h})^{0.38}
+  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}
+  &\approx& 12\eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} \nonumber \\
+  &\approx& 12 M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}
 \label{eq:rIars}
 \end{eqnarray}
-If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be approximated as a steady heating source near the stagnation radius for extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in the case of a very young stellar population ($\tau_{\star} \ll t_{\rm h}$).
-On the other hand, equation (\ref{eq:rIars}) may underestimate the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be substantially smaller than its value estimated using $v_{w}^{\rm Ia}$ if the heating rate excluding SN Ia is less than this.
-
-Even if SN Ia are rare near the stagnation radius, they may cap the SMBH accretion rate by periodically blowing gas out of the nucleus of low mass galaxies.
-Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.
-Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.
-Hence, SN Ia are in principle capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$, at least for low mass BHs with $\sigma \ll v^{\rm Ia}_{w}$.
-Thus, even in cases when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the accretion rate is limited to a maximum value,
+{\bf AG-Note the different scaling relations here.}
+If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
+approximated as a steady heating source near the stagnation radius for
+extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
+the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
+h}$).  On the other hand, equation (\ref{eq:rIars}) may underestimate
+the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
+substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
+if the heating rate excluding SN Ia is less than this.
+
+Even if SN Ia are rare near the stagnation radius, they may cap the
+SMBH accretion rate by periodically blowing gas out of the nucleus of
+low mass galaxies.  Between subsequent supernovae, stars release a
+gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
+interior to the Ia radius, which is gravitationally bound to the SMBH
+by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.  Thus, according
+to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm
+  Ia})^{2}/2\sigma^{2} \gtrsim 1$.  Hence, SN Ia are in principle
+capable of dynamically clearing out gas from radii $\sim r_{\rm Ia}
+\gtrsim r_{\rm s}$, at least for low mass BHs with $\sigma \ll v^{\rm
+  Ia}_{w}$.  Thus, even in cases when heating is sufficiently weak
+that the stagnation radius formally exceeds $r_{\rm Ia}$, the
+accretion rate is limited to a maximum value,
 \begin{eqnarray}

### 2015-02-22 ms.tex
Fixing one of the labels

@@
 
-The CNM density also influences the emission from stellar tidal disruption events (TDEs), such as the high energy
-transient {\it Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
-This event was powered by a transient relativistic jet, which produced
-synchrotron radio emission as the jet material was decelerated by
-shock interaction with the CNM of the previously quiescent SMBH
+The CNM density also influences the emission from stellar tidal
+disruption events (TDEs), such as the high energy transient {\it
+  Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11},
+\citealt{Burrows+11}; \citealt{Zauderer+11}).  This event was powered
+by a transient relativistic jet, which produced synchrotron radio
+emission as the jet material was decelerated by shock interaction with
+the CNM of the previously quiescent SMBH
 (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of J1644+57 showed that the CNM density was
-significantly lower than that measured surrounding Sgr A$^{\star}$
+modeling of J1644+57 showed that the CNM density was significantly
+lower than that measured surrounding Sgr A$^{\star}$
 (\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
 injected into a denser CNM would be decelerated more rapidly,
-producing substantially different radio emission than in J1644+57.  Variations in the properties of the CNM could thus in
-principle help explain why most TDEs appear to be radio quiet
+producing substantially different radio emission than in J1644+57.
+Variations in the properties of the CNM could thus in principle help
+explain why most TDEs appear to be radio quiet
 (e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).
 
-Gas comprising the CNM can in principle originate from several sources: (1) wind mass loss from predominantly evolved stars; (2) stellar binary collisions; and (3) unbound debris from a recent TDE.
-Stellar wind mass loss is probably the dominant source insofar as collisions are relevant only in extremely dense stellar environments for very young stellar populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find that TDEs contribute subdominantly to the time-averaged accretion rate of quiescent SMBHs.
-
-\citet{Ho:2009a} estimates the accretion rates onto a sample of early-type galaxies both by using X-ray observations to determine the Bondi accretion rate and using estimates for the mass loss rate of evolved stars.
-Both methods lead to the conclusion that the available gas reservoir is more than sufficient to power the observed low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative efficiency for thin disk accretion.
-Several independent strains of evidence now suggest that low-luminosity AGN result from accretion proceeding in a radiatively inefficient mode (\citealt{Yuan&Narayan14}), due either to the advection of gravitationally-released energy across the SMBH horizon (e.g.~\citealt{Narayan&Yi95}) or due to a low efficiency for the gas inflowing on large scales ultimately reaching the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+Gas comprising the CNM can in principle originate from several
+sources: (1) wind mass loss from predominantly evolved stars; (2)
+stellar binary collisions; and (3) unbound debris from a recent TDE.
+Stellar wind mass loss is probably the dominant source insofar as
+collisions are relevant only in extremely dense stellar environments
+for very young stellar populations (\citealt{Rubin&Loeb11}), while
+\citet{MacLeod+13} find that TDEs contribute subdominantly to the
+time-averaged accretion rate of quiescent SMBHs.
+
+\citet{Ho:2009a} estimates the accretion rates onto a sample of
+early-type galaxies both by using X-ray observations to determine the
+Bondi accretion rate and using estimates for the mass loss rate of
+evolved stars.  Both methods lead to the conclusion that the available
+gas reservoir is more than sufficient to power the observed
+low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative
+efficiency for thin disk accretion.  Several independent strains of
+evidence now suggest that low-luminosity AGN result from accretion
+proceeding in a radiatively inefficient mode
+(\citealt{Yuan&Narayan14}), due either to the advection of
+gravitationally-released energy across the SMBH horizon
+(e.g.~\citealt{Narayan&Yi95}) or due to a low efficiency for the gas
+inflowing on large scales ultimately reaching the SMBH
+(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
 
@@
 
-Another approach to determine the SMBH accretion rate, which we adopt in this paper, is to directly calculate the density, velocity and temperature profiles of the CNM using a physically motivated
+Another approach to determine the SMBH accretion rate, which we adopt
+in this paper, is to directly calculate the density, velocity and
+temperature profiles of the CNM using a physically motivated
 hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from several sources including stellar winds, supernovae, and AGN feedback (\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works focusing on modeling individual galaxies, here we systematically analyze the properties of the CNM across a sample of galaxies with a range of SMBH masses, stellar density profiles, and star formation histories (\citealt{WangMerritt:2004a}).
-
-Past studies, employing multi-dimensional numerical hydrodynamics and including variety of (parameterized) physical effects, have focused on massive elliptical galaxies (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
-A key finding of these works is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate until black hole feedback becomes sufficiently important to shut off the flow and halt SMBH growth.
-Here we instead focus on time-independent models, neglecting radiative cooling.
-This approach allows us to systematically explore the relevant parameter space and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties manifest across the expected range of galaxy properties, or whether other (non-AGN) forms of feedback can result in steady accretion.
-Even if cooling instabilties develop on galactic scales over longer timescales, e.g.
-$\sim$ Gyr, a state of quasi-steady accretion may exist between these inflow events on smaller radial scales comparable to the sphere of influence.
-We are thus motivated to explore whether steady flow is achieved within the nucleus under any circumstances, or whether the gas content is always building towards instability.
+stellar winds, while energy input results from several sources
+including stellar winds, supernovae, and AGN feedback
+(\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+Unlike previous works focusing on modeling individual galaxies, here
+we systematically analyze the properties of the CNM across a sample of
+galaxies with a range of SMBH masses, stellar density profiles, and
+star formation histories (\citealt{WangMerritt:2004a}).
+
+Past studies, employing multi-dimensional numerical hydrodynamics and
+including variety of (parameterized) physical effects, have focused on
+massive elliptical galaxies (e.g.~\citealt{Ciotti&Ostriker07};
+\citealt{Ciotti+10}).  A key finding of these works is the periodic
+development of cooling instabilities, which temporarily increase the
+gas accretion rate until black hole feedback becomes sufficiently
+important to shut off the flow and halt SMBH growth.  Here we instead
+focus on time-independent models, neglecting radiative cooling.  This
+approach allows us to systematically explore the relevant parameter
+space and to derive simple analytic expressions that prove useful in
+exploring whether cooling instabilties manifest across the expected
+range of galaxy properties, or whether other (non-AGN) forms of
+feedback can result in steady accretion.  Even if cooling instabilties
+develop on galactic scales over longer timescales, e.g. $\sim$ Gyr, a
+state of quasi-steady accretion may exist between these inflow events
+on smaller radial scales comparable to the sphere of influence.  We
+are thus motivated to explore whether steady flow is achieved within
+the nucleus under any circumstances, or whether the gas content is
+always building towards instability.
 %A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
 
-In the presence of strong heating, one-dimensional steady-state flow is characterized by an inflow-outflow structure, with a critical radius known as the``stagnation radius" $\rs$ where the radial velocity passes through zero.
-Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.
-The stagnation radius, rather than the Bondi radius, thus controls the SMBH accretion rate (although we will show that $\rs$ can in many cases lie within a factor of few of the nominal Bondi radius).
-In the case of sufficiently weak heating, however, no stagnation radius may exist at all, i.e.
-the entire ISM of the galaxy is feeding the SMBH.
-Another goal of this work is to assess under what conditions a stagnation radius exists, as this question is intimately tied to that of cooling instability.
+In the presence of strong heating, one-dimensional steady-state flow
+is characterized by an inflow-outflow structure, with a critical
+radius known as the``stagnation radius" $\rs$ where the radial
+velocity passes through zero.  Mass loss from stars interior to the
+stagnation radius is accreted, while that outside $\rs$ is unbound in
+an outflow from the nucleus.  The stagnation radius, rather than the
+Bondi radius, thus controls the SMBH accretion rate (although we will
+show that $\rs$ can in many cases lie within a factor of few of the
+nominal Bondi radius).  In the case of sufficiently weak heating,
+however, no stagnation radius may exist at all, i.e. the entire ISM of
+the galaxy is feeding the SMBH.  Another goal of this work is to
+assess under what conditions a stagnation radius exists, as this
+question is intimately tied to that of cooling instability.
 % Furthermore, in some cases we find that no stagnation
@@
 describe our model, including the sample of galaxies used in our
-analysis ($\S\ref{sec:sample}$) and our numerical procedure for
+analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
 calculating the steady-state hydrodynamic profile of the CNM
@@
 \subsection{Galaxy models}
+\label{sec:gal_model}
 \citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to measure the radial surface brightness profiles for hundreds of nearby early type galaxies.

### 2015-02-22 ms.tex
editing

--- 2015-02-21 ms.tex
@@
 
-\subsection{Combined Heating Rate for Representative Star Formation History} 
+\subsection{Combined Heating Rate} 
 \label{sec:combined}
 
-The total gas heating rate, $\vwO$, includes contributions from
-stellar winds, supernovae, pulsars, and SMBH feedback.  The strength
-of each heating source will depend explicitely on the SMBH mass and
-the star formation hstory in the galactic nuclear region, the latter
-of which will also vary systematically with the galaxy mass and hence
-with $\Mbh$.
-
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various
-heating sources as a function of time $\tau_{\star}$ after a burst of
-star formation for a black hole masses of $\Mbh = 10^{6} \Msun$ (top
-panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The stellar wind
-heating is calculated as described in appendix~\ref{app:windheat}. The
-and Ia heating ($v_{w}^{\rm Ia}$) and compton heating ($v_{\rm
-  w}^{\bullet}$) are calculated using equations~\eqref{eq:vIa}
-and~\eqref{eq:vC} respectively. Both heating sources depend on the
-value of the mass return parameter, $\eta$. We have plotted this for a
-burst of star formation in Figure~\ref{fig:vwImp}.  The Ia heating rate
-also depends be a convolution of the delay time distribution
-(eq. [\ref{eq:DTD}]) and the star formation history. This convolution
-reduces to the delay time distribution itself for a burst of star
-formation. To account for the non-steady nature of the Ia heating we
-multiply the Ia heating by $e^{-\rs/\rIa}$, where $\rIa$ is the radius
-where the time between subsequent supernovae is equal to the local
-dynamical time. The heating contribiution from
-Ia supernovae will be suppressed if the time between successive
-supernovae is much greater than the dynamical time at $\rs$. Note that
-both $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ depend on the
-total heating rate (all of the heating sources added in quadrature),
-and so we have to solve a system of impllicit eqautions for these.
-The MSP contribution is negligible for both cases and is not plotted.
-
-The overall heating rate declines with time and after some time the
-flow would become thermally unstable. The epoch when this occurs is
-shown by dashed lines in Figure~\ref{fig:vwSourcesImp}. In calculating
-this transition we have not included the compton heating. However,
-this would not be able stabilize flow as it would not respond
-immediately to cooling instabilities. Thus, if Compton
-heating is the dominant source of heating we do not expect a steady,
-thermally stable flow. Thermal instability is the norm in the burst
-limit except for very early times ($\lsim 10^7$ years) and small
-$\Mbh$ ($\Mbh\simeq 10^6 \Msun$).
+The total gas heating rate, 
+\be
+\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
+\label{eq:vtot}
+\ee
+includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
+The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
+The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
+
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
+The heating and mass input due to stellar winds is calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
+The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively using the mass input parameter from stellar winds, $\eta$ (Fig.~\ref{fig:vwImp}).
+SN Ia heating also depends on a convolution of the delay time distribution (DTD; eq.
+[\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
+We crudely account for the expected reduction in Ia heating efficiency due to the non-steady nature of the SN Ia by attenuating the Ia heating rate by a factor $e^{-\rs/\rIa}$, that reduces to zero when the stagnation radius exceeds the radius, $r_{\rm Ia}$, at which the time between subsequent supernovae is equal to the local dynamical time (eq.~[\ref{eq:rIa}]).
+Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to solve an implicit equation.
+Heating from MSPs is found to be negligible compared to other sources of heating for fiducial parameters and hence is not plotted for clarity.
+
+Figure~\ref{fig:vwSourcesImp} shows that for low mass black holes, stellar heating is the most important on timescales less than a few tens of millions of years.
+Compton heating comes to dominate at later times due to the high stellar mass loss rates coupled with the higher accretion rates that accompany an overall decrease in the heating rate.
+For higher mass black holes, Compton heating dominates at all epochs.
+Because the total heating rate declines with time, after some point the flow becomes thermally unstable near the stagnation radius, and hence across all radii.
+The epoch after this occurs according to the criterion $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \lesssim 1$ (eq.~[\ref{eq:cooling3}]) are shown as dashed lines in Figure~\ref{fig:vwSourcesImp}.
+This transition is calculated not include Compton heating, since the latter cannot truly stabilize flow due to its inability to respond instantaneously to local changes in the thermal properties of the gas.
+We thus see that thermally unstable flow is the norm in the single starburst case, except at very early times ($\lsim 10^7$ years) for small $\Mbh\simeq 10^6 \Msun$.
 

### 2015-02-22 ms.tex
blah

--- 2015-02-22 ms.tex
@@
   $\Mbh$, calculated for average star formation histories from
-  \citet{MosterNaab+:2013a}  Note that the star
-  formation histories in \citet{MosterNaab+:2013a} are in terms of
-  halo mass and for each $\Mbh$ we assign the halo mass,
-  whose star formation history would produce a bulge consistent with
-  the $\Mbh-M_{\rm bulge}$ relationship from
-  \citet{McConnellMa:2013a}.}
+  \citet{MosterNaab+:2013a} (see appendix~\ref{app:windheat} for details).}
 \end{figure}
@@
   using the equation~\eqref{eq:stag_simple} and the $\vwO$
-  corresponding to each $\Mbh$--see Figure~\ref{fig:vwSources}. For
-  the blue curve we use the total $\vwO$ from stars, MSP, and
-  black hole feedback (e.g. the solid black curve in
-  Figure~\ref{fig:vwSources}).}
+  corresponding to each $\Mbh$--see the black line
+  Figure~\ref{fig:vwSources}.}
 \end{figure}
@@
 
-Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
-core (blue) and cusp (green) galaxies superimposed with x-ray
-measurements (red stars), upper limits (red triangles) from
-\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
-\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
-calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
-the wind heating parameter, $\vw$, and the mass return parameter,
-$\eta$ set by the average star formation history for each $\Mbh$ (see
-the black lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). We
-try two different prescriptions for $\epsilon$: 
-$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
-\Mdot/0.01 \MdotEdd$ right-hand panel.
+This is shown Figure~\ref{fig:miller} shows our predicted ${\rm
+  L_{X}/L_{\rm edd}=\epsilon_X \Mdot c^2}$ for core (blue) and cusp
+  (green) galaxies superimposed with x-ray measurements (red stars),
+  upper limits (red triangles) from \citet{Miller+15}. $\epsilon_X$ is
+  an efficiency factor and $\Mdot$ is calculated using
+  Equation~\eqref{eq:mdot_analytic}, with parameters consistent with
+  the average star formation history for each $\Mbh$ (see the black
+  lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Our
+  predicted trend in  $L_{X}/L_{\rm edd}$ is steeper than the 
+  trend found in \citet{Miller+14} (black line). Note that we try two 
+  different prescriptions for $\epsilon_X$: $\epsilon_X=10^{-4}$ in
+  the left-hand panel and $\epsilon_X=10^{-1} \Mdot/0.01 \MdotEdd$
+  right-hand panel. In either case our predicted trend in $
+  L_{X}/L_{\rm edd}$ is opposite the observationally inferred
+  one. {\bf AG-Need a bit more discussion here.} We note that in the
+  right hand panel the observed galaxies are below the upper limits
+  from Ia supernovae and thermal instability and so may be accreting
+  in a thermally stable state {\bf AG-but it does not mean that they
+    actually are}.
 
@@
 % that $L_x \propto M_{\rm gal}^{0.7-0.8}$.
-
-% \begin{figure}
-% \includegraphics[width=\columnwidth]{bh_xray.eps}
-% \caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
-%   stellar mass for our solutions (points), the trend of nuclear x-ray
-%   luminosity with stellar mass (black line) and the detection upper
-%   limit (blue line) from Fig. 1 of \citealt{Miller+15}. In
-%   the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
-%   c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
-%   luminosities comparable to those observed. In the bottom panel, we
-%   take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
-%   \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
-%   we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
-% \end{figure}
 

### 2015-02-22 ms.tex
editing

@@
 \begin{eqnarray}
-\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}g}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}

### 2015-02-22 windheat.tex
editing

@@
 \end{align}
-resulting in an effective wind heating rate of
+resulting in a wind heating parameter of 
 \begin{align}
-  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t)
+  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
 \end{align}
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{vw.pdf}
-\caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
-different $S(t)$.  The yellow and orange curves are the Moster SF
-histories, with and without Type II SNe, respectively.  The red,
-purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
-function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
-respectively.  These solid curves lack SN, but the dashed purple curve
-possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
-variability timescale is greater than $\sim$ twice the duration of
-high-velocity winds.}
-\end{figure}
+The mass return parameter will be
+
+\begin{align}
+\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
+\end{align}
+
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{vw.pdf}
+% \caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
+% different $S(t)$.  The yellow and orange curves are the Moster SF
+% histories, with and without Type II SNe, respectively.  The red,
+% purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
+% function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
+% respectively.  These solid curves lack SN, but the dashed purple curve
+% possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
+% variability timescale is greater than $\sim$ twice the duration of
+% high-velocity winds.}
+% \end{figure}
 

### 2015-02-22 ms.tex
editing

@@
 \end{eqnarray}
-{\bf AG-Note the different scaling relations here.}
 If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be

### 2015-02-22 ms.tex
blah

--- 2015-02-22 ms.tex
@@
 \begin{eqnarray}
-\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}g}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 
-\subsection{Combined Heating Rate} 
+\subsection{Combined Heating Rate for Representative Star Formation History} 
 \label{sec:combined}
 
-The total gas heating rate, 
-\be
-\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
-\label{eq:vtot}
-\ee
-includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
-The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
-The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
-
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
-The heating and mass input due to stellar winds is calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
-The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively using the mass input parameter from stellar winds, $\eta$ (Fig.~\ref{fig:vwImp}).
-SN Ia heating also depends on a convolution of the delay time distribution (DTD; eq.
-[\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
-We crudely account for the expected reduction in Ia heating efficiency due to the non-steady nature of the SN Ia by attenuating the Ia heating rate by a factor $e^{-\rs/\rIa}$, that reduces to zero when the stagnation radius exceeds the radius, $r_{\rm Ia}$, at which the time between subsequent supernovae is equal to the local dynamical time (eq.~[\ref{eq:rIa}]).
-Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to solve an implicit equation.
-Heating from MSPs is found to be negligible compared to other sources of heating for fiducial parameters and hence is not plotted for clarity.
-
-Figure~\ref{fig:vwSourcesImp} shows that for low mass black holes, stellar heating is the most important on timescales less than a few tens of millions of years.
-Compton heating comes to dominate at later times due to the high stellar mass loss rates coupled with the higher accretion rates that accompany an overall decrease in the heating rate.
-For higher mass black holes, Compton heating dominates at all epochs.
-Because the total heating rate declines with time, after some point the flow becomes thermally unstable near the stagnation radius, and hence across all radii.
-The epoch after this occurs according to the criterion $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \lesssim 1$ (eq.~[\ref{eq:cooling3}]) are shown as dashed lines in Figure~\ref{fig:vwSourcesImp}.
-This transition is calculated not include Compton heating, since the latter cannot truly stabilize flow due to its inability to respond instantaneously to local changes in the thermal properties of the gas.
-We thus see that thermally unstable flow is the norm in the single starburst case, except at very early times ($\lsim 10^7$ years) for small $\Mbh\simeq 10^6 \Msun$.
+The total gas heating rate, $\vwO$, includes contributions from
+stellar winds, supernovae, pulsars, and SMBH feedback.  The strength
+of each heating source will depend explicitely on the SMBH mass and
+the star formation hstory in the galactic nuclear region, the latter
+of which will also vary systematically with the galaxy mass and hence
+with $\Mbh$.
+
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various
+heating sources as a function of time $\tau_{\star}$ after a burst of
+star formation for a black hole masses of $\Mbh = 10^{6} \Msun$ (top
+panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The stellar wind
+heating is calculated as described in appendix~\ref{app:windheat}. The
+and Ia heating ($v_{w}^{\rm Ia}$) and compton heating ($v_{\rm
+  w}^{\bullet}$) are calculated using equations~\eqref{eq:vIa}
+and~\eqref{eq:vC} respectively. Both heating sources depend on the
+value of the mass return parameter, $\eta$. We have plotted this for a
+burst of star formation in Figure~\ref{fig:vwImp}.  The Ia heating rate
+also depends be a convolution of the delay time distribution
+(eq. [\ref{eq:DTD}]) and the star formation history. This convolution
+reduces to the delay time distribution itself for a burst of star
+formation. To account for the non-steady nature of the Ia heating we
+multiply the Ia heating by $e^{-\rs/\rIa}$, where $\rIa$ is the radius
+where the time between subsequent supernovae is equal to the local
+dynamical time. The heating contribiution from
+Ia supernovae will be suppressed if the time between successive
+supernovae is much greater than the dynamical time at $\rs$. Note that
+both $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ depend on the
+total heating rate (all of the heating sources added in quadrature),
+and so we have to solve a system of impllicit eqautions for these.
+The MSP contribution is negligible for both cases and is not plotted.
+
+The overall heating rate declines with time and after some time the
+flow would become thermally unstable. The epoch when this occurs is
+shown by dashed lines in Figure~\ref{fig:vwSourcesImp}. In calculating
+this transition we have not included the compton heating. However,
+this would not be able stabilize flow as it would not respond
+immediately to cooling instabilities. Thus, if Compton
+heating is the dominant source of heating we do not expect a steady,
+thermally stable flow. Thermal instability is the norm in the burst
+limit except for very early times ($\lsim 10^7$ years) and small
+$\Mbh$ ($\Mbh\simeq 10^6 \Msun$).
 
@@
     $\alpha$ depends on the slope of the stellar density profile
-    ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively). One
-    possible solution that the wind mass loss rate (i.e. $\eta$)
+    ($\alpha\simeq0.5,1$ for cusp and core galaxies
+    respectively). {\bf AG-these explanations are prehistoric and need
+      to be modified. Actually this entire summary needs to be
+      revamped, but this can wait until we are closer to completion.}
+    One possible solution that the wind mass loss rate (i.e. $\eta$)
     increases with $\Mbh$, as would be expected if low mass SMBH
-    preferentially hosted younger stellar populations. Another possible
-    explanation is that the effective heating rate of the CNM $v_{w}$
-    decreases with decreasing SMBH mass. This could again be due to an
-    older stellar population, since $v_{w} \propto \eta^{−1/2}$
-    for heating sources such as SN Ia and millisecond pulsars.
+    preferentially hosted younger stellar populations. Another
+    possible explanation is that the effective heating rate of the CNM
+    $v_{w}$ decreases with decreasing SMBH mass. This could again be
+    due to an older stellar population, since $v_{w} \propto
+    \eta^{−1/2}$ for heating sources such as SN Ia and millisecond
+    pulsars.
   \item We compare the $\Mdot$ for each of our solution to the one

### 2015-02-22 ms.tex
editing2

--- 2015-02-22 ms.tex
@@
 \end{align} 
-Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.
+Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g.
+$v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.
+The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
+\begin{align}
+\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
+\begin{cases} 1.3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
+C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
+&, \text{core}\\ 6\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
+C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
+&, \text{cusp},
+  \end{cases}
+  \label{eq:MdotC}
+\end{align}
 
@@
 Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
-However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat deceptive because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
+However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
 Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
@@
 
+\subsubsection{Single Starburst}
+
 Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
@@
 
-However, a single burst of star formation does not describe the
-average star formation histories of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation,
-resulting in energetic young stellar winds and supernovae which
-dominate the energy budget, resulting in a high heating rate of $\vwO
-\sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on
-average have older stellar populations, with their heating rates
-dominated by Ia supernovae (on large radial scales) and SMBH feedback.
-The average value of $\vwO$ is estimated as a function of SMBH mass
-for each heating source by calculating its value using the average
-cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation
-history is used to determine the stellar wind heating $v_{\rm
-  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
-
-Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
-source (stars, MSPs, SNe Ia, and black hole feedback).  MSP heating is
-again found to be negligible at all black hole masses.  The young
-stellar populations in galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$
-results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 5\times 10^{8}
-\Msun$, the lack of younger stellar populations reduces the role of
-stellar wind heating, but Compton heating plays an important role.
+\subsubsection{Continuous Star Formation History}
+
+A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
+smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.
+Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
+We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
+Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
+
+Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
+MSP heating is
+again found to be negligible.
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind heating being dominant.
+For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.
 
@@
 \includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
-\caption{\label{fig:vwSourcesImp} Most important sources of heating
-  after a burst of star formation for $\Mbh=10^6 \Msun$ (top panel)
-  and $\Mbh= 10^8 \Msun$ (bottom panel). We also show the velocity
-  dispersion from the $\Mbh-\sigma$ relationship as a horizontal gray line
-  \citep{Gultekin+09}.}
+\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.
+Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.
+Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).
+Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
 \end{figure}

### 2015-02-22 ms.tex
editing2

@@
 Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
+Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
 
@@
 again found to be negligible.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind heating being dominant.
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant.
 For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.
@@
 \includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} {\emph Top Panel:}Sources contributing
-  to the heating rate of the CNM, $\vwO$, including stellar wind
-  heating ({\it orange}), Ia supernovae ({\it green}), millisecond
-  pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating
-  source varies with black hole mass $\Mbh$ due to the different
+\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing   to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
+Each heating source varies with black hole mass $\Mbh$ due to the different
   average star formation history of galaxies of a given halo mass (see
   Appendix~\ref{app:windheat} for the detailed description). The total
-  heating rate is shown in black. To account for the non-steady nature
-  of the Ia heating we multiply the Ia heating by $e^{-\rs/\rIa}$, so
-  the contribution that the heating contribiution from Ia supernovae
-  will be suppressed if the time between successive supernovae is much
-  greater than the dynamical time at $\rs$. {\emph Bottom panel} The
-  ratio of the heating ($\dot{q}_{\rm heat}$) to the cooling rate
-  ($\dot{q}_{\rm cool}$) at $\rs$ from the total heating rate in the
-  top panel. Above $\Mbh\simeq 5\times 10^7 \Msun$ $\dot{q}_{\rm
-    heat}(\rs)<\dot{q}_{\rm cool}(\rs)$ and a thermal instability
-  would arise. The thermally unstable region is marked in red in the
-  bottom panel. All curves become dashed in the thermally unstable
-  region of parameter space: we expect our model to break down in this
-  regime as the steady-state assumption would be violated.}
+  heating rate is shown in black. {\it Bottom Panel:} The
+  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
+  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.
+Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.
+{\bf BDM: remove the red - its tacky and will vary based on core/cusp.
+Draw a dashed line across at heating ratio of 1.
+change y axis labels!
+move stars label in top panel}}
 \end{figure}

### 2015-02-22 ms.tex
editing3

@@
 We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
+Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}; top panel).
 Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
@@
 Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
-MSP heating is
-again found to be negligible.
+Again, Ia heating is suppressed when the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in the bottom panel of Figure ~\ref{fig:eta}.
+MSP heating is again found to be negligible for all black hole masses.
 The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant.
 For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.
+Again, solid and dashed lines show black hole masses for which the flow is thermally stable and thermally unstable, respectively, as shown in the bottom panel.
 
@@
 Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).
-Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
+Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.
+{\bf BDM: change x axis range so lines start at 3e6 yr }}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{eta.pdf}
+\includegraphics[width=\columnwidth]{rs_rIa.pdf}
+\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$ characterizing stellar mass
+  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
+  $\Mbh$, calculated for average star formation histories from
+  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).
+{\it Bottom panel:} Ratio of Ia radius to stagnation radius as a function of $\Mbh$.
+The Ia radius calculated from equation~\eqref{eq:rIa} based on convolving the average star formation histories with the SN Ia DTD.
+The stagnation radius is calculated from \eqref{eq:stag_simple} using the total heating rate for each $\Mbh$ shown in the top panel.
+}
 \end{figure}
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{eta.pdf}
-\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
-  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
-  $\Mbh$, calculated for average star formation histories from
-  \citet{MosterNaab+:2013a} (see appendix~\ref{app:windheat} for details).}
-\end{figure}
-
-The bottom panel of Figure~\ref{fig:vwSources} shows the ratio of
-heating to radiative cooling at the stagnation radius
-(eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total
-heating rate from the top panel Figure \ref{fig:vwSources}.  The
-combined heating rate from stellar winds and Compton heating is
-insufficient to prevent thermal instability for the high $\Mbh$.
-{\bf AG: Should we really be talking about Compton heating stabilizing
-the flow}?
 % However, if Ia supernovae are included in the schematic way described
@@
 % \end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{rs_rIa.pdf}
-\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
-  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
-    referring to the first part of the equation here--I use the
-    appropriate convolution the Ia rate here}. $\rs$ is calculated
-  using the equation~\eqref{eq:stag_simple} and the $\vwO$
-  corresponding to each $\Mbh$--see the black line
-  Figure~\ref{fig:vwSources}.}
-\end{figure}
 

### 2015-02-22 ms.tex
fixing reference
editing3

@@
 As $r_{\rm b} \rightarrow r_{s}$, the effects of the break radius is to the push the stagnation radius inwards, decreasing the SMBH accretion rate.
+
+ Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for each of our numerical solutions in Eddington units for different values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
+{\bf BDM: say something smart}
 %% AG: Describe conservation checks to additionally validate the results.
@@
     analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively. }
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{mdot_mass.eps}
+  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm edd}$ versus SMBH mass for galaxies in our sample, calculated for different values of the wind heating parameter $\vwO =$ 300 km s$^{-1}$ ({\it green}),
+    600 km s$^{-1}$ ({\it orange}), and 1200 km s$^{-1}$ ({\it blue}).
+    Squares correspond to cusp galaxies ($\Gamma=0.8$), while
+    triangles correspond to cores ($\Gamma$=0.1).
+Solid and dashed curves correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies, respectively.
+}
 \end{figure}
@@
 Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
-The heating and mass input due to stellar winds is calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
-The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively using the mass input parameter from stellar winds, $\eta$ (Fig.~\ref{fig:vwImp}).
-SN Ia heating also depends on a convolution of the delay time distribution (DTD; eq.
+The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
+The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
+SN Ia heating depends also on a convolution of the DTD (eq.
 [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
-We crudely account for the expected reduction in Ia heating efficiency due to the non-steady nature of the SN Ia by attenuating the Ia heating rate by a factor $e^{-\rs/\rIa}$, that reduces to zero when the stagnation radius exceeds the radius, $r_{\rm Ia}$, at which the time between subsequent supernovae is equal to the local dynamical time (eq.~[\ref{eq:rIa}]).
-Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to solve an implicit equation.
-Heating from MSPs is found to be negligible compared to other sources of heating for fiducial parameters and hence is not plotted for clarity.
-
-Figure~\ref{fig:vwSourcesImp} shows that for low mass black holes, stellar heating is the most important on timescales less than a few tens of millions of years.
-Compton heating comes to dominate at later times due to the high stellar mass loss rates coupled with the higher accretion rates that accompany an overall decrease in the heating rate.
-For higher mass black holes, Compton heating dominates at all epochs.
-Because the total heating rate declines with time, after some point the flow becomes thermally unstable near the stagnation radius, and hence across all radii.
-The epoch after this occurs according to the criterion $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \lesssim 1$ (eq.~[\ref{eq:cooling3}]) are shown as dashed lines in Figure~\ref{fig:vwSourcesImp}.
-This transition is calculated not include Compton heating, since the latter cannot truly stabilize flow due to its inability to respond instantaneously to local changes in the thermal properties of the gas.
-We thus see that thermally unstable flow is the norm in the single starburst case, except at very early times ($\lsim 10^7$ years) for small $\Mbh\simeq 10^6 \Msun$.
+We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
+Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
+Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.
+
+For low mass black holes, stellar heating is the most important on timescales of less than a few tens of millions of years.
+Compton heating comes to dominate at later times due to the higher accretion rates that accompany the overall decrease in the heating rate coupled with the persistently high mass loss rates of a relatively young stellar population.
+Compton heating dominates at all epochs for higher mass black holes, with stellar winds and Ia SN competing for the most significant non-AGN heating source.
+As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by dashed lines in Fig.~\ref{fig:vwSourcesImp}.
+The thermal stability is calculated neglecting Compton heating because the latter may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
+Thermally unstable flow is seen to be the norm in the single starburst case, except at very early times, $\tau_{\star} \lesssim 1-3 \times 10^7$ yr.
 
@@
 A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.
-Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.
+smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
+Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
 We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}; top panel).
+Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ as a function of $M_{\bullet}$ (Fig.~\ref{fig:eta}; top panel).
 Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
@@
 Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
-Again, Ia heating is suppressed when the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in the bottom panel of Figure ~\ref{fig:eta}.
+Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in Fig.
+~\ref{fig:eta} (bottom panel).
 MSP heating is again found to be negligible for all black hole masses.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant.
-For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.
-Again, solid and dashed lines show black hole masses for which the flow is thermally stable and thermally unstable, respectively, as shown in the bottom panel.
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
+Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
+Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
+Realistic variations (``burstiness") in the star formation history will result in lower heating rates, as seen in Fig.~X, for which we compare the stellar wind heating rates in the case of sinusoidal star formation pattern...{\bf BDM: say more}.
 
@@
 
-\subsection{Mass accretion rate}
+\subsection{Nuclear X-ray Luminosities of Quiescent Galaxies}
 \label{sec:mdot}
 
-For each solution we calculate the accretion rate $\dot{M}$ onto the
-SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
-\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
-10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
-$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
-values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core
-($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
-
-For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ tends to increase
-with SMBH mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp)
-galaxies, respectively.  This appears to be in contradiction with the
-general down sizing trend observed for SMBH accretion in the local
-universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
-fact that for quiescent galaxies the nuclear X-ray luminosity obeys
-$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
-\citep{Miller+15}.  Our model instead predicts that $\Mdot
+Figure \ref{fig:vwSources} shows that the average heating rate is relatively constant with SMBH mass.
+For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+This appears in contradiction with the nuclear X-ray luminosities of quiescent galaxies, which though showing broad scatter instead obey $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{Pellegrini10, Miller+15}.
+Our model instead predicts that $\Mdot
 \sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
@@
   predicted trend in  $L_{X}/L_{\rm edd}$ is steeper than the 
-  trend found in \citet{Miller+14} (black line). Note that we try two 
+  trend found in \citet{Miller+15} (black line). Note that we try two 
   different prescriptions for $\epsilon_X$: $\epsilon_X=10^{-4}$ in
@@
 
+This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08})
+
 % Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{mdot_mass.eps}
-  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}$ in units of
-    the Eddington rate $\dot{M}_{\rm edd}$ as a function of SMBH mass
-    for each galaxy in our sample, calculated for different values of
-    the wind heating parameter $\vwO =$ 300 km s$^{-1}$ ({\it green}),
-    600 km s$^{-1}$ ({\it orange}), and 1200 km s$^{-1}$ ({\it blue}).
-    Squares correspond to cusp galaxies ($\Gamma=0.8$), while
-    triangles correspond to cores ($\Gamma$=0.1). The curves correspond
-    to the analytic results for $\eddr$ from equation
-    (\ref{eq:eddr_analytic}) for cusps (solid lines) and cores (dashed
-    lines).  }
-\end{figure}
-
 %% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
@@
 for individual observations, but I am not sure how to do it with our
-new gridded approach.}
+new gridded approach.  BDM: too bad!}
 % \subsubsection{Comparison to measured temperature and density profiles}

### 2015-02-22 ms.tex
omg

@@
 calculating the steady-state hydrodynamic profile of the CNM
-($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
-results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
-results, including a comparison of our gas profiles to those inferred
-from {\it Chandra} observations and to the measured $L_X-\Mbh$
-relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
-$\S\ref{sec:summary}$ we summarize our results.  Table \ref{table:definitions} provides the definitions of commonly used variables.
+($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe some
+analytic results, while in $\S\ref{sec:numerical}$ we describe our numerical results.
+In $\S\ref{sec:discussion}$ we discuss the implications of our results, to topics including...
+In $\S\ref{sec:conclusions}$ we summarize our conclusions.
+Table \ref{table:definitions} provides the definitions of commonly used variables.
+Appendix \ref{app:rs} provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in detail.
 
@@
 
-\section{Applications}
-\label{sec:applications}
+\section{Discussion}
+\label{sec:discussion}
 
@@
 
-Figure \ref{fig:vwSources} shows that the average heating rate is relatively constant with SMBH mass.
+Figure \ref{fig:vwSources} shows that the CNM heating rate is on average approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
 For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This appears in contradiction with the nuclear X-ray luminosities of quiescent galaxies, which though showing broad scatter instead obey $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{Pellegrini10, Miller+15}.
-Our model instead predicts that $\Mdot
-\sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
-\sim \Mbh^{1.5-2}$, steeper than the observed relationship.
-
-This is shown Figure~\ref{fig:miller} shows our predicted ${\rm
-  L_{X}/L_{\rm edd}=\epsilon_X \Mdot c^2}$ for core (blue) and cusp
-  (green) galaxies superimposed with x-ray measurements (red stars),
-  upper limits (red triangles) from \citet{Miller+15}. $\epsilon_X$ is
-  an efficiency factor and $\Mdot$ is calculated using
-  Equation~\eqref{eq:mdot_analytic}, with parameters consistent with
-  the average star formation history for each $\Mbh$ (see the black
-  lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Our
-  predicted trend in  $L_{X}/L_{\rm edd}$ is steeper than the 
-  trend found in \citet{Miller+15} (black line). Note that we try two 
-  different prescriptions for $\epsilon_X$: $\epsilon_X=10^{-4}$ in
-  the left-hand panel and $\epsilon_X=10^{-1} \Mdot/0.01 \MdotEdd$
-  right-hand panel. In either case our predicted trend in $
-  L_{X}/L_{\rm edd}$ is opposite the observationally inferred
-  one. {\bf AG-Need a bit more discussion here.} We note that in the
-  right hand panel the observed galaxies are below the upper limits
-  from Ia supernovae and thermal instability and so may be accreting
-  in a thermally stable state {\bf AG-but it does not mean that they
-    actually are}.
+This appears in contradiction with the nuclear X-ray luminosities of quiescent galaxies, which (though showing broad scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha\simeq -0.25$ \citep{Pellegrini10, Miller+15}.
+Figure~\ref{fig:miller} shows our predicted value of $\langle L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of black hole mass for core (blue) and cusp (green) galaxies.
+The left panel assumes a constant low radiative efficiency $\epsilon_X = 10^{-4}$ typical of those  estimated for low luminosity AGN (e.g., \citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g., \citealt{Quataert+99}, \citealt{Quataert:2004a}), while the right panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio in the way predicted by simple models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
+Superimposed with the theoretical curves are symbols showing X-ray measurements (red stars) and upper limits (red triangles) from \citet{Miller+15}, along with the best power-law fit (red line; {\bf BDM: change to this!}) and the approximate X-ray detection threshold (gray line).
+Finally, shown with purple and orange lines are the maximum accretion rates for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) and set by Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), as well as the maximum accretion rate allowed by Compton heating (eq.~[\ref{eq:MdotC}]).
+
+For either of our assumptions about radiative efficiency our predicted trend in $\langle L_{X}/L_{\rm edd}\rangle$ for core and cusp galaxies is opposite the observationally inferred one.
+However, the observed $\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of observed galaxies are below the maximum ones for thermally stable accretion if $\epsilon_X \lesssim 10^{-4}$.
+This suggests that most nearby galaxies are consistent with accreting in a thermally stable steady state, even if our estimate of their predicted heating does not match the observed trend with $M_{\bullet}$ perfectly.
+On the other hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent with the accretion rate set by Ia blow-out.
+Also note that in the case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X = \dot{M}/\dot{M}_{\rm edd}$), the predicted branches of  $\langle L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$, calling into question attempts to extrapolate the $\langle L_{X} \rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to constrain the occupation fraction of black holes in the lowest mass galaxies (\citealt{Miller+15}).
+
+\subsection{Demographics of SMBHs}
 
@@
 
+Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
+\begin{eqnarray}
+  t_{\rm growth}/t_{\rm h} \approx 
+  \begin{cases}
+    250 M_{\bullet,8}^{-0.76}
+    v_{500}^{3.8}   \eta_{0.02}  & \text{core} \\
+    140 \Mbheight^{-0.48}
+    v_{500}^{2.4}   \eta_{0.02}  & \text{cusp}, 
+  \end{cases}
+  \label{eq:tgrow_analytic}
+\end{eqnarray}
+which we have normalized in terms of the Hubble time.
+
+There is a maximum accretion rate for a thermally stable flow
+(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
+time from thermally stable accretion
+
+\begin{align}
+  t_{\rm growth}/t_{\rm h} \gsim
+  \rm{max}\begin{cases}
+    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
+    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
+    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
+  \end{cases}
+  \label{eq:tgrow_min}
+\end{align}
+
+In Figure~\ref{fig:bh_growth} we plot the growth times for core and
+cusp galaxies, with parameters chosen for the average star formation
+history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
+and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
+respectively.  We also plot the maximum growth time for thermal
+instability from equation~\eqref{eq:tgrow_min} in purple.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{bh_growth.eps}
+\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
+  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
+  ($\Gamma=0.8$, green). These are calculated from
+  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
+  average star formation history at each $\Mbh$. We also plot a lower
+  bound on growth time for a themally stable flow (purple) from
+  equation~\eqref{eq:tgrow_min}.}
+\end{figure}
+
+\begin{itemize}
+\item{Fact that some low mass BHs appear to have nearly Eddington accretion rates, suggest an external origin - since the maximum Ia rate appears to be below this}
+\item{Growth of low mass BHS, e.g. \citealt{Kauffmann&Heckman09}}
+\end{itemize}
+
+If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
+
+However, \citet{McCourt+12} argue that even if cooling is exactly
+balanced by heating everywhere, there is still a local thermal
+instability that operates to turn hot gas into cold clouds.  However,
+this local instability only causes a significant local drop-out of
+mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the
+stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
+(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
+  crit}$ is also the condition for local instability, although the
+prefactor may be slightly different.
+
+\subsection{TDE Jets}
+
+Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
+
+\subsection{Jet Feedback}
+
+We also note
+here that the kinetic heating rate is proportional to the SMBH mass to
+a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
+core(cusp) galaxies, respectively. This dependence could have
+important implications for the dependence of the average nuclear X-ray
+luminosity of quiescent galaxies on the SMBH mass
+($\S\ref{sec:mdot}$).
+
+\subsection{Jet Power Correlation}
+
+Accretion rates onto SMBHs can in principle be estimated directly by
+assuming Bondi accretion and using high resolution X-ray observations
+to estimate the gas temperature and density near the Bondi radius.
+This technique has led to the intriguing conclusion that the Bondi
+accretion power correlates with the AGN jet power (e.g.,
+\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
+\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
+required to inflate the observed cavities within the X-ray emitting
+gas.  In practice is it almost never possible to resolve the Bondi
+radius, therefore requiring all such studies to extrapolate the
+observed gas temperature and density profiles to smaller radial
+scales.
+
+\subsection{Nuclear Star Clusters}
+Do nuclear star clusters in other galaxies look like scaled up/down
+versions of the one in our own galaxy? If so this would imply a radial
+gradient in the average of the stellar population which would imply a
+heating which would be dependent on radius.
+
+\subsection{SFR-AGN connection}
+In fact it seems like the star formation rate may trace AGN
+episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
+
+\subsection{Type II Supernovae}
+Type II supernovae should provide some heating as well for younger
+stellar populations...In fact at least on large scales they may be the
+dominant source of heating on timescales of 10-40 Myr.
+
 % Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
@@
 
-\subsection{Comparison to Observations}
-{\bf AG: I do want some discussion of reproducing the density profiles
-for individual observations, but I am not sure how to do it with our
-new gridded approach.  BDM: too bad!}
 % \subsubsection{Comparison to measured temperature and density profiles}
@@
 
-\subsection{X-ray Diagnostics of SMBH Occupation}
-\label{sec:occ}
-The free-free emission from steady state gas flows in low mass
-galactic nuclei may serve as useful diagnostics of the presence or
-absence of a SMBH.  We focus primarily on low-mass galaxies in this
-subsection, both because this is the portion of parameter space in
-which gas inflow will generally proceed in a steady-state fashion, and
-because of recent observations suggesting that a nontrivial fraction
-of these galaxies may lack nuclear SMBHs.  If this absence is
-confirmed, it could have implications for galaxy evolution, SMBH
-recoil distributions, and SMBH seed formation models.
-
-We can approximate the gas temperature as
-
-\begin{equation}
-% T \approx \frac{\mu m_{\rm p} (\gamma-1)}{2\gamma k_{\rm B}}
-% \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r \right).
- \kb T \approx 2.1\times 10^{-25} \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r
- \right) {\rm [cgs]}.
-\end{equation}
-
-In the absence of a central SMBH, we can expect to see an exponential
-cutoff in the free-free X-ray spectrum at energies above
-
-\begin{equation}
-E_{\rm cut} = 0.32~{\rm keV} v_{500}^2,
-\end{equation}
-
-assuming $\gamma = 5/3$.  This cutoff will therefore be located in the
-portion of the soft X-ray covered by {\it Chandra}'s ACIS
-spectrometer.  By writing the free-free emissivity as
-
-\begin{equation} 
-\varepsilon_{\nu}^{\rm ff} = 6.8\times10^{-38}
-\frac{\rm erg}{\rm s~cm^3~Hz} Z^2n_{\rm e}n_{\rm
-i}T^{-1/2}\bar{g}_{\rm ff}\exp\left(\frac{-h\nu}{k_{\rm B}T}\right),
-\end{equation}
-
-where $Z$ is the atomic number of the ions, $n_{\rm e}$ and $n_{\rm
-  i}$ are respectively the electron and ion number density, and
-$\bar{g}_{\rm ff}$ is the Gaunt factor.  In the following we set
-$n_{\rm e}=Y_{\rm e}n_{\rm i}$, and approximate
-\begin{equation}
-n_{\rm i} \approx \frac{\dot{M}}{(4\pi/3) \rs^2 \mu \mp}\sqrt{ \frac{r_{\rm s}}{ 2 G \Mbh} } \left( \frac{r}{\rs} \right)^{-n}.
-\end{equation}
-
-We now write the total spectral luminosity density seen in unresolved
-X-ray observations above the cutoff energy as
-
-\begin{align}
- L_{\nu}^{\rm ff} =& \int_0^{r_{\rm s}} 4\pi r^2 \varepsilon_{\nu}^{\rm ff}{\rm d}r \\
-\approx & 2.8\times 10^{16} \, {\rm ergs \, s^{-1}
-  \, Hz^{-1}} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm
-      year}} \right)^2 \left(\frac{\rs}{10^{-2}~{\rm pc}} \right)^{-1}
-   \notag \\
-& \times \left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \notag \\
-\approx & 3.9\times 10^{14} {\rm ergs~s^{-1}~Hz^{-1}}
-\eta^2 \left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{1.96} \notag\\&\times
-\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^{-2.8} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
-\end{align}
-
-The second line of this equation makes the approximation that
-$GM_\bullet/r$ dominates $\tilde{v}_{\rm w}^2$ throughout the
-integrand, which will be true for energies modestly higher than
-$E_{\rm cut}$.  The lower (upper) endpoint for this integral are
-arbitrary so long as it is somewhat less (greater) than the radius at
-which the observed frequency $\nu$ sees its exponential free-free
-cutoff. We have also set $n=1$.
-
-In general, these ``cut-off'' X-ray luminosities are quite small, and
-even {\it Chandra} would have little hope of detecting them in any but
-the nearest dwarf galaxies (e.g. the Magellanic clouds).  However, if
-source confusion is not present, this technique could test for the
-presence of IMBHs in very nearby dwarf galaxies, or more speculatively
-Galactic star clusters.
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Demographics of SMBHs}
-
-Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
-\begin{eqnarray}
-  t_{\rm growth}/t_{\rm h} \approx 
-  \begin{cases}
-    250 M_{\bullet,8}^{-0.76}
-    v_{500}^{3.8}   \eta_{0.02}  & \text{core} \\
-    140 \Mbheight^{-0.48}
-    v_{500}^{2.4}   \eta_{0.02}  & \text{cusp}, 
-  \end{cases}
-  \label{eq:tgrow_analytic}
-\end{eqnarray}
-which we have normalized in terms of the Hubble time.
-
-There is a maximum accretion rate for a thermally stable flow
-(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
-time from thermally stable accretion
-
-\begin{align}
-  t_{\rm growth}/t_{\rm h} \gsim
-  \rm{max}\begin{cases}
-    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
-    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
-    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
-  \end{cases}
-  \label{eq:tgrow_min}
-\end{align}
-
-In Figure~\ref{fig:bh_growth} we plot the growth times for core and
-cusp galaxies, with parameters chosen for the average star formation
-history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
-and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
-respectively.  We also plot the maximum growth time for thermal
-instability from equation~\eqref{eq:tgrow_min} in purple.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{bh_growth.eps}
-\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
-  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
-  ($\Gamma=0.8$, green). These are calculated from
-  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
-  average star formation history at each $\Mbh$. We also plot a lower
-  bound on growth time for a themally stable flow (purple) from
-  equation~\eqref{eq:tgrow_min}.}
-\end{figure}
-
-\subsection{Cooling}
-\label{sec:cooling}
-
-\section{Discussion}
-
-\begin{itemize}
-\item{Fact that some low mass BHs appear to have nearly Eddington accretion rates, suggest an external origin - since the maximum Ia rate appears to be below this}
-\item{Growth of low mass BHS, e.g. \citealt{Kauffmann&Heckman09}}
-\end{itemize}
-
-If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
-However, \citet{McCourt+12} argue that even if cooling is exactly
-balanced by heating everywhere, there is still a local thermal
-instability that operates to turn hot gas into cold clouds.  However,
-this local instability only causes a significant local drop-out of
-mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the
-stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
-(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
-  crit}$ is also the condition for local instability, although the
-prefactor may be slightly different.
-
-\subsection{TDE Jets}
-
-Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
-
-\subsection{Jet Feedback}
-
-We also note
-here that the kinetic heating rate is proportional to the SMBH mass to
-a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
-core(cusp) galaxies, respectively. This dependence could have
-important implications for the dependence of the average nuclear X-ray
-luminosity of quiescent galaxies on the SMBH mass
-($\S\ref{sec:mdot}$).
-
-\subsection{Jet Power Correlation}
-
-Accretion rates onto SMBHs can in principle be estimated directly by
-assuming Bondi accretion and using high resolution X-ray observations
-to estimate the gas temperature and density near the Bondi radius.
-This technique has led to the intriguing conclusion that the Bondi
-accretion power correlates with the AGN jet power (e.g.,
-\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-required to inflate the observed cavities within the X-ray emitting
-gas.  In practice is it almost never possible to resolve the Bondi
-radius, therefore requiring all such studies to extrapolate the
-observed gas temperature and density profiles to smaller radial
-scales.
-
-\subsection{Nuclear Star Clusters}
-Do nuclear star clusters in other galaxies look like scaled up/down
-versions of the one in our own galaxy? If so this would imply a radial
-gradient in the average of the stellar population which would imply a
-heating which would be dependent on radius.
-
-\subsection{SFR-AGN connection}
-In fact it seems like the star formation rate may trace AGN
-episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
-
-\subsection{Type II Supernovae}
-Type II supernovae should provide some heating as well for younger
-stellar populations...In fact at least on large scales they may be the
-dominant source of heating on timescales of 10-40 Myr.
-
-  \section{Summary}
-  \label{sec:summary}
+\section{Conclusions}
+\label{sec:conclusions}
   We have calculated steady-state models for circumnuclear medium of a
@@
 
+\section{Death Row}
+
+\subsection{X-ray Diagnostics of SMBH Occupation}
+\label{sec:occ}
+The free-free emission from steady state gas flows in low mass
+galactic nuclei may serve as useful diagnostics of the presence or
+absence of a SMBH.  We focus primarily on low-mass galaxies in this
+subsection, both because this is the portion of parameter space in
+which gas inflow will generally proceed in a steady-state fashion, and
+because of recent observations suggesting that a nontrivial fraction
+of these galaxies may lack nuclear SMBHs.  If this absence is
+confirmed, it could have implications for galaxy evolution, SMBH
+recoil distributions, and SMBH seed formation models.
+
+We can approximate the gas temperature as
+
+\begin{equation}
+% T \approx \frac{\mu m_{\rm p} (\gamma-1)}{2\gamma k_{\rm B}}
+% \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r \right).
+ \kb T \approx 2.1\times 10^{-25} \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r
+ \right) {\rm [cgs]}.
+\end{equation}
+
+In the absence of a central SMBH, we can expect to see an exponential
+cutoff in the free-free X-ray spectrum at energies above
+
+\begin{equation}
+E_{\rm cut} = 0.32~{\rm keV} v_{500}^2,
+\end{equation}
+
+assuming $\gamma = 5/3$.  This cutoff will therefore be located in the
+portion of the soft X-ray covered by {\it Chandra}'s ACIS
+spectrometer.  By writing the free-free emissivity as
+
+\begin{equation} 
+\varepsilon_{\nu}^{\rm ff} = 6.8\times10^{-38}
+\frac{\rm erg}{\rm s~cm^3~Hz} Z^2n_{\rm e}n_{\rm
+i}T^{-1/2}\bar{g}_{\rm ff}\exp\left(\frac{-h\nu}{k_{\rm B}T}\right),
+\end{equation}
+
+where $Z$ is the atomic number of the ions, $n_{\rm e}$ and $n_{\rm
+  i}$ are respectively the electron and ion number density, and
+$\bar{g}_{\rm ff}$ is the Gaunt factor.  In the following we set
+$n_{\rm e}=Y_{\rm e}n_{\rm i}$, and approximate
+\begin{equation}
+n_{\rm i} \approx \frac{\dot{M}}{(4\pi/3) \rs^2 \mu \mp}\sqrt{ \frac{r_{\rm s}}{ 2 G \Mbh} } \left( \frac{r}{\rs} \right)^{-n}.
+\end{equation}
+
+We now write the total spectral luminosity density seen in unresolved
+X-ray observations above the cutoff energy as
+
+\begin{align}
+ L_{\nu}^{\rm ff} =& \int_0^{r_{\rm s}} 4\pi r^2 \varepsilon_{\nu}^{\rm ff}{\rm d}r \\
+\approx & 2.8\times 10^{16} \, {\rm ergs \, s^{-1}
+  \, Hz^{-1}} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm
+      year}} \right)^2 \left(\frac{\rs}{10^{-2}~{\rm pc}} \right)^{-1}
+   \notag \\
+& \times \left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \notag \\
+\approx & 3.9\times 10^{14} {\rm ergs~s^{-1}~Hz^{-1}}
+\eta^2 \left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{1.96} \notag\\&\times
+\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^{-2.8} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
+\end{align}
+
+The second line of this equation makes the approximation that
+$GM_\bullet/r$ dominates $\tilde{v}_{\rm w}^2$ throughout the
+integrand, which will be true for energies modestly higher than
+$E_{\rm cut}$.  The lower (upper) endpoint for this integral are
+arbitrary so long as it is somewhat less (greater) than the radius at
+which the observed frequency $\nu$ sees its exponential free-free
+cutoff. We have also set $n=1$.
+
+In general, these ``cut-off'' X-ray luminosities are quite small, and
+even {\it Chandra} would have little hope of detecting them in any but
+the nearest dwarf galaxies (e.g. the Magellanic clouds).  However, if
+source confusion is not present, this technique could test for the
+presence of IMBHs in very nearby dwarf galaxies, or more speculatively
+Galactic star clusters.
+
   \clearpage

### 2015-02-22 ms.tex
omg

@@
 
+Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
+
 \subsection{Demographics of SMBHs}
@@
   bound on growth time for a themally stable flow (purple) from
-  equation~\eqref{eq:tgrow_min}.}
+  equation~\eqref{eq:tgrow_min}. {\bf BDM: add Compton and Ia heating lines!}}
 \end{figure}

### 2015-02-23 ms.tex
regenerating mdot_mass figure to be consistent with the new analytic prescription for r_s...

@@
 
-Figure \ref{fig:vwSources} shows that the CNM heating rate is on average approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
-For fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This appears in contradiction with the nuclear X-ray luminosities of quiescent galaxies, which (though showing broad scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha\simeq -0.25$ \citep{Pellegrini10, Miller+15}.
-Figure~\ref{fig:miller} shows our predicted value of $\langle L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of black hole mass for core (blue) and cusp (green) galaxies.
-The left panel assumes a constant low radiative efficiency $\epsilon_X = 10^{-4}$ typical of those  estimated for low luminosity AGN (e.g., \citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g., \citealt{Quataert+99}, \citealt{Quataert:2004a}), while the right panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio in the way predicted by simple models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
-Superimposed with the theoretical curves are symbols showing X-ray measurements (red stars) and upper limits (red triangles) from \citet{Miller+15}, along with the best power-law fit (red line; {\bf BDM: change to this!}) and the approximate X-ray detection threshold (gray line).
-Finally, shown with purple and orange lines are the maximum accretion rates for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) and set by Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), as well as the maximum accretion rate allowed by Compton heating (eq.~[\ref{eq:MdotC}]).
-
-For either of our assumptions about radiative efficiency our predicted trend in $\langle L_{X}/L_{\rm edd}\rangle$ for core and cusp galaxies is opposite the observationally inferred one.
-However, the observed $\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of observed galaxies are below the maximum ones for thermally stable accretion if $\epsilon_X \lesssim 10^{-4}$.
-This suggests that most nearby galaxies are consistent with accreting in a thermally stable steady state, even if our estimate of their predicted heating does not match the observed trend with $M_{\bullet}$ perfectly.
-On the other hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent with the accretion rate set by Ia blow-out.
-Also note that in the case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X = \dot{M}/\dot{M}_{\rm edd}$), the predicted branches of  $\langle L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$, calling into question attempts to extrapolate the $\langle L_{X} \rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to constrain the occupation fraction of black holes in the lowest mass galaxies (\citealt{Miller+15}).
+Figure \ref{fig:vwSources} shows that the CNM heating rate is on
+average approximately constant with SMBH mass, except for the largest
+black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For
+fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
+mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies,
+respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+This appears in contradiction with the nuclear X-ray luminosities of
+quiescent galaxies, which (though showing broad scatter) instead on
+average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where
+$\alpha\simeq -0.25$ \citep{Pellegrini10, Miller+15}.
+Figure~\ref{fig:miller} shows our predicted value of $\langle
+L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of
+black hole mass for core (blue) and cusp (green) galaxies.  The left
+panel assumes a constant low radiative efficiency $\epsilon_X =
+10^{-4}$ typical of those estimated for low luminosity AGN (e.g.,
+\citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g.,
+\citealt{Quataert+99}, \citealt{Quataert:2004a}), while the right
+panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$
+that depends on the Eddington ratio in the way predicted by simple
+models for radiatively inefficient accretion flows
+(\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
+are symbols showing X-ray measurements (red stars) and upper limits
+(red triangles) from \citet{Miller+15}, along with the best power-law
+fit (red line; {\bf BDM: change to this!}) and the approximate X-ray
+detection threshold (gray line).  Finally, shown with purple and
+orange lines are the maximum accretion rates for thermally stable
+accretion (eq.~[\ref{eq:Mdotmax}]) and set by Ia blow-out
+(eq.~[\ref{eq:eddr_Ia}]), as well as the maximum accretion rate
+allowed by Compton heating (eq.~[\ref{eq:MdotC}]).
+
+For either of our assumptions about radiative efficiency our predicted
+trend in $\langle L_{X}/L_{\rm edd}\rangle$ for core and cusp galaxies
+is opposite the observationally inferred one.  However, the observed
+$\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of
+observed galaxies are below the maximum ones for thermally stable
+accretion if $\epsilon_X \lesssim 10^{-4}$.  This suggests that most
+nearby galaxies are consistent with accreting in a thermally stable
+steady state, even if our estimate of their predicted heating does not
+match the observed trend with $M_{\bullet}$ perfectly.  On the other
+hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent
+with the accretion rate set by Ia blow-out.  Also note that in the
+case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X =
+\dot{M}/\dot{M}_{\rm edd}$), the predicted branches of $\langle
+L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$,
+calling into question attempts to extrapolate the $\langle L_{X}
+\rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to
+constrain the occupation fraction of black holes in the lowest mass
+galaxies (\citealt{Miller+15}).
 

### 2015-02-23 ms.tex
magic

@@
 
-\subsection{Nuclear X-ray Luminosities of Quiescent Galaxies}
+\subsection{Nuclear X-ray Luminosities}
 \label{sec:mdot}
 
-Figure \ref{fig:vwSources} shows that the CNM heating rate is on
-average approximately constant with SMBH mass, except for the largest
-black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For
-fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
+Figure \ref{fig:vwSources} shows that the average CNM heating rate is predicted to be approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
+For
+a fixed wind heating parameter, $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
 mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies,
 respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This appears in contradiction with the nuclear X-ray luminosities of
-quiescent galaxies, which (though showing broad scatter) instead on
-average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where
-$\alpha\simeq -0.25$ \citep{Pellegrini10, Miller+15}.
+This dependence appears in contradiction with the nuclear X-ray luminosities of
+quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.
+
 Figure~\ref{fig:miller} shows our predicted value of $\langle
@@
 fit (red line; {\bf BDM: change to this!}) and the approximate X-ray
-detection threshold (gray line).  Finally, shown with purple and
+detection threshold (gray line).  Finally, shown with purple, orange, and {\bf brown} lines
 orange lines are the maximum accretion rates for thermally stable
-accretion (eq.~[\ref{eq:Mdotmax}]) and set by Ia blow-out
-(eq.~[\ref{eq:eddr_Ia}]), as well as the maximum accretion rate
-allowed by Compton heating (eq.~[\ref{eq:MdotC}]).
-
-For either of our assumptions about radiative efficiency our predicted
-trend in $\langle L_{X}/L_{\rm edd}\rangle$ for core and cusp galaxies
-is opposite the observationally inferred one.  However, the observed
+accretion (eq.~[\ref{eq:Mdotmax}]), set by SN Ia blow-out
+(eq.~[\ref{eq:eddr_Ia}]), and allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.
+
+First note that to first order, our predicted values of $\langle L_{X}/L_{\rm edd}\rangle$ for heating corresponding to average star formation reside reasonably close to the data $\langle L_{X}/L_{\rm edd}\rangle$.
+However, for either assumption about radiative efficiency, our predicted positive trend of $\langle L_{X}/L_{\rm edd}\rangle$ with black hole mass is opposite the observationally inferred one, which instead shows $L_{X}/L_{\rm edd}$ decreasing with $M_{\bullet}$.
+Comparison to the data is improved, however, by taking into account the fact that larger(smaller) black hole masses are more commonly associated with core(cusp) galaxies, resulting in a flatter predicted trend for $\langle L_X/L_{\rm edd}\rangle$ when both samples are combined.
+The large scatter observed in $L_{X}/L_{\rm edd}$ of typically two to four orders of magnitude in the \citet{Pellegrini10} sample can also be understood in our steady-accreting model by the .
+Alternatively, cases where the older stellar population precludes a steady accretion flow, the scatter could be due to (e.g.~\citealt{Pellegrini&Ciotti98}; refs).
+
+   Finally, we note that \citet{Pellegrini10} finds that $L_{X}$ does not show any dependence on the age of the stellar population in the central galactic region for old populations with stellar ages $> 3$ Gyr, although less X-ray luminous nuclei are found among galaxies with a younger stellar population.
+This
+
+ however, when the
+
+.  However, this conclusion comes with several caveats: (1)
+
+However, the observed values of 
 $\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of
@@
 galaxies (\citealt{Miller+15}).
+
+Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
 

### 2015-02-23 ms.tex
lx

--- 2015-02-23 ms.tex
@@
 
-\subsection{Nuclear X-ray Luminosities of Quiescent Galaxies}
+\subsection{Nuclear X-ray Luminosities}
 \label{sec:mdot}
 
-Figure \ref{fig:vwSources} shows that the CNM heating rate is on
-average approximately constant with SMBH mass, except for the largest
-black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For
-fixed wind heating $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
-mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies,
-respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This appears in contradiction with the nuclear X-ray luminosities of
-quiescent galaxies, which (though showing broad scatter) instead on
-average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where
-$\alpha\simeq -0.25$ \citep{Pellegrini10, Miller+15}.
-Figure~\ref{fig:miller} shows our predicted value of $\langle
-L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of
-black hole mass for core (blue) and cusp (green) galaxies.  The left
-panel assumes a constant low radiative efficiency $\epsilon_X =
+Figure \ref{fig:vwSources} shows that the CNM heating rate due to the average star formation history of a galaxy is predicted to be approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
+For a fixed wind heating parameter, $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
+mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+This dependence, show more precisely in Figure XXX, appears in contradiction with the nuclear X-ray luminosities of
+quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.
+
+Figure~\ref{fig:miller} shows our resulting predictions for $\langle L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of black hole mass for core (blue) and cusp (green) galaxies.
+The left
+panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X =
 10^{-4}$ typical of those estimated for low luminosity AGN (e.g.,
@@
 panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$
-that depends on the Eddington ratio in the way predicted by simple
-models for radiatively inefficient accretion flows
-(\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
-are symbols showing X-ray measurements (red stars) and upper limits
-(red triangles) from \citet{Miller+15}, along with the best power-law
-fit (red line; {\bf BDM: change to this!}) and the approximate X-ray
-detection threshold (gray line).  Finally, shown with purple and
-orange lines are the maximum accretion rates for thermally stable
-accretion (eq.~[\ref{eq:Mdotmax}]) and set by Ia blow-out
-(eq.~[\ref{eq:eddr_Ia}]), as well as the maximum accretion rate
-allowed by Compton heating (eq.~[\ref{eq:MdotC}]).
-
-For either of our assumptions about radiative efficiency our predicted
-trend in $\langle L_{X}/L_{\rm edd}\rangle$ for core and cusp galaxies
-is opposite the observationally inferred one.  However, the observed
+that depends on the Eddington ratio in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
+are symbols showing X-ray measurements (stars) and upper limits
+(triangles) compiled by \citet{Miller+15}, along with the best power-law
+fit (red line) and the X-ray detection threshold (gray line).  Finally, purple, orange, and {\bf brown} lines
+orange lines show the maximum accretion rates for thermally stable
+accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
+(eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.
+
+To zeroth order our predicted values of $\langle L_{X}/L_{\rm edd}\rangle$ for average star formation histories overlap with the data reasonably well.
+However, our predicted increase of $\langle L_{X}/L_{\rm edd}\rangle$ with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
+Better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
+The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude is also natural within a steady-accretion scenario due to the strong sensitivity of the Eddington ratio on the heating rate, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the likewise sensitive dependence of the heating rate on the intermittency of the star formation history (Fig.~NICK).
+Alternatively, in the case of an old stellar population incapable of supporting steady accretion, resulting in cyclic accretion episodes (e.g.~\citealt{Ciotti+10}), this large scatter can be understood by the wind range of gas masses experienced over the course of a cycle.
+The cyclic model also predicts that a higher fraction of $L_{X}$ nuclei with smaller stellar ages, consistent with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations host less X-ray luminous nuclei.
+However, this observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
+
+However, the observed values of 
 $\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of

### 2015-02-24 ms.tex
Some modifications to table
Core appreciation day
lx

@@
   {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
-{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
+  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
   \hline
-$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
+  $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
+  $    10^{ 6 }$ & 600 & 0.8 & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
+  $    10^{ 6 }$ & 1200 & 0.8 & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
+  $    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
+  $    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
+  $    10^{ 7 }$ & 1200 & 0.8 & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
+  $    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
+  $    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
+  $    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
+  $    10^{ 7 }$ & 300 & 0.8 & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
+  $    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
+  $    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
+  $    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
+  $    10^{ 8 }$ & 300 & 0.8 & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
+  $    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ &
+  $\mathbf{4.6}$ \\
+  $    10^{ 8 \dagger}$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ &
+  $\mathbf{5.6}$ \\
+  $    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ &
+  $\mathbf{0.43}$ \\
   \hline
-$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
-$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
-$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
-$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
-$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
-$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
-$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
-$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
-$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
-$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
-$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
-$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
-$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
-$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
-$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
-$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
-$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
-$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
-$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
-$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
-$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
+  $    10^{ 6 }$ & 1200 & 0.1 & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
+  $    10^{ 7 }$ & 1200 & 0.1 & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
+  $    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
+  $    10^{ 8 }$ & 600 & 0.1 & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
+  $    10^{ 6 }$ & 600 & 0.1 & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
+  $    10^{ 6 }$ & 600 & 0.1 & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
+  $    10^{ 7 }$ & 600 & 0.1 & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
+  $    10^{ 7 }$ & 600 & 0.1 & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
+  $    10^{ 8 }$ & 600 & 0.1 & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
+  $    10^{ 8 }$ & 600 & 0.1 & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
   \hline
+
 \label{table:models}  
@@
 0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
-stagnation radius.  Thermally unstable solutions are shown in bold text.  $^{(e)}$ Is solution thermally unstable?
-$\dagger$Calculated including radiative cooling, assuming $\eta =
-0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
+stagnation radius.  Thermally unstable solutions are shown in bold
+text.
+ {\bf  BDM: (3) make sure all combinations of vw and mbh
   are included. AG: Realized that the solution I ran earlier, with
@@
   according to our thermal instability. I am worried that this
-  solution may not be representative due to the small break radius. BDM: change TI column to simply bolding tcool ratio in those cases which are thermally unstable.}
+  solution may not be representative due to the small break radius.}
 \end{tablenotes}
@@
 
-Figure \ref{fig:vwSources} shows that the CNM heating rate due to the average star formation history of a galaxy is predicted to be approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
-For a fixed wind heating parameter, $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
-mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This dependence, show more precisely in Figure XXX, appears in contradiction with the nuclear X-ray luminosities of
-quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.
-
-Figure~\ref{fig:miller} shows our resulting predictions for $\langle L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of black hole mass for core (blue) and cusp (green) galaxies.
-The left
-panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X =
-10^{-4}$ typical of those estimated for low luminosity AGN (e.g.,
+The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g., \citealt{Ho08} and references therein).
+Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
+For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.
+
+Figure~\ref{fig:miller} shows our predictions for $\langle L_{X}\rangle =\epsilon_X \epsilon_{\rm bol} \Mdot c^2$ in Eddington units as a function of black hole mass for core (blue) and cusp (green) galaxies, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
+The left panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
 \citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g.,
-\citealt{Quataert+99}, \citealt{Quataert:2004a}), while the right
-panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$
-that depends on the Eddington ratio in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
+\citealt{Quataert+99}, \citealt{Quataert:2004a}).  The luminosity shown in the right
+panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
+Superimposed with the theoretical curves
 are symbols showing X-ray measurements (stars) and upper limits

### 2015-02-24 ms.tex
lx

@@
 For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.
-
-Figure~\ref{fig:miller} shows our predictions for $\langle L_{X}\rangle =\epsilon_X \epsilon_{\rm bol} \Mdot c^2$ in Eddington units as a function of black hole mass for core (blue) and cusp (green) galaxies, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
-The left panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
-\citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g.,
-\citealt{Quataert+99}, \citealt{Quataert:2004a}).  The luminosity shown in the right
+This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.
+
+Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass for core (blue) and cusp (green) galaxies, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
+The left panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}) and SgrA* (e.g.,
+\citealt{Quataert+99}).  The luminosity shown in the right
 panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
-Superimposed with the theoretical curves
-are symbols showing X-ray measurements (stars) and upper limits
-(triangles) compiled by \citet{Miller+15}, along with the best power-law
-fit (red line) and the X-ray detection threshold (gray line).  Finally, purple, orange, and {\bf brown} lines
-orange lines show the maximum accretion rates for thermally stable
-accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
+Plotted next to the theoretical curves are the X-ray measurements (stars) and upper limits
+(triangles) from \citet{Miller+15} (cf.~\citealt{Gallo+10}), along with the resulting best power-law
+fit (red line) and the X-ray detection threshold (gray line).
+Purple, orange, and {\bf brown} lines show the maximum accretion rates for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
 (eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.
 
-To zeroth order our predicted values of $\langle L_{X}/L_{\rm edd}\rangle$ for average star formation histories overlap with the data reasonably well.
-However, our predicted increase of $\langle L_{X}/L_{\rm edd}\rangle$ with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
-Better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
-The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude is also natural within a steady-accretion scenario due to the strong sensitivity of the Eddington ratio on the heating rate, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the likewise sensitive dependence of the heating rate on the intermittency of the star formation history (Fig.~NICK).
-Alternatively, in the case of an old stellar population incapable of supporting steady accretion, resulting in cyclic accretion episodes (e.g.~\citealt{Ciotti+10}), this large scatter can be understood by the wind range of gas masses experienced over the course of a cycle.
-The cyclic model also predicts that a higher fraction of $L_{X}$ nuclei with smaller stellar ages, consistent with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations host less X-ray luminous nuclei.
-However, this observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
+To first order our predicted values of $\langle L_{X}/L_{\rm edd}\rangle$ for the average galactic star formation histories overlap with the data reasonably well.
+Our prediction that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
+However, better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
+The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude can also be understood within a steady-accretion scenario due to the strong sensitivity of the accretion rate on the efficacy of gas heating, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the equally sensitive dependence of the heating rate on stochastic intermittency in the star formation history (Fig.~NICK).
+
+In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
+The cyclic model also predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages.
+This appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
+This observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
 
@@
 Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
+
+\subsection{Steady Accretion versus Cyclic Outbursts}
+
+GALEX observations have shown that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
 

### 2015-02-25 ms.tex
fixing rad

@@
 stagnation radius (marked as squares).  When $\dot{q}_{\rm
-heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
-\lesssim 10$, the flow is susceptible thermal instabilities.  {\bf
-BDM: change y axis labels to qdotheat/qdotrad, tcool/tff}.}
+heat}/\dot{q}_{\rm rad} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
+\lesssim 10$, the flow is susceptible thermal instabilities.}
 \end{figure}
@@
 Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).
-Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.
-{\bf BDM: change x axis range so lines start at 3e6 yr }}
+Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
 \end{figure}

### 2015-02-27 ms.tex
blah
n

@@
     galaxies ($\Gamma$=0.1). Squares mark the location of
-    the stagnation radius for each solution {\bf BDM: added colored labels for the $v_w$ value, e.g. a blue 1200 km/s directly to the top figure.  what does v/cs look like?} .
+    the stagnation radius for each solution
  }
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{bh_growth.eps}
-\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
-  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
-  ($\Gamma=0.8$, green). These are calculated from
+\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
+\caption{\label{fig:bh_growth} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
+  of the Hubble time $\th$ for core ($\Gamma=0.1$, solid black) and
+  cusp galaxies ($\Gamma=0.8$, dash-dotted black). These are calculated from
   equation~\ref{eq:tgrow_analytic} with parameters chosen for the
   average star formation history at each $\Mbh$. We also plot a lower
-  bound on growth time for a themally stable flow (purple) from
-  equation~\eqref{eq:tgrow_min}. {\bf BDM: add Compton and Ia heating lines!}}
+  bound on growth time for a themally stable flow (yellow) from
+  equation~\eqref{eq:tgrow_min}.}
 \end{figure}

### 2015-02-28 ms.tex
rotation

@@
 Our spherically symmetric model neglects the effects of angular momentum on the gas evolution.
-However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$, where $l_{r_{s}} = r_{s}\langle V_{\phi}\rangle |_{r_s}$ is the specific angular momentum of stars near the stagnation radius, from which most of the accreted mass originates, and $\langle v_{\phi}\rangle$ is their average azimuthal velocity.
-
-Using two-dimensional kinematic data, \citet{EmsellemCappellari+:2007a} measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
-  \begin{align}
-    \lambda_R=\frac{\langle R|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
+However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$.
+Here $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar specific angular momentum near the stagnation radius, from which most of the accreted mass originates, where $V_{\phi}$ is the stellar azimuthal velocity.
+
+\citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data to measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
+  \begin{align}
+    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
   \end{align}
@@
 \ee
-where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$ for the thermally-stable solutions of interest.
-
-\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R < 0.1$ on scales less that 10 per cent of the galaxy radius, in which case equation (\ref{eq:rcirc}) shows that $r_{\rm circ} \lesssim 0.01r_{s}$.
-Since this location lies well inside the inner sonic point of the flow, we conclude that angular momentum will only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow, justifying its neglect in calculating quantities such as the mass accretion rate.
+where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, as satisfied for thermally-stable solutions of interest.
+
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales less that 10 per cent of the galaxy half-light radius and that $\lambda_R$ is a decreasing function of $R$, in which case from equation (\ref{eq:rcirc}) we conclude that $r_{\rm circ} \lesssim 0.01r_{s}$.
+This location lies well inside the inner sonic point of the flow, suggesting that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
+To first order we are thus justifying in neglecting its effects on our quantities such as the mass accretion rate.
 

### 2015-02-28 ms.tex
rotation 2

@@
 Our spherically symmetric model neglects the effects of angular momentum on the gas evolution.
-However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$.
+However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l^{2}_{r_{s}}/(GM_{\bullet})$.
 Here $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar specific angular momentum near the stagnation radius, from which most of the accreted mass originates, where $V_{\phi}$ is the stellar azimuthal velocity.
@@
 
-\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales less that 10 per cent of the galaxy half-light radius and that $\lambda_R$ is a decreasing function of $R$, in which case from equation (\ref{eq:rcirc}) we conclude that $r_{\rm circ} \lesssim 0.01r_{s}$.
-This location lies well inside the inner sonic point of the flow, suggesting that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales less that 10 per cent of the galaxy half-light radius and that $\lambda_R$ is a decreasing function of $R$.
+From equation (\ref{eq:rcirc}) we conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, a location well inside the inner sonic point of the flow (typically located at $\sim 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).
+This suggests that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
 To first order we are thus justifying in neglecting its effects on our quantities such as the mass accretion rate.
@@
 \caption{Summary of Numerical Solutions}
-\begin{tabular}{lccccccccccccc}
+\begin{tabular}{lccccccccc}
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
-  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
   \hline
-  $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
-  $    10^{ 6 }$ & 600 & 0.8 & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
-  $    10^{ 6 }$ & 1200 & 0.8 & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
-  $    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
-  $    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
-  $    10^{ 7 }$ & 1200 & 0.8 & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
-  $    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
-  $    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
-  $    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
-  $    10^{ 7 }$ & 300 & 0.8 & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
-  $    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
-  $    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
-  $    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
-  $    10^{ 8 }$ & 300 & 0.8 & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
-  $    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ &
+ & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
+\hline
+  $    10^{ 6 }$ & 300 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
+  $    10^{ 6 }$ & 600  & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
+  $    10^{ 6 }$ & 1200  & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
+  $    10^{ 7 }$ & 300 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
+  $    10^{ 7 }$ & 600  & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
+  $    10^{ 7 }$ & 1200  & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
+  $    10^{ 8 }$ & 300 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
+  $    10^{ 8 }$ & 600  & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
+  $    10^{ 8 }$ & 1200  & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
+  $    10^{ 7 }$ & 300  & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
+  $    10^{ 7 }$ & 300  & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
+  $    10^{ 7 }$ & 300  & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
+  $    10^{ 7 }$ & 300  & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
+  $    10^{ 8 }$ & 300  & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
+  $    10^{ 8 }$ & 300  & 50 & $ 3.3 \times 10^{ -4 }$ &
   $\mathbf{4.6}$ \\
-  $    10^{ 8 \dagger}$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ &
+  $    10^{ 8 \dagger}$ & 300  & 50 & $ 9.1 \times 10^{ -4 }$ &
   $\mathbf{5.6}$ \\
-  $    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ &
+  $    10^{ 8 }$ & 300 & 200 & $ 1.4 \times 10^{ -3 }$ &
   $\mathbf{0.43}$ \\
   \hline
-  $    10^{ 6 }$ & 1200 & 0.1 & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
-  $    10^{ 7 }$ & 1200 & 0.1 & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
-  $    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
-  $    10^{ 8 }$ & 600 & 0.1 & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
-  $    10^{ 6 }$ & 600 & 0.1 & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
-  $    10^{ 6 }$ & 600 & 0.1 & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
-  $    10^{ 7 }$ & 600 & 0.1 & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
-  $    10^{ 7 }$ & 600 & 0.1 & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
-  $    10^{ 8 }$ & 600 & 0.1 & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
-  $    10^{ 8 }$ & 600 & 0.1 & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
+ & & & $\Gamma = 0.1$ & & & & & & \\
   \hline
-
+  $    10^{ 6 }$ & 1200  & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
+  $    10^{ 7 }$ & 1200  & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200  & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
+  $    10^{ 8 }$ & 1200  & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
+  $    10^{ 8 }$ & 1200  & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
+  $    10^{ 8 }$ & 600  & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
+  $    10^{ 6 }$ & 600  & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
+  $    10^{ 6 }$ & 600  & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
+  $    10^{ 7 }$ & 600  & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
+  $    10^{ 7 }$ & 600  & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
+  $    10^{ 8 }$ & 600  & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
+  $    10^{ 8 }$ & 600  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
+  $    10^{ 8 }$ & 300  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
+  \hline
 \label{table:models}  
@@
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
-temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
+temperature $T(r)$, and radial velocity $|v(r)|$ (expressed in units of the sound speed), for the cusp
 ($\Gamma=0.8$) solutions within our grid.  As expected, the gas
@@
 The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
+The flow near the stagnation radius is subsonic, but becomes supersonic at two critical points, one located at small radii, $r \lesssim 0.1r_{\rm s}$, and the other located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.
+In many cases the supersonic transition is instigated by the transition to a steeper stellar density prorfile exterior to the outer Nuker break radius, making our solutions near $r_{\rm s}$ also potentially sensitive to the break radius value.
 % {\bf BDM: I made this up - in general we need

### 2015-02-28 ms.tex
table formatting - aleksey, please take note

@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
+ & ($M_{\odot}$) & (km s$^{-1}$) & (pc) & & & & & \\ 
 \hline
  & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
-\hline
-  $    10^{ 6 }$ & 300 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
-  $    10^{ 6 }$ & 600  & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
-  $    10^{ 6 }$ & 1200  & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
-  $    10^{ 7 }$ & 300 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
-  $    10^{ 7 }$ & 600  & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
-  $    10^{ 7 }$ & 1200  & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
-  $    10^{ 8 }$ & 300 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
-  $    10^{ 8 }$ & 600  & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
-  $    10^{ 8 }$ & 1200  & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
-  $    10^{ 7 }$ & 300  & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
-  $    10^{ 7 }$ & 300  & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
-  $    10^{ 7 }$ & 300  & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
-  $    10^{ 7 }$ & 300  & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
-  $    10^{ 8 }$ & 300  & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
-  $    10^{ 8 }$ & 300  & 50 & $ 3.3 \times 10^{ -4 }$ &
+  $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
+  ... & 600  & 100 & &$ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
+   ...    & 1200  & 100 & &$ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
+  $    10^{ 7 }$ & 300 & 100 & & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
+ ...    & ...   & 25 & &$ 7.8 \times 10^{ -5 }$ & 17 \\
+ ...      & ...   & 50 & &$ 7.9 \times 10^{ -5 }$ & 12 \\
+   ...    & ...   & 200 & &$ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
+   ...    & ...   & 400 & &$ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
+   ...     & 600  & 100 && $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
+   ...     & 1200  & 100 && $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
+  $    10^{ 8 }$ & 300 & 100 & & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
+...     & ...  & 25 & &$ 1.9 \times 10^{ -4 }$ & 12 \\
+   ...     & ...  & 50 & &$ 3.3 \times 10^{ -4 }$ &
   $\mathbf{4.6}$ \\
-  $    10^{ 8 \dagger}$ & 300  & 50 & $ 9.1 \times 10^{ -4 }$ &
+     ...$^{\dagger}$ & ...  & 50& & $ 9.1 \times 10^{ -4 }$ &
   $\mathbf{5.6}$ \\
-  $    10^{ 8 }$ & 300 & 200 & $ 1.4 \times 10^{ -3 }$ &
+   ... & ... & 200 && $ 1.4 \times 10^{ -3 }$ &
   $\mathbf{0.43}$ \\
+   ...     & 600  & 100 && $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
+   ...     & 1200  & 100 && $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
   \hline
  & & & $\Gamma = 0.1$ & & & & & & \\
-  \hline
-  $    10^{ 6 }$ & 1200  & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
-  $    10^{ 7 }$ & 1200  & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200  & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
-  $    10^{ 8 }$ & 1200  & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
-  $    10^{ 8 }$ & 1200  & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
-  $    10^{ 8 }$ & 600  & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
-  $    10^{ 6 }$ & 600  & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
-  $    10^{ 6 }$ & 600  & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
-  $    10^{ 7 }$ & 600  & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
-  $    10^{ 7 }$ & 600  & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
-  $    10^{ 8 }$ & 600  & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
-  $    10^{ 8 }$ & 600  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
-  $    10^{ 8 }$ & 300  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
+$    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
+  ...  & 600  & 50 & &$ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
+  ...  & 1200  & 100 && $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
+  $    10^{ 7 }$ & 1200  & 100& & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
+  ...  & 600  & 50 && $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
+  ...  & ...  & 25 & &$ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
+$10^{8}$  & 300  & 50 & & $ 6.0 \times 10^{ -5 }$ & 56 \\
+  ...  & 600  & 100 & &$ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
+  ...  &  ...  & 25 && $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
+  ...  &  ...  & 50 && $ 6.0 \times 10^{ -5 }$ & 56 \\
+... & 1200 & 100 && $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
+  ...  & ...  & 50 && $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
+  ...  &  ...  & 200 && $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
+  ...  &  ... & 400 && $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
   \hline
@@
 stagnation radius.  Thermally unstable solutions are shown in bold
-text.
- {\bf  BDM: (3) make sure all combinations of vw and mbh
-  are included. AG: Realized that the solution I ran earlier, with
-  cooling was actually a solution that would be thermally unstable
-  according to our thermal instability. I am worried that this
-  solution may not be representative due to the small break radius.}
+text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
 \end{tablenotes}

### 2015-03-01 ms.tex
table formatting - aleksey, please take note2
table formatting - aleksey, please take note3
mdot_sfr figure

--- 2015-02-28 ms.tex
@@
 \end{align}
+{\bf AG missing correction here for black hole velocity dispersion}
 where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$).  Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
@@
 \end{eqnarray}
+{\bf AG: missing a minus n here...}
 where for the numerical estimate we adopt values of $n \approx 1$ and $n \approx 0.5$ for core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies, respectively, so chosen to match the results of our numerical calculations (Fig.~\ref{fig:stag}).
@@
 Our spherically symmetric model neglects the effects of angular momentum on the gas evolution.
-However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$.
-Here $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar specific angular momentum near the stagnation radius, from which most of the accreted mass originates, where $V_{\phi}$ is the stellar azimuthal velocity.
-
-\citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data to measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
-  \begin{align}
-    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
+However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l_{r_{s}}^{2}/(GM_{\bullet})$, where $l_{r_{s}} = r_{s}\langle V_{\phi}\rangle |_{r_s}$ is the specific angular momentum of stars near the stagnation radius, from which most of the accreted mass originates, and $\langle v_{\phi}\rangle$ is their average azimuthal velocity.
+
+Using two-dimensional kinematic data, \citet{EmsellemCappellari+:2007a} measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
+  \begin{align}
+    \lambda_R=\frac{\langle R|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
   \end{align}
@@
 \ee
-where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, as satisfied for thermally-stable solutions of interest.
-
-\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales less that 10 per cent of the galaxy half-light radius and that $\lambda_R$ is a decreasing function of $R$, in which case from equation (\ref{eq:rcirc}) we conclude that $r_{\rm circ} \lesssim 0.01r_{s}$.
-This location lies well inside the inner sonic point of the flow, suggesting that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
-To first order we are thus justifying in neglecting its effects on our quantities such as the mass accretion rate.
+where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$ for the thermally-stable solutions of interest.
+
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R < 0.1$ on scales less that 10 per cent of the galaxy radius, in which case equation (\ref{eq:rcirc}) shows that $r_{\rm circ} \lesssim 0.01r_{s}$.
+Since this location lies well inside the inner sonic point of the flow, we conclude that angular momentum will only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow, justifying its neglect in calculating quantities such as the mass accretion rate.
 

### 2015-03-01 ms.tex

--- 2015-02-28 ms.tex
@@
   {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
- & ($M_{\odot}$) & (km s$^{-1}$) & (pc) & & & & & \\ 
+  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
 \hline
- & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
+ & & & Cusp Galaxies ($\Gamma^{(a)} = 0.8)$ & & & & & \\
   $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
@@
   \hline
- & & & $\Gamma = 0.1$ & & & & & & \\
+ & & & Core Galaxies ($\Gamma = 0.1$) & & & & & & \\
 $    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\

### 2015-03-01 ms.tex
more in 5

--- 2015-02-28 ms.tex
@@
   {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
- & ($M_{\odot}$) & (km s$^{-1}$) & (pc) & & & & & \\ 
+  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
 \hline
- & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
+ & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
   $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
@@
   \hline
- & & & $\Gamma = 0.1$ & & & & & & \\
+ & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
 $    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
@@
 Our numerical results, summarized in Table \ref{table:models} and Figure XXX, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
-Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
+Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
 
@@
  Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for each of our numerical solutions in Eddington units for different values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
-{\bf BDM: say something smart}
+Shown for comparison is our analytic estimate of $\dot{M}/\dot{M}_{\rm edd}$ from equation (\ref{eq:eddr_analytic}).
+For high wind velocities ($v_{w} \gg \sigma$) the stagnation lies well inside the black hole sphere of influence and our analytic estimate provides a good fit to the numerical results.
+However, for low wind velocities and/or high $M_{\bullet}$ (large $\sigma$), the numerical accretion rate considerably exceeds the analytic estimate as the stagnation radius diverges to large radii (Fig.~\ref{fig:stag}).
 %% AG: Describe conservation checks to additionally validate the results.
@@
 $\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
-stellar population which is formed impulsively (Fig.~\ref{fig:vwimp}).
+stellar population which is formed impulsively (Fig.~\ref{fig:vwImp}).  
 At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
@@
 mass galaxies, the stellar wind heating rate produced by stellar winds
-can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.
+can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.  
 Stellar winds thus contribute a potentially important source of both
 energy and mass for the CNM.
+An additional uncertainty in the stellar wind heating rate results from the uncertain thermalization efficiency of massive stellar winds.
+We assume this efficiency to be unity, and assumption that is at least partially offset by our conservative assumption of neglecting energy input from core collapse supernovae, which contribute a comparable energy injection rate to massive stellar winds.
 
@@
 Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
-Realistic variations (``burstiness") in the star formation history will result in lower heating rates, as seen in Fig.~X, for which we compare the stellar wind heating rates in the case of sinusoidal star formation pattern...{\bf BDM: say more}.
+
+Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
+Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
+For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
+, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
+We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
+{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
 

### 2015-03-01 ms.tex
zorak

@@
 Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
-Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in Fig.
-~\ref{fig:eta} (bottom panel).
+Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius (bottom panel).
 MSP heating is again found to be negligible for all black hole masses.
@@
 Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{vwSources.pdf}
+\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing to the total heating rate of the CNM, $\vwO$ ({\it black}), including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
+Each heating source varies with black hole mass $\Mbh$ calculated for average star formation histories from
+  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:} The
+  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
+  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.
+Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.
+{\bf BDM: remove the red - its tacky and will vary based on core/cusp.
+Draw a dashed line across at heating ratio of 1.
+change y axis labels!
+move stars label in top panel}}
 \end{figure}
@@
 }
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing   to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
-Each heating source varies with black hole mass $\Mbh$ due to the different
-  average star formation history of galaxies of a given halo mass (see
-  Appendix~\ref{app:windheat} for the detailed description). The total
-  heating rate is shown in black. {\it Bottom Panel:} The
-  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
-  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.
-Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.
-{\bf BDM: remove the red - its tacky and will vary based on core/cusp.
-Draw a dashed line across at heating ratio of 1.
-change y axis labels!
-move stars label in top panel}}
 \end{figure}
@@
 For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.
+
+This dependence is shown more directly in Figure \ref{fig:bh_growth}, where we plot the
+
+appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.
 
@@
 \subsection{Demographics of SMBHs}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
+\caption{\label{fig:bh_growth} {\it Top panel:} Various critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
+Black lines show the accretion rate calculated from equation (\ref{eq:eddr}), according to the total stellar wind heating due to the average star formation histories from \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).
+Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
+Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).
+Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).
+{\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
+  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
+\end{figure}
 
@@
 instability from equation~\eqref{eq:tgrow_min} in purple.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
-  of the Hubble time $\th$ for core ($\Gamma=0.1$, solid black) and
-  cusp galaxies ($\Gamma=0.8$, dash-dotted black). These are calculated from
-  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
-  average star formation history at each $\Mbh$. We also plot a lower
-  bound on growth time for a themally stable flow (yellow) from
-  equation~\eqref{eq:tgrow_min}.}
-\end{figure}
 

### 2015-03-01 ms.tex
zorak2

@@
 
-\subsection{Combined Heating Rate} 
-\label{sec:combined}
-
-The total gas heating rate, 
-\be
-\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
-\label{eq:vtot}
-\ee
-includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
-The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
-The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
-
-\subsubsection{Single Starburst}
-
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
-The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
-The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
-SN Ia heating depends also on a convolution of the DTD (eq.
-[\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
-We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
-Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
-Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.
-
-For low mass black holes, stellar heating is the most important on timescales of less than a few tens of millions of years.
-Compton heating comes to dominate at later times due to the higher accretion rates that accompany the overall decrease in the heating rate coupled with the persistently high mass loss rates of a relatively young stellar population.
-Compton heating dominates at all epochs for higher mass black holes, with stellar winds and Ia SN competing for the most significant non-AGN heating source.
-As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by dashed lines in Fig.~\ref{fig:vwSourcesImp}.
-The thermal stability is calculated neglecting Compton heating because the latter may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
-Thermally unstable flow is seen to be the norm in the single starburst case, except at very early times, $\tau_{\star} \lesssim 1-3 \times 10^7$ yr.
-
-\subsubsection{Continuous Star Formation History}
-
-A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
-Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
-We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ as a function of $M_{\bullet}$ (Fig.~\ref{fig:eta}; top panel).
-Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
-
-Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
-Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius (bottom panel).
-MSP heating is again found to be negligible for all black hole masses.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
-Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
-Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
-Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
-
-Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
-Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
-For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
-, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
-We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
-{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
-
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Combined Heating Rate} 
+\label{sec:combined}
+
+The total gas heating rate, 
+\be
+\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
+\label{eq:vtot}
+\ee
+includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
+The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
+The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
+
+\subsubsection{Single Starburst}
+
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
+The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
+The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
+SN Ia heating depends also on a convolution of the DTD (eq.
+[\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
+We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
+Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
+Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.
+
+For low mass black holes, stellar heating is the most important on timescales of less than a few tens of millions of years.
+Compton heating comes to dominate at later times due to the higher accretion rates that accompany the overall decrease in the heating rate coupled with the persistently high mass loss rates of a relatively young stellar population.
+Compton heating dominates at all epochs for higher mass black holes, with stellar winds and Ia SN competing for the most significant non-AGN heating source.
+As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by dashed lines in Fig.~\ref{fig:vwSourcesImp}.
+The thermal stability is calculated neglecting Compton heating because the latter may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
+Thermally unstable flow is seen to be the norm in the single starburst case, except at very early times, $\tau_{\star} \lesssim 1-3 \times 10^7$ yr.
+
+\subsubsection{Continuous Star Formation History}
+
+A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
+smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
+Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
+We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
+Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ as a function of $M_{\bullet}$ (Fig.~\ref{fig:eta}; top panel).
+Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
+
+Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
+Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius (bottom panel).
+MSP heating is again found to be negligible for all black hole masses.
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
+Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
+Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
+
+Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
+Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
+For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
+, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
+We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
+{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
 
@@
 
+\subsection{Black Hole Accretion Rates}
+
+Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
+For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+Figure \ref{fig:bh_growth} displays this dependence more directly, with solid lines showing the accretion rate as calculated from equation (\ref{eq:eddr}) using the wind heating rate calculated for each black hole mass (Fig.~\ref{fig:mdot_mass}).
+This average accretion rate increases from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
+These accretion rates fall below the maximum thermally stable accretion rate $\dot{M}_{\rm TI}$ (yellow lines), except for the highest black hole masses $\sim 10^{9}M_{\odot}$, for which the average older stellar population supplies insufficient stellar wind heating while Ia supernovae are too rare near the stagnation radius to provide effective heating.
+
 \subsection{Nuclear X-ray Luminosities}
@@
 The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).
-Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
-For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-
-This dependence is shown more directly in Figure \ref{fig:bh_growth}, where we plot the
-
 appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.
@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Various critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
-Black lines show the accretion rate calculated from equation (\ref{eq:eddr}), according to the total stellar wind heating due to the average star formation histories from \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).
+\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
+Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using the stellar wind calculated for the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
 Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
@@
 \label{sec:conclusions}
+
+Apologies: we assume that average star formation histories correspond to those experienced in the nuclear region.
+
   We have calculated steady-state models for circumnuclear medium of a

### 2015-03-01 ms.tex
zorak3

@@
 For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-Figure \ref{fig:bh_growth} displays this dependence more directly, with solid lines showing the accretion rate as calculated from equation (\ref{eq:eddr}) using the wind heating rate calculated for each black hole mass (Fig.~\ref{fig:mdot_mass}).
+
+Figure \ref{fig:bh_growth} (top panel) shows with solid lines the accretion rate as a function of black hole mass for the average star formation heating, calculated from equation (\ref{eq:eddr_analytic}) using our results for the total wind heating (Fig.~\ref{fig:mdot_mass}).
 This average accretion rate increases from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
-These accretion rates fall below the maximum thermally stable accretion rate $\dot{M}_{\rm TI}$ (yellow lines), except for the highest black hole masses $\sim 10^{9}M_{\odot}$, for which the average older stellar population supplies insufficient stellar wind heating while Ia supernovae are too rare near the stagnation radius to provide effective heating.
+These fall below the maximum thermally stable accretion rate $\dot{M}_{\rm TI}$ (yellow lines), except at the highest black hole masses $\sim 10^{9}M_{\odot}$, for which the older stellar population supplies insufficient stellar wind heating and SN Ia are too rare near the stagnation radius.
+In fact, for these highest mass black holes, the maximum accretion rate set by SN Ia blow-out (green lines; eq.~[\ref{eq:eddr_Ia}]) could cap the accretion rate below the thermally-unstable value, provided that the Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia} \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just preceeding eq.~[\ref{eq:eddr_Ia}]).
+For lower mass black holes, the maximum Ia accretion rate is significantly higher and cannot prevent thermally unstable flows, i.e.
+$\dot{M}_{\rm Ia} > \dot{M}_{\rm TI}$.
+Finally, also shown for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert04} and the upper limit onto NGC3115 set by \citealt{Shcherbakov+14}.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
+\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
+Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using the stellar wind calculated for the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
+Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
+Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).
+Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).
+{\bf BDM: add SgrA* numbers derived by quataert, NGC3115 from Roman} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
+  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
+\end{figure}
 
@@
 
+Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
+
 GALEX observations have shown that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
@@
 \subsection{Demographics of SMBHs}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
-Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using the stellar wind calculated for the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
-Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
-Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).
-Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).
-{\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
-  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
-\end{figure}
 
@@
 \subsection{TDE Jets}
+
+Our results on SMBH accretion rates.
 

### 2015-03-01 ms.tex
zorak4

@@
 
-\section{Discussion}
+\section{Implications and Discussion}
 \label{sec:discussion}
@@
 In fact, for these highest mass black holes, the maximum accretion rate set by SN Ia blow-out (green lines; eq.~[\ref{eq:eddr_Ia}]) could cap the accretion rate below the thermally-unstable value, provided that the Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia} \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just preceeding eq.~[\ref{eq:eddr_Ia}]).
+This is only possible if the Ia heating efficiency is reasonably high $\epsilon_{\rm Ia} > 0.1$ than normally assumed (\citealt{Sharma+14}).
 For lower mass black holes, the maximum Ia accretion rate is significantly higher and cannot prevent thermally unstable flows, i.e.
 $\dot{M}_{\rm Ia} > \dot{M}_{\rm TI}$.
-Finally, also shown for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert04} and the upper limit onto NGC3115 set by \citealt{Shcherbakov+14}.
+
+Finally, also shown for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and the upper limit onto NGC3115 set by \citealt{ShcherbakovWong+:2014a}.
 
@@
 The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).
-appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.
-
-Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass for core (blue) and cusp (green) galaxies, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
-The left panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}) and SgrA* (e.g.,
-\citealt{Quataert+99}).  The luminosity shown in the right
-panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
-Plotted next to the theoretical curves are the X-ray measurements (stars) and upper limits
-(triangles) from \citet{Miller+15} (cf.~\citealt{Gallo+10}), along with the resulting best power-law
-fit (red line) and the X-ray detection threshold (gray line).
-Purple, orange, and {\bf brown} lines show the maximum accretion rates for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
-(eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.
-
-To first order our predicted values of $\langle L_{X}/L_{\rm edd}\rangle$ for the average galactic star formation histories overlap with the data reasonably well.
-Our prediction that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
-However, better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
-The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude can also be understood within a steady-accretion scenario due to the strong sensitivity of the accretion rate on the efficacy of gas heating, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the equally sensitive dependence of the heating rate on stochastic intermittency in the star formation history (Fig.~NICK).
-
-In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
-The cyclic model also predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages.
-This appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
-This observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
-
-However, the observed values of 
-$\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of
-observed galaxies are below the maximum ones for thermally stable
-accretion if $\epsilon_X \lesssim 10^{-4}$.  This suggests that most
-nearby galaxies are consistent with accreting in a thermally stable
-steady state, even if our estimate of their predicted heating does not
-match the observed trend with $M_{\bullet}$ perfectly.  On the other
-hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent
-with the accretion rate set by Ia blow-out.  Also note that in the
-case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X =
-\dot{M}/\dot{M}_{\rm edd}$), the predicted branches of $\langle
-L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$,
-calling into question attempts to extrapolate the $\langle L_{X}
-\rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to
-constrain the occupation fraction of black holes in the lowest mass
-galaxies (\citealt{Miller+15}).
-
-Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
-
-Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
-
-\subsection{Steady Accretion versus Cyclic Outbursts}
-
-Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
-
-GALEX observations have shown that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
-
-\subsection{Demographics of SMBHs}
+Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
+We have averaged the accretion rate used in calculating $\langle L_X \rangle$ between the values for galaxies with core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles, by fiting the average value of the inner density slope $\Gamma$ as a function of black hole mass from the \citet{LauerFaber+:2007a} galaxy sample.
+
+The left panel of Figure \ref{fig:miller} is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}) and SgrA* (e.g., \citealt{Quataert+99}).
+The luminosity shown in the right panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
+Plotted next to the theoretical curves are the X-ray measurements (green stars) and upper limits (gray triangles) compiled by \citet{Miller+15} (cf.~\citealt{Gallo+10}).
+A green line shows the resulting best power-law fit to the average X-ray luminosity, which is given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ from \citet{Miller+15}, with $\alpha = XXX$  (see also \citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
+Yellow, teal, and red lines show the maximum accretion rates, respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]).
 
@@
 
+To first order our predicted average values of $\langle L_{X}/L_{\rm edd}\rangle$ increases only weakly with black hole mass.
+
+for the average galactic star formation histories overlap with the data reasonably well.
+Our prediction that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
+However, better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
+The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude can also be understood within a steady-accretion scenario due to the strong sensitivity of the accretion rate on the efficacy of gas heating, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the equally sensitive dependence of the heating rate on stochastic intermittency in the star formation history (Fig.~NICK).
+
+In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
+The cyclic model also predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages.
+This appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
+This observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
+
+However, the observed values of 
+$\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of
+observed galaxies are below the maximum ones for thermally stable
+accretion if $\epsilon_X \lesssim 10^{-4}$.  This suggests that most
+nearby galaxies are consistent with accreting in a thermally stable
+steady state, even if our estimate of their predicted heating does not
+match the observed trend with $M_{\bullet}$ perfectly.  On the other
+hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent
+with the accretion rate set by Ia blow-out.  Also note that in the
+case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X =
+\dot{M}/\dot{M}_{\rm edd}$), the predicted branches of $\langle
+L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$,
+calling into question attempts to extrapolate the $\langle L_{X}
+\rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to
+constrain the occupation fraction of black holes in the lowest mass
+galaxies (\citealt{Miller+15}).
+
+Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
+
+Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
+
+\subsection{Steady Accretion versus Cyclic Outbursts}
+
+Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
+
+GALEX observations have shown that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+
+\subsection{Demographics of SMBHs}
+
 This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08})
@@
 \subsection{Nuclear Star Clusters}
-Do nuclear star clusters in other galaxies look like scaled up/down
-versions of the one in our own galaxy? If so this would imply a radial
-gradient in the average of the stellar population which would imply a
-heating which would be dependent on radius.
-
-\subsection{SFR-AGN connection}
-In fact it seems like the star formation rate may trace AGN
-episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
-
-\subsection{Type II Supernovae}
-Type II supernovae should provide some heating as well for younger
-stellar populations...In fact at least on large scales they may be the
-dominant source of heating on timescales of 10-40 Myr.
 
@@
 
-Apologies: we assume that average star formation histories correspond to those experienced in the nuclear region.
+Apologies: 
+\begin{itemize}
+\item{we assume that average star formation histories correspond to those experienced in the nuclear region.  }
+
+\item{
+Do nuclear star clusters in other galaxies look like scaled up/down versions of the one in our own galaxy?
+If so this would imply a radial gradient in the average of the stellar population which would imply a heating which would be dependent on radius.
+}
+
+\end{itemize}
 

### 2015-03-01 ms.tex
brak

@@
 
-To first order our predicted average values of $\langle L_{X}/L_{\rm edd}\rangle$ increases only weakly with black hole mass.
-
-for the average galactic star formation histories overlap with the data reasonably well.
-Our prediction that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass appears to be in disagreement with observed decrease of $\langle L_{X}/L_{\rm edd}\rangle$ with $M_{\bullet}$ for both core and cusp galaxies.
-However, better agreement is obtained by taking into account the fact that core(cusp) galaxie are more commonly associated with larger(smaller) black hole masses, such that when both samples are combined one predicts a flatter dependence of $\langle L_X/L_{\rm edd}\rangle$ of $M_{\bullet}$.
-The large scatter observed in $L_{X}/L_{\rm edd}$ of typically 2-4 orders of magnitude can also be understood within a steady-accretion scenario due to the strong sensitivity of the accretion rate on the efficacy of gas heating, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) and the equally sensitive dependence of the heating rate on stochastic intermittency in the star formation history (Fig.~NICK).
-
-In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
+If heating in the nuclei of elliptical galaxies is characterized by that of the average star formation history of galaxies with similar mass, then to first order we predict that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.
+This prediction is in tension with the observed trend that average Eddington ratio decreases (also weakly) with $M_{\bullet}$.
+However, the physics setting $L_X$ based on the large-scale accretion rate is notoriously uncertain and there could exist black hole mass-dependent efficiency factors we are not taking into account.
+For instance, if disk disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce nuclear X-rays (e.g.~\citealt{Blandford&Begelman99}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also affect the X-ray luminosity, potentially in a way that would depend systematically on the black hole mass.
+
+It is also important to ask whether the steady-state accretion picture can explain the large large scatter (typically 2-3 orders of magnitude) observed in $L_{X}/L_{\rm edd}$.
+Large scatter can in fact result from two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ results in scatter due to the scatter in the Nuker stellar density profile $\Gamma$; (2) the strong sensitivity of the accretion rate on the gas heating rate, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) combined with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
+The combination of (1) and (2) could well explain much of the scatter observed.
+
+However, it is also possible that many of the galactic nuclei from the \citet{Miller+14} sample are in a thermally stable state.
+The efficiency show in the right panel of Figure \ref{fig:miller} in some ways represents the maximum efficiency, since it does not take into account outflows from the accretion flow that would suppress the accreiton rate reaching large radii.
+Nevertheless, many of the observed galaxies at low black hole masses of $M_{\bullet} \lesssim 10^{7}M_{\odot}$ lie well below the predicted average value for stable accretion (black line) and even approaching or above the maximally stable accretion rate $\dot{M}_{\rm TI}$ (yellow line) .
+This suggests that these galaxies experience lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all ($\S\ref{sec:stable}$).
+
+Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
+
+\subsection{Steady Accretion versus Cyclic Outbursts}
+
+Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
+In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter in Fig \ref{fig:Miller} can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
 The cyclic model also predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages.
@@
 
-However, the observed values of 
-$\langle L_{X}/L_{\rm edd}\rangle$ do imply the accretion rates of
-observed galaxies are below the maximum ones for thermally stable
-accretion if $\epsilon_X \lesssim 10^{-4}$.  This suggests that most
-nearby galaxies are consistent with accreting in a thermally stable
-steady state, even if our estimate of their predicted heating does not
-match the observed trend with $M_{\bullet}$ perfectly.  On the other
-hand if $\epsilon_{X} \sim 10^{-5}$ then the trend would be consistent
-with the accretion rate set by Ia blow-out.  Also note that in the
-case of $\dot{M}-$dependent radiative efficiency ($\epsilon_X =
-\dot{M}/\dot{M}_{\rm edd}$), the predicted branches of $\langle
-L_{X}/L_{\rm edd}\rangle$ decreases with decreasing $M_{\bullet}$,
-calling into question attempts to extrapolate the $\langle L_{X}
-\rangle - M_{\bullet}$ relationship to low $M_{\bullet}$ in order to
-constrain the occupation fraction of black holes in the lowest mass
-galaxies (\citealt{Miller+15}).
-
-Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
-
-Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
-
-\subsection{Steady Accretion versus Cyclic Outbursts}
-
-Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
+In general we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable.
+This may be consistent with past studies which have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
 

### 2015-03-01 ms.tex
brak2

@@
 
-This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08})
-
-Our analytic expression for the accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be translated into the growth time of the SMBH $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$,
-\begin{eqnarray}
-  t_{\rm growth}/t_{\rm h} \approx 
-  \begin{cases}
-    250 M_{\bullet,8}^{-0.76}
-    v_{500}^{3.8}   \eta_{0.02}  & \text{core} \\
-    140 \Mbheight^{-0.48}
-    v_{500}^{2.4}   \eta_{0.02}  & \text{cusp}, 
-  \end{cases}
-  \label{eq:tgrow_analytic}
-\end{eqnarray}
-which we have normalized in terms of the Hubble time.
-
-There is a maximum accretion rate for a thermally stable flow
-(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
-time from thermally stable accretion
-
-\begin{align}
-  t_{\rm growth}/t_{\rm h} \gsim
-  \rm{max}\begin{cases}
-    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
-    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
-    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
-  \end{cases}
-  \label{eq:tgrow_min}
-\end{align}
-
-In Figure~\ref{fig:bh_growth} we plot the growth times for core and
-cusp galaxies, with parameters chosen for the average star formation
-history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
-and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
-respectively.  We also plot the maximum growth time for thermal
+The bottom panel of Figure~\ref{fig:bh_growth} shows the growth times for core and cusp galaxies, with parameters chosen for the average star formation history at each $\Mbh$ (see Figure~\ref{fig:vwSources} and~\ref{fig:eta}).
+Core and cusp galaxies are shown in green and blue respectively.
+We also plot the maximum growth time for thermal
 instability from equation~\eqref{eq:tgrow_min} in purple.
@@
 
-Our results on SMBH accretion rates.
-
-Plot showing final lorentz factor after the reverse shock crossing as a function of BH mass, using average star formation history.  place J1644+57 on the plot.
+Our results also have implications for jetted TDEs.
+For black hole masses characterizing those responsible for {\it Swift} J1644+57, we predict accretion rates of $\dot{M} \sim$ corresponding to gas densities of $n \sim 0.1$ cm$^{-3}$ on radial scales.
+This is similar to the value of $n \sim 1$ cm$^{-3}$ inferred for J1644+57 on radial scales $\sim 0.3$ pc (\citealt{Metzger+12}, \citealt{Berger+12}).
 

### 2015-03-01 ms.tex
brak3

@@
 This average accretion rate increases from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
-These fall below the maximum thermally stable accretion rate $\dot{M}_{\rm TI}$ (yellow lines), except at the highest black hole masses $\sim 10^{9}M_{\odot}$, for which the older stellar population supplies insufficient stellar wind heating and SN Ia are too rare near the stagnation radius.
-In fact, for these highest mass black holes, the maximum accretion rate set by SN Ia blow-out (green lines; eq.~[\ref{eq:eddr_Ia}]) could cap the accretion rate below the thermally-unstable value, provided that the Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia} \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just preceeding eq.~[\ref{eq:eddr_Ia}]).
-This is only possible if the Ia heating efficiency is reasonably high $\epsilon_{\rm Ia} > 0.1$ than normally assumed (\citealt{Sharma+14}).
-For lower mass black holes, the maximum Ia accretion rate is significantly higher and cannot prevent thermally unstable flows, i.e.
-$\dot{M}_{\rm Ia} > \dot{M}_{\rm TI}$.
-
-Finally, also shown for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and the upper limit onto NGC3115 set by \citealt{ShcherbakovWong+:2014a}.
+These fall below the maximum thermally stable accretion rate, $\dot{M}_{\rm TI}$ (plotted as yellow lines), except at the highest black hole masses $\sim 10^{9}M_{\odot}$.
+For these highest mass black holes, the maximum accretion rate as set by gas blow-out from SN Ia (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the accretion rate below the thermally-unstable value, provided that the SN Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia} \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just preceeding eq.~[\ref{eq:eddr_Ia}]).
+This is only possible if the Ia heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally assumed (\citealt{Sharma+14}).
+For lower mass black holes, the maximum accretion rate set by SN Ia is significantly higher and cannot prevent the development of thermally unstable flows, i.e.
+$\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
+
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and the upper limit on $\dot{M}$ for the black hole in NGC3115 set by \citealt{ShcherbakovWong+:2014a}.
+These points are consistent with our thermally-stable accretion rates within the expected dispersion (see next section), although NGC3115 is in fact a low luminosity AGN.
 
@@
 \caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
-Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using the stellar wind calculated for the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
+Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using our estimate of the gas heating rate provided at $z = 0$ by the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
 Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
-Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).
+Red lines show the accretion rate so obtained if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).
 Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).
@@
 
-The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).
-Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).
-We have averaged the accretion rate used in calculating $\langle L_X \rangle$ between the values for galaxies with core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles, by fiting the average value of the inner density slope $\Gamma$ as a function of black hole mass from the \citet{LauerFaber+:2007a} galaxy sample.
-
-The left panel of Figure \ref{fig:miller} is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}) and SgrA* (e.g., \citealt{Quataert+99}).
-The luminosity shown in the right panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).
-Plotted next to the theoretical curves are the X-ray measurements (green stars) and upper limits (gray triangles) compiled by \citet{Miller+15} (cf.~\citealt{Gallo+10}).
-A green line shows the resulting best power-law fit to the average X-ray luminosity, which is given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ from \citet{Miller+15}, with $\alpha = XXX$  (see also \citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
+The unresolved core X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).
+Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric correction at X-ray energies appropriate for low luminosity AGN (\citealt{Ho08}).
+We have averaged the accretion rate used in calculating $\langle L_X \rangle$ between the values for galaxies with core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles using the average value of the inner density slope $\Gamma$ as a function of black hole mass as fit from the \citet{LauerFaber+:2007a} galaxy sample, an exercise that results in the relationship $\Gamma = ...$.
+{\bf BDM: fill in}
+
+The left panel of Figure \ref{fig:miller} is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$ typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}), while the right panel luminosities are calculated instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}).
+Shown for comparison are the X-ray measurements (green stars) and upper limits (gray triangles) of early-type galaxies compiled by \citet{Miller+15} (cf.~\citealt{Gallo+10}).
+A green line shows the best power-law fit to the X-ray luminosity from \citet{Miller+15}, given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = XXX$  (see also \citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
 Yellow, teal, and red lines show the maximum accretion rates, respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]).
@@
 
-If heating in the nuclei of elliptical galaxies is characterized by that of the average star formation history of galaxies with similar mass, then to first order we predict that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.
-This prediction is in tension with the observed trend that average Eddington ratio decreases (also weakly) with $M_{\bullet}$.
-However, the physics setting $L_X$ based on the large-scale accretion rate is notoriously uncertain and there could exist black hole mass-dependent efficiency factors we are not taking into account.
-For instance, if disk disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce nuclear X-rays (e.g.~\citealt{Blandford&Begelman99}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also affect the X-ray luminosity, potentially in a way that would depend systematically on the black hole mass.
-
-It is also important to ask whether the steady-state accretion picture can explain the large large scatter (typically 2-3 orders of magnitude) observed in $L_{X}/L_{\rm edd}$.
-Large scatter can in fact result from two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ results in scatter due to the scatter in the Nuker stellar density profile $\Gamma$; (2) the strong sensitivity of the accretion rate on the gas heating rate, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) combined with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
+If heating in the nuclei of elliptical galaxies is similar to that produced by the average star formation history of galaxies with similar mass, then to first order we predict that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.
+This result is in tension with the observed down-sizing trend that the average Eddington ratio is observed to decrease (albeit also weakly) with $M_{\bullet}$.
+However, in making such comparisons it is important to keep in mind the enormous uncertainty in calculating the luminosity of the accretion flow close to the black hole in a single waveband based on the accretion rate on larger scales.
+Black hole mass-dependent efficiency factors could enter that we are not taking into account.
+For instance, if disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce the observed X-rays (e.g.~\citealt{Blandford&Begelman99}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also affect the X-ray luminosity, potentially in a way that could depend systematically on the black hole mass.
+
+Perhaps a more readily addressable test is whether a steady-state accretion picture can explain the large large scatter of typically 2-3 orders of magnitude observed in $L_{X}/L_{\rm edd}$.
+Scatter can result from at least two effects (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) will result in a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
 The combination of (1) and (2) could well explain much of the scatter observed.
 
-However, it is also possible that many of the galactic nuclei from the \citet{Miller+14} sample are in a thermally stable state.
+However, it is also possible that many of the galactic nuclei from the \citet{Miller+15} sample are in a thermally stable state.
 The efficiency show in the right panel of Figure \ref{fig:miller} in some ways represents the maximum efficiency, since it does not take into account outflows from the accretion flow that would suppress the accreiton rate reaching large radii.

### 2015-03-01 ms.tex
brak4

@@
 Black hole mass-dependent efficiency factors could enter that we are not taking into account.
-For instance, if disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce the observed X-rays (e.g.~\citealt{Blandford&Begelman99}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also affect the X-ray luminosity, potentially in a way that could depend systematically on the black hole mass.
-
-Perhaps a more readily addressable test is whether a steady-state accretion picture can explain the large large scatter of typically 2-3 orders of magnitude observed in $L_{X}/L_{\rm edd}$.
-Scatter can result from at least two effects (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) will result in a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
-The combination of (1) and (2) could well explain much of the scatter observed.
-
-However, it is also possible that many of the galactic nuclei from the \citet{Miller+15} sample are in a thermally stable state.
-The efficiency show in the right panel of Figure \ref{fig:miller} in some ways represents the maximum efficiency, since it does not take into account outflows from the accretion flow that would suppress the accreiton rate reaching large radii.
-Nevertheless, many of the observed galaxies at low black hole masses of $M_{\bullet} \lesssim 10^{7}M_{\odot}$ lie well below the predicted average value for stable accretion (black line) and even approaching or above the maximally stable accretion rate $\dot{M}_{\rm TI}$ (yellow line) .
-This suggests that these galaxies experience lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all ($\S\ref{sec:stable}$).
-
-Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady
+For instance, if disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce the observed X-rays (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also influence the X-ray luminosity, in a way that could depend systematically on $M_{\bullet}$.
+
+A more readily addressable test is whether a steady-state accretion picture is capable of explaining the large scatter of typically 2-3 orders of magnitude in the observed distribution of $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.
+Scatter is expected to result from at least two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
+The combination of (1) and (2) is capable of explaining much of the observed sample.
+
+It is also possible that many of the nuclei from the \citet{Miller+15} sample are not accreting in a steady fashion.
+The ADAF efficiency assumed in the right panel of Figure \ref{fig:miller} in some ways represents the maximum value, since it does not take into account outflows from the accretion flow that would suppress the accreiton rate reaching large radii.
+Nevertheless, many lower black hole masses of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie well above the predicted average value for stable accretion (black line), suggesting that these galaxies either experience lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all ($\S\ref{sec:cycle}$).
+Indeed, for the lowest mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ exceeds the one corresponding to the maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
+Many of the upper limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a separate ``thermally stable".
+This possible dichotomy calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
 
 \subsection{Steady Accretion versus Cyclic Outbursts}
+\label{sec:cycle}
 

### 2015-03-01 ms.tex
working on discussion despite myself

@@
 
-Figure \ref{fig:bh_growth} shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$), as will described more below.
-In the case of an old stellar population which produces insufficient heating to support steady accretion, this large scatter in Fig \ref{fig:Miller} can in principle also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
-The cyclic model also predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages.
-This appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
-This observation can also be understood in the stable accretion picture by the fact that young stars provide sufficient stellar wind heating to produce a thermally stable accretion state.
-
-In general we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable.
-This may be consistent with past studies which have found that core galaxies show a wide range of nuclear radio and X-ray luminosities, while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}).
-
-GALEX observations have shown that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
-
-\subsection{Demographics of SMBHs}
+Figure \ref{fig:bh_growth} (top panel) shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities from developing in a steady-state accretion flow ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).
+Thus, if the stellar population is sufficiently old (or the star formation sufficiently intermittent) then nuclear gas could undergo cyclic oscillations of thermal instability and high accretion rates, followed by quiescent periods once gas has been consumed and/or AGN feedback becomes effective.
+Such cycles are proposed to occur on large scales and long timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea supported, e.g.
+, by GALEX observations showing that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+If such cyclic behavior also occurs on small, parsec scales (e.g.) then the large scatter in the accretion rates and hence X-ray luminosities shown in Fig \ref{fig:Miller} could also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
+In support of this possibility, we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable.
+Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable picture.
+
+The cyclic model predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages, a result which appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
+An alternative explanation for this observation within a thermally stable accretion picture is that young stars provide higher stellar wind heating, reducing the mass accretion rate and hence nuclear X-ray luminosity.
+
+\subsection{Local Growth of SMBHs }
 

### 2015-03-01 ms.tex
working on discussion despite myself2

@@
 Scatter is expected to result from at least two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
-The combination of (1) and (2) is capable of explaining much of the observed sample.
+The combination of (1) and (2) is capable of explaining much of the observed sample, especially considering that scatter in $L_{\rm X}$ due to variations in $\dot{M}$ is exacerbated by the expectation that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
 

### 2015-03-01 ms.tex
TDE section

@@
 In support of this possibility, we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable.
-Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable picture.
+Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
 
 The cyclic model predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages, a result which appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
-An alternative explanation for this observation within a thermally stable accretion picture is that young stars provide higher stellar wind heating, reducing the mass accretion rate and hence nuclear X-ray luminosity.
-
-\subsection{Local Growth of SMBHs }
-
-The bottom panel of Figure~\ref{fig:bh_growth} shows the growth times for core and cusp galaxies, with parameters chosen for the average star formation history at each $\Mbh$ (see Figure~\ref{fig:vwSources} and~\ref{fig:eta}).
-Core and cusp galaxies are shown in green and blue respectively.
-We also plot the maximum growth time for thermal
-instability from equation~\eqref{eq:tgrow_min} in purple.
-
-\begin{itemize}
-\item{Fact that some low mass BHs appear to have nearly Eddington accretion rates, suggest an external origin - since the maximum Ia rate appears to be below this}
-\item{Growth of low mass BHS, e.g. \citealt{Kauffmann&Heckman09}}
-\end{itemize}
+An alternative explanation for this observation within a thermally stable, steady-state accretion picture is that young stars provide higher stellar wind heating, reducing the mass accretion rate and hence nuclear X-ray luminosity.
+
+\subsection{Local Growth Time of SMBHs }
+
+Low-mass SMBHs in the local universe ($M_{\bullet} \lesssim 3\times 10^{7}M_{\odot}$) are observed to be growing on a timescale comparable to the age of the universe, while the most massive SMBHs with $M_{\bullet} \gtrsim 10^{9}M_{\odot}$ possess local growth times which are more than 2 orders of magnitude longer (\citealt{Heckman+04}; \citealt{Kauffmann&Heckman09}).
+
+The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate shown in the top panel.
+For black holes accreting steadily given the stellar wind heating associated with the average star formation history of their galaxies, we see that $t_{\rm grow}$ exceeds the Hubble time by 1-3 orders of magnitude across all black hole masses.
+Steady accretion therefore cannot explain the  growth of low mass black holes, a fact which is not surprising given that approximately half of this growth occurs in AGN radiating within 10 per cent of their Eddington rate (\citealt{Heckman+04}).
+Such high accretion rates likely instead require an source of gas external to the nuclear region, triggered either by galaxy mergers associated with the hierachical growth of structure or thermal instabilities on larger, galactic scales (e.g.~\citealt{Ciotti+10}).
+That the growth time associated with thermally-unstable accretion (yellow line) exceeds the Hubble time across all SMBH masses highlights the fact that signifcant black hole growth in the local universe cannot result from thermally-stable steady accretion.
+
+Gas blow-out by SN Ia cannot prevent the growth of low-mass black holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by Ia heating (green lines), although Ia heating could play in principle a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the efficiency of Ia heating.
 
@@
 
-However, \citet{McCourt+12} argue that even if cooling is exactly
-balanced by heating everywhere, there is still a local thermal
-instability that operates to turn hot gas into cold clouds.  However,
-this local instability only causes a significant local drop-out of
-mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the
-stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
-(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
-  crit}$ is also the condition for local instability, although the
-prefactor may be slightly different.
-
 \subsection{TDE Jets}
 
-Our results also have implications for jetted TDEs.
-For black hole masses characterizing those responsible for {\it Swift} J1644+57, we predict accretion rates of $\dot{M} \sim$ corresponding to gas densities of $n \sim 0.1$ cm$^{-3}$ on radial scales.
-This is similar to the value of $n \sim 1$ cm$^{-3}$ inferred for J1644+57 on radial scales $\sim 0.3$ pc (\citealt{Metzger+12}, \citealt{Berger+12}).
+Our results also have implications for the environments encountered by relativistic jets from TDEs.
+For low-mass SMBHs  $M_{\bullet} \lesssim 10^{7}M_{\odot}$, characterizing those responsible for {\it Swift} J1644+57 (\citealt{Bloom:2011aa}), we predict gas densities of a $n \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating rates within the physically expected range $v_{\rm w} \sim 500-1000$ km s$^{-1}$ (Fig.~\ref{fig:profiles}).
+These values are within the range estimated by modeling the radioa afterglow of {\it Swift} J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).
+In fact, the flattening of the density profile inferred by \citet{Berger+12} on radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that seen in our calculations of the gas density profile for core galaxies (Fig.~\ref{fig:profiles}, solid line).
+The CNM density of the host of {\it Swift} J1644+57 was a factor of 30 times lower than that inferred by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf BDM: whats going on?}  The implications of our models for CNM profiles for the diversity of radio emission from TDE jets will be explored further in future work.
 
@@
 \end{itemize}
+
+However, \citet{McCourt+12} argue that even if cooling is exactly
+balanced by heating everywhere, there is still a local thermal
+instability that operates to turn hot gas into cold clouds.  However,
+this local instability only causes a significant local drop-out of
+mass from the hot medium (to low-T clouds), if the cooling timescale,
+\begin{align}
+\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+\end{align} 
+is locally shorter than the approximately 10 times the free-fall
+timescale $t_{\rm ff}$, where the last equality is evaluated at the
+stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
+(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
+  crit}$ is also the condition for local instability, although the
+prefactor may be slightly different.
 
@@
 
-\section{Death Row}
-
-\subsection{X-ray Diagnostics of SMBH Occupation}
-\label{sec:occ}
-The free-free emission from steady state gas flows in low mass
-galactic nuclei may serve as useful diagnostics of the presence or
-absence of a SMBH.  We focus primarily on low-mass galaxies in this
-subsection, both because this is the portion of parameter space in
-which gas inflow will generally proceed in a steady-state fashion, and
-because of recent observations suggesting that a nontrivial fraction
-of these galaxies may lack nuclear SMBHs.  If this absence is
-confirmed, it could have implications for galaxy evolution, SMBH
-recoil distributions, and SMBH seed formation models.
-
-We can approximate the gas temperature as
-
-\begin{equation}
-% T \approx \frac{\mu m_{\rm p} (\gamma-1)}{2\gamma k_{\rm B}}
-% \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r \right).
- \kb T \approx 2.1\times 10^{-25} \left(\tilde{v}_{\rm w}^2 + GM_\bullet/r
- \right) {\rm [cgs]}.
-\end{equation}
-
-In the absence of a central SMBH, we can expect to see an exponential
-cutoff in the free-free X-ray spectrum at energies above
-
-\begin{equation}
-E_{\rm cut} = 0.32~{\rm keV} v_{500}^2,
-\end{equation}
-
-assuming $\gamma = 5/3$.  This cutoff will therefore be located in the
-portion of the soft X-ray covered by {\it Chandra}'s ACIS
-spectrometer.  By writing the free-free emissivity as
-
-\begin{equation} 
-\varepsilon_{\nu}^{\rm ff} = 6.8\times10^{-38}
-\frac{\rm erg}{\rm s~cm^3~Hz} Z^2n_{\rm e}n_{\rm
-i}T^{-1/2}\bar{g}_{\rm ff}\exp\left(\frac{-h\nu}{k_{\rm B}T}\right),
-\end{equation}
-
-where $Z$ is the atomic number of the ions, $n_{\rm e}$ and $n_{\rm
-  i}$ are respectively the electron and ion number density, and
-$\bar{g}_{\rm ff}$ is the Gaunt factor.  In the following we set
-$n_{\rm e}=Y_{\rm e}n_{\rm i}$, and approximate
-\begin{equation}
-n_{\rm i} \approx \frac{\dot{M}}{(4\pi/3) \rs^2 \mu \mp}\sqrt{ \frac{r_{\rm s}}{ 2 G \Mbh} } \left( \frac{r}{\rs} \right)^{-n}.
-\end{equation}
-
-We now write the total spectral luminosity density seen in unresolved
-X-ray observations above the cutoff energy as
-
-\begin{align}
- L_{\nu}^{\rm ff} =& \int_0^{r_{\rm s}} 4\pi r^2 \varepsilon_{\nu}^{\rm ff}{\rm d}r \\
-\approx & 2.8\times 10^{16} \, {\rm ergs \, s^{-1}
-  \, Hz^{-1}} \left(\frac{\dot{M}}{10^{-5}M_\odot/{\rm
-      year}} \right)^2 \left(\frac{\rs}{10^{-2}~{\rm pc}} \right)^{-1}
-   \notag \\
-& \times \left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} \notag \\
-\approx & 3.9\times 10^{14} {\rm ergs~s^{-1}~Hz^{-1}}
-\eta^2 \left(\frac{\Mbh}{10^{6}~{\Msun}} \right)^{1.96} \notag\\&\times
-\left(\frac{h \nu}{0.5~{\rm keV}}\right)^{-3/2} v_{500}^{-2.8} \bar{Z}^2 \bar{g}_{\rm ff} Y_{\rm e} 
-\end{align}
-
-The second line of this equation makes the approximation that
-$GM_\bullet/r$ dominates $\tilde{v}_{\rm w}^2$ throughout the
-integrand, which will be true for energies modestly higher than
-$E_{\rm cut}$.  The lower (upper) endpoint for this integral are
-arbitrary so long as it is somewhat less (greater) than the radius at
-which the observed frequency $\nu$ sees its exponential free-free
-cutoff. We have also set $n=1$.
-
-In general, these ``cut-off'' X-ray luminosities are quite small, and
-even {\it Chandra} would have little hope of detecting them in any but
-the nearest dwarf galaxies (e.g. the Magellanic clouds).  However, if
-source confusion is not present, this technique could test for the
-presence of IMBHs in very nearby dwarf galaxies, or more speculatively
-Galactic star clusters.
-
   \clearpage

### 2015-03-01 ms.tex
rest

@@
 h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
-\rho_{\star}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
+\rho_{\star}|_{r_{s}}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
 j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
@@
 \subsection{Black Hole Accretion Rates}
+\label{sec:mdot}
 
@@
 \subsection{Nuclear X-ray Luminosities}
-\label{sec:mdot}
+\label{sec:Lx}
 
@@
 \subsection{Local Growth Time of SMBHs }
+\label{sec:growth}
 
@@
 
-If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
-
 \subsection{TDE Jets}
+\label{sec:TDE}
 
@@
 
-\subsection{Jet Feedback}
-
-We also note
-here that the kinetic heating rate is proportional to the SMBH mass to
-a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{1(0.5)}$ for
-core(cusp) galaxies, respectively. This dependence could have
-important implications for the dependence of the average nuclear X-ray
-luminosity of quiescent galaxies on the SMBH mass
-($\S\ref{sec:mdot}$).
-
-\subsection{Jet Power Correlation}
-
-Accretion rates onto SMBHs can in principle be estimated directly by
-assuming Bondi accretion and using high resolution X-ray observations
-to estimate the gas temperature and density near the Bondi radius.
-This technique has led to the intriguing conclusion that the Bondi
-accretion power correlates with the AGN jet power (e.g.,
-\citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-\citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-required to inflate the observed cavities within the X-ray emitting
-gas.  In practice is it almost never possible to resolve the Bondi
-radius, therefore requiring all such studies to extrapolate the
-observed gas temperature and density profiles to smaller radial
-scales.
+\subsection{Regulation by Kinetic Outflow Feedback}
+\label{sec:kinetic}
+
+We focused on Compton radiative feedback in this paper, since its efficacy was straightforward to calculate in terms of the properties of the accretion flow.
+However, if kinetic outflow feedback from the jet or accretion disk could is important, this could also have some influence on limiting the accretion rate, especially onto high mass black holes.
+The effective wind heating velocity due to kinetic heating rate is proportional to the SMBH mass to a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively (eq.~[\ref{eq:vjet}]).
+Coupled with the dependence of accretion rate on wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), SMBH heating of the formed we have adopted would lead to an Eddington ratio dependence $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
+This prediction of an increasing Eddington ratio is in better with the observed dependence of $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies (Fig.~\ref{fig:miller}), suggesting a possible explanation of stable accretion maintained by kinetic feedback as an alternative explanation for X-ray luminosities of elliptical galaxies.
+On the other hand, our assumption that outflows heat the gas uniformly in volume is arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous environment (Refs).
+
+%\subsection{Jet Power Correlation}
+
+%Accretion rates onto SMBHs can in principle be estimated directly by assuming Bondi accretion and using high resolution X-ray observations to estimate the gas temperature and density near the Bondi radius.
+%This technique has led to the intriguing conclusion that the Bondi accretion power correlates with the AGN jet power (e.g.,
+%\citealt{AllenDunn+:2006a}; \citealt{Russell+13}; \citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
+%required to inflate the observed cavities within the X-ray emitting gas.
+In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
 
 \subsection{Nuclear Star Clusters}
+
+Our results could in principle also have implications for nuclear star clusters or globular clusters.
+{\bf BDM :Do we really want to talk about this?
+or is this an apology?
+I will let Aleksey fill in his ideas...}
 
@@
 prefactor may be slightly different.
+
+If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
+There are two kinds of ``instabilities", global and local.
+The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
+the entire CNM accretes.
+In
+practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
 

### 2015-03-02 ms.tex
rest2
fixed compton accretion rate
challenges.

@@
   \end{cases}
+  \label{eq:MdotCa}
+\end{align}
+If the accretion luminosity $\epsilon = \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
+\begin{align}
+\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
+\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.11}T_{\rm
+C,9}^{-0.44}M_{\bullet,8}^{0.08}
+&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
+C,9}^{-0.4} M_{\bullet,8}^{0.08}
+&, \text{cusp}.
+  \end{cases}
   \label{eq:MdotC}
@@
 
-The cyclic model predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages, a result which appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.
-An alternative explanation for this observation within a thermally stable, steady-state accretion picture is that young stars provide higher stellar wind heating, reducing the mass accretion rate and hence nuclear X-ray luminosity.
+The cyclic model predicts that high $L_{X}$ nuclei should be more
+common in galaxies with younger stellar ages, a result which appears
+in tension with the finding by \citet{Pellegrini10} that galaxies with
+younger stellar populations are observed to host less X-ray luminous
+nuclei, at least for stellar ages $<3$ Gyr.  An alternative
+explanation for this observation within a thermally stable,
+steady-state accretion picture is that young stars provide higher
+stellar wind heating, reducing the mass accretion rate and hence
+nuclear X-ray luminosity.  {\bf AG Challenge: \citet{HeckmanBest:2014a}
+  find that ${\rm L_{[OIII]}}$ (a proxy for the bolometric luminosity)
+  ${\rm L_{[OIII]}/M_\star}$ (a proxy for the Eddington ratio)
+  increases with decreasing 4000 $\AA$ break index (decreasing stellar
+  age) (see their Figure 14). This suggests that the accretion rate is
+  actually increasing towards younger stellar ages. At young ages
+  there actually seems to be plenty of gas around, which may be
+  obscuring the x-rays and causing an anamolously low measurement of
+  $L_X$.
+
+  For a starburst the black hole accretion rate lags the star
+  formation rate by 200 Myr (\citet{WildHeckman+:2010a} Figure
+  9). This could be due to SNe feed back suppressing the black hole
+  accretion rate (massive star winds do the same thing by themselves,
+  but they cannot be sustained for 200 Myr. 
+}
 
@@
 
-Low-mass SMBHs in the local universe ($M_{\bullet} \lesssim 3\times 10^{7}M_{\odot}$) are observed to be growing on a timescale comparable to the age of the universe, while the most massive SMBHs with $M_{\bullet} \gtrsim 10^{9}M_{\odot}$ possess local growth times which are more than 2 orders of magnitude longer (\citealt{Heckman+04}; \citealt{Kauffmann&Heckman09}).
-
-The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate shown in the top panel.
-For black holes accreting steadily given the stellar wind heating associated with the average star formation history of their galaxies, we see that $t_{\rm grow}$ exceeds the Hubble time by 1-3 orders of magnitude across all black hole masses.
-Steady accretion therefore cannot explain the  growth of low mass black holes, a fact which is not surprising given that approximately half of this growth occurs in AGN radiating within 10 per cent of their Eddington rate (\citealt{Heckman+04}).
-Such high accretion rates likely instead require an source of gas external to the nuclear region, triggered either by galaxy mergers associated with the hierachical growth of structure or thermal instabilities on larger, galactic scales (e.g.~\citealt{Ciotti+10}).
-That the growth time associated with thermally-unstable accretion (yellow line) exceeds the Hubble time across all SMBH masses highlights the fact that signifcant black hole growth in the local universe cannot result from thermally-stable steady accretion.
-
-Gas blow-out by SN Ia cannot prevent the growth of low-mass black holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by Ia heating (green lines), although Ia heating could play in principle a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the efficiency of Ia heating.
+Low-mass SMBHs in the local universe ($M_{\bullet} \lesssim 3\times
+10^{7}M_{\odot}$) are observed to be growing on a timescale comparable
+to the age of the universe, while the most massive SMBHs with
+$M_{\bullet} \gtrsim 10^{9}M_{\odot}$ possess local growth times which
+are more than 2 orders of magnitude longer (\citealt{Heckman+04};
+\citealt{Kauffmann&Heckman09}).
+
+The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
+time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
+shown in the top panel.  For black holes accreting steadily given the
+stellar wind heating associated with the average star formation
+history of their galaxies, we see that $t_{\rm grow}$ exceeds the
+Hubble time by 1-3 orders of magnitude across all black hole masses.
+Steady accretion therefore cannot explain the growth of low mass black
+holes, a fact which is not surprising given that approximately half of
+this growth occurs in AGN radiating within 10 per cent of their
+Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
+likely instead require an source of gas external to the nuclear
+region, triggered either by galaxy mergers associated with the
+hierachical growth of structure or thermal instabilities on larger,
+galactic scales (e.g.~\citealt{Ciotti+10}).  That the growth time
+associated with thermally-unstable accretion (yellow line) exceeds the
+Hubble time across all SMBH masses highlights the fact that signifcant
+black hole growth in the local universe cannot result from
+thermally-stable steady accretion.
+
+Gas blow-out by SN Ia cannot prevent the growth of low-mass black
+holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
+Ia heating (green lines), although Ia heating could play in principle
+a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black
+holes, again depending on the efficiency of Ia heating.
 
@@
 
-Our results also have implications for the environments encountered by relativistic jets from TDEs.
-For low-mass SMBHs  $M_{\bullet} \lesssim 10^{7}M_{\odot}$, characterizing those responsible for {\it Swift} J1644+57 (\citealt{Bloom:2011aa}), we predict gas densities of a $n \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating rates within the physically expected range $v_{\rm w} \sim 500-1000$ km s$^{-1}$ (Fig.~\ref{fig:profiles}).
-These values are within the range estimated by modeling the radioa afterglow of {\it Swift} J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).
-In fact, the flattening of the density profile inferred by \citet{Berger+12} on radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that seen in our calculations of the gas density profile for core galaxies (Fig.~\ref{fig:profiles}, solid line).
-The CNM density of the host of {\it Swift} J1644+57 was a factor of 30 times lower than that inferred by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf BDM: whats going on?}  The implications of our models for CNM profiles for the diversity of radio emission from TDE jets will be explored further in future work.
+Our results also have implications for the environments encountered by
+relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
+10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
+J1644+57 (\citealt{Bloom:2011aa}), we predict gas densities of a $n
+\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
+rates within the physically expected range $v_{\rm w} \sim 500-1000$
+km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
+range estimated by modeling the radioa afterglow of {\it Swift}
+J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).  In fact, the
+flattening of the density profile inferred by \citet{Berger+12} on
+radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that
+seen in our calculations of the gas density profile for core galaxies
+(Fig.~\ref{fig:profiles}, solid line).  The CNM density of the host of
+{\it Swift} J1644+57 was a factor of 30 times lower than that inferred
+by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf
+  BDM: whats going on?}  The implications of our models for CNM
+profiles for the diversity of radio emission from TDE jets will be
+explored further in future work.
 
@@
 
-We focused on Compton radiative feedback in this paper, since its efficacy was straightforward to calculate in terms of the properties of the accretion flow.
-However, if kinetic outflow feedback from the jet or accretion disk could is important, this could also have some influence on limiting the accretion rate, especially onto high mass black holes.
-The effective wind heating velocity due to kinetic heating rate is proportional to the SMBH mass to a positive power, $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively (eq.~[\ref{eq:vjet}]).
-Coupled with the dependence of accretion rate on wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), SMBH heating of the formed we have adopted would lead to an Eddington ratio dependence $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
-This prediction of an increasing Eddington ratio is in better with the observed dependence of $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies (Fig.~\ref{fig:miller}), suggesting a possible explanation of stable accretion maintained by kinetic feedback as an alternative explanation for X-ray luminosities of elliptical galaxies.
-On the other hand, our assumption that outflows heat the gas uniformly in volume is arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous environment (Refs).
+We focused on Compton radiative feedback in this paper, since its
+efficacy was straightforward to calculate in terms of the properties
+of the accretion flow.  However, if kinetic outflow feedback from the
+jet or accretion disk could is important, this could also have some
+influence on limiting the accretion rate, especially onto high mass
+black holes.  The effective wind heating velocity due to kinetic
+heating rate is proportional to the SMBH mass to a positive power,
+$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
+galaxies, respectively (eq.~[\ref{eq:vjet}]).  Coupled with the
+dependence of accretion rate on wind heating, $\dot{M}/\dot{M}_{\rm
+  edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), SMBH heating
+of the formed we have adopted would lead to an Eddington ratio
+dependence $\dot{M}/\dot{M}_{\rm edd} \propto
+M_{\bullet}^{-0.5(-0.2)}$.  This prediction of an increasing Eddington
+ratio is in better with the observed dependence of $\langle
+L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
+(Fig.~\ref{fig:miller}), suggesting a possible explanation of stable
+accretion maintained by kinetic feedback as an alternative explanation
+for X-ray luminosities of elliptical galaxies.  On the other hand, our
+assumption that outflows heat the gas uniformly in volume is arbitrary
+and would need to more rigorously justified by numerical studies of
+how jets or disk outflows couple energy to their gaseous environment
+(Refs).
+
+{\bf AG Challenge: Except in the most massive systems the jet duty
+  cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
+  and then periodically turn once the gas begins to cools
+  (Refs). Thus, jets cannot be treated as a truly steady source of
+  heating. 
+}
 

### 2015-03-02 ms.tex
analytics

@@
 
+\newcommand{\densSlope}{\nu}
+
 \topmargin -1 cm
@@
 \author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
-  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
+  Columbia Astropysics Labratory, Columbia University, 550 West 120th
+  Street, New York, NY 10027}
 
@@
 \begin{abstract}
-We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of nominally quiescent galaxies for a range of central black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
-Mass is supplied to the circumnuclear medium by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
-Analytic estimates are provided for the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of black hole mass and the gas heating efficiency, the latter of which is related to the star-formation history.
-We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
-The nuclear X-ray luminosities of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
-The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.
-The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
-We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of circumnuclear environments encountered by the jetted outflows from tidal disruption events.
+  We calculate steady-state, one-dimensional hydrodynamic profiles of
+  hot gas in the nuclei of nominally quiescent galaxies for a range of
+  central black hole mass $M_{\bullet}$, parameterized gas heating
+  rate, and observationally-motivated stellar density profiles.  Mass
+  is supplied to the circumnuclear medium by stellar winds, while gas
+  is heated primarily by stellar winds, supernovae, and black hole
+  feedback.  Analytic estimates are provided for the stagnation radius
+  (where the radial velocity of the gas passes through zero) and the
+  black hole mass accretion rate, $\dot{M}$, as a function of black
+  hole mass and the gas heating efficiency, the latter of which is
+  related to the star-formation history.  We assess the conditions
+  under which radiative instabilities develop, separately in the case
+  of a single burst of star formation and in the case of the average
+  star formation history of galaxies hosting a given black hole
+  mass. The nuclear X-ray luminosities of a sample of quiescent black
+  holes are combined with our results for $\dot{M}$ and an estimate of
+  the radiative efficiency of the accretion flow to conclude that
+  quiescent black holes in the local universe are consistent with
+  accreting in a locally thermally-stable state.  The maximum
+  accretion rate of a thermally-stable flow is, however, too low to
+  explain the accretion rates and short growth time of low mass black
+  holes in the local universe.  The latter must instead result from
+  gas being fed in from large radii, either due to galaxy mergers
+  associated with hierarchical growth or thermal instabilities on
+  larger (galactic) scales.  We briefly discuss implications of our
+  results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship
+  to constrain the occupation fraction of SMBHs in low mass galaxies
+  and the diversity of circumnuclear environments encountered by the
+  jetted outflows from tidal disruption events.
 \end{abstract}
@@
 \begin{align}
-\rs=\frac{G \Mbh}{n \vw^{2}|_{\rs}}\left(\frac{9-\Gamma}{2} \frac{M_{\star}|_{\rs}}{\Mbh} +\frac{7}{2}\right),
+  \rs=\frac{G \Mbh}{\densSlope
+    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
+    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
 \label{eq:stag_analytic}
 \end{align}
-where $n \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the density power-law slope at $r = r_{\rm s}$.
-
-If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
-In this limit, equation (\ref{eq:stag_analytic}) simplifies to
+where $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
+density power-law slope at $r = r_{\rm s}$. We find that
+
+\begin{align}
+\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
+\label{eq:densSlope}
+\end{align}
+
+If the SMBH dominates the gravitational potential at the stagnation
+radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
+resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
+  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
+(\ref{eq:stag_analytic}) simplifies to
 \begin{eqnarray}
-  &\rs \underset{v_w \gtrsim \sigma}\approx \frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx \begin{cases}
-    12
+  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
+    9
  \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
-    6
+    4
  \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
@@
 \end{eqnarray}
-{\bf AG: missing a minus n here...}
-where for the numerical estimate we adopt values of $n \approx 1$ and $n \approx 0.5$ for core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies, respectively, so chosen to match the results of our numerical calculations (Fig.~\ref{fig:stag}).
-This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
-{\bf BDM: all analytic expressions have to be updated in core case to reflect this larger rs}
-
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all, formally implying that the entire ISM of the galaxy is accreting.
-This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+
+where we have used equation~\eqref{eq:densSlope} to estimate
+$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
+core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
+expression is similar to that obtained by \citet{Volonteri+11} on more
+heuristic grounds (their eq.~6).  {\bf BDM: all analytic expressions
+  have to be updated in core case to reflect this larger rs}
+
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the
+stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not
+exist at all, formally implying that the entire ISM of the galaxy is
+accreting.  This result makes intuitive sense: gas is supplied to the
+nuclear by stars which are gravitationally bound to the black hole, so
+outflows are possible only if the specific heating rate $\sim
+v_{w}^{2}$ significantly exceeds the specific gravitational binding
+energy $\sim \sigma^{2}$.
 
@@
   \begin{cases}
-    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
+    6.1 \times 10^{-5} M_{\bullet,8}^{1.76}
     v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
-    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
+    3.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
     v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
@@
   \begin{cases}
-    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
+    2.8 \times 10^{-5} M_{\bullet,8}^{0.76}
     v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
-    2.4 \times 10^{-5} \Mbheight^{0.48} 
+    1.5 \times 10^{-5} \Mbheight^{0.48} 
     v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
@@
   \begin{cases}
-    5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
+    6 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
     \, {\rm g \, cm^{-3}}& \text{core},\\
-    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
+    10 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
   \end{cases}
@@
 \begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx \frac{7}{6n}r_{\rm B},
+  \rs\approx\frac{7}{2}\frac{G \Mbh}{\densSlope \vw^2} \approx
+  \frac{7}{6 \densSlope}r_{\rm B},
   \label{eq:rs_simple}
@@
  &\approx& \begin{cases}
-    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
+    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
     & \text{core} \\
-    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
+    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
     \,{\rm g\,cm^{-3}}  & \text{cusp}, 
@@
 ($\Gamma=0.8$) solutions within our grid.  As expected, the gas
-density increases towards the SMBH $\rho\propto r^{-n}$ with
-$n\simeq1$, i.e. shallower than the $-3/2$ power law for
+density increases towards the SMBH $\rho\propto r^{-\densSlope}$ with
+$\densSlope\simeq1$, i.e. shallower than the $-3/2$ power law for
 Bondi accretion. This power law behavior does not extend
@@
 
-Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm soi}$, with different colors showing different values of $v_{w}$.
-Cusp and core galaxies are marked with square and triangles, respectively.
-Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively, calculated assuming $n = 1$ and $n= 0.5$, respectively.
-Our analytic estimates are found to provide accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but the assumptions leading to these estimates become invalid for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
-For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
-The three green squares which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
-As $r_{\rm b} \rightarrow r_{s}$, the effects of the break radius is to the push the stagnation radius inwards, decreasing the SMBH accretion rate.
+Figure~\ref{fig:stag} shows our results for the stagnation radius
+$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
+  soi}$, with different colors showing different values of $v_{w}$.
+Cusp and core galaxies are marked with square and triangles,
+respectively.  Shown for comparison are our analytic results
+(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
+galaxies, respectively, calculated assuming $\densSlope = 1$ and
+$\densSlope= 0.5$, respectively.  Our analytic estimates are found to
+provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
+\sigma$, but the assumptions leading to these estimates become invalid
+for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
+For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
+sensitively on break radius $r_{b}$, but the latter has a greater
+influence when $v_{w} \lesssim \sigma$.  The three green squares which
+are vertically aligned at the same value of $v_{w}/\sigma$ (close to
+where the analytic estimate diverges) correspond to models with the
+same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
+300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
+50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
+r_{s}$, the effects of the break radius is to the push the stagnation
+radius inwards, decreasing the SMBH accretion rate.
 
@@
   \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
-    $r_{s}$ in units of the sphere of influence radius $r_{\rm
-      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
-    function of the ratio of the effective wind heating rate $v_{w}$
-    to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
-    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
-    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
-    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively. }
+    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
+    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
+    the ratio of the effective wind heating rate $v_{w}$ to the
+    stellar velocity dispersion $\sigma$.  Green, orange, and blue
+    symbols correspond to different values of $v_{w} =$ 300, 600, and
+    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
+    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
+    ($\Gamma = 0.1$). The black curves correspond to the analytic
+    prediction from equation (\ref{eq:rs2main}), with solid and dashed
+    curves calculated for parameters $\{\Gamma=0.8, \densSlope=1\}$ and
+    $\{\Gamma=0.1,\densSlope=0.5\}$, respectively. }
 \end{figure}
@@
 for an advective accretion flow expected to produce high $T_{\rm C}$
-emission (e.g.~\citealt{Narayan&Yi95}).
-We caveat that, unlike stellar wind heating, Compton heating depends on radius, scaling as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
-$\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
-The assumption of our model that the heating parameter be constant with radius is not satisfied, but this radial variation is sufficiently weak that it should not significantly alter our conclusions.
+emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
+stellar wind heating, Compton heating depends on radius, scaling as
+$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
+r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.7}$
+for core ($\Gamma = 0.8$; $\densSlope = 1$) and cusp ($\Gamma = 0.1$;
+$\densSlope = 0.5$) galaxies, respectively.  The assumption of our model that the heating
+parameter be constant with radius is not satisfied, but this radial
+variation is sufficiently weak that it should not significantly alter
+our conclusions.
 

### 2015-03-03 ms.tex

@@
 w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
-T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}} \tilde{v}_{w}^{2}(1+\phi)}
+T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}}
+\tilde{v}_{w}^{2}}
+ \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
+    \phi \rho c_s^3}}\right)
 \nonumber \\ &\sim {\rm min}
   \begin{cases}
-  10 \eta_{0.02}^{-1}
+  20 \eta_{0.02}^{-1}
 M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
- 10 \eta_{0.02}^{-1}
+ 20 \eta_{0.02}^{-1}
 M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
-  1.0(\phi/0.1)/(2-\Gamma) & \text{saturated},
+  2 \phi & \text{saturated},
   \end{cases}
@@
 \end{align}
-where the second equality makes use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim 1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.
-We have approximated the stellar density profile as (eq.~[\ref{eq:rhostar}])
+where the second equality makes use of equations (\ref{eq:Tanalytic}),
+(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
+1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
+stellar density profile as (eq.~[\ref{eq:rhostar}])
 \begin{eqnarray}
@@
 \end{eqnarray}
-where the stagnation radius is assume to reside well inside the Nuker break radius.
-Equation (\ref{eq:conduction}) shows that even in the case of saturated conduction, the neglect of heat conduction results in at most an order unity correction for expected values of the saturation parameter $\phi < 0.1$, justifying its neglect in our analysis.
-Numerical experiments including conductivity confirm this ($\S\ref{sec:numerical}$).
+where the stagnation radius is assume to reside well inside the Nuker
+break radius.  Equation (\ref{eq:conduction}) shows that even in the
+case of saturated conduction, the neglect of heat conduction results
+in at most an order unity correction for expected values of the
+saturation parameter $\phi < 0.1$, justifying its neglect in our
+analysis.  Numerical experiments including conductivity confirm this
+($\S\ref{sec:numerical}$). {\bf AG: If we make this statement then we
+  should be sure to include the numerical experiments. The original
+  formula was not correct for the saturated case. The numerical values
+also changed somewhat. I would appreciate it if someone could double
+check this. Also note that there is a weak core/cusp dependence in the
+saturated case which I have chosen not to include.}
 
@@
 
-Radiative cooling usually has its greatest impact near or external to the stagnation radius, where the gas resides in near hydrostatic balance.
-If radiative cooling becomes important, it can qualitatively alter key features of the accretion flow.
-Initially hydrostatic gas that cools at constant pressure $P \propto nT$ at the rate $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$ (eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable (\citealt{McCourt+12} and references therein), potentially resulting in the formation of a multi-phase medium and enhanced star formation.
-Even if the hot plasma of the CNM does not condense into cold clouds, the loss of pressure can temporarily increase the black hole accretion rate; when coupled to feed-back processes, the latter can lead to time-dependent (e.g.
-limit cycle) behavior (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}), which is also inconsistent with our assumption of a steady, single-phase flow.
+Radiative cooling usually has its greatest impact near or external to
+the stagnation radius, where the gas resides in near hydrostatic
+balance.  If radiative cooling becomes important, it can qualitatively
+alter key features of the accretion flow. Initially hydrostatic gas
+that cools at constant pressure $P \propto nT$ at the rate
+$\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$
+(eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable
+(\citealt{McCourt+12} and references therein), potentially resulting
+in the formation of a multi-phase medium and enhanced star formation.
+Even if the hot plasma of the CNM does not condense into cold clouds,
+the loss of pressure can temporarily increase the black hole accretion
+rate; when coupled to feed-back processes, the latter can lead to
+time-dependent (e.g. limit cycle) behavior
+(e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10};
+\citealt{Yuan&Li11}, \citealt{Gan+14}), which is also inconsistent
+with our assumption of a steady, single-phase flow.
 
@@
   \begin{cases}
-   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
-   210 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
+   430 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
+   840 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
   \end{cases}
@@
 \end{align}
-where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gas and stellar densities at the stagnation radius, respectively.
-We have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}; his Fig.
-34.1).
-
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
+where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs})
+for the gas and stellar densities at the stagnation radius,
+respectively.  We have approximated the cooling function for $T <
+2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
+  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ assuming solar
+metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).
+
+To within a constant of order unity, equation (\ref{eq:cooling2}) also
+equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n
+kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
+stagnation radius, as can be derived using the equality
 \begin{align}
@@
   {\rm min}\begin{cases}
-   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
+   6\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
    2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
@@
     prediction from equation (\ref{eq:rs2main}), with solid and dashed
-    curves calculated for parameters $\{\Gamma=0.8, \densSlope=1\}$ and
-    $\{\Gamma=0.1,\densSlope=0.5\}$, respectively. }
+    curves calculated for parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
+    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
 \end{figure}
@@
 
-\begin{eqnarray}
-  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}
-  &\approx& 12\eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
-    Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} \nonumber \\
-  &\approx& 12 M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}
+\begin{align}
+  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}&\approx
+  \begin{cases}
+    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56}  & {\rm core}\\
+    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} &{\rm cusp}\\
+   \end{cases} \nonumber\\
+ &\approx 
+ \begin{cases}
+    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}  & {\rm core}\\
+    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74} &{\rm cusp}\\
+   \end{cases}
 \label{eq:rIars}
-\end{eqnarray}
+\end{align}
 If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
@@
 Radiative feedback is potentially effective even in low luminosity AGN via Compton heating (e.g., \citealt{Sazonov+04}, \citealt{Ciotti+10}), which provides a volumetric heating rate (\citealt{Gan+14})
-\be
+\begin{align}
 \dot{e} = 4.1\times 10^{-35}n^{2}\xi T_{\rm C}\,{\rm erg\,cm^{-3}\,s^{-1}},
-\ee
+\end{align}
 where $\xi = L/n r^{2}$ is the ionization parameter and $L$ is the SMBH luminosity with Compton temperature $T_{\rm C} \sim 10^{9}$ K $\gg T$ (e.g., \citealt{Ho99}, \citealt{Eracleous+10}).
@@
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 29 \eta_{0.02}^{0.5}T_{\rm
+  \begin{cases} 27 \eta_{0.02}^{0.5}T_{\rm
 C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
-km\,s^{-1}} &, \text{core}\\ 50 \eta_{0.02}^{0.5}T_{\rm
+km\,s^{-1}} &, \text{core}\\ 30 \eta_{0.02}^{0.5}T_{\rm
 C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
@@
 $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
-r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.7}$
-for core ($\Gamma = 0.8$; $\densSlope = 1$) and cusp ($\Gamma = 0.1$;
-$\densSlope = 0.5$) galaxies, respectively.  The assumption of our model that the heating
+r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.75}$
+for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
+$\densSlope \simeq 0.6$) galaxies, respectively.  The assumption of our model that the heating
 parameter be constant with radius is not satisfied, but this radial
@@
 C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
-&, \text{core}\\ 130 \eta_{0.02}^{0.29}T_{\rm
+&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
 C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
@@
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 1.3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
+\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
 C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
-&, \text{core}\\ 6\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
+&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
 C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
@@
 \end{align}
-If the accretion luminosity $\epsilon = \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
+If the accretion luminosity $\epsilon = 0.1 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
 \begin{align}
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.11}T_{\rm
+\begin{cases} 1.4\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
 C,9}^{-0.44}M_{\bullet,8}^{0.08}
-&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
+&, \text{core}\\ 6\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
 C,9}^{-0.4} M_{\bullet,8}^{0.08}
@@
 \end{align}
+{\bf AG: Note that I have included the bolometric correction for now.}
 

### 2015-03-03 windheat.tex
more in 5

@@
 the corresponding mean stellar mass.
+Our optimistic assumption of 100 per cent thermalization efficiency of stellar winds is at least partially offset by our conservative assumption to neglect energy input from core collapse supernovae, which contribute a comparable energy injection rate to massive stellar winds.
 
@@
   \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
-      d}t_1\\
+      d}t_1 \label{eq:MDotSFH}\\
   \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
-      d}t_1,\\
+      d}t_1, \label{eq:EDotSFH}
 \end{align}
@@
 \end{align}
-
 The mass return parameter will be
-
 \begin{align}
@@
 \end{align}
-
  % \begin{figure}
-% \includegraphics[width=\columnwidth]{vw.pdf}
-% \caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
-% different $S(t)$.  The yellow and orange curves are the Moster SF
-% histories, with and without Type II SNe, respectively.  The red,
-% purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
-% function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
-% respectively.  These solid curves lack SN, but the dashed purple curve
-% possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
-% variability timescale is greater than $\sim$ twice the duration of
-% high-velocity winds.}
+ % \includegraphics[width=\columnwidth]{NickPlot2.pdf}
+ % \caption{\label{NickPlot2} Effective wind velocities for
+ % nonstandard star formation histories.
+The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.
+Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.
+The purple curve shows a recent drop in the star formation rate, i.e.
+$t_{\rm scale}=10^6~{\rm yr}$.
+The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.
+Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively.
+}
  % \end{figure}
-
 We estimate the stellar wind heating provided by the {\it average}
 star formation history of galaxies of a given $\Mbh$ using the results
-of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]).  Note that the
+of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
 star formation histories in \citet{MosterNaab+:2013a} are in terms of
@@
 $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
+A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.
+To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs.
+\ref{eq:MDotSFH} and \ref{eq:EDotSFH}.
+
+Figure \ref{NickPlot2} shows how the wind heating varies as star formation histories deviate from their halo-averaged values.  In particular, we show
+\begin{align} 
+  \dot{\mathcal{M}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{m}}(t-t_1){\rm
+      d}t_1\\
+  \dot{\mathcal{E}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{e}}(t-t_1){\rm
+      d}t_1,\\
+  \mathcal{V}_w^2(t) &=2 \dot{\mathcal{E}}(t)/\dot{\mathcal{M}}(t).
+\end{align}
+In these equations, 
+\begin{equation}
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\epsilon)\arctan(t/t_{\rm scale}) + \epsilon \right).
+\end{equation}
+This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.
+In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
+As we can see in Fig.
+\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
 

### 2015-03-03 windheat.tex
Fixing "\densSlope"

@@
 \end{align}
- % \begin{figure}
- % \includegraphics[width=\columnwidth]{NickPlot2.pdf}
- % \caption{\label{NickPlot2} Effective wind velocities for
- % nonstandard star formation histories.
+ \begin{figure}
+ \includegraphics[width=\columnwidth]{NickPlot2.pdf}
+ \caption{\label{NickPlot2} Effective wind velocities for
+ nonstandard star formation histories.
 The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.
@@
 }
- % \end{figure}
+ \end{figure}
 We estimate the stellar wind heating provided by the {\it average}

### 2015-03-04 ms.tex
Fixing "\densSlope"
log-normal

@@
 hierachical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}).  That the growth time
-associated with thermally-unstable accretion (yellow line) exceeds the
-Hubble time across all SMBH masses highlights the fact that signifcant
-black hole growth in the local universe cannot result from
-thermally-stable steady accretion.
+galactic scales (e.g.~\citealt{Ciotti+10}).
+
+\citet{Kauffmann&Heckman09} find that the growth of low mass black
+holes is dominated by young stellar bulges which have a log normal
+distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
+0.01$. The distribution is insensitive to galaxy properties which
+suggestes that it is set by feedback from the black hole rather than
+from the gas supply in the nucleus.
+
+That the growth time associated with thermally-unstable accretion
+(yellow line) exceeds the Hubble time across all SMBH masses
+highlights the fact that signifcant black hole growth in the local
+universe cannot result from thermally-stable steady accretion of gas
+lost from the surrounding stellar population.
 

### 2015-03-05 ms.tex
Minor revision to Appendix B, substantial update to 5.5.2.

--- 2015-03-02 ms.tex
@@
 \author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
-  Columbia Astropysics Labratory, Columbia University, 550 West 120th
-  Street, New York, NY 10027}
+  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
 
@@
 \begin{abstract}
-  We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in the nuclei of nominally quiescent galaxies for a range of
-  central black hole mass $M_{\bullet}$, parameterized gas heating
-  rate, and observationally-motivated stellar density profiles.  Mass
-  is supplied to the circumnuclear medium by stellar winds, while gas
-  is heated primarily by stellar winds, supernovae, and black hole
-  feedback.  Analytic estimates are provided for the stagnation radius
-  (where the radial velocity of the gas passes through zero) and the
-  black hole mass accretion rate, $\dot{M}$, as a function of black
-  hole mass and the gas heating efficiency, the latter of which is
-  related to the star-formation history.  We assess the conditions
-  under which radiative instabilities develop, separately in the case
-  of a single burst of star formation and in the case of the average
-  star formation history of galaxies hosting a given black hole
-  mass. The nuclear X-ray luminosities of a sample of quiescent black
-  holes are combined with our results for $\dot{M}$ and an estimate of
-  the radiative efficiency of the accretion flow to conclude that
-  quiescent black holes in the local universe are consistent with
-  accreting in a locally thermally-stable state.  The maximum
-  accretion rate of a thermally-stable flow is, however, too low to
-  explain the accretion rates and short growth time of low mass black
-  holes in the local universe.  The latter must instead result from
-  gas being fed in from large radii, either due to galaxy mergers
-  associated with hierarchical growth or thermal instabilities on
-  larger (galactic) scales.  We briefly discuss implications of our
-  results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship
-  to constrain the occupation fraction of SMBHs in low mass galaxies
-  and the diversity of circumnuclear environments encountered by the
-  jetted outflows from tidal disruption events.
+We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of nominally quiescent galaxies for a range of central black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
+Mass is supplied to the circumnuclear medium by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
+Analytic estimates are provided for the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of black hole mass and the gas heating efficiency, the latter of which is related to the star-formation history.
+We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
+The nuclear X-ray luminosities of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
+The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.
+The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
+We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of circumnuclear environments encountered by the jetted outflows from tidal disruption events.
 \end{abstract}
@@
 \begin{align}
-  \rs=\frac{G \Mbh}{\densSlope
-    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
-    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
+\rs=\frac{G \Mbh}{n \vw^{2}|_{\rs}}\left(\frac{9-\Gamma}{2} \frac{M_{\star}|_{\rs}}{\Mbh} +\frac{7}{2}\right),
 \label{eq:stag_analytic}
 \end{align}
-where $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
-density power-law slope at $r = r_{\rm s}$. We find that
-
-\begin{align}
-\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
-\label{eq:densSlope}
-\end{align}
-
-If the SMBH dominates the gravitational potential at the stagnation
-radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
-resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
-  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
-(\ref{eq:stag_analytic}) simplifies to
+where $n \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the density power-law slope at $r = r_{\rm s}$.
+
+If the SMBH dominates the gravitational potential at the stagnation radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius resides well inside the sphere of influence ($r_{\rm s} < r_{\rm soi}$; eq.~[\ref{eq:rsoi}]).
+In this limit, equation (\ref{eq:stag_analytic}) simplifies to
 \begin{eqnarray}
-  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
-    9
+  &\rs \underset{v_w \gtrsim \sigma}\approx \frac{7}{2}\frac{G \Mbh}{n \tilde{v}_{w}^{2}} \approx \begin{cases}
+    12
  \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
-    4
+    6
  \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
@@
 \end{eqnarray}
-
-where we have used equation~\eqref{eq:densSlope} to estimate
-$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
-core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
-expression is similar to that obtained by \citet{Volonteri+11} on more
-heuristic grounds (their eq.~6).  {\bf BDM: all analytic expressions
-  have to be updated in core case to reflect this larger rs}
-
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the
-stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not
-exist at all, formally implying that the entire ISM of the galaxy is
-accreting.  This result makes intuitive sense: gas is supplied to the
-nuclear by stars which are gravitationally bound to the black hole, so
-outflows are possible only if the specific heating rate $\sim
-v_{w}^{2}$ significantly exceeds the specific gravitational binding
-energy $\sim \sigma^{2}$.
+{\bf AG: missing a minus n here...}
+where for the numerical estimate we adopt values of $n \approx 1$ and $n \approx 0.5$ for core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies, respectively, so chosen to match the results of our numerical calculations (Fig.~\ref{fig:stag}).
+This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
+{\bf BDM: all analytic expressions have to be updated in core case to reflect this larger rs}
+
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all, formally implying that the entire ISM of the galaxy is accreting.
+This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
 
@@
   \begin{cases}
-    6.1 \times 10^{-5} M_{\bullet,8}^{1.76}
+    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
     v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
-    3.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
+    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
     v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
@@
   \begin{cases}
-    2.8 \times 10^{-5} M_{\bullet,8}^{0.76}
+    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
     v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
-    1.5 \times 10^{-5} \Mbheight^{0.48} 
+    2.4 \times 10^{-5} \Mbheight^{0.48} 
     v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
@@
   \begin{cases}
-    6 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
+    5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
     \, {\rm g \, cm^{-3}}& \text{core},\\
-    10 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
+    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
   \end{cases}
@@
 \begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{\densSlope \vw^2} \approx
-  \frac{7}{6 \densSlope}r_{\rm B},
+  \rs\approx\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx \frac{7}{6n}r_{\rm B},
   \label{eq:rs_simple}
@@
  &\approx& \begin{cases}
-    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
+    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
     & \text{core} \\
-    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
+    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
     \,{\rm g\,cm^{-3}}  & \text{cusp}, 
@@
 ($\Gamma=0.8$) solutions within our grid.  As expected, the gas
-density increases towards the SMBH $\rho\propto r^{-\densSlope}$ with
-$\densSlope\simeq1$, i.e. shallower than the $-3/2$ power law for
+density increases towards the SMBH $\rho\propto r^{-n}$ with
+$n\simeq1$, i.e. shallower than the $-3/2$ power law for
 Bondi accretion. This power law behavior does not extend
@@
 
-Figure~\ref{fig:stag} shows our results for the stagnation radius
-$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
-  soi}$, with different colors showing different values of $v_{w}$.
-Cusp and core galaxies are marked with square and triangles,
-respectively.  Shown for comparison are our analytic results
-(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
-galaxies, respectively, calculated assuming $\densSlope = 1$ and
-$\densSlope= 0.5$, respectively.  Our analytic estimates are found to
-provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
-\sigma$, but the assumptions leading to these estimates become invalid
-for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
-For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
-sensitively on break radius $r_{b}$, but the latter has a greater
-influence when $v_{w} \lesssim \sigma$.  The three green squares which
-are vertically aligned at the same value of $v_{w}/\sigma$ (close to
-where the analytic estimate diverges) correspond to models with the
-same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
-300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
-50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
-r_{s}$, the effects of the break radius is to the push the stagnation
-radius inwards, decreasing the SMBH accretion rate.
+Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm soi}$, with different colors showing different values of $v_{w}$.
+Cusp and core galaxies are marked with square and triangles, respectively.
+Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively, calculated assuming $n = 1$ and $n= 0.5$, respectively.
+Our analytic estimates are found to provide accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but the assumptions leading to these estimates become invalid for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
+For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.
+The three green squares which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
+As $r_{\rm b} \rightarrow r_{s}$, the effects of the break radius is to the push the stagnation radius inwards, decreasing the SMBH accretion rate.
 
@@
   \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
-    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
-    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
-    the ratio of the effective wind heating rate $v_{w}$ to the
-    stellar velocity dispersion $\sigma$.  Green, orange, and blue
-    symbols correspond to different values of $v_{w} =$ 300, 600, and
-    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
-    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
-    ($\Gamma = 0.1$). The black curves correspond to the analytic
-    prediction from equation (\ref{eq:rs2main}), with solid and dashed
-    curves calculated for parameters $\{\Gamma=0.8, \densSlope=1\}$ and
-    $\{\Gamma=0.1,\densSlope=0.5\}$, respectively. }
+    $r_{s}$ in units of the sphere of influence radius $r_{\rm
+      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
+    function of the ratio of the effective wind heating rate $v_{w}$
+    to the stellar velocity dispersion $\sigma$.  Green, orange, and
+    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
+    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
+    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
+    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively. }
 \end{figure}
@@
 for an advective accretion flow expected to produce high $T_{\rm C}$
-emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
-stellar wind heating, Compton heating depends on radius, scaling as
-$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
-r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.7}$
-for core ($\Gamma = 0.8$; $\densSlope = 1$) and cusp ($\Gamma = 0.1$;
-$\densSlope = 0.5$) galaxies, respectively.  The assumption of our model that the heating
-parameter be constant with radius is not satisfied, but this radial
-variation is sufficiently weak that it should not significantly alter
-our conclusions.
+emission (e.g.~\citealt{Narayan&Yi95}).
+We caveat that, unlike stellar wind heating, Compton heating depends on radius, scaling as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
+$\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
+The assumption of our model that the heating parameter be constant with radius is not satisfied, but this radial variation is sufficiently weak that it should not significantly alter our conclusions.
 
@@
 
-A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
+A single burst of star formation does not describe the typical star formation history of most galaxies.  Qualitatively,
+smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the gas heating budget.
 Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
@@
 MSP heating is again found to be negligible for all black hole masses.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
-Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
-Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
-Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
-
-Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
-Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
-For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
-, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
-We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
-{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
+Only for the most massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack of young stellar populations significantly reduce the role of stellar wind heating.
+%Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across all black hole masses}.
+{\bf NCS: deleted a sentence referring to old results on thermal instability - it is now correct to say we are thermally stable everywhere, yes?}
+
+Realistic variations (``burstiness") in the star formation history will often result in lower heating rates.
+Figure \ref{NickPlot2} shows the heating rate as a function of average black hole mass for non-fiducial cases in which the current ($z = 0$) star formation is suppressed by a factor $\zeta$ from its average $z = 0$ value, for a characteristic timescale $t_{\rm scale}$ (for details, see Appendix \ref{app:windheat}).
+For $t_{\rm scale} \lesssim 10^{7}$ yr, we see that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$ from its average value, even for huge drops in the star formation rate ($\zeta \sim 10^{-3}$).
+However, burstiness in the star formation history over longer timescales can suppress heating more significantly.
+When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an exception to this is in galactic nuclei with $M_\bullet \gtrsim 5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).
+Our use of average cosmic star formation histories is appropriate provided local variations are either on short timescales ($t_{\rm scale} \lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim 0.1$).
+If both of these conditions are violated, then the effective heating rates for all but the most massive galaxies (where Ia explosions dominate) will fall by a factor $\approx 5$ from our fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.
+
+{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}
 

### 2015-03-05 windheat.tex
Comment
Revert "Fixing "\densSlope""
This reverts commit 07d309ce84bad0f788096d8ef99c332e42dc2e06.
Minor revision to Appendix B, substantial update to 5.5.2.

@@
 The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.
-Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively.
+Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\zeta = 0.001$, $\zeta = 0.1$, and $\zeta = 0.3$ of their halo-averaged values, respectively.
 }
@@
 formation history would produce a bulge consistent with the
-$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
-A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.
-To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs.
-\ref{eq:MDotSFH} and \ref{eq:EDotSFH}.
+$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
+slight complication occurs for the largest mass halos, where much of
+the $z=0$ stellar mass has been acquired through accretion of
+satellite halos rather than {\it in situ} star formation.  To
+accomodate this, we incorporate analytic fits for mass accretion histories, taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, assuming that the age distribution of the accreted stars is equal to the age distribution of those formed {\it in situ}.
+This assumption may be conservative if the primary galaxy's accretion history is dominated by minor mergers with younger stellar populations.
+On the other hand, the dynamical friction inspiral time for small satellite galaxies is quite long, generally much greater than the $\sim 10^7~{\rm yr}$ for which young stars can dominate the heating budget.
 
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\epsilon)\arctan(t/t_{\rm scale}) + \epsilon \right).
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\zeta)\arctan(t/t_{\rm scale}) + \zeta \right).
 \end{equation}
-This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.
-In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
+This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\mathcal{V}_{\rm w}$.
+In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\zeta$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
 As we can see in Fig.
-\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
+\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\zeta \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
 

### 2015-03-05 ms.tex
Formatting

--- 2015-03-04 ms.tex
@@
 
-Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.
-For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-
-Figure \ref{fig:bh_growth} (top panel) shows with solid lines the accretion rate as a function of black hole mass for the average star formation heating, calculated from equation (\ref{eq:eddr_analytic}) using our results for the total wind heating (Fig.~\ref{fig:mdot_mass}).
-This average accretion rate increases from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
-These fall below the maximum thermally stable accretion rate, $\dot{M}_{\rm TI}$ (plotted as yellow lines), except at the highest black hole masses $\sim 10^{9}M_{\odot}$.
-For these highest mass black holes, the maximum accretion rate as set by gas blow-out from SN Ia (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the accretion rate below the thermally-unstable value, provided that the SN Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia} \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just preceeding eq.~[\ref{eq:eddr_Ia}]).
-This is only possible if the Ia heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally assumed (\citealt{Sharma+14}).
-For lower mass black holes, the maximum accretion rate set by SN Ia is significantly higher and cannot prevent the development of thermally unstable flows, i.e.
-$\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
-
-Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and the upper limit on $\dot{M}$ for the black hole in NGC3115 set by \citealt{ShcherbakovWong+:2014a}.
-These points are consistent with our thermally-stable accretion rates within the expected dispersion (see next section), although NGC3115 is in fact a low luminosity AGN.
+Figure \ref{fig:vwSources} shows that the heating associated with the
+average star formation history of a galaxy is approximately constant
+with SMBH mass, except for the largest black holes with $M_{\bullet}
+\gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter,
+the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto
+M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+
+Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
+accretion rate as a function of black hole mass for the average star
+formation heating, calculated from equation (\ref{eq:eddr_analytic})
+using our results for the total wind heating
+(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
+from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
+black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
+10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
+These fall below the maximum thermally stable accretion rate,
+$\dot{M}_{\rm TI}$ (plotted as yellow lines), except at the highest
+black hole masses $\sim 10^{9}M_{\odot}$.  For these highest mass
+black holes, the maximum accretion rate as set by gas blow-out from SN
+Ia (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
+accretion rate below the thermally-unstable value, provided that the
+SN Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia}
+\gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just
+preceeding eq.~[\ref{eq:eddr_Ia}]).  This is only possible if the Ia
+heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally
+assumed (\citealt{Sharma+14}).  For lower mass black holes, the
+maximum accretion rate set by SN Ia is significantly higher and cannot
+prevent the development of thermally unstable flows,
+i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
+
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
+the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and
+the upper limit on $\dot{M}$ for the black hole in NGC3115 set by
+\citealt{ShcherbakovWong+:2014a}.  These points are consistent with
+our thermally-stable accretion rates within the expected dispersion
+(see next section), although NGC3115 is in fact a low luminosity AGN.
 
@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).
-Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using our estimate of the gas heating rate provided at $z = 0$ by the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
-Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).
-Red lines show the accretion rate so obtained if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).
-Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).
-{\bf BDM: add SgrA* numbers derived by quataert, NGC3115 from Roman} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
-  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
+\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
+  black hole accretion rate $\dot{M}$ in Eddington units as a function
+  of black hole mass $M_{\bullet}$, shown separately for core
+  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
+  dot-dashed lines).  Black lines show the accretion rate calculated
+  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
+  heating rate provided at $z = 0$ by the average star formation
+  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
+  lines show the maximum accretion set by Ia supernovae blow-out
+  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
+  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
+  lines show the maximum accretion rate for a thermally stable flow
+  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  {\bf BDM: add
+    SgrA* numbers derived by quataert, NGC3115 from Roman} {\it Bottom
+    panel:} Growth times $\Mbh/\Mdot$ in units of the Hubble time
+  $\th$ for each of the accretion rates shown in the top panel.}
 \end{figure}
@@
 
-The unresolved core X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).
-Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric correction at X-ray energies appropriate for low luminosity AGN (\citealt{Ho08}).
-We have averaged the accretion rate used in calculating $\langle L_X \rangle$ between the values for galaxies with core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles using the average value of the inner density slope $\Gamma$ as a function of black hole mass as fit from the \citet{LauerFaber+:2007a} galaxy sample, an exercise that results in the relationship $\Gamma = ...$.
-{\bf BDM: fill in}
-
-The left panel of Figure \ref{fig:miller} is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$ typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}), while the right panel luminosities are calculated instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}).
-Shown for comparison are the X-ray measurements (green stars) and upper limits (gray triangles) of early-type galaxies compiled by \citet{Miller+15} (cf.~\citealt{Gallo+10}).
-A green line shows the best power-law fit to the X-ray luminosity from \citet{Miller+15}, given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = XXX$  (see also \citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
-Yellow, teal, and red lines show the maximum accretion rates, respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]).
+The unresolved core X-ray luminosities of galactic nuclei provide a
+powerful diagnostic of the SMBH accretion rates and how they vary
+across different galaxy properties and SMBH masses (e.g.,
+\citealt{Ho08} and references therein).  Figure~\ref{fig:miller} shows
+our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm
+  bol} \dot{M} c^2$ in Eddington units as a function of black hole
+mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric
+correction at X-ray energies appropriate for low luminosity AGN
+(\citealt{Ho08}).  We have averaged the accretion rate used in
+calculating $\langle L_X \rangle$ between the values for galaxies with
+core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
+profiles using the average value of the inner density slope $\Gamma$
+as a function of black hole mass as fit from the
+\citet{LauerFaber+:2007a} galaxy sample, an exercise that results in
+the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$.
+
+The left panel of Figure \ref{fig:miller} is calculated assuming a
+constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$
+typical of those estimated for low luminosity AGN (e.g.,
+\citealt{Ho:2009a}), while the right panel luminosities are calculated
+instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm
+  edd}$ that depends on the Eddington ratio as predicted by some
+models for radiatively inefficient accretion flows
+(\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison
+are the X-ray measurements (green stars) and upper limits (gray
+triangles) of early-type galaxies compiled by \citet{Miller+15}
+(cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
+to the X-ray luminosity from \citet{Miller+15}, given by $\langle
+L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
+\citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
+Yellow, teal, and red lines show the maximum accretion rates,
+respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]),
+as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by
+Compton heating feedback (eq.~[\ref{eq:MdotC}]).
 
@@
 
-If heating in the nuclei of elliptical galaxies is similar to that produced by the average star formation history of galaxies with similar mass, then to first order we predict that $\langle L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.
-This result is in tension with the observed down-sizing trend that the average Eddington ratio is observed to decrease (albeit also weakly) with $M_{\bullet}$.
-However, in making such comparisons it is important to keep in mind the enormous uncertainty in calculating the luminosity of the accretion flow close to the black hole in a single waveband based on the accretion rate on larger scales.
-Black hole mass-dependent efficiency factors could enter that we are not taking into account.
-For instance, if disk outflows carry away a substantial fraction of the infalling mass before it reaches sufficiently small radii to produce the observed X-rays (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the angular momentum of the infalling gas (and hence that of stars in the galactic nucleus) might also influence the X-ray luminosity, in a way that could depend systematically on $M_{\bullet}$.
-
-A more readily addressable test is whether a steady-state accretion picture is capable of explaining the large scatter of typically 2-3 orders of magnitude in the observed distribution of $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.
-Scatter is expected to result from at least two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).
-The combination of (1) and (2) is capable of explaining much of the observed sample, especially considering that scatter in $L_{\rm X}$ due to variations in $\dot{M}$ is exacerbated by the expectation that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
-
-It is also possible that many of the nuclei from the \citet{Miller+15} sample are not accreting in a steady fashion.
-The ADAF efficiency assumed in the right panel of Figure \ref{fig:miller} in some ways represents the maximum value, since it does not take into account outflows from the accretion flow that would suppress the accreiton rate reaching large radii.
-Nevertheless, many lower black hole masses of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie well above the predicted average value for stable accretion (black line), suggesting that these galaxies either experience lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all ($\S\ref{sec:cycle}$).
-Indeed, for the lowest mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ exceeds the one corresponding to the maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
-Many of the upper limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a separate ``thermally stable".
-This possible dichotomy calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
+If heating in the nuclei of elliptical galaxies is similar to that
+produced by the average star formation history of galaxies with
+similar mass, then to first order we predict that $\langle
+L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though
+only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.  This
+result is in tension with the observed down-sizing trend that the
+average Eddington ratio is observed to decrease (albeit also weakly)
+with $M_{\bullet}$.  However, in making such comparisons it is
+important to keep in mind the enormous uncertainty in calculating the
+luminosity of the accretion flow close to the black hole in a single
+waveband based on the accretion rate on larger scales.  Black hole
+mass-dependent efficiency factors could enter that we are not taking
+into account.  For instance, if disk outflows carry away a substantial
+fraction of the infalling mass before it reaches sufficiently small
+radii to produce the observed X-rays
+(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
+angular momentum of the infalling gas (and hence that of stars in the
+galactic nucleus) might also influence the X-ray luminosity, in a way
+that could depend systematically on $M_{\bullet}$.
+
+A more readily addressable test is whether a steady-state accretion
+picture is capable of explaining the large scatter of typically 2-3
+orders of magnitude in the observed distribution of $L_{X}/L_{\rm
+  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
+least two effects: (1) the order of magnitude difference between
+$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
+(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
+to the variation in the Nuker stellar density profile $\Gamma$ at
+fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
+to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
+v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
+combination with the significant dependence of $v_w$ on stochastic
+intermittency in the star formation history (Fig.~NICK).  The
+combination of (1) and (2) is capable of explaining much of the
+observed sample, especially considering that scatter in $L_{\rm X}$
+due to variations in $\dot{M}$ is exacerbated by the expectation that
+$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
+
+It is also possible that many of the nuclei from the \citet{Miller+15}
+sample are not accreting in a steady fashion.  The ADAF efficiency
+assumed in the right panel of Figure \ref{fig:miller} in some ways
+represents the maximum value, since it does not take into account
+outflows from the accretion flow that would suppress the accreiton
+rate reaching large radii.  Nevertheless, many lower black hole masses
+of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie
+well above the predicted average value for stable accretion (black
+line), suggesting that these galaxies either experience lower levels
+of heating than average galaxies of their mass, or that they are not
+accreting stably at all ($\S\ref{sec:cycle}$).  Indeed, for the lowest
+mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$
+exceeds the one corresponding to the maximum thermally-stable
+accretion rate, $\dot{M}_{\rm TI}$ (yellow line).  Many of the upper
+limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
+separate ``thermally stable".  This possible dichotomy calls into
+question the use of simple extrapolations of power-law fits to the
+$L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
+constrain the occupation fraction of black holes in low mass galaxies
+(\citealt{Miller+15}).
 
@@
 
-Figure \ref{fig:bh_growth} (top panel) shows that across all black hole masses, Compton heating alone cannot prevent thermal instabilities from developing in a steady-state accretion flow ($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).
-Thus, if the stellar population is sufficiently old (or the star formation sufficiently intermittent) then nuclear gas could undergo cyclic oscillations of thermal instability and high accretion rates, followed by quiescent periods once gas has been consumed and/or AGN feedback becomes effective.
-Such cycles are proposed to occur on large scales and long timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea supported, e.g.
-, by GALEX observations showing that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
-If such cyclic behavior also occurs on small, parsec scales (e.g.) then the large scatter in the accretion rates and hence X-ray luminosities shown in Fig \ref{fig:Miller} could also be understood by the wide range of gas masses experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
-In support of this possibility, we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable.
-Past studies have found that core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
+Figure \ref{fig:bh_growth} (top panel) shows that across all black
+hole masses, Compton heating alone cannot prevent thermal
+instabilities from developing in a steady-state accretion flow
+($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).  Thus, if the stellar
+population is sufficiently old (or the star formation sufficiently
+intermittent) then nuclear gas could undergo cyclic oscillations of
+thermal instability and high accretion rates, followed by quiescent
+periods once gas has been consumed and/or AGN feedback becomes
+effective.  Such cycles are proposed to occur on large scales and long
+timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea
+supported, e.g. , by GALEX observations showing that a small fraction
+of early-type galaxies in the local universe have undergone recent ($<
+1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).  If such
+cyclic behavior also occurs on small, parsec scales (e.g.) then the
+large scatter in the accretion rates and hence X-ray luminosities
+shown in Fig \ref{fig:Miller} could also be understood by the wide
+range of gas masses experienced over the course of a cyclic episode
+between instabilities and periodic nuclear outbursts
+(e.g.~\citealt{Ciotti+10}).  In support of this possibility, we find
+that core galaxies are more likely to possess higher accretion rates
+and potentially be thermally unstable.  Past studies have found that
+core galaxies show a wide range of nuclear radio and X-ray
+luminosities (suggesting cyclic accretion episodes), while cusp
+galaxies are confined below a threshold (e.g., \citealt{Bender+89,
+  Pellegrini99, Capetti&Balmaverde05}), consistent with
+thermally-stable, steady-state picture.
 

### 2015-03-05 windheat.tex
Formatting

--- 2015-03-03 windheat.tex
@@
 formation history would produce a bulge consistent with the
-$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
-A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.
-To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs.
-\ref{eq:MDotSFH} and \ref{eq:EDotSFH}.
+$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
+slight complication occurs for the largest mass halos, where much of
+the $z=0$ stellar mass has been acquired through accretion of
+satellite halos rather than {\it in situ} star formation.  To
+accomodate this, we use analytic fits for mass accretion histories
+$A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}. We
+assume that accreted systems will have the same star formation history
+as the host up until the moment of accretion. To find the total mass
+(energy) injection including the contributions of accreted stars we
+convolve the specific mass (energy) injection rate with the accretion
+history $A(t)$.  The total mass ($\Mdot'(t)$) and energy
+($\dot{E}'(t)$) rates will be given by
+
+\begin{align}
+\Mdot '(t)&=\Mdot(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\Mdot(t_{\rm acc})}
+{\int_{0}^{t_{\rm acc}} S(t_1) dt_1} {\rm dt_{ acc}}.\\
+\dot{E}'(t)&=\dot{E}(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\dot{E}(t_{\rm acc})}
+{\int_{0}^{t_{\rm acc}} S(t') dt_1} {\rm dt_{acc}}.
+\end{align}
+
+The corresponding wind heating parameter $v_w'$ and mass return
+parameter, $\eta'$, will be given by
+
+\begin{align}
+\eta'&=\frac{\Mdot'(t)}{\int_0^t S(t_1) {\rm d}t_1+\int_0^t A(t_1) {\rm
+    d}t_1} \th\\
+v_w'&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
+\end{align}
 

### 2015-03-05 windheat.tex

--- 2015-03-05 windheat.tex
@@
   We estimate the stellar wind heating provided by the {\it average}
-star formation history of galaxies of a given $\Mbh$ using the results
-of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
-star formation histories in \citet{MosterNaab+:2013a} are in terms of
-halo mass. For a given $\Mbh$ we assign the halo mass whose star
+  star formation history of galaxies of a given $\Mbh$ using the
+  results of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
+  star formation histories in \citet{MosterNaab+:2013a} are in terms
+  of halo mass. For a given $\Mbh$ we assign the halo mass whose star
   formation history would produce a bulge consistent with the
@@
   satellite halos rather than {\it in situ} star formation.  To
-accomodate this, we incorporate analytic fits for mass accretion histories, taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, assuming that the age distribution of the accreted stars is equal to the age distribution of those formed {\it in situ}.
-This assumption may be conservative if the primary galaxy's accretion history is dominated by minor mergers with younger stellar populations.
-On the other hand, the dynamical friction inspiral time for small satellite galaxies is quite long, generally much greater than the $\sim 10^7~{\rm yr}$ for which young stars can dominate the heating budget.
+  accomodate this, we incorporate analytic fits for mass accretion
+  histories, taken from \citet[eqs.~21-23]{MosterNaab+:2013a},
+  assuming that the age distribution of the accreted stars is equal to
+  the age distribution of those formed {\it in situ}.  This assumption
+  may be conservative if the primary galaxy's accretion history is
+  dominated by minor mergers with younger stellar populations.  On the
+  other hand, the dynamical friction inspiral time for small satellite
+  galaxies is quite long, generally much greater than the $\sim
+  10^7~{\rm yr}$ for which young stars can dominate the heating
+  budget.  To find the total mass ($\Mdot'(t)$) and energy
+  ($\dot{E}'(t)$) injection rates, including the contribution of
+  accreted stars, we add a convolution of the specific mass and
+  injection rates with the accretion history $A(t)$ to the mass and
+  energy injection rates from star formed in-situ.  Thus,
+
+\begin{align}
+\Mdot '(t)&=\Mdot(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\Mdot(t_{\rm acc})}
+{\int_{0}^{t_{\rm acc}} S(t_1) dt_1} {\rm dt_{ acc}}\\
+\dot{E}'(t)&=\dot{E}(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\dot{E}(t_{\rm acc})}
+{\int_{0}^{t_{\rm acc}} S(t') dt_1} {\rm dt_{acc}}.
+\end{align}
+
+The corresponding wind heating parameter $v_w'$ and mass return
+parameter, $\eta'$, will be given by
+
+\begin{align}
+\eta'&=\frac{\Mdot'(t)}{\int_0^t S(t_1) {\rm d}t_1+\int_0^t A(t_1) {\rm
+    d}t_1} \th\\
+v_w'&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
+\end{align}
 

### 2015-03-06 ms.tex
updating figures.

@@
 \includegraphics[width=\columnwidth]{rs_rIa.pdf}
-\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$ characterizing stellar mass
-  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
-  $\Mbh$, calculated for average star formation histories from
-  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).
-{\it Bottom panel:} Ratio of Ia radius to stagnation radius as a function of $\Mbh$.
-The Ia radius calculated from equation~\eqref{eq:rIa} based on convolving the average star formation histories with the SN Ia DTD.
-The stagnation radius is calculated from \eqref{eq:stag_simple} using the total heating rate for each $\Mbh$ shown in the top panel.
-}
+\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
+  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
+  function of black hole mass $\Mbh$, calculated for average star
+  formation histories from \citet{MosterNaab+:2013a} (see
+  Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
+  of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
+  radius calculated from equation~\eqref{eq:rIa} based on convolving
+  the average star formation histories with the SN Ia DTD.  The
+  stagnation radius is calculated from \eqref{eq:stag_simple} using
+  the total heating rate for each $\Mbh$ shown in the top panel. }
 \end{figure}
@@
 \citealt{Ho:2009a}), while the right panel luminosities are calculated
-instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm
+instead assuming an efficiency of $\epsilon_X= 10 \dot{M}/\dot{M}_{\rm
   edd}$ that depends on the Eddington ratio as predicted by some
@@
 due to variations in $\dot{M}$ is exacerbated by the expectation that
-$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
+$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
+  AG Challenge: Scatter in L_X is similar for cores and cusps in Perllegrini}.
 

### 2015-03-06 ms.tex
caption

@@
 \includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing to the total heating rate of the CNM, $\vwO$ ({\it black}), including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
-Each heating source varies with black hole mass $\Mbh$ calculated for average star formation histories from
-  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:} The
-  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
-  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.
-Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.
-{\bf BDM: remove the red - its tacky and will vary based on core/cusp.
-Draw a dashed line across at heating ratio of 1.
-change y axis labels!
-move stars label in top panel}}
+\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
+  to the total heating rate of the CNM, $\vwO$ ({\it black}),
+  including stellar wind heating ({\it orange}), Ia supernovae ({\it
+    green}), millisecond pulsars ({\it blue}), and compton heating
+  ({\it pink}).  Each heating source varies with black hole mass
+  $\Mbh$ calculated for average star formation histories from
+  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
+  details).  {\it Middle Panel:} The ratio of the total heating rate
+  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
+  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
+  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
+  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
+  $\Mbh$, calculated for average star formation histories from and the
+  ratio of Ia radius to stagnation radius as a function of $\Mbh$.
+  The Ia radius calculated from equation~\eqref{eq:rIa} based on
+  convolving the average star formation histories with the SN Ia DTD.
+  The stagnation radius is calculated from \eqref{eq:stag_simple}
+  using the total heating rate for each $\Mbh$ shown in the top panel
+  assuming a cusp galaxy ($\Gamma=0.8$).}
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{eta.pdf}
-\includegraphics[width=\columnwidth]{rs_rIa.pdf}
-\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
-  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
-  function of black hole mass $\Mbh$, calculated for average star
-  formation histories from \citet{MosterNaab+:2013a} (see
-  Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
-  of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
-  radius calculated from equation~\eqref{eq:rIa} based on convolving
-  the average star formation histories with the SN Ia DTD.  The
-  stagnation radius is calculated from \eqref{eq:stag_simple} using
-  the total heating rate for each $\Mbh$ shown in the top panel. }
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{eta.pdf}
+% \includegraphics[width=\columnwidth]{rs_rIa.pdf}
+% \caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
+%   characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
+%   function of black hole mass $\Mbh$, calculated for average star
+%   formation histories from \citet{MosterNaab+:2013a} (see
+%   Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
+%   of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
+%   radius calculated from equation~\eqref{eq:rIa} based on convolving
+%   the average star formation histories with the SN Ia DTD.  The
+%   stagnation radius is calculated from \eqref{eq:stag_simple} using
+%   the total heating rate for each $\Mbh$ shown in the top panel. }
+% \end{figure}
 
@@
 $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
-  AG Challenge: Scatter in L_X is similar for cores and cusps in Perllegrini}.
+  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
 

### 2015-03-06 ms.tex
abstract work

--- 2015-03-05 ms.tex
@@
 We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
-The nuclear X-ray luminosities of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
+The nuclear X-ray luminosities, $L_{X}$, of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
+However, some fraction of galaxies may be recovering from a previous state thermal instability, either locally near the sphere of influence or as a part of much longer-term accretion events on galactic scales.
 The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.
 The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
-We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of circumnuclear environments encountered by the jetted outflows from tidal disruption events.
+Our results have implications for topics ranging from the physical motivation for extrapolating the measured $L_{\rm X}-M_{\bullet}$ correlation to constrain the occupation fraction of SMBHs in low mass galaxies, to the diversity of circumnuclear media densities encountered by relativistic jets from tidal disruption events.
 \end{abstract}

### 2015-03-06 ms.tex
added to definitions table

@@
 nominal Bondi radius).  In the case of sufficiently weak heating,
-however, no stagnation radius may exist at all, i.e. the entire ISM of
+however, no stagnation radius may exist at all, i.e. in principle the entire ISM of
 the galaxy is feeding the SMBH.  Another goal of this work is to
@@
 Table \ref{table:definitions} provides the definitions of commonly used variables.
-Appendix \ref{app:rs} provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in detail.
+Appendix \ref{app:rs} provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in greater detail.
 
@@
 $r_{\rm b}$ & outer break radius of stellar density profile \\  
+$\rho_{\star}(r)$ & 3D radial stellar density profile \\
+$\rho(r)$ & gas density of CNM \\
+$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
+$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
+$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
+$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
+$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
+$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
+$\sigma(r)$ & stellar velocity dispersion \\
+$\dot{M}$ & mass accretion rate \\
+$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
+$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
+$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
+$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\
 \hline

### 2015-03-06 ms.tex
random fixes

--- 2015-03-06 ms.tex
@@
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
+$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
+$\rho_{\star}(r)$ & 3D radial stellar density profile \\
+$\rho(r)$ & gas density of CNM \\
+$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
+$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
+$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
+$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
+$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
+$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
+$\sigma(r)$ & stellar velocity dispersion \\
+$\dot{M}$ & mass accretion rate \\
+$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
+$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
+$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
+$t_{\rm h}$ & Hubble timescale \\
 \hline
@@
 \end{align}
-The use of equation (\ref{eq:Msigma}) is questionable for low mass black holes (e.g., \citealt{Greene&Ho07}), but our results are not overly sensitive to this assumption.
+Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of a better alternative.
 
@@
 time-independent model.
-A main goal of this work is to use solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
+A main goal of this work is to use solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:instability}$).
 
@@
 Also note that our solutions can be scaled to any value of the mass input parameter, $\eta$, since the mass and energy source terms scale linearly with $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be specified when cooling or thermal conduction are included, since these scale as gas density {\it squared}.
-
-We assess the accuracy of our numerical solutions by checking that mass is conserved across the grid, in addition to the integral constraint on the energy (Bernoulli integral).
-Mass and energy are conserved to $\lesssim
-40$ per cent for all solutions presented in this paper.  {\bf BDM:
-  more details...}
+We check the accuracy of our numerical solutions by confirming that mass is conserved across the grid, in addition to the integral constraint on the energy (Bernoulli integral).
 
@@
 
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
+To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2\mu )/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
 \begin{align}
@@
   \subsection{Angular Momentum}
-  \label{sec:ang}
+  \label{sec:rotation}
 
@@
 This suggests that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
-To first order we are thus justifying in neglecting its effects on our quantities such as the mass accretion rate.
+We are thus justifying in neglecting the effects of rotation in calculating the mass accretion rate.
 

### 2015-03-06 ms.tex
kinetic heating section

@@
 the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
-h}$).  On the other hand, equation (\ref{eq:rIars}) may underestimate
-the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
-substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
-if the heating rate excluding SN Ia is less than this.
+h}$).
+
+%On the other hand, equation (\ref{eq:rIars}) may underestimate
+%the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
+%substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
+%if the heating rate excluding SN Ia is less than this.
 
@@
 SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between subsequent supernovae, stars release a
+low mass galaxies.  Between successive supernovae, stars release a
 gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
@@
 
-For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
-to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
-Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
-However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
-Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
+As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.
+However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating, we defer a more detailed discussion of the possible role of kinetic feedback to $\S\ref{sec:heating}$.
 
@@
 (Refs).
+
+For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
+to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
+Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
+However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
+Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
 

### 2015-03-06 ms.tex
more random errors

@@
 The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
-The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
+The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
 SN Ia heating depends also on a convolution of the DTD (eq.
@@
 We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
-Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
+Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
 Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.

### 2015-03-06 ms.tex
10th time through intro

@@
 here is whether SMBHs grow primarily by accreting gas fed in directly
-from large scales, or whether significant growth results also from
-internal, secular processes such as local stellar mass loss.
-
-Obtaining a better undersatnding of the physical mechanisms
-responsible for accretion onto quiescent SMBHs would have implications
-for observational constraints on the occupation fraction of SMBHs in
+from large scales (galactic or extra-galactic), or whether significant growth results also from
+internal, secular processes such as local stellar mass loss in the nuclear region.
+
+Obtaining a better understanding of the mechanisms regulating accretion onto quiescent SMBHs would have implications
+for a variety of observats, including constraints on the occupation fraction of SMBHs in
 low mass galaxies, and the potential existence of intermediate mass
-black holes.  \citet{Miller+15} combine the average correlation
-between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample
+black holes.  \citet{Miller+15} use the average correlation
+between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$, of a sample
 of elliptical galaxies to infer tentative evidence for a SMBH
@@
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the detection threshold, despite the potential that rather different
+the detection threshold, a potentially worrisome assumption if different
 physical processes control the accretion rates onto the lowest mass

### 2015-03-06 ms.tex
fixing the unfixable

@@
 \begin{cases}
-\rho_\star(\rsoi) \left(r/\rsoi\right)^{-1-\Gamma} & r \leq r_b\\
-\rho_\star(r_b) \left(r/r_b\right)^{-1-\beta} & r > r_b,
+\rho_\star|_{\rsoi} \left(r/\rsoi\right)^{-1-\Gamma} & r \leq r_b\\
+\rho_\star|_{r_b} \left(r/r_b\right)^{-1-\beta} & r > r_b,
 \label{eq:rhostar}
@@
 \end{align}
-where $\rho_\star(\rsoi)$ is the stellar density at the radius of the black hole sphere of influence (soi), 
+where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (soi), 
 \be
@@
 To isolate the physics of interest, our baseline calculations neglects three potentially important effects: heat conduction, radiative cooling, and rotation.
-Our justification for neglecting rotation will be discussed further in $\S\ref{sec:rotation}$.
 Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
@@
 inflow on small radial scales and a possible supersonic outflow on large scales.
-Also note that our solutions can be scaled to any value of the mass input parameter, $\eta$, since the mass and energy source terms scale linearly with $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be specified when cooling or thermal conduction are included, since these scale as gas density {\it squared}.
+Also note that our solutions can be scaled to any value of the mass input parameter, $\eta$, since the mass and energy source terms scale linearly with $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be specified when cooling or thermal conduction are included, since these scale as gas density to a different power.
 We check the accuracy of our numerical solutions by confirming that mass is conserved across the grid, in addition to the integral constraint on the energy (Bernoulli integral).
@@
 This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
-{\bf BDM: all analytic expressions have to be updated in core case to reflect this larger rs}
 
@@
 Thermal stability ($\dot{q}_{\rm heat} > |\dot{q}_{\rm rad}|$; $t_{\rm
-  cool} > t_{\rm ff}$) at the stagnation radius thus requires a
+  cool} > t_{\rm ff}$) near the stagnation radius thus requires a
 critical minimum heating rate
@@
 The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
-However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to very large radii, or may not exist at all, resulting in much higher gas densities and inevitable cooling instability.
+However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to very large radii, or may not exist at all (see also Fig.~\ref{fig:stag}), resulting in much higher gas densities and inevitable cooling instability.
 %Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
@@
 \ee
-where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, as satisfied for thermally-stable solutions of interest.
-
-\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales less that 10 per cent of the galaxy half-light radius and that $\lambda_R$ is a decreasing function of $R$.
-From equation (\ref{eq:rcirc}) we conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, a location well inside the inner sonic point of the flow (typically located at $\sim 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).
-This suggests that angular momentum is only becomes important for thermally stable flows in a region that is causally disconnected from the rest of the flow.
-We are thus justifying in neglecting the effects of rotation in calculating the mass accretion rate.
+where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied for the thermally-stable solutions of interest.
+
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy half-light radius and that $\lambda_R$ is with $R$ interior to this point.
+From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well inside the inner sonic point of the flow (typically located at $\sim 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).
+Angular momentum should only become dynamically important for thermally stable flows in a region that is causally disconnected from the outer part of the flow where the mass accretion rate is determined.
 
@@
 
-Our numerical results, summarized in Table \ref{table:models} and Figure XXX, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
+Our numerical results, summarized in Table \ref{table:models}, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
 Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.

### 2015-03-06 ms.tex
fixing the unfixable2

@@
 Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
-\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
+\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T),
+\label{eq:qdotcond}
+ \ee
 where $\kappa_{\rm
@@
 Our analytic derviations neglect the effects of heat conduction, an assumption we now check.
-The ratio of the magnitude of the conductive heating rate to the external heating rate at the stagnation radius is given by
+The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
 \begin{align}

### 2015-03-06 ms.tex

@@
 \includegraphics[width=\columnwidth]{vwSources.pdf}
-\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing to the total heating rate of the CNM, $\vwO$ ({\it black}), including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
-Each heating source varies with black hole mass $\Mbh$ calculated for average star formation histories from
-  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:} The
-  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
-  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.
-Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.
-{\bf BDM: remove the red - its tacky and will vary based on core/cusp.
-Draw a dashed line across at heating ratio of 1.
-change y axis labels!
-move stars label in top panel}}
+\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
+  to the total heating rate of the CNM, $\vwO$ ({\it black}),
+  including stellar wind heating ({\it orange}), Ia supernovae ({\it
+    green}), millisecond pulsars ({\it blue}), and compton heating
+  ({\it pink}).  Each heating source varies with black hole mass
+  $\Mbh$ calculated for average star formation histories from
+  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
+  details).  {\it Middle Panel:} The ratio of the total heating rate
+  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
+  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
+  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
+  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
+  $\Mbh$, calculated for average star formation histories from and the
+  ratio of Ia radius to stagnation radius as a function of $\Mbh$.
+  The Ia radius calculated from equation~\eqref{eq:rIa} based on
+  convolving the average star formation histories with the SN Ia DTD.
+  The stagnation radius is calculated from \eqref{eq:stag_simple}
+  using the total heating rate for each $\Mbh$ shown in the top panel
+  assuming a cusp galaxy ($\Gamma=0.8$).}
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{eta.pdf}
-\includegraphics[width=\columnwidth]{rs_rIa.pdf}
-\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$ characterizing stellar mass
-  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
-  $\Mbh$, calculated for average star formation histories from
-  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).
-{\it Bottom panel:} Ratio of Ia radius to stagnation radius as a function of $\Mbh$.
-The Ia radius calculated from equation~\eqref{eq:rIa} based on convolving the average star formation histories with the SN Ia DTD.
-The stagnation radius is calculated from \eqref{eq:stag_simple} using the total heating rate for each $\Mbh$ shown in the top panel.
-}
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{eta.pdf}
+% \includegraphics[width=\columnwidth]{rs_rIa.pdf}
+% \caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
+%   characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
+%   function of black hole mass $\Mbh$, calculated for average star
+%   formation histories from \citet{MosterNaab+:2013a} (see
+%   Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
+%   of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
+%   radius calculated from equation~\eqref{eq:rIa} based on convolving
+%   the average star formation histories with the SN Ia DTD.  The
+%   stagnation radius is calculated from \eqref{eq:stag_simple} using
+%   the total heating rate for each $\Mbh$ shown in the top panel. }
+% \end{figure}
 
@@
 due to variations in $\dot{M}$ is exacerbated by the expectation that
-$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
+$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
+  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
 

### 2015-03-06 ms.tex
Undoing damage

@@
 \end{eqnarray}
-{\bf AG: missing a minus n here...}
-where for the numerical estimate we adopt values of $n \approx 1$ and $n \approx 0.5$ for core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies, respectively, so chosen to match the results of our numerical calculations (Fig.~\ref{fig:stag}).
-This expression is similar to that obtained by \citet{Volonteri+11} on more heuristic grounds (their eq.~6).
-
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not exist at all, formally implying that the entire ISM of the galaxy is accreting.
-This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy $\sim \sigma^{2}$.
+where we have used equation~\eqref{eq:densSlope} to estimate
+$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
+core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
+expression is similar to that obtained by \citet{Volonteri+11} on more
+heuristic grounds (their eq.~6).
+
+In the opposite limit of weak heating ($v_{w} \ll \sigma$), the
+stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not
+exist at all, formally implying that the entire ISM of the galaxy is
+accreting.  This result makes intuitive sense: gas is supplied to the
+nuclear by stars which are gravitationally bound to the black hole, so
+outflows are possible only if the specific heating rate $\sim
+v_{w}^{2}$ significantly exceeds the specific gravitational binding
+energy $\sim \sigma^{2}$.
 
@@
 \end{align}
-where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs}) for the gas and stellar densities at the stagnation radius, respectively.
-We have approximated the cooling function for $T < 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}$ assuming solar metallicity gas (\citealt{Draine:2011a}; his Fig.
-34.1).
-
-To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2\mu )/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality
+
+where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs})
+for the gas and stellar densities at the stagnation radius,
+respectively.  We have approximated the cooling function for $T <
+2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
+  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ assuming solar
+metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).
+
+To within a constant of order unity, equation (\ref{eq:cooling2}) also
+equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n
+kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
+stagnation radius, as can be derived using the equality
+
 \begin{align}
@@
   \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
-    $r_{s}$ in units of the sphere of influence radius $r_{\rm
-      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
-    function of the ratio of the effective wind heating rate $v_{w}$
-    to the stellar velocity dispersion $\sigma$.  Green, orange, and
-    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
-    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
-    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
-    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively. }
+    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
+    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
+    the ratio of the effective wind heating rate $v_{w}$ to the
+    stellar velocity dispersion $\sigma$.  Green, orange, and blue
+    symbols correspond to different values of $v_{w} =$ 300, 600, and
+    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
+    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
+    ($\Gamma = 0.1$). The black curves correspond to the analytic
+    prediction from equation (\ref{eq:rs2main}), with solid and dashed
+    curves calculated for parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
+    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
 \end{figure}
@@
 for an advective accretion flow expected to produce high $T_{\rm C}$
-emission (e.g.~\citealt{Narayan&Yi95}).
-We caveat that, unlike stellar wind heating, Compton heating depends on radius, scaling as $v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto r^{(\Gamma-n-1)/2}$, i.e.
-$\propto r^{-0.6}$ and $\propto r^{-0.7}$ for core ($\Gamma = 0.8$; n = 1) and cusp ($\Gamma = 0.1$; n = 0.5) galaxies, respectively.
-The assumption of our model that the heating parameter be constant with radius is not satisfied, but this radial variation is sufficiently weak that it should not significantly alter our conclusions.
+emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
+stellar wind heating, Compton heating depends on radius, scaling as
+$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
+r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.75}$
+for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
+$\densSlope \simeq 0.6$) galaxies, respectively.  The assumption of our model that the heating
+parameter be constant with radius is not satisfied, but this radial
+variation is sufficiently weak that it should not significantly alter
+our conclusions.
 
@@
 
-A single burst of star formation does not describe the typical star formation history of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the gas heating budget.
+A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
+smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
 Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
@@
 MSP heating is again found to be negligible for all black hole masses.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
-Only for the most massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack of young stellar populations significantly reduce the role of stellar wind heating.
-%Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
-Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across all black hole masses}.
-{\bf NCS: deleted a sentence referring to old results on thermal instability - it is now correct to say we are thermally stable everywhere, yes?}
-
-Realistic variations (``burstiness") in the star formation history will often result in lower heating rates.
-Figure \ref{NickPlot2} shows the heating rate as a function of average black hole mass for non-fiducial cases in which the current ($z = 0$) star formation is suppressed by a factor $\zeta$ from its average $z = 0$ value, for a characteristic timescale $t_{\rm scale}$ (for details, see Appendix \ref{app:windheat}).
-For $t_{\rm scale} \lesssim 10^{7}$ yr, we see that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$ from its average value, even for huge drops in the star formation rate ($\zeta \sim 10^{-3}$).
-However, burstiness in the star formation history over longer timescales can suppress heating more significantly.
-When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an exception to this is in galactic nuclei with $M_\bullet \gtrsim 5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).
-Our use of average cosmic star formation histories is appropriate provided local variations are either on short timescales ($t_{\rm scale} \lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim 0.1$).
-If both of these conditions are violated, then the effective heating rates for all but the most massive galaxies (where Ia explosions dominate) will fall by a factor $\approx 5$ from our fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.
-
-{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}
+The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
+Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
+Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
+
+Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
+Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
+For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
+, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
+We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
+{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
 

### 2015-03-06 windheat.tex
updating figures.
Undoing damage

@@
 \end{align}
+
  \begin{figure}
   \includegraphics[width=\columnwidth]{NickPlot2.pdf}
-  \caption{\label{NickPlot2} Effective wind velocities for
-  nonstandard star formation histories.
-The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.
-Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.
-The purple curve shows a recent drop in the star formation rate, i.e.
-$t_{\rm scale}=10^6~{\rm yr}$.
-The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.
-Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\zeta = 0.001$, $\zeta = 0.1$, and $\zeta = 0.3$ of their halo-averaged values, respectively.
-}
+  \caption{\label{NickPlot2} Effective wind velocities for nonstandard
+    star formation histories.  The black curve shows, for reference,
+    $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other
+    colors show the effective wind velocities $\mathcal{V}_{\rm w}$
+    computed using convolved star formation histories
+    $\mathcal{S}(t)$.  The purple curve shows a recent drop in the
+    star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue
+    and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm
+      scale}=10^8~{\rm yr}$, respectively; longer scale times look
+    quite similar to the red curves.  Dashed, dotted, and dot-dashed
+    line styles show star formation rates that have declined to
+    fractions $\zeta = 0.001$, $\zeta = 0.1$, and $\zeta = 0.3$ of
+    their halo-averaged values, respectively. }
   \end{figure}
@@
     d}t_1} \th\\
-v_w'&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
+v_w'^2&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
 \end{align}
+;
 
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\zeta)\arctan(t/t_{\rm scale}) + \zeta \right).
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\epsilon)\arctan(t/t_{\rm scale}) + \epsilon \right).
 \end{equation}
-This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\mathcal{V}_{\rm w}$.
-In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\zeta$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
+This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.
+In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
 As we can see in Fig.
-\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\zeta \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
+\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
 

### 2015-03-06 ms.tex
Reincorporating some of nicks changes.

@@
 
-Realistic variations (``burstiness") in the star formation history will result in lower heating rates.
-Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).
-For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$...
-, while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.
-We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.
-{\bf BDM: augment/fix this - its just schematic till nick provides his figure}
+Realistic variations (``burstiness") in the star formation history
+will often result in lower heating rates.  Figure \ref{NickPlot2}
+shows the heating rate as a function of average black hole mass for
+non-fiducial cases in which the current ($z = 0$) star formation is
+suppressed by a factor $\zeta$ from its average $z = 0$ value, for a
+characteristic timescale $t_{\rm scale}$ (for details, see Appendix
+\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
+that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
+from its average value, even for huge drops in the star formation rate
+($\zeta \sim 10^{-3}$).  However, burstiness in the star formation
+history over longer timescales can suppress heating more
+significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
+  w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm
+  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
+smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
+exception to this is in galactic nuclei with $M_\bullet \gtrsim
+5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
+of average cosmic star formation histories is appropriate provided
+local variations are either on short timescales ($t_{\rm scale}
+\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim
+0.1$).  If both of these conditions are violated, then the effective
+heating rates for all but the most massive galaxies (where Ia
+explosions dominate) will fall by a factor $\approx 5$ from our
+fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.
+
+{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}
 

### 2015-03-06 ms.tex
recovery

@@
 where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (soi), 
-\be
+\begin{equation}
 \rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
 \label{eq:rsoi}
-\ee
+\end{equation}
 where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$ relationship of \citet{Gultekin+09},
@@
 Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
-\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T),
+\begin{equation}
+\dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T),
 \label{eq:qdotcond}
- \ee
+ \end{equation}
 where $\kappa_{\rm
@@
 Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
-\be
+\begin{equation}
 \dot{q}_{\rm rad} = -\Lambda(T)n^{2},
 \label{eq:qdot_rad}
-\ee
+\end{equation}
 where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
@@
 equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n
-kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
+kT/2 \mu)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
 stagnation radius, as can be derived using the equality
@@
 where $\sigma$ is the velocity dispersion and the brackets indicate a luminosity-weighted average.  The circularization radius of the accretion flow can be written in terms of $\lambda_R$ as
-\be
+\begin{equation}
 \frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
 \label{eq:rcirc}
-\ee
+\end{equation}
 where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied for the thermally-stable solutions of interest.
@@
 galaxies, respectively, calculated assuming $\densSlope = 1$ and
-$\densSlope= 0.5$, respectively.  Our analytic estimates are found to
+$\densSlope= 0.6$, respectively.  Our analytic estimates are found to
 provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
@@
 Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet escape timescale to the dynamical timescale $t_{\rm dyn} \sim r/\sigma$ is given by
-\be
+\begin{equation}
 \frac{t_{\rm jet}}{t_{\rm dyn}} \sim 7\times 10^{-3}M_{\bullet,8}^{0.13}\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{-1/3},
-\ee
+\end{equation}
 independent of $r$.
@@
 The total gas heating rate, 
-\be
+\begin{equation}
 \vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
 \label{eq:vtot}
-\ee
+\end{equation}
 includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
@@
 
-For low mass black holes, stellar heating is the most important on timescales of less than a few tens of millions of years.
-Compton heating comes to dominate at later times due to the higher accretion rates that accompany the overall decrease in the heating rate coupled with the persistently high mass loss rates of a relatively young stellar population.
-Compton heating dominates at all epochs for higher mass black holes, with stellar winds and Ia SN competing for the most significant non-AGN heating source.
-As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by dashed lines in Fig.~\ref{fig:vwSourcesImp}.
-The thermal stability is calculated neglecting Compton heating because the latter may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
-Thermally unstable flow is seen to be the norm in the single starburst case, except at very early times, $\tau_{\star} \lesssim 1-3 \times 10^7$ yr.
+For low mass black holes, stellar heating is the most important on
+timescales of less than a few tens of millions of years.  Compton
+heating comes to dominate at later times due to the higher accretion
+rates that accompany the overall decrease in the heating rate coupled
+with the persistently high mass loss rates of a relatively young
+stellar population.  Compton heating dominates at all epochs for
+higher mass black holes, with stellar winds and Ia SN competing for
+the most significant non-AGN heating source.  As the total heating
+rate declines with time, after some point the flow becomes thermally
+unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm
+  rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by
+dashed lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability is
+calculated neglecting Compton heating because the latter may not be
+capable of truly stabilizing the flow given its inability to respond
+instantaneously to local changes in the properties of the gas.
+Thermally unstable flow is seen to be the norm in the single starburst
+case, except at very early times, $\tau_{\star} \lesssim 1-3 \times
+10^7$ yr.
 
 \subsubsection{Continuous Star Formation History}
-
-A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
-smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget.
-Massive galaxies, on the other hand, will on average possess older stellar populations, with their heating rates dominated by SN Ia (on large radial scales) and SMBH feedback.
-We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
-Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ as a function of $M_{\bullet}$ (Fig.~\ref{fig:eta}; top panel).
-Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.
-
-Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.
-Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius (bottom panel).
-MSP heating is again found to be negligible for all black hole masses.
-The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.
-Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.
-Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
-Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.
+A single burst of star formation does not describe the typical star
+formation history of most galaxies.  Qualitatively, smaller galaxies
+will on average have more recent star formation, resulting in
+energetic young stellar winds and supernovae which dominate the gas
+heating budget.  Massive galaxies, on the other hand, will on average
+possess older stellar populations, with their heating rates dominated
+by SN Ia (on large radial scales) and SMBH feedback.  We estimate the
+average value of $\vwO$ as a function of SMBH mass for each heating
+source by calculating its value using the average cosmic star
+formation histories of \citet{MosterNaab+:2013a}.  Appendix
+\ref{app:windheat} describes how the average star formation history is
+used to determine the stellar wind heating $v_{\rm w}^{\star}$ and
+mass return parameter $\eta$ as a function of $M_{\bullet}$
+(Fig.~\ref{fig:eta}; top panel).  Star formation histories are also
+convolved with the Ia DTD distribution to determine the SN Ia heating.
+
+Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
+source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
+the average star formation history of galaxies containing a given
+black hole mass.  Again, Ia heating is suppressed in low mass galaxies
+because the Ia radius exceeds the nominal stagnation radius (bottom
+panel).  MSP heating is again found to be negligible for all black
+hole masses.  The younger stellar populations characterizing galaxies
+with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
+and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
+$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
+massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
+of young stellar populations significantly reduce the role of stellar
+wind
+heating.
+%Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+Strikingly, {\it we find that galactic nuclei experiencing the same
+  average star formation history as their host galaxies produce
+  thermally stable flows across all black hole masses}.  {\bf NCS:
+  deleted a sentence referring to old results on thermal instability -
+  it is now correct to say we are thermally stable everywhere, yes? AG
+ though note our kludgy way of including Ias if rs is inside of rIa.}
 

### 2015-03-06 ms.tex
Updating scatter relationship

@@
 (\ref{eq:stag_analytic}) simplifies to
-\begin{eqnarray}
+\begin{align}
   &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
@@
   \label{eq:stag_simple}
-\end{eqnarray}
+\end{align}
 where we have used equation~\eqref{eq:densSlope} to estimate
@@
   edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
-least two effects: (1) the order of magnitude difference between
-$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
-(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
-to the variation in the Nuker stellar density profile $\Gamma$ at
-fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
+least two effects: (1) the strong sensitivity of the accretion rate
 to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
@@
 combination with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (Fig.~NICK).  The
+intermittency in the star formation history (Fig.~NICK) (2) The
+scatter introduced in using scaling relationships ($\Mbh-\sigma$) 
+and ($\Mbh-L_{\rm bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.  The
 combination of (1) and (2) is capable of explaining much of the
@@
 due to variations in $\dot{M}$ is exacerbated by the expectation that
-$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
+$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows. At a
+wind heating parameter there is an order of magnitude difference between
+$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
+(Fig.~\ref{fig:bh_growth}) which could also lead to scatter of $\dot{M}$ due
+to the variation in the Nuker stellar density profile $\Gamma$ at
+fixed $M_{\bullet}$. However, the \citet{Pellegrini10} find that the
+scatter in $L_X$ is similar if one just looks at core/cusp galaxies separately.
+
+{\bf
   AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.

### 2015-03-06 ms.tex
test
no test
Starting on conclusions.

@@
   edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
-least two effects: (1) the strong sensitivity of the accretion rate
-to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
+least two effects: (1) the strong sensitivity of the accretion rate to
+the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
 v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
@@
 combination with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (Fig.~NICK) (2) The
-scatter introduced in using scaling relationships ($\Mbh-\sigma$) 
-and ($\Mbh-L_{\rm bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.  The
-combination of (1) and (2) is capable of explaining much of the
-observed sample, especially considering that scatter in $L_{\rm X}$
-due to variations in $\dot{M}$ is exacerbated by the expectation that
-$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows. At a
-wind heating parameter there is an order of magnitude difference between
-$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
-(Fig.~\ref{fig:bh_growth}) which could also lead to scatter of $\dot{M}$ due
-to the variation in the Nuker stellar density profile $\Gamma$ at
-fixed $M_{\bullet}$. However, the \citet{Pellegrini10} find that the
-scatter in $L_X$ is similar if one just looks at core/cusp galaxies separately.
-
-{\bf
-  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
+intermittency in the star formation history (~\ref{fig:NickPlot2}) and
+(2) angular momentum of the infalling gas and consequentiallly the
+size of small scale outflows may vary from galaxy to galaxy at fixed
+$\Mbh$. The combination of (1) and (2) is capable of explaining much
+of the observed sample, especially considering that scatter in $L_{\rm
+  X}$ due to variations in $\dot{M}$ is exacerbated by the expectation
+that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient
+flows. At a wind heating parameter there is an order of magnitude
+difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$
+and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) which could also lead to
+scatter of $\dot{M}$ due to the variation in the Nuker stellar density
+profile $\Gamma$ at fixed $M_{\bullet}$. However, \citet{Pellegrini10}
+find that the scatter in $L_X$ is similar if one just looks at
+core/cusp galaxies separately. There could also be scatter introduced
+in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
+  bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.
 
@@
 
-  We have calculated steady-state models for circumnuclear medium of a
-  sample of early type galaxies, assuming that gas is supplied
-  entirely by stellar wind mass loss and heated by shocked stellar
-  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
-  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
-  with $\Mbh$. We may then compare our results with observed trends of
+We have calculated steady-state models for circumnuclear medium of
+early type galaxies, assuming that gas is supplied entirely by stellar
+wind mass loss and heated by shocked stellar winds, supernovae and
+black hole feedback. We may use these profiles to calculate an $\Mdot$
+onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$ with
+$\Mbh$. We may then compare our results with observed trends of
 nuclear x-ray luminosity. Our main conclusions may be summarized as
@@
   %lower vw except for very young stellar populations.
-  \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
-    $\alpha$ depends on the slope of the stellar density profile
-    ($\alpha\simeq0.5,1$ for cusp and core galaxies
-    respectively). {\bf AG-these explanations are prehistoric and need
-      to be modified. Actually this entire summary needs to be
-      revamped, but this can wait until we are closer to completion.}
-    One possible solution that the wind mass loss rate (i.e. $\eta$)
-    increases with $\Mbh$, as would be expected if low mass SMBH
-    preferentially hosted younger stellar populations. Another
-    possible explanation is that the effective heating rate of the CNM
-    $v_{w}$ decreases with decreasing SMBH mass. This could again be
-    due to an older stellar population, since $v_{w} \propto
-    \eta^{−1/2}$ for heating sources such as SN Ia and millisecond
-    pulsars.
+  \item We find that $\eddr \propto \Mbh^{\alpha}$ for
+    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, where the
+    value of $\alpha$ with $\alpha\simeq$ for galaxies following the
+    average star formation histories measured in cosmological
+    simulations \citep{MosterNaab+:2013a}. This is in tension
+    observations of nuclear X-ray luminosity which suggest that
+    $\eddr$ increases towards smaller $\Mbh$
+    \citep{Miller+15}. However, it is important to note that the
+    inflow rate on large scale (which we calculate) may differ from
+    the actual accretion rate as outflows could occur on small
+    scales. The outflow rate would depend on the angular momentum of
+    the infalling gas and thus the angular momentum of stars in the
+    nucleus. The in turn would vary systematically with $\Mbh$.
+  \item We expect within scatter in nuclear x-ray luminosities at
+    fixed $\Mbh$ from (1) stochastic variation in star formation
+    history from galay to galaxy (2) Variations in small scale outflow
+    rates due to variations between galactic nuclear angular momenta.
+    These variations alone could explain much of the 2-4 orders of
+    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
+    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.
+
+    Alternatively 
   \item We compare the $\Mdot$ for each of our solution to the one
@@
     few. Thus, use of the Bondi formula is a good approximation.
-  \item We compare our solutions for density and temperature to those
-    inferred from Chandra x-ray observations by \citet{AllenDunn+:2006a}
-    and \citet{RussellMcNamara+:2013a} for a handful of galaxies in
-    which our sample overlap with theirs. In general, we cannot match
-    the observed gas density slope on large scales. 
   \end{enumerate}

### 2015-03-06 ms.tex
more conclusion

@@
 limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
-separate ``thermally stable".  This possible dichotomy calls into
-question the use of simple extrapolations of power-law fits to the
-$L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
+separate ``thermally stable" population.  This possible dichotomy
+calls into question the use of simple extrapolations of power-law fits
+to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
 constrain the occupation fraction of black holes in low mass galaxies
@@
 
-Low-mass SMBHs in the local universe ($M_{\bullet} \lesssim 3\times
+Low-mass AGN in the local universe ($M_{\bullet} \lesssim 3\times
 10^{7}M_{\odot}$) are observed to be growing on a timescale comparable
@@
 
-\item{
-Do nuclear star clusters in other galaxies look like scaled up/down versions of the one in our own galaxy?
-If so this would imply a radial gradient in the average of the stellar population which would imply a heating which would be dependent on radius.
-}
+\item{ Do nuclear star clusters in other galaxies look like scaled
+    up/down versions of the one in our own galaxy? If so this would
+    imply a radial gradient in the average of the stellar population
+    which would imply a heating which would be dependent on radius.  }
 
@@
 
-    Alternatively 
+    It is also possible that many of the galaxies in the
+    \citet{Miller+15} are accreting in a non-steady fashion and this
+    scatter arises from cyclic variation in accretion rate. In fact it
+    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
+    \Msun$ coexists with a population of smaller, steadily accreting
+    black holes (e.g. the upper limits in \citet{Miller+15}.  This
+    calls into question the use of simple extrapolations of power-law
+    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
+    to constrain the occupation fraction of black holes in low mass
+    galaxies (\citealt{Miller+15}).
+  \item Low mass AGN have growth times comparable to the Hubble
+    time. We have show that this would require accretion rates not
+    consistent with steady state thermally stable accretion of stellar
+    wind material.
   \item We compare the $\Mdot$ for each of our solution to the one

### 2015-03-07 ms.tex
comments...
Adjusting table

@@
 \caption{Definitions of commonly used variables}
-\begin{tabular}{lc}
+\begin{tabular}{ll}
 \hline
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
  & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
-  $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
-  ... & 600  & 100 & &$ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
-   ...    & 1200  & 100 & &$ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
-  $    10^{ 7 }$ & 300 & 100 & & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
- ...    & ...   & 25 & &$ 7.8 \times 10^{ -5 }$ & 17 \\
- ...      & ...   & 50 & &$ 7.9 \times 10^{ -5 }$ & 12 \\
-   ...    & ...   & 200 & &$ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
-   ...    & ...   & 400 & &$ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
-   ...     & 600  & 100 && $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
-   ...     & 1200  & 100 && $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
-  $    10^{ 8 }$ & 300 & 100 & & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
-...     & ...  & 25 & &$ 1.9 \times 10^{ -4 }$ & 12 \\
-   ...     & ...  & 50 & &$ 3.3 \times 10^{ -4 }$ &
-  $\mathbf{4.6}$ \\
-     ...$^{\dagger}$ & ...  & 50& & $ 9.1 \times 10^{ -4 }$ &
-  $\mathbf{5.6}$ \\
-   ... & ... & 200 && $ 1.4 \times 10^{ -3 }$ &
-  $\mathbf{0.43}$ \\
-   ...     & 600  & 100 && $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
-   ...     & 1200  & 100 && $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
+ $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 6.4 \times 10^{ -5 }$ & 17 \\
+... & 600 & 0.8 & 100 & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
+... & 1200 & 0.8 & 100 & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
+$    10^{ 7 }$ & 300 & 0.8 & 25 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
+... & ... & 0.8 & 50 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
+... & ... & 0.8 & 100 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
+... & ... & 0.8 & 200 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
+... & ... & 0.8 & 400 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
+... & 600 & 0.8 & 25 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
+... & ... & 0.8 & 100 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
+... & 1200 & 0.8 & 100 & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
+$    10^{ 8 }$ & 300 & 0.8 & 25 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
+... & ... & 0.8 & 50 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
+... & ... & 0.8 & 100 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
+... & ... & 0.8 & 200 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1 \times
+  10^{ -3 }}$ \\
+$    10^{ 8 }$ & 450 & 0.8 & 100 & $ 4.4 \times 10^{ -4 }$ & 4 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$ \\
+... & 600 & 0.8 & 25 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2
+}$ \\
+... & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 76 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 70 \\
+... & ... & 0.8 & 200 & $ 1.5 \times 10^{ -4 }$ & 67 \\
+... & ... & 0.8 & 400 & $ 1.6 \times 10^{ -4 }$ & 58 \\
+... & 1200 & 0.8 & 100 & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
   \hline
  & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
-$    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
-  ...  & 600  & 50 & &$ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
-  ...  & 1200  & 100 && $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
-  $    10^{ 7 }$ & 1200  & 100& & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
-  ...  & 600  & 50 && $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
-  ...  & ...  & 25 & &$ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
-$10^{8}$  & 300  & 50 & & $ 6.0 \times 10^{ -5 }$ & 56 \\
-  ...  & 600  & 100 & &$ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
-  ...  &  ...  & 25 && $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
-  ...  &  ...  & 50 && $ 6.0 \times 10^{ -5 }$ & 56 \\
-... & 1200 & 100 && $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
-  ...  & ...  & 50 && $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
-  ...  &  ...  & 200 && $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
-  ...  &  ... & 400 && $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
+$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 8.2 \times 10^{ -6 }$ & 99 \\
+... & ... & 0.1 & 50 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
+... & 1200 & 0.1 & 25 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+... & ... & 0.1 & 50 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+... & ... & 0.1 & 100 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+$    10^{ 7 }$ & 600 & 0.1 & 25 & $ 4.3 \times 10^{ -5 }$ & 41 \\
+... & ... & 0.1 & 50 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
+... & 1200 & 0.1 & 25 & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
+... & ... & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
+... & ... & 0.1 & 100 & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
+$    10^{ 8 }$ & 600 & 0.1 & 25 & $ 1.1 \times 10^{ -4 }$ & 31 \\
+... & ... & 0.1 & 50 & $ 3.0 \times 10^{ -4 }$ & 3 \\
+... & ... & 0.1 & 100 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
+... & 1200 & 0.1 & 25 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 50 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 100 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 200 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
+... & ... & 0.1 & 400 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
   \hline
+
 \label{table:models}  
@@
 Eddington units, normalized to a stellar mass input parameter $\eta =
-0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
+0.2$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
 stagnation radius.  Thermally unstable solutions are shown in bold
@@
   it is now correct to say we are thermally stable everywhere, yes? AG
- though note our kludgy way of including Ias if rs is inside of rIa.}
+  though note our kludgy way of including Ias if rs is inside of
+  rIa. I also don't think it is fair to say that we obtain stability
+  for large Mbh as the heating parameter would become comparable to
+  the velocity dispersion.}
 
@@
 
-{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}
+{\bf NCS: is this reduced heating rate thermally unstable under
+  Aleksey's revised formula?  We should comment. AG: What revised
+  formula.}
 

### 2015-03-07 ms.tex
fixing the unfixable2

--- 2015-03-06 ms.tex
@@
 \author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
-  Columbia Astropysics Labratory, Columbia University, 550 West 120th
+  Columbia Astrophysics Labratory, Columbia University, 550 West 120th
   Street, New York, NY 10027}
@@
 We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
-The nuclear X-ray luminosities, $L_{X}$, of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.
-However, some fraction of galaxies may be recovering from a previous state thermal instability, either locally near the sphere of influence or as a part of much longer-term accretion events on galactic scales.
-The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.
-The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.
-Our results have implications for topics ranging from the physical motivation for extrapolating the measured $L_{\rm X}-M_{\bullet}$ correlation to constrain the occupation fraction of SMBHs in low mass galaxies, to the diversity of circumnuclear media densities encountered by relativistic jets from tidal disruption events.
+The measured nuclear X-ray luminosities, $L_{X}$, of a sample of quiescent black holes are combined with our results for $\dot{M}$ to conclude that early-type quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state (on scales of the sphere of influence), possibly between cycles of thermal instability on larger galactic scales.
+The maximum accretion rate of a thermally-stable flow is too low to explain the short growth times of low mass black holes in the local universe.
+The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger, galactic scales.
+Our results have implications for attempts to constrain the occupation fraction of SMBHs in low mass galaxies using the mean $L_{\rm X}-M_{\bullet}$ correlation, as well as to the diversity of circumnuclear media densities encountered by relativistic jets from tidal disruption events.
 \end{abstract}

### 2015-03-07 ms.tex
intro again

@@
 down-sizing' resulting from hierarchical structure growth (e.g,
-\citealt{Gallo+08}).  However, the physical processes involved in the
-growth of low mass blacks may be distinct from those operating at
-higher SMBH masses and accretion rates in quasars.  A key question
-here is whether SMBHs grow primarily by accreting gas fed in directly
-from large scales (galactic or extra-galactic), or whether significant growth results also from
+\citealt{Gallo+08}).  However, the physical processes involved in growing low mass blacks may be distinct from those operating at
+higher SMBH masses and accretion rates in quasars.  A key open question is whether SMBHs grow primarily by accreting gas fed in directly
+from galactic or extra-galactic scales, or whether significant growth results also from
 internal, secular processes such as local stellar mass loss in the nuclear region.
 
-Obtaining a better understanding of the mechanisms regulating accretion onto quiescent SMBHs would have implications
-for a variety of observats, including constraints on the occupation fraction of SMBHs in
-low mass galaxies, and the potential existence of intermediate mass
-black holes.  \citet{Miller+15} use the average correlation
-between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$, of a sample
-of elliptical galaxies to infer tentative evidence for a SMBH
+A better understanding of what mechanisms regulate accretion onto quiescent SMBHs would have implications
+for a variety of observations, such as constraints on the occupation fraction of SMBHs in
+low mass galaxies.
+\citet{Miller+15} use the average relationship between the nuclear X-ray luminosities, $L_{X}$, of a sample of elliptical galaxies and the black hole mass to infer tentative evidence for a SMBH
 occupation fraction less than unity in galaxies with stellar masses
@@
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the detection threshold, a potentially worrisome assumption if different
+the detection threshold, a potentially problematic assumption if different
 physical processes control the accretion rates onto the lowest mass
@@
 
-The CNM density also influences the emission from stellar tidal
+The gas density in galactic nuclei also influences the emission from stellar tidal
 disruption events (TDEs), such as the high energy transient {\it
   Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11},
-\citealt{Burrows+11}; \citealt{Zauderer+11}).  This event was powered
-by a transient relativistic jet, which produced synchrotron radio
+\citealt{Burrows+11}; \citealt{Zauderer+11}).  This transient event was powered
+by an impulsive relativistic jet, which produced synchrotron radio
 emission as the jet material was decelerated by shock interaction with
@@
 (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of J1644+57 showed that the CNM density was significantly
-lower than that measured surrounding Sgr A$^{\star}$
+modeling of J1644+57 showed that the CNM density was much lower than that measured surrounding Sgr A$^{\star}$
 (\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
@@
 producing substantially different radio emission than in J1644+57.
-Variations in the properties of the CNM could thus in principle help
+Variations in the properties of the CNM could help
 explain why most TDEs appear to be radio quiet
@@
 
-\citet{Ho:2009a} estimates the accretion rates onto a sample of
-early-type galaxies both by using X-ray observations to determine the
-Bondi accretion rate and using estimates for the mass loss rate of
+\citet{Ho:2009a} estimates the SMBH accretion rates in a sample of
+early-type galaxies using X-ray observations to determine the
+Bondi accretion rate and based on estimates for the mass loss rate of
 evolved stars.  Both methods lead to the conclusion that the available
@@
 low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative
-efficiency for thin disk accretion.  Several independent strains of
+efficiency for thin disk accretion.  Much
 evidence now suggest that low-luminosity AGN result from accretion
@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to a low efficiency for the gas
-inflowing on large scales ultimately reaching the SMBH
+(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaching the viscinity of the SMBH
 (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
@@
 (\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works focusing on modeling individual galaxies, here
-we systematically analyze the properties of the CNM across a sample of
-galaxies with a range of SMBH masses, stellar density profiles, and
+Unlike previous works, which focused primarily on modeling individual galaxies, here
+we systematically analyze the CNM properties across a range of galaxy properties, including different SMBH masses, stellar density profiles, and
 star formation histories (\citealt{WangMerritt:2004a}).
@@
 \citealt{Ciotti+10}).  A key finding of these works is the periodic
-development of cooling instabilities, which temporarily increase the
-gas accretion rate until black hole feedback becomes sufficiently
-important to shut off the flow and halt SMBH growth.  Here we instead
+development of cooling instabilities on galactic scales, which temporarily increase the
+gas accretion rate towards the nucleus until feedback becomes sufficiently effective to shut off the flow and halt SMBH growth.  Here we instead
 focus on time-independent models, neglecting radiative cooling.  This
@@
 show that $\rs$ can in many cases lie within a factor of few of the
-nominal Bondi radius).  In the case of sufficiently weak heating,
-however, no stagnation radius may exist at all, i.e. in principle the entire ISM of
-the galaxy is feeding the SMBH.  Another goal of this work is to
+nominal Bondi radius).  When heating is sufficiently weak, however, no stagnation radius may exist at all, i.e. the entire ISM of the galaxy is flowing towards the SMBH.  A key goal of this work is to
 assess under what conditions a stagnation radius exists, as this

### 2015-03-07 ms.tex
we dont believe you

@@
 \end{align}
-{\bf AG missing correction here for black hole velocity dispersion}
-where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$).  Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
+where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
+density power-law slope at $r = r_{\rm s}$ {\bf BDM: FIXXXX T equation!!}.  Empirically, we find that 
+\begin{align}
+\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
+\label{eq:densSlope}
+\end{align}
+
+Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
 \begin{align}
@@
 \label{eq:stag_analytic}
-\end{align}
-where $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
-density power-law slope at $r = r_{\rm s}$. We find that
-
-\begin{align}
-\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
-\label{eq:densSlope}
 \end{align}

### 2015-03-07 ms.tex
we dont believe you2

@@
 $t_{\rm h}$ & Hubble timescale \\
+$\nu$ & gas density power-law slope at the stagnation radius (eq.~[\ref{eq:densSlope}]) \\
 \hline
@@
 where the stagnation radius is assume to reside well inside the Nuker
-break radius.  Equation (\ref{eq:conduction}) shows that even in the
+break radius and for clarity we have not distinguished between cusp and core galaxies.  Equation (\ref{eq:conduction}) shows that even in the
 case of saturated conduction, the neglect of heat conduction results
@@
 analysis.  Numerical experiments including conductivity confirm this
-($\S\ref{sec:numerical}$). {\bf AG: If we make this statement then we
-  should be sure to include the numerical experiments. The original
-  formula was not correct for the saturated case. The numerical values
-also changed somewhat. I would appreciate it if someone could double
-check this. Also note that there is a weak core/cusp dependence in the
-saturated case which I have chosen not to include.}
+($\S\ref{sec:numerical}$).
 
@@
 galaxies, respectively, calculated assuming $\densSlope = 1$ and
-$\densSlope= 0.6$, respectively.  Our analytic estimates are found to
+$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).  Our analytic estimates are found to
 provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
@@
 
+In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked in Table \ref{table:models}.
+{\bf BDM: EXPAND!!!!
+Explain that they don't matter.}
+
 \section{Sources of Heating}
@@
 An additional uncertainty in the stellar wind heating rate results from the uncertain thermalization efficiency of massive stellar winds.
-We assume this efficiency to be unity, and assumption that is at least partially offset by our conservative assumption of neglecting energy input from core collapse supernovae, which contribute a comparable energy injection rate to massive stellar winds.
+We assume this efficiency to be unity, an optimistic assumption which is offset by our neglect of energy input from core collapse supernovae, which contribute an energy comparable to that from massive stellar winds.
 
@@
   \end{align}
-  where $\tau_{\star}$ is the time since star formation
-  (c.f.~\citealt{Scannapieco&Bildsten05}).
+  where $\tau_{\star}$ is the time since star formation.
 
@@
  \begin{cases}
-    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    8\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}  & {\rm core}\\
-    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    17\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74} &{\rm cusp}\\
@@
 \end{align}
-If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
+If $r_{\rm Ia} \gg r_{\rm s}$, then SN Ia heating can only be
 approximated as a steady heating source near the stagnation radius for
@@
 for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
-$\densSlope \simeq 0.6$) galaxies, respectively.  The assumption of our model that the heating
-parameter be constant with radius is not satisfied, but this radial
-variation is sufficiently weak that it should not significantly alter
+$\densSlope \simeq 0.6$) galaxies, respectively.  Our model's assumption that the heating
+parameter be radially constant is not satisfied, but this variation is sufficiently weak that it should not significantly alter
 our conclusions.
@@
 \end{align}
-{\bf AG: Note that I have included the bolometric correction for now.}
+{\bf AG: Note that I have included the bolometric correction for now.  BDM: are you doing everything consistently?}
 
@@
 As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.
-However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating, we defer a more detailed discussion of the possible role of kinetic feedback to $\S\ref{sec:heating}$.
+However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating (see $\S\ref{sec:heating}$ for further discussion).
 
@@
   $\Mbh$, calculated for average star formation histories from and the
-  ratio of Ia radius to stagnation radius as a function of $\Mbh$.
-  The Ia radius calculated from equation~\eqref{eq:rIa} based on
-  convolving the average star formation histories with the SN Ia DTD.
-  The stagnation radius is calculated from \eqref{eq:stag_simple}
-  using the total heating rate for each $\Mbh$ shown in the top panel
-  assuming a cusp galaxy ($\Gamma=0.8$).}
+  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
+  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
+  %convolving the average star formation histories with the SN Ia DTD.
+  %The stagnation radius is calculated from \eqref{eq:stag_simple}
+  %using the total heating rate for each $\Mbh$ shown in the top panel
+  %assuming a cusp galaxy ($\Gamma=0.8$).}
 \end{figure}
@@
 \end{equation}
-includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).
+includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback.
 The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
@@
 Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
-Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.
-
-For low mass black holes, stellar heating is the most important on
+Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown.
+
+For low-mass black holes, stellar winds are the most important source of heating on
 timescales of less than a few tens of millions of years.  Compton
 heating comes to dominate at later times due to the higher accretion
-rates that accompany the overall decrease in the heating rate coupled
-with the persistently high mass loss rates of a relatively young
+rates that accompany the overall decrease in the heating rate, coupled
+with the persistently high mass loss rates and gas densities associated with a relatively young
 stellar population.  Compton heating dominates at all epochs for
@@
 mass return parameter $\eta$ as a function of $M_{\bullet}$
-(Fig.~\ref{fig:eta}; top panel).  Star formation histories are also
+(Fig.~\ref{fig:vwSources}; top panel).  Star formation histories are also
 convolved with the Ia DTD distribution to determine the SN Ia heating.
@@
   average star formation history as their host galaxies produce
-  thermally stable flows across all black hole masses}.  {\bf NCS:
-  deleted a sentence referring to old results on thermal instability -
-  it is now correct to say we are thermally stable everywhere, yes? AG
-  though note our kludgy way of including Ias if rs is inside of
-  rIa. I also don't think it is fair to say that we obtain stability
-  for large Mbh as the heating parameter would become comparable to
-  the velocity dispersion.}
+  thermally stable flows across almost all black hole masses}.
+One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion and thermal stability for the average star formation history is marginal ($\S\ref{sec:mdot}$).
 
@@
 
-{\bf NCS: is this reduced heating rate thermally unstable under
-  Aleksey's revised formula?  We should comment. AG: What revised
-  formula.}
-
-% However, if Ia supernovae are included in the schematic way described
-% above, the flow again becomes thermally stable for $\Mbh \gtrsim
-% XXXX$.
-
-%Although, in principle the Ia contribution to the heating is
-%substantial, in practice Ia's occur too infrequently to be a steady
-%contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
-%r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
-%by itself would not be able to prevent cooling instability.
-
-% \begin{figure}
-% \includegraphics[width=\columnwidth]{cooling2.pdf}
-% \caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
-%   $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
-%   and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
-%   using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
-%   $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
-% \end{figure}
-
-% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
-% depends on the age of the stellar population $\tage$ and the SMB mass
-% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
-%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
-% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
-% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
-% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
-% infrequent, in which case main sequence stars ($v_{w}^{\star}
-% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
-% interest.\footnote{Although SN Ia will still occur surrounding low
-%   mass SMBHs, if they are infrequent interior to the radius where the
-%   accretion rate is being set, then they will not affect the flow near
-%   the SMBH at most epochs.}  For very young stellar populations
-% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
-% contributions from line driven winds from high mass main sequence
-% stars.
-
- %  \begin{figure}
-%     \includegraphics[width=\columnwidth]{vw-contour.eps}
-%     \caption{\label{fig:vweff} Combined heating rate $\vwO$ of the CNM
-% in the parameter space of SMBH mass $\Mbh$ and age of the stellar
-% population $t_{\star}$.  We assume that stellar winds contribute a
-% constant heating rate $100$ km/s. The contribution from SNe Ia is
-% calculated using equation (\ref{eq:vw_sne}), with thermalization
-% efficiency $\epsilon_{\rm Ia}=0.4$. The contribution from SNe Ia is
-% only added if the $r_s$ corresponding to the resulting $\vwO$ is
-% outside $\rIa$.  {\bf BDM: Correct for dependence of Ia heating on
-% time!  among other things}}%describe other cases here.
-%   \end{figure}
-
 \section{Implications and Discussion}
@@
 maximum accretion rate set by SN Ia is significantly higher and cannot
-prevent the development of thermally unstable flows,
+also prevent the development of thermally unstable flows,
 i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
@@
   \citet{MosterNaab+:2013a} (the black lines in
-  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
+  Figures~\ref{fig:vwSources}--see
   Appendix~\ref{app:windheat} for a detailed description).
@@
 combination with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (~\ref{fig:NickPlot2}) and
+intermittency in the star formation history (~\ref{NickPlot2}) and
 (2) angular momentum of the infalling gas and consequentiallly the
@@
 exceeds the one corresponding to the maximum thermally-stable
-accretion rate, $\dot{M}_{\rm TI}$ (yellow line).  Many of the upper
+accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
+
+Many of the upper
 limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a

### 2015-03-07 windheat.tex
Reincorporating some of nicks changes.
Starting on conclusions.
we dont believe you2

@@
   \includegraphics[width=\columnwidth]{NickPlot2.pdf}
-  \caption{\label{NickPlot2} Effective wind velocities for nonstandard
+  \caption{\label{fig:NickPlot2} Effective wind velocities for nonstandard
     star formation histories.  The black curve shows, for reference,
@@
   accomodate this, we incorporate analytic fits for mass accretion
-  histories, taken from \citet[eqs.~21-23]{MosterNaab+:2013a},
+  histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},
   assuming that the age distribution of the accreted stars is equal to
@@
   10^7~{\rm yr}$ for which young stars can dominate the heating
-  budget.  To find the total mass ($\Mdot'(t)$) and energy
+  budget.
+
+To find the total mass ($\Mdot'(t)$) and energy
   ($\dot{E}'(t)$) injection rates, including the contribution of
@@
     d}t_1} \th\\
-v_w'^2&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
+v_w'^2&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}.
 \end{align}
-;
 
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\epsilon)\arctan(t/t_{\rm scale}) + \epsilon \right).
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\zeta)\arctan(t/t_{\rm scale}) + \zeta \right).
 \end{equation}

### 2015-03-08 ms.tex
temperature equation and M-sigma reference

@@
 \begin{abstract}
-We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of nominally quiescent galaxies for a range of central black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.
-Mass is supplied to the circumnuclear medium by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.
-Analytic estimates are provided for the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of black hole mass and the gas heating efficiency, the latter of which is related to the star-formation history.
-We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.
-The measured nuclear X-ray luminosities, $L_{X}$, of a sample of quiescent black holes are combined with our results for $\dot{M}$ to conclude that early-type quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state (on scales of the sphere of influence), possibly between cycles of thermal instability on larger galactic scales.
-The maximum accretion rate of a thermally-stable flow is too low to explain the short growth times of low mass black holes in the local universe.
-The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger, galactic scales.
-Our results have implications for attempts to constrain the occupation fraction of SMBHs in low mass galaxies using the mean $L_{\rm X}-M_{\bullet}$ correlation, as well as to the diversity of circumnuclear media densities encountered by relativistic jets from tidal disruption events.
+  We calculate steady-state, one-dimensional hydrodynamic profiles of
+  hot gas in the nuclei of nominally quiescent galaxies for a range of
+  central black hole mass $M_{\bullet}$, parameterized gas heating
+  rate, and observationally-motivated stellar density profiles.  Mass
+  is supplied to the circumnuclear medium by stellar winds, while gas
+  is heated primarily by stellar winds, supernovae, and black hole
+  feedback.  Analytic estimates are provided for the stagnation radius
+  (where the radial velocity of the gas passes through zero) and the
+  black hole mass accretion rate, $\dot{M}$, as a function of black
+  hole mass and the gas heating efficiency, the latter of which is
+  related to the star-formation history.  We assess the conditions
+  under which radiative instabilities develop, separately in the case
+  of a single burst of star formation and in the case of the average
+  star formation history of galaxies hosting a given black hole
+  mass. The measured nuclear X-ray luminosities, $L_{X}$, of a sample
+  of quiescent black holes are combined with our results for $\dot{M}$
+  to conclude that early-type quiescent black holes in the local
+  universe are consistent with accreting in a locally thermally-stable
+  state (on scales of the sphere of influence), possibly between
+  cycles of thermal instability on larger galactic scales.  The
+  maximum accretion rate of a thermally-stable flow is too low to
+  explain the short growth times of low mass black holes in the local
+  universe.  The latter must instead result from gas being fed in from
+  large radii, either due to galaxy mergers associated with
+  hierarchical growth or thermal instabilities on larger, galactic
+  scales.  Our results have implications for attempts to constrain the
+  occupation fraction of SMBHs in low mass galaxies using the mean
+  $L_{\rm X}-M_{\bullet}$ correlation, as well as to the diversity of
+  circumnuclear media densities encountered by relativistic jets from
+  tidal disruption events.
 \end{abstract}
@@
 down-sizing' resulting from hierarchical structure growth (e.g,
-\citealt{Gallo+08}).  However, the physical processes involved in growing low mass blacks may be distinct from those operating at
-higher SMBH masses and accretion rates in quasars.  A key open question is whether SMBHs grow primarily by accreting gas fed in directly
-from galactic or extra-galactic scales, or whether significant growth results also from
-internal, secular processes such as local stellar mass loss in the nuclear region.
-
-A better understanding of what mechanisms regulate accretion onto quiescent SMBHs would have implications
-for a variety of observations, such as constraints on the occupation fraction of SMBHs in
-low mass galaxies.
-\citet{Miller+15} use the average relationship between the nuclear X-ray luminosities, $L_{X}$, of a sample of elliptical galaxies and the black hole mass to infer tentative evidence for a SMBH
-occupation fraction less than unity in galaxies with stellar masses
-$M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
+\citealt{Gallo+08}).  However, the physical processes involved in
+growing low mass blacks may be distinct from those operating at higher
+SMBH masses and accretion rates in quasars.  A key open question is
+whether SMBHs grow primarily by accreting gas fed in directly from
+galactic or extra-galactic scales, or whether significant growth
+results also from internal, secular processes such as local stellar
+mass loss in the nuclear region.
+
+A better understanding of what mechanisms regulate accretion onto
+quiescent SMBHs would have implications for a variety of observations,
+such as constraints on the occupation fraction of SMBHs in low mass
+galaxies.  \citet{Miller+15} use the average relationship between the
+nuclear X-ray luminosities, $L_{X}$, of a sample of elliptical
+galaxies and the black hole mass to infer tentative evidence for a
+SMBH occupation fraction less than unity in galaxies with stellar
+masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
 10^{7}M_{\odot}$).  This method relies on extrapolating a power-law
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the detection threshold, a potentially problematic assumption if different
-physical processes control the accretion rates onto the lowest mass
-SMBHs.
+the detection threshold, a potentially problematic assumption if
+different physical processes control the accretion rates onto the
+lowest mass SMBHs.
 
@@
 
-The gas density in galactic nuclei also influences the emission from stellar tidal
-disruption events (TDEs), such as the high energy transient {\it
-  Swift} J1644+57 (\citealt{Levan+11}; \citealt{Bloom+11},
-\citealt{Burrows+11}; \citealt{Zauderer+11}).  This transient event was powered
-by an impulsive relativistic jet, which produced synchrotron radio
-emission as the jet material was decelerated by shock interaction with
-the CNM of the previously quiescent SMBH
-(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of J1644+57 showed that the CNM density was much lower than that measured surrounding Sgr A$^{\star}$
+The gas density in galactic nuclei also influences the emission from
+stellar tidal disruption events (TDEs), such as the high energy
+transient {\it Swift} J1644+57 (\citealt{Levan+11};
+\citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
+This transient event was powered by an impulsive relativistic jet,
+which produced synchrotron radio emission as the jet material was
+decelerated by shock interaction with the CNM of the previously
+quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).
+Detailed modeling of J1644+57 showed that the CNM density was much
+lower than that measured surrounding Sgr A$^{\star}$
 (\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
@@
 producing substantially different radio emission than in J1644+57.
-Variations in the properties of the CNM could help
-explain why most TDEs appear to be radio quiet
-(e.g.~\citealt{Bower+13}; \citealt{VanVelzen+13}).
+Variations in the properties of the CNM could help explain why most
+TDEs appear to be radio quiet (e.g.~\citealt{Bower+13};
+\citealt{VanVelzen+13}).
 
@@
 \citealt{Ciotti+10}).  A key finding of these works is the periodic
-development of cooling instabilities on galactic scales, which temporarily increase the
-gas accretion rate towards the nucleus until feedback becomes sufficiently effective to shut off the flow and halt SMBH growth.  Here we instead
-focus on time-independent models, neglecting radiative cooling.  This
-approach allows us to systematically explore the relevant parameter
-space and to derive simple analytic expressions that prove useful in
-exploring whether cooling instabilties manifest across the expected
-range of galaxy properties, or whether other (non-AGN) forms of
-feedback can result in steady accretion.  Even if cooling instabilties
-develop on galactic scales over longer timescales, e.g. $\sim$ Gyr, a
-state of quasi-steady accretion may exist between these inflow events
-on smaller radial scales comparable to the sphere of influence.  We
-are thus motivated to explore whether steady flow is achieved within
-the nucleus under any circumstances, or whether the gas content is
-always building towards instability.
+development of cooling instabilities on galactic scales, which
+temporarily increase the gas accretion rate towards the nucleus until
+feedback becomes sufficiently effective to shut off the flow and halt
+SMBH growth.  Here we instead focus on time-independent models,
+neglecting radiative cooling.  This approach allows us to
+systematically explore the relevant parameter space and to derive
+simple analytic expressions that prove useful in exploring whether
+cooling instabilties manifest across the expected range of galaxy
+properties, or whether other (non-AGN) forms of feedback can result in
+steady accretion.  Even if cooling instabilties develop on galactic
+scales over longer timescales, e.g. $\sim$ Gyr, a state of
+quasi-steady accretion may exist between these inflow events on
+smaller radial scales comparable to the sphere of influence.  We are
+thus motivated to explore whether steady flow is achieved within the
+nucleus under any circumstances, or whether the gas content is always
+building towards instability.
 %A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
@@
 $M_{\bullet}$ & Black hole mass \\
-$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
-$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
-$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
+$\tilde{v}_{w}$ & Total heating parameter, including minimum heating
+rate from stellar and black hole velocity dispersion \\
+$v_{w}$ & Total heating parameter, excluding heating rate from velocity dispersion \\
+$r_{s}$ & Stagnation radius (where gas radial velocity goes to zero) \\
 $r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
-$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
+$r_{\rm Ia}$ & radius interior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
 $\rho_{\star}(r)$ & 3D radial stellar density profile \\
@@
 \label{sec:gal_model}
-\citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to measure the radial surface brightness profiles for hundreds of nearby early type galaxies.
-The measured brightness profile is generally well-fit by a ``Nuker" law parameterization:
+\citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to
+measure the radial surface brightness profiles for hundreds of nearby
+early type galaxies. The measured brightness profile is generally
+well-fit by a ``Nuker" law parameterization:
 \begin{equation}
@@
 \end{equation}
-i.e., a broken power law that transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta > \Gamma$, at a break radius, $\rb$.
-Assuming the stellar population is spherically symmetric, this corresponds to a stellar density $\rhostar \propto r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for $r \gg \rb$.
-To good approximation
+i.e., a broken power law that transitions from an inner power law
+slope, $\Gamma$, to an outer power law slope, $\beta > \Gamma$, at a
+break radius, $\rb$.  Assuming the stellar population is spherically
+symmetric, this corresponds to a stellar density $\rhostar \propto
+r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
+$r \gg \rb$.  To good approximation
 \begin{align}
@@
 \end{equation}
-where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$ relationship of \citet{Gultekin+09},
+where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the
+second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$
+relationship of \citet{McConnellMa+:2011a},
  \begin{align}
@@
 
-We fix $\beta = 2$ (a typical value) because our results are generally not sensitive to the
-properties of the gas flow on radial scales $\gtrsim r_b$.
-The presence of the break radius $r_{b}$ is, however, necessary to obtain a converged steady state for some regions of our parameter space.
-We consider solutions calculated for up to four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the range of break radii from the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.
-Most the cusp galaxies have
-$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In practice we calculate solutions for a range of $\rb$ only in cases when its precise value is expected to have a significant affect on the solution, in particular for high SMBH masses and low heating rates, for which the stagnation radius approaches large radii.
+We fix $\beta = 2$ (a typical value) because our results are generally
+not sensitive to the properties of the gas flow on radial scales
+$\gtrsim r_b$. The presence of the break radius $r_{b}$ is, however,
+necessary to obtain a converged steady state for some regions of our
+parameter space.  We consider solutions calculated for up to four
+values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
+range of break radii from the \citet{LauerFaber+:2007a}
+sample.\footnote{For the core galaxies the break radius follows the
+  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
+  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
+  between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In
+practice we calculate solutions for a range of $\rb$ only in cases
+when its precise value is expected to have a significant affect on the
+solution, in particular for high SMBH masses and low heating rates,
+for which the stagnation radius approaches large radii.
 
@@
 
-The term $\propto \vw^2 = \sigma(r)^2+v_{w}^2$ in the entropy
-equation accounts for external heating sources (e.g.,
+The term $\propto \vw^2 = \sigma(r)^2+v_{w}^2$ in the entropy equation
+accounts for external heating sources (e.g.,
 \citealt{ShcherbakovWong+:2014a}).  The first term approximates the
-minimum amount of shock heating from stellar winds due to the random movement
-of stars with respect to one another at the characteristic velocity of $\sigma \approx \sqrt{GM_{\rm enc}/r}$.
-This heating is present even in old stellar populations for which mass and energy injection are dominated by AGB winds with low velocities $\ll \sigma$.
-The second term, $v_{w}^{2}$, parameterizes all additional sources of heating, including faster main
-sequence or Wolf-Rayet stellar winds, spin-down energy from millisecond pulsars, supernovae, AGN
-feedback, etc.  As will be discussed in $\S\ref{sec:heating}$, the value of
-$v_{w}$ will in general depend on the SMBH mass and
-the age of the stellar population.  We further assume that $v_w$ is constant with radius, i.e. that the volumetric heating rate is proportional to the local stellar density.
+minimum amount of shock heating from stellar winds due to the random
+movement of stars with respect to one another at the characteristic
+velocity of $\sigma \approx \sqrt{GM_{\rm enc}/r}$.  This heating is
+present even in old stellar populations for which mass and energy
+injection are dominated by AGB winds with low velocities $\ll \sigma$.
+The second term, $v_{w}^{2}$, parameterizes all additional sources of
+heating, including faster main sequence or Wolf-Rayet stellar winds,
+spin-down energy from millisecond pulsars, supernovae, AGN feedback,
+etc.  As will be discussed in $\S\ref{sec:heating}$, the value of
+$v_{w}$ will in general depend on the SMBH mass and the age of the
+stellar population.  We further assume that $v_w$ is constant with
+radius, i.e. that the volumetric heating rate is proportional to the
+local stellar density.
 
@@
 \begin{align}
-T|_{r_{s}} \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
-\times 10^6\ \, v_{500}^2 \,\,{\rm K},
+T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
+  \tilde{v}_{w}^{2}}{2k} \nonumber\\
+ &\approx \frac{2}{5} \frac{7-2\nu}{7} \frac{\mu m_p
+   v_{w}^{2}}{2k}\nonumber\\ 
+ &\approx
+ \begin{cases}
+  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
+  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
+ \end{cases}
 \label{eq:Tanalytic}
 \end{align}
-where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
-density power-law slope at $r = r_{\rm s}$ {\bf BDM: FIXXXX T equation!!}.  Empirically, we find that 
+where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
+s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
+    s}}$ is the density power-law slope at $r = r_{\rm s}$.
+Empirically, we find that
 \begin{align}
@@
   \begin{cases}
-   430 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
-   840 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
+   380 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
+   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
   \end{cases}
@@
 Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).
-Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
+Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{McConnellMa+:2011a}.}
 \end{figure}

### 2015-03-08 ms.tex
table--headings still need adjustment
Fixing the MdotCompton to be consistent with new prescription.

@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
  & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
- $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 6.4 \times 10^{ -5 }$ & 17 \\
-... & 600 & 0.8 & 100 & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
-... & 1200 & 0.8 & 100 & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
-$    10^{ 7 }$ & 300 & 0.8 & 25 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
-... & ... & 0.8 & 50 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
-... & ... & 0.8 & 100 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
-... & ... & 0.8 & 200 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
-... & ... & 0.8 & 400 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
-... & 600 & 0.8 & 25 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
-... & ... & 0.8 & 100 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
-... & 1200 & 0.8 & 100 & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
-$    10^{ 8 }$ & 300 & 0.8 & 25 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
-... & ... & 0.8 & 50 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
-... & ... & 0.8 & 100 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
-... & ... & 0.8 & 200 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1 \times
-  10^{ -3 }}$ \\
-$    10^{ 8 }$ & 450 & 0.8 & 100 & $ 4.4 \times 10^{ -4 }$ & 4 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$ \\
-... & 600 & 0.8 & 25 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2
-}$ \\
-... & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 76 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 70 \\
-... & ... & 0.8 & 200 & $ 1.5 \times 10^{ -4 }$ & 67 \\
-... & ... & 0.8 & 400 & $ 1.6 \times 10^{ -4 }$ & 58 \\
-... & 1200 & 0.8 & 100 & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
+$    10^{ 6 }$ & 300 & 0.8 & 100 & 0.14 & $ 6.4 \times 10^{ -5 }$ & 17 \\
+... & 600 & 0.8 & 100 & $ 3.4 \times 10^{ -2 }$ & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
+... & 1200 & 0.8 & 100 & $ 8.2 \times 10^{ -3 }$ & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
+$    10^{ 7 }$ & 300 & 0.8 & 25 & 0.65 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
+... & ... & 0.8 & 50 & 0.65 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
+... & ... & 0.8 & 100 & 0.83 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
+... & ... & 0.8 & 200 & 0.91 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
+... & ... & 0.8 & 400 & 2.3 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
+... & 600 & 0.8 & 25 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
+... & ... & 0.8 & 100 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
+... & 1200 & 0.8 & 100 & $ 2.1 \times 10^{ -2 }$ & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
+$    10^{ 8 }$ & 300 & 0.8 & 25 & 1.3 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
+... & ... & 0.8 & 50 & 2.1 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
+... & ... & 0.8 & 100 & 3.8 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
+... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1
+  \times 10^{ -3 }}$ \\
+... & 450 & 0.8 & 100 & 0.72 & $ 4.4 \times 10^{ -4 }$ & 4 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & 3.3 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$\\
+... & 600 & 0.8 & 25 & 0.26 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2 }$ \\
+... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ & 70 \\
+... & ... & 0.8 & 200 & 0.3 & $ 1.5 \times 10^{ -4 }$ & 67 \\
+... & ... & 0.8 & 400 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 58 \\
+... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{
+  -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
   \hline
  & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
-$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 8.2 \times 10^{ -6 }$ & 99 \\
-... & ... & 0.1 & 50 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
-... & 1200 & 0.1 & 25 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-... & ... & 0.1 & 50 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-... & ... & 0.1 & 100 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-$    10^{ 7 }$ & 600 & 0.1 & 25 & $ 4.3 \times 10^{ -5 }$ & 41 \\
-... & ... & 0.1 & 50 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
-... & 1200 & 0.1 & 25 & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
-... & ... & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
-... & ... & 0.1 & 100 & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
-$    10^{ 8 }$ & 600 & 0.1 & 25 & $ 1.1 \times 10^{ -4 }$ & 31 \\
-... & ... & 0.1 & 50 & $ 3.0 \times 10^{ -4 }$ & 3 \\
-... & ... & 0.1 & 100 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
-... & 1200 & 0.1 & 25 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 50 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 100 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 200 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
-... & ... & 0.1 & 400 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
+$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2 \times 10^{ -6 }$ & 99 \\
+... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
+... & 1200 & 0.1 & 25 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+... & ... & 0.1 & 50 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+... & ... & 0.1 & 100 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
+$    10^{ 7 }$ & 600 & 0.1 & 25 & 0.24 & $ 4.3 \times 10^{ -5 }$ & 41 \\
+... & ... & 0.1 & 50 & 0.57 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
+... & 1200 & 0.1 & 25 & $ 4.4 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
+... & ... & 0.1 & 50 & $ 4.7 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
+... & ... & 0.1 & 100 & $ 5.3 \times 10^{ -2 }$ & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
+$    10^{ 8 }$ & 600 & 0.1 & 25 & 0.39 & $ 1.1 \times 10^{ -4 }$ & 31 \\
+... & ... & 0.1 & 50 & 0.66 & $ 3.0 \times 10^{ -4 }$ & 3 \\
+... & ... & 0.1 & 100 & 2.6 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
+... & 1200 & 0.1 & 25 & 0.1 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 50 & 0.11 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 100 & 0.12 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
+... & ... & 0.1 & 200 & 0.16 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
+... & ... & 0.1 & 400 & 3.3 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
   \hline
@@
 \end{align}
-If the accretion luminosity $\epsilon = 0.1 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
+If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
+depends on the Eddington ratio as predicted by some models for
+radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
+\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
 \begin{align}
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 1.4\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
+\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
 C,9}^{-0.44}M_{\bullet,8}^{0.08}
-&, \text{core}\\ 6\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
+&, \text{core}\\ 8.7\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
 C,9}^{-0.4} M_{\bullet,8}^{0.08}
@@
 \end{align}
-{\bf AG: Note that I have included the bolometric correction for now.  BDM: are you doing everything consistently?}
+{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
 

### 2015-03-09 ms.tex
conclusion

@@
 
-Apologies: 
-\begin{itemize}
-\item{we assume that average star formation histories correspond to those experienced in the nuclear region.  }
-
-\item{ Do nuclear star clusters in other galaxies look like scaled
-    up/down versions of the one in our own galaxy? If so this would
-    imply a radial gradient in the average of the stellar population
-    which would imply a heating which would be dependent on radius.  }
-
-\end{itemize}
-
-However, \citet{McCourt+12} argue that even if cooling is exactly
-balanced by heating everywhere, there is still a local thermal
-instability that operates to turn hot gas into cold clouds.  However,
-this local instability only causes a significant local drop-out of
-mass from the hot medium (to low-T clouds), if the cooling timescale,
-\begin{align}
-\frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-\end{align} 
-is locally shorter than the approximately 10 times the free-fall
-timescale $t_{\rm ff}$, where the last equality is evaluated at the
-stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
-(\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
-  crit}$ is also the condition for local instability, although the
-prefactor may be slightly different.
-
-If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
+% Apologies: 
+% \begin{itemize}
+% \item{we assume that average star formation histories correspond to those experienced in the nuclear region.  }
+
+% \item{ Do nuclear star clusters in other galaxies look like scaled
+%     up/down versions of the one in our own galaxy? If so this would
+%     imply a radial gradient in the average of the stellar population
+%     which would imply a heating which would be dependent on radius.  }
+
+% \end{itemize}
+
+% However, \citet{McCourt+12} argue that even if cooling is exactly
+% balanced by heating everywhere, there is still a local thermal
+% instability that operates to turn hot gas into cold clouds.  However,
+% this local instability only causes a significant local drop-out of
+% mass from the hot medium (to low-T clouds), if the cooling timescale,
+% \begin{align}
+% \frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
+% \end{align} 
+% is locally shorter than the approximately 10 times the free-fall
+% timescale $t_{\rm ff}$, where the last equality is evaluated at the
+% stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
+% (\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
+%   crit}$ is also the condition for local instability, although the
+% prefactor may be slightly different.
+
+% If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
 There are two kinds of ``instabilities", global and local.
@@
 In
-practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
+% practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
 This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
@@
 We have calculated steady-state models for circumnuclear medium of
-early type galaxies, assuming that gas is supplied entirely by stellar
+quiescent galaxies, assuming that gas is supplied entirely by stellar
 wind mass loss and heated by shocked stellar winds, supernovae and
-black hole feedback. We may use these profiles to calculate an $\Mdot$
-onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$ with
-$\Mbh$. We may then compare our results with observed trends of
-nuclear x-ray luminosity. Our main conclusions may be summarized as
-follows.
+black hole feedback. We compute profile for a range of different black
+hole masses, heating rates, and stellar density profiles and use these
+profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and get the
+scaling of $\Mdot$ with $\Mbh$. We may then compare our results with
+observed trends of Our main conclusions may be summarized as follows.
 
@@
   %lower vw except for very young stellar populations.
-  \item We find that $\eddr \propto \Mbh^{\alpha}$ for
-    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, where the
-    value of $\alpha$ with $\alpha\simeq$ for galaxies following the
-    average star formation histories measured in cosmological
-    simulations \citep{MosterNaab+:2013a}. This is in tension
-    observations of nuclear X-ray luminosity which suggest that
-    $\eddr$ increases towards smaller $\Mbh$
+  \item We find that $\eddr \propto \Mbh^{}$ for
+    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, for galaxies
+    following the average star formation histories measured in
+    cosmological simulations \citep{MosterNaab+:2013a}. This is in
+    tension observations of nuclear X-ray luminosity which suggest
+    that $\eddr$ increases towards smaller $\Mbh$
     \citep{Miller+15}. However, it is important to note that the
@@
     \Msun$ coexists with a population of smaller, steadily accreting
-    black holes (e.g. the upper limits in \citet{Miller+15}.  This
+    black holes (e.g. the upper limits in \citet{Miller+15}).  This
     calls into question the use of simple extrapolations of power-law
@@
     galaxies (\citealt{Miller+15}).
-  \item Low mass AGN have growth times comparable to the Hubble
-    time. We have show that this would require accretion rates not
-    consistent with steady state thermally stable accretion of stellar
-    wind material.
+  \item Low mass AGN have growth times comparable to the Hubble time
+    \citet{Heckman+04}. We have shown that this would require accretion
+    rates not consistent with steady-state thermally stable accretion
+    of stellar wind material, and is driven by an external supply of gas.
   \item We compare the $\Mdot$ for each of our solution to the one
-    calculated from the Bondi formula. We find that they generally to
-    a factor of a few. In our model the accretion rate is determined
-    from the gas properties at the stagnation radius, $\rs$, which
-    agrees with the Bondi radius, $\rb$, within a factor of a
-    few. Thus, use of the Bondi formula is a good approximation.
+    calculated from the Bondi formula. We find that they agree to
+    within a factor of order unity. This is because in our model the
+    accretion rate is determined by the flow properties at the
+    stagnation radius, $\rs$, which is within a factor of a few of the
+    Bondi radius $\rb$. Thus, use of the Bondi formula is a
+    good approximation.
   \end{enumerate}

### 2015-03-09 ms.tex
More conclusion.

@@
     good approximation.
+
+    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
+    the observed nuclear x-ray luminosities in quiescent, early type
+    galaxies could be understood as coming from thermally stable
+    steady-state accretion of stellar winds shed in the galactic
+    nucleus.  However, we would like to draw attention to the
+    following limitations of our model
+
+    \begin{enumerate}
+    \item Overall the accretion rate onto the cetral SMBH will be strongly
+    tied to the properties of the stellar population (e.g. age) within
+    the sphere of influence of the black hole. Thus, our model cannot
+    say anything definitive about the mode accretion for indivudual
+    galaxies which may have significant variations about our assumed
+    average star formation histories.
+    \item Also, the star formation history of bulges may (and probably
+      does) systematically differ from the average star formation
+      history for galaxies as a whole.
+    \item Furthermore, there could be a radial gradient in the star
+      formation history within a given bulge... 
     \end{enumerate}

### 2015-03-09 ms.tex
cooling/conduction

@@
 
-Radiative cooling can, however, be stabilized if it is overwhelmed by other sources of cooling, namely the term $\propto -q c_{s}^{2} \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
-Neglecting radiative cooling, this term is balanced at the stagnation radius by the wind heating term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.
-Thermal stability near the stagnation radius can thus be assessed by comparing the ratio of wind heating to radiative cooling $|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:qdot_rad}]),
+Radiative cooling can, however, be stabilized if it is overwhelmed by
+other sources of cooling, namely the term $\propto -q c_{s}^{2}
+\propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
+Neglecting radiative cooling, this term is balanced at the stagnation
+radius by the wind heating term, $\dot{q}_{\rm heat} = q
+\tilde{v}_{w}^{2}/2$.  Thermal stability near the stagnation radius
+can thus be assessed by comparing the ratio of wind heating to
+radiative cooling $|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:qdot_rad}]),
 \begin{align}
@@
 
-Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
-For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$ can be less than unity, depending on the wind mass loss parameter $\eta$.
-At the stagnation radius, the ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor of two of its minimum across the entire grid;  thus, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a diagnostic of thermal instabilty for the entire solution.
-
-Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$ near the stagnation radius.
-However, the two ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true gas density, which is greater in a subsonic inflow (weak heating) than in a supersonic outflow (strong heating).
-
-In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked in Table \ref{table:models}.
-{\bf BDM: EXPAND!!!!
-Explain that they don't matter.}
+Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative
+cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$
+(eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of
+radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
+For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling
+is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$
+we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$
+can be less than unity, depending on the wind mass loss parameter
+$\eta$.  At the stagnation radius, the ratio $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor
+of two of its minimum across the entire grid; thus, the value of
+$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a
+diagnostic of thermal instabilty for the entire solution.
+
+Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$
+near the stagnation radius.  However, the two ratios diverge from each
+other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because
+equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true
+gas density, which is greater in a subsonic inflow (weak heating) than
+in a supersonic outflow (strong heating).
+
+In addition to our standard set of solutions neglecting thermal
+conduction and cooling, we explore a few test simulations including
+these effects, as marked in Table \ref{table:models}. For solutions we
+with large wind heating parameters ($\vwO \gsim 1200 km/s$ km/s), we
+expect radiative cooling to have virtually no effect on the solution
+for reasonable values of the mass return parameter.  For cusp galaxies
+Thermally stable solutions are possible for values of the wind heating
+parameter as low as $\vwO=300$ km/s. However, this will be dependent
+on the value of the mass return parameter (and thus on the age of the
+stellar population) and on the break radius, $\rb$. For $\vwO\simeq
+300$ km/s, solutions with large $\rb$ will have large stagnation radii
+and thus larger densities. Thus, solution with $v_w$=300 km/s
+$\rb\gsim 100$ pc, would be thermally unstable.  The picture is
+qualitatively similar for core galaxies. However, the stagnation
+radius ``runs away'' to large radii at much smaller values of the wind
+heating paramter ($\vwO\simeq 600 km/s$). Thus, thermal instability
+sets in for higher values of $\vwO$ for core galaxies.
+
+In practice we expect that the effective wind heating will
+be or order $\sim 1000$ km/s if heating is dominated by young
+stars as would be the case for small black holes. This region of
+parameter space should be thermally stable. For higher mass
+black holes heating would be dominated by the supernovae and black
+hole feedback and would be comparable to the stellar velocity
+dispersion of the galaxy. Since core galaxies dominate for large
+$\Mbh$ we expect this region of parameter space to be thermally unstable.
+
+From our analytic results (see equation~\eqref{eq:conduction}) and
+direct numerical experiments, we expect that thermal conduction would
+introduce at most order unity changes in our solutions. The conductive
+heating flux saturates, so that at the stagnation radius the
+conductive heating rate is comparable to the external heating rate.
 
@@
 One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion and thermal stability for the average star formation history is marginal ($\S\ref{sec:mdot}$).
+{\bf AG: I wouldn't put too much stock in this since for higher masses
+vw is comparable to sigma, and thus rs should run away to large
+radii. This is especially true for core galaxies.}
 

### 2015-03-09 ms.tex
enum and figure
the issues column is back.
minor

@@
 terms of the fraction $\eta$ of the stellar density $\rhostar$ being
-recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
-yr.
-To good approximation $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ at time $\tau_{\star}$ following an impulsive star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return rate from evolved stars as a function of B-band luminosity instead of volumetrically, but our expressions are equivalent.}, although $\eta$ is significantly higher for continuous star formation histories (Fig.~\ref{fig:eta}).
+recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$ yr.
+To good approximation $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ at
+time $\tau_{\star}$ following an impulsive star burst (e.g.,
+\citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return
+  rate from evolved stars as a function of B-band luminosity instead
+  of volumetrically, but our expressions are equivalent.}, although
+$\eta$ is significantly higher for continuous star formation histories
+(bottom panel of Fig.~\ref{fig:vwSources}).
 
@@
 where the stagnation radius is assume to reside well inside the Nuker
-break radius and for clarity we have not distinguished between cusp and core galaxies.  Equation (\ref{eq:conduction}) shows that even in the
-case of saturated conduction, the neglect of heat conduction results
-in at most an order unity correction for expected values of the
-saturation parameter $\phi < 0.1$, justifying its neglect in our
+break radius and for clarity we have not distinguished between cusp
+and core galaxies.  Equation (\ref{eq:conduction}) shows that even in
+the case of saturated conduction, the neglect of heat conduction
+results in at most an order unity correction for expected {\bf (AG:
+  this sounds a bit too sharp perhaps replace with the word
+  plausible. Perhaps we should also mention the phi=1 solutions have
+  acausal conductivity (perhaps they are unphysical?).} values of
+the saturation parameter $\phi < 0.1$, justifying its neglect in our
 analysis.  Numerical experiments including conductivity confirm this
@@
 
-Our spherically symmetric model neglects the effects of angular momentum on the gas evolution.
-However, all galaxies possess some net rotation, resulting in centrifugal forces becoming important at some radius $r_{\rm circ} = l^{2}_{r_{s}}/(GM_{\bullet})$.
-Here $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar specific angular momentum near the stagnation radius, from which most of the accreted mass originates, where $V_{\phi}$ is the stellar azimuthal velocity.
-
-\citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data to measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
+  Our spherically symmetric model neglects the effects of angular
+  momentum on the gas evolution.  However, all galaxies possess some
+  net rotation, resulting in centrifugal forces becoming important at
+  some radius $r_{\rm circ} = l^{2}_{r_{s}}/(GM_{\bullet})$.  Here
+  $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar
+  specific angular momentum near the stagnation radius, from which
+  most of the accreted mass originates, where $V_{\phi}$ is the
+  stellar azimuthal velocity.
+
+  \citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data
+  to measure the ratio of ordered to random motion in a sample of
+  early type galaxies, which they quantify at each galactic radius $R$
+  by the parameter
   \begin{align}
@@
   \end{align}
-where $\sigma$ is the velocity dispersion and the brackets indicate a luminosity-weighted average.  The circularization radius of the accretion flow can be written in terms of $\lambda_R$ as
+
+  where $\sigma$ is the velocity dispersion and the brackets indicate
+  a luminosity-weighted average.  The circularization radius of the
+  accretion flow can be written in terms of $\lambda_R$ as
+
 \begin{equation}
@@
 \end{equation}
-where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied for the thermally-stable solutions of interest.
-
-\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy half-light radius and that $\lambda_R$ is with $R$ interior to this point.
-From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well inside the inner sonic point of the flow (typically located at $\sim 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).
-Angular momentum should only become dynamically important for thermally stable flows in a region that is causally disconnected from the outer part of the flow where the mass accretion rate is determined.
+
+where we have used the definition $r_{\rm soi} \equiv
+GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed
+that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied
+for the thermally-stable solutions of interest.
+
+\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$
+is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
+half-light radius and that $\lambda_R$ is with $R$ interior to this
+point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm
+  circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well
+inside the inner sonic point of the flow (typically located at $r\lsim
+0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).  Angular momentum should only
+become dynamically important for thermally stable flows in a region
+that is causally disconnected from the outer part of the flow where
+the mass accretion rate is determined.
 
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm
+    s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm
+          edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
+  {$\left(\frac{t_{\rm cool}}{t_{\rm
+          ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
 ... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ & 70 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &
+70 \\
+...$^{\ddagger}$ & ... & 0.8 & 100 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 73 \\
 ... & ... & 0.8 & 200 & 0.3 & $ 1.5 \times 10^{ -4 }$ & 67 \\
@@
  & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
-$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2 \times 10^{ -6 }$ & 99 \\
+$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2
+\times 10^{ -6 }$ & 99 & Conv\\
 ... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
@@
 \begin{tablenotes}
-\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
-Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
-Eddington units, normalized to a stellar mass input parameter $\eta =
-0.2$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
-stagnation radius.  Thermally unstable solutions are shown in bold
-text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
+\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
+  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
+  rate in Eddington units, normalized to a stellar mass input
+  parameter $\eta = 0.2$.  $^{(d)}$Ratio of cooling timescale to
+  free-fall timescale at stagnation radius.  Thermally unstable
+  solutions are shown in bold text.  $\dagger$Calculated with
+  radiative cooling included, assuming mass loss parameter $\eta =
+  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
+  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
+  saturatioon parameter $\phi=0.1$ (recall that we assume that the
+  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
 \end{tablenotes}
@@
 Realistic variations (``burstiness") in the star formation history
-will often result in lower heating rates.  Figure \ref{NickPlot2}
+will often result in lower heating rates.  Figure \ref{fig:NickPlot2}
 shows the heating rate as a function of average black hole mass for
@@
 large scatter in the accretion rates and hence X-ray luminosities
-shown in Fig \ref{fig:Miller} could also be understood by the wide
+shown in Fig \ref{fig:miller} could also be understood by the wide
 range of gas masses experienced over the course of a cyclic episode
@@
 wind mass loss and heated by shocked stellar winds, supernovae and
-black hole feedback. We compute profile for a range of different black
-hole masses, heating rates, and stellar density profiles and use these
-profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and get the
-scaling of $\Mdot$ with $\Mbh$. We may then compare our results with
-observed trends of Our main conclusions may be summarized as follows.
+black hole feedback. We compute profiles for a range of different
+black hole masses, heating rates, and stellar density profiles and use
+these profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and
+get the scaling of $\Mdot$ with $\Mbh$. We may then compare our
+results with observed trends of nuclear x-ray luminosity with galaxy
+properties. Our main conclusions may be summarized as follows.
 
@@
     \citep{Miller+15}. However, it is important to note that the
-    inflow rate on large scale (which we calculate) may differ from
+    inflow rate on large scales (which we calculate) may differ from
     the actual accretion rate as outflows could occur on small
@@
     fixed $\Mbh$ from (1) stochastic variation in star formation
-    history from galay to galaxy (2) Variations in small scale outflow
+    history from galaxy to galaxy (2) Variations in small scale outflow
     rates due to variations between galactic nuclear angular momenta.
@@
   \item Low mass AGN have growth times comparable to the Hubble time
-    \citet{Heckman+04}. We have shown that this would require accretion
+    (\citet{Heckman+04}). We have shown that this would require accretion
     rates not consistent with steady-state thermally stable accretion
@@
     good approximation.
+    \end{enumerate}
 

### 2015-03-09 ms.tex
power

@@
   %lower vw except for very young stellar populations.
-  \item We find that $\eddr \propto \Mbh^{}$ for
-    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, for galaxies
-    following the average star formation histories measured in
+  \item We find that for $\Mbh\gsim 10^6 \Msun$ and $\Mbh\lsim 10^8
+    \Msun$, $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim
+    0.5 \, (0.8)$ for core (cusp) galaxies, 
+    following average star formation histories measured in
     cosmological simulations \citep{MosterNaab+:2013a}. This is in

### 2015-03-09 ms.tex
updating figures to new fiducial value of eta=0.2

@@
     history from galaxy to galaxy (2) Variations in small scale outflow
-    rates due to variations between galactic nuclear angular momenta.
+    rates due to variations between galactic nuclear angular
+    momenta. {\bf AG: some more explanation of why 1 might not show up
+    in Pellegrini...}
     These variations alone could explain much of the 2-4 orders of

### 2015-03-09 ms.tex
eliot and roman

@@
   lines show the maximum accretion rate for a thermally stable flow
-  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  {\bf BDM: add
-    SgrA* numbers derived by quataert, NGC3115 from Roman} {\it Bottom
+  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
+  Eddington ratios inferred for the galactic center from
+  \citet{Quataert:2004a} (black circle) and for NGC3115 from
+  \citet{ShcherbakovWong+:2014a} (black diamonds). The top and bottom
+  diamonds correspond to solution without and with conductivity
+  respectively. Note that \citet{ShcherbakovWong+:2014a} do not
+  include saturation of the thermal conductivity in their model {\it Bottom
     panel:} Growth times $\Mbh/\Mdot$ in units of the Hubble time

### 2015-03-09 ms.tex
references

@@
 combination with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (~\ref{NickPlot2}) and
+intermittency in the star formation history (~\ref{fig:NickPlot2}) and
 (2) angular momentum of the infalling gas and consequentiallly the
@@
 10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
-J1644+57 (\citealt{Bloom:2011aa}), we predict gas densities of a $n
+J1644+57 (\citealt{Bloom+2011}), we predict gas densities of a $n
 \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating

### 2015-03-10 ms.tex
Fixing references

@@
 the co-evolution of SMBHs and their host galaxies with cosmic time
-(e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).  SMBH growth
+(e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  SMBH growth
 in the low redshift universe is dominated by low mass black holes,
@@
 lower than that measured surrounding Sgr A$^{\star}$
-(\citealt{Metzger+12}; \citealt{Berger+12}).  However, a TDE jet
+(\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a TDE jet
 injected into a denser CNM would be decelerated more rapidly,
@@
 in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
-  bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.
+  bulge}$) to measure $\Mbh$ as \citet{Miller+15} do.
 
@@
 10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
-J1644+57 (\citealt{Bloom+2011}), we predict gas densities of a $n
+J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
 \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
@@
 range estimated by modeling the radioa afterglow of {\it Swift}
-J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).  In fact, the
-flattening of the density profile inferred by \citet{Berger+12} on
+J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).  In fact, the
+flattening of the density profile inferred by \citet{BergerZauderer+:2012a} on
 radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that

### 2015-03-10 windheat.tex
Fixing references

@@
 
-Figure \ref{NickPlot2} shows how the wind heating varies as star formation histories deviate from their halo-averaged values.  In particular, we show
+Figure \ref{fig:NickPlot2} shows how the wind heating varies as star formation histories deviate from their halo-averaged values.  In particular, we show
 \begin{align} 
@@
 As we can see in Fig.
-\ref{NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
+\ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
 

### 2015-03-10 ms.tex
Fixing some table labels

@@
           edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
-  {$\left(\frac{t_{\rm cool}}{t_{\rm
-          ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
+  {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
   rate in Eddington units, normalized to a stellar mass input
-  parameter $\eta = 0.2$.  $^{(d)}$Ratio of cooling timescale to
-  free-fall timescale at stagnation radius.  Thermally unstable
+  parameter $\eta = 0.2$.  $^{(d)}$Ratio of wind heating rate to
+  radiative cooling rate at the stagnation radius.  Thermally unstable
   solutions are shown in bold text.  $\dagger$Calculated with
@@
   included, assuming mass loss parameter $\eta = 0.2$ and conductivity
-  saturatioon parameter $\phi=0.1$ (recall that we assume that the
+  saturatioon parameter $\phi=0.1$ (recall that the
   conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 

### 2015-03-10 ms.tex
mispellings galore

@@
 \author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
-  Columbia Astrophysics Labratory, Columbia University, 550 West 120th
+  Columbia Astrophysics Laboratory, Columbia University, 550 West 120th
   Street, New York, NY 10027}
@@
 energy and momentum output on larger physical scales (`feedback').
-The presence of dense gas in the nucleus may also lead to runaway
+The presence of dense gas in the nuclear region may also lead to runaway
 cooling, resulting in bursty episodes of star formation and AGN

### 2015-03-11 ms.tex
fixed paragraph on cooling/conduction solutions

@@
 
-In addition to our standard set of solutions neglecting thermal
-conduction and cooling, we explore a few test simulations including
-these effects, as marked in Table \ref{table:models}. For solutions we
-with large wind heating parameters ($\vwO \gsim 1200 km/s$ km/s), we
-expect radiative cooling to have virtually no effect on the solution
-for reasonable values of the mass return parameter.  For cusp galaxies
-Thermally stable solutions are possible for values of the wind heating
-parameter as low as $\vwO=300$ km/s. However, this will be dependent
-on the value of the mass return parameter (and thus on the age of the
-stellar population) and on the break radius, $\rb$. For $\vwO\simeq
-300$ km/s, solutions with large $\rb$ will have large stagnation radii
-and thus larger densities. Thus, solution with $v_w$=300 km/s
-$\rb\gsim 100$ pc, would be thermally unstable.  The picture is
-qualitatively similar for core galaxies. However, the stagnation
-radius ``runs away'' to large radii at much smaller values of the wind
-heating paramter ($\vwO\simeq 600 km/s$). Thus, thermal instability
-sets in for higher values of $\vwO$ for core galaxies.
-
-In practice we expect that the effective wind heating will
-be or order $\sim 1000$ km/s if heating is dominated by young
-stars as would be the case for small black holes. This region of
-parameter space should be thermally stable. For higher mass
-black holes heating would be dominated by the supernovae and black
-hole feedback and would be comparable to the stellar velocity
-dispersion of the galaxy. Since core galaxies dominate for large
-$\Mbh$ we expect this region of parameter space to be thermally unstable.
-
-From our analytic results (see equation~\eqref{eq:conduction}) and
-direct numerical experiments, we expect that thermal conduction would
-introduce at most order unity changes in our solutions. The conductive
-heating flux saturates, so that at the stagnation radius the
-conductive heating rate is comparable to the external heating rate.
+In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
+For solutions which are far from being thermally unstable when cooling is neglected (e.g.
+$M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.
+However, for solutions in which cooling stability is marginal (e.g.
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.
+Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e.
+to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
 

### 2015-03-11 ms.tex
random stuff

@@
 nuclear X-ray luminosities, $L_{X}$, of a sample of elliptical
-galaxies and the black hole mass to infer tentative evidence for a
+galaxies and their associated SMBH masses to infer tentative evidence for a
 SMBH occupation fraction less than unity in galaxies with stellar
@@
 
-\citet{Ho:2009a} estimates the SMBH accretion rates in a sample of
+\citet{Ho:2009a} determines the SMBH accretion rates in a sample of
 early-type galaxies using X-ray observations to determine the
@@
 temporarily increase the gas accretion rate towards the nucleus until
-feedback becomes sufficiently effective to shut off the flow and halt
+feedback becomes effective to shut off the flow and halt
 SMBH growth.  Here we instead focus on time-independent models,
@@
 steady accretion.  Even if cooling instabilties develop on galactic
-scales over longer timescales, e.g. $\sim$ Gyr, a state of
+scales over longer $\sim$ Gyr timescales, a state of
 quasi-steady accretion may exist between these inflow events on
@@
 Table \ref{table:definitions} provides the definitions of commonly used variables.
-Appendix \ref{app:rs} provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in greater detail.
+Appendices \ref{app:rs} and XXX provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in greater detail.
 
@@
 We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}; $\S\ref{sec:instability}$) that cannot be accounted for by our 1D
+However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
 time-independent model.
@@
 T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
-  \tilde{v}_{w}^{2}}{2k} \nonumber\\
- &\approx \frac{2}{5} \frac{7-2\nu}{7} \frac{\mu m_p
+  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7-2\nu}{7} \frac{\mu m_p
    v_{w}^{2}}{2k}\nonumber\\ 
@@
 energy $\sim \sigma^{2}$.
+In fact, for core galaxies the specific heating rate necessary to produce an unbound outflow can greatly exceed $\sigma^{2}$ due to the additional gravitational potential of stars outside the sphere of influence (Appendix XXX).
 
@@
     \, {\rm g \, cm^{-3}}& \text{core},\\
-    10 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
+    1.0 \times 10^{-25}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}.
   \end{cases}
@@
 the case of saturated conduction, the neglect of heat conduction
-results in at most an order unity correction for expected {\bf (AG:
-  this sounds a bit too sharp perhaps replace with the word
-  plausible. Perhaps we should also mention the phi=1 solutions have
-  acausal conductivity (perhaps they are unphysical?).} values of
+results in at most an order unity correction for plausible, causal values of
 the saturation parameter $\phi < 0.1$, justifying its neglect in our
@@
 \end{align}
-
 where we have used equations (\ref{eq:rhors}) and (\ref{eq:rhostarrs})
@@
    200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}\\
-\sigma,     
+f(r_b/r_{\rm soi})\sigma,     
   \end{cases}
@@
 The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
-However, when $v_{\rm w} \lesssim \sigma$ the stagnation radius moves to very large radii, or may not exist at all (see also Fig.~\ref{fig:stag}), resulting in much higher gas densities and inevitable cooling instability.
+However, when $v_{\rm w} \lesssim f(r_b/r_{\rm soi})\sigma$ the stagnation radius moves to very large radii, or may not exist at all (see also Fig.~\ref{fig:stag}), resulting in much higher gas densities and inevitable cooling instability.
+The dimensionless function f is approximately unity for cusp galaxies, but increases $\propto (r_b/r_{\rm soi})^{1/2}$ for core galaxies (Fig.~XXX).
 %Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
@@
   \end{align}
-
   where $\sigma$ is the velocity dispersion and the brackets indicate
@@
 \end{equation}
-
 where we have used the definition $r_{\rm soi} \equiv
@@
 is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
-half-light radius and that $\lambda_R$ is with $R$ interior to this
-point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm
+half-light radius and that $\lambda_R$ decreases with decreasing $R$ interior to this point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm
   circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well

### 2015-03-11 ms.tex
random stuff2

@@
   included, assuming mass loss parameter $\eta = 0.2$ and conductivity
-  saturatioon parameter $\phi=0.1$ (recall that the
+  saturation parameter $\phi = 0.1$ (recall that the
   conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
@@
 The flow near the stagnation radius is subsonic, but becomes supersonic at two critical points, one located at small radii, $r \lesssim 0.1r_{\rm s}$, and the other located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.
-In many cases the supersonic transition is instigated by the transition to a steeper stellar density prorfile exterior to the outer Nuker break radius, making our solutions near $r_{\rm s}$ also potentially sensitive to the break radius value.
+In many cases the supersonic transition is instigated by the transition to a steeper stellar density profile exterior to the outer Nuker break radius, making our solutions near $r_{\rm s}$ also potentially sensitive to the break radius value.
 % {\bf BDM: I made this up - in general we need

### 2015-03-11 ms.tex
random stuff3

@@
     galaxies ($\Gamma$=0.1). Squares mark the location of
-    the stagnation radius for each solution
+    the stagnation radius for each solution.
  }
@@
 The importance of Compton heating can be estimated by assuming the SMBH
-radiates with a luminosity $L = \epsilon_{\rm rad} \dot{M}c^{2}$, where
-$\epsilon_{\rm rad}$ is the radiative efficiency and where $\dot{M}$ is
+radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
+$\epsilon$ is the radiative efficiency and where $\dot{M}$ is
 estimated from equation (\ref{eq:mdot_analytic}).  Then using
@@
 \end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
-\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency
-for an advective accretion flow expected to produce high $T_{\rm C}$
-emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
+\epsilon/0.01 \sim 1$.  We caveat that, unlike
 stellar wind heating, Compton heating depends on radius, scaling as
@@
 \end{align}
-{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
+%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
 
@@
 Further assume that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
-heat}^{3}$.  The resulting volumetric heating rate $\dot{e} = \epsilon_{\rm
+heat}^{3}$.  The resulting volumetric heating rate $e = \epsilon_{\rm
 j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a heating parameter given by
@@
 10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.
-However, if this energy is deposited over much larger physical scales comparable to the size of the galaxy, i.e.
+However, if this energy is instead deposited over much larger physical scales comparable to the size of the galaxy, i.e.
 $r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 1$.
@@
 As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.
-However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating (see $\S\ref{sec:heating}$ for further discussion).
+However, given the uncertainty in the efficiency of jet heating, we defer a more detailed discussion to $\S\ref{sec:kinetic}$.
 
@@
 Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
-Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown.
+Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).
 

### 2015-03-11 ms.tex
fixed quataert discussion

@@
 interior to the Ia radius, which is gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.  Thus, according
+by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}f^{2}$  {\bf BDM: update discussion}.  Thus, according
 to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm
@@
 heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally
-assumed (\citealt{Sharma+14}).  For lower mass black holes, the
+assumed (\citealt{Sharma+14}) and if the galaxy is a core.  For lower mass black holes, the
 maximum accretion rate set by SN Ia is significantly higher and cannot
@@
 
-Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
-the accretion rate onto SgrA* estimated by \citet{Quataert:2004a} and
-the upper limit on $\dot{M}$ for the black hole in NGC3115 set by
-\citealt{ShcherbakovWong+:2014a}.  These points are consistent with
-our thermally-stable accretion rates within the expected dispersion
-(see next section), although NGC3115 is in fact a low luminosity AGN.
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}, as well as the range of $\dot{M}$ for the low-luminosity AGN NGC3115 from \citealt{ShcherbakovWong+:2014a} (who find a range of accretion rates depending on the assumed model for thermal conductivity, although they do not include saturation of the conductive flux).
+The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for galaxies with the same mass black hole by almost two orders of magnitude.
+This discrepency can be understood by the fact that star formation in the central parsec of the Galaxy is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
+Such a star formation history is better described as a `burst' of stars, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
 
@@
   \citet{Quataert:2004a} (black circle) and for NGC3115 from
-  \citet{ShcherbakovWong+:2014a} (black diamonds). The top and bottom
-  diamonds correspond to solution without and with conductivity
-  respectively. Note that \citet{ShcherbakovWong+:2014a} do not
-  include saturation of the thermal conductivity in their model {\it Bottom
+  \citet{ShcherbakovWong+:2014a} (black diamonds).  {\bf BDM: turn quataert/sch into lines, add J1644+57 lines extending below 1e7 msun} {\it Bottom
     panel:} Growth times $\Mbh/\Mdot$ in units of the Hubble time

### 2015-03-11 ms.tex
fixed discussion

@@
 
-The unresolved core X-ray luminosities of galactic nuclei provide a
-powerful diagnostic of the SMBH accretion rates and how they vary
-across different galaxy properties and SMBH masses (e.g.,
+The (unresolved) core X-ray luminosities of galactic nuclei provide a
+powerful diagnostic of the SMBH accretion rates and how they vary with SMBH mass and other galaxy properties (e.g.,
 \citealt{Ho08} and references therein).  Figure~\ref{fig:miller} shows
-our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm
-  bol} \dot{M} c^2$ in Eddington units as a function of black hole
-mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric
-correction at X-ray energies appropriate for low luminosity AGN
-(\citealt{Ho08}).  We have averaged the accretion rate used in
-calculating $\langle L_X \rangle$ between the values for galaxies with
+our predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of black hole
+mass, where $\epsilon_{X} = \epsilon\epsilon_{\rm bol}$, $\epsilon$ is the total radiative efficiency, and $\epsilon_{\rm bol} \sim 0.1$ is the bolometric
+correction into the measured X-ray band for low luminosity AGN (\citealt{Ho08}).  The value of $\langle L_X \rangle$ is calculated using the average accretion for galaxies with
 core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
-profiles using the average value of the inner density slope $\Gamma$
-as a function of black hole mass as fit from the
-\citet{LauerFaber+:2007a} galaxy sample, an exercise that results in
-the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$.
+profiles, using the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$ fit to the \citet{LauerFaber+:2007a} galaxy sample.
 
 The left panel of Figure \ref{fig:miller} is calculated assuming a
-constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$
+constant low value for the radiative efficiency of $\epsilon_X = 10^{-4}$,
 typical of those estimated for low luminosity AGN (e.g.,
 \citealt{Ho:2009a}), while the right panel luminosities are calculated
-instead assuming an efficiency of $\epsilon_X= 10 \dot{M}/\dot{M}_{\rm
+instead assuming an efficiency of $\epsilon_X= 10 \epsilon_{\rm bol}\dot{M}/\dot{M}_{\rm
   edd}$ that depends on the Eddington ratio as predicted by some
@@
 are the X-ray measurements (green stars) and upper limits (gray
-triangles) of early-type galaxies compiled by \citet{Miller+15}
+triangles) from the sample of early-type galaxies compiled by \citet{Miller+15}
 (cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
@@
 L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
-\citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
-Yellow, teal, and red lines show the maximum accretion rates,
-respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]),
-as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by
-Compton heating feedback (eq.~[\ref{eq:MdotC}]).
+\citep{Zhang+09, Pellegrini10, Gallo+10}).  Also shown are the maximum accretion rates,
+respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]; yellow),
+as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
+Compton heating feedback (eq.~[\ref{eq:MdotC}]; red).
 
@@
 
-If heating in the nuclei of elliptical galaxies is similar to that
-produced by the average star formation history of galaxies with
+If the nuclei of elliptical galaxies are heated in a way similar to that due to the average star formation history of galaxies with
 similar mass, then to first order we predict that $\langle
@@
 result is in tension with the observed down-sizing trend that the
-average Eddington ratio is observed to decrease (albeit also weakly)
-with $M_{\bullet}$.  However, in making such comparisons it is
-important to keep in mind the enormous uncertainty in calculating the
+average Eddington ratio is seen to decrease (albeit also weakly)
+with $M_{\bullet}$.  However, one must keep in mind the enormous uncertainty in calculating the
 luminosity of the accretion flow close to the black hole in a single
-waveband based on the accretion rate on larger scales.  Black hole
-mass-dependent efficiency factors could enter that we are not taking
-into account.  For instance, if disk outflows carry away a substantial
-fraction of the infalling mass before it reaches sufficiently small
-radii to produce the observed X-rays
-(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
-angular momentum of the infalling gas (and hence that of stars in the
-galactic nucleus) might also influence the X-ray luminosity, in a way
-that could depend systematically on $M_{\bullet}$.
-
-A more readily addressable test is whether a steady-state accretion
-picture is capable of explaining the large scatter of typically 2-3
-orders of magnitude in the observed distribution of $L_{X}/L_{\rm
-  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
-least two effects: (1) the strong sensitivity of the accretion rate to
+waveband based on the feeding rate on larger scales.
+If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
+angular momentum of the infalling gas might also influence the X-ray luminosity, in a way
+that could depend systematically on the stellar population and hence $M_{\bullet}$.
+
+Perhaps a more readily addressable test is whether a steady-state accretion
+picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
+  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
+least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
+  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
 the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
 v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
-(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
-combination with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (~\ref{fig:NickPlot2}) and
-(2) angular momentum of the infalling gas and consequentiallly the
-size of small scale outflows may vary from galaxy to galaxy at fixed
-$\Mbh$. The combination of (1) and (2) is capable of explaining much
-of the observed sample, especially considering that scatter in $L_{\rm
-  X}$ due to variations in $\dot{M}$ is exacerbated by the expectation
-that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient
-flows. At a wind heating parameter there is an order of magnitude
-difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$
-and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) which could also lead to
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
+combined with the significant dependence of $v_w$ on stochastic
+intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) possible differences angular momentum of the infalling gas and consequentiallly the
+efficacy of disk outflows may vary from galaxy to galaxy at fixed
+$\Mbh$.
+Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ (Fig.~\ref{fig:bh_growth}) which could also lead to
 scatter of $\dot{M}$ due to the variation in the Nuker stellar density
-profile $\Gamma$ at fixed $M_{\bullet}$. However, \citet{Pellegrini10}
-find that the scatter in $L_X$ is similar if one just looks at
-core/cusp galaxies separately. There could also be scatter introduced
-in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
-  bulge}$) to measure $\Mbh$ as \citet{Miller+15} do.
+profile $\Gamma$ at fixed $M_{\bullet}$.  Any such differences in $\dot{M}$ are exacerbated by the expectation
+that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
+flows.
+
+%Many of the upper
+%limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
+%separate ``thermally stable" population.  This possible dichotomy
+%calls into question the use of simple extrapolations of power-law fits
+%to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
+%constrain the occupation fraction of black holes in low mass galaxies
+%(\citealt{Miller+15}).
+
+\subsection{Steady Accretion versus Cyclic Outbursts}
+\label{sec:cycle}
 
@@
 accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
-
-Many of the upper
-limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
-separate ``thermally stable" population.  This possible dichotomy
-calls into question the use of simple extrapolations of power-law fits
-to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
-constrain the occupation fraction of black holes in low mass galaxies
-(\citealt{Miller+15}).
-
-\subsection{Steady Accretion versus Cyclic Outbursts}
-\label{sec:cycle}
 

### 2015-03-11 ms.tex
fixed discussion of scatter in lx

@@
 combined with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) possible differences angular momentum of the infalling gas and consequentiallly the
-efficacy of disk outflows may vary from galaxy to galaxy at fixed
-$\Mbh$.
-Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ (Fig.~\ref{fig:bh_growth}) which could also lead to
-scatter of $\dot{M}$ due to the variation in the Nuker stellar density
-profile $\Gamma$ at fixed $M_{\bullet}$.  Any such differences in $\dot{M}$ are exacerbated by the expectation
-that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
-flows.
+intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) differences angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows, $\Mbh$.
+Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).
+Differences in $\dot{M}$ are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient flows.
 

### 2015-03-11 ms.tex
caption

@@
 \includegraphics[width=\textwidth]{miller.pdf}
-\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
-  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
-  upper limits (red triangles) from \citet{Miller+15}.
-  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
-  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
-  blue curves represent our predictions for core ($\Gamma=0.1$)
-  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
-  from equation~\eqref{eq:mdot_analytic}, with the wind heating
-  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
-  the the average star formation histories in
-  \citet{MosterNaab+:2013a} (the black lines in
-  Figures~\ref{fig:vwSources}--see
-  Appendix~\ref{app:windheat} for a detailed description).
-  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
-  thermal stability (purple) and Ia supernovae (orange).}
+\caption{\label{fig:miller} Average (unresolved) nuclear X-ray luminosity $\langle L_X \rangle = \epsilon_X \Mdot c^2$ as a function of SMBH mass, predicted from our models for the average star formation history (Fig.~\ref{fig:bh_growth}; {\it black line}) calculated for the average Nuker power-law index $\Gamma(M_{\bullet})$ derived from the galaxy sample of \citet{LauerFaber+:2007a}.
+Shown for comparison are the measurements $L_X/L_{\rm edd}$ values (red stars) and
+  upper limits (red triangles) from the \citet{Miller+15} sample of early-type galaxies, with a green line showing the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$.
+The left panel shows the case of a constant radiative efficiency $\epsilon_X=10^{-4}$, while the right hand panel shows an efficiency $\epsilon_X=
+  \left(\frac{\epsilon_{\rm bol}}{0.1}\right)\frac{\Mdot}{\MdotEdd}$ predicted by some models for radiatively inefficient accretion.
+Also shown for comparison are the X-ray luminosities calculated using the maximum thermally-stable accretion rate ({\it orange line}), SN Ia-regulated accretion rate, and Compton-regulated accretion rate ({\it pink line}),  again calculated for the average star formation history.}
 \end{figure*}

### 2015-03-11 ms.tex
fixed 6.3

@@
 
-It is also possible that many of the nuclei from the \citet{Miller+15}
-sample are not accreting in a steady fashion.  The ADAF efficiency
-assumed in the right panel of Figure \ref{fig:miller} in some ways
-represents the maximum value, since it does not take into account
-outflows from the accretion flow that would suppress the accreiton
-rate reaching large radii.  Nevertheless, many lower black hole masses
-of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie
-well above the predicted average value for stable accretion (black
-line), suggesting that these galaxies either experience lower levels
-of heating than average galaxies of their mass, or that they are not
-accreting stably at all ($\S\ref{sec:cycle}$).  Indeed, for the lowest
-mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$
-exceeds the one corresponding to the maximum thermally-stable
-accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
-
-Figure \ref{fig:bh_growth} (top panel) shows that across all black
-hole masses, Compton heating alone cannot prevent thermal
-instabilities from developing in a steady-state accretion flow
-($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).  Thus, if the stellar
-population is sufficiently old (or the star formation sufficiently
-intermittent) then nuclear gas could undergo cyclic oscillations of
-thermal instability and high accretion rates, followed by quiescent
-periods once gas has been consumed and/or AGN feedback becomes
-effective.  Such cycles are proposed to occur on large scales and long
-timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea
-supported, e.g. , by GALEX observations showing that a small fraction
-of early-type galaxies in the local universe have undergone recent ($<
-1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).  If such
-cyclic behavior also occurs on small, parsec scales (e.g.) then the
-large scatter in the accretion rates and hence X-ray luminosities
-shown in Fig \ref{fig:miller} could also be understood by the wide
-range of gas masses experienced over the course of a cyclic episode
-between instabilities and periodic nuclear outbursts
-(e.g.~\citealt{Ciotti+10}).  In support of this possibility, we find
-that core galaxies are more likely to possess higher accretion rates
-and potentially be thermally unstable.  Past studies have found that
-core galaxies show a wide range of nuclear radio and X-ray
-luminosities (suggesting cyclic accretion episodes), while cusp
-galaxies are confined below a threshold (e.g., \citealt{Bender+89,
-  Pellegrini99, Capetti&Balmaverde05}), consistent with
-thermally-stable, steady-state picture.
-
-The cyclic model predicts that high $L_{X}$ nuclei should be more
-common in galaxies with younger stellar ages, a result which appears
-in tension with the finding by \citet{Pellegrini10} that galaxies with
-younger stellar populations are observed to host less X-ray luminous
-nuclei, at least for stellar ages $<3$ Gyr.  An alternative
-explanation for this observation within a thermally stable,
-steady-state accretion picture is that young stars provide higher
-stellar wind heating, reducing the mass accretion rate and hence
-nuclear X-ray luminosity.  {\bf AG Challenge: \citet{HeckmanBest:2014a}
-  find that ${\rm L_{[OIII]}}$ (a proxy for the bolometric luminosity)
-  ${\rm L_{[OIII]}/M_\star}$ (a proxy for the Eddington ratio)
-  increases with decreasing 4000 $\AA$ break index (decreasing stellar
-  age) (see their Figure 14). This suggests that the accretion rate is
-  actually increasing towards younger stellar ages. At young ages
-  there actually seems to be plenty of gas around, which may be
-  obscuring the x-rays and causing an anamolously low measurement of
-  $L_X$.
-
-  For a starburst the black hole accretion rate lags the star
-  formation rate by 200 Myr (\citet{WildHeckman+:2010a} Figure
-  9). This could be due to SNe feed back suppressing the black hole
-  accretion rate (massive star winds do the same thing by themselves,
-  but they cannot be sustained for 200 Myr. 
-}
+It is also possible that many of the galactic nuclei from the \citet{Miller+15} sample are not accreting in a steady fashion.
+The efficiency assumed in the right panel of Figure \ref{fig:miller} in some ways represents a maximum value, since it does not take into suppression of the accretion rate due to disk outflows on small scales.
+If the actual X-ray efficiency is lower than assumed, then many of the detections in the case of low SMBH masses, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, would lie even further above above the predicted average value for stable accretion (black line).
+These galaxies either experience significantly lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all.
+Indeed, for the lowest mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
+It is not surprising that this sample is more likely to be thermally unstable as compared to an average galaxy with this black hole mass, because the \citet{Miller+15} sample includes only early-type galaxies with on averager older stellar populations.
+
+Figure \ref{fig:bh_growth} (top panel) also shows that across all black hole masses, Compton heating also cannot prevent average accretion rates which are thermally unstable, i.e.
+$\dot{M}_{\rm C} > \dot{M}_{\rm TI}$.
+In the case of thermal instabilities, nuclear gas may undergo cyclic oscillations of rapid cooling and high accretion rates, followed by quiescent
+periods once gas has been consumed and/or AGN feedback becomes effective.
+Such cycles are proposed to occur on large scales and long timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea possibly supported by, e.g., GALEX observations showing that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+Similiar cyclic AGN activity have been proposed to occur on the smaller scale of the sphere of influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuarda+15}).
+
+If such cyclic outbursts also manifest on the properties of gas on small, parsec scales, then the large scatter in the accretion rates and hence X-ray luminosities in Fig \ref{fig:miller} could result from the wide range of inflow rates experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
+Due to their deeper potential well, we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable for a fixed wind heating rate than cusp galaxies (Fig.~XXX).
+This could help explain why core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89,   Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
+
+If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$ in Fig \ref{fig:miller} represent thermally-unstable galaxies, then many of the upper limits may correspond to a separate ``thermally stable" population, for instance including SgrA*.
+The possibility of a mixed population of stable versus unstable galaxies calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
+
+%The cyclic model predicts that high $L_{X}$ nuclei should be more
+%common in galaxies with younger stellar ages, a result which appears
+%in tension with the finding by \citet{Pellegrini10} that galaxies with
+%younger stellar populations are observed to host less X-ray luminous
+%nuclei, at least for stellar ages $<3$ Gyr.  An alternative
+%explanation for this observation within a thermally stable,
+%steady-state accretion picture is that young stars provide higher
+%stellar wind heating, reducing the mass accretion rate and hence
+%nuclear X-ray luminosity.  {\bf AG Challenge: \citet{HeckmanBest:2014a}
+ % find that ${\rm L_{[OIII]}}$ (a proxy for the bolometric luminosity)
+  %${\rm L_{[OIII]}/M_\star}$ (a proxy for the Eddington ratio)
+  %increases with decreasing 4000 $\AA$ break index (decreasing stellar
+ % age) (see their Figure 14). This suggests that the accretion rate is
+  %actually increasing towards younger stellar ages. At young ages
+  %there actually seems to be plenty of gas around, which may be
+  %obscuring the x-rays and causing an anamolously low measurement of
+  %$L_X$.
+
+  %For a starburst the black hole accretion rate lags the star
+  %formation rate by 200 Myr (\citet{WildHeckman+:2010a} Figure
+ % 9). This could be due to SNe feed back suppressing the black hole
+  %accretion rate (massive star winds do the same thing by themselves,
+ % but they cannot be sustained for 200 Myr. 
+%}
 
@@
 history of their galaxies, we see that $t_{\rm grow}$ exceeds the
-Hubble time by 1-3 orders of magnitude across all black hole masses.
+Hubble time by 1$-$3 orders of magnitude across all black hole masses.
 Steady accretion therefore cannot explain the growth of low mass black

### 2015-03-11 ms.tex
fixed TDE section

@@
 hierachical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}).
-
-\citet{Kauffmann&Heckman09} find that the growth of low mass black
-holes is dominated by young stellar bulges which have a log normal
+galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this, \citet{Kauffmann&Heckman09} find that the growth of low mass black holes is dominated by young stellar bulges which have a log normal
 distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
-0.01$. The distribution is insensitive to galaxy properties which
-suggestes that it is set by feedback from the black hole rather than
-from the gas supply in the nucleus.
+0.01$. That this distribution is insensitive to galaxy properties suggestes that it is set by SMBH feedback instead of the nuclear gas supply.
 
@@
 universe cannot result from thermally-stable steady accretion of gas
-lost from the surrounding stellar population.
-
-Gas blow-out by SN Ia cannot prevent the growth of low-mass black
-holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
-Ia heating (green lines), although Ia heating could play in principle
-a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black
-holes, again depending on the efficiency of Ia heating.
+lost from the surrounding stellar population studied in this paper.
+Gas blow-out by SN Ia cannot prevent the growth of low-mass black holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
+Ia heating (green lines), although Ia heating could play in principle a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the efficiency of Ia heating and whether the galaxy is a core or cusp.
 
@@
 km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
-range estimated by modeling the radioa afterglow of {\it Swift}
-J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).  In fact, the
-flattening of the density profile inferred by \citet{BergerZauderer+:2012a} on
-radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that
-seen in our calculations of the gas density profile for core galaxies
-(Fig.~\ref{fig:profiles}, solid line).  The CNM density of the host of
-{\it Swift} J1644+57 was a factor of 30 times lower than that inferred
-by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf
-  BDM: whats going on?}  The implications of our models for CNM
-profiles for the diversity of radio emission from TDE jets will be
+range estimated by modeling the radio afterglow of {\it Swift}
+J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).
+
+\citet{BergerZauderer+:2012a}  infer a flattening of the gas density profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks qualitiatively similar to that the density profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid line).
+Their inferred  gas profile also shows a break at radii $\sim 0.6$ pc, which in our model corresponds to the break radius of the galaxy and hence would imply a SMBH mass of TINY accroding to the mean relationship from the \citet{Lauer+Faber:2007a} sample.
+More detailed models for the environment, and the implications of our models for CNM profiles for the diversity of radio emission from TDE jets, will be
 explored further in future work.

### 2015-03-11 ms.tex
analytic temperature.

@@
 T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
-  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7-2\nu}{7} \frac{\mu m_p
+  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7}{7-2\nu} \frac{\mu m_p
    v_{w}^{2}}{2k}\nonumber\\ 
@@
 combined with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) differences angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows, $\Mbh$.
-Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).
-Differences in $\dot{M}$ are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient flows.
+intermittency in the star formation history (Appendix
+\ref{fig:NickPlot2}), this can lead to order of magnitude differences
+in $\dot{M}$; (3) differences angular momentum of the infalling gas
+from galaxy to galaxy, resulting in differences in the fraction of the
+gas lost to outflows, $\Mbh$.  Also potentially contributing is the
+order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$,
+between $\dot{M}$ for core and cusp galaxies
+(Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are augmented by
+the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively
+inefficient flows {\bf AG: Don't forget differences in eta}.
 

### 2015-03-16 be.tex
Start on the new appendix.

We assume that the stellar density profile follows a broken power law
with the stellar density $\rhostar\sim r^{-1-\Gamma}= r^{-\delta}$ inside of the
break radius $\rb$, where ($0<\Gamma<1$). We derive an expression for
the specific enthalpy of the gas, $\ke +\gammaf \frac{p}{\rho}$ as a
function of $\zeta=v_w/\sigma$, $x=r/r_s$, and $r_s/\rsoi$. We show
that if the break radius, $\rb$ goes to infinity this quantity
necessarily goes to infinity as the potential well becomes infinitely
deep, hence a break radius is necessary for an outflow to be possible.

Consider the steady state energy conservation equation. {\bf AG perhaps
  put a brief explanation of how this relates to the steady state
  entropy equation via laws of thermodynamics?.}

\begin{align}
\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \left(\frac{v^2}{2} + \Phi
    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi
\label{eq:enCons}
\end{align}

Where $\kew=v_w^2+\sigma^2\simeq v_w^2+\frac{G M_{\rm enc}(r)}{r}$ and
$\Menc$ is the sum of the black hole mass and the stellar mass.

Now integrate both sides with respect from r to the stagnation radius

\begin{align}
  r^2 \rho v \left(\ke+\Phi+\gammaf \frac{p}{\rho} \right)= \int_{\rs}^{r}
    r^2 \left(q \kew + q\Phi\right) dr
    \label{eq:enConsInt}
\end{align}

We know $f\equiv r^2 \rho v$ from the steady state mass conservation
equation.

\begin{align}
 \frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v\right) = q 
\end{align}

Where q is the rate of the mass injection per volume, which is
proportional to the stellar density. Let $x=r/\rs$ and $q_o= q
(\rs)$. Then $q=q_o x^{-\delta}$.

Then one obtains for the mass flux, $f$

\begin{align}
 f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right]
 \label{eq:massFlux}
\end{align}

The gravitational potential $\Phi$ is given by

\begin{align}
\Phi= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\rs} \rhostar(dr') r'
dr'.
\label{eq:Phi}
\end{align}

Note our unconventional choice of gauge: the upper limit of the
integral on the right hand side is $\rs$ whereas conventionally the
upper limit is taken to be $\infty$. This means that our definition
will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
gauge invariant.

Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
and~\eqref{eq:Phi}, we may obtain an expression for the enthalpy,
$\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
$\rb$.

\begin{align}
&\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} + \frac{G
  M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
&-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
&+\frac{v_w^2}{2}-\frac{G \Mbh}{2 r_s} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1} -\frac{G M_\star}{2 r_s} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}

where $U_o=4 \pi G \rhostar(\rs) \rs^2$.  We may rewrite this as

\begin{multline}
  \frac{v^2}{2}+\gammaf \frac{p}{\rho}=\frac{G \Mbh}{\rs}
  \biggl[\zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
-\frac{1}{2} \frac{3-\delta}{2-\delta} \frac{x^{2 -\delta}-1}{x^{3-\delta}-1}\\
  -w (3 -\delta) \left(-\frac{3-\delta}{(5-2\delta)(2-\delta)}\frac{x^{5 -2 \delta}-1}{ \left(x^{3-\delta}-1\right)}\right)\\
  -\frac{w (3
    -\delta) x^{2 -\delta}}{2
    -\delta}-\frac{w (3 -\delta) \left(x^{5
        -2 \delta}-1\right)}{2 (5 -2 \delta)
    \left(x^{3 -\delta}-1\right)}
  \biggr]
\end{multline}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ms"
%%% End:

### 2015-03-16 ms.tex
Start on the new appendix.
Modifying the mdot_mass figure.

@@
   Eddington ratios inferred for the galactic center from
-  \citet{Quataert:2004a} (black circle) and for NGC3115 from
-  \citet{ShcherbakovWong+:2014a} (black diamonds).  {\bf BDM: turn quataert/sch into lines, add J1644+57 lines extending below 1e7 msun} {\it Bottom
-    panel:} Growth times $\Mbh/\Mdot$ in units of the Hubble time
-  $\th$ for each of the accretion rates shown in the top panel.}
+  \citet{Quataert:2004a} (line with black circle) and for NGC3115 from
+  \citet{ShcherbakovWong+:2014a} (line with black diamonds) and for
+  the Swift J1644+57 event from \citet{BergerZauderer+:2012a} (line
+  with black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
+  in units of the Hubble time $\th$ for each of the accretion rates
+  shown in the top panel.}
 \end{figure}
@@
   \appendix
-  \section{Analytic Expression for the stagnation radius}
+  \section{Analytic expression for the stagnation radius}
   \label{app:rs}
   \input{rs}
+
+  \section{Analytic expression for specific enthalpy of gas}
+  {\bf AG: double check that what we are deriving here is actually
+    specific enthalpy}
+  \label{app:be}
+  \input{be}
 

### 2015-03-17 ms.tex
spacing

@@
 The (unresolved) core X-ray luminosities of galactic nuclei provide a
-powerful diagnostic of the SMBH accretion rates and how they vary with SMBH mass and other galaxy properties (e.g.,
-\citealt{Ho08} and references therein).  Figure~\ref{fig:miller} shows
-our predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of black hole
-mass, where $\epsilon_{X} = \epsilon\epsilon_{\rm bol}$, $\epsilon$ is the total radiative efficiency, and $\epsilon_{\rm bol} \sim 0.1$ is the bolometric
-correction into the measured X-ray band for low luminosity AGN (\citealt{Ho08}).  The value of $\langle L_X \rangle$ is calculated using the average accretion for galaxies with
+powerful diagnostic of the SMBH accretion rates and how they vary with
+SMBH mass and other galaxy properties (e.g., \citealt{Ho08} and
+references therein).  Figure~\ref{fig:miller} shows our predictions
+for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of
+black hole mass, where $\epsilon_{X} = \epsilon\epsilon_{\rm bol}$,
+$\epsilon$ is the total radiative efficiency, and $\epsilon_{\rm bol}
+\sim 0.1$ is the bolometric correction into the measured X-ray band
+for low luminosity AGN (\citealt{Ho08}).  The value of $\langle L_X
+\rangle$ is calculated using the average accretion for galaxies with
 core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
-profiles, using the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$ fit to the \citet{LauerFaber+:2007a} galaxy sample.
+profiles, using the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$ fit
+to the \citet{LauerFaber+:2007a} galaxy sample.
 

### 2015-03-17 be.tex
Rewriting formula in appendix
Adding to appendix

@@
 $\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
-$\rb$.
+$\rb$. {\bf AG: 2s with question marks would not be included if the $G
+\Mstar/r$ }
 
@@
 &-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
-&+\frac{v_w^2}{2}-\frac{G \Mbh}{2 r_s} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1} -\frac{G M_\star}{2 r_s} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
+&+\frac{v_w^2}{2}-\frac{G \Mbh}{2 r_s} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1} -\frac{G M_\star}{2? r_s} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
 \end{align}
@@
 \begin{multline}
-  \frac{v^2}{2}+\gammaf \frac{p}{\rho}=\frac{G \Mbh}{\rs}
-  \biggl[\zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
+  \frac{v^2}{2}+\gammaf \frac{p}{\rho}
+=\frac{G \Mbh}{\rs} 
+\biggl[
+  \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
   -\frac{1}{2} \frac{3-\delta}{2-\delta} \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
-  -w (3 -\delta) \left(-\frac{3-\delta}{(5-2\delta)(2-\delta)}\frac{x^{5 -2 \delta}-1}{ \left(x^{3-\delta}-1\right)}\right)\\
-  -\frac{w (3
-    -\delta) x^{2 -\delta}}{2
-    -\delta}-\frac{w (3 -\delta) \left(x^{5
-        -2 \delta}-1\right)}{2 (5 -2 \delta)
-    \left(x^{3 -\delta}-1\right)}
-  \biggr]
+  -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
+  -w \frac{(2-\delta)(3-\delta)-2?(3-\beta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
+\biggr].
+\label{eq:enthAnal}
 \end{multline}
+
+Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta$ is
+the ratio of the extra heating rate to the stellar velocity in of the
+influence radius $\rsoi$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
+$\delta$ is the power law slope of the stellar density profile inside
+of the break radius, $\rb$.
+
+For a given $\zeta$ we define a critical $\rs/\rsoi=min{
+  \frac{frac{7}{2}-\densSlope}{\densSlope \zeta^2, 1}}$ for thermal stability, 
+where the first term in the brackets corresponds to twice the value
+predicted by equation~\eqref{eq:rsRinf}, in the limit the stellar mass
+as $\rs$ is small compared to $\Mbh$. This prescription is somehwat
+ad hoc, but...{\bf AG--some motivation...}
+
+Then from equation~\eqref{eq:enthAnal} we may obtain the critical
+wind heating parameter $v_{w, \rm crit}/\sigma_{\rm inf}$ for thermal stability as
+a function of $\rb/\rsoi$. This is shown in Fig.~\ref{fig:vwCrit}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{vwCrit.pdf}
+\caption{\label{fig:vwCrit} Critical heating rate required for thermal
+  stability normalized to the velocity dispersion at the sphere
+  influence radius, $\sigma_{\rm soi}$ versus $\rb/\rsoi$, the ratio
+  of the break radius in the stellar density profile to the sphere of
+  influence radius. We assume a core stellar dnsity profile inside of
+  $\rb$, so that $\rhostar\sim r^{-1-\Gamma}$ with $\Gamma=0.1$.}
+\end{figure}
+
 %%% Local Variables: 

### 2015-03-17 ms.tex
Adding to appendix

@@
 ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe some
-analytic results, while in $\S\ref{sec:numerical}$ we describe our numerical results.
-In $\S\ref{sec:discussion}$ we discuss the implications of our results, to topics including...
-In $\S\ref{sec:conclusions}$ we summarize our conclusions.
-Table \ref{table:definitions} provides the definitions of commonly used variables.
-Appendices \ref{app:rs} and XXX provides useful analytic results, while Appendix \ref{app:windheat} describes our method for calculating stellar wind heating and mass input in greater detail.
+analytic results, while in $\S\ref{sec:numerical}$ we describe our
+numerical results.  In $\S\ref{sec:discussion}$ we discuss the
+implications of our results, to topics including...  In
+$\S\ref{sec:conclusions}$ we summarize our conclusions.  Table
+\ref{table:definitions} provides the definitions of commonly used
+variables.  Appendices \ref{app:rs} and \ref{app:be} provides useful
+analytic results, while Appendix \ref{app:windheat} describes our
+method for calculating stellar wind heating and mass input in greater
+detail.
 
@@
 v_{w}^{2}$ significantly exceeds the specific gravitational binding
-energy $\sim \sigma^{2}$.
-In fact, for core galaxies the specific heating rate necessary to produce an unbound outflow can greatly exceed $\sigma^{2}$ due to the additional gravitational potential of stars outside the sphere of influence (Appendix XXX).
+energy $\sim \sigma^{2}$.  In fact, for core galaxies the specific
+heating rate necessary to produce an unbound outflow can greatly
+exceed $\sigma^{2}$ due to the additional gravitational potential of
+stars outside the sphere of influence (Appendix~\ref{app:be}).
 
@@
 \end{align}
-The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
-However, when $v_{\rm w} \lesssim f(r_b/r_{\rm soi})\sigma$ the stagnation radius moves to very large radii, or may not exist at all (see also Fig.~\ref{fig:stag}), resulting in much higher gas densities and inevitable cooling instability.
-The dimensionless function f is approximately unity for cusp galaxies, but increases $\propto (r_b/r_{\rm soi})^{1/2}$ for core galaxies (Fig.~XXX).
+The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two
+lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
+However, when $v_{\rm w} \lesssim f(r_b/r_{\rm soi})\sigma$ the
+stagnation radius moves to very large radii, or may not exist at all
+(see also Fig.~\ref{fig:stag}), resulting in much higher gas densities
+and inevitable cooling instability.  The dimensionless function f is
+approximately unity for cusp galaxies, but increases $\propto
+(r_b/r_{\rm soi})^{1/2}$ for core galaxies (Fig.~\ref{fig:vwCrit}).  
 %Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
@@
 \end{equation}
-independent of $r$.
-A jet with power sufficient to appreciably heat the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim 10^{-6}$) also necessarily has sufficient power to escape the nucler region and propagate to much larger radii.
-Slower outflows from the accretion disk, instead of a collimated relativistic jet, may provide a more promising source of feedback in these systems (e.g.~\citealt{Li+13}).
-
-As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.
-However, given the uncertainty in the efficiency of jet heating, we defer a more detailed discussion to $\S\ref{sec:kinetic}$.
+independent of $r$.  A jet with power sufficient to appreciably heat
+the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim
+10^{-6}$) also necessarily has sufficient power to escape the nucler
+region and propagate to much larger radii.  Slower outflows from the
+accretion disk, instead of a collimated relativistic jet, may provide
+a more promising source of feedback in these systems
+(e.g.~\citealt{Li+13}).
+
+As in the case of Compton heating, kinetic heating could in principle
+`self-regulate' the accretion flow insofar as a lower heating rate
+results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in
+turn may create stronger jet feedback.  However, given the uncertainty
+in the efficiency of jet heating, we defer a more detailed discussion
+to $\S\ref{sec:kinetic}$.
 
@@
 
-Figure \ref{fig:bh_growth} (top panel) also shows that across all black hole masses, Compton heating also cannot prevent average accretion rates which are thermally unstable, i.e.
-$\dot{M}_{\rm C} > \dot{M}_{\rm TI}$.
-In the case of thermal instabilities, nuclear gas may undergo cyclic oscillations of rapid cooling and high accretion rates, followed by quiescent
-periods once gas has been consumed and/or AGN feedback becomes effective.
-Such cycles are proposed to occur on large scales and long timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea possibly supported by, e.g., GALEX observations showing that a small fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
-Similiar cyclic AGN activity have been proposed to occur on the smaller scale of the sphere of influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuarda+15}).
-
-If such cyclic outbursts also manifest on the properties of gas on small, parsec scales, then the large scatter in the accretion rates and hence X-ray luminosities in Fig \ref{fig:miller} could result from the wide range of inflow rates experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts (e.g.~\citealt{Ciotti+10}).
-Due to their deeper potential well, we find that core galaxies are more likely to possess higher accretion rates and potentially be thermally unstable for a fixed wind heating rate than cusp galaxies (Fig.~XXX).
-This could help explain why core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89,   Pellegrini99, Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
-
-If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$ in Fig \ref{fig:miller} represent thermally-unstable galaxies, then many of the upper limits may correspond to a separate ``thermally stable" population, for instance including SgrA*.
-The possibility of a mixed population of stable versus unstable galaxies calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
+Figure \ref{fig:bh_growth} (top panel) also shows that across all
+black hole masses, Compton heating also cannot prevent average
+accretion rates which are thermally unstable, i.e. $\dot{M}_{\rm C} >
+\dot{M}_{\rm TI}$.  In the case of thermal instabilities, nuclear gas
+may undergo cyclic oscillations of rapid cooling and high accretion
+rates, followed by quiescent periods once gas has been consumed and/or
+AGN feedback becomes effective.  Such cycles are proposed to occur on
+large scales and long timescales in elliptical galaxies
+(\citealt{Ciotti+10}), an idea possibly supported by, e.g., GALEX
+observations showing that a small fraction of early-type galaxies in
+the local universe have undergone recent ($< 1-2$ Gyr old) star
+formation episodes (\citealt{Donas+07}).  Similiar cyclic AGN activity
+have been proposed to occur on the smaller scale of the sphere of
+influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuarda+15}).
+
+If such cyclic outbursts also manifest on the properties of gas on
+small, parsec scales, then the large scatter in the accretion rates
+and hence X-ray luminosities in Fig \ref{fig:miller} could result from
+the wide range of inflow rates experienced over the course of a cyclic
+episode between instabilities and periodic nuclear outbursts
+(e.g.~\citealt{Ciotti+10}).  Due to their deeper potential well, we
+find that core galaxies are more likely to possess higher accretion
+rates and potentially be thermally unstable for a fixed wind heating
+rate than cusp galaxies (Fig.~XXX).  This could help explain why core
+galaxies show a wide range of nuclear radio and X-ray luminosities
+(suggesting cyclic accretion episodes), while cusp galaxies are
+confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99,
+  Capetti&Balmaverde05}), consistent with thermally-stable,
+steady-state picture. ({\bf AG: This picture may be dubious...Review
+  the literature but I think that the higher upper bound for cores is
+  just due to a mass selection effect.})
+
+If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$ in Fig
+\ref{fig:miller} represent thermally-unstable galaxies, then many of
+the upper limits may correspond to a separate ``thermally stable"
+population, for instance including SgrA*.  The possibility of a mixed
+population of stable versus unstable galaxies calls into question the
+use of simple extrapolations of power-law fits to the $L_{\rm
+  X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the
+occupation fraction of black holes in low mass galaxies
+(\citealt{Miller+15}).
 
@@
 % %the tabulated black hole mass from the Mbh-Mbulge relation.
-% Fig. 1 of \citealt{Miller+15} plots the observed
+% Fig.1 of \citealt{Miller+15} plots the observed
 % relationship of unresolved x-ray luminosity versus galactic stellar

### 2015-03-17 ms.tex
TDE jets

@@
 
-It is also possible that many of the galactic nuclei from the \citet{Miller+15} sample are not accreting in a steady fashion.
-The efficiency assumed in the right panel of Figure \ref{fig:miller} in some ways represents a maximum value, since it does not take into suppression of the accretion rate due to disk outflows on small scales.
-If the actual X-ray efficiency is lower than assumed, then many of the detections in the case of low SMBH masses, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, would lie even further above above the predicted average value for stable accretion (black line).
-These galaxies either experience significantly lower levels of heating than average galaxies of their mass, or that they are not accreting stably at all.
-Indeed, for the lowest mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow line).
-It is not surprising that this sample is more likely to be thermally unstable as compared to an average galaxy with this black hole mass, because the \citet{Miller+15} sample includes only early-type galaxies with on averager older stellar populations.
+It is also possible that many of the galactic nuclei from the
+\citet{Miller+15} sample are not accreting in a steady fashion.  The
+efficiency assumed in the right panel of Figure \ref{fig:miller} in
+some ways represents a maximum value, since it does not take into
+suppression of the accretion rate due to disk outflows on small
+scales.  If the actual X-ray efficiency is lower than assumed, then
+many of the detections in the case of low SMBH masses, $M_{\bullet}
+\lesssim 10^{8}M_{\odot}$, would lie even further above above the
+predicted average value for stable accretion (black line).  These
+galaxies either experience significantly lower levels of heating than
+average galaxies of their mass, or that they are not accreting stably
+at all.  Indeed, for the lowest mass holes, $M_{\bullet} \lesssim
+10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the
+maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow
+line).  It is not surprising that this sample is more likely to be
+thermally unstable as compared to an average galaxy with this black
+hole mass, because the \citet{Miller+15} sample includes only
+early-type galaxies with on averager older stellar populations.
 
@@
 lost from the surrounding stellar population studied in this paper.
-Gas blow-out by SN Ia cannot prevent the growth of low-mass black holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
-Ia heating (green lines), although Ia heating could play in principle a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the efficiency of Ia heating and whether the galaxy is a core or cusp.
+Gas blow-out by SN Ia cannot prevent the growth of low-mass black
+holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
+Ia heating (green lines), although Ia heating could play in principle
+a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black
+holes, again depending on the efficiency of Ia heating and whether the
+galaxy is a core or cusp.
 
@@
 
-\citet{BergerZauderer+:2012a}  infer a flattening of the gas density profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks qualitiatively similar to that the density profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid line).
-Their inferred  gas profile also shows a break at radii $\sim 0.6$ pc, which in our model corresponds to the break radius of the galaxy and hence would imply a SMBH mass of TINY accroding to the mean relationship from the \citet{Lauer+Faber:2007a} sample.
-More detailed models for the environment, and the implications of our models for CNM profiles for the diversity of radio emission from TDE jets, will be
-explored further in future work.
+\citet{BergerZauderer+:2012a} infer a flattening of the gas density
+profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
+qualitiatively similar to that the density profile we predict for core
+galaxies (Fig.~\ref{fig:profiles}, solid line), although to obtain
+such a flattening on the inferred radial scale, would require a large
+$\Mbh\sim 10^7 \Msun$.  Their inferred gas profile also shows a break
+at radii $\sim 0.6$ pc, which in our model corresponds to the break
+radius of the galaxy and hence would imply an unrealistically small
+SMBH mass $\Mbh\simeq 100\Msun$.  accroding to the mean relationship
+from the \citet{Lauer+Faber:2007a} sample. A more likely explanation
+is that the observed break in the gas density is associated with a
+break in a nuclear star cluster in the galaxy {\bf AGs-ref Carson et
+  al. 2015.}.
+
+More detailed models for the environment, and the implications of our
+models for CNM profiles for the diversity of radio emission from TDE
+jets, will be explored further in future work.
 

### 2015-03-20 ms.tex
fixing the description of sigma

@@
 movement of stars with respect to one another at the characteristic
-velocity of $\sigma \approx \sqrt{GM_{\rm enc}/r}$.  This heating is
+velocity of $\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
+    r}+\sigma_0^2}$, where $\sigma_0$ is a constant. The first term
+corresponds to the velocity dispersion of a power law stellar density
+profile with slope $-1-\Gamma$ in the presence of black hole. The
+second term represents the observed constant velocity dispersion at
+radii outside of the black hole sphere of influence \citep{ChaeBernardi+:2014a}. For a given
+$\Mbh$, we take $\sigma_0^2\approx 3 \sigma_{\Mbh}^2$, where
+$\sigma_{\Mbh}$ is the velocity dispersion from the
+\citet{McConnellMa+:2011a} $\Mbh-\sigma$ relation.  This heating is
 present even in old stellar populations for which mass and energy

### 2015-03-20 windheat.tex
fixing the description of sigma

@@
-% If we assume that a stellar population forms
-% impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
-% $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
-% future time $t$ is given by
-% \begin{equation}
-% f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
-% \end{equation}
-% where the main sequence turnoff mass is approximately
-% \begin{equation}
-% m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
-% \end{equation}
-% For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
-% \begin{equation}
-% f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
-% \end{equation}
-% {\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
-% If we approximate post-main sequence evolution as instantaneous and define $\lambda(\Mstar)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
-% \begin{equation}
-% q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
-% \end{equation}
-% where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} \Mstar\mu(\Mstar)d\Mstar \approx 0.3 M_\odot$.
-Further approximating $\lambda(\Mstar)=0.5$, and using the Salpeter IMF once more, gives
-% \begin{equation}
-% q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
-% \end{equation}
-% This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
-Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
-Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
-Crudely approximating $v_{\rm w}=75~{\rm km~s}^{-1}$ for $m_{\rm T} < 10M_{\odot}$ and $v_{\rm w}=3000~{\rm km~s}^{-1}$ for $m_{\rm T} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss from Wolf-Rayet stars), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
-% {\bf AG:As I previously mentioned this discussion of the eta is not
-%   quite correct...}
-% \begin{figure}
-% \includegraphics[width=\columnwidth]{NickPlot.eps}
-% \caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times \Mstar(r_{\rm s})$, in arbitrary units.
-The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
-Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.
-{\bf NCS: I think these old continuous curves are wrong, need to revise}}
-% \end{figure}
-
-% In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
-% function of time, for three different stellar density profiles $\Gamma
-% = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
-% influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
-% SMBH).  We parametrize the wind velocity as
-% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
-% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
-% yr}}\right). \label{NickV1}
-% \end{equation} This counts Type II SNe heating as ``winds;'' if
-% instead we are in the portion of parameter space where $r_{\rm II}$ is
-% very large, then we use the alternate parametrization
-% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
-% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
-% yr}}\right), \label{NickV2}
-% \end{equation} which only allows short lived Wolf-Rayet stars to
-% contribute to the high-heating mode.  The ``impulsive burst'' mode of
-% star formation produces large ($\sim 10$) differences between the
-% three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
-% smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
-% large.  We also plot, as dotted curves, a simple model for the
-% ``continuous'' mode of star formation, where mass loss is calculated
-% as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
-% energy injection in the wind is calculated as $\bar{v_{\rm
-% w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
-% km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
-% produces small differences from late-time $\dot{M}$ seen in cusp
-% galaxies with impulsive star formation; however, continuous mode star
-% formation decreases late-time $\dot{M}$ by an order of magnitude
-% relative to impulsive star formation in core galaxies.  {\bf NCS: I
-% think this old discussion of MDot in the continuous limit is wrong,
-% need to revise}
-
 \subsection{Single Burst}
@@
 of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
-is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar} \propto
-M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low mass end and at
-$100 \Msun$ on the high mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is
-the corresponding mean stellar mass.
-Our optimistic assumption of 100 per cent thermalization efficiency of stellar winds is at least partially offset by our conservative assumption to neglect energy input from core collapse supernovae, which contribute a comparable energy injection rate to massive stellar winds.
+is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar}
+\propto M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low
+mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ =
+0.35 $\Msun$ is the corresponding mean stellar mass.  Our optimistic
+assumption of 100 per cent thermalization efficiency of stellar winds
+is at least partially offset by our conservative assumption to neglect
+energy input from core collapse supernovae, which contribute a
+comparable energy injection rate to massive stellar winds.
 
-The quantity of mass lost in PMS winds $\Delta M(t)$ is estimated from the expression given by \citet{CiottiOstriker:2007a} (their eq.~[10]),
+The quantity of mass lost in PMS winds $\Delta M(t)$ is estimated from
+the expression given by \citet{CiottiOstriker:2007a} (their eq.~[10]),
 \begin{align}
@@
 
-The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]) as
+{\bf AG: Go back to the old mass loss prescription ASAP so that we don't
+  violate mass conservation!}
+The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on
+the generalization of Reimer's law given in
+\citet{SchroderCuntz:2005a} (their eq.~[4]) as
 \begin{align}

### 2015-03-20 ms.tex
new generozov

@@
 second term represents the observed constant velocity dispersion at
-radii outside of the black hole sphere of influence \citep{ChaeBernardi+:2014a}. For a given
-$\Mbh$, we take $\sigma_0^2\approx 3 \sigma_{\Mbh}^2$, where
-$\sigma_{\Mbh}$ is the velocity dispersion from the
-\citet{McConnellMa+:2011a} $\Mbh-\sigma$ relation.  This heating is
-present even in old stellar populations for which mass and energy
-injection are dominated by AGB winds with low velocities $\ll \sigma$.
-The second term, $v_{w}^{2}$, parameterizes all additional sources of
-heating, including faster main sequence or Wolf-Rayet stellar winds,
-spin-down energy from millisecond pulsars, supernovae, AGN feedback,
-etc.  As will be discussed in $\S\ref{sec:heating}$, the value of
-$v_{w}$ will in general depend on the SMBH mass and the age of the
-stellar population.  We further assume that $v_w$ is constant with
-radius, i.e. that the volumetric heating rate is proportional to the
-local stellar density.
+radii outside of the black hole sphere of influence
+\citep{ChaeBernardi+:2014a}. For a given $\Mbh$, we take
+$\sigma_0^2\approx 3 \sigma_{\Mbh}^2$, where $\sigma_{\Mbh}$ is the
+velocity dispersion from the \citet{McConnellMa+:2011a} $\Mbh-\sigma$
+relation.  This heating is present even in old stellar populations for
+which mass and energy injection are dominated by AGB winds with low
+velocities $\ll \sigma$.  The second term, $v_{w}^{2}$, parameterizes
+all additional sources of heating, including faster main sequence or
+Wolf-Rayet stellar winds, spin-down energy from millisecond pulsars,
+supernovae, AGN feedback, etc.  As will be discussed in
+$\S\ref{sec:heating}$, the value of $v_{w}$ will in general depend on
+the SMBH mass and the age of the stellar population.  We further
+assume that $v_w$ is constant with radius, i.e. that the volumetric
+heating rate is proportional to the local stellar density.
 

### 2015-03-23 ms.tex
correcting more of the analytics

@@
 T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
-  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7}{7-2\nu} \frac{\mu m_p
-   v_{w}^{2}}{2k}\nonumber\\ 
+  \tilde{v}_{w}^{2}}{2k} \approx \frac{\gamma-1}{\gamma}\frac{\mu
+  m_p v_w^2}{2k} \frac{3+8\Gamma}{3+8\Gamma-6\nu} \nonumber\\ 
  &\approx
@@
 where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
-s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
+s$^{-1}$), $v_w\gg\sigma_0$,  and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
     s}}$ is the density power-law slope at $r = r_{\rm s}$.
@@
 \begin{align}
-  \rs=\frac{G \Mbh}{\densSlope
-    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
-    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
+ \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[2
+    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
 \label{eq:stag_analytic}
@@
 \begin{align}
-  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
-    9
+  &\rs \underset{v_w \gtrsim \sigma}\approx
+  \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
+    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}
+  \approx \begin{cases} 9
     \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
-    4
- \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
+    4 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear & \text{cusp},
   \end{cases}

### 2015-03-23 ms.tex
Fixing stagnation radius description in text.

@@
 
-If the SMBH dominates the gravitational potential at the stagnation
-radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
-resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
-  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
-(\ref{eq:stag_analytic}) simplifies to
+If the stagnation radius is well inside the influence radius, $\rsoi$,
+then $\Mstar/\Mbh|_{\rs}\ll1$. Also, equation~\eqref{eq:rsRinf}
+implies that $v_w\gg \sigma_0$, since
+$\rs/\rsoi=\frac{k(\Gamma)}{3\zeta^2}$, where
+$\zeta=\sqrt{\frac{v_w^2+\sigma_0^2}{\sigma_0^2}}$ and $k(\Gamma)$ is
+of order unity then equation~\eqref{eq:stag_analytic} simplifies to
 \begin{align}
@@
 
-In the opposite limit of weak heating ($v_{w} \ll \sigma$), the
-stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not
-exist at all, formally implying that the entire ISM of the galaxy is
+In the opposite limit of weak heating ($v_{w} \ll \sigma_0$),
+the stagnation radius moves towards the break radius, $\rb$ in the
+stellar density profile, formally implying that almost entire ISM of the galaxy is
 accreting.  This result makes intuitive sense: gas is supplied to the
@@
 v_{w}^{2}$ significantly exceeds the specific gravitational binding
-energy $\sim \sigma^{2}$.  In fact, for core galaxies the specific
-heating rate necessary to produce an unbound outflow can greatly
-exceed $\sigma^{2}$ due to the additional gravitational potential of
-stars outside the sphere of influence (Appendix~\ref{app:be}).
+energy.
+%   In fact, for core galaxies the specific
+% heating rate necessary to produce an unbound outflow can greatly
+% exceed $\sigma^{2}$ due to the additional gravitational potential of
+% stars outside the sphere of influence (Appendix~\ref{app:be}).
 

### 2015-03-27 be.tex
analytics...

@@
 $\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
-$\rb$. {\bf AG: 2s with question marks would not be included if the $G
-\Mstar/r$ }
+$\rb$.
 
 \begin{align}
-&\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} + \frac{G
+  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} +
+  \frac{G
     M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
   &-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
-&+\frac{v_w^2}{2}-\frac{G \Mbh}{2 r_s} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1} -\frac{G M_\star}{2? r_s} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
+  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
+  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
+  \nonumber\\
+  &-\frac{G M_\star}{r_s}
+  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
 \end{align}
@@
 \biggl[
-  \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
-  -\frac{1}{2} \frac{3-\delta}{2-\delta} \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
+  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
+  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
   -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
-  -w \frac{(2-\delta)(3-\delta)-2?(3-\beta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
+  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
 \biggr].
@@
 
-Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta$ is
-the ratio of the extra heating rate to the stellar velocity in of the
-influence radius $\rsoi$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
+Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{(v_w^2+\sigma_0^2)/\sigma_0}$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
 $\delta$ is the power law slope of the stellar density profile inside

### 2015-03-27 be.tex
appendix...

@@
 
-Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{(v_w^2+\sigma_0^2)/\sigma_0}$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
+Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
 $\delta$ is the power law slope of the stellar density profile inside
@@
 
-For a given $\zeta$ we define a critical $\rs/\rsoi=min{
-  \frac{frac{7}{2}-\densSlope}{\densSlope \zeta^2, 1}}$ for thermal stability, 
-where the first term in the brackets corresponds to twice the value
-predicted by equation~\eqref{eq:rsRinf}, in the limit the stellar mass
-as $\rs$ is small compared to $\Mbh$. This prescription is somehwat
-ad hoc, but...{\bf AG--some motivation...}
+For sufficiently large radii ($x$), the expression above always
+becomes negative, which means that a break in the stellar density
+profile is necessary in order to obtain an outflow. For a given
+$\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such that if
+$\zeta>\zeta_c$, an outflow will be possible from any
+radius. On the other hand if $\zeta<\zeta_c$, then there is a
+minimum radius from which an outflow is possible, so that we have a
+constraint on $\rs/\rsoi$.
 
-Then from equation~\eqref{eq:enthAnal} we may obtain the critical
-wind heating parameter $v_{w, \rm crit}/\sigma_{\rm inf}$ for thermal stability as
-a function of $\rb/\rsoi$. This is shown in Fig.~\ref{fig:vwCrit}
+For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
+($v_w\simeq\sigma_0$).  On the other hand for core galaxies
+($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$. We also
+find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
+for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
+less than this value the gas enthalpy would become negative inside of
+the break radius which is clearly unphysical.  This may be roughly
+approximated using (see Fig.~\ref{fig:rbRinf})
+
+\begin{align}
+&\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
+&\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
+\label{eq:rsRinfCrit}
+\end{align}
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{vwCrit.pdf}
-\caption{\label{fig:vwCrit} Critical heating rate required for thermal
-  stability normalized to the velocity dispersion at the sphere
-  influence radius, $\sigma_{\rm soi}$ versus $\rb/\rsoi$, the ratio
-  of the break radius in the stellar density profile to the sphere of
-  influence radius. We assume a core stellar dnsity profile inside of
-  $\rb$, so that $\rhostar\sim r^{-1-\Gamma}$ with $\Gamma=0.1$.}
+\includegraphics[width=\columnwidth]{rbRinf.pdf}
+\caption{\label{fig:rbRinf} Mininmum value for ratio of the stagnation
+  radius to the influence radius, $\rs/\rsoi$ for core galaxies
+  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
+  positive out to the break radius $\rb$. The solid lines correspond
+  to the constraint computed numerically from
+  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
+  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
+  x-intercept of each curve corresponds to the critical $\zeta$,
+  $\zeta_c$ above which an outflow is possible from any radius}
 \end{figure}

### 2015-03-27 be.tex
more changes to the Bernoulli appendix.

@@
 \frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \left(\frac{v^2}{2} + \Phi
-    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi
+    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi,
 \label{eq:enCons}
@@
 
-Where $\kew=v_w^2+\sigma^2\simeq v_w^2+\frac{G M_{\rm enc}(r)}{r}$ and
-$\Menc$ is the sum of the black hole mass and the stellar mass.
+Where $\vw^2=v_w^2+\sigma^2= v_w^2+\frac{3}{\Gamma+2}\frac{G
+  \Mbh}{r}+\sigma_0^2$.
 
@@
 
-Then one obtains for the mass flux, $f$
+Then one obtains for the mass flux, $f=r^2 \rho v$,
 
 \begin{align}
- f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right]
+ f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right].
  \label{eq:massFlux}
@@
 \begin{align}
-\Phi= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\rs} \rhostar(dr') r'
-dr'.
+\Phi&= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\infty} \rhostar(r') r'
+dr'.\nonumber\\
+&\simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr'
 \label{eq:Phi}
@@
 
-Note our unconventional choice of gauge: the upper limit of the
-integral on the right hand side is $\rs$ whereas conventionally the
-upper limit is taken to be $\infty$. This means that our definition
-will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
-our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
-gauge invariant.
+Where in the scond line we have neglected the contribution of the
+stars outside of the break radius, $\rb$, to the gravitational potential.
+
+% Note our unconventional choice of gauge: the upper limit of the
+% integral on the right hand side is $\rs$ whereas conventionally the
+% upper limit is taken to be $\infty$. This means that our definition
+% will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
+% our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
+% gauge invariant.
 
 Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
-and~\eqref{eq:Phi}, we may obtain an expression for the enthalpy,
-$\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
-$\rb$.
+and~\eqref{eq:Phi}, we may obtain an expression for the Bernoulli
+parameter of the gas, $\ke+\gammaf \frac{p}{\rho} +\Phi$ of the gas inside
+of the break radius $\rb$.
 
 \begin{align}
-  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} +
-  \frac{G
-    M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
-  &-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
+  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} +\Phi = \nonumber\\
+  &-U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
   &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
@@
 \begin{multline}
-  \frac{v^2}{2}+\gammaf \frac{p}{\rho}
+  \frac{v^2}{2}+\gammaf \frac{p}{\rho}+\Phi
 =\frac{G \Mbh}{\rs} 
 \biggl[
-  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
+  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}
   -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
-  -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
+  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2 -\delta} 
   -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
@@
 
-For sufficiently large radii ($x$), the expression above always
-becomes negative, which means that a break in the stellar density
-profile is necessary in order to obtain an outflow. For a given
-$\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such that if
-$\zeta>\zeta_c$, an outflow will be possible from any
-radius. On the other hand if $\zeta<\zeta_c$, then there is a
-minimum radius from which an outflow is possible, so that we have a
-constraint on $\rs/\rsoi$.
+% For sufficiently large radii ($x$), the expression above always
+% becomes negative, which means that a break in the stellar density
+% profile is necessary in order to obtain an outflow.
+ For a given $\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such
+ that if $\zeta>\zeta_c$, an outflow will be possible from any
+radius, since the Bernoulli parameter will be positive inside of the
+break radius. On the other hand if $\zeta<\zeta_c$, then there is a
+minimum value of $(\rs/\rsoi)_{\rm min}$. If we have had
+$\rs/\rsoi<(\rs/\rsoi)_{\rm min}$, then the Bernoulli parameter would
+become negative inside of $\rb$ and no outflow would be possible.
 
@@
 ($v_w\simeq\sigma_0$).  On the other hand for core galaxies
-($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$. We also
-find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
-for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
-less than this value the gas enthalpy would become negative inside of
-the break radius which is clearly unphysical.  This may be roughly
-approximated using (see Fig.~\ref{fig:rbRinf})
+($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$, see the top
+panel of Fig.~\ref{fig:zetaCrit}. For values of $\zeta<\zeta_c$, the
+stagnation radius rapidly approaches the break radius as shown in the
+bottom panel of Fig.~\ref{fig:zetaCrit}.
+% We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
+% for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
+% less than this value the gas enthalpy would become negative inside of
+% the break radius which is clearly unphysical.  This may be roughly
+% approximated using (see Fig.~\ref{fig:rbRinf})
 
-\begin{align}
-&\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
-&\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
-\label{eq:rsRinfCrit}
-\end{align}
+% \begin{align}
+% &\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
+% &\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
+% \label{eq:rsRinfCrit}
+% \end{align}
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{rbRinf.pdf}
-\caption{\label{fig:rbRinf} Mininmum value for ratio of the stagnation
+\includegraphics[width=\columnwidth]{zetaCrit.pdf}
+\caption{\label{fig:zetaCrit} Mininmum value for ratio of the stagnation
   radius to the influence radius, $\rs/\rsoi$ for core galaxies

### 2015-03-27 ms.tex
fixing a few typos
analytics...
more changes to the Bernoulli appendix.

@@
 \begin{align}
- \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[2
+ \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[4
     \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
@@
 
-In the opposite limit of weak heating ($v_{w} \ll \sigma_0$),
-the stagnation radius moves towards the break radius, $\rb$ in the
-stellar density profile, formally implying that almost entire ISM of the galaxy is
-accreting.  This result makes intuitive sense: gas is supplied to the
-nuclear by stars which are gravitationally bound to the black hole, so
-outflows are possible only if the specific heating rate $\sim
-v_{w}^{2}$ significantly exceeds the specific gravitational binding
-energy.
+In the opposite limit of weak heating ($v_{w} \ll \sigma_0$), the
+stagnation radius moves towards the break radius, $\rb$ in the stellar
+density profile, formally implying that almost entire ISM of the
+galaxy is accreting.  This result makes intuitive sense: gas is
+supplied to the nuclear by stars which are gravitationally bound to
+the black hole, so outflows are possible only if the specific heating
+rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational
+binding energy.
 %   In fact, for core galaxies the specific
@@
 ... & ... & 0.8 & 100 & 3.8 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
-... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1
-  \times 10^{ -3 }}$ \\
+... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1  \times 10^{ -3 }}$ \\
 ... & 450 & 0.8 & 100 & 0.72 & $ 4.4 \times 10^{ -4 }$ & 4 \\
@@
 ... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &
-70 \\
+...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &70 \\
 ...$^{\ddagger}$ & ... & 0.8 & 100 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 73 \\
@@
 ... & ... & 0.8 & 400 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 58 \\
-... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{
-  -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
+... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
   \hline
  & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
-$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2
-\times 10^{ -6 }$ & 99 & Conv\\
+$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2\times 10^{ -6 }$ & 99 & Conv\\
 ... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
@@
   \includegraphics[width=\columnwidth]{rs.eps}
-  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
+  \caption{\label{fig:stag} Stagnation radius
     $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
@@
 
-% Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.
-Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.
-What could cause this dependence?
-Maybe Ia SNa...
-
-% This is shown in the top panel Figure~\ref{fig:bh_xray}. The
-% relationship from \citealt{Miller+15} and their detection
-% upper limits are the black and blue solid lines
-% respectively. The points correspond to the $\dot{M} c^2$ for our
-% solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
-% each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
-% heating expected from main sequence the stellar winds and MSPs. If
-% $L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
-% bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
-% 10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
-% \citealt{Miller+15}.
-
-% One possible solution that the wind mass loss rate $\eta$ increases
-% with $\Mbh$, as would be expected if low mass SMBH preferentially
-% hosted younger stellar populations.  Another possible explanation is
-% that the effective heating rate of the CNM $v_{w}$ decreases
-% with decreasing SMBH mass.  This could again be due to an older
-% stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
-% sources such as SN Ia and millisecond pulsars.
-% {\bf AG given our new results on stellar wind heating as a function of
-% Mbh. It seems like the first statement is indeed true but I suspect
-% vwO actually increases for low Mbh and that this effect actually dominates.}
-%, or it could be due to the fact that Ia occur too infrequently inside
-%the stagnation radius for low mass black holes.
-%AG-We now think that SNe Ia would become important only at the
-%highest values of Mbh.
-%AG-Note sure where the best place for this discussion would
-%be--here or after presenting the comparisons with Miller et al.
-
-%% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
-
-% \subsubsection{Comparison to measured temperature and density profiles}
-% \citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.
-\citet{RussellMcNamara+:2013a} performed a similar analysis with a somewhat enlarged galaxy sample.
-Interestingly, these works find a correlation between the accretion rate inferred assuming Bondi accretion and the AGN jet power, which is estimated by the PdV work required to inflate observed cavities in the X-ray emitting gas.
-% % At some point it would be useful to describe the differences between
-% % these two sets of observations \citealt{RussellMcNamara+:2013a}
-% % tries several different extrapolation schemes for the gas density,
-% % and finds that that the uncertainty in extrapolating the density
-% % profile is the dominant source of uncertainty in measuring the
-% % accretion rate. Find total number which overlaps once the Russell
-% % galaxies are included...
-
-% Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.
-We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
-The results of this exercise are presented in Fig.~\ref{fig:allen_compare}.
-
-% Note that we have two free parameters ($\eta$ and $\vwO$) in our
-% model, which implies that we can always match the observed temperature
-% and densities at at least one point.  As a general rule, we find that
-% a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
-% with the observed temperatures.  We now highlight results for specific
-% galaxies.
-% % Thus, we choose $\vwO=500$ km/s.  We choose an
-% % $\eta$ so that our solution would be consistent with the observed
-% % density profiles. The comparison is shown in
-% %% AG-The chosen properties, in particular eta may be summarized in a tabe.
-% %% AG-Mention rising temperature profiles on large scales.
-
-% \begin{itemize}
-% % \item \emph{NGC4486} %eta=0.2
-% %   On scales of $\sim1$ kpc the density profile in
-% %   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
-% %   has a break in the gas density at $\sim 300$ pc--near the location
-% %   of the Nuker break radius for this galaxy at 560 pc. There is an
-% %   observed break in the density, but on a scale of a few kpc.
-
-% %   The temperature is assumed to be flat from the resolution limit
-% %   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
-% %   increases monotonically towards the galactic center. This increase
-% %   is due to the increased velocity dispersion (and thus increased
-% %   heating) towards the galactic center.
-
-% \item \emph{NGC5813} %eta=0.1 
-%   The observed density profile (\citealt{RussellMcNamara+:2013a}) is
-%   shallower than our calculated density profile, which has a sharp
-%   break at $\sim$0.1 kpc, the location of the break radius in the
-%   Nuker profile (this is the radius where the stellar light profile
-%   transitions from a shallower inner power law slope to a steeper
-%   outer power law slope).
-
-%   For this galaxy we found that we could reproduce the observed
-%   temperature on large scales with $\vwO=500$ km/s. The increased
-%   velocity disperision towards the galactic center results in a sharp
-%   increase in $T$ at small radii, which is not captured in the
-%   observations due to resolution issues.
-% \end{itemize}
-
-% %It would be nice to have error bars for the observational points in this plot...
-% \begin{figure*}
-%   \includegraphics[width=\columnwidth]{NGC5813_T.eps}
-%   \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
-%   \caption{\label{fig:allen_compare} Comparison of the radial profiles
-%     (blue lines) of electron number density $n_e$ and temperature $T$
-%     to the measured values (black square) in \citet{AllenDunn+:2006a}
-%     and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
-%     power law extrapolations of our profiles. Note that in going from
-%     $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
-%   %% AG in the future we will have to be carfeful of the mean molecular weight.
-% \end{figure*}
-
-% \subsubsection{Comparison with observed X-ray Luminosity-Mass
-%   Relation}
-% %Note currently I reverse-engineer the stellar mass from the black
-% %hole mass inferred from M-sigma; however, it would be better to use
-% %the tabulated black hole mass from the Mbh-Mbulge relation.
-% Fig.1 of \citealt{Miller+15} plots the observed
-% relationship of unresolved x-ray luminosity versus galactic stellar
-% mass for a sample of quiescent galaxies. We may construct a similar
-% relationship with our own sample using the inferred accretion rates
-% from our solutions.  To infer an x-ray luminosity for each solution,
-% we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
-% 10^{-7}$, which gives x-ray luminosities comparable to
-% those in \citealt{Miller+15}. We also try an alternate
-% prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
-% take $L_x=2 \times 10^{-4} (\eddr) \Mdot c^2$.
-
-% We must make choose a $\vwO$ for each galaxy.  We select $\vwO$=200
-% km/s if $\rs<\rIa$ for this solution, $\vwO$=500 km/s if $\rs>\rIa$
-% for this solution, or exclude it.  At low $\Mbh$ we have $\vwO$=200
-% km/s and at high $\Mbh$ we have $\vwO$=500 km/s.  Note that much of
-% our sample is excluded in this Fig., since for $\vwO$=200 km/s we
-% would have $\rs>\rIa$ and four $\vwO$=500 km/s we would have
-% $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$ would be
-% inconsistent with the assumed level of heating).
-
-% %AG-power law may be closer to 1.4 & 1.8 than to 1.5 & 2.
-% Our results are plotted in Fig.~\ref{fig:bh_xray}. In our model
-% there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
-% \citealt{Miller+15}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
-% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{Miller+15} finds
-% that $L_x \propto M_{\rm gal}^{0.7-0.8}$.
-
 \section{Conclusions}
 \label{sec:conclusions}
-
-% Apologies: 
-% \begin{itemize}
-% \item{we assume that average star formation histories correspond to those experienced in the nuclear region.  }
-
-% \item{ Do nuclear star clusters in other galaxies look like scaled
-%     up/down versions of the one in our own galaxy? If so this would
-%     imply a radial gradient in the average of the stellar population
-%     which would imply a heating which would be dependent on radius.  }
-
-% \end{itemize}
-
-% However, \citet{McCourt+12} argue that even if cooling is exactly
-% balanced by heating everywhere, there is still a local thermal
-% instability that operates to turn hot gas into cold clouds.  However,
-% this local instability only causes a significant local drop-out of
-% mass from the hot medium (to low-T clouds), if the cooling timescale,
-% \begin{align}
-% \frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
-% \end{align} 
-% is locally shorter than the approximately 10 times the free-fall
-% timescale $t_{\rm ff}$, where the last equality is evaluated at the
-% stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
-% (\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
-%   crit}$ is also the condition for local instability, although the
-% prefactor may be slightly different.
-
-% If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.
-There are two kinds of ``instabilities", global and local.
-The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e.
-the entire CNM accretes.
-In
-% practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.
-This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.
 
@@
 
-  \section{Analytic expression for specific enthalpy of gas}
-  {\bf AG: double check that what we are deriving here is actually
-    specific enthalpy}
+  \section{Analytic expression for Bernoulli parameter of gas}
   \label{app:be}

### 2015-03-27 be.tex
caption

@@
 \includegraphics[width=\columnwidth]{zetaCrit.pdf}
-\caption{\label{fig:zetaCrit} Mininmum value for ratio of the stagnation
-  radius to the influence radius, $\rs/\rsoi$ for core galaxies
-  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
-  positive out to the break radius $\rb$. The solid lines correspond
-  to the constraint computed numerically from
-  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
-  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
-  x-intercept of each curve corresponds to the critical $\zeta$,
-  $\zeta_c$ above which an outflow is possible from any radius}
+\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
+  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$. If $\zeta<\zeta_c$ outflows are
+  only possible if the ratio of the stagnation radius to the influence
+  radius exceeds a minimum value. Plotted as a function of the ratio
+  of the break radius to the influence radius ($\rb/\rsoi$) {\emph Bottom
+    Panel:} Mininmum value for ratio of the stagnation radius to the
+  influence radius, $\rs/\rsoi$ for core galaxies ($\Gamma=0.1$)
+  derived by requiring enthalpy of the gas to remain positive out to
+  the break radius $\rb$. This is calculated numerically from
+  equation~\eqref{eq:enthAnal}. The x-intercept of each curve
+  corresponds to the critical $\zeta_c$}
 \end{figure}

### 2015-03-28 be.tex
spelling

@@
-We assume that the stellar density profile follows a broken power law
-with the stellar density $\rhostar\sim r^{-1-\Gamma}= r^{-\delta}$ inside of the
-break radius $\rb$, where ($0<\Gamma<1$). We derive an expression for
-the specific enthalpy of the gas, $\ke +\gammaf \frac{p}{\rho}$ as a
-function of $\zeta=v_w/\sigma$, $x=r/r_s$, and $r_s/\rsoi$. We show
-that if the break radius, $\rb$ goes to infinity this quantity
-necessarily goes to infinity as the potential well becomes infinitely
-deep, hence a break radius is necessary for an outflow to be possible.
+We derive an expression for the bernoulli parameter of the gas, $\ke
++\gammaf \frac{p}{\rho}+\Phi$, assuming that the stellar density
+profile $\rhostar\sim r^{\delta}$ inside of the break radius $\rb$.
 

### 2015-03-28 ms.tex
spelling

@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaching the viscinity of the SMBH
+(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaching the vicinity of the SMBH
 (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
@@
 simple analytic expressions that prove useful in exploring whether
-cooling instabilties manifest across the expected range of galaxy
+cooling instabilities manifest across the expected range of galaxy
 properties, or whether other (non-AGN) forms of feedback can result in
-steady accretion.  Even if cooling instabilties develop on galactic
+steady accretion.  Even if cooling instabilities develop on galactic
 scales over longer $\sim$ Gyr timescales, a state of
@@
 $M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
-$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
+$M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
 $q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
@@
   eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
-the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
+the conductivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
 classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
@@
 \end{align}
- in conjuction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:rs_simple}), one derives
+ in conjunction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:rs_simple}), one derives
 \begin{align}
@@
 
-Our analytic derviations neglect the effects of heat conduction, an assumption we now check.
+Our analytic derivations neglect the effects of heat conduction, an assumption we now check.
 The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
@@
 $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a
-diagnostic of thermal instabilty for the entire solution.
+diagnostic of thermal instability for the entire solution.
 
@@
 is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  We show
-in $\S\ref{sec:combined}$ that for the case of quasi-continueous star
+in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
 formation representative of the average star formation history of loss
@@
 \lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the most optimistc assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
+under the most optimistic assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
 On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
@@
 the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim
-10^{-6}$) also necessarily has sufficient power to escape the nucler
+10^{-6}$) also necessarily has sufficient power to escape the nuclear
 region and propagate to much larger radii.  Slower outflows from the
@@
 \gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just
-preceeding eq.~[\ref{eq:eddr_Ia}]).  This is only possible if the Ia
+preceding eq.~[\ref{eq:eddr_Ia}]).  This is only possible if the Ia
 heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally
@@
 The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for galaxies with the same mass black hole by almost two orders of magnitude.
-This discrepency can be understood by the fact that star formation in the central parsec of the Galaxy is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
+This discrepancy can be understood by the fact that star formation in the central parsec of the Galaxy is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
 Such a star formation history is better described as a `burst' of stars, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
@@
   edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
-least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
+least three effects: (1) intrinsic scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
   bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
@@
 hole mass, because the \citet{Miller+15} sample includes only
-early-type galaxies with on averager older stellar populations.
+early-type galaxies with on average older stellar populations.
 
@@
 the local universe have undergone recent ($< 1-2$ Gyr old) star
-formation episodes (\citealt{Donas+07}).  Similiar cyclic AGN activity
+formation episodes (\citealt{Donas+07}).  Similar cyclic AGN activity
 have been proposed to occur on the smaller scale of the sphere of
@@
 region, triggered either by galaxy mergers associated with the
-hierachical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this, \citet{Kauffmann&Heckman09} find that the growth of low mass black holes is dominated by young stellar bulges which have a log normal
+hierarchical growth of structure or thermal instabilities on larger,
+galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this,
+\citet{Kauffmann&Heckman09} find that the growth of low mass black
+holes is dominated by young stellar bulges which have a log normal
 distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
-0.01$. That this distribution is insensitive to galaxy properties suggestes that it is set by SMBH feedback instead of the nuclear gas supply.
+0.01$. That this distribution is insensitive to galaxy properties
+suggests that it is set by SMBH feedback instead of the nuclear gas
+supply.
 
@@
 (yellow line) exceeds the Hubble time across all SMBH masses
-highlights the fact that signifcant black hole growth in the local
+highlights the fact that significant black hole growth in the local
 universe cannot result from thermally-stable steady accretion of gas
@@
 profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
-qualitiatively similar to that the density profile we predict for core
+qualitatively similar to that the density profile we predict for core
 galaxies (Fig.~\ref{fig:profiles}, solid line), although to obtain
@@
 radius of the galaxy and hence would imply an unrealistically small
-SMBH mass $\Mbh\simeq 100\Msun$.  accroding to the mean relationship
+SMBH mass $\Mbh\simeq 100\Msun$.  according to the mean relationship
 from the \citet{Lauer+Faber:2007a} sample. A more likely explanation
@@
     \begin{enumerate}
-    \item Overall the accretion rate onto the cetral SMBH will be strongly
+    \item Overall the accretion rate onto the central SMBH will be strongly
     tied to the properties of the stellar population (e.g. age) within
     the sphere of influence of the black hole. Thus, our model cannot
-    say anything definitive about the mode accretion for indivudual
+    say anything definitive about the mode accretion for individual
     galaxies which may have significant variations about our assumed

### 2015-03-28 ms.tex
more spelling

@@
 classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
-cgs units).  The flux limitor $\psi = \kappa_{\rm spitz} \nabla
+cgs units).  The flux limiter $\psi = \kappa_{\rm spitz} \nabla
 T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free

### 2015-03-29 be.tex
conclusions,

@@
 +\gammaf \frac{p}{\rho}+\Phi$, assuming that the stellar density
-profile $\rhostar\sim r^{\delta}$ inside of the break radius $\rb$.
+profile $\rhostar\sim r^{-1-\Gamma}=r^{-\delta}$ inside of the break radius $\rb$
 
@@
 
-Where $\vw^2=v_w^2+\sigma^2= v_w^2+\frac{3}{\Gamma+2}\frac{G
-  \Mbh}{r}+\sigma_0^2$.
+Where $\vw^2=\sigma^2+v_w^2= \frac{3}{1+\delta}\frac{G
+  \Mbh}{r}+\sigma_0^2+v_w^2$. The first term to the black hole
+velocity dispersion, the second term corresponds to the velocity
+dispersion of stars which we rake to be constant, and $v_w$
+corresponds to any additional heating.
 
-Now integrate both sides with respect from r to the stagnation radius
+Now integrate both sides of equation~\eqref{eq:enCons} with respect from r to the stagnation radius $\rs$.
 
@@
 proportional to the stellar density. Let $x=r/\rs$ and $q_o= q
-(\rs)$. Then $q=q_o x^{-\delta}$.
-
-Then one obtains for the mass flux, $f=r^2 \rho v$,
+(\rs)$. Then $q=q_o x^{-\delta}$. Thus,
 
@@
 
-Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
+Recall that $\rs$ is the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
 $\delta$ is the power law slope of the stellar density profile inside
@@
 break radius. On the other hand if $\zeta<\zeta_c$, then there is a
-minimum value of $(\rs/\rsoi)_{\rm min}$. If we have had
+minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$. If we have had
 $\rs/\rsoi<(\rs/\rsoi)_{\rm min}$, then the Bernoulli parameter would
@@
 ($v_w\simeq\sigma_0$).  On the other hand for core galaxies
-($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$, see the top
-panel of Fig.~\ref{fig:zetaCrit}. For values of $\zeta<\zeta_c$, the
-stagnation radius rapidly approaches the break radius as shown in the
-bottom panel of Fig.~\ref{fig:zetaCrit}.
+($\Gamma$=0.1, $\delta$=1.1) we find $\zeta_c\simeq
+(\rb/\rsoi)^{0.44}$, see the top panel of Fig.~\ref{fig:zetaCrit}. For
+values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches
+the break radius as shown in the bottom panel of
+Fig.~\ref{fig:zetaCrit}.
 % We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum

### 2015-03-29 ms.tex
conclusions,

@@
 rate from stellar and black hole velocity dispersion \\
-$v_{w}$ & Total heating parameter, excluding heating rate from velocity dispersion \\
+$v_{w}$ & Total heating parameter, excluding heating rate from
+velocity dispersion \\
+$\sigma_0$ & Stellar velocity dispersion--assumed to be constant.\\
+$\zeta$ & $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$\\
 $r_{s}$ & Stagnation radius (where gas radial velocity goes to zero) \\
@@
 $\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
-$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
-$\sigma(r)$ & stellar velocity dispersion \\
+$\Gamma$ & power-law slope of radial stellar surface brightness
+profile interior to the break radius \\
+$\delta$ & power-law slope of the 3d stellar density profile inside of
+the break radius. $\delta=\Gamma+1$.\\
 $\dot{M}$ & mass accretion rate \\
@@
 $t_{\rm h}$ & Hubble timescale \\
-$\nu$ & gas density power-law slope at the stagnation radius (eq.~[\ref{eq:densSlope}]) \\
+$\nu$ & gas density power-law slope at the stagnation radius
+(eq.~[\ref{eq:densSlope}]) \\
 \hline
@@
   %lower vw except for very young stellar populations.
+  \item The gas will be divided between an accretion flow and an
+    outward flow at the stagnation radius, $\rs$. In a steady state
+    the gas inflow rate towards the hole will be proportional to the
+    stellar mass enclosed inside of $\rs$. 
+  \item The location of the stagnation radius and thus the accretion
+    rate is quite sensitive to the effective heating rate of the
+    gas. In our model gas is supplied by stellar winds and the kinetic
+    energy of the winds is thermalized as the winds
+    collide. Supernovae and AGN feedback may provide additional
+    sources of heating. Each source of heating is related to the star
+    formation history of the galaxy.  For example, a galaxy with star
+    formation within the last $\sim10^7$ years would have mass
+    injection from very fast stellar winds ($w_w\simeq 1000$ km/s). In
+    contrast, an older population would have heating only from AGN
+    feedback and supernovae.
+
+    Quantitatively $\rs\sim v_w^{-2}$, which implies $\Mdot\sim
+    v_w^{-3.8 (-2.4)}$ for core (cusp galaxies). However, $\Mdot$ may
+    increase more rapidly for small $v_w$ for two reasons. (1) When
+    $v_w$ becomes comparable to the stellar velocity dispersion, the
+    gas inside of the break radius inside of the break radius inside
+    of the stellar density profile is bound and cannot move
+    outflow. (2) For $v_w\simeq200 $ km/s the gas may become thermally
+    unstable and there may be a cycle of alternating high and low
+    accretion rates onto the BH as described in...{\bf AG: Fill in}
+
   \item We find that for $\Mbh\gsim 10^6 \Msun$ and $\Mbh\lsim 10^8
@@
     nucleus. The in turn would vary systematically with $\Mbh$.
-  \item We expect within scatter in nuclear x-ray luminosities at
+  \item We expect scatter in nuclear x-ray luminosities at
     fixed $\Mbh$ from (1) stochastic variation in star formation

### 2015-03-29 ms.tex
conclusions...

@@
 
-  \item We find that for $\Mbh\gsim 10^6 \Msun$ and $\Mbh\lsim 10^8
-    \Msun$, $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim
-    0.5 \, (0.8)$ for core (cusp) galaxies, 
-    following average star formation histories measured in
-    cosmological simulations \citep{MosterNaab+:2013a}. This is in
+  \item We find that galaxies with $\Mbh\gsim 10^6 \Msun$ and
+    $\Mbh\lsim 10^8$ following average star formation histories
+    measured in cosmological simulations \citep{MosterNaab+:2013a}
+    have sufficient recent star formation to have an effective
+    $v_w\simeq 1000$ km/s. $\eddr \propto \Mbh^{\alpha}$ with
+    $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies This is in
     tension observations of nuclear X-ray luminosity which suggest
@@
     nucleus. The in turn would vary systematically with $\Mbh$.
+
+    For $\Mbh\gsim 10^8 \Msun$, the flow from stellar winds onto the
+    BH is more susceptible to thermal instability due to the lower
+    effective wind velocity $v_w$. 
   \item We expect scatter in nuclear x-ray luminosities at

### 2015-03-29 be.tex
more general relationship for zeta_crit.

@@
 ($v_w\simeq\sigma_0$).  On the other hand for core galaxies
-($\Gamma$=0.1, $\delta$=1.1) we find $\zeta_c\simeq
-(\rb/\rsoi)^{0.44}$, see the top panel of Fig.~\ref{fig:zetaCrit}. For
-values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches
-the break radius as shown in the bottom panel of
-Fig.~\ref{fig:zetaCrit}.
+($\Gamma$=0, $\delta$=1) we find $\zeta_c\simeq
+(\rb/\rsoi)^{0.5}$. More generally, we find $\zeta_c\sim
+(\rb/\rsoi)^{0.5(1-\Gamma)}$ (see the top panel of
+Fig.~\ref{fig:zetaCrit}).  For values of $\zeta<\zeta_c$, the
+stagnation radius rapidly approaches the break radius as shown in the
+bottom panel of Fig.~\ref{fig:zetaCrit}.
 % We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum

### 2015-03-29 ms.tex
Modifying description of rs

@@
 
-In the opposite limit of weak heating ($v_{w} \ll \sigma_0$), the
+In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the
 stagnation radius moves towards the break radius, $\rb$ in the stellar
@@
 binding energy.
-%   In fact, for core galaxies the specific
-% heating rate necessary to produce an unbound outflow can greatly
-% exceed $\sigma^{2}$ due to the additional gravitational potential of
-% stars outside the sphere of influence (Appendix~\ref{app:be}).
+
+More precisely we find that there is a critical $\zeta_c$
+($\zeta\equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$), such that if
+$\zeta\lsim\zeta_c$, then $\rs\simeq\rb$. For $\rb\gsim\rsoi$ we find
+
+\begin{align}
+\zeta_c\simeq \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)},
+\end{align}
+
+as described in Appendix~\ref{app:be}.
 

### 2015-03-30 ms.tex
analytics adjusted

@@
  \begin{cases}
-  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
-  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
+  5.0\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
+  5.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
  \end{cases}
@@
 \begin{align}
- \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[4
-    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
+  \rs&=\frac{G \Mbh}{\densSlope \vw^2}\left[\frac{13+ 8\Gamma}{4+2\Gamma}\right]\nonumber\\
+  &=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[4
+    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+
+      8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right]. 
 \label{eq:stag_analytic}
@@
 \begin{align}
-  &\rs \underset{v_w \gtrsim \sigma}\approx
+  &\rs \underset{v_w \gtrsim \sigma_0}\approx
   \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
-    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}
-  \approx \begin{cases} 9
+    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}\nonumber\\
+  &\approx \begin{cases} 8
     \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
@@
   \begin{cases}
-    6.1 \times 10^{-5} M_{\bullet,8}^{1.76}
+    4.5 \times 10^{-5} M_{\bullet,8}^{1.76}
     v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
-    3.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
+    3.2 \times 10^{-5} M_{\bullet,8}^{1.48} 
     v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
@@
   \begin{cases}
-    2.8 \times 10^{-5} M_{\bullet,8}^{0.76}
+    2.0 \times 10^{-5} M_{\bullet,8}^{0.76}
     v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
-    1.5 \times 10^{-5} \Mbheight^{0.48} 
+    1.4 \times 10^{-5} \Mbheight^{0.48} 
     v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
@@
 \end{eqnarray}
-where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$  is the Eddington accretion rate, assuming a radiative efficiency of ten per cent.
-Note the sensitive inverse dependence of the accretion rate on the wind heating rate.
+where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
+Eddington accretion rate, assuming a radiative efficiency of ten per
+cent.  Note the sensitive inverse dependence of the accretion rate on
+the wind heating rate.
 %To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$
 
-The gas density at the stagnation radius $\rho|_{r_{\rm s}}$ is more challenging to estimate accurately.
-Using an alternative estimate of $\dot{M}$ as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}|_{r_{\rm s}} = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$,
+The gas density at the stagnation radius $\rho|_{r_{\rm s}}$ is more
+challenging to estimate accurately.  Using an alternative estimate of
+$\dot{M}$ as the gaseous mass within the stagnation radius divided by
+the free-fall time $t_{\rm ff}|_{r_{\rm s}} = (r_{\rm
+  s}^{3}/GM_{\bullet})^{1/2}$,
 \begin{align}
@@
   \begin{cases}
-    6 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
+    5.2 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
     \, {\rm g \, cm^{-3}}& \text{core},\\
@@
 \end{align}
-where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius, $c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} = (GM_{\bullet}/r_{\rm B})^{1/2}$ and $\lambda$ is a parameter of order unity.
-
-One observes a similarity between equation (\ref{eq:mdot_gas}) and the Bondi formula (eq.~[\ref{eq:bondi}]) if $r_{\rm B}$ is replaced by $\rs$.
-Indeed, when the stagnation radius resides interior to the sphere of influence we find that (eq.~[\ref{eq:stag_simple}])
-\begin{align}
-  \rs\approx\frac{7}{2}\frac{G \Mbh}{\densSlope \vw^2} \approx
-  \frac{7}{6 \densSlope}r_{\rm B},
+where $r_{\rm B} \equiv GM/c_{\rm s,ad}^{2}$ is the Bondi radius,
+$c_{\rm s,ad} = \sqrt{\gamma kT/\mu m_p}$ is the adiabatic sound
+speed, $v_{\rm ff}|_{r_{\rm B}} = r_{\rm B}/t_{\rm ff}|_{r_{\rm B}} =
+(GM_{\bullet}/r_{\rm B})^{1/2}$ and $\lambda$ is a parameter of order
+unity.
+
+One observes a similarity between equation (\ref{eq:mdot_gas}) and the
+Bondi formula (eq.~[\ref{eq:bondi}]) if $r_{\rm B}$ is replaced by
+$\rs$.  Indeed, when the stagnation radius resides interior to the
+sphere of influence we find that (eq.~[\ref{eq:stag_simple}])
+\begin{align}
+  \rs\approx\frac{13+8\Gamma}{4+2\Gamma}\frac{G \Mbh}{\densSlope
+    \vw^2} \approx \frac{13+8\Gamma}{12+6\Gamma}r_{\rm B},
   \label{eq:rs_simple}
@@
 
-Our analytic derivations neglect the effects of heat conduction, an assumption we now check.
-The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
+Our analytic derivations neglect the effects of heat conduction, an
+assumption we now check.  The ratio of the magnitude of the conductive
+heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at
+the stagnation radius is given by
 \begin{align}
@@
 M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
- 20 \eta_{0.02}^{-1}
+ 30 \eta_{0.02}^{-1}
 M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
@@
  &\approx& \begin{cases}
-    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
+    7.9 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
     & \text{core} \\
-    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
+    2.3 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
     \,{\rm g\,cm^{-3}}  & \text{cusp}, 
@@
   \begin{cases}
-   380 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
-   590 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
+   630 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.76}v_{500}^{7.2}  &, \text{core}\\
+   660 \eta_{0.02}^{-1} M_{\bullet,8}^{-0.48}v_{500}^{5.8}  &, \text{cusp},     
   \end{cases}
@@
    200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}\\
-f(r_b/r_{\rm soi})\sigma,     
+   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}   
   \end{cases}
@@
 \end{align}
-The requirement $v_{\rm w} \gtrsim \sigma$ results because the top two
-lines are derived using equation (\ref{eq:rs_simple}) for $r_s$.
-However, when $v_{\rm w} \lesssim f(r_b/r_{\rm soi})\sigma$ the
-stagnation radius moves to very large radii, or may not exist at all
-(see also Fig.~\ref{fig:stag}), resulting in much higher gas densities
-and inevitable cooling instability.  The dimensionless function f is
-approximately unity for cusp galaxies, but increases $\propto
-(r_b/r_{\rm soi})^{1/2}$ for core galaxies (Fig.~\ref{fig:vwCrit}).  
-%Our numerical results in $\S\ref{sec:numerical}$ demonstrate that $\tilde{v}_{w} \gtrsim v_{\rm CI} \sim 200-300$ km s$^{-1}$ is generally sufficient for stability at all radii (Fig.~\ref{fig:cooling}).
 
@@
   {\rm min}\begin{cases}
-   6\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
-   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
-\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 6. 6\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
+   5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}\\
+   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}
   \end{cases}
@@
 \end{align}
-which is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$.
+which is derived using equation (\ref{eq:eddr_analytic}) to calculate
+$\dot{M}(v_{\rm TI})$.
 
@@
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
-C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
-&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
-C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
+  \begin{cases} 160 \eta_{0.02}^{0.23}T_{\rm
+C,9}^{0.12}\epsilon_{-2}^{0.23} M_{\bullet,8}^{0.18}\,{\rm km\,s^{-1}}
+&, \text{core}\\ 90 \eta_{0.02}^{0.34}T_{\rm
+C,9}^{0.17}\epsilon_{-2}^{0.34} M_{\bullet,8}^{0.17}\,{\rm km\,s^{-1}}
 &, \text{cusp},
@@
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
-C,9}^{-0.44}M_{\bullet,8}^{0.08}
+\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
+C,9}^{-0.44}M_{\bullet,8}^{0.09}
 &, \text{core}\\ 8.7\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm

### 2015-03-30 ms.tex
more changes to analytics
table now has solutions corresponding to the latest sigma prescription.

@@
   & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
-$    10^{ 6 }$ & 300 & 0.8 & 100 & 0.14 & $ 6.4 \times 10^{ -5 }$ & 17 \\
-... & 600 & 0.8 & 100 & $ 3.4 \times 10^{ -2 }$ & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
-... & 1200 & 0.8 & 100 & $ 8.2 \times 10^{ -3 }$ & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
-$    10^{ 7 }$ & 300 & 0.8 & 25 & 0.65 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
-... & ... & 0.8 & 50 & 0.65 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
-... & ... & 0.8 & 100 & 0.83 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
-... & ... & 0.8 & 200 & 0.91 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
-... & ... & 0.8 & 400 & 2.3 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
-... & 600 & 0.8 & 25 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
-... & ... & 0.8 & 100 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
-... & 1200 & 0.8 & 100 & $ 2.1 \times 10^{ -2 }$ & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
-$    10^{ 8 }$ & 300 & 0.8 & 25 & 1.3 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
-... & ... & 0.8 & 50 & 2.1 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
-... & ... & 0.8 & 100 & 3.8 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
-... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1  \times 10^{ -3 }}$ \\
-... & 450 & 0.8 & 100 & 0.72 & $ 4.4 \times 10^{ -4 }$ & 4 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & 3.3 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$\\
-... & 600 & 0.8 & 25 & 0.26 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2 }$ \\
-... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
-...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &70 \\
-...$^{\ddagger}$ & ... & 0.8 & 100 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 73 \\
-... & ... & 0.8 & 200 & 0.3 & $ 1.5 \times 10^{ -4 }$ & 67 \\
-... & ... & 0.8 & 400 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 58 \\
-... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
+  $    10^{ 6 }$ & 300 & 100 & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
+... & 600 & 100 & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
+... & 1200 & 100 & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
+$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 \\
+... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 \\
+... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
+... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
+... & ... & 400 & 1.1 & $ 7.0 \times 10^{ -4 }$ & $\mathbf{0.28}$ \\
+... & 600 & 25 & $ 8.1 \times 10^{ -2 }$ & $ 3.2 \times 10^{ -5 }$ & $ 6.2 \times 10^{ 2 }$ \\
+... & ... & 100 & $ 8.1 \times 10^{ -2 }$ & $ 3.2 \times 10^{ -5 }$ & $ 6.2 \times 10^{ 2 }$ \\
+... & 1200 & 100 & $ 2.0 \times 10^{ -2 }$ & $ 6.0 \times 10^{ -6 }$ & $ 2.6 \times 10^{ 4 }$ \\
+$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 \\
+... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 \\
+... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
+... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $\mathbf{ 5.3 \times
+  10^{ -2 }}$ \\
+...$^{\dagger}$ & 450 & 100 & 1.2 & $ 8.1 \times 10^{ -4 }$ & 2.6 \\
+... & 600 & 25 & 0.21 & $ 1.0 \times 10^{ -4 }$ & $ 2.1 \times 10^{ 2 }$ \\
+... & ... & 100 & 0.22 & $ 1.1 \times 10^{ -4 }$ & $ 1.7 \times 10^{ 2
+}$ \\
+...$^{\dagger}$ & ... & 100 & 0.22 & $ 1.1 \times 10^{ -4 }$ & $ 1.6 \times 10^{ 2 }$ \\
+...$^{\ddagger}$  & ... & 100 & 0.27 & $ 1.4 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2
+}$ \\
+... & ... & 200 & 0.23 & $ 1.1 \times 10^{ -4 }$ & $ 1.6 \times 10^{ 2 }$ \\
+... & ... & 400 & 0.23 & $ 1.1 \times 10^{ -4 }$ & $ 1.5 \times 10^{ 2 }$ \\
+... & 1200 & 100 & $ 5.0 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -5 }$ & $ 8.3 \times 10^{ 3 }$ \\
   \hline
   & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
-$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2\times 10^{ -6 }$ & 99 & Conv\\
-... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
-... & 1200 & 0.1 & 25 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-... & ... & 0.1 & 50 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-... & ... & 0.1 & 100 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
-$    10^{ 7 }$ & 600 & 0.1 & 25 & 0.24 & $ 4.3 \times 10^{ -5 }$ & 41 \\
-... & ... & 0.1 & 50 & 0.57 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
-... & 1200 & 0.1 & 25 & $ 4.4 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
-... & ... & 0.1 & 50 & $ 4.7 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
-... & ... & 0.1 & 100 & $ 5.3 \times 10^{ -2 }$ & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
-$    10^{ 8 }$ & 600 & 0.1 & 25 & 0.39 & $ 1.1 \times 10^{ -4 }$ & 31 \\
-... & ... & 0.1 & 50 & 0.66 & $ 3.0 \times 10^{ -4 }$ & 3 \\
-... & ... & 0.1 & 100 & 2.6 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
-... & 1200 & 0.1 & 25 & 0.1 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 50 & 0.11 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 100 & 0.12 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
-... & ... & 0.1 & 200 & 0.16 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
-... & ... & 0.1 & 400 & 3.3 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
+  $    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\
+... & 1200 & 25 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\
+... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0 \times 10^{ -2 }}$ \\
+... & 1200 & 25 & $ 3.9 \times 10^{ -2 }$ & $ 1.4 \times 10^{ -6 }$ & $ 2.9 \times 10^{ 4 }$ \\
+... & ... & 50 & $ 4.1 \times 10^{ -2 }$ & $ 1.5 \times 10^{ -6 }$ & $ 2.3 \times 10^{ 4 }$ \\
+... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\
+$    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ & $ 1.0 \times 10^{ 2 }$ \\
+... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 \\
+... & 1200 & 25 & $ 8.5 \times 10^{ -2 }$ & $ 6.1 \times 10^{ -6 }$ & $ 8.2 \times 10^{ 3 }$ \\
+... & ... & 50 & $ 9.2 \times 10^{ -2 }$ & $ 7.0 \times 10^{ -6 }$ & $ 6.0 \times 10^{ 3 }$ \\
+... & ... & 100 & 0.1 & $ 8.8 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 3 }$ \\
+... & ... & 200 & 0.15 & $ 1.7 \times 10^{ -5 }$ & $ 8.0 \times 10^{ 2 }$ \\
+... & ... & 400 & 6.8 & $ 2.5 \times 10^{ -2 }$ & $\mathbf{ 3.1 \times 10^{ -4 }}$ \\
   \hline
-
 \label{table:models}  
@@
 There are two types of SMBH feedback: kinetic and radiative.
-Radiative feedback is potentially effective even in low luminosity AGN via Compton heating (e.g., \citealt{Sazonov+04}, \citealt{Ciotti+10}), which provides a volumetric heating rate (\citealt{Gan+14})
+Radiative feedback is potentially effective even in low luminosity AGN
+via Compton heating (e.g., \citealt{Sazonov+04}, \citealt{Ciotti+10}),
+which provides a volumetric heating rate (\citealt{Gan+14})
 \begin{align}
@@
 \end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
-\epsilon/0.01 \sim 1$.  We caveat that, unlike
-stellar wind heating, Compton heating depends on radius, scaling as
-$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
-r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.75}$
-for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
-$\densSlope \simeq 0.6$) galaxies, respectively.  Our model's assumption that the heating
-parameter be radially constant is not satisfied, but this variation is sufficiently weak that it should not significantly alter
-our conclusions.
-
-If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
-(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
+\epsilon/0.01 \sim 1$.  We caveat that, unlike stellar wind heating,
+Compton heating depends on radius, scaling as $v_{w}^{\rm C}(r)
+\propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
+r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto
+r^{-0.75}$ for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp
+($\Gamma = 0.1$; $\densSlope \simeq 0.6$) galaxies, respectively.  Our
+model's assumption that the heating parameter be radially constant is
+not satisfied, but this variation is sufficiently weak that it should
+not significantly alter our conclusions.
+
+If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
+solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 160 \eta_{0.02}^{0.23}T_{\rm
-C,9}^{0.12}\epsilon_{-2}^{0.23} M_{\bullet,8}^{0.18}\,{\rm km\,s^{-1}}
-&, \text{core}\\ 90 \eta_{0.02}^{0.34}T_{\rm
-C,9}^{0.17}\epsilon_{-2}^{0.34} M_{\bullet,8}^{0.17}\,{\rm km\,s^{-1}}
+  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
+C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
+&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
+C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
 &, \text{cusp},
@@
 \end{align} 
-Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g.
-$v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.
-The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
+Compton heating can thus be significant in young stellar populations
+with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
+km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate
+corresponding to the state where Compton heating limits the average
+accretion rate is given by substituting equation (\ref{eq:vC2}) into
+equation (\ref{eq:eddr_analytic}):
 \begin{align}
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
-C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
-&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
+\begin{cases} 2\times 10^{-3} \eta_{0.02}^{0.2}T_{\rm
+C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.16}
+&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.3}T_{\rm
 C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
@@
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
+\begin{cases} 1.7\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
 C,9}^{-0.44}M_{\bullet,8}^{0.09}
-&, \text{core}\\ 8.7\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
+&, \text{core}\\ 8.6\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
 C,9}^{-0.4} M_{\bullet,8}^{0.08}

### 2015-03-31 ms.tex
bdm

@@
 controls the mass accretion rate, $\dot{M}$.  The accretion rate in
-turn sets the luminosity of the black hole and the impact of this
-energy and momentum output on larger physical scales (`feedback').
-The presence of dense gas in the nuclear region may also lead to runaway
+turn sets the luminosity of the black hole and the feedback of this
+energy and momentum output on larger physical scales.
+The presence of dense gas in the nuclear region may lead to runaway
 cooling, resulting in bursty episodes of star formation and AGN
@@
 growing low mass blacks may be distinct from those operating at higher
-SMBH masses and accretion rates in quasars.  A key open question is
+SMBH masses and accretion rates in quasars.  A key question is
 whether SMBHs grow primarily by accreting gas fed in directly from
@@
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the detection threshold, a potentially problematic assumption if
+the detection threshold.  This assumption is questionable if
 different physical processes control the accretion rates onto the
@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaching the vicinity of the SMBH
+(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaches the SMBH
 (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).

### 2015-03-31 ms.tex
bdm2

@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ can in many cases lie within a factor of few of the
-nominal Bondi radius).  When heating is sufficiently weak, however, no stagnation radius may exist at all, i.e. the entire ISM of the galaxy is flowing towards the SMBH.  A key goal of this work is to
+show that $\rs$ can in many cases reside near the
+nominal Bondi radius).  When heating is sufficiently weak, however, no stagnation radius may exist at all, i.e. the entire ISM of the galaxy is flowing towards the SMBH.  A goal of this work is to
 assess under what conditions a stagnation radius exists, as this
@@
 numerical results.  In $\S\ref{sec:discussion}$ we discuss the
-implications of our results, to topics including...  In
-$\S\ref{sec:conclusions}$ we summarize our conclusions.  Table
+implications of our results, to topics including the nuclear X-ray luminosities of quiescent black holes, jetted TDEs, and the growth time of SMBHs.
+In $\S\ref{sec:conclusions}$ we summarize our conclusions.
+Table
 \ref{table:definitions} provides the definitions of commonly used
@@
 velocity dispersion \\
-$\sigma_0$ & Stellar velocity dispersion--assumed to be constant.\\
+$\sigma_0$ & Stellar velocity dispersion--assumed to be radially constant.\\
 $\zeta$ & $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$\\
@@
 movement of stars with respect to one another at the characteristic
-velocity of $\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
-    r}+\sigma_0^2}$, where $\sigma_0$ is a constant. The first term
-corresponds to the velocity dispersion of a power law stellar density
-profile with slope $-1-\Gamma$ in the presence of black hole. The
-second term represents the observed constant velocity dispersion at
-radii outside of the black hole sphere of influence
-\citep{ChaeBernardi+:2014a}. For a given $\Mbh$, we take
-$\sigma_0^2\approx 3 \sigma_{\Mbh}^2$, where $\sigma_{\Mbh}$ is the
-velocity dispersion from the \citet{McConnellMa+:2011a} $\Mbh-\sigma$
-relation.  This heating is present even in old stellar populations for
-which mass and energy injection are dominated by AGB winds with low
-velocities $\ll \sigma$.  The second term, $v_{w}^{2}$, parameterizes
-all additional sources of heating, including faster main sequence or
-Wolf-Rayet stellar winds, spin-down energy from millisecond pulsars,
-supernovae, AGN feedback, etc.  As will be discussed in
-$\S\ref{sec:heating}$, the value of $v_{w}$ will in general depend on
-the SMBH mass and the age of the stellar population.  We further
-assume that $v_w$ is constant with radius, i.e. that the volumetric
-heating rate is proportional to the local stellar density.
+velocity of 
+\be\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
+    r}+\sigma_0^2},
+\ee
+where the first term is the velocity dispersion of the power law stellar density profile in the SMBH potential.
+The second term, $\sigma_0\approx 3 \sigma^2$ is a constant, motivated by the observed velocity dispersion outside of the SMBH sphere of influence \citep{ChaeBernardi+:2014a}, where $\sigma$ is the velocity dispersion in the $\Mbh-\sigma$
+relation (eq.~[\ref{eq:Msigma}]).
+The second component of the total heating, $v_{w}^{2}$, parameterizes all additional sources of energy input, including faster winds from young stars, millisecond pulsars, supernovae, AGN feedback, etc.
+We assume that $v_w$ is constant with radius, i.e.
+that the volumetric heating rate is proportional to the local stellar density.
+The value of $v_w$ will in general depend on the SMBH mass and the age of the stellar population ($\S\ref{sec:heating}$).
 

### 2015-03-31 ms.tex
fixed zeta discussion

@@
 
-To isolate the physics of interest, our baseline calculations neglects three potentially important effects: heat conduction, radiative cooling, and rotation.
+To isolate the physics of greatest interest, our baseline calculations neglects three potentially important effects: heat conduction, radiative cooling, and rotation.
 Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
@@
     \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+
-      8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right]. 
+      8\Gamma}{4+2\Gamma}- \frac{3\nu}{2+\Gamma}\right]. 
 \label{eq:stag_analytic}
 \end{align}
-
-If the stagnation radius is well inside the influence radius, $\rsoi$,
-then $\Mstar/\Mbh|_{\rs}\ll1$. Also, equation~\eqref{eq:rsRinf}
-implies that $v_w\gg \sigma_0$, since
-$\rs/\rsoi=\frac{k(\Gamma)}{3\zeta^2}$, where
-$\zeta=\sqrt{\frac{v_w^2+\sigma_0^2}{\sigma_0^2}}$ and $k(\Gamma)$ is
-of order unity then equation~\eqref{eq:stag_analytic} simplifies to
+For low heating rates $v_w \ll \sigma_0$, the stagnation radius resides well inside the SMBH sphere of influence.
+In this case $\Mstar|_{\rs}/\Mbh \ll1$, such that equation~\eqref{eq:stag_analytic} simplifies to
 \begin{align}
   &\rs \underset{v_w \gtrsim \sigma_0}\approx
-  \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
-    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}\nonumber\\
+  \left(\frac{13+8\Gamma}{4+2\Gamma}-
+    \frac{3\nu}{2+\Gamma}\right)\frac{G \Mbh}{\nu v_w^2}\nonumber\\
   &\approx \begin{cases} 8
@@
 where we have used equation~\eqref{eq:densSlope} to estimate
-$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
-core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
+$\densSlope$ separately for
+core ($\Gamma = 0.1$; $\densSlope\approx 1$) and cusp ($\Gamma = 0.8$; $\densSlope \approx 0.6$) galaxies.  This
 expression is similar to that obtained by \citet{Volonteri+11} on more
@@
 
-In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the
-stagnation radius moves towards the break radius, $\rb$ in the stellar
-density profile, formally implying that almost entire ISM of the
-galaxy is accreting.  This result makes intuitive sense: gas is
-supplied to the nuclear by stars which are gravitationally bound to
-the black hole, so outflows are possible only if the specific heating
-rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational
-binding energy.
-
-More precisely we find that there is a critical $\zeta_c$
-($\zeta\equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$), such that if
-$\zeta\lsim\zeta_c$, then $\rs\simeq\rb$. For $\rb\gsim\rsoi$ we find
-
-\begin{align}
-\zeta_c\simeq \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)},
-\end{align}
-
-as described in Appendix~\ref{app:be}.
+In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the stagnation radius moves to large radii, approaching the break radius $\rb$ in the stellar density profile, formally implying that almost entire ISM of the galaxy is accreting.
+In particular, in Appendix \ref{app:be} we show that $\rs \Rightarrow \rb$ for heating below a critical threshold
+\be
+\zeta\equiv \frac{\sqrt{v_w^2+\sigma_0^2}}{\sigma_0} < \zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
+\label{eq:zetacrit}
+\ee
+This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy.
+Condition (\ref{eq:zetacrit}) approximately corresponds to the condition that the wind heating parameter be less than the escape speed from the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
 

### 2015-03-31 ms.tex
fixed more

@@
 
-The accretion rate onto the SMBH is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
+The accretion rate onto the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
 \begin{eqnarray}
-  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta \Menc|_{r_{\rm s}}}{\th} \nonumber \\
+  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta M_{\star}|_{r_{\rm s}}}{\th} \nonumber \\
 &\approx&
@@
 Eddington accretion rate, assuming a radiative efficiency of ten per
-cent.  Note the sensitive inverse dependence of the accretion rate on
+cent.  Note the sensitive dependence of the accretion rate on
 the wind heating rate.
@@
 
-Our expression for the mass accretion rate (eq.~[\ref{eq:mdot_analytic}]) can be compared to the traditional Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
+Our expression for $\dot{M}$ (eq.~[\ref{eq:mdot_analytic}]) is usefully compared to the Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
 \begin{align}
@@
 
-One observes a similarity between equation (\ref{eq:mdot_gas}) and the
-Bondi formula (eq.~[\ref{eq:bondi}]) if $r_{\rm B}$ is replaced by
-$\rs$.  Indeed, when the stagnation radius resides interior to the
-sphere of influence we find that (eq.~[\ref{eq:stag_simple}])
+Equation (\ref{eq:mdot_gas}) closely resembles the Bondi formula (eq.~[\ref{eq:bondi}]) provided that $r_{\rm B}$ is replaced by $\rs$.
+Indeed, for $r_{s} < r_{\rm soi}$ we have that (eq.~[\ref{eq:stag_simple}])
 \begin{align}
@@
 \tilde{v}_{w}^{2}}
- \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
-    \phi \rho c_s^3}}\right)
+ \left(1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
+    \phi \rho c_s^3}\right)^{-1}
 \nonumber \\ &\sim {\rm min}
@@
 where the second equality makes use of equations (\ref{eq:Tanalytic}),
-(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
-1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
-stellar density profile as (eq.~[\ref{eq:rhostar}])
+(\ref{eq:stag_simple}), and we have made the approximations $\nabla^{2} \sim
+1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  The
+stellar density profile is approximated as (eq.~[\ref{eq:rhostar}])
 \begin{eqnarray}
@@
 where the stagnation radius is assume to reside well inside the Nuker
-break radius and for clarity we have not distinguished between cusp
-and core galaxies.  Equation (\ref{eq:conduction}) shows that even in
-the case of saturated conduction, the neglect of heat conduction
+break radius.  Equation (\ref{eq:conduction}) shows that, even when conduction is saturated, our neglect of heat conduction
 results in at most an order unity correction for plausible, causal values of
-the saturation parameter $\phi < 0.1$, justifying its neglect in our
-analysis.  Numerical experiments including conductivity confirm this
+the saturation parameter $\phi < 0.1$.  Numerical experiments which include conductive heating confirm this
 ($\S\ref{sec:numerical}$).

### 2015-03-31 ms.tex
fixed 28

@@
 $\sigma_0$ & Stellar velocity dispersion--assumed to be radially constant.\\
-$\zeta$ & $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$\\
+$\zeta$ & $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ (eq.~[\ref{eq:zetacrit}])\\
 $r_{s}$ & Stagnation radius (where gas radial velocity goes to zero) \\
@@
 the loss of pressure can temporarily increase the black hole accretion
-rate; when coupled to feed-back processes, the latter can lead to
+rate.  When coupled to feed-back processes, the latter can lead to
 time-dependent (e.g. limit cycle) behavior
@@
 
-Thermal stability ($\dot{q}_{\rm heat} > |\dot{q}_{\rm rad}|$; $t_{\rm
-  cool} > t_{\rm ff}$) near the stagnation radius thus requires a
+Based on our numerical results and the recent work of \citet{McCourt+10}) we define thermal stability according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
+  cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius {\bf BDM: decide here}.  This condition translates into a
 critical minimum heating rate
@@
    200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}   
+   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
+\sigma_0(\zeta_c^{2}-1)^{1/2} \approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)}, 
   \end{cases}
@@
 \end{align}
-
-The existence of a minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) implies a corresponding maximum accretion rate,
+where the final condition corresponds to the low wind heating limit (eq.~[\ref{eq:zetacrit}]), for which the stagnation radius moves out to the break radius $r_b$, resulting in thermal instability.
+
+The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
 \begin{align}
@@
    5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}\\
-   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}
+3\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.38}\\
+   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}\\
+2.5\times 10^{-4}\eta_{0.02}
   \end{cases}
@@
 \end{align}
-which is derived using equation (\ref{eq:eddr_analytic}) to calculate
-$\dot{M}(v_{\rm TI})$.
+where the first line for each case is derived using equation (\ref{eq:eddr_analytic}) to calculate
+$\dot{M}(v_{\rm TI})$, whereas the second line corresponds to the low wind heating limit and is calculated for core galaxies using the empirical correlation $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{0.2}$ which follows from equation (\ref{eq:rsoi}) and the results of \citet{LauerFaber+:2007a}.
 
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm
     s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm

### 2015-03-31 ms.tex
Thermally unstable solutions marked in table.
fixed results

@@
 Our numerical results, summarized in Table \ref{table:models}, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
-Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
+Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 10$ {\bf BDM: correct?} at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
 
@@
 
-Figure~\ref{fig:stag} shows our results for the stagnation radius
-$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
+Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
   soi}$, with different colors showing different values of $v_{w}$.
@@
 galaxies, respectively, calculated assuming $\densSlope = 1$ and
-$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).  Our analytic estimates are found to
-provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
-\sigma$, but the assumptions leading to these estimates become invalid
-for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
-For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
-sensitively on break radius $r_{b}$, but the latter has a greater
-influence when $v_{w} \lesssim \sigma$.  The three green squares which
-are vertically aligned at the same value of $v_{w}/\sigma$ (close to
-where the analytic estimate diverges) correspond to models with the
-same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
-300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
-50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
-r_{s}$, the effects of the break radius is to the push the stagnation
-radius inwards, decreasing the SMBH accretion rate.
+$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).
+
+Our analytic estimates accurately reproduce the numerical results in the high heating limit $v_{\rm w} \gg
+\sigma_0$ ($r_{\rm s} \lesssim r_{\rm soi}$).
+However, for sufficiently low $v_{\rm w}/\sigma_0$ the stagnation radius exceeds the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.
+This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $v_w/\sigma_0$ in the case of a core galaxies ($\Gamma = 0.8$) with large break radii.
+This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
 

### 2015-03-31 ms.tex
fixed results nightmare

@@
 Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
-  soi}$, with different colors showing different values of $v_{w}$.
+  soi}$ as a function of the wind heating parameter $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors showing different values of $v_{w}$.
 Cusp and core galaxies are marked with square and triangles,
@@
 
-Our analytic estimates accurately reproduce the numerical results in the high heating limit $v_{\rm w} \gg
-\sigma_0$ ($r_{\rm s} \lesssim r_{\rm soi}$).
-However, for sufficiently low $v_{\rm w}/\sigma_0$ the stagnation radius exceeds the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.
-This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $v_w/\sigma_0$ in the case of a core galaxies ($\Gamma = 0.8$) with large break radii.
-This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
+Our analytic estimates accurately reproduce the numerical results in the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s} \lesssim r_{\rm soi}$).
+However, for sufficiently low heating the stagnation radius diverges above the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.
+This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $\zeta$ in the case of core galaxies ($\Gamma = 0.8$) with large break radii.
+This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $\zeta$ close to where the analytic estimate diverges; these correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom) corresponding to successively larger values of $\zeta_c$.
 

### 2015-03-31 ms.tex
fixed Ia section

@@
     $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
-    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
-    the ratio of the effective wind heating rate $v_{w}$ to the
-    stellar velocity dispersion $\sigma$.  Green, orange, and blue
+    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of the stellar wind heating parameter $\zeta \equiv \sqrt{v_w^{2} + \sigma_0^{2}}/\sigma_0$.  Green, orange, and blue
     symbols correspond to different values of $v_{w} =$ 300, 600, and
@@
 interior to the Ia radius, which is gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}f^{2}$  {\bf BDM: update discussion}.  Thus, according
-to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm
-  Ia})^{2}/2\sigma^{2} \gtrsim 1$.  Hence, SN Ia are in principle
-capable of dynamically clearing out gas from radii $\sim r_{\rm Ia}
-\gtrsim r_{\rm s}$, at least for low mass BHs with $\sigma \ll v^{\rm
-  Ia}_{w}$.  Thus, even in cases when heating is sufficiently weak
-that the stagnation radius formally exceeds $r_{\rm Ia}$, the
-accretion rate is limited to a maximum value,
+by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}f^{2}$, where $f \sim 1$ for cusp galaxies and $f \sim$ few for core galaxies due to the greater escape speed from core galaxies.
+
+According
+to the above definitions, we thus find that 
+\be
+E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2f^{2}\sigma^{2}.  
+\ee
+Hence, for low mass BHs with $\sigma_0 \ll f v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Thus, even when heating is sufficiently weak for the stagnation radius to formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is limited to a value
 \begin{eqnarray}
-\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{r_{\rm Ia}}{r_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]).
-Note that $\dot{M}_{\rm Ia}$ usually exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
-Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.
+Note, however, that for low mass black holes $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
+
+The deep potential wells of high mass galaxies $\sigma \gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas.
+Equation (\ref{eq:eddr_Ia}) may nevertheless cap the accretion rate in practice because, even if other source of heating are ineffective, the Ia heating rate (eq.~[\ref{eq:vIa}]) is sufficiently great to prevent the stagnation radius from substantially exceeding $r_{\rm Ia}$.
+
+%Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.
 due to a galaxy merger or to cooling flows developing within the galaxy over much longer timescales (e.g.~\citealt{Ciotti&Ostriker07}).
@@
 \subsection{Millisecond Pulsars}
- Energy injection from the spin-down of millisecond pulsars (MSPs) is a potentially
+ Energy injection from the magnetic braking of millisecond pulsars (MSPs) is a potentially
 important heating source.  If the number of MSPs per unit stellar mass

### 2015-03-31 ms.tex
blah

@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm
-    s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm
-          edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
   {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
@@
 ... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 \\
-... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
-... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
-... & ... & 400 & 1.1 & $ 7.0 \times 10^{ -4 }$ & $\mathbf{0.28}$ \\
+% ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
+% ... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
+% ... & ... & 400 & 1.1 & $ 7.0 \times 10^{ -4 }$ & $\mathbf{0.28}$ \\
+... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+... & ... & 400 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
 ... & 600 & 25 & $ 8.1 \times 10^{ -2 }$ & $ 3.2 \times 10^{ -5 }$ & $ 6.2 \times 10^{ 2 }$ \\
@@
 ... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 \\
-... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
-... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $\mathbf{ 5.3 \times
-  10^{ -2 }}$ \\
+% ... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
+% ... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $\mathbf{ 5.3 \times
+%   10^{ -2 }}$ \\
+ ... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
 ...$^{\dagger}$ & 450 & 100 & 1.2 & $ 8.1 \times 10^{ -4 }$ & 2.6 \\
@@
 $    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\
-... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0 \times 10^{ -2 }}$ \\
+%... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0
+%\times 10^{ -2 }}$ \\
+... & ... & 50 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
 ... & 1200 & 25 & $ 3.9 \times 10^{ -2 }$ & $ 1.4 \times 10^{ -6 }$ & $ 2.9 \times 10^{ 4 }$ \\
@@
 ... & ... & 200 & 0.15 & $ 1.7 \times 10^{ -5 }$ & $ 8.0 \times 10^{ 2 }$ \\
-... & ... & 400 & 6.8 & $ 2.5 \times 10^{ -2 }$ & $\mathbf{ 3.1 \times 10^{ -4 }}$ \\
+% ... & ... & 400 & 0.8  & $ 2.5 \times 10^{ -2 }$ & $\mathbf{ 3.1 \times 10^{ -4 }}$ \\
 \hline
@@
 results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in
-turn may create stronger jet feedback.  However, given the uncertainty
-in the efficiency of jet heating, we defer a more detailed discussion
+turn may create stronger kinetic feedback.  However, given the uncertainty
+in the efficiency of kinetic heating, we defer a more detailed discussion
 to $\S\ref{sec:kinetic}$.
@@
 [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
+{\bf BDM: do we even include Ia heating?}
+
 We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).

### 2015-03-31 ms.tex
blah blah

@@
 unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm
-  rad}|)_{r_{s}} \lesssim 1$ (eq.~[\ref{eq:cooling3}]), as shown by
-dashed lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability is
-calculated neglecting Compton heating because the latter may not be
+  rad}|)_{r_{s}} \lesssim 10$ (eq.~[\ref{eq:cooling3}]) {\bf BDM: correct?}, as shown by
+dashed lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability threshold is
+calculated neglecting Compton heating because SMBH feedback may not be
 capable of truly stabilizing the flow given its inability to respond
@@
   thermally stable flows across almost all black hole masses}.
-One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion and thermal stability for the average star formation history is marginal ($\S\ref{sec:mdot}$).
-{\bf AG: I wouldn't put too much stock in this since for higher masses
-vw is comparable to sigma, and thus rs should run away to large
-radii. This is especially true for core galaxies.}
+One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion ($\zeta \sim \zeta_c$) and thermal stability for the average star formation history is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
 
@@
 non-fiducial cases in which the current ($z = 0$) star formation is
-suppressed by a factor $\zeta$ from its average $z = 0$ value, for a
+suppressed by a factor $\iota$ from its average $z = 0$ value, for a
 characteristic timescale $t_{\rm scale}$ (for details, see Appendix
@@
 from its average value, even for huge drops in the star formation rate
-($\zeta \sim 10^{-3}$).  However, burstiness in the star formation
+($\iota \sim 10^{-3}$).  However, burstiness in the star formation
 history over longer timescales can suppress heating more
 significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
-  w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm
+  w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm
   w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
-smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
+smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
 exception to this is in galactic nuclei with $M_\bullet \gtrsim
@@
 local variations are either on short timescales ($t_{\rm scale}
-\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim
+\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\iota \gtrsim
 0.1$).  If both of these conditions are violated, then the effective

### 2015-03-31 windheat.tex
blah blah

@@
     line styles show star formation rates that have declined to
-    fractions $\zeta = 0.001$, $\zeta = 0.1$, and $\zeta = 0.3$ of
+    fractions $\iota= 0.001$, $\iota = 0.1$, and $\iota = 0.3$ of
     their halo-averaged values, respectively. }
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\zeta)\arctan(t/t_{\rm scale}) + \zeta \right).
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/t_{\rm scale}) + \iota \right).
 \end{equation}

### 2015-03-31 ms.tex
fixed 6.1

@@
 $\dot{M}$ & mass accretion rate \\
-$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
+$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
 $\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
@@
 These fall below the maximum thermally stable accretion rate,
-$\dot{M}_{\rm TI}$ (plotted as yellow lines), except at the highest
+$\dot{M}_{\rm TI}$ (yellow lines), except at the highest
 black hole masses $\sim 10^{9}M_{\odot}$.  For these highest mass
-black holes, the maximum accretion rate as set by gas blow-out from SN
-Ia (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
-accretion rate below the thermally-unstable value, provided that the
-SN Ia heating efficiency is sufficiently high that $v_{\rm w}^{\rm Ia}
-\gg \sqrt{2}\sigma \sim 400$ km s$^{-1}$ (see discussion just
-preceding eq.~[\ref{eq:eddr_Ia}]).  This is only possible if the Ia
-heating efficiency is higher $\epsilon_{\rm Ia} > 0.1$ than normally
-assumed (\citealt{Sharma+14}) and if the galaxy is a core.  For lower mass black holes, the
-maximum accretion rate set by SN Ia is significantly higher and cannot
+black holes, the maximum accretion rate as set by the SN Ia
+radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
+accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
+For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
 also prevent the development of thermally unstable flows,

### 2015-03-31 ms.tex
fixed 6.2

@@
 
-Based on our numerical results and the recent work of \citet{McCourt+10}) we define thermal stability according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
+Based on our numerical results and the recent work of \citet{McCourt+12}) we define thermal stability according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
   cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius {\bf BDM: decide here}.  This condition translates into a
@@
   near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
-  Eddington ratios inferred for the galactic center from
-  \citet{Quataert:2004a} (line with black circle) and for NGC3115 from
-  \citet{ShcherbakovWong+:2014a} (line with black diamonds) and for
-  the Swift J1644+57 event from \citet{BergerZauderer+:2012a} (line
+  Eddington ratios inferred for SgrA* from
+  \citet{Quataert:2004a} (line with black circle), for NGC3115 from
+  \citet{ShcherbakovWong+:2014a} (line with black diamonds), and for
+  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (line
   with black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
@@
 Perhaps a more readily addressable test is whether a steady-state accretion
-picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
+picture developed in this work can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
   edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
@@
   bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
-the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
-v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
+the stellar wind velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
+\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
 (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
@@
 the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively
-inefficient flows {\bf AG: Don't forget differences in eta}.
+inefficient flows.
 
@@
 have been proposed to occur on the smaller scale of the sphere of
-influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuarda+15}).
+influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuadra+15}).
 
@@
 SMBH mass $\Mbh\simeq 100\Msun$.  according to the mean relationship
-from the \citet{Lauer+Faber:2007a} sample. A more likely explanation
+from the \citet{LauerFaber+:2007a} sample. A more likely explanation
 is that the observed break in the gas density is associated with a

### 2015-03-31 ms.tex
the ghost of balmaverde edited 6.3

@@
 
-It is also possible that many of the galactic nuclei from the
-\citet{Miller+15} sample are not accreting in a steady fashion.  The
-efficiency assumed in the right panel of Figure \ref{fig:miller} in
-some ways represents a maximum value, since it does not take into
-suppression of the accretion rate due to disk outflows on small
-scales.  If the actual X-ray efficiency is lower than assumed, then
-many of the detections in the case of low SMBH masses, $M_{\bullet}
-\lesssim 10^{8}M_{\odot}$, would lie even further above above the
-predicted average value for stable accretion (black line).  These
-galaxies either experience significantly lower levels of heating than
-average galaxies of their mass, or that they are not accreting stably
-at all.  Indeed, for the lowest mass holes, $M_{\bullet} \lesssim
+It is also possible that many of the
+\citet{Miller+15} sample of galactic nuclei are not accreting in steady state.  The
+value of the X-ray efficiency assumed in the right panel of Figure \ref{fig:miller} represents a maximum value, since it does not account for suppression of the SMBH accretion rate due to outflows from the accretion disk on small
+radial scales.
+If the actual radiative efficiency is lower, then many of the X-ray detections would lie even further above above the predicted value of $\langle L_X \rangle$ for stable accretion (black line).
+Either these
+galaxies experience much less heating than average galaxies of the same mass, or they are not accreting stably
+at all.  Indeed, for $M_{\bullet} \lesssim
 10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the
 maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow
-line).  It is not surprising that this sample is more likely to be
-thermally unstable as compared to an average galaxy with this black
-hole mass, because the \citet{Miller+15} sample includes only
-early-type galaxies with on average older stellar populations.
-
-Figure \ref{fig:bh_growth} (top panel) also shows that across all
-black hole masses, Compton heating also cannot prevent average
+line).
+Since the \citet{Miller+15} sample includes only early-type galaxies with older stellar populations than the average for their black hole mass, it would not be too surprising if many of these galaxies were thermally unstable.
+
+Figure \ref{fig:bh_growth} (top panel) also shows that Compton heating cannot prevent average
 accretion rates which are thermally unstable, i.e. $\dot{M}_{\rm C} >
-\dot{M}_{\rm TI}$.  In the case of thermal instabilities, nuclear gas
-may undergo cyclic oscillations of rapid cooling and high accretion
-rates, followed by quiescent periods once gas has been consumed and/or
-AGN feedback becomes effective.  Such cycles are proposed to occur on
-large scales and long timescales in elliptical galaxies
-(\citealt{Ciotti+10}), an idea possibly supported by, e.g., GALEX
-observations showing that a small fraction of early-type galaxies in
-the local universe have undergone recent ($< 1-2$ Gyr old) star
-formation episodes (\citealt{Donas+07}).  Similar cyclic AGN activity
-have been proposed to occur on the smaller scale of the sphere of
-influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuadra+15}).
-
-If such cyclic outbursts also manifest on the properties of gas on
-small, parsec scales, then the large scatter in the accretion rates
-and hence X-ray luminosities in Fig \ref{fig:miller} could result from
-the wide range of inflow rates experienced over the course of a cyclic
-episode between instabilities and periodic nuclear outbursts
-(e.g.~\citealt{Ciotti+10}).  Due to their deeper potential well, we
-find that core galaxies are more likely to possess higher accretion
-rates and potentially be thermally unstable for a fixed wind heating
-rate than cusp galaxies (Fig.~XXX).  This could help explain why core
-galaxies show a wide range of nuclear radio and X-ray luminosities
-(suggesting cyclic accretion episodes), while cusp galaxies are
-confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99,
-  Capetti&Balmaverde05}), consistent with thermally-stable,
-steady-state picture. ({\bf AG: This picture may be dubious...Review
+\dot{M}_{\rm TI}$, across all
+black hole masses.
+When thermal instabilities become manifest, nuclear gas may undergo cyclic oscillations of rapid cooling and high accretion rates, followed by quiescent periods once gas has been consumed and/or
+AGN feedback becomes effective.  Such cycles are seen in numerical simulations of elliptical galaxies on 
+large scales and long timescales (\citealt{Ciotti+10}), an idea which supported by observations showing that a fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+
+Similar cyclic AGN activity could occur on the smaller radial scale of the sphere of influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuadra+15}).
+In this case the large scatter in the X-ray luminosities shown in Fig \ref{fig:miller} could result from
+the wide range of inflow rates experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts.
+Due to their deeper potential wells, we find that core galaxies are more likely to possess higher accretion
+rates and potentially be thermally unstable for a fixed wind heating rate than cusp galaxies.
+This could help explain why core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99,   Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
+({\bf AG: This picture may be dubious...Review
   the literature but I think that the higher upper bound for cores is
-  just due to a mass selection effect.})
-
-If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$ in Fig
-\ref{fig:miller} represent thermally-unstable galaxies, then many of
-the upper limits may correspond to a separate ``thermally stable"
-population, for instance including SgrA*.  The possibility of a mixed
-population of stable versus unstable galaxies calls into question the
-use of simple extrapolations of power-law fits to the $L_{\rm
-  X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the
-occupation fraction of black holes in low mass galaxies
-(\citealt{Miller+15}).
+  just due to a mass selection effect.  BDM: The ghost of Balmaverde disagrees.})
+
+If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$ in Fig
+\ref{fig:miller} indeed represent thermally-unstable galaxies, then a fraction of the upper limits may contribute to a separate thermally stable population, for instance including SgrA*.
+However, the possibility of a mixed population of stable versus unstable galaxies calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
 

### 2015-03-31 ms.tex
fixed TDE section

@@
 range estimated by modeling the radio afterglow of {\it Swift}
-J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).
+J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}), as shown in Fig.~\ref{fig:bh_growth}.
 
 \citet{BergerZauderer+:2012a} infer a flattening of the gas density
-profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
-qualitatively similar to that the density profile we predict for core
-galaxies (Fig.~\ref{fig:profiles}, solid line), although to obtain
-such a flattening on the inferred radial scale, would require a large
-$\Mbh\sim 10^7 \Msun$.  Their inferred gas profile also shows a break
-at radii $\sim 0.6$ pc, which in our model corresponds to the break
-radius of the galaxy and hence would imply an unrealistically small
-SMBH mass $\Mbh\simeq 100\Msun$.  according to the mean relationship
-from the \citet{LauerFaber+:2007a} sample. A more likely explanation
-is that the observed break in the gas density is associated with a
-break in a nuclear star cluster in the galaxy {\bf AGs-ref Carson et
-  al. 2015.}.
-
-More detailed models for the environment, and the implications of our
-models for CNM profiles for the diversity of radio emission from TDE
-jets, will be explored further in future work.
+profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
+qualitatively similar to the shape density profile we predict for core
+galaxies (Fig.~\ref{fig:profiles}, solid line).
+To obtain such a flattening on the inferred radial scales would require a black hole of $\Mbh\sim 10^7 \Msun$.
+However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
+Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).
+Such compact star clusters could greatly enhance the rate of TDEs (e.g.~\citealt{Stone&Metzger15}), making this association uncoincidental.
+
+%The implications of our model for the CNM profiles of quiescent galaxies on the diversity of radio emission from TDE
+%jets will be further developed in future work.
 
@@
 
-\subsection{Nuclear Star Clusters}
-
-Our results could in principle also have implications for nuclear star clusters or globular clusters.
-{\bf BDM :Do we really want to talk about this?
-or is this an apology?
-I will let Aleksey fill in his ideas...}
-
 \section{Conclusions}

### 2015-03-31 ms.tex
more updates to table.
Lx caption

@@
 \includegraphics[width=\textwidth]{miller.pdf}
-\caption{\label{fig:miller} Average (unresolved) nuclear X-ray luminosity $\langle L_X \rangle = \epsilon_X \Mdot c^2$ as a function of SMBH mass, predicted from our models for the average star formation history (Fig.~\ref{fig:bh_growth}; {\it black line}) calculated for the average Nuker power-law index $\Gamma(M_{\bullet})$ derived from the galaxy sample of \citet{LauerFaber+:2007a}.
-Shown for comparison are the measurements $L_X/L_{\rm edd}$ values (red stars) and
-  upper limits (red triangles) from the \citet{Miller+15} sample of early-type galaxies, with a green line showing the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$.
-The left panel shows the case of a constant radiative efficiency $\epsilon_X=10^{-4}$, while the right hand panel shows an efficiency $\epsilon_X=
-  \left(\frac{\epsilon_{\rm bol}}{0.1}\right)\frac{\Mdot}{\MdotEdd}$ predicted by some models for radiatively inefficient accretion.
-Also shown for comparison are the X-ray luminosities calculated using the maximum thermally-stable accretion rate ({\it orange line}), SN Ia-regulated accretion rate, and Compton-regulated accretion rate ({\it pink line}),  again calculated for the average star formation history.}
+\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
+Black lines show our prediction in the case of heating due to the average star formation history for galaxies corresponding to each black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the relationship  $\Gamma(M_{\bullet})$ derived from the \citet{LauerFaber+:2007a} sample.
+Shown for comparison are the measurements ({\it red stars}) and
+  upper limits ({\it red triangles}) for $L_X/L_{\rm edd}$ values, from the \citet{Miller+15} sample of early-type galaxies (a green line shows the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).
+The left panel is calculated assuming a constant radiative efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand panel assumes $\epsilon_X=
+  (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g., \citealt{Narayan&Yi95}).
+Shown for comparison are the X-ray luminosities calculated for the maximum thermally-stable accretion rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion rate  ({\it pink line}; eq.~[\ref{eq:MdotCa}]),  again all calculated for the average star formation history corresponding to each SMBH mass.}
 \end{figure*}

### 2015-04-01 ms.tex
quelled the challenge

@@
   & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
-  $    10^{ 6 }$ & 300 & 100 & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
-... & 600 & 100 & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
-... & 1200 & 100 & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
+  $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
+... & 600 & -- & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
+... & 1200 & -- & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
 $    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 \\
@@
 ... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+... & 450 & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 19 \\
 ...$^{\dagger}$ & 450 & 100 & 1.2 & $ 8.1 \times 10^{ -4 }$ & 2.6 \\
@@
 ... & 1200 & 25 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
-... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
-... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+% ... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+% ... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
 $    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\
@@
  ... & ... & 50 & $ 4.1 \times 10^{ -2 }$ & $ 1.5 \times 10^{ -6 }$ & $ 2.3 \times 10^{ 4 }$ \\
-... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\
+% ... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\
 $    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ & $ 1.0 \times 10^{ 2 }$ \\
@@
 
-We focused on Compton radiative feedback in this paper, since its
-efficacy was straightforward to calculate in terms of the properties
-of the accretion flow.  However, if kinetic outflow feedback from the
-jet or accretion disk could is important, this could also have some
-influence on limiting the accretion rate, especially onto high mass
-black holes.  The effective wind heating velocity due to kinetic
-heating rate is proportional to the SMBH mass to a positive power,
-$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
-galaxies, respectively (eq.~[\ref{eq:vjet}]).  Coupled with the
-dependence of accretion rate on wind heating, $\dot{M}/\dot{M}_{\rm
-  edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
-(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), SMBH heating
-of the formed we have adopted would lead to an Eddington ratio
-dependence $\dot{M}/\dot{M}_{\rm edd} \propto
-M_{\bullet}^{-0.5(-0.2)}$.  This prediction of an increasing Eddington
-ratio is in better with the observed dependence of $\langle
-L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
-(Fig.~\ref{fig:miller}), suggesting a possible explanation of stable
-accretion maintained by kinetic feedback as an alternative explanation
-for X-ray luminosities of elliptical galaxies.  On the other hand, our
-assumption that outflows heat the gas uniformly in volume is arbitrary
-and would need to more rigorously justified by numerical studies of
-how jets or disk outflows couple energy to their gaseous environment
-(Refs).
-
-For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
-to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
+Our analysis of black hole feedback has focused on Compton heating instead of kinetic feedback, since the efficacy of radiative feedback is relatively straightforward to calculate given the properties of the accretion flow.
+However, if kinetic feedback instead dominates, this could play an important role in regulating SMBH growth.
+Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an effectic wind velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.
+Coupled with the dependence of the SMBH accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), kinetic feedback of the form we have adopted leads to an Eddington ratio dependence on SMBH mass of $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
+
+This prediction is in better with the observed dependence of $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies (Fig.~\ref{fig:miller}, green line), hinting that accretion regulation by kinetic feedback may serve as an alternative explanation for X-ray luminosities of elliptical galaxies.
+However, our assumption that kinetic outflows heat the gas uniformly in volume is somewhat arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous environment.
+It is furthermore unclear whether our steady-state model can be applied at all, because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scales.
+
+%For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
+%to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
 Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
-However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
+%However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
 Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
 
-{\bf AG Challenge: Except in the most massive systems the jet duty
-  cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
-  and then periodically turn once the gas begins to cools
-  (Refs). Thus, jets cannot be treated as a truly steady source of
-  heating. 
-}
+%{\bf AG Challenge: Except in the most massive systems the jet duty
+ % cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
+  %and then periodically turn once the gas begins to cools
+  %(Refs). Thus, jets cannot be treated as a truly steady source of
+  %heating. 
+%}
 

### 2015-04-01 ms.tex
conclusions1

@@
   Eddington ratios inferred for SgrA* from
-  \citet{Quataert:2004a} (line with black circle), for NGC3115 from
-  \citet{ShcherbakovWong+:2014a} (line with black diamonds), and for
-  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (line
-  with black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
+  \citet{Quataert:2004a} (black circles), for NGC3115 from
+  \citet{ShcherbakovWong+:2014a} (black diamonds), and for
+  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
   in units of the Hubble time $\th$ for each of the accretion rates
@@
 
-We have calculated steady-state models for circumnuclear medium of
-quiescent galaxies, assuming that gas is supplied entirely by stellar
-wind mass loss and heated by shocked stellar winds, supernovae and
-black hole feedback. We compute profiles for a range of different
-black hole masses, heating rates, and stellar density profiles and use
-these profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and
-get the scaling of $\Mdot$ with $\Mbh$. We may then compare our
-results with observed trends of nuclear x-ray luminosity with galaxy
-properties. Our main conclusions may be summarized as follows.
+We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.
+We compute solutions for a range of different black hole masses, heating rates, and stellar density profiles.
+Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}), which are in turn used to calculate the black hole accretion rate and how it varies with $\Mbh$ and the galaxy's star formation history.
+Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, as well as to address other key questions, such as the thermal stability of their accretion flows.
+Our conclusions may be summarized as follows.
 
@@
   %lower vw except for very young stellar populations.
-  \item The gas will be divided between an accretion flow and an
-    outward flow at the stagnation radius, $\rs$. In a steady state
-    the gas inflow rate towards the hole will be proportional to the
+  \item The stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
+    outward wind. In a steady state the gas inflow rate towards the black hole will be proportional to the
     stellar mass enclosed inside of $\rs$. 
   \item The location of the stagnation radius and thus the accretion
-    rate is quite sensitive to the effective heating rate of the
-    gas. In our model gas is supplied by stellar winds and the kinetic
-    energy of the winds is thermalized as the winds
-    collide. Supernovae and AGN feedback may provide additional
-    sources of heating. Each source of heating is related to the star
-    formation history of the galaxy.  For example, a galaxy with star
-    formation within the last $\sim10^7$ years would have mass
-    injection from very fast stellar winds ($w_w\simeq 1000$ km/s). In
-    contrast, an older population would have heating only from AGN
-    feedback and supernovae.
+    rate is very sensitive to the effective heating rate of the
+    gas.  Stellar wind heating, supernovae, and AGN feedback depend on the black hole mass as well as the star
+    formation history of the galaxy.
+For example, for a galaxy with star formation within the last $\sim10^7$ years, both mass and energy injection are dominated by fast stellar winds from young stars ($w_w\simeq 1000$ km/s).
+In contrast, a galaxy with star formation relegated to the distant pass would have mass input dominated by old stars and heating dominated by AGN feedback and supernovae.
+The energy input for galaxies with ongoing, continuous star formation is usually dominated by the youngest stars, while mass input is dominated by the old stellar poupation.
 

### 2015-04-01 ms.tex
conclusions2

@@
     \vw^2} \approx \frac{13+8\Gamma}{12+6\Gamma}r_{\rm B},
-  \label{eq:rs_simple}
+  \label{eq:rbondi}
 \end{align}
@@
 We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.
-We compute solutions for a range of different black hole masses, heating rates, and stellar density profiles.
-Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}), which are in turn used to calculate the black hole accretion rate and how it varies with $\Mbh$ and the galaxy's star formation history.
-Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, as well as to address other key questions, such as the thermal stability of their accretion flows.
+We compute solutions for a range of different black hole masses, heating rates, and observationally-motivated stellar density profiles.
+Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).
+The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's star formation history.
+Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, and used to address other key questions, such as the thermal stability of their accretion flows.
 Our conclusions may be summarized as follows.
@@
   %lower vw except for very young stellar populations.
-  \item The stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
+  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
     outward wind. In a steady state the gas inflow rate towards the black hole will be proportional to the
-    stellar mass enclosed inside of $\rs$. 
-  \item The location of the stagnation radius and thus the accretion
-    rate is very sensitive to the effective heating rate of the
-    gas.  Stellar wind heating, supernovae, and AGN feedback depend on the black hole mass as well as the star
-    formation history of the galaxy.
-For example, for a galaxy with star formation within the last $\sim10^7$ years, both mass and energy injection are dominated by fast stellar winds from young stars ($w_w\simeq 1000$ km/s).
-In contrast, a galaxy with star formation relegated to the distant pass would have mass input dominated by old stars and heating dominated by AGN feedback and supernovae.
-The energy input for galaxies with ongoing, continuous star formation is usually dominated by the youngest stars, while mass input is dominated by the old stellar poupation.
-
-    Quantitatively $\rs\sim v_w^{-2}$, which implies $\Mdot\sim
-    v_w^{-3.8 (-2.4)}$ for core (cusp galaxies). However, $\Mdot$ may
-    increase more rapidly for small $v_w$ for two reasons. (1) When
-    $v_w$ becomes comparable to the stellar velocity dispersion, the
+    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius is close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
+  \item The location of the stagnation radius, and thus the SMBH accretion rate, is extremely sensitive to the effective heating rate of the gas.
+Stellar wind heating, supernovae, and AGN feedback depend on the SMBH mass as well as the star
+    formation history in the galactic nucleus.
+For example, a recent burst of star formation within the last $\sim 10$ Myr results in both mass and energy injection being dominated by the fast stellar winds of young stars ($v_w \sim 1000$ km s$^{-1}$).
+By contrast, when star formation is relegated to the distant pass, mass input becomes dominated by old stars while heating is dominated by AGN feedback and supernovae.
+For nuclei with ongoing, continuous star formation, energy input is usually dominated by the youngest stars, while mass input is dominated by the old stellar population.
+
+    Quantitatively $\rs\propto v_w^{-2}$, which implies that $\Mdot\sim
+    v_w^{-3.8 (-2.4)}$ for core (cusp galaxies).
+However, $\Mdot$ may increase more rapidly for small $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), the
     gas inside of the break radius inside of the break radius inside

### 2015-04-01 ms.tex
conclusions4

@@
 Our analysis of black hole feedback has focused on Compton heating instead of kinetic feedback, since the efficacy of radiative feedback is relatively straightforward to calculate given the properties of the accretion flow.
-However, if kinetic feedback instead dominates, this could play an important role in regulating SMBH growth.
+However, if kinetic feedback instead dominates, this could play an important role in regulating the accretion.
 Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an effectic wind velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.
@@
   \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
-    outward wind. In a steady state the gas inflow rate towards the black hole will be proportional to the
+    outward wind. In a steady state the gas inflow rate towards the black hole is proportional to the
     stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius is close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
-  \item The location of the stagnation radius, and thus the SMBH accretion rate, is extremely sensitive to the effective heating rate of the gas.
+  \item The location of the stagnation radius, and thus the SMBH accretion rate, is sensitive to the effective heating rate of the gas.
 Stellar wind heating, supernovae, and AGN feedback depend on the SMBH mass as well as the star
     formation history in the galactic nucleus.
-For example, a recent burst of star formation within the last $\sim 10$ Myr results in both mass and energy injection being dominated by the fast stellar winds of young stars ($v_w \sim 1000$ km s$^{-1}$).
-By contrast, when star formation is relegated to the distant pass, mass input becomes dominated by old stars while heating is dominated by AGN feedback and supernovae.
-For nuclei with ongoing, continuous star formation, energy input is usually dominated by the youngest stars, while mass input is dominated by the old stellar population.
-
-    Quantitatively $\rs\propto v_w^{-2}$, which implies that $\Mdot\sim
-    v_w^{-3.8 (-2.4)}$ for core (cusp galaxies).
-However, $\Mdot$ may increase more rapidly for small $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), the
-    gas inside of the break radius inside of the break radius inside
-    of the stellar density profile is bound and cannot move
-    outflow. (2) For $v_w\simeq200 $ km/s the gas may become thermally
-    unstable and there may be a cycle of alternating high and low
-    accretion rates onto the BH as described in...{\bf AG: Fill in}
-
-  \item We find that galaxies with $\Mbh\gsim 10^6 \Msun$ and
-    $\Mbh\lsim 10^8$ following average star formation histories
-    measured in cosmological simulations \citep{MosterNaab+:2013a}
-    have sufficient recent star formation to have an effective
-    $v_w\simeq 1000$ km/s. $\eddr \propto \Mbh^{\alpha}$ with
-    $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies This is in
-    tension observations of nuclear X-ray luminosity which suggest
-    that $\eddr$ increases towards smaller $\Mbh$
-    \citep{Miller+15}. However, it is important to note that the
-    inflow rate on large scales (which we calculate) may differ from
-    the actual accretion rate as outflows could occur on small
-    scales. The outflow rate would depend on the angular momentum of
-    the infalling gas and thus the angular momentum of stars in the
-    nucleus. The in turn would vary systematically with $\Mbh$.
+A recent burst of star formation within the last $\sim 10$ Myr results in mass and energy injection both being dominated by fast stellar winds from young stars ($v_w \sim 1000$ km s$^{-1}$).
+If star formation is instead relegated to the distant past, mass input becomes dominated by old stars while heating is dominated by AGN feedback and supernovae.
+For nuclei with ongoing, continuous star formation, energy input is usually dominated by the youngest stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
+
+Quantitatively $\rs\propto v_w^{-2}$, which implies that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+However, $\Mdot$ will increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), gas remains bound to the stellar bulge and cannot flow out (Appendix \ref{app:be}).
+(2) For sufficiently low $v_w$ the gas near the stagnation radius becomes thermally unstable, potentially resulting in cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$; e.g.,\citealt{Ciotti+10}).
+
+  \item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8 \Msun$ with star formation histories matching the average values derived from the cosmological simulations of \citet{MosterNaab+:2013a} possess an effective heating rate
+    $v_w\sim 1000$ km s$^{-1}$, relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).
+This results in a prediction for the average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension with the trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}), which instead find that $\eddr$ increases towards smaller $\Mbh$.
+However, high X-ray radiative efficiencies are required for these galaxies to be consistent with thermally-stable accretion, instead suggesting that (at least at low black hole masses), the possibility of two branches of accretion states.
+
+%However, it is important to note that the
+ %   inflow rate on large scales (which we calculate) may differ from
+  %  the actual accretion rate as outflows could occur on small
+   % scales. The outflow rate would depend on the angular momentum of
+    %the infalling gas and thus the angular momentum of stars in the
+    %nucleus. The in turn would vary systematically with $\Mbh$.
 

### 2015-04-02 ms.tex
ahhhh

@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ can in many cases reside near the
-nominal Bondi radius).  When heating is sufficiently weak, however, no stagnation radius may exist at all, i.e. the entire ISM of the galaxy is flowing towards the SMBH.  A goal of this work is to
-assess under what conditions a stagnation radius exists, as this
-question is intimately tied to that of cooling instability.
+show that $\rs$ can in many cases resides near the nominal Bondi
+radius).  When heating is sufficiently weak, however, the stagnation
+radius may not exist at all, i.e. the entire ISM of the galaxy is flowing
+towards the SMBH.  A goal of this work is to assess under what
+conditions a stagnation radius exists, as this question is intimately
+tied to that of cooling instability.
 % Furthermore, in some cases we find that no stagnation
@@
 numerical results.  In $\S\ref{sec:discussion}$ we discuss the
-implications of our results, to topics including the nuclear X-ray luminosities of quiescent black holes, jetted TDEs, and the growth time of SMBHs.
-In $\S\ref{sec:conclusions}$ we summarize our conclusions.
-Table
-\ref{table:definitions} provides the definitions of commonly used
-variables.  Appendices \ref{app:rs} and \ref{app:be} provides useful
-analytic results, while Appendix \ref{app:windheat} describes our
-method for calculating stellar wind heating and mass input in greater
-detail.
+implications of our results, to topics including the nuclear X-ray
+luminosities of quiescent black holes, jetted TDEs, and the growth
+time of SMBHs.  In $\S\ref{sec:conclusions}$ we summarize our
+conclusions.  Table \ref{table:definitions} provides the definitions
+of commonly used variables.  Appendices \ref{app:rs} and \ref{app:be}
+provide useful analytic results for the stagnation radius and the
+Bernoulli parameter of the flow, while Appendix
+\ref{app:windheat} describes our method for calculating stellar wind
+heating and mass input in greater detail.
 
@@
 solution, in particular for high SMBH masses and low heating rates,
-for which the stagnation radius approaches large radii.
+for which the stagnation radius approaches large radii. {\bf AG
+  describe unphysically large rb for the case of cores.}
 
@@
 
-We first describe analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.
-Our results are expressed in terms of the SMBH mass $M_{\bullet}$, total heating rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
+We first describe analytic estimates of physical quantities, such as
+the stagnation radius $\rs$ and the mass accretion rate, the detailed
+derivation of which are given in Appendix \ref{app:rs}.  Our results
+are expressed in terms of the SMBH mass $M_{\bullet}$, total heating
+rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
 
@@
   \tilde{v}_{w}^{2}}{2k} \approx \frac{\gamma-1}{\gamma}\frac{\mu
-  m_p v_w^2}{2k} \frac{3+8\Gamma}{3+8\Gamma-6\nu} \nonumber\\ 
+  m_p v_w^2}{2k} \frac{13+8\Gamma}{13+8\Gamma-6\nu} \nonumber\\ 
  &\approx
@@
 \end{align}
-where the first line for each case is derived using equation (\ref{eq:eddr_analytic}) to calculate
-$\dot{M}(v_{\rm TI})$, whereas the second line corresponds to the low wind heating limit and is calculated for core galaxies using the empirical correlation $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{0.2}$ which follows from equation (\ref{eq:rsoi}) and the results of \citet{LauerFaber+:2007a}.
-
-% For each of our galaxies Table \ref{tab:eta} provides the maximum value of $\eta$ such that $H/C >$1 at all radii.
-Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
-If cooling is important, the CNM is likely to be thermally unstable, resulting in the formation of a cold medium that could substantially enhance the rate of accretion onto the SMBH.
-
-%\begin{align}
- % \Lambda(T)\simeq
-  %\begin{cases}
-   % 2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
-   % 1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
-  %\end{cases}
-  %\label{eq:cooling}
-%\end{align}
+where the first line for each case is derived using equation
+(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
+the second line corresponds to the low wind heating limit and is
+calculated for core galaxies using the empirical correlation
+$r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which follows from
+equation (\ref{eq:rsoi}) and the results of \citet{LauerFaber+:2007a}.
 
@@
 
-Our numerical results, summarized in Table \ref{table:models}, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.
-Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 10$ {\bf BDM: correct?} at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
+Our numerical results, summarized in Table \ref{table:models}, allow
+us to study a range of CNM properties and to assess the validity of
+the analytic estimates from the previous section.
+
+We include a few solutions with cooling (marked with a $\dagger$) and
+conductivity (marked with a $\ddagger$) Table \ref{table:models} to
+assess whether it is valid to neglect these effects. As expected
+solutions for which $\dot{q}_{\rm heat}/\dot{q}_{\rm rad}\gg 1$ are
+unaffected when radiative cooling is included (see the solution with
+$\Mbh=10^{8} \Msun, v_w=600 {\rm km/s and} \gamma=0.8$. However, we
+find that as we decrease the heating further, to cooling begins to
+become more important (see $\Mbh=10^{8} \Msun, v_w=450 {\rm km/s and}
+\gamma=0.8$). Overall, we find radiative cooling has negligible effect
+on cusp solutions $v_w\geq 600 km/s$ in and core solutions with
+$v_w=1200$ km/s {\bf AG for the purposes of description it may be
+  simpler to just rerun all of our models with radiative cooling}.
+
+We re-ran all cusps ($\Gamma=0.8$) with $v_w=300$ km/s and
+all cores ($\Gamma=0.1$) with $v_w=600 $ km/s with radiative cooling
+for three different values of the mass input parameter $\eta$--0.02,
+0.2, and 0.6.  Note that $\eta=0.02$ is the minimum expected physical
+mass input parameter. Solutions which were unstable for all values of
+$\eta$ are marked with a $\mathbf{TI}$ {\bf solution that were
+  unstable for only some choices of eta}.
 
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
-temperature $T(r)$, and radial velocity $|v(r)|$ (expressed in units of the sound speed), for the cusp
-($\Gamma=0.8$) solutions within our grid.  As expected, the gas
-density increases towards the SMBH $\rho\propto r^{-\densSlope}$ with
-$\densSlope\simeq1$, i.e. shallower than the $-3/2$ power law for
-Bondi accretion. This power law behavior does not extend
-through all radii, however, as the gas density profile has a break coincident
-with the location of the break in the stellar light profile ($\rb=100$
-pc). The temperature profile is relatively flat at large radii, but
-increases as $\propto 1/r^{k}$ interior to the sphere of influence,
-where $k\lesssim 1$, somewhat shallower than expected for virialized gas within the black hole sphere of influence.
-The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
-The flow near the stagnation radius is subsonic, but becomes supersonic at two critical points, one located at small radii, $r \lesssim 0.1r_{\rm s}$, and the other located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.
-In many cases the supersonic transition is instigated by the transition to a steeper stellar density profile exterior to the outer Nuker break radius, making our solutions near $r_{\rm s}$ also potentially sensitive to the break radius value.
-% {\bf BDM: I made this up - in general we need
-%   more explanation of what the plots are actually showing, with some
-%   physical explanation.}
-% AG -- things are not quite approaching Bondi on the inner grid. I
-% don't have a good physical explanation yet...
-
-Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
-  soi}$ as a function of the wind heating parameter $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors showing different values of $v_{w}$.
-Cusp and core galaxies are marked with square and triangles,
-respectively.  Shown for comparison are our analytic results
-(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
-galaxies, respectively, calculated assuming $\densSlope = 1$ and
-$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).
-
-Our analytic estimates accurately reproduce the numerical results in the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s} \lesssim r_{\rm soi}$).
-However, for sufficiently low heating the stagnation radius diverges above the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.
-This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $\zeta$ in the case of core galaxies ($\Gamma = 0.8$) with large break radii.
-This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $\zeta$ close to where the analytic estimate diverges; these correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom) corresponding to successively larger values of $\zeta_c$.
-
- Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for each of our numerical solutions in Eddington units for different values of $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).
-Shown for comparison is our analytic estimate of $\dot{M}/\dot{M}_{\rm edd}$ from equation (\ref{eq:eddr_analytic}).
-For high wind velocities ($v_{w} \gg \sigma$) the stagnation lies well inside the black hole sphere of influence and our analytic estimate provides a good fit to the numerical results.
-However, for low wind velocities and/or high $M_{\bullet}$ (large $\sigma$), the numerical accretion rate considerably exceeds the analytic estimate as the stagnation radius diverges to large radii (Fig.~\ref{fig:stag}).
-%% AG: Describe conservation checks to additionally validate the results.
+temperature $T(r)$, and radial velocity $|v(r)|$ (expressed in units
+of the sound speed), for the cusp ($\Gamma=0.8$) solutions within our
+grid.  As expected, the gas density increases towards the SMBH
+$\rho\propto r^{-\densSlope}$ with $\densSlope\simeq1$, i.e. shallower
+than the $-3/2$ power law for Bondi accretion. This power law behavior
+does not extend through all radii, however, as the gas density profile
+has a break coincident with the location of the break in the stellar
+light profile ($\rb=100$ pc). The temperature profile is relatively
+flat at large radii, but increases as $\propto 1/r^{k}$ interior to
+the sphere of influence, where $k\lesssim 1$, somewhat shallower than
+expected for virialized gas within the black hole sphere of influence.
+The inwardly directed velocity increases towards the hole with a
+profile that is somewhat steeper than the local free-fall velocity $v
+\propto v_{\rm ff}\propto r^{-1/2}$.  The flow near the stagnation
+radius is subsonic, but becomes supersonic at two critical points, one
+located at small radii, $r \lesssim 0.1r_{\rm s}$, and the other
+located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.  In many cases
+the supersonic transition is instigated by the transition to a steeper
+stellar density profile exterior to the outer Nuker break radius,
+making our solutions near $r_{\rm s}$ also potentially sensitive to
+the break radius value.
+
+Figure~\ref{fig:stag} shows our calculation of the stagnation radius
+$r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
+$\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors
+showing different values of $v_{w}$.  Cusp and core galaxies are
+marked with square and triangles, respectively.  Shown for comparison
+are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and
+dashed lines for cusp and core galaxies, respectively, calculated
+assuming $\densSlope = 1$ and $\densSlope= 0.6$, respectively
+(eq.~[\ref{eq:densSlope}]).
+
+Our analytic estimates accurately reproduce the numerical results in
+the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
+\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
+stagnation radius diverges above the analytic estimate, approaching
+the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
+occurs approximately when $\zeta =
+\sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix
+\ref{app:be}), and hence occurs at a higher value of $\zeta$ in the
+case of core galaxies ($\Gamma = 0.8$) with large break radii.
+
+As $\zeta$ approached $\zeta_c$, the results the location of the
+stagnation radius will depend on the location of the break radius
+$\rb$.  This explains the behavior of the two core galaxies, shown as
+orange triangles vertically aligned at the same value of
+$\zeta$. These correspond to models with the same black hole mass
+($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
+different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
+bottom). {\bf AG still needs work}
+
+Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for each of
+our numerical solutions in Eddington units for different values of
+$\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core
+($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).  Shown for comparison
+is our analytic estimate of $\dot{M}/\dot{M}_{\rm edd}$ from equation
+(\ref{eq:eddr_analytic}).  For high wind velocities ($v_{w} \gg
+\sigma$) the stagnation lies well inside the black hole sphere of
+influence and our analytic estimate provides a good fit to the
+numerical results.  However, for low wind velocities and/or high
+$M_{\bullet}$ (large $\sigma$), the numerical accretion rate
+considerably exceeds the analytic estimate as the stagnation radius
+diverges to large radii (Fig.~\ref{fig:stag}).
 
@@
   \includegraphics[width=\columnwidth]{rs.eps}
-  \caption{\label{fig:stag} Stagnation radius
-    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
-    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of the stellar wind heating parameter $\zeta \equiv \sqrt{v_w^{2} + \sigma_0^{2}}/\sigma_0$.  Green, orange, and blue
-    symbols correspond to different values of $v_{w} =$ 300, 600, and
-    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
-    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
-    ($\Gamma = 0.1$). The black curves correspond to the analytic
-    prediction from equation (\ref{eq:rs2main}), with solid and dashed
-    curves calculated for parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
-    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
+  \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
+    sphere of influence radius $r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]) for
+    galaxies in our sample as a function of the stellar wind heating
+    parameter $\zeta \equiv \sqrt{v_w^{2} + \sigma_0^{2}}/\sigma_0$.
+    Green, orange, and blue symbols correspond to different values of
+    $v_{w} =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
+    correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
+    correspond to cores ($\Gamma = 0.1$). Green crosses correspond to
+    cusp solutions which would be thermally unstable. The black curves correspond
+    to the analytic prediction from equation (\ref{eq:rs2main}), with
+    solid and dashed curves calculated for parameters $\{\Gamma=0.8,
+    \densSlope\simeq1\}$ and $\{\Gamma=0.1,\densSlope\simeq0.6\}$,
+    respectively. }
 \end{figure}

### 2015-04-02 ms.tex
references.

@@
 \end{align}
- in conjunction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:rs_simple}), one derives
+ in conjunction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:stag_simple}), one derives
 \begin{align}
@@
     correspond to cores ($\Gamma = 0.1$). Green crosses correspond to
-    cusp solutions which would be thermally unstable. The black curves correspond
-    to the analytic prediction from equation (\ref{eq:rs2main}), with
-    solid and dashed curves calculated for parameters $\{\Gamma=0.8,
-    \densSlope\simeq1\}$ and $\{\Gamma=0.1,\densSlope\simeq0.6\}$,
-    respectively. }
+    cusp solutions which would be thermally unstable. The black curves
+    correspond to the analytic prediction from equation
+    (\ref{eq:rs2main}), with solid and dashed curves calculated for
+    parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
+    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
 \end{figure}
@@
 Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting
-$v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:rs_simple})
+$v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:stag_simple})
 for the stagnation radius, we find that
@@
 estimated from equation (\ref{eq:mdot_analytic}).  Then using
-equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}),
+equations (\ref{eq:stag_simple}), (\ref{eq:mdot_analytic}),
 (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
@@
 
-Our analysis of black hole feedback has focused on Compton heating instead of kinetic feedback, since the efficacy of radiative feedback is relatively straightforward to calculate given the properties of the accretion flow.
-However, if kinetic feedback instead dominates, this could play an important role in regulating the accretion.
-Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an effectic wind velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.
-Coupled with the dependence of the SMBH accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
-(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), kinetic feedback of the form we have adopted leads to an Eddington ratio dependence on SMBH mass of $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
+Our analysis of black hole feedback has focused on Compton heating
+instead of kinetic feedback, since the efficacy of radiative feedback
+is relatively straightforward to calculate given the properties of the
+accretion flow.  However, if kinetic feedback instead dominates, this
+could play an important role in regulating the accretion.  Our simple
+parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an
+effectic wind velocity which increases with SMBH mass as
+$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
+galaxies, respectively.  Coupled with the dependence of the SMBH
+accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto
+M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass};
+eq.~[\ref{eq:eddr_analytic}]), kinetic feedback of the form we have
+adopted leads to an Eddington ratio dependence on SMBH mass of
+$\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
 

### 2015-04-03 be.tex
more changes

--- 2015-03-28 be.tex
@@
-We derive an expression for the bernoulli parameter of the gas, $\ke
-+\gammaf \frac{p}{\rho}+\Phi$, assuming that the stellar density
-profile $\rhostar\sim r^{\delta}$ inside of the break radius $\rb$.
+Here we derive an expression for the Bernoulli parameter, 
+\be
+\mathcal{B} \equiv \ke
++\gammaf \frac{p}{\rho}+\Phi,
+\ee
+assuming a stellar density profile $\rhostar\sim r^{-1-\Gamma}=r^{-\delta}$ characteristic of that inside the break radius $\rb$.
 
-Consider the steady state energy conservation equation. {\bf AG perhaps
-  put a brief explanation of how this relates to the steady state
-  entropy equation via laws of thermodynamics?.}
-
+Basic manipulation of the equations of hydrodynamics (eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following relationship between the Bernoulli parameter and the net heating rate $\propto q \vw^{2}$,
 \begin{align}
-\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \left(\frac{v^2}{2} + \Phi
-    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi,
+\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \mathcal{B} \right) = q \kew + q \Phi = \frac{3}{1+\delta}\frac{G
+  \Mbh}{r}+\sigma_0^2+v_w^2 + q \Phi,
 \label{eq:enCons}
 \end{align}
+where the first and second terms on the right hand side correspond, respectively, to the black hole and stellar contributions to the velocity dispersion.
 
-Where $\vw^2=v_w^2+\sigma^2= v_w^2+\frac{3}{\Gamma+2}\frac{G
-  \Mbh}{r}+\sigma_0^2$.
-
-Now integrate both sides with respect from r to the stagnation radius
-
+Integrating both sides of equation~\eqref{eq:enCons} from the stagnation radius $r = \rs$ outwards,
 \begin{align}
@@
 \end{align}
-
-We know $f\equiv r^2 \rho v$ from the steady state mass conservation
-equation.
-
+From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be written
+\be
+ f\equiv r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
+ \label{eq:massFlux}
+\ee
+where $x \equiv r/\rs$ and we have used the fact that the mass source term $q = q_o x^{-\delta}$ is proportional to the stellar density.  Likewise, the gravitational potential $\Phi$ is given by
 \begin{align}
- \frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v\right) = q 
-\end{align}
-
-Where q is the rate of the mass injection per volume, which is
-proportional to the stellar density. Let $x=r/\rs$ and $q_o= q
-(\rs)$. Then $q=q_o x^{-\delta}$.
-
-Then one obtains for the mass flux, $f=r^2 \rho v$,
-
-\begin{align}
- f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right].
- \label{eq:massFlux}
-\end{align}
-
-The gravitational potential $\Phi$ is given by
-
-\begin{align}
-\Phi&= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\infty} \rhostar(r') r'
-dr'.\nonumber\\
-&\simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr'
+\Phi \simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr',
 \label{eq:Phi}
 \end{align}
+where by truncating the integral at $r = \rb$ we are neglecting the contribution to the potential of the stars outside of the break radius.
 
-Where in the scond line we have neglected the contribution of the
-stars outside of the break radius, $\rb$, to the gravitational potential.
-
-% Note our unconventional choice of gauge: the upper limit of the
-% integral on the right hand side is $\rs$ whereas conventionally the
-% upper limit is taken to be $\infty$. This means that our definition
-% will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
-% our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
-% gauge invariant.
-
-Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
-and~\eqref{eq:Phi}, we may obtain an expression for the Bernoulli
-parameter of the gas, $\ke+\gammaf \frac{p}{\rho} +\Phi$ of the gas inside
-of the break radius $\rb$.
-
+Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with the result of equation \eqref{eq:Phi}, we obtain 
 \begin{align}
-  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} +\Phi = \nonumber\\
-  &-U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
+  &\mathcal{B} = -U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
   &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
@@
 \end{align}
-
 where $U_o=4 \pi G \rhostar(\rs) \rs^2$.  We may rewrite this as
@@
 \begin{multline}
-  \frac{v^2}{2}+\gammaf \frac{p}{\rho}+\Phi
-=\frac{G \Mbh}{\rs} 
+  \mathcal{B} =\frac{G \Mbh}{\rs} 
 \biggl[
@@
   -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
-\biggr].
+\biggr],
 \label{eq:enthAnal}
 \end{multline}
-
-Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
+where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv (\rs/\rsoi)^{3\delta}$, and
 $\delta$ is the power law slope of the stellar density profile inside
@@
 
-% For sufficiently large radii ($x$), the expression above always
-% becomes negative, which means that a break in the stellar density
-% profile is necessary in order to obtain an outflow.
- For a given $\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such
- that if $\zeta>\zeta_c$, an outflow will be possible from any
-radius, since the Bernoulli parameter will be positive inside of the
-break radius. On the other hand if $\zeta<\zeta_c$, then there is a
-minimum value of $(\rs/\rsoi)_{\rm min}$. If we have had
-$\rs/\rsoi<(\rs/\rsoi)_{\rm min}$, then the Bernoulli parameter would
-become negative inside of $\rb$ and no outflow would be possible.
-
-For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
-($v_w\simeq\sigma_0$).  On the other hand for core galaxies
-($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$, see the top
-panel of Fig.~\ref{fig:zetaCrit}. For values of $\zeta<\zeta_c$, the
-stagnation radius rapidly approaches the break radius as shown in the
+When the rate of external heating is high, we have $\mathcal{B} > 0$ at all radii, requiring an outflow.
+As heating ($\zeta$) is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ first becomes negative.
+If $\zeta<\zeta_c$, then there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$, above which we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive kinetic energy at infinity.
+The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
+Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
+Fig.~\ref{fig:zetaCrit}).
+Likewise $(r_{\rm s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right numbers here}.
+For values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches the break radius as shown in the
 bottom panel of Fig.~\ref{fig:zetaCrit}.
-% We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
-% for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
-% less than this value the gas enthalpy would become negative inside of
-% the break radius which is clearly unphysical.  This may be roughly
-% approximated using (see Fig.~\ref{fig:rbRinf})
-
-% \begin{align}
-% &\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
-% &\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
-% \label{eq:rsRinfCrit}
-% \end{align}
 

### 2015-04-03 be.tex
appendix

@@
-Here we derive an expression for the Bernoulli parameter, 
-\be
-\mathcal{B} \equiv \ke
-+\gammaf \frac{p}{\rho}+\Phi,
-\ee
-assuming a stellar density profile $\rhostar\sim r^{-1-\Gamma}=r^{-\delta}$ characteristic of that inside the break radius $\rb$.
+Here we derive an expression for the Bernoulli parameter, \be
+\mathcal{B} \equiv \ke +\gammaf \frac{p}{\rho}+\Phi, \ee assuming a
+stellar density profile $\rhostar\sim r^{-1-\Gamma}=r^{-\delta}$
+characteristic of that inside the break radius $\rb$.
 
-Basic manipulation of the equations of hydrodynamics (eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following relationship between the Bernoulli parameter and the net heating rate $\propto q \vw^{2}$,
+Basic manipulation of the equations of hydrodynamics
+(eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following
+relationship between the Bernoulli parameter and the net heating rate
+$\propto q \vw^{2}$,
 \begin{align}
@@
 \end{align}
-where the first and second terms on the right hand side correspond, respectively, to the black hole and stellar contributions to the velocity dispersion.
+where the first and second terms on the right hand side correspond,
+respectively, to the black hole and stellar contributions to the
+velocity dispersion.
 
-Integrating both sides of equation~\eqref{eq:enCons} from the stagnation radius $r = \rs$ outwards,
+Integrating both sides of equation~\eqref{eq:enCons} from the
+stagnation radius $r = \rs$ outwards,
 \begin{align}
@@
 \end{align}
-From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be written
-\be
+From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be
+written
+
+\begin{equation}
  f\equiv r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
  \label{eq:massFlux}
-\ee
-where $x \equiv r/\rs$ and we have used the fact that the mass source term $q = q_o x^{-\delta}$ is proportional to the stellar density.  Likewise, the gravitational potential $\Phi$ is given by
+ \end{equation}
+
+where $x \equiv r/\rs$ and we have used the fact that the mass
+ source term $q = q_o x^{-\delta}$ is proportional to the stellar
+ density.  Likewise, the gravitational potential $\Phi$ is given by
 \begin{align}
@@
 \end{align}
-where by truncating the integral at $r = \rb$ we are neglecting the contribution to the potential of the stars outside of the break radius.
+where by truncating the integral at $r = \rb$ we are neglecting the
+contribution to the potential of the stars outside of the break
+radius.
 
-Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with the result of equation \eqref{eq:Phi}, we obtain 
+Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with
+the result of equation \eqref{eq:Phi}, we obtain
 \begin{align}
@@
   &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
-  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
+  \frac{1-2\delta}{2(\delta+1)}
+  \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
   \nonumber\\
@@
 \begin{multline}
-  \mathcal{B} =\frac{G \Mbh}{\rs} 
-\biggl[
-  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}
+  \mathcal{B} =\frac{G \Mbh}{\rs} \biggl[ \frac{3}{2} \zeta^2
+  w^{\frac{1}{3 -\delta}}
   -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
-  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2 -\delta} 
-  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
-\biggr],
+  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2
+    -\delta} -w
+  \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)}
+  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1} \biggr],
 \label{eq:enthAnal}
 \end{multline}
-where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv (\rs/\rsoi)^{3\delta}$, and
-$\delta$ is the power law slope of the stellar density profile inside
-of the break radius, $\rb$.
+where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv
+(\rs/\rsoi)^{3\delta}$, and $\delta$ is the power law slope of the
+stellar density profile inside of the break radius, $\rb$.
 
-When the rate of external heating is high, we have $\mathcal{B} > 0$ at all radii, requiring an outflow.
-As heating ($\zeta$) is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ first becomes negative.
-If $\zeta<\zeta_c$, then there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$, above which we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive kinetic energy at infinity.
-The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
-Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
-Fig.~\ref{fig:zetaCrit}).
-Likewise $(r_{\rm s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right numbers here}.
-For values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches the break radius as shown in the
-bottom panel of Fig.~\ref{fig:zetaCrit}.
+When the rate of external heating is high, we have $\mathcal{B} > 0$
+at all radii, requiring an outflow.  As heating ($\zeta$) is
+decreased, there exists a critical value of $\zeta = \zeta_{c}$ below
+which $\mathcal{B}$ first becomes negative.  If $\zeta<\zeta_c$, then
+there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$,
+above which we have $\mathcal{B} > 0$ at the break radius, allowing an
+outflow with positive kinetic energy at infinity.  The value of
+$\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a
+greater heating rate is required to unbind gas from a deeper stellar
+potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find
+$\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the
+top panel of Fig.~\ref{fig:zetaCrit}). Likewise $(r_{\rm
+  s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$,
+approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right
+  numbers here}.  For values of $\zeta<\zeta_c$, the stagnation radius
+rapidly approaches the break radius as shown in the bottom panel of
+Fig.~\ref{fig:zetaCrit}.
 
@@
 \caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
-  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$. If $\zeta<\zeta_c$ outflows are
-  only possible if the ratio of the stagnation radius to the influence
-  radius exceeds a minimum value. Plotted as a function of the ratio
-  of the break radius to the influence radius ($\rb/\rsoi$) {\emph Bottom
-    Panel:} Mininmum value for ratio of the stagnation radius to the
-  influence radius, $\rs/\rsoi$ for core galaxies ($\Gamma=0.1$)
-  derived by requiring enthalpy of the gas to remain positive out to
-  the break radius $\rb$. This is calculated numerically from
-  equation~\eqref{eq:enthAnal}. The x-intercept of each curve
-  corresponds to the critical $\zeta_c$}
+  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ for core ($\Gamma=0.1$)
+  galaxies. If $\zeta<\zeta_c$ outflows are only possible if the ratio
+  of the stagnation radius to the influence radius exceeds a minimum
+  value. Plotted as a function of the ratio of the break radius to the
+  influence radius ($\rb/\rsoi$) {\emph Bottom Panel:} Mininmum value
+  for ratio of the stagnation radius to the break radius, $\rs/\rb$
+  for core galaxies ($\Gamma=0.1$) derived by requiring the Bernoulli
+  parameter of the gas to remain positive out to the break radius
+  $\rb$. This is calculated numerically from
+  equation~\eqref{eq:enthAnal}.}
 \end{figure}

### 2015-04-04 be.tex
appendix B3

--- 2015-04-03 be.tex
@@
 \end{align}
-where $U_o=4 \pi G \rhostar(\rs) \rs^2$.  We may rewrite this as
-
+where $U_o=4 \pi G \rhostar|_{\rs} \rs^2$.  This can be rewritten as
 \begin{multline}
@@
 
-When the rate of external heating is high, we have $\mathcal{B} > 0$ at all radii, requiring an outflow.
-As heating ($\zeta$) is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ first becomes negative.
+When the rate of external heating is high ($\zeta \gg 1$), we have $\mathcal{B} > 0$ at all radii, requiring an outflow.
+As $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative near the stagnation radius.
 If $\zeta<\zeta_c$, then there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$, above which we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive kinetic energy at infinity.
-The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
+
+The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
 Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of

### 2015-04-04 be.tex
appendix B4

--- 2015-04-03 be.tex
@@
 
-When the rate of external heating is high, we have $\mathcal{B} > 0$
-at all radii, requiring an outflow.  As heating ($\zeta$) is
-decreased, there exists a critical value of $\zeta = \zeta_{c}$ below
-which $\mathcal{B}$ first becomes negative.  If $\zeta<\zeta_c$, then
-there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$,
-above which we have $\mathcal{B} > 0$ at the break radius, allowing an
-outflow with positive kinetic energy at infinity.  The value of
-$\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a
-greater heating rate is required to unbind gas from a deeper stellar
-potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find
-$\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the
-top panel of Fig.~\ref{fig:zetaCrit}). Likewise $(r_{\rm
-  s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$,
-approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right
-  numbers here}.  For values of $\zeta<\zeta_c$, the stagnation radius
-rapidly approaches the break radius as shown in the bottom panel of
-Fig.~\ref{fig:zetaCrit}.
+Analysis of equation (\ref{eq:enthAnal}) results in the following.
+When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow.
+As $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative, first near the stagnation radius and then at larger radii as $\zeta$ is reduced further.
+If $\zeta<\zeta_c$, then we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.
+
+The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
+Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
+Fig.~\ref{fig:zetaCrit} for the case of core galaxies). Likewise $(r_{\rm s,min}/r_{b})$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.86\zeta_c$, as shown in the
+bottom panel of Fig.~\ref{fig:zetaCrit}.
+In practice, as $\zeta \rightarrow 0.86\zeta_c$ we find that the stagnation radius moves its value predicted by equations (\ref{eq:stag_analytic}), (\ref{eq:densSlope}) to the break radius.
 

### 2015-04-04 ms.tex
abstract

@@
   We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in the nuclei of nominally quiescent galaxies for a range of
-  central black hole mass $M_{\bullet}$, parameterized gas heating
-  rate, and observationally-motivated stellar density profiles.  Mass
+  hot gas in the nominally quiescent galactic nuclei for a range of
+  central black hole masses $M_{\bullet}$, parameterized gas heating
+  rates, and observationally-motivated stellar density profiles.  Mass
   is supplied to the circumnuclear medium by stellar winds, while gas
   is heated primarily by stellar winds, supernovae, and black hole
-  feedback.  Analytic estimates are provided for the stagnation radius
+  feedback.  Analytic estimates are derived for the stagnation radius
   (where the radial velocity of the gas passes through zero) and the
-  black hole mass accretion rate, $\dot{M}$, as a function of black
-  hole mass and the gas heating efficiency, the latter of which is
+  black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and the gas heating efficiency, the latter of which is
   related to the star-formation history.  We assess the conditions
   under which radiative instabilities develop, separately in the case
-  of a single burst of star formation and in the case of the average
-  star formation history of galaxies hosting a given black hole
-  mass. The measured nuclear X-ray luminosities, $L_{X}$, of a sample
-  of quiescent black holes are combined with our results for $\dot{M}$
-  to conclude that early-type quiescent black holes in the local
-  universe are consistent with accreting in a locally thermally-stable
-  state (on scales of the sphere of influence), possibly between
-  cycles of thermal instability on larger galactic scales.  The
-  maximum accretion rate of a thermally-stable flow is too low to
-  explain the short growth times of low mass black holes in the local
+  of a single burst of star formation and for the average
+  star formation history, as predicted by cosmological simulations, of galaxies hosting black holes of a given mass.
+The measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent galactic nuclei and low luminosity AGN are combined with our results for $\dot{M}(M_{\bullet})$ to address whether the nuclei of most nearby galaxies are consistent with accreting in a steady-state, thermally-stable manner.
+The maximum accretion rate of a thermally-stable flow is too low to explain the short average growth times of low mass black holes in the local
   universe.  The latter must instead result from gas being fed in from
@@
   occupation fraction of SMBHs in low mass galaxies using the mean
-  $L_{\rm X}-M_{\bullet}$ correlation, as well as to the diversity of
-  circumnuclear media densities encountered by relativistic jets from
+  $L_{\rm X}-M_{\bullet}$ correlation, as well as applications to other topics, such as the predicted diversity of the
+  circumnuclear media encountered by relativistic outflows from
   tidal disruption events.

### 2015-04-04 ms.tex
intro

@@
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the detection threshold.  This assumption is questionable if
+the instrument detection threshold, an assumption which is questionable if
 different physical processes control the accretion rates onto the
@@
 \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
-This transient event was powered by an impulsive relativistic jet,
+This event was powered by an impulsive relativistic jet,
 which produced synchrotron radio emission as the jet material was
@@
 Detailed modeling of J1644+57 showed that the CNM density was much
-lower than that measured surrounding Sgr A$^{\star}$
+lower than that measured surrounding Sgr A$^{\star}$ on a similar radial scale
 (\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a TDE jet
 injected into a denser CNM would be decelerated more rapidly,
-producing substantially different radio emission than in J1644+57.
+producing potentially much different radio emission than in J1644+57.
 Variations in the properties of the CNM could help explain why most
@@
 low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative
-efficiency for thin disk accretion.  Much
-evidence now suggest that low-luminosity AGN result from accretion
+efficiency for thin disk accretion.  Several lines of evidence now suggest that low-luminosity AGN result from accretion
 proceeding in a radiatively inefficient mode
@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaches the SMBH
-(e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaches the SMBH due to disk outflows (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
 
@@
 systematically explore the relevant parameter space and to derive
-simple analytic expressions that prove useful in exploring whether
+simple analytic expressions that prove useful to determine whether
 cooling instabilities manifest across the expected range of galaxy
@@
 smaller radial scales comparable to the sphere of influence.  We are
-thus motivated to explore whether steady flow is achieved within the
-nucleus under any circumstances, or whether the gas content is always
+thus motivated to explore whether steady flow is typically expected within the
+nucleus under, or whether in most galaxies the nuclear gas content is always
 building towards instability.
@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ can in many cases resides near the nominal Bondi
+show that $\rs$ will in many cases reside near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation
-radius may not exist at all, i.e. the entire ISM of the galaxy is flowing
+radius may move to much larger radii or not exist at all, in which case the entire ISM of the galaxy is flowing
 towards the SMBH.  A goal of this work is to assess under what

### 2015-04-04 ms.tex
up to 3.4

@@
 This paper is organized as followed.  In $\S\ref{sec:model}$ we
-describe our model, including the sample of galaxies used in our
+describe our model, including the sample of galaxy properties used in our
 analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
@@
 \hline
-$M_{\bullet}$ & Black hole mass \\
-$\tilde{v}_{w}$ & Total heating parameter, including minimum heating
+$M_{\bullet}$ & black hole mass \\
+$\tilde{v}_{w}$ & total heating parameter, including minimum heating
 rate from stellar and black hole velocity dispersion \\
-$v_{w}$ & Total heating parameter, excluding heating rate from
+$v_{w}$ & total heating parameter, excluding heating rate from
 velocity dispersion \\
-$\sigma_0$ & Stellar velocity dispersion--assumed to be radially constant.\\
-$\zeta$ & $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ (eq.~[\ref{eq:zetacrit}])\\
-$r_{s}$ & Stagnation radius (where gas radial velocity goes to zero) \\
+$\sigma_0$ & stellar velocity dispersion--assumed to be radially constant.\\
+$\zeta$ & heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
+$r_{s}$ & stagnation radius (where gas radial velocity goes to zero) \\
 $r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
@@
 $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
-$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
+$\dot{M}_{\rm C}$ & `equilibrium' accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
 $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
@@
 \end{tabular}
-\begin{tablenotes}
-\item{$^{(a)}FILL IN$}
-\end{tablenotes}
+%\begin{tablenotes}
+%\end{tablenotes}
 \end{minipage}
@@
 \be
-\zeta\equiv \frac{\sqrt{v_w^2+\sigma_0^2}}{\sigma_0} < \zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
+\zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} < \zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
 \label{eq:zetacrit}
@@
 results in at most an order unity correction for plausible, causal values of
-the saturation parameter $\phi < 0.1$.  Numerical experiments which include conductive heating confirm this
+the saturation parameter $\phi < 0.1$.  Our numerical experiments which include conductive heating confirm this
 ($\S\ref{sec:numerical}$).
@@
 
-Radiative cooling can, however, be stabilized if it is overwhelmed by
-other sources of cooling, namely the term $\propto -q c_{s}^{2}
+Cooling instability can, however, be prevented if destabilizing radiation is overwhelmed by
+other sources of cooling, namely the stabilizing term $\propto -q c_{s}^{2}
 \propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
-Neglecting radiative cooling, this term is balanced at the stagnation
+Neglecting radiative cooling to first order, this term is balanced at the stagnation
 radius by the wind heating term, $\dot{q}_{\rm heat} = q
@@
 $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which follows from
-equation (\ref{eq:rsoi}) and the results of \citet{LauerFaber+:2007a}.
+equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$ correlation derived from the results of \citet{LauerFaber+:2007a}.
 

### 2015-04-04 ms.tex
section 4

@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
   {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
@@
 
-We include a few solutions with cooling (marked with a $\dagger$) and
-conductivity (marked with a $\ddagger$) Table \ref{table:models} to
-assess whether it is valid to neglect these effects. As expected
-solutions for which $\dot{q}_{\rm heat}/\dot{q}_{\rm rad}\gg 1$ are
-unaffected when radiative cooling is included (see the solution with
-$\Mbh=10^{8} \Msun, v_w=600 {\rm km/s and} \gamma=0.8$. However, we
-find that as we decrease the heating further, to cooling begins to
-become more important (see $\Mbh=10^{8} \Msun, v_w=450 {\rm km/s and}
-\gamma=0.8$). Overall, we find radiative cooling has negligible effect
-on cusp solutions $v_w\geq 600 km/s$ in and core solutions with
-$v_w=1200$ km/s {\bf AG for the purposes of description it may be
-  simpler to just rerun all of our models with radiative cooling}.
-
-We re-ran all cusps ($\Gamma=0.8$) with $v_w=300$ km/s and
-all cores ($\Gamma=0.1$) with $v_w=600 $ km/s with radiative cooling
-for three different values of the mass input parameter $\eta$--0.02,
-0.2, and 0.6.  Note that $\eta=0.02$ is the minimum expected physical
-mass input parameter. Solutions which were unstable for all values of
-$\eta$ are marked with a $\mathbf{TI}$ {\bf solution that were
-  unstable for only some choices of eta}.
-
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
@@
 $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.
+In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all cores with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter spanning the physically expected range $\eta = 0.02,
+0.2, 0.6$.  Solutions which are found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.
+
 Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e.

### 2015-04-04 ms.tex
section 4 refixing

@@
 $r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
-$\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors
+$\zeta = \sqrt{1+(v_w/\sigma_0)^{2}}$, with different colors
 showing different values of $v_{w}$.  Cusp and core galaxies are
@@
 the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
-occurs approximately when $\zeta =
-\sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix
-\ref{app:be}), and hence occurs at a higher value of $\zeta$ in the
-case of core galaxies ($\Gamma = 0.8$) with large break radii.
-
-As $\zeta$ approached $\zeta_c$, the results the location of the
-stagnation radius will depend on the location of the break radius
-$\rb$.  This explains the behavior of the two core galaxies, shown as
+occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
+\ref{app:be} is shown to coincide with the critical heating below which the Bernoulli parameter of the gas decreases below unity near the stagnation radius.
+This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.
+This dependence explains the behavior of the two core galaxies, shown as
 orange triangles vertically aligned at the same value of
@@
 different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
-bottom). {\bf AG still needs work}
+bottom). {\bf AG still needs work.  BDM: what work? this looks sufficient to me}
 

### 2015-04-04 ms.tex
section 4 refixing

@@
   {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
-  {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
+  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
   soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
-\ref{app:be} is shown to coincide with the critical heating below which the Bernoulli parameter of the gas decreases below unity near the stagnation radius.
+\ref{app:be} is shown to coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius.
 This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.
@@
 $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.
-In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all cores with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter spanning the physically expected range $\eta = 0.02,
-0.2, 0.6$.  Solutions which are found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.
+In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02,
+0.2, 0.6$, spanning the physical range.  Solutions found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.
 

### 2015-04-04 ms.tex
section 4 refixing

@@
 
-Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e.
+We find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e.
 to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
@@
 \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
-is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  We show
-in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
 formation representative of the average star formation history of loss
@@
 can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
+
 Stellar winds thus contribute a potentially important source of both
 energy and mass for the CNM.
-An additional uncertainty in the stellar wind heating rate results from the uncertain thermalization efficiency of massive stellar winds.
-We assume this efficiency to be unity, an optimistic assumption which is offset by our neglect of energy input from core collapse supernovae, which contribute an energy comparable to that from massive stellar winds.
+An additional uncertainty results from the thermalization efficiency of massive stellar winds.
+We assume this efficiency to be unity, an optimistic assumption which is partially offset by our neglect of energy input from core collapse supernovae, which contribute a heating rate comparable to that from massive stellar winds.
 
@@
 equations (\ref{eq:stag_simple}), (\ref{eq:mdot_analytic}),
-(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
+(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate from equation
 (\ref{eq:vw_eff}) that the effective heating rate at the stagnation radius is given by
@@
 r^{-0.75}$ for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp
-($\Gamma = 0.1$; $\densSlope \simeq 0.6$) galaxies, respectively.  Our
+($\Gamma = 0.1$; $\densSlope \simeq 0.6$) galaxies, respectively.  Although our
 model's assumption that the heating parameter be radially constant is
-not satisfied, but this variation is sufficiently weak that it should
+not satisfied, this variation is sufficiently weak that it should
 not significantly alter our conclusions.

### 2015-04-04 ms.tex
fixed nicks tscale definition to something more palatable

@@
 with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
-km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate
-corresponding to the state where Compton heating limits the average
-accretion rate is given by substituting equation (\ref{eq:vC2}) into
-equation (\ref{eq:eddr_analytic}):
+km s$^{-1}$ for $\eta \gtrsim 1$.  The accretion rate
+corresponding to a state in which Compton heating self-regulates the accretion flow is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
 \begin{align}
@@
 C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
-&, \text{cusp},
+&, \text{cusp}.
   \end{cases}
@@
 \end{align}
-If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
-depends on the Eddington ratio as predicted by some models for
+If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for
 radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
@@
 \end{align}
+We note that accretion is unlikely to be steady in cases where AGN heating dominates, due to the inherent delay between black hole feedback and the structure of the accretion flow on larger scales.  
 %{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
@@
 However, if this energy is instead deposited over much larger physical scales comparable to the size of the galaxy, i.e.
-$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 1$.
-
-Using the results of \citet{Bromberg+11}, the time required for a jet of luminosity $L_{\rm
+$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 0.1$.
+
+The time required for a jet of luminosity $L_{\rm
   j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
-AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated to be
+AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated from \citet{Bromberg+11} to be 
 \begin{eqnarray}
-t_{\rm jet} &\sim& 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
+t_{\rm jet} \sim 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
 \end{eqnarray}
@@
 [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
-{\bf BDM: do we even include Ia heating?}
-
-We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
+
+We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated excluding Ia heating) exceeds the Ia radius $r_{\rm Ia}$ exterior to which the interval between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
 Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
@@
 suppressed by a factor $\iota$ from its average $z = 0$ value, for a
-characteristic timescale $t_{\rm scale}$ (for details, see Appendix
+characteristic timescale $\delta t_{\star}$ (for details, see Appendix
 \ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see

### 2015-04-04 windheat.tex
references.
fixed nicks tscale definition to something more palatable

@@
 \eta = \dot{\bar{m}}(t) \th
-\label{eq:vwImp}
+\label{eq:etaImp}
 \end{align}
- Figur~\ref{fig:vwImp} shows the values of $\bar{v}_w(t)$ and $\eta(t)$ as a function of stellar age, $\tau_{\star}$.
+ Figure~\ref{fig:vwImp} shows the values of $\bar{v}_w(t)$ and $\eta(t)$ as a function of stellar age, $\tau_{\star}$.
 
@@
     $\mathcal{S}(t)$.  The purple curve shows a recent drop in the
-    star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue
-    and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm
+    star formation rate, i.e. $\delta t_{\star}=10^6~{\rm yr}$.  The blue
+    and red curves show $\delta t_{\star}=10^7~{\rm yr}$ and $t_{\rm
       scale}=10^8~{\rm yr}$, respectively; longer scale times look
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/t_{\rm scale}) + \iota \right).
+\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/\delta t_{\star}) + \iota \right).
 \end{equation}
 This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.
-In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.
+In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $\delta t_{\star}$ into the past.
 As we can see in Fig.
-\ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
+\ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $\delta t_{\star} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
 

### 2015-04-05 ms.tex
fixed nicks tscale definition to something more palatable
fixed abstract

@@
   We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in the nominally quiescent galactic nuclei for a range of
+  hot gas in ``quiescent" galactic nuclei for a range of
   central black hole masses $M_{\bullet}$, parameterized gas heating
@@
   (where the radial velocity of the gas passes through zero) and the
-  black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and the gas heating efficiency, the latter of which is
-  related to the star-formation history.  We assess the conditions
-  under which radiative instabilities develop, separately in the case
-  of a single burst of star formation and for the average
-  star formation history, as predicted by cosmological simulations, of galaxies hosting black holes of a given mass.
-The measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent galactic nuclei and low luminosity AGN are combined with our results for $\dot{M}(M_{\bullet})$ to address whether the nuclei of most nearby galaxies are consistent with accreting in a steady-state, thermally-stable manner.
-The maximum accretion rate of a thermally-stable flow is too low to explain the short average growth times of low mass black holes in the local
-  universe.  The latter must instead result from gas being fed in from
-  large radii, either due to galaxy mergers associated with
-  hierarchical growth or thermal instabilities on larger, galactic
-  scales.  Our results have implications for attempts to constrain the
-  occupation fraction of SMBHs in low mass galaxies using the mean
-  $L_{\rm X}-M_{\bullet}$ correlation, as well as applications to other topics, such as the predicted diversity of the
-  circumnuclear media encountered by relativistic outflows from
+  black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and the gas heating efficiency, the latter being related to the star-formation history.
+We assess the conditions under which radiative instabilities develop, separately in the case
+  of a single burst of star formation and for the average star formation history predicted by cosmological simulations for galaxies hosting black holes of a given mass.
+By combining a sample of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent galactic nuclei with our results for $\dot{M}(M_{\bullet})$ we show that most nuclei are consistent with accreting in a steady-state, thermally-stable manner.
+However, thermally-stable accretion cannot explain the short average growth times of low mass black holes in the local universe, which must instead result from gas being fed in from
+  large radii, due either to galaxy mergers or thermal instabilities acting on larger, galactic scales.
+Our results have implications for attempts to constrain the occupation fraction of SMBHs in low mass galaxies using the mean
+  $L_{\rm X}-M_{\bullet}$ correlation, as well as the predicted diversity of the
+  circumnuclear densities encountered by relativistic outflows from
   tidal disruption events.
@@
 For low-mass black holes, stellar winds are the most important source of heating on
-timescales of less than a few tens of millions of years.  Compton
+timescales of $\tau_{\star} \lesssim $ few $10^{7}$ years.  Compton
 heating comes to dominate at later times due to the higher accretion

### 2015-04-05 ms.tex
fixed abstract2

@@
 characteristic timescale $\delta t_{\star}$ (for details, see Appendix
-\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
+\ref{app:windheat}).  For $\delta t_{\star} \lesssim 10^{7}$ yr, we see
 that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
@@
 history over longer timescales can suppress heating more
-significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
+significantly.  When $\delta t_{\star} \gtrsim 10^8~{\rm yr}$, $v_{\rm
   w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm
@@
 of average cosmic star formation histories is appropriate provided
-local variations are either on short timescales ($t_{\rm scale}
+local variations are either on short timescales ($\delta t_{\star}
 \lesssim 10^7~{\rm yr}$), or limited in magnitude ($\iota \gtrsim

### 2015-04-05 ms.tex
fixed abstract2

@@
   thermally stable flows across almost all black hole masses}.
-One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion ($\zeta \sim \zeta_c$) and thermal stability for the average star formation history is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
+One important exception occurs for the highest mass black holes, for which the total effective wind velocity is comparable to the stellar velocity dispersion ($\zeta \sim \zeta_c$) and thermal stability for the average star formation history is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
 
@@
 $\dot{M}_{\rm TI}$ (yellow lines), except at the highest
-black hole masses $\sim 10^{9}M_{\odot}$.  For these highest mass
-black holes, the maximum accretion rate as set by the SN Ia
-radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
-accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
+black hole masses $\sim 10^{9}M_{\odot}$.
+
+For low mass black holes, blow out from near the SN Ia radius caps the SMBH accretion rate at a value $\dot{M}_{\rm Ia} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines; eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent otherwise thermally-unstable flow at smaller radii (see discussion following eq.~[\ref{eq:eddr_Ia}]).
+For higher mass black holes the stagnation resides close to the Ia radius, but the energy released by a single Ia is insufficient to unbind gas from the stellar bulge (although Ia heating contributes to the steady heating rate).
+
+%For these highest mass
+%black holes, the maximum accretion rate as set by the SN Ia
+%radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
+%accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
 For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
-also prevent the development of thermally unstable flows,
-i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
-
-Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}, as well as the range of $\dot{M}$ for the low-luminosity AGN NGC3115 from \citealt{ShcherbakovWong+:2014a} (who find a range of accretion rates depending on the assumed model for thermal conductivity, although they do not include saturation of the conductive flux).
-The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for galaxies with the same mass black hole by almost two orders of magnitude.
-This discrepancy can be understood by the fact that star formation in the central parsec of the Galaxy is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
-Such a star formation history is better described as a `burst' of stars, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
+%also prevent the development of thermally unstable flows,
+%i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
+
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}, as well as the range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through detailed modeling by \citealt{ShcherbakovWong+:2014a} (who find a range of accretion rates depending on the assumed model for thermal conductivity, although they do not include saturation of the conductive flux as considered in this work).
+The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for the same $M_{\bullet}$ by almost two orders of magnitude.
+This discrepancy can be understood by the fact that star formation in the central parsec of the Milky Way is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
+Such a star formation history is better described by our `star burst' scenario, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
 
@@
 
-The (unresolved) core X-ray luminosities of galactic nuclei provide a
+The unresolved core X-ray luminosities of nearby galactic nuclei provide a
 powerful diagnostic of the SMBH accretion rates and how they vary with

### 2015-04-05 ms.tex
salvaged appendix A
blah

@@
 
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel).
-The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).
-The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.
-SN Ia heating depends also on a convolution of the DTD (eq.
-[\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.
-
-We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated excluding Ia heating) exceeds the Ia radius $r_{\rm Ia}$ exterior to which the interval between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).
-Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.
-Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).
-
-For low-mass black holes, stellar winds are the most important source of heating on
-timescales of $\tau_{\star} \lesssim $ few $10^{7}$ years.  Compton
-heating comes to dominate at later times due to the higher accretion
-rates that accompany the overall decrease in the heating rate, coupled
-with the persistently high mass loss rates and gas densities associated with a relatively young
-stellar population.  Compton heating dominates at all epochs for
-higher mass black holes, with stellar winds and Ia SN competing for
-the most significant non-AGN heating source.  As the total heating
-rate declines with time, after some point the flow becomes thermally
-unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm
-  rad}|)_{r_{s}} \lesssim 10$ (eq.~[\ref{eq:cooling3}]) {\bf BDM: correct?}, as shown by
-dashed lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability threshold is
-calculated neglecting Compton heating because SMBH feedback may not be
-capable of truly stabilizing the flow given its inability to respond
-instantaneously to local changes in the properties of the gas.
+Figure~\ref{fig:vwSourcesImp} shows the contributions of various
+heating sources as a function of time $\tau_{\star}$ after a burst of
+star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top
+panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass
+input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$
+and $\eta(\tau_{\star})$, are calculated as described in
+Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from
+SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are
+calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC}
+respectively, also making use of $\eta(\tau_{\star})$ from stellar
+winds.  SN Ia heating depends also on a convolution of the DTD
+(eq. [\ref{eq:DTD}]) and the star formation history, which reduces to
+the DTD itself for a single star burst.
+
+We crudely account for the expected suppression of SN Ia heating
+resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$
+when the stagnation radius (calculated excluding Ia heating) exceeds
+the Ia radius $r_{\rm Ia}$ exterior to which the interval between
+subsequent supernovae exceeds the local dynamical time
+(eq.~[\ref{eq:rIa}]) {\bf AG have not yet done this in the impulsive limit}.  Finally, note that $v_{\rm w}^{\rm C}$ and
+depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
+to simultaneously solve a series of implicit equations to determine
+each heating rate.  Heating from MSPs is found to be negligibly small
+for fiducial parameters and hence is not shown, while kinetic feedback
+is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).
+
+For low-mass black holes, stellar winds are the most important source
+of heating on timescales of $\tau_{\star} \lesssim $ few $10^{7}$
+years.  Compton heating comes to dominate at later times due to the
+higher accretion rates that accompany the overall decrease in the
+heating rate, coupled with the persistently high mass loss rates and
+gas densities associated with a relatively young stellar population.
+Compton heating dominates at all epochs for higher mass black holes,
+with stellar winds and Ia SN competing for the most significant
+non-AGN heating source.  As the total heating rate declines with time,
+after some point the flow becomes thermally unstable according to the
+criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim
+10$ (eq.~[\ref{eq:cooling3}]) {\bf BDM: correct?}, as shown by dashed
+lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability threshold
+is calculated neglecting Compton heating because SMBH feedback may not
+be capable of truly stabilizing the flow given its inability to
+respond instantaneously to local changes in the properties of the gas.
 Thermally unstable flow is seen to be the norm in the single starburst
@@
 
-Similar cyclic AGN activity could occur on the smaller radial scale of the sphere of influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuadra+15}).
-In this case the large scatter in the X-ray luminosities shown in Fig \ref{fig:miller} could result from
-the wide range of inflow rates experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts.
-Due to their deeper potential wells, we find that core galaxies are more likely to possess higher accretion
-rates and potentially be thermally unstable for a fixed wind heating rate than cusp galaxies.
-This could help explain why core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99,   Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture.
-({\bf AG: This picture may be dubious...Review
+Similar cyclic AGN activity could occur on the smaller radial scale of
+the sphere of influence (e.g.~\citealt{Yuan&Li11},
+\citealt{Cuadra+15}).  In this case the large scatter in the X-ray
+luminosities shown in Fig \ref{fig:miller} could result from the wide
+range of inflow rates experienced over the course of a cyclic episode
+between instabilities and periodic nuclear outbursts.  Due to their
+deeper potential wells {\bf AG: Cores don't necessarily have deeper
+  potential wells overall}, we find that core
+galaxies are more likely to possess higher accretion rates and
+potentially be thermally unstable for a fixed wind heating rate than
+cusp galaxies.  This could help explain why core galaxies show a wide
+range of nuclear radio and X-ray luminosities (suggesting cyclic
+accretion episodes), while cusp galaxies are confined below a
+threshold (e.g., \citealt{Bender+89, Pellegrini99,
+  Capetti&Balmaverde05}), consistent with thermally-stable,
+steady-state picture. ({\bf AG: This picture may be dubious...Review
   the literature but I think that the higher upper bound for cores is
-  just due to a mass selection effect.  BDM: The ghost of Balmaverde disagrees.})
+  just due to a mass selection effect.  BDM: The ghost of Balmaverde
+  disagrees.})
 

### 2015-04-05 be.tex
salvaged appendix B

@@
 Here we derive an expression for the Bernoulli parameter, \be
-\mathcal{B} \equiv \ke +\gammaf \frac{p}{\rho}+\Phi, \ee assuming a
-stellar density profile $\rhostar\sim r^{-1-\Gamma}=r^{-\delta}$
-characteristic of that inside the break radius $\rb$.
-
-Basic manipulation of the equations of hydrodynamics
-(eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following
-relationship between the Bernoulli parameter and the net heating rate
-$\propto q \vw^{2}$,
+\mathcal{B} \equiv \ke +\gammaf \frac{p}{\rho}+\Phi, \ee
+as a function of radius $x \equiv r/\rs$.  Straightforward manipulation of the hydrodynamic equations (eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following relationship: 
 \begin{align}
-\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \mathcal{B} \right) = q \kew + q \Phi = \frac{3}{1+\delta}\frac{G
-  \Mbh}{r}+\sigma_0^2+v_w^2 + q \Phi,
+\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \mathcal{B} \right) = q \kew + q \Phi,
 \label{eq:enCons}
 \end{align}
-where the first and second terms on the right hand side correspond,
-respectively, to the black hole and stellar contributions to the
-velocity dispersion.
-
-Integrating both sides of equation~\eqref{eq:enCons} from the
-stagnation radius $r = \rs$ outwards,
+which upon integration from the stagnation radius $r = \rs$ outwards,
 \begin{align}
-  r^2 \rho v \left(\ke+\Phi+\gammaf \frac{p}{\rho} \right)= \int_{\rs}^{r}
-    r^2 \left(q \kew + q\Phi\right) dr
+  r^2 \rho v(\mathcal{B} - \mathcal{B}|_{\rs})= \int_{\rs}^{r}
+    r^2 \left(\frac{3}{1+\delta}\frac{G
+  \Mbh}{r}+\sigma_0^2+v_w^2 + q \Phi\right) dr,
     \label{eq:enConsInt}
 \end{align}
-From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be
-written
+where the right hand side makes use of the definition of $\vw^{2}$ (eq.~[\ref{eq:sigmarel}]).
 
+The mass flux follows from mass continuity (eq.~[\ref{eq:drhodt}]) and the condition that $v|_{\rs} = 0$:
 \begin{equation}
- f\equiv r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
+ \drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \Rightarrow r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
  \label{eq:massFlux}
  \end{equation}
-
-where $x \equiv r/\rs$ and we have used the fact that the mass
- source term $q = q_o x^{-\delta}$ is proportional to the stellar
- density.  Likewise, the gravitational potential $\Phi$ is given by
+where the source term obeys $q = q_o x^{-\delta} \propto \rho_{\star} \propto r^{-1-\Gamma}$ and $\delta \equiv -1-\Gamma$.  The gravitational potential $\Phi$ is given by
 \begin{align}
@@
 \end{align}
-where by truncating the integral at $r = \rb$ we are neglecting the
-contribution to the potential of the stars outside of the break
-radius.
+where by truncating the integral at $r = \rb$ we neglect contributions to the potential from stars outside of the break radius, as is generally a good assumption.
 
-Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with
-the result of equation \eqref{eq:Phi}, we obtain
+Tedious but straightforward manipulation of equations~\eqref{eq:enConsInt}, \eqref{eq:massFlux}, \eqref{eq:Phi}, results in the following:
 \begin{align}
@@
 \end{multline}
-where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv
-(\rs/\rsoi)^{3\delta}$, and $\delta$ is the power law slope of the
-stellar density profile inside of the break radius, $\rb$.
+where $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ and $w\equiv
+(\rs/\rsoi)^{3\delta}$.
 
-Analysis of equation (\ref{eq:enthAnal}) results in the following.
-When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow.
-As $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative, first near the stagnation radius and then at larger radii as $\zeta$ is reduced further.
-If $\zeta<\zeta_c$, then we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.
+Analysis of equation (\ref{eq:enthAnal}) results in the following interpretation of the behavior of the Bernoulli integral as a function of the heating rate.
+When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow with positive kinetic energy at infinity.
+However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative; this occurs first near the stagnation radius and then the region where $\mathcal{B} < 0$ grows to larger radii as $\zeta$ is reduced further.
+If $\zeta$ is just less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.
 
-The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
-Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
-Fig.~\ref{fig:zetaCrit} for the case of core galaxies). Likewise $(r_{\rm s,min}/r_{b})$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.86\zeta_c$, as shown in the
-bottom panel of Fig.~\ref{fig:zetaCrit}.
-In practice, as $\zeta \rightarrow 0.86\zeta_c$ we find that the stagnation radius moves its value predicted by equations (\ref{eq:stag_analytic}), (\ref{eq:densSlope}) to the break radius.
+The critical heating value $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
+Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core galaxies).
+Likewise the minimum $r_{\rm s,min}/r_{b}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.86\zeta_c$, as shown in the bottom panel of Fig.~\ref{fig:zetaCrit}.
+As $\zeta \rightarrow 0.86\zeta_c$ our numerical simulations show that that the stagnation radius diverges from its value predicted by equations (\ref{eq:stag_analytic}) and (\ref{eq:densSlope}) and moves out to the break radius.
 

### 2015-04-05 ms.tex
salvaged appendix B
intro again

--- 2015-04-05 ms.tex
@@
 Understanding why most SMBHs appear to be inactive requires
-characterizing their gaseous environments.  Gas near the sphere of
-influence of the SMBH, hereafter the `circumnuclear medium' (CNM),
+characterizing their gaseous environments.  Gas near the SMBH sphere of
+influence, hereafter denoted the `circumnuclear medium' (CNM),
 controls the mass accretion rate, $\dot{M}$.  The accretion rate in
-turn sets the luminosity of the black hole and the feedback of this
-energy and momentum output on larger physical scales.
-The presence of dense gas in the nuclear region may lead to runaway
-cooling, resulting in bursty episodes of star formation and AGN
+turn determines the SMBH luminosity and the feedback of its energy and momentum output on larger scales.
+The presence of dense gas in the nucleus may lead to runaway cooling, resulting in bursty episodes of star formation and AGN
 activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
@@
 Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
-properties of the galactic nucleus informs key questions related to
+properties of the nucleus informs key questions related to
 the co-evolution of SMBHs and their host galaxies with cosmic time
-(e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  SMBH growth
-in the low redshift universe is dominated by low mass black holes,
+(e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  In the low redshift universe, SMBH growth
+is dominated by low mass black holes,
 $M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a
-fact which is often attributed to the general trend of `cosmic
+fact often attributed to the trend of `cosmic
 down-sizing' resulting from hierarchical structure growth (e.g,
-\citealt{Gallo+08}).  However, the physical processes involved in
-growing low mass blacks may be distinct from those operating at higher
-SMBH masses and accretion rates in quasars.  A key question is
-whether SMBHs grow primarily by accreting gas fed in directly from
+\citealt{Gallo+08}).
+However, the physical processes by which low mass black holes accrete could in principle be distinct from those operating at higher SMBH masses and accretion rates in high redshift quasars.
+One key question is
+whether SMBHs grow primarily by the accretion of gas fed in directly from
 galactic or extra-galactic scales, or whether significant growth
-results also from internal, secular processes such as local stellar
-mass loss in the nuclear region.
+can result also from local stellar mass loss in the nuclear region.
 
 A better understanding of what mechanisms regulate accretion onto
-quiescent SMBHs would have implications for a variety of observations,
-such as constraints on the occupation fraction of SMBHs in low mass
+quiescent SMBHs would shed new light on a variety of observations,
+such as the occupation fraction of SMBHs in low mass
 galaxies.  \citet{Miller+15} use the average relationship between the
-nuclear X-ray luminosities, $L_{X}$, of a sample of elliptical
-galaxies and their associated SMBH masses to infer tentative evidence for a
-SMBH occupation fraction less than unity in galaxies with stellar
+nuclear X-ray luminosities, $L_{X}$, of a sample of early type
+galaxies and their associated SMBH masses to infer tentative evidence that the
+SMBH occupation fraction becomes less than unity for galaxies with stellar
 masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
@@
 Bondi accretion rate and based on estimates for the mass loss rate of
-evolved stars.  Both methods lead to the conclusion that the available
+evolved stars.  Both methods lead him to conclude that the available
 gas reservoir is more than sufficient to power the observed
@@
 
-Past studies, employing multi-dimensional numerical hydrodynamics and
+Previous studies, employing multi-dimensional numerical hydrodynamics and
 including variety of (parameterized) physical effects, have focused on
 massive elliptical galaxies (e.g.~\citealt{Ciotti&Ostriker07};
-\citealt{Ciotti+10}).  A key finding of these works is the periodic
+\citealt{Ciotti+10}).  These works show the periodic
 development of cooling instabilities on galactic scales, which
@@
 feedback becomes effective to shut off the flow and halt
-SMBH growth.  Here we instead focus on time-independent models,
+SMBH growth.
+
+In this paper we instead focus on time-independent models,
 neglecting radiative cooling.  This approach allows us to
 systematically explore the relevant parameter space and to derive
-simple analytic expressions that prove useful to determine whether
+analytic expressions that prove useful in determining whether
 cooling instabilities manifest across the expected range of galaxy
-properties, or whether other (non-AGN) forms of feedback can result in
-steady accretion.  Even if cooling instabilities develop on galactic
-scales over longer $\sim$ Gyr timescales, a state of
-quasi-steady accretion may exist between these inflow events on
+properties, or whether other (non-AGN) forms of feedback can produce a prolonged state of steady, thermally stable accretion.
+Even if cooling instabilities develop on galactic scales over longer $\sim$ Gyr timescales, a quasi steady-state  may exist between these inflow events on
 smaller radial scales comparable to the sphere of influence.  We are
-thus motivated to explore whether steady flow is typically expected within the
+thus motivated to explore whether such steady flows are generally expected within the
 nucleus under, or whether in most galaxies the nuclear gas content is always
@@
 
-This paper is organized as followed.  In $\S\ref{sec:model}$ we
+This paper is organized as follows.  In $\S\ref{sec:model}$ we
 describe our model, including the sample of galaxy properties used in our
@@
 calculating the steady-state hydrodynamic profile of the CNM
-($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe some
-analytic results, while in $\S\ref{sec:numerical}$ we describe our
+($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our analytic results, which are justified via numerical solutions in $\S\ref{sec:numerical}$ we describe our
 numerical results.  In $\S\ref{sec:discussion}$ we discuss the
-implications of our results, to topics including the nuclear X-ray
-luminosities of quiescent black holes, jetted TDEs, and the growth
-time of SMBHs.  In $\S\ref{sec:conclusions}$ we summarize our
-conclusions.  Table \ref{table:definitions} provides the definitions
+implications of our results for topics which include the nuclear X-ray
+luminosities of quiescent black holes, jetted TDEs, and the growth of SMBHs in the local universe.
+In $\S\ref{sec:conclusions}$ we summarize our conclusions.
+Table \ref{table:definitions} provides the definitions
 of commonly used variables.  Appendices \ref{app:rs} and \ref{app:be}
 provide useful analytic results for the stagnation radius and the
-Bernoulli parameter of the flow, while Appendix
-\ref{app:windheat} describes our method for calculating stellar wind
-heating and mass input in greater detail.
+Bernoulli parameter of the flow, while Appendix \ref{app:windheat} provides the details of our method for calculating stellar wind heating and mass input.
 
@@
     r}+\sigma_0^2},
+\label{eq:sigmarel}
 \ee
@@
   \appendix
-  \section{Analytic expression for the stagnation radius}
+  \section{Derivation of stagnation radius}
   \label{app:rs}
@@
 
-  \section{Analytic expression for Bernoulli parameter of gas}
+  \section{Analytic expression for Bernoulli parameter}
   \label{app:be}

### 2015-04-05 ms.tex
more

@@
 where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
-enclosed mass.  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
+enclosed mass (we neglect dark matter contributions).  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
 

### 2015-04-05 ms.tex
3.4

@@
 by stellar winds and the mean properties of the background flow.  The
-term $\propto -q c_{s}^{2}$ is important because it acts to potentially stabilize the flow to runaway cooling ($\S\ref{sec:instability}$).
+term $\propto -q c_{s}^{2}$ is important because it acts to potentially stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
 
@@
 
-The gas density at the stagnation radius $\rho|_{r_{\rm s}}$ is more
-challenging to estimate accurately.  Using an alternative estimate of
+The gas density at the stagnation radius, $\rho|_{r_{\rm s}}$, is more
+challenging to estimate accurately.  By using an alternative estimate of
 $\dot{M}$ as the gaseous mass within the stagnation radius divided by
@@
 \end{align}
- in conjunction with equations (\ref{eq:mdot_analytic}) and (\ref{eq:stag_simple}), one derives
+ in conjunction with eqs. (\ref{eq:mdot_analytic}) and (\ref{eq:stag_simple}), we find that
 \begin{align}
@@
 
-Our expression for $\dot{M}$ (eq.~[\ref{eq:mdot_analytic}]) is usefully compared to the Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
+It is useful to compare our expression for $\dot{M}$ (eq.~[\ref{eq:mdot_analytic}]) to the standard Bondi rate for accretion onto a point source from an external medium of specified density and temperature (\citealt{Bondi52}):
 \begin{align}
@@
 the loss of pressure can temporarily increase the black hole accretion
-rate.  When coupled to feed-back processes, the latter can lead to
-time-dependent (e.g. limit cycle) behavior
+rate.  When coupled to feed-back processes which result from such enhanced accretion, this can lead to
+time-dependent limit cycle behavior
 (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10};
@@
 
-Cooling instability can, however, be prevented if destabilizing radiation is overwhelmed by
-other sources of cooling, namely the stabilizing term $\propto -q c_{s}^{2}
-\propto -qT$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
+Cooling instability can, however, be prevented if destabilizing radiative cooling ($\dot{q}_{\rm rad} \propto T^{-2.7}$) is overwhelmed by
+other sources of cooling, namely the {\it stabilizing} term $\propto -q c_{s}^{2}
+\propto -T$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
 Neglecting radiative cooling to first order, this term is balanced at the stagnation
-radius by the wind heating term, $\dot{q}_{\rm heat} = q
-\tilde{v}_{w}^{2}/2$.  Thermal stability near the stagnation radius
-can thus be assessed by comparing the ratio of wind heating to
+radius by the external heating term, $\dot{q}_{\rm heat} = q
+\tilde{v}_{w}^{2}/2$.  We assess thermal stability near the stagnation radius by comparing the ratio of external heating to
 radiative cooling $|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:qdot_rad}]),
@@
 2\times 10^{7}$ K as $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
-  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ assuming solar
+  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$, which assumes solar
 metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).
@@
 
-Based on our numerical results and the recent work of \citet{McCourt+12}) we define thermal stability according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
-  cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius {\bf BDM: decide here}.  This condition translates into a
+Based on our numerical results (\ref{sec:numerical}) and the work of \citet{McCourt+12}) we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
+  cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius.  This condition translates into a
 critical minimum heating rate
@@
    200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
-\sigma_0(\zeta_c^{2}-1)^{1/2} \approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)}, 
+\approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
   \end{cases}
@@
 \end{align}
-where the final condition corresponds to the low wind heating limit (eq.~[\ref{eq:zetacrit}]), for which the stagnation radius moves out to the break radius $r_b$, resulting in thermal instability.
+where the final condition corresponds to the low wind heating limit ($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our numerical and analytic results show that the stagnation radius moves out to the break radius $r_b$; the quasi-hydrostatic structure that develops in this case greatly increases the gas density, resulting in thermal instability.
 
@@
   {\rm min}\begin{cases}
-   5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}\\
-3\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.38}\\
-   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}\\
-2.5\times 10^{-4}\eta_{0.02}
+   5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
+3\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.38} &, \text{core}, \zeta < \zeta_c \\
+   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
+2.5\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
   \end{cases}
@@
 (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
-the second line corresponds to the low wind heating limit and is
-calculated for core galaxies using the empirical correlation
+the second line corresponds to the low wind heating limit $\zeta \ll \zeta_c$.  $\zeta_c$ is
+calculated using the empirical correlation for core galaxies
 $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which follows from

### 2015-04-06 ms.tex
4

@@
 calculated using the empirical correlation for core galaxies
-$r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which follows from
-equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$ correlation derived from the results of \citet{LauerFaber+:2007a}.
+$r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{0.2}$ which follows from
+equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$ correlation derived from the results of \citet{LauerFaber+:2007a}.  {\bf BDM: check this}
 
@@
 orange triangles vertically aligned at the same value of
-$\zeta$. These correspond to models with the same black hole mass
-($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
+$\zeta$; the solutions correspond to the same black hole mass
+($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but are calculated assuming
 different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
-bottom). {\bf AG still needs work.  BDM: what work? this looks sufficient to me}
+bottom).
 
@@
 
-In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g.
-$M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.
-However, for solutions in which cooling stability is marginal (e.g.
-$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.
-In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02,
-0.2, 0.6$, spanning the physical range.  Solutions found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.
-
-We find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e.
-to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+In addition to our standard set of solutions which neglect thermal conduction and radiative cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
+For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the flow (e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$).
+However, for solutions which are marginally stable (e.g., $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), the inclusion of radiative acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater amount.
+We ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02, 0.2, 0.6$, spanning the physical range.
+Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}.
+By contrast, changes due to the inclusion of thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, although conduction is seen to offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
 

### 2015-04-06 ms.tex
fixed Ia section 5.2

@@
 
-Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
+Type Ia SNe represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
+If each SN Ia injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SN rate per stellar mass is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
 E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
@@
   \begin{align}
-    r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \sim
-    38 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc}
+    r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma_0}\right)^{1/2} \sim
+    29 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc}
     \label{eq:rIa}
@@
   subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm
-    Ia})^{-1} \sim G/(r\sigma^{2}R_{\rm Ia})$ exceeds the local
-  dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again
+    Ia})^{-1} \sim G/(r\sigma_0^{2}R_{\rm Ia})$ exceeds the local
+  dynamical timescale $t_{\rm dyn} \sim r/\sigma_0$, where we again
   adopt the Ia rate for an old stellar population and in the final
-  equality we estimate the velocity dispersion using the
-  $M_{\bullet}-\sigma$ relationship (eq.~[\ref{eq:Msigma}]).
+  equality we estimate $\sigma_0 \approx \sqrt{3}\sigma$ using $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
 
@@
 for the stagnation radius, we find that
-
 \begin{align}
@@
 \end{align}
-If $r_{\rm Ia} \gg r_{\rm s}$, then SN Ia heating can only be
-approximated as a steady heating source near the stagnation radius for
-extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
-the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
-h}$).
-
-%On the other hand, equation (\ref{eq:rIars}) may underestimate
-%the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
-%substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
-%if the heating rate excluding SN Ia is less than this.
-
-Even if SN Ia are rare near the stagnation radius, they may cap the
+Equation (\ref{eq:rIars}) shows that SN Ia can only be approximated as a steady heating source near the stagnation radius for
+extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or for a very young stellar population ($\tau_{\star} \ll t_{\rm h}$).
+
+However, even if SN Ia are rare near the stagnation radius, SN Ia may cap the
 SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between successive supernovae, stars release a
+low mass galaxies.  Between successive SNe, stars release a
 gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
-interior to the Ia radius, which is gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}f^{2}$, where $f \sim 1$ for cusp galaxies and $f \sim$ few for core galaxies due to the greater escape speed from core galaxies.
-
-According
-to the above definitions, we thus find that 
+interior to the Ia radius, which is locally gravitationally bound to the SMBH
+by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F} 
+\lesssim$ few.  From the above definitions we find that 
 \be
-E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2f^{2}\sigma^{2}.  
+\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.  
 \ee
-Hence, for low mass BHs with $\sigma_0 \ll f v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Thus, even when heating is sufficiently weak for the stagnation radius to formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is limited to a value
+Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
 \begin{eqnarray}
@@
 obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]).
-Note, however, that for low mass black holes $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
-
-The deep potential wells of high mass galaxies $\sigma \gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas.
-Equation (\ref{eq:eddr_Ia}) may nevertheless cap the accretion rate in practice because, even if other source of heating are ineffective, the Ia heating rate (eq.~[\ref{eq:vIa}]) is sufficiently great to prevent the stagnation radius from substantially exceeding $r_{\rm Ia}$.
+Note, however, that for low mass SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
+
+The deep gravitational potential wells of high mass galaxies $\sigma_0 \gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas in these systems.
+Equation (\ref{eq:eddr_Ia}) nevertheless represents a cap on the accretion rate in practice because if other source of heating are ineffective, then the Ia heating rate (eq.~[\ref{eq:vIa}]) is usually sufficiently high to prevent the stagnation radius (calculated including the heating from SN Ia) from substantially exceeding $r_{\rm Ia}$.
 

### 2015-04-06 ms.tex
section 5.5.1

@@
 
-The total gas heating rate, 
+The total external gas heating rate, 
 \begin{equation}
@@
 The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
-The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
+As we now describe, the latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
 
@@
 subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]) {\bf AG have not yet done this in the impulsive limit}.  Finally, note that $v_{\rm w}^{\rm C}$ and
+(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and
 depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
@@
 
-For low-mass black holes, stellar winds are the most important source
-of heating on timescales of $\tau_{\star} \lesssim $ few $10^{7}$
+For low-mass black holes (Fig.~\ref{fig:vwSourcesImp}, top panel), stellar winds are the most important source
+of heating on timescales of $\tau_{\star} \lesssim 10^{7}$
 years.  Compton heating comes to dominate at later times due to the
@@
 gas densities associated with a relatively young stellar population.
-Compton heating dominates at all epochs for higher mass black holes,
-with stellar winds and Ia SN competing for the most significant
-non-AGN heating source.  As the total heating rate declines with time,
-after some point the flow becomes thermally unstable according to the
-criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim
-10$ (eq.~[\ref{eq:cooling3}]) {\bf BDM: correct?}, as shown by dashed
-lines in Fig.~\ref{fig:vwSourcesImp}.  The thermal stability threshold
-is calculated neglecting Compton heating because SMBH feedback may not
-be capable of truly stabilizing the flow given its inability to
+Interestingly, Ia SN dominate the heating briefly around 10$^{9}$ yr due to a window of time in which $r_Ia < \rs$.
+For high-mass black holes (Fig.~\ref{fig:vwSourcesImp}, bottom panel), Compton heating dominates at all epochs, while SN Ia  dominate after 10$^{8}$ yr.
+
+As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the
+criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 10$ (eq.~[\ref{eq:cooling3}]), as shown by dashed
+lines in Fig.~\ref{fig:vwSourcesImp}.
+Compton heating is neglected in calculating thermal stability because unlike local stellar feedback mechanisms, SMBH feedback may not be capable of truly stabilizing the flow given its inability to
 respond instantaneously to local changes in the properties of the gas.
-Thermally unstable flow is seen to be the norm in the single starburst
-case, except at very early times, $\tau_{\star} \lesssim 1-3 \times
-10^7$ yr.
+Thermally unstable flow is present throughout the single starburst case except at very early times, $\tau_{\star} \lesssim 10^7$ yr, and at late times $\tau_{\star} \gtrsim 10^{8}$ yr in the high $M_{\bullet}$ case.
 

### 2015-04-06 ms.tex
section 5

@@
 the average star formation history of galaxies containing a given
-black hole mass.  Again, Ia heating is suppressed in low mass galaxies
-because the Ia radius exceeds the nominal stagnation radius (bottom
-panel).  MSP heating is again found to be negligible for all black
-hole masses.  The younger stellar populations characterizing galaxies
-with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
-and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
-$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
-massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
+black hole mass.  The younger stellar populations characterizing galaxies
+with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar wind, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.
+Only for the most massive galaxies, with $\Mbh\gsim 3\times 10^{8} \Msun$, does the lack
 of young stellar populations significantly reduce the role of stellar
-wind
-heating.
-%Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
+wind heating.
+But for these massive galaxies, Ia heating contributes a comparable level of heating $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$.
+However, for low mass galaxies Ia heating does not contribute to the total heating rate because the Ia radius exceeds the nominal stagnation radius (bottom panel).
+Finall, MSP and Compton heating is found to be negligible for all black hole masses.
 Strikingly, {\it we find that galactic nuclei experiencing the same
-  average star formation history as their host galaxies produce
-  thermally stable flows across almost all black hole masses}.
-One important exception occurs for the highest mass black holes, for which the total effective wind velocity is comparable to the stellar velocity dispersion ($\zeta \sim \zeta_c$) and thermal stability for the average star formation history is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
+  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses}.  
+We must caveat, however, that for high $M_{\bullet}$ the total effective wind velocity is only a factor of 2-3 times higher than the stellar velocity dispersion ($\zeta \sim \zeta_c$), such that thermal stability is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
 
 Realistic variations (``burstiness") in the star formation history
-will often result in lower heating rates.  Figure \ref{fig:NickPlot2}
+will also often result in lower heating rates (Appendix
+\ref{app:windheat}).  Figure \ref{fig:NickPlot2}
 shows the heating rate as a function of average black hole mass for
@@
 suppressed by a factor $\iota$ from its average $z = 0$ value, for a
-characteristic timescale $\delta t_{\star}$ (for details, see Appendix
-\ref{app:windheat}).  For $\delta t_{\star} \lesssim 10^{7}$ yr, we see
+characteristic timescale $\delta t_{\star}$.  For $\delta t_{\star} \lesssim 10^{7}$ yr, we see
 that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$

### 2015-04-06 ms.tex
fixed table caption
fixed 6.1

@@
   saturation parameter $\phi = 0.1$ (recall that the
-  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
+  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$).  Entries for solutions found to be thermally unstable for all values of $\eta > 0.02$ are denoted as {\bf TI}.
 \end{tablenotes}
@@
 \frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.  
+\label{eq:blowout}
 \ee
@@
 
-Figure \ref{fig:vwSources} shows that the heating associated with the
-average star formation history of a galaxy is approximately constant
-with SMBH mass, except for the largest black holes with $M_{\bullet}
-\gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter,
-the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto
-M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively
-(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
-
-Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
-accretion rate as a function of black hole mass for the average star
-formation heating, calculated from equation (\ref{eq:eddr_analytic})
-using our results for the total wind heating
-(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
-from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
-black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
-10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
-These fall below the maximum thermally stable accretion rate,
-$\dot{M}_{\rm TI}$ (yellow lines), except at the highest
-black hole masses $\sim 10^{9}M_{\odot}$.
-
-For low mass black holes, blow out from near the SN Ia radius caps the SMBH accretion rate at a value $\dot{M}_{\rm Ia} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines; eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent otherwise thermally-unstable flow at smaller radii (see discussion following eq.~[\ref{eq:eddr_Ia}]).
-For higher mass black holes the stagnation resides close to the Ia radius, but the energy released by a single Ia is insufficient to unbind gas from the stellar bulge (although Ia heating contributes to the steady heating rate).
-
-%For these highest mass
-%black holes, the maximum accretion rate as set by the SN Ia
-%radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
-%accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
-For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
-%also prevent the development of thermally unstable flows,
-%i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
-
-Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}, as well as the range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through detailed modeling by \citealt{ShcherbakovWong+:2014a} (who find a range of accretion rates depending on the assumed model for thermal conductivity, although they do not include saturation of the conductive flux as considered in this work).
-The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for the same $M_{\bullet}$ by almost two orders of magnitude.
-This discrepancy can be understood by the fact that star formation in the central parsec of the Milky Way is not in steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
-Such a star formation history is better described by our `star burst' scenario, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
-
 \begin{figure}
@@
 
+Figure \ref{fig:vwSources} shows that the heating associated with the
+average star formation history of a galaxy is approximately constant
+with SMBH mass, except for the largest black holes with $M_{\bullet}
+\gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter,
+the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto
+M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).
+
+Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
+accretion rate as a function of black hole mass for the average star
+formation heating, calculated from equation (\ref{eq:eddr_analytic})
+using our results for the total wind heating
+(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
+from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
+black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
+10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
+These fall below the maximum thermally stable accretion rate,
+$\dot{M}_{\rm TI}$ (yellow lines), although they become closer at the highest
+black hole masses $\sim 10^{9}M_{\odot}$.
+
+For low mass black holes, blow out from SN Ia radius caps the SMBH accretion rate at a value $\dot{M}_{\rm Ia} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines; eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent otherwise thermally-unstable flow at smaller radii (see discussion following eq.~[\ref{eq:eddr_Ia}]).
+On the other hand, for higher $M_{\bullet}$ the stagnation resides close to the Ia radius so Ia heating contributes to the steady gas heating rate, however the energy released by a single Ia is insufficient to unbind gas from the stellar bulge (eq.~[\ref{eq:blowout}]).
+
+%For these highest mass
+%black holes, the maximum accretion rate as set by the SN Ia
+%radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
+%accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
+For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
+%also prevent the development of thermally unstable flows,
+%i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
+
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
+Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through detailed modeling by \citealt{ShcherbakovWong+:2014a}, who find a range of accretion rates depending on the assumed model for thermal conductivity (although we expect this range would be smaller had they included saturation of the conductive flux).
+The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for the same $M_{\bullet}$ by almost two orders of magnitude.
+This discrepancy can be understood by the fact that star formation in the central parsec of the Milky Way cannot be described as steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
+Such a star formation history is better described by our `star burst' scenario, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
+
 \subsection{Nuclear X-ray Luminosities}

### 2015-04-06 ms.tex
fixed 6.3

@@
 similar mass, then to first order we predict that $\langle
-L_{X}/L_{\rm edd}\rangle$ should increase with black hole mass, though
-only weakly for $M_{\bullet} \lesssim 3\times 10^{8}M_{\odot}$.  This
-result is in tension with the observed down-sizing trend that the
-average Eddington ratio is seen to decrease (albeit also weakly)
-with $M_{\bullet}$.  However, one must keep in mind the enormous uncertainty in calculating the
-luminosity of the accretion flow close to the black hole in a single
-waveband based on the feeding rate on larger scales.
+L_{X}/L_{\rm edd}\rangle$ should be relatively independent of BH mass.  To within the uncertainties, this
+result is consistent with the observed down-sizing trend that the average Eddington ratio is seen to decrease (albeit weakly)
+with $M_{\bullet}$, although tension is somewhat greater in the $\epsilon_X=
+  (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$ model.
+
+%However, one must keep in mind the enormous uncertainty in calculating the
+%luminosity of the accretion flow close to the black hole in a single
+%waveband based on the feeding rate on larger scales.
 If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
-angular momentum of the infalling gas might also influence the X-ray luminosity, in a way
-that could depend systematically on the stellar population and hence $M_{\bullet}$.
+%angular momentum of the infalling gas might also influence the X-ray luminosity, in a way
+%that could depend systematically on the stellar population and hence $M_{\bullet}$.
 
@@
 value of the X-ray efficiency assumed in the right panel of Figure \ref{fig:miller} represents a maximum value, since it does not account for suppression of the SMBH accretion rate due to outflows from the accretion disk on small
-radial scales.
-If the actual radiative efficiency is lower, then many of the X-ray detections would lie even further above above the predicted value of $\langle L_X \rangle$ for stable accretion (black line).
-Either these
-galaxies experience much less heating than average galaxies of the same mass, or they are not accreting stably
-at all.  Indeed, for $M_{\bullet} \lesssim
+radial scales (e.g., \citealt{Blandford&Begelman99}).
+If the actual radiative efficiency is lower than our fiducial assumption, then many of the X-ray detections would lie above the predicted value of $\langle L_X \rangle$ for stable accretion (black line).
+In this case the X-ray detected galaxies either experience less heating than average galaxies of the same mass, or they are not accreting stably at all.
+{\bf BDM: we may need to remove - why did this change so much?} Indeed, for $M_{\bullet} \lesssim
 10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the
@@
 
-Figure \ref{fig:bh_growth} (top panel) also shows that Compton heating cannot prevent average
-accretion rates which are thermally unstable, i.e. $\dot{M}_{\rm C} >
-\dot{M}_{\rm TI}$, across all
-black hole masses.
+Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm C} >
+\dot{M}_{\rm TI}$ across all black hole masses.
+Thus, even if Compton heating could act to stabilize the flow (which, as already mentioned, is unlikely), for fiducial parameters it is insufficient to produce a thermally stable accretion rate given conditions corresponding to the average star formation history.
 When thermal instabilities become manifest, nuclear gas may undergo cyclic oscillations of rapid cooling and high accretion rates, followed by quiescent periods once gas has been consumed and/or
 AGN feedback becomes effective.  Such cycles are seen in numerical simulations of elliptical galaxies on 
-large scales and long timescales (\citealt{Ciotti+10}), an idea which supported by observations showing that a fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+large scales and long timescales (\citealt{Ciotti+10}), an idea which is supported by observations showing that a fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
 
@@
 between instabilities and periodic nuclear outbursts.  Due to their
-deeper potential wells {\bf AG: Cores don't necessarily have deeper
-  potential wells overall}, we find that core
-galaxies are more likely to possess higher accretion rates and
+deeper potential well on scales of the sphere of influence, core galaxies are more likely to possess higher accretion rates and
 potentially be thermally unstable for a fixed wind heating rate than
-cusp galaxies.  This could help explain why core galaxies show a wide
-range of nuclear radio and X-ray luminosities (suggesting cyclic
-accretion episodes), while cusp galaxies are confined below a
-threshold (e.g., \citealt{Bender+89, Pellegrini99,
-  Capetti&Balmaverde05}), consistent with thermally-stable,
-steady-state picture. ({\bf AG: This picture may be dubious...Review
-  the literature but I think that the higher upper bound for cores is
-  just due to a mass selection effect.  BDM: The ghost of Balmaverde
-  disagrees.})
+cusp galaxies.
+
+%This could help explain why core galaxies show a wide
+%range of nuclear radio luminosities (suggesting cyclic
+%accretion episodes), while cusp galaxies are confined below a
+%threshold (e.g., \citealt{Bender+89, Pellegrini99,
+ % Capetti&Balmaverde05}), consistent with thermally-stable,
+%steady-state picture. ({\bf AG: This picture may be dubious...Review
+ % the literature but I think that the higher upper bound for cores is
+  %just due to a mass selection effect.  BDM: Balmaverde
+ % disagrees.})
 
 If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$ in Fig
-\ref{fig:miller} indeed represent thermally-unstable galaxies, then a fraction of the upper limits may contribute to a separate thermally stable population, for instance including SgrA*.
-However, the possibility of a mixed population of stable versus unstable galaxies calls into question the use of simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of black holes in low mass galaxies (\citealt{Miller+15}).
+\ref{fig:miller} are indeed in a state of thermally-unstable cyclic behavior, then a subset of the galaxies with X-ray upper limits may contribute to a separate steady-state, thermally stable population, for instance including SgrA* (which has a much lower X-ray luminosity for its black hole mass than predicted by the \citet{Miller+15} trend).
+One consequence of a potentially bimodal population of steady and cyclic galactic nuclei calls into question the physical justification of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass galaxies.
 

### 2015-04-06 ms.tex
spelling

@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ will in many cases reside near the nominal Bondi
+show that $\rs$ will in many cases resides near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation

### 2015-04-06 ms.tex
intro

@@
 
-In this paper we instead focus on time-independent models,
-neglecting radiative cooling.  This approach allows us to
-systematically explore the relevant parameter space and to derive
-analytic expressions that prove useful in determining whether
-cooling instabilities manifest across the expected range of galaxy
-properties, or whether other (non-AGN) forms of feedback can produce a prolonged state of steady, thermally stable accretion.
-Even if cooling instabilities develop on galactic scales over longer $\sim$ Gyr timescales, a quasi steady-state  may exist between these inflow events on
-smaller radial scales comparable to the sphere of influence.  We are
-thus motivated to explore whether such steady flows are generally expected within the
-nucleus under, or whether in most galaxies the nuclear gas content is always
-building towards instability.
+In this paper we instead focus on time-independent models, with
+sufficient heating to have negligible radiative cooling.  This
+approach allows us to systematically explore the relevant parameter
+space and to derive analytic expressions that prove useful in
+determining whether cooling instabilities manifest across the expected
+range of galaxy properties, or whether other (non-AGN) forms of
+feedback can produce a prolonged state of steady, thermally stable
+accretion.  Even if cooling instabilities develop on galactic scales
+over longer $\sim$ Gyr timescales, a quasi steady-state may exist
+between these inflow events on smaller radial scales comparable to the
+sphere of influence.  We are thus motivated to explore whether such
+steady flows are generally expected within the nucleus under, or
+whether in most galaxies the nuclear gas content is always building
+towards instability.
 %A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
@@
 radius).  When heating is sufficiently weak, however, the stagnation
-radius may move to much larger radii or not exist at all, in which case the entire ISM of the galaxy is flowing
-towards the SMBH.  A goal of this work is to assess under what
-conditions a stagnation radius exists, as this question is intimately
-tied to that of cooling instability.
-% Furthermore, in some cases we find that no stagnation
-% radius exists at all; this formally implies that the entire of ISM of
-% the galaxy is feeding the SMBH, potentially resulting in much higher
-% accretion rate than would be predicted by simple Bondi accretion.
+radius may move to much larger radii or not exist at all, in which
+case nearly entire ISM of the galaxy is flowing towards the SMBH.  A goal
+of this work is to assess under what conditions a stagnation radius
+exists, as this question is intimately tied to that of cooling
+instability.
 
 This paper is organized as follows.  In $\S\ref{sec:model}$ we
-describe our model, including the sample of galaxy properties used in our
-analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
+describe our model, including the sample of galaxy properties used in
+our analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
 calculating the steady-state hydrodynamic profile of the CNM
-($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our analytic results, which are justified via numerical solutions in $\S\ref{sec:numerical}$ we describe our
-numerical results.  In $\S\ref{sec:discussion}$ we discuss the
-implications of our results for topics which include the nuclear X-ray
-luminosities of quiescent black holes, jetted TDEs, and the growth of SMBHs in the local universe.
-In $\S\ref{sec:conclusions}$ we summarize our conclusions.
-Table \ref{table:definitions} provides the definitions
-of commonly used variables.  Appendices \ref{app:rs} and \ref{app:be}
-provide useful analytic results for the stagnation radius and the
-Bernoulli parameter of the flow, while Appendix \ref{app:windheat} provides the details of our method for calculating stellar wind heating and mass input.
+($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
+analytic results, which are justified via numerical solutions in
+$\S\ref{sec:numerical}$ we describe our numerical results.  In
+$\S\ref{sec:discussion}$ we discuss the implications of our results
+for topics which include the nuclear X-ray luminosities of quiescent
+black holes, jetted TDEs, and the growth of SMBHs in the local
+universe.  In $\S\ref{sec:conclusions}$ we summarize our conclusions.
+Table \ref{table:definitions} provides the definitions of commonly
+used variables.  Appendices \ref{app:rs} and \ref{app:be} provide
+useful analytic results for the stagnation radius and the Bernoulli
+parameter of the flow, while Appendix \ref{app:windheat} provides the
+details of our method for calculating stellar wind heating and mass
+input.
 

### 2015-04-06 ms.tex
language

@@
 solution, in particular for high SMBH masses and low heating rates,
-for which the stagnation radius approaches large radii. {\bf AG
-  describe unphysically large rb for the case of cores.}
+for which the stagnation radius approaches large radii. We also
+neglect value of $r_b$ which would give unphysically large bulges for
+a given $\Mbh$.
 
@@
 
-Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the density $\rho$, temperature $T$, and radial velocity $v$ of the CNM for each galaxy model by solving the equations of one-dimensional, time-dependent hydrodynamics,
+Following \citet{Quataert:2004a} (see also
+\citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}),
+we calculate the density $\rho$, temperature $T$, and radial velocity
+$v$ of the CNM for each galaxy model by solving the equations of
+one-dimensional, time-dependent hydrodynamics,
 \begin{align}
@@
 \label{eq:sigmarel}
-\ee
-where the first term is the velocity dispersion of the power law stellar density profile in the SMBH potential.
-The second term, $\sigma_0\approx 3 \sigma^2$ is a constant, motivated by the observed velocity dispersion outside of the SMBH sphere of influence \citep{ChaeBernardi+:2014a}, where $\sigma$ is the velocity dispersion in the $\Mbh-\sigma$
-relation (eq.~[\ref{eq:Msigma}]).
-The second component of the total heating, $v_{w}^{2}$, parameterizes all additional sources of energy input, including faster winds from young stars, millisecond pulsars, supernovae, AGN feedback, etc.
-We assume that $v_w$ is constant with radius, i.e.
-that the volumetric heating rate is proportional to the local stellar density.
-The value of $v_w$ will in general depend on the SMBH mass and the age of the stellar population ($\S\ref{sec:heating}$).
-
-To isolate the physics of greatest interest, our baseline calculations neglects three potentially important effects: heat conduction, radiative cooling, and rotation.
-Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:
+\ee where the first term is the velocity dispersion of the power law
+stellar density profile in the SMBH potential.  The second term,
+$\sigma_0\approx 3 \sigma^2$ is a constant, motivated by the observed
+velocity dispersion outside of the SMBH sphere of influence
+\citep{ChaeBernardi+:2014a}, where $\sigma$ is the velocity dispersion
+in the $\Mbh-\sigma$ relation (eq.~[\ref{eq:Msigma}]).  The second
+component of the total heating, $v_{w}^{2}$, parameterizes all
+additional sources of energy input, including faster winds from young
+stars, millisecond pulsars, supernovae, AGN feedback, etc.  We assume
+that $v_w$ is constant with radius, i.e. that the volumetric heating
+rate is proportional to the local stellar density.  The value of $v_w$
+will in general depend on the SMBH mass and the age of the stellar
+population ($\S\ref{sec:heating}$).
+
+To isolate the physics of greatest interest, our baseline calculations
+neglects three potentially important effects: heat conduction,
+radiative cooling, and rotation.  Electron heat conduction results in
+an an additional term on the right hand side of the entropy equation
+of the form:
 \begin{equation}
@@
  \end{equation}
-where $\kappa_{\rm
-  eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
-the conductivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
-classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
-cgs units).  The flux limiter $\psi = \kappa_{\rm spitz} \nabla
-T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free
-path for electron coulomb scattering exceeds the
-temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the
-isothermal sound speed and $\phi \lesssim 1$ is an uncertain
-dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
-field that is oriented perpendicular to the flow could suppress the
-conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
-of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).
-We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity errors in the key properties of the solutions.
+ where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$
+ (\citealt{DaltonBalbus:1993a}) is the conductivity and $\kappa_{\rm
+   spitz} = \kappa_0 T^{5/2}$ is the classical \citet{Spitzer62} value
+ ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units).  The flux limiter
+ $\psi = \kappa_{\rm spitz} \nabla T/(5\phi \rho c_s^3)$ saturates the
+ conductive flux if the mean free path for electron coulomb scattering
+ exceeds the temperature length scale, where $c_s \equiv (kT/\mu
+ m_p)^{1/2}$ is the isothermal sound speed and $\phi \lesssim 1$ is an
+ uncertain dimensionless constant (we adopt $\phi = 0.1$).  Even a
+ weak magnetic field that is oriented perpendicular to the flow could
+ suppress the conductivity by greatly reducing the electron mean free
+ path.  However, for radially-decreasing temperature profiles of
+ interest, the flow is susceptible to the magneto-thermal instability
+ (\citealt{Balbus01}), the non-linear evolution of which is believed
+ to result in a radially-directed field geometry
+ (\citealt{Parrish&Stone07}).  We show later in
+ $\S\ref{sec:conductivity}$ that neglecting conductivity results in at
+ most only order-unity errors in the key properties of the solutions.
 
@@
 \end{equation}
-where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.
-We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
-time-independent model.
-A main goal of this work is to use solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:instability}$).
+where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is
+the cooling function.  We neglect radiative cooling in our baseline
+calculations, despite the fact that this is not justified when the
+wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
+However, once radiative cooling becomes important compared to other
+sources of heating and cooling, its presence leads to thermal
+instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for
+by our 1D time-independent model.  A main goal of this work is to use
+solutions neglecting radiation to ascertain over what range of
+physical conditions cooling instabilities are most likely to develop
+($\S\ref{sec:instability}$).
 
@@
 and entropy equations for numerical stability
-(\citealt{Brandenburg:2003a}).  We assume different
-choices of $v_{w} = 300, 600, 1200$ km s$^{-1}$ spanning a
-physically plausible range of heating rates.
-Although we are interested in the steady-state inflow/outflow solution (assuming one exists), the time-dependent equations are solved to avoid numerical issues that arise near the critical sonic points, of which there are up to two because of the supersonic
-inflow on small radial scales and a possible supersonic outflow on large scales.
-Also note that our solutions can be scaled to any value of the mass input parameter, $\eta$, since the mass and energy source terms scale linearly with $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be specified when cooling or thermal conduction are included, since these scale as gas density to a different power.
-We check the accuracy of our numerical solutions by confirming that mass is conserved across the grid, in addition to the integral constraint on the energy (Bernoulli integral).
+(\citealt{Brandenburg:2003a}).  We assume different choices of $v_{w}
+= 300, 600, 1200$ km s$^{-1}$ spanning a physically plausible range of
+thermally stable {\bf AG phrasing ok?} heating rates.  Although we are
+interested in the steady-state inflow/outflow solution (assuming one
+exists), the time-dependent equations are solved to avoid numerical
+issues that arise near the critical sonic points, of which there are
+up to two because of the supersonic inflow on small radial scales and
+a possible supersonic outflow on large scales.  Also note that our
+solutions can be scaled to any value of the mass input parameter,
+$\eta$, since the mass and energy source terms scale linearly with
+$\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be
+specified when cooling or thermal conduction are included, since these
+scale as gas density to a different power.  We check the accuracy of
+our numerical solutions by confirming that mass is conserved across
+the grid, in addition to the integral constraint on the energy
+(Bernoulli integral).
 

### 2015-04-06 ms.tex
fixing brian rounding errors

@@
 
-In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the stagnation radius moves to large radii, approaching the break radius $\rb$ in the stellar density profile, formally implying that almost entire ISM of the galaxy is accreting.
-In particular, in Appendix \ref{app:be} we show that $\rs \Rightarrow \rb$ for heating below a critical threshold
-\be
-\zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} < \zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
+In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the
+stagnation radius moves to large radii, approaching the break radius
+$\rb$ in the stellar density profile, formally implying that almost
+entire ISM of the galaxy is accreting.  In particular, in Appendix
+\ref{app:be} we show that $\rs \Rightarrow \rb$ for heating below a
+critical threshold \be \zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
+\zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
 \label{eq:zetacrit}
-\ee
-This result makes intuitive sense: gas is supplied to the nuclear by stars which are gravitationally bound to the black hole, so outflows are possible only if the specific heating rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational binding energy.
-Condition (\ref{eq:zetacrit}) approximately corresponds to the condition that the wind heating parameter be less than the escape speed from the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
+\ee This result makes intuitive sense: gas is supplied to the nuclear
+by stars which are gravitationally bound to the black hole, so
+outflows are possible only if the specific heating rate $\sim
+v_{w}^{2}$ significantly exceeds the specific gravitational binding
+energy.  Condition (\ref{eq:zetacrit}) approximately corresponds to
+the condition that the wind heating parameter be less than the escape
+speed from the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
+    b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
 
@@
 \end{eqnarray}
-where we have assumed $v_{w} \gg \sigma$ by adopting equation (\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is given by 
+where we have assumed $v_{w} \gg \sigma$ by adopting equation
+(\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
+given by
 \begin{eqnarray}
@@
 Eddington accretion rate, assuming a radiative efficiency of ten per
-cent.  Note the sensitive dependence of the accretion rate on
-the wind heating rate.
+cent.  Note the sensitive dependence of the accretion rate on the wind
+heating rate.
 %To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$
@@
 \begin{align}
-  \dot{M}_{\rm B} =4\pi \lambda r_{\rm B}^2 \rho|_{r_{\rm B}}v_{\rm ff}|_{r_{\rm B}},
+  \dot{M}_{\rm B} =4\pi \lambda r_{\rm B}^2 \rho|_{r_{\rm B}}v_{\rm
+    ff}|_{r_{\rm B}},
 \label{eq:bondi}
@@
   {\rm max}\begin{cases}
-   200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
+   300 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   260 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
 \approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
@@
 \end{align}
-where the final condition corresponds to the low wind heating limit ($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our numerical and analytic results show that the stagnation radius moves out to the break radius $r_b$; the quasi-hydrostatic structure that develops in this case greatly increases the gas density, resulting in thermal instability.
+where the final condition corresponds to the low wind heating limit
+($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our
+numerical and analytic results show that the stagnation radius moves
+out to the break radius $r_b$; the quasi-hydrostatic structure that
+develops in this case greatly increases the gas density, resulting in
+thermal instability.
 
@@
 \begin{align}
-\frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq
-  {\rm min}\begin{cases}
-   5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
-3\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.38} &, \text{core}, \zeta < \zeta_c \\
-   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
-2.5\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
+  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq {\rm
+    min}\begin{cases}
+    2\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
+    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
+    7\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
+    1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
   \end{cases}
@@
 (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
-the second line corresponds to the low wind heating limit $\zeta \ll \zeta_c$.  $\zeta_c$ is
-calculated using the empirical correlation for core galaxies
-$r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{0.2}$ which follows from
-equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$ correlation derived from the results of \citet{LauerFaber+:2007a}.  {\bf BDM: check this}
+the second line corresponds to the low wind heating limit $\zeta \ll
+\zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
+core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ {\bf
+AG: this is the second time I have caught this, is there any
+particular reason you think this should be +0.2 not -0.2} which
+follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
+correlation derived from the results of \citet{LauerFaber+:2007a}.
+{\bf BDM: check this}
 
@@
 \end{equation}
-includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback.
-The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.
-As we now describe, the latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.
+includes contributions from stellar winds, supernovae, pulsars, and
+radiative SMBH feedback.  The strength of each heating source depends
+explicitly on the SMBH mass and the stellar population in the galactic
+nuclear region.  As we now describe, the latter could best be
+described by a single star burst formation in the past, or by a more
+continuous star formation history that itself varies systematically
+with the galaxy mass and hence $\Mbh$.
 
@@
 
-For low mass black holes, blow out from SN Ia radius caps the SMBH accretion rate at a value $\dot{M}_{\rm Ia} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines; eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent otherwise thermally-unstable flow at smaller radii (see discussion following eq.~[\ref{eq:eddr_Ia}]).
-On the other hand, for higher $M_{\bullet}$ the stagnation resides close to the Ia radius so Ia heating contributes to the steady gas heating rate, however the energy released by a single Ia is insufficient to unbind gas from the stellar bulge (eq.~[\ref{eq:blowout}]).
-
-%For these highest mass
-%black holes, the maximum accretion rate as set by the SN Ia
-%radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
-%accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).
-For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
-%also prevent the development of thermally unstable flows,
-%i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.
-
-Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
-Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through detailed modeling by \citealt{ShcherbakovWong+:2014a}, who find a range of accretion rates depending on the assumed model for thermal conductivity (although we expect this range would be smaller had they included saturation of the conductive flux).
-The SgrA* rate exceeds our estimate of $\dot{M}$ due to the average star formation history for the same $M_{\bullet}$ by almost two orders of magnitude.
-This discrepancy can be understood by the fact that star formation in the central parsec of the Milky Way cannot be described as steady-state: feedback is instead dominated by the stellar winds from the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).
-Such a star formation history is better described by our `star burst' scenario, for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the value of $\eta \sim 1$ predicted in the average SFH case (Fig.~\ref{fig:vwSources}, bottom panel).
+For low mass black holes, blow out from SN Ia radius caps the SMBH
+accretion rate at a value $\dot{M}_{\rm Ia} \sim
+10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines;
+eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
+otherwise thermally-unstable flow at smaller radii (see discussion
+following eq.~[\ref{eq:eddr_Ia}]).  On the other hand, for higher
+$M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
+heating contributes to the steady gas heating rate, however the energy
+released by a single Ia is insufficient to unbind gas from the stellar
+bulge (eq.~[\ref{eq:blowout}]).
+
+% For these highest mass black holes, the maximum accretion rate as
+% set by the SN Ia radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could
+% instead cap the accretion rate close to the thermally-unstable value
+% (see discussion following eq.~[\ref{eq:eddr_Ia}]).  For lower mass
+% black holes, the maximum accretion rate set by SNe Ia is
+% significantly higher and cannot also prevent the development of
+% thermally unstable flows, i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm
+% TI}$.
+
+Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
+the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
+Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115
+derived through detailed modeling by \citealt{ShcherbakovWong+:2014a},
+who find a range of accretion rates depending on the assumed model for
+thermal conductivity (although we expect this range would be smaller
+had they included saturation of the conductive flux).  The SgrA* rate
+exceeds our estimate of $\dot{M}$ due to the average star formation
+history for the same $M_{\bullet}$ by almost two orders of magnitude.
+This discrepancy can be understood by the fact that star formation in
+the central parsec of the Milky Way cannot be described as
+steady-state: feedback is instead dominated by the stellar winds from
+the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and
+estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).  Such a star
+formation history is better described by our `star burst' scenario,
+for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
+(Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
+value of $\eta \sim 1$ predicted in the average SFH case
+(Fig.~\ref{fig:vwSources}, bottom panel).
 
@@
 The left panel of Figure \ref{fig:miller} is calculated assuming a
-constant low value for the radiative efficiency of $\epsilon_X = 10^{-4}$,
-typical of those estimated for low luminosity AGN (e.g.,
+constant low value for the radiative efficiency of $\epsilon_X =
+10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
 \citealt{Ho:2009a}), while the right panel luminosities are calculated
-instead assuming an efficiency of $\epsilon_X= 10 \epsilon_{\rm bol}\dot{M}/\dot{M}_{\rm
-  edd}$ that depends on the Eddington ratio as predicted by some
-models for radiatively inefficient accretion flows
-(\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison
-are the X-ray measurements (green stars) and upper limits (gray
-triangles) from the sample of early-type galaxies compiled by \citet{Miller+15}
-(cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
-to the X-ray luminosity from \citet{Miller+15}, given by $\langle
-L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
-\citep{Zhang+09, Pellegrini10, Gallo+10}).  Also shown are the maximum accretion rates,
-respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]; yellow),
-as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
+instead assuming an efficiency of $\epsilon_X= 10 \epsilon_{\rm
+  bol}\dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio
+as predicted by some models for radiatively inefficient accretion
+flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for
+comparison are the X-ray measurements (green stars) and upper limits
+(gray triangles) from the sample of early-type galaxies compiled by
+\citet{Miller+15} (cf.~\citealt{Gallo+10}).  A green line shows the
+best power-law fit to the X-ray luminosity from \citet{Miller+15},
+given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with
+$\alpha = -0.2$ (see also \citep{Zhang+09, Pellegrini10, Gallo+10}).
+Also shown are the maximum accretion rates, respectively, for
+thermally stable accretion (eq.~[\ref{eq:Mdotmax}]; yellow), as set by
+SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
 Compton heating feedback (eq.~[\ref{eq:MdotC}]; red).
@@
 \includegraphics[width=\textwidth]{miller.pdf}
-\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
-Black lines show our prediction in the case of heating due to the average star formation history for galaxies corresponding to each black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the relationship  $\Gamma(M_{\bullet})$ derived from the \citet{LauerFaber+:2007a} sample.
-Shown for comparison are the measurements ({\it red stars}) and
-  upper limits ({\it red triangles}) for $L_X/L_{\rm edd}$ values, from the \citet{Miller+15} sample of early-type galaxies (a green line shows the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).
-The left panel is calculated assuming a constant radiative efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand panel assumes $\epsilon_X=
-  (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g., \citealt{Narayan&Yi95}).
-Shown for comparison are the X-ray luminosities calculated for the maximum thermally-stable accretion rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion rate  ({\it pink line}; eq.~[\ref{eq:MdotCa}]),  again all calculated for the average star formation history corresponding to each SMBH mass.}
+\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
+  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
+  Black lines show our prediction in the case of heating due to the
+  average star formation history for galaxies corresponding to each
+  black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a
+  power-law fit for the relationship $\Gamma(M_{\bullet})$ derived
+  from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are
+  the measurements ({\it red stars}) and upper limits ({\it red
+    triangles}) for $L_X/L_{\rm edd}$ values, from the
+  \citet{Miller+15} sample of early-type galaxies (a green line shows
+  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
+  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
+  calculated assuming a constant radiative efficiency
+  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
+  panel assumes $\epsilon_X= (\epsilon_{\rm
+    bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g.,
+  \citealt{Narayan&Yi95}).  Shown for comparison are the X-ray
+  luminosities calculated for the maximum thermally-stable accretion
+  rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
+  Ia-regulated accretion rate ({\it teal line};
+  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
+  rate ({\it pink line}; eq.~[\ref{eq:MdotCa}]), again all calculated
+  for the average star formation history corresponding to each SMBH
+  mass.}
 \end{figure*}
 
-If the nuclei of elliptical galaxies are heated in a way similar to that due to the average star formation history of galaxies with
+If the nuclei of elliptical galaxies are heated in a way similar to
+that due to the average star formation history of galaxies with
 similar mass, then to first order we predict that $\langle
-L_{X}/L_{\rm edd}\rangle$ should be relatively independent of BH mass.  To within the uncertainties, this
-result is consistent with the observed down-sizing trend that the average Eddington ratio is seen to decrease (albeit weakly)
-with $M_{\bullet}$, although tension is somewhat greater in the $\epsilon_X=
-  (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$ model.
+L_{X}/L_{\rm edd}\rangle$ should be relatively independent of BH mass.
+To within the uncertainties, this result is consistent with the
+observed down-sizing trend that the average Eddington ratio is seen to
+decrease (albeit weakly) with $M_{\bullet}$, although tension is
+somewhat greater in the $\epsilon_X= (\epsilon_{\rm
+  bol}/0.1)(\Mdot/\MdotEdd)$ model.
 
@@
 
-Perhaps a more readily addressable test is whether a steady-state accretion
-picture developed in this work can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
-  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
-least three effects: (1) intrinsic scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
-  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
-the stellar wind velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
-\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
-(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
-combined with the significant dependence of $v_w$ on stochastic
-intermittency in the star formation history (Appendix
-\ref{fig:NickPlot2}), this can lead to order of magnitude differences
-in $\dot{M}$; (3) differences angular momentum of the infalling gas
-from galaxy to galaxy, resulting in differences in the fraction of the
-gas lost to outflows, $\Mbh$.  Also potentially contributing is the
-order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$,
-between $\dot{M}$ for core and cusp galaxies
-(Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are augmented by
-the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively
-inefficient flows.
+  Perhaps a more readily addressable test is whether a steady-state
+  accretion picture developed in this work can account for the the
+  large scatter, typically of $2-3$ orders of magnitude, in
+  $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.  Scatter could result
+  from at least three effects: (1) intrinsic scatter in the scaling
+  relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to
+  measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
+  the stellar wind velocity and mass loss parameter,
+  $\dot{M}/\dot{M}_{\rm edd} \propto \eta v_{w}^{-3.8(-2.4)}$ for
+  core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass};
+  eq.~[\ref{eq:eddr_analytic}]).  When combined with the significant
+  dependence of $v_w$ on stochastic intermittency in the star
+  formation history (Appendix \ref{fig:NickPlot2}), this can lead to
+  order of magnitude differences in $\dot{M}$; (3) differences angular
+  momentum of the infalling gas from galaxy to galaxy, resulting in
+  differences in the fraction of the gas lost to outflows, $\Mbh$.
+  Also potentially contributing is the order of magnitude difference,
+  at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and
+  cusp galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$
+  are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2}
+  $ for radiatively inefficient flows.
 
@@
 
-This prediction is in better with the observed dependence of $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies (Fig.~\ref{fig:miller}, green line), hinting that accretion regulation by kinetic feedback may serve as an alternative explanation for X-ray luminosities of elliptical galaxies.
-However, our assumption that kinetic outflows heat the gas uniformly in volume is somewhat arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous environment.
-It is furthermore unclear whether our steady-state model can be applied at all, because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scales.
+This prediction is in better with the observed dependence of $\langle
+L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
+(Fig.~\ref{fig:miller}, green line), hinting that accretion regulation
+by kinetic feedback may serve as an alternative explanation for X-ray
+luminosities of elliptical galaxies.  However, our assumption that
+kinetic outflows heat the gas uniformly in volume is somewhat
+arbitrary and would need to more rigorously justified by numerical
+studies of how jets or disk outflows couple energy to their gaseous
+environment.  It is furthermore unclear whether our steady-state model
+can be applied at all, because black hole feedback depends on the
+central accretion rate, which (unlike stellar feedback) does not
+respond instantaneously to changes in the thermodynamic properties of
+the gas on larger scales.
 
@@
 
-  \item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8 \Msun$ with star formation histories matching the average values derived from the cosmological simulations of \citet{MosterNaab+:2013a} possess an effective heating rate
-    $v_w\sim 1000$ km s$^{-1}$, relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).
-This results in a prediction for the average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension with the trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}), which instead find that $\eddr$ increases towards smaller $\Mbh$.
-However, high X-ray radiative efficiencies are required for these galaxies to be consistent with thermally-stable accretion, instead suggesting that (at least at low black hole masses), the possibility of two branches of accretion states.
-
-%However, it is important to note that the
- %   inflow rate on large scales (which we calculate) may differ from
+\item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
+  \Msun$ with star formation histories matching the average values
+  derived from the cosmological simulations of
+  \citet{MosterNaab+:2013a} possess an effective heating rate $v_w\sim
+  1000$ km s$^{-1}$, relatively independent of SMBH mass
+  (Fig.~\ref{fig:vwSources}).  This results in a prediction for the
+  average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with
+  $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension
+  with the trend of measured nuclear X-ray luminosities of early-type
+  galaxies (e.g., \citealt{Miller+15}), which instead find that
+  $\eddr$ increases towards smaller $\Mbh$.  However, high X-ray
+  radiative efficiencies are required for these galaxies to be
+  consistent with thermally-stable accretion, instead suggesting that
+  (at least at low black hole masses), the possibility of two branches
+  of accretion states.
+
+    % However, it is important to note that the inflow rate on large
+    % scales (which we calculate) may differ from
     % the actual accretion rate as outflows could occur on small
     % scales. The outflow rate would depend on the angular momentum of
-    %the infalling gas and thus the angular momentum of stars in the
-    %nucleus. The in turn would vary systematically with $\Mbh$.
+    % the infalling gas and thus the angular momentum of stars in the
+    % nucleus. The in turn would vary systematically with $\Mbh$.
 

### 2015-04-06 ms.tex
more challenges to quell

@@
 \begin{minipage}{18cm}
-\caption{Summary of Numerical Solutions}
+  \caption{Summary of Numerical Solutions {\bf AG make sure the
+      headings are consistent. Mark solutions which are unstable for
+      some values of eta.}}
 \begin{tabular}{lccccccccc}
@@
 \end{eqnarray}
-obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$ (eq.~[$\ref{eq:eddr_analytic}$]).
-Note, however, that for low mass SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate for a thermally stable flow $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe Ia cannot alone prevent cooling instabilities in the nuclei of low mass galaxies.
-
-The deep gravitational potential wells of high mass galaxies $\sigma_0 \gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas in these systems.
-Equation (\ref{eq:eddr_Ia}) nevertheless represents a cap on the accretion rate in practice because if other source of heating are ineffective, then the Ia heating rate (eq.~[\ref{eq:vIa}]) is usually sufficiently high to prevent the stagnation radius (calculated including the heating from SN Ia) from substantially exceeding $r_{\rm Ia}$.
+obtained substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}])
+for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$
+(eq.~[$\ref{eq:eddr_analytic}$]).  Note, however, that for low mass
+SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
+for a thermally stable flow $\dot{M}_{\rm TI}$
+(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
+Ia cannot alone prevent cooling instabilities in the nuclei of low
+mass galaxies {\bf AG--careful one needs a separate criterion for
+  thermal stability when heating is dominated by the Ias}.
+
+The deep gravitational potential wells of high mass galaxies $\sigma_0
+\gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
+in these systems.  Equation (\ref{eq:eddr_Ia}) nevertheless represents
+a cap on the accretion rate in practice because if other source of
+heating are ineffective, then the Ia heating rate (eq.~[\ref{eq:vIa}])
+is usually sufficiently high to prevent the stagnation radius
+(calculated including the heating from SN Ia) from substantially
+exceeding $r_{\rm Ia}$.
 
@@
 
-For low-mass black holes (Fig.~\ref{fig:vwSourcesImp}, top panel), stellar winds are the most important source
-of heating on timescales of $\tau_{\star} \lesssim 10^{7}$
-years.  Compton heating comes to dominate at later times due to the
-higher accretion rates that accompany the overall decrease in the
-heating rate, coupled with the persistently high mass loss rates and
-gas densities associated with a relatively young stellar population.
-Interestingly, Ia SN dominate the heating briefly around 10$^{9}$ yr due to a window of time in which $r_Ia < \rs$.
-For high-mass black holes (Fig.~\ref{fig:vwSourcesImp}, bottom panel), Compton heating dominates at all epochs, while SN Ia  dominate after 10$^{8}$ yr.
-
-As the total heating rate declines with time, after some point the flow becomes thermally unstable according to the
-criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 10$ (eq.~[\ref{eq:cooling3}]), as shown by dashed
-lines in Fig.~\ref{fig:vwSourcesImp}.
-Compton heating is neglected in calculating thermal stability because unlike local stellar feedback mechanisms, SMBH feedback may not be capable of truly stabilizing the flow given its inability to
-respond instantaneously to local changes in the properties of the gas.
-Thermally unstable flow is present throughout the single starburst case except at very early times, $\tau_{\star} \lesssim 10^7$ yr, and at late times $\tau_{\star} \gtrsim 10^{8}$ yr in the high $M_{\bullet}$ case.
+For low-mass black holes (Fig.~\ref{fig:vwSourcesImp}, top panel),
+stellar winds are the most important source of heating on timescales
+of $\tau_{\star} \lesssim 10^{7}$ years.  Compton heating comes to
+dominate at later times due to the higher accretion rates that
+accompany the overall decrease in the heating rate, coupled with the
+persistently high mass loss rates and gas densities associated with a
+relatively young stellar population.  Interestingly, Ia SN dominate
+the heating briefly around 10$^{9}$ yr due to a window of time in
+which $r_{ \rm Ia} < \rs$.  For high-mass black holes
+(Fig.~\ref{fig:vwSourcesImp}, bottom panel), Compton heating dominates
+at all epochs, while SN Ia dominate after 10$^{8}$ yr.
+
+As the total heating rate declines with time, after some point the
+flow becomes thermally unstable according to the criterion
+$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 10$
+(eq.~[\ref{eq:cooling3}]), as shown by dashed lines in
+Fig.~\ref{fig:vwSourcesImp}.  Compton heating is neglected in
+calculating thermal stability because unlike local stellar feedback
+mechanisms, SMBH feedback may not be capable of truly stabilizing the
+flow given its inability to respond instantaneously to local changes
+in the properties of the gas.  Thermally unstable flow is present
+throughout the single starburst case except at very early times,
+$\tau_{\star} \lesssim 10^7$ yr, and at late times $\tau_{\star}
+\gtrsim 10^{8}$ yr in the high $M_{\bullet}$ case.
 
@@
 will also often result in lower heating rates (Appendix
-\ref{app:windheat}).  Figure \ref{fig:NickPlot2}
-shows the heating rate as a function of average black hole mass for
-non-fiducial cases in which the current ($z = 0$) star formation is
-suppressed by a factor $\iota$ from its average $z = 0$ value, for a
-characteristic timescale $\delta t_{\star}$.  For $\delta t_{\star} \lesssim 10^{7}$ yr, we see
-that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
-from its average value, even for huge drops in the star formation rate
-($\iota \sim 10^{-3}$).  However, burstiness in the star formation
-history over longer timescales can suppress heating more
-significantly.  When $\delta t_{\star} \gtrsim 10^8~{\rm yr}$, $v_{\rm
-  w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm
-  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
-smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
+\ref{app:windheat}).  Figure \ref{fig:NickPlot2} shows the heating
+rate as a function of average black hole mass for non-fiducial cases
+in which the current ($z = 0$) star formation is suppressed by a
+factor $\iota$ from its average $z = 0$ value, for a characteristic
+timescale $\delta t_{\star}$.  For $\delta t_{\star} \lesssim 10^{7}$
+yr, we see that $v_{\rm w}^{\star}$ is reduced by at most a factor of
+$\approx 2$ from its average value, even for huge drops in the star
+formation rate ($\iota \sim 10^{-3}$).  However, burstiness in the
+star formation history over longer timescales can suppress heating
+more significantly.  When $\delta t_{\star} \gtrsim 10^8~{\rm yr}$,
+$v_{\rm w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$,
+$v_{\rm w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but
+for smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
 exception to this is in galactic nuclei with $M_\bullet \gtrsim
@@
 black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
-10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.
+10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{8}M_{\sun}$.
 These fall below the maximum thermally stable accretion rate,
-$\dot{M}_{\rm TI}$ (yellow lines), although they become closer at the highest
-black hole masses $\sim 10^{9}M_{\odot}$.
+$\dot{M}_{\rm TI}$ (yellow lines).
+% , although they become closer at the highest
+% black hole masses $\sim 10^{9}M_{\odot}$.
 
@@
 
-It is also possible that many of the
-\citet{Miller+15} sample of galactic nuclei are not accreting in steady state.  The
-value of the X-ray efficiency assumed in the right panel of Figure \ref{fig:miller} represents a maximum value, since it does not account for suppression of the SMBH accretion rate due to outflows from the accretion disk on small
-radial scales (e.g., \citealt{Blandford&Begelman99}).
-If the actual radiative efficiency is lower than our fiducial assumption, then many of the X-ray detections would lie above the predicted value of $\langle L_X \rangle$ for stable accretion (black line).
-In this case the X-ray detected galaxies either experience less heating than average galaxies of the same mass, or they are not accreting stably at all.
-{\bf BDM: we may need to remove - why did this change so much?} Indeed, for $M_{\bullet} \lesssim
-10^{8}M_{\odot}$, $L_{\rm X}$ nearly exceeds that predicted for the
-maximum thermally-stable accretion rate, $\dot{M}_{\rm TI}$ (yellow
-line).
-Since the \citet{Miller+15} sample includes only early-type galaxies with older stellar populations than the average for their black hole mass, it would not be too surprising if many of these galaxies were thermally unstable.
-
-Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm C} >
-\dot{M}_{\rm TI}$ across all black hole masses.
-Thus, even if Compton heating could act to stabilize the flow (which, as already mentioned, is unlikely), for fiducial parameters it is insufficient to produce a thermally stable accretion rate given conditions corresponding to the average star formation history.
-When thermal instabilities become manifest, nuclear gas may undergo cyclic oscillations of rapid cooling and high accretion rates, followed by quiescent periods once gas has been consumed and/or
-AGN feedback becomes effective.  Such cycles are seen in numerical simulations of elliptical galaxies on 
-large scales and long timescales (\citealt{Ciotti+10}), an idea which is supported by observations showing that a fraction of early-type galaxies in the local universe have undergone recent ($< 1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+It is also possible that many of the \citet{Miller+15} sample of
+galactic nuclei are not accreting in steady state.  The value of the
+X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
+represents a maximum value, since it does not account for suppression
+of the SMBH accretion rate due to outflows from the accretion disk on
+small radial scales (e.g., \citealt{Blandford&Begelman99}).  If the
+actual radiative efficiency is lower than our fiducial assumption,
+then many of the X-ray detections would lie above the predicted value
+of $\langle L_X \rangle$ for stable accretion (black line).  In this
+case the X-ray detected galaxies either experience less heating than
+average galaxies of the same mass, or they are not accreting stably at
+all.  {\bf BDM: we may need to remove - why did this change so much?}
+Indeed, for $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ nearly
+exceeds that predicted for the maximum thermally-stable accretion
+rate, $\dot{M}_{\rm TI}$ (yellow line).  Since the \citet{Miller+15}
+sample includes only early-type galaxies with older stellar
+populations than the average for their black hole mass, it would not
+be too surprising if many of these galaxies were thermally unstable.
+
+Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
+  C} > \dot{M}_{\rm TI}$ across all black hole masses.  Thus, even if
+Compton heating could act to stabilize the flow (which, as already
+mentioned, is unlikely), for fiducial parameters it is insufficient to
+produce a thermally stable accretion rate given conditions
+corresponding to the average star formation history.  When thermal
+instabilities become manifest, nuclear gas may undergo cyclic
+oscillations of rapid cooling and high accretion rates, followed by
+quiescent periods once gas has been consumed and/or AGN feedback
+becomes effective.  Such cycles are seen in numerical simulations of
+elliptical galaxies on large scales and long timescales
+(\citealt{Ciotti+10}), an idea which is supported by observations
+showing that a fraction of early-type galaxies in the local universe
+have undergone recent ($< 1-2$ Gyr old) star formation episodes
+(\citealt{Donas+07}).
 
@@
       formation history within a given bulge... 
+     {\bf AG this section needs to be finished...}
     \end{enumerate}

### 2015-04-06 ms.tex
more rounding erros
randome

@@
 = 300, 600, 1200$ km s$^{-1}$ spanning a physically plausible range of
-thermally stable {\bf AG phrasing ok?} heating rates.  Although we are
+thermally stable heating rates.  Although we are
 interested in the steady-state inflow/outflow solution (assuming one
@@
 \zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
-core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ {\bf
-AG: this is the second time I have caught this, is there any
-particular reason you think this should be +0.2 not -0.2} which
+core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which
 follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
 correlation derived from the results of \citet{LauerFaber+:2007a}.
-{\bf BDM: check this}
 
@@
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
-temperature $T(r)$, and radial velocity $|v(r)|$ (expressed in units
-of the sound speed), for the cusp ($\Gamma=0.8$) solutions within our
+temperature $T(r)$, and radial velocity $|v(r)|/c_s$, for the cusp ($\Gamma=0.8$) solutions within our
 grid.  As expected, the gas density increases towards the SMBH
@@
     galaxies in our sample as a function of the stellar wind heating
-    parameter $\zeta \equiv \sqrt{v_w^{2} + \sigma_0^{2}}/\sigma_0$.
+    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.
     Green, orange, and blue symbols correspond to different values of
@@
     (\ref{eq:rs2main}), with solid and dashed curves calculated for
-    parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
-    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
+    parameters $(\Gamma=0.8, \densSlope\simeq1)$ and
+    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. }
 \end{figure}
@@
 
-Type Ia SNe represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
+Type Ia SNe represent a source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
 If each SN Ia injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SN rate per stellar mass is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
@@
   \begin{cases}
-    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    7\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56}  & {\rm core}\\
-    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    14\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} &{\rm cusp}\\
@@
  \begin{cases}
-    8\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    7\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}  & {\rm core}\\
-    17\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
+    14\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
      Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74} &{\rm cusp}\\
@@
 \end{align}
-Equation (\ref{eq:rIars}) shows that SN Ia can only be approximated as a steady heating source near the stagnation radius for
-extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or for a very young stellar population ($\tau_{\star} \ll t_{\rm h}$).
+Equation (\ref{eq:rIars}) shows that SN Ia can only be approximated as
+a steady heating source near the stagnation radius for extremely
+massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or for a very
+young stellar population ($\tau_{\star} \ll t_{\rm h}$).
 

### 2015-04-06 ms.tex
randome2

@@
 Fig.~\ref{fig:vwSourcesImp}.  Compton heating is neglected in
-calculating thermal stability because unlike local stellar feedback
+calculating thermal stability because, unlike local stellar feedback
 mechanisms, SMBH feedback may not be capable of truly stabilizing the
@@
 black hole mass.  The younger stellar populations characterizing galaxies
-with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar wind, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.
-Only for the most massive galaxies, with $\Mbh\gsim 3\times 10^{8} \Msun$, does the lack
+with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar winds, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.  Only for $\Mbh\gsim 3\times 10^{8} \Msun$ does the lack
 of young stellar populations significantly reduce the role of stellar
 wind heating.
-But for these massive galaxies, Ia heating contributes a comparable level of heating $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$.
-However, for low mass galaxies Ia heating does not contribute to the total heating rate because the Ia radius exceeds the nominal stagnation radius (bottom panel).
-Finall, MSP and Compton heating is found to be negligible for all black hole masses.
-Strikingly, {\it we find that galactic nuclei experiencing the same
-  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses}.  
-We must caveat, however, that for high $M_{\bullet}$ the total effective wind velocity is only a factor of 2-3 times higher than the stellar velocity dispersion ($\zeta \sim \zeta_c$), such that thermal stability is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
+But for these massive galaxies, that Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (for low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+Strikingly, we find that galactic nuclei experiencing the same
+  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses.
+
+An important caveat, however, is that $\vw$ is only a few times higher than the stellar velocity dispersion, i.e.
+$\zeta \sim \zeta_c$.
+This implies that the true stagnation radius could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
 
 Realistic variations (``burstiness") in the star formation history
-will also often result in lower heating rates (Appendix
+will also often produce lower stellar wind heating rates (Appendix
 \ref{app:windheat}).  Figure \ref{fig:NickPlot2} shows the heating

### 2015-04-06 ms.tex
changed soi=> inf

@@
 \newcommand{\phirs}{\frac{G \Menc}{\rs}}
-\newcommand{\soi}{\rm soi}
+\newcommand{\soi}{\rm inf}
 \newcommand{\rsoi}{r_{\soi}}
@@
 $r_{s}$ & stagnation radius (where gas radial velocity goes to zero) \\
-$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
+$r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
@@
 \end{align}
-where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (soi), 
+where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (inf), 
 \begin{equation}
@@
 Equation (\ref{eq:mdot_gas}) closely resembles the Bondi formula (eq.~[\ref{eq:bondi}]) provided that $r_{\rm B}$ is replaced by $\rs$.
-Indeed, for $r_{s} < r_{\rm soi}$ we have that (eq.~[\ref{eq:stag_simple}])
+Indeed, for $r_{s} < r_{\rm inf}$ we have that (eq.~[\ref{eq:stag_simple}])
 \begin{align}
@@
 \begin{eqnarray}
-  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
+  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm inf}^{3}}\left(\frac{r_{\rm s}}{r_{\rm inf}}\right)^{-1-\Gamma} \nonumber \\
  &\approx& \begin{cases}
@@
    260 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
-\approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
+\approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
   \end{cases}
@@
 \zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
-core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ which
+core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
 follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
@@
   \begin{align}
-    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
+    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm inf}}\sim \frac{V_{\phi}}{\sigma},
   \end{align}
@@
 \begin{equation}
-\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
+\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm inf}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
 \label{eq:rcirc}
 \end{equation}
-where we have used the definition $r_{\rm soi} \equiv
+where we have used the definition $r_{\rm inf} \equiv
 GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed
-that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied
+that $r_{\rm s} \lesssim r_{\rm inf}$, a condition which is satisfied
 for the thermally-stable solutions of interest.
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
   {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
@@
 Figure~\ref{fig:stag} shows our calculation of the stagnation radius
-$r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
+$r_{\rm s}/r_{\rm inf}$ as a function of the wind heating parameter
 $\zeta = \sqrt{1+(v_w/\sigma_0)^{2}}$, with different colors
@@
 the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
-\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
+\lesssim r_{\rm inf}$).  However, for sufficiently low heating the
 stagnation radius diverges above the analytic estimate, approaching
-the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
+the stellar break radius $r_b \gg r_{\rm inf}$.  This divergence
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
@@
   \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
-    sphere of influence radius $r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]) for
+    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
     galaxies in our sample as a function of the stellar wind heating
@@
 \begin{eqnarray}
-\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{r_{\rm Ia}}{r_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{r_{\rm Ia}}{r_{\rm inf}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
-M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
+M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
 If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
@@
 given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with
-$\alpha = -0.2$ (see also \citep{Zhang+09, Pellegrini10, Gallo+10}).
+$\alpha = -0.2$ (see also \citealt{Zhang+09, Pellegrini10, Gallo+10}).
 Also shown are the maximum accretion rates, respectively, for

### 2015-04-06 ms.tex
6.3

@@
 X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
-represents a maximum value, since it does not account for suppression
+represents a maximum value, which does not for instance account for suppression
 of the SMBH accretion rate due to outflows from the accretion disk on
-small radial scales (e.g., \citealt{Blandford&Begelman99}).  If the
-actual radiative efficiency is lower than our fiducial assumption,
+small radial scales (e.g., \citealt{Blandford&Begelman99}).
+Furthermore, our SFH-averaged accretion rates are derived using analytic expressions for the stagnation radius that may underpredict the true accretion rate if $\zeta < \zeta_c$, as may occur in massive core galaxies with large break radii.
+If the actual radiative efficiency is lower than our fiducial assumption,
 then many of the X-ray detections would lie above the predicted value
 of $\langle L_X \rangle$ for stable accretion (black line).  In this
-case the X-ray detected galaxies either experience less heating than
-average galaxies of the same mass, or they are not accreting stably at
-all.  {\bf BDM: we may need to remove - why did this change so much?}
-Indeed, for $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$ nearly
-exceeds that predicted for the maximum thermally-stable accretion
-rate, $\dot{M}_{\rm TI}$ (yellow line).  Since the \citet{Miller+15}
-sample includes only early-type galaxies with older stellar
-populations than the average for their black hole mass, it would not
-be too surprising if many of these galaxies were thermally unstable.
+case the X-ray detected galaxies experience less heating than
+average galaxies of the same mass, and may not be stably accreting at
+all.  This is particularly plausible because the \citet{Miller+15} sample includes only early-type galaxies, with older stellar
+populations than the average for their black hole mass.
 
@@
   C} > \dot{M}_{\rm TI}$ across all black hole masses.  Thus, even if
-Compton heating could act to stabilize the flow (which, as already
-mentioned, is unlikely), for fiducial parameters it is insufficient to
-produce a thermally stable accretion rate given conditions
-corresponding to the average star formation history.  When thermal
-instabilities become manifest, nuclear gas may undergo cyclic
+Compton heating could act to self-stabilize the flow (which, as already
+mentioned, appears unlikely), its magnitude appears to be insufficient to
+produce a thermally stable accretion rate even given conditions
+corresponding to the average star formation history.
+
+If prsent, thermal
+instabilities may cause the CNM to undergo cyclic
 oscillations of rapid cooling and high accretion rates, followed by
@@
 elliptical galaxies on large scales and long timescales
-(\citealt{Ciotti+10}), an idea which is supported by observations
+(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes observations
 showing that a fraction of early-type galaxies in the local universe
@@
 range of inflow rates experienced over the course of a cyclic episode
-between instabilities and periodic nuclear outbursts.  Due to their
-deeper potential well on scales of the sphere of influence, core galaxies are more likely to possess higher accretion rates and
-potentially be thermally unstable for a fixed wind heating rate than
-cusp galaxies.
+between instabilities and periodic nuclear outbursts.
+
+% Due to their
+%deeper potential well on scales of the sphere of influence, core galaxies are more likely to possess higher accretion rates and
+%potentially be thermally unstable for a fixed wind heating rate than
+%cusp galaxies.
 
@@
 If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$ in Fig
-\ref{fig:miller} are indeed in a state of thermally-unstable cyclic behavior, then a subset of the galaxies with X-ray upper limits may contribute to a separate steady-state, thermally stable population, for instance including SgrA* (which has a much lower X-ray luminosity for its black hole mass than predicted by the \citet{Miller+15} trend).
-One consequence of a potentially bimodal population of steady and cyclic galactic nuclei calls into question the physical justification of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass galaxies.
+\ref{fig:miller} are indeed in a state of thermally-unstable cyclic behavior, then a subset of the galaxies with X-ray upper limits may contribute to a separate population of thermally stable, steadily accreting nuclei.
+Such a population could include SgrA*, which has a much lower X-ray luminosity for its black hole mass than predicted by the \citet{Miller+15} trend.
+A potentially bimodal population of steady and cyclic galactic nuclei calls into question the physical justification of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass galaxies.
 
@@
 time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
-shown in the top panel.  For black holes accreting steadily given the
+shown in the top panel.  For black holes accreting steadily at the rate set by the
 stellar wind heating associated with the average star formation
-history of their galaxies, we see that $t_{\rm grow}$ exceeds the
-Hubble time by 1$-$3 orders of magnitude across all black hole masses.
+history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
+Hubble time by 2$-$3 orders of magnitude across all black hole masses.
 Steady accretion therefore cannot explain the growth of low mass black

### 2015-04-06 ms.tex
6.6

@@
 
-Low-mass AGN in the local universe ($M_{\bullet} \lesssim 3\times
-10^{7}M_{\odot}$) are observed to be growing on a timescale comparable
+Low-mass AGN in the local universe with $M_{\bullet} \lesssim 3\times
+10^{7}M_{\odot}$ are observed to be growing on a timescale comparable
 to the age of the universe, while the most massive SMBHs with
@@
 The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
-time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
-shown in the top panel.  For black holes accreting steadily at the rate set by the
-stellar wind heating associated with the average star formation
+time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion rate
+shown in the top panel.  For SMBHs which accrete steadily at the rate set by the
+stellar wind heating due to the average star formation
 history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
-Hubble time by 2$-$3 orders of magnitude across all black hole masses.
+Hubble time by 2$-$3 orders of magnitude across all $M_{\bullet}$.
 Steady accretion therefore cannot explain the growth of low mass black
@@
 holes is dominated by young stellar bulges which have a log normal
-distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
+distribution of Eddington ratios peaked at $\Mdot/\dot{M}_{\rm edd} \sim
 0.01$. That this distribution is insensitive to galaxy properties
@@
 That the growth time associated with thermally-unstable accretion
-(yellow line) exceeds the Hubble time across all SMBH masses
+(yellow line in Fig.~\ref{fig:bh_growth}) exceeds the Hubble time across all SMBH masses
 highlights the fact that significant black hole growth in the local
@@
 relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
-10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
+10^{7}M_{\odot}$, such as that responsible for powering the transient {\it Swift}
 J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
@@
 Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).
-Such compact star clusters could greatly enhance the rate of TDEs (e.g.~\citealt{Stone&Metzger15}), making this association uncoincidental.
+The high stellar densities of such a compact star cluster could greatly enhance the TDE rate (e.g.~\citealt{Stone&Metzger15}), possibly making this association uncoincidental.
 
@@
 
-\subsection{Regulation by Kinetic Outflow Feedback}
+\subsection{Regulation by SMBH Kinetic Feedback}
 \label{sec:kinetic}
 
-Our analysis of black hole feedback has focused on Compton heating
-instead of kinetic feedback, since the efficacy of radiative feedback
-is relatively straightforward to calculate given the properties of the
-accretion flow.  However, if kinetic feedback instead dominates, this
-could play an important role in regulating the accretion.  Our simple
-parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an
+Our analysis of SMBH feedback has focused on Compton heating
+instead of kinetic feedback, since the effects of radiative feedback
+are relatively straightforward to calculate from the properties of the
+accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion.  Our simple
+parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assuming heating which is volumetrically uniform predicts an
 effectic wind velocity which increases with SMBH mass as
@@
 M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass};
-eq.~[\ref{eq:eddr_analytic}]), kinetic feedback of the form we have
+eq.~[\ref{eq:eddr_analytic}]), a dominant source of kinetic feedback of the form we have
 adopted leads to an Eddington ratio dependence on SMBH mass of
@@
 
-This prediction is in better with the observed dependence of $\langle
+This prediction is also consistent with the observed dependence of $\langle
 L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies

### 2015-04-06 ms.tex
putting heating/cooling in Ia limit.

--- 2015-04-06 ms.tex
@@
 \newcommand{\phirs}{\frac{G \Menc}{\rs}}
-\newcommand{\soi}{\rm inf}
+\newcommand{\soi}{\rm soi}
 \newcommand{\rsoi}{r_{\soi}}
@@
 $r_{s}$ & stagnation radius (where gas radial velocity goes to zero) \\
-$r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
+$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
@@
 \end{align}
-where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (inf), 
+where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (soi), 
 \begin{equation}
@@
 = 300, 600, 1200$ km s$^{-1}$ spanning a physically plausible range of
-thermally stable heating rates.  Although we are
+thermally stable {\bf AG phrasing ok?} heating rates.  Although we are
 interested in the steady-state inflow/outflow solution (assuming one
@@
 Equation (\ref{eq:mdot_gas}) closely resembles the Bondi formula (eq.~[\ref{eq:bondi}]) provided that $r_{\rm B}$ is replaced by $\rs$.
-Indeed, for $r_{s} < r_{\rm inf}$ we have that (eq.~[\ref{eq:stag_simple}])
+Indeed, for $r_{s} < r_{\rm soi}$ we have that (eq.~[\ref{eq:stag_simple}])
 \begin{align}
@@
 \begin{eqnarray}
-  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm inf}^{3}}\left(\frac{r_{\rm s}}{r_{\rm inf}}\right)^{-1-\Gamma} \nonumber \\
+  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
  &\approx& \begin{cases}
@@
    260 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
-\approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
+\approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
   \end{cases}
@@
 \zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
-core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
+core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ {\bf
+AG: this is the second time I have caught this, is there any
+particular reason you think this should be +0.2 not -0.2} which
 follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
 correlation derived from the results of \citet{LauerFaber+:2007a}.
+{\bf BDM: check this}
 
@@
   \begin{align}
-    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm inf}}\sim \frac{V_{\phi}}{\sigma},
+    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
   \end{align}
@@
 \begin{equation}
-\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm inf}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
+\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
 \label{eq:rcirc}
 \end{equation}
-where we have used the definition $r_{\rm inf} \equiv
+where we have used the definition $r_{\rm soi} \equiv
 GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed
-that $r_{\rm s} \lesssim r_{\rm inf}$, a condition which is satisfied
+that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied
 for the thermally-stable solutions of interest.
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
   {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
@@
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
-temperature $T(r)$, and radial velocity $|v(r)|/c_s$, for the cusp ($\Gamma=0.8$) solutions within our
+temperature $T(r)$, and radial velocity $|v(r)|$ (expressed in units
+of the sound speed), for the cusp ($\Gamma=0.8$) solutions within our
 grid.  As expected, the gas density increases towards the SMBH
@@
 Figure~\ref{fig:stag} shows our calculation of the stagnation radius
-$r_{\rm s}/r_{\rm inf}$ as a function of the wind heating parameter
+$r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
 $\zeta = \sqrt{1+(v_w/\sigma_0)^{2}}$, with different colors
@@
 the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
-\lesssim r_{\rm inf}$).  However, for sufficiently low heating the
+\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
 stagnation radius diverges above the analytic estimate, approaching
-the stellar break radius $r_b \gg r_{\rm inf}$.  This divergence
+the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
@@
   \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
-    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
+    sphere of influence radius $r_{\rm soi}$ (eq.~[\ref{eq:rsoi}]) for
     galaxies in our sample as a function of the stellar wind heating
-    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.
+    parameter $\zeta \equiv \sqrt{v_w^{2} + \sigma_0^{2}}/\sigma_0$.
     Green, orange, and blue symbols correspond to different values of
@@
     (\ref{eq:rs2main}), with solid and dashed curves calculated for
-    parameters $(\Gamma=0.8, \densSlope\simeq1)$ and
-    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. }
+    parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
+    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
 \end{figure}
@@
 
-In addition to our standard set of solutions which neglect thermal conduction and radiative cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the flow (e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$).
-However, for solutions which are marginally stable (e.g., $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), the inclusion of radiative acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater amount.
-We ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02, 0.2, 0.6$, spanning the physical range.
-Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}.
-By contrast, changes due to the inclusion of thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, although conduction is seen to offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+In addition to our standard set of solutions which neglect thermal
+conduction and radiative cooling, we explore a few test simulations
+including these effects, as marked by dagger symbols in Table
+\ref{table:models}.  For solutions which are far from being thermally
+unstable when cooling is neglected (e.g., $M_{\bullet} =
+10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
+0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including
+radiative cooling has little effect on the key properties of the flow
+(e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$).  However, for solutions which are
+marginally stable (e.g., $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim
+$few), the inclusion of radiative acts to decrease the value of
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater amount.  We ran
+solutions with radiative cooling for all cusp galaxies with $v_w=300$
+km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each
+for three different values of the mass input parameter $\eta = 0.02,
+0.2, 0.6$, spanning the physical range.  Solutions found to be
+unstable for all values of $\eta$ are marked in boldface as ``TI" in
+Table \ref{table:models}.  By contrast, changes due to the inclusion
+of thermal conduction are always minor for our choice of the
+saturation parameter $\phi = 0.1$, although conduction is seen to
+offset the effects of radiative cooling, making the flow more
+thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
 
@@
 
-Type Ia SNe represent a source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each SN Ia injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SN rate per stellar mass is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
-E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
+Type Ia SNe represent a potentially important source of heating, which
+unlike core collapse SNe is present even in an evolved stellar
+population.  If each SN Ia injects thermal energy $E_{\rm Ia}$ into
+the interstellar medium, and the SN rate per stellar mass is given by
+$R_{\rm Ia}$, then the resulting volumetric heating rate of $E_{\rm
+  Ia}R_{\rm Ia}$ produces an effective heating parameter
+(eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2
+      t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
 \end{align} The thermal energy injected by each SN Ia, $E_{\rm Ia} \simeq
@@
 
-The SN Ia rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.
-In
-the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
-approximate functional form \begin{align}
-  R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm
-      h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
+The SN Ia rate, $\RateIa$, depends on the age of the stellar
+population, as it represent the convolution of the star formation rate
+and the Ia delay time distribution (DTD) divided by the present
+stellar mass.  In the limit of impulsive star formation, $\RateIa$ is
+the DTD evaluated at the time since the star formation episode.  The
+observationally-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a})
+has the approximate functional form \begin{align} R_{\rm Ia}
+  =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm h}\right)^{-1.12}
+  M_{\odot}^{-1}\,{\rm yr^{-1}}
 \label{eq:DTD}
@@
 
-However, even if SN Ia are rare near the stagnation radius, SN Ia may cap the
-SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between successive SNe, stars release a
+However, even if SN Ia are rare near the stagnation radius, SN Ia may
+cap the SMBH accretion rate by periodically blowing gas out of the
+nucleus of low mass galaxies.  Between successive SNe, stars release a
 gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
-interior to the Ia radius, which is locally gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F} 
+interior to the Ia radius, which is locally gravitationally bound to
+the SMBH by an energy $E_{\rm bind} \sim M_{\rm
+  g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F}
 \lesssim$ few.  From the above definitions we find that
-\be
-\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.  
+
+\begin{equation}
+\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm
+    Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.
 \label{eq:blowout}
-\ee
-Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
+\end{equation}
+
+Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm
+  Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from
+radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.  Even when heating is
+sufficiently weak that the stagnation radius formally exceeds $r_{\rm
+  Ia}$, the SMBH accretion rate is still potentially limited to a
+value
 \begin{eqnarray}
-\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{r_{\rm Ia}}{r_{\rm inf}}\right)^{2-\Gamma} \approx \nonumber \\
+\frac{\dot{M}_{\rm Ia}}{\dot{M}_{\rm edd}} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{r_{\rm Ia}}{r_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
  && \begin{cases}
@@
 Ia cannot alone prevent cooling instabilities in the nuclei of low
-mass galaxies {\bf AG--careful one needs a separate criterion for
-  thermal stability when heating is dominated by the Ias}.
+mass galaxies.
 
@@
 
-%Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.
-due to a galaxy merger or to cooling flows developing within the galaxy over much longer timescales (e.g.~\citealt{Ciotti&Ostriker07}).
+If Ia supernovae are the dominant source of heating we expect $\rs\sim
+r_{\rm Ia}$. If the stagnation radius moves inwards from $\rIa$, the
+decreased heating will force it outwards again. If the it moves
+outwards the Ia heating will force it inwards. Thus,
+equations~\eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} will no longer
+be valid as they assume that $\rs$ follows equation
+\eqref{eq:stag_simple}. We derive $\dot{q}_{\rm
+  heat}/\left|\dot{q}_{\rm rad}\right|$ for $\rs=\rIa$ to evaluate
+thermal stability in SNe Ia dominate the heating.
+
+\begin{align}
+&\rho(\rIa)\simeq \frac{3 q(\rIa)}{2-\Gamma} \nonumber\\
+&T(\rIa)\simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v^{\rm Ia \,\,
+    2}_{w}}{2k}\nonumber\\
+&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
+\begin{cases}
+  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
+  \eta_{0.02}^{-2.7} & \text{core}\nonumber\\
+   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
+  \eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
+\end{cases}\\&\simeq
+\begin{cases}
+  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
+  (\tau_{\star}/\th)^{0.5}
+ & \text{core}\\
+   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
+  & \text{cusp}\\
+\end{cases}
+\end{align}
 
 \subsection{Millisecond Pulsars}
- Energy injection from the magnetic braking of millisecond pulsars (MSPs) is a potentially
-important heating source.  If the number of MSPs per unit stellar mass
-is $n_{\rm msp}$ and each contributes on average a spin-down
-luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
-volume $\dot{e} \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
-effective heating rate (eq.~ [\ref{eq:vw_eff}]) of 
+Energy injection from the magnetic braking of millisecond pulsars
+(MSPs) is a potentially important heating source.  If the number of
+MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes on
+average a spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting
+heating per unit volume $\dot{e} \approx \bar{L}_{\rm sd}n_{\rm
+  msp}\epsilon_{\rm msp}$ results in an effective heating rate (eq.~
+[\ref{eq:vw_eff}]) of
 \begin{eqnarray} v_{w}^{\rm MSP} \sim
@@
 where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
-M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
+M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
 If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
@@
 Fig.~\ref{fig:vwSourcesImp}.  Compton heating is neglected in
-calculating thermal stability because, unlike local stellar feedback
+calculating thermal stability because unlike local stellar feedback
 mechanisms, SMBH feedback may not be capable of truly stabilizing the
@@
 black hole mass.  The younger stellar populations characterizing galaxies
-with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar winds, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.  Only for $\Mbh\gsim 3\times 10^{8} \Msun$ does the lack
+with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar wind, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.
+Only for the most massive galaxies, with $\Mbh\gsim 3\times 10^{8} \Msun$, does the lack
 of young stellar populations significantly reduce the role of stellar
 wind heating.
-But for these massive galaxies, that Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (for low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
-Strikingly, we find that galactic nuclei experiencing the same
-  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses.
-
-An important caveat, however, is that $\vw$ is only a few times higher than the stellar velocity dispersion, i.e.
-$\zeta \sim \zeta_c$.
-This implies that the true stagnation radius could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
+But for these massive galaxies, Ia heating contributes a comparable level of heating $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$.
+However, for low mass galaxies Ia heating does not contribute to the total heating rate because the Ia radius exceeds the nominal stagnation radius (bottom panel).
+Finall, MSP and Compton heating is found to be negligible for all black hole masses.
+Strikingly, {\it we find that galactic nuclei experiencing the same
+  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses}.  
+We must caveat, however, that for high $M_{\bullet}$ the total effective wind velocity is only a factor of 2-3 times higher than the stellar velocity dispersion ($\zeta \sim \zeta_c$), such that thermal stability is marginal, especially for core galaxies ($\S\ref{sec:mdot}$).
 
 Realistic variations (``burstiness") in the star formation history
-will also often produce lower stellar wind heating rates (Appendix
+will also often result in lower heating rates (Appendix
 \ref{app:windheat}).  Figure \ref{fig:NickPlot2} shows the heating
@@
 given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with
-$\alpha = -0.2$ (see also \citealt{Zhang+09, Pellegrini10, Gallo+10}).
+$\alpha = -0.2$ (see also \citep{Zhang+09, Pellegrini10, Gallo+10}).
 Also shown are the maximum accretion rates, respectively, for

### 2015-04-06 be.tex
fixed app b

@@
 \begin{align}
-  r^2 \rho v(\mathcal{B} - \mathcal{B}|_{\rs})= \int_{\rs}^{r}
+  r^2 \rho v\mathcal{B} = \int_{\rs}^{r}
     r^2 \left(\frac{3}{1+\delta}\frac{G
@@
 When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow with positive kinetic energy at infinity.
-However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative; this occurs first near the stagnation radius and then the region where $\mathcal{B} < 0$ grows to larger radii as $\zeta$ is reduced further.
-If $\zeta$ is just less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.
+However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative near the break radius for some value of $\rs$.
+When $\zeta$ is moderately less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$, which increases from 0 when $\zeta = \zeta_c$ to $\sim r_{b}$ as $\zeta$ is decreased well below $\zeta_c$.
 
@@
 \includegraphics[width=\columnwidth]{zetaCrit.pdf}
-\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
-  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ for core ($\Gamma=0.1$)
-  galaxies. If $\zeta<\zeta_c$ outflows are only possible if the ratio
-  of the stagnation radius to the influence radius exceeds a minimum
-  value. Plotted as a function of the ratio of the break radius to the
-  influence radius ($\rb/\rsoi$) {\emph Bottom Panel:} Mininmum value
-  for ratio of the stagnation radius to the break radius, $\rs/\rb$
-  for core galaxies ($\Gamma=0.1$) derived by requiring the Bernoulli
-  parameter of the gas to remain positive out to the break radius
-  $\rb$. This is calculated numerically from
-  equation~\eqref{eq:enthAnal}.}
+\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value $\zeta_c$ of the wind heating parameter
+  $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of the flow $\mathcal{B}$ is positive near the break radius for some value of $\rs$, calculated for core ($\Gamma=0.1$)
+  galaxies using equation~\eqref{eq:enthAnal}..
+{\emph Bottom Panel:} Minimum value of the stagnation radius for which $\mathcal{B} > 0$ at the break radius as a function of $\zeta/\zeta_c < 1$, again calculated for core galaxies ($\Gamma=0.1$).}
 \end{figure}

### 2015-04-06 ms.tex

--- 2015-04-06 ms.tex
@@
 
-Type Ia SNe represent a source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each SN Ia injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SN rate per stellar mass is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
-E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
-\end{align} The thermal energy injected by each SN Ia, $E_{\rm Ia} \simeq
+Type Ia SNe represent a potentially important source of heating, which
+unlike core collapse SNe is present even in an evolved stellar
+population.  If each SN Ia injects thermal energy $E_{\rm Ia}$ into
+the interstellar medium, and the SN rate per stellar mass is given by
+$R_{\rm Ia}$, then the resulting volumetric heating rate of $E_{\rm
+  Ia}R_{\rm Ia}$ produces an effective heating parameter
+(eq.~[\ref{eq:vw_eff}]) of
+
+\begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2
+      t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
+\end{align}
+
+The thermal energy injected by each SN Ia, $E_{\rm Ia} \simeq
 \epsilon_{\rm Ia} 10^{51}$ erg, depends on the efficiency $\epsilon_{\rm Ia}$
@@
 
-However, even if SN Ia are rare near the stagnation radius, SN Ia may cap the
-SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between successive SNe, stars release a
+However, even if SN Ia are rare near the stagnation radius, SN Ia may
+cap the SMBH accretion rate by periodically blowing gas out of the
+nucleus of low mass galaxies.  Between successive SNe, stars release a
 gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
-interior to the Ia radius, which is locally gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F} 
+interior to the Ia radius, which is locally gravitationally bound to
+the SMBH by an energy $E_{\rm bind} \sim M_{\rm
+  g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F}
 \lesssim$ few.  From the above definitions we find that
-\be
-\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.  
+
+\begin{equation}
+\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm
+    Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.
 \label{eq:blowout}
-\ee
-Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
+\end{equation}
+
+Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm
+  Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from
+radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.  Even when heating is
+sufficiently weak that the stagnation radius formally exceeds $r_{\rm
+  Ia}$, the SMBH accretion rate is still potentially limited to a
+value
 \begin{eqnarray}

### 2015-04-06 ms.tex
fixed 6

--- 2015-04-06 ms.tex
@@
 are relatively straightforward to calculate from the properties of the
-accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion.  Our simple
-parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assuming heating which is volumetrically uniform predicts an
-effectic wind velocity which increases with SMBH mass as
+accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion, even in low luminosity AGN.
+
+Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assumes a uniform volumetric heating and predicts an
+effective wind velocity which increases with SMBH mass as
 $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
@@
 L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
-(Fig.~\ref{fig:miller}, green line), hinting that accretion regulation
-by kinetic feedback may serve as an alternative explanation for X-ray
+(Fig.~\ref{fig:miller}, green line), suggesting that accretion regulation
+by kinetic feedback could play a role in determining the X-ray
 luminosities of elliptical galaxies.  However, our assumption that
-kinetic outflows heat the gas uniformly in volume is somewhat
-arbitrary and would need to more rigorously justified by numerical
-studies of how jets or disk outflows couple energy to their gaseous
-environment.  It is furthermore unclear whether our steady-state model
-can be applied at all, because black hole feedback depends on the
-central accretion rate, which (unlike stellar feedback) does not
-respond instantaneously to changes in the thermodynamic properties of
-the gas on larger scales.
+kinetic outflows heat the gas uniformly in volume is rather arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous
+environment.
+As already discussed, it is furthermore unclear whether a steady-state accretion model is at all relevant in the case when SMBH feedback dominates due to the time delay between the small scale accretion flow and the thermodynamic response of the CNM on larger scales.
 

### 2015-04-06 ms.tex
conclusions 1

@@
 Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, and used to address other key questions, such as the thermal stability of their accretion flows.
-Our conclusions may be summarized as follows.
+Our conclusions are summarized as follows.
 
   \begin{enumerate}
-  %Younger population=>higher accretion rate; generally higher eta and
-  %lower vw except for very young stellar populations.
   \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
-    outward wind. In a steady state the gas inflow rate towards the black hole is proportional to the
-    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius is close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
-  \item The location of the stagnation radius, and thus the SMBH accretion rate, is sensitive to the effective heating rate of the gas.
-Stellar wind heating, supernovae, and AGN feedback depend on the SMBH mass as well as the star
-    formation history in the galactic nucleus.
-A recent burst of star formation within the last $\sim 10$ Myr results in mass and energy injection both being dominated by fast stellar winds from young stars ($v_w \sim 1000$ km s$^{-1}$).
-If star formation is instead relegated to the distant past, mass input becomes dominated by old stars while heating is dominated by AGN feedback and supernovae.
-For nuclei with ongoing, continuous star formation, energy input is usually dominated by the youngest stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
-
-Quantitatively $\rs\propto v_w^{-2}$, which implies that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ will increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), gas remains bound to the stellar bulge and cannot flow out (Appendix \ref{app:be}).
-(2) For sufficiently low $v_w$ the gas near the stagnation radius becomes thermally unstable, potentially resulting in cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$; e.g.,\citealt{Ciotti+10}).
+    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
+    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
+  \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.
+Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.
+A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
+Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
+
+Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+However, $\Mdot$ may increase even more rapidly as $v_w$ decreases for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy at infinity (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
 

### 2015-04-06 ms.tex
conclusions 2

@@
 
-\item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
-  \Msun$ with star formation histories matching the average values
-  derived from the cosmological simulations of
-  \citet{MosterNaab+:2013a} possess an effective heating rate $v_w\sim
-  1000$ km s$^{-1}$, relatively independent of SMBH mass
-  (Fig.~\ref{fig:vwSources}).  This results in a prediction for the
-  average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with
-  $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension
-  with the trend of measured nuclear X-ray luminosities of early-type
-  galaxies (e.g., \citealt{Miller+15}), which instead find that
-  $\eddr$ increases towards smaller $\Mbh$.  However, high X-ray
-  radiative efficiencies are required for these galaxies to be
-  consistent with thermally-stable accretion, instead suggesting that
-  (at least at low black hole masses), the possibility of two branches
-  of accretion states.
+\item The nuclei of galaxies with relatively low mass black holes, $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
+  \Msun$, and star formation histories which match their average value derived from the cosmological simulations, receive a stellar wind heating rate $v_w\sim 800$ km s$^{-1}$, relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).
+This predicts an average Eddington ratio that increases weakly with $M_{\bullet}$, in mild tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type
+  galaxies (e.g., \citealt{Miller+15}).
+
+For thermally-stable models, scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude can result from from (1) stochastic variation in star formation history from galaxy to galaxy; (2) Variations in small scale outflow rates due to variations between galactic nuclear angular momenta.
+
+However, only for relatively high X-ray radiative efficiencies do distant galaxies with measured X-ray luminosities accretion rates low enough to be consistent with thermally-stable accretion.
+The possibility that high mass quiescent BHs may in fact occupy a thermally-unstable state is excacerbated by the deep potential wells of these galaxies relative to the wind heating.
+If the current sample , this may suggest a separate "thermally stable" branch (at least for low mass BHs).
+t
 

### 2015-04-06 ms.tex
conclusions 3

--- 2015-04-06 ms.tex
@@
 Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ may increase even more rapidly as $v_w$ decreases for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy at infinity (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
-
-\item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
-  \Msun$ with star formation histories matching the average values
-  derived from the cosmological simulations of
-  \citet{MosterNaab+:2013a} possess an effective heating rate $v_w\sim
-  1000$ km s$^{-1}$, relatively independent of SMBH mass
-  (Fig.~\ref{fig:vwSources}).  This results in a prediction for the
-  average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with
-  $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension
-  with the trend of measured nuclear X-ray luminosities of early-type
-  galaxies (e.g., \citealt{Miller+15}), which instead find that
-  $\eddr$ increases towards smaller $\Mbh$.  However, high X-ray
-  radiative efficiencies are required for these galaxies to be
-  consistent with thermally-stable accretion, instead suggesting that
-  (at least at low black hole masses), the possibility of two branches
-  of accretion states.
-
-    % However, it is important to note that the inflow rate on large
-    % scales (which we calculate) may differ from
-    % the actual accretion rate as outflows could occur on small
-    % scales. The outflow rate would depend on the angular momentum of
-    % the infalling gas and thus the angular momentum of stars in the
-    % nucleus. The in turn would vary systematically with $\Mbh$.
-
-    For $\Mbh\gsim 10^8 \Msun$, the flow from stellar winds onto the
-    BH is more susceptible to thermal instability due to the lower
-    effective wind velocity $v_w$. 
-  \item We expect scatter in nuclear x-ray luminosities at
-    fixed $\Mbh$ from (1) stochastic variation in star formation
-    history from galaxy to galaxy (2) Variations in small scale outflow
-    rates due to variations between galactic nuclear angular
-    momenta. {\bf AG: some more explanation of why 1 might not show up
-    in Pellegrini...}
-    These variations alone could explain much of the 2-4 orders of
-    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
-    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.
-
-    It is also possible that many of the galaxies in the
-    \citet{Miller+15} are accreting in a non-steady fashion and this
-    scatter arises from cyclic variation in accretion rate. In fact it
-    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
-    \Msun$ coexists with a population of smaller, steadily accreting
-    black holes (e.g. the upper limits in \citet{Miller+15}).  This
-    calls into question the use of simple extrapolations of power-law
-    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
-    to constrain the occupation fraction of black holes in low mass
-    galaxies (\citealt{Miller+15}).
-  \item Low mass AGN have growth times comparable to the Hubble time
-    (\citet{Heckman+04}). We have shown that this would require accretion
-    rates not consistent with steady-state thermally stable accretion
-    of stellar wind material, and is driven by an external supply of gas.
+However, $\Mdot$ may increase even more rapidly as $v_w$ decreases for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
+
+\item The nuclei of galaxies with low mass black holes $\Mbh \lesssim 10^8
+  \Msun$ and star formation histories which match their average value derived from cosmological simulations, receive a stellar wind heating rate $v_w\sim 800$ km s$^{-1}$ which is relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).
+The resulting Eddington ratio is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in moderate tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
+
+For thermally stable accretion models, scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude can result from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
+
+\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value consistent with thermally-stable accretion (Fig.~\ref{fig:miller}).
+High mass SMBHs are particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.
+If the current X-ray sample is instead comprised mainly of thermally unstable nuclei, then a separate branch of low $L_x$ "thermally stable" nuclei may exist, especially at low $M_{\bullet}$.
+Such a dichotomy calls into question the accuracy of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in constraining the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+
+  \item Low mass AGN have growth times comparable to the Hubble time (\citet{Heckman+04}).
+Our results show that this would require accretion rates which are not consistent with steady-state, thermally stable accretion of stellar wind material.
+Low mass black hole growth must instead be driven by an external supply of gas.
   \item We compare the $\Mdot$ for each of our solution to the one

### 2015-04-06 ms.tex
conclusions 4

@@
 
-  \item Low mass AGN have growth times comparable to the Hubble time (\citet{Heckman+04}).
-Our results show that this would require accretion rates which are not consistent with steady-state, thermally stable accretion of stellar wind material.
-Low mass black hole growth must instead be driven by an external supply of gas.
-  \item We compare the $\Mdot$ for each of our solution to the one
-    calculated from the Bondi formula. We find that they agree to
-    within a factor of order unity. This is because in our model the
-    accretion rate is determined by the flow properties at the
-    stagnation radius, $\rs$, which is within a factor of a few of the
-    Bondi radius $\rb$. Thus, use of the Bondi formula is a
-    good approximation.
+  \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).
+This requires accretion rates which are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
+Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplies external to the nuclear region.
+
+%  \item Our calculation of $\Mdot$ agrees well with the one calculated from the Bondi formula. We find that they agree to
+ %   within a factor of order unity. This is because in our model the
+  %  accretion rate is determined by the flow properties at the
+   % stagnation radius, $\rs$, which is within a factor of a few of the
+    %Bondi radius $\rb$. Thus, use of the Bondi formula is a
+    %good approximation.
+
 \end{enumerate}

### 2015-04-06 ms.tex
conclusions 5

@@
     outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
-    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
+    stellar mass enclosed inside of $\rs$.
+In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]).
+In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetac}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$.
+
+\item The inclusion of thermal conduction results in only moderate changes to the key properties of the flow (e.g.
+stagnation radius, mass accretion rate, and thermal stability) for causal values of the saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
+
   \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.
@@
 
+\section*{Acknowledgments}
+We acknowledge helpful conversations with Jerry Ostriker, Eliot Quataert, ....
+BDM gratefully acknowledges support from NASA {\it Fermi} grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P.
+Sloan Foundation.
+
   \clearpage

### 2015-04-06 windheat.tex
fixing the wind heating appendix.

@@
 
-{\bf AG: Go back to the old mass loss prescription ASAP so that we don't
-  violate mass conservation!}
 The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on
-the generalization of Reimer's law given in
-\citet{SchroderCuntz:2005a} (their eq.~[4]) as
+the generalization of Reimer's law
 \begin{align}
-  \dot{m}=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
-  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
-  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
+  \dot{m}=4 \times 10^{-13} \frac{L_* R_*}{\Mstar} \Msun \pyear,\
 \end{align}
@@
 \end{align}
-The wind velocity of main sequence winds is assumed
-to equal $v_w (\Mstar, t) = v_{w,\odot}(M_{\star}/M_{\odot})^{1/2}(R_{\star}/R_{\odot})^{-1/2}$, i.e.~scaling as the stellar escape velocity and normalized to the velocity of the solar wind $v_{w,\odot} = 430$ km s$^{-1}$; this produces an effective wind heating velocity for main
-sequence winds alone of $\sim 100$ km s$^{-1}$ for $\tau_{\star} \sim t_{\rm h}$, close to the value found by \citet{NaimanSoares-Furtado+:2013a} for globular clusters based on a more
-sophisticated population synthesis treatment.
+The wind velocity of main sequence winds is assumed to equal $v_w
+(\Mstar, t) =
+v_{w,\odot}(M_{\star}/M_{\odot})^{1/2}(R_{\star}/R_{\odot})^{-1/2}$,
+i.e.~scaling as the stellar escape velocity and normalized to the
+velocity of the solar wind $v_{w,\odot} = 430$ km s$^{-1}$; this
+produces an effective wind heating velocity for main sequence winds
+alone of $\sim 100$ km s$^{-1}$ for $\tau_{\star} \sim t_{\rm h}$,
+close to the value found by \citet{NaimanSoares-Furtado+:2013a} for
+globular clusters based on a more sophisticated population synthesis
+treatment.
 
-The rate of energy input from PMS winds, $\dot{e}_{\rm TO}(t) = f_{8}\dot{\mathcal{E}}/\bar{m}_*$, is dominated by fast Wolf-Rayet winds and core-collapse supernovae from massive stars ($M_{\star} > 8M_{\odot}$), where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the stellar mass with $M_{\star} > 8M_{\odot}$ for our assumed Salpeter IMF.
-Here $\dot{\mathcal{E}} (t)$ is the energy injection rate per massive star, which we estimate as
+The rate of energy input from PMS winds, $\dot{e}_{\rm TO}(t) =
+f_{8}\dot{\mathcal{E}}/\bar{m}_*$, is dominated by fast Wolf-Rayet
+winds and core-collapse supernovae from massive stars ($M_{\star} >
+8M_{\odot}$), where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the
+stellar mass with $M_{\star} > 8M_{\odot}$ for our assumed Salpeter
+IMF.  Here $\dot{\mathcal{E}} (t)$ is the energy injection rate per
+massive star, which we estimate as
 \begin{align}
@@
   1 & t<4 \times 10^6 {\rm yr}\\
-  \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} & t \ge 4 \times 10^6 {\rm yr},
+  \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} &  4\times
+  10^{6} {\rm yr}  \le t \le 10^{8} {\rm yr}
+  \times 10^6 {\rm yr},\\
+  0 & t > 10^8 {\rm yr}
 \end{cases}
@@
 \end{align}
-based on the results of \citet{VossDiehl+:2009a} (their Fig.~7, top panel), who use a population synthesis code to simulate the mass and energy injection into the ISM from an OB association.
-Although equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr, in practice the precise functional form of $\dot{e}_{\rm TO}(t)$ is generally unimportant for our purposes, so we adopt equation~\eqref{eq:voss} as being valid for all times.
+based on the results of \citet{VossDiehl+:2009a} (their Fig.~7, top
+panel), who use a population synthesis code to simulate the mass and
+energy injection into the ISM from an OB association.  Although
+equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr, in
+practice the precise functional form of $\dot{e}_{\rm TO}(t)$ is
+generally unimportant for our purposes, so we adopt
+equation~\eqref{eq:voss} as being valid for all times.
 
-The effective wind velocity in the limit of an impulsive star formation may then be written
-as 
+The effective wind velocity in the limit of an impulsive star
+formation may then be written as
 \begin{align}
@@
   10^7~{\rm yr}$ for which young stars can dominate the heating
-  budget.
+  budget.  The mass of stars accreted for halo masses, $M_{\rm halo}< 3
+  \times 10^{12} \Msun$, and redshifts, $z>4$, is small and is neglected.
 
-To find the total mass ($\Mdot'(t)$) and energy
-  ($\dot{E}'(t)$) injection rates, including the contribution of
-  accreted stars, we add a convolution of the specific mass and
-  injection rates with the accretion history $A(t)$ to the mass and
-  energy injection rates from star formed in-situ.  Thus,
+  To find the total mass ($\Mdot'(t)$) and energy ($\dot{E}'(t)$)
+  injection rates, including the contribution of accreted stars, we
+  add a convolution of the specific mass and injection rates with the
+  accretion history $A(t)$ to the mass and energy injection rates from
+  star formed in-situ.  Thus,
 

### 2015-04-07 ms.tex
conclusions 6
marking out solutions which are unstable for some values of eta.

@@
   {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
-  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\
+  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm
+          rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Unstable
+  $\eta$'s  \\
   ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
 ... & 1200 & -- & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
-$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 \\
-... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 \\
+$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
+... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
 % ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
@@
 ... & 1200 & 100 & $ 2.0 \times 10^{ -2 }$ & $ 6.0 \times 10^{ -6 }$ & $ 2.6 \times 10^{ 4 }$ \\
-$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 \\
-... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 \\
+$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 & 0.6\\
+... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 & 0.6\\
 % ... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
@@
 $    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\
-... & 1200 & 25 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
+... & 1200 & -- & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
 % ... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
 % ... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
-$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\
+$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 & 0.6 \\
 %... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0
@@
 $    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ & $ 1.0 \times 10^{ 2 }$ \\
-... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 \\
+... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 & 0.2, 0.6\\
 ... & 1200 & 25 & $ 8.5 \times 10^{ -2 }$ & $ 6.1 \times 10^{ -6 }$ & $ 8.2 \times 10^{ 3 }$ \\
@@
   included, assuming mass loss parameter $\eta = 0.2$ and conductivity
-  saturation parameter $\phi = 0.1$ (recall that the
-  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$).  Entries for solutions found to be thermally unstable for all values of $\eta > 0.02$ are denoted as {\bf TI}.
+  saturation parameter $\phi = 0.1$ (recall that the conductive heat
+  flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). We ran solutions
+  with radiative cooling for all cusp galaxies with $v_w=300 $ km/s
+  and all core galaxies with $v_w=600 $ km/s with three different
+  values of the mass loss parameter $\eta$: 0.02, 0.2, and 0.6. Any
+  values of $\eta$ for which a solution turned out to be thermally
+  unstable are marked in the ``Unstable $\eta$'s'' column.  Entries
+  for solutions found to be thermally unstable for all values of $\eta
+  > 0.02$ are denoted as {\bf TI}.
 \end{tablenotes}
@@
 
+\item Radiative cooling has a more pronounced influence on the structure of the gas flow.
+The approximate condition for cooling instabilities develop is that the rate of radiative cooling exceed the external heating rate at the stagnation radius.
+
   \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.

### 2015-04-07 ms.tex
caption...
figure

@@
 
-We fix $\beta = 2$ (a typical value) because our results are generally
-not sensitive to the properties of the gas flow on radial scales
-$\gtrsim r_b$. The presence of the break radius $r_{b}$ is, however,
-necessary to obtain a converged steady state for some regions of our
-parameter space.  We consider solutions calculated for up to four
-values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
-range of break radii from the \citet{LauerFaber+:2007a}
+We fix $\beta = 2$ (a typical value ${\bf AG beta=1.5 may be more
+  typical...but it still may not matter...}$) because our results are
+generally not sensitive to the properties of the gas flow on radial
+scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
+however, necessary to obtain a converged steady state for some regions
+of our parameter space.  We consider solutions calculated for up to
+four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by
+the range of break radii from the \citet{LauerFaber+:2007a}
 sample.\footnote{For the core galaxies the break radius follows the
@@
   \includegraphics[width=\columnwidth]{mdot_mass.eps}
-  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm edd}$ versus SMBH mass for galaxies in our sample, calculated for different values of the wind heating parameter $\vwO =$ 300 km s$^{-1}$ ({\it green}),
-    600 km s$^{-1}$ ({\it orange}), and 1200 km s$^{-1}$ ({\it blue}).
-    Squares correspond to cusp galaxies ($\Gamma=0.8$), while
-    triangles correspond to cores ($\Gamma$=0.1).
-Solid and dashed curves correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies, respectively.
-}
+  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
+      edd}$ versus SMBH mass for galaxies in our sample, calculated
+    for different values of the wind heating parameter $\vwO =$ 300 km
+    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
+    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
+    ($\Gamma=0.8$), while triangles correspond to cores
+    ($\Gamma$=0.1). Green crosses correspond to cusp solutions which
+    would be thermally unstable.  Solid and dashed curves correspond
+    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
+    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
+    respectively. }
 \end{figure}

### 2015-04-07 ms.tex
putting back Ia h/c

@@
 
+If Ia supernovae are the dominant source of heating we expect $\rs\sim
+r_{\rm Ia}$. If the stagnation radius moves inwards from $\rIa$, the
+decreased heating will force it outwards again. If the it moves
+outwards the Ia heating will force it inwards. Thus,
+equations~\eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} will no longer
+be valid as they assume that $\rs$ follows equation
+\eqref{eq:stag_simple}. We derive $\dot{q}_{\rm
+  heat}/\left|\dot{q}_{\rm rad}\right|$ for $\rs=\rIa$ to evaluate
+thermal stability in SNe Ia dominate the heating.
+
+\begin{align}
+&\rho(\rIa)\simeq \frac{3 q(\rIa)}{2-\Gamma} \nonumber\\
+&T(\rIa)\simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v^{\rm Ia \,\,
+    2}_{w}}{2k}\nonumber\\
+&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
+\begin{cases}
+  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
+  \eta_{0.02}^{-2.7} & \text{core}\nonumber\\
+   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
+  \eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
+\end{cases}\\&\simeq
+\begin{cases}
+  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
+  (\tau_{\star}/\th)^{0.5}
+ & \text{core}\\
+   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
+  & \text{cusp}\\
+\end{cases}
+\end{align}
+
 %Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.

### 2015-04-07 ms.tex
yeti acknowledgement.
more changes

@@
   We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in ``quiescent" galactic nuclei for a range of
+  hot gas in slowly accreting (``quiescent") galactic nuclei for a range of
   central black hole masses $M_{\bullet}$, parameterized gas heating
@@
 rate from stellar and black hole velocity dispersion \\
-$v_{w}$ & total heating parameter, excluding heating rate from
+$v_{w}$ & total heating parameter, excluding minimum heating rate from
 velocity dispersion \\
-$\sigma_0$ & stellar velocity dispersion--assumed to be radially constant.\\
+$\sigma_0$ & stellar velocity dispersion (assumed to be radially constant)\\
 $\zeta$ & heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
-$r_{s}$ & stagnation radius (where gas radial velocity goes to zero) \\
+$r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
 $r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
-$r_{\rm Ia}$ & radius interior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
+$r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
 $\rho_{\star}(r)$ & 3D radial stellar density profile \\
@@
 $M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
-$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
+$q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
 $\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
@@
 profile interior to the break radius \\
-$\delta$ & power-law slope of the 3d stellar density profile inside of
-the break radius. $\delta=\Gamma+1$.\\
+$\delta$ & power-law slope of the 3D stellar density profile inside of
+the break radius, $\delta \equiv \Gamma+1$.\\
 $\dot{M}$ & mass accretion rate  \\
@@
 
-We fix $\beta = 2$ (a typical value ${\bf AG beta=1.5 may be more
-  typical...but it still may not matter...}$) because our results are
+We fix $\beta = 2$ because our results are
 generally not sensitive to the properties of the gas flow on radial
@@
 sources of heating and cooling, its presence leads to thermal
-instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for
+instability (e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be accounted for
 by our 1D time-independent model.  A main goal of this work is to use
@@
 energy.  Condition (\ref{eq:zetacrit}) approximately corresponds to
-the condition that the wind heating parameter be less than the escape
-speed from the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
+the condition that the wind heating parameter be less than the local escape
+speed from near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
     b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
@@
 (eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable
-(\citealt{McCourt+12} and references therein), potentially resulting
-in the formation of a multi-phase medium and enhanced star formation.
+(e.g., \citealt{McCourt+12}, \citealt{Li&Bryan14a}), potentially resulting
+in the formation of a multi-phase medium and enhanced star formation (\citealt{Li&Bryan14b}).
 Even if the hot plasma of the CNM does not condense into cold clouds,
@@
 \eqref{eq:rhostarrs}.  \citet{McCourt+12} argue cooling instability
-develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$,
+develops in a hydrostatic atmosphere if $t_{\rm cool} \lesssim 10 t_{\rm ff}$,
 so equation (\ref{eq:cooling2}) represents a good proxy for
-instability in this case as well.
+instability in this case as well (see also \citealt{Li&Bryan14a}, \citealt{Li&Bryan14b}).
 
@@
 the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
-\lesssim r_{\rm inf}$).  However, for sufficiently low heating the
+\lesssim r_{\rm inf}$).  However, for low heating the
 stagnation radius diverges above the analytic estimate, approaching
@@
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
-\ref{app:be} is shown to coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius.
-This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.
-This dependence explains the behavior of the two core galaxies, shown as
-orange triangles vertically aligned at the same value of
-$\zeta$; the solutions correspond to the same black hole mass
-($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but are calculated assuming
-different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
+This divergence of the stagnation radius to large radii occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii, explaining the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange triangles.
+These solutions correspond to the same black hole mass
+($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break radii of $r_{b} =$ 25, 50 pc (from top to
 bottom).
@@
 can be less than unity, depending on the wind mass loss parameter
-$\eta$.  At the stagnation radius, the ratio $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor
-of two of its minimum across the entire grid; thus, the value of
-$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a
-diagnostic of thermal instability for the entire solution.
+$\eta$.  Because at the stagnation radius $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$ reaches within a factor
+of two of its minimum across the entire grid, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be taken as diagnostic of thermal instability at all radii.
 
@@
 
-In addition to our standard set of solutions which neglect thermal conduction and radiative cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the flow (e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$).
-However, for solutions which are marginally stable (e.g., $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), the inclusion of radiative acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater amount.
-We ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02, 0.2, 0.6$, spanning the physical range.
-Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}.
-By contrast, changes due to the inclusion of thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, although conduction is seen to offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
-
-\section{Sources of Heating}
+In addition to our solutions which neglect thermal conduction and radiative cooling, we explore a smaller set of simulations including these effects explicitly, as marked by dagger symbols in Table \ref{table:models}.
+For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
+However, for solutions which are already marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
+We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
+Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}, with the unstable values of $\eta$ provided in the final column.
+In contrast, changes in the solution when thermal conduction was included were always found to be minor for our choice of the saturation parameter $\phi = 0.1$.
+Conduction does, however, offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+
+\section{Heating Sources}
 \label{sec:heating}
@@
 \section*{Acknowledgments}
-We acknowledge helpful conversations with Jerry Ostriker, Eliot Quataert, ....
-BDM gratefully acknowledges support from NASA {\it Fermi} grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P.
-Sloan Foundation.
+We acknowledge helpful conversations with Jerry Ostriker, Eliot
+Quataert, .... This work relied on Columbia University's Yeti compute
+cluster,and we acknowledge the Columbia HPC support staff for
+assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
+grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
+Foundation.
 

### 2015-04-07 ms.tex
fixed Ia radius

@@
 stagnation radius, as can be derived using the equality
-
 \begin{align}
@@
 \ee
-Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Hence, for low mass BHs with $\sigma_0 \ll v^{\rm Ia}_{w}$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
 Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
@@
 for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$
-(eq.~[$\ref{eq:eddr_analytic}$]).  Note, however, that for low mass
-SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
-for a thermally stable flow $\dot{M}_{\rm TI}$
-(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
-Ia cannot alone prevent cooling instabilities in the nuclei of low
-mass galaxies {\bf AG--careful one needs a separate criterion for
-  thermal stability when heating is dominated by the Ias}.
+(eq.~[$\ref{eq:eddr_analytic}$]).  
+%Note, however, that for low mass
+%SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
+%for a thermally stable flow $\dot{M}_{\rm TI}$
+%(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
+%Ia cannot alone prevent cooling instabilities in the nuclei of low
+%mass galaxies.
 
 The deep gravitational potential wells of high mass galaxies $\sigma_0
-\gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
+\gg  v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
 in these systems.  Equation (\ref{eq:eddr_Ia}) nevertheless represents
@@
 exceeding $r_{\rm Ia}$.
-
-If Ia supernovae are the dominant source of heating we expect $\rs\sim
-r_{\rm Ia}$. If the stagnation radius moves inwards from $\rIa$, the
-decreased heating will force it outwards again. If the it moves
-outwards the Ia heating will force it inwards. Thus,
-equations~\eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} will no longer
-be valid as they assume that $\rs$ follows equation
-\eqref{eq:stag_simple}. We derive $\dot{q}_{\rm
-  heat}/\left|\dot{q}_{\rm rad}\right|$ for $\rs=\rIa$ to evaluate
-thermal stability in SNe Ia dominate the heating.
-
-\begin{align}
-&\rho(\rIa)\simeq \frac{3 q(\rIa)}{2-\Gamma} \nonumber\\
-&T(\rIa)\simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v^{\rm Ia \,\,
-    2}_{w}}{2k}\nonumber\\
+Stated another way, if the stagnation radius moves inwards from $\rIa$, then decreased heating will force it outwards again.
+However, if the stagnation radius moves well outside of $\rIa$, then the high level of Ia heating will force it inwards.
+
+Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
+However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we the ratio of heating to radiative cooling at $\rIa$ is given by
+\begin{align}
 &\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
@@
 \end{align}
+Thus, only for high mass galaxies and/or relatively old stellar populations is Ia heating is sufficient to prevent cooling instabilities on scales of the stagnation radius.
 

### 2015-04-07 ms.tex
fixed Ia discussion later

@@
 \begin{align}
+\label{eq:heatingratioIa}
 &\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
@@
 \end{align}
-Thus, only for high mass galaxies and/or relatively old stellar populations is Ia heating is sufficient to prevent cooling instabilities on scales of the stagnation radius.
+Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad})_{\rIa})$.
+However, for lower mass galaxies or younger stellar populations, Ia blow-out is itself unlikely to prevent cooling instabilities.
 
@@
 An important caveat, however, is that $\vw$ is only a few times higher than the stellar velocity dispersion, i.e.
-$\zeta \sim \zeta_c$.
-This implies that the true stagnation radius could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
+$\zeta \sim \zeta_c$ (eq.~[\ref{eq:zetacrit}]).
+This implies that the true stagnation radius and SMBH accretion rate could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
 
@@
 eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
-otherwise thermally-unstable flow at smaller radii (see discussion
-following eq.~[\ref{eq:eddr_Ia}]).  On the other hand, for higher
+otherwise thermally-unstable flow at smaller radii (eq.~[\ref{eq:heatingratioIa}]).  On the other hand, for higher
 $M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
-heating contributes to the steady gas heating rate, however the energy
+heating contributes to the steady gas heating rate, even if the energy
 released by a single Ia is insufficient to unbind gas from the stellar

### 2015-04-07 ms.tex
conclusions 7

@@
 is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
-formation representative of the average star formation history of loss
+formation representative of the average star formation history (SFH) of loss
 mass galaxies, the stellar wind heating rate produced by stellar winds
@@
   mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
-  $\Mbh$, calculated for average star formation histories from and the
+  $\Mbh$, calculated for average star SFHs from \citealt{MosterNaab+:2013a} and the
   ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
@@
 
-If the nuclei of elliptical galaxies are heated in a way similar to
-that due to the average star formation history of galaxies with
+If the nuclei of elliptical galaxies are heated as expected for the average star formation history of galaxies with
 similar mass, then to first order we predict that $\langle
-L_{X}/L_{\rm edd}\rangle$ should be relatively independent of BH mass.
-To within the uncertainties, this result is consistent with the
-observed down-sizing trend that the average Eddington ratio is seen to
-decrease (albeit weakly) with $M_{\bullet}$, although tension is
-somewhat greater in the $\epsilon_X= (\epsilon_{\rm
+L_{X}/L_{\rm edd}\rangle$ should be a weakly increasing function of BH mass.
+This result is in tension with the observed down-sizing trend that the average Eddington ratio is seen to
+decrease (albeit weakly) with $M_{\bullet}$, especially in the $\epsilon_X= (\epsilon_{\rm
   bol}/0.1)(\Mdot/\MdotEdd)$ model.
-
-%However, one must keep in mind the enormous uncertainty in calculating the
-%luminosity of the accretion flow close to the black hole in a single
-%waveband based on the feeding rate on larger scales.
-If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
-%angular momentum of the infalling gas might also influence the X-ray luminosity, in a way
-%that could depend systematically on the stellar population and hence $M_{\bullet}$.
+However, one must keep in mind the enormous uncertainty in calculating the luminosity of the accretion flow close to the black hole in a single waveband based on the feeding rate on larger scales.
+If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the angular momentum of the infalling gas might also influence the X-ray luminosity, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.
 
@@
 Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
-  C} > \dot{M}_{\rm TI}$ across all black hole masses.  Thus, even if
-Compton heating could act to self-stabilize the flow (which, as already
-mentioned, appears unlikely), its magnitude appears to be insufficient to
-produce a thermally stable accretion rate even given conditions
+  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates that even if
+Compton heating could act to stabilize the flow in a quasi-steady state (which, as already discussed, is unlikely), the magnitude of the heating is insufficient to produce a thermally stable accretion rate given conditions
 corresponding to the average star formation history.
@@
 
-\subsection{Local Growth Time of SMBHs }
+\subsection{SMBH Growth Times }
 \label{sec:growth}
@@
 history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
-Hubble time by 2$-$3 orders of magnitude across all $M_{\bullet}$.
+Hubble time by 1$-$3 orders of magnitude across all $M_{\bullet}$.
 Steady accretion therefore cannot explain the growth of low mass black
@@
 hierarchical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this,
+galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In support of this,
 \citet{Kauffmann&Heckman09} find that the growth of low mass black
@@
 However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
+
 Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).
@@
 The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's star formation history.
-Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, and used to address other key questions, such as the thermal stability of their accretion flows.
+Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN.
+They are also used to address key questions such as the thermal stability of the accretion flow.
 Our conclusions are summarized as follows.
@@
     stellar mass enclosed inside of $\rs$.
-In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]).
-In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetac}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$.
-
-\item The inclusion of thermal conduction results in only moderate changes to the key properties of the flow (e.g.
-stagnation radius, mass accretion rate, and thermal stability) for causal values of the saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
+In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]), and the Bernoulli parameter of the flow at large radii is positive (Appendix \ref{app:be}).
+In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetacrit}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$, greatly increasing the density of gas on smaller radial scales.
+
+\item Including the effects of energy transport by electron conduction results in only moderate changes to the key properties of the flow (e.g.
+stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
 
 \item Radiative cooling has a more pronounced influence on the structure of the gas flow.
-The approximate condition for cooling instabilities develop is that the rate of radiative cooling exceed the external heating rate at the stagnation radius.
+The approximate condition for cooling instabilities develop at all radii is that the radiative cooling rate exceed the external gas heating rate near the stagnation radius.
+This condition is equivalent to the more commonly invoked $t_{\rm cool} \gg t_{\rm ff}$ criterion (e.g.~\citealt{McCourt+12}; \citealt{Li&Bryan14a}).
 
@@
 
-Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ may increase even more rapidly as $v_w$ decreases for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
-
-\item The nuclei of galaxies with low mass black holes $\Mbh \lesssim 10^8
-  \Msun$ and star formation histories which match their average value derived from cosmological simulations, receive a stellar wind heating rate $v_w\sim 800$ km s$^{-1}$ which is relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).
-The resulting Eddington ratio is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in moderate tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
-
-For thermally stable accretion models, scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude can result from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
-
-\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value consistent with thermally-stable accretion (Fig.~\ref{fig:miller}).
-High mass SMBHs are particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.
-If the current X-ray sample is instead comprised mainly of thermally unstable nuclei, then a separate branch of low $L_x$ "thermally stable" nuclei may exist, especially at low $M_{\bullet}$.
-Such a dichotomy calls into question the accuracy of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in constraining the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous numerical studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
+
+\item Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$ (Fig.~\ref{fig:vwSources}) sufficient to result in thermally-stable, steady-state accretion.
+The resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
+However, given the large uncertainties in translating predictions for the gas inflow rate on parsec scales to the disk X-ray luminosity, these differences may not be significant.
+
+Thermally stable accretion models can reproduce scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
+
+\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value allowed for thermally-stable accretion (Fig.~\ref{fig:miller}).
+Massive galaxies are also particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.
+It is thus possible that the current X-ray detected sample is instead comprised mainly of nuclei undergoing non-steady accretion as a part of local thermal instabilities.
+In this case a separate branch of low $L_x$ (undetected) thermally-stable nuclei may exist, especially at low $M_{\bullet}$.
+Such a dichotomy challenges the practice of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
 
   \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).
-This requires accretion rates which are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
-Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplies external to the nuclear region.
+This accretion rates so required are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
+Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplied externally to the nuclear region, e.g.
+due to galaxy mergers or thermal instabilities on larger, galactic scales (e.g.~\citealt{Voit+15}).
 
@@
 
-    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
-    the observed nuclear x-ray luminosities in quiescent, early type
-    galaxies could be understood as coming from thermally stable
-    steady-state accretion of stellar winds shed in the galactic
-    nucleus.  However, we would like to draw attention to the
-    following limitations of our model
-
+%    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
+ %   the observed nuclear x-ray luminosities in quiescent, early type
+  %  galaxies could be understood as coming from thermally stable
+   % steady-state accretion of stellar winds shed in the galactic
+    %nucleus.
+
+We conclude by drawing attention to the following limitations of our model
     \begin{enumerate}
@@
 \section*{Acknowledgments}
-We acknowledge helpful conversations with Jerry Ostriker, Eliot
-Quataert, .... This work relied on Columbia University's Yeti compute
+We acknowledge helpful conversations with Greg Bryan, Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot
+Quataert.  This work relied on Columbia University's Yeti compute
 cluster,and we acknowledge the Columbia HPC support staff for

### 2015-04-07 ms.tex
zetaCrit figure

--- 2015-04-07 ms.tex
@@
   We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in slowly accreting (``quiescent") galactic nuclei for a range of
+  hot gas in ``quiescent" galactic nuclei for a range of
   central black hole masses $M_{\bullet}$, parameterized gas heating
@@
 rate from stellar and black hole velocity dispersion \\
-$v_{w}$ & total heating parameter, excluding minimum heating rate from
+$v_{w}$ & total heating parameter, excluding heating rate from
 velocity dispersion \\
-$\sigma_0$ & stellar velocity dispersion (assumed to be radially constant)\\
+$\sigma_0$ & stellar velocity dispersion--assumed to be radially constant.\\
 $\zeta$ & heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
-$r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
+$r_{s}$ & stagnation radius (where gas radial velocity goes to zero) \\
 $r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
 $r_{\rm b}$ & outer break radius of stellar density profile \\ 
-$r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
+$r_{\rm Ia}$ & radius interior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
 $\rho_{\star}(r)$ & 3D radial stellar density profile \\
@@
 $M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
-$q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
+$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
 $\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
@@
 profile interior to the break radius \\
-$\delta$ & power-law slope of the 3D stellar density profile inside of
-the break radius, $\delta \equiv \Gamma+1$.\\
+$\delta$ & power-law slope of the 3d stellar density profile inside of
+the break radius. $\delta=\Gamma+1$.\\
 $\dot{M}$ & mass accretion rate  \\
@@
 
-We fix $\beta = 2$ because our results are
+We fix $\beta = 2$ (a typical value ${\bf AG beta=1.5 may be more
+  typical...but it still may not matter...}$) because our results are
 generally not sensitive to the properties of the gas flow on radial
@@
 sources of heating and cooling, its presence leads to thermal
-instability (e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be accounted for
+instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for
 by our 1D time-independent model.  A main goal of this work is to use
@@
 energy.  Condition (\ref{eq:zetacrit}) approximately corresponds to
-the condition that the wind heating parameter be less than the local escape
-speed from near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
+the condition that the wind heating parameter be less than the escape
+speed from the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
     b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
@@
 (eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable
-(e.g., \citealt{McCourt+12}, \citealt{Li&Bryan14a}), potentially resulting
-in the formation of a multi-phase medium and enhanced star formation (\citealt{Li&Bryan14b}).
+(\citealt{McCourt+12} and references therein), potentially resulting
+in the formation of a multi-phase medium and enhanced star formation.
 Even if the hot plasma of the CNM does not condense into cold clouds,
@@
 stagnation radius, as can be derived using the equality
+
 \begin{align}
@@
 \eqref{eq:rhostarrs}.  \citet{McCourt+12} argue cooling instability
-develops in a hydrostatic atmosphere if $t_{\rm cool} \lesssim 10 t_{\rm ff}$,
+develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$,
 so equation (\ref{eq:cooling2}) represents a good proxy for
-instability in this case as well (see also \citealt{Li&Bryan14a}, \citealt{Li&Bryan14b}).
+instability in this case as well.
 
@@
 the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
-\lesssim r_{\rm inf}$).  However, for low heating the
+\lesssim r_{\rm inf}$).  However, for sufficiently low heating the
 stagnation radius diverges above the analytic estimate, approaching
@@
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
-This divergence of the stagnation radius to large radii occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii, explaining the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange triangles.
-These solutions correspond to the same black hole mass
-($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break radii of $r_{b} =$ 25, 50 pc (from top to
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
+\ref{app:be} is shown to coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius.
+This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.
+This dependence explains the behavior of the two core galaxies, shown as
+orange triangles vertically aligned at the same value of
+$\zeta$; the solutions correspond to the same black hole mass
+($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but are calculated assuming
+different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
 bottom).
@@
 can be less than unity, depending on the wind mass loss parameter
-$\eta$.  Because at the stagnation radius $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$ reaches within a factor
-of two of its minimum across the entire grid, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be taken as diagnostic of thermal instability at all radii.
+$\eta$.  At the stagnation radius, the ratio $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$ reaches a value that lies within a factor
+of two of its minimum across the entire grid; thus, the value of
+$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ provides a
+diagnostic of thermal instability for the entire solution.
 
@@
 
-In addition to our solutions which neglect thermal conduction and radiative cooling, we explore a smaller set of simulations including these effects explicitly, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions which are already marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
-We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
-Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}, with the unstable values of $\eta$ provided in the final column.
-In contrast, changes in the solution when thermal conduction was included were always found to be minor for our choice of the saturation parameter $\phi = 0.1$.
-Conduction does, however, offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
-
-\section{Heating Sources}
+In addition to our standard set of solutions which neglect thermal conduction and radiative cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.
+For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the flow (e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$).
+However, for solutions which are marginally stable (e.g., $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), the inclusion of radiative acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater amount.
+We ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02, 0.2, 0.6$, spanning the physical range.
+Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}.
+By contrast, changes due to the inclusion of thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, although conduction is seen to offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+
+\section{Sources of Heating}
 \label{sec:heating}
@@
 \ee
-Hence, for low mass BHs with $\sigma_0 \ll v^{\rm Ia}_{w}$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
+Hence, for low mass BHs with $\sigma_0 \ll \mathcal{F}v^{\rm Ia}_{w}/2$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
 Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
@@
 for $r_{\rm s}$ in the derivation leading to our estimate of $\dot{M}$
-(eq.~[$\ref{eq:eddr_analytic}$]).  
-%Note, however, that for low mass
-%SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
-%for a thermally stable flow $\dot{M}_{\rm TI}$
-%(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
-%Ia cannot alone prevent cooling instabilities in the nuclei of low
-%mass galaxies.
+(eq.~[$\ref{eq:eddr_analytic}$]).  Note, however, that for low mass
+SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
+for a thermally stable flow $\dot{M}_{\rm TI}$
+(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
+Ia cannot alone prevent cooling instabilities in the nuclei of low
+mass galaxies {\bf AG--careful one needs a separate criterion for
+  thermal stability when heating is dominated by the Ias}.
 
 The deep gravitational potential wells of high mass galaxies $\sigma_0
-\gg  v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
+\gg f v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
 in these systems.  Equation (\ref{eq:eddr_Ia}) nevertheless represents
@@
 exceeding $r_{\rm Ia}$.
-Stated another way, if the stagnation radius moves inwards from $\rIa$, then decreased heating will force it outwards again.
-However, if the stagnation radius moves well outside of $\rIa$, then the high level of Ia heating will force it inwards.
-
-Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we the ratio of heating to radiative cooling at $\rIa$ is given by
-\begin{align}
+
+If Ia supernovae are the dominant source of heating we expect $\rs\sim
+r_{\rm Ia}$. If the stagnation radius moves inwards from $\rIa$, the
+decreased heating will force it outwards again. If the it moves
+outwards the Ia heating will force it inwards. Thus,
+equations~\eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} will no longer
+be valid as they assume that $\rs$ follows equation
+\eqref{eq:stag_simple}. We derive $\dot{q}_{\rm
+  heat}/\left|\dot{q}_{\rm rad}\right|$ for $\rs=\rIa$ to evaluate
+thermal stability in SNe Ia dominate the heating.
+
+\begin{align}
+&\rho(\rIa)\simeq \frac{3 q(\rIa)}{2-\Gamma} \nonumber\\
+&T(\rIa)\simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v^{\rm Ia \,\,
+    2}_{w}}{2k}\nonumber\\
 &\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
@@
 \end{align}
-Thus, only for high mass galaxies and/or relatively old stellar populations is Ia heating is sufficient to prevent cooling instabilities on scales of the stagnation radius.
 
@@
 Quataert, .... This work relied on Columbia University's Yeti compute
-cluster,and we acknowledge the Columbia HPC support staff for
+cluster, and we acknowledge the Columbia HPC support staff for
 assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}

### 2015-04-07 ms.tex
conclusions 9

--- 2015-04-07 ms.tex
@@
 
-\item Including the effects of energy transport by electron conduction results in only moderate changes to the key properties of the flow (e.g.
+\item Including the effects of heat transport by electron conduction results in only moderate changes to the key properties of the flow (e.g.
 stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
 
-\item Radiative cooling has a more pronounced influence on the structure of the gas flow.
-The approximate condition for cooling instabilities develop at all radii is that the radiative cooling rate exceed the external gas heating rate near the stagnation radius.
-This condition is equivalent to the more commonly invoked $t_{\rm cool} \gg t_{\rm ff}$ criterion (e.g.~\citealt{McCourt+12}; \citealt{Li&Bryan14a}).
+\item Radiation has a more pronounced influence on the structure of the gas flow.
+Cooling instabilities are likely to develop when the radiative cooling rate exceed the rate of external heating near the stagnation radius.
+This condition is equivalent to the more commonly invoked criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion (e.g.~\citealt{McCourt+12}; \citealt{Li&Bryan14a}).
 
   \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.
-Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.
+Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous numerical studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
+
+\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.
 A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
 Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
-
-Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous numerical studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
-
-\item Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$ (Fig.~\ref{fig:vwSources}) sufficient to result in thermally-stable, steady-state accretion.
+Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.
+
+\item Type Ia SNe only provide a continuous heating source exterior to the radius $\rIa$ (eq.~[\ref{eq:RIa}]) where the time interval between subsequent SNe exceeds the local dynamical timescale.
+The heating provided by the average star formation history results in $\rIa < \rs$, except for the most massive galaxies.
+Nevertheless, even if other sources of heating are low enough that $\rIa > \rs$, the stagnation radius is unlikely to exceed $\rIa$ due to Ia heating.
+SN Ia thus cap the SMBH accretion rate at the value $\dot{M}_{Ia}$ (eq.~[\ref{eq:MdotIa}]), except possibly in high mass elliptical galaxies with large break radii, for which $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
+
+\item Stellar wind heating due to the average star formation history is sufficient to result in thermally-stable, steady-state accretion.
 The resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
@@
 \section*{Acknowledgments}
-We acknowledge helpful conversations with Greg Bryan, Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot
-Quataert.  This work relied on Columbia University's Yeti compute
-cluster,and we acknowledge the Columbia HPC support staff for
-assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
-grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
-Foundation.
+
+We acknowledge helpful conversations with Greg Bryan, Jules Halpern,
+Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work
+relied on Columbia University's Yeti compute cluster,and we
+acknowledge the Columbia HPC support staff for assistance.  BDM
+gratefully acknowledges support from NASA {\it Fermi} grant
+NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.
 

### 2015-04-07 ms.tex
conclusions 10

@@
 Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
-Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.
+Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ that experience heating corresponding to their average star formation histories from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.
 

### 2015-04-07 ms.tex
conclusions 11
conclusions 12

@@
 we systematically analyze the CNM properties across a range of galaxy properties, including different SMBH masses, stellar density profiles, and
-star formation histories (\citealt{WangMerritt:2004a}).
+star formation histories (SFHs; \citealt{WangMerritt:2004a}).
 
@@
   of volumetrically, but our expressions are equivalent.}, although
-$\eta$ is significantly higher for continuous star formation histories
+$\eta$ is significantly higher for continuous SFHss
 (bottom panel of Fig.~\ref{fig:vwSources}).
@@
 is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
-formation representative of the average star formation history (SFH) of loss
+formation representative of the average SFHs of low
 mass galaxies, the stellar wind heating rate produced by stellar winds
@@
 turn may create stronger kinetic feedback.  However, given the uncertainty
-in the efficiency of kinetic heating, we defer a more detailed discussion
+in the efficiency of kinetic heating, we hereafter exclude its effect and defer further discussion
 to $\S\ref{sec:kinetic}$.
@@
   ({\it pink}).  Each heating source varies with black hole mass
-  $\Mbh$ calculated for average star formation histories from
+  $\Mbh$ calculated for average SFHs from
   \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
@@
 described by a single star burst formation in the past, or by a more
-continuous star formation history that itself varies systematically
+continuous SFH that itself varies systematically
 with the galaxy mass and hence $\Mbh$.
@@
 winds.  SN Ia heating depends also on a convolution of the DTD
-(eq. [\ref{eq:DTD}]) and the star formation history, which reduces to
+(eq. [\ref{eq:DTD}]) and the SFH, which reduces to
 the DTD itself for a single star burst.
@@
 
-\subsubsection{Continuous Star Formation History}
+\subsubsection{Continuous SFH}
 A single burst of star formation does not describe the typical star
@@
 formation histories of \citet{MosterNaab+:2013a}.  Appendix
-\ref{app:windheat} describes how the average star formation history is
+\ref{app:windheat} describes how the average SFH is
 used to determine the stellar wind heating $v_{\rm w}^{\star}$ and
 mass return parameter $\eta$ as a function of $M_{\bullet}$
-(Fig.~\ref{fig:vwSources}; top panel).  Star formation histories are also
+(Fig.~\ref{fig:vwSources}; top panel).  SFHs are also
 convolved with the Ia DTD distribution to determine the SN Ia heating.
@@
 source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
-the average star formation history of galaxies containing a given
+the average SFH of galaxies containing a given
 black hole mass.  The younger stellar populations characterizing galaxies
@@
 Strikingly, we find that galactic nuclei experiencing the same
-  average star formation history as their host galaxies produce thermally stable flows across almost all black hole masses.
+  average SFH as their host galaxies produce thermally stable flows across almost all black hole masses.
 
@@
 
-Realistic variations (``burstiness") in the star formation history
+Realistic variations (``burstiness") in the SFH
 will also often produce lower stellar wind heating rates (Appendix
@@
 formation rate ($\iota \sim 10^{-3}$).  However, burstiness in the
-star formation history over longer timescales can suppress heating
+SFH over longer timescales can suppress heating
 more significantly.  When $\delta t_{\star} \gtrsim 10^8~{\rm yr}$,
@@
 5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
-of average cosmic star formation histories is appropriate provided
+of average cosmic SFHs is appropriate provided
 local variations are either on short timescales ($\delta t_{\star}
@@
 Figure \ref{fig:vwSources} shows that the heating associated with the
-average star formation history of a galaxy is approximately constant
+average SFH of a galaxy is approximately constant
 with SMBH mass, except for the largest black holes with $M_{\bullet}
@@
   Black lines show our prediction in the case of heating due to the
-  average star formation history for galaxies corresponding to each
+  average SFH for galaxies corresponding to each
   black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a
@@
   rate ({\it pink line}; eq.~[\ref{eq:MdotCa}]), again all calculated
-  for the average star formation history corresponding to each SMBH
+  for the average SFH corresponding to each SMBH
   mass.}
@@
 
-If the nuclei of elliptical galaxies are heated as expected for the average star formation history of galaxies with
+If the nuclei of elliptical galaxies are heated as expected for the average SFH of galaxies with
 similar mass, then to first order we predict that $\langle
@@
 Compton heating could act to stabilize the flow in a quasi-steady state (which, as already discussed, is unlikely), the magnitude of the heating is insufficient to produce a thermally stable accretion rate given conditions
-corresponding to the average star formation history.
+corresponding to the average SFH.
 
@@
 Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).
-The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's star formation history.
+The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's SFH.
 Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN.
@@
 
-\item Including the effects of heat transport by electron conduction results in only moderate changes to the key properties of the flow (e.g.
+\item Including the effects of heat transport by electron conduction results in at most order unity changes to the key properties of the flow (e.g.
 stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
-
-\item Radiation has a more pronounced influence on the structure of the gas flow.
-Cooling instabilities are likely to develop when the radiative cooling rate exceed the rate of external heating near the stagnation radius.
-This condition is equivalent to the more commonly invoked criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion (e.g.~\citealt{McCourt+12}; \citealt{Li&Bryan14a}).
+Angular momentum is also unlikely to invalidate our spherically symmetric models given the extrapolated rotation curves of galaxies to the nuclear scales of interest ($\S\ref{sec:rotation}$).
+
+\item Radiative cooling has a more pronounced influence on the structure of the gas flow.
+Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.
+This condition is approximately equivalent to the more criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
 
@@
 Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous numerical studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).
-
-\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.
-A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
-Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).
-Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ that experience heating corresponding to their average star formation histories from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.
-
-\item Type Ia SNe only provide a continuous heating source exterior to the radius $\rIa$ (eq.~[\ref{eq:RIa}]) where the time interval between subsequent SNe exceeds the local dynamical timescale.
-The heating provided by the average star formation history results in $\rIa < \rs$, except for the most massive galaxies.
+However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the stellar break radius (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on the results of previous numerical studies (e.g.,\citealt{Ciotti+10}) is instead likely to result in time-dependent cycles of alternating high and low accretion phases ($\S\ref{sec:cycle}$).
+
+\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the SFH in the galactic nuclear region.
+A young starburst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old stellar populations  mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
+Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).
+Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w\sim 800$ km s$^{-1}$, although this number can be somewhat lower if the star formation is intermittent (Fig.~\ref{fig:NickPlot2}).
+
+\item Type Ia SNe only provide a continuous heating source exterior to the Ia radius $\rIa$ (eq.~[\ref{eq:rIa}]) where the time between subsequent SNe exceeds the dynamical timescale.
+Average SFH heating results in $\rIa < \rs$, except for the most massive galaxies.
 Nevertheless, even if other sources of heating are low enough that $\rIa > \rs$, the stagnation radius is unlikely to exceed $\rIa$ due to Ia heating.
@@
 
-\item Stellar wind heating due to the average star formation history is sufficient to result in thermally-stable, steady-state accretion.
+\item Stellar wind heating due to the average SFH is sufficient to result in thermally-stable, steady-state accretion.
 The resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
@@
 
-Thermally stable accretion models can reproduce scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
+Thermally stable accretion models can reproduce scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in SFH from galaxy to galaxy, or from time to time due to burstiness in the SFH (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
 
@@
     galaxies which may have significant variations about our assumed
-    average star formation histories.
-    \item Also, the star formation history of bulges may (and probably
+    average SFHs.
+    \item Also, the SFH of bulges may (and probably
       does) systematically differ from the average star formation
@@
 Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work
-relied on Columbia University's Yeti compute cluster,and we
+relied on Columbia University's Yeti computer cluster, and we
 acknowledge the Columbia HPC support staff for assistance.  BDM

### 2015-04-07 ms.tex

@@
 Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).
-Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w\sim 800$ km s$^{-1}$, although this number can be somewhat lower if the star formation is intermittent (Fig.~\ref{fig:NickPlot2}).
+Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$, although this number can be somewhat lower if the star formation is intermittent (Fig.~\ref{fig:NickPlot2}).
 
 \item Type Ia SNe only provide a continuous heating source exterior to the Ia radius $\rIa$ (eq.~[\ref{eq:rIa}]) where the time between subsequent SNe exceeds the dynamical timescale.
-Average SFH heating results in $\rIa < \rs$, except for the most massive galaxies.
-Nevertheless, even if other sources of heating are low enough that $\rIa > \rs$, the stagnation radius is unlikely to exceed $\rIa$ due to Ia heating.
-SN Ia thus cap the SMBH accretion rate at the value $\dot{M}_{Ia}$ (eq.~[\ref{eq:MdotIa}]), except possibly in high mass elliptical galaxies with large break radii, for which $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
-
-\item Stellar wind heating due to the average SFH is sufficient to result in thermally-stable, steady-state accretion.
-The resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
-However, given the large uncertainties in translating predictions for the gas inflow rate on parsec scales to the disk X-ray luminosity, these differences may not be significant.
-
-Thermally stable accretion models can reproduce scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in SFH from galaxy to galaxy, or from time to time due to burstiness in the SFH (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.
-
-\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value allowed for thermally-stable accretion (Fig.~\ref{fig:miller}).
-Massive galaxies are also particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.
-It is thus possible that the current X-ray detected sample is instead comprised mainly of nuclei undergoing non-steady accretion as a part of local thermal instabilities.
-In this case a separate branch of low $L_x$ (undetected) thermally-stable nuclei may exist, especially at low $M_{\bullet}$.
-Such a dichotomy challenges the practice of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+Heating from the average SFH results in $\rIa < \rs$, except for the most massive galaxies (Fig.~\ref{fig:vwSources}).
+Nevertheless, even if other sources of heating are low enough for $\rs$ to approach $\rIa$, the SN Ia heating supplied when $\rs \gtrsim \rIa$ is sufficiently large that $\rs$ is unlikely to greatly exceed $\rIa$.
+SNe Ia thus cap the SMBH accretion rate at the value $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high mass elliptical galaxies with large break radii, for which $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
+
+\item Stellar wind heating from the average SFH is sufficient to permit thermally-stable, steady-state accretion.
+However, the resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
+However, these differences may not be discriminating given the huge uncertainty in translating the predicted gas inflow rate on parsec scales to the disk X-ray luminosity.
+
+Thermally stable accretion models can reproduce the observed scatter in nuclear X-ray luminosities at fixed $\Mbh$ of 2-4 orders of magnitude due to combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in SFH from galaxy to galaxy, or from time to time due to burstiness in the SFH (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas (e.g.~\citealt{Li+13}).
+
+\item Only for high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value allowed for thermally-stable accretion $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}).
+It is thus well possible that the current sample of X-ray detections is instead comprised mainly of nuclei undergoing non-steady accretion due to (local) thermal instabilities.
+In this case there may exist a separate branch of low $L_x$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
+Such a bimodal population would call into question extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
 
   \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).
-This accretion rates so required are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
-Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplied externally to the nuclear region, e.g.
+This accretion rates so required are too high to be consistent with the value predicted for the average SFH history and the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
+Low-$M_{\bullet}$ growth and AGN activity must instead be driven by a supply of gas external to the nucleaus, e.g.
 due to galaxy mergers or thermal instabilities on larger, galactic scales (e.g.~\citealt{Voit+15}).

### 2015-04-08 ms.tex
caption
conclusions 15

@@
 
+\item SMBH feedback, unlike stellar heating sources, depends on the SMBH accretion rate, which is itself a function of the heating rate.
+Compton heating is generally unimportant compared to stellar wind heating when the latter corresponds to the average SFH; however, Compton heating can dominate in the case of an impulsive burst of star formation (\ref{fig:vwSourcesImp}).
+In principle the Compton heating rate is sufficiently high to prevent thermal instabilities in steady-state, i.e.
+$\dot{M}_{C} \lesssim \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth})  However, unlike local stellar feedback
+mechanisms, SMBH feedback may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
+Kinetic feedback is more difficult to quantify, but could also be important in determining $\dot{M}(M_{\bullet}$) when stellar heating is weak ($\S\ref{sec:kinetic}$).
+
 \item Stellar wind heating from the average SFH is sufficient to permit thermally-stable, steady-state accretion.

### 2015-04-08 windheat.tex

@@
 
-For a stellar population that forms impulsively, the rate of mass and energy injection per unit stellar mass at age $t$ are given, respectively, by 
+In the case of a single implusive burst of star formation, the mass and energy injection rate per unit stellar mass at time $t$ after the burst are given, respectively, by 
 \begin{align} 
@@
 \end{align}
-where $x=\log(t/10^9 {\rm years})$.  This functional fit is designed
+where $x=\log(t/10^9 {\rm yr})$.  This functional fit is designed
 to reproduce the results of \citet{MaederMeynet:1987a} (their Table 9)
@@
 \subsection{Over Star Formation History}
-Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
+Generalizing to an arbitrary SFH $S(t)$, the total rate of mass and energy input can be written as
 \begin{align} 

### 2015-04-08 ms.tex
colorful

@@
     correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
-    correspond to cores ($\Gamma = 0.1$). Green crosses correspond to
+    correspond to cores ($\Gamma = 0.1$). Green circles correspond to
     cusp solutions which would be thermally unstable. The black curves
@@
     ($\Gamma=0.8$), while triangles correspond to cores
-    ($\Gamma$=0.1). Green crosses correspond to cusp solutions which
+    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
     would be thermally unstable.  Solid and dashed curves correspond
@@
 \includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
-\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.
-Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.
-Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).
-Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{McConnellMa+:2011a}.}
+\caption{\label{fig:vwSourcesImp} Different sources contributing to
+  the gas heating rate in galactic nuclei at time $\tau_{\star}$ after
+  a single burst of star formation.  Top and bottom panels show cases
+  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$,
+  respectively.  Solid and dashed lines show the ranges of
+  $\tau_{\star}$ for which the accretion flow is thermally stable and
+  unstable, respectively, according to the ratio of $\dot{q}_{\rm
+    heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius
+  (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
+  are the velocity dispersions according to $\Mbh-\sigma$
+  \citep{McConnellMa+:2011a}.}
 \end{figure}
@@
   ({\it pink}).  Each heating source varies with black hole mass
-  $\Mbh$ calculated for average SFHs from
-  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
-  details).  {\it Middle Panel:} The ratio of the total heating rate
-  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
-  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
-  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
-  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
-  $\Mbh$, calculated for average star SFHs from \citealt{MosterNaab+:2013a} and the
-  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
-  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
-  %convolving the average star formation histories with the SN Ia DTD.
-  %The stagnation radius is calculated from \eqref{eq:stag_simple}
-  %using the total heating rate for each $\Mbh$ shown in the top panel
-  %assuming a cusp galaxy ($\Gamma=0.8$).}
+  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a}
+  (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:}
+  The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
+  v_{w}^{2}$) from the top panel to the radiative cooling rate
+  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter $\eta$
+  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
+  function of black hole mass $\Mbh$, calculated for average star SFHs
+  from \citealt{MosterNaab+:2013a} (blue) and the ratio of Ia radius to
+  stagnation radius as a function of $\Mbh$ (green).}
 \end{figure}

### 2015-04-08 ms.tex
adjusting caption

@@
   L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
-  Black lines show our prediction in the case of heating due to the
-  average SFH for galaxies corresponding to each
-  black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a
-  power-law fit for the relationship $\Gamma(M_{\bullet})$ derived
-  from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are
-  the measurements ({\it red stars}) and upper limits ({\it red
+  Green lines show our prediction in the case of heating due to the
+  average SFH for galaxies corresponding to each black hole mass
+  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
+  relationship $\Gamma(M_{\bullet})$ derived from the
+  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
+  measurements ({\it black stars}) and upper limits ({\it gray 
     triangles}) for $L_X/L_{\rm edd}$ values, from the
-  \citet{Miller+15} sample of early-type galaxies (a green line shows
+  \citet{Miller+15} sample of early-type galaxies (a black line shows
   the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
@@
   luminosities calculated for the maximum thermally-stable accretion
-  rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
-  Ia-regulated accretion rate ({\it teal line};
+  rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
+  Ia-regulated accretion rate ({\it dashed teal line};
   eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
-  rate ({\it pink line}; eq.~[\ref{eq:MdotCa}]), again all calculated
-  for the average SFH corresponding to each SMBH
-  mass.}
+  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
+  calculated for the average SFH corresponding to each SMBH mass.}
 \end{figure*}

### 2015-04-08 ms.tex
mdot_mass plot

@@
     ($\Gamma$=0.1). Green circles correspond to cusp solutions which
-    would be thermally unstable.  Solid and dashed curves correspond
+    would be thermally unstable.  Solid and dot-dashed curves correspond
     to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$

### 2015-04-08 be.tex
zetaCrit plot

@@
 \includegraphics[width=\columnwidth]{zetaCrit.pdf}
-\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value $\zeta_c$ of the wind heating parameter
-  $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of the flow $\mathcal{B}$ is positive near the break radius for some value of $\rs$, calculated for core ($\Gamma=0.1$)
-  galaxies using equation~\eqref{eq:enthAnal}..
-{\emph Bottom Panel:} Minimum value of the stagnation radius for which $\mathcal{B} > 0$ at the break radius as a function of $\zeta/\zeta_c < 1$, again calculated for core galaxies ($\Gamma=0.1$).}
+\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value
+  $\zeta_c$ of the wind heating parameter $\zeta \equiv
+  \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of
+  the flow $\mathcal{B}$ is positive near the break radius for some
+  value of $\rs$, calculated for core ($\Gamma=0.1$, dot-dashed line)
+  and cusp ($\Gamma=0.8$, solid line) galaxies using
+  equation~\eqref{eq:enthAnal}.. {\emph Bottom Panel:} Minimum value
+  of the stagnation radius for which $\mathcal{B} > 0$ at the break
+  radius as a function of $\zeta/\zeta_c < 1$. }
 \end{figure}

### 2015-04-08 be.tex
conclusions 16

@@
   and cusp ($\Gamma=0.8$, solid line) galaxies using
-  equation~\eqref{eq:enthAnal}.. {\emph Bottom Panel:} Minimum value
+  equation~\eqref{eq:enthAnal}. {\emph Bottom Panel:} Minimum value
   of the stagnation radius for which $\mathcal{B} > 0$ at the break

### 2015-04-08 ms.tex
conclusions 16

@@
 Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).
-The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's SFH.
+We use the latter to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's SFH.
 Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN.
@@
 stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
-Angular momentum is also unlikely to invalidate our spherically symmetric models given the extrapolated rotation curves of galaxies to the nuclear scales of interest ($\S\ref{sec:rotation}$).
-
-\item Radiative cooling has a more pronounced influence on the structure of the gas flow.
+Angular momentum is also unlikely to invalidate our spherically symmetric model, given the inferred stellar rotation rates near the stagnation radius ($\S\ref{sec:rotation}$).
+
+\item Radiative cooling has a more pronounced influence on the flow structure.
 Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.
@@
 Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).
-Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$, although this number can be somewhat lower if the star formation is intermittent (Fig.~\ref{fig:NickPlot2}).
+Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$.
+This heating can be suppressed if the star formation is sufficiently intermittent (Fig.~\ref{fig:NickPlot2}).
 
 \item Type Ia SNe only provide a continuous heating source exterior to the Ia radius $\rIa$ (eq.~[\ref{eq:rIa}]) where the time between subsequent SNe exceeds the dynamical timescale.
-Heating from the average SFH results in $\rIa < \rs$, except for the most massive galaxies (Fig.~\ref{fig:vwSources}).
-Nevertheless, even if other sources of heating are low enough for $\rs$ to approach $\rIa$, the SN Ia heating supplied when $\rs \gtrsim \rIa$ is sufficiently large that $\rs$ is unlikely to greatly exceed $\rIa$.
-SNe Ia thus cap the SMBH accretion rate at the value $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high mass elliptical galaxies with large break radii, for which $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
-
-\item SMBH feedback, unlike stellar heating sources, depends on the SMBH accretion rate, which is itself a function of the heating rate.
-Compton heating is generally unimportant compared to stellar wind heating when the latter corresponds to the average SFH; however, Compton heating can dominate in the case of an impulsive burst of star formation (\ref{fig:vwSourcesImp}).
-In principle the Compton heating rate is sufficiently high to prevent thermal instabilities in steady-state, i.e.
-$\dot{M}_{C} \lesssim \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth})  However, unlike local stellar feedback
-mechanisms, SMBH feedback may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
-Kinetic feedback is more difficult to quantify, but could also be important in determining $\dot{M}(M_{\bullet}$) when stellar heating is weak ($\S\ref{sec:kinetic}$).
+Non-Ia heating due to the average SFH results in $\rs <\rIa$, except for the most massive galaxies (Fig.~\ref{fig:vwSources}).
+However, if $\rs$ does approach or exceed $\rIa$, then the SN Ia heating is usually sufficiently large to prevent $\rs$ from greatly exceeding $\rIa$.
+SNe Ia thus regulates the SMBH accretion rate below the value $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high mass elliptical galaxies with large break radii and $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
+
+\item Heating from SMBH feedback, unlike stellar heating, depends on the SMBH accretion rate, which is itself a function of the heating rate.
+Compton heating is generally unimportant compared to stellar wind heating for the average SFH, but it can dominate in the case of an impulsive star burst (Fig.~\ref{fig:vwSourcesImp}).
+Although in principle Compton heating is sufficiently high to prevent thermal instabilities when acting alone, i.e.
+$\dot{M}_{C} \lesssim \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not however be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
+Kinetic feedback could also be important in determining $\dot{M}(M_{\bullet}$) when stellar heating is weak ($\S\ref{sec:kinetic}$) but is more challenging to quantify.
 

### 2015-04-08 windheat.tex
bumpy

@@
 
-In the case of a single implusive burst of star formation, the mass and energy injection rate per unit stellar mass at time $t$ after the burst are given, respectively, by 
+In the case of a single implusive burst of star formation, the mass
+and energy injection rate per unit stellar mass at time $t$ after the
+burst are given, respectively, by
 \begin{align} 
@@
  \begin{figure}
-  \includegraphics[width=\columnwidth]{NickPlot2.pdf}
-  \caption{\label{fig:NickPlot2} Effective wind velocities for nonstandard
-    star formation histories.  The black curve shows, for reference,
-    $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other
-    colors show the effective wind velocities $\mathcal{V}_{\rm w}$
-    computed using convolved star formation histories
-    $\mathcal{S}(t)$.  The purple curve shows a recent drop in the
-    star formation rate, i.e. $\delta t_{\star}=10^6~{\rm yr}$.  The blue
-    and red curves show $\delta t_{\star}=10^7~{\rm yr}$ and $t_{\rm
-      scale}=10^8~{\rm yr}$, respectively; longer scale times look
-    quite similar to the red curves.  Dashed, dotted, and dot-dashed
-    line styles show star formation rates that have declined to
-    fractions $\iota= 0.001$, $\iota = 0.1$, and $\iota = 0.3$ of
-    their halo-averaged values, respectively. }
+  \includegraphics[width=\columnwidth]{bumpy.pdf}
+  \caption{\label{fig:NickPlot2} Effective wind velocities for
+    nonstandard star formation histories.  The black curves shows, for
+    reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$,
+    and gray curves show wind heating resulting from perturbed star
+    formation histories of the form of
+    equation~\eqref{sfrPerturbed}. In the top panel the star formation
+    rate declines for a time, $\delta t_*=10^{7}$ years to
+    fractions $\iota= 0.001$ (dashed), $\iota =0.1$ (dotted), and
+    $\iota = 0.3$ (dot-dashed) of the halo averaged value. The bottom
+    panel shows results for $\delta t_*=10^{8}$ years and
+    $\iota$=0.001 (dashed) and 0.1 (dotted).}
   \end{figure}
@@
 \begin{equation}
-\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/\delta t_{\star}) + \iota \right).
+\mathcal{S}(t) = S(t) \times
+\left(\frac{2}{\pi}(1-\iota)\arctan(t/\delta t_{\star}) + \iota
+\right).
+\label{eq:sfrPerturbed}
 \end{equation}
-This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.
-In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $\delta t_{\star}$ into the past.
-As we can see in Fig.
-\ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $\delta t_{\star} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
-
- % Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.
-For comparison we also show cases in which the star formation rate is modulated sinuisoidally from its average value.
-It seems that ``bumpy'' SF histories severely diminish $v_{\rm w}$ if the timescale for SF variability is a factor of a few or more greater than the duration of high-velocity winds (either 10 or 40 Myr).
-{\bf AG: this plot still uses the old ad hoc vw
-  % prescription? If so it would need to be fixed. In any case, we still
-  % differ in detail on the vw from stars}.
+This function convolves the recent ($z \approx 0$) halo-averaged star
+formation history with local variation to give a more pessimistic
+estimate for the value of $\tilde{v}_{\rm w}$.  In particular,
+replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star
+formation rate to a fraction $\epsilon$ of its halo-averaged value,
+and does so for a characteristic time $\delta t_{\star}$ into the
+past.  As we can see in Fig. \ref{fig:NickPlot2}, this dramatically
+lowers the effective wind speed when both $\delta t_{\star} \gtrsim
+10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too
+modest of an effect to change the thermal stability properties of the
+flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$
+may change significantly).
 

### 2015-04-08 windheat.tex
caption adjustment

@@
     and gray curves show wind heating resulting from perturbed star
-    formation histories of the form of
-    equation~\eqref{sfrPerturbed}. In the top panel the star formation
-    rate declines for a time, $\delta t_*=10^{7}$ years to
-    fractions $\iota= 0.001$ (dashed), $\iota =0.1$ (dotted), and
-    $\iota = 0.3$ (dot-dashed) of the halo averaged value. The bottom
-    panel shows results for $\delta t_*=10^{8}$ years and
-    $\iota$=0.001 (dashed) and 0.1 (dotted).}
+    formation histories given by equation~\eqref{eq:sfrPerturbed}. In
+    the top panel the star formation rate declines for a time, $\delta
+    t_*=10^{7}$ years to fractions $\iota= 0.001$ (dashed), $\iota
+    =0.1$ (dotted), and $\iota = 0.3$ (dot-dashed) of the halo
+    averaged value. The bottom panel shows results for $\delta
+    t_*=10^{8}$ years and $\iota$=0.001 (dashed) and 0.1 (dotted).}
   \end{figure}

### 2015-04-08 ms.tex
adjusting numbers in bumpy description

@@
 $v_{\rm w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$,
-$v_{\rm w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but
+$v_{\rm w}^\star \approx 400~{\rm km~s}^{-1}$ in most galaxies, but
 for smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
 exception to this is in galactic nuclei with $M_\bullet \gtrsim
-5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
+10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
 of average cosmic SFHs is appropriate provided
@@
 heating rates for all but the most massive galaxies (where Ia
-explosions dominate) will fall by a factor $\approx 5$ from our
+explosions dominate) will fall by a factor $\approx 4$ from our
 fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

### 2015-04-08 ms.tex
changing mn2e

@@
 \makeatother
+%\renewcommand{\citeauthoryear}[3]{}
+
 \usepackage{threeparttable}
@@
   We calculate steady-state, one-dimensional hydrodynamic profiles of
-  hot gas in slowly accreting (``quiescent") galactic nuclei for a range of
-  central black hole masses $M_{\bullet}$, parameterized gas heating
-  rates, and observationally-motivated stellar density profiles.  Mass
-  is supplied to the circumnuclear medium by stellar winds, while gas
-  is heated primarily by stellar winds, supernovae, and black hole
-  feedback.  Analytic estimates are derived for the stagnation radius
-  (where the radial velocity of the gas passes through zero) and the
-  black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and the gas heating efficiency, the latter being related to the star-formation history.
-We assess the conditions under which radiative instabilities develop, separately in the case
-  of a single burst of star formation and for the average star formation history predicted by cosmological simulations for galaxies hosting black holes of a given mass.
-By combining a sample of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent galactic nuclei with our results for $\dot{M}(M_{\bullet})$ we show that most nuclei are consistent with accreting in a steady-state, thermally-stable manner.
-However, thermally-stable accretion cannot explain the short average growth times of low mass black holes in the local universe, which must instead result from gas being fed in from
-  large radii, due either to galaxy mergers or thermal instabilities acting on larger, galactic scales.
-Our results have implications for attempts to constrain the occupation fraction of SMBHs in low mass galaxies using the mean
-  $L_{\rm X}-M_{\bullet}$ correlation, as well as the predicted diversity of the
-  circumnuclear densities encountered by relativistic outflows from
-  tidal disruption events.
+  hot gas in slowly accreting (``quiescent") galactic nuclei for a
+  range of central black hole masses $M_{\bullet}$, parameterized gas
+  heating rates, and observationally-motivated stellar density
+  profiles.  Mass is supplied to the circumnuclear medium by stellar
+  winds, while gas is heated primarily by stellar winds, supernovae,
+  and black hole feedback.  Analytic estimates are derived for the
+  stagnation radius (where the radial velocity of the gas passes
+  through zero) and the black hole accretion rate, $\dot{M}$, as a
+  function of $M_{\bullet}$ and the gas heating efficiency, the latter
+  being related to the star-formation history.  We assess the
+  conditions under which radiative instabilities develop, separately
+  in the case of a single burst of star formation and for the average
+  star formation history predicted by cosmological simulations for
+  galaxies hosting black holes of a given mass.  By combining a sample
+  of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent
+  galactic nuclei with our results for $\dot{M}(M_{\bullet})$ we show
+  that most nuclei are consistent with accreting in a steady-state,
+  thermally-stable manner.  However, thermally-stable accretion cannot
+  explain the short average growth times of low mass black holes in
+  the local universe, which must instead result from gas being fed in
+  from large radii, due either to galaxy mergers or thermal
+  instabilities acting on larger, galactic scales.  Our results have
+  implications for attempts to constrain the occupation fraction of
+  SMBHs in low mass galaxies using the mean $L_{\rm X}-M_{\bullet}$
+  correlation, as well as the predicted diversity of the circumnuclear
+  densities encountered by relativistic outflows from tidal disruption
+  events.
 \end{abstract}
@@
 
-\item Heating from SMBH feedback, unlike stellar heating, depends on the SMBH accretion rate, which is itself a function of the heating rate.
-Compton heating is generally unimportant compared to stellar wind heating for the average SFH, but it can dominate in the case of an impulsive star burst (Fig.~\ref{fig:vwSourcesImp}).
-Although in principle Compton heating is sufficiently high to prevent thermal instabilities when acting alone, i.e.
-$\dot{M}_{C} \lesssim \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not however be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.
-Kinetic feedback could also be important in determining $\dot{M}(M_{\bullet}$) when stellar heating is weak ($\S\ref{sec:kinetic}$) but is more challenging to quantify.
-
-\item Stellar wind heating from the average SFH is sufficient to permit thermally-stable, steady-state accretion.
-However, the resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).
-However, these differences may not be discriminating given the huge uncertainty in translating the predicted gas inflow rate on parsec scales to the disk X-ray luminosity.
+\item Heating from SMBH feedback, unlike stellar heating, depends on
+  the SMBH accretion rate, which is itself a function of the heating
+  rate.  Compton heating is generally unimportant compared to stellar
+  wind heating for the average SFH, but it can dominate in the case of
+  an impulsive star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in
+  principle Compton heating is sufficiently high to prevent thermal
+  instabilities when acting alone, i.e. $\dot{M}_{C} \lesssim
+  \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not
+  however be capable of truly stabilizing the flow given its inability
+  to respond instantaneously to local changes in the properties of the
+  gas.  Kinetic feedback could also be important in determining
+  $\dot{M}(M_{\bullet}$) when stellar heating is weak
+  ($\S\ref{sec:kinetic}$) but is more challenging to quantify.
+
+\item Stellar wind heating from the average SFH is sufficient to
+  permit thermally-stable, steady-state accretion.  However, the
+  resulting average Eddington-normalized accretion rate is predicted
+  to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in
+  tension with the (also weak) downsizing trend of measured nuclear
+  X-ray luminosities of early-type galaxies (e.g.,
+  \citealt{Miller+15}).  However, these differences may not be
+  discriminating given the huge uncertainty in translating the
+  predicted gas inflow rate on parsec scales to the disk X-ray
+  luminosity.
 
@@
 
-%    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
- %   the observed nuclear x-ray luminosities in quiescent, early type
-  %  galaxies could be understood as coming from thermally stable
-   % steady-state accretion of stellar winds shed in the galactic
-    %nucleus.
-
 We conclude by drawing attention to the following limitations of our model
     \begin{enumerate}
-    \item Overall the accretion rate onto the central SMBH will be strongly
-    tied to the properties of the stellar population (e.g. age) within
-    the sphere of influence of the black hole. Thus, our model cannot
-    say anything definitive about the mode accretion for individual
-    galaxies which may have significant variations about our assumed
-    average SFHs.
-    \item Also, the SFH of bulges may (and probably
-      does) systematically differ from the average star formation
-      history for galaxies as a whole.
-    \item Furthermore, there could be a radial gradient in the star
-      formation history within a given bulge... 
-     {\bf AG this section needs to be finished...}
+    \item We assume that there is no large scale inflow of gas to the
+      nucleus, and the only source of gas feeding the black hole is
+      stellar wind mass loss from the local stellar population. Thus,
+      our estimates of gas density are a lower bound on the nuclear
+      gas density {\bf AG: make sense?}.
+
+      As we have already pointed out AGN activity cannot be explained
+      by steady thermally stable accretion of mass lost from stellar
+      winds.
+
+    \item Overall the accretion rate onto the central SMBH will be
+      strongly tied to the properties of the stellar population
+      (e.g. age) within the sphere of influence of the black
+      hole. Thus, our model cannot say anything definitive about the
+      mode accretion for individual galaxies unless something is known
+      about their specific star formation history.
+
+    \item We adopt halo average star formation rates measured in
+      cosmological simulations by \citet{MosterNaab+:2013a}, and
+      neglect any spatial variation in the star formation rate for any
+      given galaxy. Galaxies with masses$\gsim 7\times 10^{10} \Msun$,
+      assemble their stars from the inside out
+      \citet{PerezCidFernandes+:2013a}
+      and so for a given halo mass
+      the galactic nucleus may be significantly older than in our
+      model and thus more prone to thermal instability.
+
+      On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
+      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
+      (generally unresolved) emission in excess of the inward
+      extrapolation of the Nuker law, and noted that these nuclei are bluer
+      than the background galaxy starlight, suggesting the presence of
+      younger stars towards the center of the galaxy.
+
+      In fact it is possible that the mass injection is in fact
+      dominated by a nuclear star cluster with a break radius on
+      parsec scales. Although this is much smaller than our fiducial
+      break radius (100 pc). If the heating is sufficiently high
+      moving the break radius inwards would merely change the outer
+      gas density profile, without changing the stagnation radius in
+      the flow and thus the accretion rate onto the black hole. Of
+      course if one moves the break radius to where the stagnation
+      radius would be the stagnation radius would move inwards
+      somewhat. However note the for high heating rate ($v_w \gsim 500
+      $ km/s and small black hole masses $\Mbh \lsim 10^7 \Msun$), we
+      predict stagnation radii smaller than a parsec.
+
     \end{enumerate}

### 2015-04-08 ms.tex
blah

@@
       assemble their stars from the inside out
-      \citet{PerezCidFernandes+:2013a}
+      \citep{PerezCidFernandes+:2013a}
       and so for a given halo mass

### 2015-04-09 ms.tex
comment

@@
       assemble their stars from the inside out
-      \citep{PerezCidFernandes+:2013a}
-      and so for a given halo mass
+      \citep{PerezCidFernandes+:2013a} and so for a given halo mass
       the galactic nucleus may be significantly older than in our
@@
       than the background galaxy starlight, suggesting the presence of
-      younger stars towards the center of the galaxy.
-
-      In fact it is possible that the mass injection is in fact
-      dominated by a nuclear star cluster with a break radius on
-      parsec scales. Although this is much smaller than our fiducial
-      break radius (100 pc). If the heating is sufficiently high
-      moving the break radius inwards would merely change the outer
-      gas density profile, without changing the stagnation radius in
-      the flow and thus the accretion rate onto the black hole. Of
-      course if one moves the break radius to where the stagnation
-      radius would be the stagnation radius would move inwards
-      somewhat. However note the for high heating rate ($v_w \gsim 500
-      $ km/s and small black hole masses $\Mbh \lsim 10^7 \Msun$), we
-      predict stagnation radii smaller than a parsec.
+      younger stars towards the center of the galaxy {\bf AG mass
+        threshold for this effect}.
+
+      In fact it is possible that the mass injection is dominated by a
+      nuclear star cluster with a break radius on parsec
+      scales. Although this is much smaller than our fiducial break
+      radius (100 pc). If the heating is sufficiently high moving the
+      break radius inwards would merely change the outer gas density
+      profile, without changing the stagnation radius in the flow and
+      thus the accretion rate onto the black hole. Of course if one
+      moves the break radius inside where the stagnation radius would
+      be for large break radii, the stagnation radius would move
+      inwards somewhat. However note the for high heating rate ($v_w
+      \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
+      \Msun$), we predict stagnation radii smaller than a parsec.
 

### 2015-04-09 ms.tex
got rid of the spurrious WM citation.

@@
 Understanding why most SMBHs appear to be inactive requires
-characterizing their gaseous environments.  Gas near the SMBH sphere of
-influence, hereafter denoted the `circumnuclear medium' (CNM),
+characterizing their gaseous environments.  Gas near the SMBH sphere
+of influence, hereafter denoted the `circumnuclear medium' (CNM),
 controls the mass accretion rate, $\dot{M}$.  The accretion rate in
-turn determines the SMBH luminosity and the feedback of its energy and momentum output on larger scales.
-The presence of dense gas in the nucleus may lead to runaway cooling, resulting in bursty episodes of star formation and AGN
-activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
+turn determines the SMBH luminosity and the feedback of its energy and
+momentum output on larger scales.  The presence of dense gas in the
+nucleus may lead to runaway cooling, resulting in bursty episodes of
+star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07};
+\citealt{Ciotti+10}).
 
 Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
-properties of the nucleus informs key questions related to
-the co-evolution of SMBHs and their host galaxies with cosmic time
-(e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  In the low redshift universe, SMBH growth
-is dominated by low mass black holes,
-$M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a
-fact often attributed to the trend of `cosmic
-down-sizing' resulting from hierarchical structure growth (e.g,
-\citealt{Gallo+08}).
-However, the physical processes by which low mass black holes accrete could in principle be distinct from those operating at higher SMBH masses and accretion rates in high redshift quasars.
-One key question is
-whether SMBHs grow primarily by the accretion of gas fed in directly from
-galactic or extra-galactic scales, or whether significant growth
-can result also from local stellar mass loss in the nuclear region.
+properties of the nucleus informs key questions related to the
+co-evolution of SMBHs and their host galaxies with cosmic time
+(e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  In the
+low redshift universe, SMBH growth is dominated by low mass black
+holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$
+(e.g.~\citealt{Heckman+04}), a fact often attributed to the trend of
+`cosmic down-sizing' resulting from hierarchical structure growth
+(e.g, \citealt{Gallo+08}).  However, the physical processes by which
+low mass black holes accrete could in principle be distinct from those
+operating at higher SMBH masses and accretion rates in high redshift
+quasars.  One key question is whether SMBHs grow primarily by the
+accretion of gas fed in directly from galactic or extra-galactic
+scales, or whether significant growth can result also from local
+stellar mass loss in the nuclear region.
 
@@
 quiescent SMBHs would shed new light on a variety of observations,
-such as the occupation fraction of SMBHs in low mass
-galaxies.  \citet{Miller+15} use the average relationship between the
-nuclear X-ray luminosities, $L_{X}$, of a sample of early type
-galaxies and their associated SMBH masses to infer tentative evidence that the
-SMBH occupation fraction becomes less than unity for galaxies with stellar
+such as the occupation fraction of SMBHs in low mass galaxies.
+\citet{Miller+15} use the average relationship between the nuclear
+X-ray luminosities, $L_{X}$, of a sample of early type galaxies and
+their associated SMBH masses to infer tentative evidence that the SMBH
+occupation fraction becomes less than unity for galaxies with stellar
 masses $M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
@@
 fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
-the instrument detection threshold, an assumption which is questionable if
-different physical processes control the accretion rates onto the
-lowest mass SMBHs.
+the instrument detection threshold, an assumption which is
+questionable if different physical processes control the accretion
+rates onto the lowest mass SMBHs.
 
@@
 (\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-Unlike previous works, which focused primarily on modeling individual galaxies, here
-we systematically analyze the CNM properties across a range of galaxy properties, including different SMBH masses, stellar density profiles, and
-star formation histories (SFHs; \citealt{WangMerritt:2004a}).
+Unlike previous works, which focused primarily on modeling individual
+galaxies, here we systematically analyze the CNM properties across a
+range of galaxy properties, including different SMBH masses, stellar
+density profiles, and star formation histories (SFHs).
 
@@
 radius may move to much larger radii or not exist at all, in which
-case nearly entire ISM of the galaxy is flowing towards the SMBH.  A goal
-of this work is to assess under what conditions a stagnation radius
-exists, as this question is intimately tied to that of cooling
+case nearly the entire ISM of the galaxy is flowing towards the SMBH.
+A goal of this work is to assess under what conditions a stagnation
+radius exists, as this question is intimately tied to that of cooling
 instability.

### 2015-04-09 ms.tex
language

@@
 
-Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for each of
+Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for a sample of
 our numerical solutions in Eddington units for different values of
@@
   (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
-  are the velocity dispersions according to $\Mbh-\sigma$
-  \citep{McConnellMa+:2011a}.}
+  are the value of the stellar velocity dispersion, $\sigma_0$,
+  approximated as $\sqrt{3}$ time the $\sigma$ from the $\Mbh-\sigma$
+  relation \citep{McConnellMa+:2011a}.}
 \end{figure}
@@
 The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
-time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion rate
-shown in the top panel.  For SMBHs which accrete steadily at the rate set by the
-stellar wind heating due to the average star formation
+time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion
+rate shown in the top panel.  For SMBHs which accrete steadily at the
+rate set by the stellar wind heating due to the average star formation
 history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
@@
 hierarchical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In support of this,
-\citet{Kauffmann&Heckman09} find that the growth of low mass black
-holes is dominated by young stellar bulges which have a log normal
-distribution of Eddington ratios peaked at $\Mdot/\dot{M}_{\rm edd} \sim
-0.01$. That this distribution is insensitive to galaxy properties
-suggests that it is set by SMBH feedback instead of the nuclear gas
-supply.
+galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In
+support of this, \citet{Kauffmann&Heckman09} find that the growth of
+low mass black holes is dominated by young stellar bulges which have a
+log normal distribution of Eddington ratios peaked at
+$\Mdot/\dot{M}_{\rm edd} \sim 0.01$. That this distribution is
+insensitive to galaxy properties suggests that it is set by SMBH
+feedback instead of the nuclear gas supply.
 

### 2015-04-09 ms.tex
colors

@@
   for solutions found to be thermally unstable for all values of $\eta
-  > 0.02$ are denoted as {\bf TI}.
+  \geq 0.02$ are denoted as {\bf TI}.
 \end{tablenotes}
@@
   heating rate provided at $z = 0$ by the average star formation
-  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
+  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal
   lines show the maximum accretion set by Ia supernovae blow-out
@@
   near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
-  Eddington ratios inferred for SgrA* from
-  \citet{Quataert:2004a} (black circles), for NGC3115 from
-  \citet{ShcherbakovWong+:2014a} (black diamonds), and for
-  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
-  in units of the Hubble time $\th$ for each of the accretion rates
-  shown in the top panel.}
+  Eddington ratios inferred for SgrA* from \citet{Quataert:2004a}
+  (gray circles), for NGC3115 from \citet{ShcherbakovWong+:2014a}
+  (gray diamonds), and for the Swift J1644+57 TDE from
+  \citet{BergerZauderer+:2012a} (gray triangles) {\it Bottom panel:}
+  Growth times $\Mbh/\Mdot$ in units of the Hubble time $\th$ for each
+  of the accretion rates shown in the top panel.}
 \end{figure}

### 2015-04-09 ms.tex
spellimg

@@
 
-If prsent, thermal
+If present, thermal
 instabilities may cause the CNM to undergo cyclic

### 2015-04-09 be.tex
caption.

@@
 
-Analysis of equation (\ref{eq:enthAnal}) results in the following interpretation of the behavior of the Bernoulli integral as a function of the heating rate.
-When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow with positive kinetic energy at infinity.
-However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative near the break radius for some value of $\rs$.
-When $\zeta$ is moderately less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$, which increases from 0 when $\zeta = \zeta_c$ to $\sim r_{b}$ as $\zeta$ is decreased well below $\zeta_c$.
+Analysis of equation (\ref{eq:enthAnal}) results in the following
+interpretation of the behavior of the Bernoulli integral as a function
+of the heating rate.  When the rate of external heating is high
+($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an
+outflow with positive kinetic energy at infinity.  However, as $\zeta$
+is decreased, there exists a critical value of $\zeta = \zeta_{c}$
+below which $\mathcal{B}$ becomes negative near the break radius for
+some value of $\rs$.  When $\zeta$ is moderately less than $\zeta_c$,
+then we can have still $\mathcal{B} > 0$ at the break radius, but only
+if $\rs$ exceeds a minimum value, $r_{\rm s,min}$, which increases
+from 0 when $\zeta = \zeta_c$ to $\sim r_{b}$ as $\zeta$ is decreased
+well below $\zeta_c$.
 
-The critical heating value $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).
-Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core galaxies).
-Likewise the minimum $r_{\rm s,min}/r_{b}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.86\zeta_c$, as shown in the bottom panel of Fig.~\ref{fig:zetaCrit}.
-As $\zeta \rightarrow 0.86\zeta_c$ our numerical simulations show that that the stagnation radius diverges from its value predicted by equations (\ref{eq:stag_analytic}) and (\ref{eq:densSlope}) and moves out to the break radius.
+The critical heating value $\zeta_c$ is an increasing function of
+$r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp
+galaxies, since a greater heating rate is required to unbind gas from
+a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically,
+we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$
+(see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core
+galaxies). Likewise the minimum $r_{\rm s,min}/r_{b}$ is an increasing
+function of $\zeta/\zeta_{c}$, approaching unity for $\zeta <
+0.86\zeta_c$, as shown in the bottom panel of Fig.~\ref{fig:zetaCrit}.
+As $\zeta \rightarrow 0.86\zeta_c$ our numerical simulations show that
+that the stagnation radius diverges from its value predicted by
+equations (\ref{eq:stag_analytic}) and (\ref{eq:densSlope}) and moves
+out to the break radius.
 
@@
   of the stagnation radius for which $\mathcal{B} > 0$ at the break
-  radius as a function of $\zeta/\zeta_c < 1$. }
+  radius as a function of $\zeta/\zeta_c < 1$ for $\rb/\rinf=10$.}
 \end{figure}

### 2015-04-09 ms.tex
caption.

@@
 X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
-represents a maximum value, which does not for instance account for suppression
-of the SMBH accretion rate due to outflows from the accretion disk on
-small radial scales (e.g., \citealt{Blandford&Begelman99}).
-Furthermore, our SFH-averaged accretion rates are derived using analytic expressions for the stagnation radius that may underpredict the true accretion rate if $\zeta < \zeta_c$, as may occur in massive core galaxies with large break radii.
-If the actual radiative efficiency is lower than our fiducial assumption,
-then many of the X-ray detections would lie above the predicted value
-of $\langle L_X \rangle$ for stable accretion (black line).  In this
-case the X-ray detected galaxies experience less heating than
-average galaxies of the same mass, and may not be stably accreting at
-all.  This is particularly plausible because the \citet{Miller+15} sample includes only early-type galaxies, with older stellar
-populations than the average for their black hole mass.
+represents a maximum value, which does not for instance account for
+suppression of the SMBH accretion rate due to outflows from the
+accretion disk on small radial scales (e.g.,
+\citealt{Blandford&Begelman99}).  Furthermore, our SFH-averaged
+accretion rates are derived using analytic expressions for the
+stagnation radius that may underpredict the true accretion rate if
+$\zeta < \zeta_c$, as may occur in massive core galaxies with large
+break radii.  If the actual radiative efficiency is lower than our
+fiducial assumption, then many of the X-ray detections would lie above
+the predicted value of $\langle L_X \rangle$ for stable accretion
+(green line).  In this case the X-ray detected galaxies experience
+less heating than average galaxies of the same mass, and may not be
+stably accreting at all.  This is particularly plausible because the
+\citet{Miller+15} sample includes only early-type galaxies, with older
+stellar populations than the average for their black hole mass.
 
 Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
-  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates that even if
-Compton heating could act to stabilize the flow in a quasi-steady state (which, as already discussed, is unlikely), the magnitude of the heating is insufficient to produce a thermally stable accretion rate given conditions
-corresponding to the average SFH.
-
-If present, thermal
-instabilities may cause the CNM to undergo cyclic
+  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates
+that even if Compton heating could act to stabilize the flow in a
+quasi-steady state (which, as already discussed, is unlikely), the
+magnitude of the heating is insufficient to produce a thermally stable
+accretion rate given conditions corresponding to the average SFH.
+
+If present, thermal instabilities may cause the CNM to undergo cyclic
 oscillations of rapid cooling and high accretion rates, followed by
@@
 elliptical galaxies on large scales and long timescales
-(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes observations
-showing that a fraction of early-type galaxies in the local universe
-have undergone recent ($< 1-2$ Gyr old) star formation episodes
-(\citealt{Donas+07}).
+(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes
+observations showing that a fraction of early-type galaxies in the
+local universe have undergone recent ($< 1-2$ Gyr old) star formation
+episodes (\citealt{Donas+07}).
 
@@
 between instabilities and periodic nuclear outbursts.
-
-% Due to their
-%deeper potential well on scales of the sphere of influence, core galaxies are more likely to possess higher accretion rates and
-%potentially be thermally unstable for a fixed wind heating rate than
-%cusp galaxies.
 
@@
 
-If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$ in Fig
-\ref{fig:miller} are indeed in a state of thermally-unstable cyclic behavior, then a subset of the galaxies with X-ray upper limits may contribute to a separate population of thermally stable, steadily accreting nuclei.
-Such a population could include SgrA*, which has a much lower X-ray luminosity for its black hole mass than predicted by the \citet{Miller+15} trend.
-A potentially bimodal population of steady and cyclic galactic nuclei calls into question the physical justification of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass galaxies.
+If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$
+in Fig \ref{fig:miller} are indeed in a state of thermally-unstable
+cyclic behavior, then a subset of the galaxies with X-ray upper limits
+may contribute to a separate population of thermally stable, steadily
+accreting nuclei.  Such a population could include SgrA*, which has a
+much lower X-ray luminosity for its black hole mass than predicted by
+the \citet{Miller+15} trend.  A potentially bimodal population of
+steady and cyclic galactic nuclei calls into question the physical
+justification of using simple extrapolations of power-law fits to the
+$L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
+constrain the occupation fraction of SMBHs in the nuclei of low mass
+galaxies.
 
@@
 
-\item Type Ia SNe only provide a continuous heating source exterior to the Ia radius $\rIa$ (eq.~[\ref{eq:rIa}]) where the time between subsequent SNe exceeds the dynamical timescale.
-Non-Ia heating due to the average SFH results in $\rs <\rIa$, except for the most massive galaxies (Fig.~\ref{fig:vwSources}).
-However, if $\rs$ does approach or exceed $\rIa$, then the SN Ia heating is usually sufficiently large to prevent $\rs$ from greatly exceeding $\rIa$.
-SNe Ia thus regulates the SMBH accretion rate below the value $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high mass elliptical galaxies with large break radii and $\zeta(v_w^{\rm Ia}) \gtrsim \zeta_c$.
+\item Type Ia SNe only provide a continuous heating source exterior to
+  the Ia radius $\rIa$ (eq.~[\ref{eq:rIa}]) where the time between
+  subsequent SNe exceeds the dynamical timescale.  Non-Ia heating due
+  to the average SFH results in $\rs <\rIa$, except for the most
+  massive galaxies (Fig.~\ref{fig:vwSources}).  However, if $\rs$ does
+  approach or exceed $\rIa$, then the SN Ia heating is usually
+  sufficiently large to prevent $\rs$ from greatly exceeding $\rIa$.
+  SNe Ia thus regulates the SMBH accretion rate below the value
+  $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high
+  mass elliptical galaxies with large break radii and $\zeta(v_w^{\rm
+    Ia}) \gtrsim \zeta_c$.
 
@@
 
-Thermally stable accretion models can reproduce the observed scatter in nuclear X-ray luminosities at fixed $\Mbh$ of 2-4 orders of magnitude due to combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in SFH from galaxy to galaxy, or from time to time due to burstiness in the SFH (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas (e.g.~\citealt{Li+13}).
+  Thermally stable accretion models can reproduce the observed scatter
+  in nuclear X-ray luminosities at fixed $\Mbh$ of 2-4 orders of
+  magnitude due to combination of (1) intrinsic scatter in the SMBH
+  scaling relations; (2) stochastic variation in SFH from galaxy to
+  galaxy, or from time to time due to burstiness in the SFH
+  (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of
+  inflowing mass which is lost to small scale outflows from the SMBH
+  accretion disk, due to variations in the angular momentum of the
+  accreting gas (e.g.~\citealt{Li+13}).
 

### 2015-04-09 be.tex
Stylistic changes, minor revisions. Nick

--- 2015-04-08 be.tex
@@
   of the stagnation radius for which $\mathcal{B} > 0$ at the break
-  radius as a function of $\zeta/\zeta_c < 1$. }
+  radius as a function of $\zeta /\zeta_{\rm c} < 1$ for $r_{\rm b}/r_{\rm inf}=10$.}
 \end{figure}

### 2015-04-09 ms.tex
Stylistic changes, minor revisions. Nick

@@
 
-\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
+\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas C. Stone, Brian~D.~Metzger\\
   Columbia Astrophysics Laboratory, Columbia University, 550 West 120th
@@
   profiles.  Mass is supplied to the circumnuclear medium by stellar
-  winds, while gas is heated primarily by stellar winds, supernovae,
+  winds, while energy is injected primarily by stellar winds, supernovae,
   and black hole feedback.  Analytic estimates are derived for the
@@
   being related to the star-formation history.  We assess the
-  conditions under which radiative instabilities develop, separately
+  conditions under which radiative instabilities develop, both
   in the case of a single burst of star formation and for the average
-  star formation history predicted by cosmological simulations for
-  galaxies hosting black holes of a given mass.  By combining a sample
+  star formation history predicted by cosmological simulations.  By combining a sample
   of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent
@@
 `cosmic down-sizing' resulting from hierarchical structure growth
-(e.g, \citealt{Gallo+08}).  However, the physical processes by which
+(e.g, \citealt{Gallo+08}).  However, the physical processes by which typical
 low mass black holes accrete could in principle be distinct from those
-operating at higher SMBH masses and accretion rates in high redshift
-quasars.  One key question is whether SMBHs grow primarily by the
+operating at higher SMBH masses, or those in AGN.  One key question is whether SMBHs grow primarily by the
 accretion of gas fed in directly from galactic or extra-galactic
@@
 This event was powered by an impulsive relativistic jet,
-which produced synchrotron radio emission as the jet material was
-decelerated by shock interaction with the CNM of the previously
+which produced synchrotron radio emission as the jet material
+decelerated from shock interaction with the CNM of the previously
 quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).
@@
 lower than that measured surrounding Sgr A$^{\star}$ on a similar radial scale
-(\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a TDE jet
+(\citealt{Metzger+12}; \citealt{BergerZauderer+2012a}).  However, a TDE jet
 injected into a denser CNM would be decelerated more rapidly,
-producing potentially much different radio emission than in J1644+57.
+producing potentially very different radio emission than in J1644+57.
 Variations in the properties of the CNM could help explain why most
@@
 \citet{Ho:2009a} determines the SMBH accretion rates in a sample of
-early-type galaxies using X-ray observations to determine the
+early-type galaxies by using X-ray observations to determine the
 Bondi accretion rate and based on estimates for the mass loss rate of
@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaches the SMBH due to disk outflows (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+(e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which reduce the efficiency with which the inflowing gas ultimately reaches the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
 
@@
 temperature profiles of the CNM using a physically motivated
-hydrodynamic model.  Mass is injected to the nuclear environment via
-stellar winds, while energy input results from several sources
+hydrodynamic model.  Mass is injected into the nuclear environment via
+stellar winds, while energy is input from several sources
 including stellar winds, supernovae, and AGN feedback
@@
 Unlike previous works, which focused primarily on modeling individual
-galaxies, here we systematically analyze the CNM properties across a
+galaxies, here we systematically analyze the CNM properties across a representative
 range of galaxy properties, including different SMBH masses, stellar
@@
 temporarily increase the gas accretion rate towards the nucleus until
-feedback becomes effective to shut off the flow and halt
+feedback becomes strong enough to shut off the flow and halt
 SMBH growth.
@@
 In this paper we instead focus on time-independent models, with
-sufficient heating to have negligible radiative cooling.  This
+sufficient heating to make radiative cooling negligible.  This
 approach allows us to systematically explore the relevant parameter
@@
 sphere of influence.  We are thus motivated to explore whether such
-steady flows are generally expected within the nucleus under, or
+steady flows are generally expected within the nucleus, or
 whether in most galaxies the nuclear gas content is always building
@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ will in many cases resides near the nominal Bondi
+show that $\rs$ will in many cases reside near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation
@@
 ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
-analytic results, which are justified via numerical solutions in
-$\S\ref{sec:numerical}$ we describe our numerical results.  In
+analytic results, which are justified via the numerical solutions we present in
+$\S\ref{sec:numerical}$.
+We move from a general and parametrized treatment of heating to a physically motivated one in \S \ref{sec:heating}, where we consider a range of physical processes that can inject energy into the CNM.
+In
 $\S\ref{sec:discussion}$ we discuss the implications of our results
@@
 i.e., a broken power law that transitions from an inner power law
-slope, $\Gamma$, to an outer power law slope, $\beta > \Gamma$, at a
+slope, $\Gamma$, to an outer power law slope, $\beta$, at a
 break radius, $\rb$.  Assuming the stellar population is spherically
@@
 r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
-$r \gg \rb$.  To good approximation
+$r \gg \rb$.  We can write the deprojected stellar density approximately (formally, this is the $\alpha \rightarrow \infty$ limit) as
 \begin{align}
@@
 \end{align}
-where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (inf), 
+where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence\footnote{This approximate expression agrees surprisingly well with the mean empirical scaling relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of \citet{Stone&Metzger15}, although we note that this relation has significant scatter.},
 \begin{equation}
@@
 \end{align}
-Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of a better alternative.
+Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of an obviously better alternative.
 
@@
   scatter of approximately one dex.  Most the cusp galaxies have $\rb$
-  between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In
+  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  In
 practice we calculate solutions for a range of $\rb$ only in cases
@@
 
-Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
+Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}), of the form
 \begin{equation}
@@
 
-Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
+Hydrostatic equilibrium likewise determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
 \begin{align}
@@
 stagnation radius moves to large radii, approaching the break radius
-$\rb$ in the stellar density profile, formally implying that almost
+$\rb$ in the stellar density profile, formally implying that almost the
 entire ISM of the galaxy is accreting.  In particular, in Appendix
@@
 \label{eq:zetacrit}
-\ee This result makes intuitive sense: gas is supplied to the nuclear
+\ee This result makes intuitive sense: gas is supplied to the nucleus
 by stars which are gravitationally bound to the black hole, so
@@
 the condition that the wind heating parameter be less than the local escape
-speed from near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
+speed near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
     b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
@@
 equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n
-kT/2 \mu)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
+kT/2 \mu)/|\dot{q}_{\rm rad}|$ to the free-fall time $t_{\rm ff}$ at the
 stagnation radius, as can be derived using the equality
@@
 
-Based on our numerical results (\ref{sec:numerical}) and the work of \citet{McCourt+12}) we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
+Based on our numerical results (\S \ref{sec:numerical}) and the work of \citet{McCourt+12} we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
   cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius.  This condition translates into a
@@
 where the first line for each case is derived using equation
-(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
+(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and
 the second line corresponds to the low wind heating limit $\zeta \ll
@@
       orange}), and 300 km s$^{-1}$ ({\it green}).  Different
-    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
+    line styles correspond to different values of $\Mbh$: $\Mbh=10^6
     \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
@@
   net rotation, resulting in centrifugal forces becoming important at
-  some radius $r_{\rm circ} = l^{2}_{r_{s}}/(GM_{\bullet})$.  Here
-  $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar
+  some radius $r_{\rm circ} = l^{2}_{s}/(GM_{\bullet})$.  Here
+  $l_{s} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar
   specific angular momentum near the stagnation radius, from which
@@
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincides with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
 This divergence of the stagnation radius to large radii occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii, explaining the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange triangles.
@@
 (\ref{eq:eddr_analytic}).  For high wind velocities ($v_{w} \gg
-\sigma$) the stagnation lies well inside the black hole sphere of
+\sigma$) the stagnation radius lies well inside the black hole sphere of
 influence and our analytic estimate provides a good fit to the
@@
 For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions which are already marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
+However, for solutions that are only marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
 We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
@@
 \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
-is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
-formation representative of the average SFHs of low
-mass galaxies, the stellar wind heating rate produced by stellar winds
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$, for the case of quasi-continuous star
+formation (representative of the average SFHs of low
+mass galaxies), the stellar wind heating rate produced by stellar winds
 can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
@@
 Stellar winds thus contribute a potentially important source of both
-energy and mass for the CNM.
+energy and mass to the CNM.
 An additional uncertainty results from the thermalization efficiency of massive stellar winds.
@@
   \end{align}
-  as the location exterior of which the time interval between
+  as the location exterior to which the time interval between
   subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm
@@
 Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we the ratio of heating to radiative cooling at $\rIa$ is given by
+However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find the ratio of heating to radiative cooling at $\rIa$ is given by
 \begin{align}
@@
 Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad})_{\rIa})$.
-However, for lower mass galaxies or younger stellar populations, Ia blow-out is itself unlikely to prevent cooling instabilities.
+However, for lower mass galaxies or younger stellar populations, Ia blow-out is by itself unlikely to prevent cooling instabilities.
 
@@
 \caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
-  to the total heating rate of the CNM, $\vwO$ ({\it black}),
-  including stellar wind heating ({\it orange}), Ia supernovae ({\it
+  to the total heating rate of the CNM, $\vwO$ ({\it black}):
+  stellar wind heating ({\it orange}), Ia supernovae ({\it
     green}), millisecond pulsars ({\it blue}), and compton heating
   ({\it pink}).  Each heating source varies with black hole mass
-  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a}
-  (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:}
+  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a};
+  see Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:}
   The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
@@
 subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and
+(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$
 depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
@@
 mechanisms, SMBH feedback may not be capable of truly stabilizing the
-flow given its inability to respond instantaneously to local changes
-in the properties of the gas.  Thermally unstable flow is present
+flow, given its inability to respond instantaneously to local changes
+in gas properties.  Thermally unstable flow is present
 throughout the single starburst case except at very early times,
@@
 wind heating.
-But for these massive galaxies, that Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (for low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+But for these massive galaxies, the Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (in low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
 Strikingly, we find that galactic nuclei experiencing the same
@@
 explosions dominate) will fall by a factor $\approx 4$ from our
-fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.
+fiducial volumetric averages, calculated using SFHs from \citet{MosterNaab+:2013a}.
 
@@
   lines show the maximum accretion set by Ia supernovae blow-out
-  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
+  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained
   if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
@@
   formation history (Appendix \ref{fig:NickPlot2}), this can lead to
-  order of magnitude differences in $\dot{M}$; (3) differences angular
+  order of magnitude differences in $\dot{M}$; (3) differences in angular
   momentum of the infalling gas from galaxy to galaxy, resulting in
-  differences in the fraction of the gas lost to outflows, $\Mbh$.
+  differences in the fraction of the gas lost to outflows.
   Also potentially contributing is the order of magnitude difference,
@@
 It is also possible that many of the \citet{Miller+15} sample of
-galactic nuclei are not accreting in steady state.  The value of the
+galactic nuclei are not accreting in steady state.  The 
 X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
@@
 lost from the surrounding stellar population studied in this paper.
-Gas blow-out by SN Ia cannot prevent the growth of low-mass black
+Gas blow-out by SN Ia cannot alone prevent the growth of low-mass black
 holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
@@
 Our results also have implications for the environments encountered by
-relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
+relativistic jets from TDEs.  For low-mass SMBHs with $M_{\bullet} \lesssim
 10^{7}M_{\odot}$, such as that responsible for powering the transient {\it Swift}

### 2015-04-09 ms.tex
intro

@@
 low mass black holes accrete could in principle be distinct from those
-operating at higher SMBH masses, or those in AGN.  One key question is whether SMBHs grow primarily by the
+operating at higher SMBH masses, or those in AGN.  Of key importance is whether SMBHs grow primarily by the
 accretion of gas fed in directly from galactic or extra-galactic
@@
 
-In this paper we instead focus on time-independent models, with
-sufficient heating to make radiative cooling negligible.  This
-approach allows us to systematically explore the relevant parameter
+In this paper we instead focus on time-independent models, in cases when the nuclear gas receives sufficient heating to render radiative cooling negligible.
+This approach allows us to systematically explore the relevant parameter
 space and to derive analytic expressions that prove useful in
@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ will in many cases reside near the nominal Bondi
+show that $\rs$ will usually reside near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation
@@
 case nearly the entire ISM of the galaxy is flowing towards the SMBH.
-A goal of this work is to assess under what conditions a stagnation
-radius exists, as this question is intimately tied to that of cooling
+Here we assess under what conditions a stagnation
+radius exists, a question intimately tied to that of cooling
 instability.

### 2015-04-09 ms.tex
2.2

@@
 measure the radial surface brightness profiles for hundreds of nearby
-early type galaxies. The measured brightness profile is generally
-well-fit by a ``Nuker" law parameterization:
+early type galaxies. The measured profile is fit by a ``Nuker" law parameterization:
 \begin{equation}
@@
 slope, $\Gamma$, to an outer power law slope, $\beta$, at a
-break radius, $\rb$.  Assuming the stellar population is spherically
-symmetric, this corresponds to a stellar density $\rhostar \propto
+break radius, $\rb$.  If the stellar population is spherically
+symmetric, then this corresponds to a 3D stellar density $\rhostar \propto
 r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
@@
 
-We fix $\beta = 2$ because our results are
-generally not sensitive to the properties of the gas flow on radial
-scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
+We fix $\beta = 2$ because our results are not overly sensitive to the properties of the gas flow on radial scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
 however, necessary to obtain a converged steady state for some regions
@@
   of volumetrically, but our expressions are equivalent.}, although
-$\eta$ is significantly higher for continuous SFHss
+$\eta$ is significantly higher for continuous SFHs
 (bottom panel of Fig.~\ref{fig:vwSources}).
@@
 and energy relative to the mean flow.  Physically, these result from
-the mismatch between the properties of virialized gas injected locally
-by stellar winds and the mean properties of the background flow.  The
-term $\propto -q c_{s}^{2}$ is important because it acts to potentially stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
+the mismatch between the properties of virialized gas injected by stellar winds and the mean background flow.  The
+term $\propto p/\rho = c_{s}^{2}$ is important because it acts to stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
 
@@
 accounts for external heating sources (e.g.,
-\citealt{ShcherbakovWong+:2014a}).  The first term approximates the
-minimum amount of shock heating from stellar winds due to the random
-movement of stars with respect to one another at the characteristic
-velocity of 
+\citealt{ShcherbakovWong+:2014a}), where
 \be\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
@@
 \label{eq:sigmarel}
-\ee where the first term is the velocity dispersion of the power law
-stellar density profile in the SMBH potential.  The second term,
-$\sigma_0\approx 3 \sigma^2$ is a constant, motivated by the observed
+\ee 
+is the stellar velocity dispersion and which accounts for the minimal amount of shock heating from stellar winds due to the random motion of stars in the SMBH potential, while $\sigma_0^{2} \approx 3 \sigma^2$ is assumed to be constant, corresponding to the observed
 velocity dispersion outside of the SMBH sphere of influence
-\citep{ChaeBernardi+:2014a}, where $\sigma$ is the velocity dispersion
-in the $\Mbh-\sigma$ relation (eq.~[\ref{eq:Msigma}]).  The second
-component of the total heating, $v_{w}^{2}$, parameterizes all
-additional sources of energy input, including faster winds from young
-stars, millisecond pulsars, supernovae, AGN feedback, etc.  We assume
+\citep{ChaeBernardi+:2014a}.  The second term, $v_{w}^{2}$, parameterizes additional sources of energy input, including faster winds from young
+stars, millisecond pulsars, supernovae, AGN feedback, etc  ($\S\ref{sec:heating}$).  We assume
 that $v_w$ is constant with radius, i.e. that the volumetric heating
-rate is proportional to the local stellar density.  The value of $v_w$
-will in general depend on the SMBH mass and the age of the stellar
-population ($\S\ref{sec:heating}$).
+rate is proportional to the local stellar density.  
+%The value of $v_w$
+%will in general depend on the SMBH mass and the age of the stellar
+%population ($\S\ref{sec:heating}$).
 

### 2015-04-09 ms.tex
2.3

@@
 
-To isolate the physics of greatest interest, our baseline calculations
+To isolate the physics of interest, our baseline calculations
 neglects three potentially important effects: heat conduction,
-radiative cooling, and rotation.  Electron heat conduction results in
-an an additional term on the right hand side of the entropy equation
-of the form:
+radiative cooling, and rotation.  Heat conduction results in
+an an additional heating term in equation (\ref{eq:dsdt}),
 \begin{equation}
@@
  weak magnetic field that is oriented perpendicular to the flow could
- suppress the conductivity by greatly reducing the electron mean free
+ suppress the conductivity by reducing the electron mean free
  path.  However, for radially-decreasing temperature profiles of
  interest, the flow is susceptible to the magneto-thermal instability
- (\citealt{Balbus01}), the non-linear evolution of which is believed
- to result in a radially-directed field geometry
- (\citealt{Parrish&Stone07}).  We show later in
- $\S\ref{sec:conductivity}$ that neglecting conductivity results in at
- most only order-unity errors in the key properties of the solutions.
+ (\citealt{Balbus01}), the non-linear evolution of which results in a radially-directed field geometry
+ (\citealt{Parrish&Stone07}).  In $\S\ref{sec:conductivity}$ we show that neglecting conductivity results in at
+ most order-unity errors in the key properties of the solutions.
 
@@
 \end{equation}
-where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is
+where $n \equiv \rho/\mu m_p$ and $\Lambda(T)$ is
 the cooling function.  We neglect radiative cooling in our baseline
@@
 wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-However, once radiative cooling becomes important compared to other
+Once radiative cooling becomes important compared to other
 sources of heating and cooling, its presence leads to thermal
 instability (e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be accounted for
-by our 1D time-independent model.  A main goal of this work is to use
-solutions neglecting radiation to ascertain over what range of
-physical conditions cooling instabilities are most likely to develop
+by our 1D time-independent model.  Our goal is to use solutions which neglect radiation to determine over what range of conditions cooling instabilities will develop
 ($\S\ref{sec:instability}$).
@@
 interested in the steady-state inflow/outflow solution (assuming one
-exists), the time-dependent equations are solved to avoid numerical
+exists), we solve the time-dependent equations to avoid numerical
 issues that arise near the critical sonic points, of which there are
 up to two because of the supersonic inflow on small radial scales and
-a possible supersonic outflow on large scales.  Also note that our
+a possible supersonic outflow on large scales.  Our
 solutions can be scaled to any value of the mass input parameter,
@@
 $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be
-specified when cooling or thermal conduction are included, since these
-scale as gas density to a different power.  We check the accuracy of
+specified when cooling or thermal conduction are included.  We check the accuracy of
 our numerical solutions by confirming that mass is conserved across

### 2015-04-09 ms.tex
various

@@
 \end{align}
-For low heating rates $v_w \ll \sigma_0$, the stagnation radius resides well inside the SMBH sphere of influence.
+For high heating rates $v_w \gg \sigma_0$, the stagnation radius resides well inside the SMBH sphere of influence.
 In this case $\Mstar|_{\rs}/\Mbh \ll1$, such that equation~\eqref{eq:stag_analytic} simplifies to
@@
 \ref{app:be} we show that $\rs \Rightarrow \rb$ for heating below a
-critical threshold \be \zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
+critical threshold (Fig.~\ref{fig:zetaCrit}) \be \zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
 \zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
@@
 break radius.  Equation (\ref{eq:conduction}) shows that, even when conduction is saturated, our neglect of heat conduction
-results in at most an order unity correction for plausible, causal values of
+results in at most an order unity correction for causal values of
 the saturation parameter $\phi < 0.1$.  Our numerical experiments which include conductive heating confirm this
@@
   circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well
-inside the inner sonic point of the flow (typically located at $r\lsim
+inside the inner sonic point of the flow ($r\lsim
 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).  Angular momentum should only
@@
 \begin{minipage}{18cm}
-  \caption{Summary of Numerical Solutions {\bf AG make sure the
-      headings are consistent. Mark solutions which are unstable for
-      some values of eta.}}
+  \caption{Summary of Numerical Solutions}
 \begin{tabular}{lccccccccc}
@@
 located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.  In many cases
-the supersonic transition is instigated by the transition to a steeper
-stellar density profile exterior to the outer Nuker break radius,
-making our solutions near $r_{\rm s}$ also potentially sensitive to
-the break radius value.
+the outer supersonic transition is instigated by the transition to a steeper
+stellar density profile exterior to the outer Nuker break radius.
 
@@
 Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for a sample of
-our numerical solutions in Eddington units for different values of
+our numerical solutions for different values of
 $\vwO =$ 300, 600 and 1200 km s$^{-1}$, and for both core
@@
 For high heating rates both ratios are approximately equal at the
-stagnation radius (marked as squares).  When $\dot{q}_{\rm
-heat}/\dot{q}_{\rm rad} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
-\lesssim 10$, the flow is susceptible thermal instabilities.}
+stagnation radius (squares).  When $\dot{q}_{\rm
+heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm cool}/t_{\rm ff}
+\lesssim 10$ near the stagnation radius), then the flow is susceptible to thermal instabilities.}
 \end{figure}
@@
 radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
+Radiative cooling is calculated using the cooling function from \citealt{Draine:2011a}.
 For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling
@@
 Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}, with the unstable values of $\eta$ provided in the final column.
-In contrast, changes in the solution when thermal conduction was included were always found to be minor for our choice of the saturation parameter $\phi = 0.1$.
-Conduction does, however, offset the effects of radiative cooling, making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+
+Thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$.
+Conduction may, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
 
@@
 \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
-is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$, for the case of quasi-continuous star
-formation (representative of the average SFHs of low
-mass galaxies), the stellar wind heating rate produced by stellar winds
-can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As will be shown in $\S\ref{sec:combined}$, for the case of quasi-continuous star
+formation representative of the average SFHs of low
+mass galaxies, the heating rate from stellar winds can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
 
@@
 energy and mass to the CNM.
-An additional uncertainty results from the thermalization efficiency of massive stellar winds.
-We assume this efficiency to be unity, an optimistic assumption which is partially offset by our neglect of energy input from core collapse supernovae, which contribute a heating rate comparable to that from massive stellar winds.
+However, two additional uncertainties are (1) the efficiency with which massive stellar winds thermalize their energy and (2) heating from core collapse supernovae, which is potentially comparable to that provided by stellar winds.
+We neglect both effects, but expect they will act in different directions in changing the total heating rate.
 
@@
 Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find the ratio of heating to radiative cooling at $\rIa$ is given by
+However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find the ratio of heating to radiative cooling at $\rIa$ to be given by
 \begin{align}
@@
 \end{align}
-Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad})_{\rIa})$.
-However, for lower mass galaxies or younger stellar populations, Ia blow-out is by itself unlikely to prevent cooling instabilities.
+Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius, i.e.
+$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{\rIa} \gtrsim 10$.
+However, for lower mass galaxies or younger stellar populations, Ia blow-out cannot prevent cooling instabilities.
 
@@
 We note that accretion is unlikely to be steady in cases where AGN heating dominates, due to the inherent delay between black hole feedback and the structure of the accretion flow on larger scales.
+Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless represent characteristic average value for the accretion rate, assuming a quasi-equilibrium state is achieved over many cycles.
 %{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
@@
 \end{eqnarray} 
-where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
+where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) =
 M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
-If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
+If the bulk of the energy from kinetic feedback is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
 10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.
@@
 subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$
+(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$
 depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
@@
 $\tau_{\star} \lesssim 10^7$ yr, and at late times $\tau_{\star}
-\gtrsim 10^{8}$ yr in the high $M_{\bullet}$ case.
+\gtrsim 10^{9}$ yr in the high $M_{\bullet}$ case.
 
@@
 wind heating.
-But for these massive galaxies, the Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (in low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+But for these massive galaxies, the Ia radius is sufficiently small for SN Ia to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (in low mass galaxies SN Ia do not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
 Strikingly, we find that galactic nuclei experiencing the same
@@
   of black hole mass $M_{\bullet}$, shown separately for core
-  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
-  dot-dashed lines).  Black lines show the accretion rate calculated
+  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$,
+  solid).  Black lines show the accretion rate calculated
   from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
@@
 fiducial assumption, then many of the X-ray detections would lie above
-the predicted value of $\langle L_X \rangle$ for stable accretion
-(green line).  In this case the X-ray detected galaxies experience
+the predictions for stable accretion, i.e., $L_X \gtrsim \epsilon_X \dot{M}_{\rm TI}$ (yellow line).  In this case the X-ray detected galaxies experience
 less heating than average galaxies of the same mass, and may not be

### 2015-04-09 ms.tex
various

@@
 This implies that the true stagnation radius and SMBH accretion rate could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
+In other words, the CNM of some subset of massive ellipticals be thermally unstable, not necessarily because they are receiving lower stellar feedback than the average for their galaxy mass, but due to the high heating required for stability given the structure of their stellar potential.
 
@@
   cusp galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$
-  are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2}
+  are augmented by the theoretical expectation that $L_{\rm X} \propto \dot{M}^{2}
   $ for radiatively inefficient flows.
@@
 $\zeta < \zeta_c$, as may occur in massive core galaxies with large
-break radii.  If the actual radiative efficiency is lower than our
+break radii.
+
+If the actual radiative efficiency is lower than our
 fiducial assumption, then many of the X-ray detections would lie above
@@
 Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.
-This condition is approximately equivalent to the more criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
+This condition is approximately equivalent to the criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
 
@@
 It is thus well possible that the current sample of X-ray detections is instead comprised mainly of nuclei undergoing non-steady accretion due to (local) thermal instabilities.
-In this case there may exist a separate branch of low $L_x$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
-Such a bimodal population would call into question extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+In this case there may exist a separate branch of low $L_X$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
+The existence of such a bimodal population would call into question extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
 
@@
 
-We conclude by drawing attention to the following limitations of our model
-    \begin{enumerate}
-    \item We assume that there is no large scale inflow of gas to the
-      nucleus, and the only source of gas feeding the black hole is
-      stellar wind mass loss from the local stellar population. Thus,
-      our estimates of gas density are a lower bound on the nuclear
-      gas density {\bf AG: make sense?}.
-
-      As we have already pointed out AGN activity cannot be explained
-      by steady thermally stable accretion of mass lost from stellar
-      winds.
-
-    \item Overall the accretion rate onto the central SMBH will be
-      strongly tied to the properties of the stellar population
-      (e.g. age) within the sphere of influence of the black
-      hole. Thus, our model cannot say anything definitive about the
-      mode accretion for individual galaxies unless something is known
-      about their specific star formation history.
-
-    \item We adopt halo average star formation rates measured in
-      cosmological simulations by \citet{MosterNaab+:2013a}, and
-      neglect any spatial variation in the star formation rate for any
-      given galaxy. Galaxies with masses$\gsim 7\times 10^{10} \Msun$,
-      assemble their stars from the inside out
-      \citep{PerezCidFernandes+:2013a} and so for a given halo mass
-      the galactic nucleus may be significantly older than in our
-      model and thus more prone to thermal instability.
-
+We conclude by drawing attention to the following limitations of our model.
+First, by neglecting any large scale inflow of gas to the nucleus and assuming the only source of gas feeding the black hole is stellar wind mass loss from the local stellar population, our estimates represent a lower bound on the gas density of the CNM.
+Our model therefore cannot account for most AGN activity.
+
+The predicted SMBH accretion rate is also strongly tied to the age and radial distribution of the stellar population within the sphere of influence.
+Our model cannot make definitive predictions for the accretion mode of individual galaxies without knowledge of their specific SFH.
+
+We adopt halo average star formation rates measured in cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any spatial variation in the star formation rate for any given galaxy.
+Galaxies of mass $\gsim 7\times 10^{10} \Msun$, assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, such that for a given halo mass the galactic nucleus may be older than in our model and thus more prone to thermal instability.
 On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
@@
       (generally unresolved) emission in excess of the inward
-      extrapolation of the Nuker law, and noted that these nuclei are bluer
+      extrapolation of the Nuker law.  They note that these nuclei are bluer
       than the background galaxy starlight, suggesting the presence of
-      younger stars towards the center of the galaxy {\bf AG mass
+      younger stars towards galactic centre {\bf AG mass
         threshold for this effect}.
@@
       nuclear star cluster with a break radius on parsec
-      scales. Although this is much smaller than our fiducial break
-      radius (100 pc). If the heating is sufficiently high moving the
+      scales, i.e. much smaller than our fiducial break
+      radius of $r_b \sim 100$ pc. If the heating is sufficiently high moving the
       break radius inwards would merely change the outer gas density
@@
 
-    \end{enumerate}
-
 \section*{Acknowledgments}

### 2015-04-10 ms.tex
mdot_mass

--- 2015-04-09 ms.tex
@@
 
-\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas C. Stone, Brian~D.~Metzger\\
+\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
   Columbia Astrophysics Laboratory, Columbia University, 550 West 120th
@@
   profiles.  Mass is supplied to the circumnuclear medium by stellar
-  winds, while energy is injected primarily by stellar winds, supernovae,
+  winds, while gas is heated primarily by stellar winds, supernovae,
   and black hole feedback.  Analytic estimates are derived for the
@@
   being related to the star-formation history.  We assess the
-  conditions under which radiative instabilities develop, both
+  conditions under which radiative instabilities develop, separately
   in the case of a single burst of star formation and for the average
-  star formation history predicted by cosmological simulations.  By combining a sample
+  star formation history predicted by cosmological simulations for
+  galaxies hosting black holes of a given mass.  By combining a sample
   of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent
@@
 `cosmic down-sizing' resulting from hierarchical structure growth
-(e.g, \citealt{Gallo+08}).  However, the physical processes by which typical
+(e.g, \citealt{Gallo+08}).  However, the physical processes by which
 low mass black holes accrete could in principle be distinct from those
-operating at higher SMBH masses, or those in AGN.  Of key importance is whether SMBHs grow primarily by the
+operating at higher SMBH masses and accretion rates in high redshift
+quasars.  One key question is whether SMBHs grow primarily by the
 accretion of gas fed in directly from galactic or extra-galactic
@@
 This event was powered by an impulsive relativistic jet,
-which produced synchrotron radio emission as the jet material
-decelerated from shock interaction with the CNM of the previously
+which produced synchrotron radio emission as the jet material was
+decelerated by shock interaction with the CNM of the previously
 quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).
@@
 lower than that measured surrounding Sgr A$^{\star}$ on a similar radial scale
-(\citealt{Metzger+12}; \citealt{BergerZauderer+2012a}).  However, a TDE jet
+(\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a TDE jet
 injected into a denser CNM would be decelerated more rapidly,
-producing potentially very different radio emission than in J1644+57.
+producing potentially much different radio emission than in J1644+57.
 Variations in the properties of the CNM could help explain why most
@@
 \citet{Ho:2009a} determines the SMBH accretion rates in a sample of
-early-type galaxies by using X-ray observations to determine the
+early-type galaxies using X-ray observations to determine the
 Bondi accretion rate and based on estimates for the mass loss rate of
@@
 gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which reduce the efficiency with which the inflowing gas ultimately reaches the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+(e.g.~\citealt{Narayan&Yi95}) or due to the low efficiency with which the inflowing gas ultimately reaches the SMBH due to disk outflows (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
 
@@
 temperature profiles of the CNM using a physically motivated
-hydrodynamic model.  Mass is injected into the nuclear environment via
-stellar winds, while energy is input from several sources
+hydrodynamic model.  Mass is injected to the nuclear environment via
+stellar winds, while energy input results from several sources
 including stellar winds, supernovae, and AGN feedback
@@
 Unlike previous works, which focused primarily on modeling individual
-galaxies, here we systematically analyze the CNM properties across a representative
+galaxies, here we systematically analyze the CNM properties across a
 range of galaxy properties, including different SMBH masses, stellar
@@
 temporarily increase the gas accretion rate towards the nucleus until
-feedback becomes strong enough to shut off the flow and halt
+feedback becomes effective to shut off the flow and halt
 SMBH growth.
 
-In this paper we instead focus on time-independent models, in cases when the nuclear gas receives sufficient heating to render radiative cooling negligible.
-This approach allows us to systematically explore the relevant parameter
+In this paper we instead focus on time-independent models, with
+sufficient heating to have negligible radiative cooling.  This
+approach allows us to systematically explore the relevant parameter
 space and to derive analytic expressions that prove useful in
@@
 sphere of influence.  We are thus motivated to explore whether such
-steady flows are generally expected within the nucleus, or
+steady flows are generally expected within the nucleus under, or
 whether in most galaxies the nuclear gas content is always building
@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ will usually reside near the nominal Bondi
+show that $\rs$ will in many cases resides near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation
@@
 case nearly the entire ISM of the galaxy is flowing towards the SMBH.
-Here we assess under what conditions a stagnation
-radius exists, a question intimately tied to that of cooling
+A goal of this work is to assess under what conditions a stagnation
+radius exists, as this question is intimately tied to that of cooling
 instability.
@@
 ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
-analytic results, which are justified via the numerical solutions we present in
-$\S\ref{sec:numerical}$.
-We move from a general and parametrized treatment of heating to a physically motivated one in \S \ref{sec:heating}, where we consider a range of physical processes that can inject energy into the CNM.
-In
+analytic results, which are justified via numerical solutions in
+$\S\ref{sec:numerical}$ we describe our numerical results.  In
 $\S\ref{sec:discussion}$ we discuss the implications of our results
@@
 measure the radial surface brightness profiles for hundreds of nearby
-early type galaxies. The measured profile is fit by a ``Nuker" law parameterization:
+early type galaxies. The measured brightness profile is generally
+well-fit by a ``Nuker" law parameterization:
 \begin{equation}
@@
 i.e., a broken power law that transitions from an inner power law
-slope, $\Gamma$, to an outer power law slope, $\beta$, at a
-break radius, $\rb$.  If the stellar population is spherically
-symmetric, then this corresponds to a 3D stellar density $\rhostar \propto
+slope, $\Gamma$, to an outer power law slope, $\beta > \Gamma$, at a
+break radius, $\rb$.  Assuming the stellar population is spherically
+symmetric, this corresponds to a stellar density $\rhostar \propto
 r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
-$r \gg \rb$.  We can write the deprojected stellar density approximately (formally, this is the $\alpha \rightarrow \infty$ limit) as
+$r \gg \rb$.  To good approximation
 \begin{align}
@@
 \end{align}
-where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence\footnote{This approximate expression agrees surprisingly well with the mean empirical scaling relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of \citet{Stone&Metzger15}, although we note that this relation has significant scatter.},
+where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence (inf), 
 \begin{equation}
@@
 \end{align}
-Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of an obviously better alternative.
+Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of a better alternative.
 
@@
 
-We fix $\beta = 2$ because our results are not overly sensitive to the properties of the gas flow on radial scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
+We fix $\beta = 2$ because our results are
+generally not sensitive to the properties of the gas flow on radial
+scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
 however, necessary to obtain a converged steady state for some regions
@@
   scatter of approximately one dex.  Most the cusp galaxies have $\rb$
-  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  In
+  between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In
 practice we calculate solutions for a range of $\rb$ only in cases
@@
   of volumetrically, but our expressions are equivalent.}, although
-$\eta$ is significantly higher for continuous SFHs
+$\eta$ is significantly higher for continuous SFHss
 (bottom panel of Fig.~\ref{fig:vwSources}).
@@
 and energy relative to the mean flow.  Physically, these result from
-the mismatch between the properties of virialized gas injected by stellar winds and the mean background flow.  The
-term $\propto p/\rho = c_{s}^{2}$ is important because it acts to stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
+the mismatch between the properties of virialized gas injected locally
+by stellar winds and the mean properties of the background flow.  The
+term $\propto -q c_{s}^{2}$ is important because it acts to potentially stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
 
@@
 accounts for external heating sources (e.g.,
-\citealt{ShcherbakovWong+:2014a}), where
+\citealt{ShcherbakovWong+:2014a}).  The first term approximates the
+minimum amount of shock heating from stellar winds due to the random
+movement of stars with respect to one another at the characteristic
+velocity of 
 \be\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
@@
 \label{eq:sigmarel}
-\ee 
-is the stellar velocity dispersion and which accounts for the minimal amount of shock heating from stellar winds due to the random motion of stars in the SMBH potential, while $\sigma_0^{2} \approx 3 \sigma^2$ is assumed to be constant, corresponding to the observed
+\ee where the first term is the velocity dispersion of the power law
+stellar density profile in the SMBH potential.  The second term,
+$\sigma_0\approx 3 \sigma^2$ is a constant, motivated by the observed
 velocity dispersion outside of the SMBH sphere of influence
-\citep{ChaeBernardi+:2014a}.  The second term, $v_{w}^{2}$, parameterizes additional sources of energy input, including faster winds from young
-stars, millisecond pulsars, supernovae, AGN feedback, etc  ($\S\ref{sec:heating}$).  We assume
+\citep{ChaeBernardi+:2014a}, where $\sigma$ is the velocity dispersion
+in the $\Mbh-\sigma$ relation (eq.~[\ref{eq:Msigma}]).  The second
+component of the total heating, $v_{w}^{2}$, parameterizes all
+additional sources of energy input, including faster winds from young
+stars, millisecond pulsars, supernovae, AGN feedback, etc.  We assume
 that $v_w$ is constant with radius, i.e. that the volumetric heating
-rate is proportional to the local stellar density.  
-%The value of $v_w$
-%will in general depend on the SMBH mass and the age of the stellar
-%population ($\S\ref{sec:heating}$).
-
-To isolate the physics of interest, our baseline calculations
+rate is proportional to the local stellar density.  The value of $v_w$
+will in general depend on the SMBH mass and the age of the stellar
+population ($\S\ref{sec:heating}$).
+
+To isolate the physics of greatest interest, our baseline calculations
 neglects three potentially important effects: heat conduction,
-radiative cooling, and rotation.  Heat conduction results in
-an an additional heating term in equation (\ref{eq:dsdt}),
+radiative cooling, and rotation.  Electron heat conduction results in
+an an additional term on the right hand side of the entropy equation
+of the form:
 \begin{equation}
@@
  weak magnetic field that is oriented perpendicular to the flow could
- suppress the conductivity by reducing the electron mean free
+ suppress the conductivity by greatly reducing the electron mean free
  path.  However, for radially-decreasing temperature profiles of
  interest, the flow is susceptible to the magneto-thermal instability
- (\citealt{Balbus01}), the non-linear evolution of which results in a radially-directed field geometry
- (\citealt{Parrish&Stone07}).  In $\S\ref{sec:conductivity}$ we show that neglecting conductivity results in at
- most order-unity errors in the key properties of the solutions.
-
-Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}), of the form
+ (\citealt{Balbus01}), the non-linear evolution of which is believed
+ to result in a radially-directed field geometry
+ (\citealt{Parrish&Stone07}).  We show later in
+ $\S\ref{sec:conductivity}$ that neglecting conductivity results in at
+ most only order-unity errors in the key properties of the solutions.
+
+Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
 \begin{equation}
@@
 \end{equation}
-where $n \equiv \rho/\mu m_p$ and $\Lambda(T)$ is
+where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is
 the cooling function.  We neglect radiative cooling in our baseline
@@
 wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-Once radiative cooling becomes important compared to other
+However, once radiative cooling becomes important compared to other
 sources of heating and cooling, its presence leads to thermal
 instability (e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be accounted for
-by our 1D time-independent model.  Our goal is to use solutions which neglect radiation to determine over what range of conditions cooling instabilities will develop
+by our 1D time-independent model.  A main goal of this work is to use
+solutions neglecting radiation to ascertain over what range of
+physical conditions cooling instabilities are most likely to develop
 ($\S\ref{sec:instability}$).
@@
 interested in the steady-state inflow/outflow solution (assuming one
-exists), we solve the time-dependent equations to avoid numerical
+exists), the time-dependent equations are solved to avoid numerical
 issues that arise near the critical sonic points, of which there are
 up to two because of the supersonic inflow on small radial scales and
-a possible supersonic outflow on large scales.  Our
+a possible supersonic outflow on large scales.  Also note that our
 solutions can be scaled to any value of the mass input parameter,
@@
 $\rho$ or $\rho_{\star}$; however, the precise value of $\eta$ must be
-specified when cooling or thermal conduction are included.  We check the accuracy of
+specified when cooling or thermal conduction are included, since these
+scale as gas density to a different power.  We check the accuracy of
 our numerical solutions by confirming that mass is conserved across
@@
 
-Hydrostatic equilibrium likewise determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
+Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
 \begin{align}
@@
 stagnation radius moves to large radii, approaching the break radius
-$\rb$ in the stellar density profile, formally implying that almost the
+$\rb$ in the stellar density profile, formally implying that almost
 entire ISM of the galaxy is accreting.  In particular, in Appendix
@@
 \label{eq:zetacrit}
-\ee This result makes intuitive sense: gas is supplied to the nucleus
+\ee This result makes intuitive sense: gas is supplied to the nuclear
 by stars which are gravitationally bound to the black hole, so
@@
 the condition that the wind heating parameter be less than the local escape
-speed near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
+speed from near the break radius, $v_{\rm esc} \sim (GM_{\star}|_{r_{\rm
     b}}/r_b)^{1/2}$, where $M_{\star} \propto r^{2-\Gamma}$.
@@
 equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n
-kT/2 \mu)/|\dot{q}_{\rm rad}|$ to the free-fall time $t_{\rm ff}$ at the
+kT/2 \mu)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the
 stagnation radius, as can be derived using the equality
@@
 
-Based on our numerical results (\S \ref{sec:numerical}) and the work of \citet{McCourt+12} we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
+Based on our numerical results (\ref{sec:numerical}) and the work of \citet{McCourt+12}) we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
   cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius.  This condition translates into a
@@
 where the first line for each case is derived using equation
-(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and
+(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
 the second line corresponds to the low wind heating limit $\zeta \ll
@@
       orange}), and 300 km s$^{-1}$ ({\it green}).  Different
-    line styles correspond to different values of $\Mbh$: $\Mbh=10^6
+    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
     \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
@@
   net rotation, resulting in centrifugal forces becoming important at
-  some radius $r_{\rm circ} = l^{2}_{s}/(GM_{\bullet})$.  Here
-  $l_{s} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar
+  some radius $r_{\rm circ} = l^{2}_{r_{s}}/(GM_{\bullet})$.  Here
+  $l_{r_{s}} = \langle r V_{\phi}\rangle |_{r_s}$ is the stellar
   specific angular momentum near the stagnation radius, from which
@@
 occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincides with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
 This divergence of the stagnation radius to large radii occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii, explaining the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange triangles.
@@
 (\ref{eq:eddr_analytic}).  For high wind velocities ($v_{w} \gg
-\sigma$) the stagnation radius lies well inside the black hole sphere of
+\sigma$) the stagnation lies well inside the black hole sphere of
 influence and our analytic estimate provides a good fit to the
@@
 For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions that are only marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
+However, for solutions which are already marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
 We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
@@
 \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
-is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$, for the case of quasi-continuous star
-formation (representative of the average SFHs of low
-mass galaxies), the stellar wind heating rate produced by stellar winds
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
+formation representative of the average SFHs of low
+mass galaxies, the stellar wind heating rate produced by stellar winds
 can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
@@
 Stellar winds thus contribute a potentially important source of both
-energy and mass to the CNM.
+energy and mass for the CNM.
 An additional uncertainty results from the thermalization efficiency of massive stellar winds.
@@
   \end{align}
-  as the location exterior to which the time interval between
+  as the location exterior of which the time interval between
   subsequent supernovae $\tau_{\rm Ia} \sim (M_{\rm enc}R_{\rm
@@
 Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find the ratio of heating to radiative cooling at $\rIa$ is given by
+However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we the ratio of heating to radiative cooling at $\rIa$ is given by
 \begin{align}
@@
 Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad})_{\rIa})$.
-However, for lower mass galaxies or younger stellar populations, Ia blow-out is by itself unlikely to prevent cooling instabilities.
+However, for lower mass galaxies or younger stellar populations, Ia blow-out is itself unlikely to prevent cooling instabilities.
 
@@
 \caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
-  to the total heating rate of the CNM, $\vwO$ ({\it black}):
-  stellar wind heating ({\it orange}), Ia supernovae ({\it
+  to the total heating rate of the CNM, $\vwO$ ({\it black}),
+  including stellar wind heating ({\it orange}), Ia supernovae ({\it
     green}), millisecond pulsars ({\it blue}), and compton heating
   ({\it pink}).  Each heating source varies with black hole mass
-  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a};
-  see Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:}
+  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a}
+  (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:}
   The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
@@
 subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$
+(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and
 depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
@@
 mechanisms, SMBH feedback may not be capable of truly stabilizing the
-flow, given its inability to respond instantaneously to local changes
-in gas properties.  Thermally unstable flow is present
+flow given its inability to respond instantaneously to local changes
+in the properties of the gas.  Thermally unstable flow is present
 throughout the single starburst case except at very early times,
@@
 wind heating.
-But for these massive galaxies, the Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (in low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+But for these massive galaxies, that Ia radius is sufficiently small for Ia heating to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (for low mass galaxies Ia heating does not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
 Strikingly, we find that galactic nuclei experiencing the same
@@
 explosions dominate) will fall by a factor $\approx 4$ from our
-fiducial volumetric averages, calculated using SFHs from \citet{MosterNaab+:2013a}.
+fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.
 
@@
   lines show the maximum accretion set by Ia supernovae blow-out
-  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained
+  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
   if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
@@
   formation history (Appendix \ref{fig:NickPlot2}), this can lead to
-  order of magnitude differences in $\dot{M}$; (3) differences in angular
+  order of magnitude differences in $\dot{M}$; (3) differences angular
   momentum of the infalling gas from galaxy to galaxy, resulting in
-  differences in the fraction of the gas lost to outflows.
+  differences in the fraction of the gas lost to outflows, $\Mbh$.
   Also potentially contributing is the order of magnitude difference,
@@
 It is also possible that many of the \citet{Miller+15} sample of
-galactic nuclei are not accreting in steady state.  The 
+galactic nuclei are not accreting in steady state.  The value of the
 X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
@@
 lost from the surrounding stellar population studied in this paper.
-Gas blow-out by SN Ia cannot alone prevent the growth of low-mass black
+Gas blow-out by SN Ia cannot prevent the growth of low-mass black
 holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
@@
 Our results also have implications for the environments encountered by
-relativistic jets from TDEs.  For low-mass SMBHs with $M_{\bullet} \lesssim
+relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
 10^{7}M_{\odot}$, such as that responsible for powering the transient {\it Swift}
@@
 
-  \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).
-This accretion rates so required are too high to be consistent with the value predicted for the average SFH history and the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).
-Low-$M_{\bullet}$ growth and AGN activity must instead be driven by a supply of gas external to the nucleaus, e.g.
-due to galaxy mergers or thermal instabilities on larger, galactic scales (e.g.~\citealt{Voit+15}).
+\item Low mass black holes grow in the low redshift universe over
+  timescales comparable to the Hubble time (\citet{Heckman+04}).  This
+  accretion rates so required are too high to be consistent with the
+  value predicted for the average SFH history and the maximum allowed
+  for steady-state, thermally stable accretion
+  (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN
+  activity must instead be driven by a supply of gas external to the
+  nucleaus, e.g. due to galaxy mergers or thermal instabilities on
+  larger, galactic scales (e.g.~\citealt{Voit+15}).
 

### 2015-04-10 be.tex
rinf

@@
   -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
-  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2
+  -\frac{\rb}{\rinf} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2
     -\delta} -w
@@
 where $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ and $w\equiv
-(\rs/\rsoi)^{3\delta}$.
+(\rs/\rinf)^{3\delta}$.
 
@@
 a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically,
-we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$
+we find $\zeta_c\sim (\rb/\rinf)^{0.5(1-\Gamma)}$ for $\rb\gsim\rinf$
 (see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core

### 2015-04-10 ms.tex
rinf

--- 2015-04-09 ms.tex
@@
 \newcommand{\soi}{\rm inf}
-\newcommand{\rsoi}{r_{\soi}}
+\newcommand{\rinf}{r_{\rm inf}}
 \newcommand{\rIa}{r_{\rm Ia}}
@@
 \newcommand{\kewO}{\frac{\vwO^2}{2}}
-\newcommand{\x}{\frac{r_s}{\rsoi}}
+\newcommand{\x}{\frac{r_s}{\rinf}}
 \newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
@@
 \begin{cases}
-\rho_\star|_{\rsoi} \left(r/\rsoi\right)^{-1-\Gamma} & r \leq r_b\\
+\rho_\star|_{\rinf} \left(r/\rinf\right)^{-1-\Gamma} & r \leq r_b\\
 \rho_\star|_{r_b} \left(r/r_b\right)^{-1-\beta} & r > r_b,
@@
 \end{align}
-where $\rho_\star|_{\rsoi}$ is the stellar density at the radius of the black hole sphere of influence\footnote{This approximate expression agrees surprisingly well with the mean empirical scaling relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of \citet{Stone&Metzger15}, although we note that this relation has significant scatter.},
+where $\rho_\star|_{\rinf}$ is the stellar density at the radius of the black hole sphere of influence\footnote{This approximate expression agrees surprisingly well with the mean empirical scaling relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of \citet{Stone&Metzger15}, although we note that this relation has significant scatter.},
 \begin{equation}
-\rsoi \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
+\rinf \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
 \label{eq:rsoi}
@@
 \ref{app:be} we show that $\rs \Rightarrow \rb$ for heating below a
-critical threshold (Fig.~\ref{fig:zetaCrit}) \be \zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
-\zeta_c \approx \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)}.
+critical threshold (Fig.~\ref{fig:zetaCrit})
+
+\begin{equation} 
+\zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
+\zeta_c \approx \left(\frac{\rb}{\rinf}\right)^{0.5(1-\Gamma)}.
 \label{eq:zetacrit}
-\ee This result makes intuitive sense: gas is supplied to the nucleus
+\end{equation}
+
+This result makes intuitive sense: gas is supplied to the nucleus
 by stars which are gravitationally bound to the black hole, so
@@
     galaxies in our sample as a function of the stellar wind heating
-    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.
-    Green, orange, and blue symbols correspond to different values of
-    $v_{w} =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
+    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.  Green,
+    orange, and blue symbols correspond to different values of $v_{w}
+    =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
     correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
@@
     correspond to the analytic prediction from equation
-    (\ref{eq:rs2main}), with solid and dashed curves calculated for
-    parameters $(\Gamma=0.8, \densSlope\simeq1)$ and
-    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. }
+    (\ref{eq:rs2main}), with thick solid and dot-dashed curves
+    calculated for parameters $(\Gamma=0.8, \densSlope\simeq 1)$ and
+    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. The thin black
+    solid line corresponds to the simplified analytic result for $\rs$
+    from equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
+    \Mbheight^{0.6} {\rm pc}$).}
 \end{figure}
@@
     ($\Gamma$=0.1). Green circles correspond to cusp solutions which
-    would be thermally unstable.  Solid and dot-dashed curves correspond
-    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
-    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
-    respectively. }
+    would be thermally unstable.  Thin solid and dot-dashed curves
+    correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm
+      edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
+    respectively. Equation ~[\ref{eq:eddr_analytic}] is derived from
+    the approximate analytic result for the stagnation radius given by
+    equation~\eqref{eq:stag_simple}. If we instead use the more
+    accurate result from equation~\eqref{eq:rs2main} we obtain the
+    thick curves.}
 \end{figure}
@@
 \citet{BergerZauderer+:2012a} infer a flattening of the gas density
-profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
-qualitatively similar to the shape density profile we predict for core
-galaxies (Fig.~\ref{fig:profiles}, solid line).
-To obtain such a flattening on the inferred radial scales would require a black hole of $\Mbh\sim 10^7 \Msun$.
-However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
+profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc
+(their Fig.~6) which looks qualitatively similar to the shape density
+profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid
+line).  To obtain such a flattening on the inferred radial scales
+would require a black hole of $\Mbh\sim 10^7 \Msun$.  However, this is
+inconsistent with the break in the gas density seen at $\sim 0.6$ pc
+by \citet{BergerZauderer+:2012a}, which should correspond to the break
+radius of the {\it stellar density} profile, thus implying an
+unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
+the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
 
@@
 
-%{\bf AG Challenge: Except in the most massive systems the jet duty
- % cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
-  %and then periodically turn once the gas begins to cools
-  %(Refs). Thus, jets cannot be treated as a truly steady source of
-  %heating. 
-%}
-
 %\subsection{Jet Power Correlation}
 
-%Accretion rates onto SMBHs can in principle be estimated directly by assuming Bondi accretion and using high resolution X-ray observations to estimate the gas temperature and density near the Bondi radius.
-%This technique has led to the intriguing conclusion that the Bondi accretion power correlates with the AGN jet power (e.g.,
-%\citealt{AllenDunn+:2006a}; \citealt{Russell+13}; \citealt{FujitaKawakatu+:2014a}), the latter estimated from the energy
-%required to inflate the observed cavities within the X-ray emitting gas.
-In practice is it almost never possible to resolve the Bondi radius, therefore requiring all such studies to extrapolate the observed gas temperature and density profiles to smaller radial scales.
+%Accretion rates onto SMBHs can in principle be estimated directly by
+% assuming Bondi accretion and using high resolution X-ray
+% observations to estimate the gas temperature and density near the
+% Bondi radius.  This technique has led to the intriguing conclusion
+% that the Bondi accretion power correlates with the AGN jet power
+% (e.g., \citealt{AllenDunn+:2006a}; \citealt{Russell+13};
+% \citealt{FujitaKawakatu+:2014a}), the latter estimated from the
+% energy required to inflate the observed cavities within the X-ray
+% emitting gas.  In practice is it almost never possible to resolve
+% the Bondi radius, therefore requiring all such studies to
+% extrapolate the observed gas temperature and density profiles to
+% smaller radial scales.
 
@@
 
-We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.
-We compute solutions for a range of different black hole masses, heating rates, and observationally-motivated stellar density profiles.
-Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).
-We use the latter to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's SFH.
-Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN.
-They are also used to address key questions such as the thermal stability of the accretion flow.
-Our conclusions are summarized as follows.
+We have calculated steady-state models for the hot gaseous
+circumnuclear media of quiescent galaxies, under the assumption that
+gas is supplied exclusively by stellar wind mass loss and heated by
+shocked stellar winds, supernovae and black hole feedback.  We compute
+solutions for a range of different black hole masses, heating rates,
+and observationally-motivated stellar density profiles.  Our numerical
+results (Table \ref{table:models}) are used to verify and calibrate
+analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use
+the latter to explore systematically how the SMBH accretion rate
+varies with black hole mass and the galaxy's SFH.  Our results for
+$\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray
+luminosities of quiescent SMBHs and low luminosity AGN.  They are also
+used to address key questions such as the thermal stability of the
+accretion flow.  Our conclusions are summarized as follows.
 

### 2015-04-10 ms.tex
cleaned up

@@
 Galaxies of mass $\gsim 7\times 10^{10} \Msun$, assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, such that for a given halo mass the galactic nucleus may be older than in our model and thus more prone to thermal instability.
+
 On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
@@
 
-      In fact it is possible that the mass injection is dominated by a
-      nuclear star cluster with a break radius on parsec
-      scales, i.e. much smaller than our fiducial break
-      radius of $r_b \sim 100$ pc. If the heating is sufficiently high moving the
-      break radius inwards would merely change the outer gas density
-      profile, without changing the stagnation radius in the flow and
-      thus the accretion rate onto the black hole. Of course if one
-      moves the break radius inside where the stagnation radius would
-      be for large break radii, the stagnation radius would move
-      inwards somewhat. However note the for high heating rate ($v_w
-      \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
-      \Msun$), we predict stagnation radii smaller than a parsec.
+      It is thus possible that the mass injection to the nucleus could in some cases be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e.
+much smaller than our fiducial value of $r_b \sim 100$ pc.
+For a sufficiently high heating rate, a smaller break radius would not appreciably change the stagnation radius, resulting in a similar accretion rate onto the black hole.
+On the other hand, a break radius smaller than the nominal stagnation radius would likely decrease the stagation radius and SMBH accretion rate.
+%      be for large break radii, the stagnation radius would move
+ %     inwards somewhat. However note the for high heating rate ($v_w
+  %    \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
+   %   \Msun$), we predict stagnation radii smaller than a parsec.
 

### 2015-04-10 ms.tex
sigma_bullet

--- 2015-04-10 ms.tex
@@
 \begin{equation}
-\rinf \simeq G \Mbh/\sigma^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
+  \rinf \simeq G \Mbh/\sigma_{\bullet}^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
 \label{eq:rsoi}
@@
  \begin{align}
-M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
+M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma_{\bullet}{200\,{\rm
       km\,s^{-1}}}\right)^{5.1}M_{\odot}.
@@
 \citealt{ShcherbakovWong+:2014a}), where
-\be\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
+
+\begin{equation}
+\sigma \approx \sqrt{\frac{3 G \Mbh}{(\Gamma+2)
     r}+\sigma_0^2},
 \label{eq:sigmarel}
-\ee 
-is the stellar velocity dispersion and which accounts for the minimal amount of shock heating from stellar winds due to the random motion of stars in the SMBH potential, while $\sigma_0^{2} \approx 3 \sigma^2$ is assumed to be constant, corresponding to the observed
-velocity dispersion outside of the SMBH sphere of influence
-\citep{ChaeBernardi+:2014a}.  The second term, $v_{w}^{2}$, parameterizes additional sources of energy input, including faster winds from young
-stars, millisecond pulsars, supernovae, AGN feedback, etc  ($\S\ref{sec:heating}$).  We assume
-that $v_w$ is constant with radius, i.e. that the volumetric heating
-rate is proportional to the local stellar density.  
+\end{equation}
+
+is the stellar velocity dispersion and which accounts for the minimal
+amount of shock heating from stellar winds due to the random motion of
+stars in the SMBH potential. We take $\sigma_0$ to be constant and use
+$\sigma_0^{2} \approx 3 \sigma_{\bullet}^2$, where
+$\sigma_{\bullet}\simeq 170 \Mbheight^{0.2}$ km/s is the velocity
+dispersion from the \citet{McConnellMa+:2011a} $\Mbh-\sigma$
+relation. 
+% \citep{ChaeBernardi+:2014a}
+.  The second term, $v_{w}^{2}$, parameterizes additional sources of
+energy input, including faster winds from young stars, millisecond
+pulsars, supernovae, AGN feedback, etc ($\S\ref{sec:heating}$).  We
+assume that $v_w$ is constant with radius, i.e. that the volumetric
+heating rate is proportional to the local stellar density.
 %The value of $v_w$
@@
 \end{eqnarray}
-where we have assumed $v_{w} \gg \sigma$ by adopting equation
+where we have assumed $v_{w} \gg \sigma_0$ by adopting equation
 (\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
@@
 where we have used the definition $r_{\rm inf} \equiv
-GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed
+GM_{\bullet}/\sigma_{\bullet}^{2}$ and in the second inequality have assumed
 that $r_{\rm s} \lesssim r_{\rm inf}$, a condition which is satisfied
@@
   \hline
-  & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
+ Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & & & & \\
   $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
@@
 \hline
-& & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
+Core Galaxies, $\Gamma = 0.1$  &  & & & & & & & & \\
 $    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\
@@
   adopt the Ia rate for an old stellar population and in the final
-  equality we estimate $\sigma_0 \approx \sqrt{3}\sigma$ using $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+  equality we estimate $\sigma_0 \approx \sqrt{3}\sigma_{\bullet}$ using $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
 

### 2015-04-10 ms.tex
oops
table heading

@@
 ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
-analytic results, which are justified via the numerical solutions we present in
-$\S\ref{sec:numerical}$.
-We move from a general and parametrized treatment of heating to a physically motivated one in \S \ref{sec:heating}, where we consider a range of physical processes that can inject energy into the CNM.
-In
-$\S\ref{sec:discussion}$ we discuss the implications of our results
-for topics which include the nuclear X-ray luminosities of quiescent
-black holes, jetted TDEs, and the growth of SMBHs in the local
-universe.  In $\S\ref{sec:conclusions}$ we summarize our conclusions.
-Table \ref{table:definitions} provides the definitions of commonly
-used variables.  Appendices \ref{app:rs} and \ref{app:be} provide
-useful analytic results for the stagnation radius and the Bernoulli
-parameter of the flow, while Appendix \ref{app:windheat} provides the
-details of our method for calculating stellar wind heating and mass
-input.
+analytic results, which are justified via the numerical solutions we
+present in $\S\ref{sec:numerical}$.  We move from a general and
+parametrized treatment of heating to a physically motivated one in \S
+\ref{sec:heating}, where we consider a range of physical processes
+that can inject energy into the CNM.  In $\S\ref{sec:discussion}$ we
+discuss the implications of our results for topics which include the
+nuclear X-ray luminosities of quiescent black holes, jetted TDEs, and
+the growth of SMBHs in the local universe.  In
+$\S\ref{sec:conclusions}$ we summarize our conclusions.  Table
+\ref{table:definitions} provides the definitions of commonly used
+variables.  Appendices \ref{app:rs} and \ref{app:be} provide useful
+analytic results for the stagnation radius and the Bernoulli parameter
+of the flow, while Appendix \ref{app:windheat} provides the details of
+our method for calculating stellar wind heating and mass input.
 
@@
  \begin{align}
-M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma_{\bullet}{200\,{\rm
+M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma_{\bullet}}{200\,{\rm
       km\,s^{-1}}}\right)^{5.1}M_{\odot}.
@@
   \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$, which assumes solar
-metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).
-
+metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).  Note that in
+our runs with radiative cooling we take $\Lambda(T)$ to be a piecewise
+function with $\Lambda = $. 
 To within a constant of order unity, equation (\ref{eq:cooling2}) also
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &
-  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm
-          rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Unstable
-  $\eta$'s  \\
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm
+    inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\right)_{r_{s}}^{(c)}
+      (\eta=0.2)$} & {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm
+            rad}|}\right)_{r_s}^{(d)} (\eta=0.2)$} & Unstable $\eta$'s  \\
     ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
@@
 the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
-\lesssim r_{\rm inf}$).  However, for low heating the
-stagnation radius diverges above the analytic estimate, approaching
-the stellar break radius $r_b \gg r_{\rm inf}$.  This divergence
-occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
-  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincides with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius (Appendix \ref{app:be}).
-This divergence of the stagnation radius to large radii occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii, explaining the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange triangles.
-These solutions correspond to the same black hole mass
-($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break radii of $r_{b} =$ 25, 50 pc (from top to
-bottom).
+\lesssim r_{\rm inf}$).  However, for low heating the stagnation
+radius diverges above the analytic estimate, approaching the stellar
+break radius $r_b \gg r_{\rm inf}$.  This divergence occurs
+approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
+  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which coincides
+with the Bernoulli parameter of the gas decreasing below unity near
+the stagnation radius (Appendix \ref{app:be}).  This divergence of the
+stagnation radius to large radii occurs at a higher value of $\zeta$
+in core galaxies ($\Gamma = 0.8$) with large break radii, explaining
+the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as
+vertically aligned orange triangles.  These solutions correspond to
+the same black hole mass ($\Mbh = 10^8 \Msun$) and heating rate ($v_w
+= 600$ km s$^{-1}$) but assume different break radii of $r_{b} =$ 25,
+50 pc (from top to bottom).
 
@@
 (\ref{eq:eddr_analytic}).  For high wind velocities ($v_{w} \gg
-\sigma$) the stagnation radius lies well inside the black hole sphere of
+\sigma_0$) the stagnation radius lies well inside the black hole sphere of
 influence and our analytic estimate provides a good fit to the
 numerical results.  However, for low wind velocities and/or high
-$M_{\bullet}$ (large $\sigma$), the numerical accretion rate
+$M_{\bullet}$ (large $\sigma_0$), the numerical accretion rate
 considerably exceeds the analytic estimate as the stagnation radius
@@
 
-Assuming that $v_{w}^{\rm Ia} \gg \sigma$ then by substituting
+Assuming that $v_{w}^{\rm Ia} \gg \sigma_0$ then by substituting
 $v_{w}^{\rm Ia}$ (eq.~\ref{eq:vIa}) into equation (\ref{eq:stag_simple})
@@
 \end{eqnarray}
-Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet escape timescale to the dynamical timescale $t_{\rm dyn} \sim r/\sigma$ is given by
+Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet
+escape timescale to the dynamical timescale $t_{\rm dyn} \sim
+r/\sigma$ is given by
 \begin{equation}
@@
   (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
-  are the value of the stellar velocity dispersion, $\sigma_0$,
-  approximated as $\sqrt{3}$ time the $\sigma$ from the $\Mbh-\sigma$
+  are the values of the stellar velocity dispersion, $\sigma_0$,
+  approximated as $\sqrt{3} \sigma_{\bullet}$, where
+  $\sigma_{\bullet}$ is the velocity dispersion from the $\Mbh-\sigma$
   relation \citep{McConnellMa+:2011a}.}

### 2015-04-10 ms.tex
cooling
cleaned up2

@@
   that most nuclei are consistent with accreting in a steady-state,
-  thermally-stable manner.  However, thermally-stable accretion cannot
-  explain the short average growth times of low mass black holes in
+  thermally-stable manner for radiative efficiencies predicted by ADAF models. 
+However, thermally-stable accretion cannot explain the short average growth times of low mass black holes in
   the local universe, which must instead result from gas being fed in
@@
 dispersion from the \citet{McConnellMa+:2011a} $\Mbh-\sigma$
-relation. 
-% \citep{ChaeBernardi+:2014a}
-.  The second term, $v_{w}^{2}$, parameterizes additional sources of
+relation.  The second term, $v_{w}^{2}$, parameterizes additional sources of
 energy input, including faster winds from young stars, millisecond
@@
  \end{equation}
- where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$
+ where $\kappa =\kappa_{\rm spitz}/(1+\psi)$
  (\citealt{DaltonBalbus:1993a}) is the conductivity and $\kappa_{\rm

### 2015-04-10 ms.tex
cleaned up2

@@
 our runs with radiative cooling we take $\Lambda(T)$ to be a piecewise
-function with $\Lambda = $. 
+function with $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
+  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ for $T\leq 2\times
+10^{7}$ K and $\Lambda = 2.3 \times 10^{-24} \left(T/10^6
+  \text{K}\right)^{0.5}$ for $T>2\times 10^{7}$ K.
+
 To within a constant of order unity, equation (\ref{eq:cooling2}) also
@@
 equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true
-gas density, which is greater in a subsonic inflow (weak heating) than
+gas density, which is greater in a subsonic flow (weak heating) than
 in a supersonic outflow (strong heating).
@@
 Thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$.
-Conduction may, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+Conduction can, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
 
@@
 
-\item Heating from SMBH feedback, unlike stellar heating, depends on
-  the SMBH accretion rate, which is itself a function of the heating
-  rate.  Compton heating is generally unimportant compared to stellar
+\item Unlike stellar heating, heating from SMBH feedback depends on
+  the accretion rate, which itself depends on the heating.  Compton heating is generally unimportant compared to stellar
   wind heating for the average SFH, but it can dominate in the case of

### 2015-04-10 ms.tex
cleaned up3

@@
 
-\item Only for high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value allowed for thermally-stable accretion $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}).
-It is thus well possible that the current sample of X-ray detections is instead comprised mainly of nuclei undergoing non-steady accretion due to (local) thermal instabilities.
-In this case there may exist a separate branch of low $L_X$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
-The existence of such a bimodal population would call into question extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+\item  The accretion rates of early-type galaxies are below the maximum value for thermally stable flow, $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies, similar to the maximum values predicted by ADAF models.
+Therefore the current X-ray detections could instead be comprised mostly of nuclei undergoing non-steady accretion due to thermal instabilities.
+In this case there may exist a separate branch of low-$L_X$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
+Such a bimodal population would call into question methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in order to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
 
@@
 First, by neglecting any large scale inflow of gas to the nucleus and assuming the only source of gas feeding the black hole is stellar wind mass loss from the local stellar population, our estimates represent a lower bound on the gas density of the CNM.
-Our model therefore cannot account for most AGN activity.
-
-The predicted SMBH accretion rate is also strongly tied to the age and radial distribution of the stellar population within the sphere of influence.
-Our model cannot make definitive predictions for the accretion mode of individual galaxies without knowledge of their specific SFH.
-
+Our model therefore cannot account for AGN.
+
+Predictions for the  SMBH accretion rate are strongly tied to the age and radial distribution of the stellar population within the sphere of influence.
+Our model therefore cannot make definitive predictions for the accretion mode of individual galaxies without knowledge of their specific SFH.
 We adopt halo average star formation rates measured in cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any spatial variation in the star formation rate for any given galaxy.
-Galaxies of mass $\gsim 7\times 10^{10} \Msun$, assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, such that for a given halo mass the galactic nucleus may be older than in our model and thus more prone to thermal instability.
+However, galaxies of mass $\gsim 7\times 10^{10} \Msun$ assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, resulting in galactic nuclei which may be systematically older than assumed in our model and thus more prone to thermal instability.
 
@@
         threshold for this effect}.
-
-      It is thus possible that the mass injection to the nucleus could in some cases be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e.
+Mass injection to the nucleus could in some cases therefore be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e.
 much smaller than our fiducial value of $r_b \sim 100$ pc.
-For a sufficiently high heating rate, a smaller break radius would not appreciably change the stagnation radius, resulting in a similar accretion rate onto the black hole.
-On the other hand, a break radius smaller than the nominal stagnation radius would likely decrease the stagation radius and SMBH accretion rate.
+In the case of high heating, a smaller break radius does not appreciably change the stagnation radius, resulting in a similar SMBH accretion rate.
+For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagation radius and accretion rate.
 %      be for large break radii, the stagnation radius would move

### 2015-04-10 ms.tex
fixing bondi and Ia radius.

--- 2015-04-10 ms.tex
@@
   that most nuclei are consistent with accreting in a steady-state,
-  thermally-stable manner for radiative efficiencies predicted by ADAF models. 
-However, thermally-stable accretion cannot explain the short average growth times of low mass black holes in
+  thermally-stable manner.  However, thermally-stable accretion cannot
+  explain the short average growth times of low mass black holes in
   the local universe, which must instead result from gas being fed in
@@
 dispersion from the \citet{McConnellMa+:2011a} $\Mbh-\sigma$
-relation.  The second term, $v_{w}^{2}$, parameterizes additional sources of
+relation. 
+% \citep{ChaeBernardi+:2014a}
+.  The second term, $v_{w}^{2}$, parameterizes additional sources of
 energy input, including faster winds from young stars, millisecond
@@
  \end{equation}
- where $\kappa =\kappa_{\rm spitz}/(1+\psi)$
+ where $\kappa_{\rm eff}=\kappa_{\rm spitz}/(1+\psi)$
  (\citealt{DaltonBalbus:1993a}) is the conductivity and $\kappa_{\rm
@@
   \rs\approx\frac{13+8\Gamma}{4+2\Gamma}\frac{G \Mbh}{\densSlope
-    \vw^2} \approx \frac{13+8\Gamma}{12+6\Gamma}r_{\rm B},
+    \vw^2} \approx 2 \frac{13+8\Gamma}{(4+2\Gamma)(3+4\Gamma)}r_{\rm B},
   \label{eq:rbondi}
@@
 
-Type Ia SNe represent a source of heating, which unlike core collapse SNe is present even in an evolved stellar population.
-If each SN Ia injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SN rate per stellar mass is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate of $E_{\rm Ia}R_{\rm  Ia}$ produces an effective heating parameter (eq.~[\ref{eq:vw_eff}]) of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
-E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
+Type Ia SNe represent a source of heating, which unlike core collapse
+SNe is present even in an evolved stellar population.  If each SN Ia
+injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and
+the SN rate per stellar mass is given by $R_{\rm Ia}$, then the
+resulting volumetric heating rate of $E_{\rm Ia}R_{\rm Ia}$ produces
+an effective heating parameter (eq.~[\ref{eq:vw_eff}])
+of \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm
+        Ia}}{\eta}} \label{eq:vw_sne}.
 \end{align} The thermal energy injected by each SN Ia, $E_{\rm Ia} \simeq
@@
   \end{eqnarray}
-where the second line assumes $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation (e.g. , \citealt{Ciotti+91}).
+  where the second line assumes $\eta\simeq 0.02
+  (\tau_{\star}/t_h)^{-1.3}$ for a single burst of star formation
+  (e.g. , \citealt{Ciotti+91}).
 
@@
     r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma_0}\right)^{1/2} \sim
-    29 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc}
+    35 M_{\bullet,8}^{-0.1}(\tau_{\star}/t_{\rm h})^{0.56}\,{\rm pc}
     \label{eq:rIa}
@@
   adopt the Ia rate for an old stellar population and in the final
-  equality we estimate $\sigma_0 \approx \sqrt{3}\sigma_{\bullet}$ using $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
+  equality we estimate $\sigma_0 \approx \sqrt{3}\sigma_{\bullet}$
+  using $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).
 
@@
 
-However, even if SN Ia are rare near the stagnation radius, SN Ia may cap the
-SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between successive SNe, stars release a
+However, even if SN Ia are rare near the stagnation radius, SN Ia may
+cap the SMBH accretion rate by periodically blowing gas out of the
+nucleus of low mass galaxies.  Between successive SNe, stars release a
 gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
-interior to the Ia radius, which is locally gravitationally bound to the SMBH
-by an energy $E_{\rm bind} \sim M_{\rm g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F} 
-\lesssim$ few.  From the above definitions we find that 
-\be
-\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.  
+interior to the Ia radius, which is locally gravitationally bound to
+the SMBH by an energy $E_{\rm bind} \sim M_{\rm
+  g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F}
+\lesssim$ few.  From the above definitions we find that \be
+\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm
+    Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.
 \label{eq:blowout}

### 2015-04-10 ms.tex
zakamska

@@
 
-In addition to our solutions which neglect thermal conduction and radiative cooling, we explore a smaller set of simulations including these effects explicitly, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions that are only marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
-We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
-Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}, with the unstable values of $\eta$ provided in the final column.
-
-Thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$.
-Conduction may, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+In addition to our solutions which neglect thermal conduction and
+radiative cooling, we explore a smaller set of simulations including
+these effects explicitly, as marked by dagger symbols in Table
+\ref{table:models}.  For solutions which are far from being thermally
+unstable when cooling is neglected (e.g., $M_{\bullet} =
+10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
+0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
+radiative cooling has little effect on the key properties of the flow,
+e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
+marginally thermally stable, including radiative losses acts to
+decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
+greater fractional amount.  We calculated solutions with radiative
+cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
+core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
+values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
+expected mass loss rates.  Solutions found to be unstable for all
+values of $\eta$ are marked in boldface as ``TI" in Table
+\ref{table:models}, with the unstable values of $\eta$ provided in the
+final column.
+
+Thermal conduction, by contrast, results in only order unity changes
+to our results for the stagnation radius (and hence the accretion
+rate) for our fiducial value of the saturation parameter $\phi =0.1$.
+% Conduction may, however, offset the effects of radiative cooling in
+% making the flow more thermally stable
+% (e.g.~\citealt{Zakamska&Narayan03}).
 

### 2015-04-10 ms.tex

--- 2015-04-10 ms.tex
@@
   profiles.  Mass is supplied to the circumnuclear medium by stellar
-  winds, while energy is injected primarily by stellar winds, supernovae,
-  and black hole feedback.  Analytic estimates are derived for the
-  stagnation radius (where the radial velocity of the gas passes
-  through zero) and the black hole accretion rate, $\dot{M}$, as a
-  function of $M_{\bullet}$ and the gas heating efficiency, the latter
-  being related to the star-formation history.  We assess the
-  conditions under which radiative instabilities develop, both
-  in the case of a single burst of star formation and for the average
-  star formation history predicted by cosmological simulations.  By combining a sample
-  of measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent
-  galactic nuclei with our results for $\dot{M}(M_{\bullet})$ we show
-  that most nuclei are consistent with accreting in a steady-state,
-  thermally-stable manner for radiative efficiencies predicted by ADAF models. 
-However, thermally-stable accretion cannot explain the short average growth times of low mass black holes in
-  the local universe, which must instead result from gas being fed in
-  from large radii, due either to galaxy mergers or thermal
-  instabilities acting on larger, galactic scales.  Our results have
-  implications for attempts to constrain the occupation fraction of
-  SMBHs in low mass galaxies using the mean $L_{\rm X}-M_{\bullet}$
-  correlation, as well as the predicted diversity of the circumnuclear
-  densities encountered by relativistic outflows from tidal disruption
-  events.
+  winds, while energy is injected primarily by stellar winds,
+  supernovae, and black hole feedback.  Analytic estimates are derived
+  for the stagnation radius (where the radial velocity of the gas
+  passes through zero) and the black hole accretion rate, $\dot{M}$,
+  as a function of $M_{\bullet}$ and the gas heating efficiency, the
+  latter being related to the star-formation history.  We assess the
+  conditions under which radiative instabilities develop, both in the
+  case of a single burst of star formation and for the average star
+  formation history predicted by cosmological simulations.  By
+  combining a sample of measured nuclear X-ray luminosities, $L_{X}$,
+  of nearby quiescent galactic nuclei with our results for
+  $\dot{M}(M_{\bullet})$ we show that most nuclei are consistent with
+  accreting in a steady-state, thermally-stable manner for radiative
+  efficiencies predicted by ADAF models.  However, thermally-stable
+  accretion cannot explain the short average growth times of low mass
+  black holes in the local universe, which must instead result from
+  gas being fed in from large radii, due either to galaxy mergers or
+  thermal instabilities acting on larger, galactic scales.  Our
+  results have implications for attempts to constrain the occupation
+  fraction of SMBHs in low mass galaxies using the mean $L_{\rm
+    X}-M_{\bullet}$ correlation, as well as the predicted diversity of
+  the circumnuclear densities encountered by relativistic outflows
+  from tidal disruption events.
 \end{abstract}
@@
 
-In addition to our solutions which neglect thermal conduction and radiative cooling, we explore a smaller set of simulations including these effects explicitly, as marked by dagger symbols in Table \ref{table:models}.
-For solutions which are far from being thermally unstable when cooling is neglected (e.g., $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of radiative cooling has little effect on the key properties of the flow, e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions that are only marginally thermally stable, including radiative losses acts to decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fractional amount.
-We calculated solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of expected mass loss rates.
-Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table \ref{table:models}, with the unstable values of $\eta$ provided in the final column.
-
-Thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$.
-Conduction can, however, offset the effects of radiative cooling in making the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
+In addition to our solutions which neglect thermal conduction and
+radiative cooling, we explore a smaller set of simulations including
+these effects explicitly, as marked by dagger symbols in Table
+\ref{table:models}.  For solutions which are far from being thermally
+unstable when cooling is neglected (e.g., $M_{\bullet} =
+10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
+0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
+radiative cooling has little effect on the key properties of the flow,
+e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
+marginally thermally stable, including radiative losses acts to
+decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
+greater fractional amount.  We calculated solutions with radiative
+cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
+core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
+values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
+expected mass loss rates (see Fig.~\ref{fig:vwSources}).  Solutions
+found to be unstable for all values of $\eta$ are marked in boldface
+as ``TI" in Table \ref{table:models}, with the unstable values of
+$\eta$ provided in the final column.
+
+Thermal conduction, by contrast, results in only order unity changes
+to our results for the stagnation radius (and hence the accretion
+rate) for our fiducial value of the saturation parameter $\phi =0.1$.
+% Conduction may, however, offset the effects of radiative cooling in
+% making the flow more thermally stable
+% (e.g.~\citealt{Zakamska&Narayan03}).
+
+In addition to our solutions which neglect thermal conduction and
+radiative cooling, we explore a smaller set of simulations including
+these effects explicitly, as marked by dagger symbols in Table
+\ref{table:models}.  For solutions which are far from being thermally
+unstable when cooling is neglected (e.g., $M_{\bullet} =
+10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
+0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
+radiative cooling has little effect on the key properties of the flow,
+e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
+marginally thermally stable, including radiative losses acts to
+decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
+greater fractional amount.  We calculated solutions with radiative
+cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
+core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
+values of $\eta = 0.02, 0.2,$ and 0.6, spanning the physical range of
+expected mass loss rates for the halo average star formation
+histories (see figure.  Solutions found to be unstable for all values of $\eta$
+are marked in boldface as ``TI" in Table \ref{table:models}, with the
+unstable values of $\eta$ provided in the final column.
+
+Thermal conduction, by contrast, results in only minor changes to our
+solutions for our fiducial value of the saturation parameter $\phi =
+0.1$.  Thermal conduction, by contrast, results in only order unity
+changes to our results for the stagnation radius (and hence the
+accretion rate) for our fiducial value of the saturation parameter
+$\phi =0.1$.
 

### 2015-04-10 ms.tex
fix repeat

@@
 radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
-Radiative cooling is calculated using the cooling function from \citealt{Draine:2011a}.
-For high heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling
-is unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$
-we see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$
-can be less than unity, depending on the wind mass loss parameter
-$\eta$.  Because at the stagnation radius $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$ reaches within a factor
-of two of its minimum across the entire grid, the value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be taken as diagnostic of thermal instability at all radii.
+Radiative cooling is calculated using the cooling function from
+\citealt{Draine:2011a}.  For high heating rates of $v_{w} = 600$ and
+$1200$ km s$^{-1}$ cooling is unimportant across all radii, while for
+$v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$ can be less than unity,
+depending on the wind mass loss parameter $\eta$.  Because at the
+stagnation radius $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches
+within a factor of two of its minimum across the entire grid, the
+value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be
+taken as diagnostic of thermal instability at all radii.
 
@@
 values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
-expected mass loss rates (see Fig.~\ref{fig:vwSources}).  Solutions
-found to be unstable for all values of $\eta$ are marked in boldface
-as ``TI" in Table \ref{table:models}, with the unstable values of
-$\eta$ provided in the final column.
-
-Thermal conduction, by contrast, results in only order unity changes
-to our results for the stagnation radius (and hence the accretion
-rate) for our fiducial value of the saturation parameter $\phi =0.1$.
-% Conduction may, however, offset the effects of radiative cooling in
-% making the flow more thermally stable
-% (e.g.~\citealt{Zakamska&Narayan03}).
-
-In addition to our solutions which neglect thermal conduction and
-radiative cooling, we explore a smaller set of simulations including
-these effects explicitly, as marked by dagger symbols in Table
-\ref{table:models}.  For solutions which are far from being thermally
-unstable when cooling is neglected (e.g., $M_{\bullet} =
-10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
-0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
-radiative cooling has little effect on the key properties of the flow,
-e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
-marginally thermally stable, including radiative losses acts to
-decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
-greater fractional amount.  We calculated solutions with radiative
-cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
-core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
-values of $\eta = 0.02, 0.2,$ and 0.6, spanning the physical range of
-expected mass loss rates for the halo average star formation
-histories (see figure.  Solutions found to be unstable for all values of $\eta$
-are marked in boldface as ``TI" in Table \ref{table:models}, with the
-unstable values of $\eta$ provided in the final column.
+expected mass loss for continuous star formation (see
+Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all
+values of $\eta$ are marked in boldface as ``TI" in Table
+\ref{table:models}, with the unstable values of $\eta$ provided in the
+final column.
 

### 2015-04-10 be.tex
spell checker

@@
 The critical heating value $\zeta_c$ is an increasing function of
-$r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp
+$r_{b}/r_{\rm inf}$ and is larger for core galaxies than cusp
 galaxies, since a greater heating rate is required to unbind gas from

### 2015-04-10 windheat.tex
spell checker

@@
 
-In the case of a single implusive burst of star formation, the mass
+In the case of a single impulsive burst of star formation, the mass
 and energy injection rate per unit stellar mass at time $t$ after the
@@
   satellite halos rather than {\it in situ} star formation.  To
-  accomodate this, we incorporate analytic fits for mass accretion
+  accommodate this, we incorporate analytic fits for mass accretion
   histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},

### 2015-04-10 ms.tex
spell checker
spelling

@@
 present in $\S\ref{sec:numerical}$.  We move from a general and
-parametrized treatment of heating to a physically motivated one in \S
+parameterized treatment of heating to a physically motivated one in \S
 \ref{sec:heating}, where we consider a range of physical processes
@@
 
-\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the SFH in the galactic nuclear region.
+\item Stellar wind heating, supernovae, and AGN feedback depend explicitly on the SMBH mass as well as the SFH in the galactic nuclear region.
 A young starburst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old stellar populations  mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
@@
   activity must instead be driven by a supply of gas external to the
-  nucleaus, e.g. due to galaxy mergers or thermal instabilities on
+  nucleus, e.g. due to galaxy mergers or thermal instabilities on
   larger, galactic scales (e.g.~\citealt{Voit+15}).
@@
       than the background galaxy starlight, suggesting the presence of
-      younger stars towards galactic centre {\bf AG mass
+      younger stars towards galactic center {\bf AG mass
         threshold for this effect}.
@@
 In the case of high heating, a smaller break radius does not appreciably change the stagnation radius, resulting in a similar SMBH accretion rate.
-For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagation radius and accretion rate.
+For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagnation radius and accretion rate.
 %      be for large break radii, the stagnation radius would move

### 2015-04-10 ms.tex
figure show now reflect new Ia radius prescription
runaway and nscs.

@@
 with the Bernoulli parameter of the gas decreasing below unity near
-the stagnation radius (Appendix \ref{app:be}).  This divergence of the
-stagnation radius to large radii occurs at a higher value of $\zeta$
-in core galaxies ($\Gamma = 0.8$) with large break radii, explaining
-the behavior of the two core galaxies shown in Fig.~\ref{fig:stag} as
-vertically aligned orange triangles.  These solutions correspond to
-the same black hole mass ($\Mbh = 10^8 \Msun$) and heating rate ($v_w
-= 600$ km s$^{-1}$) but assume different break radii of $r_{b} =$ 25,
-50 pc (from top to bottom).
+the stagnation radius (Appendix \ref{app:be}).  Thus, for small values
+of the heating rate (small $\zeta$) the location of the stagnation
+radius will vary strongly with the break radius. This explains the
+behavior of the two vertically aligned green circles. These are two cusp
+($\Gamma=0.8$) galaxies with the $\Mbh=10^7 \Msun$ and $v_w=300$ km/s
+but with different break radii ($\rb=100, 400$ pc from top to
+bottom). This divergence of the stagnation radius to large radii
+occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.1$),
+explaining the behavior of the two core galaxies shown in
+Fig.~\ref{fig:stag} as vertically aligned orange triangles.  These
+solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
+and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
+radii of $r_{b} =$ 25, 50 pc (from top to bottom).
 
@@
     correspond to cores ($\Gamma = 0.1$). Green circles correspond to
-    cusp solutions which would be thermally unstable. The black curves
-    correspond to the analytic prediction from equation
-    (\ref{eq:rs2main}), with thick solid and dot-dashed curves
-    calculated for parameters $(\Gamma=0.8, \densSlope\simeq 1)$ and
-    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. The thin black
-    solid line corresponds to the simplified analytic result for $\rs$
-    from equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
+    cusp solutions which would be thermally unstable. The green circle
+    with an upwards arrow corresponds to a lower bound--this is a
+    model for where we were not able to obtain a converged value for
+    the stagnation radius as it moves outwards when the outer boundary
+    is moved outwards. The black curves correspond to the analytic
+    prediction from equation (\ref{eq:rs2main}), with thick solid and
+    dot-dashed curves calculated for parameters $(\Gamma=0.8,
+    \densSlope\simeq 1)$ and $(\Gamma=0.1,\densSlope\simeq0.6)$,
+    respectively. The thin black solid line corresponds to the
+    simplified analytic result for $\rs$ from
+    equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
     \Mbheight^{0.6} {\rm pc}$).}
@@
     ($\Gamma$=0.1). Green circles correspond to cusp solutions which
-    would be thermally unstable.  Thin solid and dot-dashed curves
-    correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm
-      edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
+    would be thermally unstable.  The green circle with an upwards
+    arrow corresponds to a lower bound--this is a model for where we
+    were not able to obtain a converged value for the stagnation
+    radius as it moves outwards when the outer boundary is moved
+    outwards.  Thin solid and dot-dashed curves correspond to our
+    analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
+    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
     respectively. Equation ~[\ref{eq:eddr_analytic}] is derived from
@@
 
-% \begin{figure}
-% \includegraphics[width=\columnwidth]{eta.pdf}
-% \includegraphics[width=\columnwidth]{rs_rIa.pdf}
-% \caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
-%   characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
-%   function of black hole mass $\Mbh$, calculated for average star
-%   formation histories from \citet{MosterNaab+:2013a} (see
-%   Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
-%   of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
-%   radius calculated from equation~\eqref{eq:rIa} based on convolving
-%   the average star formation histories with the SN Ia DTD.  The
-%   stagnation radius is calculated from \eqref{eq:stag_simple} using
-%   the total heating rate for each $\Mbh$ shown in the top panel. }
-% \end{figure}
-
 \subsection{Combined Heating Rate} 
@@
 source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
-the average SFH of galaxies containing a given
-black hole mass.  The younger stellar populations characterizing galaxies
-with $\Mbh\lsim 3\times 10^{8} \Msun$ are dominated by stellar winds, with $v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.  Only for $\Mbh\gsim 3\times 10^{8} \Msun$ does the lack
-of young stellar populations significantly reduce the role of stellar
-wind heating.
-But for these massive galaxies, the Ia radius is sufficiently small for SN Ia to contribute a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km s$^{-1}$ (in low mass galaxies SN Ia do not contribute to the total heating rate because $r_{\rm Ia} > \rs$; bottom panel).
-Strikingly, we find that galactic nuclei experiencing the same
-  average SFH as their host galaxies produce thermally stable flows across almost all black hole masses.
-
-An important caveat, however, is that $\vw$ is only a few times higher than the stellar velocity dispersion, i.e.
-$\zeta \sim \zeta_c$ (eq.~[\ref{eq:zetacrit}]).
-This implies that the true stagnation radius and SMBH accretion rate could be larger than our analytic estimates, potentially resulting in thermal instability, especially for core galaxies with large break radii ($\S\ref{sec:mdot}$).
-In other words, the CNM of some subset of massive ellipticals be thermally unstable, not necessarily because they are receiving lower stellar feedback than the average for their galaxy mass, but due to the high heating required for stability given the structure of their stellar potential.
+the average SFH of galaxies containing a given black hole mass.  The
+younger stellar populations characterizing galaxies with $\Mbh\lsim
+3\times 10^{8} \Msun$ are dominated by stellar winds, with
+$v_{w}^{\star} \gtrsim 700$ km s$^{-1}$.  Only for $\Mbh\gsim 3\times
+10^{8} \Msun$ does the lack of young stellar populations significantly
+reduce the role of stellar wind heating.  But for these massive
+galaxies, the Ia radius is sufficiently small for SN Ia to contribute
+a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km
+s$^{-1}$ (in low mass galaxies SN Ia do not contribute to the total
+heating rate because $r_{\rm Ia} > \rs$; bottom panel).  Strikingly,
+we find that galactic nuclei experiencing the same average SFH as
+their host galaxies produce thermally stable flows across almost all
+black hole masses.
+
+An important caveat, however, is that $\vw$ is only a few times higher
+than the stellar velocity dispersion, i.e. $\zeta \sim \zeta_c$
+(eq.~[\ref{eq:zetacrit}]).  This implies that the true stagnation
+radius and SMBH accretion rate could be larger than our analytic
+estimates, potentially resulting in thermal instability, especially
+for core galaxies with large break radii ($\S\ref{sec:mdot}$).  In
+other words, the CNM of some subset of massive ellipticals be
+thermally unstable, not necessarily because they are receiving lower
+stellar feedback than the average for their galaxy mass, but due to
+the high heating required for stability given the structure of their
+stellar potential.
 
@@
 
-We conclude by drawing attention to the following limitations of our model.
-First, by neglecting any large scale inflow of gas to the nucleus and assuming the only source of gas feeding the black hole is stellar wind mass loss from the local stellar population, our estimates represent a lower bound on the gas density of the CNM.
-Our model therefore cannot account for AGN.
-
-Predictions for the  SMBH accretion rate are strongly tied to the age and radial distribution of the stellar population within the sphere of influence.
-Our model therefore cannot make definitive predictions for the accretion mode of individual galaxies without knowledge of their specific SFH.
-We adopt halo average star formation rates measured in cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any spatial variation in the star formation rate for any given galaxy.
-However, galaxies of mass $\gsim 7\times 10^{10} \Msun$ assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, resulting in galactic nuclei which may be systematically older than assumed in our model and thus more prone to thermal instability.
-
-On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
-      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
-      (generally unresolved) emission in excess of the inward
-      extrapolation of the Nuker law.  They note that these nuclei are bluer
-      than the background galaxy starlight, suggesting the presence of
-      younger stars towards galactic center {\bf AG mass
-        threshold for this effect}.
-Mass injection to the nucleus could in some cases therefore be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e.
-much smaller than our fiducial value of $r_b \sim 100$ pc.
-In the case of high heating, a smaller break radius does not appreciably change the stagnation radius, resulting in a similar SMBH accretion rate.
-For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagnation radius and accretion rate.
-%      be for large break radii, the stagnation radius would move
- %     inwards somewhat. However note the for high heating rate ($v_w
-  %    \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
-   %   \Msun$), we predict stagnation radii smaller than a parsec.
+We conclude by drawing attention to the following limitations of our
+model.  First, by neglecting any large scale inflow of gas to the
+nucleus and assuming the only source of gas feeding the black hole is
+stellar wind mass loss from the local stellar population, our
+estimates represent a lower bound on the time averaged gas density of
+the CNM.  Our model therefore cannot account for AGN.
+
+Predictions for the SMBH accretion rate are strongly tied to the age
+and radial distribution of the stellar population within the sphere of
+influence.  Our model therefore cannot make definitive predictions for
+the accretion mode of individual galaxies without knowledge of their
+specific SFH.  We adopt halo average star formation rates measured in
+cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any
+spatial variation in the star formation rate for any given
+galaxy. However, galaxies of mass $\gsim 7\times 10^{10} \Msun$
+assemble their stars from the inside out
+\citep{PerezCidFernandes+:2013a}, resulting in galactic nuclei which
+may be systematically older than assumed in our model and thus more
+prone to thermal instability.
+
+On the other hand, \citealt{LauerFaber+:2005a} find that $\sim 60\%$
+of cusp galaxies and $\sim29\%$ of core galaxies have (generally
+unresolved) emission in excess of the inward extrapolation of the
+Nuker law.  They note that these nuclei are bluer than the background
+galaxy starlight, suggesting the presence of younger stars towards
+galactic center. Nuclear star cluster could be important for small
+values of $M_{\rm bulge}\lsim 10^{11} \Msun$ ($\Mbh\lsim 2\times 10^8
+\Msun$), but are extremely subdominant for higher mass galaxies
+\citep{GrahamSpitler:2009a}.
+
+Mass injection to the nucleus could (for $\Mbh\lsim 2 \times 10^{8}
+\Msun$) therefore be dominated by a nuclear star cluster with its own
+break radius on parsec scales, i.e. much smaller than our fiducial
+value of $r_b \sim 100$ pc.  In the case of high heating, a smaller
+break radius does not appreciably change the stagnation radius,
+resulting in a similar SMBH accretion rate.  For break radii smaller
+than the nominal stagnation radius, the presence of a smaller break
+radius would likely decrease the stagnation radius and accretion rate.
 

### 2015-04-10 ms.tex
remove non-converged.

@@
     ... & 1200 & -- & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
-    $    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
-    ... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
+%    $    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
+   10$^{7}$ & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
 % ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
@@
 radius will vary strongly with the break radius. This explains the
-behavior of the two vertically aligned green circles. These are two cusp
-($\Gamma=0.8$) galaxies with the $\Mbh=10^7 \Msun$ and $v_w=300$ km/s
-but with different break radii ($\rb=100, 400$ pc from top to
-bottom). This divergence of the stagnation radius to large radii
-occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.1$),
-explaining the behavior of the two core galaxies shown in
-Fig.~\ref{fig:stag} as vertically aligned orange triangles.  These
-solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
-and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
-radii of $r_{b} =$ 25, 50 pc (from top to bottom).
+behavior of the two vertically aligned green circles with a green
+circle on top. These are two cusp ($\Gamma=0.8$) galaxies with
+$\Mbh=10^8 \Msun$ and $v_w=300$ km/s but with different break radii
+($\rb=$ 25, 50, and 100 pc from top to bottom). This divergence of the
+stagnation radius to large radii occurs at a higher value of $\zeta$
+in core galaxies ($\Gamma = 0.1$), explaining the behavior of the two
+core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned
+orange triangles.  These solutions correspond to the same black hole
+mass ($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$)
+but assume different break radii of $r_{b} =$ 25, 50 pc (from top to
+bottom).
 
@@
     correspond to cores ($\Gamma = 0.1$). Green circles correspond to
-    cusp solutions which would be thermally unstable. The green circle
-    with an upwards arrow corresponds to a lower bound--this is a
-    model for where we were not able to obtain a converged value for
-    the stagnation radius as it moves outwards when the outer boundary
-    is moved outwards. The black curves correspond to the analytic
-    prediction from equation (\ref{eq:rs2main}), with thick solid and
-    dot-dashed curves calculated for parameters $(\Gamma=0.8,
-    \densSlope\simeq 1)$ and $(\Gamma=0.1,\densSlope\simeq0.6)$,
-    respectively. The thin black solid line corresponds to the
-    simplified analytic result for $\rs$ from
-    equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
+    cusp solutions which would be thermally unstable.  The black
+    curves correspond to the analytic prediction from equation
+    (\ref{eq:rs2main}), with thick solid and dot-dashed curves
+    calculated for parameters $(\Gamma=0.8, \densSlope\simeq 1)$ and
+    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. The thin black
+    solid line corresponds to the simplified analytic result for $\rs$
+    from equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
     \Mbheight^{0.6} {\rm pc}$).}
@@
     ($\Gamma$=0.1). Green circles correspond to cusp solutions which
-    would be thermally unstable.  The green circle with an upwards
-    arrow corresponds to a lower bound--this is a model for where we
-    were not able to obtain a converged value for the stagnation
-    radius as it moves outwards when the outer boundary is moved
-    outwards.  Thin solid and dot-dashed curves correspond to our
-    analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
-    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
+    would be thermally unstable.  Thin solid and dot-dashed curves
+    correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm
+      edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
     respectively. Equation ~[\ref{eq:eddr_analytic}] is derived from

### 2015-04-11 ms.tex
cleaned up3

@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ will usually reside near the nominal Bondi
+show that $\rs$ usually resides near the nominal Bondi
 radius).  When heating is sufficiently weak, however, the stagnation
@@
   \rs\approx\frac{13+8\Gamma}{4+2\Gamma}\frac{G \Mbh}{\densSlope
-    \vw^2} \approx 2 \frac{13+8\Gamma}{(4+2\Gamma)(3+4\Gamma)}r_{\rm B},
+    \vw^2} \approx \frac{13+8\Gamma}{(2+\Gamma)(3+4\Gamma)}r_{\rm B},
   \label{eq:rbondi}
@@
 \item Low mass black holes grow in the low redshift universe over
-  timescales comparable to the Hubble time (\citet{Heckman+04}).  This
+  timescales comparable to the Hubble time (\citealt{Heckman+04}).  This
   accretion rates so required are too high to be consistent with the

### 2015-04-11 ms.tex
fixing missing berger file.

@@
 \citealt{Bloom+11}, \citealt{Burrows+11}; \citealt{Zauderer+11}).
-This event was powered by an impulsive relativistic jet,
-which produced synchrotron radio emission as the jet material
-decelerated from shock interaction with the CNM of the previously
-quiescent SMBH (\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).
-Detailed modeling of J1644+57 showed that the CNM density was much
-lower than that measured surrounding Sgr A$^{\star}$ on a similar radial scale
-(\citealt{Metzger+12}; \citealt{BergerZauderer+2012a}).  However, a TDE jet
-injected into a denser CNM would be decelerated more rapidly,
+This event was powered by an impulsive relativistic jet, which
+produced synchrotron radio emission as the jet material decelerated
+from shock interaction with the CNM of the previously quiescent SMBH
+(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
+modeling of J1644+57 showed that the CNM density was much lower than
+that measured surrounding Sgr A$^{\star}$ on a similar radial scale
+(\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a
+TDE jet injected into a denser CNM would be decelerated more rapidly,
 producing potentially very different radio emission than in J1644+57.

### 2015-04-13 ms.tex
cleaned up4

--- 2015-04-11 ms.tex
@@
 Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.
-This condition is approximately equivalent to the criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
+This condition is approximately equivalent to the $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
 

### 2015-04-13 ms.tex
adjusting the vwTI

--- 2015-04-11 ms.tex
@@
   {\rm max}\begin{cases}
-   300 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
-   260 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
+   280 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
+   240 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
 \approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 

### 2015-04-13 ms.tex
adjusting ti

@@
     4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
-    7\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
+    8\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
     1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c

### 2015-04-20 ms.tex
modifying figures for new compton prescription.
modifying angular momentum description.

@@
 is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
-half-light radius and that $\lambda_R$ decreases with decreasing $R$ interior to this point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm
-  circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well
-inside the inner sonic point of the flow ($r\lsim
-0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).  Angular momentum should only
-become dynamically important for thermally stable flows in a region
-that is causally disconnected from the outer part of the flow where
-the mass accretion rate is determined.
+half-light radius and that $\lambda_R$ decreases with decreasing $R$
+interior to this point.  From equation (\ref{eq:rcirc}) we thus
+conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will
+circularize the inner sonic point of the flow ($r\gsim 0.01r_{\rm s}$;
+Fig.~\ref{fig:profiles}).  Angular momentum should only become
+dynamically important for thermally stable flows in a region that is
+causally disconnected from the outer part of the flow. Thus, the flow
+properties on large scales will generally be unaffected by angular momentum.
+
+For $r\simeq r_{\rm circ} $ the gas will encounter a centrifugal
+barrier, which means that much of the gas flowing in from larger
+scales will be driven out in a conical outflow. The actual accretion
+rate will be $\sim\alpha$ times the accretion rate on large scales
+\citep{Li+2013}.
 
@@
 \end{align}
-If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for
-radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
-\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
+
+\citet{Sharma+2007} calculate the radiative efficiency, $\epsilon$,
+based on MHD shearing box simulations of collisionless plasmas. For
+accretion rates $10^{-4} \gsim \eddr \lsim 10^{-2}$, the radiative
+efficiency is $\sim 2.6\%$ {\bf AG described in more
+  detail?}. Additionally, a large fraction of the $\dot{M}$ on large scales
+will be driven out in outflows as the gas has some non-zero angular
+momentum and a centrifugal barrier will stop it from accreting
+\citet{Li+2013}. In the limit weak cooling appropriate for low
+accretion rates the accretion rate on small scales will be of order
+$\alpha \Mdot$. Here we adopt $\alpha=0.1$ so that our overall
+efficiency is 0.26\%
+
 \begin{align}
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 1.7\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
+\begin{cases} 5.9\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
 C,9}^{-0.44}M_{\bullet,8}^{0.09}
-&, \text{core}\\ 8.6\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
+&, \text{core}\\ 2.1\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
 C,9}^{-0.4} M_{\bullet,8}^{0.08}
@@
 \end{align}
-We note that accretion is unlikely to be steady in cases where AGN heating dominates, due to the inherent delay between black hole feedback and the structure of the accretion flow on larger scales.
-Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless represent characteristic average value for the accretion rate, assuming a quasi-equilibrium state is achieved over many cycles.
+We note that accretion is unlikely to be steady in cases where AGN
+heating dominates, due to the inherent delay between black hole
+feedback and the structure of the accretion flow on larger scales.
+Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless
+represent characteristic average value for the accretion rate,
+assuming a quasi-equilibrium state is achieved over many cycles.
 %{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

### 2015-04-20 ms.tex
outflows...

@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
-  black hole accretion rate $\dot{M}$ in Eddington units as a function
-  of black hole mass $M_{\bullet}$, shown separately for core
-  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$,
-  solid).  Black lines show the accretion rate calculated
-  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
+\caption{\label{fig:bh_growth} {\it Top panel:} Black hole accretion
+  rate (excluding small-scale outflows) $\dot{M}$ in Eddington units
+  as a function of black hole mass $M_{\bullet}$, shown separately for
+  core ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$,
+  solid).  Black lines show the accretion rate calculated from
+  equation (\ref{eq:eddr_analytic}) using our estimate of the gas
   heating rate provided at $z = 0$ by the average star formation
@@
   lines show the maximum accretion set by Ia supernovae blow-out
-  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained
-  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
+  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if
+  Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
   lines show the maximum accretion rate for a thermally stable flow
@@
   (gray diamonds), and for the Swift J1644+57 TDE from
-  \citet{BergerZauderer+:2012a} (gray triangles) {\it Bottom panel:}
-  Growth times $\Mbh/\Mdot$ in units of the Hubble time $\th$ for each
-  of the accretion rates shown in the top panel.}
+  \citet{BergerZauderer+:2012a} (gray triangles). Note that the actual
+  black hole accretion rate will be a factor of the Shakura-Sunyaev
+  $\alpha$ smaller than the $\Mdot$s here due to small scale
+  outflows. Thus the plot is really showing the gas inflow rate on
+  large scales (e.g. near the stagnation radius) {\it Bottom panel:} Growth
+  times $\Mbh/\Mdot$ in units of the Hubble time $\th$ for each of the
+  accretion rates shown in the top panel.}
 \end{figure}

### 2015-04-20 ms.tex
reminder

@@
 unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
-the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
-
-Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).
-The high stellar densities of such a compact star cluster could greatly enhance the TDE rate (e.g.~\citealt{Stone&Metzger15}), possibly making this association uncoincidental.
+the mean $r_b-M_{\bullet}$ relationship
+\citep{LauerFaber+:2007a}. {\bf Other constraints on gas density:
+  J1644 gone mad}
+
+Alternatively, the observed density break in J1644+57 could result
+from the outer edge of a sub-parsec nuclear star cluster (e.g.,
+\citealt{Carson+15}).  The high stellar densities of such a compact
+star cluster could greatly enhance the TDE rate
+(e.g.~\citealt{Stone&Metzger15}), possibly making this association
+uncoincidental.
 

### 2015-04-21 ms.tex
fixing description of impulsive limit

@@
 which $r_{ \rm Ia} < \rs$.  For high-mass black holes
-(Fig.~\ref{fig:vwSourcesImp}, bottom panel), Compton heating dominates
-at all epochs, while SN Ia dominate after 10$^{8}$ yr.
+(Fig.~\ref{fig:vwSourcesImp}, bottom panel), stellar wind heating
+dominates early epochs, while SN Ia dominate after $10^{7}$ yr.
 

### 2015-04-21 ms.tex
cyclic

@@
 
-In this paper we instead focus on time-independent models, in cases when the nuclear gas receives sufficient heating to render radiative cooling negligible.
-This approach allows us to systematically explore the relevant parameter
-space and to derive analytic expressions that prove useful in
-determining whether cooling instabilities manifest across the expected
-range of galaxy properties, or whether other (non-AGN) forms of
-feedback can produce a prolonged state of steady, thermally stable
-accretion.  Even if cooling instabilities develop on galactic scales
-over longer $\sim$ Gyr timescales, a quasi steady-state may exist
-between these inflow events on smaller radial scales comparable to the
-sphere of influence.  We are thus motivated to explore whether such
-steady flows are generally expected within the nucleus, or
-whether in most galaxies the nuclear gas content is always building
-towards instability.
-%A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.
+Between outbursts \citealt{Ciotti+10} find that galactic nuclei exist
+in a quasi-stationary thermal stable state. We focus on this region of
+parameter space calculating time-independent models, in which the
+nuclear gas receives sufficient heating to render radiative cooling
+negligible.  This approach allows us to systematically explore the
+relevant parameter space and to derive analytic expressions that prove
+useful in determining under what conditions cooling instabilities
+manifest across the expected range of galaxy properties, or whether
+other (non-AGN) forms of feedback can produce a prolonged state of
+steady, thermally stable accretion.  Even if cooling instabilities
+develop on galactic scales over longer $\sim$ Gyr timescales, a quasi
+steady-state may exist between these inflow events on smaller radial
+scales comparable to the sphere of influence.  We are thus motivated
+to explore whether such steady flows are generally expected within the
+nucleus, or whether in most galaxies the nuclear gas content is always
+building towards instability.
 
@@
 radius exists, a question intimately tied to that of cooling
-instability.
+instability. {\bf AG this section still needs work...}
 
@@
 based on MHD shearing box simulations of collisionless plasmas. For
-accretion rates $10^{-4} \gsim \eddr \lsim 10^{-2}$, the radiative
+accretion rates $10^{-4} \lsim \eddr \lsim 10^{-2}$, the radiative
 efficiency is $\sim 2.6\%$ {\bf AG described in more
@@
 
-If the nuclei of elliptical galaxies are heated as expected for the average SFH of galaxies with
-similar mass, then to first order we predict that $\langle
-L_{X}/L_{\rm edd}\rangle$ should be a weakly increasing function of BH mass.
-This result is in tension with the observed down-sizing trend that the average Eddington ratio is seen to
-decrease (albeit weakly) with $M_{\bullet}$, especially in the $\epsilon_X= (\epsilon_{\rm
-  bol}/0.1)(\Mdot/\MdotEdd)$ model.
-However, one must keep in mind the enormous uncertainty in calculating the luminosity of the accretion flow close to the black hole in a single waveband based on the feeding rate on larger scales.
-If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the angular momentum of the infalling gas might also influence the X-ray luminosity, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.
+If the nuclei of elliptical galaxies are heated as expected for the
+average SFH of galaxies with similar mass, then to first order we
+predict that $\langle L_{X}/L_{\rm edd}\rangle$ should be a weakly
+increasing function of BH mass.  This result is in tension with the
+observed down-sizing trend that the average Eddington ratio is seen to
+decrease (albeit weakly) with $M_{\bullet}$, especially in the
+$\epsilon_X= (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$ model.
+However, one must keep in mind the enormous uncertainty in calculating
+the luminosity of the accretion flow close to the black hole in a
+single waveband based on the feeding rate on larger scales.  If disk
+outflows carry away most of the infalling mass before it reaches X-ray
+producing radii (e.g.~\citealt{Blandford&Begelman99};
+\citealt{Li+13}), then the angular momentum of the infalling gas might
+also influence the X-ray luminosity, in a way that could depend
+systematically on the stellar population and hence $M_{\bullet}$.
 
 Perhaps a more readily addressable test is whether a steady-state
-  accretion picture developed in this work can account for the the
-  large scatter, typically of $2-3$ orders of magnitude, in
-  $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.  Scatter could result
-  from at least three effects: (1) intrinsic scatter in the scaling
-  relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to
-  measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
-  the stellar wind velocity and mass loss parameter,
-  $\dot{M}/\dot{M}_{\rm edd} \propto \eta v_{w}^{-3.8(-2.4)}$ for
-  core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass};
-  eq.~[\ref{eq:eddr_analytic}]).  When combined with the significant
-  dependence of $v_w$ on stochastic intermittency in the star
-  formation history (Appendix \ref{fig:NickPlot2}), this can lead to
-  order of magnitude differences in $\dot{M}$; (3) differences in angular
-  momentum of the infalling gas from galaxy to galaxy, resulting in
-  differences in the fraction of the gas lost to outflows.
-  Also potentially contributing is the order of magnitude difference,
-  at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and
-  cusp galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$
-  are augmented by the theoretical expectation that $L_{\rm X} \propto \dot{M}^{2}
-  $ for radiatively inefficient flows.
-
-%Many of the upper
-%limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
-%separate ``thermally stable" population.  This possible dichotomy
-%calls into question the use of simple extrapolations of power-law fits
-%to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
-%constrain the occupation fraction of black holes in low mass galaxies
-%(\citealt{Miller+15}).
-
-\subsection{Steady Accretion versus Cyclic Outbursts}
+accretion picture developed in this work can account for the the large
+scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
+  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at least
+three effects: (1) intrinsic scatter in the scaling relationships
+($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to measure $\Mbh$; (2)
+the strong sensitivity of the accretion rate to the stellar wind
+velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
+\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
+(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When
+combined with the significant dependence of $v_w$ on stochastic
+intermittency in the star formation history (Appendix
+\ref{fig:NickPlot2}), this can lead to order of magnitude differences
+in $\dot{M}$; (3) differences in angular momentum of the infalling gas
+from galaxy to galaxy, resulting in differences in the fraction of the
+gas lost to outflows.  Also potentially contributing is the order of
+magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between
+$\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).
+Differences in $\dot{M}$ are augmented by the theoretical expectation
+that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
+flows.
+
+\subsection{Steady Accretion versus outbursts}
 \label{sec:cycle}
@@
 It is also possible that many of the \citet{Miller+15} sample of
-galactic nuclei are not accreting in steady state.  The 
-X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
-represents a maximum value, which does not for instance account for
-suppression of the SMBH accretion rate due to outflows from the
-accretion disk on small radial scales (e.g.,
-\citealt{Blandford&Begelman99}).  Furthermore, our SFH-averaged
-accretion rates are derived using analytic expressions for the
-stagnation radius that may underpredict the true accretion rate if
-$\zeta < \zeta_c$, as may occur in massive core galaxies with large
-break radii.
-
-If the actual radiative efficiency is lower than our
-fiducial assumption, then many of the X-ray detections would lie above
-the predictions for stable accretion, i.e., $L_X \gtrsim \epsilon_X \dot{M}_{\rm TI}$ (yellow line).  In this case the X-ray detected galaxies experience
-less heating than average galaxies of the same mass, and may not be
-stably accreting at all.  This is particularly plausible because the
-\citet{Miller+15} sample includes only early-type galaxies, with older
-stellar populations than the average for their black hole mass.
+galactic nuclei are not accreting in steady state. Within our steady
+state solutions gas outside the stagnation radius $\rs$ is being blown
+out in wind. However, for very massive galaxies ($\Mbh\gsim 10^8
+\Msun$) the energy injected into the gas is not enough to truly blow
+the gas out of the potential well of the galaxy. This gas is likely to
+build up on the outskirts of the galaxy until a thermal instability
+develops, causing the CNM to undergo cyclic oscillations of rapid
+cooling and high accretion rates, followed by quiescent periods once
+gas has been consumed and/or AGN feedback becomes effective. Such
+cycles are seen in numerical simulations of elliptical galaxies on
+large scales and long timescales (\citealt{Ciotti+10}).  Evidence for
+such periodic outbursts includes observations showing that a fraction
+of early-type galaxies in the local universe have undergone recent ($<
+1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
+
+Furthermore, our SFH-averaged accretion rates are derived using
+analytic expressions for the stagnation radius that may underpredict
+the true accretion rate if $\zeta < \zeta_c$, as may occur in massive
+core galaxies with large break radii.
+
+If the actual radiative efficiency is lower than our fiducial
+assumption, then many of the X-ray detections would lie above the
+predictions for stable accretion, i.e., $L_X \gtrsim \epsilon_X
+\dot{M}_{\rm TI}$ (yellow line).  For example, we assume 10\% 
+of the mass inflow rate is drive out in small scale outflows, but this
+fraction could be considerably large. In this case the X-ray detected
+galaxies experience less heating than average galaxies of the same
+mass, and may not be stably accreting at all.  This is particularly
+plausible because the \citet{Miller+15} sample includes only
+early-type galaxies, with older stellar populations than the average
+for their black hole mass.
 
@@
 
-If present, thermal instabilities may cause the CNM to undergo cyclic
-oscillations of rapid cooling and high accretion rates, followed by
-quiescent periods once gas has been consumed and/or AGN feedback
-becomes effective.  Such cycles are seen in numerical simulations of
-elliptical galaxies on large scales and long timescales
-(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes
-observations showing that a fraction of early-type galaxies in the
-local universe have undergone recent ($< 1-2$ Gyr old) star formation
-episodes (\citealt{Donas+07}).
-
 Similar cyclic AGN activity could occur on the smaller radial scale of
@@
 
-%This could help explain why core galaxies show a wide
-%range of nuclear radio luminosities (suggesting cyclic
-%accretion episodes), while cusp galaxies are confined below a
-%threshold (e.g., \citealt{Bender+89, Pellegrini99,
- % Capetti&Balmaverde05}), consistent with thermally-stable,
-%steady-state picture. ({\bf AG: This picture may be dubious...Review
- % the literature but I think that the higher upper bound for cores is
-  %just due to a mass selection effect.  BDM: Balmaverde
- % disagrees.})
-
 If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$
 in Fig \ref{fig:miller} are indeed in a state of thermally-unstable
-cyclic behavior, then a subset of the galaxies with X-ray upper limits
+outburst, then a subset of the galaxies with X-ray upper limits
 may contribute to a separate population of thermally stable, steadily
@@
 galaxies.
-
-%The cyclic model predicts that high $L_{X}$ nuclei should be more
-%common in galaxies with younger stellar ages, a result which appears
-%in tension with the finding by \citet{Pellegrini10} that galaxies with
-%younger stellar populations are observed to host less X-ray luminous
-%nuclei, at least for stellar ages $<3$ Gyr.  An alternative
-%explanation for this observation within a thermally stable,
-%steady-state accretion picture is that young stars provide higher
-%stellar wind heating, reducing the mass accretion rate and hence
-%nuclear X-ray luminosity.  {\bf AG Challenge: \citet{HeckmanBest:2014a}
- % find that ${\rm L_{[OIII]}}$ (a proxy for the bolometric luminosity)
-  %${\rm L_{[OIII]}/M_\star}$ (a proxy for the Eddington ratio)
-  %increases with decreasing 4000 $\AA$ break index (decreasing stellar
- % age) (see their Figure 14). This suggests that the accretion rate is
-  %actually increasing towards younger stellar ages. At young ages
-  %there actually seems to be plenty of gas around, which may be
-  %obscuring the x-rays and causing an anamolously low measurement of
-  %$L_X$.
-
-  %For a starburst the black hole accretion rate lags the star
-  %formation rate by 200 Myr (\citet{WildHeckman+:2010a} Figure
- % 9). This could be due to SNe feed back suppressing the black hole
-  %accretion rate (massive star winds do the same thing by themselves,
- % but they cannot be sustained for 200 Myr. 
-%}
 
@@
 That the growth time associated with thermally-unstable accretion
-(yellow line in Fig.~\ref{fig:bh_growth}) exceeds the Hubble time across all SMBH masses
-highlights the fact that significant black hole growth in the local
-universe cannot result from thermally-stable steady accretion of gas
-lost from the surrounding stellar population studied in this paper.
-Gas blow-out by SN Ia cannot alone prevent the growth of low-mass black
-holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
-Ia heating (green lines), although Ia heating could play in principle
-a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black
-holes, again depending on the efficiency of Ia heating and whether the
-galaxy is a core or cusp.
+(yellow line in Fig.~\ref{fig:bh_growth}) exceeds the Hubble time
+across all SMBH masses highlights the fact that significant black hole
+growth in the local universe cannot result from thermally-stable
+steady accretion of gas lost from the surrounding stellar population
+studied in this paper.  Gas blow-out by SN Ia cannot alone prevent the
+growth of low-mass black holes, as indicated by the low growth times
+$\ll t_{\rm h}$ allowed by Ia heating (green lines), although Ia
+heating could play in principle a role in capping the growth rate of
+$\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the
+efficiency of Ia heating and whether the galaxy is a core or cusp.
 
@@
 Our results also have implications for the environments encountered by
-relativistic jets from TDEs.  For low-mass SMBHs with $M_{\bullet} \lesssim
-10^{7}M_{\odot}$, such as that responsible for powering the transient {\it Swift}
-J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
-\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
-rates within the physically expected range $v_{\rm w} \sim 500-1000$
-km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
-range estimated by modeling the radio afterglow of {\it Swift}
-J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}), as shown in Fig.~\ref{fig:bh_growth}.
+relativistic jets from TDEs.  For low-mass SMBHs with $M_{\bullet}
+\lesssim 10^{7}M_{\odot}$, such as that responsible for powering the
+transient {\it Swift} J1644+57 (\citealt{Bloom+11}), we predict gas
+densities of a $n \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for
+wind heating rates within the physically expected range $v_{\rm w}
+\sim 500-1000$ km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values
+are within the range estimated by modeling the radio afterglow of {\it
+  Swift} J1644+57 (\citealt{Metzger+12},
+\citealt{BergerZauderer+:2012a}), as shown in
+Fig.~\ref{fig:bh_growth}.
 
@@
 
-%The implications of our model for the CNM profiles of quiescent galaxies on the diversity of radio emission from TDE
-%jets will be further developed in future work.
-
 \subsection{Regulation by SMBH Kinetic Feedback}
@@
 
-Our analysis of SMBH feedback has focused on Compton heating
-instead of kinetic feedback, since the effects of radiative feedback
-are relatively straightforward to calculate from the properties of the
-accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion, even in low luminosity AGN.
-
-Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assumes a uniform volumetric heating and predicts an
-effective wind velocity which increases with SMBH mass as
-$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
-galaxies, respectively.  Coupled with the dependence of the SMBH
-accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto
+Our analysis of SMBH feedback has focused on Compton heating instead
+of kinetic feedback, since the effects of radiative feedback are
+relatively straightforward to calculate from the properties of the
+accretion flow.  However, it is possible kinetic feedback from SMBH
+outflows could play an equal or greater role in regulating accretion,
+even in low luminosity AGN.
+
+Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}])
+assumes a uniform volumetric heating and predicts an effective wind
+velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto
+M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.
+Coupled with the dependence of the SMBH accretion rate on the wind
+heating, $\dot{M}/\dot{M}_{\rm edd} \propto
 M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass};
-eq.~[\ref{eq:eddr_analytic}]), a dominant source of kinetic feedback of the form we have
-adopted leads to an Eddington ratio dependence on SMBH mass of
-$\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.
-
-This prediction is also consistent with the observed dependence of $\langle
-L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
-(Fig.~\ref{fig:miller}, green line), suggesting that accretion regulation
-by kinetic feedback could play a role in determining the X-ray
-luminosities of elliptical galaxies.  However, our assumption that
-kinetic outflows heat the gas uniformly in volume is rather arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous
-environment.
-As already discussed, it is furthermore unclear whether a steady-state accretion model is at all relevant in the case when SMBH feedback dominates due to the time delay between the small scale accretion flow and the thermodynamic response of the CNM on larger scales.
+eq.~[\ref{eq:eddr_analytic}]), a dominant source of kinetic feedback
+of the form we have adopted leads to an Eddington ratio dependence on
+SMBH mass of $\dot{M}/\dot{M}_{\rm edd} \propto
+M_{\bullet}^{-0.5(-0.2)}$.
+
+This prediction is also consistent with the observed dependence of
+$\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
+(Fig.~\ref{fig:miller}, green line), suggesting that accretion
+regulation by kinetic feedback could play a role in determining the
+X-ray luminosities of elliptical galaxies.  However, our assumption
+that kinetic outflows heat the gas uniformly in volume is rather
+arbitrary and would need to more rigorously justified by numerical
+studies of how jets or disk outflows couple energy to their gaseous
+environment.  As already discussed, it is furthermore unclear whether
+a steady-state accretion model is at all relevant in the case when
+SMBH feedback dominates due to the time delay between the small scale
+accretion flow and the thermodynamic response of the CNM on larger
+scales.
 

### 2015-04-21 ms.tex
outflows

@@
 cent.  Note the sensitive dependence of the accretion rate on the wind
-heating rate.
-%To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$
+heating rate. Also, we emphasize that
+equation~\eqref{eq:eddr_analytic} represents the mass inflow rate on
+large scales and does not include small scale outflows. In reality, only
+a fraction $\alpha$ (the standard Shakura-Sunyaev parameter--assumed
+to be 0.1) will make it down to the black hole \citep{Li+2013}.
 
@@
 
-\item  The accretion rates of early-type galaxies are below the maximum value for thermally stable flow, $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies, similar to the maximum values predicted by ADAF models.
-Therefore the current X-ray detections could instead be comprised mostly of nuclei undergoing non-steady accretion due to thermal instabilities.
-In this case there may exist a separate branch of low-$L_X$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.
-Such a bimodal population would call into question methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in order to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).
+\item The accretion rates of early-type galaxies are below the maximum
+  value for thermally stable flow, $\dot{M}_{\rm TI}$
+  (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies.
+  Therefore the current X-ray detections could instead be comprised
+  mostly of nuclei undergoing outburst due to thermal instabilities.
+  In this case there may exist a separate branch of low-$L_X$
+  (undetected) thermally-stable nuclei, especially at low
+  $M_{\bullet}$.  Such a bimodal population would call into question
+  methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
+  to low $M_{\bullet}$ in order to constrain the SMBH occupation
+  fraction in low mass galaxies (\citealt{Miller+15}).
 

### 2015-04-21 ms.tex
piddling

@@
   \begin{enumerate}
-  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
-    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
-    stellar mass enclosed inside of $\rs$.
-In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]), and the Bernoulli parameter of the flow at large radii is positive (Appendix \ref{app:be}).
-In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetacrit}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$, greatly increasing the density of gas on smaller radial scales.
-
-\item Including the effects of heat transport by electron conduction results in at most order unity changes to the key properties of the flow (e.g.
-stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).
-Angular momentum is also unlikely to invalidate our spherically symmetric model, given the inferred stellar rotation rates near the stagnation radius ($\S\ref{sec:rotation}$).
-
-\item Radiative cooling has a more pronounced influence on the flow structure.
-Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.
-This condition is approximately equivalent to the $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
-
-  \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.
-Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
-However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the stellar break radius (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on the results of previous numerical studies (e.g.,\citealt{Ciotti+10}) is instead likely to result in time-dependent cycles of alternating high and low accretion phases ($\S\ref{sec:cycle}$).
-
-\item Stellar wind heating, supernovae, and AGN feedback depend explicitly on the SMBH mass as well as the SFH in the galactic nuclear region.
-A young starburst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old stellar populations  mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.
-Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).
-Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$.
-This heating can be suppressed if the star formation is sufficiently intermittent (Fig.~\ref{fig:NickPlot2}).
+  \item A stagnation radius, $\rs$, divides the nuclear gas between an
+    accretion flow and an outward wind. In steady-state the gas inflow
+    rate towards the black hole is proportional to the stellar mass
+    enclosed inside of $\rs$.  In the limit of strong heating, the
+    stagnation radius resides interior to the SMBH influence radius
+    and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]), and
+    the Bernoulli parameter of the flow at large radii is positive
+    (Appendix \ref{app:be}).  In the limit of weak heating ($\zeta <
+    \zeta_c$; eq.~[\ref{eq:zetacrit}]), the stagnation radius moves to
+    large radii, near or exceeding the stellar break radius $r_b \gg
+    r_{\rm inf}$, greatly increasing the density of gas on smaller
+    radial scales.
+
+  \item Including the effects of heat transport by electron conduction
+    results in at most order unity changes to the key properties of
+    the flow (e.g. stagnation radius, mass accretion rate, and thermal
+    stability) for causal values of the conduction saturation
+    parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).  Angular
+    momentum is also unlikely to invalidate our spherically symmetric
+    model, given the inferred stellar rotation rates near the
+    stagnation radius ($\S\ref{sec:rotation}$).
+
+\item Radiative cooling has a more pronounced influence on the flow
+  structure.  Cooling instabilities are likely to develop when the
+  radiative cooling rate exceeds the gas heating rate near the
+  stagnation radius.  This condition is approximately equivalent to
+  the $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by
+  \citet{McCourt+12} and \citet{Li&Bryan14a}.
+
+\item The location of the stagnation radius, and hence the SMBH
+  accretion rate, is a sensitive function of the gas heating rate
+  $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$, implying
+  that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+  However, $\Mdot$ can increase even more rapidly with decreasing
+  $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the
+  stellar velocity dispersion ($\zeta < \zeta_c$;
+  eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar
+  bulge and cannot produce a flow with a positive kinetic energy
+  interior to the stellar break radius (Appendix \ref{app:be}); (2)
+  For low $v_w$, gas near the stagnation radius becomes thermally
+  unstable, which based on the results of previous numerical studies
+  (e.g.,\citealt{Ciotti+10}) is instead likely to result in
+  time-dependent cycles of alternating high and low accretion phases
+  ($\S\ref{sec:cycle}$).
+
+  \item Stellar wind heating, supernovae, and AGN feedback depend
+    explicitly on the SMBH mass as well as the SFH in the galactic
+    nuclear region.  A young starburst of age $\lesssim 10$ Myr
+    produces mass and energy injection dominated by young stellar
+    winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old
+    stellar populations mass input is dominated by AGB winds and
+    heating is dominated by AGN feedback and supernovae.  Ongoing,
+    continuous star formation presents a hybrid situation, with energy
+    input usually dominated by young stars and mass input dominated by
+    the old stars (Appendix \ref{app:windheat}).  Galactic nuclei with
+    $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs
+    (as derived from cosmological simulations) receive a stellar wind
+    heating of $v_w \sim 700$ km s$^{-1}$.  This heating can be
+    suppressed if the star formation is sufficiently intermittent
+    (Fig.~\ref{fig:NickPlot2}).
 
@@
 \item Unlike stellar heating, heating from SMBH feedback depends on
-  the accretion rate, which itself depends on the heating.  Compton heating is generally unimportant compared to stellar
-  wind heating for the average SFH, but it can dominate in the case of
-  an impulsive star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in
-  principle Compton heating is sufficiently high to prevent thermal
+  the accretion rate, which itself depends on the heating.  Compton
+  heating is generally unimportant compared to stellar wind heating
+  for the average SFH, but it can be significant in the case of an impulsive
+  star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in principle
+  Compton heating is sufficiently high to prevent thermal
   instabilities when acting alone, i.e. $\dot{M}_{C} \lesssim
   \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not
-  however be capable of truly stabilizing the flow given its inability
+  be capable of truly stabilizing the flow given its inability
   to respond instantaneously to local changes in the properties of the
@@
 
-%  \item Our calculation of $\Mdot$ agrees well with the one calculated from the Bondi formula. We find that they agree to
+  % \item Our calculation of $\Mdot$ agrees well with the one
+  %   calculated from the Bondi formula. We find that they agree to
   %   within a factor of order unity. This is because in our model the
   %   accretion rate is determined by the flow properties at the
-   % stagnation radius, $\rs$, which is within a factor of a few of the
-    %Bondi radius $\rb$. Thus, use of the Bondi formula is a
-    %good approximation.
+  %   stagnation radius, $\rs$, which is within a factor of a few of
+  %   the
+  %   Bondi radius $\rb$. Thus, use of the Bondi formula is a
+  %   good approximation.
 

### 2015-04-22 ms.tex
Rewording things.

@@
 
-Between outbursts \citealt{Ciotti+10} find that galactic nuclei exist
-in a quasi-stationary thermal stable state. We focus on this region of
-parameter space calculating time-independent models, in which the
+In the this paper we focus on time-independent models, in which the
 nuclear gas receives sufficient heating to render radiative cooling
@@
 steady-state may exist between these inflow events on smaller radial
-scales comparable to the sphere of influence.  We are thus motivated
-to explore whether such steady flows are generally expected within the
-nucleus, or whether in most galaxies the nuclear gas content is always
-building towards instability.
+scales comparable to the sphere of influence.  We note that
+\citealt{Ciotti+10} find that between outbursts gas may exist in a
+quasi-steady state {\bf AG reworded}.
 
@@
 radius exists, a question intimately tied to that of cooling
-instability. {\bf AG this section still needs work...}
+instability.
 
@@
 i.e., a broken power law that transitions from an inner power law
-slope, $\Gamma$, to an outer power law slope, $\beta$, at a
-break radius, $\rb$.  If the stellar population is spherically
-symmetric, then this corresponds to a 3D stellar density $\rhostar \propto
+slope, $\Gamma$, to an outer power law slope, $\beta$, at a break
+radius, $\rb$.  If the stellar population is spherically symmetric,
+then this corresponds to a 3D stellar density $\rhostar \propto
 r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
-$r \gg \rb$.  We can write the deprojected stellar density approximately (formally, this is the $\alpha \rightarrow \infty$ limit) as
+$r \gg \rb$.  We can write the deprojected stellar density
+approximately (formally, this is the $\alpha \rightarrow \infty$
+limit) as
 \begin{align}
@@
 \end{align}
-where $\rho_\star|_{\rinf}$ is the stellar density at the radius of the black hole sphere of influence\footnote{This approximate expression agrees surprisingly well with the mean empirical scaling relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of \citet{Stone&Metzger15}, although we note that this relation has significant scatter.},
+where $\rho_\star|_{\rinf}$ is the stellar density at the radius of
+the black hole sphere of influence\footnote{This approximate
+  expression agrees surprisingly well with the mean empirical scaling
+  relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of
+  \citet{Stone&Metzger15}, although we note that this relation has
+  significant scatter.},
 \begin{equation}
@@
 \end{align}
-Though of questionable validity for low mass black holes (e.g., \citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack of an obviously better alternative.
+Though of questionable validity for low mass black holes (e.g.,
+\citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack
+of an obviously better alternative.
 
@@
 
-We fix $\beta = 2$ because our results are not overly sensitive to the properties of the gas flow on radial scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
-however, necessary to obtain a converged steady state for some regions
-of our parameter space.  We consider solutions calculated for up to
-four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by
-the range of break radii from the \citet{LauerFaber+:2007a}
-sample.\footnote{For the core galaxies the break radius follows the
-  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
-  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
-  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  In
-practice we calculate solutions for a range of $\rb$ only in cases
-when its precise value is expected to have a significant affect on the
-solution, in particular for high SMBH masses and low heating rates,
-for which the stagnation radius approaches large radii. We also
-neglect value of $r_b$ which would give unphysically large bulges for
-a given $\Mbh$.
+We fix $\beta = 2$ because our results are not overly sensitive to the
+properties of the gas flow on radial scales $\gtrsim r_b$ {\bf AG:
+  beta=1 could be problematic for low heating rates}. The presence of
+the break radius $r_{b}$ is, however, necessary to obtain a converged
+steady state for some regions of our parameter space.  We consider
+solutions calculated for up to four values of $\rb$: 50 pc, 100 pc,
+200 pc, and 400 pc, motivated by the range of break radii from the
+\citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the
+  break radius follows the scaling relationship $\rb\sim 106 \,
+  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
+  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
+  clear trend with $\Mbh$.}  In practice we calculate solutions for a
+range of $\rb$ only in cases when its precise value is expected to
+have a significant affect on the solution, in particular for high SMBH
+masses and low heating rates, for which the stagnation radius
+approaches large radii. We also neglect values of $r_b$ which would
+give unphysically large bulges for a given $\Mbh$.
+
+For low mass galaxies, nuclear star clusters $\Mbh\lsim 2\times 10^8
+\Msun$ may be present \citep{GrahamSpitler:2009a}.  Mass injection to
+the nucleus could (for $\Mbh\lsim 2 \times 10^{8} \Msun$) therefore be
+dominated by a nuclear star cluster with its own break radius on
+parsec scales, i.e. much smaller than our fiducial value of $r_b \sim
+100$ pc. However, for high heating rates the stagnation radius is not
+sensitive to the location of the break radius, and out models could
+also describe the accretion rate in the case of a nuclear star cluster.
 
@@
 one-dimensional, time-dependent hydrodynamics,
+
 \begin{align}
@@
   &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
-      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
-, 
+      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] ,
 \label{eq:dsdt}
 \end{align}
-where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
-enclosed mass (we neglect dark matter contributions).  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
+
+where $p$ and $s$ are the pressure and specific entropy, respectively,
+and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the enclosed mass (we
+neglect dark matter contributions).  We adopt an ideal gas equation of
+state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$ and $\gamma = 5/3$.
 
@@
 equation~\eqref{eq:eddr_analytic} represents the mass inflow rate on
-large scales and does not include small scale outflows. In reality, only
-a fraction $\alpha$ (the standard Shakura-Sunyaev parameter--assumed
-to be 0.1) will make it down to the black hole \citep{Li+2013}.
+large scales and does not include small scale
+outflows. \citep{Li+2013} suggest only a fraction $\alpha$ (the
+standard Shakura-Sunyaev parameter--assumed to be 0.1) will make it
+down to the black hole.
 
@@
 \end{align}
-
-%Note that by combining equations~\eqref{eq:mdot_analytic}
-%and~\eqref{eq:mdot_gas}, one can also write
-%\begin{align}
-%\rho|_{r_{\rm s}}=\frac{3 q|_{r_{\rm s}} \tff|_{r_{\rm s}}}{2-\Gamma}.
-%\label{eq:rhors2}
-%\end{align}
 
@@
 where the stagnation radius is assume to reside well inside the Nuker
-break radius.  Equation (\ref{eq:conduction}) shows that, even when conduction is saturated, our neglect of heat conduction
-results in at most an order unity correction for causal values of
-the saturation parameter $\phi < 0.1$.  Our numerical experiments which include conductive heating confirm this
-($\S\ref{sec:numerical}$).
+break radius.  Equation (\ref{eq:conduction}) shows that, even when
+conduction is saturated, our neglect of heat conduction results in at
+most an order unity correction for causal values of the saturation
+parameter $\phi < 0.1$.  Our numerical experiments which include
+conductive heating confirm this ($\S\ref{sec:numerical}$).
 
@@
 $\dot{q}_{\rm rad} = n^{2}\Lambda \propto T^{-2.7}$
-(eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable
-(e.g., \citealt{McCourt+12}, \citealt{Li&Bryan14a}), potentially resulting
-in the formation of a multi-phase medium and enhanced star formation (\citealt{Li&Bryan14b}).
-Even if the hot plasma of the CNM does not condense into cold clouds,
-the loss of pressure can temporarily increase the black hole accretion
-rate.  When coupled to feed-back processes which result from such enhanced accretion, this can lead to
-time-dependent limit cycle behavior
-(e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10};
-\citealt{Yuan&Li11}, \citealt{Gan+14}), which is also inconsistent
-with our assumption of a steady, single-phase flow.
-
-Cooling instability can, however, be prevented if destabilizing radiative cooling ($\dot{q}_{\rm rad} \propto T^{-2.7}$) is overwhelmed by
-other sources of cooling, namely the {\it stabilizing} term $\propto -q c_{s}^{2}
-\propto -T$ in the entropy equation (eq.~[\ref{eq:dsdt}]).
-Neglecting radiative cooling to first order, this term is balanced at the stagnation
-radius by the external heating term, $\dot{q}_{\rm heat} = q
-\tilde{v}_{w}^{2}/2$.  We assess thermal stability near the stagnation radius by comparing the ratio of external heating to
-radiative cooling $|\dot{q}_{\rm rad}|$ (eq.~[\ref{eq:qdot_rad}]),
+(eq.~[\ref{eq:qdot_rad}]; see below) is thermally unstable (e.g.,
+\citealt{McCourt+12}, \citealt{Li&Bryan14a}), potentially resulting in
+the formation of a multi-phase medium and enhanced star formation
+(\citealt{Li&Bryan14b}).  Even if the hot plasma of the CNM does not
+condense into cold clouds, the loss of pressure can temporarily
+increase the black hole accretion rate.  When coupled to feed-back
+processes which result from such enhanced accretion, this can lead to
+time-dependent limit cycle behavior (e.g.~\citealt{Ciotti&Ostriker07};
+\citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}), which is
+also inconsistent with our assumption of a steady, single-phase flow.
+
+Cooling instability can, however, be prevented if destabilizing
+radiative cooling ($\dot{q}_{\rm rad} \propto T^{-2.7}$) is
+overwhelmed by other sources of cooling, namely the {\it stabilizing}
+term $\propto -q c_{s}^{2} \propto -T$ in the entropy equation
+(eq.~[\ref{eq:dsdt}]).  Neglecting radiative cooling to first order,
+this term is balanced at the stagnation radius by the external heating
+term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.  We assess thermal
+stability near the stagnation radius by comparing the ratio of
+external heating to radiative cooling $|\dot{q}_{\rm rad}|$
+(eq.~[\ref{eq:qdot_rad}]),
 \begin{align}
@@
 barrier, which means that much of the gas flowing in from larger
-scales will be driven out in a conical outflow. The actual accretion
-rate will be $\sim\alpha$ times the accretion rate on large scales
-\citep{Li+2013}.
+scales will be driven out in a conical outflow. \citep{Li+2013}
+suggest that the actual accretion rate will be $\sim\alpha$ times the
+accretion rate on large scales.
 
@@
 accretion rates $10^{-4} \lsim \eddr \lsim 10^{-2}$, the radiative
-efficiency is $\sim 2.6\%$ {\bf AG described in more
-  detail?}. Additionally, a large fraction of the $\dot{M}$ on large scales
-will be driven out in outflows as the gas has some non-zero angular
-momentum and a centrifugal barrier will stop it from accreting
-\citet{Li+2013}. In the limit weak cooling appropriate for low
-accretion rates the accretion rate on small scales will be of order
-$\alpha \Mdot$. Here we adopt $\alpha=0.1$ so that our overall
-efficiency is 0.26\%
+efficiency is $\epsilon_{\rm rad}\sim 2.6\%$\footnote{for $\eddr\lsim
+  10^{-4} \epsilon_{\rm rad}\sim \eddr^{0.9}$. For $\eddr\gg 0.01$
+  $\epsilon_{\rm rad}\sim 0.1$...}. Additionally, a large
+fraction of the $\dot{M}$ on large scales will be driven out in
+outflows as the gas has some non-zero angular momentum and a
+centrifugal barrier will stop it from accreting \citet{Li+2013}. In
+the limit weak cooling appropriate for low accretion rates the
+accretion rate on small scales will be of order $\alpha \Mdot$. Here
+we adopt $\alpha=0.1$ so that our overall efficiency is 0.26\%
 
@@
   $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
-  panel assumes $\epsilon_X= (\epsilon_{\rm
-    bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g.,
-  \citealt{Narayan&Yi95}).  Shown for comparison are the X-ray
+  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
+  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm
+    rad}\simeq 0.026$ for $\lsim 10^{-4} \eddr\lsim 10^{-2} $, as
+  motivated by shearing box simulations of collisionless plasma (see
+  \citet{Sharma+2007}).  Shown for comparison are the X-ray
   luminosities calculated for the maximum thermally-stable accretion

### 2015-04-22 ms.tex
adjusting table entries
adjusting table
trimming axis range on mdot_mass plot.

@@
 Though of questionable validity for low mass black holes (e.g.,
-\citealt{Greene&Ho07}), we adopt equation (\ref{eq:Msigma}) for lack
+\citealt{Kormendy+2013}), we adopt equation (\ref{eq:Msigma}) for lack
 of an obviously better alternative.
@@
 Source terms $\propto q$ also appear in the momentum and entropy
-equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because the isotropic injection of mass represents, in the SMBH rest frame, a source of momentum
-and energy relative to the mean flow.  Physically, these result from
-the mismatch between the properties of virialized gas injected by stellar winds and the mean background flow.  The
-term $\propto p/\rho = c_{s}^{2}$ is important because it acts to stabilize the flow against runaway cooling ($\S\ref{sec:instability}$).
+equations (eqs.~[\ref{eq:dvdt}] and [\ref{eq:dsdt}]) because the
+isotropic injection of mass represents, in the SMBH rest frame, a
+source of momentum and energy relative to the mean flow.  Physically,
+these result from the mismatch between the properties of virialized
+gas injected by stellar winds and the mean background flow.  The term
+$\propto p/\rho = c_{s}^{2}$ is important because it acts to stabilize
+the flow against runaway cooling ($\S\ref{sec:instability}$).
 
@@
    10$^{7}$ & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
-% ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
+% ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 & 0.2, 0.6 \\
 % ... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
@@
 ... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 & 0.6\\
-% ... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
-% ... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $\mathbf{ 5.3 \times
-%   10^{ -2 }}$ \\
- ... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
-... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+ ... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & 0.48 & 0.2, 0.6 \\
+ ... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $5.3 \times  10^{
+   -2 }$ & 0.2, 0.6  \\
+% ... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
+%... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
 ... & 450 & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 19 \\
@@
 radius will vary strongly with the break radius. This explains the
-behavior of the two vertically aligned green circles with a green
-circle on top. These are two cusp ($\Gamma=0.8$) galaxies with
-$\Mbh=10^8 \Msun$ and $v_w=300$ km/s but with different break radii
-($\rb=$ 25, 50, and 100 pc from top to bottom). This divergence of the
-stagnation radius to large radii occurs at a higher value of $\zeta$
-in core galaxies ($\Gamma = 0.1$), explaining the behavior of the two
-core galaxies shown in Fig.~\ref{fig:stag} as vertically aligned
-orange triangles.  These solutions correspond to the same black hole
-mass ($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$)
-but assume different break radii of $r_{b} =$ 25, 50 pc (from top to
-bottom).
+behavior of the three vertically aligned green squares. These are three
+cusp ($\Gamma=0.8$) galaxies with $\Mbh=10^8 \Msun$ and $v_w=300$ km/s
+but with different break radii ($\rb=$ 25, 50, and 100 pc from top to
+bottom). This divergence of the stagnation radius to large radii
+occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.1$),
+explaining the behavior of the two core galaxies shown in
+Fig.~\ref{fig:stag} as vertically aligned orange triangles.  These
+solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
+and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
+radii of $r_{b} =$ 25, 50 pc (from top to bottom).
 

### 2015-04-22 ms.tex
changing the description of the efficiency.

@@
 \citet{Sharma+2007} calculate the radiative efficiency, $\epsilon$,
-based on MHD shearing box simulations of collisionless plasmas. For
-accretion rates $10^{-4} \lsim \eddr \lsim 10^{-2}$, the radiative
-efficiency is $\epsilon_{\rm rad}\sim 2.6\%$\footnote{for $\eddr\lsim
-  10^{-4} \epsilon_{\rm rad}\sim \eddr^{0.9}$. For $\eddr\gg 0.01$
-  $\epsilon_{\rm rad}\sim 0.1$...}. Additionally, a large
-fraction of the $\dot{M}$ on large scales will be driven out in
-outflows as the gas has some non-zero angular momentum and a
-centrifugal barrier will stop it from accreting \citet{Li+2013}. In
-the limit weak cooling appropriate for low accretion rates the
-accretion rate on small scales will be of order $\alpha \Mdot$. Here
-we adopt $\alpha=0.1$ so that our overall efficiency is 0.26\%
+based on MHD shearing box simulations of collisionless plasmas. The
+following piecewise power law approximately reproduces
+their results for the radiative efficiency, $\epsilon_{\rm rad}$
+
+\begin{align}
+\epsilon_{\rm rad} \simeq 
+\begin{cases}
+  2.6 \times 10^{-2} \left(\eddr\right)^{0.9} & \eddr \lsim 10^{-4} \\
+  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
+  0.1 \left(\eddr\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
+  0.1 & \eddr \gsim 0.1
+\end{cases}
+\label{eq:efficiency}
+\end{align}
+
+The first two lines are a piecewise power law fit designed to
+approximately reproduce the solid line in Figure 6
+in \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
+heats the electrons. For $\eddr\gsim 0.1$, $\epsilon_{rad}$ should saturate
+to 0.1, hence the fourth line. The third line is a power law which
+connects $\epsilon_{\rm rad} (\eddr=0.01) = 0.026$ to $\epsilon_{\rm
+  rad} (\eddr=0.1) = 0.1$.
+
+Additionally, a large fraction of the $\dot{M}$ on large scales will
+be driven out in outflows as the gas has some non-zero angular
+momentum and a centrifugal barrier will stop it from accreting
+\citet{Li+2013}. In the limit weak cooling appropriate for low
+accretion rates the accretion rate on small scales will be of order
+$\alpha \Mdot$.  Taking $epsilon=\alpha \epsilon_{\rm rad}$ for the
+overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
+equation~\eqref{eq:efficiency} we obtain {\bf AG note the change in
+  the description of the efficiency},
 
@@
   panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
-  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm
-    rad}\simeq 0.026$ for $\lsim 10^{-4} \eddr\lsim 10^{-2} $, as
-  motivated by shearing box simulations of collisionless plasma (see
-  \citet{Sharma+2007}).  Shown for comparison are the X-ray
-  luminosities calculated for the maximum thermally-stable accretion
-  rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
-  Ia-regulated accretion rate ({\it dashed teal line};
+  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm rad}$ is
+  given by equation~\eqref{eq:efficiency}.  Shown for comparison are
+  the X-ray luminosities calculated for the maximum thermally-stable
+  accretion rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]);
+  the SN Ia-regulated accretion rate ({\it dashed teal line};
   eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion

### 2015-04-23 ms.tex
greene
beta and efficiency.

@@
 Though of questionable validity for low mass black holes (e.g.,
-\citealt{Kormendy+2013}), we adopt equation (\ref{eq:Msigma}) for lack
-of an obviously better alternative.
+\citealt{Greene+2010, Kormendy+2013}), we adopt equation
+(\ref{eq:Msigma}) for lack of an obviously better alternative.
 
@@
 
-We fix $\beta = 2$ because our results are not overly sensitive to the
-properties of the gas flow on radial scales $\gtrsim r_b$ {\bf AG:
-  beta=1 could be problematic for low heating rates}. The presence of
-the break radius $r_{b}$ is, however, necessary to obtain a converged
-steady state for some regions of our parameter space.  We consider
-solutions calculated for up to four values of $\rb$: 50 pc, 100 pc,
-200 pc, and 400 pc, motivated by the range of break radii from the
-\citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the
-  break radius follows the scaling relationship $\rb\sim 106 \,
+We fix $\beta = 2$ but have our results are not overly sensitive to
+the properties of the gas flow on radial scales $\gtrsim r_b$ for
+$\beta\gsim 1.5$ (this is near the peak of the distribution of $\beta$
+in \citet{LauerFaber+:2007a}) {\bf AG: a little more detail}. The
+presence of the break radius $r_{b}$ is, however, necessary to obtain
+a converged steady state for some regions of our parameter space.  We
+consider solutions calculated for up to four values of $\rb$: 50 pc,
+100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
+the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
+  the break radius follows the scaling relationship $\rb\sim 106 \,
   (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
@@
  weak magnetic field that is oriented perpendicular to the flow could
- suppress the conductivity by reducing the electron mean free
- path.  However, for radially-decreasing temperature profiles of
- interest, the flow is susceptible to the magneto-thermal instability
- (\citealt{Balbus01}), the non-linear evolution of which results in a radially-directed field geometry
- (\citealt{Parrish&Stone07}).  In $\S\ref{sec:conductivity}$ we show that neglecting conductivity results in at
- most order-unity errors in the key properties of the solutions.
-
-Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}), of the form
+ suppress the conductivity by reducing the electron mean free path.
+ However, for radially-decreasing temperature profiles of interest,
+ the flow is susceptible to the magneto-thermal instability
+ (\citealt{Balbus01}), the non-linear evolution of which results in a
+ radially-directed field geometry (\citealt{Parrish&Stone07}).  In
+ $\S\ref{sec:conductivity}$ we show that neglecting conductivity
+ results in at most order-unity errors in the key properties of the
+ solutions.
+
+ Radiative cooling contributes an additional term to equation
+ (\ref{eq:dsdt}), of the form
 \begin{equation}
@@
 \end{equation}
-where $n \equiv \rho/\mu m_p$ and $\Lambda(T)$ is
-the cooling function.  We neglect radiative cooling in our baseline
-calculations, despite the fact that this is not justified when the
-wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.
-Once radiative cooling becomes important compared to other
-sources of heating and cooling, its presence leads to thermal
-instability (e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be accounted for
-by our 1D time-independent model.  Our goal is to use solutions which neglect radiation to determine over what range of conditions cooling instabilities will develop
+where $n \equiv \rho/\mu m_p$ and $\Lambda(T)$ is the cooling
+function.  We neglect radiative cooling in our baseline calculations,
+despite the fact that this is not justified when the wind heating
+$\vwO$ is low or if the mass return rate $\eta$ is high.  Once
+radiative cooling becomes important compared to other sources of
+heating and cooling, its presence leads to thermal instability
+(e.g.~\citealt{McCourt+12}, \citealt{Li&Bryan14a}) that cannot be
+accounted for by our 1D time-independent model.  Our goal is to use
+solutions which neglect radiation to determine over what range of
+conditions cooling instabilities will develop
 ($\S\ref{sec:instability}$).
@@
 \begin{cases}
-  2.6 \times 10^{-2} \left(\eddr\right)^{0.9} & \eddr \lsim 10^{-4} \\
+  2.6 \times 10^{-2} \left(\frac{\eddr}{10^{-4}}\right)^{0.9} & \eddr \lsim 10^{-4} \\
   2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
-  0.1 \left(\eddr\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
+  0.1 \left(\frac{\eddr}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
   0.1 & \eddr \gsim 0.1

### 2015-04-23 ms.tex
gone mad.

@@
   black holes in the local universe, which must instead result from
-  gas being fed in from large radii, due either to galaxy mergers or
+  gas being fed in from large radii, due either to gas inflows or
   thermal instabilities acting on larger, galactic scales.  Our
@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Black hole accretion
-  rate (excluding small-scale outflows) $\dot{M}$ in Eddington units
-  as a function of black hole mass $M_{\bullet}$, shown separately for
-  core ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$,
-  solid).  Black lines show the accretion rate calculated from
-  equation (\ref{eq:eddr_analytic}) using our estimate of the gas
-  heating rate provided at $z = 0$ by the average star formation
-  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal
-  lines show the maximum accretion set by Ia supernovae blow-out
-  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if
-  Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
-  lines show the maximum accretion rate for a thermally stable flow
-  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
-  Eddington ratios inferred for SgrA* from \citet{Quataert:2004a}
-  (gray circles), for NGC3115 from \citet{ShcherbakovWong+:2014a}
-  (gray diamonds), and for the Swift J1644+57 TDE from
-  \citet{BergerZauderer+:2012a} (gray triangles). Note that the actual
-  black hole accretion rate will be a factor of the Shakura-Sunyaev
-  $\alpha$ smaller than the $\Mdot$s here due to small scale
-  outflows. Thus the plot is really showing the gas inflow rate on
-  large scales (e.g. near the stagnation radius) {\it Bottom panel:} Growth
-  times $\Mbh/\Mdot$ in units of the Hubble time $\th$ for each of the
-  accretion rates shown in the top panel.}
+\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate
+  (excluding small-scale outflows) $\dot{M}$ in Eddington units as a
+  function of black hole mass $M_{\bullet}$, shown separately for core
+  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$, solid).
+  Black lines show the accretion rate calculated from equation
+  (\ref{eq:eddr_analytic}) using our estimate of the gas heating rate
+  provided at $z = 0$ by the average star formation histories for each
+  galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the maximum
+  accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red
+  lines show the accretion rate obtained if Compton heating alone was
+  acting (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum
+  accretion rate for a thermally stable flow near the stagnation
+  radius (eq.~[\ref{eq:Mdotmax}]).  We also show Eddington ratios
+  inferred for SgrA* from \citet{Quataert:2004a} (gray circles), for
+  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for
+  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (gray
+  triangles). Note that the actual black hole accretion rate could one
+  to several orders of magnitude smaller due to the presence of small
+  scale outflows. Thus the plot is really showing
+  the gas inflow rate on large scales (e.g. near the stagnation
+  radius) {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units of
+  the Hubble time $\th$ for each of the accretion rates shown in the
+  top panel.}
 \end{figure}
@@
 the \citet{Miller+15} trend.  A potentially bimodal population of
-steady and cyclic galactic nuclei calls into question the physical
+steady and outbursting galactic nuclei calls into question the physical
 justification of using simple extrapolations of power-law fits to the
@@
 unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
-the mean $r_b-M_{\bullet}$ relationship
-\citep{LauerFaber+:2007a}. {\bf Other constraints on gas density:
-  J1644 gone mad}
+the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}. We
+also note that other constraints (the observed jet power, the jet
+shut-off (if linked with the accretion becoming sub-Eddington), and an
+observed QPO in the x-ray light curve) favor a smaller black hole
+($10^5-10^6 \Msun$) \citep{Tchekhovskoy+2014}.
 
@@
     momentum is also unlikely to invalidate our spherically symmetric
-    model, given the inferred stellar rotation rates near the
-    stagnation radius ($\S\ref{sec:rotation}$).
+    model on large scales, given the inferred stellar rotation rates
+    near the stagnation radius ($\S\ref{sec:rotation}$). However, on
+    small scales gas would encounter a centrifugal barrier which would
+    cause much of the gas flowing inwards on large scales to be driven
+    outwards in an outflow (as in \citealt{Li+2013}).
 
@@
 
-  % \item Our calculation of $\Mdot$ agrees well with the one
-  %   calculated from the Bondi formula. We find that they agree to
-  %   within a factor of order unity. This is because in our model the
-  %   accretion rate is determined by the flow properties at the
-  %   stagnation radius, $\rs$, which is within a factor of a few of
-  %   the
-  %   Bondi radius $\rb$. Thus, use of the Bondi formula is a
-  %   good approximation.
-
 \end{enumerate}

### 2015-04-23 ms.tex
efficiency tangle.

@@
 \newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
+\newcommand{\eddrt}{\tilde{\dot{M}}/\dot{M}_{\rm Edd}}
 \newcommand{\MdotEdd}{\dot{M}_{\rm Edd}}
@@
 \begin{cases}
-  2.6 \times 10^{-2} \left(\frac{\eddr}{10^{-4}}\right)^{0.9} & \eddr \lsim 10^{-4} \\
-  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
-  0.1 \left(\frac{\eddr}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
-  0.1 & \eddr \gsim 0.1
+  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
+  2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
+  0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
+  0.1 & \eddrt \gsim 0.1
 \end{cases}
@@
 The first two lines are a piecewise power law fit designed to
-approximately reproduce the solid line in Figure 6
-in \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
-heats the electrons. For $\eddr\gsim 0.1$, $\epsilon_{rad}$ should saturate
-to 0.1, hence the fourth line. The third line is a power law which
-connects $\epsilon_{\rm rad} (\eddr=0.01) = 0.026$ to $\epsilon_{\rm
-  rad} (\eddr=0.1) = 0.1$.
+approximately reproduce the solid line in Figure 6 in
+\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
+heats the electrons. For $\eddrt\gsim 0.1$, $\epsilon_{\rm rad}$
+should saturate to 0.1, hence the fourth line. The third line is a
+power law which connects $\epsilon_{\rm rad} (\eddrt=0.01) = 0.026$ to
+$\epsilon_{\rm rad} (\eddrt=0.1) = 0.1$. The tildes are put in as a
+reminder that the efficiency will depend on the small scale $\Mdot$
+($\tilde{\dot{M}}$) which will in general be different from the large
+scale $\Mdot$.
 
@@
 accretion rates the accretion rate on small scales will be of order
-$\alpha \Mdot$.  Taking $epsilon=\alpha \epsilon_{\rm rad}$ for the
+$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
 overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
-equation~\eqref{eq:efficiency} we obtain {\bf AG note the change in
-  the description of the efficiency},
+equation~\eqref{eq:efficiency}. This means that the bolometric
+luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
+\eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
+$\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
+the mass inflow rate on small scales. Note that in evaluating the
+efficiency one has to account for the $\alpha$ suppression in $\eddr$.
+we obtain {\bf AG note the change in the description of the
+  efficiency. Also, the alpha's kept tripping me up},
 
@@
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 5.9\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
+\begin{cases} 6\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
 C,9}^{-0.44}M_{\bullet,8}^{0.09}
-&, \text{core}\\ 2.1\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
+&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
 C,9}^{-0.4} M_{\bullet,8}^{0.08}
@@
 
-Kinetic feedback results from outflows of energy or momentum from close to the black hole in the form of a disk wind or jet, which deposits its energy as heat, e.g.
-via shocks or wave dissipation, over much larger radial scales (e.g.~\citealt{McNamara&Nulsen07}; \citealt{Novak+11}; \citealt{Gaspari+12}).
-
-Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
-\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor.
-Further assume that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
-heat}^{3}$.  The resulting volumetric heating rate $e = \epsilon_{\rm
-j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a heating parameter given by
+Kinetic feedback results from outflows of energy or momentum from
+close to the black hole in the form of a disk wind or jet, which
+deposits its energy as heat, e.g. via shocks or wave dissipation, over
+much larger radial scales (e.g.~\citealt{McNamara&Nulsen07};
+\citealt{Novak+11}; \citealt{Gaspari+12}).
+
+Assume that the outflow power is proportional to the SMBH accretion
+rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}c^{2}$, where
+$\epsilon_{\rm j} < 1$ is a jet efficiency factor.  Further assume
+that this energy is deposited as heat uniformly interior to a radius
+$r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$.
+The resulting volumetric heating rate $e = \epsilon_{\rm
+  j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a
+heating parameter given by
 \begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
         h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
-\rho_{\star}|_{r_{s}}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
+      \rho_{\star}|_{r_{s}}}\right)^{1/2} \sim
+  \left(\frac{\epsilon_{\rm
         j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
-&\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
+  &\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm
+        j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
         heat}}\right)^{1-\Gamma/2},
@@
   panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
-  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm rad}$ is
-  given by equation~\eqref{eq:efficiency}.  Shown for comparison are
-  the X-ray luminosities calculated for the maximum thermally-stable
-  accretion rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]);
-  the SN Ia-regulated accretion rate ({\it dashed teal line};
-  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
-  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
-  calculated for the average SFH corresponding to each SMBH mass.}
+  (\alpha/0.1) \epsilon_{rad} ( (\alpha/0.1) 0.1 \eddr) $, where
+  $\epsilon_{\rm rad}$ is given by equation~\eqref{eq:efficiency} and
+  $\eddr$ corresponds to the gas inflow rate on large scales.  Shown
+  for comparison are the X-ray luminosities calculated for the maximum
+  thermally-stable accretion rate ({\it dashed orange line};
+  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
+    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
+  heating-regulated accretion rate ({\it dashed pink line};
+  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
+  corresponding to each SMBH mass.}
 \end{figure*}

### 2015-04-23 ms.tex
cooling flow

@@
 
-The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
+Note that in practice when $v_{w}<v_{\rm TI}$, a cooling flow may
+develop rather than a true local thermal instability: in the former
+case the stagnation radius $\rs$ may move to large radii, greatly
+increasing the density in the inner part of the flow, which increases
+cooling and creates a large inflow of cold gas towards the center of
+the galaxy.  In this paper we do not attempt to distinguish under what
+conditions a global cooling flow would develop vs. a local thermal
+instability.
+
+The minimum heating rate for thermal stability
+(eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable
+accretion rate,
 \begin{align}

### 2015-04-23 ms.tex
gone mad!

@@
 the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}. We
-also note that other constraints (the observed jet power, the jet
-shut-off (if linked with the accretion becoming sub-Eddington), and an
-observed QPO in the x-ray light curve) favor a smaller black hole
-($10^5-10^6 \Msun$) \citep{Tchekhovskoy+2014}.
+also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
+($10^5-10^6 \Msun$) based on the observed jet power, the jet
+shut-off time (if linked with the accretion becoming sub-Eddington), and an
+observed QPO in the x-ray light curve favor a smaller black hole {\bf
+  AG Gone mad!}.
 

### 2015-04-23 ms.tex
simplifying discussion.

--- 2015-04-23 ms.tex
@@
 \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
-heats the electrons. For $\eddrt\gsim 0.1$, $\epsilon_{\rm rad}$
-should saturate to 0.1, hence the fourth line. The third line is a
-power law which connects $\epsilon_{\rm rad} (\eddrt=0.01) = 0.026$ to
-$\epsilon_{\rm rad} (\eddrt=0.1) = 0.1$. The tildes are put in as a
-reminder that the efficiency will depend on the small scale $\Mdot$
-($\tilde{\dot{M}}$) which will in general be different from the large
-scale $\Mdot$.
+heats the electrons. We assume that $\epsilon_{\rm rad}$ saturates to
+0.1 at $\eddrt\simeq 0.1$. $\tilde{\dot{M}}$ correspond to the true
+accretion rate (as opposed to the inflow rate on large scales--which
+is generally what we mean by $\Mdot$).
 
@@
 overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
-equation~\eqref{eq:efficiency}. This means that the bolometric
-luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
-\eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
-$\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
-the mass inflow rate on small scales. Note that in evaluating the
-efficiency one has to account for the $\alpha$ suppression in $\eddr$.
-we obtain {\bf AG note the change in the description of the
+equation~\eqref{eq:efficiency}. Note that in evaluating the efficiency
+one has to use $\tilde{\dot{M}}\simeq \alpha \Mdot$. 
+% This means that the bolometric
+% luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
+% \eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
+% $\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
+% the mass inflow rate on small scales. Note that in evaluating the
+% efficiency one has to account for the $\alpha$ suppression in $\eddr$.
+% we obtain 
+{\bf AG note the change in the description of the
   efficiency. Also, the alpha's kept tripping me up},
@@
 unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
-the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}. We
-also note that other constraints (the observed jet power, the jet
-shut-off (if linked with the accretion becoming sub-Eddington), and an
-observed QPO in the x-ray light curve) favor a smaller black hole
-($10^5-10^6 \Msun$) \citep{Tchekhovskoy+2014}.
-
+the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
 Alternatively, the observed density break in J1644+57 could result
@@
 uncoincidental.
+
+ We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
+($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
+shut-off time (if linked with the accretion becoming sub-Eddington), and an
+observed QPO in the x-ray light curve favor a smaller black hole {\bf
+  AG Gone mad!}.
 

### 2015-04-24 ms.tex
note
fixing rounding errors
impulsive plot.

@@
 suggest that the actual accretion rate will be $\sim\alpha$ times the
-accretion rate on large scales.
+accretion rate on large scales {\bf Note that new ending paragraph}.
 
@@
 \begin{align} v_{w}^{\rm C} \simeq
-  \begin{cases} 27 \eta_{0.02}^{0.5}T_{\rm
+  \begin{cases} 24 \eta_{0.02}^{0.5}T_{\rm
 C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
@@
 r^{-0.75}$ for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp
-($\Gamma = 0.1$; $\densSlope \simeq 0.6$) galaxies, respectively.  Although our
-model's assumption that the heating parameter be radially constant is
-not satisfied, this variation is sufficiently weak that it should
-not significantly alter our conclusions.
+($\Gamma = 0.1$; $\densSlope \simeq 0.6$) galaxies, respectively.
+Although our model's assumption that the heating parameter be radially
+constant is not satisfied, this variation is sufficiently weak that it
+should not significantly alter our conclusions.
 
@@
   a single burst of star formation.  Top and bottom panels show cases
-  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$,
-  respectively.  Solid and dashed lines show the ranges of
+  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
+  (both cusps).  Solid and dashed lines show the ranges of
   $\tau_{\star}$ for which the accretion flow is thermally stable and

### 2015-04-24 ms.tex
changing efficiency description.

@@
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
-  0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
-  0.1 & \eddrt \gsim 0.1
-\end{cases}
+%   0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
+%   0.1 & \eddrt \gsim 0.1
+% \end{cases}
 \label{eq:efficiency}
@@
 \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
-heats the electrons. We assume that $\epsilon_{\rm rad}$ saturates to
-0.1 at $\eddrt\simeq 0.1$. $\tilde{\dot{M}}$ correspond to the true
-accretion rate (as opposed to the inflow rate on large scales--which
-is generally what we mean by $\Mdot$).
+heats the electrons. $\epsilon_{\rm rad}$ should saturate to 0.1 at
+larger values of $\eddrt>0.01$, but such a black hole would certainly
+be active and thermally unstable (and thus outside the scope of our
+models). We note they $\eddrt<0.01$ for all of our models.
 
@@
 subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$
-depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
-to simultaneously solve a series of implicit equations to determine
-each heating rate.  Heating from MSPs is found to be negligibly small
-for fiducial parameters and hence is not shown, while kinetic feedback
-is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).
+(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and
+$v_{\rm w}^{\rm Ia}$ depends on the total heating rate
+(eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series
+of implicit equations to determine each heating rate.  Heating from
+MSPs is found to be negligibly small for fiducial parameters and hence
+is not shown, while kinetic feedback is neglected given its uncertain
+efficiency ($\S\ref{sec:kinetic}$).
 

### 2015-04-24 ms.tex
captions

@@
 %   0.1 & \eddrt \gsim 0.1
-% \end{cases}
+\end{cases}
 \label{eq:efficiency}
@@
 \end{eqnarray} 
-where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) =
-M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).
-If the bulk of the energy from kinetic feedback is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
-10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.
-However, if this energy is instead deposited over much larger physical scales comparable to the size of the galaxy, i.e.
-$r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 0.1$.
+where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm
+    s}}/t_{\rm h}$ and, for radii inside the Nuker break radius,
+$M_{\star}(r) = M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$
+(eq.~[\ref{eq:rhostar}]).  If the bulk of the energy from kinetic
+feedback is released near the stagnation radius, then even a small
+heating efficiency $\epsilon_{\rm j} \gtrsim 10^{-5}$ is sufficient
+for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered
+heating.  However, if this energy is instead deposited over much
+larger physical scales comparable to the size of the galaxy,
+i.e. $r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then
+kinetic feedback is unimportant, even for a powerful jet with
+$\epsilon_{\rm j} \sim 0.1$.
 
@@
   for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
-  (both cusps).  Solid and dashed lines show the ranges of
+  (both cusps with $\Gamma=0.8$).  Solid and dashed lines show the ranges of
   $\tau_{\star}$ for which the accretion flow is thermally stable and
@@
 \caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
-  to the total heating rate of the CNM, $\vwO$ ({\it black}):
-  stellar wind heating ({\it orange}), Ia supernovae ({\it
-    green}), millisecond pulsars ({\it blue}), and compton heating
-  ({\it pink}).  Each heating source varies with black hole mass
-  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a};
-  see Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:}
-  The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
+  to the total heating rate of the CNM, $\vwO$ ({\it black}): stellar
+  wind heating ({\it orange}), Ia supernovae ({\it green}),
+  millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
+  Each heating source varies with black hole mass $\Mbh$ calculated
+  for average SFHs from \citet{MosterNaab+:2013a}; see
+  Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:} The
+  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
   v_{w}^{2}$) from the top panel to the radiative cooling rate
-  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter $\eta$
-  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
+  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter
+  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
   function of black hole mass $\Mbh$, calculated for average star SFHs
-  from \citealt{MosterNaab+:2013a} (blue) and the ratio of Ia radius to
-  stagnation radius as a function of $\Mbh$ (green).}
+  from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
+  stagnation radius as a function of $\Mbh$ (green), and the ratio of
+  the normalized heating rate
+  $\zeta=\sqrt{1+\frac{v_w^2}{\sigma_0^2}}$ to the critical heating
+  rate $\zeta_c$ for which no outflow is possible (see
+  eq.~\eqref{eq:zetacrit}). In evaluating the latter quantity we use
+  scaling relations for $r_b$, $\rinf$, and $\Gamma$ based on
+  \citet{LauerFaber+:2007a}. {\bf AG added the zeta/zetac line}.}
+
+ % $\Gamma=0.3
+ %  \Mbheight^{-0.24}$, $\rinf=14 \Mbheight^{0.6}$ pc
+ %  (eq~\eqref{\eqref{eq:rsoi}}), $\rb\simeq 106 \Mbheight^{0.39} $ pc
+ %  (for $\Gamma<0.3$), and $\rb\simeq 100$ pc (for $\Gamma\geq 0.3$)
+ %  {\bf Added zeta/zeta_c line but unfortunately caption became
+ %    somewhat verbose (I don't think all of this description is
+ %    necessary--maybe just say we use scaling relations based on Lauer
+ %    et al. sample?) Also being so close to zeta/zeta_c=1 implies
+ %    there is a limit to how much scatter we could explain just by
+ %    variations in the heating rate}.
+
 \end{figure}
@@
   (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
-  relationship $\Gamma(M_{\bullet})$ derived from the
+  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived from the
   \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
@@
 \ref{fig:NickPlot2}), this can lead to order of magnitude differences
-in $\dot{M}$; (3) differences in angular momentum of the infalling gas
-from galaxy to galaxy, resulting in differences in the fraction of the
-gas lost to outflows.  Also potentially contributing is the order of
-magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between
-$\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).
-Differences in $\dot{M}$ are augmented by the theoretical expectation
-that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
-flows.
+in $\dot{M}$ {\bf AG limitation from zetac}; (3) differences in
+angular momentum of the infalling gas from galaxy to galaxy, resulting
+in differences in the fraction of the gas lost to outflows.  Also
+potentially contributing is the order of magnitude difference, at
+fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp
+galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are
+augmented by the theoretical expectation that $L_{\rm X} \propto
+\dot{M}^{2} $ for radiatively inefficient flows.
 

### 2015-04-26 ms.tex
intro

@@
   latter being related to the star-formation history.  We assess the
-  conditions under which radiative instabilities develop, both in the
+  conditions under which radiative instabilities develop in the hydrostatic region near the stagnation radius, both in the
   case of a single burst of star formation and for the average star
@@
 turn determines the SMBH luminosity and the feedback of its energy and
-momentum output on larger scales.  The presence of dense gas in the
-nucleus may lead to runaway cooling, resulting in bursty episodes of
-star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07};
-\citealt{Ciotti+10}).
+momentum output on larger scales.  Dense gas in the nucleus may lead to runaway cooling, resulting in bursty episodes of
+star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}).
 
@@
 from shock interaction with the CNM of the previously quiescent SMBH
-(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Detailed
-modeling of J1644+57 showed that the CNM density was much lower than
+(\citealt{Giannios&Metzger11}; \citealt{Zauderer+11}).  Modeling of J1644+57 showed that the CNM density was much lower than
 that measured surrounding Sgr A$^{\star}$ on a similar radial scale
 (\citealt{Metzger+12}; \citealt{BergerZauderer+:2012a}).  However, a
-TDE jet injected into a denser CNM would be decelerated more rapidly,
-producing potentially very different radio emission than in J1644+57.
+TDE jet which encounters a denser CNM would be decelerated more rapidly,
+producing different radio emission than in J1644+57.
 Variations in the properties of the CNM could help explain why most
@@
 
-In the this paper we focus on time-independent models, in which the
+In this paper we focus on time-independent models, in which the
 nuclear gas receives sufficient heating to render radiative cooling
@@
 useful in determining under what conditions cooling instabilities
-manifest across the expected range of galaxy properties, or whether
+manifest in the nuclear region across the expected range of galaxy properties, or whether
 other (non-AGN) forms of feedback can produce a prolonged state of
 steady, thermally stable accretion.  Even if cooling instabilities
-develop on galactic scales over longer $\sim$ Gyr timescales, a quasi
-steady-state may exist between these inflow events on smaller radial
-scales comparable to the sphere of influence.  We note that
-\citealt{Ciotti+10} find that between outbursts gas may exist in a
-quasi-steady state {\bf AG reworded}.
+develop on galactic scales over longer $\sim$ Gyr timescales, we aim to explore whether a quasi
+steady-state may exist between these inflow events on smaller radial scales comparable to the sphere of influence.
+
+%For instance, \citealt{Ciotti+10} find that between outbursts gas may exist in a
+%quasi-steady state {\bf AG reworded}.
 
@@
 radius may move to much larger radii or not exist at all, in which
-case nearly the entire ISM of the galaxy is flowing towards the SMBH.
-Here we assess under what conditions a stagnation
-radius exists, a question intimately tied to that of cooling
-instability.
+case nearly the entire ISM of the galaxy is flowing towards the SMBH, i.e. a ``cooling flow".
+However, the hydrostatic nature of gas near the stagnation radius also renders the CNM at this location particularly susceptible to {\it local} thermal instabilities, the outcome of which could be distinct from the development of a cooling flow.
 

### 2015-04-26 ms.tex
fixed 2.1

@@
 
-We fix $\beta = 2$ but have our results are not overly sensitive to
-the properties of the gas flow on radial scales $\gtrsim r_b$ for
-$\beta\gsim 1.5$ (this is near the peak of the distribution of $\beta$
-in \citet{LauerFaber+:2007a}) {\bf AG: a little more detail}. The
+We fix $\beta = 2$ but find that our results are not overly sensitive to
+the properties of the gas flow on radial scales $\gtrsim r_b$ for values of
+$\beta\gsim 1.5$, which characterize most of the \citet{LauerFaber+:2007a} sample.  The
 presence of the break radius $r_{b}$ is, however, necessary to obtain
@@
 
-For low mass galaxies, nuclear star clusters $\Mbh\lsim 2\times 10^8
-\Msun$ may be present \citep{GrahamSpitler:2009a}.  Mass injection to
-the nucleus could (for $\Mbh\lsim 2 \times 10^{8} \Msun$) therefore be
-dominated by a nuclear star cluster with its own break radius on
-parsec scales, i.e. much smaller than our fiducial value of $r_b \sim
-100$ pc. However, for high heating rates the stagnation radius is not
-sensitive to the location of the break radius, and out models could
-also describe the accretion rate in the case of a nuclear star cluster.
+Finally, we note that some low mass galaxies with $\Mbh\lsim 2 \times 10^{8} \Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}), which are not accounted for by our simple parametrization of the stellar density.
+In such cases gas and energy injection could be dominated by the cluster itself, i.e.
+concentrated within its own pc-scale ``break radius" which is much smaller than the outer break in the older stellar population on much larger scales.
+If the extent of the cluster is known, however, our model can be fully generalized to this case.
+Furthermore, for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the location of the break radius.
 

### 2015-04-26 ms.tex
fixed Ia

@@
 steady-state may exist between these inflow events on smaller radial scales comparable to the sphere of influence.  
-
-%For instance, \citealt{Ciotti+10} find that between outbursts gas may exist in a
+%For instance, for massive galaxies \citealt{Ciotti+10} find that between outbursts gas may exist in a
 %quasi-steady state {\bf AG reworded}.
@@
 case nearly the entire ISM of the galaxy is flowing towards the SMBH, i.e. a ``cooling flow".
-However, the hydrostatic nature of gas near the stagnation radius also renders the CNM at this location particularly susceptible to {\it local} thermal instabilities, the outcome of which could be distinct from the development of a cooling flow.
+However, the hydrostatic nature of gas near the stagnation radius also renders the CNM at this location particularly susceptible to {\it local} thermal instabilities, the outcome of which could well be distinct from the development of a cooling flow.
 
@@
   the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
-  clear trend with $\Mbh$.}  In practice we calculate solutions for a
-range of $\rb$ only in cases when its precise value is expected to
-have a significant affect on the solution, in particular for high SMBH
-masses and low heating rates, for which the stagnation radius
-approaches large radii. We also neglect values of $r_b$ which would
+  clear trend with $\Mbh$.}  We neglect values of $r_b$ which would
 give unphysically large bulges for a given $\Mbh$.
-
-Finally, we note that some low mass galaxies with $\Mbh\lsim 2 \times 10^{8} \Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}), which are not accounted for by our simple parametrization of the stellar density.
+% In practice we calculate solutions for a
+%range of $\rb$ only in cases when its precise value is expected to
+%have a significant affect on the solution, in particular for high SMBH
+%masses and low heating rates, for which the stagnation radius
+%approaches large radii. 
+%We also neglect values of $r_b$ which would
+%give unphysically large bulges for a given $\Mbh$.
+
+Finally, we note that \citealt{LauerFaber+:2005a} find that $\sim 60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have (generally unresolved) emission in excess of the inward extrapolation of the Nuker law.
+Indeed, some low mass galaxies with $\Mbh\lsim 10^{8} \Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}), which are not accounted for by our simple parametrization of the stellar density.
 In such cases gas and energy injection could be dominated by the cluster itself, i.e.
 concentrated within its own pc-scale ``break radius" which is much smaller than the outer break in the older stellar population on much larger scales.
-If the extent of the cluster is known, however, our model can be fully generalized to this case.
-Furthermore, for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the location of the break radius.
+Although our analysis does not take into account the influence such an inner break, for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the location of the break radius.
 
@@
 neglect dark matter contributions).  We adopt an ideal gas equation of
-state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$ and $\gamma = 5/3$.
-
-The source term in equation (\ref{eq:drhodt}),
+state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$ and $\gamma = 5/3$.  The source term in equation (\ref{eq:drhodt}),
 \begin{align}
@@
 T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
-  \tilde{v}_{w}^{2}}{2k} \approx \frac{\gamma-1}{\gamma}\frac{\mu
+  \tilde{v}_{w}^{2}}{2k} \underset{v_w \gg \sigma_0}\approx \frac{\gamma-1}{\gamma}\frac{\mu
   m_p v_w^2}{2k} \frac{13+8\Gamma}{13+8\Gamma-6\nu} \nonumber\\ 
@@
 \end{align}
-where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
-s$^{-1}$), $v_w\gg\sigma_0$,  and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
-    s}}$ is the density power-law slope at $r = r_{\rm s}$.
-Empirically, we find that
+where $v_{500} \equiv v_{w}/(500$ km s$^{-1}$)  and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the density power-law slope at $r = r_{\rm s}$.
+Empirically, we find from our numerical solutions that
 \begin{align}
@@
 \begin{equation} 
-\zeta\equiv \sqrt{1 + \frac{v_w}{\sigma_0}^2} <
+\zeta\equiv \sqrt{1 + \left(\frac{v_w}{\sigma_0}\right)^2} <
 \zeta_c \approx \left(\frac{\rb}{\rinf}\right)^{0.5(1-\Gamma)}.
@@
 
-\subsection{SMBH Accretion Rate}
-
-The accretion rate onto the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
+\subsection{Accretion Rate}
+
+The accretion rate towards the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
 \begin{eqnarray}
@@
 cent.  Note the sensitive dependence of the accretion rate on the wind
-heating rate. Also, we emphasize that
-equation~\eqref{eq:eddr_analytic} represents the mass inflow rate on
-large scales and does not include small scale
-outflows. \citep{Li+2013} suggest only a fraction $\alpha$ (the
-standard Shakura-Sunyaev parameter--assumed to be 0.1) will make it
-down to the black hole.
+heating rate.
+We emphasize that equation~\eqref{eq:eddr_analytic} represents the radial mass inflow rate on relatively large scales and does not include outflows from the accretion disk on small scales (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), which could significantly reduce the fraction of $\dot{M}$ actually reaching the SMBH.
 
@@
 parameter $\phi < 0.1$.  Our numerical experiments which include
-conductive heating confirm this ($\S\ref{sec:numerical}$).
+conductive heating confirm this ($\S\ref{sec:numerical}$).  {\bf BDM: whats going on wrt johnson and quataert?}
 
@@
 the formation of a multi-phase medium and enhanced star formation
-(\citealt{Li&Bryan14b}).  Even if the hot plasma of the CNM does not
+(\citealt{Li&Bryan14b}).
+
+Even if the hot plasma of the CNM does not
 condense into cold clouds, the loss of pressure can temporarily
-increase the black hole accretion rate.  When coupled to feed-back
-processes which result from such enhanced accretion, this can lead to
+increase the black hole accretion rate by producing a large-scale cooling flow.  When coupled to feed-back processes which result from such enhanced accretion, this can lead to
 time-dependent limit cycle behavior (e.g.~\citealt{Ciotti&Ostriker07};
@@
   \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$, which assumes solar
-metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).  Note that in
-our runs with radiative cooling we take $\Lambda(T)$ to be a piecewise
-function with $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
-  \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ for $T\leq 2\times
-10^{7}$ K and $\Lambda = 2.3 \times 10^{-24} \left(T/10^6
-  \text{K}\right)^{0.5}$ for $T>2\times 10^{7}$ K.
+metallicity gas (\citealt{Draine:2011a}; his Fig. 34.1).
+
+%Note that in
+%our runs with radiative cooling we take $\Lambda(T)$ to be a piecewise
+%function with $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
+ % \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ for $T\leq 2\times
+%10^{7}$ K and $\Lambda = 2.3 \times 10^{-24} \left(T/10^6
+ % \text{K}\right)^{0.5}$ for $T>2\times 10^{7}$ K.
 
@@
 kT/2 \mu)/|\dot{q}_{\rm rad}|$ to the free-fall time $t_{\rm ff}$ at the
-stagnation radius, as can be derived using the equality
+stagnation radius.  This equivalence can be derived using the equality
 \begin{align}
@@
 out to the break radius $r_b$; the quasi-hydrostatic structure that
-develops in this case greatly increases the gas density, resulting in
+develops in this case greatly increases the gas density, resulting in local
 thermal instability.
@@
 
-For $r\simeq r_{\rm circ} $ the gas will encounter a centrifugal
-barrier, which means that much of the gas flowing in from larger
-scales will be driven out in a conical outflow. \citep{Li+2013}
-suggest that the actual accretion rate will be $\sim\alpha$ times the
-accretion rate on large scales {\bf Note that new ending paragraph}.
+%At $r\simeq r_{\rm circ} $ the gas will encounter a centrifugal
+%barrier, which means that much of the gas flowing in from larger
+%scales will be driven out in a conical outflow. \citep{Li+2013}
+%suggest that the actual accretion rate will be $\sim\alpha$ times the
+%accretion rate on large scales {\bf Note that new ending paragraph}.
 
@@
 radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
-Radiative cooling is calculated using the cooling function from
-\citealt{Draine:2011a}.  For high heating rates of $v_{w} = 600$ and
+Radiative cooling is calculated using the cooling function of \citet{Draine:2011a} for solar metallicity.  For high heating rates of $v_{w} = 600$ and
 $1200$ km s$^{-1}$ cooling is unimportant across all radii, while for
@@
 solutions for our fiducial value of the saturation parameter $\phi =
-0.1$.  Thermal conduction, by contrast, results in only order unity
-changes to our results for the stagnation radius (and hence the
-accretion rate) for our fiducial value of the saturation parameter
-$\phi =0.1$.
+0.1$.
 
@@
 \end{align}
-Equation (\ref{eq:rIars}) shows that SN Ia can only be approximated as
-a steady heating source near the stagnation radius for extremely
+SN Ia can only be approximated as a steady heating source near the stagnation radius for extremely
 massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or for a very
@@
 
-However, even if SN Ia are rare near the stagnation radius, SN Ia may
-cap the SMBH accretion rate by periodically blowing gas out of the
-nucleus of low mass galaxies.  Between successive SNe, stars release a
-gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
+Even if SN Ia are rare near the stagnation radius, they may cap the SMBH accretion rate by periodically blowing gas out of the nucleus of low mass galaxies.
+Between successive SNe, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
 interior to the Ia radius, which is locally gravitationally bound to
 the SMBH by an energy $E_{\rm bind} \sim M_{\rm
-  g}\sigma_0^{2}\mathcal{F}^{2}$, where typically $\mathcal{F}
-\lesssim$ few.  From the above definitions we find that \be
+  g}\sigma_0^{2}$.  From the above definitions we find that
+ \be
 \frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm
-    Ia})^{2}}{2\mathcal{F}^{2}\sigma_0^{2}}.
+    Ia})^{2}}{2\sigma_0^{2}}.
 \label{eq:blowout}
@@
 Hence, for low mass BHs with $\sigma_0 \ll v^{\rm Ia}_{w}$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still potentially limited to a value
+Thus even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still limited to a value
 \begin{eqnarray}
@@
 
-The deep gravitational potential wells of high mass galaxies $\sigma_0
-\gg  v^{\rm Ia}_{w}$ prevent SN Ia from dynamically clearing out gas
-in these systems.  Equation (\ref{eq:eddr_Ia}) nevertheless represents
-a cap on the accretion rate in practice because if other source of
-heating are ineffective, then the Ia heating rate (eq.~[\ref{eq:vIa}])
-is usually sufficiently high to prevent the stagnation radius
-(calculated including the heating from SN Ia) from substantially
-exceeding $r_{\rm Ia}$.
-Stated another way, if the stagnation radius moves inwards from $\rIa$, then decreased heating will force it outwards again.
-However, if the stagnation radius moves well outside of $\rIa$, then the high level of Ia heating will force it inwards.
-
-Our criterion for cooling instability given by equations \eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-However, by re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find the ratio of heating to radiative cooling at $\rIa$ to be given by
+The deep gravitational potential wells of high mass galaxies prevent SN Ia from dynamically clearing out gas in these systems ($\sigma_0 \gg  v^{\rm Ia}_{w}$).
+Equation (\ref{eq:eddr_Ia}) nevertheless still represents a cap on the accretion rate in practice because the Ia heating rate (eq.~[\ref{eq:vIa}])
+is usually high enough to prevent the stagnation radius (calculated including the Ia heating) from substantially exceeding $r_{\rm Ia}$.
+If the stagnation radius moves inwards from $\rIa$, then decreased heating will force it outwards again.
+On the other hand, if the stagnation radius moves well outside of $\rIa$, then the high level of Ia heating will force it inwards.
+
+Finally, note that our criterion for cooling instability (eq.~[\ref{eq:cooling2}], [\ref{eq:Mdotmax}]) is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
+By re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find that
 \begin{align}
@@
 \end{align}
-Thus, for high mass galaxies and/or relatively old stellar populations, Ia heating is capable of preventing cooling instabilities on scales of the stagnation radius, i.e.
+For high mass galaxies and relatively old stellar populations, Ia heating can preventing cooling instabilities on scales of the stagnation radius, i.e.
 $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{\rIa} \gtrsim 10$.
@@
 
-On the other hand, \citealt{LauerFaber+:2005a} find that $\sim 60\%$
-of cusp galaxies and $\sim29\%$ of core galaxies have (generally
-unresolved) emission in excess of the inward extrapolation of the
-Nuker law.  They note that these nuclei are bluer than the background
-galaxy starlight, suggesting the presence of younger stars towards
-galactic center. Nuclear star cluster could be important for small
-values of $M_{\rm bulge}\lsim 10^{11} \Msun$ ($\Mbh\lsim 2\times 10^8
-\Msun$), but are extremely subdominant for higher mass galaxies
-\citep{GrahamSpitler:2009a}.
-
-Mass injection to the nucleus could (for $\Mbh\lsim 2 \times 10^{8}
-\Msun$) therefore be dominated by a nuclear star cluster with its own
-break radius on parsec scales, i.e. much smaller than our fiducial
-value of $r_b \sim 100$ pc.  In the case of high heating, a smaller
-break radius does not appreciably change the stagnation radius,
-resulting in a similar SMBH accretion rate.  For break radii smaller
-than the nominal stagnation radius, the presence of a smaller break
-radius would likely decrease the stagnation radius and accretion rate.
+%Finally, as already mentioned, our models 
+%On the other hand, \citealt{LauerFaber+:2005a} find that $\sim 60\%$
+%of cusp galaxies and $\sim29\%$ of core galaxies have (generally
+%unresolved) emission in excess of the inward extrapolation of the
+%Nuker law.  They note that these nuclei are bluer than the background
+%galaxy starlight, suggesting the presence of younger stars towards
+%galactic center. Nuclear star cluster could be important for small
+%values of $M_{\rm bulge}\lsim 10^{11} \Msun$ ($\Mbh\lsim 2\times 10^8
+%\Msun$), but are extremely subdominant for higher mass galaxies
+%\citep{GrahamSpitler:2009a}.
+
+%Mass injection to the nucleus could (for $\Mbh\lsim 2 \times 10^{8}
+%\Msun$) therefore be dominated by a nuclear star cluster with its own
+%break radius on parsec scales, i.e. much smaller than our fiducial
+%value of $r_b \sim 100$ pc.  In the case of high heating, a smaller
+%break radius does not appreciably change the stagnation radius,
+%resulting in a similar SMBH accretion rate.  For break radii smaller
+%than the nominal stagnation radius, the presence of a smaller break
+%radius would likely decrease the stagnation radius and accretion rate.
 

### 2015-04-26 ms.tex
fixed Ia
fixed compton

@@
 under the most optimistic assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
-On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
+%  On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
 
@@
 \end{align} 
-Compton heating can thus be significant in young stellar populations
+Compton heating is thus significant in young stellar populations
 with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
-km s$^{-1}$ for $\eta \gtrsim 1$.  The accretion rate
-corresponding to a state in which Compton heating self-regulates the accretion flow is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
+km s$^{-1}$ for $\eta \gtrsim 1$.
+
+The accretion rate corresponding to a state in which Compton heating self-regulates the accretion flow is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
 \begin{align}
@@
 
-\citet{Sharma+2007} calculate the radiative efficiency, $\epsilon$,
-based on MHD shearing box simulations of collisionless plasmas. The
-following piecewise power law approximately reproduces
-their results for the radiative efficiency, $\epsilon_{\rm rad}$
-
+\citet{Sharma+2007} estimate the value of the radiative efficiency of low luminosity AGN, $\epsilon_{\rm rad}$,
+based on MHD shearing box simulations of collisionless plasmas.  For Eddington ratios of relevance, their results (shown in their Fig.~6) are well approximated by
 \begin{align}
@@
 \begin{cases}
-  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
- 2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
-%   0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
-%   0.1 & \eddrt \gsim 0.1
+  0.03 \left(\frac{\dot{M}_{\bullet}}{10^{-4}\dot{M}_{\rm edd}}\right)^{0.9} & \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim 10^{-4} \\
+ 0.03 &  10^{-2} \lsim \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim  10^{-4},
 \end{cases}
@@
 \end{align}
-
-The first two lines are a piecewise power law fit designed to
-approximately reproduce the solid line in Figure 6 in
-\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
-heats the electrons. $\epsilon_{\rm rad}$ should saturate to 0.1 at
-larger values of $\eddrt>0.01$, but such a black hole would certainly
-be active and thermally unstable (and thus outside the scope of our
-models). We note they $\eddrt<0.01$ for all of our models.
-
-Additionally, a large fraction of the $\dot{M}$ on large scales will
-be driven out in outflows as the gas has some non-zero angular
-momentum and a centrifugal barrier will stop it from accreting
-\citet{Li+2013}. In the limit weak cooling appropriate for low
-accretion rates the accretion rate on small scales will be of order
-$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
-overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
-equation~\eqref{eq:efficiency}. Note that in evaluating the efficiency
-one has to use $\tilde{\dot{M}}\simeq \alpha \Mdot$. 
-% This means that the bolometric
-% luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
-% \eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
-% $\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
-% the mass inflow rate on small scales. Note that in evaluating the
-% efficiency one has to account for the $\alpha$ suppression in $\eddr$.
-% we obtain 
-{\bf AG note the change in the description of the
-  efficiency. Also, the alpha's kept tripping me up},
-
+where $\dot{M}_{\bullet}$ is the BH accretion.
+In general $\dot{M}_{\bullet}$ will be smaller than the inflow rate $\dot{M}$ calculated thus far by a factor $\alpha < 1$ due to outflows from the accretion disk on small scales.
+Thus, the full efficiency relating the mass inflow rate to the radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following \citet{Li+2013}, who find that the fraction of the inflowing matter lost to outflows equals the effective Shakura-Sunyaev viscosity parameter of the disk.
+Substituting $\epsilon$ into equation (\ref{eq:MdotCa}) and solving for the accretion rate results in
 \begin{align}
@@
 \end{align}
-We note that accretion is unlikely to be steady in cases where AGN
+Accretion may not be truly steady in cases where AGN
 heating dominates, due to the inherent delay between black hole
 feedback and the structure of the accretion flow on larger scales.
-Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless
-represent characteristic average value for the accretion rate,
-assuming a quasi-equilibrium state is achieved over many cycles.
-%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
+Equation (\ref{eq:MdotC}) may nevertheless
+represent a characteristic average value for the accretion rate if a quasi-equilibrium is achieved over many cycles.
+
+%Additionally, a large fraction of the $\dot{M}$ on large scales will
+%be driven out in outflows as the gas has some non-zero angular
+%momentum and a centrifugal barrier will stop it from accreting
+%\citet{Li+2013}. In the limit weak cooling appropriate for low
+%accretion rates the accretion rate on small scales will be of order
+%$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
+%overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
+%equation~\eqref{eq:efficiency}. Note that in evaluating the efficiency
+%one has to use $\tilde{\dot{M}}\simeq \alpha \Mdot$. 
+% This means that the bolometric
+% luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
+% \eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
+% $\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
+% the mass inflow rate on small scales. Note that in evaluating the
+% efficiency one has to account for the $\alpha$ suppression in $\eddr$.
+% we obtain
 

### 2015-04-26 ms.tex
fixed kinetic

@@
 Assume that the outflow power is proportional to the SMBH accretion
-rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}c^{2}$, where
-$\epsilon_{\rm j} < 1$ is a jet efficiency factor.  Further assume
+rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}_{\bullet}c^{2} = 0.1\epsilon_{\rm j} \dot{M}c^{2} $, where
+$\epsilon_{\rm j} < 1$ is an outflow efficiency factor and we have again assumed a fraction $\alpha = 0.1$ of the infall rate reaches the SMBH.  Further assume
 that this energy is deposited as heat uniformly interior to a radius
 $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$.
-The resulting volumetric heating rate $e = \epsilon_{\rm
+The resulting volumetric heating rate $e = 0.1\epsilon_{\rm
   j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a
 heating parameter given by
-\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
+\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{0.2t_{\rm
         h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
       \rho_{\star}|_{r_{s}}}\right)^{1/2} \sim
-  \left(\frac{\epsilon_{\rm
+  \left(\frac{0.1\epsilon_{\rm
         j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
   &\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm
-        j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
+        j}}{10^{-5}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
         heat}}\right)^{1-\Gamma/2},
@@
 where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm
-    s}}/t_{\rm h}$ and, for radii inside the Nuker break radius,
+    s}}/t_{\rm h}$ and, for radii inside the stellar break radius,
 $M_{\star}(r) = M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$
@@
 feedback is released near the stagnation radius, then even a small
-heating efficiency $\epsilon_{\rm j} \gtrsim 10^{-5}$ is sufficient
+heating efficiency $\epsilon_{\rm j} \gtrsim 10^{-4}$ is sufficient
 for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered
@@
 i.e. $r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then
-kinetic feedback is unimportant, even for a powerful jet with
+kinetic feedback is unimportant, even for a powerful outflow with
 $\epsilon_{\rm j} \sim 0.1$.
@@
 the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim
-10^{-6}$) also necessarily has sufficient power to escape the nuclear
+10^{-5}$) also necessarily has sufficient power to escape the nuclear
 region and propagate to much larger radii.  Slower outflows from the
-accretion disk, instead of a collimated relativistic jet, may provide
-a more promising source of feedback in these systems
-(e.g.~\citealt{Li+13}).
+accretion disk, instead of a collimated relativistic jet, provide
+a potentially more promising source of feedback in these systems.
 
@@
 turn may create stronger kinetic feedback.  However, given the uncertainty
-in the efficiency of kinetic heating, we hereafter exclude its effect and defer further discussion
+in the efficiency of kinetic heating, we hereafter neglect its effect and defer further discussion
 to $\S\ref{sec:kinetic}$.
@@
 explicitly on the SMBH mass and the stellar population in the galactic
-nuclear region.  As we now describe, the latter could best be
+nuclear region.  The latter could best be
 described by a single star burst formation in the past, or by a more

### 2015-04-26 ms.tex
cutting fat - and lots of it

@@
     ({\it top}), temperature ({\it middle}), and velocity ({\it bottom}),
-    calculated for a representative sample of galaxies.  Different colors
-    denote different values of the effective wind heating rate,
-    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
-      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
-    line styles correspond to different values of $\Mbh$: $\Mbh=10^6
-    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
-    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
-    galaxies ($\Gamma$=0.8) and thick lines correspond to core
-    galaxies ($\Gamma$=0.1). Squares mark the location of
-    the stagnation radius for each solution.
+    calculated for a representative sample of galaxies.  Colors
+    denote values of the effective wind heating rate,
+    $\vwO=1200$ km s$^{-1}$ ({\it blue}), 600 km s$^{-1}$ ({\it
+      orange}), and 300 km s$^{-1}$ ({\it green}).  Line styles denote different black hole masses: $\Mbh=10^6
+    \Msun$ ({\it dot-dashed}), $10^7 \Msun$ ({\it solid}), and
+    $10^8 \Msun$ ({\it dashed}). Thin and thick lines denote cusp galaxies ($\Gamma$=0.8) and core galaxies ($\Gamma$=0.1), respectively.  Squares mark the locations of the stagnation radius.
  }
@@
   \hline
-  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm
-    inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\right)_{r_{s}}^{(c)}
+  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(a)}$} &   $r_{\rm s}/r_{\rm
+    inf}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\right)_{r_{s}}^{(b)}
       (\eta=0.2)$} & {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm
-            rad}|}\right)_{r_s}^{(d)} (\eta=0.2)$} & Unstable $\eta$'s  \\
-    ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
+            rad}|}\right)_{r_s}^{(c)} (\eta=0.2)$} & Unstable $\eta$'s  \\
+    ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  - & \\ 
     \hline
-    Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & & & & \\
+    Cusp Galaxies, $\Gamma = 0.8$ & & & & & & & & \\
     $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
@@
 \begin{tablenotes}
-\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
-  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
+\item $^{(a)}$ Break radius of stellar density profile.  $^{(b)}$Accretion
   rate in Eddington units, normalized to a stellar mass input
-  parameter $\eta = 0.2$.  $^{(d)}$Ratio of wind heating rate to
-  radiative cooling rate at the stagnation radius.  Thermally unstable
-  solutions are shown in bold text.  $\dagger$Calculated with
+  parameter $\eta = 0.2$.  $^{(c)}$Ratio of wind heating rate to
+  radiative cooling rate at the stagnation radius. $\dagger$Calculated with
   radiative cooling included, assuming mass loss parameter $\eta =
@@
   included, assuming mass loss parameter $\eta = 0.2$ and conductivity
-  saturation parameter $\phi = 0.1$ (recall that the conductive heat
-  flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). We ran solutions
-  with radiative cooling for all cusp galaxies with $v_w=300 $ km/s
-  and all core galaxies with $v_w=600 $ km/s with three different
-  values of the mass loss parameter $\eta$: 0.02, 0.2, and 0.6. Any
-  values of $\eta$ for which a solution turned out to be thermally
-  unstable are marked in the ``Unstable $\eta$'s'' column.  Entries
-  for solutions found to be thermally unstable for all values of $\eta
+  saturation parameter $\phi = 0.1$.
+Solutions including radiative cooling were performed for cusp galaxies with $v_w=300 $ km s$^{-1}$ and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$ = 0.02, 0.2, and 0.6.
+Values of $\eta$ resulting in thermally unstable solutions are marked in the final column.
+Solutions found to be thermally unstable for all $\eta
   \geq 0.02$ are denoted as {\bf TI}.
@@
 massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or for a very
-young stellar population ($\tau_{\star} \ll t_{\rm h}$).
+young stellar population with $\tau_{\star} \ll t_{\rm h}$.
 
@@
 interior to the Ia radius, which is locally gravitationally bound to
-the SMBH by an energy $E_{\rm bind} \sim M_{\rm
-  g}\sigma_0^{2}$.  From the above definitions we find that
+the SMBH by an energy $E_{\rm bind} \gtrsim M_{\rm
+  g}\sigma_0^{2}$.  From the above definitions it follows that
  \be
-\frac{E_{\rm Ia}}{E_{\rm bind}} \sim \frac{(v_{w}^{\rm
+\frac{E_{\rm Ia}}{E_{\rm bind}} \lesssim \frac{(v_{w}^{\rm
     Ia})^{2}}{2\sigma_0^{2}}.

### 2015-04-26 ms.tex
cutting fat - and lots of it2

@@
 $\dot{M}$ & mass accretion rate  \\
+$\dot{M}_{\bullet} = \alpha\dot{M}$ & SMBH accretion rate, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
 $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
@@
 concentrated within its own pc-scale ``break radius" which is much smaller than the outer break in the older stellar population on much larger scales.
-Although our analysis does not take into account the influence such an inner break, for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the location of the break radius.
+Although our analysis does not account for such an inner break, we note that for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the break radius.
 

### 2015-04-27 ms.tex
cutting fat - and lots of it3

@@
 the stagnation radius $\rs$ and the mass accretion rate, the detailed
-derivation of which are given in Appendix \ref{app:rs}.  Our results
-are expressed in terms of the SMBH mass $M_{\bullet}$, total heating
-rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
+derivation of which are given in Appendix \ref{app:rs}.  
+%Our results
+%are expressed in terms of the SMBH mass $M_{\bullet}$, total heating
+%rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
 
@@
 heating rate.
-We emphasize that equation~\eqref{eq:eddr_analytic} represents the radial mass inflow rate on relatively large scales and does not include outflows from the accretion disk on small scales (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), which could significantly reduce the fraction of $\dot{M}$ actually reaching the SMBH.
+As will be discussed later, equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on relatively large scales and does not include outflows from the SMBH accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), which may significantly reduce the fraction of $\dot{M}$ that actually reaches the SMBH.
 
@@
 behavior of the three vertically aligned green squares. These are three
-cusp ($\Gamma=0.8$) galaxies with $\Mbh=10^8 \Msun$ and $v_w=300$ km/s
+cusp ($\Gamma=0.8$) galaxies with t$\Mbh=10^8 \Msun$ and $v_w=300$ km s$^{-1}$
 but with different break radii ($\rb=$ 25, 50, and 100 pc from top to
@@
 explaining the behavior of the two core galaxies shown in
-Fig.~\ref{fig:stag} as vertically aligned orange triangles.  These
-solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
-and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
-radii of $r_{b} =$ 25, 50 pc (from top to bottom).
+Fig.~\ref{fig:stag} as vertically aligned orange triangles.  
+%These
+%solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
+%and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
+%radii of $r_{b} =$ 25, 50 pc (from top to bottom).
 
@@
 
-Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have that
-$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$
-near the stagnation radius.  However, the two ratios diverge from each
-other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$) because
-equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true
-gas density, which is greater in a subsonic flow (weak heating) than
-in a supersonic outflow (strong heating).
-
-In addition to our solutions which neglect thermal conduction and
-radiative cooling, we explore a smaller set of simulations including
-these effects explicitly, as marked by dagger symbols in Table
-\ref{table:models}.  For solutions which are far from being thermally
+Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$
+near the stagnation radius, but these ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$).
+This results because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true gas density in the case of subsonic flow (weak heating).
+
+Although most of our solutions neglect thermal conduction and
+radiative cooling, these effects are explore explicitly in subset of simulations, as marked by dagger symbols in Table \ref{table:models}.  For cases which are far from being thermally
 unstable when cooling is neglected (e.g., $M_{\bullet} =
 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
-0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
-radiative cooling has little effect on the key properties of the flow,
-e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
-marginally thermally stable, including radiative losses acts to
-decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
-greater fractional amount.  We calculated solutions with radiative
+0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the solution, such as the stagnation radius, mass accretion rate, and the cooling ratio $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$.
+However, for solutions that are marginally thermally stable, including radiative losses acts to significantly decrease $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
+We calculated solutions with radiative
 cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
@@
 values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
-expected mass loss for continuous star formation (see
-Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all
-values of $\eta$ are marked in boldface as ``TI" in Table
-\ref{table:models}, with the unstable values of $\eta$ provided in the
-final column.
-
-Thermal conduction, by contrast, results in only minor changes to our
-solutions for our fiducial value of the saturation parameter $\phi =
-0.1$.
+expected mass loss for continuous star formation (Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table
+\ref{table:models}, with the unstable values of $\eta$ provided in the final column.
+
+Including thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$, consistent with our analytic expectation (eq.~[\ref{eq:conduction}]).
 

### 2015-04-27 ms.tex
cutting fat - and lots of it4

@@
     would be thermally unstable.  Thin solid and dot-dashed curves
-    correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm
+    correspond to our simple analytic estimates of $\dot{M}/\dot{M}_{\rm
       edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
-    respectively. Equation ~[\ref{eq:eddr_analytic}] is derived from
-    the approximate analytic result for the stagnation radius given by
-    equation~\eqref{eq:stag_simple}. If we instead use the more
-    accurate result from equation~\eqref{eq:rs2main} we obtain the
-    thick curves.}
+    respectively.  Thick curves correspond to the more accurate implicit analytic expression given by equation \eqref{eq:rs2main}.}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{cooling.eps}
-  \caption{\label{fig:cooling} Ratio of the rate of heating to
+  \caption{\label{fig:cooling} Ratio of the rates of heating to
 radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
 function of radius (solid lines) for each of our solutions shown in
-Figure \ref{fig:profiles}.  Dashed lines show for comparison the ratio
-of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
+Figure \ref{fig:profiles}.  Dashed lines show the ratio
+of the cooling timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
 For high heating rates both ratios are approximately equal at the
@@
 \includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
-\caption{\label{fig:vwSourcesImp} Different sources contributing to
-  the gas heating rate in galactic nuclei at time $\tau_{\star}$ after
-  a single burst of star formation.  Top and bottom panels show cases
-  for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
+\caption{\label{fig:vwSourcesImp} Sources contributing to
+  the gas heating rate at time $\tau_{\star}$ after
+  a single burst of star formation.  Top and bottom panels show black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$
   (both cusps with $\Gamma=0.8$).  Solid and dashed lines show the ranges of
@@
     heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius
-  (eq.~[\ref{eq:cooling3}]).  Also shown with horizontal gray lines
-  are the values of the stellar velocity dispersion, $\sigma_0$,
-  approximated as $\sqrt{3} \sigma_{\bullet}$, where
-  $\sigma_{\bullet}$ is the velocity dispersion from the $\Mbh-\sigma$
-  relation \citep{McConnellMa+:2011a}.}
+  (eq.~[\ref{eq:cooling3}]).  Shown with horizontal gray lines
+  are the stellar velocity dispersion for each SMBH mass, estimated as $\sigma_0=\sqrt{3} \sigma_{\bullet}$ (eq.~[\ref{eq:Msigma}]).}
 \end{figure}
@@
 
-Figure~\ref{fig:vwSourcesImp} shows the contributions of various
-heating sources as a function of time $\tau_{\star}$ after a burst of
-star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top
-panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass
+Figure~\ref{fig:vwSourcesImp} shows the contributions of heating sources as a function of time $\tau_{\star}$ after a burst of
+star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top) and $\Mbh = 10^{8} \Msun$ (bottom). The heating and mass
 input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$
 and $\eta(\tau_{\star})$, are calculated as described in
-Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from
-SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are
-calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC}
-respectively, also making use of $\eta(\tau_{\star})$ from stellar
-winds.  SN Ia heating depends also on a convolution of the DTD
-(eq. [\ref{eq:DTD}]) and the SFH, which reduces to
-the DTD itself for a single star burst.
-
-We crudely account for the expected suppression of SN Ia heating
-resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$
-when the stagnation radius (calculated excluding Ia heating) exceeds
-the Ia radius $r_{\rm Ia}$ exterior to which the interval between
-subsequent supernovae exceeds the local dynamical time
-(eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and
-$v_{\rm w}^{\rm Ia}$ depends on the total heating rate
+Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The SN Ia and Compton heating rates, $v_{w}^{\rm Ia}$ and $v_{\rm w}^{\rm C}$, are
+calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC},
+respectively, which also make use of $\eta(\tau_{\star})$ as set by stellar winds.\footnote{Both $v_{\rm w}^{\rm C}$ and
+$v_{\rm w}^{\rm Ia}$ depend on the total heating rate
 (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series
-of implicit equations to determine each heating rate.  Heating from
-MSPs is found to be negligibly small for fiducial parameters and hence
-is not shown, while kinetic feedback is neglected given its uncertain
-efficiency ($\S\ref{sec:kinetic}$).
-
-For low-mass black holes (Fig.~\ref{fig:vwSourcesImp}, top panel),
-stellar winds are the most important source of heating on timescales
-of $\tau_{\star} \lesssim 10^{7}$ years.  Compton heating comes to
-dominate at later times due to the higher accretion rates that
-accompany the overall decrease in the heating rate, coupled with the
-persistently high mass loss rates and gas densities associated with a
-relatively young stellar population.  Interestingly, Ia SN dominate
-the heating briefly around 10$^{9}$ yr due to a window of time in
-which $r_{ \rm Ia} < \rs$.  For high-mass black holes
-(Fig.~\ref{fig:vwSourcesImp}, bottom panel), stellar wind heating
-dominates early epochs, while SN Ia dominate after $10^{7}$ yr.
-
-As the total heating rate declines with time, after some point the
-flow becomes thermally unstable according to the criterion
-$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 10$
+of implicit equations to determine each.}  SN Ia heating depends also on a convolution of the DTD (eq.
+[\ref{eq:DTD}]) and the SFH, which reduces to the DTD itself for a single star burst.
+We account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated {\it excluding} Ia heating) exceeds
+the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]).  
+Heating from
+
+Figure \ref{fig:vwSourcesImp} shows that stellar winds are the most important heating source at early times, $\tau_{\star} \lesssim 10^{7}$ years.
+Compton heating becomes more important at later times due to (1) the higher accretion rates that accompany the overall decrease in all sources of heating, coupled with (2) the persistently high mass loss rates and gas densities associated with the still relatively young stellar population.
+Interestingly, for $M_{\bullet} = 10^{6}M_{\odot}$, SN Ia dominate the heating briefly around 10$^{9}$ yr due to a window of time in which $r_{\rm Ia} < \rs$.
+For high-mass black holes (Fig.~\ref{fig:vwSourcesImp}, bottom panel), SN Ia dominate at all times after $10^{7}$ yr.
+
+As the total heating rate declines with time, the flow inevitably becomes thermally unstable according to the criterion $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} \lesssim 10$
 (eq.~[\ref{eq:cooling3}]), as shown by dashed lines in
 Fig.~\ref{fig:vwSourcesImp}.  Compton heating is neglected in
-calculating thermal stability because, unlike local stellar feedback
-mechanisms, SMBH feedback may not be capable of truly stabilizing the
-flow, given its inability to respond instantaneously to local changes
-in gas properties.  Thermally unstable flow is present
-throughout the single starburst case except at very early times,
-$\tau_{\star} \lesssim 10^7$ yr, and at late times $\tau_{\star}
+calculating thermal stability because$-$unlike local stellar feedback
+mechanisms$-$it is not clear that SMBH feedback is capable of stabilizing the
+flow given its inability to respond instantaneously to local changes
+in gas properties.
+Thermally unstable flow is present throughout the single starburst case except at very early times, $\tau_{\star} \lesssim 10^7$ yr, in the low $M_{\bullet}$ case and at late times $\tau_{\star}
 \gtrsim 10^{9}$ yr in the high $M_{\bullet}$ case.
+
+Finally, note that MSP heating is negligibly small for fiducial parameters and hence
+is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).
 

### 2015-04-27 ms.tex
cutting fat - and lots of it5

@@
   from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
-  stagnation radius as a function of $\Mbh$ (green), and the ratio of
-  the normalized heating rate
-  $\zeta=\sqrt{1+\frac{v_w^2}{\sigma_0^2}}$ to the critical heating
-  rate $\zeta_c$ for which no outflow is possible (see
-  eq.~\eqref{eq:zetacrit}). In evaluating the latter quantity we use
-  scaling relations for $r_b$, $\rinf$, and $\Gamma$ based on
-  \citet{LauerFaber+:2007a}. {\bf AG added the zeta/zetac line}.}
+  stagnation radius as a function of $\Mbh$ (green), and the ratio of $\zeta/\zeta_{c}$ (blue), where $\zeta_c$ (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are impossible.
+The latter quantity is evalulated using mean scaling relations for $r_b$, $\rinf$, and $\Gamma$ from the \citet{LauerFaber+:2007a} galaxy sample.}
 
@@
 formation history of most galaxies.  Qualitatively, smaller galaxies
-will on average have more recent star formation, resulting in
+will on average experience more recent star formation, resulting in
 energetic young stellar winds and supernovae which dominate the gas
@@
 the average SFH of galaxies containing a given black hole mass.  The
-younger stellar populations characterizing galaxies with $\Mbh\lsim
+younger stellar populations characterizing low mass galaxies with $\Mbh\lsim
 3\times 10^{8} \Msun$ are dominated by stellar winds, with
@@
 10^{8} \Msun$ does the lack of young stellar populations significantly
-reduce the role of stellar wind heating.  But for these massive
-galaxies, the Ia radius is sufficiently small for SN Ia to contribute
-a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 600$ km
+reduce the role of stellar wind heating.  For these massive
+galaxies, however, the Ia radius is sufficiently small that SN Ia contribute
+a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 500$ km
 s$^{-1}$ (in low mass galaxies SN Ia do not contribute to the total
-heating rate because $r_{\rm Ia} > \rs$; bottom panel).  Strikingly,
-we find that galactic nuclei experiencing the same average SFH as
-their host galaxies produce thermally stable flows across almost all
-black hole masses.
-
-An important caveat, however, is that $\vw$ is only a few times higher
-than the stellar velocity dispersion, i.e. $\zeta \sim \zeta_c$
-(eq.~[\ref{eq:zetacrit}]).  This implies that the true stagnation
-radius and SMBH accretion rate could be larger than our analytic
-estimates, potentially resulting in thermal instability, especially
-for core galaxies with large break radii ($\S\ref{sec:mdot}$).  In
-other words, the CNM of some subset of massive ellipticals be
-thermally unstable, not necessarily because they are receiving lower
-stellar feedback than the average for their galaxy mass, but due to
-the high heating required for stability given the structure of their
-stellar potential.
+heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+
+Strikingly, we find that galactic nuclei that experience the same average SFH as
+their host galaxies possess thermally stable flows across all
+black hole masses.  An important caveat, however, is that $\vw$ is generally only a few times higher than the stellar velocity dispersion, i.e. $\zeta \sim \zeta_c$
+(eq.~[\ref{eq:zetacrit}]).
+This implies that the true stagnation radius and SMBH accretion rate could be larger than our analytic estimates, potentially resulting in thermal instability in a significant fraction of galaxies.
+The bottom panel of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where $\zeta_c$ is estimated from the best-fit power-law dependence of $r_b$, $\rinf$, and $\Gamma$ on $M_{\bullet}$ from the \citet{LauerFaber+:2007a} galaxy sample.
+In other words, the CNM of a significant fraction of massive ellipticals may be thermally unstable, not necessarily because they are receiving lower stellar feedback than the average for their galaxy mass, but due to the high heating required for stability given the structure of their stellar potential.
 

### 2015-04-27 ms.tex
cutting fat - and lots of it6

@@
 a comparable level of heating, $v_{w}^{\rm Ia} \gtrsim 500$ km
-s$^{-1}$ (in low mass galaxies SN Ia do not contribute to the total
-heating rate because $r_{\rm Ia} > \rs$; bottom panel).
+s$^{-1}$ (SN Ia do not contribute to the heating in low mass galaxies because $r_{\rm Ia} > \rs$; bottom panel).
 

### 2015-04-27 ms.tex

@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate
-  (excluding small-scale outflows) $\dot{M}$ in Eddington units as a
+\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate $\dot{M}/\dot{M}_{\rm edd}$ as a
   function of black hole mass $M_{\bullet}$, shown separately for core
@@
   the gas inflow rate on large scales (e.g. near the stagnation
-  radius) {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units of
+  radius) {\it Bottom panel:} Growth times $\Mbh/\dot{M}_{\bullet}$ in units of
   the Hubble time $\th$ for each of the accretion rates shown in the
-  top panel.}
+  top panel, where $\dot{M}_{\bullet} = 0.1\dot{M}$ to account for the fraction of the inflowing matter lost to outflows from the accretion disk.}
 \end{figure}
@@
 eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
-otherwise thermally-unstable flow at smaller radii (eq.~[\ref{eq:heatingratioIa}]).  On the other hand, for higher
+otherwise thermally-unstable flow at smaller radii (eq.~[\ref{eq:heatingratioIa}]).  For higher
 $M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
@@
 released by a single Ia is insufficient to unbind gas from the stellar
-bulge (eq.~[\ref{eq:blowout}]).
+bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and yellow lines mean at high $M_{\bullet}$.
 
@@
 Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115
-derived through detailed modeling by \citealt{ShcherbakovWong+:2014a},
+derived through detailed modeling by \citet{ShcherbakovWong+:2014a},
 who find a range of accretion rates depending on the assumed model for
-thermal conductivity (although we expect this range would be smaller
-had they included saturation of the conductive flux).  The SgrA* rate
-exceeds our estimate of $\dot{M}$ due to the average star formation
-history for the same $M_{\bullet}$ by almost two orders of magnitude.
-This discrepancy can be understood by the fact that star formation in
+thermal conductivity\footnote{We expect this range would be have been smaller
+had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux}.  The SgrA* rate
+exceeds our estimate of $\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost two orders of magnitude.
+This discrepancy can in part be understood by the fact that star formation in
 the central parsec of the Milky Way cannot be described as
@@
 estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).  Such a star
-formation history is better described by our `star burst' scenario,
+formation history is better described by our impulsive (starburst) scenario,
 for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
@@
 \citealt{Ho:2009a}), while the right panel luminosities are calculated
-instead assuming an efficiency of $\epsilon_X= 10 \epsilon_{\rm
-  bol}\dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio
-as predicted by some models for radiatively inefficient accretion
-flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for
-comparison are the X-ray measurements (green stars) and upper limits
+instead assuming an efficiency of $\epsilon_X= \epsilon_{\rm
+  bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio
+as predicted by \citet{Sharma+2007} (see eq.~[\ref{eq:efficiency}] and surrounding discussion).  Shown for comparison are the X-ray measurements (green stars) and upper limits
 (gray triangles) from the sample of early-type galaxies compiled by
@@
   $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
-  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
-  (\alpha/0.1) \epsilon_{rad} ( (\alpha/0.1) 0.1 \eddr) $, where
-  $\epsilon_{\rm rad}$ is given by equation~\eqref{eq:efficiency} and
-  $\eddr$ corresponds to the gas inflow rate on large scales.  Shown
+  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.
+Shown
   for comparison are the X-ray luminosities calculated for the maximum

### 2015-04-27 ms.tex
cutting fat - and lots of it8

@@
 \caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate $\dot{M}/\dot{M}_{\rm edd}$ as a
-  function of black hole mass $M_{\bullet}$, shown separately for core
+  function of black hole mass $M_{\bullet}$, shown for core
   ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$, solid).
   Black lines show the accretion rate calculated from equation
-  (\ref{eq:eddr_analytic}) using our estimate of the gas heating rate
-  provided at $z = 0$ by the average star formation histories for each
-  galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the maximum
-  accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red
-  lines show the accretion rate obtained if Compton heating alone was
-  acting (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum
-  accretion rate for a thermally stable flow near the stagnation
-  radius (eq.~[\ref{eq:Mdotmax}]).  We also show Eddington ratios
-  inferred for SgrA* from \citet{Quataert:2004a} (gray circles), for
-  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for
-  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (gray
-  triangles). Note that the actual black hole accretion rate could one
-  to several orders of magnitude smaller due to the presence of small
-  scale outflows. Thus the plot is really showing
-  the gas inflow rate on large scales (e.g. near the stagnation
-  radius) {\it Bottom panel:} Growth times $\Mbh/\dot{M}_{\bullet}$ in units of
+  (\ref{eq:eddr_analytic}) using the heating rate provided at $z = 0$ by the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
+Teal lines show the maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).
+Red lines show the accretion rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$ (eq.~[\ref{eq:MdotC}]).
+Yellow lines show the maximum
+  accretion rate for a thermally stable flow near the stagnation radius, $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).
+Also shown are the inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray circles), for
+  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a} (gray
+  triangles).  {\it Bottom panel:} Growth times $t_{\rm grow} \equiv \Mbh/\dot{M}_{\bullet}$ in units of
   the Hubble time $\th$ for each of the accretion rates shown in the
-  top panel, where $\dot{M}_{\bullet} = 0.1\dot{M}$ to account for the fraction of the inflowing matter lost to outflows from the accretion disk.}
+  top panel, where $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to account for the fraction of inflowing mass lost to disk outflows on small scales.}
 \end{figure}
@@
   $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
-  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.
+  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency of low luminosity accretion disks calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.
 Shown
@@
 observed down-sizing trend that the average Eddington ratio is seen to
-decrease (albeit weakly) with $M_{\bullet}$, especially in the
-$\epsilon_X= (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$ model.
+decrease (albeit weakly) with $M_{\bullet}$, especially in the model where
+$\epsilon_X$ increases with the Eddington ratio.
 However, one must keep in mind the enormous uncertainty in calculating

### 2015-04-27 ms.tex
cutting fat - and lots of it8

@@
 thermal conductivity\footnote{We expect this range would be have been smaller
-had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux}.  The SgrA* rate
+had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux.}.  The SgrA* rate
 exceeds our estimate of $\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost two orders of magnitude.
@@
 
-We acknowledge helpful conversations with Greg Bryan, Jules Halpern,
+We acknowledge helpful conversations with Greg Bryan, Jenny Greene, Jules Halpern,
 Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work

### 2015-04-27 ms.tex
cutting fat - and lots of it8

@@
 $\sigma_0$ & stellar velocity dispersion (assumed to be radially constant)\\
-$\zeta$ & heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
+$\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
 $r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
@@
 the break radius, $\delta \equiv \Gamma+1$.\\
-$\dot{M}$ & mass accretion rate  \\
-$\dot{M}_{\bullet} = \alpha\dot{M}$ & SMBH accretion rate, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
+$\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
+$\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
 $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
-$\dot{M}_{\rm C}$ & `equilibrium' accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
+$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
 $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\

### 2015-04-27 ms.tex
cutting fat - and lots of it9
cutting fat - and lots of it10

@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{TI.pdf}
+  \caption{
+ }
+\label{fig:TI}
+\end{figure}
+
 Radiative cooling usually has its greatest impact near or external to
@@
 this term is balanced at the stagnation radius by the external heating
-term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.  We assess thermal
-stability near the stagnation radius by comparing the ratio of
+term, $\dot{q}_{\rm heat} = q \tilde{v}_{w}^{2}/2$.  One can therefore assess thermal
+stability by comparing the ratio of
 external heating to radiative cooling $|\dot{q}_{\rm rad}|$
@@
    240 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
-\approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
+%\approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c. 
   \end{cases}
@@
 \end{align}
-where the final condition corresponds to the low wind heating limit
-($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our
-numerical and analytic results show that the stagnation radius moves
-out to the break radius $r_b$; the quasi-hydrostatic structure that
-develops in this case greatly increases the gas density, resulting in local
-thermal instability.
-
-Note that in practice when $v_{w}<v_{\rm TI}$, a cooling flow may
-develop rather than a true local thermal instability: in the former
-case the stagnation radius $\rs$ may move to large radii, greatly
-increasing the density in the inner part of the flow, which increases
-cooling and creates a large inflow of cold gas towards the center of
-the galaxy.  In this paper we do not attempt to distinguish under what
-conditions a global cooling flow would develop vs. a local thermal
-instability.
+Equations (\ref{eq:cooling2}) and (\ref{eq:cooling3}) are derived using expressions for the stagnation radius and gas density in the high heating limit of $\zeta > \zeta_c = (r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]).
+However, for $\zeta < \zeta_c$, the stagnation radius diverges to the break radius $r_b$ (Appendix \ref{app:be}).
+The quasi-hydrostatic structure that results in this case greatly increases the gas density, which in practice we find renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$ according to equation (\ref{eq:cooling3}).
+In other words, the true condition for thermal instability  can be written
+\be
+v_w > {\rm max}[v_{\rm TI},\sigma_0\{1-(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}\}]
+\ee
+
+Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass input parameters $\eta$, as well as the $\zeta > \zeta_c$ criterion, shown separately for cusp and core galaxies.
+We calculate $\zeta_c$ using the empirical correlation for
+core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
+follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
+correlation derived from the results of \citet{LauerFaber+:2007a}.
+For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$ criterion is generally more strigent, while for core galaxies the $\zeta > \zeta_c$ criterion is more strigent for core galaxies, except for very high mass loss rates $\eta > 10$.
 
@@
 correlation derived from the results of \citet{LauerFaber+:2007a}.
+
+Note that in practice  what we describe as "thermal instability" may simply indicate the transition of an inflow-outflow solution to a global cooling flow, instead of a true local thermal instability.
+In the former case the stagnation radius diverges to large radii, increasing the density in the inner parts of the flow, which increases cooling and creates a large inflow of cold gas towards the nucleus.
+A true thermal instability would cause parts of the hot ISM to condense into cold clouds.
+In this paper we do not distinguish between these possibilities, although both are likely present at some level.
+Note that if the CNM were to somehow ``regulate" itself to a state of local marginal thermal instability (as has previously been invoked on cluster scales; e.g., \citealt{Voit+15}), then equation (\ref{eq:Mdotmax}) could reflect the assocated mass ``fall-out" rate and concomitant star formation rate.
 
@@
 behavior of the three vertically aligned green squares. These are three
-cusp ($\Gamma=0.8$) galaxies with t$\Mbh=10^8 \Msun$ and $v_w=300$ km s$^{-1}$
+cusp ($\Gamma=0.8$) galaxies with $\Mbh=10^8 \Msun$ and $v_w=300$ km s$^{-1}$
 but with different break radii ($\rb=$ 25, 50, and 100 pc from top to

### 2015-04-27 ms.tex
cutting fat - and lots of it11

@@
 for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of
-black hole mass, where $\epsilon_{X} = \epsilon\epsilon_{\rm bol}$,
-$\epsilon$ is the total radiative efficiency, and $\epsilon_{\rm bol}
-\sim 0.1$ is the bolometric correction into the measured X-ray band
-for low luminosity AGN (\citealt{Ho08}).  The value of $\langle L_X
-\rangle$ is calculated using the average accretion for galaxies with
+black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of the inflowing matter loss to outflows from the accretion disk, $\epsilon_{\rm rad}$ is the radiative efficiency of the accreted matter, and $\epsilon_{\rm bol} \sim 0.1$ is the bolometric correction into the measured X-ray band
+for low luminosity AGN (\citealt{Ho08}).  In all cases the value of $\langle L_X
+\rangle$ is calculated using the average accretion rate for galaxies with
 core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
-profiles, using the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$ fit
-to the \citet{LauerFaber+:2007a} galaxy sample.
+profiles, using the mean power-law relationship $\Gamma = 0.3 \Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a} galaxy sample.
 
@@
 10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
-\citealt{Ho:2009a}), while the right panel luminosities are calculated
+\citealt{Ho:2009a}).  The right panel luminosities are calculated
 instead assuming an efficiency of $\epsilon_X= \epsilon_{\rm
   bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio
-as predicted by \citet{Sharma+2007} (see eq.~[\ref{eq:efficiency}] and surrounding discussion).  Shown for comparison are the X-ray measurements (green stars) and upper limits
+as predicted by MHD sheaing box simulations by \citet{Sharma+2007} (see eq.~[\ref{eq:efficiency}] and surrounding discussion).
+Shown for comparison are the X-ray measurements (green stars) and upper limits
 (gray triangles) from the sample of early-type galaxies compiled by
@@
 single waveband based on the feeding rate on larger scales.  If disk
-outflows carry away most of the infalling mass before it reaches X-ray
+outflows indeed carry away most of the infalling mass before it reaches X-ray
 producing radii (e.g.~\citealt{Blandford&Begelman99};
 \citealt{Li+13}), then the angular momentum of the infalling gas might
-also influence the X-ray luminosity, in a way that could depend
-systematically on the stellar population and hence $M_{\bullet}$.
+also influence the X-ray luminosity indirectly through the inflow efficiency $\alpha$, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.
 
@@
 velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
-\eta v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
+v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
 (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When
@@
 \ref{fig:NickPlot2}), this can lead to order of magnitude differences
-in $\dot{M}$ {\bf AG limitation from zetac}; (3) differences in
+in $\dot{M}$; (3) differences in
 angular momentum of the infalling gas from galaxy to galaxy, resulting
@@
 It is also possible that many of the \citet{Miller+15} sample of
-galactic nuclei are not accreting in steady state. Within our steady
-state solutions gas outside the stagnation radius $\rs$ is being blown
+galactic nuclei are not accreting in steady state.
+This is supported by the fact that many of the X-say luminosities in Figure \ref{fig:miller} lie above the predictions for stable accretion, i.e., $L_X \gtrsim \epsilon_X \dot{M}_{\rm TI}c^{2}$ (yellow line), at least for our choice of radiative efficiency.
+
+Within our steady state solutions gas outside the stagnation radius $\rs$ is being blown
 out in wind. However, for very massive galaxies ($\Mbh\gsim 10^8
@@
 
-Furthermore, our SFH-averaged accretion rates are derived using
-analytic expressions for the stagnation radius that may underpredict
-the true accretion rate if $\zeta < \zeta_c$, as may occur in massive
-core galaxies with large break radii.
+%Furthermore, our SFH-averaged accretion rates are derived using
+%analytic expressions for the stagnation radius that may underpredict
+%the true accretion rate if $\zeta < \zeta_c$, as may occur in massive
+%core galaxies with large break radii.
 
 If the actual radiative efficiency is lower than our fiducial
-assumption, then many of the X-ray detections would lie above the
-predictions for stable accretion, i.e., $L_X \gtrsim \epsilon_X
-\dot{M}_{\rm TI}$ (yellow line).  For example, we assume 10\% 
-of the mass inflow rate is drive out in small scale outflows, but this
-fraction could be considerably large. In this case the X-ray detected
-galaxies experience less heating than average galaxies of the same
-mass, and may not be stably accreting at all.  This is particularly
-plausible because the \citet{Miller+15} sample includes only
-early-type galaxies, with older stellar populations than the average
-for their black hole mass.
+assumption, then an even larger fraction of the X-ray detections would lie above the
+predictions for stable accretion.  For example, we assume that a fraction $\alpha = 0.1$ 
+of the mass inflow rate reaches the SMBH, but this fraction could be considerably smaller.
+In such a case the X-ray detected galaxies will be experience less heating than we calculate for the average SFH, and may not be stably accreting at all.
+This is plausible given that the \citet{Miller+15} sample includes only early-type galaxies with older stellar populations than the average for their stellar mass.
 
@@
 that even if Compton heating could act to stabilize the flow in a
-quasi-steady state (which, as already discussed, is unlikely), the
-magnitude of the heating is insufficient to produce a thermally stable
-accretion rate given conditions corresponding to the average SFH.
+quasi-steady state, the magnitude of Compton heating is not sufficient to produce a thermally stable accretion rate, at least for conditions corresponding to the average SFH.
 
@@
 
-If the galaxies for which $L_{\rm X}$ is measured at low $M_{\bullet}$
-in Fig \ref{fig:miller} are indeed in a state of thermally-unstable
-outburst, then a subset of the galaxies with X-ray upper limits
-may contribute to a separate population of thermally stable, steadily
-accreting nuclei.  Such a population could include SgrA*, which has a
-much lower X-ray luminosity for its black hole mass than predicted by
-the \citet{Miller+15} trend.  A potentially bimodal population of
-steady and outbursting galactic nuclei calls into question the physical
-justification of using simple extrapolations of power-law fits to the
-$L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
-constrain the occupation fraction of SMBHs in the nuclei of low mass
+If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$
+in Figure \ref{fig:miller} are indeed in a state of thermally-unstable
+outburst, then some of the galaxies with X-ray upper limits could be contributing to a separate population of thermally-stable, steadily accreting nuclei.
+Such a population could include SgrA*, which has a much lower X-ray luminosity for its SMBH mass than predicted by the \citet{Miller+15} trend.
+A potentially bimodal population of steady and outbursting galactic nuclei calls into question the practice of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass
 galaxies.

### 2015-04-27 ms.tex
cutting fat - and lots of it12

@@
 The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
-time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion
-rate shown in the top panel.  For SMBHs which accrete steadily at the
+time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}_{\bullet}$, for each accretion
+rate shown in the top panel, where we remind that $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$.  For SMBHs which accrete steadily at the
 rate set by the stellar wind heating due to the average star formation
 history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
-Hubble time by 1$-$3 orders of magnitude across all $M_{\bullet}$.
+Hubble time by 2$-$4 orders of magnitude across all $M_{\bullet}$.
 Steady accretion therefore cannot explain the growth of low mass black
@@
 
- We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
-($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
-shut-off time (if linked with the accretion becoming sub-Eddington), and an
-observed QPO in the x-ray light curve favor a smaller black hole {\bf
-  AG Gone mad!}.
+% We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
+%($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
+%shut-off time (if linked with the accretion becoming sub-Eddington), and an
+%observed QPO in the x-ray light curve favor a smaller black hole {\bf
+ % AG Gone mad!}.
 
@@
 
-This prediction is also consistent with the observed dependence of
+This prediction is also consistent with the observed downsizing trend of
 $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies

### 2015-04-27 ms.tex
cutting fat - and lots ofit15

@@
 parameter $\phi < 0.1$.  Our numerical experiments which include
-conductive heating confirm this ($\S\ref{sec:numerical}$).  {\bf BDM: whats going on wrt johnson and quataert?}
+conductive heating confirm this ($\S\ref{sec:numerical}$).
 
@@
 However, for $\zeta < \zeta_c$, the stagnation radius diverges to the break radius $r_b$ (Appendix \ref{app:be}).
-The quasi-hydrostatic structure that results in this case greatly increases the gas density, which in practice we find renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$ according to equation (\ref{eq:cooling3}).
+The quasi-hydrostatic structure that results in this case greatly increases the gas density, which in practice renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$ according to equation (\ref{eq:cooling3}).
 In other words, the true condition for thermal instability  can be written
@@
 
-Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass input parameters $\eta$, as well as the $\zeta > \zeta_c$ criterion, shown separately for cusp and core galaxies.
-We calculate $\zeta_c$ using the empirical correlation for
-core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
+Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass input parameters $\eta$, as well as the [$\eta$-independent] $\zeta > \zeta_c$ criterion, shown separately for cusp and core galaxies.
+For core galaxies, we calculate $\zeta_c$ using the empirical relation, $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$, which
 follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
@@
 
-The minimum heating rate for thermal stability
-(eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable
-accretion rate,
-\begin{align}
-  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq {\rm
-    min}\begin{cases}
-    2\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
-    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
-    8\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
-    1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
+The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to {\it maximum} thermally-stable accretion rate,
+\begin{align}
+  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq \begin{cases}
+    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \\
+    8\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp},\\
   \end{cases}
@@
 \end{align}
-where the first line for each case is derived using equation
-(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and
-the second line corresponds to the low wind heating limit $\zeta \ll
-\zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
-core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
-follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
-correlation derived from the results of \citet{LauerFaber+:2007a}.
-
-Note that in practice  what we describe as "thermal instability" may simply indicate the transition of an inflow-outflow solution to a global cooling flow, instead of a true local thermal instability.
+where the cusp case is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and the core case corresponds to the more stringent $\zeta > \zeta_c$ criterion, calculated again using the mean $r_{b}/r_{\rm inf}$ relation from \citet{LauerFaber+:2007a}.
+
+What we describe above as ``thermal instability" may in practice simply indicate an abruption transition from a steady inflow-outflow solution to a global cooling flow, as opposed a true thermal instability.
 In the former case the stagnation radius diverges to large radii, increasing the density in the inner parts of the flow, which increases cooling and creates a large inflow of cold gas towards the nucleus.
-A true thermal instability would cause parts of the hot ISM to condense into cold clouds.
+A true thermal instability would likely result in a portion of the hot ISM condensing into cold clouds, a situation which may or may not be present in a cooling flow.
 In this paper we do not distinguish between these possibilities, although both are likely present at some level.
-Note that if the CNM were to somehow ``regulate" itself to a state of local marginal thermal instability (as has previously been invoked on cluster scales; e.g., \citealt{Voit+15}), then equation (\ref{eq:Mdotmax}) could reflect the assocated mass ``fall-out" rate and concomitant star formation rate.
+Finally, note that if the CNM were to ``regulate" itself to a state of local marginal thermal instability (as has previously been invoked on cluster scales; e.g., \citealt{Voit+15}), then equation (\ref{eq:Mdotmax}) might naturally reflect the characteristic mass fall-out rate and concomitant star formation rate.
 
@@
 
-This prediction is also consistent with the observed downsizing trend of
+This prediction is also consistent with the observed dependence of
 $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies

### 2015-04-27 ms.tex
cutting fat - and lots ofit16

@@
 uncoincidental.
-
-% We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
-%($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
+On the other hand, we note that some models for J1644+57  (e.g., \citealt{Tchekhovskoy+2014}) favor a much smaller black hole ($10^5-10^6 \Msun$) than we estimate would be required to produce the observed inner break.
+
+% based on the observed jet power, the jet
 %shut-off time (if linked with the accretion becoming sub-Eddington), and an
@@
 $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray
-luminosities of quiescent SMBHs and low luminosity AGN.  They are also
-used to address key questions such as the thermal stability of the
-accretion flow.  Our conclusions are summarized as follows.
+luminosities of quiescent SMBHs and low luminosity AGN.  Our conclusions are summarized as follows.
 
@@
     model on large scales, given the inferred stellar rotation rates
-    near the stagnation radius ($\S\ref{sec:rotation}$). However, on
-    small scales gas would encounter a centrifugal barrier which would
-    cause much of the gas flowing inwards on large scales to be driven
-    outwards in an outflow (as in \citealt{Li+2013}).
+    near the stagnation radius ($\S\ref{sec:rotation}$). 
+%However, on
+ %   small scales gas would encounter a centrifugal barrier which would
+  %  cause much of the gas flowing inwards on large scales to be driven
+   % outwards in an outflow (as in \citealt{Li+2013}).
 
 \item Radiative cooling has a more pronounced influence on the flow
-  structure.  Cooling instabilities are likely to develop when the
+  structure.  Cooling becomes important when the
   radiative cooling rate exceeds the gas heating rate near the
-  stagnation radius.  This condition is approximately equivalent to
-  the $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by
+  stagnation radius, where the gas is in nearly hydrostatic equilibrium (Fig.~\ref{fig:TI}).  This condition is approximately equivalent to
+  the $t_{\rm cool} \gg t_{\rm ff}$ criterion for thermal instability advocated by
   \citet{McCourt+12} and \citet{Li&Bryan14a}.
+The transition in the flow properties that occurs as heating is reduced may represent a true ``thermal instability" (hot ISM condensing into a cooler clouds), or it may simply represent an abruption transition from a steady inflow-outflow solution to a global cooling flow.
+We leave distinguishing between these possibilities to future work.
 
@@
 
-\item Stellar wind heating from the average SFH is sufficient to
-  permit thermally-stable, steady-state accretion.  However, the
+\item Stellar wind heating from the average SFH may be sufficient to
+  permit thermally-stable, steady-state accretion, depending on the accretion efficiency of the SMBH.  However, the
   resulting average Eddington-normalized accretion rate is predicted
@@
   X-ray luminosities of early-type galaxies (e.g.,
-  \citealt{Miller+15}).  However, these differences may not be
-  discriminating given the huge uncertainty in translating the
-  predicted gas inflow rate on parsec scales to the disk X-ray
-  luminosity.
-
-  Thermally stable accretion models can reproduce the observed scatter
+  \citealt{Miller+15}).  Thermally stable accretion models can reproduce the observed scatter
   in nuclear X-ray luminosities at fixed $\Mbh$ of 2-4 orders of
@@
   galaxy, or from time to time due to burstiness in the SFH
-  (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of
+  (e.g.~Fig.~\ref{fig:NickPlot2}); (3) Variations in the amount of
   inflowing mass which is lost to small scale outflows from the SMBH
@@
 
-\item The accretion rates of early-type galaxies are below the maximum
-  value for thermally stable flow, $\dot{M}_{\rm TI}$
-  (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies.
-  Therefore the current X-ray detections could instead be comprised
+\item However, for lower X-ray radiative efficiencies, the accretion rates of early-type galaxies are above the maximum value for thermally stable flow, $\dot{M}_{\rm TI}$
+  (Fig.~\ref{fig:miller}).  This implies that current X-ray detections could instead be comprised
   mostly of nuclei undergoing outburst due to thermal instabilities.
-  In this case there may exist a separate branch of low-$L_X$
-  (undetected) thermally-stable nuclei, especially at low
-  $M_{\bullet}$.  Such a bimodal population would call into question
+  In such a case, there may exist a separate (usually undetected) branch of low-$L_X$ nuclei accreting stably.  The existence of such a bimodal population might call into question
   methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
-  to low $M_{\bullet}$ in order to constrain the SMBH occupation
-  fraction in low mass galaxies (\citealt{Miller+15}).
+  to low $M_{\bullet}$ to constrain the SMBH occupation
+  fraction of low mass galaxies (\citealt{Miller+15}).
 
@@
   for steady-state, thermally stable accretion
-  (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN
+  (Fig.~\ref{fig:bh_growth}).  Perhaps unsurprisingly, low-$M_{\bullet}$ growth and AGN
   activity must instead be driven by a supply of gas external to the
@@
 
-We conclude by drawing attention to the following limitations of our
-model.  First, by neglecting any large scale inflow of gas to the
-nucleus and assuming the only source of gas feeding the black hole is
-stellar wind mass loss from the local stellar population, our
+We conclude by drawing attention to a few limitations of our
+model.  First, we have neglected any large scale inflow of gas to the
+nucleus by assuming the only source of gas feeding the black hole is
+stellar wind mass loss from the local stellar population.  Our
 estimates represent a lower bound on the time averaged gas density of
-the CNM.  Our model therefore cannot account for AGN.
+the CNM.  Our model cannot account for AGN.
 

### 2015-04-28 ms.tex

@@
   \includegraphics[width=\columnwidth]{TI.pdf}
-  \caption{
+  \caption{Minimum effective wind heating parameter required for thermal stability as a function of SMBH mass.
+Black lines show $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the high-heating limit when the stagnation radius lies interior to the influence radius, for different values of the mass loss parameter $\eta$ as marked.
+{\bf Blue ???}  lines show the minimum heating parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for cusp (solid) and core (dashed) galaxies, using the mean $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the \citet{LauerFaber+:2007a} galaxy sample.
+For $\zeta < \zeta_c$ the stagnation radius moves from inside the influence radius, out to the stellar break radius $r_b$ (Appendix \ref{app:be}); in practice renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$.
+For cusp galaxies the $v_w > v_{\rm TI}$ is usually the more strigent criterion for stability, while for core galaxies the $\zeta > \zeta_c$ is usually more relevant.
  }

### 2015-04-28 ms.tex
Wording changes to the conclusions

@@
   \item A stagnation radius, $\rs$, divides the nuclear gas between an
-    accretion flow and an outward wind. In steady-state the gas inflow
+    accretion flow and an outgoing wind. In steady-state the gas inflow
     rate towards the black hole is proportional to the stellar mass
@@
     momentum is also unlikely to invalidate our spherically symmetric
-    model on large scales, given the inferred stellar rotation rates
+    model on large scales, given observationally inferred rotation rates of galactic nuclei
     near the stagnation radius ($\S\ref{sec:rotation}$). 
@@
   $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$, implying
-  that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.
+  that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core (cusp) galaxies.
   However, $\Mdot$ can increase even more rapidly with decreasing
@@
   bulge and cannot produce a flow with a positive kinetic energy
-  interior to the stellar break radius (Appendix \ref{app:be}); (2)
+  interior to the stellar break radius, as we show in Appendix \ref{app:be}; (2)
   For low $v_w$, gas near the stagnation radius becomes thermally
@@
     explicitly on the SMBH mass as well as the SFH in the galactic
-    nuclear region.  A young starburst of age $\lesssim 10$ Myr
+    nucleus.  A young starburst of age $\lesssim 10$ Myr
     produces mass and energy injection dominated by young stellar
@@
     input usually dominated by young stars and mass input dominated by
-    the old stars (Appendix \ref{app:windheat}).  Galactic nuclei with
-    $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs
+    old stars (Appendix \ref{app:windheat}).  Galactic nuclei with
+    $\Mbh \lesssim 10^8\Msun$ that are heated according to their average SFHs
     (as derived from cosmological simulations) receive a stellar wind
@@
   massive galaxies (Fig.~\ref{fig:vwSources}).  However, if $\rs$ does
-  approach or exceed $\rIa$, then the SN Ia heating is usually
-  sufficiently large to prevent $\rs$ from greatly exceeding $\rIa$.
-  SNe Ia thus regulates the SMBH accretion rate below the value
+  approach $\rIa$, then SN Ia heating is usually
+  large enough to prevent $\rs$ from greatly exceeding $\rIa$.
+  SNe Ia thus regulate the SMBH accretion rate below the value
   $\dot{M}_{\rm Ia}$ (eq.~[\ref{eq:eddr_Ia}]), except possibly in high
@@
   to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in
-  tension with the (also weak) downsizing trend of measured nuclear
-  X-ray luminosities of early-type galaxies (e.g.,
+  tension with the (also weak) downsizing trend of measured 
+  X-ray luminosities in early-type galactic nuclei (e.g.,
   \citealt{Miller+15}).  Thermally stable accretion models can reproduce the observed scatter
-  in nuclear X-ray luminosities at fixed $\Mbh$ of 2-4 orders of
-  magnitude due to combination of (1) intrinsic scatter in the SMBH
-  scaling relations; (2) stochastic variation in SFH from galaxy to
-  galaxy, or from time to time due to burstiness in the SFH
-  (e.g.~Fig.~\ref{fig:NickPlot2}); (3) Variations in the amount of
+  in nuclear X-ray luminosities at fixed $\Mbh$ (2-4 orders of
+  magnitude) due to the combination of (1) intrinsic scatter in the SMBH
+  scaling relations; (2) stochastic variation in SFH between galaxies, or within one galaxy due to burstiness in the SFH, as in ~Fig.~\ref{fig:NickPlot2}; (3) Variations in the amount of
   inflowing mass which is lost to small scale outflows from the SMBH
-  accretion disk, due to variations in the angular momentum of the
+  accretion disk, likely due to variations in the angular momentum of the
   accreting gas (e.g.~\citealt{Li+13}).
@@
   mostly of nuclei undergoing outburst due to thermal instabilities.
-  In such a case, there may exist a separate (usually undetected) branch of low-$L_X$ nuclei accreting stably.  The existence of such a bimodal population might call into question
-  methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
-  to low $M_{\bullet}$ to constrain the SMBH occupation
-  fraction of low mass galaxies (\citealt{Miller+15}).
+  In such a case, there may exist a separate (usually undetected) branch of low-$L_X$ nuclei accreting stably.
+The existence of such a bimodal population would call into question constraints on the SMBH occupation
+  fraction in low mass galaxies (\citealt{Miller+15}) derived by
+  extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
+  to small $M_{\bullet}$.
 
 \item Low mass black holes grow in the low redshift universe over
-  timescales comparable to the Hubble time (\citealt{Heckman+04}).  This
-  accretion rates so required are too high to be consistent with the
-  value predicted for the average SFH history and the maximum allowed
+  timescales comparable to the Hubble time (\citealt{Heckman+04}).  The
+  accretion rates so required are too high to be consistent with either the
+  value predicted for the average SFH history or the maximum allowed
   for steady-state, thermally stable accretion
@@
   activity must instead be driven by a supply of gas external to the
-  nucleus, e.g. due to galaxy mergers or thermal instabilities on
+  nucleus, such as galaxy mergers or thermal instabilities on
   larger, galactic scales (e.g.~\citealt{Voit+15}).
@@
 estimates represent a lower bound on the time averaged gas density of
-the CNM.  Our model cannot account for AGN.
+the CNM.  Although our model can, under certain assumptions, describe quiescent galactic nuclei, it cannot account for AGN.
 
@@
 the accretion mode of individual galaxies without knowledge of their
-specific SFH.  We adopt halo average star formation rates measured in
+specific SFH.  We adopt halo-averaged star formation rates measured in
 cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any

### 2015-04-28 ms.tex
fixing color description.

@@
   \includegraphics[width=\columnwidth]{TI.pdf}
-  \caption{Minimum effective wind heating parameter required for thermal stability as a function of SMBH mass.
-Black lines show $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the high-heating limit when the stagnation radius lies interior to the influence radius, for different values of the mass loss parameter $\eta$ as marked.
-{\bf Blue ???}  lines show the minimum heating parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for cusp (solid) and core (dashed) galaxies, using the mean $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the \citet{LauerFaber+:2007a} galaxy sample.
-For $\zeta < \zeta_c$ the stagnation radius moves from inside the influence radius, out to the stellar break radius $r_b$ (Appendix \ref{app:be}); in practice renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$.
-For cusp galaxies the $v_w > v_{\rm TI}$ is usually the more strigent criterion for stability, while for core galaxies the $\zeta > \zeta_c$ is usually more relevant.
- }
+  \caption{Minimum effective wind heating parameter required for
+    thermal stability as a function of SMBH mass.  Black lines show
+    $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required
+    for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the
+    high-heating limit when the stagnation radius lies interior to the
+    influence radius, for different values of the mass loss parameter
+    $\eta$ as marked.  {\bf Blue ???}  lines show the minimum heating
+    parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
+      inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for
+    cusp (solid) and core (dashed) galaxies, using the mean
+    $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the
+    \citet{LauerFaber+:2007a} galaxy sample.  For $\zeta < \zeta_c$
+    the stagnation radius moves from inside the influence radius, out
+    to the stellar break radius $r_b$ (Appendix \ref{app:be}); in
+    practice renders the flow susceptible to thermal runaway, even if
+    $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w > v_{\rm TI}$ is
+    usually the more strigent criterion for stability, while for core
+    galaxies the $\zeta > \zeta_c$ is usually more relevant.  }
 \label{fig:TI}
@@
 
-Even if the hot plasma of the CNM does not
-condense into cold clouds, the loss of pressure can temporarily
-increase the black hole accretion rate by producing a large-scale cooling flow.  When coupled to feed-back processes which result from such enhanced accretion, this can lead to
-time-dependent limit cycle behavior (e.g.~\citealt{Ciotti&Ostriker07};
-\citealt{Ciotti+10}; \citealt{Yuan&Li11}, \citealt{Gan+14}), which is
-also inconsistent with our assumption of a steady, single-phase flow.
+Even if the hot plasma of the CNM does not condense into cold clouds,
+the loss of pressure can temporarily increase the black hole accretion
+rate by producing a large-scale cooling flow.  When coupled to
+feed-back processes which result from such enhanced accretion, this
+can lead to time-dependent limit cycle behavior
+(e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10};
+\citealt{Yuan&Li11}, \citealt{Gan+14}), which is also inconsistent
+with our assumption of a steady, single-phase flow.
 
@@
 instead assuming an efficiency of $\epsilon_X= \epsilon_{\rm
-  bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio
-as predicted by MHD sheaing box simulations by \citet{Sharma+2007} (see eq.~[\ref{eq:efficiency}] and surrounding discussion).
-Shown for comparison are the X-ray measurements (green stars) and upper limits
+  bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio as
+predicted by MHD sheaing box simulations by \citet{Sharma+2007} (see
+eq.~[\ref{eq:efficiency}] and surrounding discussion).  Shown for
+comparison are the X-ray measurements (black stars) and upper limits
 (gray triangles) from the sample of early-type galaxies compiled by
-\citet{Miller+15} (cf.~\citealt{Gallo+10}).  A green line shows the
+\citet{Miller+15} (cf.~\citealt{Gallo+10}).  A black line shows the
 best power-law fit to the X-ray luminosity from \citet{Miller+15},
@@
 SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
-Compton heating feedback (eq.~[\ref{eq:MdotC}]; red).
+Compton heating feedback (eq.~[\ref{eq:MdotC}]; pink).
 

### 2015-04-29 ms.tex

@@
   of nearby quiescent galactic nuclei with our results for
-  $\dot{M}(M_{\bullet})$ we show that most nuclei are consistent with
+  $\dot{M}(M_{\bullet})$ we address whether the nuclei are consistent with
   accreting in a steady-state, thermally-stable manner for radiative
-  efficiencies predicted by ADAF models.  However, thermally-stable
+  efficiencies predicted for radiatively inefficiency accretion flows.  However, thermally-stable
   accretion cannot explain the short average growth times of low mass
@@
 
-Gas comprising the CNM can in principle originate from several
+Gas comprising the CNM of quiescent (non-AGN) galaxies can in principle originate from several
 sources: (1) wind mass loss from predominantly evolved stars; (2)
@@
 up to two because of the supersonic inflow on small radial scales and
-a possible supersonic outflow on large scales.  Our
+a possible supersonic outflow on large scales.
+
+Our
 solutions can be scaled to any value of the mass input parameter,
@@
 where the stagnation radius is assume to reside well inside the Nuker
-break radius.  Equation (\ref{eq:conduction}) shows that, even when
+break radius.
+
+Equation (\ref{eq:conduction}) shows that, even when
 conduction is saturated, our neglect of heat conduction results in at
@@
     influence radius, for different values of the mass loss parameter
-    $\eta$ as marked.  {\bf Blue ???}  lines show the minimum heating
+    $\eta$ as marked.  Blue lines show the minimum heating
     parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
@@
     $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the
-    \citet{LauerFaber+:2007a} galaxy sample.  For $\zeta < \zeta_c$
+    \citet{LauerFaber+:2007a} galaxy sample for cores and assuming a fixed value of $r_{b} = 100$ pc for cusps.  For $\zeta < \zeta_c$
     the stagnation radius moves from inside the influence radius, out
@@
 v_{w} > v_{\rm TI} \simeq
-  {\rm max}\begin{cases}
+  \begin{cases}
    280 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
@@
 correlation derived from the results of \citet{LauerFaber+:2007a}.
-For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$ criterion is generally more strigent, while for core galaxies the $\zeta > \zeta_c$ criterion is more strigent for core galaxies, except for very high mass loss rates $\eta > 10$.
+For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$ criterion is generally more strigent, while for core galaxies the $\zeta > \zeta_c$ criterion is more strigent for core galaxies, except for high mass loss rates $\eta > 1$.
 
@@
 interior to this point.  From equation (\ref{eq:rcirc}) we thus
-conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will
-circularize the inner sonic point of the flow ($r\gsim 0.01r_{\rm s}$;
-Fig.~\ref{fig:profiles}).  Angular momentum should only become
+conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will most likely
+circularize within the inner sonic point of the flow (Fig.~\ref{fig:profiles}).  Angular momentum should only become
 dynamically important for thermally stable flows in a region that is
@@
 ($\Gamma$=0.1) and cusp galaxies ($\Gamma$=0.8).  Shown for comparison
-is our analytic estimate of $\dot{M}/\dot{M}_{\rm edd}$ from equation
+is our simple analytic estimate of $\dot{M}/\dot{M}_{\rm edd}$ from equation
 (\ref{eq:eddr_analytic}).  For high wind velocities ($v_{w} \gg
@@
 $M_{\bullet}$ (large $\sigma_0$), the numerical accretion rate
-considerably exceeds the analytic estimate as the stagnation radius
+considerably exceeds the simple analytic estimate as the stagnation radius
 diverges to large radii (Fig.~\ref{fig:stag}).
@@
 that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
-the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  Hereafter we adopt $\epsilon_{\rm Ia} = 0.4$ as fiducial.
+the SNe occur in a hot dilute medium, as may characterize the CNM.  Hereafter we adopt $\epsilon_{\rm Ia} = 0.4$ as fiducial.
 
@@
 
-Finally, note that our criterion for cooling instability (eq.~[\ref{eq:cooling2}], [\ref{eq:Mdotmax}]) is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
+%Finally, note that our criterion for cooling instability (eq.~[\ref{eq:cooling2}], [\ref{eq:Mdotmax}]) is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
 By re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find that
-\begin{align}
-\label{eq:heatingratioIa}
-&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
-\begin{cases}
-  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
-  \eta_{0.02}^{-2.7} & \text{core}\nonumber\\
-   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
-  \eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
-\end{cases}\\&\simeq
-\begin{cases}
-  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
-  (\tau_{\star}/\th)^{0.5}
- & \text{core}\\
-   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
-  & \text{cusp}\\
-\end{cases}
-\end{align}
-For high mass galaxies and relatively old stellar populations, Ia heating can preventing cooling instabilities on scales of the stagnation radius, i.e.
+%\begin{align}
+%\label{eq:heatingratioIa}
+%&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
+%\begin{cases}
+ % 90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
+  %\eta_{0.02}^{-2.7} & \text{core}\nonumber\\
+   %90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
+  %\eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
+%\end{cases}\\&\simeq
+%\begin{cases}
+ % 90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
+  %(\tau_{\star}/\th)^{0.5}
+ %& \text{core}\\
+  % 90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
+  %& \text{cusp}\\
+%\end{cases}
+%\end{align}
+%For high mass galaxies and relatively old stellar populations, Ia heating can preventing cooling instabilities on scales of the stagnation radius, i.e.
 $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{\rIa} \gtrsim 10$.
@@
 \end{align}
-where $\dot{M}_{\bullet}$ is the BH accretion.
+where $\dot{M}_{\bullet}$ is the BH accretion (we use a more general parametrization of the \citet{Sharma+2007} results in our numerical results presented later).
 In general $\dot{M}_{\bullet}$ will be smaller than the inflow rate $\dot{M}$ calculated thus far by a factor $\alpha < 1$ due to outflows from the accretion disk on small scales.
-Thus, the full efficiency relating the mass inflow rate to the radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following \citet{Li+2013}, who find that the fraction of the inflowing matter lost to outflows equals the effective Shakura-Sunyaev viscosity parameter of the disk.
+Thus, the full efficiency relating the mass inflow rate to the radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following \citet{Li+2013}, who find that the fraction of the inflowing matter lost to outflows equals the Shakura-Sunyaev viscosity parameter of the disk.
+
 Substituting $\epsilon$ into equation (\ref{eq:MdotCa}) and solving for the accretion rate results in
@@
   from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
-  stagnation radius as a function of $\Mbh$ (green), and the ratio of $\zeta/\zeta_{c}$ (blue), where $\zeta_c$ (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are impossible.
+  stagnation radius as a function of $\Mbh$ (green), and the ratio of $\zeta/\zeta_{c}$ (purple), where $\zeta_c$ (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are impossible.
 The latter quantity is evalulated using mean scaling relations for $r_b$, $\rinf$, and $\Gamma$ from the \citet{LauerFaber+:2007a} galaxy sample.}
@@
 respectively, which also make use of $\eta(\tau_{\star})$ as set by stellar winds.\footnote{Both $v_{\rm w}^{\rm C}$ and
-$v_{\rm w}^{\rm Ia}$ depend on the total heating rate
+$v_{\rm w}^{\rm Ia}$ (through $r_{\rm s}/r_{\rm Ia}$) depend on the total heating rate
 (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series
@@
 flow given its inability to respond instantaneously to local changes
-in gas properties.
-Thermally unstable flow is present throughout the single starburst case except at very early times, $\tau_{\star} \lesssim 10^7$ yr, in the low $M_{\bullet}$ case and at late times $\tau_{\star}
+in gas properties.  Thermally unstable flow is present throughout the single starburst case except at very early times, $\tau_{\star} \lesssim 10^7$ yr and at late times $\tau_{\star}
 \gtrsim 10^{9}$ yr in the high $M_{\bullet}$ case.
@@
 heating rates for all but the most massive galaxies (where Ia
-explosions dominate) will fall by a factor $\approx 4$ from our
+explosions dominate) will fall by a factor $\gtrsim 4$ from our
 fiducial volumetric averages, calculated using SFHs from \citet{MosterNaab+:2013a}.
@@
 These fall below the maximum thermally stable accretion rate,
-$\dot{M}_{\rm TI}$ (yellow lines).
+$\dot{M}_{\rm TI}$ (yellow lines), except possibly for high mass core galaxies.
 % , although they become closer at the highest
@@
 eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
-otherwise thermally-unstable flow at smaller radii (eq.~[\ref{eq:heatingratioIa}]).  For higher
+otherwise thermally-unstable flow at smaller radii.  For higher
 $M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
@@
 for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of
-black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of the inflowing matter loss to outflows from the accretion disk, $\epsilon_{\rm rad}$ is the radiative efficiency of the accreted matter, and $\epsilon_{\rm bol} \sim 0.1$ is the bolometric correction into the measured X-ray band
+black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of the inflowing matter loss to outflows from the accretion disk, $\epsilon_{\rm rad}$ is the radiative efficiency of the accreted matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric correction into the measured X-ray band
 for low luminosity AGN (\citealt{Ho08}).  In all cases the value of $\langle L_X
@@
 the luminosity of the accretion flow close to the black hole in a
-single waveband based on the feeding rate on larger scales.  If disk
+single waveband based on the feeding rate on larger scales.  Also, if disk
 outflows indeed carry away most of the infalling mass before it reaches X-ray
@@
 also influence the X-ray luminosity indirectly through the inflow efficiency $\alpha$, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.
+However, in general the efficiency with which inflowing matter reaches the SMBH (and hence X-ray luminosity) would naively be expected to {\it decrease} with decreasing $M_{\bullet}$ due to the increasing angular momentum of low mass galaxies, exacerbating the tension between our findings and the observed downsizing trend.
 
@@
 scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
-  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at least
-three effects: (1) intrinsic scatter in the scaling relationships
-($\Mbh-\sigma$ and $\Mbh-L_{\rm bulge}$) used to measure $\Mbh$; (2)
-the strong sensitivity of the accretion rate to the stellar wind
+  edd}$ at fixed $M_{\bullet}$.  Scatter could result from the strong sensitivity of the accretion rate to the stellar wind
 velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
@@
 \ref{fig:NickPlot2}), this can lead to order of magnitude differences
-in $\dot{M}$; (3) differences in
-angular momentum of the infalling gas from galaxy to galaxy, resulting
-in differences in the fraction of the gas lost to outflows.  Also
-potentially contributing is the order of magnitude difference, at
+in $\dot{M}$.
+However, we note that $v_w$ is not expected to vary by more than a factor of a few for a thermally-stable flow, limiting the allowed variation of  $\dot{M}/\dot{M}_{\rm edd}$.
+Variations in $L_{X}/L_{\rm
+  edd}$ could also result from differences in angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows.
+Also potentially contributing is the order of magnitude difference, at
 fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp
@@
 Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
-  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates
-that even if Compton heating could act to stabilize the flow in a
-quasi-steady state, the magnitude of Compton heating is not sufficient to produce a thermally stable accretion rate, at least for conditions corresponding to the average SFH.
+  C} > \dot{M}_{\rm TI}$ across all black hole masses.
+This indicates that Compton heating is not sufficient to produce a thermally stable accretion rate, at least for conditions corresponding to the average SFH.
 
@@
 hierarchical growth of structure or thermal instabilities on larger,
-galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In
-support of this, \citet{Kauffmann&Heckman09} find that the growth of
-low mass black holes is dominated by young stellar bulges which have a
-log normal distribution of Eddington ratios peaked at
-$\Mdot/\dot{M}_{\rm edd} \sim 0.01$. That this distribution is
-insensitive to galaxy properties suggests that it is set by SMBH
-feedback instead of the nuclear gas supply.
+galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  
+%In
+%support of this, \citet{Kauffmann&Heckman09} find that the growth of
+%low mass black holes is dominated by young stellar bulges which have a
+%log normal distribution of Eddington ratios peaked at
+%$\Mdot/\dot{M}_{\rm edd} \sim 0.01$.
 
@@
   for the average SFH, but it can be significant in the case of an impulsive
-  star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in principle
-  Compton heating is sufficiently high to prevent thermal
-  instabilities when acting alone, i.e. $\dot{M}_{C} \lesssim
-  \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not
+  star burst (Fig.~\ref{fig:vwSourcesImp}).  However, SMBH feedback may not
   be capable of truly stabilizing the flow given its inability
@@
   in nuclear X-ray luminosities at fixed $\Mbh$ (2-4 orders of
-  magnitude) due to the combination of (1) intrinsic scatter in the SMBH
-  scaling relations; (2) stochastic variation in SFH between galaxies, or within one galaxy due to burstiness in the SFH, as in ~Fig.~\ref{fig:NickPlot2}; (3) Variations in the amount of
-  inflowing mass which is lost to small scale outflows from the SMBH
-  accretion disk, likely due to variations in the angular momentum of the
-  accreting gas (e.g.~\citealt{Li+13}).
+  magnitude) due to the combination of (1) differences in the stellar wind heating rate due to stochastic variation in SFH between galaxies, or within one galaxy due to burstiness in the SFH, as in ~Fig.~\ref{fig:NickPlot2}; (2) Variations in the amount of
+  inflowing mass which is lost to small scale outflows from the SMBH accretion disk, likely due to variations in the angular momentum of the accreting gas (cf.~\citealt{Pellegrini10}).
 

### 2015-04-29 ms.tex
Eddington accretion rate.

@@
 \end{eqnarray}
-where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
+where $\dot{M}_{\rm edd} = 2.2M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
 Eddington accretion rate, assuming a radiative efficiency of ten per

### 2015-04-29 ms.tex
going back to old TI prescription.

@@
   \citet{Stone&Metzger15}, although we note that this relation has
-  significant scatter.},
+  significant scatter. Also, we note that scaling is somewhat
+  different for cores and cusps. Fixing the power law slope,
+  $\rinf\simeq 25 (8) \Mbheight^{0.6}$ for core (cusp)
+  galaxies. Unless otherwise notes we will use the single relation in
+  equation~\eqref{eq:rsoi}},
 \begin{equation}
@@
 cent.  Note the sensitive dependence of the accretion rate on the wind
-heating rate.
-As will be discussed later, equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on relatively large scales and does not include outflows from the SMBH accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), which may significantly reduce the fraction of $\dot{M}$ that actually reaches the SMBH.
+heating rate.  As will be discussed later,
+equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on
+relatively large scales and does not include outflows from the SMBH
+accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}),
+which may significantly reduce the fraction of $\dot{M}$ that actually
+reaches the SMBH.
 
@@
     influence radius, for different values of the mass loss parameter
-    $\eta$ as marked.  Blue lines show the minimum heating
-    parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
+    $\eta$ as marked.  Blue lines show the minimum heating parameter
+    required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
       inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for
-    cusp (solid) and core (dashed) galaxies, using the mean
-    $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the
-    \citet{LauerFaber+:2007a} galaxy sample for cores and assuming a fixed value of $r_{b} = 100$ pc for cusps.  For $\zeta < \zeta_c$
-    the stagnation radius moves from inside the influence radius, out
-    to the stellar break radius $r_b$ (Appendix \ref{app:be}); in
-    practice renders the flow susceptible to thermal runaway, even if
-    $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w > v_{\rm TI}$ is
-    usually the more strigent criterion for stability, while for core
-    galaxies the $\zeta > \zeta_c$ is usually more relevant.  }
+    cusp (solid) and core (dashed) galaxies. Based on the
+    \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
+    pc$ and $\rb=106 \Mbheight^{0.4}$ (100 pc)  for cores (cusps). For
+    $\zeta < \zeta_c$ the stagnation radius moves from inside the
+    influence radius, out to the stellar break radius $r_b$ (Appendix
+    \ref{app:be}); in practice renders the flow susceptible to thermal
+    runaway, even if $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w
+    > v_{\rm TI}$ is usually the more strigent criterion for
+    stability, while for core galaxies the $\zeta > \zeta_c$ is
+    usually more relevant.}
 \label{fig:TI}
@@
 \end{align}
-Equations (\ref{eq:cooling2}) and (\ref{eq:cooling3}) are derived using expressions for the stagnation radius and gas density in the high heating limit of $\zeta > \zeta_c = (r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]).
-However, for $\zeta < \zeta_c$, the stagnation radius diverges to the break radius $r_b$ (Appendix \ref{app:be}).
-The quasi-hydrostatic structure that results in this case greatly increases the gas density, which in practice renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$ according to equation (\ref{eq:cooling3}).
-In other words, the true condition for thermal instability  can be written
-\be
-v_w > {\rm max}[v_{\rm TI},\sigma_0\{1-(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}\}]
-\ee
-
-Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass input parameters $\eta$, as well as the [$\eta$-independent] $\zeta > \zeta_c$ criterion, shown separately for cusp and core galaxies.
-For core galaxies, we calculate $\zeta_c$ using the empirical relation, $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$, which
-follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
-correlation derived from the results of \citet{LauerFaber+:2007a}.
-For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$ criterion is generally more strigent, while for core galaxies the $\zeta > \zeta_c$ criterion is more strigent for core galaxies, except for high mass loss rates $\eta > 1$.
-
-The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to {\it maximum} thermally-stable accretion rate,
+Equations (\ref{eq:cooling2}) and (\ref{eq:cooling3}) are derived
+using expressions for the stagnation radius and gas density in the
+high heating limit of $\zeta > \zeta_c = (r_{b}/r_{\rm
+  inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]).  However, for
+$\zeta < \zeta_c$, the stagnation radius diverges to the break radius
+$r_b$ (Appendix \ref{app:be}).  The quasi-hydrostatic structure that
+results in this case greatly increases the gas density, which in
+practice renders the flow susceptible to thermal runaway, even if
+$v_{w} > v_{\rm TI}$ according to equation (\ref{eq:cooling3}).  In
+other words, the true condition for thermal instability  can be
+written
+
+\begin{equation}
+v_w > {\rm max}[v_{\rm TI},\sigma_0\{1-(r_{b}/r_{\rm
+  inf})^{0.5(1-\Gamma)}\}]
+\label{eq:cooling4}
+\end{equation}
+
+Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass
+input parameters $\eta$, as well as the [$\eta$-independent] $\zeta >
+\zeta_c$ criterion, shown separately for cusp and core galaxies.
+Based on the \citet{LauerFaber+:2007a} sample we take $\rinf = 25(8)M
+0.6$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
+$\rb/\rinf\simeq 4 \Mbheight^{-0.2} (13 \Mbheight^{-0.6})$ for cores
+(cusps).  For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$
+criterion is generally more stringent, while for core galaxies the
+$\zeta > \zeta_c$ criterion is more strigent for core galaxies, except
+for high mass loss rates $\eta > 1$.
+
+The minimum heating rate for thermal stability corresponds to {\it
+  maximum} thermally-stable accretion rate. Due to the large scatter
+in galaxy structural parameters at a given $\Mbh$, we use
+equation~\eqref{eq:cooling3} instead of equation~\eqref{eq:cooling4}:
+the $\zeta_c$ criterion should be evaluated on a galaxy-by-galaxy
+basis. Thus, the maximum thermally stable $\Mdot$ (for
+$\zeta>\zeta_c$) is
+
 \begin{align}
   \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq \begin{cases}
-    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \\
+    2\times 10^{-4}\eta_{0.02}^{0.47}M_{\bullet,8}^{0.36} &, \text{core}, \\
     8\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp},\\
@@
 \end{align}
-where the cusp case is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and the core case corresponds to the more stringent $\zeta > \zeta_c$ criterion, calculated again using the mean $r_{b}/r_{\rm inf}$ relation from \citet{LauerFaber+:2007a}.
-
-What we describe above as ``thermal instability" may in practice simply indicate an abruption transition from a steady inflow-outflow solution to a global cooling flow, as opposed a true thermal instability.
-In the former case the stagnation radius diverges to large radii, increasing the density in the inner parts of the flow, which increases cooling and creates a large inflow of cold gas towards the nucleus.
-A true thermal instability would likely result in a portion of the hot ISM condensing into cold clouds, a situation which may or may not be present in a cooling flow.
-In this paper we do not distinguish between these possibilities, although both are likely present at some level.
-Finally, note that if the CNM were to ``regulate" itself to a state of local marginal thermal instability (as has previously been invoked on cluster scales; e.g., \citealt{Voit+15}), then equation (\ref{eq:Mdotmax}) might naturally reflect the characteristic mass fall-out rate and concomitant star formation rate.
+where the cusp case is derived using equation (\ref{eq:eddr_analytic})
+to calculate $\dot{M}(v_{\rm TI})$, and the core case corresponds to
+the more stringent $\zeta > \zeta_c$ criterion, calculated again using
+the mean $r_{b}/r_{\rm inf}$ relation from \citet{LauerFaber+:2007a}.
+
+What we describe above as ``thermal instability" may in practice
+simply indicate an abruption transition from a steady inflow-outflow
+solution to a global cooling flow, as opposed a true thermal
+instability.  In the former case the stagnation radius diverges to
+large radii, increasing the density in the inner parts of the flow,
+which increases cooling and creates a large inflow of cold gas towards
+the nucleus.  A true thermal instability would likely result in a
+portion of the hot ISM condensing into cold clouds, a situation which
+may or may not be present in a cooling flow.  In this paper we do not
+distinguish between these possibilities, although both are likely
+present at some level.  Finally, note that if the CNM were to
+``regulate" itself to a state of local marginal thermal instability
+(as has previously been invoked on cluster scales; e.g.,
+\citealt{Voit+15}), then equation (\ref{eq:Mdotmax}) might naturally
+reflect the characteristic mass fall-out rate and concomitant star
+formation rate.
 
@@
 
-Even if SN Ia are rare near the stagnation radius, they may cap the SMBH accretion rate by periodically blowing gas out of the nucleus of low mass galaxies.
-Between successive SNe, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
+Even if SN Ia are rare near the stagnation radius, they may cap the
+SMBH accretion rate by periodically blowing gas out of the nucleus of
+low mass galaxies.  Between successive SNe, stars release a gaseous
+mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
 interior to the Ia radius, which is locally gravitationally bound to
-the SMBH by an energy $E_{\rm bind} \gtrsim M_{\rm
-  g}\sigma_0^{2}$.  From the above definitions it follows that
- \be
-\frac{E_{\rm Ia}}{E_{\rm bind}} \lesssim \frac{(v_{w}^{\rm
+the SMBH by an energy $E_{\rm bind} \gtrsim M_{\rm g}\sigma_0^{2}$.
+From the above definitions it follows that \be \frac{E_{\rm
+    Ia}}{E_{\rm bind}} \lesssim \frac{(v_{w}^{\rm
     Ia})^{2}}{2\sigma_0^{2}}.
@@
 \subsection{Millisecond Pulsars}
- Energy injection from the magnetic braking of millisecond pulsars (MSPs) is a potentially
-important heating source.  If the number of MSPs per unit stellar mass
-is $n_{\rm msp}$ and each contributes on average a spin-down
-luminosity $\bar{L}_{\rm sd}$, then the resulting heating per unit
-volume $\dot{e} \approx \bar{L}_{\rm sd}n_{\rm msp}\epsilon_{\rm msp}$ results in an
-effective heating rate (eq.~ [\ref{eq:vw_eff}]) of 
+Energy injection from the magnetic braking of millisecond pulsars
+(MSPs) is a potentially important heating source.  If the number of
+MSPs per unit stellar mass is $n_{\rm msp}$ and each contributes on
+average a spin-down luminosity $\bar{L}_{\rm sd}$, then the resulting
+heating per unit volume $\dot{e} \approx \bar{L}_{\rm sd}n_{\rm
+  msp}\epsilon_{\rm msp}$ results in an effective heating rate (eq.~
+[\ref{eq:vw_eff}]) of
 \begin{eqnarray} v_{w}^{\rm MSP} \sim
@@
   \end{eqnarray} 
-where $\epsilon_{\rm msp}$ is the thermalization efficiency of
-the wind, normalized to a value $\lesssim 0.1$ based on that inferred by modeling the interstellar media of globular clusters
-\citep{NaimanSoares-Furtado+:2013a}.  Our numerical estimate assumes a
-pulsar density $n_{\rm msp} \sim 3 \times 10^{-40} $ MSPs g$^{-1}$, calculated from the estimated $\sim 30,000$ MSPs in the Milky Way (\citealt{Lorimer13}) of stellar mass $\approx 6\times 10^{10}M_{\odot}$.
-
-Based on the ATNF radio pulsar catalog (\citealt{Manchester+05}), we estimate the average spin-down luminosity of millisecond pulsars in the field to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$, resulting in $v_{w}^{\rm MSP} \lesssim 30$ km s$^{-1}$ for $\eta \gtrsim 0.02$.
-For higher spin-down
-luminosities, $L_{\rm sd}\simeq 10^{35}$ ergs s$^{-1}$ characteristic
-of some Fermi-detected pulsars, then the higher value of $v_{w}^{\rm MSP}
-\lesssim 300$ km s$^{-1}$ makes MSP heating in principle important
-under the most optimistic assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
+  where $\epsilon_{\rm msp}$ is the thermalization efficiency of the
+  wind, normalized to a value $\lesssim 0.1$ based on that inferred by
+  modeling the interstellar media of globular clusters
+  \citep{NaimanSoares-Furtado+:2013a}.  Our numerical estimate assumes
+  a pulsar density $n_{\rm msp} \sim 3 \times 10^{-40} $ MSPs
+  g$^{-1}$, calculated from the estimated $\sim 30,000$ MSPs in the
+  Milky Way (\citealt{Lorimer13}) of stellar mass $\approx 6\times
+  10^{10}M_{\odot}$.
+
+  Based on the ATNF radio pulsar catalog (\citealt{Manchester+05}), we
+  estimate the average spin-down luminosity of millisecond pulsars in
+  the field to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg s$^{-1}$,
+  resulting in $v_{w}^{\rm MSP} \lesssim 30$ km s$^{-1}$ for $\eta
+  \gtrsim 0.02$.  For higher spin-down luminosities, $L_{\rm sd}\simeq
+  10^{35}$ ergs s$^{-1}$ characteristic of some Fermi-detected
+  pulsars, then the higher value of $v_{w}^{\rm MSP} \lesssim 300$ km
+  s$^{-1}$ makes MSP heating in principle important under the most
+  optimistic assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
 %  On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
@@
 
-The importance of Compton heating can be estimated by assuming the SMBH
-radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
+The importance of Compton heating can be estimated by assuming the
+SMBH radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
 $\epsilon$ is the radiative efficiency and where $\dot{M}$ is
@@
 (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate from equation
-(\ref{eq:vw_eff}) that the effective heating rate at the stagnation radius is given by
+(\ref{eq:vw_eff}) that the effective heating rate at the stagnation
+radius is given by
 \begin{align} v_{w}^{\rm C} \simeq
@@
 
-The accretion rate corresponding to a state in which Compton heating self-regulates the accretion flow is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
+The accretion rate corresponding to a state in which Compton heating
+self-regulates the accretion flow is given by substituting equation
+(\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
 \begin{align}
@@
 
-\citet{Sharma+2007} estimate the value of the radiative efficiency of low luminosity AGN, $\epsilon_{\rm rad}$,
-based on MHD shearing box simulations of collisionless plasmas.  For Eddington ratios of relevance, their results (shown in their Fig.~6) are well approximated by
+\citet{Sharma+2007} estimate the value of the radiative efficiency of
+low luminosity AGN, $\epsilon_{\rm rad}$, based on MHD shearing box
+simulations of collisionless plasmas.  For Eddington ratios of
+relevance, their results (shown in their Fig.~6) are well approximated
+by
 \begin{align}
@@
 \end{align}
-where $\dot{M}_{\bullet}$ is the BH accretion (we use a more general parametrization of the \citet{Sharma+2007} results in our numerical results presented later).
-In general $\dot{M}_{\bullet}$ will be smaller than the inflow rate $\dot{M}$ calculated thus far by a factor $\alpha < 1$ due to outflows from the accretion disk on small scales.
-Thus, the full efficiency relating the mass inflow rate to the radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following \citet{Li+2013}, who find that the fraction of the inflowing matter lost to outflows equals the Shakura-Sunyaev viscosity parameter of the disk.
+where $\dot{M}_{\bullet}$ is the BH accretion (we use a more general
+parametrization of the \citet{Sharma+2007} results in our numerical
+results presented later).  In general $\dot{M}_{\bullet}$ will be
+smaller than the inflow rate $\dot{M}$ calculated thus far by a factor
+$\alpha < 1$ due to outflows from the accretion disk on small scales.
+Thus, the full efficiency relating the mass inflow rate to the
+radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we
+take $\alpha = 0.1$ following \citet{Li+2013}, who find that the
+fraction of the inflowing matter lost to outflows equals the
+Shakura-Sunyaev viscosity parameter of the disk.
 
@@
   from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
-  stagnation radius as a function of $\Mbh$ (green), and the ratio of $\zeta/\zeta_{c}$ (purple), where $\zeta_c$ (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are impossible.
-The latter quantity is evalulated using mean scaling relations for $r_b$, $\rinf$, and $\Gamma$ from the \citet{LauerFaber+:2007a} galaxy sample.}
+  stagnation radius as a function of $\Mbh$ (green), and the ratio of
+  $\zeta/\zeta_{c}$ (purple), where $\zeta_c$
+  (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta
+  \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are
+  impossible.  The latter quantity is evalulated using mean scaling
+  relations for $r_b$, $\rinf$, and $\Gamma$ from the
+  \citet{LauerFaber+:2007a} galaxy sample.}
 
@@
 
-Figure~\ref{fig:vwSourcesImp} shows the contributions of heating sources as a function of time $\tau_{\star}$ after a burst of
-star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top) and $\Mbh = 10^{8} \Msun$ (bottom). The heating and mass
-input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$
-and $\eta(\tau_{\star})$, are calculated as described in
-Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The SN Ia and Compton heating rates, $v_{w}^{\rm Ia}$ and $v_{\rm w}^{\rm C}$, are
+Figure~\ref{fig:vwSourcesImp} shows the contributions of heating
+sources as a function of time $\tau_{\star}$ after a burst of star
+formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top) and
+$\Mbh = 10^{8} \Msun$ (bottom). The heating and mass input parameters
+due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and
+$\eta(\tau_{\star})$, are calculated as described in
+Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The SN Ia and
+Compton heating rates, $v_{w}^{\rm Ia}$ and $v_{\rm w}^{\rm C}$, are
 calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC},
-respectively, which also make use of $\eta(\tau_{\star})$ as set by stellar winds.\footnote{Both $v_{\rm w}^{\rm C}$ and
-$v_{\rm w}^{\rm Ia}$ (through $r_{\rm s}/r_{\rm Ia}$) depend on the total heating rate
-(eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series
-of implicit equations to determine each.}  SN Ia heating depends also on a convolution of the DTD (eq.
-[\ref{eq:DTD}]) and the SFH, which reduces to the DTD itself for a single star burst.
-We account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated {\it excluding} Ia heating) exceeds
-the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]).  
-Heating from
-
-Figure \ref{fig:vwSourcesImp} shows that stellar winds are the most important heating source at early times, $\tau_{\star} \lesssim 10^{7}$ years.
-Compton heating becomes more important at later times due to (1) the higher accretion rates that accompany the overall decrease in all sources of heating, coupled with (2) the persistently high mass loss rates and gas densities associated with the still relatively young stellar population.
-Interestingly, for $M_{\bullet} = 10^{6}M_{\odot}$, SN Ia dominate the heating briefly around 10$^{9}$ yr due to a window of time in which $r_{\rm Ia} < \rs$.
-For high-mass black holes (Fig.~\ref{fig:vwSourcesImp}, bottom panel), SN Ia dominate at all times after $10^{7}$ yr.
+respectively, which also make use of $\eta(\tau_{\star})$ as set by
+stellar winds.\footnote{Both $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm
+    Ia}$ (through $r_{\rm s}/r_{\rm Ia}$) depend on the total heating
+  rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a
+  series of implicit equations to determine each.}  SN Ia heating
+depends also on a convolution of the DTD (eq. [\ref{eq:DTD}]) and the
+SFH, which reduces to the DTD itself for a single star burst.  We
+account for the expected suppression of SN Ia heating resulting from
+its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the
+stagnation radius (calculated {\it excluding} Ia heating) exceeds the
+Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]).  Heating from
+
+Figure \ref{fig:vwSourcesImp} shows that stellar winds are the most
+important heating source at early times, $\tau_{\star} \lesssim
+10^{7}$ years.  Compton heating becomes more important at later times
+due to (1) the higher accretion rates that accompany the overall
+decrease in all sources of heating, coupled with (2) the persistently
+high mass loss rates and gas densities associated with the still
+relatively young stellar population.  Interestingly, for $M_{\bullet}
+= 10^{6}M_{\odot}$, SN Ia dominate the heating briefly around 10$^{9}$
+yr due to a window of time in which $r_{\rm Ia} < \rs$.  For high-mass
+black holes (Fig.~\ref{fig:vwSourcesImp}, bottom panel), SN Ia
+dominate at all times after $10^{7}$ yr.
 
@@
 
-Strikingly, we find that galactic nuclei that experience the same average SFH as
-their host galaxies possess thermally stable flows across all
-black hole masses.  An important caveat, however, is that $\vw$ is generally only a few times higher than the stellar velocity dispersion, i.e. $\zeta \sim \zeta_c$
-(eq.~[\ref{eq:zetacrit}]).
-This implies that the true stagnation radius and SMBH accretion rate could be larger than our analytic estimates, potentially resulting in thermal instability in a significant fraction of galaxies.
-The bottom panel of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where $\zeta_c$ is estimated from the best-fit power-law dependence of $r_b$, $\rinf$, and $\Gamma$ on $M_{\bullet}$ from the \citet{LauerFaber+:2007a} galaxy sample.
-In other words, the CNM of a significant fraction of massive ellipticals may be thermally unstable, not necessarily because they are receiving lower stellar feedback than the average for their galaxy mass, but due to the high heating required for stability given the structure of their stellar potential.
+Strikingly, we find that galactic nuclei that experience the same
+average SFH as their host galaxies possess thermally stable flows
+across all black hole masses.  An important caveat, however, is that
+$\vw$ is generally only a few times higher than the stellar velocity
+dispersion, i.e. $\zeta \sim \zeta_c$ (eq.~[\ref{eq:zetacrit}]).  This
+implies that the true stagnation radius and SMBH accretion rate could
+be larger than our analytic estimates, potentially resulting in
+thermal instability in a significant fraction of galaxies.  The bottom
+panel of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where
+$\zeta_c$ is estimated from the best-fit power-law dependence of
+$r_b$, $\rinf$, and $\Gamma$ on $M_{\bullet}$ from the
+\citet{LauerFaber+:2007a} galaxy sample.  In other words, the CNM of a
+significant fraction of massive ellipticals may be thermally unstable,
+not necessarily because they are receiving lower stellar feedback than
+the average for their galaxy mass, but due to the high heating
+required for stability given the structure of their stellar potential.
 
@@
 \includegraphics[width=\columnwidth]{mdot_sfr.pdf}
-\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate $\dot{M}/\dot{M}_{\rm edd}$ as a
-  function of black hole mass $M_{\bullet}$, shown for core
-  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$, solid).
-  Black lines show the accretion rate calculated from equation
-  (\ref{eq:eddr_analytic}) using the heating rate provided at $z = 0$ by the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).
-Teal lines show the maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).
-Red lines show the accretion rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$ (eq.~[\ref{eq:MdotC}]).
-Yellow lines show the maximum
-  accretion rate for a thermally stable flow near the stagnation radius, $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).
-Also shown are the inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray circles), for
-  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a} (gray
-  triangles).  {\it Bottom panel:} Growth times $t_{\rm grow} \equiv \Mbh/\dot{M}_{\bullet}$ in units of
-  the Hubble time $\th$ for each of the accretion rates shown in the
-  top panel, where $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to account for the fraction of inflowing mass lost to disk outflows on small scales.}
+\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate
+  $\dot{M}/\dot{M}_{\rm edd}$ as a function of black hole mass
+  $M_{\bullet}$, shown for core ($\Gamma=0.1$, dot-dashed) and cusp
+  galaxies ($\Gamma=0.8$, solid).  Black lines show the accretion rate
+  calculated from equation (\ref{eq:eddr_analytic}) using the heating
+  rate provided at $z = 0$ by the average star formation histories for
+  each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the
+  maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$
+  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if
+  Compton heating acts alone, $\dot{M}_{\rm C}$
+  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion
+  rate for a thermally stable flow near the stagnation radius,
+  $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the
+  inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray
+  circles), for NGC3115 from \citet{ShcherbakovWong+:2014a} (gray
+  diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a}
+  (gray triangles).  {\it Bottom panel:} Growth times $t_{\rm grow}
+  \equiv \Mbh/\dot{M}_{\bullet}$ in units of the Hubble time $\th$ for
+  each of the accretion rates shown in the top panel, where
+  $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to
+  account for the fraction of inflowing mass lost to disk outflows on
+  small scales.}
 \end{figure}
@@
 who find a range of accretion rates depending on the assumed model for
-thermal conductivity\footnote{We expect this range would be have been smaller
-had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux.}.  The SgrA* rate
-exceeds our estimate of $\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost two orders of magnitude.
-This discrepancy can in part be understood by the fact that star formation in
-the central parsec of the Milky Way cannot be described as
-steady-state: feedback is instead dominated by the stellar winds from
-the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and
-estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).  Such a star
-formation history is better described by our impulsive (starburst) scenario,
-for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
+thermal conductivity\footnote{We expect this range would be have been
+  smaller had \citet{ShcherbakovWong+:2014a} included saturation of
+  the conductive flux.}.  The SgrA* rate exceeds our estimate of
+$\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost
+two orders of magnitude.  This discrepancy can in part be understood
+by the fact that star formation in the central parsec of the Milky Way
+cannot be described as steady-state: feedback is instead dominated by
+the stellar winds from the ring of young massive stars of mass $\sim
+10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g.,
+\citealt{Schodel+07}).  Such a star formation history is better
+described by our impulsive (starburst) scenario, for which the value
+of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
 (Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
@@
 
-The unresolved core X-ray luminosities of nearby galactic nuclei provide a
-powerful diagnostic of the SMBH accretion rates and how they vary with
-SMBH mass and other galaxy properties (e.g., \citealt{Ho08} and
-references therein).  Figure~\ref{fig:miller} shows our predictions
-for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a function of
-black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of the inflowing matter loss to outflows from the accretion disk, $\epsilon_{\rm rad}$ is the radiative efficiency of the accreted matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric correction into the measured X-ray band
-for low luminosity AGN (\citealt{Ho08}).  In all cases the value of $\langle L_X
-\rangle$ is calculated using the average accretion rate for galaxies with
-core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
-profiles, using the mean power-law relationship $\Gamma = 0.3 \Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a} galaxy sample.
+The unresolved core X-ray luminosities of nearby galactic nuclei
+provide a powerful diagnostic of the SMBH accretion rates and how they
+vary with SMBH mass and other galaxy properties (e.g., \citealt{Ho08}
+and references therein).  Figure~\ref{fig:miller} shows our
+predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a
+function of black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm
+  rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of
+the inflowing matter loss to outflows from the accretion disk,
+$\epsilon_{\rm rad}$ is the radiative efficiency of the accreted
+matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric
+correction into the measured X-ray band for low luminosity AGN
+(\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
+calculated using the average accretion rate for galaxies with core
+($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles,
+using the mean power-law relationship $\Gamma = 0.3
+\Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a}
+galaxy sample.
 
@@
   (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
-  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived from the
-  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
-  measurements ({\it black stars}) and upper limits ({\it gray
+  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived
+  from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are
+  the measurements ({\it black stars}) and upper limits ({\it gray
     triangles}) for $L_X/L_{\rm edd}$ values, from the
@@
   $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
-  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency of low luminosity accretion disks calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.
-Shown
-  for comparison are the X-ray luminosities calculated for the maximum
+  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm
+    rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency of
+  low luminosity accretion disks calculated by \citet{Sharma+2007}
+  (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of
+  the mass inflowing on large scales that reaches the SMBH.  Shown for
+  comparison are the X-ray luminosities calculated for the maximum
   thermally-stable accretion rate ({\it dashed orange line};

### 2015-04-29 ms.tex
this and that

@@
   \citet{Stone&Metzger15}, although we note that this relation has
-  significant scatter. Also, we note that scaling is somewhat
+  significant scatter. Also, we note that the  scaling is somewhat
   different for cores and cusps. Fixing the power law slope,
   $\rinf\simeq 25 (8) \Mbheight^{0.6}$ for core (cusp)
-  galaxies. Unless otherwise notes we will use the single relation in
+  galaxies. Unless otherwise noted we will use the single relation in
   equation~\eqref{eq:rsoi}},
@@
     \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
-    pc$ and $\rb=106 \Mbheight^{0.4}$ (100 pc)  for cores (cusps). For
+    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc)  for cores (cusps). For
     $\zeta < \zeta_c$ the stagnation radius moves from inside the
@@
 These fall below the maximum thermally stable accretion rate,
-$\dot{M}_{\rm TI}$ (yellow lines), except possibly for high mass core galaxies.
+$\dot{M}_{\rm TI}$ (yellow lines), although in practice high mass core
+galaxies may be thermally unstable as we do not include the
+$\zeta<\zeta_c$ criterion in Fig.~\ref{fig:mdot_mass} (see
+equation~\eqref{eq:cooling4}).
 % , although they become closer at the highest
@@
 bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and yellow lines mean at high $M_{\bullet}$.
-
-% For these highest mass black holes, the maximum accretion rate as
-% set by the SN Ia radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could
-% instead cap the accretion rate close to the thermally-unstable value
-% (see discussion following eq.~[\ref{eq:eddr_Ia}]).  For lower mass
-% black holes, the maximum accretion rate set by SNe Ia is
-% significantly higher and cannot also prevent the development of
-% thermally unstable flows, i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm
-% TI}$.
 

### 2015-04-29 ms.tex
beta footnote

@@
 
-We fix $\beta = 2$ but find that our results are not overly sensitive to
-the properties of the gas flow on radial scales $\gtrsim r_b$ for values of
-$\beta\gsim 1.5$, which characterize most of the \citet{LauerFaber+:2007a} sample.  The
-presence of the break radius $r_{b}$ is, however, necessary to obtain
-a converged steady state for some regions of our parameter space.  We
-consider solutions calculated for up to four values of $\rb$: 50 pc,
-100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
-the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
-  the break radius follows the scaling relationship $\rb\sim 106 \,
-  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
-  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
-  clear trend with $\Mbh$.}  We neglect values of $r_b$ which would
-give unphysically large bulges for a given $\Mbh$.
+We fix $\beta = 2$ but find that our results are not overly sensitive
+to the properties of the gas flow on radial scales $\gtrsim r_b$ for
+values of $\beta\gsim 1.5$, which characterize most of the
+\citet{LauerFaber+:2007a} sample\footnote{The median $\beta$ in the
+  \citet{LauerFaber+:2007a} sample is 1.39 (1.64) for core (cusp)
+  galaxies}.  The presence of the break radius $r_{b}$ is, however,
+necessary to obtain a converged steady state for some regions of our
+parameter space.  We consider solutions calculated for up to four
+values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
+range of break radii from the \citet{LauerFaber+:2007a}
+sample.\footnote{For the core galaxies the break radius follows the
+  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
+  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
+  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  We
+neglect values of $r_b$ which would give unphysically large bulges for
+a given $\Mbh$.
 % In practice we calculate solutions for a

### 2015-04-29 ms.tex
zeta_c line just for core galaxies.

@@
 a given $\Mbh$.
-% In practice we calculate solutions for a
-%range of $\rb$ only in cases when its precise value is expected to
-%have a significant affect on the solution, in particular for high SMBH
-%masses and low heating rates, for which the stagnation radius
-%approaches large radii. 
-%We also neglect values of $r_b$ which would
-%give unphysically large bulges for a given $\Mbh$.
-
-Finally, we note that \citealt{LauerFaber+:2005a} find that $\sim 60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have (generally unresolved) emission in excess of the inward extrapolation of the Nuker law.
-Indeed, some low mass galaxies with $\Mbh\lsim 10^{8} \Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}), which are not accounted for by our simple parametrization of the stellar density.
-In such cases gas and energy injection could be dominated by the cluster itself, i.e.
-concentrated within its own pc-scale ``break radius" which is much smaller than the outer break in the older stellar population on much larger scales.
-Although our analysis does not account for such an inner break, we note that for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the break radius.
+
+Finally, we note that \citealt{LauerFaber+:2005a} find that $\sim
+60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have (generally
+unresolved) emission in excess of the inward extrapolation of the
+Nuker law.  Indeed, some low mass galaxies with $\Mbh\lsim 10^{8}
+\Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}),
+which are not accounted for by our simple parametrization of the
+stellar density.  In such cases gas and energy injection could be
+dominated by the cluster itself, i.e. concentrated within its own
+pc-scale ``break radius" which is much smaller than the outer break in
+the older stellar population on much larger scales.  Although our
+analysis does not account for such an inner break, we note that for
+high heating rates the stagnation radius and concomitant accretion
+rate are not sensitive to the break radius.
 

### 2015-04-29 ms.tex
strategic clear page.

@@
   \caption{\label{fig:profiles}Radial profiles of the CNM density
-    ({\it top}), temperature ({\it middle}), and velocity ({\it bottom}),
-    calculated for a representative sample of galaxies.  Colors
-    denote values of the effective wind heating rate,
+    ({\it top}), temperature ({\it middle}), and velocity ({\it
+      bottom}), calculated for a representative sample of galaxies.
+    Colors denote values of the effective wind heating rate,
     $\vwO=1200$ km s$^{-1}$ ({\it blue}), 600 km s$^{-1}$ ({\it
-      orange}), and 300 km s$^{-1}$ ({\it green}).  Line styles denote different black hole masses: $\Mbh=10^6
-    \Msun$ ({\it dot-dashed}), $10^7 \Msun$ ({\it solid}), and
-    $10^8 \Msun$ ({\it dashed}). Thin and thick lines denote cusp galaxies ($\Gamma$=0.8) and core galaxies ($\Gamma$=0.1), respectively.  Squares mark the locations of the stagnation radius.
- }
+      orange}), and 300 km s$^{-1}$ ({\it green}).  Line styles denote
+    different black hole masses: $\Mbh=10^6 \Msun$ ({\it dot-dashed}),
+    $10^7 \Msun$ ({\it solid}), and $10^8 \Msun$ ({\it dashed}). Thin
+    and thick lines denote cusp galaxies ($\Gamma$=0.8) and core
+    galaxies ($\Gamma$=0.1), respectively.  Squares mark the locations
+    of the stagnation radius.  }
 \end{figure}
+
+\clearpage
 
@@
   \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are
-  impossible.  The latter quantity is evalulated using mean scaling
+  impossible.  The latter quantity is calculated for core
+  ($\Gamma=0.1$) galaxies  using mean scaling
   relations for $r_b$, $\rinf$, and $\Gamma$ from the

### 2015-04-30 ms.tex
get of extraneous clear page.
this and that.

@@
   velocity dispersion \\
-$\sigma_0$ & stellar velocity dispersion (assumed to be radially constant)\\
+  $\sigma_{\bullet}$ & The line of sight velocity dispersion from the  $\Mbh-\sigma$ relation (eq.~\eqref{eq:Msigma})\\
+  $\sigma_0$ & stellar velocity dispersion (assumed to be radially
+  constant and equal to $\sqrt{3} \Mbh$).\\
   $\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
@@
 \begin{eqnarray}
-  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta M_{\star}|_{r_{\rm s}}}{\th} \nonumber \\
+  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta
+    M_{\star}|_{r_{\rm s}}}{\th} = \frac{\eta \Mbh (\rs/\rinf)^{2-\Gamma}}{\th} \nonumber \\
   &\approx&
@@
 
-\clearpage
+%\clearpage
 
@@
 \end{align}
-where $\dot{M}_{\bullet}$ is the BH accretion (we use a more general
-parametrization of the \citet{Sharma+2007} results in our numerical
-results presented later).  In general $\dot{M}_{\bullet}$ will be
-smaller than the inflow rate $\dot{M}$ calculated thus far by a factor
-$\alpha < 1$ due to outflows from the accretion disk on small scales.
-Thus, the full efficiency relating the mass inflow rate to the
-radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we
-take $\alpha = 0.1$ following \citet{Li+2013}, who find that the
-fraction of the inflowing matter lost to outflows equals the
-Shakura-Sunyaev viscosity parameter of the disk.
+where $\dot{M}_{\bullet}$ is the BH accretion rate. In general
+$\dot{M}_{\bullet}$ will be smaller than the inflow rate $\dot{M}$
+calculated thus far by a factor $\alpha < 1$ due to outflows from the
+accretion disk on small scales.  Thus, the full efficiency relating
+the mass inflow rate to the radiative output is $\epsilon = \alpha
+\epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following
+\citet{Li+2013}, who find that the fraction of the inflowing matter
+lost to outflows equals the Shakura-Sunyaev viscosity parameter of the
+disk.
 
@@
   each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the
-  maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$
-  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if
-  Compton heating acts alone, $\dot{M}_{\rm C}$
+  maximum accretion set by Ia supernovae blow-out or heating,
+  $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).  Red lines show the accretion
+  rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$
   (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion
@@
 $\dot{M}_{\rm TI}$ (yellow lines), although in practice high mass core
-galaxies may be thermally unstable as we do not include the
-$\zeta<\zeta_c$ criterion in Fig.~\ref{fig:mdot_mass} (see
-equation~\eqref{eq:cooling4}).
-% , although they become closer at the highest
-% black hole masses $\sim 10^{9}M_{\odot}$.
+galaxies may be thermally unstable due to their deep potential wells
+(we do not include the $\zeta<\zeta_c$ criterion in
+Fig.~\ref{fig:mdot_mass}--see equation~\eqref{eq:cooling4} and
+surrounding discussion).
 
@@
 released by a single Ia is insufficient to unbind gas from the stellar
-bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and yellow lines mean at high $M_{\bullet}$.
+bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and teal lines mean at high $M_{\bullet}$.
 
@@
 (\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
-calculated using the average accretion rate for galaxies with core
-($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles,
-using the mean power-law relationship $\Gamma = 0.3
+calculated using the accretion rate from the top line of
+equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.3
 \Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a}
@@
 scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
-  edd}$ at fixed $M_{\bullet}$.  Scatter could result from the strong sensitivity of the accretion rate to the stellar wind
-velocity and mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
+  edd}$ at fixed $M_{\bullet}$.  Scatter could result from the strong
+sensitivity of the accretion rate to the stellar wind velocity and
+mass loss parameter, $\dot{M}/\dot{M}_{\rm edd} \propto
 v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
@@
 \ref{fig:NickPlot2}), this can lead to order of magnitude differences
-in $\dot{M}$.
-However, we note that $v_w$ is not expected to vary by more than a factor of a few for a thermally-stable flow, limiting the allowed variation of  $\dot{M}/\dot{M}_{\rm edd}$.
-Variations in $L_{X}/L_{\rm
-  edd}$ could also result from differences in angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows.
-Also potentially contributing is the order of magnitude difference, at
+in $\dot{M}$.  However, we note that $v_w$ is not expected to vary by
+more than a factor of a few for a thermally-stable flow, limiting the
+allowed variation of $\dot{M}/\dot{M}_{\rm edd}$.  Variations in
+$L_{X}/L_{\rm edd}$ could also result from differences in angular
+momentum of the infalling gas from galaxy to galaxy, resulting in
+differences in the fraction of the gas lost to outflows.  Also
+potentially contributing is the order of magnitude difference, at
 fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp
@@
 gas is supplied exclusively by stellar wind mass loss and heated by
-shocked stellar winds, supernovae and black hole feedback.  We compute
-solutions for a range of different black hole masses, heating rates,
-and observationally-motivated stellar density profiles.  Our numerical
-results (Table \ref{table:models}) are used to verify and calibrate
-analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use
-the latter to explore systematically how the SMBH accretion rate
-varies with black hole mass and the galaxy's SFH.  Our results for
+shocked stellar winds, supernovae and black hole feedback.  We
+numerically compute solutions for a range of different black hole
+masses, heating rates, and observationally-motivated stellar density
+profiles.  Then we use our numerical results (Table
+\ref{table:models}) are used to verify and calibrate analytic
+relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use the
+latter to explore systematically how the SMBH accretion rate varies
+with black hole mass and the galaxy's SFH.  Our results for
 $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray
-luminosities of quiescent SMBHs and low luminosity AGN.  Our conclusions are summarized as follows.
+luminosities of quiescent SMBHs and low luminosity AGN.  Our
+conclusions are summarized as follows.
 
@@
     momentum is also unlikely to invalidate our spherically symmetric
-    model on large scales, given observationally inferred rotation rates of galactic nuclei
-    near the stagnation radius ($\S\ref{sec:rotation}$). 
-%However, on
- %   small scales gas would encounter a centrifugal barrier which would
-  %  cause much of the gas flowing inwards on large scales to be driven
-   % outwards in an outflow (as in \citealt{Li+2013}).
+    model on large scales, given observationally inferred rotation
+    rates of galactic nuclei near the stagnation radius
+    ($\S\ref{sec:rotation}$).
 
   \item Radiative cooling has a more pronounced influence on the flow
-  structure.  Cooling becomes important when the
-  radiative cooling rate exceeds the gas heating rate near the
-  stagnation radius, where the gas is in nearly hydrostatic equilibrium (Fig.~\ref{fig:TI}).  This condition is approximately equivalent to
-  the $t_{\rm cool} \gg t_{\rm ff}$ criterion for thermal instability advocated by
-  \citet{McCourt+12} and \citet{Li&Bryan14a}.
-The transition in the flow properties that occurs as heating is reduced may represent a true ``thermal instability" (hot ISM condensing into a cooler clouds), or it may simply represent an abruption transition from a steady inflow-outflow solution to a global cooling flow.
-We leave distinguishing between these possibilities to future work.
+    structure when the radiative cooling rate exceeds the gas heating
+    rate near the stagnation radius, where the gas is in nearly
+    hydrostatic equilibrium (Fig.~\ref{fig:TI}).  This condition is
+    approximately equivalent to the $t_{\rm cool} \gg t_{\rm ff}$
+    criterion for thermal instability advocated by \citet{McCourt+12}
+    and \citet{Li&Bryan14a}.  The transition in the flow properties
+    that occurs as heating is reduced may represent a true ``thermal
+    instability" (hot ISM condensing into a cooler clouds), or it may
+    simply represent an abrupt transition from a steady inflow-outflow
+    solution to a global cooling flow.  We leave distinguishing
+    between these possibilities to future work.
 
@@
     accretion rate, is a sensitive function of the gas heating rate
-  $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$, implying
-  that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core (cusp) galaxies.
-  However, $\Mdot$ can increase even more rapidly with decreasing
-  $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the
-  stellar velocity dispersion ($\zeta < \zeta_c$;
+    $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$,
+    implying that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core
+    (cusp) galaxies.  However, $\Mdot$ can increase even more rapidly
+    with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes
+    comparable to the stellar velocity dispersion ($\zeta < \zeta_c$;
     eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar
     bulge and cannot produce a flow with a positive kinetic energy
-  interior to the stellar break radius, as we show in Appendix \ref{app:be}; (2)
-  For low $v_w$, gas near the stagnation radius becomes thermally
-  unstable, which based on the results of previous numerical studies
-  (e.g.,\citealt{Ciotti+10}) is instead likely to result in
-  time-dependent cycles of alternating high and low accretion phases
-  ($\S\ref{sec:cycle}$).
+    interior to the stellar break radius, as we show in Appendix
+    \ref{app:be}; (2) For low $v_w$, gas near the stagnation radius
+    becomes thermally unstable, which based on the results of previous
+    numerical studies (e.g.,\citealt{Ciotti+10}) is instead likely to
+    result in a burst of high accretion ($\S\ref{sec:cycle}$).
 

### 2015-04-30 ms.tex
this and that.

@@
   velocity dispersion \\
-  $\sigma_{\bullet}$ & The line of sight velocity dispersion from the  $\Mbh-\sigma$ relation (eq.~\eqref{eq:Msigma})\\
    $\sigma_0$ & stellar velocity dispersion (assumed to be radially
-  constant and equal to $\sqrt{3} \Mbh$).\\
+   constant).\\
   $\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
@@
 
-Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) are solved using a sixth
+Equations (\ref{eq:drhodt})-(\ref{eq:dsdt}) 
+are solved using a sixth
 order finite difference scheme with a third order Runge-Kutta scheme
@@
   \citet{LauerFaber+:2007a} galaxy sample.}
-
- % $\Gamma=0.3
- %  \Mbheight^{-0.24}$, $\rinf=14 \Mbheight^{0.6}$ pc
- %  (eq~\eqref{\eqref{eq:rsoi}}), $\rb\simeq 106 \Mbheight^{0.39} $ pc
- %  (for $\Gamma<0.3$), and $\rb\simeq 100$ pc (for $\Gamma\geq 0.3$)
- %  {\bf Added zeta/zeta_c line but unfortunately caption became
- %    somewhat verbose (I don't think all of this description is
- %    necessary--maybe just say we use scaling relations based on Lauer
- %    et al. sample?) Also being so close to zeta/zeta_c=1 implies
- %    there is a limit to how much scatter we could explain just by
- %    variations in the heating rate}.
-
 \end{figure}

### 2015-04-30 ms.tex
fixing things (e.g. table)

@@
 %    $    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
-   10$^{7}$ & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
+   10$^{7}$ & 300 & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
 % ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 & 0.2, 0.6 \\
@@
 Core Galaxies, $\Gamma = 0.1$  &  & & & & & & & & \\
-$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\
+$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
+10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\
 ... & 1200 & -- & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
@@
     radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
-function of radius (solid lines) for each of our solutions shown in
-Figure \ref{fig:profiles}.  Dashed lines show the ratio
-of the cooling timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
+    function of radius (solid lines) for a $\Mbh=10^7 \Msun$ cusp
+    galaxy ($\Gamma=0.8$).  Dashed lines show the ratio of the cooling
+    timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
     For high heating rates both ratios are approximately equal at the
     stagnation radius (squares).  When $\dot{q}_{\rm
-heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm cool}/t_{\rm ff}
-\lesssim 10$ near the stagnation radius), then the flow is susceptible to thermal instabilities.}
+      heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm
+      cool}/t_{\rm ff} \lesssim 10$ near the stagnation radius), then
+    the flow is susceptible to thermal instabilities.}
 \end{figure}
@@
 (eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of
-radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
-Radiative cooling is calculated using the cooling function of \citet{Draine:2011a} for solar metallicity.  For high heating rates of $v_{w} = 600$ and
-$1200$ km s$^{-1}$ cooling is unimportant across all radii, while for
-$v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$ can be less than unity,
-depending on the wind mass loss parameter $\eta$.  Because at the
-stagnation radius $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches
-within a factor of two of its minimum across the entire grid, the
-value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be
-taken as diagnostic of thermal instability at all radii.
-
-Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$
-near the stagnation radius, but these ratios diverge from each other at low heating ($v_{w} \lesssim 300$ km s$^{-1}$).
-This results because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate the true gas density in the case of subsonic flow (weak heating).
+radius for $v_w=300, 600,$ and 1200 km/s, $\Mbh=10^{7} \Msun$, and
+$\Gamma=0.8$.  Radiative cooling is calculated using the cooling
+function of \citet{Draine:2011a} for solar metallicity.  For high
+heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is
+unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we
+see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$
+can be less than unity, depending on the wind mass loss parameter
+$\eta$.  Because at the stagnation radius $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$ reaches within a factor of two of its
+minimum across the entire grid, the value of $(\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be taken as diagnostic of
+thermal instability at all radii.
+
+Also note that for $v_{w}=600$ and $1200$ km s$^{-1}$ we have
+$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim t_{\rm cool}/t_{\rm ff}$
+near the stagnation radius, but these ratios diverge from each other
+at low heating ($v_{w} \lesssim 300$ km s$^{-1}$).  This results
+because equations (\ref{eq:mdot_gas}), (\ref{eq:rhors}) underestimate
+the true gas density in the case of subsonic flow (weak heating).
 
 Although most of our solutions neglect thermal conduction and
-radiative cooling, these effects are explore explicitly in subset of simulations, as marked by dagger symbols in Table \ref{table:models}.  For cases which are far from being thermally
-unstable when cooling is neglected (e.g., $M_{\bullet} =
-10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
-0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the solution, such as the stagnation radius, mass accretion rate, and the cooling ratio $\dot{q}_{\rm
-  heat}/|\dot{q}_{\rm rad}|$.
-However, for solutions that are marginally thermally stable, including radiative losses acts to significantly decrease $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.
-We calculated solutions with radiative
+radiative cooling, these effects are explored explicitly in subset of
+simulations.  Dagger symbols in Table \ref{table:models} correspond to
+solutions for which we turned on radiative cooling.  For cases which
+are far from being thermally unstable when cooling is neglected (e.g.,
+$M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} =
+100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$),
+including radiative cooling has little effect on the key properties of
+the solution, such as the stagnation radius, mass accretion rate, and
+the cooling ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.  However,
+for solutions that are marginally thermally stable, including
+radiative losses acts to significantly decrease $\dot{q}_{\rm
+  heat}/|\dot{q}_{\rm rad}|$.  We calculated solutions with radiative
 cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
@@
 values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
-expected mass loss for continuous star formation (Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table
-\ref{table:models}, with the unstable values of $\eta$ provided in the final column.
-
-Including thermal conduction, by contrast, results in only minor changes to our solutions for our fiducial value of the saturation parameter $\phi = 0.1$, consistent with our analytic expectation (eq.~[\ref{eq:conduction}]).
+expected mass loss for continuous star formation
+(Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all
+values of $\eta$ are marked in boldface as ``TI" in Table
+\ref{table:models}, with the unstable values of $\eta$ provided in the
+final column.
+
+Including thermal conduction, by contrast, results in only minor
+changes to our solutions for our fiducial value of the saturation
+parameter $\phi = 0.1$, consistent with our analytic expectation
+(eq.~[\ref{eq:conduction}]).
 

### 2015-04-30 ms.tex
core caption
fixing the kinetic feedback

@@
 conductive heating confirm this ($\S\ref{sec:numerical}$).
+
+% For supersonic inflow, we find that conductivity has little effect on our
+% solutions, and our analytics confirm that its effect of redistributing
+% heat near the stagnation radius is at most an order unity correction.  We
+% do not consider the possibility that the conduction of heat from the very
+% inner accretion flow can affect the flow on much larger scales \
 
@@
 
-Key properties of the flow, such as the SMBH accretion rate and the likelihood of thermal instability depend sensitively on the assumed heating rate $\propto qv_{w}^{2}$.
-This section summarizes individual heating sources, providing estimates of the value of
+Key properties of the flow, such as the SMBH accretion rate and the
+likelihood of thermal instability depend sensitively on the assumed
+heating rate $\propto qv_{w}^{2}$.  This section summarizes individual
+heating sources, providing estimates of the value of the effective
+wind velocity
 \begin{align}
@@
 
-Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence populations.
-At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars (e.g., \citealt{VossDiehl+:2009a}).
-At later times energy input is dominated by main sequence winds (e.g., \citealt{NaimanSoares-Furtado+:2013a}).
-Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages the slow AGB winds of evolved low-mass stars dominate the mass budget.
+Energy and mass input to the CNM by stellar winds is the sum of
+contributions from main sequence and post-main sequence populations.
+At early times following star formation, energy input is dominated by
+core collapse supernovae and by the fast outflows of Wolf-Rayet stars
+(e.g., \citealt{VossDiehl+:2009a}).  At later times energy input is
+dominated by main sequence winds (e.g.,
+\citealt{NaimanSoares-Furtado+:2013a}).  Mass input is also dominated
+by massive stars for very young stellar populations, but for most
+stellar ages the slow AGB winds of evolved low-mass stars dominate the
+mass budget.
 
@@
 \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
-is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As will be shown in $\S\ref{sec:combined}$, for the case of quasi-continuous star
-formation representative of the average SFHs of low
-mass galaxies, the heating rate from stellar winds can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
+is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As will
+be shown in $\S\ref{sec:combined}$, for the case of quasi-continuous
+star formation representative of the average SFHs of low mass
+galaxies, the heating rate from stellar winds can also be significant,
+$v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.
 
 Stellar winds thus contribute a potentially important source of both
-energy and mass to the CNM.
-However, two additional uncertainties are (1) the efficiency with which massive stellar winds thermalize their energy and (2) heating from core collapse supernovae, which is potentially comparable to that provided by stellar winds.
-We neglect both effects, but expect they will act in different directions in changing the total heating rate.
+energy and mass to the CNM.  However, two additional uncertainties are
+(1) the efficiency with which massive stellar winds thermalize their
+energy and (2) heating from core collapse supernovae, which is
+potentially comparable to that provided by stellar winds.  We neglect
+both effects, but expect they will act in different directions in
+changing the total heating rate.
 
@@
 
-The deep gravitational potential wells of high mass galaxies prevent SN Ia from dynamically clearing out gas in these systems ($\sigma_0 \gg  v^{\rm Ia}_{w}$).
-Equation (\ref{eq:eddr_Ia}) nevertheless still represents a cap on the accretion rate in practice because the Ia heating rate (eq.~[\ref{eq:vIa}])
-is usually high enough to prevent the stagnation radius (calculated including the Ia heating) from substantially exceeding $r_{\rm Ia}$.
-If the stagnation radius moves inwards from $\rIa$, then decreased heating will force it outwards again.
-On the other hand, if the stagnation radius moves well outside of $\rIa$, then the high level of Ia heating will force it inwards.
+The deep gravitational potential wells of high mass galaxies prevent
+SN Ia from dynamically clearing out gas in these systems ($\sigma_0
+\gg v^{\rm Ia}_{w}$).  Equation (\ref{eq:eddr_Ia}) nevertheless still
+represents a cap on the accretion rate in practice because the Ia
+heating rate (eq.~[\ref{eq:vIa}]) is usually high enough to prevent
+the stagnation radius (calculated including the Ia heating) from
+substantially exceeding $r_{\rm Ia}$. If the stagnation radius moves
+inwards from $\rIa$, then decreased heating will force it outwards
+again.  On the other hand, if the stagnation radius moves well outside
+of $\rIa$, then the high level of Ia heating will force it inwards.
 
@@
 Assume that the outflow power is proportional to the SMBH accretion
-rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}_{\bullet}c^{2} = 0.1\epsilon_{\rm j} \dot{M}c^{2} $, where
-$\epsilon_{\rm j} < 1$ is an outflow efficiency factor and we have again assumed a fraction $\alpha = 0.1$ of the infall rate reaches the SMBH.  Further assume
-that this energy is deposited as heat uniformly interior to a radius
-$r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$.
-The resulting volumetric heating rate $e = 0.1\epsilon_{\rm
+rate, $L_{\rm j} = \epsilon_{\rm j} \dot{M}_{\bullet}c^{2} =
+0.1\epsilon_{\rm j} \dot{M}c^{2} $, where $\epsilon_{\rm j} < 1$ is an
+outflow efficiency factor and we have again assumed a fraction $\alpha
+= 0.1$ of the infall rate reaches the SMBH.  Further assume that this
+energy is deposited as heat uniformly interior to a radius $r_{\rm
+  heat}$ and volume $V_{\rm heat} \propto r_{\rm heat}^{3}$.  The
+resulting volumetric heating rate $e = 0.1\epsilon_{\rm
   j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a
 heating parameter given by
-\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{0.2t_{\rm
-        h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
-      \rho_{\star}|_{r_{s}}}\right)^{1/2} \sim
-  \left(\frac{0.1\epsilon_{\rm
-        j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
-  &\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm
+\begin{eqnarray} 
+  v_{w}^{\bullet} &\approx& \left(\frac{0.2 \th \epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
+      \rho_{\star}|_{r_{s}}}\right)^{1/2} \\
+  &\approx& \frac{700}{\sqrt{2-\Gamma}}\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm
         j}}{10^{-5}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
-        heat}}\right)^{1-\Gamma/2},
+        heat}}\right)^{3/2} ,
 \label{eq:vjet}
@@
 where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm
-    s}}/t_{\rm h}$ and, for radii inside the stellar break radius,
-$M_{\star}(r) = M_{\bullet}(r/r_{\rm inf})^{2-\Gamma}$
-(eq.~[\ref{eq:rhostar}]).  If the bulk of the energy from kinetic
+    s}}/t_{\rm h}$ and $\rho_{\star}(\rs) = M_{\star}(\rs)
+(2-\Gamma)/(4 \pi \rs^3)$.  If the bulk of the energy from kinetic
 feedback is released near the stagnation radius, then even a small
@@
 
-The time required for a jet of luminosity $L_{\rm
-  j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
-AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated from \citet{Bromberg+11} to be 
+The time required for a jet of luminosity $L_{\rm j}$ and half opening
+angle $\theta_{\rm j} = 0.1$ (characteristic of AGN jets) to propagate
+through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated from
+\citet{Bromberg+11} to be
 \begin{eqnarray}
@@
   \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are
-  impossible.  The latter quantity is calculated for core
-  ($\Gamma=0.1$) galaxies  using mean scaling
-  relations for $r_b$, $\rinf$, and $\Gamma$ from the
-  \citet{LauerFaber+:2007a} galaxy sample.}
+  impossible.  All quantities are calculated for core
+  ($\Gamma=0.1$) galaxies, but the results for cusp galaxies are
+  qualitatively similar.}
 \end{figure}
@@
 velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto
-M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.
+M_{\bullet}^{0.38}$ for core(cusp) galaxies, respectively.
 Coupled with the dependence of the SMBH accretion rate on the wind
@@
 SMBH mass of $\dot{M}/\dot{M}_{\rm edd} \propto
-M_{\bullet}^{-0.5(-0.2)}$.
-
-This prediction is also consistent with the observed dependence of
+M_{\bullet}^{-0.7(-0.4)}$.
+
+This prediction is more in line with the observed dependence of
 $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
@@
 scales.
-
-%For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
-%to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).
-Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.
-%However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.
-Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).
-
-%\subsection{Jet Power Correlation}
-
-%Accretion rates onto SMBHs can in principle be estimated directly by
-% assuming Bondi accretion and using high resolution X-ray
-% observations to estimate the gas temperature and density near the
-% Bondi radius.  This technique has led to the intriguing conclusion
-% that the Bondi accretion power correlates with the AGN jet power
-% (e.g., \citealt{AllenDunn+:2006a}; \citealt{Russell+13};
-% \citealt{FujitaKawakatu+:2014a}), the latter estimated from the
-% energy required to inflate the observed cavities within the X-ray
-% emitting gas.  In practice is it almost never possible to resolve
-% the Bondi radius, therefore requiring all such studies to
-% extrapolate the observed gas temperature and density profiles to
-% smaller radial scales.
 

### 2015-04-30 ms.tex
core/cusp

@@
 velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto
-M_{\bullet}^{0.38}$ for core(cusp) galaxies, respectively.
+M_{\bullet}^{0.38}$ for core and cusp galaxies, respectively.
 Coupled with the dependence of the SMBH accretion rate on the wind

### 2015-04-30 ms.tex
abstract

@@
   latter being related to the star-formation history.  We assess the
-  conditions under which radiative instabilities develop in the hydrostatic region near the stagnation radius, both in the
-  case of a single burst of star formation and for the average star
-  formation history predicted by cosmological simulations.  By
-  combining a sample of measured nuclear X-ray luminosities, $L_{X}$,
-  of nearby quiescent galactic nuclei with our results for
-  $\dot{M}(M_{\bullet})$ we address whether the nuclei are consistent with
-  accreting in a steady-state, thermally-stable manner for radiative
-  efficiencies predicted for radiatively inefficiency accretion flows.  However, thermally-stable
-  accretion cannot explain the short average growth times of low mass
-  black holes in the local universe, which must instead result from
-  gas being fed in from large radii, due either to gas inflows or
-  thermal instabilities acting on larger, galactic scales.  Our
-  results have implications for attempts to constrain the occupation
-  fraction of SMBHs in low mass galaxies using the mean $L_{\rm
-    X}-M_{\bullet}$ correlation, as well as the predicted diversity of
-  the circumnuclear densities encountered by relativistic outflows
-  from tidal disruption events.
+  conditions under which radiative instabilities develop in the
+  hydrostatic region near the stagnation radius, both in the case of a
+  single burst of star formation and for the average star formation
+  history predicted by cosmological simulations.  By combining a
+  sample of measured nuclear X-ray luminosities, $L_{X}$, of nearby
+  quiescent galactic nuclei with our results for
+  $\dot{M}(M_{\bullet})$ we address whether the nuclei are consistent
+  with accreting in a steady-state, thermally-stable manner for
+  radiative efficiencies predicted for radiatively inefficiency
+  accretion flows.  We find thermally-stable accretion cannot explain
+  the short average growth times of low mass black holes in the local
+  universe, which must instead result from gas being fed in from large
+  radii, due either to gas inflows or thermal instabilities acting on
+  larger, galactic scales.  Our results have implications for attempts
+  to constrain the occupation fraction of SMBHs in low mass galaxies
+  using the mean $L_{\rm X}-M_{\bullet}$ correlation, as well as the
+  predicted diversity of the circumnuclear densities encountered by
+  relativistic outflows from tidal disruption events.
 \end{abstract}
@@
 hydrodynamic model.  Mass is injected into the nuclear environment via
-stellar winds, while energy is input from several sources
-including stellar winds, supernovae, and AGN feedback
+stellar winds, while energy is input from several sources including
+stellar winds, supernovae, and AGN feedback
 (\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
 Unlike previous works, which focused primarily on modeling individual
-galaxies, here we systematically analyze the CNM properties across a representative
-range of galaxy properties, including different SMBH masses, stellar
-density profiles, and star formation histories (SFHs).
+galaxies, here we systematically analyze the CNM properties across a
+representative range of galaxy properties, including different SMBH
+masses, stellar density profiles, and star formation histories (SFHs).
 
@@
 useful in determining under what conditions cooling instabilities
-manifest in the nuclear region across the expected range of galaxy properties, or whether
-other (non-AGN) forms of feedback can produce a prolonged state of
-steady, thermally stable accretion.  Even if cooling instabilities
-develop on galactic scales over longer $\sim$ Gyr timescales, we aim to explore whether a quasi
-steady-state may exist between these inflow events on smaller radial scales comparable to the sphere of influence.  
+manifest in the nuclear region across the expected range of galaxy
+properties, or whether other (non-AGN) forms of feedback can produce a
+prolonged state of steady, thermally stable accretion.  Even if
+cooling instabilities develop on galactic scales over longer $\sim$
+Gyr timescales, we aim to explore whether a quasi steady-state may
+exist between these inflow events on smaller radial scales comparable
+to the sphere of influence.
 %For instance, for massive galaxies \citealt{Ciotti+10} find that between outbursts gas may exist in a
@@
 Bondi radius, thus controls the SMBH accretion rate (although we will
-show that $\rs$ usually resides near the nominal Bondi
-radius).  When heating is sufficiently weak, however, the stagnation
-radius may move to much larger radii or not exist at all, in which
-case nearly the entire ISM of the galaxy is flowing towards the SMBH, i.e. a ``cooling flow".
-However, the hydrostatic nature of gas near the stagnation radius also renders the CNM at this location particularly susceptible to {\it local} thermal instabilities, the outcome of which could well be distinct from the development of a cooling flow.
+show that $\rs$ usually resides near the nominal Bondi radius).  When
+heating is sufficiently weak, however, the stagnation radius may move
+to much larger radii or not exist at all, in which case nearly the
+entire ISM of the galaxy is flowing towards the SMBH, i.e. a ``cooling
+flow".  However, the hydrostatic nature of gas near the stagnation
+radius also renders the CNM at this location particularly susceptible
+to {\it local} thermal instabilities, the outcome of which could well
+be distinct from the development of a cooling flow.
 

### 2015-05-01 ms.tex
switching to pdf figures.
comment out hyperref package.
fixing capitalization of ti file.
Adding Johnson & Quataert to bib file.

@@
 \usepackage{epstopdf}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \epstopdfsetup{outdir=./figures/}
@@
 
-Equation (\ref{eq:conduction}) shows that, even when
-conduction is saturated, our neglect of heat conduction results in at
-most an order unity correction for causal values of the saturation
-parameter $\phi < 0.1$.  Our numerical experiments which include
-conductive heating confirm this ($\S\ref{sec:numerical}$).
-
-% For supersonic inflow, we find that conductivity has little effect on our
-% solutions, and our analytics confirm that its effect of redistributing
-% heat near the stagnation radius is at most an order unity correction.  We
-% do not consider the possibility that the conduction of heat from the very
-% inner accretion flow can affect the flow on much larger scales \
+Equation (\ref{eq:conduction}) shows that, even when conduction is
+saturated, our neglecting of heat conduction near the stagnation
+radius results in at most an order unity correction for causal values
+of the saturation parameter $\phi < 0.1$.  Our numerical experiments
+which include conductive heating confirm this
+($\S\ref{sec:numerical}$).  We do not consider the possibility that
+the conduction of heat from the very inner accretion flow can affect
+the flow on much larger scales \citep{Johnson+2007}.
 
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{TI.pdf}
+  \includegraphics[width=\columnwidth]{ti.pdf}
   \caption{Minimum effective wind heating parameter required for
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{profiles.eps}
+  \includegraphics[width=\columnwidth]{profiles.pdf}
   \caption{\label{fig:profiles}Radial profiles of the CNM density
@@
     Cusp Galaxies, $\Gamma = 0.8$ & & & & & & & & \\
-    $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
+    $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 & 0.6\\
     ... & 600 & -- & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{rs.eps}
+  \includegraphics[width=\columnwidth]{rs.pdf}
   \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{mdot_mass.eps}
+  \includegraphics[width=\columnwidth]{mdot_mass.pdf}
   \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{cooling.eps}
+  \includegraphics[width=\columnwidth]{cooling.pdf}
   \caption{\label{fig:cooling} Ratio of the rates of heating to
@@
 
-  \item Including the effects of heat transport by electron conduction
-    results in at most order unity changes to the key properties of
-    the flow (e.g. stagnation radius, mass accretion rate, and thermal
-    stability) for causal values of the conduction saturation
-    parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).  Angular
-    momentum is also unlikely to invalidate our spherically symmetric
-    model on large scales, given observationally inferred rotation
-    rates of galactic nuclei near the stagnation radius
-    ($\S\ref{sec:rotation}$).
+  \item In the vicinity of the stagnation radius including the effects
+    of heat transport by electron conduction results in at most order
+    unity changes to the key properties of the flow (e.g. stagnation
+    radius, mass accretion rate, and thermal stability) for causal
+    values of the conduction saturation parameter $\phi < 0.1$
+    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
+    of heat from the very inner accretion flow can affect the flow on
+    much larger scales \citep{Johnson+2007}. Angular momentum is also
+    unlikely to invalidate our spherically symmetric model on large
+    scales, given observationally inferred rotation rates of galactic
+    nuclei near the stagnation radius ($\S\ref{sec:rotation}$).
 
@@
     explicitly on the SMBH mass as well as the SFH in the galactic
-    nucleus.  A young starburst of age $\lesssim 10$ Myr
-    produces mass and energy injection dominated by young stellar
-    winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old
-    stellar populations mass input is dominated by AGB winds and
-    heating is dominated by AGN feedback and supernovae.  Ongoing,
-    continuous star formation presents a hybrid situation, with energy
-    input usually dominated by young stars and mass input dominated by
-    old stars (Appendix \ref{app:windheat}).  Galactic nuclei with
-    $\Mbh \lesssim 10^8\Msun$ that are heated according to their average SFHs
-    (as derived from cosmological simulations) receive a stellar wind
+    nucleus.  A young starburst of age $\lesssim 10$ Myr produces mass
+    and energy injection dominated by young stellar winds ($v_w \sim
+    1000$ km s$^{-1}$), while for exclusively old stellar populations
+    mass input is dominated by AGB winds and heating is dominated by
+    AGN feedback and supernovae.  Ongoing, continuous star formation
+    presents a hybrid situation, with energy input usually dominated
+    by young stars and mass input dominated by old stars (Appendix
+    \ref{app:windheat}).  Galactic nuclei with $\Mbh \lesssim
+    10^8\Msun$ that are heated according to their average SFHs (as
+    derived from cosmological simulations) receive a stellar wind
     heating of $v_w \sim 700$ km s$^{-1}$.  This heating can be
@@
 \item Stellar wind heating from the average SFH may be sufficient to
-  permit thermally-stable, steady-state accretion, depending on the accretion efficiency of the SMBH.  However, the
-  resulting average Eddington-normalized accretion rate is predicted
-  to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in
-  tension with the (also weak) downsizing trend of measured 
-  X-ray luminosities in early-type galactic nuclei (e.g.,
-  \citealt{Miller+15}).  Thermally stable accretion models can reproduce the observed scatter
-  in nuclear X-ray luminosities at fixed $\Mbh$ (2-4 orders of
-  magnitude) due to the combination of (1) differences in the stellar wind heating rate due to stochastic variation in SFH between galaxies, or within one galaxy due to burstiness in the SFH, as in ~Fig.~\ref{fig:NickPlot2}; (2) Variations in the amount of
-  inflowing mass which is lost to small scale outflows from the SMBH accretion disk, likely due to variations in the angular momentum of the accreting gas (cf.~\citealt{Pellegrini10}).
-
-\item However, for lower X-ray radiative efficiencies, the accretion rates of early-type galaxies are above the maximum value for thermally stable flow, $\dot{M}_{\rm TI}$
-  (Fig.~\ref{fig:miller}).  This implies that current X-ray detections could instead be comprised
-  mostly of nuclei undergoing outburst due to thermal instabilities.
-  In such a case, there may exist a separate (usually undetected) branch of low-$L_X$ nuclei accreting stably.
-The existence of such a bimodal population would call into question constraints on the SMBH occupation
-  fraction in low mass galaxies (\citealt{Miller+15}) derived by
-  extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
-  to small $M_{\bullet}$.
+  permit thermally-stable, steady-state accretion, depending on the
+  accretion efficiency of the SMBH.  However, the resulting average
+  Eddington-normalized accretion rate is predicted to increase weakly
+  with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the
+  (also weak) downsizing trend of measured X-ray luminosities in
+  early-type galactic nuclei (e.g., \citealt{Miller+15}).  Thermally
+  stable accretion models can reproduce the observed scatter in
+  nuclear X-ray luminosities at fixed $\Mbh$ (2-4 orders of magnitude)
+  due to the combination of (1) differences in the stellar wind
+  heating rate due to stochastic variation in SFH between galaxies, or
+  within one galaxy due to burstiness in the SFH, as in
+  ~Fig.~\ref{fig:NickPlot2}; (2) Variations in the amount of inflowing
+  mass which is lost to small scale outflows from the SMBH accretion
+  disk, likely due to variations in the angular momentum of the
+  accreting gas (cf.~\citealt{Pellegrini10}).
+
+\item However, for lower X-ray radiative efficiencies, the accretion
+  rates of early-type galaxies are above the maximum value for
+  thermally stable flow, $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}).
+  This implies that current X-ray detections could instead be
+  comprised mostly of nuclei undergoing outburst due to thermal
+  instabilities.  In such a case, there may exist a separate (usually
+  undetected) branch of low-$L_X$ nuclei accreting stably.  The
+  existence of such a bimodal population would call into question
+  constraints on the SMBH occupation fraction in low mass galaxies
+  (\citealt{Miller+15}) derived by extrapolating the $L_{\rm
+    X}(M_{\bullet}$) relationship to small $M_{\bullet}$.
 
@@
 
-We acknowledge helpful conversations with Greg Bryan, Jenny Greene, Jules Halpern,
-Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work
-relied on Columbia University's Yeti computer cluster, and we
-acknowledge the Columbia HPC support staff for assistance.  BDM
+We acknowledge helpful conversations with Greg Bryan, Jenny Greene,
+Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.
+This work relied on Columbia University's Yeti computer cluster, and
+we acknowledge the Columbia HPC support staff for assistance.  BDM
 gratefully acknowledges support from NASA {\it Fermi} grant

### 2015-05-01 ms.tex
minor improvements in language.

@@
 in galaxy structural parameters at a given $\Mbh$, we use
-equation~\eqref{eq:cooling3} instead of equation~\eqref{eq:cooling4}:
-the $\zeta_c$ criterion should be evaluated on a galaxy-by-galaxy
-basis. Thus, the maximum thermally stable $\Mdot$ (for
-$\zeta>\zeta_c$) is
+equation~\eqref{eq:cooling3} instead of equation~\eqref{eq:cooling4}
+to calculate the minimum heating rate: the $\zeta_c$ criterion should
+be evaluated on a galaxy-by-galaxy basis. Thus, the maximum thermally
+stable $\Mdot$ (for $\zeta>\zeta_c$) is
 
@@
     (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
-    of heat from the very inner accretion flow can affect the flow on
-    much larger scales \citep{Johnson+2007}. Angular momentum is also
-    unlikely to invalidate our spherically symmetric model on large
-    scales, given observationally inferred rotation rates of galactic
-    nuclei near the stagnation radius ($\S\ref{sec:rotation}$).
+    of heat from the very inner accretion flow can affect the solution
+    properties on much larger scales \citep{Johnson+2007}. Angular
+    momentum is also unlikely to invalidate our spherically symmetric
+    model on large scales, given observationally inferred rotation
+    rates of galactic nuclei near the stagnation radius
+    ($\S\ref{sec:rotation}$).
 

### 2015-05-01 ms.tex
deleting comments 1
deleting more comments

@@
 \makeatother
-%\renewcommand{\citeauthoryear}[3]{}
 
@@
 \usepackage{deluxetable}
-% \usepackage{natbib}
-
-% \renewcommand{\l}{\left}
-% \renewcommand{\r}{\right}
 
@@
 \citet{Ho:2009a} determines the SMBH accretion rates in a sample of
-early-type galaxies by using X-ray observations to determine the
-Bondi accretion rate and based on estimates for the mass loss rate of
+early-type galaxies by using X-ray observations to determine the Bondi
+accretion rate and based on estimates for the mass loss rate of
 evolved stars.  Both methods lead him to conclude that the available
@@
 low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative
-efficiency for thin disk accretion.  Several lines of evidence now suggest that low-luminosity AGN result from accretion
-proceeding in a radiatively inefficient mode
-(\citealt{Yuan&Narayan14}), due either to the advection of
-gravitationally-released energy across the SMBH horizon
-(e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which reduce the efficiency with which the inflowing gas ultimately reaches the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
-%In fact, the temperature profile is assumed to be flat inside of the
-%Bondi radius.  In reality, the cusp in the velocity dispersion near
-%the SMBH, should cause a cusp in the gas temperature profile (assuming
-%the kinetic energy of stellar winds is efficiently thermalized in
-%shocks).
-%% AG-give sense of scale.
+efficiency for thin disk accretion.  Several lines of evidence now
+suggest that low-luminosity AGN result from accretion proceeding in a
+radiatively inefficient mode (\citealt{Yuan&Narayan14}), due either to
+the advection of gravitationally-released energy across the SMBH
+horizon (e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which
+reduce the efficiency with which the inflowing gas ultimately reaches
+the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
 
@@
 to the sphere of influence.
-%For instance, for massive galaxies \citealt{Ciotti+10} find that between outbursts gas may exist in a
-%quasi-steady state {\bf AG reworded}.
 
@@
 \begin{threeparttable}
-%\centering
 \begin{minipage}{18cm}
@@
 heating rate is proportional to the local stellar density.
-%The value of $v_w$
-%will in general depend on the SMBH mass and the age of the stellar
-%population ($\S\ref{sec:heating}$).
 
@@
 derivation of which are given in Appendix \ref{app:rs}.
-%Our results
-%are expressed in terms of the SMBH mass $M_{\bullet}$, total heating
-%rate $\tilde{v}_{w}$, and wind mass loss parameter $\eta$.
 
@@
 
-%Note that in
-%our runs with radiative cooling we take $\Lambda(T)$ to be a piecewise
-%function with $\Lambda(T) = 1.1 \times 10^{-22} \left(T/10^6
- % \text{K}\right)^{-0.7} $erg cm$^3 $s$^{-1}$ for $T\leq 2\times
-%10^{7}$ K and $\Lambda = 2.3 \times 10^{-24} \left(T/10^6
- % \text{K}\right)^{0.5}$ for $T>2\times 10^{7}$ K.
-
 To within a constant of order unity, equation (\ref{eq:cooling2}) also
@@
 interior to this point.  From equation (\ref{eq:rcirc}) we thus
-conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will most likely
-circularize within the inner sonic point of the flow (Fig.~\ref{fig:profiles}).  Angular momentum should only become
+conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will
+most likely circularize within the inner sonic point of the flow
+(Fig.~\ref{fig:profiles}).  Angular momentum should only become
 dynamically important for thermally stable flows in a region that is
 causally disconnected from the outer part of the flow. Thus, the flow
-properties on large scales will generally be unaffected by angular momentum.
-
-%At $r\simeq r_{\rm circ} $ the gas will encounter a centrifugal
-%barrier, which means that much of the gas flowing in from larger
-%scales will be driven out in a conical outflow. \citep{Li+2013}
-%suggest that the actual accretion rate will be $\sim\alpha$ times the
-%accretion rate on large scales {\bf Note that new ending paragraph}.
+properties on large scales will generally be unaffected by angular
+momentum.
 
@@
     ... & 1200 & -- & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
-%    $    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
    10$^{7}$ & 300 & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\
-% ... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 & 0.2, 0.6 \\
-% ... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
-% ... & ... & 400 & 1.1 & $ 7.0 \times 10^{ -4 }$ & $\mathbf{0.28}$ \\
 ... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
@@
    -2 }$ & 0.2, 0.6  \\
-% ... & ... & 100 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
-%... & ... & 200 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
 ... & 450 & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 19 \\
@@
 ... & 1200 & -- & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
-% ... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
-% ... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
 $    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 & 0.6 \\
-%... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0
-%\times 10^{ -2 }}$ \\
 ... & ... & 50 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$ \\
@@
  ... & ... & 50 & $ 4.1 \times 10^{ -2 }$ & $ 1.5 \times 10^{ -6 }$ & $ 2.3 \times 10^{ 4 }$ \\
-% ... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\
-$    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ & $ 1.0 \times 10^{ 2 }$ \\
+$    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ &
+ $ 1.0 \times 10^{ 2 }$ \\
 ... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 & 0.2, 0.6\\
@@
 ... & ... & 200 & 0.15 & $ 1.7 \times 10^{ -5 }$ & $ 8.0 \times 10^{ 2 }$ \\
-% ... & ... & 400 & 0.8  & $ 2.5 \times 10^{ -2 }$ & $\mathbf{ 3.1 \times 10^{ -4 }}$ \\
 \hline
@@
 
-%\begin{table*}
-%\centering
-%\begin{minipage}{18cm}
-%\caption{Comparison of numerical solutions with and without
- % cooling. We have chosen $\eta=0.04$, which one would expect for 
-  %the average star formation history for $\Mbh=10^8\Msun$ 
- % (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
-  %  figure once it is made.}). Note that we have deliberately chosen a solution
-  %near our thermal stability threshold where cooling is beginning
-  %to become important.
-%}
-%\begin{tabular}{lccccccccccccc}
-%\hline
-%{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
-%{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
-%\hline
-%1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
-%1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
-%\hline
-%\label{table:models}  
-%\end{tabular}
-%\end{minipage}
-%\end{table*}
-
 Our numerical results, summarized in Table \ref{table:models}, allow
@@
 Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
-temperature $T(r)$, and radial velocity $|v(r)|/c_s$, for the cusp ($\Gamma=0.8$) solutions within our
-grid.  As expected, the gas density increases towards the SMBH
-$\rho\propto r^{-\densSlope}$ with $\densSlope\simeq1$, i.e. shallower
-than the $-3/2$ power law for Bondi accretion. This power law behavior
-does not extend through all radii, however, as the gas density profile
-has a break coincident with the location of the break in the stellar
-light profile ($\rb=100$ pc). The temperature profile is relatively
-flat at large radii, but increases as $\propto 1/r^{k}$ interior to
-the sphere of influence, where $k\lesssim 1$, somewhat shallower than
-expected for virialized gas within the black hole sphere of influence.
-The inwardly directed velocity increases towards the hole with a
-profile that is somewhat steeper than the local free-fall velocity $v
-\propto v_{\rm ff}\propto r^{-1/2}$.  The flow near the stagnation
-radius is subsonic, but becomes supersonic at two critical points, one
-located at small radii, $r \lesssim 0.1r_{\rm s}$, and the other
-located at large radii, $r \gtrsim 10^{3}r_{\rm s}$.  In many cases
-the outer supersonic transition is instigated by the transition to a steeper
-stellar density profile exterior to the outer Nuker break radius.
+temperature $T(r)$, and radial velocity $|v(r)|/c_s$, for the cusp
+($\Gamma=0.8$) solutions within our grid.  As expected, the gas
+density increases towards the SMBH $\rho\propto r^{-\densSlope}$ with
+$\densSlope\simeq1$, i.e. shallower than the $-3/2$ power law for
+Bondi accretion. This power law behavior does not extend through all
+radii, however, as the gas density profile has a break coincident with
+the location of the break in the stellar light profile ($\rb=100$
+pc). The temperature profile is relatively flat at large radii, but
+increases as $\propto 1/r^{k}$ interior to the sphere of influence,
+where $k\lesssim 1$, somewhat shallower than expected for virialized
+gas within the black hole sphere of influence.  The inwardly directed
+velocity increases towards the hole with a profile that is somewhat
+steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto
+r^{-1/2}$.  The flow near the stagnation radius is subsonic, but
+becomes supersonic at two critical points, one located at small radii,
+$r \lesssim 0.1r_{\rm s}$, and the other located at large radii, $r
+\gtrsim 10^{3}r_{\rm s}$.  In many cases the outer supersonic
+transition is instigated by the transition to a steeper stellar
+density profile exterior to the outer Nuker break radius.
 
@@
 radius will vary strongly with the break radius. This explains the
-behavior of the three vertically aligned green squares. These are three
-cusp ($\Gamma=0.8$) galaxies with $\Mbh=10^8 \Msun$ and $v_w=300$ km s$^{-1}$
-but with different break radii ($\rb=$ 25, 50, and 100 pc from top to
-bottom). This divergence of the stagnation radius to large radii
-occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.1$),
-explaining the behavior of the two core galaxies shown in
-Fig.~\ref{fig:stag} as vertically aligned orange triangles.  
-%These
-%solutions correspond to the same black hole mass ($\Mbh = 10^8 \Msun$)
-%and heating rate ($v_w = 600$ km s$^{-1}$) but assume different break
-%radii of $r_{b} =$ 25, 50 pc (from top to bottom).
+behavior of the three vertically aligned green squares. These are
+three cusp ($\Gamma=0.8$) galaxies with $\Mbh=10^8 \Msun$ and
+$v_w=300$ km s$^{-1}$ but with different break radii ($\rb=$ 25, 50,
+and 100 pc from top to bottom). This divergence of the stagnation
+radius to large radii occurs at a higher value of $\zeta$ in core
+galaxies ($\Gamma = 0.1$), explaining the behavior of the two core
+galaxies shown in Fig.~\ref{fig:stag} as vertically aligned orange
+triangles.
 
@@
 (eq.~[$\ref{eq:eddr_analytic}$]).
-%Note, however, that for low mass
-%SMBHs, $\dot{M}_{\rm Ia}$ generally exceeds the maximum accretion rate
-%for a thermally stable flow $\dot{M}_{\rm TI}$
-%(eq.~[\ref{eq:Mdotmax}]), implying that dynamical `blow-out' from SNe
-%Ia cannot alone prevent cooling instabilities in the nuclei of low
-%mass galaxies.
 
@@
 of $\rIa$, then the high level of Ia heating will force it inwards.
-
-%Finally, note that our criterion for cooling instability (eq.~[\ref{eq:cooling2}], [\ref{eq:Mdotmax}]) is no longer valid if $\rs$ is regulated to $\rIa$ instead of being determined by equation \eqref{eq:stag_simple}.
-By re-evaluating the density and temperature of gas at $\rIa$ using equations  (\ref{eq:rhors2}) and (\ref{eq:Tanalytic}) for $v_w = v_{w}^{\rm Ia}$, we find that
-%\begin{align}
-%\label{eq:heatingratioIa}
-%&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
-%\begin{cases}
- % 90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
-  %\eta_{0.02}^{-2.7} & \text{core}\nonumber\\
-   %90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
-  %\eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
-%\end{cases}\\&\simeq
-%\begin{cases}
- % 90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
-  %(\tau_{\star}/\th)^{0.5}
- %& \text{core}\\
-  % 90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
-  %& \text{cusp}\\
-%\end{cases}
-%\end{align}
-%For high mass galaxies and relatively old stellar populations, Ia heating can preventing cooling instabilities on scales of the stagnation radius, i.e.
-$(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{\rIa} \gtrsim 10$.
-However, for lower mass galaxies or younger stellar populations, Ia blow-out cannot prevent cooling instabilities.
-
-%Also note that Ia supernovae only cap the accretion rate to this maximum value if the gas feeding the black hole is supplied by local stellar mass loss: the gaseous mass can become much greater if the nucleus is fed externally, e.g.
-due to a galaxy merger or to cooling flows developing within the galaxy over much longer timescales (e.g.~\citealt{Ciotti&Ostriker07}).
 
@@
   optimistic assumptions $\epsilon_{\rm msp} = 1$ and $\eta = 0.02$.
-%  On the other hand, it seems likely that the stellar binaries giving rise to MSPs could be disassociated by stellar interactions in the dense nuclear cluster, reducing the numbers of MSPs as compared to the field population estimate above.
 
@@
 represent a characteristic average value for the accretion rate if a quasi-equilibrium is achieved over many cycles.
-
-%Additionally, a large fraction of the $\dot{M}$ on large scales will
-%be driven out in outflows as the gas has some non-zero angular
-%momentum and a centrifugal barrier will stop it from accreting
-%\citet{Li+2013}. In the limit weak cooling appropriate for low
-%accretion rates the accretion rate on small scales will be of order
-%$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
-%overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
-%equation~\eqref{eq:efficiency}. Note that in evaluating the efficiency
-%one has to use $\tilde{\dot{M}}\simeq \alpha \Mdot$. 
-% This means that the bolometric
-% luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
-% \eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
-% $\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
-% the mass inflow rate on small scales. Note that in evaluating the
-% efficiency one has to account for the $\alpha$ suppression in $\eddr$.
-% we obtain
 
@@
 
-Within our steady state solutions gas outside the stagnation radius $\rs$ is being blown
-out in wind. However, for very massive galaxies ($\Mbh\gsim 10^8
-\Msun$) the energy injected into the gas is not enough to truly blow
-the gas out of the potential well of the galaxy. This gas is likely to
-build up on the outskirts of the galaxy until a thermal instability
-develops, causing the CNM to undergo cyclic oscillations of rapid
-cooling and high accretion rates, followed by quiescent periods once
-gas has been consumed and/or AGN feedback becomes effective. Such
-cycles are seen in numerical simulations of elliptical galaxies on
-large scales and long timescales (\citealt{Ciotti+10}).  Evidence for
-such periodic outbursts includes observations showing that a fraction
-of early-type galaxies in the local universe have undergone recent ($<
-1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).
-
-%Furthermore, our SFH-averaged accretion rates are derived using
-%analytic expressions for the stagnation radius that may underpredict
-%the true accretion rate if $\zeta < \zeta_c$, as may occur in massive
-%core galaxies with large break radii.
+Within our steady state solutions gas outside the stagnation radius
+$\rs$ is being blown out in wind. However, for very massive galaxies
+($\Mbh\gsim 10^8 \Msun$) the energy injected into the gas is not
+enough to truly blow the gas out of the potential well of the
+galaxy. This gas is likely to build up on the outskirts of the galaxy
+until a thermal instability develops, causing the CNM to undergo
+cyclic oscillations of rapid cooling and high accretion rates,
+followed by quiescent periods once gas has been consumed and/or AGN
+feedback becomes effective. Such cycles are seen in numerical
+simulations of elliptical galaxies on large scales and long timescales
+(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes
+observations showing that a fraction of early-type galaxies in the
+local universe have undergone recent ($< 1-2$ Gyr old) star formation
+episodes (\citealt{Donas+07}).
 
 If the actual radiative efficiency is lower than our fiducial
-assumption, then an even larger fraction of the X-ray detections would lie above the
-predictions for stable accretion.  For example, we assume that a fraction $\alpha = 0.1$ 
-of the mass inflow rate reaches the SMBH, but this fraction could be considerably smaller.
-In such a case the X-ray detected galaxies will be experience less heating than we calculate for the average SFH, and may not be stably accreting at all.
-This is plausible given that the \citet{Miller+15} sample includes only early-type galaxies with older stellar populations than the average for their stellar mass.
+assumption, then an even larger fraction of the X-ray detections would
+lie above the predictions for stable accretion.  For example, we
+assume that a fraction $\alpha = 0.1$ of the mass inflow rate reaches
+the SMBH, but this fraction could be considerably smaller. In such a
+case the X-ray detected galaxies will be experience less heating than
+we calculate for the average SFH, and may not be stably accreting at
+all.  This is plausible given that the \citet{Miller+15} sample
+includes only early-type galaxies with older stellar populations than
+the average for their stellar mass.
 
 Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
-  C} > \dot{M}_{\rm TI}$ across all black hole masses.
-This indicates that Compton heating is not sufficient to produce a thermally stable accretion rate, at least for conditions corresponding to the average SFH.
+  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates
+that Compton heating is not sufficient to produce a thermally stable
+accretion rate, at least for conditions corresponding to the average
+SFH.
 
@@
 galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).
-%In
-%support of this, \citet{Kauffmann&Heckman09} find that the growth of
-%low mass black holes is dominated by young stellar bulges which have a
-%log normal distribution of Eddington ratios peaked at
-%$\Mdot/\dot{M}_{\rm edd} \sim 0.01$.
 
@@
 (e.g.~\citealt{Stone&Metzger15}), possibly making this association
-uncoincidental.
-On the other hand, we note that some models for J1644+57  (e.g., \citealt{Tchekhovskoy+2014}) favor a much smaller black hole ($10^5-10^6 \Msun$) than we estimate would be required to produce the observed inner break.
-
-% based on the observed jet power, the jet
-%shut-off time (if linked with the accretion becoming sub-Eddington), and an
-%observed QPO in the x-ray light curve favor a smaller black hole {\bf
- % AG Gone mad!}.
+uncoincidental.  On the other hand, we note that some models for
+J1644+57 (e.g., \citealt{Tchekhovskoy+2014}) favor a much smaller
+black hole ($10^5-10^6 \Msun$) than we estimate would be required to
+produce the observed inner break.
 
@@
 
-%Finally, as already mentioned, our models 
-%On the other hand, \citealt{LauerFaber+:2005a} find that $\sim 60\%$
-%of cusp galaxies and $\sim29\%$ of core galaxies have (generally
-%unresolved) emission in excess of the inward extrapolation of the
-%Nuker law.  They note that these nuclei are bluer than the background
-%galaxy starlight, suggesting the presence of younger stars towards
-%galactic center. Nuclear star cluster could be important for small
-%values of $M_{\rm bulge}\lsim 10^{11} \Msun$ ($\Mbh\lsim 2\times 10^8
-%\Msun$), but are extremely subdominant for higher mass galaxies
-%\citep{GrahamSpitler:2009a}.
-
-%Mass injection to the nucleus could (for $\Mbh\lsim 2 \times 10^{8}
-%\Msun$) therefore be dominated by a nuclear star cluster with its own
-%break radius on parsec scales, i.e. much smaller than our fiducial
-%value of $r_b \sim 100$ pc.  In the case of high heating, a smaller
-%break radius does not appreciably change the stagnation radius,
-%resulting in a similar SMBH accretion rate.  For break radii smaller
-%than the nominal stagnation radius, the presence of a smaller break
-%radius would likely decrease the stagnation radius and accretion rate.
-
 \section*{Acknowledgments}

### 2015-06-16 ms.tex
more comments
comment...
referee 1

@@
   for the stagnation radius (where the radial velocity of the gas
-  passes through zero) and the black hole accretion rate, $\dot{M}$,
+  passes through zero) and the large scale gas inflow rate, $\dot{M}$,
   as a function of $M_{\bullet}$ and the gas heating efficiency, the
@@
 
-%The conclusions of
-%\citet{Miller+15} are thus sensitive to possible changes in
-%the $L_X$-$\Mbh$ relationship at small $\Mbh$.
-% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
-
 The gas density in galactic nuclei also influences the emission from
@@
 Unlike previous works, which focused primarily on modeling individual
-galaxies, here we systematically analyze the CNM properties across a
+galaxies, here we model the CNM properties across a
 representative range of galaxy properties, including different SMBH
@@
   the break radius, $\delta \equiv \Gamma+1$.\\
-  $\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
+  $\dot{M}$ & large scale inflow rate (not necessarily equal to the SMBH accretion rate)   \\
   $\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
-  $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
-  $\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
+  $\dot{M}_{\rm Ia}$ & maximum accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
+  $\dot{M}_{\rm C}$ & equilibrium inflow rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
   $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
@@
 analysis does not account for such an inner break, we note that for
-high heating rates the stagnation radius and concomitant accretion
+high heating rates the stagnation radius and concomitant inflow
 rate are not sensitive to the break radius.
@@
 We first describe analytic estimates of physical quantities, such as
-the stagnation radius $\rs$ and the mass accretion rate, the detailed
+the stagnation radius $\rs$ and the mass inflow rate, the detailed
 derivation of which are given in Appendix \ref{app:rs}.
@@
 
-\subsection{Accretion Rate}
-
-The accretion rate towards the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
+\subsection{Inflow Rate}
+
+The large scale inflow rate towards the SMBH is given by the total
+mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]),
 \begin{eqnarray}
@@
 Eddington accretion rate, assuming a radiative efficiency of ten per
-cent.  Note the sensitive dependence of the accretion rate on the wind
+cent.  Note the sensitive dependence of the inflow rate on the wind
 heating rate.  As will be discussed later,
@@
 which may significantly reduce the fraction of $\dot{M}$ that actually
-reaches the SMBH.
+reaches the SMBH. Thus we distinguish between the large scale inflow
+rate, $\dot{M}$, and the accretion rate onto the black hole,
+$\dot{M}_{\bullet}$.
 
@@
 Even if the hot plasma of the CNM does not condense into cold clouds,
-the loss of pressure can temporarily increase the black hole accretion
-rate by producing a large-scale cooling flow.  When coupled to
+the loss of pressure can temporarily increase the inflow and accretion
+rates by producing a large-scale cooling flow.  When coupled to
 feed-back processes which result from such enhanced accretion, this
@@
    240 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
-%\approx \sigma_0(r_{b}/r_{\rm inf})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c. 
   \end{cases}
@@
 The minimum heating rate for thermal stability corresponds to {\it
-  maximum} thermally-stable accretion rate. Due to the large scatter
+  maximum} thermally-stable inflow rate. Due to the large scatter
 in galaxy structural parameters at a given $\Mbh$, we use
@@
 \begin{tablenotes}
-\item $^{(a)}$ Break radius of stellar density profile.  $^{(b)}$Accretion
-  rate in Eddington units, normalized to a stellar mass input
-  parameter $\eta = 0.2$.  $^{(c)}$Ratio of wind heating rate to
-  radiative cooling rate at the stagnation radius. $\dagger$Calculated with
-  radiative cooling included, assuming mass loss parameter $\eta =
-  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
-  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
-  saturation parameter $\phi = 0.1$.
-Solutions including radiative cooling were performed for cusp galaxies with $v_w=300 $ km s$^{-1}$ and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$ = 0.02, 0.2, and 0.6.
-Values of $\eta$ resulting in thermally unstable solutions are marked in the final column.
-Solutions found to be thermally unstable for all $\eta
-  \geq 0.02$ are denoted as {\bf TI}.
+\item $^{(a)}$ Break radius of stellar density profile.
+  $^{(b)}$Inflow rate in Eddington units, normalized to a stellar mass
+  input parameter $\eta = 0.2$.  $^{(c)}$Ratio of wind heating rate to
+  radiative cooling rate at the stagnation radius. $\dagger$Calculated
+  with radiative cooling included, assuming mass loss parameter $\eta
+  = 0.2$.  $\ddagger$Calculated with radiative cooling and
+  conductivity included, assuming mass loss parameter $\eta = 0.2$ and
+  conductivity saturation parameter $\phi = 0.1$.  Solutions including
+  radiative cooling were performed for cusp galaxies with $v_w=300 $
+  km s$^{-1}$ and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$
+  = 0.02, 0.2, and 0.6.  Values of $\eta$ resulting in thermally
+  unstable solutions are marked in the final column.  Solutions found
+  to be thermally unstable for all $\eta \geq 0.02$ are denoted as
+  {\bf TI}.
 \end{tablenotes}
@@
 
-Figure~\ref{fig:mdot_mass} shows the SMBH accretion rate for a sample of
+Figure~\ref{fig:mdot_mass} shows the inflow rate for a sample of
 our numerical solutions for different values of
@@
   \includegraphics[width=\columnwidth]{mdot_mass.pdf}
-  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
+  \caption{\label{fig:mdot_mass} Inflow rate $\dot{M}/\dot{M}_{\rm
       edd}$ versus SMBH mass for galaxies in our sample, calculated
@@
 including radiative cooling has little effect on the key properties of
-the solution, such as the stagnation radius, mass accretion rate, and
+the solution, such as the stagnation radius, mass inflow rate, and
 the cooling ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.  However,
@@
 
-Key properties of the flow, such as the SMBH accretion rate and the
+Key properties of the flow, such as the mass inflow rate and the
 likelihood of thermal instability depend sensitively on the assumed
@@
 Even if SN Ia are rare near the stagnation radius, they may cap the
-SMBH accretion rate by periodically blowing gas out of the nucleus of
-low mass galaxies.  Between successive SNe, stars release a gaseous
-mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$
-interior to the Ia radius, which is locally gravitationally bound to
-the SMBH by an energy $E_{\rm bind} \gtrsim M_{\rm g}\sigma_0^{2}$.
-From the above definitions it follows that \be \frac{E_{\rm
+inflow rate (and thus the SMBH accretion) rate by periodically blowing
+gas out of the nucleus of low mass galaxies.  Between successive SNe,
+stars release a gaseous mass $M_{\rm g} \approx \eta
+M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is
+locally gravitationally bound to the SMBH by an energy $E_{\rm bind}
+\gtrsim M_{\rm g}\sigma_0^{2}$.  From the above definitions it follows
+that
+
+\begin{equation}
+ \frac{E_{\rm
     Ia}}{E_{\rm bind}} \lesssim \frac{(v_{w}^{\rm
@@
 \label{eq:blowout}
-\ee
-Hence, for low mass BHs with $\sigma_0 \ll v^{\rm Ia}_{w}$, SN Ia are capable of dynamically clearing out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.
-Thus even when heating is sufficiently weak that the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH accretion rate is still limited to a value
+\end{equation}
+
+Hence, for low mass BHs with $\sigma_0 \ll v^{\rm Ia}_{w}$, SN Ia are
+capable of dynamically clearing out gas from radii $\sim r_{\rm Ia}
+\gtrsim r_{\rm s}$.  Thus even when heating is sufficiently weak that
+the stagnation radius formally exceeds $r_{\rm Ia}$, the SMBH
+accretion rate is still limited to a value
 \begin{eqnarray}
@@
 
-Feedback from accretion onto the SMBH represents an important source of heating which, however, is also the most difficult to quantify (e.g., \citealt{Brighenti&Mathews03}, \citealt{DiMatteo+05}; \citealt{Kurosawa&Proga09}; \citealt{Fabian12} for a recent review).
-A key difference between AGN heating and the other sources discussed thus far is its dependence on the SMBH accretion rate $\dot{M}$, which is itself a function of the heating rate (eq.~[\ref{eq:mdot_analytic}]).
+Feedback from accretion onto the SMBH represents an important source
+of heating which, however, is also the most difficult to quantify
+(e.g., \citealt{Brighenti&Mathews03}, \citealt{DiMatteo+05};
+\citealt{Kurosawa&Proga09}; \citealt{Fabian12} for a recent review).
+A key difference between AGN heating and the other sources discussed
+thus far is its dependence on the SMBH accretion rate
+$\dot{M}_{\bullet}$, which is itself a function of the heating rate
+(eq.~[\ref{eq:mdot_analytic}]).
 
@@
 
-The accretion rate corresponding to a state in which Compton heating
+The inflow rate corresponding to a state in which Compton heating
 self-regulates the accretion flow is given by substituting equation
@@
 
-Substituting $\epsilon$ into equation (\ref{eq:MdotCa}) and solving for the accretion rate results in
+Substituting $\epsilon$ into equation (\ref{eq:MdotCa}) and solving
+for the inflow rate results in
 \begin{align}
@@
 \end{align}
-Accretion may not be truly steady in cases where AGN
-heating dominates, due to the inherent delay between black hole
-feedback and the structure of the accretion flow on larger scales.
-Equation (\ref{eq:MdotC}) may nevertheless
-represent a characteristic average value for the accretion rate if a quasi-equilibrium is achieved over many cycles.
+Accretion may not be truly steady in cases where AGN heating
+dominates, due to the inherent delay between black hole feedback and
+the structure of the accretion flow on larger scales.  Equation
+(\ref{eq:MdotC}) may nevertheless represent a characteristic average
+value for the inflow rate if a quasi-equilibrium is achieved over
+many cycles.
 
@@
 \end{equation}
+
+where we implicitly the different sources of energy injection mix
+efficiently. In reality, this may not be the case as slower velocity
+sources cool and form high density structure due to external pressure
+from faster winds \citep{Cuadra+2005}.
+
 includes contributions from stellar winds, supernovae, pulsars, and
@@
 dispersion, i.e. $\zeta \sim \zeta_c$ (eq.~[\ref{eq:zetacrit}]).  This
-implies that the true stagnation radius and SMBH accretion rate could
+implies that the true stagnation radius and the inflow rate could
 be larger than our analytic estimates, potentially resulting in
@@
 
-\subsection{Black Hole Accretion Rates}
+\subsection{Inflow and Black Hole Accretion Rates}
 \label{sec:mdot}
@@
   $M_{\bullet}$, shown for core ($\Gamma=0.1$, dot-dashed) and cusp
-  galaxies ($\Gamma=0.8$, solid).  Black lines show the accretion rate
+  galaxies ($\Gamma=0.8$, solid).  Black lines show the inflow rate
   calculated from equation (\ref{eq:eddr_analytic}) using the heating
@@
   maximum accretion set by Ia supernovae blow-out or heating,
-  $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).  Red lines show the accretion
+  $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).  Red lines show the inflow
   rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$
-  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion
+  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum inflow
   rate for a thermally stable flow near the stagnation radius,
   $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the
-  inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray
+  inferred inflow rates of SgrA* from \citet{Quataert:2004a} (gray
   circles), for NGC3115 from \citet{ShcherbakovWong+:2014a} (gray
@@
 Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
-accretion rate as a function of black hole mass for the average star
+inflow rate as a function of black hole mass for the average star
 formation heating, calculated from equation (\ref{eq:eddr_analytic})
 using our results for the total wind heating
-(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
+(Fig.~\ref{fig:mdot_mass}).  This average inflow rate increases
 from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
@@
 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{8}M_{\sun}$.
-These fall below the maximum thermally stable accretion rate,
+These fall below the maximum thermally stable inflow rate,
 $\dot{M}_{\rm TI}$ (yellow lines), although in practice high mass core
@@
 released by a single Ia is insufficient to unbind gas from the stellar
-bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and teal lines mean at high $M_{\bullet}$.
+bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and teal
+lines mean at high $M_{\bullet}$.
 
 Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
-the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
-Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115
-derived through detailed modeling by \citet{ShcherbakovWong+:2014a},
-who find a range of accretion rates depending on the assumed model for
-thermal conductivity\footnote{We expect this range would be have been
-  smaller had \citet{ShcherbakovWong+:2014a} included saturation of
-  the conductive flux.}.  The SgrA* rate exceeds our estimate of
-$\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost
-two orders of magnitude.  This discrepancy can in part be understood
-by the fact that star formation in the central parsec of the Milky Way
-cannot be described as steady-state: feedback is instead dominated by
-the stellar winds from the ring of young massive stars of mass $\sim
+the inflow rate, $\dot{M}$, onto SgrA* calculated by
+\citet{Quataert:2004a}.  Also shown is the range of $\dot{M}$ for the
+low-luminosity AGN NGC3115 derived through detailed modeling by
+\citet{ShcherbakovWong+:2014a}, who find a range of inflow rates
+depending on the assumed model for thermal conductivity\footnote{We
+  expect this range would be have been smaller had
+  \citet{ShcherbakovWong+:2014a} included saturation of the conductive
+  flux.}.  The SgrA* rate exceeds our estimate of $\dot{M}$ due to the
+average SFH for the same $M_{\bullet}$ by almost two orders of
+magnitude.  This discrepancy can in part be understood by the fact
+that star formation in the central parsec of the Milky Way cannot be
+described as steady-state: feedback is instead dominated by the
+stellar winds from the ring of young massive stars of mass $\sim
 10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g.,
@@
 profiles.  Then we use our numerical results (Table
-\ref{table:models}) are used to verify and calibrate analytic
+\ref{table:models}) to verify and calibrate analytic
 relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use the

### 2015-06-19 ms.tex
referee 2

@@
 \begin{document}
-\title{Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes}
+\title{Circumnuclear Media of Quiescent Supermassive Black Holes}
 \maketitle
@@
 of influence, hereafter denoted the `circumnuclear medium' (CNM),
-controls the mass accretion rate, $\dot{M}$.  The accretion rate in
-turn determines the SMBH luminosity and the feedback of its energy and
-momentum output on larger scales.  Dense gas in the nucleus may lead to runaway cooling, resulting in bursty episodes of
-star formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}).
-
-Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
-properties of the nucleus informs key questions related to the
-co-evolution of SMBHs and their host galaxies with cosmic time
+controls the mass accretion rate, $\dot{M}_{\bullet}$.  The accretion
+rate in turn determines the SMBH luminosity and the feedback of its
+energy and momentum output on larger scales.  Dense gas in the nucleus
+may lead to runaway cooling, resulting in bursty episodes of star
+formation and AGN activity (e.g.~\citealt{Ciotti&Ostriker07}).
+
+Knowledge of how $\dot{M}_{\bullet}$ depends on the SMBH mass, $\Mbh$,
+and other properties of the nucleus informs key questions related to
+the co-evolution of SMBHs and their host galaxies with cosmic time
 (e.g.~\citealt{Kormendy&Ho13}; \citealt{HeckmanBest:2014a}).  In the
@@
 `cosmic down-sizing' resulting from hierarchical structure growth
-(e.g, \citealt{Gallo+08}).  However, the physical processes by which typical
-low mass black holes accrete could in principle be distinct from those
-operating at higher SMBH masses, or those in AGN.  Of key importance is whether SMBHs grow primarily by the
-accretion of gas fed in directly from galactic or extra-galactic
-scales, or whether significant growth can result also from local
-stellar mass loss in the nuclear region.
+(e.g, \citealt{Gallo+08}).  However, the physical processes by which
+typical low mass black holes accrete could in principle be distinct
+from those operating at higher SMBH masses, or those in AGN.  Of key
+importance is whether SMBHs grow primarily by the accretion of gas fed
+in directly from galactic or extra-galactic scales, or whether
+significant growth can result also from local stellar mass loss in the
+nuclear region.
 
@@
 
-Gas comprising the CNM of quiescent (non-AGN) galaxies can in principle originate from several
-sources: (1) wind mass loss from predominantly evolved stars; (2)
-stellar binary collisions; and (3) unbound debris from a recent TDE.
-Stellar wind mass loss is probably the dominant source insofar as
-collisions are relevant only in extremely dense stellar environments
-for very young stellar populations (\citealt{Rubin&Loeb11}), while
-\citet{MacLeod+13} find that TDEs contribute subdominantly to the
-time-averaged accretion rate of quiescent SMBHs.
-
-\citet{Ho:2009a} determines the SMBH accretion rates in a sample of
-early-type galaxies by using X-ray observations to determine the Bondi
-accretion rate and based on estimates for the mass loss rate of
-evolved stars.  Both methods lead him to conclude that the available
-gas reservoir is more than sufficient to power the observed
-low-luminosity AGN, assuming the standard $\sim$ 10 per cent radiative
-efficiency for thin disk accretion.  Several lines of evidence now
-suggest that low-luminosity AGN result from accretion proceeding in a
-radiatively inefficient mode (\citealt{Yuan&Narayan14}), due either to
-the advection of gravitationally-released energy across the SMBH
-horizon (e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which
-reduce the efficiency with which the inflowing gas ultimately reaches
-the SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
-
-Another approach to determine the SMBH accretion rate, which we adopt
+Gas comprising the CNM of quiescent (non-AGN) galaxies can in
+principle originate from several sources: (1) wind mass loss from
+predominantly evolved stars; (2) stellar binary collisions; and (3)
+unbound debris from a recent TDE.  Stellar wind mass loss is probably
+the dominant source insofar as collisions are relevant only in
+extremely dense stellar environments for very young stellar
+populations (\citealt{Rubin&Loeb11}), while \citet{MacLeod+13} find
+that TDEs contribute subdominantly to the time-averaged accretion rate
+of quiescent SMBHs.
+
+{\bf AG need to introduce concept of inflow rate here}
+\citet{Ho:2009a} determines the inflow rates in a sample of early-type
+galaxies by using X-ray observations to determine the Bondi accretion
+rate and based on estimates for the mass loss rate of evolved stars.
+Both methods lead him to conclude that the available gas reservoir is
+more than sufficient to power the observed low-luminosity AGN,
+assuming the standard $\sim$ 10 per cent radiative efficiency for thin
+disk accretion.  Several lines of evidence now suggest that
+low-luminosity AGN result from accretion proceeding in a radiatively
+inefficient mode (\citealt{Yuan&Narayan14}), due either to the
+advection of gravitationally-released energy across the SMBH horizon
+(e.g.~\citealt{Narayan&Yi95}) or due to disk outflows, which reduce
+the efficiency with which the inflowing gas ultimately reaches the
+SMBH (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}).
+
+Another approach to determine the inflow rates, which we adopt
 in this paper, is to directly calculate the density, velocity and
@@
 development of cooling instabilities on galactic scales, which
-temporarily increase the gas accretion rate towards the nucleus until
+temporarily increase the gas inflow rate towards the nucleus until
 feedback becomes strong enough to shut off the flow and halt
@@
 an outflow from the nucleus.  The stagnation radius, rather than the
-Bondi radius, thus controls the SMBH accretion rate (although we will
+Bondi radius, thus controls the inflow rate (although we will
 show that $\rs$ usually resides near the nominal Bondi radius).  When
@@
 \end{align}
-Though of questionable validity for low mass black holes (e.g.,
-\citealt{Greene+2010, Kormendy+2013}), we adopt equation
-(\ref{eq:Msigma}) for lack of an obviously better alternative.
+This may be of questionable validity for low mass black holes (e.g.,
+\citealt{Greene+2010, Kormendy+2013}). Also, several of the black hole
+masses used in \citealt{McConnellMa+:2011a} were underestimated
+\citep{Kormendy+2013}.
 
@@
 heating rate is proportional to the local stellar density.
+
+Our model does not take into account complications such as more
+complicated geometries or the discrete nature of real stars
+\citep{Cuadra+2006, Cuadra+2008}. In the case of Sgr A* these effects
+reduce the time average inflow rate to $\sim10^{-6} \Msun \pyear$ --
+an order of magnitude less than a 1D spherical model
+\citep{Cuadra+2006}.  Motions of individual stars can produce ~order
+of magnitude spikes in the accretion rate \citep{Cuadra+2008}.
 
@@
 cent.  Note the sensitive dependence of the inflow rate on the wind
-heating rate.  As will be discussed later,
-equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on
-relatively large scales and does not include outflows from the SMBH
-accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}),
-which may significantly reduce the fraction of $\dot{M}$ that actually
-reaches the SMBH. Thus we distinguish between the large scale inflow
-rate, $\dot{M}$, and the accretion rate onto the black hole,
-$\dot{M}_{\bullet}$.
+heating rate.  Equation~\eqref{eq:eddr_analytic} is the radial mass
+inflow rate on relatively large scales and does not include outflows
+from the SMBH accretion disk (e.g.~\citealt{Blandford&Begelman99};
+\citealt{Li+13}), which may significantly reduce the fraction of
+$\dot{M}$ that actually reaches the SMBH. Thus we distinguish between
+the large scale inflow rate, $\dot{M}$, and the accretion rate onto
+the black hole, $\dot{M}_{\bullet}$.
 
@@
 \end{align}
-where the cusp case is derived using equation (\ref{eq:eddr_analytic})
-to calculate $\dot{M}(v_{\rm TI})$, and the core case corresponds to
-the more stringent $\zeta > \zeta_c$ criterion, calculated again using
-the mean $r_{b}/r_{\rm inf}$ relation from \citet{LauerFaber+:2007a}.
+
+Note that since SMBH accretion rate cannot exceed the large scale
+inflow rate, $\dot{M}_{\rm TI}$ also represents the maximum thermally
+stable accretion rate.
 
 What we describe above as ``thermal instability" may in practice
-simply indicate an abruption transition from a steady inflow-outflow
+simply indicate an abrupt transition from a steady inflow-outflow
 solution to a global cooling flow, as opposed a true thermal
@@
 likelihood of thermal instability depend sensitively on the assumed
-heating rate $\propto qv_{w}^{2}$.  This section summarizes individual
-heating sources, providing estimates of the value of the effective
-wind velocity
+heating rate $\propto qv_{w}^{2}$.  In this section we estimate the
+heating rate, $v_w$, taking into account contribution from stellar
+winds, supernovae, millisecond pulsars and SMBH feedback. We assume
+that all sources of energy injection are efficiently mixed into the
+bulk of CNM gas. In fact, slower stellar wind material may cool and
+form high density structures as in \citet{Cuadra+2005}. Additionally,
+some of the injected energy may leak away from the bulk of the CNM
+material through low density holes, as described by
+\citet{Harper-Clark+2009} for stellar feedback and by
+\citet{Zubovas+2014} for AGN feedback.
+
+We summarize the individual heating sources below, providing estimates
+of the value of the effective wind velocity
 \begin{align}
@@
 efficiently. In reality, this may not be the case as slower velocity
-sources cool and form high density structure due to external pressure
-from faster winds \citep{Cuadra+2005}.
+sources cool and form high density structure due to high pressure from
+the environment\citep{Cuadra+2005}.
 
@@
 more than a factor of a few for a thermally-stable flow, limiting the
-allowed variation of $\dot{M}/\dot{M}_{\rm edd}$.  Variations in
-$L_{X}/L_{\rm edd}$ could also result from differences in angular
-momentum of the infalling gas from galaxy to galaxy, resulting in
-differences in the fraction of the gas lost to outflows.  Also
-potentially contributing is the order of magnitude difference, at
+allowed variation of $\dot{M}/\dot{M}_{\rm edd}$. The discrete nature
+of stellar wind sources and their motions could result in an
+additional order of magnitude variation $\dot{M}$ \citep{Cuadra+2008}.
+
+Variations in $L_{X}/L_{\rm edd}$ could also result from differences
+in angular momentum of the infalling gas from galaxy to galaxy,
+resulting in differences in the fraction of the gas lost to outflows.
+Also potentially contributing is the order of magnitude difference, at
 fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp
@@
 
-  \item The location of the stagnation radius, and hence the SMBH
-    accretion rate, is a sensitive function of the gas heating rate
-    $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$,
-    implying that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core
-    (cusp) galaxies.  However, $\Mdot$ can increase even more rapidly
-    with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes
+  \item The location of the stagnation radius, and hence the inflow
+    rate, is a sensitive function of the gas heating rate $\propto
+    v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$, implying that
+    $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core (cusp)
+    galaxies.  However, $\Mdot$ can increase even more rapidly with
+    decreasing $v_w$ for two reasons: (1) when $v_w$ becomes
     comparable to the stellar velocity dispersion ($\zeta < \zeta_c$;
@@
 \item Low mass black holes grow in the low redshift universe over
-  timescales comparable to the Hubble time (\citealt{Heckman+04}).  The
-  accretion rates so required are too high to be consistent with either the
-  value predicted for the average SFH history or the maximum allowed
-  for steady-state, thermally stable accretion
-  (Fig.~\ref{fig:bh_growth}).  Perhaps unsurprisingly, low-$M_{\bullet}$ growth and AGN
-  activity must instead be driven by a supply of gas external to the
-  nucleus, such as galaxy mergers or thermal instabilities on
-  larger, galactic scales (e.g.~\citealt{Voit+15}).
+  timescales comparable to the Hubble time (\citealt{Heckman+04}).
+  The accretion rates so required are too high to be consistent with
+  either the value predicted for the average SFH history or the
+  maximum allowed for steady-state, thermally stable accretion
+  (Fig.~\ref{fig:bh_growth}).  Perhaps unsurprisingly,
+  low-$M_{\bullet}$ growth and AGN activity must instead be driven by
+  a supply of gas external to the nucleus, such as galaxy mergers or
+  thermal instabilities on larger, galactic scales
+  (e.g.~\citealt{Voit+15}).
 
@@
 
+Finally, we do not account for the effects of non-spherical geometry
+or discreteness of stellar wind sources \citep{Cuadra+2006,
+  Cuadra+2008}. We assume all of the mass and energy sources are
+efficiently mixed, and do not take into account the possibility of
+slower wind material condensing into high density structures (as
+described in \citealt{Cuadra+2005}) or some of the energy injection
+leaking away in 3-d \citep{Harper-Clark+2009,Zubovas+2014}.
+
 \section*{Acknowledgments}

### 2015-06-26 ms.tex
typo
Adding referee acknowledgement.
angular momentum discussion and eqn typo.

@@
 \begin{equation}
-v_w > {\rm max}[v_{\rm TI},\sigma_0\{1-(r_{b}/r_{\rm
-  inf})^{0.5(1-\Gamma)}\}]
+v_w > {\rm max}[v_{\rm TI},\sigma_0\{(r_{b}/r_{\rm
+  inf})^{(1-\Gamma)}-1\}^{1/2}\}]
 \label{eq:cooling4}
@@
 Based on the \citet{LauerFaber+:2007a} sample we take $\rinf = 25(8)M
-0.6$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
+^{0.6}$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
 $\rb/\rinf\simeq 4 \Mbheight^{-0.2} (13 \Mbheight^{-0.6})$ for cores
@@
 interior to this point.  From equation (\ref{eq:rcirc}) we thus
-conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will
-most likely circularize within the inner sonic point of the flow
-(Fig.~\ref{fig:profiles}).  Angular momentum should only become
-dynamically important for thermally stable flows in a region that is
-causally disconnected from the outer part of the flow. Thus, the flow
-properties on large scales will generally be unaffected by angular
-momentum.
+conclude that $r_{\rm circ} \lesssim 0.01r_{s}$. For the low inflow
+rates considered the gas ($\eddr<0.01$) would be unable to cool on a
+dynamical time and would likely drive a bipolar outflow
+\citep{Li+2013}. Our model cannot capture such two dimensional
+structures, but would still be relevant for large scale flow
+properties in regions where the gas is inflowing.
 
@@
 
-where we implicitly the different sources of energy injection mix
+where we implicitly assume the different sources of energy injection mix
 efficiently. In reality, this may not be the case as slower velocity
@@
 
-We conclude by drawing attention to a few limitations of our
-model.  First, we have neglected any large scale inflow of gas to the
-nucleus by assuming the only source of gas feeding the black hole is
-stellar wind mass loss from the local stellar population.  Our
-estimates represent a lower bound on the time averaged gas density of
-the CNM.  Although our model can, under certain assumptions, describe quiescent galactic nuclei, it cannot account for AGN.
+We conclude by drawing attention to a few limitations of our model.
+First, we have neglected any large scale inflow of gas to the nucleus
+by assuming the only source of gas feeding the black hole is stellar
+wind mass loss from the local stellar population.  Our estimates
+represent a lower bound on the time averaged gas density of the CNM.
+Although our model can, under certain assumptions, describe quiescent
+galactic nuclei, it cannot account for AGN.
 
@@
 
-We acknowledge helpful conversations with Greg Bryan, Jenny Greene,
-Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.
-This work relied on Columbia University's Yeti computer cluster, and
-we acknowledge the Columbia HPC support staff for assistance.  BDM
-gratefully acknowledges support from NASA {\it Fermi} grant
-NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.
+We thank the referee, Sergei Nayakshin, for several insightful
+comments. We acknowledge helpful conversations with Greg Bryan, Jenny
+Greene, Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot
+Quataert.  This work relied on Columbia University's Yeti computer
+cluster, and we acknowledge the Columbia HPC support staff for
+assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
+grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
+Foundation.
 

### 2015-06-26 windheat.tex
angular momentum discussion and eqn typo.

@@
     \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
-        T}(t)}
-    \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar }{\bar{m}_*}\\
-  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
-  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
+        T}(t)} \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
+  }{\bar{m}_*}\label{eq:mdotImp}
+  \\
+  \dot{\bar{e}}(t) &=f_{\rm OB} \, \dot{e}_{\rm OB}(t)+ f_{\rm MS}
+  \int_{m_0}^{m_{\rm T}(t)} \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t)
+    \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
   \label{eq:edotImp}
 \end{align} 
-where the first and second terms in each expression corresponds to
-contributions from main sequence (MS) stars and post-main sequence
-(PMS) stars, respectively.  Here $ f_{\rm MS} < 1$ is the efficiency
-with which main sequence winds thermalize their energy with the rest
-of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
-is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar}
-\propto M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low
-mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ =
-0.35 $\Msun$ is the corresponding mean stellar mass.  Our optimistic
-assumption of 100 per cent thermalization efficiency of stellar winds
-is at least partially offset by our conservative assumption to neglect
-energy input from core collapse supernovae, which contribute a
-comparable energy injection rate to massive stellar winds.
+In the top line, the first and second terms correspond to contributions
+from main sequence (MS) stars and post-main sequence (PMS) stars,
+respectively. Here $\mu$ is the IMF, which we take to be of the
+Salpeter form $\mu|_{\Mstar} \propto M_{\star}^{-2.35}$, truncated at
+$m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high
+mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean
+stellar mass. In practice the contribution of main sequence winds to
+the mass budget is negligible, and so we drop the second term in
+equation~\eqref{eq:mdotImp}.
+
+The first term in equation~\eqref{eq:edotImp} corresponds energy
+injection from massive O \& B stars, while the second term accounts
+for energy injection from stars on the lower main sequence. Both terms
+have a thermalization efficiency, $f$, which we talk to be $1$. Note
+we do not account for energy from Type II supernovae. However, the
+mass injection from type II supernovae is implicitly included in the
+first term of equation~\eqref{eq:mdotImp}
+
+Winds from lower main sequence stars only dominate the energy
+injection a late times ~10 Gyr after an impulsive burst of star
+formation. Even with 100\% thermalization efficiency these winds could
+not thermally stabilize the CNM. Thus, we could not describe this
+regime within our steady formalism.
 
@@
 
-The rate of energy input from PMS winds, $\dot{e}_{\rm TO}(t) =
-f_{8}\dot{\mathcal{E}}/\bar{m}_*$, is dominated by fast Wolf-Rayet
-winds and core-collapse supernovae from massive stars ($M_{\star} >
-8M_{\odot}$), where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the
-stellar mass with $M_{\star} > 8M_{\odot}$ for our assumed Salpeter
-IMF.  Here $\dot{\mathcal{E}} (t)$ is the energy injection rate per
-massive star, which we estimate as
+The rate of energy injection due to winds from massive
+stars, $\dot{e}_{\rm OB}(t) = f_{8}\dot{\mathcal{E}}/\bar{m}_*$, where
+$f_{8} =2.6 \times 10^{-3}$ is the fraction of the stellar mass with
+$M_{\star} > 8M_{\odot}$ for our assumed Salpeter IMF.  Here
+$\dot{\mathcal{E}} (t)$ is the energy injection rate per massive star,
+which we estimate as
 \begin{align}
@@
 panel), who use a population synthesis code to simulate the mass and
-energy injection into the ISM from an OB association.  Although
-equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr, in
-practice the precise functional form of $\dot{e}_{\rm TO}(t)$ is
-generally unimportant for our purposes, so we adopt
-equation~\eqref{eq:voss} as being valid for all times.
+energy injection into the ISM from an OB association. {\bf AG--should
+  just truncate the energy injection at $10^7$ years. Explain why
+  turn-off energy injection is negligible in lower mass stars.}
 

### 2015-06-29 ms.tex
not to self

@@
   scatter of approximately one dex.  Most the cusp galaxies have $\rb$
-  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  We
-neglect values of $r_b$ which would give unphysically large bulges for
-a given $\Mbh$.
+  between 100 and 1000 pc, and lack a clear trend with $\Mbh$. {\bf AG
+    I redid the fitting and found $\rb\sim 90 \, (\Mbheight)^{0.5}$
+    pc}} We neglect values of $r_b$ which would give unphysically
+large bulges for a given $\Mbh$.
 
@@
     \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
-    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc)  for cores (cusps). For
+    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc)  for cores (cusps)
+    {\bf AG update rb fit}. For
     $\zeta < \zeta_c$ the stagnation radius moves from inside the
@@
   0.03 \left(\frac{\dot{M}_{\bullet}}{10^{-4}\dot{M}_{\rm edd}}\right)^{0.9} & \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim 10^{-4} \\
- 0.03 &  10^{-2} \lsim \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim  10^{-4},
+ 0.03 &  10^{-2} \gsim \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \gsim  10^{-4},
 \end{cases}
@@
 for the inflow rate results in
+
 \begin{align}
 \frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
-\begin{cases} 6\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
-C,9}^{-0.44}M_{\bullet,8}^{0.09}
-&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
-C,9}^{-0.4} M_{\bullet,8}^{0.08}
+\begin{cases} 4\times 10^{-2} \eta_{0.02}^{0.2}T_{\rm
+C,9}^{-0.8} M_{\bullet,8}^{0.16}
+&, \text{core}\\ 9\times 10^{-3} \eta_{0.02}^{0.3}T_{\rm
+C,9}^{-0.7} M_{\bullet,8}^{0.14}
 &, \text{cusp}.
@@
 \end{align}
+
 Accretion may not be truly steady in cases where AGN heating
@@
 panel of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where
-$\zeta_c$ is estimated from the best-fit power-law dependence of
-$r_b$, $\rinf$, and $\Gamma$ on $M_{\bullet}$ from the
-\citet{LauerFaber+:2007a} galaxy sample.  In other words, the CNM of a
+$\zeta_c$ is estimated ...{\bf AG this sentence needs to be
+  fixed. Power law fits different for cores and cusps. Power law fixed
+to be 0.6 for influence radius in doing fits}.  In other words, the CNM of a
 significant fraction of massive ellipticals may be thermally unstable,
@@
 calculated using the accretion rate from the top line of
-equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.3
-\Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a}
-galaxy sample.
+equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.8$ for $\Mbh < 3
+\times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
+\left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
+\times 10^7 \Msun$. This is functional form is designed to
+approximately reproduce the behavior of $\Gamma(\Mbh)$ in the
+\citet{LauerFaber+:2007a} sample.
 
@@
   average SFH for galaxies corresponding to each black hole mass
-  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
-  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived
-  from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are
-  the measurements ({\it black stars}) and upper limits ({\it gray
-    triangles}) for $L_X/L_{\rm edd}$ values, from the
-  \citet{Miller+15} sample of early-type galaxies (a black line shows
-  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
-  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
-  calculated assuming a constant radiative efficiency
-  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
-  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm
-    rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency of
-  low luminosity accretion disks calculated by \citet{Sharma+2007}
-  (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of
-  the mass inflowing on large scales that reaches the SMBH.  Shown for
-  comparison are the X-ray luminosities calculated for the maximum
-  thermally-stable accretion rate ({\it dashed orange line};
-  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
-    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
-  heating-regulated accretion rate ({\it dashed pink line};
-  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
-  corresponding to each SMBH mass.}
+  (Fig.~\ref{fig:bh_growth}), calculated using $\Gamma = 0.8$ for
+  $\Mbh < 3 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
+  \left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
+  \times 10^7 \Msun$ derived from the \citet{LauerFaber+:2007a}
+  sample.  Shown for comparison are the measurements ({\it black
+    stars}) and upper limits ({\it gray triangles}) for $L_X/L_{\rm
+    edd}$ values, from the \citet{Miller+15} sample of early-type
+  galaxies (a black line shows the best power-law fit $\langle
+  L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha =
+  -0.2$).  The left panel is calculated assuming a constant radiative
+  efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the
+  right hand panel assumes $\epsilon_X= \alpha \epsilon_{\rm
+    bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the
+  radiative efficiency of low luminosity accretion disks calculated by
+  \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$
+  is the fraction of the mass inflowing on large scales that reaches
+  the SMBH.  Shown for comparison are the X-ray luminosities
+  calculated for the maximum thermally-stable accretion rate ({\it
+    dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated
+  accretion rate ({\it dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and
+  the Compton heating-regulated accretion rate ({\it dashed pink
+    line}; eq.~[\ref{eq:MdotCa}]), again all calculated for the
+  average SFH corresponding to each SMBH mass.}
 \end{figure*}
@@
 average SFH of galaxies with similar mass, then to first order we
-predict that $\langle L_{X}/L_{\rm edd}\rangle$ should be a weakly
+predict that $\langle L_{X}/L_{\rm edd}\rangle$ should be an 
 increasing function of BH mass.  This result is in tension with the
@@
   accretion efficiency of the SMBH.  However, the resulting average
-  Eddington-normalized accretion rate is predicted to increase weakly
-  with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the
-  (also weak) downsizing trend of measured X-ray luminosities in
-  early-type galactic nuclei (e.g., \citealt{Miller+15}).  Thermally
-  stable accretion models can reproduce the observed scatter in
-  nuclear X-ray luminosities at fixed $\Mbh$ (2-4 orders of magnitude)
-  due to the combination of (1) differences in the stellar wind
-  heating rate due to stochastic variation in SFH between galaxies, or
-  within one galaxy due to burstiness in the SFH, as in
+  Eddington-normalized accretion rate is predicted to increase with
+  $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also
+  weak) downsizing trend of measured X-ray luminosities in early-type
+  galactic nuclei (e.g., \citealt{Miller+15}).  Thermally stable
+  accretion models can reproduce the observed scatter in nuclear X-ray
+  luminosities at fixed $\Mbh$ (2-4 orders of magnitude) due to the
+  combination of (1) differences in the stellar wind heating rate due
+  to stochastic variation in SFH between galaxies, or within one
+  galaxy due to burstiness in the SFH, as in
   ~Fig.~\ref{fig:NickPlot2}; (2) Variations in the amount of inflowing

### 2015-07-01 ms.tex
updating figures for new mass loss prescription.

@@
 ($\S\ref{sec:numerical}$).  We do not consider the possibility that
-the conduction of heat from the very inner accretion flow can affect
+the conduction of heat from the inner accretion flow can affect
 the flow on much larger scales \citep{Johnson+2007}.
@@
     pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc) for cores (cusps)
-    {\bf AG update rb fit}. For
-    $\zeta < \zeta_c$ the stagnation radius moves from inside the
-    influence radius, out to the stellar break radius $r_b$ (Appendix
-    \ref{app:be}); in practice renders the flow susceptible to thermal
-    runaway, even if $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w
-    > v_{\rm TI}$ is usually the more strigent criterion for
-    stability, while for core galaxies the $\zeta > \zeta_c$ is
-    usually more relevant.}
+    {\bf AG update rb fit}. For $\zeta < \zeta_c$ the stagnation
+    radius moves from inside the influence radius, out to the stellar
+    break radius $r_b$ (Appendix \ref{app:be}); in practice renders
+    the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm
+      TI}$.  For cusp galaxies the $v_w > v_{\rm TI}$ is usually the
+    more strigent criterion for stability, while for core galaxies the
+    $\zeta > \zeta_c$ is usually more relevant.}
 \label{fig:TI}
@@
 ...$^{\dagger}$ & ... & 100 & 0.22 & $ 1.1 \times 10^{ -4 }$ & $ 1.6 \times 10^{ 2 }$ \\
-...$^{\ddagger}$  & ... & 100 & 0.27 & $ 1.4 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2
+...$^{\ddagger}$  & ... & 100 & 0.07 & $ 2.8 \times 10^{ -5 }$ & $ 4.7 \times 10^{ 2
 }$ \\
@@
 Core Galaxies, $\Gamma = 0.1$  &  & & & & & & & & \\
-$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
-10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\
+%$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
+%10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\
+$    10^{ 6 }$ & 600 & 25 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$  & \\
 ... & 1200 & -- & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
@@
   with radiative cooling included, assuming mass loss parameter $\eta
-  = 0.2$.  $\ddagger$Calculated with radiative cooling and
-  conductivity included, assuming mass loss parameter $\eta = 0.2$ and
-  conductivity saturation parameter $\phi = 0.1$.  Solutions including
-  radiative cooling were performed for cusp galaxies with $v_w=300 $
-  km s$^{-1}$ and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$
-  = 0.02, 0.2, and 0.6.  Values of $\eta$ resulting in thermally
-  unstable solutions are marked in the final column.  Solutions found
-  to be thermally unstable for all $\eta \geq 0.02$ are denoted as
-  {\bf TI}.
+  = 0.2$.  $\ddagger$Calculated with conductivity and cooling
+  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
+  saturation parameter $\phi = 0.1$.  Solutions including radiative
+  cooling were performed for cusp galaxies with $v_w=300 $ km s$^{-1}$
+  and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$ = 0.02,
+  0.2, and 0.6.  Values of $\eta$ resulting in thermally unstable
+  solutions are marked in the final column.  Solutions found to be
+  thermally unstable for all $\eta \geq 0.02$ are denoted as {\bf TI}.
 \end{tablenotes}
@@
 
-Including thermal conduction, by contrast, results in only minor
+Including thermal conduction, by contrast, results in only order unity
 changes to our solutions for our fiducial value of the saturation
-parameter $\phi = 0.1$, consistent with our analytic expectation
-(eq.~[\ref{eq:conduction}]).
+parameter $\phi = 0.1$, consistent with our analytic expectations
+(eq.~[\ref{eq:conduction}]). However, we found that for runs which
+included conductivity the stagnation radius varied with the location
+of the inner grid boundary: as the boundary is moved inwards more heat
+can be conducted outwards from deeper in the gravitational potential
+well of the black hole. We expect conductivity would begin to have a
+significant effect for an inner boundary $\lsim 0.01 \rs$ (the
+conductive run in Table~\ref{table:models} has an inner grid boundary
+at $\sim 0.03 \rs$). However, it is not clear physically if the
+magnetic field could remain coherent over so many decades in radius.
 
@@
 contributions from main sequence and post-main sequence populations.
-At early times following star formation, energy input is dominated by
+t early times following star formation, energy input is dominated by
 core collapse supernovae and by the fast outflows of Wolf-Rayet stars
@@
 \end{align} 
-Compton heating is thus significant in young stellar populations
+ompton heating is thus significant in young stellar populations
 with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
@@
 
+% \begin{table*}
+% \begin{threeparttable}
+% \begin{minipage}{18cm}
+% \caption{Comparison of CNM gas density at r=10$^{18}$ between our
+%   model and existing constraints on the gas density on this scale for
+%   the Milky Way from Chandra x-ray observations (first row) and from
+%   modeling the radio light curve in the Swift J1644 transient (second row).}
+% \begin{tabular}{lll}
+%   {System} &  {Model} & {Comparison} \\
+%   %\hline
+%   Milky Way & 3 cm${-3}$ & 26 cm$^{-3}$\\
+%   Swift J1644+57 & 5 cm$^{-3}$ & 0.8 cm$^{-3}$\\
+%   %\hline
+% \label{table:compare}  
+% \end{tabular}
+% % \begin{tablenotes}
+% %   Model estimate has been corrected for the fact the analytic
+% %   prescription underestimates gas density. This corresponds to model
+% %   estimate for core galaxies.
+% % \end{tablenotes}
+% \end{minipage}
+% \end{threeparttable}
+% \end{table*}
+
 \section{Implications and Discussion}
@@
 the inflow rate, $\dot{M}$, onto SgrA* calculated by
-\citet{Quataert:2004a}.  Also shown is the range of $\dot{M}$ for the
-low-luminosity AGN NGC3115 derived through detailed modeling by
-\citet{ShcherbakovWong+:2014a}, who find a range of inflow rates
-depending on the assumed model for thermal conductivity\footnote{We
-  expect this range would be have been smaller had
-  \citet{ShcherbakovWong+:2014a} included saturation of the conductive
-  flux.}.  The SgrA* rate exceeds our estimate of $\dot{M}$ due to the
+\citet{Quataert:2004a} and by \citet{Cuadra+2008}.  Also shown is the
+range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through
+detailed modeling by \citet{ShcherbakovWong+:2014a}, who find a range
+of inflow rates depending on the assumed model for thermal
+conductivity.  The inflow rate SgrA* estimated from
+\citet{Quataert2004} exceeds our estimate of $\dot{M}$ due to the
 average SFH for the same $M_{\bullet}$ by almost two orders of
-magnitude.  This discrepancy can in part be understood by the fact
-that star formation in the central parsec of the Milky Way cannot be
+magnitude. This is because the mass source term in
+\citet{Quataert2004} exceeds ours by several orders of magnitude.
+The star formation in the central parsec of the Milky Way cannot be
 described as steady-state: feedback is instead dominated by the
@@
 (Fig.~\ref{fig:vwSources}, bottom panel).
+
+However, simulations by \citet{Cuadra+2006} find that
+the inflow rate for Sgr A* is reduced by up to an order of magnitude
+compared to the result in \citet{Quataert2004} when the discreteness
+and disk geometry of stellar sources is taken into account.
 
@@
 calculated using the accretion rate from the top line of
-equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.8$ for $\Mbh < 3
+equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.7$ for $\Mbh < 4
 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
-\left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
+\left(\frac{\Mbh}{4\times 10^7 \Msun}\right)$+0.7 for $\Mbh \geq 4
 \times 10^7 \Msun$. This is functional form is designed to
@@
   average SFH for galaxies corresponding to each black hole mass
-  (Fig.~\ref{fig:bh_growth}), calculated using $\Gamma = 0.8$ for
-  $\Mbh < 3 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
-  \left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
+  (Fig.~\ref{fig:bh_growth}), calculated using $\Gamma = 0.7$ for
+  $\Mbh < 4 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
+  \left(\frac{\Mbh}{4\times 10^7 \Msun}\right)$+0.7 for $\Mbh \geq 4
   \times 10^7 \Msun$ derived from the \citet{LauerFaber+:2007a}
@@
     (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
-    of heat from the very inner accretion flow can affect the solution
-    properties on much larger scales \citep{Johnson+2007}. Angular
-    momentum is also unlikely to invalidate our spherically symmetric
-    model on large scales, given observationally inferred rotation
-    rates of galactic nuclei near the stagnation radius
-    ($\S\ref{sec:rotation}$).
+    of heat from the inner accretion flow can affect the solution
+    properties on much larger scales \citep{Johnson+2007}. For
+    example, \citet{Tanaka+2006} find that conductivity can contribute
+    to driving bipolar outflows.
+
+    Angular momentum is likely unimportant for large scale flow
+    properties ($\S\ref{sec:rotation}$). However, it will become
+    important on small scales, where gas stopped by a centrifugal
+    barrier and unable to cool could drive a bipolar outflow.
 

### 2015-07-01 windheat.tex
updating figures for new mass loss prescription.

@@
 \begin{align} 
-  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
-    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
-        T}(t)} \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
-  }{\bar{m}_*}\label{eq:mdotImp}
-  \\
+  \dot{\bar{m}}(t) &= f_{\rm TO} \dot{m}_{\rm TO} + f_{\rm OB}
+  \dot{m}_{\rm OB}\\
+% + f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
+%$  \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
+%}{\bar{m}_*}\label{eq:mdotImp}
 \dot{\bar{e}}(t) &=f_{\rm OB} \, \dot{e}_{\rm OB}(t)+ f_{\rm MS}
@@
 \end{align}
-In the top line, the first and second terms correspond to contributions
-from main sequence (MS) stars and post-main sequence (PMS) stars,
-respectively. Here $\mu$ is the IMF, which we take to be of the
-Salpeter form $\mu|_{\Mstar} \propto M_{\star}^{-2.35}$, truncated at
-$m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high
-mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean
-stellar mass. In practice the contribution of main sequence winds to
-the mass budget is negligible, and so we drop the second term in
-equation~\eqref{eq:mdotImp}.
 
-The first term in equation~\eqref{eq:edotImp} corresponds energy
-injection from massive O \& B stars, while the second term accounts
-for energy injection from stars on the lower main sequence. Both terms
-have a thermalization efficiency, $f$, which we talk to be $1$. Note
-we do not account for energy from Type II supernovae. However, the
-mass injection from type II supernovae is implicitly included in the
-first term of equation~\eqref{eq:mdotImp}
+In the top line, the first term corresponds to mass injection due
+winds from post-main sequence stars. The second term corresponds to
+mass injection due to stellar winds from massive and O and B
+stars. For the latter we use population synthesis calculations by
+\citet{VossDiehl+:2009a}. From the bottom panel of their Figure 7, the
+stellar wind mass loss rate per massive star can be approximated to within
+a factor of a few by
 
-Winds from lower main sequence stars only dominate the energy
-injection a late times ~10 Gyr after an impulsive burst of star
-formation. Even with 100\% thermalization efficiency these winds could
-not thermally stabilize the CNM. Thus, we could not describe this
-regime within our steady formalism.
+\begin{equation}
+\dot{\mathcal{M}}=10^{-5.4} \left(\frac{t}{4\times 10^6 {\rm
+       yr}}\right)^{-3} 4 {\, \rm Myr} \leq t \leq 40 {\, \rm Myr}. 
+\end{equation}
+
+and 0 for all later times. We neglect the mass injection due to
+stellar winds for times $t\lsim 4$ Myr. $\dot{m}_{\rm OB}=f_{8}
+\dot{\mathcal{M}}/\bar{m}_{\star}$, where $f_{8} =2.6 \times 10^{-3}$
+is the fraction of the stellar mass with $M_{\star} > 8M_{\odot}$ and
+$m_{\star}=0.35 \Msun$ is the mean stellar mass for our assumed
+Salpeter IMF, $\mu\sim M_\star^{-2.35}$.
+
+For the mass loss rate from post-main sequence winds, we take
+
+\begin{equation}
+  \dot{m}_{\rm TO}=\frac{\Delta M(t) |\dot{M}_{\rm TO}(t)|
+    \mu|_{M_{\rm TO}(t)}}{\bar{m}_{\star}}  \,\,  t \geq {\rm 40 Myr},
+\end{equation}
+
+and 0 for earlier times. By truncating $dot{m}_{\rm TO}$ at 40 Myr, we
+are ignoring the non-steady mass injection by type II supernovae.
 
@@
 times ($t \gsim 10^8$ years).
+
+The first term in equation~\eqref{eq:edotImp} corresponds energy
+injection from massive O \& B stars, while the second term accounts
+for energy injection from stars on the lower main sequence. Both terms
+have a thermalization efficiency, $f$, which w e talk to be $1$. Note
+we do not account for energy from Type II supernovae.
+
+Winds from lower main sequence stars only dominate the energy
+injection a late times ~10 Gyr after an impulsive burst of star
+formation. Even with 100\% thermalization efficiency these winds could
+not thermally stabilize the CNM. Thus, we could not describe this
+regime within our steady formalism.
 

### 2015-07-02 ms.tex
sclaing relations and caveats

@@
 masses used in \citealt{McConnellMa+:2011a} were underestimated
-\citep{Kormendy+2013}.
+\citep{Kormendy+2013}. However, our results are not overly sensitive
+to the exact form of the $\Mbh-\sigma$ relationship that we use.
 
@@
 We fix $\beta = 2$ but find that our results are not overly sensitive
-to the properties of the gas flow on radial scales $\gtrsim r_b$ for
-values of $\beta\gsim 1.5$, which characterize most of the
-\citet{LauerFaber+:2007a} sample\footnote{The median $\beta$ in the
-  \citet{LauerFaber+:2007a} sample is 1.39 (1.64) for core (cusp)
-  galaxies}.  The presence of the break radius $r_{b}$ is, however,
-necessary to obtain a converged steady state for some regions of our
-parameter space.  We consider solutions calculated for up to four
-values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
-range of break radii from the \citet{LauerFaber+:2007a}
-sample.\footnote{For the core galaxies the break radius follows the
-  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
-  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
-  between 100 and 1000 pc, and lack a clear trend with $\Mbh$. {\bf AG
-    I redid the fitting and found $\rb\sim 90 \, (\Mbheight)^{0.5}$
-    pc}} We neglect values of $r_b$ which would give unphysically
-large bulges for a given $\Mbh$.
+to the properties of the gas flow on radial scales $\gtrsim r_b$.  The
+presence of the break radius $r_{b}$ is, however, necessary to obtain
+a converged steady state for some regions of our parameter space.  We
+consider solutions calculated for up to four values of $\rb$: 50 pc,
+100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
+the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
+  the break radius follows the scaling relationship $\rb\sim 90 \,
+  (\Mbheight)^{0.5}$ pc, with scatter of approximately one dex. Most
+  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
+  clear trend with $\Mbh$. The mean $r_b$ for cusp galaxies in the
+  \citet{LauerFaber+:2007a} sample is $\sim 240$ pc} We neglect
+values of $r_b$ which would give unphysically large bulges for a given
+$\Mbh$.
 
@@
     \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
-    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc) for cores (cusps)
-    {\bf AG update rb fit}. For $\zeta < \zeta_c$ the stagnation
-    radius moves from inside the influence radius, out to the stellar
-    break radius $r_b$ (Appendix \ref{app:be}); in practice renders
-    the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm
-      TI}$.  For cusp galaxies the $v_w > v_{\rm TI}$ is usually the
-    more strigent criterion for stability, while for core galaxies the
-    $\zeta > \zeta_c$ is usually more relevant.}
+    pc$ and $\rb=90 \Mbheight^{0.5}$ pc (240 pc) for cores
+    (cusps). For $\zeta < \zeta_c$ the stagnation radius moves from
+    inside the influence radius, out to the stellar break radius $r_b$
+    (Appendix \ref{app:be}); in practice renders the flow susceptible
+    to thermal runaway, even if $v_{w} > v_{\rm TI}$.  
+    % For cusp
+%     galaxies the $v_w > v_{\rm TI}$ is usually the more stringent
+%     criterion for stability, while for core galaxies the $\zeta >
+%     \zeta_c$ is usually more relevant.
+}
 \label{fig:TI}
@@
 Based on the \citet{LauerFaber+:2007a} sample we take $\rinf = 25(8)M
-^{0.6}$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
-$\rb/\rinf\simeq 4 \Mbheight^{-0.2} (13 \Mbheight^{-0.6})$ for cores
+^{0.6}$ pc and $\rb = 90 \Mbheight^{0.5}$ (240 pc) and thus
+$\rb/\rinf\simeq 4 \Mbheight^{-0.1} (30 \Mbheight^{-0.6})$ for cores
 (cusps).  For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$
-criterion is generally more stringent, while for core galaxies the
-$\zeta > \zeta_c$ criterion is more strigent for core galaxies, except
-for high mass loss rates $\eta > 1$.
+criterion is more stringent for $\eta \gsim 0.1$. The $\zeta >
+\zeta_c$ is more important for core galaxies especially for $\Mbh
+\gsim 10^8 \Msun$, where most core galaxies are found.
 
@@
 dispersion, i.e. $\zeta \sim \zeta_c$ (eq.~[\ref{eq:zetacrit}]).  This
-implies that the true stagnation radius and the inflow rate could
-be larger than our analytic estimates, potentially resulting in
-thermal instability in a significant fraction of galaxies.  The bottom
-panel of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where
-$\zeta_c$ is estimated ...{\bf AG this sentence needs to be
-  fixed. Power law fits different for cores and cusps. Power law fixed
-to be 0.6 for influence radius in doing fits}.  In other words, the CNM of a
-significant fraction of massive ellipticals may be thermally unstable,
-not necessarily because they are receiving lower stellar feedback than
-the average for their galaxy mass, but due to the high heating
-required for stability given the structure of their stellar potential.
-
-Realistic variations (``burstiness") in the SFH
-will also often produce lower stellar wind heating rates (Appendix
+implies that the true stagnation radius and the inflow rate could be
+larger than our analytic estimates, potentially resulting in thermal
+instability in a significant fraction of galaxies.  The bottom panel
+of Figure~\ref{fig:vwSources} also shows $\zeta/\zeta_c$, where
+$\zeta_c$ is estimated using fits for $r_b$, $\rinf$, and $\Gamma$
+derived from the \citet{LauerFaber+:2007a} sample.  In other words,
+the CNM of a significant fraction of massive ellipticals may be
+thermally unstable, not necessarily because they are receiving lower
+stellar feedback than the average for their galaxy mass, but due to
+the high heating required for stability given the structure of their
+stellar potential.
+
+Realistic variations (``burstiness") in the SFH will also often
+produce lower stellar wind heating rates (Appendix
 \ref{app:windheat}).  Figure \ref{fig:NickPlot2} shows the heating
@@
 $\approx 2$ from its average value, even for huge drops in the star
-formation rate ($\iota \sim 10^{-3}$).  However, burstiness in the
-SFH over longer timescales can suppress heating
-more significantly.  When $\delta t_{\star} \gtrsim 10^8~{\rm yr}$,
-$v_{\rm w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$,
-$v_{\rm w}^\star \approx 400~{\rm km~s}^{-1}$ in most galaxies, but
-for smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
-exception to this is in galactic nuclei with $M_\bullet \gtrsim
-10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
-of average cosmic SFHs is appropriate provided
-local variations are either on short timescales ($\delta t_{\star}
-\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\iota \gtrsim
-0.1$).  If both of these conditions are violated, then the effective
-heating rates for all but the most massive galaxies (where Ia
-explosions dominate) will fall by a factor $\gtrsim 4$ from our
-fiducial volumetric averages, calculated using SFHs from \citet{MosterNaab+:2013a}.
-
-% \begin{table*}
-% \begin{threeparttable}
-% \begin{minipage}{18cm}
-% \caption{Comparison of CNM gas density at r=10$^{18}$ between our
-%   model and existing constraints on the gas density on this scale for
-%   the Milky Way from Chandra x-ray observations (first row) and from
-%   modeling the radio light curve in the Swift J1644 transient (second row).}
-% \begin{tabular}{lll}
-%   {System} &  {Model} & {Comparison} \\
-%   %\hline
-%   Milky Way & 3 cm${-3}$ & 26 cm$^{-3}$\\
-%   Swift J1644+57 & 5 cm$^{-3}$ & 0.8 cm$^{-3}$\\
-%   %\hline
-% \label{table:compare}  
-% \end{tabular}
-% % \begin{tablenotes}
-% %   Model estimate has been corrected for the fact the analytic
-% %   prescription underestimates gas density. This corresponds to model
-% %   estimate for core galaxies.
-% % \end{tablenotes}
-% \end{minipage}
-% \end{threeparttable}
-% \end{table*}
+formation rate ($\iota \sim 10^{-3}$).  However, burstiness in the SFH
+over longer timescales can suppress heating more significantly.  When
+$\delta t_{\star} \gtrsim 10^8~{\rm yr}$, $v_{\rm w}^\star$ becomes
+very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm w}^\star \approx
+400~{\rm km~s}^{-1}$ in most galaxies, but for smaller $\iota$,
+$v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an exception to this is
+in galactic nuclei with $M_\bullet \gtrsim 10^8~M_\odot$, where
+heating is stabilized by SN Ia).  Our use of average cosmic SFHs is
+appropriate provided local variations are either on short timescales
+($\delta t_{\star} \lesssim 10^7~{\rm yr}$), or limited in magnitude
+($\iota \gtrsim 0.1$).  If both of these conditions are violated, then
+the effective heating rates for all but the most massive galaxies
+(where Ia explosions dominate) will fall by a factor $\gtrsim 4$ from
+our fiducial volumetric averages, calculated using SFHs from
+\citet{MosterNaab+:2013a}.
 
@@
   rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$
-  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum inflow
-  rate for a thermally stable flow near the stagnation radius,
+  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum inflow rate
+  for a thermally stable flow near the stagnation radius,
   $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the
-  inferred inflow rates of SgrA* from \citet{Quataert:2004a} (gray
-  circles), for NGC3115 from \citet{ShcherbakovWong+:2014a} (gray
-  diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a}
-  (gray triangles).  {\it Bottom panel:} Growth times $t_{\rm grow}
-  \equiv \Mbh/\dot{M}_{\bullet}$ in units of the Hubble time $\th$ for
-  each of the accretion rates shown in the top panel, where
-  $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to
-  account for the fraction of inflowing mass lost to disk outflows on
-  small scales.}
+  inferred inflow rates of SgrA* from \citet{Quataert:2004a} and
+  \citet{Cuadra+2008} (gray circles) and for NGC3115 from
+  \citet{ShcherbakovWong+:2014a} (gray diamonds).  {\it Bottom panel:}
+  Growth times $t_{\rm grow} \equiv \Mbh/\dot{M}_{\bullet}$ in units
+  of the Hubble time $\th$ for each of the accretion rates shown in
+  the top panel, where $\dot{M}_{\bullet} = \alpha\dot{M}$, where
+  $\alpha = 0.1$, to account for the fraction of inflowing mass lost
+  to disk outflows on small scales.}
 \end{figure}
@@
 conductivity.  The inflow rate SgrA* estimated from
-\citet{Quataert2004} exceeds our estimate of $\dot{M}$ due to the
+\citet{Quataert:2004a} exceeds our estimate of $\dot{M}$ due to the
 average SFH for the same $M_{\bullet}$ by almost two orders of
 magnitude. This is because the mass source term in
-\citet{Quataert2004} exceeds ours by several orders of magnitude.
+\citet{Quataert:2004a} exceeds ours by several orders of magnitude.
 The star formation in the central parsec of the Milky Way cannot be
@@
 the inflow rate for Sgr A* is reduced by up to an order of magnitude
-compared to the result in \citet{Quataert2004} when the discreteness
+compared to the result in \citet{Quataert:2004a} when the discreteness
 and disk geometry of stellar sources is taken into account.
@@
 observed down-sizing trend that the average Eddington ratio is seen to
-decrease (albeit weakly) with $M_{\bullet}$, especially in the model where
-$\epsilon_X$ increases with the Eddington ratio.
-However, one must keep in mind the enormous uncertainty in calculating
-the luminosity of the accretion flow close to the black hole in a
-single waveband based on the feeding rate on larger scales.  Also, if disk
-outflows indeed carry away most of the infalling mass before it reaches X-ray
-producing radii (e.g.~\citealt{Blandford&Begelman99};
+decrease (albeit weakly) with $M_{\bullet}$, especially in the model
+where $\epsilon_X$ increases with the Eddington ratio.  However, one
+must keep in mind the enormous uncertainty in calculating the
+luminosity of the accretion flow close to the black hole in a single
+waveband based on the feeding rate on larger scales.  Also, if disk
+outflows indeed carry away most of the infalling mass before it
+reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99};
 \citealt{Li+13}), then the angular momentum of the infalling gas might
-also influence the X-ray luminosity indirectly through the inflow efficiency $\alpha$, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.
-However, in general the efficiency with which inflowing matter reaches the SMBH (and hence X-ray luminosity) would naively be expected to {\it decrease} with decreasing $M_{\bullet}$ due to the increasing angular momentum of low mass galaxies, exacerbating the tension between our findings and the observed downsizing trend.
+also influence the X-ray luminosity indirectly through the inflow
+efficiency $\alpha$, in a way that could depend systematically on the
+stellar population and hence $M_{\bullet}$.  However, in general the
+efficiency with which inflowing matter reaches the SMBH (and hence
+X-ray luminosity) would naively be expected to {\it decrease} with
+decreasing $M_{\bullet}$ due to the increasing angular momentum of low
+mass galaxies, exacerbating the tension between our findings and the
+observed downsizing trend.
 
@@
 
-If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$
-in Figure \ref{fig:miller} are indeed in a state of thermally-unstable
-outburst, then some of the galaxies with X-ray upper limits could be contributing to a separate population of thermally-stable, steadily accreting nuclei.
-Such a population could include SgrA*, which has a much lower X-ray luminosity for its SMBH mass than predicted by the \citet{Miller+15} trend.
-A potentially bimodal population of steady and outbursting galactic nuclei calls into question the practice of using simple extrapolations of power-law fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the occupation fraction of SMBHs in the nuclei of low mass
-galaxies.
+If the galaxies with measured $L_{\rm X}$ at low $M_{\bullet}$ in
+Figure \ref{fig:miller} are indeed in a state of thermally-unstable
+outburst, then some of the galaxies with X-ray upper limits could be
+contributing to a separate population of thermally-stable, steadily
+accreting nuclei.  Such a population could include SgrA*, which has a
+much lower X-ray luminosity for its SMBH mass than predicted by the
+\citet{Miller+15} trend.  A potentially bimodal population of steady
+and outbursting galactic nuclei calls into question the practice of
+using simple extrapolations of power-law fits to the $L_{\rm
+  X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the
+occupation fraction of SMBHs in the nuclei of low mass galaxies.
 
@@
 transient {\it Swift} J1644+57 (\citealt{Bloom+11}), we predict gas
-densities of a $n \sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for
+densities of a $n \sim $few cm$^{-3}$ on radial scales of 0.3 pc for
 wind heating rates within the physically expected range $v_{\rm w}
-\sim 500-1000$ km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values
-are within the range estimated by modeling the radio afterglow of {\it
-  Swift} J1644+57 (\citealt{Metzger+12},
-\citealt{BergerZauderer+:2012a}), as shown in
-Fig.~\ref{fig:bh_growth}.
+\sim 500-1000$ km s$^{-1}$ and $\eta=0.4$ {\bf AG might be good to
+  cite figure 2 here but this has eta=0.2}.  These values are within
+the range estimated by modeling the radio afterglow of {\it Swift}
+J1644+57 (\citealt{Metzger+12},\citealt{BergerZauderer+:2012a}). However,
+\citet{Mimica+2015} find a much higher density of $60 cm^{-3}$ at 0.3 pc.
 
@@
 outflows could play an equal or greater role in regulating accretion,
-even in low luminosity AGN.
+even in low luminosity AG.
 

### 2015-07-02 windheat.tex
sclaing relations and caveats

@@
 \begin{equation}
-\dot{\mathcal{M}}=10^{-5.4} \left(\frac{t}{4\times 10^6 {\rm
-       yr}}\right)^{-3} 4 {\, \rm Myr} \leq t \leq 40 {\, \rm Myr}. 
+\dot{\mathcal{M}}=
+\begin{cases}
+10^{-6.5} \Msun {\rm yr^{-1}} & t < 4 Myr\\
+10^{-5.4} \Msun {\rm yr^{-1}} \left(\frac{t}{4\times 10^6 {\rm
+       yr}}\right)^{-3} & 4 {\, \rm Myr} \leq t \leq 40 {\, \rm Myr}. \\
+0 & t>40 {\rm Myr}
+\end{cases}
 \end{equation}
 
-and 0 for all later times. We neglect the mass injection due to
-stellar winds for times $t\lsim 4$ Myr. $\dot{m}_{\rm OB}=f_{8}
-\dot{\mathcal{M}}/\bar{m}_{\star}$, where $f_{8} =2.6 \times 10^{-3}$
-is the fraction of the stellar mass with $M_{\star} > 8M_{\odot}$ and
-$m_{\star}=0.35 \Msun$ is the mean stellar mass for our assumed
-Salpeter IMF, $\mu\sim M_\star^{-2.35}$.
+We neglect the mass injection due to stellar winds for times $t\lsim
+4$ Myr. $\dot{m}_{\rm OB}=f_{8} \dot{\mathcal{M}}/\bar{m}_{\star}$,
+where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the stellar mass
+with $M_{\star} > 8M_{\odot}$ and $m_{\star}=0.35 \Msun$ is the mean
+stellar mass for our assumed Salpeter IMF, $\mu\sim M_\star^{-2.35}$.
 
@@
 
-and 0 for earlier times. By truncating $dot{m}_{\rm TO}$ at 40 Myr, we
+and 0 for earlier times. By truncating $\dot{m}_{\rm TO}$ at 40 Myr, we
 are ignoring the non-steady mass injection by type II supernovae.
@@
   \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} &  4\times
-  10^{6} {\rm yr}  \le t \le 10^{8} {\rm yr}
-  \times 10^6 {\rm yr},\\
+  10^{6} {\rm yr}  \le t \le 10^{8} {\rm yr},\\
   0 & t > 10^8 {\rm yr}
